### 2022-10-13 README.Rmd
REVISED interoception scale

---
output: github_document
editor_options: 
  chunk_output_type: console
---

# Interoceptive Accuracy Scale Re-analysed (IAS-R)

```{r, message=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 450,
  fig.path = "figures/",
  comment = "#",
  message = FALSE,
  warning = FALSE
)

options(
  knitr.kable.NA = "",
  digits = 4,
  width = 80
)
```

- Murphy, J., Brewer, R., Plans, D., Khalsa, S. S., Catmur, C., & Bird, G. (2020). [Testing the independence of self-reported interoceptive accuracy and attention](https://journals.sagepub.com/doi/full/10.1177/1747021819879826). Quarterly Journal of Experimental Psychology, 73(1), 115-133. https://doi.org/10.31234/osf.io/fqgu4

**Aim**. Re-analyze the raw data from [Murphy et al. (2020)](https://journals.sagepub.com/doi/full/10.1177/1747021819879826) (study 1) regarding the factor structure of the Interoceptive Accuracy Scale (IAS) by using the *Method Agreement Procedure* for the number of factors to extract and performing a CFA model comparison.

**Conclusion**. EFA suggested a 1-factor and 4-factors solutions, but the latter was favoured by CFA. Additionally, CFA suggested that a 5-factors model (obtained by separating *Nociception* from *Interoception*) was superior:

- *Interoception*: Heart, Hungry, Breathing, Thirsty, Temperature, Sexual arousal.
- *Nociception*: Muscles, Bruise, Pain.
- *Expulsion*: Burp, Sneeze, Wind.
- *Elimination*: Vomit, Defecate, Urinate.
- *Skin*: Itch, Tickle, Affective touch.

The final revised scale, made of 18 items (6 for interoception and 3 per secondary dimension), is available below.

## Data

Data from the [study 1](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) was downloaded from OSF.

```{r, message=FALSE, warning=FALSE, results='asis'}
library(tidyverse)
library(easystats)

df <- haven::read_sav("Study 1.sav") |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(Gender == 1, "Male", "Female")))

report::report_participants(df, age = "Age", sex = NA, gender = "Gender")
```

## EFA

```{r, message=FALSE, warning=FALSE}
data <- select(df, -Age, -Gender)

n <- parameters::n_factors(data)

n
plot(n)
```

The *Method Agreement Procedure*

```{r, message=FALSE, warning=FALSE}
efa1 <- parameters::factor_analysis(data, n=1, sort = TRUE)
efa1

efa4 <- parameters::factor_analysis(data, n=4, rotation = "oblimin", sort = TRUE)
efa4
```

## CFA

We compared the two models suggested by EFA (1-factor and 4-factors), with two additional model based on the latter: one with 2 items removed (Blood sugar and Taste), and one with additionally the *Interoception* factor split into two (with the pain-related items grouped together).

```{r, message=FALSE, warning=FALSE}
library(lavaan)

cfa1 <- lavaan::cfa(parameters::efa_to_cfa(efa1, 
                                           names="IAS"), data=data)
cfa4 <- lavaan::cfa(parameters::efa_to_cfa(efa4, 
                                           names=c("Skin", "Expulsion", "Interoception", "Elimination"),
                                           threshold = "max"), data=data)

cfa4mod <- "
Skin =~ Affective_touch + Tickle + Itch
Expulsion =~ Sneeze + Cough + Wind + Burp
Interoception =~ Heart + Hungry + Breathing + Thirsty + Temp + Sex_arousal + Muscles + Bruise + Pain
Elimination =~ Urinate + Defecate + Vomit
" |> 
lavaan::cfa(data=data)

cfa5 <- "
Skin =~ Affective_touch + Tickle + Itch
Expulsion =~ Sneeze + Cough + Wind + Burp
Interoception =~ Heart + Hungry + Breathing + Thirsty + Temp + Sex_arousal
Nociception =~ Muscles + Bruise + Pain
Elimination =~ Urinate + Defecate + Vomit
" |> 
lavaan::cfa(data=data)

anova(cfa1, cfa4, cfa4mod, cfa5)
```

## Final Model

Additionally, we removed the least loaded items of expulsion (cough) to improve the balance (3 items per secondary scales, and 6 for interoception).

```{r, message=FALSE, warning=FALSE}
cfa5mod <- "
Skin =~ Affective_touch + Tickle + Itch
Expulsion =~ Sneeze + Wind + Burp
Interoception =~ Heart + Hungry + Breathing + Thirsty + Temp + Sex_arousal
Nociception =~ Muscles + Bruise + Pain
Elimination =~ Urinate + Defecate + Vomit
" |> 
lavaan::cfa(data=data)

anova(cfa5, cfa5mod)
```

```{r, message=FALSE, warning=FALSE}
parameters::parameters(cfa5) |> 
  display()
```

```{r, message=FALSE, warning=FALSE, fig.width=16, fig.height=10}
library(tidySEM)

graph_data <- tidySEM::prepare_graph(cfa5mod, 
                   layout=get_layout(cfa5mod, layout_algorithm = "layout_with_kk"), 
                   variance_diameter=NA)

nodes(graph_data) <- nodes(graph_data) |> 
  mutate(fill = ifelse(shape == "rect", "grey", "#F06292"))

plot(graph_data)
```

## Final Scale

**Instructions**. Below are several statements regarding how accurately you can perceive specific bodily sensations. Please rate on the scale how well you believe you can perceive each specific signal. For example, if you often feel you need to urinate and then realise you do not need to when you go to the toilet you would rate your accuracy perceiving this bodily signal as low.

Please only rate how well you can perceive these signals without using external cues, for example, if you can only perceive how fast your heart is beating when you measure it by taking your pulse this would not count as accurate internal perception.

**Scale**. Disagree - Agree.

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
set.seed(3)

items <- c(
  "***(Interoception)*** I can always accurately perceive when my heart is beating fast",
  "***(Interoception)*** I can always accurately perceive when I am hungry",
  "***(Interoception)*** I can always accurately perceive when I am breathing fast",
  "***(Interoception)*** I can always accurately perceive when I am thirsty",
  "***(Interoception)*** I can always accurately perceive when I am hot/cold",
  "***(Interoception)*** I can always accurately perceive when I am sexually aroused",
  "***(Elimination)*** I can always accurately perceive when I need to urinate",
  "***(Elimination)*** I can always accurately perceive when I need to defecate",
  "***(Elimination)*** I can always accurately perceive when I am going to vomit",
  "***(Expulsion)*** I can always accurately perceive when I am going to pass wind",
  "***(Expulsion)*** I can always accurately perceive when I am going to burp",
  "***(Expulsion)*** I can always accurately perceive when I am going to sneeze",
  "***(Nociception)*** I can always accurately perceive when my muscles are tired/sore",
  "***(Nociception)*** I can always accurately perceive when I am going to get a bruise",
  "***(Nociception)*** I can always accurately perceive when I am in pain",
  "***(Skin)*** I can always accurately perceive when someone is touching me affectionately rather than non-affectionately",
  "***(Skin)*** I can always accurately perceive when something is going to be ticklish",
  "***(Skin)*** I can always accurately perceive when something is going to be itchy"
)

cat(paste0(1:18, ". ", items, collapse = "\n"))
```

### 2022-10-13 README.Rmd
update

@@
 
-# Interoceptive Accuracy Scale Re-analysed (IAS-R)
+# Interoceptive Accuracy Scale Revised (IAS-R)
 
@@
 
-- Murphy, J., Brewer, R., Plans, D., Khalsa, S.
+<sub>A reanalysis of Murphy, J., Brewer, R., Plans, D., Khalsa, S.
 S., Catmur, C., & Bird, G.
@@
 Quarterly Journal of Experimental Psychology, 73(1), 115-133.
-https://doi.org/10.31234/osf.io/fqgu4
+https://doi.org/10.31234/osf.io/fqgu4</sub>
 
-**Aim**.
-Re-analyze the raw data from [Murphy et al.
-(2020)](https://journals.sagepub.com/doi/full/10.1177/1747021819879826) (study 1) regarding the factor structure of the Interoceptive Accuracy Scale (IAS) by using the *Method Agreement Procedure* for the number of factors to extract and performing a CFA model comparison.
+We present a re-analysis of the data from [**Murphy et al.
+(2020)**](https://journals.sagepub.com/doi/full/10.1177/1747021819879826) (study 1) regarding the factor structure of the **Interoceptive Accuracy Scale (IAS)**.
+In particular, we apply the *Method Agreement Procedure* to estimate the optimal number of latent factors, and perform a further model comparison using Confirmatory Factor Analysis (CFA).
 
-**Conclusion**.
-EFA suggested a 1-factor and 4-factors solutions, but the latter was favoured by CFA.
-Additionally, CFA suggested that a 5-factors model (obtained by separating *Nociception* from *Interoception*) was superior:
+Exploratory Factor Analysis suggested a 1-factor and 4-factors solutions, but the latter was favoured by CFA.
+Further comparison suggested that a 5-factors model (obtained by separating *Nociception* from *Interoception*) had a superior fit.
+The 5 factors are:
 
-- *Interoception*: Heart, Hungry, Breathing, Thirsty, Temperature, Sexual arousal.
-- *Nociception*: Muscles, Bruise, Pain.
-- *Expulsion*: Burp, Sneeze, Wind.
-- *Elimination*: Vomit, Defecate, Urinate.
-- *Skin*: Itch, Tickle, Affective touch.
+- **Interoception**: Heart, Hungry, Breathing, Thirsty, Temperature, Sexual arousal.
+- **Nociception**: Muscles, Bruise, Pain.
+- **Expulsion**: Burp, Sneeze, Wind.
+- **Elimination**: Vomit, Defecate, Urinate.
+- **Skin**: Itch, Tickle, Affective touch.
 
-The final revised scale, made of 18 items (6 for interoception and 3 per secondary dimension), is available below.
+The final revised scale, made of 18 items (6 for interoception and 3 per secondary dimension), is available [below](#IAS-R).
 
-## Data
-
-Data from the [study 1](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) was downloaded from OSF.
+## Participants
 
@@
 
-report::report_participants(df, age = "Age", sex = NA, gender = "Gender")
+paste0(
+  "Data from the [study 1](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) (Murphy et al., 2020), downloaded from OSF, included ",
+  report::report_participants(df, age = "Age", sex = NA, gender = "Gender"),
+  "."
+)
 ```
@@
 
-The *Method Agreement Procedure*
+The *Method Agreement Procedure* suggested that 1 factor was optimal, followed by 4 factors.
 
@@
 
-We compared the two models suggested by EFA (1-factor and 4-factors), with two additional model based on the latter: one with 2 items removed (Blood sugar and Taste), and one with additionally the *Interoception* factor split into two (with the pain-related items grouped together).
-
 ```{r, message=FALSE, warning=FALSE}
@@
 
+anova(cfa1, cfa4)
+```
+
+The 4-factors model suggested by EFA presented a significantly better fit than the 1-factor model.
+We then compared that model to two variants: one with 2 items removed (Blood sugar and Taste), and another with, additionally, the *Interoception* factor split into two (with the pain-related items grouped together).
+The latter model (*CFA-5*), was significantly superior to the others.
+Additionally, we removed the least loaded items of expulsion (cough) to improve the balance (3 items per secondary scales, and 6 for interoception), which significantly improved the model fit.
+
+```{r, message=FALSE, warning=FALSE}
 cfa4mod <- "
@@
 
-anova(cfa1, cfa4, cfa4mod, cfa5)
+anova(cfa4, cfa4mod, cfa5)
 ```
-
-## Final Model
-
-Additionally, we removed the least loaded items of expulsion (cough) to improve the balance (3 items per secondary scales, and 6 for interoception).
 
@@
 
-```{r, message=FALSE, warning=FALSE}
-parameters::parameters(cfa5) |> 
-  display()
-```
+## Final Model
 
@@
 
-## Final Scale
+```{r, message=FALSE, warning=FALSE}
+performance::performance(cfa5mod) |> 
+  display()
+```
+
+```{r, message=FALSE, warning=FALSE}
+parameters::parameters(cfa5mod) |> 
+  display()
+```
+
+## IAS-R
 

### 2022-10-13 README.Rmd
update

@@
   mutate_all(as.numeric) |> 
-  mutate(Gender = as.character(ifelse(Gender == 1, "Male", "Female")))
+  mutate(Gender = as.character(ifelse(Gender == 1, "Male", ifelse(Gender == 2, "Female", "Other"))))
 
@@
 
+## New sample
+
+```{r, message=FALSE, warning=FALSE, results='asis'}
+df2 <- haven::read_sav("Study 6 IAS.sav") |> 
+  mutate_all(as.numeric) |> 
+  mutate(Gender = as.character(ifelse(Gender == 1, "Male", ifelse(Gender == 2, "Female", "Other"))))
+
+paste0(
+  "Data from the [study 6](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) (Murphy et al., 2020), downloaded from OSF, included ",
+  report::report_participants(df2, age = "Age", sex = NA, gender = "Gender"),
+  "."
+)
+```
+
+```{r, message=FALSE, warning=FALSE}
+cfa5mod_refit <- update(cfa5mod, data=df2)
+cfa5_refit <- update(cfa5, data=df2)
+cfa4mod_refit <- update(cfa4mod, data=df2)
+
+anova(cfa5mod_refit, cfa5_refit, cfa4mod_refit)
+```
+
 ## Final Model
+
+```{r, message=FALSE, warning=FALSE}
+final <- update(cfa5mod, data = datawizard::data_merge(df, df2, join="bind"))
+```
 
@@
 graph_data <- tidySEM::prepare_graph(cfa5mod, 
-                   layout=get_layout(cfa5mod, layout_algorithm = "layout_with_kk"), 
+                   layout=get_layout(cfa5mod, layout_algorithm = "layout_nicely"), 
                    variance_diameter=NA)

### 2023-01-16 README.Rmd
update

--- 2022-10-13 README.Rmd
@@
 Quarterly Journal of Experimental Psychology, 73(1), 115-133.
-https://doi.org/10.31234/osf.io/fqgu4
+https://doi.org/10.31234/osf.io/fqgu4</sub>
 
-**Aim**.
-Re-analyze the raw data from [Murphy et al.
-(2020)](https://journals.sagepub.com/doi/full/10.1177/1747021819879826) (study 1) regarding the factor structure of the Interoceptive Accuracy Scale (IAS) by using the *Method Agreement Procedure* for the number of factors to extract and performing a CFA model comparison.
-
-**Conclusion**.
-EFA suggested a 1-factor and 4-factors solutions, but the latter was favoured by CFA.
-Additionally, CFA suggested that a 5-factors model (obtained by separating *Nociception* from *Interoception*) was superior:
-
-- *Interoception*: Heart, Hungry, Breathing, Thirsty, Temperature, Sexual arousal.
-- *Nociception*: Muscles, Bruise, Pain.
-- *Expulsion*: Burp, Sneeze, Wind.
-- *Elimination*: Vomit, Defecate, Urinate.
-- *Skin*: Itch, Tickle, Affective touch.
-
-The final revised scale, made of 18 items (6 for interoception and 3 per secondary dimension), is available below.
-
-## Data
-
-Data from the [study 1](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) was downloaded from OSF.
-
-```{r, message=FALSE, warning=FALSE, results='asis'}
-library(tidyverse)
-library(easystats)
-
-df <- haven::read_sav("Study 1.sav") |> 
-  mutate_all(as.numeric) |> 
-  mutate(Gender = as.character(ifelse(Gender == 1, "Male", "Female")))
-
-report::report_participants(df, age = "Age", sex = NA, gender = "Gender")
-```
-
-## EFA
-
-```{r, message=FALSE, warning=FALSE}
-data <- select(df, -Age, -Gender)
-
-n <- parameters::n_factors(data)
-
-n
-plot(n)
-```
-
-The *Method Agreement Procedure*
-
-```{r, message=FALSE, warning=FALSE}
-efa1 <- parameters::factor_analysis(data, n=1, sort = TRUE)
-efa1
-
-efa4 <- parameters::factor_analysis(data, n=4, rotation = "oblimin", sort = TRUE)
-efa4
-```
-
-## CFA
-
-We compared the two models suggested by EFA (1-factor and 4-factors), with two additional model based on the latter: one with 2 items removed (Blood sugar and Taste), and one with additionally the *Interoception* factor split into two (with the pain-related items grouped together).
-
-```{r, message=FALSE, warning=FALSE}
-library(lavaan)
-
-cfa1 <- lavaan::cfa(parameters::efa_to_cfa(efa1, 
-                                           names="IAS"), data=data)
-cfa4 <- lavaan::cfa(parameters::efa_to_cfa(efa4, 
-                                           names=c("Skin", "Expulsion", "Interoception", "Elimination"),
-                                           threshold = "max"), data=data)
-
-cfa4mod <- "
-Skin =~ Affective_touch + Tickle + Itch
-Expulsion =~ Sneeze + Cough + Wind + Burp
-Interoception =~ Heart + Hungry + Breathing + Thirsty + Temp + Sex_arousal + Muscles + Bruise + Pain
-Elimination =~ Urinate + Defecate + Vomit
-" |> 
-lavaan::cfa(data=data)
-
-cfa5 <- "
-Skin =~ Affective_touch + Tickle + Itch
-Expulsion =~ Sneeze + Cough + Wind + Burp
-Interoception =~ Heart + Hungry + Breathing + Thirsty + Temp + Sex_arousal
-Nociception =~ Muscles + Bruise + Pain
-Elimination =~ Urinate + Defecate + Vomit
-" |> 
-lavaan::cfa(data=data)
-
-anova(cfa1, cfa4, cfa4mod, cfa5)
-```
-
-## Final Model
-
-Additionally, we removed the least loaded items of expulsion (cough) to improve the balance (3 items per secondary scales, and 6 for interoception).
-
-```{r, message=FALSE, warning=FALSE}
-cfa5mod <- "
-Skin =~ Affective_touch + Tickle + Itch
-Expulsion =~ Sneeze + Wind + Burp
-Interoception =~ Heart + Hungry + Breathing + Thirsty + Temp + Sex_arousal
-Nociception =~ Muscles + Bruise + Pain
-Elimination =~ Urinate + Defecate + Vomit
-" |> 
-lavaan::cfa(data=data)
-
-anova(cfa5, cfa5mod)
-```
-
-```{r, message=FALSE, warning=FALSE}
-parameters::parameters(cfa5) |> 
-  display()
-```
-
-```{r, message=FALSE, warning=FALSE, fig.width=16, fig.height=10}
-library(tidySEM)
-
-graph_data <- tidySEM::prepare_graph(cfa5mod, 
-                   layout=get_layout(cfa5mod, layout_algorithm = "layout_with_kk"), 
-                   variance_diameter=NA)
-
-nodes(graph_data) <- nodes(graph_data) |> 
-  mutate(fill = ifelse(shape == "rect", "grey", "#F06292"))
-
-plot(graph_data)
-```
-
-## Final Scale
+## IAS-R
 

### 2023-01-16 analysis.Rmd
update

---
title: "PHQ-4-R: Adaptation of the 4-item screening for Anxiety and Depression for a subclinical sensitivity"
subtitle: "Analysis"
author: "Dominique Makowski et al."
output:
  html_document:
    toc: true
    toc_depth: 2
    theme: paper
    code_folding: hide
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE, warning=FALSE, message=FALSE}
options(
  digits = 3,
  mc.cores = 4,
  brms.algorithm = "sampling",
  brms.backend = "cmdstanr",
  dplyr.summarise.inform = FALSE,
  knitr.kable.NA = ""
)

fig.width <- see::golden_ratio(7)
fig.height <- 7
set.seed(333)

knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 450,
  fig.path = "./figures/",
  fig.width = fig.width,
  fig.height = fig.height
)
```

# Study 1

## Participants

```{r, message=FALSE, warning=FALSE, results='asis'}
library(tidyverse)
library(easystats)
library(patchwork)
library(lavaan)
library(ggraph)
library(tidySEM)

df <- haven::read_sav("data/Study 1.sav") |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(Gender == 1, "Male", ifelse(Gender == 2, "Female", "Other"))))

paste0(
  "Data from the [study 1](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) (Murphy et al., 2020), downloaded from OSF, included ",
  report::report_participants(df, age = "Age", sex = NA, gender = "Gender"),
  "."
)
```

## Descriptive

```{r, message=FALSE, warning=FALSE}
data <- select(df, -Age, -Gender)

dens1 <- estimate_density(data, method="kernSmooth")

plot(dens1)

data <- standardize(data)
```

## EFA

```{r, message=FALSE, warning=FALSE}
n <- parameters::n_factors(data, n_max = 15)

n

knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 4), ])
plot(n)
```

```{r, message=FALSE, warning=FALSE}
efa1 <- parameters::factor_analysis(data, n=1, sort = TRUE)
efa1

efa4 <- parameters::factor_analysis(data, n=4, rotation = "oblimin", sort = TRUE)
efa4

plot(efa4)
```

## CFA

```{r, message=FALSE, warning=FALSE}
cfa1 <-  parameters::efa_to_cfa(efa1, names="IAS") |> 
  lavaan::cfa(data=data)

cfa4 <- parameters::efa_to_cfa(efa4, names=c("Skin", "Expulsion", "Interoception", "Elimination"), threshold = "max") |> 
  lavaan::cfa(data=data)

anova(cfa1, cfa4)
```

```{r, message=FALSE, warning=FALSE}
cfa4mod <- "
Skin =~ Affective_touch + Tickle + Itch
Expulsion =~ Sneeze + Cough + Wind + Burp
Interoception =~ Heart + Hungry + Breathing + Thirsty + Temp + Sex_arousal + Muscles + Bruise + Pain
Elimination =~ Urinate + Defecate + Vomit
" |> 
lavaan::cfa(data=data)

cfa5 <- "
Skin =~ Affective_touch + Tickle + Itch
Expulsion =~ Sneeze + Cough + Wind + Burp
Interoception =~ Heart + Hungry + Breathing + Thirsty + Temp + Sex_arousal
Nociception =~ Muscles + Bruise + Pain
Elimination =~ Urinate + Defecate + Vomit
" |> 
lavaan::cfa(data=data)

anova(cfa4mod, cfa5)
```

```{r, message=FALSE, warning=FALSE}
cfa5mod <- "
Skin =~ Affective_touch + Tickle + Itch
Expulsion =~ Sneeze + Wind + Burp
Interoception =~ Heart + Hungry + Breathing + Thirsty + Temp + Sex_arousal
Nociception =~ Muscles + Bruise + Pain
Elimination =~ Urinate + Defecate + Vomit
" |> 
lavaan::cfa(data=data)

anova(cfa5, cfa5mod)
```

```{r, message=FALSE, warning=FALSE}
cfa5h <- "
Skin =~ Affective_touch + Tickle + Itch
Expulsion =~ Sneeze + Wind + Burp
Nociception =~ Muscles + Bruise + Pain
Elimination =~ Urinate + Defecate + Vomit
Interoception =~ Heart + Hungry + Breathing + Thirsty + Temp + Sex_arousal + Skin + Expulsion + Nociception + Elimination
" |> 
lavaan::cfa(data=data)

anova(cfa5mod, cfa5h)
```

```{r, message=FALSE, warning=FALSE}
check_perf <- function(mod) {
  perf <- model_performance(mod, metrics = c("RMSEA", "CFI", "SRMR", "AGFI", "NNFI"))
  interpret(perf) |> 
    data_rename(pattern = c("Name", "Value"), replacement = c("Index", "Score")) |> 
    arrange(Index)
}

knitr::kable(check_perf(cfa5mod))
```

## New sample

```{r, message=FALSE, warning=FALSE, results='asis'}
df2 <- haven::read_sav("data/Study 6 IAS.sav") |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(Gender == 1, "Male", ifelse(Gender == 2, "Female", "Other")))) |> 
  select(-ESL)

paste0(
  "Data from the [study 6](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) (Murphy et al., 2020), downloaded from OSF, included ",
  report::report_participants(df2, age = "Age", sex = NA, gender = "Gender"),
  "."
)
```

### Descriptive

```{r, message=FALSE, warning=FALSE}
data <- select(df2, -Age, -Gender)

dens2 <- estimate_density(data, method="kernSmooth")

plot(dens2)

data <- standardize(data)
```

```{r, message=FALSE, warning=FALSE}
efa4b <- parameters::factor_analysis(data, n=4, rotation = "oblimin", sort = TRUE)
```

```{r, message=FALSE, warning=FALSE}
cfa1_refit <- "IAS =~ Pain + Sneeze + Temp + Wind + Affective_touch + Muscles + Tickle + Itch + Defecate + Vomit + Taste + Cough + Bruise + Burp + Urinate + Breathing + Thirsty + Sex_arousal + Hungry + Heart + Blood_Sugar" |> lavaan::cfa(data=data)
cfa4mod_refit <- update(cfa4mod, data=data)
cfa5_refit <- update(cfa5, data=data)
cfa5mod_refit <- update(cfa5mod, data=data)
cfa5h_refit <- update(cfa5h, data=data)

table <- anova(cfa5mod_refit, cfa5h_refit, cfa5_refit, cfa4mod_refit, cfa1_refit)
table
```

```{r, message=FALSE, warning=FALSE}
knitr::kable(check_perf(cfa5mod_refit))
```

# Study 2

## Participants

```{r, message=FALSE, warning=FALSE, results='asis'}
# df <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |>
df3 <- read.csv("../IllusionGameReliability/data/preprocessed_questionnaires.csv") |>
  select(Participant, Sex, Age, starts_with("Item_IAS")) |> 
  filter(!is.na(Item_IAS_Elimination_2))

names(df3) <- str_remove_all(names(df3), "Item_IAS_")
names(df3) <- case_when(
  names(df3) == "Interoception_1" ~ "Heart",
  names(df3) == "Interoception_2" ~ "Hungry",
  names(df3) == "Interoception_3" ~ "Breathing",
  names(df3) == "Interoception_4" ~ "Thirsty",
  names(df3) == "Interoception_5" ~ "Temp",
  names(df3) == "Interoception_6" ~ "Sex_arousal",
  names(df3) == "Elimination_1" ~ "Urinate",
  names(df3) == "Elimination_2" ~ "Defecate",
  names(df3) == "Elimination_3" ~ "Vomit",
  names(df3) == "Expulsion_1" ~ "Wind",
  names(df3) == "Expulsion_2" ~ "Burp",
  names(df3) == "Expulsion_3" ~ "Sneeze",
  names(df3) == "Nociception_1" ~ "Muscles",
  names(df3) == "Nociception_2" ~ "Bruise",
  names(df3) == "Nociception_3" ~ "Pain",
  names(df3) == "Skin_1" ~ "Affective_touch",
  names(df3) == "Skin_2" ~ "Tickle",
  names(df3) == "Skin_3" ~ "Itch",
  TRUE ~ names(df3)
  )

report::report_participants(df3, age = "Age", sex = "Sex")
```

## Descriptive

```{r, message=FALSE, warning=FALSE}
data <- select(df3, -Age, -Sex, -Participant)

dens3 <- estimate_density(data, method="kernSmooth")

plot(dens3) +
  theme_modern()

data[] <- standardize(data) |> 
  sapply(as.numeric)
```

## EFA

```{r, message=FALSE, warning=FALSE}
n <- parameters::n_factors(data, n_max = 15)

n
plot(n)
```

```{r, message=FALSE, warning=FALSE}
efa4c <- parameters::factor_analysis(data, n=4, rotation = "oblimin", sort = TRUE, fm="ml")
efa4c

plot(efa4c)
```

##CFA

```{r, message=FALSE, warning=FALSE}
cfa1 <- paste("Interoception =~ ", paste(names(data), collapse = " + ")) |> 
  lavaan::cfa(data=data)

cfa5 <- "
Skin =~ Affective_touch + Tickle + Itch
Expulsion =~ Wind + Burp + Sneeze
Interoception =~ Heart + Hungry + Breathing + Thirsty + Temp + Sex_arousal
Nociception =~ Muscles + Bruise + Pain
Elimination =~ Urinate + Defecate + Vomit
" |> 
  lavaan::cfa(data=data)

cfa4 <- "
Homeostasis =~ Hungry + Thirsty + Sex_arousal + Pain + Temp + Affective_touch + Urinate
Skin =~ Affective_touch + Tickle + Itch + Bruise + Wind
Elimination =~ Defecate + Sneeze + Vomit + Urinate + Burp
Muscle =~ Breathing + Heart + Muscles
" |> 
  lavaan::cfa(data=data)

anova(cfa1, cfa5, cfa4)

cfa4mod <- "
Homeostasis =~ Hungry + Thirsty + Sex_arousal 
Skin =~ Tickle + Itch + Bruise 
Elimination =~ Defecate + Sneeze + Vomit 
Muscle =~ Breathing + Heart + Muscles
" |> 
  lavaan::cfa(data=data)

cfa5short <- "
Skin =~ Tickle + Itch
Expulsion =~ Sneeze
Interoception =~ Heart + Hungry + Breathing + Thirsty + Sex_arousal
Nociception =~ Muscles + Bruise
Elimination =~ Defecate + Vomit
"

anova(cfa4mod, lavaan::cfa(cfa5short, data=data))

cfa4h <- "
Homeostasis =~ Hungry + Thirsty + Sex_arousal 
Skin =~ Tickle + Itch + Bruise 
Elimination =~ Defecate + Sneeze + Vomit 
Muscle =~ Breathing + Heart + Muscles
Interoception =~ Homeostasis + Skin + Elimination + Muscle
" |> 
  lavaan::cfa(data=data)

anova(cfa4mod, cfa4h)

check_perf(cfa4mod)

check_perf(cfa4h)
check_perf(update(cfa4h, data=standardize(df)))
check_perf(update(cfa4h, data=standardize(df2)))
```

```{r, message=FALSE, warning=FALSE, fig.width=16, fig.height=10}
graph_data <- tidySEM::prepare_graph(cfa4h, 
                                     variance_diameter=NA)

nodes <- graph_data$nodes |> 
  mutate(fill = ifelse(shape == "rect", "grey", "#F06292"),
         textsize = ifelse(shape == "rect", rel(3.5), rel(4)),
         fontface = ifelse(shape == "oval", "bold", "plain"),
         hjust = ifelse(shape == "oval", 0.5, -0.3),
         textcolor = ifelse(shape == "oval", "white", "black"),
         label = str_replace(label, "Sex_arousal", "Arousal")) |> 
  select(-x, -y)

edges <- graph_data$edges |>
  mutate(est = as.numeric(est))

p_graph <- tidygraph::tbl_graph(nodes = nodes, edges = edges) |> 
  ggraph(layout = "kk") +
  geom_edge_arc(aes(filter=lhs!="Interoception",
                    edge_width = est,
                    label=est_std),
                strength = 0.15,
                color="#2196F3",
                angle_calc="along",
                label_dodge=unit(-0.02, "npc"),
                label_size = rel(4)) +
  geom_edge_link(aes(filter=lhs=="Interoception",
                     edge_width = est, 
                     # color = color,
                     label=est_std), 
                 color="#3F51B5",
                 angle_calc="along", 
                 label_dodge=unit(-0.02, "npc"),
                 label_size = rel(5)) +
  geom_node_point(aes(shape = shape, color=name, size=shape)) +
  geom_node_text(aes(label = label, fontface=shape),
                 size=nodes$textsize,
                 fontface = nodes$fontface,
                 hjust = nodes$hjust,
                 color = nodes$textcolor) +
  # scale_y_continuous(expand = expansion(add=c(0.1, 0.1))) +
  scale_x_continuous(expand = expansion(add=c(0.3, 0.4))) +
  scale_edge_width_continuous(range=c(0.5, 2), guide="none") +
  scale_color_manual(values=c("Interoception" = "red",
                              "Muscles" = "#E91E63",
                              "Heart" = "#E91E63",
                              "Breathing" = "#E91E63",
                              "Muscle" = "#E91E63",
                              "Skin" = "#FF5722",
                              "Tickle" = "#FF5722",
                              "Itch" = "#FF5722",
                              "Bruise" = "#FF5722",
                              "Elimination" = "#FFC107",
                              "Defecate" = "#FFC107",
                              "Sneeze" = "#FFC107",
                              "Vomit" = "#FFC107",
                              "Homeostasis" = "#9C27B0",
                              "Hungry" = "#9C27B0",
                              "Thirsty" = "#9C27B0",
                              "Sex_arousal" = "#9C27B0"), guide="none") +
  scale_shape_manual(values=c("oval"="circle", "rect"="square"), guide="none") +
  scale_size_manual(values = c(35, 5), guide="none") +
  labs(title = "C. Structural Equation Model")  +
  theme_graph() +
  theme(plot.title = element_text(hjust=0.5))
p_graph
```

## Comparison with MAIA

```{r, message=FALSE, warning=FALSE}
scores <- as.data.frame(predict(cfa4h))
scores$Participant <- df3$Participant
write.csv(scores, "data/IASR_scores.csv", row.names = FALSE)
```

# Study 3

```{r, message=FALSE, warning=FALSE}
df <- read.csv("../IllusionGameReliability/data/preprocessed_questionnaires.csv") |> 
  merge(read.csv("data/IASR_scores.csv"), by="Participant") |> 
  select(-ends_with("_RT"), -ends_with("_SD"))

df$Average <- rowMeans(select(df, starts_with("Item_IAS")))

vars <- c("Homeostasis", "Skin", "Elimination", "Muscle", "Interoception")

# correlation(df[vars], select(df, starts_with("Item_IAS"))) |> 
#   summary() |> 
#   plot()
```

## Personality

```{r, message=FALSE, warning=FALSE}
make_correlation <- function(x, y) {
  cor <- correlation::correlation(x,
    y,
    bayesian = TRUE,
    bayesian_prior = "medium.narrow",
    sort = TRUE
  ) |>
    datawizard::data_remove(c("ROPE_Percentage"))

  cor$BF_Spearman <- format_bf(
    correlation::correlation(
      x, y,
      bayesian = TRUE,
      ranktransform = TRUE,
      bayesian_prior = "medium.narrow"
    )$BF,
    name = NULL, stars = FALSE
  )

  r <- filter(cor, BF >= 10)

  if(nrow(r) == 0) list(data = cor, print = "No significant (BF >= 10) correlations.")

  to_print <- r |>
    arrange(Parameter1, desc(BF)) |>
    format_table() |>
    mutate(Coefficient = paste(rho, `95% CI`)) |>
    select(Parameter1, Parameter2, Coefficient, BF, `BF (Spearman)` = BF_Spearman)

  list(data = cor, print = to_print)
}

ipip <- make_correlation(df[vars], select(df, starts_with("IPIP6_"))) 
export_table(ipip$print)

pid <- make_correlation(df[vars], select(df, starts_with("PID5_"))) 
export_table(pid$print)
```

## Psychopathology

```{r, message=FALSE, warning=FALSE}
asq <- make_correlation(df[vars], select(df, starts_with("ASQ_")))
export_table(asq$print)
spq <- make_correlation(df[vars], select(df, starts_with("SPQ_"))) 
export_table(spq$print)
bpd <- make_correlation(df[vars], select(df, starts_with("BPD_"))) 
export_table(bpd$print)
phq <- make_correlation(df[vars], select(df, starts_with("PHQ4_"))) 
export_table(phq$print)
```

## Other

```{r, message=FALSE, warning=FALSE}
pi <- make_correlation(df[vars], select(df, starts_with("PI_")))
export_table(pi$print)
gcbs <- make_correlation(df[vars], select(df, starts_with("GCBS_"))) 
export_table(gcbs$print)
age <- make_correlation(df[vars], select(df, Age)) 
export_table(age$print)
```

```{r, message=FALSE, warning=FALSE}
p_cor <- rbind(
  mutate(ipip$data, Domain = "Normal Personality"),
  mutate(pid$data, Domain = "Maladaptive Personality"),
  mutate(asq$data, Domain = "Autistic Traits"),
  mutate(spq$data, Domain = "Schizotypic Traits")
) |> 
  mutate(alpha = ifelse(BF >= 10, "BF >= 10", "BF < 10"),
         Parameter1 = fct_relevel(Parameter1, "Interoception", "Muscle", "Homeostasis", "Elimination", "Skin"),
         Domain = fct_relevel(Domain, "Normal Personality", "Maladaptive Personality", "Autistic Traits", "Schizotypic Traits"),
         Parameter2 = str_remove_all(Parameter2, "IPIP6_|PID5_|ASQ_|SPQ_")) |>
  ggplot(aes(x = rho, y = Parameter2)) +
  geom_bar(aes(alpha = alpha, fill = rho), stat = "identity") +
  facet_grid(Domain~Parameter1, scales="free_y", switch ="y") +
  scale_alpha_manual(values = c(0.2, 1)) +
  scale_fill_gradient2(low = "#2196F3", high = "#FF5722") +
  labs(title = "Correlates of IAS-R Dimensions") +
  guides(alpha = "none", fill = "none") +
  theme_minimal() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        strip.placement.y = "outside",
        strip.background.x = element_rect(fill = "#E0E0E0", color = "white"),
        strip.text = element_text(face = "bold", size = rel(1)))
p_cor
```

# Figures

```{r, message=FALSE, warning=FALSE}
p_dens <- rbind(
  mutate(dens1, Study = "Study 1a"),
  filter(mutate(dens2, Study = "Study 1b"), Parameter %in% dens1$Parameter),
  filter(mutate(dens3, Study = "Study 2"), Parameter %in% dens1$Parameter)
) |> 
  ggplot(aes(x=x, y=y, color=Parameter)) +
  geom_line() +
  facet_wrap(~Study, scales = "free", ncol = 1, strip.position = "right") +
  scale_color_metro_d() +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(y = "Density", x = "Answer", title = "A. Distribution of Answers") +
  guides(color = guide_legend(title="Item", ncol=1, byrow=TRUE, keyheight=0)) +
  theme_modern(axis.title.space = 5) +
  theme(axis.text.y = element_blank(),
        axis.line.y = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0),
        legend.text = element_text(size = rel(0.8)),
        legend.spacing.y = unit(0.1, 'cm'),
        strip.background = element_rect(fill = "#E0E0E0", color = "white"))

p_efa <- rbind(
  attributes(efa4)$dataset[names(data)] |> 
    parameters::factor_analysis(n=4, rotation = "oblimin", sort = TRUE, fm="ml") |> 
    data_plot() |> 
    mutate(Study = "Study 1a"),
  attributes(efa4b)$dataset[names(data)] |> 
    parameters::factor_analysis(n=4, rotation = "oblimin", sort = TRUE, fm="ml") |> 
    data_plot() |> 
    mutate(Study = "Study 1b"),
  efa4c |> 
    data_plot() |> 
    mutate(Study = "Study 2") 
) |> 
  mutate(Variable = fct_relevel(Variable, sort(levels(Variable), decreasing = TRUE)),
         fill = as.factor(sign(y)),
         x = abs(y),
         Component = str_replace_all(Component, "ML", "Factor ")) |> 
  ggplot(aes(x = x, y = Variable, fill = fill)) +
  geom_bar(stat = "identity") + 
  scale_x_continuous(expand = c(0, 0), breaks = c(0, 0.25, 0.5, 0.75), labels = c("0", ".25", ".50", ".75")) +
  scale_fill_manual(values = c("#E91E63", "#4CAF50")) +
  labs(x = "Loading", title = "B. Exploratory Factor Analysis") +
  guides(fill = "none") +
  theme_modern(axis.title.space = 5) +
  theme(panel.grid.major.y = element_line(),
        axis.title.y = element_blank(),
        axis.line.x = element_blank(),
        axis.text.y = element_text(size = rel(0.5)),
        axis.text.x = element_text(size = rel(0.8)),
        plot.title = element_text(face = "bold", hjust = 0),
        strip.placement = "outside",
        strip.background.y = element_rect(fill = "#E0E0E0", color = "white"),
        strip.background.x = element_rect(fill = "#F8BBD0", color = "white")) +
  facet_grid(Study ~ Component, switch = "y")

fig <- ((wrap_elements(p_dens) + wrap_elements(p_efa)) / p_graph)
ggsave("figures/Figure1.png", fig, width=fig.width, height=fig.width*1.3, dpi=150)
ggsave("figures/Figure2.png", p_cor, width=21*0.35, height=29.7*0.35, dpi=150, bg="white")
```

### 2023-01-16 paper/1_Initial/manuscript.Rmd
update

---
title             : "**The Revised Interoceptive Accuracy Scale (IAS-R)**"
shorttitle        : "PHQ-4R"
author:
  - name          : "Dominique Makowski"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "HSS 04-18, 48 Nanyang Avenue, Singapore"
    email         : "dom.makowski@gmail.com"
    orcid         : 0000-0001-5375-9967
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Data curation"
      - "Formal Analysis"
      - "Funding acquisition"
      - "Investigation"
      - "Methodology"
      - "Project administration"
      - "Resources"
      - "Software"
      - "Supervision"
      - "Validation"
      - "Visualization"
      - "Writing – original draft"
  - name          : "An Shu Te"
    affiliation   : "2"
    orcid         : 0000-0001-8008-2824
    role:
      - "Project administration"
      - "Resources"
      - "Software"
      - "Investigation"
      - "Writing – original draft"
  - name          : "S.H. Annabel Chen"
    affiliation   : "2, 3, 4, 5"
    orcid         : 0000-0002-1540-5516
    role:
      - "Project administration"
      - "Supervision"
      - "Writing – review & editing"
affiliation:
  - id            : "1"
    institution   : "School of Psychology, University of Sussex, UK"
  - id            : "2"
    institution   : "School of Social Sciences, Nanyang Technological University, Singapore"
  - id            : "3"
    institution   : "LKC Medicine, Nanyang Technological University, Singapore"
  - id            : "4"
    institution   : "National Institute of Education, Singapore"
  - id            : "5"
    institution   : "Centre for Research and Development in Learning, Nanyang Technological University, Singapore"
abstract: |
  Something something.

keywords          : "PHQ-4; depression; anxiety; brief questionnaire; short scale"
wordcount         : "1249"
bibliography      : references.bib
floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no
figurelist        : yes
tablelist         : no
footnotelist      : no
classoption       : "man"
output            : papaja::apa6_pdf
csl: "../utils/apa.csl"
header-includes:
  - \usepackage[labelfont=bf, font={scriptsize, color=gray}]{caption}
editor_options:
  chunk_output_type: console
---

```{r, echo = FALSE, warning=FALSE, message=FALSE}
# options and parameters
options(digits = 3)

knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 450,
  fig.width = see::golden_ratio(9),
  fig.height = 9,
  fig.path = "../../figures/"
)

cache <- TRUE
```

# Introduction

Interoception - definition - is the trending topic. 
Unfortunately, it is also notably hard to measure.

Scales are useful to capture metacognitive and subjective aspects and beliefs
While the relationship between scales and tasks is a strong point of contention, it is important to continue developing sound scales from a structural (i.e., factorial) standpoint.

One of the most recent scale is the IAS, which is interesting because... It has *n* items, such as ...
However, the study analysis did not go in depth in the analysis of the factor structure, focusing instead on ....

The purpose of this work is to re-analyze the factor structure of the scale using complementary statistical approaches. and propose a revised version. And to compare it with one of the most popular questionnaire of interoception, the MAIA-2 (*ref*).

# Study 1

Study 1 is a re-analysis of the data from @murphy2020testing regarding the factor structure of the Interoceptive Accuracy Scale (IAS). The aim is to use a finer-grained method for estimating the optimal number of latent factors [namely, the *Method Agreement Procedure*, in @ludecke2020extracting; @makowski2018psycho], and perform a statistical model comparison using Confirmatory Factor Analysis (CFA).

## Participants

The exploratory factor analysis (EFA) and initial model selection was performed on the data from [study 1](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) of @murphy2020testing, downloaded from OSF, included 451 participants (Mean age = 25.8, SD = 8.4, range: [18, 69]; Gender: 69.4% women, 29.5% men, 1.11% non-binary). Data from the [study 6](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769), which included 375 participants (Mean age = 35.3, SD = 16.9, range: [18, 91]; Gender: 70.1% women, 28.5% men, 1.33% non-binary), was used as a test-set for confirmatory analysis.

## Results

The *Method Agreement Procedure* suggested 1 latent factor as optimal, supported by 5 (31.25%) out of 16 methods (Bentler, Acceleration factor, Scree (R2), VSS complexity 1, Velicer's MAP), followed by 4 factors supported by 4 methods (Kaiser criterion, beta score, optimal coordinates, parallel analysis).

We fitted the simple-structure (i.e., each variable loading only unto its maximal latent factor) of these two models using CFA, underlining the 4-factors model as having a significantly better fit ($\Delta \chi^2(6) = 232, p < .001; BIC_{CFA-1} = 25141, BIC_{CFA-4} = 24945$). Using the EFA loading patterns and the CFA modification indices, we then compared the initial 4-factor model to two variants: one with 2 items removed (Blood sugar and Taste), and another with, additionally, the *Interoception* factor split into two (with the pain-related items grouped together as a *Nociception* factor). The latter model (*CFA-5*), was significantly superior to the others ($\Delta \chi^2(4) = 28.8, p < .001; BIC_{CFA-4mod} = 22563, BIC_{CFA-5} = 22559$). We then removed the least loaded items of *Expulsion* (cough) to improve the balance (6 items for interoception and 3 per secondary scales), which significantly improved the model fit ($\Delta \chi^2(17) = 61.4, p < .001; BIC_{CFA-5mod} = 21256$). Finally, we tested a hierarchical model in which the interoception dimension was, in addition to its own 6 items, loaded by the secondary latent factors (Skin, Expulsion, Nociception, Elimination), but this model did not improve the fit ($BIC_{CFA-5h} = 21452$), suggesting that the 4 secondary latent factors are not subdimensions of the interoception factor.

Finally, we re-fitted the CFA models on a new data set [study 6 of @murphy2020testing], which confirmed that the 5-factor balanced model had the better fit ($BIC_{CFA-5mod} = 17316; BIC_{CFA-5h} = 17323; BIC_{CFA-5} = 18257; BIC_{EFA-4mod} = 18265$). However, the final model had barely acceptable indices of fit in both samples (Sample 1: $RMSEA = .067$ (acceptable < .08), $CFI = .878$ (acceptable > .9), $SRMR = .057$ (acceptable < .08); Sample 2: $RMSEA = .068$, $CFI = .906$, $SRMR = .063$).

## Summary

Exploratory Factor Analysis suggested a 1-factor and 4-factors solutions, but the latter was favoured by CFA. Further comparison suggested that a 5-factors model (obtained by separating *Nociception* from *Interoception* and balancing the number of items per dimension) had a superior fit. The 5 factors (with their items) are **Interoception** (Heart, Hungry, Breathing, Thirsty, Temperature, Sexual arousal); **Nociception** (Muscles, Bruise, Pain); **Expulsion** (Burp, Sneeze, Wind); **Elimination** (Vomit, Defecate, Urinate); **Skin** (Itch, Tickle, Affective touch). However, the indices of fit for this model were relatively low.

# Study 2

The final revised scale, made of 18 items (6 for interoception and 3 per secondary dimension), was administered to a new sample in an online study. The response was chained from a 5-point Likert scale (**ANSHU TO CONFIRM**) to a analog scale.

## Participants

485 participants (Mean age = 30.1, SD = 10.1, range: [18, 73]; Sex: 50.3% females, 49.7% males).
**Update based on para from PHQ4**

## Results

Despite changing the response format for analog scales, the distribution of answers was similar to that of the original validation samples, with a modal answer of around 75% of the scale for most of the items (see **Figure 1A**). Contrary to our expectations, the *Method Agreement Procedure* for EFA suggested 4 latent factor (supported by 31.58% of methods), rather than the 5 hypothesized (supported by 0 methods). CFA confirmed that the 4-factor model derived from the EFA had a better fit than this 5-factor model and than a 1-factor model ($BIC_{CFA-4} = 22758, BIC_{CFA-1} = 22911, BIC_{CFA-1} = 23065$). We then re-balanced the 4-factor model to keep 3 items per factor and remove items that strongly loaded on more than one factor in the EFA (e.g., Temperature and Sneeze, see **Figure 1B**). Finally, we compare the resulting model to one with a fifth latent factor (*Interoception*) loaded by the 4 others latent factors. Adding this general score did not significantly change the model's fit ($\Delta \chi^2(2) = 5.85, p = .054; BIC_{CFA-4mod} = 15140, BIC_{CFA-4h} = 15259$). Importantly, the resulting model (see **Figure 1C**) had excellent indices of fit ($RMSEA = .0347$, $CFI = .9796$, $SRMR = .0364$). Finally, we re-fitted this model on the two samples from study 1, and report improved indices of fit over the initial best model (Sample 1: $RMSEA = .068$, $CFI = .9020$, $SRMR = .0556$; Sample 2: $RMSEA = .066$, $CFI = .9315$, $SRMR = .0504$).

# Study 3

# General Discussion

\newpage

# Data Availability

The dataset analysed during the current study are available in the GitHub repository https://github.com/DominiqueMakowski/InteroceptiveAccuracyScale.

# Funding

This work was supported by the Presidential Postdoctoral Fellowship Grant (NTU-PPF-2020-10014) from Nanyang Technological University (awarded to DM).

# Acknowledgments

We warmly thank the original authors of [@murphy2020testing] for making their data and material open-access, which enabled the present follow-up study.

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::

### 2023-01-16 paper/1_Initial/manuscript.tex
update

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{PHQ-4; depression; anxiety; brief questionnaire; short scale\newline\indent Word count: 1249}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage[titles]{tocloft}
\cftpagenumbersoff{figure}
\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
\renewcommand{\cftfigaftersnum}{.\space}
\setlength{\cftfigindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cftfignumwidth}{Figure 10.\qquad}
\usepackage[labelfont=bf, font={scriptsize, color=gray}]{caption}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={The Revised Interoceptive Accuracy Scale (IAS-R)},
  pdfauthor={Dominique Makowski1, An Shu Te2, \& S.H. Annabel Chen2, 3, 4, 5},
  pdflang={en-EN},
  pdfkeywords={PHQ-4; depression; anxiety; brief questionnaire; short scale},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{\textbf{The Revised Interoceptive Accuracy Scale (IAS-R)}}
\author{Dominique Makowski\textsuperscript{1}, An Shu Te\textsuperscript{2}, \& S.H. Annabel Chen\textsuperscript{2, 3, 4, 5}}
\date{}

\shorttitle{PHQ-4R}

\authornote{

The authors made the following contributions. Dominique Makowski: Conceptualization, Data curation, Formal Analysis, Funding acquisition, Investigation, Methodology, Project administration, Resources, Software, Supervision, Validation, Visualization, Writing -- original draft; An Shu Te: Project administration, Resources, Software, Investigation, Writing -- original draft; S.H. Annabel Chen: Project administration, Supervision, Writing -- review \& editing.

Correspondence concerning this article should be addressed to Dominique Makowski, HSS 04-18, 48 Nanyang Avenue, Singapore. E-mail: \href{mailto:dom.makowski@gmail.com}{\nolinkurl{dom.makowski@gmail.com}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} School of Psychology, University of Sussex, UK\\\textsuperscript{2} School of Social Sciences, Nanyang Technological University, Singapore\\\textsuperscript{3} LKC Medicine, Nanyang Technological University, Singapore\\\textsuperscript{4} National Institute of Education, Singapore\\\textsuperscript{5} Centre for Research and Development in Learning, Nanyang Technological University, Singapore}

\abstract{%
Something something.
}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Interoception - definition - is the trending topic.
Unfortunately, it is also notably hard to measure.

Scales are useful to capture metacognitive and subjective aspects and beliefs
While the relationship between scales and tasks is a strong point of contention, it is important to continue developing sound scales from a structural (i.e., factorial) standpoint.

One of the most recent scale is the IAS, which is interesting because\ldots{}

The purpose of this work is to re-analyze the factor structure of the scale using complementary statistical approaches. and propose a revised version.

\hypertarget{study-1}{%
\section{Study 1}\label{study-1}}

Study 1 is a re-analysis of the data from Murphy et al. (2020) regarding the factor structure of the Interoceptive Accuracy Scale (IAS). The aim is to use a finer-grained method for estimating the optimal number of latent factors (namely, the \emph{Method Agreement Procedure}, in Lüdecke et al., 2020; Makowski, 2018), and perform a statistical model comparison using Confirmatory Factor Analysis (CFA).

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

The exploratory factor analysis (EFA) and initial model selection was performed on the data from \href{https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769}{study 1} of Murphy et al. (2020), downloaded from OSF, included 451 participants (Mean age = 25.8, SD = 8.4, range: {[}18, 69{]}; Gender: 69.4\% women, 29.5\% men, 1.11\% non-binary). Data from the \href{https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769}{study 6}, which included 375 participants (Mean age = 35.3, SD = 16.9, range: {[}18, 91{]}; Gender: 70.1\% women, 28.5\% men, 1.33\% non-binary), was used as a test-set for confirmatory analysis.

\hypertarget{results}{%
\subsection{Results}\label{results}}

The \emph{Method Agreement Procedure} suggested 1 latent factor as optimal, supported by 5 (31.25\%) out of 16 methods (Bentler, Acceleration factor, Scree (R2), VSS complexity 1, Velicer's MAP), followed by 4 factors supported by 4 methods (Kaiser criterion, beta score, optimal coordinates, parallel analysis).

We fitted the simple-structure (i.e., each variable loading only unto its maximal latent factor) of these two models using CFA, underlining the 4-factors model as having a significantly better fit (\(\Delta \chi^2(6) = 232, p < .001; BIC_{EFA-1} = 23041, BIC_{EFA-4} = 23846\)). Using the EFA loading patterns and the CFA modification indices, we then compared the initial 4-factor model to two variants: one with 2 items removed (Blood sugar and Taste), and another with, additionally, the \emph{Interoception} factor split into two (with the pain-related items grouped together). The latter model (\emph{CFA-5}), was significantly superior to the others (\(\Delta \chi^2(4) = 28.8, p < .001; BIC_{EFA-4mod} = 21555, BIC_{CFA-5} = 21551\)). Finally, we removed the least loaded items of expulsion (cough) to improve the balance (3 items per secondary scales, and 6 for interoception), which significantly improved the model fit (\(\Delta \chi^2(17) = 61.4, p < .001; BIC_{CFA-5mod} = 20552\)).

Finally, we re-fitted the models on a new data set (study 6 of Murphy et al., 2020).

\hypertarget{summary}{%
\subsection{Summary}\label{summary}}

Exploratory Factor Analysis suggested a 1-factor and 4-factors solutions, but the latter was favoured by CFA. Further comparison suggested that a 5-factors model (obtained by separating \emph{Nociception} from \emph{Interoception}) had a superior fit. The 5 factors are:

\begin{itemize}
\tightlist
\item
  \textbf{Interoception}: Heart, Hungry, Breathing, Thirsty, Temperature, Sexual arousal.
\item
  \textbf{Nociception}: Muscles, Bruise, Pain.
\item
  \textbf{Expulsion}: Burp, Sneeze, Wind.
\item
  \textbf{Elimination}: Vomit, Defecate, Urinate.
\item
  \textbf{Skin}: Itch, Tickle, Affective touch.
\end{itemize}

The final revised scale, made of 18 items (6 for interoception and 3 per secondary dimension), is available \protect\hyperlink{IAS-R}{below}.

\hypertarget{study-2}{%
\section{Study 2}\label{study-2}}

\newpage

\hypertarget{data-availability}{%
\section{Data Availability}\label{data-availability}}

The dataset analysed during the current study are available in the GitHub repository \url{https://github.com/DominiqueMakowski/InteroceptiveAccuracyScale}.

\hypertarget{funding}{%
\section{Funding}\label{funding}}

This work was supported by the Presidential Postdoctoral Fellowship Grant (NTU-PPF-2020-10014) from Nanyang Technological University (awarded to DM).

\hypertarget{acknowledgments}{%
\section{Acknowledgments}\label{acknowledgments}}

We warmly thank the original authors of (Murphy et al., 2020) for making their data and material open-access, which enabled the present follow-up study.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-ludecke2020extracting}{}}%
Lüdecke, D., Ben-Shachar, M. S., Patil, I., \& Makowski, D. (2020). Extracting, computing and exploring the parameters of statistical models using r. \emph{Journal of Open Source Software}, \emph{5}(53), 2445.

\leavevmode\vadjust pre{\hypertarget{ref-makowski2018psycho}{}}%
Makowski, D. (2018). The psycho package: An efficient and publishing-oriented workflow for psychological science. \emph{Journal of Open Source Software}, \emph{3}(22), 470.

\leavevmode\vadjust pre{\hypertarget{ref-murphy2020testing}{}}%
Murphy, J., Brewer, R., Plans, D., Khalsa, S. S., Catmur, C., \& Bird, G. (2020). Testing the independence of self-reported interoceptive accuracy and attention. \emph{Quarterly Journal of Experimental Psychology}, \emph{73}(1), 115--133.

\end{CSLReferences}

\clearpage
\renewcommand{\listfigurename}{Figure captions}

\end{document}

### 2023-01-17 analysis.Rmd
manu

@@
 make_correlation <- function(x, y) {
-  cor <- correlation::correlation(x,
-    y,
+  set.seed(3)
+  cor <- correlation::correlation(
+    x, y,
     bayesian = TRUE,
-    bayesian_prior = "medium.narrow",
-    sort = TRUE
+    bayesian_prior = "medium.narrow"
   ) |>
@@
 
-  if(nrow(r) == 0) list(data = cor, print = "No significant (BF >= 10) correlations.")
+  if(nrow(r) == 0) return(list(data = cor, print = "No significant (BF >= 10) correlations."))
 
@@
 export_table(spq$print)
-bpd <- make_correlation(df[vars], select(df, starts_with("BPD_"))) 
+bpd <- make_correlation(df[vars], select(df, starts_with("BPD"))) 
 export_table(bpd$print)
@@
 export_table(gcbs$print)
-age <- make_correlation(df[vars], select(df, Age)) 
+age <- make_correlation(df[vars], data.frame(Age = df$Age)) 
 export_table(age$print)
+sex <- make_correlation(df[vars], data.frame(Sex = ifelse(df$Sex == "Male", 0, 1)) )
+export_table(sex$print)
 ```
@@
   mutate(asq$data, Domain = "Autistic Traits"),
-  mutate(spq$data, Domain = "Schizotypic Traits")
+  mutate(spq$data, Domain = "Schizotypic Traits"),
+  mutate(phq$data, Domain = "Mood Disorders"),
+  mutate(gcbs$data, Domain = "Conspiracy Beliefs")
+  # mutate(age$data, Domain = "Demographic"),
+  # mutate(sex$data, Domain = "Demographic")
 ) |> 
@@
          Domain = fct_relevel(Domain, "Normal Personality", "Maladaptive Personality", "Autistic Traits", "Schizotypic Traits"),
-         Parameter2 = str_remove_all(Parameter2, "IPIP6_|PID5_|ASQ_|SPQ_")) |>
+         Parameter2 = str_remove_all(Parameter2, "IPIP6_|PID5_|ASQ_|SPQ_|GCBS_"),
+         Parameter2 = str_replace(Parameter2, "Sex", "Sex (Female vs. Male)"),
+         Parameter2 = str_replace(Parameter2, "HonestyHumility", "Honesty-Humility"),
+         color = as.character(sign(rho))) |>
   ggplot(aes(x = rho, y = Parameter2)) +
   geom_bar(aes(alpha = alpha, fill = rho), stat = "identity") +
+  geom_linerange(aes(alpha = alpha, xmin = CI_low, xmax = CI_high, color = color)) +
+  geom_vline(xintercept = 0) +
   facet_grid(Domain~Parameter1, scales="free_y", switch ="y") +
   scale_alpha_manual(values = c(0.2, 1)) +
-  scale_fill_gradient2(low = "#2196F3", high = "#FF5722") +
+  scale_fill_gradient2(low = "#2196F3", high = "#FF5722", limits = c(-0.25, 0.25)) +
+  scale_colour_manual(values = c("#2196F3", "#FF5722")) +
+  scale_x_continuous(expand = c(0, 0)) +
+  coord_cartesian(xlim = c(-0.3, 0.3)) +
   labs(title = "Correlates of IAS-R Dimensions") +
-  guides(alpha = "none", fill = "none") +
+  guides(alpha = "none", fill = "none", color="none") +
   theme_minimal() +

### 2023-01-17 paper/1_Initial/manuscript.Rmd
manu

@@
 ---
-title             : "**The Revised Interoceptive Accuracy Scale (IAS-R)**"
+title             : "**The Revised Interoceptive Accuracy Scale (IAS-R) Confirms Links between Interoception and Personality and Psychopathological Traits**"
 shorttitle        : "PHQ-4R"
@@
 
-keywords          : "PHQ-4; depression; anxiety; brief questionnaire; short scale"
+keywords          : "IAS-R; Interoception; Personality; Psychopathology; Validation"
 wordcount         : "1249"
@@
 
-We fitted the simple-structure (i.e., each variable loading only unto its maximal latent factor) of these two models using CFA, underlining the 4-factors model as having a significantly better fit ($\Delta \chi^2(6) = 232, p < .001; BIC_{CFA-1} = 25141, BIC_{CFA-4} = 24945$).
-Using the EFA loading patterns and the CFA modification indices, we then compared the initial 4-factor model to two variants: one with 2 items removed (Blood sugar and Taste), and another with, additionally, the *Interoception* factor split into two (with the pain-related items grouped together as a *Nociception* factor).
+We fitted the simple-structure (i.e., each variable loading only unto its maximal latent factor) of these two models using CFA, which underlined the 4-factors model as having a significantly better fit ($\Delta \chi^2(6) = 232, p < .001; BIC_{CFA-1} = 25141, BIC_{CFA-4} = 24945$).
+Using the EFA loading patterns and the CFA modification indices, we then compared the initial 4-factor model to two variants: one with 2 items removed (Blood sugar and Taste), and another with, additionally, the *Interoception* factor split into two (with the pain-related items grouped together in a *Nociception* factor).
 The latter model (*CFA-5*), was significantly superior to the others ($\Delta \chi^2(4) = 28.8, p < .001; BIC_{CFA-4mod} = 22563, BIC_{CFA-5} = 22559$).
-We then removed the least loaded items of *Expulsion* (cough) to improve the balance (6 items for interoception and 3 per secondary scales), which significantly improved the model fit ($\Delta \chi^2(17) = 61.4, p < .001; BIC_{CFA-5mod} = 21256$).
-Finally, we tested a hierarchical model in which the interoception dimension was, in addition to its own 6 items, loaded by the secondary latent factors (Skin, Expulsion, Nociception, Elimination), but this model did not improve the fit ($BIC_{CFA-5h} = 21452$), suggesting that the 4 secondary latent factors are not subdimensions of the interoception factor.
+We then removed the least loaded item of *Expulsion* (cough) to improve the balance (6 items for interoception and 3 per secondary scales), which significantly improved the model fit ($\Delta \chi^2(17) = 61.4, p < .001; BIC_{CFA-5mod} = 21256$).
+Finally, we tested a hierarchical model in which the interoception dimension was, in addition to its own 6 items, loaded by the secondary latent factors (*Skin*, *Expulsion*, *Nociception*, *Elimination*), but this model did not improve the fit ($BIC_{CFA-5h} = 21452$).
 
-Finally, we re-fitted the CFA models on a new data set [study 6 of @murphy2020testing], which confirmed that the 5-factor balanced model had the better fit ($BIC_{CFA-5mod} = 17316; BIC_{CFA-5h} = 17323; BIC_{CFA-5} = 18257; BIC_{EFA-4mod} = 18265$).
-However, the final model had barely acceptable indices of fit in both samples (Sample 1: $RMSEA = .067$ (acceptable < .08), $CFI = .878$ (acceptable > .9), $SRMR = .057$ (acceptable < .08); Sample 2: $RMSEA = .068$, $CFI = .906$, $SRMR = .063$).
+Finally, we re-fitted the CFA models on a new data set [study 6 of @murphy2020testing], which confirmed that the 5-factor balanced model had the better fit relative to the other models ($BIC_{CFA-5mod} = 17316; BIC_{CFA-5h} = 17323; BIC_{CFA-5} = 18257; BIC_{EFA-4mod} = 18265$).
+However, the final model had poor to barely acceptable absolute indices of fit in both samples (Sample 1: $RMSEA = .067$ (acceptable < .08), $CFI = .878$ (acceptable > .9), $SRMR = .057$ (acceptable < .08); Sample 2: $RMSEA = .068$, $CFI = .906$, $SRMR = .063$).
 
@@
 The 5 factors (with their items) are **Interoception** (Heart, Hungry, Breathing, Thirsty, Temperature, Sexual arousal); **Nociception** (Muscles, Bruise, Pain); **Expulsion** (Burp, Sneeze, Wind); **Elimination** (Vomit, Defecate, Urinate); **Skin** (Itch, Tickle, Affective touch).
-However, the indices of fit for this model were relatively low.
+However, absolute indices of fit for this model were relatively low.
 
@@
 
-The final revised scale, made of 18 items (6 for interoception and 3 per secondary dimension), was administered to a new sample in an online study.
-The response was chained from a 5-point Likert scale (**ANSHU TO CONFIRM**) to a analog scale.
+The revised scale, made of 18 items (6 for interoception and 3 per secondary dimension), was administered to a new sample in an online study.
+The response was changed from a 5-point Likert scale (**ANSHU TO CONFIRM**) to a analog scale.
 
@@
 
+Note that as the MAIA and the PI were done on a different session 2, we only have n = ... for their correlations.
+
 ## Results
 
-Despite changing the response format for analog scales, the distribution of answers was similar to that of the original validation samples, with a modal answer of around 75% of the scale for most of the items (see **Figure 1A**).
-Contrary to our expectations, the *Method Agreement Procedure* for EFA suggested 4 latent factor (supported by 31.58% of methods), rather than the 5 hypothesized (supported by 0 methods).
+Despite changing the response format to analog scales, the distribution of answers was similar to that of the original validation samples, with a modal answer at around 75% of the scale for most of the items (see **Figure 1A**).
+Contrary to our expectations, the *Method Agreement Procedure* for EFA suggested 4 latent factor (supported by 5/16 methods), rather than the 5 hypothesized (supported by 0 methods).
 CFA confirmed that the 4-factor model derived from the EFA had a better fit than this 5-factor model and than a 1-factor model ($BIC_{CFA-4} = 22758, BIC_{CFA-1} = 22911, BIC_{CFA-1} = 23065$).
 We then re-balanced the 4-factor model to keep 3 items per factor and remove items that strongly loaded on more than one factor in the EFA (e.g., Temperature and Sneeze, see **Figure 1B**).
-Finally, we compare the resulting model to one with a fifth latent factor (*Interoception*) loaded by the 4 others latent factors.
+Finally, we compared the resulting model to one with a fifth latent factor (*Interoception*) loaded by the 4 others latent factors.
 Adding this general score did not significantly change the model's fit ($\Delta \chi^2(2) = 5.85, p = .054; BIC_{CFA-4mod} = 15140, BIC_{CFA-4h} = 15259$).
 Importantly, the resulting model (see **Figure 1C**) had excellent indices of fit ($RMSEA = .0347$, $CFI = .9796$, $SRMR = .0364$).
-Finally, we re-fitted this model on the two samples from study 1, and report improved indices of fit over the initial best model (Sample 1: $RMSEA = .068$, $CFI = .9020$, $SRMR = .0556$; Sample 2: $RMSEA = .066$, $CFI = .9315$, $SRMR = .0504$).
+Finally, we re-fitted this model on the two samples from study 1, which revealed much improved indices of fit over the initial best model (Sample 1: $RMSEA = .068$, $CFI = .9020$, $SRMR = .0556$; Sample 2: $RMSEA = .066$, $CFI = .9315$, $SRMR = .0504$).
 
-# Study 3
+We ran a Bayesian correlations analysis (with a narrow prior centred around 0)
+<!-- , which allows to quantify in favour and against the null hypothesis, -->
+between the individual facet scores extracted from the final model and the MAIA-2 dimensions (administered online on a different session).
+As all correlations are presented in **Figure 2**, we will focus in the following on a subset of key results.
+<!-- (with at least strong evidence in favour of a relationship, i.e., BF >= 10).  -->
+
+Correlations with the IPIP6 personality scale highlighted a positive relationship between the *Homeostatis* interoceptive dimension with *Agreeableness* ($r_{homeostasis} = .14, BF = 17.91$) and *Conscientiousness* ($TODO$); and a negative relationship with *Honesty-Humility* ($TODO$) and *Neuroticism* ($TODO$).
+This facet also negatively related to several pathological personality traits measured by the PID-5, such as *Psychoticism* ($TODO$), *Negative Affect* ($TODO$), and *Detachment* ($TODO$).
+In line with that, we also report negative relationships with schizotypical characteristics, including *Social Anxiety* ($TODO$), *Odd Speech*($TODO$), *No Close Friends* ($TODO$) and *Constricted Affect* ($TODO$); as well positive relationship with autistic traits, such as *Switching* ($TODO$) and *Social Skills* ($TODO$).
+
+## Summary
 
 # General Discussion
+
+Whether this scale truly captures interoceptive accuracy is still a matter of debate (as is whether accuracy should even be focus of interoception research, see **recent review paper that I shared**).
+In any case, this scale has some advantages over others in that the items are straightforward and do directly relate to bodily processes, without being conflated (at least in their formulation) with emotional or attentional aspects.
+Despite being at first glance very different from the other personality measures, we found consistent and strong relationships.
+
+The fact that the *Homeostatis* dimension was the most significantly correlated with other subjective measures could be that it captures the most overt and key features of bodily signals (that relates to primal needs).
+As such, it might be the subscale with the most meaningful variability and accuracy.
+However, the relationships observed with this subscale were also consistently present for the other subscales (though typically with a lesser magnitude).
+
+\newpage
+
+# Revised Interoceptive Accuracy Scale (IAS-R)
+
+**Scoring**. Each scale can be answered on an analog scale (Disagree - Agree). Items can be averaged per dimension, and dimensions can be averaged to get a general Interoception score.
+
+**Instructions**.
+"Below are several statements regarding how accurately you can perceive specific bodily sensations.
+Please rate on the scale on how well you believe you can perceive each specific signal.
+For example, if you often feel you need to urinate and then realise you do not need to when you go to the toilet you would rate your accuracy perceiving this bodily signal as low.
+Please only rate how well you can perceive these signals without using external cues.
+For example, if you can only perceive how fast your heart is beating when you measure it by taking your pulse this would not count as accurate internal perception".
+
+```{r message=FALSE, warning=FALSE, out.width="100%"}
+papaja::apa_table(
+  data.frame(
+    Facet = c("\\textbf{Anxiety}", "", "", "\\textbf{Homeostatis}", "", ""),
+    Item = c("Breathing", "Muscles", "I can always accurately perceive when my heart is beating fast", "Itch", "Tickle", "Bruise")
+    ),
+  caption = "",
+  escape = FALSE,
+  font_size = "scriptsize",
+  col.names = c("Facet", "Item"),
+  midrules = c(3),
+  placement = "!h")
+```
 

### 2023-01-17 paper/1_Initial/manuscript.tex
manu

@@
 {}{\PatchFailed}
-\keywords{PHQ-4; depression; anxiety; brief questionnaire; short scale\newline\indent Word count: 1249}
+\keywords{IAS-R; Interoception; Personality; Psychopathology; Validation\newline\indent Word count: 1249}
 \usepackage{lineno}
@@
 \hypersetup{
-  pdftitle={The Revised Interoceptive Accuracy Scale (IAS-R)},
+  pdftitle={The Revised Interoceptive Accuracy Scale (IAS-R) Confirms Links between Interoception and Personality and Psychopathological Traits},
   pdfauthor={Dominique Makowski1, An Shu Te2, \& S.H. Annabel Chen2, 3, 4, 5},
   pdflang={en-EN},
-  pdfkeywords={PHQ-4; depression; anxiety; brief questionnaire; short scale},
+  pdfkeywords={IAS-R; Interoception; Personality; Psychopathology; Validation},
   hidelinks,
@@
 
-\title{\textbf{The Revised Interoceptive Accuracy Scale (IAS-R)}}
+\title{\textbf{The Revised Interoceptive Accuracy Scale (IAS-R) Confirms Links between Interoception and Personality and Psychopathological Traits}}
 \author{Dominique Makowski\textsuperscript{1}, An Shu Te\textsuperscript{2}, \& S.H. Annabel Chen\textsuperscript{2, 3, 4, 5}}
@@
 
-One of the most recent scale is the IAS, which is interesting because\ldots{}
+One of the most recent scale is the IAS, which is interesting because\ldots{} It has \emph{n} items, such as \ldots{}
+However, the study analysis did not go in depth in the analysis of the factor structure, focusing instead on \ldots.
 
-The purpose of this work is to re-analyze the factor structure of the scale using complementary statistical approaches. and propose a revised version.
+The purpose of this work is to re-analyze the factor structure of the scale using complementary statistical approaches.
+and propose a revised version.
+And to compare it with one of the most popular questionnaire of interoception, the MAIA-2 (\emph{ref}).
 
@@
 
-We fitted the simple-structure (i.e., each variable loading only unto its maximal latent factor) of these two models using CFA, underlining the 4-factors model as having a significantly better fit (\(\Delta \chi^2(6) = 232, p < .001; BIC_{EFA-1} = 23041, BIC_{EFA-4} = 23846\)).
-Using the EFA loading patterns and the CFA modification indices, we then compared the initial 4-factor model to two variants: one with 2 items removed (Blood sugar and Taste), and another with, additionally, the \emph{Interoception} factor split into two (with the pain-related items grouped together).
-The latter model (\emph{CFA-5}), was significantly superior to the others (\(\Delta \chi^2(4) = 28.8, p < .001; BIC_{EFA-4mod} = 21555, BIC_{CFA-5} = 21551\)).
-Finally, we removed the least loaded items of expulsion (cough) to improve the balance (3 items per secondary scales, and 6 for interoception), which significantly improved the model fit (\(\Delta \chi^2(17) = 61.4, p < .001; BIC_{CFA-5mod} = 20552\)).
+We fitted the simple-structure (i.e., each variable loading only unto its maximal latent factor) of these two models using CFA, underlining the 4-factors model as having a significantly better fit (\(\Delta \chi^2(6) = 232, p < .001; BIC_{CFA-1} = 25141, BIC_{CFA-4} = 24945\)).
+Using the EFA loading patterns and the CFA modification indices, we then compared the initial 4-factor model to two variants: one with 2 items removed (Blood sugar and Taste), and another with, additionally, the \emph{Interoception} factor split into two (with the pain-related items grouped together as a \emph{Nociception} factor).
+The latter model (\emph{CFA-5}), was significantly superior to the others (\(\Delta \chi^2(4) = 28.8, p < .001; BIC_{CFA-4mod} = 22563, BIC_{CFA-5} = 22559\)).
+We then removed the least loaded items of \emph{Expulsion} (cough) to improve the balance (6 items for interoception and 3 per secondary scales), which significantly improved the model fit (\(\Delta \chi^2(17) = 61.4, p < .001; BIC_{CFA-5mod} = 21256\)).
+Finally, we tested a hierarchical model in which the interoception dimension was, in addition to its own 6 items, loaded by the secondary latent factors (Skin, Expulsion, Nociception, Elimination), but this model did not improve the fit (\(BIC_{CFA-5h} = 21452\)), suggesting that the 4 secondary latent factors are not subdimensions of the interoception factor.
 
-Finally, we re-fitted the models on a new data set (study 6 of Murphy et al., 2020).
+Finally, we re-fitted the CFA models on a new data set (study 6 of Murphy et al., 2020), which confirmed that the 5-factor balanced model had the better fit (\(BIC_{CFA-5mod} = 17316; BIC_{CFA-5h} = 17323; BIC_{CFA-5} = 18257; BIC_{EFA-4mod} = 18265\)).
+However, the final model had barely acceptable indices of fit in both samples (Sample 1: \(RMSEA = .067\) (acceptable \textless{} .08), \(CFI = .878\) (acceptable \textgreater{} .9), \(SRMR = .057\) (acceptable \textless{} .08); Sample 2: \(RMSEA = .068\), \(CFI = .906\), \(SRMR = .063\)).
 
@@
 Exploratory Factor Analysis suggested a 1-factor and 4-factors solutions, but the latter was favoured by CFA.
-Further comparison suggested that a 5-factors model (obtained by separating \emph{Nociception} from \emph{Interoception}) had a superior fit.
-The 5 factors are:
-
-\begin{itemize}
-\tightlist
-\item
-  \textbf{Interoception}: Heart, Hungry, Breathing, Thirsty, Temperature, Sexual arousal.
-\item
-  \textbf{Nociception}: Muscles, Bruise, Pain.
-\item
-  \textbf{Expulsion}: Burp, Sneeze, Wind.
-\item
-  \textbf{Elimination}: Vomit, Defecate, Urinate.
-\item
-  \textbf{Skin}: Itch, Tickle, Affective touch.
-\end{itemize}
-
-The final revised scale, made of 18 items (6 for interoception and 3 per secondary dimension), is available \protect\hyperlink{IAS-R}{below}.
+Further comparison suggested that a 5-factors model (obtained by separating \emph{Nociception} from \emph{Interoception} and balancing the number of items per dimension) had a superior fit.
+The 5 factors (with their items) are \textbf{Interoception} (Heart, Hungry, Breathing, Thirsty, Temperature, Sexual arousal); \textbf{Nociception} (Muscles, Bruise, Pain); \textbf{Expulsion} (Burp, Sneeze, Wind); \textbf{Elimination} (Vomit, Defecate, Urinate); \textbf{Skin} (Itch, Tickle, Affective touch).
+However, the indices of fit for this model were relatively low.
 
@@
 \section{Study 2}\label{study-2}}
+
+The final revised scale, made of 18 items (6 for interoception and 3 per secondary dimension), was administered to a new sample in an online study.
+The response was chained from a 5-point Likert scale (\textbf{ANSHU TO CONFIRM}) to a analog scale.
+
+\hypertarget{participants-1}{%
+\subsection{Participants}\label{participants-1}}
+
+485 participants (Mean age = 30.1, SD = 10.1, range: {[}18, 73{]}; Sex: 50.3\% females, 49.7\% males).
+\textbf{Update based on para from PHQ4}
+
+\hypertarget{results-1}{%
+\subsection{Results}\label{results-1}}
+
+Despite changing the response format for analog scales, the distribution of answers was similar to that of the original validation samples, with a modal answer of around 75\% of the scale for most of the items (see \textbf{Figure 1A}).
+Contrary to our expectations, the \emph{Method Agreement Procedure} for EFA suggested 4 latent factor (supported by 31.58\% of methods), rather than the 5 hypothesized (supported by 0 methods).
+CFA confirmed that the 4-factor model derived from the EFA had a better fit than this 5-factor model and than a 1-factor model (\(BIC_{CFA-4} = 22758, BIC_{CFA-1} = 22911, BIC_{CFA-1} = 23065\)).
+We then re-balanced the 4-factor model to keep 3 items per factor and remove items that strongly loaded on more than one factor in the EFA (e.g., Temperature and Sneeze, see \textbf{Figure 1B}).
+Finally, we compare the resulting model to one with a fifth latent factor (\emph{Interoception}) loaded by the 4 others latent factors.
+Adding this general score did not significantly change the model's fit (\(\Delta \chi^2(2) = 5.85, p = .054; BIC_{CFA-4mod} = 15140, BIC_{CFA-4h} = 15259\)).
+Importantly, the resulting model (see \textbf{Figure 1C}) had excellent indices of fit (\(RMSEA = .0347\), \(CFI = .9796\), \(SRMR = .0364\)).
+Finally, we re-fitted this model on the two samples from study 1, and report improved indices of fit over the initial best model (Sample 1: \(RMSEA = .068\), \(CFI = .9020\), \(SRMR = .0556\); Sample 2: \(RMSEA = .066\), \(CFI = .9315\), \(SRMR = .0504\)).
+
+We ran Bayesian correlations analysis (with a narrow prior centred around 0)
+between the individual facet scores extracted from the final model and the MAIA-2 dimensions (administered online on a different session).
+As all correlations are presented in \textbf{Figure 2}, we will focus in the following on a subset of key results.
+
+Correlations with the IPIP6 personality scale highlighted a positive relationship between the \emph{Homeostatis} interoceptive dimension with \emph{Agreeableness} (\(r_{homeostasis} = .14, BF = 17.91\)) and \emph{Conscientiousness} (\(TODO\)); and a negative relationship with \emph{Honesty-Humility} (\(TODO\)) and \emph{Neuroticism} (\(TODO\)).
+This facet also negatively related to several pathological personality traits measured by the PID-5, such as \emph{Psychoticism} (\(TODO\)), \emph{Negative Affect} (\(TODO\)), and \emph{Detachment} (\(TODO\)).
+In line with that, we also report negative relationships with schizotypical characteristics, including \emph{Social Anxiety} (\(TODO\)), \emph{Odd Speech}(\(TODO\)), \emph{No Close Friends} (\(TODO\)) and \emph{Constricted Affect} (\(TODO\)); as well positive relationship with autistic traits, such as \emph{Switching} (\(TODO\)) and \emph{Social Skills} (\(TODO\)).
+
+\hypertarget{summary-1}{%
+\subsection{Summary}\label{summary-1}}
+
+\hypertarget{general-discussion}{%
+\section{General Discussion}\label{general-discussion}}
+
+Whether this scale truly captures interoceptive accuracy is still a matter of debate (as is whether accuracy should even be focus of interoception research, see \textbf{recent review paper that I shared}).
+In any case, this scale has some advantages over others in that the items are straightforward and do directly relate to bodily processes, without being conflated (at least in their formulation) with emotional or attentional aspects.
+Despite being at first glance very different from the other personality measures, we found consistent and strong relationships.
+
+The fact that the \emph{Homeostatis} dimension was the most significantly correlated with other subjective measures could be that it captures the most overt and key features of bodily signals (that relates to primal needs).
+As such, it might be the subscale with the most meaningful variability and accuracy.
+However, the relationships observed with this subscale were also consistently present for the other subscales (though typically with a lesser magnitude).
+
+\newpage
+
+\hypertarget{revised-interoceptive-accuracy-scale-ias-r}{%
+\section{Revised Interoceptive Accuracy Scale (IAS-R)}\label{revised-interoceptive-accuracy-scale-ias-r}}
+
+\textbf{Scoring}. Each scale can be answered on an analog scale (Disagree - Agree). Items can be averaged per dimension, and dimensions can be averaged to get a general Interoception score.
+
+\textbf{Instructions}.
+``Below are several statements regarding how accurately you can perceive specific bodily sensations.
+Please rate on the scale on how well you believe you can perceive each specific signal.
+For example, if you often feel you need to urinate and then realise you do not need to when you go to the toilet you would rate your accuracy perceiving this bodily signal as low.
+Please only rate how well you can perceive these signals without using external cues.
+For example, if you can only perceive how fast your heart is beating when you measure it by taking your pulse this would not count as accurate internal perception''.
+
+\begin{table}[!h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:unnamed-chunk-2}}
+
+\scriptsize{
+
+\begin{tabular}{ll}
+\toprule
+Facet & Item\\
+\midrule
+\textbf{Anxiety} & Breathing\\
+ & Muscles\\
+ & Heart\\ \midrule
+\textbf{Homeostatis} & Itch\\
+ & Tickle\\
+ & Bruise\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 

### 2023-02-09 analysis.Rmd
update with final sample

@@
 
-## Comparison with MAIA
+## Omega
+
+```{r, message=FALSE, warning=FALSE}
+semTools::compRelSEM(cfa4h)
+```
 
@@
 
-# Study 3
+## Comparison with MAIA
 
@@
 
-# correlation(df[vars], select(df, starts_with("Item_IAS"))) |> 
-#   summary() |> 
-#   plot()
-```
-
-## Personality
-
-```{r, message=FALSE, warning=FALSE}
 make_correlation <- function(x, y) {
@@
 
+maia <- make_correlation(df[vars], select(df, starts_with("MAIA_"))) 
+export_table(maia$print)
+
+maia$data |> 
+  arrange(Parameter2) |> 
+  tidygraph::as_tbl_graph() |> 
+  mutate(Type = ifelse(str_detect(name, "MAIA_"), "MAIA", "IAS")) |> 
+  tidygraph::activate("edges") |> 
+  filter(BF > 10) |> 
+  ggraph(layout = 'stress', weight=rho) + 
+  # geom_edge_arc(aes(edge_width = rho),
+  #               strength=0) +
+  geom_edge_link(aes(edge_alpha = after_stat(index), edge_width = rho), 
+                 edge_colour = "black") +
+  geom_node_point(aes(color = Type)) +
+  geom_node_text(aes(label=name)) +
+  scale_edge_width_continuous(range = c(0.1, 3)) +
+  coord_fixed() +
+  theme_graph()
+```
+
+# Study 3
+
+## Personality
+
+```{r, message=FALSE, warning=FALSE}
 ipip <- make_correlation(df[vars], select(df, starts_with("IPIP6_"))) 
@@
 p_cor <- rbind(
+  mutate(maia$data, Domain = "MAIA"),
   mutate(ipip$data, Domain = "Normal Personality"),
@@
   mutate(spq$data, Domain = "Schizotypic Traits"),
-  mutate(phq$data, Domain = "Mood Disorders"),
+  mutate(phq$data, Domain = "Mood"),
   mutate(gcbs$data, Domain = "Conspiracy Beliefs")
@@
          Parameter1 = fct_relevel(Parameter1, "Interoception", "Muscle", "Homeostasis", "Elimination", "Skin"),
-         Domain = fct_relevel(Domain, "Normal Personality", "Maladaptive Personality", "Autistic Traits", "Schizotypic Traits"),
-         Parameter2 = str_remove_all(Parameter2, "IPIP6_|PID5_|ASQ_|SPQ_|GCBS_"),
+         Domain = fct_relevel(Domain, "MAIA", "Normal Personality", "Maladaptive Personality", "Autistic Traits", "Schizotypic Traits"),
+         Parameter2 = str_remove_all(Parameter2, "MAIA_|IPIP6_|PID5_|ASQ_|SPQ_|GCBS_|PHQ4_"),
          Parameter2 = str_replace(Parameter2, "Sex", "Sex (Female vs. Male)"),
          Parameter2 = str_replace(Parameter2, "HonestyHumility", "Honesty-Humility"),
+         Parameter2 = str_replace(Parameter2, "AttentionRegulation", "Attention Regulation"),
+         Parameter2 = str_replace(Parameter2, "EmotionalAwareness", "Emotional Awareness"),
+         Parameter2 = str_replace(Parameter2, "SelfRegulation", "Self-Regulation"),
+         Parameter2 = str_replace(Parameter2, "BodyListening", "Body Listening"),
+         Parameter2 = str_replace(Parameter2, "NotWorrying", "Not Worrying"),
+         Parameter2 = str_replace(Parameter2, "NotDistracting", "Not Distracting"),
+         Parameter2 = str_replace(Parameter2, "NegativeAffect", "Negative Affect"),
+         Parameter2 = str_replace(Parameter2, "Patterns", "Patterns and Numbers"),
+         Parameter2 = str_replace(Parameter2, "Routine", "Routines"),
+         Parameter2 = str_replace(Parameter2, "LackSocialSkills", "Lack of Social Skills"),
+         Parameter2 = str_replace(Parameter2, "LowAttentionalSwitching", "Low Attentional Switching"),
+         Parameter2 = str_replace(Parameter2, "MagicalThinking", "Magical Thinking"),
+         Parameter2 = str_replace(Parameter2, "UnusualPerceptions", "Unusual Perceptions"),
+         Parameter2 = str_replace(Parameter2, "OddSpeech", "Odd Speech"),
+         Parameter2 = str_replace(Parameter2, "ConstrictedAffect", "Constricted Affect"),
+         Parameter2 = str_replace(Parameter2, "SocialAnxiety", "Social Anxiety"),
+         Parameter2 = str_replace(Parameter2, "NoCloseFriends", "No Close Friends"),
+         Parameter2 = str_replace(Parameter2, "GlobalConspiracies", "Global Conspiracies"),
+         Parameter2 = str_replace(Parameter2, "PersonalWellbeing", "Personal Wellbeing"),
+         Parameter2 = str_replace(Parameter2, "InformationControl", "Information Control"),
+         Parameter2 = str_replace(Parameter2, "GovernmentMalfeasance", "Government Malfeasance"),
+         Parameter2 = fct_reorder(Parameter2, rho),
          color = as.character(sign(rho))) |>
+  filter(Parameter2 != "Total") |> 
   ggplot(aes(x = rho, y = Parameter2)) +
@@
   scale_alpha_manual(values = c(0.2, 1)) +
-  scale_fill_gradient2(low = "#2196F3", high = "#FF5722", limits = c(-0.25, 0.25)) +
+  scale_fill_gradient2(low = "#2196F3", high = "#FF5722", limits = c(-0.4, 0.4)) +
   scale_colour_manual(values = c("#2196F3", "#FF5722")) +
-  scale_x_continuous(expand = c(0, 0)) +
-  coord_cartesian(xlim = c(-0.3, 0.3)) +
+  scale_x_continuous(expand = c(0, 0), breaks = c(-0.3, 0, 0.3)) +
+  coord_cartesian(xlim = c(-0.45, 0.45)) +
   labs(title = "Correlates of IAS-R Dimensions") +
@@
         strip.background.x = element_rect(fill = "#E0E0E0", color = "white"),
-        strip.text = element_text(face = "bold", size = rel(1)))
+        strip.text.x = element_text(face = "bold", size = rel(1.1)),
+        strip.text.y = element_text(face = "bold", size = rel(0.95)))
 p_cor

### 2023-02-09 paper/1_Initial/manuscript.Rmd
update with final sample

@@
 between the individual facet scores extracted from the final model and the MAIA-2 dimensions (administered online on a different session).
+All dimensions of the IAS-R correlated with all the MAIA facets with the notable exception of *Not-reacting* and *Not-worrying*.
 As all correlations are presented in **Figure 2**, we will focus in the following on a subset of key results.
@@
 This facet also negatively related to several pathological personality traits measured by the PID-5, such as *Psychoticism* ($TODO$), *Negative Affect* ($TODO$), and *Detachment* ($TODO$).
-In line with that, we also report negative relationships with schizotypical characteristics, including *Social Anxiety* ($TODO$), *Odd Speech*($TODO$), *No Close Friends* ($TODO$) and *Constricted Affect* ($TODO$); as well positive relationship with autistic traits, such as *Switching* ($TODO$) and *Social Skills* ($TODO$).
+In line with that, we also report negative relationships with schizotypical characteristics, including *Social Anxiety* ($TODO$), *Odd Speech*($TODO$), *No Close Friends* ($TODO$) and *Constricted Affect* ($TODO$); as well with autistic traits, including as *Switching* ($TODO$) and *Social Skills* ($TODO$).
 

### 2023-03-14 analysis.Rmd
add primals

@@
 export_table(pi$print)
+lie <- make_correlation(df[vars], select(df, starts_with("LIE_")))
+export_table(lie$print)
 gcbs <- make_correlation(df[vars], select(df, starts_with("GCBS_"))) 
@@
   mutate(phq$data, Domain = "Mood"),
-  mutate(gcbs$data, Domain = "Conspiracy Beliefs")
+  mutate(bpd$data, Domain = "Mood"),
+  mutate(gcbs$data, Domain = "Conspiracy Beliefs"),
+  mutate(pi$data, Domain = "World Beliefs"),
+  mutate(lie$data, Domain = "Lying Profile")
   # mutate(age$data, Domain = "Demographic"),
@@
          Parameter1 = fct_relevel(Parameter1, "Interoception", "Muscle", "Homeostasis", "Elimination", "Skin"),
-         Domain = fct_relevel(Domain, "MAIA", "Normal Personality", "Maladaptive Personality", "Autistic Traits", "Schizotypic Traits"),
-         Parameter2 = str_remove_all(Parameter2, "MAIA_|IPIP6_|PID5_|ASQ_|SPQ_|GCBS_|PHQ4_"),
+         Domain = fct_relevel(Domain, "MAIA", "Normal Personality", "Maladaptive Personality", "Autistic Traits", "Schizotypic Traits", "Mood", "Lying Profile", "Conspiracy Beliefs", "World Beliefs"),
+         Parameter2 = str_remove_all(Parameter2, "MAIA_|IPIP6_|PID5_|ASQ_|SPQ_|GCBS_|PHQ4_|LIE_|PI_"),
          Parameter2 = str_replace(Parameter2, "Sex", "Sex (Female vs. Male)"),
@@
   facet_grid(Domain~Parameter1, scales="free_y", switch ="y") +
-  scale_alpha_manual(values = c(0.2, 1)) +
+  scale_alpha_manual(values = c(0.3, 1)) +
   scale_fill_gradient2(low = "#2196F3", high = "#FF5722", limits = c(-0.4, 0.4)) +
@@
 fig <- ((wrap_elements(p_dens) + wrap_elements(p_efa)) / p_graph)
-ggsave("figures/Figure1.png", fig, width=fig.width, height=fig.width*1.3, dpi=150)
-ggsave("figures/Figure2.png", p_cor, width=21*0.35, height=29.7*0.35, dpi=150, bg="white")
+ggsave("figures/Figure1.png", fig, width=fig.width, height=fig.width*1.3, dpi=200)
+ggsave("figures/Figure2.png", p_cor, width=21*0.35, height=29.7*0.44, dpi=200, bg="white")
 ```

### 2023-03-25 paper/1_Initial/manuscript.Rmd
links

@@
 
-Interoception - definition - is the trending topic. 
+Interoception - definition - is a trending topic, becoming a central mechanism of embodied cognition, and showing a key contribution to higher order processes such as .... 
 Unfortunately, it is also notably hard to measure.
@@
 Scales are useful to capture metacognitive and subjective aspects and beliefs
-While the relationship between scales and tasks is a strong point of contention, it is important to continue developing sound scales from a structural (i.e., factorial) standpoint.
+While the relationship between interoceptive scales and tasks is a strong point of contention, it is important to continue developing sound scales from a structural (i.e., factorial) standpoint.
 
-One of the most recent scale is the IAS, which is interesting because... It has *n* items, such as ...
+One of the most recent scale developped is the IAS, which is interesting because... It has *n* items, such as ...
 However, the study analysis did not go in depth in the analysis of the factor structure, focusing instead on ....
 
-The purpose of this work is to re-analyze the factor structure of the scale using complementary statistical approaches.
-and propose a revised version.
-And to compare it with one of the most popular questionnaire of interoception, the MAIA-2 (*ref*).
+The purpose of this work is to re-analyze the factor structure of the scale using complementary statistical approaches, a further extend its validation by comparing a revised version with one of the most popular questionnaire of interoception, the MAIA-2 (*ref*), as well as other relevant indices (such as psychopathological traits).
 
@@
 
+One of the most intriguing new results was the reilationship between interoceptive abilities and several specific primal world beliefs.
+
 \newpage
@@
 
-**Scoring**. Each scale can be answered on an analog scale (Disagree - Agree). Items can be averaged per dimension, and dimensions can be averaged to get a general Interoception score.
+**Scoring**. Each scale can be answered on an analogue scale (Disagree - Agree). Items can be averaged per dimension, and dimensions can be averaged to get a general Interoception score.
 

### 2023-10-15 analysis/analysis.Rmd
put analysis in folder

--- 2023-03-14 analysis.Rmd
@@
 
-df <- haven::read_sav("data/Study 1.sav") |> 
+df <- haven::read_sav("../data/Study 1.sav") |> 
   mutate_all(as.numeric) |> 
@@
 ```{r, message=FALSE, warning=FALSE, results='asis'}
-df2 <- haven::read_sav("data/Study 6 IAS.sav") |> 
+df2 <- haven::read_sav("../data/Study 6 IAS.sav") |> 
   mutate_all(as.numeric) |> 
@@
 ```{r, message=FALSE, warning=FALSE}
-semTools::compRelSEM(cfa4h)
+semTools::compRelSEM(cfa4h, higher="Interoception")
 ```
@@
 scores$Participant <- df3$Participant
-write.csv(scores, "data/IASR_scores.csv", row.names = FALSE)
+write.csv(scores, "../data/IASR_scores.csv", row.names = FALSE)
 ```
@@
   mutate(gcbs$data, Domain = "Conspiracy Beliefs"),
-  mutate(pi$data, Domain = "World Beliefs"),
+  mutate(pi$data, Domain = "Primal World Beliefs"),
   mutate(lie$data, Domain = "Lying Profile")

### 2023-10-15 paper/1_Initial/manuscript.Rmd
minor

@@
 title             : "**The Revised Interoceptive Accuracy Scale (IAS-R) Confirms Links between Interoception and Personality and Psychopathological Traits**"
-shorttitle        : "PHQ-4R"
+shorttitle        : "IAS-R"
 author:
@@
 
-The purpose of this work is to re-analyze the factor structure of the scale using complementary statistical approaches, a further extend its validation by comparing a revised version with one of the most popular questionnaire of interoception, the MAIA-2 (*ref*), as well as other relevant indices (such as psychopathological traits).
+The purpose of this work is to reanalyse the factor structure of the scale using complementary statistical approaches, a further extend its validation by comparing a revised version with one of the most popular questionnaire of interoception, the MAIA-2 (*ref*), as well as other relevant indices (such as psychopathological traits).
 
-# Study 1
+# Study 1 - Reanalysis of Murphy et al. (2020)
 
-Study 1 is a re-analysis of the data from @murphy2020testing regarding the factor structure of the Interoceptive Accuracy Scale (IAS).
-The aim is to use a finer-grained method for estimating the optimal number of latent factors [namely, the *Method Agreement Procedure*, in @ludecke2020extracting; @makowski2018psycho], and perform a statistical model comparison using Confirmatory Factor Analysis (CFA).
+Study 1 is a reanalysis of the data from @murphy2020testing regarding the factor structure of the Interoceptive Accuracy Scale (IAS).
+The aim is to use a more fine-grained method for estimating the optimal number of latent factors [namely, the *Method Agreement Procedure*, in @ludecke2020extracting; @makowski2018psycho], and perform a statistical model comparison using Confirmatory Factor Analysis (CFA).
 
@@
 
-The *Method Agreement Procedure* suggested 1 latent factor as optimal, supported by 5 (31.25%) out of 16 methods (Bentler, Acceleration factor, Scree (R2), VSS complexity 1, Velicer's MAP), followed by 4 factors supported by 4 methods (Kaiser criterion, beta score, optimal coordinates, parallel analysis).
+The *Method Agreement Procedure* suggested 1 latent factor as optimal, supported by 5 (31.25%) out of 16 methods (Bentler, Acceleration factor, Scree - R2, VSS complexity 1, Velicer's MAP), followed by 4 factors supported by 4 methods (Kaiser criterion, beta score, optimal coordinates, parallel analysis).
 
@@
 
-Finally, we re-fitted the CFA models on a new data set [study 6 of @murphy2020testing], which confirmed that the 5-factor balanced model had the better fit relative to the other models ($BIC_{CFA-5mod} = 17316; BIC_{CFA-5h} = 17323; BIC_{CFA-5} = 18257; BIC_{EFA-4mod} = 18265$).
+Finally, we re-fitted the CFA models on a new dataset [sample 2, from study 6 of @murphy2020testing], which confirmed that the 5-factor balanced model had the better fit relative to the other models ($BIC_{CFA-5mod} = 17316; BIC_{CFA-5h} = 17323; BIC_{CFA-5} = 18257; BIC_{EFA-4mod} = 18265$).
 However, the final model had poor to barely acceptable absolute indices of fit in both samples (Sample 1: $RMSEA = .067$ (acceptable < .08), $CFI = .878$ (acceptable > .9), $SRMR = .057$ (acceptable < .08); Sample 2: $RMSEA = .068$, $CFI = .906$, $SRMR = .063$).
@@
 
-# Study 2
+# Study 2 - Online validation of new structure
 
@@
 
-One of the most intriguing new results was the reilationship between interoceptive abilities and several specific primal world beliefs.
+<!-- One of the most intriguing new results was the relationship between interoceptive abilities and several specific primal world beliefs. -->
 

### 2023-10-15 analysis/analysis.Rmd
minor

@@
 ---
-title: "PHQ-4-R: Adaptation of the 4-item screening for Anxiety and Depression for a subclinical sensitivity"
+title: "Revised Interoceptive Accuracy Scale (IAS-R)"
 subtitle: "Analysis"
@@
 ```
+
+### CFA
 

### 2024-02-13 analysis/analysis.qmd
update analysis

---
title: "Revised Interoceptive Accuracy Scale (IAS-R)"
subtitle: "Analysis"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: true
    toc: true
    fig-dpi: 300
    fig-width: 11.33
execute: 
  cache: true
---

```{r}
#| message: false
#| warning: false

library(tidyverse)
library(easystats)
library(patchwork)
library(lavaan)
library(ggraph)
library(tidySEM)
library(EGAnet)
```

## Study 1 - Reanalysis of Murphy et al. (2020)

Reanalyze their data to confirm the factor structure of the IAS.

### Data Preparation

```{r}
# https://osf.io/3m5nh
df1 <- haven::read_sav("../data/Murphy2020/Study 1.sav") |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(Gender == 1, "Male", ifelse(Gender == 2, "Female", "Other"))))

# https://osf.io/3m5nh
df2 <- haven::read_sav("../data/Murphy2020/Study 6 IAS.sav") |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(Gender == 1, "Male", ifelse(Gender == 2, "Female", "Other"))))

# Campos (2022) - Study 1 (https://osf.io/j6ef3)
df3 <- haven::read_sav("../data/Campos2022/Dataset_Test.sav") |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(Sex == 1, "Male", ifelse(Sex == 0, "Female", "Other")))) |> 
  rename(Heart=IAS1, Hungry=IAS2, Breathing=IAS3, Thirsty=IAS4,
         Urinate=IAS5, Defecate=IAS6, Taste=IAS7, Vomit=IAS8, Sneeze=IAS9,
         Cough=IAS10, Temp=IAS11, Sex_arousal=IAS12, Wind=IAS13, Burp=IAS14,
         Muscles=IAS15, Bruise=IAS16, Pain=IAS17, Blood_Sugar=IAS18,
         Affective_touch=IAS19, Tickle=IAS20, Itch=IAS21)

# https://osf.io/3eztd
df4 <- haven::read_sav("../data/Lin2023/Study 1 & 3.sav") |> 
  mutate(Gender = as.character(ifelse(sex_dummy == 1, "Male", ifelse(sex_dummy == 0, "Female", "Other")))) |> 
  rename(Age=age, 
         Heart=Heart, Hungry=HUNGR, Breathing=BREAT, Thirsty=Thirs,
         Urinate=URINA, Defecate=Defec, Taste=TASTE, Vomit=VOMIT, Sneeze=Sneez,
         Cough=COUGH, Temp=TEMPE, Sex_arousal=SEXAR, Wind=WIND, Burp=Burp,
         Muscles=MUSCL, Bruise=Bruis, Pain=PAIN, Blood_Sugar=BloSu,
         Affective_touch=Touch, Itch=ITCH)  # No tickle because same Chinese character

# https://osf.io/3eztd
df5 <- haven::read_sav("../data/Lin2023/Study 2.sav") |> 
  mutate(Gender = as.character(ifelse(Sex == "男", "Male", ifelse(Sex == "女", "Female", "Other")))) |> 
  rename(Heart=Heart, Hungry=HUNGR, Breathing=BREAT, Thirsty=Thirs,
         Urinate=URINA, Defecate=Defec, Taste=TASTE, Vomit=VOMIT, Sneeze=Sneez,
         Cough=COUGH, Temp=TEMPE, Sex_arousal=SEXAR, Wind=WIND, Burp=Burp,
         Muscles=MUSCL, Bruise=Bruis, Pain=PAIN, Blood_Sugar=BloSu,
         Affective_touch=Touch, Itch=ITCH)  # No tickle because same Chinese character

df6 <- read.csv("https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv") |>
  rename(Heart=IAS_1, Hungry=IAS_2, Breathing=IAS_3, Thirsty=IAS_4, 
         Urinate=IAS_5, Defecate=IAS_6, Taste=IAS_7, Vomit=IAS_8, Sneeze=IAS_9, 
         Cough=IAS_10, Temp=IAS_11, Sex_arousal=IAS_12, Wind=IAS_13, Burp=IAS_14,
         Muscles=IAS_15, Bruise=IAS_16, Pain=IAS_17, Blood_Sugar=IAS_18,
         Affective_touch=IAS_19, Tickle=IAS_20, Itch=IAS_21)

df7 <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |>
  rename(Gender=Sex, Heart=Item_IAS_Interoception_1, Hungry=Item_IAS_Interoception_2, 
         Breathing=Item_IAS_Interoception_3, Thirsty=Item_IAS_Interoception_4, 
         Temp=Item_IAS_Interoception_5, Sex_arousal=Item_IAS_Interoception_6,
         Urinate=Item_IAS_Elimination_1, Defecate=Item_IAS_Elimination_2,
         Vomit=Item_IAS_Elimination_3, Wind=Item_IAS_Expulsion_1, 
         Burp=Item_IAS_Expulsion_2, Sneeze=Item_IAS_Expulsion_3,
         Muscles=Item_IAS_Nociception_1, Bruise=Item_IAS_Nociception_2,
         Pain=Item_IAS_Nociception_3, Affective_touch=Item_IAS_Skin_1, 
         Tickle=Item_IAS_Skin_2, Itch=Item_IAS_Skin_3) |>
  filter(!is.na(Urinate))
```

### Participants

- **Sample 1**: Data from Murphy's (2020) [study 1](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769), downloaded from OSF, included `r report::report_participants(df1, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 2**: Data from Murphy's (2020) [study 6](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769), downloaded from OSF, included `r report::report_participants(df2, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 3**: Data from Campos' (2022) [study 1](https://osf.io/j6ef3), downloaded from OSF, included `r report::report_participants(df3, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 4**: Data from Lin's (2023) [study 1 and 3](#ttps://osf.io/3eztd), downloaded from OSF, included `r report::report_participants(df4, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 5**: Data from Lin's (2023) [study 2](#ttps://osf.io/3eztd), downloaded from OSF, included `r report::report_participants(df5, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 6**: New dataset from [Makowski (under preparation)](https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv), included `r report::report_participants(df6, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7**: New dataset from [Makowski (under preparation)](https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv), included `r report::report_participants(df7, age = "Age", sex = NA, gender = "Gender")`.

Total N = `r nrow(df1) + nrow(df2) + nrow(df3) + nrow(df4) + nrow(df5) + nrow(df6) + nrow(df7)`.

### Descriptive

#### Distribution

```{r}
vars <- c("Heart", "Hungry", "Breathing", "Thirsty", "Urinate", "Defecate", "Taste", "Vomit", "Sneeze", "Cough", "Temp",
          "Sex_arousal", "Wind", "Burp", "Muscles", "Bruise", "Pain", "Blood_Sugar", "Affective_touch", "Tickle", "Itch")

dens1 <- estimate_density(select(df1, all_of(vars)), method="kernSmooth") |> 
  mutate(Sample = "Sample 1")
dens2 <- estimate_density(select(df2, all_of(vars)), method="kernSmooth") |> 
  mutate(Sample = "Sample 2")
dens3 <- estimate_density(select(df3, all_of(vars)), method="kernSmooth") |> 
  mutate(Sample = "Sample 3")
dens4 <- estimate_density(select(df4, all_of(setdiff(vars, "Tickle"))), method="kernSmooth") |> 
  mutate(Sample = "Sample 4")
dens5 <- estimate_density(select(df5, all_of(setdiff(vars, "Tickle"))), method="kernSmooth") |> 
  mutate(Sample = "Sample 5")
dens6 <- estimate_density(select(df6, all_of(vars)), method="kernSmooth") |> 
  mutate(Sample = "Sample 6")
dens7 <- estimate_density(select(df7, all_of(setdiff(vars, c("Taste", "Cough", "Blood_Sugar")))), method="kernSmooth") |> 
  mutate(Sample = "Sample 7")

rbind(dens1, dens2, dens3, dens4, dens5, dens6, dens7) |> 
  ggplot(aes(x = x, y = y, color = Parameter)) +
  geom_line() +
  theme_minimal() +
  labs(title = "Distribution of Responses", x = "Response", y = "Density", color = "Item") +
  facet_wrap(~Sample, scales = "free", nrow=4)
```

```{r}
data1 <- normalize(select(df1, all_of(dens1$Parameter)), range=c(1, 5))
data2 <- normalize(select(df2, all_of(dens2$Parameter)), range=c(1, 5))
data3 <- normalize(select(df3, all_of(dens3$Parameter)), range=c(1, 5))
data4 <- normalize(select(df4, all_of(dens4$Parameter)), range=c(1, 5))
data5 <- normalize(select(df5, all_of(dens5$Parameter)), range=c(1, 5))
data6 <- select(df6, all_of(dens6$Parameter))
data7 <- select(df7, all_of(dens7$Parameter))

data_all <- rbind(data1, data2, data3, 
                  mutate(data4, Tickle=NA), mutate(data5, Tickle=NA), 
                  data6, mutate(data7, Taste=NA, Cough=NA, Blood_Sugar=NA)) 
```

#### Correlations

An overall positive intercorrelation pattern, with no clear structure emerging.

::: {.panel-tabset}

##### All data

```{r}
make_correlation <- function(df) {
  correlation::correlation(df, redundant=TRUE) |> 
    correlation::cor_sort() |> 
    correlation::cor_lower() |> 
    mutate(val = paste0(insight::format_value(r), format_p(p, stars_only=TRUE))) |>
    mutate(Parameter2 = fct_rev(Parameter2)) |>
    ggplot(aes(x=Parameter1, y=Parameter2)) +
    geom_tile(aes(fill = r), color = "white") +
    geom_text(aes(label = val), size = 3) +
    labs(title = "Correlation Matrix") +
    scale_fill_metro_c(limit = c(0, 0.75), guide = guide_colourbar(ticks=FALSE)) +
    theme_minimal() +
    theme(legend.title = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_text(angle = 45, hjust = 1))
}

make_correlation(data_all)
```

##### Sample 1

```{r}
make_correlation(data1)
```

##### Sample 2

```{r}
make_correlation(data2)
```

##### Sample 3

```{r}
make_correlation(data3)
```

##### Sample 4

```{r}
make_correlation(data4)
```

##### Sample 5

```{r}
make_correlation(data5)
```

##### Sample 6

```{r}
make_correlation(data6)
```

##### Sample 7

```{r}
make_correlation(data7)
```

:::

### EGA

See https://r-ega.net/articles/ega.html for details.

#### Unique Variable Analysis (UVA)

::: {.panel-tabset}

##### All data

```{r}
uva <- EGAnet::UVA(data = data_all, cut.off = 0.3)
uva
uva$keep_remove
```

##### Sample 1

```{r}
uva <- EGAnet::UVA(data = data1, cut.off = 0.3)
uva
uva$keep_remove
```

##### Sample 2

```{r}
uva <- EGAnet::UVA(data = data2, cut.off = 0.3)
uva
uva$keep_remove
```

##### Sample 3

```{r}
uva <- EGAnet::UVA(data = data3, cut.off = 0.3)
uva
uva$keep_remove
```

##### Sample 4

```{r}
uva <- EGAnet::UVA(data = data4, cut.off = 0.3)
uva
uva$keep_remove
```

##### Sample 5

```{r}
uva <- EGAnet::UVA(data = data5, cut.off = 0.3)
uva
uva$keep_remove
```

##### Sample 6

```{r}
uva <- EGAnet::UVA(data = data6, cut.off = 0.3)
uva
uva$keep_remove
```

##### Sample 7

```{r}
uva <- EGAnet::UVA(data = data7, cut.off = 0.3)
uva
uva$keep_remove
```

:::

#### Item Stability

```{r ega1}
#| fig-height: 20
#| fig-width: 12

plots <- list()
for(model in c("glasso", "TMFG")) {
  for(algo in c("walktrap", "louvain")) {
    for(type in c("ega", "ega.fit")) {  # "hierega"
      print(type)
      ega <- EGAnet::bootEGA(
        data = data_all,
        seed=123,
        model=model,
        algorithm=algo,
        EGA.type=type,
        type="resampling",
        plot.itemStability=FALSE,
        verbose=FALSE)
      plots[[length(plots) + 1]] <- plot(ega) + 
        labs(title = paste0(model, " (", algo, ") - ", type))
      }
    }
}

length(plots)
patchwork::wrap_plots(plots, nrow = 4)
```

<!-- ::: {.panel-tabset} -->

<!-- ##### glasso model (Walktrap) -->

<!-- ```{r ega1} -->
<!-- #| fig-height: 12 -->

<!-- plots <- list() -->
<!-- for(d in list(data1, data2, data3, data4, data5, data6)) { -->
<!--   ega <- EGAnet::bootEGA( -->
<!--     data = d, -->
<!--     seed=123, -->
<!--     model="glasso", -->
<!--     algorithm="walktrap", -->
<!--     type="resampling", -->
<!--     EGA.type="ega", -->
<!--     plot.itemStability=FALSE,  -->
<!--     verbose=FALSE) -->
<!--   plots[[length(plots) + 1]] <- plot(ega) -->
<!-- } -->

<!-- EGAnet::dimensionStability(ega) -->
<!-- (plots[[1]] + labs(title = "Sample 1") + -->
<!--   plots[[2]] + labs(title = "Sample 2")) / -->
<!--   (plots[[3]] + labs(title = "Sample 3") + -->
<!--   plots[[4]] + labs(title = "Sample 4")) / -->
<!--   (plots[[5]] + labs(title = "Sample 5") + -->
<!--   plots[[6]] + labs(title = "Sample 6")) -->
<!-- ``` -->

<!-- ##### glasso model (Louvain) -->

<!-- ```{r ega2} -->
<!-- #| fig-height: 12 -->

<!-- plots <- list() -->
<!-- for(d in list(data1, data2, data3, data4, data5, data6)) { -->
<!--   ega <- EGAnet::bootEGA( -->
<!--     data = d, -->
<!--     seed=123, -->
<!--     model="glasso", -->
<!--     algorithm="louvain", -->
<!--     plot.itemStability=FALSE) -->
<!--   plots[[length(plots) + 1]] <- plot(ega) -->
<!-- } -->

<!-- (plots[[1]] + labs(title = "Sample 1") + -->
<!--   plots[[2]] + labs(title = "Sample 2")) / -->
<!--   (plots[[3]] + labs(title = "Sample 3") + -->
<!--   plots[[4]] + labs(title = "Sample 4")) / -->
<!--   (plots[[5]] + labs(title = "Sample 5") + -->
<!--   plots[[6]] + labs(title = "Sample 6")) -->
<!-- ``` -->

<!-- ##### TMFG model (Walktrap) -->

<!-- ```{r ega3} -->
<!-- #| fig-height: 12 -->

<!-- plots <- list() -->
<!-- for(d in list(data1, data2, data3, data4, data5, data6)) { -->
<!--   ega <- EGAnet::bootEGA( -->
<!--     data = d, -->
<!--     seed=123, -->
<!--     model="TMFG", -->
<!--     algorithm="walktrap", -->
<!--     plot.itemStability=FALSE) -->
<!--   plots[[length(plots) + 1]] <- plot(ega) -->
<!-- } -->

<!-- (plots[[1]] + labs(title = "Sample 1") + -->
<!--   plots[[2]] + labs(title = "Sample 2")) / -->
<!--   (plots[[3]] + labs(title = "Sample 3") + -->
<!--   plots[[4]] + labs(title = "Sample 4")) / -->
<!--   (plots[[5]] + labs(title = "Sample 5") + -->
<!--   plots[[6]] + labs(title = "Sample 6")) -->
<!-- ``` -->

<!-- ##### TMFG model (Louvain) -->

<!-- ```{r ega4} -->
<!-- #| fig-height: 12 -->

<!-- plots <- list() -->
<!-- for(d in list(data1, data2, data3, data4, data5, data6)) { -->
<!--   ega <- EGAnet::bootEGA( -->
<!--     data = d, -->
<!--     seed=123, -->
<!--     model="TMFG", -->
<!--     algorithm="louvain", -->
<!--     plot.itemStability=FALSE) -->
<!--   plots[[length(plots) + 1]] <- plot(ega) -->
<!-- } -->

<!-- (plots[[1]] + labs(title = "Sample 1") + -->
<!--   plots[[2]] + labs(title = "Sample 2")) / -->
<!--   (plots[[3]] + labs(title = "Sample 3") + -->
<!--   plots[[4]] + labs(title = "Sample 4")) / -->
<!--   (plots[[5]] + labs(title = "Sample 5") + -->
<!--   plots[[6]] + labs(title = "Sample 6")) -->
<!-- ``` -->

<!-- ##### All data -->

<!-- ```{r ega1} -->
<!-- #| fig-height: 12 -->

<!-- plots <- list() -->
<!-- for(model in c("glasso", "TMFG")) { -->
<!--   for(algo in c("walktrap", "louvain")) { -->
<!--     ega <- EGAnet::bootEGA( -->
<!--       data = data_all, -->
<!--       seed=123, -->
<!--       model=model, -->
<!--       algorithm=algo, -->
<!--       plot.itemStability=FALSE) -->
<!--     plots[[length(plots) + 1]] <- plot(ega) +  -->
<!--       labs(title = paste0(model, " (", algo, ")")) -->
<!--   } -->
<!-- } -->

<!-- patchwork::wrap_plots(plots) -->
<!-- ``` -->

<!-- ::: -->

### Exploratory Factor Analysis (EFA)

#### How Many Factors

::: {.panel-tabset}

##### All data

```{r}
n <- parameters::n_factors(data_all, n_max = 12)

plot(n)

knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 4, 5 ), ], row.names = FALSE)
```

##### Sample 1

```{r}
n <- parameters::n_factors(data1, n_max = 12)

plot(n)
knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 4), ], row.names = FALSE)
```

##### Sample 2

```{r}
n <- parameters::n_factors(data2, n_max = 12)

plot(n)
knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 4), ], row.names = FALSE)
```

##### Sample 3

```{r}
n <- parameters::n_factors(data3, n_max = 12)

plot(n)

knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 4), ], row.names = FALSE)
```

##### Sample 4

```{r}
n <- parameters::n_factors(data4, n_max = 12)

plot(n)

knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 4), ], row.names = FALSE)
```

##### Sample 5

```{r}
n <- parameters::n_factors(data5, n_max = 12)

plot(n)

knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 4), ], row.names = FALSE)
```

##### Sample 6

```{r}
n <- parameters::n_factors(data6, n_max = 12)

plot(n)

knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 4), ], row.names = FALSE)
```

##### Sample 7

```{r}
n <- parameters::n_factors(data7, n_max = 12)

plot(n)

knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 4), ], row.names = FALSE)
```

:::

#### EFA Models

::: {.panel-tabset}

##### All data

```{r}
#| fig-height: 10

efa5 <- parameters::factor_analysis(data_all, n=5, rotation = "oblimin", sort = TRUE)
plot(efa5)

display(efa5)
```

##### Sample 1

```{r}
#| fig-height: 10

efa4 <- parameters::factor_analysis(data2, n=4, rotation = "oblimin", sort = TRUE)
plot(efa4)

display(efa4)
```

##### Sample 2

```{r}
#| fig-height: 10

efa4 <- parameters::factor_analysis(data2, n=4, rotation = "oblimin", sort = TRUE)
plot(efa4)

display(efa4)
```

##### Sample 3

```{r}
#| fig-height: 10

efa4 <- parameters::factor_analysis(data3, n=4, rotation = "oblimin", sort = TRUE)
plot(efa4)

display(efa4)
```

##### Sample 4

```{r}
#| fig-height: 10

efa5 <- parameters::factor_analysis(data4, n=5, rotation = "oblimin", sort = TRUE)
plot(efa5)

display(efa5)
```

##### Sample 5

```{r}
#| fig-height: 10

efa5 <- parameters::factor_analysis(data5, n=5, rotation = "oblimin", sort = TRUE)
plot(efa5)

display(efa5)
```

##### Sample 6

```{r}
#| fig-height: 10

efa4 <- parameters::factor_analysis(data5, n=4, rotation = "oblimin", sort = TRUE)
plot(efa4)

display(efa4)
```

:::

### Model Construction

#### Structure

```{r}
m1 <- "
Interoception =~ Hungry + Thirsty + Urinate + Defecate + Itch + Bruise + Muscles + Pain + Breathing + Heart + Cough + Sneeze + Wind + Burp
"

m7 <- "
# ----
Sustenance =~ Hungry + Thirsty
Elimination =~ Urinate + Defecate
Skin =~ Itch + Bruise
Nociception =~ Muscles + Pain
Affect =~ Breathing + Heart
# ----
Expulsion =~ Cough + Sneeze + Wind + Burp

# --- 
# Ambiguous: Temp + Vomit + Affective_touch + Sex_arousal + Taste
# Discard: Tickle + Blood_Sugar
"

m8 <- "
# ----
Sustenance =~ Hungry + Thirsty
Elimination =~ Urinate + Defecate
Skin =~ Itch + Bruise
Nociception =~ Muscles + Pain
Affect =~ Breathing + Heart
# ----
Expulsion_Sudden =~ Cough + Sneeze 
Expulsion_Gastric =~ Wind + Burp
" 
# Ambiguous: Temp + Vomit + Affective_touch + Sex_arousal + Taste
# Discard: Tickle + Blood_Sugar

m1_all <- lavaan::cfa(m1, data = data_all)
m7_all <- lavaan::cfa(m7, data = data_all)
m8_all <- lavaan::cfa(m8, data = data_all)

anova(m1_all, m7_all, m8_all) |> 
  parameters::parameters() |> 
  display()
```

#### Higher Order Factors

```{r}
m8h1 <- paste0(m8, "
              Interoception =~ Sustenance + Elimination + Skin + Nociception + Affect + Expulsion_Sudden + Expulsion_Gastric
              ")

m8h3 <- paste0(m8, "
              Valenced =~ Nociception + Affect + Skin
              Expulsion =~ Expulsion_Sudden + Expulsion_Gastric 
              Homeostasis =~ Sustenance + Elimination
              ")

m8h1_all <- lavaan::cfa(m8h1, data = data_all)
m8h3_all <- lavaan::cfa(m8h3, data = data_all)
anova(m8_all, m8h1_all, m8h3_all) |> 
  parameters::parameters() |> 
  display()
```

#### Model Performance

```{r}
#| warning: false

rbind(
  performance::performance(m8_all, metrics=c("Chi2", "RMSEA", "CFI", "SRMR")) |> 
    mutate(Sample = "All"),
  performance::performance(update(m8_all, data=data1), metrics=c("Chi2", "RMSEA", "CFI", "SRMR")) |> 
    mutate(Sample = "Sample 1"),
  performance::performance(update(m8_all, data=data2), metrics=c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 2"),
  performance::performance(update(m8_all, data=data3), metrics=c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 3"),
  performance::performance(update(m8_all, data=data4), metrics=c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 4"),
  performance::performance(update(m8_all, data=data5), metrics=c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 5"),
  performance::performance(update(m8_all, data=data6), metrics=c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 6"),
  performance::performance(lavaan::cfa(str_remove(m8, fixed("\nExpulsion_Sudden =~ Cough + Sneeze")), data=data7), metrics=c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 7")
) |> 
  display()
```

No evidence for higher order factors. The unidimensionality might be a byproduct of the similarities in phrasing of the items.

## Study 2 - Correlates

```{r}
#| warning: false

df1 <- cbind(df1, as.data.frame(predict(lavaan::cfa(m8, data = data1)))) |> 
  mutate(Sample = "Sample 1")
df2 <- cbind(df2, as.data.frame(predict(lavaan::cfa(m8, data = data2)))) |> 
  mutate(Sample = "Sample 2")
df3 <- cbind(df3, as.data.frame(predict(lavaan::cfa(m8, data = data3)))) |> 
  mutate(Sample = "Sample 3")
df4 <- cbind(df4, as.data.frame(predict(lavaan::cfa(m8, data = data4)))) |> 
  mutate(Sample = "Sample 4")
df5 <- cbind(df5, as.data.frame(predict(lavaan::cfa(m8, data = data5)))) |> 
  mutate(Sample = "Sample 5")
df6 <- cbind(df6, as.data.frame(predict(lavaan::cfa(m8, data = data6)))) |> 
  mutate(Sample = "Sample 6")
df7 <- cbind(df7, as.data.frame(predict(lavaan::cfa(str_remove(m8, fixed("\nExpulsion_Sudden =~ Cough + Sneeze")), data = data7)))) |> 
  mutate(Sample = "Sample 7", Expulsion_Sudden = NA)

vars <- names(as.data.frame(predict(m8_all)))
```

### Demographics

```{r}
df_demo <- rbind(
  select(df1, Sample, Age, Gender, all_of(vars)),
  select(df2, Sample, Age, Gender, all_of(vars)),
  select(df3, Sample, Age, Gender, all_of(vars)),
  select(df4, Sample, Age, Gender, all_of(vars)),
  select(df5, Sample, Age, Gender, all_of(vars)),
  select(df6, Sample, Age, Gender, all_of(vars)),
  select(df7, Sample, Age, Gender, all_of(vars))
)

make_lm_data <- function(df, vars, predictor="Age") {
  dat <- data.frame()
  for(resp in vars) {
      if(length(unique(df$Sample)) == 1) {
        m <- lm(as.formula(paste0(resp, " ~ ", predictor)), data = df)
        param <- parameters::parameters(m)[2, ] |> 
          mutate(Sample = unique(df$Sample)) |> 
          select(-Parameter)
      } else {
        m <- lm(as.formula(paste0(resp, " ~ Sample / ", predictor)), data = df)
        param <- parameters::parameters(m) |> 
          filter(str_detect(Parameter, ":")) |> 
          separate(Parameter, c("Predictor", "Sample"), sep = "Sample ") |> 
          mutate(Sample = paste0("Sample ", str_remove(Sample, fixed(paste0(":", predictor)))))
      }

      dat <- param |> 
        mutate(Predictor = predictor,
               Repsonse = resp,
               t_low = CI_low / SE,
               t_high = CI_high / SE) |> 
        rbind(dat)
  }
  dat
}

data <- rbind(
  make_lm_data(df_demo, vars, predictor="Age"),
  make_lm_data(filter(df_demo, Gender %in% c("Male", "Female")), vars, predictor="Gender")
)
```

### BPQ

```{r}
x <- intersect(names(df3)[str_detect(names(df3), "BPQ")], 
               names(df4)[str_starts(names(df4), "BPQ")])

df_bpq <- rbind(
  select(df3, Sample, all_of(x), all_of(vars)),
  select(df4, Sample, all_of(x), all_of(vars))
)

# estimate_density(select(df_bpq, Sample, starts_with("BPQ")), at="Sample")  |> 
#   plot() +
#   facet_grid(~Sample)

plot(parameters::n_components(select(df_bpq, starts_with("BPQ"))))
df_bpq$BPQ_PCA1 <- predict(parameters::principal_components(select(df_bpq, starts_with("BPQ")), n=1))$PC1

data <- rbind(data,
              make_lm_data(df_bpq, vars, predictor="BPQ_PCA1"))

# Why opposite effects?
```

### TAS

```{r}
x <- intersect(names(df3)[str_detect(names(df3), "TAS")], 
               names(df5)[str_starts(names(df5), "TAS")])
```

### PHQ

```{r}
names(df5)[str_detect(names(df5), "PHQ")]

data <- rbind(data,
              make_lm_data(df5, vars, predictor="PHQ9_sum"),
              make_lm_data(df5, vars, predictor="PHQ15_sum"))
```

### BDI

```{r}
# names(df1)
# names(df2)
# names(df3)  # TAS, BPQ
# names(df4)  # BPQ
# names(df5)  # PHQ, TAS
# names(df6)  # BDI, STAI
# names(df7)  # MAIA

data <- rbind(data,
              make_lm_data(df6, vars, predictor="BDI2_Total"))
```

### Summary

```{r}
#| fig-height: 20

data |> 
  mutate(sig = ifelse(p < .01, "p < .01", ifelse(p < .001, "p < .001", "N.S."))) |> 
  ggplot(aes(x=Predictor)) +
  geom_hline(yintercept=0, linetype="dashed") +
  geom_pointrange(aes(y=t, ymin=t_low, ymax=t_high, color=sig), position=position_dodge2(width=0.3)) +
  facet_grid(~Repsonse, scales = "free_y") +
  coord_flip()
```

## Discussion

Benefits of the IAS:
- Straightforward and sensation-centered items

Recommendations:
- Remove Itch (redundant + issue in Chinese)
- Use analog scales

Limitations:
- Not much clear theorethical or empirical structure (small grouping of items)
- Limited variability (clear mode at 4/5)
- Ambiguous items which grouping depends on the context (and its awareness)
  - E.g., heart beating fast, vomit when nauseaous
- Few items for some modalities (e.g., 1 for heart)
- Positive phrasing: benefits but also might exacerbate positivity bias (and thus unidimensionality)

Need for context-specific items (cross-modal when possible, i.E., cardioception, respiroception, etc.).

New Scale: Multimodal Interoceptive Sensitivity Scale (MISS)

### 2024-02-13 analysis/old/analysis.Rmd
update analysis

--- 2023-10-15 analysis/analysis.Rmd
@@
 
-df <- haven::read_sav("../data/Study 1.sav") |> 
+df <- haven::read_sav("../../data/Murphy2020/Study 1.sav") |> 
   mutate_all(as.numeric) |> 
@@
 ```{r, message=FALSE, warning=FALSE, results='asis'}
-df2 <- haven::read_sav("../data/Study 6 IAS.sav") |> 
+df2 <- haven::read_sav("../../data/Murphy2020/Study 6 IAS.sav") |> 
   mutate_all(as.numeric) |> 
@@
 ```{r, message=FALSE, warning=FALSE, results='asis'}
-# df <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |>
-df3 <- read.csv("../IllusionGameReliability/data/preprocessed_questionnaires.csv") |>
+df3 <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |>
   select(Participant, Sex, Age, starts_with("Item_IAS")) |> 
@@
 scores$Participant <- df3$Participant
-write.csv(scores, "../data/IASR_scores.csv", row.names = FALSE)
+write.csv(scores, "IASR_scores.csv", row.names = FALSE)
 ```
@@
 ```{r, message=FALSE, warning=FALSE}
-df <- read.csv("../IllusionGameReliability/data/preprocessed_questionnaires.csv") |> 
-  merge(read.csv("data/IASR_scores.csv"), by="Participant") |> 
+df <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |> 
+  merge(read.csv("IASR_scores.csv"), by="Participant") |> 
   select(-ends_with("_RT"), -ends_with("_SD"))

### 2024-02-13 paper/1_Initial/old/manuscript.Rmd
update analysis

--- 2023-10-15 paper/1_Initial/manuscript.Rmd
@@
 
-Interoception - definition - is a trending topic, becoming a central mechanism of embodied cognition, and showing a key contribution to higher order processes such as .... 
+Interoception - definition - is a trending topic, becoming a central mechanism of embodied cognition, and showing a key contribution to higher order processes such as ...
 Unfortunately, it is also notably hard to measure.
 
-Scales are useful to capture metacognitive and subjective aspects and beliefs
-While the relationship between interoceptive scales and tasks is a strong point of contention, it is important to continue developing sound scales from a structural (i.e., factorial) standpoint.
+Scales are useful to capture metacognitive and subjective aspects and beliefs While the relationship between interoceptive scales and tasks is a strong point of contention, it is important to continue developing sound scales from a structural (i.e., factorial) standpoint.
 
-One of the most recent scale developped is the IAS, which is interesting because... It has *n* items, such as ...
+One of the most recent scale developped is the IAS, which is interesting because...
+It has *n* items, such as ...
 However, the study analysis did not go in depth in the analysis of the factor structure, focusing instead on ....
@@
 Finally, we re-fitted the CFA models on a new dataset [sample 2, from study 6 of @murphy2020testing], which confirmed that the 5-factor balanced model had the better fit relative to the other models ($BIC_{CFA-5mod} = 17316; BIC_{CFA-5h} = 17323; BIC_{CFA-5} = 18257; BIC_{EFA-4mod} = 18265$).
-However, the final model had poor to barely acceptable absolute indices of fit in both samples (Sample 1: $RMSEA = .067$ (acceptable < .08), $CFI = .878$ (acceptable > .9), $SRMR = .057$ (acceptable < .08); Sample 2: $RMSEA = .068$, $CFI = .906$, $SRMR = .063$).
+However, the final model had poor to barely acceptable absolute indices of fit in both samples (Sample 1: $RMSEA = .067$ (acceptable \< .08), $CFI = .878$ (acceptable \> .9), $SRMR = .057$ (acceptable \< .08); Sample 2: $RMSEA = .068$, $CFI = .906$, $SRMR = .063$).
 
@@
 
-485 participants (Mean age = 30.1, SD = 10.1, range: [18, 73]; Sex: 50.3% females, 49.7% males).
-**Update based on para from PHQ4**
+485 participants (Mean age = 30.1, SD = 10.1, range: [18, 73]; Sex: 50.3% females, 49.7% males). **Update based on para from PHQ4**
 
@@
 
-We ran a Bayesian correlations analysis (with a narrow prior centred around 0)
-<!-- , which allows to quantify in favour and against the null hypothesis, -->
-between the individual facet scores extracted from the final model and the MAIA-2 dimensions (administered online on a different session).
+We ran a Bayesian correlations analysis (with a narrow prior centred around 0) <!-- , which allows to quantify in favour and against the null hypothesis, --> between the individual facet scores extracted from the final model and the MAIA-2 dimensions (administered online on a different session).
 All dimensions of the IAS-R correlated with all the MAIA facets with the notable exception of *Not-reacting* and *Not-worrying*.
 As all correlations are presented in **Figure 2**, we will focus in the following on a subset of key results.
-<!-- (with at least strong evidence in favour of a relationship, i.e., BF >= 10).  -->
+<!-- (with at least strong evidence in favour of a relationship, i.e., BF >= 10).
+-->
 
@@
 ## Summary
+
+# Study 3 - Replication and Convergent Validity
 
@@
 
-The dataset analysed during the current study are available in the GitHub repository https://github.com/DominiqueMakowski/InteroceptiveAccuracyScale.
+The dataset analysed during the current study are available in the GitHub repository <https://github.com/DominiqueMakowski/InteroceptiveAccuracyScale>.
 

### 2024-02-13 paper/1_Initial/old/manuscript.tex
update analysis

--- 2023-01-17 paper/1_Initial/manuscript.tex
@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 
-\shorttitle{PHQ-4R}
+\shorttitle{IAS-R}
 
@@
 
-Interoception - definition - is the trending topic.
+Interoception - definition - is a trending topic, becoming a central mechanism of embodied cognition, and showing a key contribution to higher order processes such as \ldots.
 Unfortunately, it is also notably hard to measure.
@@
 Scales are useful to capture metacognitive and subjective aspects and beliefs
-While the relationship between scales and tasks is a strong point of contention, it is important to continue developing sound scales from a structural (i.e., factorial) standpoint.
+While the relationship between interoceptive scales and tasks is a strong point of contention, it is important to continue developing sound scales from a structural (i.e., factorial) standpoint.
 
-One of the most recent scale is the IAS, which is interesting because\ldots{} It has \emph{n} items, such as \ldots{}
+One of the most recent scale developped is the IAS, which is interesting because\ldots{} It has \emph{n} items, such as \ldots{}
 However, the study analysis did not go in depth in the analysis of the factor structure, focusing instead on \ldots.
 
-The purpose of this work is to re-analyze the factor structure of the scale using complementary statistical approaches.
-and propose a revised version.
-And to compare it with one of the most popular questionnaire of interoception, the MAIA-2 (\emph{ref}).
+The purpose of this work is to reanalyse the factor structure of the scale using complementary statistical approaches, a further extend its validation by comparing a revised version with one of the most popular questionnaire of interoception, the MAIA-2 (\emph{ref}), as well as other relevant indices (such as psychopathological traits).
 
-\hypertarget{study-1}{%
-\section{Study 1}\label{study-1}}
+\hypertarget{study-1---reanalysis-of-murphy-et-al.-2020}{%
+\section{Study 1 - Reanalysis of Murphy et al.~(2020)}\label{study-1---reanalysis-of-murphy-et-al.-2020}}
 
-Study 1 is a re-analysis of the data from Murphy et al.
+Study 1 is a reanalysis of the data from Murphy et al.
 (2020) regarding the factor structure of the Interoceptive Accuracy Scale (IAS).
-The aim is to use a finer-grained method for estimating the optimal number of latent factors (namely, the \emph{Method Agreement Procedure}, in Lüdecke et al., 2020; Makowski, 2018), and perform a statistical model comparison using Confirmatory Factor Analysis (CFA).
+The aim is to use a more fine-grained method for estimating the optimal number of latent factors (namely, the \emph{Method Agreement Procedure}, in Lüdecke et al., 2020; Makowski, 2018), and perform a statistical model comparison using Confirmatory Factor Analysis (CFA).
 
@@
 
-The \emph{Method Agreement Procedure} suggested 1 latent factor as optimal, supported by 5 (31.25\%) out of 16 methods (Bentler, Acceleration factor, Scree (R2), VSS complexity 1, Velicer's MAP), followed by 4 factors supported by 4 methods (Kaiser criterion, beta score, optimal coordinates, parallel analysis).
+The \emph{Method Agreement Procedure} suggested 1 latent factor as optimal, supported by 5 (31.25\%) out of 16 methods (Bentler, Acceleration factor, Scree - R2, VSS complexity 1, Velicer's MAP), followed by 4 factors supported by 4 methods (Kaiser criterion, beta score, optimal coordinates, parallel analysis).
 
-We fitted the simple-structure (i.e., each variable loading only unto its maximal latent factor) of these two models using CFA, underlining the 4-factors model as having a significantly better fit (\(\Delta \chi^2(6) = 232, p < .001; BIC_{CFA-1} = 25141, BIC_{CFA-4} = 24945\)).
-Using the EFA loading patterns and the CFA modification indices, we then compared the initial 4-factor model to two variants: one with 2 items removed (Blood sugar and Taste), and another with, additionally, the \emph{Interoception} factor split into two (with the pain-related items grouped together as a \emph{Nociception} factor).
+We fitted the simple-structure (i.e., each variable loading only unto its maximal latent factor) of these two models using CFA, which underlined the 4-factors model as having a significantly better fit (\(\Delta \chi^2(6) = 232, p < .001; BIC_{CFA-1} = 25141, BIC_{CFA-4} = 24945\)).
+Using the EFA loading patterns and the CFA modification indices, we then compared the initial 4-factor model to two variants: one with 2 items removed (Blood sugar and Taste), and another with, additionally, the \emph{Interoception} factor split into two (with the pain-related items grouped together in a \emph{Nociception} factor).
 The latter model (\emph{CFA-5}), was significantly superior to the others (\(\Delta \chi^2(4) = 28.8, p < .001; BIC_{CFA-4mod} = 22563, BIC_{CFA-5} = 22559\)).
-We then removed the least loaded items of \emph{Expulsion} (cough) to improve the balance (6 items for interoception and 3 per secondary scales), which significantly improved the model fit (\(\Delta \chi^2(17) = 61.4, p < .001; BIC_{CFA-5mod} = 21256\)).
-Finally, we tested a hierarchical model in which the interoception dimension was, in addition to its own 6 items, loaded by the secondary latent factors (Skin, Expulsion, Nociception, Elimination), but this model did not improve the fit (\(BIC_{CFA-5h} = 21452\)), suggesting that the 4 secondary latent factors are not subdimensions of the interoception factor.
+We then removed the least loaded item of \emph{Expulsion} (cough) to improve the balance (6 items for interoception and 3 per secondary scales), which significantly improved the model fit (\(\Delta \chi^2(17) = 61.4, p < .001; BIC_{CFA-5mod} = 21256\)).
+Finally, we tested a hierarchical model in which the interoception dimension was, in addition to its own 6 items, loaded by the secondary latent factors (\emph{Skin}, \emph{Expulsion}, \emph{Nociception}, \emph{Elimination}), but this model did not improve the fit (\(BIC_{CFA-5h} = 21452\)).
 
-Finally, we re-fitted the CFA models on a new data set (study 6 of Murphy et al., 2020), which confirmed that the 5-factor balanced model had the better fit (\(BIC_{CFA-5mod} = 17316; BIC_{CFA-5h} = 17323; BIC_{CFA-5} = 18257; BIC_{EFA-4mod} = 18265\)).
-However, the final model had barely acceptable indices of fit in both samples (Sample 1: \(RMSEA = .067\) (acceptable \textless{} .08), \(CFI = .878\) (acceptable \textgreater{} .9), \(SRMR = .057\) (acceptable \textless{} .08); Sample 2: \(RMSEA = .068\), \(CFI = .906\), \(SRMR = .063\)).
+Finally, we re-fitted the CFA models on a new dataset (sample 2, from study 6 of Murphy et al., 2020), which confirmed that the 5-factor balanced model had the better fit relative to the other models (\(BIC_{CFA-5mod} = 17316; BIC_{CFA-5h} = 17323; BIC_{CFA-5} = 18257; BIC_{EFA-4mod} = 18265\)).
+However, the final model had poor to barely acceptable absolute indices of fit in both samples (Sample 1: \(RMSEA = .067\) (acceptable \textless{} .08), \(CFI = .878\) (acceptable \textgreater{} .9), \(SRMR = .057\) (acceptable \textless{} .08); Sample 2: \(RMSEA = .068\), \(CFI = .906\), \(SRMR = .063\)).
 
@@
 The 5 factors (with their items) are \textbf{Interoception} (Heart, Hungry, Breathing, Thirsty, Temperature, Sexual arousal); \textbf{Nociception} (Muscles, Bruise, Pain); \textbf{Expulsion} (Burp, Sneeze, Wind); \textbf{Elimination} (Vomit, Defecate, Urinate); \textbf{Skin} (Itch, Tickle, Affective touch).
-However, the indices of fit for this model were relatively low.
+However, absolute indices of fit for this model were relatively low.
 
-\hypertarget{study-2}{%
-\section{Study 2}\label{study-2}}
+\hypertarget{study-2---online-validation-of-new-structure}{%
+\section{Study 2 - Online validation of new structure}\label{study-2---online-validation-of-new-structure}}
 
-The final revised scale, made of 18 items (6 for interoception and 3 per secondary dimension), was administered to a new sample in an online study.
-The response was chained from a 5-point Likert scale (\textbf{ANSHU TO CONFIRM}) to a analog scale.
+The revised scale, made of 18 items (6 for interoception and 3 per secondary dimension), was administered to a new sample in an online study.
+The response was changed from a 5-point Likert scale (\textbf{ANSHU TO CONFIRM}) to a analog scale.
 
@@
 
+Note that as the MAIA and the PI were done on a different session 2, we only have n = \ldots{} for their correlations.
+
 \hypertarget{results-1}{%
@@
 
-Despite changing the response format for analog scales, the distribution of answers was similar to that of the original validation samples, with a modal answer of around 75\% of the scale for most of the items (see \textbf{Figure 1A}).
-Contrary to our expectations, the \emph{Method Agreement Procedure} for EFA suggested 4 latent factor (supported by 31.58\% of methods), rather than the 5 hypothesized (supported by 0 methods).
+Despite changing the response format to analog scales, the distribution of answers was similar to that of the original validation samples, with a modal answer at around 75\% of the scale for most of the items (see \textbf{Figure 1A}).
+Contrary to our expectations, the \emph{Method Agreement Procedure} for EFA suggested 4 latent factor (supported by 5/16 methods), rather than the 5 hypothesized (supported by 0 methods).
 CFA confirmed that the 4-factor model derived from the EFA had a better fit than this 5-factor model and than a 1-factor model (\(BIC_{CFA-4} = 22758, BIC_{CFA-1} = 22911, BIC_{CFA-1} = 23065\)).
 We then re-balanced the 4-factor model to keep 3 items per factor and remove items that strongly loaded on more than one factor in the EFA (e.g., Temperature and Sneeze, see \textbf{Figure 1B}).
-Finally, we compare the resulting model to one with a fifth latent factor (\emph{Interoception}) loaded by the 4 others latent factors.
+Finally, we compared the resulting model to one with a fifth latent factor (\emph{Interoception}) loaded by the 4 others latent factors.
 Adding this general score did not significantly change the model's fit (\(\Delta \chi^2(2) = 5.85, p = .054; BIC_{CFA-4mod} = 15140, BIC_{CFA-4h} = 15259\)).
 Importantly, the resulting model (see \textbf{Figure 1C}) had excellent indices of fit (\(RMSEA = .0347\), \(CFI = .9796\), \(SRMR = .0364\)).
-Finally, we re-fitted this model on the two samples from study 1, and report improved indices of fit over the initial best model (Sample 1: \(RMSEA = .068\), \(CFI = .9020\), \(SRMR = .0556\); Sample 2: \(RMSEA = .066\), \(CFI = .9315\), \(SRMR = .0504\)).
+Finally, we re-fitted this model on the two samples from study 1, which revealed much improved indices of fit over the initial best model (Sample 1: \(RMSEA = .068\), \(CFI = .9020\), \(SRMR = .0556\); Sample 2: \(RMSEA = .066\), \(CFI = .9315\), \(SRMR = .0504\)).
 
-We ran Bayesian correlations analysis (with a narrow prior centred around 0)
+We ran a Bayesian correlations analysis (with a narrow prior centred around 0)
 between the individual facet scores extracted from the final model and the MAIA-2 dimensions (administered online on a different session).
+All dimensions of the IAS-R correlated with all the MAIA facets with the notable exception of \emph{Not-reacting} and \emph{Not-worrying}.
 As all correlations are presented in \textbf{Figure 2}, we will focus in the following on a subset of key results.
@@
 This facet also negatively related to several pathological personality traits measured by the PID-5, such as \emph{Psychoticism} (\(TODO\)), \emph{Negative Affect} (\(TODO\)), and \emph{Detachment} (\(TODO\)).
-In line with that, we also report negative relationships with schizotypical characteristics, including \emph{Social Anxiety} (\(TODO\)), \emph{Odd Speech}(\(TODO\)), \emph{No Close Friends} (\(TODO\)) and \emph{Constricted Affect} (\(TODO\)); as well positive relationship with autistic traits, such as \emph{Switching} (\(TODO\)) and \emph{Social Skills} (\(TODO\)).
+In line with that, we also report negative relationships with schizotypical characteristics, including \emph{Social Anxiety} (\(TODO\)), \emph{Odd Speech}(\(TODO\)), \emph{No Close Friends} (\(TODO\)) and \emph{Constricted Affect} (\(TODO\)); as well with autistic traits, including as \emph{Switching} (\(TODO\)) and \emph{Social Skills} (\(TODO\)).
 
@@
 \subsection{Summary}\label{summary-1}}
+
+\hypertarget{study-3---replication-and-convergent-validity}{%
+\section{Study 3 - Replication and Convergent Validity}\label{study-3---replication-and-convergent-validity}}
 
@@
 
-\textbf{Scoring}. Each scale can be answered on an analog scale (Disagree - Agree). Items can be averaged per dimension, and dimensions can be averaged to get a general Interoception score.
+\textbf{Scoring}. Each scale can be answered on an analogue scale (Disagree - Agree). Items can be averaged per dimension, and dimensions can be averaged to get a general Interoception score.
 
@@
  & Muscles\\
- & Heart\\ \midrule
+ & I can always accurately perceive when my heart is beating fast\\ \midrule
 \textbf{Homeostatis} & Itch\\

### 2024-02-13 paper/1_Initial/manuscript.qmd
add empty ms

---
title: "The Revised Interoceptive Accuracy Scale (IAS-R) Confirms Links between Interoception and Mental Health"
blank-lines-above-title: 2  # Lines above title in .docx format
shorttitle: "Revised Interoceptive Accuracy Scale (IAS-R)"
author:
  - name: Dominique Makowski
    corresponding: true
    orcid: "0000-0001-5375-9967"
    email: D.Makowski@sussex.ac.uk
    url: https://realitybending.github.io/
    # Roles are optional (note: The two writing roles have en dashes, not hyphens. You can use their aliases, w)
    # Select from the CRediT: Contributor Roles Taxonomy https://credit.niso.org/
    # Conceptualization, Data curation, Formal Analysis, Funding acquisition, Investigation, 
    # Methodology, Project administration, Resources, Software, Supervision, Validation, 
    # Visualization, Writing – original draft, Writing – review & editing
    roles:
      - conceptualization: lead
      - Writing - original draft
    affiliations:
      - id: id1
        name: "University of Sussex"
        group: Reality Bending Lab
        department: School of Psychology
        city: Brighton
        region: UK
        postal-code: "BN1 9RH"
  - name: X. Y
    # roles:
    #   - Project administration
    #   - Formal Analysis
    affiliations: 
      - ref: id1
  - name: Annabel Chen
    orcid: "0000-0002-1540-5516"
    # roles:
    #   - Resources
    #   - Project administration
    affiliations:
      - name: "School of Social Sciences, Nanyang Technological University, Singapore"
author-note:
  blank-lines-above-author-note: 1
abstract: "This document is a template demonstrating the apaquarto format."
keywords: [Interoception, Accuracy, Scale, Questionnaire, Personality, Psychopathology, Validation]
floatsintext: true
bibliography: "bibliography.bib"
format:
  apaquarto-docx:
    numbered-lines: true
---

```{r}
#| label: setup
#| include: false
library(conflicted)
library(tidyverse)
```

intro

# Methods

blabla

# Results

blabla

# Discussion

blabla

# References

::: {#refs}
:::

### 2024-02-13 paper/1_Initial/manuscript.tex
add empty ms

--- 2023-01-16 paper/1_Initial/manuscript.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
+\documentclass[
+  jou,
+  floatsintext,
+  longtable,
+  colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{apa7}
+
+\RequirePackage{longtable}
+% \setlength\LTleft{0pt}
+\RequirePackage{threeparttablex}
+
+% %
+
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+	{0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+	{-.5em}%
+	{\normalfont\normalsize\bfseries\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{0.5em}%
+	{0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+	{-\z@\relax}%
+	{\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
+\usepackage{amsmath}
+
+\usepackage{longtable, booktabs, multirow, multicol, colortbl, hhline, caption, array, float, tcolorbox}
+
 %
-\documentclass[
-  man,floatsintext]{apa6}
-\usepackage{amsmath,amssymb}
-\usepackage{lmodern}
-\usepackage{iftex}
-\ifPDFTeX
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
+
+\newlength\Oldarrayrulewidth
+\newlength\Oldtabcolsep
+
+\usepackage{hyperref}
+\usepackage{float}
+
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
 \makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
 \makeatother
-\usepackage{xcolor}
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+
 \usepackage{graphicx}
@@
 \makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-% Make \paragraph and \subparagraph free-standing
-\ifx\paragraph\undefined\else
-  \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-  \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
+
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
   \fi
   % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-\ifLuaTeX
-\usepackage[bidi=basic]{babel}
-\else
-\usepackage[bidi=default]{babel}
-\fi
-\babelprovide[main,import]{english}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-% Manuscript styling
-\usepackage{upgreek}
-\captionsetup{font=singlespacing,justification=justified}
 
-% Table formatting
-\usepackage{longtable}
-\usepackage{lscape}
-% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
-\usepackage{multirow}		% Table styling
-\usepackage{tabularx}		% Control Column width
-\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
-\usepackage{threeparttablex}            % Lets threeparttable work with longtable
+\usepackage{times}
 
-% Create new environments so endfloat can handle them
-% \newenvironment{ltable}
-%   {\begin{landscape}\centering\begin{threeparttable}}
-%   {\end{threeparttable}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
+\usepackage{lineno}
 
-% Enables adjusting longtable caption width to table width
-% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
+\title{The Revised Interoceptive Accuracy Scale (IAS-R) Confirms Links
+between Interoception and Mental Health}
+\shorttitle{Revised Interoceptive Accuracy Scale (IAS-R)}
+
+\usepackage{etoolbox}
+
+\course{Introduction to Assessment}
+\professor{W. Joel Schneider}
+\duedate{12/22/2024}
+
+\authorsnames[{1},{1},{2}]{
+Dominique Makowski,X. Y,Annabel Chen
+}
+
+\authorsaffiliations{
+{School of Psychology, University of Sussex},{School of Social Sciences,
+Nanyang Technological University, Singapore}}
+
+\leftheader{Makowski, Y and Chen}
+
+\abstract{This document is a template demonstrating the apaquarto
+format.}
+% % \addbibresource{bibliography.bib}
+% 
+\keywords{Interoception, Accuracy, Scale, Questionnaire, Personality, Psychopathology, Validation}
+
+\authornote{\par{\addORCIDlink{Dominique
+Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{Annabel
+Chen}{0000-0002-1540-5516}}
+\par{ }
+\par{       Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows: Dominique
+Makowski:   conceptualization, Writing - original draft}
+\par{Correspondence concerning this article should be addressed to Dominique
+Makowski, Email: D.Makowski@sussex.ac.uk}
+}
+
+\usepackage{float}
 \makeatletter
-\newcommand\LastLTentrywidth{1em}
-\newlength\longtablewidth
-\setlength{\longtablewidth}{1in}
-\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
-
-% \setlength{\parindent}{0.5in}
-% \setlength{\parskip}{0pt plus 0pt minus 0pt}
-
-% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
-% See https://github.com/crsh/papaja/issues/292
-\makeatletter
-\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-1em}%
-  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
-
-\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-\z@\relax}%
-  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\let\oldtpt\ThreePartTable
+\let\endoldtpt\endThreePartTable
+\def\ThreePartTable{\@ifnextchar[\ThreePartTable@i \ThreePartTable@ii}
+\def\ThreePartTable@i[#1]{\begin{figure}
+\onecolumn
+\begin{minipage}{0.5\textwidth}
+\oldtpt[#1]
+}
+\def\ThreePartTable@ii{\begin{figure}
+\onecolumn
+\begin{minipage}{0.5\textwidth}
+\oldtpt
+}
+\def\endThreePartTable{
+\endoldtpt
+\end{minipage}
+\twocolumn
+\end{figure}}
 \makeatother
 
-% \usepackage{etoolbox}
 \makeatletter
-\patchcmd{\HyOrg@maketitle}
-  {\section{\normalfont\normalsize\abstractname}}
-  {\section*{\normalfont\normalsize\abstractname}}
-  {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
-  {\section{\protect\normalfont{\@title}}}
-  {\section*{\protect\normalfont{\@title}}}
-  {}{\typeout{Failed to patch title.}}
+\let\endoldlt\endlongtable		
+\def\endlongtable{
+\hline
+\endoldlt}
 \makeatother
 
-\usepackage{xpatch}
-\makeatletter
-\xapptocmd\appendix
-  {\xapptocmd\section
-    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
-    {}{\InnerPatchFailed}%
-  }
-{}{\PatchFailed}
-\keywords{PHQ-4; depression; anxiety; brief questionnaire; short scale\newline\indent Word count: 1249}
-\usepackage{lineno}
+\newenvironment{twocolumntable}% environment name
+{% begin code
+\begin{table*}%
+\onecolumn%
+}%
+{%
+\twocolumn%
+\end{table*}%
+}% end code
 
-\linenumbers
-\usepackage{csquotes}
-\usepackage[titles]{tocloft}
-\cftpagenumbersoff{figure}
-\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
-\renewcommand{\cftfigaftersnum}{.\space}
-\setlength{\cftfigindent}{0pt}
-\setlength{\cftafterloftitleskip}{0pt}
-\settowidth{\cftfignumwidth}{Figure 10.\qquad}
-\usepackage[labelfont=bf, font={scriptsize, color=gray}]{caption}
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={The Revised Interoceptive Accuracy Scale (IAS-R)},
-  pdfauthor={Dominique Makowski1, An Shu Te2, \& S.H. Annabel Chen2, 3, 4, 5},
-  pdflang={en-EN},
-  pdfkeywords={PHQ-4; depression; anxiety; brief questionnaire; short scale},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-
-\title{\textbf{The Revised Interoceptive Accuracy Scale (IAS-R)}}
-\author{Dominique Makowski\textsuperscript{1}, An Shu Te\textsuperscript{2}, \& S.H. Annabel Chen\textsuperscript{2, 3, 4, 5}}
-\date{}
-
-\shorttitle{PHQ-4R}
-
-\authornote{
-
-The authors made the following contributions.
-Dominique Makowski: Conceptualization, Data curation, Formal Analysis, Funding acquisition, Investigation, Methodology, Project administration, Resources, Software, Supervision, Validation, Visualization, Writing -- original draft; An Shu Te: Project administration, Resources, Software, Investigation, Writing -- original draft; S.H.
-Annabel Chen: Project administration, Supervision, Writing -- review \& editing.
-
-Correspondence concerning this article should be addressed to Dominique Makowski, HSS 04-18, 48 Nanyang Avenue, Singapore.
-E-mail: \href{mailto:dom.makowski@gmail.com}{\nolinkurl{dom.makowski@gmail.com}}
-
-}
-
-\affiliation{\vspace{0.5cm}\textsuperscript{1} School of Psychology, University of Sussex, UK\\\textsuperscript{2} School of Social Sciences, Nanyang Technological University, Singapore\\\textsuperscript{3} LKC Medicine, Nanyang Technological University, Singapore\\\textsuperscript{4} National Institute of Education, Singapore\\\textsuperscript{5} Centre for Research and Development in Learning, Nanyang Technological University, Singapore}
-
-\abstract{%
-Something something.
-}
+\urlstyle{same}
 
@@
 \maketitle
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\setlength\LTleft{0pt}
 
-Interoception - definition - is the trending topic.
-Unfortunately, it is also notably hard to measure.
+intro
 
-Scales are useful to capture metacognitive and subjective aspects and beliefs
-While the relationship between scales and tasks is a strong point of contention, it is important to continue developing sound scales from a structural (i.e., factorial) standpoint.
+\section{Methods}\label{methods}
 
-One of the most recent scale is the IAS, which is interesting because\ldots{}
+blabla
 
-The purpose of this work is to re-analyze the factor structure of the scale using complementary statistical approaches. and propose a revised version.
+\section{Results}\label{results}
 
-\hypertarget{study-1}{%
-\section{Study 1}\label{study-1}}
+blabla
 
-Study 1 is a re-analysis of the data from Murphy et al.
-(2020) regarding the factor structure of the Interoceptive Accuracy Scale (IAS).
-The aim is to use a finer-grained method for estimating the optimal number of latent factors (namely, the \emph{Method Agreement Procedure}, in Lüdecke et al., 2020; Makowski, 2018), and perform a statistical model comparison using Confirmatory Factor Analysis (CFA).
+\section{Discussion}\label{discussion}
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+blabla
 
-The exploratory factor analysis (EFA) and initial model selection was performed on the data from \href{https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769}{study 1} of Murphy et al.
-(2020), downloaded from OSF, included 451 participants (Mean age = 25.8, SD = 8.4, range: {[}18, 69{]}; Gender: 69.4\% women, 29.5\% men, 1.11\% non-binary).
-Data from the \href{https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769}{study 6}, which included 375 participants (Mean age = 35.3, SD = 16.9, range: {[}18, 91{]}; Gender: 70.1\% women, 28.5\% men, 1.33\% non-binary), was used as a test-set for confirmatory analysis.
+\section{References}\label{references}
 
-\hypertarget{results}{%
-\subsection{Results}\label{results}}
-
-The \emph{Method Agreement Procedure} suggested 1 latent factor as optimal, supported by 5 (31.25\%) out of 16 methods (Bentler, Acceleration factor, Scree (R2), VSS complexity 1, Velicer's MAP), followed by 4 factors supported by 4 methods (Kaiser criterion, beta score, optimal coordinates, parallel analysis).
-
-We fitted the simple-structure (i.e., each variable loading only unto its maximal latent factor) of these two models using CFA, underlining the 4-factors model as having a significantly better fit (\(\Delta \chi^2(6) = 232, p < .001; BIC_{EFA-1} = 23041, BIC_{EFA-4} = 23846\)).
-Using the EFA loading patterns and the CFA modification indices, we then compared the initial 4-factor model to two variants: one with 2 items removed (Blood sugar and Taste), and another with, additionally, the \emph{Interoception} factor split into two (with the pain-related items grouped together).
-The latter model (\emph{CFA-5}), was significantly superior to the others (\(\Delta \chi^2(4) = 28.8, p < .001; BIC_{EFA-4mod} = 21555, BIC_{CFA-5} = 21551\)).
-Finally, we removed the least loaded items of expulsion (cough) to improve the balance (3 items per secondary scales, and 6 for interoception), which significantly improved the model fit (\(\Delta \chi^2(17) = 61.4, p < .001; BIC_{CFA-5mod} = 20552\)).
-
-Finally, we re-fitted the models on a new data set (study 6 of Murphy et al., 2020).
-
-\hypertarget{summary}{%
-\subsection{Summary}\label{summary}}
-
-Exploratory Factor Analysis suggested a 1-factor and 4-factors solutions, but the latter was favoured by CFA.
-Further comparison suggested that a 5-factors model (obtained by separating \emph{Nociception} from \emph{Interoception}) had a superior fit.
-The 5 factors are:
-
-\begin{itemize}
-\tightlist
-\item
-  \textbf{Interoception}: Heart, Hungry, Breathing, Thirsty, Temperature, Sexual arousal.
-\item
-  \textbf{Nociception}: Muscles, Bruise, Pain.
-\item
-  \textbf{Expulsion}: Burp, Sneeze, Wind.
-\item
-  \textbf{Elimination}: Vomit, Defecate, Urinate.
-\item
-  \textbf{Skin}: Itch, Tickle, Affective touch.
-\end{itemize}
-
-The final revised scale, made of 18 items (6 for interoception and 3 per secondary dimension), is available \protect\hyperlink{IAS-R}{below}.
-
-\hypertarget{study-2}{%
-\section{Study 2}\label{study-2}}
-
-\newpage
-
-\hypertarget{data-availability}{%
-\section{Data Availability}\label{data-availability}}
-
-The dataset analysed during the current study are available in the GitHub repository \url{https://github.com/DominiqueMakowski/InteroceptiveAccuracyScale}.
-
-\hypertarget{funding}{%
-\section{Funding}\label{funding}}
-
-This work was supported by the Presidential Postdoctoral Fellowship Grant (NTU-PPF-2020-10014) from Nanyang Technological University (awarded to DM).
-
-\hypertarget{acknowledgments}{%
-\section{Acknowledgments}\label{acknowledgments}}
-
-We warmly thank the original authors of (Murphy et al., 2020) for making their data and material open-access, which enabled the present follow-up study.
-
-\newpage
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-ludecke2020extracting}{}}%
-Lüdecke, D., Ben-Shachar, M.
-S., Patil, I., \& Makowski, D.
-(2020).
-Extracting, computing and exploring the parameters of statistical models using r.
-\emph{Journal of Open Source Software}, \emph{5}(53), 2445.
-
-\leavevmode\vadjust pre{\hypertarget{ref-makowski2018psycho}{}}%
-Makowski, D. (2018). The psycho package: An efficient and publishing-oriented workflow for psychological science. \emph{Journal of Open Source Software}, \emph{3}(22), 470.
-
-\leavevmode\vadjust pre{\hypertarget{ref-murphy2020testing}{}}%
-Murphy, J., Brewer, R., Plans, D., Khalsa, S.
-S., Catmur, C., \& Bird, G.
-(2020).
-Testing the independence of self-reported interoceptive accuracy and attention.
-\emph{Quarterly Journal of Experimental Psychology}, \emph{73}(1), 115--133.
-
+\phantomsection\label{refs}
+\begin{CSLReferences}{0}{1}
 \end{CSLReferences}
 
-\clearpage
-\renewcommand{\listfigurename}{Figure captions}
-
 \end{document}

### 2024-02-20 analysis/analysis.qmd
update stats

@@
   mutate(Gender = as.character(ifelse(Sex == 1, "Male", ifelse(Sex == 0, "Female", "Other")))) |>
-  rename(Heart=IAS1, Hungry=IAS2, Breathing=IAS3, Thirsty=IAS4,
-         Urinate=IAS5, Defecate=IAS6, Taste=IAS7, Vomit=IAS8, Sneeze=IAS9,
-         Cough=IAS10, Temp=IAS11, Sex_arousal=IAS12, Wind=IAS13, Burp=IAS14,
-         Muscles=IAS15, Bruise=IAS16, Pain=IAS17, Blood_Sugar=IAS18,
-         Affective_touch=IAS19, Tickle=IAS20, Itch=IAS21)
+  rename(
+    Heart = IAS1, Hungry = IAS2, Breathing = IAS3, Thirsty = IAS4,
+    Urinate = IAS5, Defecate = IAS6, Taste = IAS7, Vomit = IAS8, Sneeze = IAS9,
+    Cough = IAS10, Temp = IAS11, Sex_arousal = IAS12, Wind = IAS13, Burp = IAS14,
+    Muscles = IAS15, Bruise = IAS16, Pain = IAS17, Blood_Sugar = IAS18,
+    Affective_touch = IAS19, Tickle = IAS20, Itch = IAS21
+  )
 
@@
 df4 <- haven::read_sav("../data/Lin2023/Study 1 & 3.sav") |>
+  select(-sex) |> 
+  mutate_all(as.numeric) |>
   mutate(Gender = as.character(ifelse(sex_dummy == 1, "Male", ifelse(sex_dummy == 0, "Female", "Other")))) |>
-  rename(Age=age, 
-         Heart=Heart, Hungry=HUNGR, Breathing=BREAT, Thirsty=Thirs,
-         Urinate=URINA, Defecate=Defec, Taste=TASTE, Vomit=VOMIT, Sneeze=Sneez,
-         Cough=COUGH, Temp=TEMPE, Sex_arousal=SEXAR, Wind=WIND, Burp=Burp,
-         Muscles=MUSCL, Bruise=Bruis, Pain=PAIN, Blood_Sugar=BloSu,
-         Affective_touch=Touch, Itch=ITCH)  # No tickle because same Chinese character
+  rename(
+    Age = age,
+    Heart = Heart, Hungry = HUNGR, Breathing = BREAT, Thirsty = Thirs,
+    Urinate = URINA, Defecate = Defec, Taste = TASTE, Vomit = VOMIT, Sneeze = Sneez,
+    Cough = COUGH, Temp = TEMPE, Sex_arousal = SEXAR, Wind = WIND, Burp = Burp,
+    Muscles = MUSCL, Bruise = Bruis, Pain = PAIN, Blood_Sugar = BloSu,
+    Affective_touch = Touch, Itch = ITCH
+  ) # No tickle because same Chinese character
 
@@
   mutate(Gender = as.character(ifelse(Sex == "男", "Male", ifelse(Sex == "女", "Female", "Other")))) |>
-  rename(Heart=Heart, Hungry=HUNGR, Breathing=BREAT, Thirsty=Thirs,
-         Urinate=URINA, Defecate=Defec, Taste=TASTE, Vomit=VOMIT, Sneeze=Sneez,
-         Cough=COUGH, Temp=TEMPE, Sex_arousal=SEXAR, Wind=WIND, Burp=Burp,
-         Muscles=MUSCL, Bruise=Bruis, Pain=PAIN, Blood_Sugar=BloSu,
-         Affective_touch=Touch, Itch=ITCH)  # No tickle because same Chinese character
+  rename(
+    Heart = Heart, Hungry = HUNGR, Breathing = BREAT, Thirsty = Thirs,
+    Urinate = URINA, Defecate = Defec, Taste = TASTE, Vomit = VOMIT, Sneeze = Sneez,
+    Cough = COUGH, Temp = TEMPE, Sex_arousal = SEXAR, Wind = WIND, Burp = Burp,
+    Muscles = MUSCL, Bruise = Bruis, Pain = PAIN, Blood_Sugar = BloSu,
+    Affective_touch = Touch, Itch = ITCH
+  ) # No tickle because same Chinese character
 
 df6 <- read.csv("https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv") |>
-  rename(Heart=IAS_1, Hungry=IAS_2, Breathing=IAS_3, Thirsty=IAS_4, 
-         Urinate=IAS_5, Defecate=IAS_6, Taste=IAS_7, Vomit=IAS_8, Sneeze=IAS_9, 
-         Cough=IAS_10, Temp=IAS_11, Sex_arousal=IAS_12, Wind=IAS_13, Burp=IAS_14,
-         Muscles=IAS_15, Bruise=IAS_16, Pain=IAS_17, Blood_Sugar=IAS_18,
-         Affective_touch=IAS_19, Tickle=IAS_20, Itch=IAS_21)
+  rename(
+    Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
+    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
+    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
+    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
+    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
+  )
 
 df7 <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |>
-  rename(Gender=Sex, Heart=Item_IAS_Interoception_1, Hungry=Item_IAS_Interoception_2, 
-         Breathing=Item_IAS_Interoception_3, Thirsty=Item_IAS_Interoception_4, 
-         Temp=Item_IAS_Interoception_5, Sex_arousal=Item_IAS_Interoception_6,
-         Urinate=Item_IAS_Elimination_1, Defecate=Item_IAS_Elimination_2,
-         Vomit=Item_IAS_Elimination_3, Wind=Item_IAS_Expulsion_1, 
-         Burp=Item_IAS_Expulsion_2, Sneeze=Item_IAS_Expulsion_3,
-         Muscles=Item_IAS_Nociception_1, Bruise=Item_IAS_Nociception_2,
-         Pain=Item_IAS_Nociception_3, Affective_touch=Item_IAS_Skin_1, 
-         Tickle=Item_IAS_Skin_2, Itch=Item_IAS_Skin_3) |>
+  rename(
+    Gender = Sex, Heart = Item_IAS_Interoception_1, Hungry = Item_IAS_Interoception_2,
+    Breathing = Item_IAS_Interoception_3, Thirsty = Item_IAS_Interoception_4,
+    Temp = Item_IAS_Interoception_5, Sex_arousal = Item_IAS_Interoception_6,
+    Urinate = Item_IAS_Elimination_1, Defecate = Item_IAS_Elimination_2,
+    Vomit = Item_IAS_Elimination_3, Wind = Item_IAS_Expulsion_1,
+    Burp = Item_IAS_Expulsion_2, Sneeze = Item_IAS_Expulsion_3,
+    Muscles = Item_IAS_Nociception_1, Bruise = Item_IAS_Nociception_2,
+    Pain = Item_IAS_Nociception_3, Affective_touch = Item_IAS_Skin_1,
+    Tickle = Item_IAS_Skin_2, Itch = Item_IAS_Skin_3
+  ) |>
   filter(!is.na(Urinate))
@@
 ```{r}
-vars <- c("Heart", "Hungry", "Breathing", "Thirsty", "Urinate", "Defecate", "Taste", "Vomit", "Sneeze", "Cough", "Temp",
-          "Sex_arousal", "Wind", "Burp", "Muscles", "Bruise", "Pain", "Blood_Sugar", "Affective_touch", "Tickle", "Itch")
-
-dens1 <- estimate_density(select(df1, all_of(vars)), method="kernSmooth") |> 
+vars <- c(
+  "Heart", "Hungry", "Breathing", "Thirsty", "Urinate", "Defecate", "Taste", "Vomit", "Sneeze", "Cough", "Temp",
+  "Sex_arousal", "Wind", "Burp", "Muscles", "Bruise", "Pain", "Blood_Sugar", "Affective_touch", "Tickle", "Itch"
+)
+
+dens1 <- estimate_density(select(df1, all_of(vars)), method = "kernSmooth") |>
   mutate(Sample = "Sample 1")
-dens2 <- estimate_density(select(df2, all_of(vars)), method="kernSmooth") |> 
+dens2 <- estimate_density(select(df2, all_of(vars)), method = "kernSmooth") |>
   mutate(Sample = "Sample 2")
-dens3 <- estimate_density(select(df3, all_of(vars)), method="kernSmooth") |> 
+dens3 <- estimate_density(select(df3, all_of(vars)), method = "kernSmooth") |>
   mutate(Sample = "Sample 3")
-dens4 <- estimate_density(select(df4, all_of(setdiff(vars, "Tickle"))), method="kernSmooth") |> 
+dens4 <- estimate_density(select(df4, all_of(setdiff(vars, "Tickle"))), method = "kernSmooth") |>
   mutate(Sample = "Sample 4")
-dens5 <- estimate_density(select(df5, all_of(setdiff(vars, "Tickle"))), method="kernSmooth") |> 
+dens5 <- estimate_density(select(df5, all_of(setdiff(vars, "Tickle"))), method = "kernSmooth") |>
   mutate(Sample = "Sample 5")
-dens6 <- estimate_density(select(df6, all_of(vars)), method="kernSmooth") |> 
+dens6 <- estimate_density(select(df6, all_of(vars)), method = "kernSmooth") |>
   mutate(Sample = "Sample 6")
-dens7 <- estimate_density(select(df7, all_of(setdiff(vars, c("Taste", "Cough", "Blood_Sugar")))), method="kernSmooth") |> 
+dens7 <- estimate_density(select(df7, all_of(setdiff(vars, c("Taste", "Cough", "Blood_Sugar")))), method = "kernSmooth") |>
   mutate(Sample = "Sample 7")
@@
   labs(title = "Distribution of Responses", x = "Response", y = "Density", color = "Item") +
-  facet_wrap(~Sample, scales = "free", nrow=4)
-```
-
-```{r}
-data1 <- normalize(select(df1, all_of(dens1$Parameter)), range=c(1, 5))
-data2 <- normalize(select(df2, all_of(dens2$Parameter)), range=c(1, 5))
-data3 <- normalize(select(df3, all_of(dens3$Parameter)), range=c(1, 5))
-data4 <- normalize(select(df4, all_of(dens4$Parameter)), range=c(1, 5))
-data5 <- normalize(select(df5, all_of(dens5$Parameter)), range=c(1, 5))
+  facet_wrap(~Sample, scales = "free", nrow = 4)
+```
+
+```{r}
+data1 <- normalize(select(df1, all_of(dens1$Parameter)), range = c(1, 5))
+data2 <- normalize(select(df2, all_of(dens2$Parameter)), range = c(1, 5))
+data3 <- normalize(select(df3, all_of(dens3$Parameter)), range = c(1, 5))
+data4 <- normalize(select(df4, all_of(dens4$Parameter)), range = c(1, 5))
+data5 <- normalize(select(df5, all_of(dens5$Parameter)), range = c(1, 5))
 data6 <- select(df6, all_of(dens6$Parameter))
@@
 
-data_all <- rbind(data1, data2, data3, 
-                  mutate(data4, Tickle=NA), mutate(data5, Tickle=NA), 
-                  data6, mutate(data7, Taste=NA, Cough=NA, Blood_Sugar=NA)) 
+data_all <- rbind(
+  data1, data2, data3,
+  mutate(data4, Tickle = NA), mutate(data5, Tickle = NA),
+  data6, mutate(data7, Taste = NA, Cough = NA, Blood_Sugar = NA)
+)
 ```
@@
 make_correlation <- function(df) {
-  correlation::correlation(df, redundant=TRUE) |> 
+  correlation::correlation(df, redundant = TRUE) |>
     correlation::cor_sort() |>
     correlation::cor_lower() |>
-    mutate(val = paste0(insight::format_value(r), format_p(p, stars_only=TRUE))) |>
+    mutate(val = paste0(insight::format_value(r), format_p(p, stars_only = TRUE))) |>
     mutate(Parameter2 = fct_rev(Parameter2)) |>
-    ggplot(aes(x=Parameter1, y=Parameter2)) +
+    ggplot(aes(x = Parameter1, y = Parameter2)) +
     geom_tile(aes(fill = r), color = "white") +
@@
     labs(title = "Correlation Matrix") +
-    scale_fill_metro_c(limit = c(0, 0.75), guide = guide_colourbar(ticks=FALSE)) +
+    scale_fill_metro_c(limit = c(0, 0.75), guide = guide_colourbar(ticks = FALSE)) +
     theme_minimal() +
-    theme(legend.title = element_blank(),
+    theme(
+      legend.title = element_blank(),
       axis.title.x = element_blank(),
       axis.title.y = element_blank(),
-          axis.text.x = element_text(angle = 45, hjust = 1))
+      axis.text.x = element_text(angle = 45, hjust = 1)
+    )
 }
@@
 
-### EGA
-
+### Graph Analysis
+
+Exploratory Graph Analysis (EGA) is a recently developed framework for psychometric assessment, that can be used to estimate the number of dimensions in questionnaire data using network estimation methods and community detection algorithms, and assess the stability of dimensions and items using bootstrapping.
 See https://r-ega.net/articles/ega.html for details.
@@
 #### Unique Variable Analysis (UVA)
+
+Unique Variable Analysis (Christensen, Garrido, & Golino, 2023) uses the weighted topological overlap measure (Nowick et al., 2009) on an estimated network.
+Values greater than 0.25 are determined to have considerable local dependence (i.e., redundancy) that should be handled (variables with the highest maximum weighted topological overlap to all other variables (other than the one it is redundant with) should be removed).
 
@@
 
-#### Item Stability
+#### Networks
+
+::: {.panel-tabset}
+
+##### All data
 
@@
 
-plots <- list()
-for(model in c("glasso", "TMFG")) {
-  for(algo in c("walktrap", "louvain")) {
-    for(type in c("ega", "ega.fit")) {  # "hierega"
-      print(type)
-      ega <- EGAnet::bootEGA(
-        data = data_all,
-        seed=123,
-        model=model,
-        algorithm=algo,
-        EGA.type=type,
-        type="resampling",
-        plot.itemStability=FALSE,
-        verbose=FALSE)
-      plots[[length(plots) + 1]] <- plot(ega) + 
-        labs(title = paste0(model, " (", algo, ") - ", type))
+make_egas <- function(data) {
+  egas <- list()
+  for (model in c("glasso", "TMFG")) {
+    for (algo in c("walktrap", "louvain")) {
+      for (type in c("ega", "ega.fit")) { # "hierega"
+        if (type == "ega.fit" & algo == "louvain") next # Too slow
+        egas[[paste0(model, "_", algo, "_", type)]] <- EGAnet::bootEGA(
+          data = data,
+          seed = 123,
+          model = model,
+          algorithm = algo,
+          EGA.type = type,
+          type = "resampling",
+          plot.itemStability = FALSE,
+          verbose = FALSE
+        )
       }
@@
 
-length(plots)
-patchwork::wrap_plots(plots, nrow = 4)
-```
-
-<!-- ::: {.panel-tabset} -->
-
-<!-- ##### glasso model (Walktrap) -->
-
-<!-- ```{r ega1} -->
-<!-- #| fig-height: 12 -->
-
-<!-- plots <- list() -->
-<!-- for(d in list(data1, data2, data3, data4, data5, data6)) { -->
-<!--   ega <- EGAnet::bootEGA( -->
-<!--     data = d, -->
-<!--     seed=123, -->
-<!--     model="glasso", -->
-<!--     algorithm="walktrap", -->
-<!--     type="resampling", -->
-<!--     EGA.type="ega", -->
-<!--     plot.itemStability=FALSE,  -->
-<!--     verbose=FALSE) -->
-<!--   plots[[length(plots) + 1]] <- plot(ega) -->
-<!-- } -->
-
-<!-- EGAnet::dimensionStability(ega) -->
-<!-- (plots[[1]] + labs(title = "Sample 1") + -->
-<!--   plots[[2]] + labs(title = "Sample 2")) / -->
-<!--   (plots[[3]] + labs(title = "Sample 3") + -->
-<!--   plots[[4]] + labs(title = "Sample 4")) / -->
-<!--   (plots[[5]] + labs(title = "Sample 5") + -->
-<!--   plots[[6]] + labs(title = "Sample 6")) -->
-<!-- ``` -->
-
-<!-- ##### glasso model (Louvain) -->
-
-<!-- ```{r ega2} -->
-<!-- #| fig-height: 12 -->
-
-<!-- plots <- list() -->
-<!-- for(d in list(data1, data2, data3, data4, data5, data6)) { -->
-<!--   ega <- EGAnet::bootEGA( -->
-<!--     data = d, -->
-<!--     seed=123, -->
-<!--     model="glasso", -->
-<!--     algorithm="louvain", -->
-<!--     plot.itemStability=FALSE) -->
-<!--   plots[[length(plots) + 1]] <- plot(ega) -->
-<!-- } -->
-
-<!-- (plots[[1]] + labs(title = "Sample 1") + -->
-<!--   plots[[2]] + labs(title = "Sample 2")) / -->
-<!--   (plots[[3]] + labs(title = "Sample 3") + -->
-<!--   plots[[4]] + labs(title = "Sample 4")) / -->
-<!--   (plots[[5]] + labs(title = "Sample 5") + -->
-<!--   plots[[6]] + labs(title = "Sample 6")) -->
-<!-- ``` -->
-
-<!-- ##### TMFG model (Walktrap) -->
-
-<!-- ```{r ega3} -->
-<!-- #| fig-height: 12 -->
-
-<!-- plots <- list() -->
-<!-- for(d in list(data1, data2, data3, data4, data5, data6)) { -->
-<!--   ega <- EGAnet::bootEGA( -->
-<!--     data = d, -->
-<!--     seed=123, -->
-<!--     model="TMFG", -->
-<!--     algorithm="walktrap", -->
-<!--     plot.itemStability=FALSE) -->
-<!--   plots[[length(plots) + 1]] <- plot(ega) -->
-<!-- } -->
-
-<!-- (plots[[1]] + labs(title = "Sample 1") + -->
-<!--   plots[[2]] + labs(title = "Sample 2")) / -->
-<!--   (plots[[3]] + labs(title = "Sample 3") + -->
-<!--   plots[[4]] + labs(title = "Sample 4")) / -->
-<!--   (plots[[5]] + labs(title = "Sample 5") + -->
-<!--   plots[[6]] + labs(title = "Sample 6")) -->
-<!-- ``` -->
-
-<!-- ##### TMFG model (Louvain) -->
-
-<!-- ```{r ega4} -->
-<!-- #| fig-height: 12 -->
-
-<!-- plots <- list() -->
-<!-- for(d in list(data1, data2, data3, data4, data5, data6)) { -->
-<!--   ega <- EGAnet::bootEGA( -->
-<!--     data = d, -->
-<!--     seed=123, -->
-<!--     model="TMFG", -->
-<!--     algorithm="louvain", -->
-<!--     plot.itemStability=FALSE) -->
-<!--   plots[[length(plots) + 1]] <- plot(ega) -->
-<!-- } -->
-
-<!-- (plots[[1]] + labs(title = "Sample 1") + -->
-<!--   plots[[2]] + labs(title = "Sample 2")) / -->
-<!--   (plots[[3]] + labs(title = "Sample 3") + -->
-<!--   plots[[4]] + labs(title = "Sample 4")) / -->
-<!--   (plots[[5]] + labs(title = "Sample 5") + -->
-<!--   plots[[6]] + labs(title = "Sample 6")) -->
-<!-- ``` -->
-
-<!-- ##### All data -->
-
-<!-- ```{r ega1} -->
-<!-- #| fig-height: 12 -->
-
-<!-- plots <- list() -->
-<!-- for(model in c("glasso", "TMFG")) { -->
-<!--   for(algo in c("walktrap", "louvain")) { -->
-<!--     ega <- EGAnet::bootEGA( -->
-<!--       data = data_all, -->
-<!--       seed=123, -->
-<!--       model=model, -->
-<!--       algorithm=algo, -->
-<!--       plot.itemStability=FALSE) -->
-<!--     plots[[length(plots) + 1]] <- plot(ega) +  -->
-<!--       labs(title = paste0(model, " (", algo, ")")) -->
-<!--   } -->
-<!-- } -->
-
-<!-- patchwork::wrap_plots(plots) -->
-<!-- ``` -->
-
-<!-- ::: -->
-
-### Exploratory Factor Analysis (EFA)
+  p <- EGAnet::compare.EGA.plots(
+    egas$glasso_walktrap_ega, egas$glasso_walktrap_ega.fit,
+    egas$glasso_louvain_ega, egas$TMFG_louvain_ega,
+    egas$TMFG_walktrap_ega, egas$TMFG_walktrap_ega.fit,
+    labels = c(
+      "glasso_walktrap_ega", "glasso_walktrap_ega.fit",
+      "glasso_louvain_ega", "TMFG_louvain_ega",
+      "TMFG_walktrap_ega", "TMFG_walktrap_ega.fit"
+    ),
+    rows = 3,
+    plot.all = FALSE
+  )$all
+  list(egas = egas, p = p)
+}
+
+egas_all <- make_egas(data_all)
+egas_all$p
+```
+
+##### Sample 1
+
+```{r}
+egas1 <- make_egas(data1)
+egas1$p
+```
+
+##### Sample 2
+
+```{r}
+egas2 <- make_egas(data2)
+egas2$p
+```
+
+##### Sample 3
+
+```{r}
+egas3 <- make_egas(data3)
+egas3$p
+```
+
+##### Sample 4
+
+```{r}
+egas4 <- make_egas(data4)
+egas4$p
+```
+
+##### Sample 5
+
+```{r}
+egas5 <- make_egas(data5)
+egas5$p
+```
+
+##### Sample 6
+
+```{r}
+egas6 <- make_egas(data6)
+egas6$p
+```
+
+##### Sample 7
+
+```{r}
+egas7 <- make_egas(data7)
+egas7$p
+```
+
+:::
+
+#### Structure Stability
+
+::: {.panel-tabset}
+
+```{r}
+#| fig-height: 20
+#| fig-width: 12
+
+patchwork::wrap_plots(lapply(egas_all$egas, plot), nrow = 3)
+```
+
+:::
+
+#### Scores
+
+```{r}
+ega <- egas_all$egas$glasso_louvain_ega$EGA
+plot(ega)
+
+ega_scores_1 <- EGAnet::net.scores(data1, ega)$scores$std.scores |>
+  as.data.frame() |>
+  setNames(c("EGA1", "EGA2", "EGA3", "EGA4"))
+
+ega_scores_2 <- EGAnet::net.scores(data2, ega)$scores$std.scores |>
+  as.data.frame() |>
+  setNames(c("EGA1", "EGA2", "EGA3", "EGA4"))
+
+ega_scores_3 <- EGAnet::net.scores(data3, ega)$scores$std.scores |>
+  as.data.frame() |>
+  setNames(c("EGA1", "EGA2", "EGA3", "EGA4"))
+
+ega_scores_4 <- EGAnet::net.scores(data4, ega)$scores$std.scores |>
+  as.data.frame() |>
+  setNames(c("EGA1", "EGA2", "EGA3", "EGA4"))
+
+ega_scores_5 <- EGAnet::net.scores(data5, ega)$scores$std.scores |>
+  as.data.frame() |>
+  setNames(c("EGA1", "EGA2", "EGA3", "EGA4"))
+
+ega_scores_6 <- EGAnet::net.scores(data6, ega)$scores$std.scores |>
+  as.data.frame() |>
+  setNames(c("EGA1", "EGA2", "EGA3", "EGA4"))
+
+ega_scores_7 <- EGAnet::net.scores(data7, ega)$scores$std.scores |>
+  as.data.frame() |>
+  setNames(c("EGA1", "EGA2", "EGA3", "EGA4"))
+```
+
+### Factor Analysis
 
@@
 
-knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 4, 5 ), ], row.names = FALSE)
+knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 4, 5), ], row.names = FALSE)
 ```
@@
 
-#### EFA Models
+#### EFA
 
@@
 
-efa5 <- parameters::factor_analysis(data_all, n=5, rotation = "oblimin", sort = TRUE)
+efa5 <- parameters::factor_analysis(data_all, n = 5, rotation = "oblimin", sort = TRUE)
 plot(efa5)
@@
 
-efa4 <- parameters::factor_analysis(data2, n=4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data2, n = 4, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
-efa4 <- parameters::factor_analysis(data3, n=4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data3, n = 4, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
-efa5 <- parameters::factor_analysis(data4, n=5, rotation = "oblimin", sort = TRUE)
+efa5 <- parameters::factor_analysis(data4, n = 5, rotation = "oblimin", sort = TRUE)
 plot(efa5)
@@
 
-efa5 <- parameters::factor_analysis(data5, n=5, rotation = "oblimin", sort = TRUE)
+efa5 <- parameters::factor_analysis(data5, n = 5, rotation = "oblimin", sort = TRUE)
 plot(efa5)
@@
 
-efa4 <- parameters::factor_analysis(data5, n=4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data6, n = 4, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
+##### Sample 7
+
+```{r}
+#| fig-height: 10
+
+efa4 <- parameters::factor_analysis(data7, n = 4, rotation = "oblimin", sort = TRUE)
+plot(efa4)
+
+display(efa4)
+```
+
 :::
 
-### Model Construction
+### CFA
 
@@
 
-```{r}
+::: {.panel-tabset}
+
+##### All data
+
+```{r}
+# Ambiguous: Temp + Vomit + Affective_touch + Sex_arousal + Taste
+# Discard: Tickle + Blood_Sugar
+
 m1 <- "
@@
 
+m4 <- "
+Sustenance =~ Hungry + Thirsty + Urinate + Defecate + Muscles + Pain
+Skin =~ Itch + Bruise
+HeartBreathing =~ Breathing + Heart
+Expulsion =~ Cough + Sneeze + Wind + Burp
+"
+
+m5 <- "
+Sustenance =~ Hungry + Thirsty + Pain
+UrinateDefecate =~ Urinate + Defecate
+Skin =~ Itch + Bruise + Muscles
+HeartBreathing =~ Breathing + Heart
+Expulsion =~ Cough + Sneeze + Wind + Burp
+"
+
+m6 <- "
+HungryThirsty =~ Hungry + Thirsty
+UrinateDefecate =~ Urinate + Defecate
+ItchBruise =~ Itch + Bruise
+MusclesPain =~ Muscles + Pain
+HeartBreathing =~ Breathing + Heart
+Expulsion =~ Cough + Sneeze + Wind + Burp
+"
+
 m7 <- "
-# ----
-Sustenance =~ Hungry + Thirsty
-Elimination =~ Urinate + Defecate
-Skin =~ Itch + Bruise
-Nociception =~ Muscles + Pain
-Affect =~ Breathing + Heart
-# ----
-Expulsion =~ Cough + Sneeze + Wind + Burp
-
-# --- 
-# Ambiguous: Temp + Vomit + Affective_touch + Sex_arousal + Taste
-# Discard: Tickle + Blood_Sugar
+HungryThirsty =~ Hungry + Thirsty
+UrinateDefecate =~ Urinate + Defecate
+ItchBruise =~ Itch + Bruise
+MusclesPain =~ Muscles + Pain
+HeartBreathing =~ Breathing + Heart
+CoughSneeze =~ Cough + Sneeze
+WindBurp =~ Wind + Burp
 "
 
-m8 <- "
-# ----
-Sustenance =~ Hungry + Thirsty
-Elimination =~ Urinate + Defecate
-Skin =~ Itch + Bruise
-Nociception =~ Muscles + Pain
-Affect =~ Breathing + Heart
-# ----
-Expulsion_Sudden =~ Cough + Sneeze 
-Expulsion_Gastric =~ Wind + Burp
-" 
-# Ambiguous: Temp + Vomit + Affective_touch + Sex_arousal + Taste
-# Discard: Tickle + Blood_Sugar
-
 m1_all <- lavaan::cfa(m1, data = data_all)
+m4_all <- lavaan::cfa(m4, data = data_all)
+m5_all <- lavaan::cfa(m5, data = data_all)
+m6_all <- lavaan::cfa(m6, data = data_all)
 m7_all <- lavaan::cfa(m7, data = data_all)
-m8_all <- lavaan::cfa(m8, data = data_all)
-
-anova(m1_all, m7_all, m8_all) |> 
-  parameters::parameters() |> 
-  display()
-```
+
+anova(m1_all, m4_all, m5_all, m6_all, m7_all) |>
+  parameters::parameters() |>
+  display()
+
+parameters::parameters(m7_all, standardize=TRUE) |>
+  display()
+```
+
+##### Sample 1
+
+```{r}
+anova(
+  lavaan::cfa(m1, data = data1),
+  lavaan::cfa(m4, data = data1),
+  lavaan::cfa(m5, data = data1),
+  lavaan::cfa(m6, data = data1),
+  lavaan::cfa(m7, data = data1)
+  ) |>
+  parameters::parameters() |>
+  display()
+```
+
+##### Sample 2
+
+```{r}
+anova(
+  lavaan::cfa(m1, data = data2),
+  lavaan::cfa(m4, data = data2),
+  lavaan::cfa(m5, data = data2),
+  lavaan::cfa(m6, data = data2),
+  lavaan::cfa(m7, data = data2)
+  ) |>
+  parameters::parameters() |>
+  display()
+```
+
+##### Sample 3
+
+```{r}
+anova(
+  lavaan::cfa(m1, data = data3),
+  lavaan::cfa(m4, data = data3),
+  lavaan::cfa(m5, data = data3),
+  lavaan::cfa(m6, data = data3),
+  lavaan::cfa(m7, data = data3)
+  ) |>
+  parameters::parameters() |>
+  display()
+```
+
+##### Sample 4
+
+```{r}
+anova(
+  lavaan::cfa(m1, data = data4),
+  lavaan::cfa(m4, data = data4),
+  lavaan::cfa(m5, data = data4),
+  lavaan::cfa(m6, data = data4),
+  lavaan::cfa(m7, data = data4)
+  ) |>
+  parameters::parameters() |>
+  display()
+```
+
+##### Sample 5
+
+```{r}
+anova(
+  lavaan::cfa(m1, data = data5),
+  lavaan::cfa(m4, data = data5),
+  lavaan::cfa(m5, data = data5),
+  lavaan::cfa(m6, data = data5),
+  lavaan::cfa(m7, data = data5)
+  ) |>
+  parameters::parameters() |>
+  display()
+```
+
+##### Sample 6
+
+```{r}
+anova(
+  lavaan::cfa(m1, data = data6),
+  lavaan::cfa(m4, data = data6),
+  lavaan::cfa(m5, data = data6),
+  lavaan::cfa(m6, data = data6),
+  lavaan::cfa(m7, data = data6)
+  ) |>
+  parameters::parameters() |>
+  display()
+```
+
+##### Sample 7
+
+```{r}
+anova(
+  lavaan::cfa(str_remove(m5, fixed("Cough + ")), data = data7),
+  lavaan::cfa(str_remove(m1, fixed("Cough + ")), data = data7),
+  lavaan::cfa(str_remove(m4, fixed("Cough + ")), data = data7),
+  lavaan::cfa(str_remove(m6, fixed("Cough + ")), data = data7),
+  lavaan::cfa(str_remove(m7, fixed("\nCoughSneeze =~ Cough + Sneeze")), data = data7)
+  ) |>
+  parameters::parameters() |>
+  display()
+```
+
+:::
 
@@
 
-```{r}
-m8h1 <- paste0(m8, "
-              Interoception =~ Sustenance + Elimination + Skin + Nociception + Affect + Expulsion_Sudden + Expulsion_Gastric
+::: {.panel-tabset}
+
+##### All data
+
+```{r}
+m7h1 <- paste0(m7, "
+              Interoception =~ HungryThirsty + UrinateDefecate + ItchBruise + MusclesPain + HeartBreathing + CoughSneeze + WindBurp
               ")
 
-m8h3 <- paste0(m8, "
-              Valenced =~ Nociception + Affect + Skin
-              Expulsion =~ Expulsion_Sudden + Expulsion_Gastric 
-              Homeostasis =~ Sustenance + Elimination
+m7h3 <- paste0(m7, "
+              Valenced =~ MusclesPain + HeartBreathing + ItchBruise
+              Expulsion =~ CoughSneeze + WindBurp
+              Homeostasis =~ HungryThirsty + UrinateDefecate
               ")
 
-m8h1_all <- lavaan::cfa(m8h1, data = data_all)
-m8h3_all <- lavaan::cfa(m8h3, data = data_all)
-anova(m8_all, m8h1_all, m8h3_all) |> 
-  parameters::parameters() |> 
-  display()
-```
+m7h1_all <- lavaan::cfa(m7h1, data = data_all)
+m7h3_all <- lavaan::cfa(m7h3, data = data_all)
+anova(m7_all, m7h1_all, m7h3_all) |>
+  parameters::parameters() |>
+  display()
+```
+
+##### Sample 1
+
+```{r}
+anova(
+  lavaan::cfa(m7, data = data1), 
+  lavaan::cfa(m7h1, data = data1), 
+  lavaan::cfa(m7h3, data = data1)) |>
+  parameters::parameters() |>
+  display()
+```
+
+##### Sample 2
+
+```{r}
+anova(
+  lavaan::cfa(m7, data = data2), 
+  lavaan::cfa(m7h1, data = data2), 
+  lavaan::cfa(m7h3, data = data2)) |>
+  parameters::parameters() |>
+  display()
+```
+
+##### Sample 3
+
+```{r}
+anova(
+  lavaan::cfa(m7, data = data3), 
+  lavaan::cfa(m7h1, data = data3), 
+  lavaan::cfa(m7h3, data = data3)) |>
+  parameters::parameters() |>
+  display()
+```
+
+##### Sample 4
+
+```{r}
+anova(
+  lavaan::cfa(m7, data = data4), 
+  lavaan::cfa(m7h1, data = data4), 
+  lavaan::cfa(m7h3, data = data4)) |>
+  parameters::parameters() |>
+  display()
+```
+
+##### Sample 5
+
+```{r}
+anova(
+  lavaan::cfa(m7, data = data5), 
+  lavaan::cfa(m7h1, data = data5), 
+  lavaan::cfa(m7h3, data = data5)) |>
+  parameters::parameters() |>
+  display()
+```
+
+##### Sample 6
+
+```{r}
+anova(
+  lavaan::cfa(m7, data = data6), 
+  lavaan::cfa(m7h1, data = data6), 
+  lavaan::cfa(m7h3, data = data6)) |>
+  parameters::parameters() |>
+  display()
+```
+
+##### Sample 7
+
+None of the model can be properly estimated (variances are negative).
+
+```{r}
+NA
+# anova(
+#   lavaan::cfa(str_remove(m7, fixed("\nCoughSneeze =~ Cough + Sneeze")), data = data7), 
+#   lavaan::cfa(str_remove(str_remove(m7h1, fixed("\nCoughSneeze =~ Cough + Sneeze")), fixed("CoughSneeze +")), data = data7), 
+#   lavaan::cfa(str_remove(str_remove(m7h3, fixed("\nCoughSneeze =~ Cough + Sneeze")), fixed("CoughSneeze +")), data = data7)) |>
+#   parameters::parameters() |>
+#   display()
+```
+
+:::
 
@@
 rbind(
-  performance::performance(m8_all, metrics=c("Chi2", "RMSEA", "CFI", "SRMR")) |> 
+  performance::performance(m7_all, metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
     mutate(Sample = "All"),
-  performance::performance(update(m8_all, data=data1), metrics=c("Chi2", "RMSEA", "CFI", "SRMR")) |> 
+  performance::performance(update(m7_all, data = data1), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
     mutate(Sample = "Sample 1"),
-  performance::performance(update(m8_all, data=data2), metrics=c("Chi2", "RMSEA", "CFI", "SRMR")) |>
+  performance::performance(update(m7_all, data = data2), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
     mutate(Sample = "Sample 2"),
-  performance::performance(update(m8_all, data=data3), metrics=c("Chi2", "RMSEA", "CFI", "SRMR")) |>
+  performance::performance(update(m7_all, data = data3), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
     mutate(Sample = "Sample 3"),
-  performance::performance(update(m8_all, data=data4), metrics=c("Chi2", "RMSEA", "CFI", "SRMR")) |>
+  performance::performance(update(m7_all, data = data4), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
     mutate(Sample = "Sample 4"),
-  performance::performance(update(m8_all, data=data5), metrics=c("Chi2", "RMSEA", "CFI", "SRMR")) |>
+  performance::performance(update(m7_all, data = data5), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
     mutate(Sample = "Sample 5"),
-  performance::performance(update(m8_all, data=data6), metrics=c("Chi2", "RMSEA", "CFI", "SRMR")) |>
+  performance::performance(update(m7_all, data = data6), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
     mutate(Sample = "Sample 6"),
-  performance::performance(lavaan::cfa(str_remove(m8, fixed("\nExpulsion_Sudden =~ Cough + Sneeze")), data=data7), metrics=c("Chi2", "RMSEA", "CFI", "SRMR")) |>
+  performance::performance(lavaan::cfa(str_remove(m7, fixed("\nCoughSneeze =~ Cough + Sneeze")), data = data7), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
     mutate(Sample = "Sample 7")
@@
 
-No evidence for higher order factors. The unidimensionality might be a byproduct of the similarities in phrasing of the items.
+No evidence for higher order factors.
+
+### Scores
+
+Note the usage of descriptive factor names relating directly to the items to avoid abstraction.
+
+```{r}
+#| warning: false
+
+scores <- list(
+  sample1 = cbind(ega_scores_1, as.data.frame(predict(lavaan::cfa(m7, data = data1)))) |>
+    mutate(Sample = "Sample 1"),
+  sample2 = cbind(ega_scores_2, as.data.frame(predict(lavaan::cfa(m7, data = data2)))) |>
+    mutate(Sample = "Sample 2"),
+  sample3 = cbind(ega_scores_3, as.data.frame(predict(lavaan::cfa(m7, data = data3)))) |>
+    mutate(Sample = "Sample 3"),
+  sample4 = cbind(ega_scores_4, as.data.frame(predict(lavaan::cfa(m7, data = data4)))) |>
+    mutate(Sample = "Sample 4"),
+  sample5 = cbind(ega_scores_5, as.data.frame(predict(lavaan::cfa(m7, data = data5)))) |>
+    mutate(Sample = "Sample 5"),
+  sample6 = cbind(ega_scores_6, as.data.frame(predict(lavaan::cfa(m7, data = data6)))) |>
+    mutate(Sample = "Sample 6"),
+  sample7 = cbind(ega_scores_7, as.data.frame(predict(lavaan::cfa(str_remove(m7, fixed("\nCoughSneeze =~ Cough + Sneeze")), data = data7)))) |>
+    mutate(Sample = "Sample 7", CoughSneeze = NA)
+)
+
+save(scores, file = "../data/scores.RData")
+```
 
@@
 
-df1 <- cbind(df1, as.data.frame(predict(lavaan::cfa(m8, data = data1)))) |> 
-  mutate(Sample = "Sample 1")
-df2 <- cbind(df2, as.data.frame(predict(lavaan::cfa(m8, data = data2)))) |> 
-  mutate(Sample = "Sample 2")
-df3 <- cbind(df3, as.data.frame(predict(lavaan::cfa(m8, data = data3)))) |> 
-  mutate(Sample = "Sample 3")
-df4 <- cbind(df4, as.data.frame(predict(lavaan::cfa(m8, data = data4)))) |> 
-  mutate(Sample = "Sample 4")
-df5 <- cbind(df5, as.data.frame(predict(lavaan::cfa(m8, data = data5)))) |> 
-  mutate(Sample = "Sample 5")
-df6 <- cbind(df6, as.data.frame(predict(lavaan::cfa(m8, data = data6)))) |> 
-  mutate(Sample = "Sample 6")
-df7 <- cbind(df7, as.data.frame(predict(lavaan::cfa(str_remove(m8, fixed("\nExpulsion_Sudden =~ Cough + Sneeze")), data = data7)))) |> 
-  mutate(Sample = "Sample 7", Expulsion_Sudden = NA)
-
-vars <- names(as.data.frame(predict(m8_all)))
-```
-
-### Demographics
-
-```{r}
-df_demo <- rbind(
-  select(df1, Sample, Age, Gender, all_of(vars)),
-  select(df2, Sample, Age, Gender, all_of(vars)),
-  select(df3, Sample, Age, Gender, all_of(vars)),
-  select(df4, Sample, Age, Gender, all_of(vars)),
-  select(df5, Sample, Age, Gender, all_of(vars)),
-  select(df6, Sample, Age, Gender, all_of(vars)),
-  select(df7, Sample, Age, Gender, all_of(vars))
-)
-
-make_lm_data <- function(df, vars, predictor="Age") {
-  dat <- data.frame()
-  for(resp in vars) {
-      if(length(unique(df$Sample)) == 1) {
-        m <- lm(as.formula(paste0(resp, " ~ ", predictor)), data = df)
-        param <- parameters::parameters(m)[2, ] |> 
-          mutate(Sample = unique(df$Sample)) |> 
-          select(-Parameter)
-      } else {
-        m <- lm(as.formula(paste0(resp, " ~ Sample / ", predictor)), data = df)
-        param <- parameters::parameters(m) |> 
-          filter(str_detect(Parameter, ":")) |> 
-          separate(Parameter, c("Predictor", "Sample"), sep = "Sample ") |> 
-          mutate(Sample = paste0("Sample ", str_remove(Sample, fixed(paste0(":", predictor)))))
-      }
-
-      dat <- param |> 
-        mutate(Predictor = predictor,
-               Repsonse = resp,
-               t_low = CI_low / SE,
-               t_high = CI_high / SE) |> 
-        rbind(dat)
-  }
-  dat
-}
-
-data <- rbind(
-  make_lm_data(df_demo, vars, predictor="Age"),
-  make_lm_data(filter(df_demo, Gender %in% c("Male", "Female")), vars, predictor="Gender")
-)
-```
-
-### BPQ
-
-```{r}
-x <- intersect(names(df3)[str_detect(names(df3), "BPQ")], 
-               names(df4)[str_starts(names(df4), "BPQ")])
-
-df_bpq <- rbind(
-  select(df3, Sample, all_of(x), all_of(vars)),
-  select(df4, Sample, all_of(x), all_of(vars))
-)
-
-# estimate_density(select(df_bpq, Sample, starts_with("BPQ")), at="Sample")  |> 
-#   plot() +
-#   facet_grid(~Sample)
-
-plot(parameters::n_components(select(df_bpq, starts_with("BPQ"))))
-df_bpq$BPQ_PCA1 <- predict(parameters::principal_components(select(df_bpq, starts_with("BPQ")), n=1))$PC1
-
-data <- rbind(data,
-              make_lm_data(df_bpq, vars, predictor="BPQ_PCA1"))
-
-# Why opposite effects?
-```
-
-### TAS
-
-```{r}
-x <- intersect(names(df3)[str_detect(names(df3), "TAS")], 
-               names(df5)[str_starts(names(df5), "TAS")])
-```
-
-### PHQ
-
-```{r}
-names(df5)[str_detect(names(df5), "PHQ")]
-
-data <- rbind(data,
-              make_lm_data(df5, vars, predictor="PHQ9_sum"),
-              make_lm_data(df5, vars, predictor="PHQ15_sum"))
-```
-
-### BDI
-
-```{r}
+load("../data/scores.RData")
+
+df1 <- cbind(df1, scores$sample1)
+df2 <- cbind(df2, scores$sample2)
+df3 <- cbind(df3, scores$sample3)
+df4 <- cbind(df4, scores$sample4)
+df5 <- cbind(df5, scores$sample5)
+df6 <- cbind(df6, scores$sample6)
+df7 <- cbind(df7, scores$sample7)
+
+vars_intero <- names(select(scores$sample1, -Sample))
+vars_cfa <- names(select(scores$sample1, -Sample, -starts_with("EGA")))
+vars_cfa7 <- vars_cfa[vars_cfa != "CoughSneeze"]
+
 # names(df1)
@@
 # names(df6)  # BDI, STAI
-# names(df7)  # MAIA
-
-data <- rbind(data,
-              make_lm_data(df6, vars, predictor="BDI2_Total"))
+# names(df7)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
+```
+
+### EGA and CFA
+
+```{r}
+#| warning: false
+
+df_scores <- rbind(
+  select(df1, all_of(vars_intero)),
+  select(df2, all_of(vars_intero)),
+  select(df3, all_of(vars_intero)),
+  select(df4, all_of(vars_intero)),
+  select(df5, all_of(vars_intero)),
+  select(df6, all_of(vars_intero)),
+  select(df7, all_of(vars_intero))
+)
+
+correlation::correlation(df_scores, redundant = TRUE) |>
+    correlation::cor_sort() |>
+    correlation::cor_lower() |>
+    mutate(val = paste0(insight::format_value(r), format_p(p, stars_only = TRUE))) |>
+    mutate(Parameter2 = fct_rev(Parameter2)) |>
+    ggplot(aes(x = Parameter1, y = Parameter2)) +
+    geom_tile(aes(fill = r), color = "white") +
+    geom_text(aes(label = val), size = 3) +
+    labs(title = "Correlation Matrix") +
+    scale_fill_metro_c(limit = c(0, 1), guide = guide_colourbar(ticks = FALSE)) +
+    theme_minimal() +
+    theme(
+      legend.title = element_blank(),
+      axis.title.x = element_blank(),
+      axis.title.y = element_blank(),
+      axis.text.x = element_text(angle = 45, hjust = 1)
+    )
+```
+
+### Demographics
+
+```{r}
+make_diff <- function(df, vars, component=NA) {
+  dat <- data.frame()
+  for (resp in vars) {
+    f <- as.formula(paste0(resp, "~ Gender"))
+    d <- filter(df, Gender %in% c("Male", "Female")) |> 
+      mutate(Gender = fct_relevel(Gender, "Male", "Female"))
+    dat <- effectsize::cohens_d(f, data=d) |> 
+      mutate(var_Correlate = "Gender", var_Interoception = resp, 
+             p=t.test(f, data=d)$p.val) |> 
+      as.data.frame() |> 
+      rbind(dat)
+  }
+
+  dat$r <- effectsize::d_to_r(dat$Cohens_d, n1=sum(df$Gender=="Male"), n2=sum(df$Gender=="Female"))
+  dat$CI_low <- effectsize::d_to_r(dat$CI_low, n1=sum(df$Gender=="Male"), n2=sum(df$Gender=="Female"))
+  dat$CI_high <- effectsize::d_to_r(dat$CI_high, n1=sum(df$Gender=="Male"), n2=sum(df$Gender=="Female"))
+  dat$Sample <- unique(df$Sample)
+  dat$Component <- component
+  select(dat, -Cohens_d)
+}
+
+data <- rbind(
+  make_diff(df1, vars_cfa, component="Demographic"),
+  make_diff(df2, vars_cfa, component="Demographic"),
+  make_diff(df3, vars_cfa, component="Demographic"),
+  make_diff(df4, vars_cfa, component="Demographic"),
+  make_diff(df5, vars_cfa, component="Demographic"),
+  make_diff(df6, vars_cfa, component="Demographic"),
+  make_diff(df7, vars_cfa7, component="Demographic")
+) |> 
+  mutate(var_Correlate = "Gender (Male vs. Female)")
+```
+
+```{r}
+make_cor <- function(df, vars, with = "Age", component=NA) {
+  dat <- data.frame() 
+  for (v in vars) {
+    dat <- correlation::cor_test(df, v, with) |> 
+      rename(var_Interoception = Parameter1, var_Correlate = Parameter2) |> 
+      as.data.frame() |> 
+      rbind(dat)
+  }
+
+  dat$Sample <- unique(df$Sample)
+  dat$Component <- component
+  select(dat, -df_error, -t, -Method, -n_Obs)
+}
+
+data <- rbind(
+  data,
+  make_cor(df1, vars_cfa, with = "Age", component="Demographic"),
+  make_cor(df2, vars_cfa, with = "Age", component="Demographic"),
+  make_cor(df3, vars_cfa, with = "Age", component="Demographic"),
+  make_cor(df4, vars_cfa, with = "Age", component="Demographic"),
+  make_cor(df5, vars_cfa, with = "Age", component="Demographic"),
+  make_cor(df6, vars_cfa, with = "Age", component="Demographic"),
+  make_cor(df7, vars_cfa7, with = "Age", component="Demographic")
+) 
+```
+
+### Body
+
+```{r}
+# Reverse (TODO: Ana confirm why)
+df3$BPQ_BodyAwareness <- -1*normalize(df3$BPQ_BodyAwareness)
+df3$BPQ_AutonomicReactivity <- -1*normalize(df3$BPQ_AutonomicReactivity)
+
+data <- rbind(
+  data,
+  make_cor(df3, vars_cfa, with = "BPQ_BodyAwareness", component="Body") |> 
+    mutate(var_Correlate = "Body Awareness"),
+  make_cor(df3, vars_cfa, with = "BPQ_AutonomicReactivity", component="Body") |> 
+    mutate(var_Correlate = "Autonomic Reactivity"),
+  make_cor(df4, vars_cfa, with = "BPQ_A", component="Body") |> 
+    mutate(var_Correlate = "Body Awareness")
+)
+```
+
+```{r}
+data <- rbind(
+  data,
+  make_cor(df7, vars_cfa7, with = "MAIA_AttentionRegulation", component="MAIA")  |> 
+    mutate(var_Correlate = "Attention Regulation"),
+  make_cor(df7, vars_cfa7, with = "MAIA_BodyListening", component="MAIA") |> 
+    mutate(var_Correlate = "Body Listening"),
+  make_cor(df7, vars_cfa7, with = "MAIA_EmotionalAwareness", component="MAIA") |> 
+    mutate(var_Correlate = "Emotional Awareness"),
+  make_cor(df7, vars_cfa7, with = "MAIA_NotDistracting", component="MAIA") |> 
+    mutate(var_Correlate = "Not Distracting"),
+  make_cor(df7, vars_cfa7, with = "MAIA_Noticing", component="MAIA") |> 
+    mutate(var_Correlate = "Noticing"),
+  make_cor(df7, vars_cfa7, with = "MAIA_NotWorrying", component="MAIA") |> 
+    mutate(var_Correlate = "Not Worrying"),
+  make_cor(df7, vars_cfa7, with = "MAIA_SelfRegulation", component="MAIA") |> 
+    mutate(var_Correlate = "Self Regulation"),
+  make_cor(df7, vars_cfa7, with = "MAIA_Trusting", component="MAIA") |> 
+    mutate(var_Correlate = "Trusting")
+)
+```
+
+```{r}
+# names(df3)[str_detect(names(df3), "TAS")]
+# names(df5)[str_starts(names(df5), "TAS")]
+
+data <- rbind(
+  data,
+  make_cor(df3, vars_cfa, with = "TAS_IdentifyingFeelings", component="Body") |> 
+    mutate(var_Correlate = "Difficulties Identifying Feelings"),
+  make_cor(df3, vars_cfa, with = "TAS_DescribingFeelings", component="Body") |> 
+    mutate(var_Correlate = "Difficulties Describing Feelings"),
+  make_cor(df3, vars_cfa, with = "TAS_ExternallyOrientedThinking", component="Body") |> 
+    mutate(var_Correlate = "External Thinking"),
+  make_cor(df5, vars_cfa, with = "TAS_DIF", component="Body") |> 
+    mutate(var_Correlate = "Difficulties Identifying Feelings"),
+  make_cor(df5, vars_cfa, with = "TAS_DDF", component="Body") |> 
+    mutate(var_Correlate = "Difficulties Describing Feelings")
+)
+```
+
+### Mood
+
+```{r}
+data <- rbind(
+  data,
+  make_cor(df5, vars_cfa, with = "PHQ15_sum", component="Mood") |> 
+    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
+  make_cor(df5, vars_cfa, with = "PHQ9_sum", component="Mood")|> 
+    mutate(var_Correlate = "Depression (PHQ-9)"),
+  make_cor(df7, vars_cfa7, with = "PHQ4_Depression", component="Mood") |> 
+    mutate(var_Correlate = "Depression (PHQ-4)"),
+  make_cor(df7, vars_cfa7, with = "PHQ4_Anxiety", component="Mood") |> 
+    mutate(var_Correlate = "Anxiety (PHQ-4)")
+)
+```
+
+```{r}
+data <- rbind(
+  data,
+  make_cor(df6, vars_cfa, with = "BDI2_Total", component="Mood") |> 
+    mutate(var_Correlate = "Depression (BDI-II)")
+)
+```
+
+```{r}
+data <- rbind(
+  data,
+  make_cor(df6, vars_cfa, with = "STAI5_General", component="Mood") |> 
+    mutate(var_Correlate = "Anxiety (STAI-5)")
+)
+```
+
+```{r}
+data <- rbind(
+  data,
+  make_cor(df7, vars_cfa7, with = "BPD", component="Mood") |> 
+    mutate(var_Correlate = "Boderline Personality")
+)
+```
+
+### Psychopathology
+
+```{r}
+data <- rbind(
+  data,
+  make_cor(df7, vars_cfa7, with = "PID5_Antagonism", component="Maladaptive") |> 
+    mutate(var_Correlate = "Antagonism"),
+  make_cor(df7, vars_cfa7, with = "PID5_Detachment", component="Maladaptive") |> 
+    mutate(var_Correlate = "Detachment"),
+  make_cor(df7, vars_cfa7, with = "PID5_Disinhibition", component="Maladaptive") |> 
+    mutate(var_Correlate = "Disinhibition"),
+  make_cor(df7, vars_cfa7, with = "PID5_NegativeAffect", component="Maladaptive") |> 
+    mutate(var_Correlate = "Negative Affect"),
+  make_cor(df7, vars_cfa7, with = "PID5_Psychoticism", component="Maladaptive") |> 
+    mutate(var_Correlate = "Psychoticism")
+)
+```
+
+```{r}
+data <- rbind(
+  data,
+  make_cor(df7, vars_cfa7, with = "SPQ_ConstrictedAffect", component="Schizotypic") |> 
+    mutate(var_Correlate = "Constricted Affect"),
+  make_cor(df7, vars_cfa7, with = "SPQ_Eccentric", component="Schizotypic") |> 
+    mutate(var_Correlate = "Eccentric"),
+  make_cor(df7, vars_cfa7, with = "SPQ_MagicalThinking", component="Schizotypic") |> 
+    mutate(var_Correlate = "Magical Thinking"),
+  make_cor(df7, vars_cfa7, with = "SPQ_NoCloseFriends", component="Schizotypic") |> 
+    mutate(var_Correlate = "No Close Friends"),
+  make_cor(df7, vars_cfa7, with = "SPQ_OddSpeech", component="Schizotypic") |> 
+    mutate(var_Correlate = "Odd Speech"),
+  make_cor(df7, vars_cfa7, with = "SPQ_Reference", component="Schizotypic") |> 
+    mutate(var_Correlate = "Reference"),
+  make_cor(df7, vars_cfa7, with = "SPQ_SocialAnxiety", component="Schizotypic") |> 
+    mutate(var_Correlate = "Social Anxiety"),
+  make_cor(df7, vars_cfa7, with = "SPQ_Suspiciousness", component="Schizotypic") |> 
+    mutate(var_Correlate = "Suspiciousness"),
+  make_cor(df7, vars_cfa7, with = "SPQ_UnusualPerceptions", component="Schizotypic") |> 
+    mutate(var_Correlate = "Unusual Perceptions")
+)
+```
+
+```{r}
+#  names(select(df7, starts_with("ASQ")))
+data <- rbind(
+  data,
+  make_cor(df7, vars_cfa7, with = "ASQ_Imagination", component="Autistic") |> 
+    mutate(var_Correlate = "Imagination"),
+  make_cor(df7, vars_cfa7, with = "ASQ_LackSocialSkills", component="Autistic") |>
+    mutate(var_Correlate = "Lack of Social Skills"),
+  make_cor(df7, vars_cfa7, with = "ASQ_LowAttentionalSwitching", component="Autistic") |>
+    mutate(var_Correlate = "Low Attentional Switching"),
+  make_cor(df7, vars_cfa7, with = "ASQ_Patterns", component="Autistic") |>
+    mutate(var_Correlate = "Patterns and Numbers"),
+  make_cor(df7, vars_cfa7, with = "ASQ_Routine", component="Autistic") |>
+    mutate(var_Correlate = "Routines")
+)
+```
+
+### Personality
+
+```{r}
+data <- rbind(
+  data,
+  make_cor(df7, vars_cfa7, with = "IPIP6_Agreeableness", component="Personality") |> 
+    mutate(var_Correlate = "Agreeableness"),
+  make_cor(df7, vars_cfa7, with = "IPIP6_Conscientiousness", component="Personality") |>
+    mutate(var_Correlate = "Conscientiousness"),
+  make_cor(df7, vars_cfa7, with = "IPIP6_Neuroticism", component="Personality") |>
+    mutate(var_Correlate = "Neuroticism"),
+  make_cor(df7, vars_cfa7, with = "IPIP6_Openness", component="Personality") |>
+    mutate(var_Correlate = "Openness"),
+  make_cor(df7, vars_cfa7, with = "IPIP6_Extraversion", component="Personality") |>
+    mutate(var_Correlate = "Extraversion"),
+  make_cor(df7, vars_cfa7, with = "IPIP6_HonestyHumility", component="Personality") |>
+    mutate(var_Correlate = "Honesty-Humility")
+)
+```
+
+```{r}
+data <- rbind(
+  data,
+  make_cor(df7, vars_cfa7, with = "PI_Alive", component="World Beliefs") |> 
+    mutate(var_Correlate = "Alive"),
+  make_cor(df7, vars_cfa7, with = "PI_Changing", component="World Beliefs") |>
+    mutate(var_Correlate = "Changing"),
+  make_cor(df7, vars_cfa7, with = "PI_Enticing", component="World Beliefs") |>
+    mutate(var_Correlate = "Enticing"),
+  make_cor(df7, vars_cfa7, with = "PI_Good", component="World Beliefs") |>
+    mutate(var_Correlate = "Good"),
+  make_cor(df7, vars_cfa7, with = "PI_Hierarchical", component="World Beliefs") |>
+    mutate(var_Correlate = "Hierarchical"),
+  make_cor(df7, vars_cfa7, with = "PI_Safe", component="World Beliefs") |>
+    mutate(var_Correlate = "Safe")
+)
+```
+
+```{r}
+data <- rbind(
+  data,
+  make_cor(df7, vars_cfa7, with = "GCBS_Extraterrestrial", component="Conspiracy Beliefs") |> 
+    mutate(var_Correlate = "Extraterrestrial"),
+  make_cor(df7, vars_cfa7, with = "GCBS_GlobalConspiracies", component="Conspiracy Beliefs") |>
+    mutate(var_Correlate = "Global Conspiracies"),
+  make_cor(df7, vars_cfa7, with = "GCBS_GovernmentMalfeasance", component="Conspiracy Beliefs") |>
+    mutate(var_Correlate = "Government Malfeasance"),
+  make_cor(df7, vars_cfa7, with = "GCBS_InformationControl", component="Conspiracy Beliefs") |>
+    mutate(var_Correlate = "Information Control"),
+  make_cor(df7, vars_cfa7, with = "GCBS_PersonalWellbeing", component="Conspiracy Beliefs") |>
+    mutate(var_Correlate = "Personal Wellbeing")
+)
+```
+
+```{r}
+data <- rbind(
+  data,
+  make_cor(df7, vars_cfa7, with = "LIE_Ability", component="Lying Profile") |> 
+    mutate(var_Correlate = "Ability"),
+  make_cor(df7, vars_cfa7, with = "LIE_Frequency", component="Lying Profile") |>
+    mutate(var_Correlate = "Frequency"),
+  make_cor(df7, vars_cfa7, with = "LIE_Contextuality", component="Lying Profile") |>
+    mutate(var_Correlate = "Contextuality"),
+  make_cor(df7, vars_cfa7, with = "LIE_Negativity", component="Lying Profile") |>
+    mutate(var_Correlate = "Negativity")
+)
 ```
@@
 #| fig-height: 20
-
-data |> 
-  mutate(sig = ifelse(p < .01, "p < .01", ifelse(p < .001, "p < .001", "N.S."))) |> 
-  ggplot(aes(x=Predictor)) +
-  geom_hline(yintercept=0, linetype="dashed") +
-  geom_pointrange(aes(y=t, ymin=t_low, ymax=t_high, color=sig), position=position_dodge2(width=0.3)) +
-  facet_grid(~Repsonse, scales = "free_y") +
-  coord_flip()
+#| fig-width: 15
+
+p <- data |>
+  mutate(sig = ifelse(p < .01, "p < .01", ifelse(p < .001, "p < .001", "N.S.")),
+         dir = sign(r),
+         var_Interoception = str_replace(var_Interoception, "CoughSneeze", "Cough/Sneeze"),
+         var_Interoception = str_replace(var_Interoception, "HeartBreathing", "Heart/Breathing"),
+         var_Interoception = str_replace(var_Interoception, "HungryThirsty", "Hungry/Thirsty"),
+         var_Interoception = str_replace(var_Interoception, "ItchBruise", "Itch/Bruise"),
+         var_Interoception = str_replace(var_Interoception, "MusclesPain", "Muscles/Pain"),
+         var_Interoception = str_replace(var_Interoception, "UrinateDefecate", "Urinate/Defecate"),
+         var_Interoception = str_replace(var_Interoception, "WindBurp", "Wind/Burp"),
+         var_Interoception = str_replace(var_Interoception, "Expulsion_Sudden", "Expulsion - Sudden"),
+         var_Interoception = fct_relevel(var_Interoception, "Heart/Breathing", "Muscles/Pain", "Itch/Bruise", "Hungry/Thirsty", "Urinate/Defecate", "Wind/Burp", "Cough/Sneeze"),
+         Component = fct_relevel(
+           Component, "Demographic", "MAIA", "Body", "Mood", "Maladaptive",
+           "Schizotypic", "Autistic", "Personality", "Conspiracy Beliefs", "World Beliefs", "Lying Profile")) |>
+  ggplot(aes(x = var_Correlate)) +
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  # geom_bar(aes(fill=Sample, alpha=sig, y=r, group=Sample), stat="identity", position = position_dodge2(width = 0.8)) +
+  geom_linerange(aes(color=dir, alpha=sig, ymin=0, ymax=r, group=Sample), position = position_dodge2(width = 0.7), linewidth=2.5) +
+  geom_linerange(aes(ymin = CI_low, ymax = CI_high, color = dir, alpha=sig, group=Sample), position = position_dodge2(width = 0.7)) +
+  scale_fill_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
+  scale_color_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
+  scale_alpha_discrete(range = c(0.2, 0.7), guide = "none") +
+  scale_y_continuous(expand = c(0, 0), breaks = c(-0.3, 0, 0.3)) +
+  facet_grid(Component ~ var_Interoception, scales = "free_y", switch = "y") +
+  coord_flip(ylim = c(-0.45, 0.45)) +
+  theme_modern(axis.title.space = 5) +
+  theme(panel.grid.major.y = element_line(),
+        axis.title.y = element_blank(),
+        axis.line.x = element_blank(),
+        axis.text.y = element_text(size = rel(0.5)),
+        axis.text.x = element_text(size = rel(0.8)),
+        plot.title = element_text(face = "bold", hjust = 0),
+        strip.placement = "outside",
+        strip.background.y = element_rect(fill = "#E0E0E0", color = "white"),
+        strip.background.x = element_rect(fill = "#F8BBD0", color = "white")) 
+ggsave("figures/Figure2.png", p, width=21*0.6, height=29.7*0.45, dpi=200, bg="white")
+p
 ```

### 2024-02-20 analysis/analysis.qmd
add fig 1

@@
 
+The items with the differing distribution pattern (with a lower mode around 2/5) are "Affective Touch", "Blood Sugar" and "Bruise".
+
 ```{r}
@@
 
-rbind(dens1, dens2, dens3, dens4, dens5, dens6, dens7) |>
+p1 <- rbind(dens1, dens2, dens3, dens4, dens5, dens6, dens7) |>
+  # mutate(Dashed = ifelse(Parameter %in% c("Affective_touch", "Blood_Sugar", "Bruise"), TRUE, FALSE)) |> 
   ggplot(aes(x = x, y = y, color = Parameter)) +
   geom_line() +
+  scale_color_material_d() +
+  scale_linetype_manual(values = c("solid", "dashed"), guide="none") +
   theme_minimal() +
-  labs(title = "Distribution of Responses", x = "Response", y = "Density", color = "Item") +
+  theme(axis.text.y = element_blank(),
+        plot.title = element_text(face="bold", hjust=0.5)) +
+  labs(title = "Distribution of responses for all items across various datasets", x = "Response", y = "Density", color = "Item") +
   facet_wrap(~Sample, scales = "free", nrow = 4)
+
+ggsave("figures/Figure1.png", p1, width=10, height=10, dpi=200, bg="white")
+p1
 ```
@@
 - Not much clear theorethical or empirical structure (small grouping of items)
-- Limited variability (clear mode at 4/5)
+- Limited variability (clear mode at 4/5), very low prevalence of 5/5 responses.
 - Ambiguous items which grouping depends on the context (and its awareness)

### 2024-02-22 analysis/analysis.qmd
update

@@
 ```{r}
-# https://osf.io/3m5nh
-df1 <- haven::read_sav("../data/Murphy2020/Study 1.sav") |>
+# Murphy (https://osf.io/3m5nh)
+df1a <- haven::read_sav("../data/Murphy2020/Study 1.sav") |>
   mutate_all(as.numeric) |>
@@
 
-# https://osf.io/3m5nh
-df2 <- haven::read_sav("../data/Murphy2020/Study 6 IAS.sav") |>
+df1b <- haven::read_sav("../data/Murphy2020/Study 6 IAS.sav") |>
   mutate_all(as.numeric) |>
   mutate(Gender = as.character(ifelse(Gender == 1, "Male", ifelse(Gender == 2, "Female", "Other"))))
+
+# Gaggero (2021) (https://osf.io/5x9sg)
+load("../data/Gaggero2021/data.rda")
+df2 <- data |> 
+  mutate_all(as.numeric) |>
+  rename(
+    Gender=gender, Age=age, Heart = `IAS 1`, Hungry = `IAS 2`, Breathing = `IAS 3`, Thirsty = `IAS 4`,
+    Urinate = `IAS 5`, Defecate = `IAS 6`, Taste = `IAS 7`, Vomit = `IAS 8`, Sneeze = `IAS 9`,
+    Cough = `IAS 10`, Temp = `IAS 11`, Sex_arousal = `IAS 12`, Wind = `IAS 13`, Burp = `IAS 14`,
+    Muscles = `IAS 15`, Bruise = `IAS 16`, Pain = `IAS 17`, Blood_Sugar = `IAS 18`,
+    Affective_touch = `IAS 19`, Tickle = `IAS 20`, Itch = `IAS 21`)
 
@@
 
+# Brand (2023) - Study 1 (https://osf.io/3f2h6/)
+df4a <- haven::read_sav("../data/Brand2023/Data_Giessen.sav") |> 
+  select(-COUNTRY_OTHER) |> 
+  mutate_all(as.numeric) |>
+  mutate(Gender = as.character(ifelse(SEX == 1, "Male", ifelse(SEX == 2, "Female", "Other")))) |> 
+  rename(
+    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
+    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
+    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
+    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
+    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
+  )
+
+df4b <- haven::read_sav("../data/Brand2023/Data_Mainz.sav") |> 
+  select(-COUNTRY_OTHER, -EDUCATION_OTHER) |> 
+  mutate_all(as.numeric) |> 
+  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
+  rename(
+    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
+    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
+    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
+    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
+    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
+  )
+
+df4c <- haven::read_sav("../data/Brand2023/Data_PotVie.sav") |> 
+  select(-ID) |> 
+  mutate_all(as.numeric) |>
+  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
+  rename(
+    Age=AGE, Heart = IA02_01, Hungry = IA02_02, Breathing = IA02_03, Thirsty = IA02_04,
+    Urinate = IA02_05, Defecate = IA02_06, Taste = IA02_07, Vomit = IA02_08, Sneeze = IA02_09,
+    Cough = IA02_10, Temp = IA02_11, Sex_arousal = IA02_12, Wind = IA02_13, Burp = IA02_14,
+    Muscles = IA02_15, Bruise = IA02_16, Pain = IA02_17, Blood_Sugar = IA02_18,
+    Affective_touch = IA02_19, Tickle = IA02_20, Itch = IA02_21
+  )
+
 # https://osf.io/3eztd
-df4 <- haven::read_sav("../data/Lin2023/Study 1 & 3.sav") |>
+df5a <- haven::read_sav("../data/Lin2023/Study 1 & 3.sav") |>
   select(-sex) |> 
@@
 # https://osf.io/3eztd
-df5 <- haven::read_sav("../data/Lin2023/Study 2.sav") |>
+df5b <- haven::read_sav("../data/Lin2023/Study 2.sav") |>
   mutate(Gender = as.character(ifelse(Sex == "男", "Male", ifelse(Sex == "女", "Female", "Other")))) |>
@@
 
-df6 <- read.csv("https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv") |>
-  rename(
-    Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
-    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
-    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
-    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
-    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
-  )
-
-df7 <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |>
+df6a <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |>
   rename(
@@
   filter(!is.na(Urinate))
+
+df6b <- read.csv("https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv") |>
+  rename(
+    Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
+    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
+    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
+    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
+    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
+  )
 ```
@@
 
-- **Sample 1**: Data from Murphy's (2020) [study 1](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769), downloaded from OSF, included `r report::report_participants(df1, age = "Age", sex = NA, gender = "Gender")`.
-- **Sample 2**: Data from Murphy's (2020) [study 6](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769), downloaded from OSF, included `r report::report_participants(df2, age = "Age", sex = NA, gender = "Gender")`.
-- **Sample 3**: Data from Campos' (2022) [study 1](https://osf.io/j6ef3), downloaded from OSF, included `r report::report_participants(df3, age = "Age", sex = NA, gender = "Gender")`.
-- **Sample 4**: Data from Lin's (2023) [study 1 and 3](#ttps://osf.io/3eztd), downloaded from OSF, included `r report::report_participants(df4, age = "Age", sex = NA, gender = "Gender")`.
-- **Sample 5**: Data from Lin's (2023) [study 2](#ttps://osf.io/3eztd), downloaded from OSF, included `r report::report_participants(df5, age = "Age", sex = NA, gender = "Gender")`.
-- **Sample 6**: New dataset from [Makowski (under preparation)](https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv), included `r report::report_participants(df6, age = "Age", sex = NA, gender = "Gender")`.
-- **Sample 7**: New dataset from [Makowski (under preparation)](https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv), included `r report::report_participants(df7, age = "Age", sex = NA, gender = "Gender")`.
-
-Total N = `r nrow(df1) + nrow(df2) + nrow(df3) + nrow(df4) + nrow(df5) + nrow(df6) + nrow(df7)`.
+- **Sample 1a**: Data from Murphy's (2020) [study 1](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769), downloaded from OSF, included `r report::report_participants(df1a, age = "Age", sex = NA, gender = "Gender")`.
+- **Sample 1b**: Data from Murphy's (2020) [study 6](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769), downloaded from OSF, included `r report::report_participants(df1b, age = "Age", sex = NA, gender = "Gender")`.
+<!-- - **Sample 2**: Data from Campos' (2022) [study 1](https://osf.io/j6ef3), downloaded from OSF, included `r report::report_participants(df2, age = "Age", sex = NA, gender = "Gender")`. -->
+<!-- - Sample 3: TODO -->
+<!-- - **Sample 4a**: Data from Lin's (2023) [study 1 and 3](#ttps://osf.io/3eztd), downloaded from OSF, included `r report::report_participants(df4a, age = "Age", sex = NA, gender = "Gender")`. -->
+<!-- - **Sample 4b**: Data from Lin's (2023) [study 2](#ttps://osf.io/3eztd), downloaded from OSF, included `r report::report_participants(df4b, age = "Age", sex = NA, gender = "Gender")`. -->
+<!-- - **Sample 5a**: New dataset from [Makowski (under preparation)](https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv), included `r report::report_participants(df5a, age = "Age", sex = NA, gender = "Gender")`.
+-->
+<!-- - **Sample 5b**: New dataset from [Makowski (under preparation)](https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv), included `r report::report_participants(df5b, age = "Age", sex = NA, gender = "Gender")`.
+-->
+
+Total N = `r nrow(df1a) + nrow(df1b) + nrow(df2) + nrow(df3) + nrow(df4a) + nrow(df4b) + nrow(df4c) + nrow(df5a) + nrow(df5b) + nrow(df6a) + nrow(df6b)`.
 
@@
 
-dens1 <- estimate_density(select(df1, all_of(vars)), method = "kernSmooth") |>
-  mutate(Sample = "Sample 1")
+dens1a <- estimate_density(select(df1a, all_of(vars)), method = "kernSmooth") |>
+  mutate(Sample = "Sample 1a")
+dens1b <- estimate_density(select(df1b, all_of(vars)), method = "kernSmooth") |>
+  mutate(Sample = "Sample 1b")
 dens2 <- estimate_density(select(df2, all_of(vars)), method = "kernSmooth") |>
@@
   mutate(Sample = "Sample 3")
-dens4 <- estimate_density(select(df4, all_of(setdiff(vars, "Tickle"))), method = "kernSmooth") |>
-  mutate(Sample = "Sample 4")
-dens5 <- estimate_density(select(df5, all_of(setdiff(vars, "Tickle"))), method = "kernSmooth") |>
-  mutate(Sample = "Sample 5")
-dens6 <- estimate_density(select(df6, all_of(vars)), method = "kernSmooth") |>
-  mutate(Sample = "Sample 6")
-dens7 <- estimate_density(select(df7, all_of(setdiff(vars, c("Taste", "Cough", "Blood_Sugar")))), method = "kernSmooth") |>
-  mutate(Sample = "Sample 7")
-
-p1 <- rbind(dens1, dens2, dens3, dens4, dens5, dens6, dens7) |>
+dens4a <- estimate_density(select(df4a, all_of(vars)), method = "kernSmooth") |>
+  mutate(Sample = "Sample 4a")
+dens4b <- estimate_density(select(df4b, all_of(vars)), method = "kernSmooth") |>
+  mutate(Sample = "Sample 4b")
+dens4c <- estimate_density(select(df4c, all_of(vars)), method = "kernSmooth") |>
+  mutate(Sample = "Sample 4c")
+dens5a <- estimate_density(select(df5a, all_of(setdiff(vars, "Tickle"))), method = "kernSmooth") |>
+  mutate(Sample = "Sample 5a")
+dens5b <- estimate_density(select(df5b, all_of(setdiff(vars, "Tickle"))), method = "kernSmooth") |>
+  mutate(Sample = "Sample 5b")
+dens6a <- estimate_density(select(df6a, all_of(setdiff(vars, c("Taste", "Cough", "Blood_Sugar")))), method = "kernSmooth") |>
+  mutate(Sample = "Sample 6a")
+dens6b <- estimate_density(select(df6b, all_of(vars)), method = "kernSmooth") |>
+  mutate(Sample = "Sample 6b")
+
+p1 <- rbind(dens1a, dens1b, dens2, dens3, dens4a, dens4b, dens4c, dens5a, dens5b, dens6a, dens6b) |>
   # mutate(Dashed = ifelse(Parameter %in% c("Affective_touch", "Blood_Sugar", "Bruise"), TRUE, FALSE)) |> 
@@
   theme(axis.text.y = element_blank(),
-        plot.title = element_text(face="bold", hjust=0.5)) +
+        plot.title = element_text(face="bold")) +
   labs(title = "Distribution of responses for all items across various datasets", x = "Response", y = "Density", color = "Item") +
@@
 ```{r}
-data1 <- normalize(select(df1, all_of(dens1$Parameter)), range = c(1, 5))
+data1a <- normalize(select(df1a, all_of(dens1a$Parameter)), range = c(1, 5))
+data1b <- normalize(select(df1b, all_of(dens1b$Parameter)), range = c(1, 5))
 data2 <- normalize(select(df2, all_of(dens2$Parameter)), range = c(1, 5))
 data3 <- normalize(select(df3, all_of(dens3$Parameter)), range = c(1, 5))
-data4 <- normalize(select(df4, all_of(dens4$Parameter)), range = c(1, 5))
-data5 <- normalize(select(df5, all_of(dens5$Parameter)), range = c(1, 5))
-data6 <- select(df6, all_of(dens6$Parameter))
-data7 <- select(df7, all_of(dens7$Parameter))
+data4a <- normalize(select(df4a, all_of(dens4a$Parameter)), range = c(1, 5))
+data4b <- normalize(select(df4b, all_of(dens4b$Parameter)), range = c(1, 5))
+data4c <- normalize(select(df4c, all_of(dens4c$Parameter)), range = c(1, 5))
+data5a <- normalize(select(df5a, all_of(dens5a$Parameter)), range = c(1, 5))
+data5b <- normalize(select(df5b, all_of(dens5b$Parameter)), range = c(1, 5))
+data6a <- select(df6a, all_of(dens6a$Parameter))
+data6b <- select(df6b, all_of(dens6b$Parameter))
 
 data_all <- rbind(
-  data1, data2, data3,
-  mutate(data4, Tickle = NA), mutate(data5, Tickle = NA),
-  data6, mutate(data7, Taste = NA, Cough = NA, Blood_Sugar = NA)
+  data1a, data1b, data2, data3, data4a, data4b, data4c,
+  mutate(data5a, Tickle = NA), mutate(data5b, Tickle = NA),
+  mutate(data6a, Taste = NA, Cough = NA, Blood_Sugar = NA), data6b
 )
@@
 
-##### Sample 1
-
-```{r}
-make_correlation(data1)
+##### Sample 1a
+
+```{r}
+make_correlation(data1a)
+```
+
+##### Sample 1b
+
+```{r}
+make_correlation(data1b)
 ```
@@
 
-##### Sample 4
-
-```{r}
-make_correlation(data4)
-```
-
-##### Sample 5
-
-```{r}
-make_correlation(data5)
-```
-
-##### Sample 6
-
-```{r}
-make_correlation(data6)
-```
-
-##### Sample 7
-
-```{r}
-make_correlation(data7)
+##### Sample 4a
+
+```{r}
+make_correlation(data4a)
+```
+
+##### Sample 4b
+
+```{r}
+make_correlation(data4b)
+```
+
+##### Sample 4c
+
+```{r}
+make_correlation(data4c)
+```
+
+##### Sample 5a
+
+```{r}
+make_correlation(data5a)
+```
+
+##### Sample 5b
+
+```{r}
+make_correlation(data5b)
+```
+
+##### Sample 6a
+
+```{r}
+make_correlation(data6a)
+```
+
+##### Sample 6b
+
+```{r}
+make_correlation(data6b)
 ```
@@
 
-##### Sample 1
-
-```{r}
-egas1 <- make_egas(data1)
+##### Sample 1a
+
+```{r}
+egas1 <- make_egas(data1a)
 egas1$p
@@
 
-##### Sample 2
-
-```{r}
-egas2 <- make_egas(data2)
+##### Sample 1b
+
+```{r}
+egas2 <- make_egas(data1b)
 egas2$p
@@
 
-df1 <- cbind(df1, scores$sample1)
-df2 <- cbind(df2, scores$sample2)
+df1a <- cbind(df1a, scores$sample1)
+df1b <- cbind(df1b, scores$sample2)
 df3 <- cbind(df3, scores$sample3)
-df4 <- cbind(df4, scores$sample4)
-df5 <- cbind(df5, scores$sample5)
-df6 <- cbind(df6, scores$sample6)
-df7 <- cbind(df7, scores$sample7)
+df4a <- cbind(df4a, scores$sample4)
+df4b <- cbind(df4b, scores$sample5)
+df5b <- cbind(df5b, scores$sample6)
+df5a <- cbind(df5a, scores$sample7)
 
@@
 
-# names(df1)
-# names(df2)
+# names(df1a)
+# names(df1b)
 # names(df3)  # TAS, BPQ
-# names(df4)  # BPQ
-# names(df5)  # PHQ, TAS
-# names(df6)  # BDI, STAI
-# names(df7)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
+# names(df4a)  # BPQ
+# names(df4b)  # PHQ, TAS
+# names(df5b)  # BDI, STAI
+# names(df5a)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
 ```
@@
 df_scores <- rbind(
-  select(df1, all_of(vars_intero)),
-  select(df2, all_of(vars_intero)),
+  select(df1a, all_of(vars_intero)),
+  select(df1b, all_of(vars_intero)),
   select(df3, all_of(vars_intero)),
-  select(df4, all_of(vars_intero)),
-  select(df5, all_of(vars_intero)),
-  select(df6, all_of(vars_intero)),
-  select(df7, all_of(vars_intero))
+  select(df4a, all_of(vars_intero)),
+  select(df4b, all_of(vars_intero)),
+  select(df5b, all_of(vars_intero)),
+  select(df5a, all_of(vars_intero))
 )
@@
 data <- rbind(
-  make_diff(df1, vars_cfa, component="Demographic"),
-  make_diff(df2, vars_cfa, component="Demographic"),
+  make_diff(df1a, vars_cfa, component="Demographic"),
+  make_diff(df1b, vars_cfa, component="Demographic"),
   make_diff(df3, vars_cfa, component="Demographic"),
-  make_diff(df4, vars_cfa, component="Demographic"),
-  make_diff(df5, vars_cfa, component="Demographic"),
-  make_diff(df6, vars_cfa, component="Demographic"),
-  make_diff(df7, vars_cfa7, component="Demographic")
+  make_diff(df4a, vars_cfa, component="Demographic"),
+  make_diff(df4b, vars_cfa, component="Demographic"),
+  make_diff(df5b, vars_cfa, component="Demographic"),
+  make_diff(df5a, vars_cfa7, component="Demographic")
 ) |> 
@@
   data,
-  make_cor(df1, vars_cfa, with = "Age", component="Demographic"),
-  make_cor(df2, vars_cfa, with = "Age", component="Demographic"),
+  make_cor(df1a, vars_cfa, with = "Age", component="Demographic"),
+  make_cor(df1b, vars_cfa, with = "Age", component="Demographic"),
   make_cor(df3, vars_cfa, with = "Age", component="Demographic"),
-  make_cor(df4, vars_cfa, with = "Age", component="Demographic"),
-  make_cor(df5, vars_cfa, with = "Age", component="Demographic"),
-  make_cor(df6, vars_cfa, with = "Age", component="Demographic"),
-  make_cor(df7, vars_cfa7, with = "Age", component="Demographic")
+  make_cor(df4a, vars_cfa, with = "Age", component="Demographic"),
+  make_cor(df4b, vars_cfa, with = "Age", component="Demographic"),
+  make_cor(df5b, vars_cfa, with = "Age", component="Demographic"),
+  make_cor(df5a, vars_cfa7, with = "Age", component="Demographic")
 ) 
@@
     mutate(var_Correlate = "Autonomic Reactivity"),
-  make_cor(df4, vars_cfa, with = "BPQ_A", component="Body") |> 
+  make_cor(df4a, vars_cfa, with = "BPQ_A", component="Body") |> 
     mutate(var_Correlate = "Body Awareness")
@@
   data,
-  make_cor(df7, vars_cfa7, with = "MAIA_AttentionRegulation", component="MAIA")  |> 
+  make_cor(df5a, vars_cfa7, with = "MAIA_AttentionRegulation", component="MAIA")  |> 
     mutate(var_Correlate = "Attention Regulation"),
-  make_cor(df7, vars_cfa7, with = "MAIA_BodyListening", component="MAIA") |> 
+  make_cor(df5a, vars_cfa7, with = "MAIA_BodyListening", component="MAIA") |> 
     mutate(var_Correlate = "Body Listening"),
-  make_cor(df7, vars_cfa7, with = "MAIA_EmotionalAwareness", component="MAIA") |> 
+  make_cor(df5a, vars_cfa7, with = "MAIA_EmotionalAwareness", component="MAIA") |> 
     mutate(var_Correlate = "Emotional Awareness"),
-  make_cor(df7, vars_cfa7, with = "MAIA_NotDistracting", component="MAIA") |> 
+  make_cor(df5a, vars_cfa7, with = "MAIA_NotDistracting", component="MAIA") |> 
     mutate(var_Correlate = "Not Distracting"),
-  make_cor(df7, vars_cfa7, with = "MAIA_Noticing", component="MAIA") |> 
+  make_cor(df5a, vars_cfa7, with = "MAIA_Noticing", component="MAIA") |> 
     mutate(var_Correlate = "Noticing"),
-  make_cor(df7, vars_cfa7, with = "MAIA_NotWorrying", component="MAIA") |> 
+  make_cor(df5a, vars_cfa7, with = "MAIA_NotWorrying", component="MAIA") |> 
     mutate(var_Correlate = "Not Worrying"),
-  make_cor(df7, vars_cfa7, with = "MAIA_SelfRegulation", component="MAIA") |> 
+  make_cor(df5a, vars_cfa7, with = "MAIA_SelfRegulation", component="MAIA") |> 
     mutate(var_Correlate = "Self Regulation"),
-  make_cor(df7, vars_cfa7, with = "MAIA_Trusting", component="MAIA") |> 
+  make_cor(df5a, vars_cfa7, with = "MAIA_Trusting", component="MAIA") |> 
     mutate(var_Correlate = "Trusting")
@@
 # names(df3)[str_detect(names(df3), "TAS")]
-# names(df5)[str_starts(names(df5), "TAS")]
+# names(df4b)[str_starts(names(df4b), "TAS")]
 
@@
     mutate(var_Correlate = "External Thinking"),
-  make_cor(df5, vars_cfa, with = "TAS_DIF", component="Body") |> 
+  make_cor(df4b, vars_cfa, with = "TAS_DIF", component="Body") |> 
     mutate(var_Correlate = "Difficulties Identifying Feelings"),
-  make_cor(df5, vars_cfa, with = "TAS_DDF", component="Body") |> 
+  make_cor(df4b, vars_cfa, with = "TAS_DDF", component="Body") |> 
     mutate(var_Correlate = "Difficulties Describing Feelings")
@@
   data,
-  make_cor(df5, vars_cfa, with = "PHQ15_sum", component="Mood") |> 
+  make_cor(df4b, vars_cfa, with = "PHQ15_sum", component="Mood") |> 
     mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
-  make_cor(df5, vars_cfa, with = "PHQ9_sum", component="Mood")|> 
+  make_cor(df4b, vars_cfa, with = "PHQ9_sum", component="Mood")|> 
     mutate(var_Correlate = "Depression (PHQ-9)"),
-  make_cor(df7, vars_cfa7, with = "PHQ4_Depression", component="Mood") |> 
+  make_cor(df5a, vars_cfa7, with = "PHQ4_Depression", component="Mood") |> 
     mutate(var_Correlate = "Depression (PHQ-4)"),
-  make_cor(df7, vars_cfa7, with = "PHQ4_Anxiety", component="Mood") |> 
+  make_cor(df5a, vars_cfa7, with = "PHQ4_Anxiety", component="Mood") |> 
     mutate(var_Correlate = "Anxiety (PHQ-4)")
@@
   data,
-  make_cor(df6, vars_cfa, with = "BDI2_Total", component="Mood") |> 
+  make_cor(df5b, vars_cfa, with = "BDI2_Total", component="Mood") |> 
     mutate(var_Correlate = "Depression (BDI-II)")
@@
   data,
-  make_cor(df6, vars_cfa, with = "STAI5_General", component="Mood") |> 
+  make_cor(df5b, vars_cfa, with = "STAI5_General", component="Mood") |> 
     mutate(var_Correlate = "Anxiety (STAI-5)")
@@
   data,
-  make_cor(df7, vars_cfa7, with = "BPD", component="Mood") |> 
+  make_cor(df5a, vars_cfa7, with = "BPD", component="Mood") |> 
     mutate(var_Correlate = "Boderline Personality")
@@
   data,
-  make_cor(df7, vars_cfa7, with = "PID5_Antagonism", component="Maladaptive") |> 
+  make_cor(df5a, vars_cfa7, with = "PID5_Antagonism", component="Maladaptive") |> 
     mutate(var_Correlate = "Antagonism"),
-  make_cor(df7, vars_cfa7, with = "PID5_Detachment", component="Maladaptive") |> 
+  make_cor(df5a, vars_cfa7, with = "PID5_Detachment", component="Maladaptive") |> 
     mutate(var_Correlate = "Detachment"),
-  make_cor(df7, vars_cfa7, with = "PID5_Disinhibition", component="Maladaptive") |> 
+  make_cor(df5a, vars_cfa7, with = "PID5_Disinhibition", component="Maladaptive") |> 
     mutate(var_Correlate = "Disinhibition"),
-  make_cor(df7, vars_cfa7, with = "PID5_NegativeAffect", component="Maladaptive") |> 
+  make_cor(df5a, vars_cfa7, with = "PID5_NegativeAffect", component="Maladaptive") |> 
     mutate(var_Correlate = "Negative Affect"),
-  make_cor(df7, vars_cfa7, with = "PID5_Psychoticism", component="Maladaptive") |> 
+  make_cor(df5a, vars_cfa7, with = "PID5_Psychoticism", component="Maladaptive") |> 
     mutate(var_Correlate = "Psychoticism")
@@
   data,
-  make_cor(df7, vars_cfa7, with = "SPQ_ConstrictedAffect", component="Schizotypic") |> 
+  make_cor(df5a, vars_cfa7, with = "SPQ_ConstrictedAffect", component="Schizotypic") |> 
     mutate(var_Correlate = "Constricted Affect"),
-  make_cor(df7, vars_cfa7, with = "SPQ_Eccentric", component="Schizotypic") |> 
+  make_cor(df5a, vars_cfa7, with = "SPQ_Eccentric", component="Schizotypic") |> 
     mutate(var_Correlate = "Eccentric"),
-  make_cor(df7, vars_cfa7, with = "SPQ_MagicalThinking", component="Schizotypic") |> 
+  make_cor(df5a, vars_cfa7, with = "SPQ_MagicalThinking", component="Schizotypic") |> 
     mutate(var_Correlate = "Magical Thinking"),
-  make_cor(df7, vars_cfa7, with = "SPQ_NoCloseFriends", component="Schizotypic") |> 
+  make_cor(df5a, vars_cfa7, with = "SPQ_NoCloseFriends", component="Schizotypic") |> 
     mutate(var_Correlate = "No Close Friends"),
-  make_cor(df7, vars_cfa7, with = "SPQ_OddSpeech", component="Schizotypic") |> 
+  make_cor(df5a, vars_cfa7, with = "SPQ_OddSpeech", component="Schizotypic") |> 
     mutate(var_Correlate = "Odd Speech"),
-  make_cor(df7, vars_cfa7, with = "SPQ_Reference", component="Schizotypic") |> 
+  make_cor(df5a, vars_cfa7, with = "SPQ_Reference", component="Schizotypic") |> 
     mutate(var_Correlate = "Reference"),
-  make_cor(df7, vars_cfa7, with = "SPQ_SocialAnxiety", component="Schizotypic") |> 
+  make_cor(df5a, vars_cfa7, with = "SPQ_SocialAnxiety", component="Schizotypic") |> 
     mutate(var_Correlate = "Social Anxiety"),
-  make_cor(df7, vars_cfa7, with = "SPQ_Suspiciousness", component="Schizotypic") |> 
+  make_cor(df5a, vars_cfa7, with = "SPQ_Suspiciousness", component="Schizotypic") |> 
     mutate(var_Correlate = "Suspiciousness"),
-  make_cor(df7, vars_cfa7, with = "SPQ_UnusualPerceptions", component="Schizotypic") |> 
+  make_cor(df5a, vars_cfa7, with = "SPQ_UnusualPerceptions", component="Schizotypic") |> 
     mutate(var_Correlate = "Unusual Perceptions")
@@
 ```{r}
-#  names(select(df7, starts_with("ASQ")))
+#  names(select(df5a, starts_with("ASQ")))
 data <- rbind(
   data,
-  make_cor(df7, vars_cfa7, with = "ASQ_Imagination", component="Autistic") |> 
+  make_cor(df5a, vars_cfa7, with = "ASQ_Imagination", component="Autistic") |> 
     mutate(var_Correlate = "Imagination"),
-  make_cor(df7, vars_cfa7, with = "ASQ_LackSocialSkills", component="Autistic") |>
+  make_cor(df5a, vars_cfa7, with = "ASQ_LackSocialSkills", component="Autistic") |>
     mutate(var_Correlate = "Lack of Social Skills"),
-  make_cor(df7, vars_cfa7, with = "ASQ_LowAttentionalSwitching", component="Autistic") |>
+  make_cor(df5a, vars_cfa7, with = "ASQ_LowAttentionalSwitching", component="Autistic") |>
     mutate(var_Correlate = "Low Attentional Switching"),
-  make_cor(df7, vars_cfa7, with = "ASQ_Patterns", component="Autistic") |>
+  make_cor(df5a, vars_cfa7, with = "ASQ_Patterns", component="Autistic") |>
     mutate(var_Correlate = "Patterns and Numbers"),
-  make_cor(df7, vars_cfa7, with = "ASQ_Routine", component="Autistic") |>
+  make_cor(df5a, vars_cfa7, with = "ASQ_Routine", component="Autistic") |>
     mutate(var_Correlate = "Routines")
@@
   data,
-  make_cor(df7, vars_cfa7, with = "IPIP6_Agreeableness", component="Personality") |> 
+  make_cor(df5a, vars_cfa7, with = "IPIP6_Agreeableness", component="Personality") |> 
     mutate(var_Correlate = "Agreeableness"),
-  make_cor(df7, vars_cfa7, with = "IPIP6_Conscientiousness", component="Personality") |>
+  make_cor(df5a, vars_cfa7, with = "IPIP6_Conscientiousness", component="Personality") |>
     mutate(var_Correlate = "Conscientiousness"),
-  make_cor(df7, vars_cfa7, with = "IPIP6_Neuroticism", component="Personality") |>
+  make_cor(df5a, vars_cfa7, with = "IPIP6_Neuroticism", component="Personality") |>
     mutate(var_Correlate = "Neuroticism"),
-  make_cor(df7, vars_cfa7, with = "IPIP6_Openness", component="Personality") |>
+  make_cor(df5a, vars_cfa7, with = "IPIP6_Openness", component="Personality") |>
     mutate(var_Correlate = "Openness"),
-  make_cor(df7, vars_cfa7, with = "IPIP6_Extraversion", component="Personality") |>
+  make_cor(df5a, vars_cfa7, with = "IPIP6_Extraversion", component="Personality") |>
     mutate(var_Correlate = "Extraversion"),
-  make_cor(df7, vars_cfa7, with = "IPIP6_HonestyHumility", component="Personality") |>
+  make_cor(df5a, vars_cfa7, with = "IPIP6_HonestyHumility", component="Personality") |>
     mutate(var_Correlate = "Honesty-Humility")
@@
   data,
-  make_cor(df7, vars_cfa7, with = "PI_Alive", component="World Beliefs") |> 
+  make_cor(df5a, vars_cfa7, with = "PI_Alive", component="World Beliefs") |> 
     mutate(var_Correlate = "Alive"),
-  make_cor(df7, vars_cfa7, with = "PI_Changing", component="World Beliefs") |>
+  make_cor(df5a, vars_cfa7, with = "PI_Changing", component="World Beliefs") |>
     mutate(var_Correlate = "Changing"),
-  make_cor(df7, vars_cfa7, with = "PI_Enticing", component="World Beliefs") |>
+  make_cor(df5a, vars_cfa7, with = "PI_Enticing", component="World Beliefs") |>
     mutate(var_Correlate = "Enticing"),
-  make_cor(df7, vars_cfa7, with = "PI_Good", component="World Beliefs") |>
+  make_cor(df5a, vars_cfa7, with = "PI_Good", component="World Beliefs") |>
     mutate(var_Correlate = "Good"),
-  make_cor(df7, vars_cfa7, with = "PI_Hierarchical", component="World Beliefs") |>
+  make_cor(df5a, vars_cfa7, with = "PI_Hierarchical", component="World Beliefs") |>
     mutate(var_Correlate = "Hierarchical"),
-  make_cor(df7, vars_cfa7, with = "PI_Safe", component="World Beliefs") |>
+  make_cor(df5a, vars_cfa7, with = "PI_Safe", component="World Beliefs") |>
     mutate(var_Correlate = "Safe")
+  # TODO: Add understanble
 )
@@
   data,
-  make_cor(df7, vars_cfa7, with = "GCBS_Extraterrestrial", component="Conspiracy Beliefs") |> 
+  make_cor(df5a, vars_cfa7, with = "GCBS_Extraterrestrial", component="Conspiracy Beliefs") |> 
     mutate(var_Correlate = "Extraterrestrial"),
-  make_cor(df7, vars_cfa7, with = "GCBS_GlobalConspiracies", component="Conspiracy Beliefs") |>
+  make_cor(df5a, vars_cfa7, with = "GCBS_GlobalConspiracies", component="Conspiracy Beliefs") |>
     mutate(var_Correlate = "Global Conspiracies"),
-  make_cor(df7, vars_cfa7, with = "GCBS_GovernmentMalfeasance", component="Conspiracy Beliefs") |>
+  make_cor(df5a, vars_cfa7, with = "GCBS_GovernmentMalfeasance", component="Conspiracy Beliefs") |>
     mutate(var_Correlate = "Government Malfeasance"),
-  make_cor(df7, vars_cfa7, with = "GCBS_InformationControl", component="Conspiracy Beliefs") |>
+  make_cor(df5a, vars_cfa7, with = "GCBS_InformationControl", component="Conspiracy Beliefs") |>
     mutate(var_Correlate = "Information Control"),
-  make_cor(df7, vars_cfa7, with = "GCBS_PersonalWellbeing", component="Conspiracy Beliefs") |>
+  make_cor(df5a, vars_cfa7, with = "GCBS_PersonalWellbeing", component="Conspiracy Beliefs") |>
     mutate(var_Correlate = "Personal Wellbeing")
@@
   data,
-  make_cor(df7, vars_cfa7, with = "LIE_Ability", component="Lying Profile") |> 
+  make_cor(df5a, vars_cfa7, with = "LIE_Ability", component="Lying Profile") |> 
     mutate(var_Correlate = "Ability"),
-  make_cor(df7, vars_cfa7, with = "LIE_Frequency", component="Lying Profile") |>
+  make_cor(df5a, vars_cfa7, with = "LIE_Frequency", component="Lying Profile") |>
     mutate(var_Correlate = "Frequency"),
-  make_cor(df7, vars_cfa7, with = "LIE_Contextuality", component="Lying Profile") |>
+  make_cor(df5a, vars_cfa7, with = "LIE_Contextuality", component="Lying Profile") |>
     mutate(var_Correlate = "Contextuality"),
-  make_cor(df7, vars_cfa7, with = "LIE_Negativity", component="Lying Profile") |>
+  make_cor(df5a, vars_cfa7, with = "LIE_Negativity", component="Lying Profile") |>
     mutate(var_Correlate = "Negativity")

### 2024-02-25 data/Arslanova2022/inferringHR_Arslanova.Rmd
add new data

---
title: "Seeing through each other’s hearts: Inferring others' heart rate as a function of own heart rate perception and perceived social intelligence"
author: "Irena Arslanova"
date: "27/05/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

# This markdown is an analysis pipeline for Actor HR & Schandry online replication study. 
Main excel files should be downloaded along this file from OSF and put into the same folder.
The excel files are already pre-organised, meaning that each set of participants was loaded from Gorilla and put together into a single sheet with only relevant columns selected
## Load packages and functions:
```{r, message = FALSE}
library(openxlsx)
library(tidyverse)
library(Hmisc)
library(corrplot)
library(ggpubr)
library(nlme)
library(lme4)
library(ggplot2)
library(mediation)
library(rsq)
library(ggpubr)
library(cowplot)
library(plyr)
library(plotrix)
library(cowplot)
library(rstatix)
library(BayesFactor)
library(bayestestR)
library(ez)
library(psychReport)
library(metaSDT)
library(data.table)
library(wesanderson)
library(performance)
library(car)
library(BayesFactor)
library(bayestestR)
library(interactions)
library(viridis)
library(ggstance)
library(broom.mixed)
library(scales)
library(psych)

# The source for the violin distribution plot:
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

lb <- function(x) mean(x) - std.error(x)
ub <- function(x) mean(x) + std.error(x)

knitr::opts_chunk$set(message = FALSE)

# I want to set the working directory based on the computer I am using
# first, I will try to find where this markdown is located on the system:
work_dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(work_dir)
getwd()
knitr::opts_knit$set(root.dir = work_dir)

```

## Load and organise all the data: Schandry, Questionnaires (IAS, SI), ActorHR task

### SCANDRY

#### Load pre-existing Schandry dataset:
```{r}
exel_file <- paste(work_dir, "Schandry_Irena.xlsx", sep="/")
Schandry <- read.xlsx(xlsxFile= exel_file, sheet = "Sheet 1")

```

#### Remove excluded participants:
for Schandry we only look at the reduced sample
```{r}
removep <- c("5b82d4fda284bc000193094c", "5bdb50e3ee652a0001efa0e0", "5db43b6a2f45e7000bb7ab5c", "5dc1e711900e3e15813f7c38", "5de7ccc24b7cf973d7b05bfb", "5e03fdb2ac9e16edc91d0108", "5e4314ad234956000a8a91f3", "5f573b18a6a8b51a94fdbd08", "5f75cd50d19e2a28374120ff", "5f78879e60d68143137b5931", "5fae5291ec402509e2885604", "6002e90144049f32edaf9ccf", "60087da4a426a14ac248b803", "601c84e07ab4907ded068d0d", "6032af5b3a3b7a2f5570fbdf", "603d301c7ebc27be3c7b5ea4", "604e1a9533738c74ad5879d2", "605996d037bce4fb5488a375", "606168c7da6829aa69acf033", "60719da557d8241609b26e83", "607f0ad32fd52dbc961cefc0", "60a183e7a5e5e6991afd6796", "60a7c099a678670592ba187a", "60af52990d170be944d0df18", "60b68fc2c92926cd9af2733b", "60b713c5f76777e302824caf", "60b87b074ce3cf9de9d47962", "60b895235deea4c7bf48b85a", "60e7360a87d1675a8574cd30", "60eb105221914f6f26a89908")

Schandry_onlyaccepted <- Schandry[ !(Schandry$Subj.ID %in% removep), ] # ActorHR exclusion

removep2 <- c("575b2b408b705300078ae5e6", "588093c6704f1100014a3d01", "5a9b20c535237b0001129820", "5aeb063b2f05b500013028a0", "5bf1ecfcaf38d100016c1171", "5d07fc124e753800168ccafe", "5d68c8aa40524c00189e8ac2", "5d88b1c27250e90001c40cfc", "5d8cef3c28e183001a335ab0", "5e15e7a61d4607bd245169d9", "5e28e735ea776009d4d15c34", "5e3e11a36a0b8a000c609d5e", "5e4bc6e3a767d8018bd8e2be", "5e7d09e7f0a5a00c4a1ccf96", "5e92f26b444572122fdfe44d", "5ea976c0ae936906ffed032e", "5eaaec78a563dc0724c63b98", "5ebc2b0a9b711a04722d7382", "5ec4e3db7e31c83dfc851b83", "5ef1bb10c673fd7d2d14e439", "5f50191209e6d018aeb925f5", "5f600669b846780f0fe45709", "5f6ea775bc475b407020431f", "5f8cbc5c355ea745e6cef2ca", "5fa949031fdafd084c4d0812", "5fbb7aae04da87a3fe5f129c", "5fc92eb719e43600082952d9", "601129f77e0c21000b0c408a", "601952130cd928000a796a8b", "6022dfbafb748f0ca0385db9", "602d965dc8c74282fc222c7e", "60338f35010951035cca4a91", "603862f99e00971c55fe0874", "603ecc7968ff0bf9b25e4bf1", "603ffa13fa433c1989bff9e3", "60445f787075a64dbae085c5", "60527c19066274811cb7ca77", "607071077825ce1b96d83505", "6074b929f753216d88c77e88", "60850f02822cdda28b5ecfcb", "609478fa9e5b4d075246cfaf", "609d2b711c0593de2807d045", "60a2dffd4d05d87faf96873b", "60b405631fbdf499c48838ca", "60b60d67bbc65b38b155536e", "60c07a36ba668880b8010450", "60eb841bc608d3c01a7c5582")

Schandry_onlyaccepted <- Schandry_onlyaccepted[ !(Schandry_onlyaccepted$Subj.ID %in% removep2), ] # Schandry exclusion

```

#### Plot HR across the 3 intervals for each participant:
```{r}
# for each participant: interval - HR - counted - difference (Iacc)
Schandry_onlyaccepted$diff <- 1 - abs(Schandry_onlyaccepted$HR - Schandry_onlyaccepted$HR_counted) / Schandry_onlyaccepted$HR

x <- dplyr::select(Schandry_onlyaccepted, Subj.ID, smoothy, interval, diff)

# plot smoothy
p_HR <- ggplot(x, aes(x = interval, y=smoothy)) +
  #geom_point(size= 2, shape = 21, colour = "black", fill =  "black", position=position_jitter(width = 0.4, height = 0)) +
  geom_line(aes(x = interval, y=smoothy, group = Subj.ID), colour = "black", alpha = 0.5) +
  scale_y_continuous(limits= c(50,106), breaks = c(50, 60, 70, 80, 90, 100), labels = c("50","60", "70", "80","90","100")) +
  scale_x_continuous(limits= c(24.5,45.5), breaks = c(25,35,45), labels = c("25", "35", "45"))
  #scale_fill_manual(values = colors_9)

p_HR <- p_HR + theme_classic() +
  theme(text = element_text(size = 10),
        legend.position = "none") +
  labs(y="heart rate (bpm)", x = "interval")

# plot IAcc
p_Iacc <- ggplot(x, aes(x = interval, y=diff)) +
  #geom_point(size= 2, shape = 21, colour = "black", fill =  "black", position=position_jitter(width = 0.4, height = 0)) +
  geom_line(aes(x = interval, y=diff, group = Subj.ID), colour = "black", alpha = 0.5) +
  scale_y_continuous(limits= c(0,1), breaks = c(0, 0.25, 0.5, 0.75, 1), labels = c("0","0.25", "0.5", "0.75","1")) +
  scale_x_continuous(limits= c(24.5,45.5), breaks = c(25,35,45), labels = c("25", "35", "45"))
  #scale_fill_manual(values = colors_9)

p_Iacc <- p_Iacc + theme_classic() +
  theme(text = element_text(size = 10),
        legend.position = "none") +
  labs(y="I_Acc", x = "interval")

g <- ggarrange(p_HR, p_Iacc,
          labels = c("A", "B"),
          ncol = 2, nrow = 1)
suppressWarnings(print(g))

ggsave("prem.pdf", g, width = 6, height = 3, dpi= 300)

```

#### Difference in IAcc and HR across the three trials with ICC
```{r}
# HR:
x <- dplyr::select(Schandry_onlyaccepted, Subj.ID, smoothy, interval)

wide <- dcast(setDT(x), Subj.ID ~ paste0("interval", interval), value.var = "smoothy", sep = "_")
wide <- dplyr::select(wide, -Subj.ID)

i <- ICC(as.matrix(wide))
i

# IAcc
x <- dplyr::select(Schandry_onlyaccepted, Subj.ID, diff, interval)

wide <- dcast(setDT(x), Subj.ID ~ paste0("interval", interval), value.var = "diff", sep = "_")
wide <- dplyr::select(wide, -Subj.ID)

i <- ICC(as.matrix(wide))
i

```

#### Check stability of the HR power across the intervals:
```{r}
subs <- unique(Schandry_onlyaccepted$Subj.ID)
subs_num <- length(subs)

# check order:
# ABC -> diff 25-35 & 35-45
# BCA -> diff 35-45 & 45-25
# CAB -> diff 45-25 & 25-35
HRraw_check <- matrix(NA, nrow = subs_num, ncol = 3)

for(r in 1:subs_num){
  x <- subset(Schandry_onlyaccepted, Subj.ID == subs[r])
  HRraw_check[r, 1] <- subs[r]

  num_available_intervals <- nrow(x)
  available_intervals <- unique(x$interval)

  if(x$order[1] == "ABC"){
    HRraw_check[r, 2] <-  abs(round(x$smoothy[x$interval==25] - x$smoothy[x$interval==35], digits = 1))
    HRraw_check[r, 3] <-  abs(round(x$smoothy[x$interval==35] - x$smoothy[x$interval==45], digits = 1))
  }
  else if(x$order[1] == "BCA"){
    HRraw_check[r, 2] <-  abs(round(x$smoothy[x$interval==35] - x$smoothy[x$interval==45], digits = 1))
    HRraw_check[r, 3] <-  abs(round(x$smoothy[x$interval==45] - x$smoothy[x$interval==25], digits = 1))
  }
  else if(x$order[1] == "CAB"){
    HRraw_check[r, 2] <-  abs(round(x$smoothy[x$interval==45] - x$smoothy[x$interval==25], digits = 1))
    HRraw_check[r, 3] <-  abs(round(x$smoothy[x$interval==25] - x$smoothy[x$interval==35], digits = 1))
  }

}

HRraw_check <- as.data.frame(HRraw_check)
names(HRraw_check) = c("Subj", "Smoothy_diff1", "Smoothy_diff2")

# add a variable that shows maximum in each measure:
for(r in 1:nrow(HRraw_check)){
  row <- as.matrix(HRraw_check[r, 2:3])
  HRraw_check$Smoothy_max[r] <- max(as.numeric(row))
}

HRraw_check$Smoothy_max <- as.numeric(HRraw_check$Smoothy_max)

```

#### Plot the degree of difference:
```{r fig.width = 5, fig.height= 3}

HRraw_check2 <- gather(HRraw_check, Factor, Difference, HR_power_25vs35:Smoothy_max, factor_key=FALSE)
HRraw_check2 <- filter(HRraw_check2, Factor == "HR_power_max" | Factor == "Smoothy_max")
HRraw_check2$Factor <- as.factor(HRraw_check2$Factor)
HRraw_check2$Subj <- as.factor(HRraw_check2$Subj)
HRraw_check2$Difference <- as.numeric(HRraw_check2$Difference)

p <- ggplot(HRraw_check2, aes(x = reorder(Subj, Difference), y = Difference, fill = Factor)) + 
  geom_bar(stat="identity", position=position_dodge()) +
  scale_y_continuous(limits= c(0,74), breaks = c(7, 20, 40, 60), labels = c("7", "20","40","60")) +
  geom_abline(intercept = 7, slope = 0, color="#899DA4", linetype="dashed") +
  geom_abline(intercept = 20, slope = 0, color="#C93312", linetype="dashed") +
  scale_fill_manual(values = c("#899DA4", "#C93312"))

p <- p + theme_classic() +
  theme(text = element_text(size = 12), 
        axis.text.x=element_blank(),
        plot.title = element_text(vjust = -6, hjust = 0.1),
        legend.position = c(0.2, 0.5)) +
  labs(x="Subject", y = "Max difference across intervals", title = "Maximum difference between intervals")

p
ggsave("HR_interval_maxdiff.png", width = 5, height = 3, dpi= 300)

```

#### Calculate Iacc and Iawareness for each participant (make sure you account that some participants might be missing an interval)
```{r}
subs <- unique(Schandry_onlyaccepted$Subj.ID)
subs_num <- length(subs)
Intero_perf <- matrix(NA, nrow = subs_num, ncol = 4)

for(r in 1:subs_num){
  x <- subset(Schandry_onlyaccepted, Subj.ID == subs[r])
  num_available_intervals <- nrow(x)
  available_intervals <- unique(x$interval)
  interval_vec <- matrix(NA, nrow = 1, ncol = num_available_intervals)

  for(i in 1:num_available_intervals){
    x2 <- subset(x, interval==available_intervals[i])
    interval_vec[i] <- 1- abs(x2$HR - x2$HR_counted) / x2$HR # acc for each available interval
  }

  Intero_perf[r, 1] <- x2$Subj.ID
  Intero_perf[r, 2] <- sum(interval_vec) / num_available_intervals

  x$Confidence <- x$Confidence / 10 # to put the confidence on a scale from 0 to 1

  interval_conf <- matrix(NA, nrow = 1, ncol = num_available_intervals)
  interval_meanconf <- matrix(NA, nrow = 1, ncol = num_available_intervals)

  for(i in 1:num_available_intervals){
    x2 <- subset(x, interval==available_intervals[i])
    interval_conf[i] <- interval_vec[i] - x2$Confidence # conf for each available interval
    interval_meanconf[i] <- x2$Confidence
  }

  # positive values on Iawareness reflect underestimation of Iacc
  # negative values reflect overestimation of Iacc

  Intero_perf[r, 3] <- sum(interval_conf) / num_available_intervals
  Intero_perf[r, 4] <- mean(interval_meanconf)
}

Intero_perf <- as.data.frame(Intero_perf)
names(Intero_perf) = c("Subj", "IAcc", "Iawareness", "meanConfidence")
Intero_perf$Subj <- as.factor(Intero_perf$Subj)
Intero_perf$IAcc <- as.numeric(Intero_perf$IAcc)
Intero_perf$Iawareness <- as.numeric(Intero_perf$Iawareness)
Intero_perf$meanConfidence <- as.numeric(Intero_perf$meanConfidence)
```

### IAS SCALE

#### Load the preorgnised data:
```{r}
exel_file <- paste(work_dir, "Murphy_Iacc_scale.xlsx", sep="/")
Murphy_Iacc_scale <- read.xlsx(xlsxFile= exel_file, sheet = "Sheet 1")

```

##### Attention check:
```{r}
Murphy_Iacc_scale <- filter(Murphy_Iacc_scale, Question.Key != "NA")
subs <- unique(Murphy_Iacc_scale$Participant.Public.ID)
subs_num <- length(subs)

IAC_check <- matrix(NA, nrow = subs_num, ncol = 3)

for(r in 1:subs_num){
  IAC_check[r, 1] <- subs[r]
  IAC_check[r, 2] <- Murphy_Iacc_scale$Response[Murphy_Iacc_scale$Participant.Public.ID==subs[r] & Murphy_Iacc_scale$Question.Key=="response-catch-2-quantised"] == 2 # attention check
  IAC_check[r, 3] <- Murphy_Iacc_scale$Response[Murphy_Iacc_scale$Participant.Public.ID==subs[r] & Murphy_Iacc_scale$Question.Key=="IACC-Interpretation-quantised"] == 2 # interpretation check
}

```

#### Remove excluded:
```{r}
# if you are running the initial analysis
removep <- c("5b82d4fda284bc000193094c", "5bdb50e3ee652a0001efa0e0", "5db43b6a2f45e7000bb7ab5c", "5dc1e711900e3e15813f7c38", "5de7ccc24b7cf973d7b05bfb", "5e03fdb2ac9e16edc91d0108", "5e4314ad234956000a8a91f3", "5f573b18a6a8b51a94fdbd08", "5f75cd50d19e2a28374120ff", "5f78879e60d68143137b5931", "5fae5291ec402509e2885604", "6002e90144049f32edaf9ccf", "60087da4a426a14ac248b803", "601c84e07ab4907ded068d0d", "6032af5b3a3b7a2f5570fbdf", "603d301c7ebc27be3c7b5ea4", "604e1a9533738c74ad5879d2", "605996d037bce4fb5488a375", "606168c7da6829aa69acf033", "60719da557d8241609b26e83", "607f0ad32fd52dbc961cefc0", "60a183e7a5e5e6991afd6796", "60a7c099a678670592ba187a", "60af52990d170be944d0df18", "60b68fc2c92926cd9af2733b", "60b713c5f76777e302824caf", "60b87b074ce3cf9de9d47962", "60b895235deea4c7bf48b85a", "60e7360a87d1675a8574cd30", "60eb105221914f6f26a89908")

Murphy_Iacc_scale <- Murphy_Iacc_scale[ !(Murphy_Iacc_scale$Participant.Public.ID %in% removep), ]

# add if you are running the reduced sample for Schandry
removep2 <- c("575b2b408b705300078ae5e6", "588093c6704f1100014a3d01", "5a9b20c535237b0001129820", "5aeb063b2f05b500013028a0", "5bf1ecfcaf38d100016c1171", "5d07fc124e753800168ccafe", "5d68c8aa40524c00189e8ac2", "5d88b1c27250e90001c40cfc", "5d8cef3c28e183001a335ab0", "5e15e7a61d4607bd245169d9", "5e28e735ea776009d4d15c34", "5e3e11a36a0b8a000c609d5e", "5e4bc6e3a767d8018bd8e2be", "5e7d09e7f0a5a00c4a1ccf96", "5e92f26b444572122fdfe44d", "5ea976c0ae936906ffed032e", "5eaaec78a563dc0724c63b98", "5ebc2b0a9b711a04722d7382", "5ec4e3db7e31c83dfc851b83", "5ef1bb10c673fd7d2d14e439", "5f50191209e6d018aeb925f5", "5f600669b846780f0fe45709", "5f6ea775bc475b407020431f", "5f8cbc5c355ea745e6cef2ca", "5fa949031fdafd084c4d0812", "5fbb7aae04da87a3fe5f129c", "5fc92eb719e43600082952d9", "601129f77e0c21000b0c408a", "601952130cd928000a796a8b", "6022dfbafb748f0ca0385db9", "602d965dc8c74282fc222c7e", "60338f35010951035cca4a91", "603862f99e00971c55fe0874", "603ecc7968ff0bf9b25e4bf1", "603ffa13fa433c1989bff9e3", "60445f787075a64dbae085c5", "60527c19066274811cb7ca77", "607071077825ce1b96d83505", "6074b929f753216d88c77e88", "60850f02822cdda28b5ecfcb", "609478fa9e5b4d075246cfaf", "609d2b711c0593de2807d045", "60a2dffd4d05d87faf96873b", "60b405631fbdf499c48838ca", "60b60d67bbc65b38b155536e", "60c07a36ba668880b8010450", "60eb841bc608d3c01a7c5582")

Murphy_Iacc_scale <- Murphy_Iacc_scale[ !(Murphy_Iacc_scale$Participant.Public.ID %in% removep2), ]
```

#### Calculate the IAC score:
```{r}
# filter data to get only the responses:
Murphy_Iacc_scale <- filter(Murphy_Iacc_scale, Question.Key== "IAC_Itchy-quantised" | Question.Key== "IAC_BreatheFast-quantised" | Question.Key== "IAC_PleasantAffectionate-quantised" | Question.Key== "IAC_Ticklish-quantised" |
                             Question.Key== "IAC_Cough-quantised" | Question.Key== "IAC_Vomit-quantised" | Question.Key== "IAC_TiredMuscles-quantised" | Question.Key== "IAC_Thirsty-quantised" |
                             Question.Key== "IAC_Bruise-quantised" | Question.Key== "IAC_Pain-quantised" | Question.Key== "IAC_Wind-quantised" | Question.Key== "IAC_HotCold-quantised" |
                             Question.Key== "IAC_Urinate-quantised" | Question.Key== "IAC_SexuallyAroused-quantised" | Question.Key== "IAC_Sneeze-quantised" | Question.Key== "IAC_Defecate-quantised" |
                             Question.Key== "IAC_BloodSugar-quantised" | Question.Key== "IAC_Hungry-quantised" | Question.Key== "IAC_Tastes-quantised" | Question.Key == "IAC_FastHeart-quantised" | Question.Key== "IAC_Burp-quantised")

data2 <- dplyr::select(Murphy_Iacc_scale, Participant.Public.ID, Question.Key, Response)
data2$Response <- as.numeric(data2$Response)

Murphy_Iacc_data_wide <- spread(data2, Question.Key, Response)
Murphy_scores <- dplyr::mutate(Murphy_Iacc_data_wide,"total" = rowSums(Murphy_Iacc_data_wide[,2:ncol(Murphy_Iacc_data_wide)]))

Murphy_scores2 <- gather(Murphy_scores, Question.Key, Response, "IAC_BloodSugar-quantised":"total", factor_key=FALSE)

Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_BloodSugar-quantised"] <- "BloodSugar"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_BreatheFast-quantised"] <- "BreatheFast"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_Bruise-quantised"] <- "Bruise"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_Burp-quantised"] <- "Burp"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_Cough-quantised"] <- "Cough"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_Defecate-quantised"] <- "Defecate"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_FastHeart-quantised"] <- "FastHeart"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_HotCold-quantised"] <- "HotCold"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_Hungry-quantised"] <- "Hungry"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_Itchy-quantised"] <- "Itchy"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_Pain-quantised"] <- "Pain"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_PleasantAffectionate-quantised"] <- "Affectionate"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_SexuallyAroused-quantised"] <- "Aroused"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_Sneeze-quantised"] <- "Sneeze"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_Tastes-quantised"] <- "Taste"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_Thirsty-quantised"] <- "Thirsty"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_Ticklish-quantised"] <- "Ticklish"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_TiredMuscles-quantised"] <- "Muscles"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_Urinate-quantised"] <- "Urinate"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_Vomit-quantised"] <- "Vomit"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="IAC_Wind-quantised"] <- "Wind"
Murphy_scores2$Question.Key[Murphy_scores2$Question.Key=="total"] <- "Total"

Murphy_scores2$Participant.Public.ID <- as.factor(Murphy_scores2$Participant.Public.ID)
Murphy_scores2$Question.Key <- as.factor(Murphy_scores2$Question.Key)
Murphy_scores2$Response <- as.numeric(Murphy_scores2$Response)
```

#### Plot the scores:
```{r fig.width = 7, fig.height= 5}
sumld <- ddply(subset(Murphy_scores2, Question.Key != "Total"), .(Question.Key), summarise, mean = mean(Response), lb = lb(Response), ub = ub(Response))
sumld_total <- ddply(subset(Murphy_scores2, Question.Key == "Total"), .(), summarise, mean = mean(Response), lb = lb(Response), ub = ub(Response))

ddply(subset(Murphy_scores2, Question.Key == "Total"), .(), summarise, mean = mean(Response), sd = sd(Response), min = min(Response), max = max(Response))

# item-wise
p <- ggplot(sumld, aes(x = Question.Key, y = mean)) + 
  geom_point(data= subset(Murphy_scores2, Question.Key != "Total"), aes(x = Question.Key, y = Response), size= 1, color = "#899DA4", alpha = 0.1, position = position_jitter(width = 0.2, height = 0.2)) +
  geom_flat_violin(data= subset(Murphy_scores2, Question.Key != "Total"), aes(x = Question.Key, y = Response), position = position_nudge(x = 0, y = 0), alpha = 0.3, color = NA, fill = "#899DA4") +
  geom_point(aes(y = mean), size= 2, color = "#C93312") +
  geom_errorbar(aes(ymin=lb, ymax=ub), width=0, color = "#C93312") +
  geom_line(aes(y = mean, group=1), alpha= .1, color = "#C93312") +
  scale_y_continuous(limits= c(0.5,5.5), breaks = c(1:5), labels = c("1", "2", "3", "4", "5"))

p <- p + theme_classic() +
  theme(legend.position="top", 
        legend.title = element_blank(),
        text = element_text(size = 14),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(size = 14, vjust = -2, hjust = 0.5)) +
  labs(y = "Score", title = "Interoceptive accuracy scale")

# total
t <- ggplot(sumld_total, aes(x = 1, y = mean)) + 
  geom_point(data= subset(Murphy_scores2, Question.Key == "Total"), aes(x = Question.Key, y = Response), size= 1, color = "#899DA4", alpha = 0.1, position = position_jitter(width = 0.1, height = 0)) +
  geom_flat_violin(data= subset(Murphy_scores2, Question.Key == "Total"), aes(x = Question.Key, y = Response), position = position_nudge(x = 0, y = 0), alpha = 0.3, color = NA, fill = "#899DA4") +
  geom_point(aes(y = mean), size= 2, color = "#C93312") +
  geom_errorbar(aes(ymin=lb, ymax=ub), width=0, color = "#C93312") +
  scale_y_continuous(limits= c(21,105), breaks = c(25,50,75,100), labels = c("25", "50", "75", "100"))

t <- t + theme_classic() +
  theme(legend.position="top", 
        legend.title = element_blank(),
        text = element_text(size = 14),
        axis.text.x = element_blank()) +
  labs(y = "Total score", x = "")

ggdraw() +
  draw_plot(p, x = 0, y = .3, width = .6, height = .6) +
  draw_plot(t, x = .6, y = .45, width = .2, height = .5) +
  draw_plot_label(label = c("A", "B"), size = 15,
                  x = c(0.01, 0.6), y = c(0.88, 0.95))

ggsave("IAS_scores.png", width = 7, height = 5, dpi= 300)

```

### SI SCALE

#### Load the preorganised ata :
```{r}
exel_file <- paste(work_dir, "Social_scale.xlsx", sep="/")
Social_scale <- read.xlsx(xlsxFile= exel_file, sheet = "Sheet 1")

```

##### Attention check:
```{r}
Social_scale <- filter(Social_scale, Question.Key != "NA")
subs <- unique(Social_scale$Participant.Public.ID)
subs_num <- length(subs)

SI_check <- matrix(NA, nrow = subs_num, ncol = 2)

for(r in 1:subs_num){
  SI_check[r, 1] <- subs[r]
  SI_check[r, 2] <- Social_scale$Response[Social_scale$Participant.Public.ID==subs[r] & Social_scale$Question.Key=="catch-4-quantised"] == 4 # attention check
}

```

#### Remove excluded:
```{r}
# if you are running the initial analysis
removep <- c("5b82d4fda284bc000193094c", "5bdb50e3ee652a0001efa0e0", "5db43b6a2f45e7000bb7ab5c", "5dc1e711900e3e15813f7c38", "5de7ccc24b7cf973d7b05bfb", "5e03fdb2ac9e16edc91d0108", "5e4314ad234956000a8a91f3", "5f573b18a6a8b51a94fdbd08", "5f75cd50d19e2a28374120ff", "5f78879e60d68143137b5931", "5fae5291ec402509e2885604", "6002e90144049f32edaf9ccf", "60087da4a426a14ac248b803", "601c84e07ab4907ded068d0d", "6032af5b3a3b7a2f5570fbdf", "603d301c7ebc27be3c7b5ea4", "604e1a9533738c74ad5879d2", "605996d037bce4fb5488a375", "606168c7da6829aa69acf033", "60719da557d8241609b26e83", "607f0ad32fd52dbc961cefc0", "60a183e7a5e5e6991afd6796", "60a7c099a678670592ba187a", "60af52990d170be944d0df18", "60b68fc2c92926cd9af2733b", "60b713c5f76777e302824caf", "60b87b074ce3cf9de9d47962", "60b895235deea4c7bf48b85a", "60e7360a87d1675a8574cd30", "60eb105221914f6f26a89908")

Social_scale <- Social_scale[ !(Social_scale$Participant.Public.ID %in% removep), ]

# add if you are running the reduced sample for Schandry
removep2 <- c("575b2b408b705300078ae5e6", "588093c6704f1100014a3d01", "5a9b20c535237b0001129820", "5aeb063b2f05b500013028a0", "5bf1ecfcaf38d100016c1171", "5d07fc124e753800168ccafe", "5d68c8aa40524c00189e8ac2", "5d88b1c27250e90001c40cfc", "5d8cef3c28e183001a335ab0", "5e15e7a61d4607bd245169d9", "5e28e735ea776009d4d15c34", "5e3e11a36a0b8a000c609d5e", "5e4bc6e3a767d8018bd8e2be", "5e7d09e7f0a5a00c4a1ccf96", "5e92f26b444572122fdfe44d", "5ea976c0ae936906ffed032e", "5eaaec78a563dc0724c63b98", "5ebc2b0a9b711a04722d7382", "5ec4e3db7e31c83dfc851b83", "5ef1bb10c673fd7d2d14e439", "5f50191209e6d018aeb925f5", "5f600669b846780f0fe45709", "5f6ea775bc475b407020431f", "5f8cbc5c355ea745e6cef2ca", "5fa949031fdafd084c4d0812", "5fbb7aae04da87a3fe5f129c", "5fc92eb719e43600082952d9", "601129f77e0c21000b0c408a", "601952130cd928000a796a8b", "6022dfbafb748f0ca0385db9", "602d965dc8c74282fc222c7e", "60338f35010951035cca4a91", "603862f99e00971c55fe0874", "603ecc7968ff0bf9b25e4bf1", "603ffa13fa433c1989bff9e3", "60445f787075a64dbae085c5", "60527c19066274811cb7ca77", "607071077825ce1b96d83505", "6074b929f753216d88c77e88", "60850f02822cdda28b5ecfcb", "609478fa9e5b4d075246cfaf", "609d2b711c0593de2807d045", "60a2dffd4d05d87faf96873b", "60b405631fbdf499c48838ca", "60b60d67bbc65b38b155536e", "60c07a36ba668880b8010450", "60eb841bc608d3c01a7c5582")

Social_scale <- Social_scale[ !(Social_scale$Participant.Public.ID %in% removep2), ]
```

#### Calculate the SI score:
```{r}
# filter data to get only the responses:
Social_data <- filter(Social_scale, Question.Key== "SI-socialproc-1-quantised" | Question.Key== "SI-socialproc-2-quantised" | Question.Key== "SI-socialproc-3-quantised" | Question.Key== "SI-socialproc-4-quantised" | 
                        Question.Key== "SI-socialproc-5-quantised" | Question.Key== "SI-socialproc-6-quantised" | Question.Key== "SI-socialproc-7-quantised" | Question.Key== "SI-socialawareness-1-quantised" | 
                        Question.Key== "SI-socialawareness-2-quantised" | Question.Key== "SI-socialawareness-3-quantised" | Question.Key== "SI-socialawareness-4-quantised" | Question.Key== "SI-socialawareness-5-quantised" | 
                        Question.Key== "SI-socialawareness-6-quantised" | Question.Key== "SI-socialawareness-7-quantised"| Question.Key== "SI-socialskills-1-quantised" | Question.Key== "SI-socialskills-2-quantised" |
                        Question.Key== "SI-socialskills-3-quantised" | Question.Key== "SI-socialskills-4-quantised" | Question.Key== "SI-socialskills-5-quantised" | Question.Key== "SI-socialskills-6-quantised" |
                        Question.Key== "SI-socialskills-7-quantised")
data2 <- dplyr::select(Social_data, Participant.Public.ID, Question.Key, Response) # add ID in real experiment

# reverse code necessary items:
data2$Response[(data2$Question.Key=="SI-socialawareness-1-quantised" |  data2$Question.Key=="SI-socialawareness-2-quantised" | data2$Question.Key=="SI-socialawareness-3-quantised" |
                  data2$Question.Key=="SI-socialawareness-4-quantised" | data2$Question.Key=="SI-socialawareness-5-quantised" | data2$Question.Key=="SI-socialawareness-6-quantised" |
                  data2$Question.Key=="SI-socialawareness-7-quantised" | data2$Question.Key=="SI-socialskills-1-quantised" | data2$Question.Key=="SI-socialskills-4-quantised" |
                  data2$Question.Key=="SI-socialskills-5-quantised" | data2$Question.Key=="SI-socialskills-7-quantised") & data2$Response == "1"] <- 5
data2$Response[(data2$Question.Key=="SI-socialawareness-1-quantised" |  data2$Question.Key=="SI-socialawareness-2-quantised" | data2$Question.Key=="SI-socialawareness-3-quantised" |
                  data2$Question.Key=="SI-socialawareness-4-quantised" | data2$Question.Key=="SI-socialawareness-5-quantised" | data2$Question.Key=="SI-socialawareness-6-quantised" |
                  data2$Question.Key=="SI-socialawareness-7-quantised" | data2$Question.Key=="SI-socialskills-1-quantised" | data2$Question.Key=="SI-socialskills-4-quantised" |
                  data2$Question.Key=="SI-socialskills-5-quantised" | data2$Question.Key=="SI-socialskills-7-quantised") & data2$Response == "2"] <- 4
data2$Response[(data2$Question.Key=="SI-socialawareness-1-quantised" |  data2$Question.Key=="SI-socialawareness-2-quantised" | data2$Question.Key=="SI-socialawareness-3-quantised" |
                  data2$Question.Key=="SI-socialawareness-4-quantised" | data2$Question.Key=="SI-socialawareness-5-quantised" | data2$Question.Key=="SI-socialawareness-6-quantised" |
                  data2$Question.Key=="SI-socialawareness-7-quantised" | data2$Question.Key=="SI-socialskills-1-quantised" | data2$Question.Key=="SI-socialskills-4-quantised" |
                  data2$Question.Key=="SI-socialskills-5-quantised" | data2$Question.Key=="SI-socialskills-7-quantised") & data2$Response == "4"] <- 2
data2$Response[(data2$Question.Key=="SI-socialawareness-1-quantised" |  data2$Question.Key=="SI-socialawareness-2-quantised" | data2$Question.Key=="SI-socialawareness-3-quantised" |
                  data2$Question.Key=="SI-socialawareness-4-quantised" | data2$Question.Key=="SI-socialawareness-5-quantised" | data2$Question.Key=="SI-socialawareness-6-quantised" |
                  data2$Question.Key=="SI-socialawareness-7-quantised" | data2$Question.Key=="SI-socialskills-1-quantised" | data2$Question.Key=="SI-socialskills-4-quantised" |
                  data2$Question.Key=="SI-socialskills-5-quantised" | data2$Question.Key=="SI-socialskills-7-quantised") & data2$Response == "5"] <- 1

data2$Response <- as.numeric(data2$Response)

# put scores together
Social_data_wide <- spread(data2, Question.Key, Response)
Social_data_wide$SP_total <- rowSums(Social_data_wide[ ,c("SI-socialproc-1-quantised", "SI-socialproc-2-quantised", "SI-socialproc-3-quantised", "SI-socialproc-4-quantised", 
                                                         "SI-socialproc-5-quantised", "SI-socialproc-6-quantised", "SI-socialproc-7-quantised")])
Social_data_wide$SA_total <- rowSums(Social_data_wide[ ,c("SI-socialawareness-1-quantised", "SI-socialawareness-2-quantised", "SI-socialawareness-3-quantised", "SI-socialawareness-4-quantised",
                                                          "SI-socialawareness-5-quantised", "SI-socialawareness-6-quantised", "SI-socialawareness-7-quantised")])
Social_data_wide$SS_total <- rowSums(Social_data_wide[ ,c("SI-socialskills-1-quantised", "SI-socialskills-2-quantised", "SI-socialskills-3-quantised", "SI-socialskills-4-quantised", 
                                                          "SI-socialskills-5-quantised", "SI-socialskills-6-quantised", "SI-socialskills-7-quantised")])
Social_data_wide$total <- rowSums(Social_data_wide[ ,c("SP_total", "SA_total", "SS_total")])
Social_data_wide <- dplyr::select(Social_data_wide, Participant.Public.ID, SP_total, SA_total, SS_total, total)

SI_scores <- gather(Social_data_wide, Question.Key, Response, SP_total:total, factor_key=FALSE)

SI_scores$Participant.Public.ID <- as.factor(SI_scores$Participant.Public.ID)
SI_scores$Question.Key <- as.factor(SI_scores$Question.Key)
SI_scores$Response <- as.numeric(SI_scores$Response)

```

#### Plot the scores:
```{r fig.width = 6, fig.height= 4}
sumld <- ddply(subset(SI_scores, Question.Key != "total"), .(Question.Key), summarise, mean = mean(Response), lb = lb(Response), ub = ub(Response))
sumld_total <- ddply(subset(SI_scores, Question.Key == "total"), .(), summarise, mean = mean(Response), lb = lb(Response), ub = ub(Response))

ddply(subset(SI_scores, Question.Key == "total"), .(), summarise, mean = mean(Response), sd = sd(Response), min = min(Response), max = max(Response))

# item-wise
p <- ggplot(sumld, aes(x = Question.Key, y = mean)) + 
  geom_point(data= subset(SI_scores, Question.Key != "total"), aes(x = Question.Key, y = Response), size= 1, color = "#899DA4", alpha = 0.1, position = position_jitter(width = 0.1, height = 0)) +
  geom_flat_violin(data= subset(SI_scores, Question.Key != "total"), aes(x = Question.Key, y = Response), position = position_nudge(x = 0, y = 0), alpha = 0.3, color = NA, fill = "#899DA4") +
  geom_point(aes(y = mean), size= 2, color = "#C93312") +
  geom_errorbar(aes(ymin=lb, ymax=ub), width=0, color = "#C93312") +
  geom_line(aes(y = mean, group=1), alpha= .1, color = "#C93312") +
  scale_y_continuous(limits= c(6,35), breaks = c(10,20,30), labels = c("10", "20", "30")) +
  scale_x_discrete(labels = c("Awareness", "Processing", "Skill"))

p <- p + theme_classic() +
  theme(legend.position="top", 
        legend.title = element_blank(),
        text = element_text(size = 14),
        plot.title = element_text(size = 14, vjust = -2, hjust = 0.5)) +
  labs(y = "Score", x ="" ,title = "Tromo's social intelligence scale")

# total
t <- ggplot(sumld_total, aes(x = 1, y = mean)) + 
  geom_point(data= subset(SI_scores, Question.Key == "total"), aes(x = Question.Key, y = Response), size= 1, color = "#899DA4", alpha = 0.1, position = position_jitter(width = 0.1, height = 0)) +
  geom_flat_violin(data= subset(SI_scores, Question.Key == "total"), aes(x = Question.Key, y = Response), position = position_nudge(x = 0, y = 0), alpha = 0.3, color = NA, fill = "#899DA4") +
  geom_point(aes(y = mean), size= 2, color = "#C93312") +
  geom_errorbar(aes(ymin=lb, ymax=ub), width=0, color = "#C93312") +
  scale_y_continuous(limits= c(21,105), breaks = c(25,50,75,100), labels = c("25", "50", "75", "100"))

t <- t + theme_classic() +
  theme(legend.position="top", 
        legend.title = element_blank(),
        text = element_text(size = 14),
        axis.text.x = element_blank()) +
  labs(y = "Total score", x = "")

ggdraw() +
  draw_plot(p, x = 0, y = .3, width = .6, height = .6) +
  draw_plot(t, x = .6, y = .35, width = .2, height = .5) +
  draw_plot_label(label = c("A", "B"), size = 15,
                  x = c(0.01, 0.6), y = c(0.87, 0.87))

ggsave("SI_scores.pdf", width = 6, height = 4, dpi= 300)

```

#### Correlate the sub scores:
```{r fig.width = 2.5, fig.height= 2.5}
# needs to be in long format -> each column a variable -> so I will use Social_data_wide
names(Social_data_wide) <- c("Participant", "Processing", "Awareness", "Skill", "total")

res <- rcorr(as.matrix(Social_data_wide[ ,2:5])) # this gives both: r and p values
round(res$P, 3)

# produce and save the plot (saving [png and dev.off] is commented to not overwrite existing save)

# pdf(file="SI_corrs.pdf", width = 3, height = 3)

cor <- corrplot(res$r, type="upper", 
         p.mat = res$P, sig.level = 0.05, 
         tl.col = "black", tl.srt = 45, tl.cex = .8, cl.align = "l")

# dev.off() # onlt works when chunks are displayed in console and not inline!!

```

### I will add some values from IAS (diff between objctive-subjective) to interoceptive measure dataframe
```{r}
Murphy <- subset(Murphy_scores2, Question.Key == "Total")
Murphy$Participant.Public.ID <- as.character(Murphy$Participant.Public.ID)

# transform Murphy's scores to 0 and 1:
# (1) subtract 21: so min score is 0:
Murphy$score_standard <- Murphy$Response - 21
# (2) 84 = 1, so x = Resp / 84
Murphy$score_standard <- Murphy$score_standard/84

#Murphy['score_standard'] <- as.data.frame(scale(Murphy$Response, center = FALSE, scale = TRUE)) # z transform - need to do this way otherwise saves it in a weird format
#Intero_perf['IAcc_standard'] <- as.data.frame(scale(Intero_perf$IAcc, center = FALSE, scale = TRUE)) # z transform - need to do this way otherwise saves it in a weird format

# Calculate the difference:
subs <- unique(Schandry_onlyaccepted$Subj.ID)
subs_num <- length(subs)

for(s in 1:subs_num) {

Intero_perf$SubjvsObj[Intero_perf$Subj==subs[s]] <- Intero_perf$IAcc[Intero_perf$Subj==subs[s]] - Murphy$score_standard[Murphy$Participant.Public.ID==subs[s]]
Intero_perf$IAS[Intero_perf$Subj==subs[s]] <- Murphy$Response[Murphy$Participant.Public.ID==subs[s]]
}

# positive values on SubjvsObj mean underestimation (IAcc is gearter than IAS)
# negative values mean overestimation (IAcc is smaller than IAS)

```

#### Plot the interoceptive measures:
```{r}
## IAcc
# check if above chance:
x <- dplyr::select(Intero_perf, IAcc)
shapiro.test(x$IAcc) # p-value = 0.22 so normal distribution
res <- t.test(x$IAcc, mu = 0)
format(res$p.value, scientific = FALSE)

if (res$p.value < .001){p_string = "p < .001"} else {p_string = paste("p =", round(res$p.value, digits=3), sep = " ")}

coh <- cohens_d(data= x, IAcc ~ 1, mu= 0)
p_string2 <- paste(p_string, ", d =", round(coh$effsize, digits = 2), sep = " ")

ddply(x, .(), summarise, mean = mean(IAcc), min = min(IAcc), max = max(IAcc), sd = sd(IAcc))

# plot
sumld <- ddply(x, .(), summarise, mean = mean(IAcc), lb = lb(IAcc), ub = ub(IAcc))

p <- ggplot(sumld, aes(x = 1, y=mean)) +
  geom_bar(stat="identity", color="black", fill= "#C93312", position=position_dodge()) +
  geom_errorbar(aes(ymin=lb, ymax=ub), width=0, size= 2, position=position_dodge(.9)) +
  geom_point(data= x, aes(x = 1, y=IAcc), alpha= 0.2, position=position_jitter(width = 0.1, height = 0)) +
  geom_abline(intercept = 0, slope = 0, color="#899DA4", linetype="dashed") +
  scale_y_continuous(limits= c(0,1), breaks = c(0, 0.5, 1), labels = c("0", "0.5", "1")) +
  scale_x_continuous(limits= c(0,2), breaks = c(1), labels = c("")) +
  annotate("text", x = 1, y = 1, label = p_string2)

p <- p + theme_classic() +
  theme(text = element_text(size = 12),
        legend.position = "none") +
  labs(x="", y = "Accuracy")

## meanConfidence
x <- dplyr::select(Intero_perf, meanConfidence)
ddply(x, .(), summarise, mean = mean(meanConfidence), min = min(meanConfidence), max = max(meanConfidence), sd = sd(meanConfidence))

# plot
sumld <- ddply(x, .(), summarise, mean = mean(meanConfidence), lb = lb(meanConfidence), ub = ub(meanConfidence))

c <- ggplot(sumld, aes(x = 1, y=mean)) +
  geom_bar(stat="identity", color="black", fill= "#C93312", position=position_dodge()) +
  geom_errorbar(aes(ymin=lb, ymax=ub), width=0, size= 2, position=position_dodge(.9)) +
  geom_point(data= x, aes(x = 1, y=meanConfidence), alpha= 0.2, position=position_jitter(width = 0.1, height = 0)) +
  #geom_abline(intercept = 0.5, slope = 0, color="#899DA4", linetype="dashed") +
  scale_y_continuous(limits= c(0,1), breaks = c(0, 0.5, 1), labels = c("0", "0.5", "1")) +
  scale_x_continuous(limits= c(0,2), breaks = c(1), labels = c(""))

c <- c + theme_classic() +
  theme(text = element_text(size = 12),
        legend.position = "none") +
  labs(x="", y = "Mean confidence")

## IAwareness
# check if above chance:
x <- dplyr::select(Intero_perf, Iawareness)
shapiro.test(x$Iawareness) # p-value = 0.22 so normal distribution
res <- t.test(x$Iawareness, mu = 0)
format(res$p.value, scientific = FALSE)

if (res$p.value < .001){p_string = "p < .001"} else {p_string = paste("p =", round(res$p.value, digits=3), sep = " ")}

coh <- cohens_d(data= x, Iawareness ~ 1, mu= 0)
p_string2 <- paste(p_string, ", d =", round(coh$effsize, digits = 2), sep = " ")

ddply(x, .(), summarise, mean = mean(Iawareness), min = min(Iawareness), max = max(Iawareness), sd = sd(Iawareness))

# plot
sumld <- ddply(x, .(), summarise, mean = mean(Iawareness), lb = lb(Iawareness), ub = ub(Iawareness))

i <- ggplot(sumld, aes(x = 1, y=mean)) +
  geom_bar(stat="identity", color="black", fill= "#C93312", position=position_dodge()) +
  geom_errorbar(aes(ymin=lb, ymax=ub), width=0, size= 2, position=position_dodge(.9)) +
  geom_point(data= x, aes(x = 1, y=Iawareness), alpha= 0.2, position=position_jitter(width = 0.1, height = 0)) +
  geom_abline(intercept = 0, slope = 0, color="#899DA4", linetype="dashed") +
  #scale_y_continuous(limits= c(0,1.1), breaks = c(0, 0.5, 1), labels = c("0", "0.5", "1")) +
  scale_x_continuous(limits= c(0,2), breaks = c(1), labels = c("")) +
  annotate("text", x = 1, y = 1.1, label = p_string2)

i <- i + theme_classic() +
  theme(text = element_text(size = 12),
        legend.position = "none") +
  labs(x="", y = "Congruence: acc & conf")

## Conguency between subjective accuracy and objective accuracy
# check if above chance:
x <- dplyr::select(Intero_perf, SubjvsObj)
shapiro.test(x$SubjvsObj) # p-value = 0.22 so normal distribution
res <- t.test(x$SubjvsObj, mu = 0)
format(res$p.value, scientific = FALSE)

if (res$p.value < .001){p_string = "p < .001"} else {p_string = paste("p =", round(res$p.value, digits=3), sep = " ")}

coh <- cohens_d(data= x, SubjvsObj ~ 1, mu= 0)
p_string2 <- paste(p_string, ", d =", round(coh$effsize, digits = 2), sep = " ")

ddply(x, .(), summarise, mean = mean(SubjvsObj), min = min(SubjvsObj), max = max(SubjvsObj), sd = sd(SubjvsObj))

# plot
sumld <- ddply(x, .(), summarise, mean = mean(SubjvsObj), lb = lb(SubjvsObj), ub = ub(SubjvsObj))

sub <- ggplot(sumld, aes(x = 1, y=mean)) +
  geom_bar(stat="identity", color="black", fill= "#C93312", position=position_dodge()) +
  geom_errorbar(aes(ymin=lb, ymax=ub), width=0, size= 2, position=position_dodge(.9)) +
  geom_point(data= x, aes(x = 1, y=SubjvsObj), alpha= 0.2, position=position_jitter(width = 0.1, height = 0)) +
  geom_abline(intercept = 0, slope = 0, color="#899DA4", linetype="dashed") +
  #scale_y_continuous(limits= c(0,1.1), breaks = c(0, 0.5, 1), labels = c("0", "0.5", "1")) +
  scale_x_continuous(limits= c(0,2), breaks = c(1), labels = c("")) +
  annotate("text", x = 1, y = 1.1, label = p_string2)

sub <- sub + theme_classic() +
  theme(text = element_text(size = 12),
        legend.position = "none") +
  labs(x="", y = "Congruence: Acc & IAS")

```

#### Plot all together:
```{r fig.width = 5, fig.height= 5}
g <- ggarrange(p, c, i, sub,
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2)
suppressWarnings(print(g))

ggsave("Intero_measures.png", g, width = 5, height = 5, dpi= 300)

```

#### Correlation between interoceptive measures:
```{r}
res <- rcorr(as.matrix(Intero_perf[ ,2:6])) # this gives both: r and p values
round(res$P, 3)

# produce and save the plot (saving [png and dev.off] is commented to not overwrite existing save)

# pdf(file="Intero_corrs.pdf", width = 4, height = 4)

cor <- corrplot(res$r, type="upper", 
         p.mat = res$P, sig.level = 0.05, 
         tl.col = "black", tl.srt = 45, tl.cex = .8, cl.align = "l")

# dev.off() # onlt works when chunks are displayed in console and not inline!!

# explore the correlations
ggscatter(Intero_perf, x = "IAcc", y = "Iawareness", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "I_Acc", ylab = "SubjvsObj")

# ggsave("fig.pdf", width = 3, height = 3, dpi= 300)

ggscatter(Intero_perf, x = "Iawareness", y = "meanConfidence", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Iawareness", ylab = "meanConfidence")

```

### ACTOR HR TASK
#### Load the data:
```{r}
exel_file <- paste(work_dir, "ActorHR_data.xlsx", sep="/")
ActorHR_data <- read.xlsx(xlsxFile= exel_file, sheet = "Sheet 1")

```

##### Checks:
(1) device needs to be computer, (2) the window size needs to stay the same, 
(3) owl attention checks correct

```{r}
ActorHR_data <- filter(ActorHR_data, Participant.Device.Type != "NA" & Spreadsheet.Row != "NA")
subs <- unique(ActorHR_data$Participant.Public.ID)
subs_num <- length(subs)

ActorHR_check <- matrix(NA, nrow = subs_num, ncol = 6)

for(r in 1:subs_num){
  ActorHR_check[r, 1] <- subs[r]
  ActorHR_check[r, 2] <- ActorHR_data$Participant.Device.Type[ActorHR_data$Participant.Public.ID==subs[r]][1] # should be always "computer"
  ActorHR_check[r, 3] <- length(unique(ActorHR_data$Participant.Viewport.Size[ActorHR_data$Participant.Public.ID==subs[r]])) # should be always 1
  ActorHR_check[r, 4] <- sum(as.numeric(na.omit(ActorHR_data$Response[ActorHR_data$Participant.Public.ID==subs[r] & ActorHR_data$Zone.Type == "response_text_entry"])[1:2])) == 12 # owl responses must equal 12 [5 + 7]
  ActorHR_check[r, 5:6] <- ActorHR_data$Response[ActorHR_data$Participant.Public.ID==subs[r] & ActorHR_data$Zone.Type == "response_text_area"]
}

```

#### Organise into workabale sheet:
```{r}
data <- filter(ActorHR_data, Screen.Name == "Response" | (Screen.Name == "Confidence rating" & Zone.Type == "response_slider_endValue"))
data2 <- dplyr::select(data, Participant.Public.ID, Trial.Number, Spreadsheet.Row, Screen.Name, Response)
data_wide <- tidyr::spread(data2, Screen.Name, Response)

```

#### Get the spreadsheet and define the specific videos used:
```{r}
exel_file <- paste(work_dir, "spreadsheet.xlsx", sep="/")
spreadsheet <- read.xlsx(xlsxFile= exel_file, sheet = "task")

# loop through each row of data_wide and get the Spreadsheet.Row
# depending on that take the video combination, left_screen, right_screen, correct
stim <- matrix(, nrow = nrow(data_wide), ncol = 4)

for(r in 1:nrow(data_wide)) {
  sheet_row <- data_wide$Spreadsheet.Row[r]
  stim[r, 1] <- spreadsheet$video.combination[sheet_row]
  stim[r, 2] <- spreadsheet$left_screen[sheet_row]
  stim[r, 3] <- spreadsheet$right_screen[sheet_row]
  stim[r, 4] <- spreadsheet$correct[sheet_row]
}
colnames(stim) <- c("video_comb", "left_actor", "right_actor", "correct")
stim2 <- as.data.frame(stim)

data_wide <- cbind(data_wide, stim2)

data_wide$resp[data_wide$Response=="a"] <- "left"
data_wide$resp[data_wide$Response=="k"] <- "right"

data_wide$Trial.Number <- as.numeric(data_wide$Trial.Number)
data_wide$`Confidence rating` <- as.numeric(data_wide$`Confidence rating`)

names(data_wide)[names(data_wide) == "Confidence rating"] <- "Confidence.Rating"

```
#### Add the values required for d prime:
H <- response == L & HB == L
F <- response == L & HB == R
```{r}
for(r in 1:nrow(data_wide)) {

  if(data_wide$resp[r]== "left" & data_wide$correct[r]== "left"){
    data_wide$H[r] <- 1
    data_wide$acc[r] <- 1
    data_wide$F[r] <- 0}
  else if(data_wide$resp[r]== "left" & data_wide$correct[r]== "right"){
    data_wide$H[r] <- 0
    data_wide$acc[r] <- 0
    data_wide$F[r] <- 1}
  else if(data_wide$resp[r]== "right" & data_wide$correct[r]== "right"){
    data_wide$H[r] <- 0
    data_wide$acc[r] <- 1
    data_wide$F[r] <- 0}
  else if(data_wide$resp[r]== "right" & data_wide$correct[r]== "left"){
    data_wide$H[r] <- 0
    data_wide$acc[r] <- 0
    data_wide$F[r] <- 0}
}

data_wide$acc_factor[data_wide$acc==0] <- 1
data_wide$acc_factor[data_wide$acc==1] <- 2
data_wide$acc_factor <- factor(data_wide$acc_factor, levels=c(1,2), labels=c("incorrect", "correct"))

```

#### Get the mean measures for each participant:
```{r}
subs <- unique(data_wide$Participant.Public.ID)
subs_num <- length(subs)
ActorHR_measures <- matrix(NA, nrow = subs_num, ncol = 5)

for(r in 1:subs_num){
  x <- subset(data_wide, Participant.Public.ID==subs[r])

  pH <- sum(x$H)/42 # 42 because it is half of all trials (84)
  pF <- sum(x$F)/42

  ActorHR_measures[r, 1] <- subs[r]
  ActorHR_measures[r, 2] <- round(sum(x$acc)/84, digits = 2) # accuray - proportion correct
  ActorHR_measures[r, 3] <- round(qnorm(pH)-qnorm(pF), digits = 2) # d prime
  ActorHR_measures[r, 4] <- round((-0.5)*(qnorm(pH)+qnorm(pF)), digits = 2) # neg values -> bias towards HIT -> in our case left
  ActorHR_measures[r, 5] <- round(mean(x$Confidence.Rating), digits = 2)
}

# make into a dataframe:
ActorHR_measures <- as.data.frame(ActorHR_measures)
names(ActorHR_measures) <- c("Participant", "pAcc", "dprime", "bias", "mConfidence")
ActorHR_measures$pAcc <- as.numeric(ActorHR_measures$pAcc)
ActorHR_measures$dprime <- as.numeric(ActorHR_measures$dprime)
ActorHR_measures$bias <- as.numeric(ActorHR_measures$bias)
ActorHR_measures$mConfidence <- as.numeric(ActorHR_measures$mConfidence)

```

#### Remove participants:
```{r}
# if you are running the initial analysis
removep <- c("5b82d4fda284bc000193094c", "5bdb50e3ee652a0001efa0e0", "5db43b6a2f45e7000bb7ab5c", "5dc1e711900e3e15813f7c38", "5de7ccc24b7cf973d7b05bfb", "5e03fdb2ac9e16edc91d0108", "5e4314ad234956000a8a91f3", "5f573b18a6a8b51a94fdbd08", "5f75cd50d19e2a28374120ff", "5f78879e60d68143137b5931", "5fae5291ec402509e2885604", "6002e90144049f32edaf9ccf", "60087da4a426a14ac248b803", "601c84e07ab4907ded068d0d", "6032af5b3a3b7a2f5570fbdf", "603d301c7ebc27be3c7b5ea4", "604e1a9533738c74ad5879d2", "605996d037bce4fb5488a375", "606168c7da6829aa69acf033", "60719da557d8241609b26e83", "607f0ad32fd52dbc961cefc0", "60a183e7a5e5e6991afd6796", "60a7c099a678670592ba187a", "60af52990d170be944d0df18", "60b68fc2c92926cd9af2733b", "60b713c5f76777e302824caf", "60b87b074ce3cf9de9d47962", "60b895235deea4c7bf48b85a", "60e7360a87d1675a8574cd30", "60eb105221914f6f26a89908")

ActorHR_measures_onlyAccepted <- ActorHR_measures[ !(ActorHR_measures$Participant %in% removep), ]
data_wide_onlyAccepted <- data_wide[ !(data_wide$Participant.Public.ID %in% removep), ]

# add if you are running the reduced sample for Schandry
removep2 <- c("575b2b408b705300078ae5e6", "588093c6704f1100014a3d01", "5a9b20c535237b0001129820", "5aeb063b2f05b500013028a0", "5bf1ecfcaf38d100016c1171", "5d07fc124e753800168ccafe", "5d68c8aa40524c00189e8ac2", "5d88b1c27250e90001c40cfc", "5d8cef3c28e183001a335ab0", "5e15e7a61d4607bd245169d9", "5e28e735ea776009d4d15c34", "5e3e11a36a0b8a000c609d5e", "5e4bc6e3a767d8018bd8e2be", "5e7d09e7f0a5a00c4a1ccf96", "5e92f26b444572122fdfe44d", "5ea976c0ae936906ffed032e", "5eaaec78a563dc0724c63b98", "5ebc2b0a9b711a04722d7382", "5ec4e3db7e31c83dfc851b83", "5ef1bb10c673fd7d2d14e439", "5f50191209e6d018aeb925f5", "5f600669b846780f0fe45709", "5f6ea775bc475b407020431f", "5f8cbc5c355ea745e6cef2ca", "5fa949031fdafd084c4d0812", "5fbb7aae04da87a3fe5f129c", "5fc92eb719e43600082952d9", "601129f77e0c21000b0c408a", "601952130cd928000a796a8b", "6022dfbafb748f0ca0385db9", "602d965dc8c74282fc222c7e", "60338f35010951035cca4a91", "603862f99e00971c55fe0874", "603ecc7968ff0bf9b25e4bf1", "603ffa13fa433c1989bff9e3", "60445f787075a64dbae085c5", "60527c19066274811cb7ca77", "607071077825ce1b96d83505", "6074b929f753216d88c77e88", "60850f02822cdda28b5ecfcb", "609478fa9e5b4d075246cfaf", "609d2b711c0593de2807d045", "60a2dffd4d05d87faf96873b", "60b405631fbdf499c48838ca", "60b60d67bbc65b38b155536e", "60c07a36ba668880b8010450", "60eb841bc608d3c01a7c5582")

ActorHR_measures_onlyAccepted <- ActorHR_measures_onlyAccepted[ !(ActorHR_measures_onlyAccepted$Participant %in% removep2), ]
data_wide_onlyAccepted <- data_wide_onlyAccepted[ !(data_wide_onlyAccepted$Participant.Public.ID %in% removep2), ]

# or use ALL:
#ActorHR_measures_onlyAccepted <- ActorHR_measures
#data_wide_onlyAccepted <- data_wide

```

#### Create plot for the measures and perform one-sample t-test analysis:
```{r}
## pAcc
# check if above chance:
x <- dplyr::select(ActorHR_measures_onlyAccepted, pAcc)
shapiro.test(x$pAcc) # p-value = 0.22 so normal distribution
res <- t.test(x$pAcc, mu = 0.5)
format(res$p.value, scientific = FALSE)

if (res$p.value < .001){p_string = "p < .001"} else {p_string = paste("p =", round(res$p.value, digits=3), sep = " ")}

coh <- cohens_d(data= x, pAcc ~ 1, mu= 0.5)
p_string2 <- paste(p_string, ", d =", round(coh$effsize, digits = 3), sep = " ")

ddply(x, .(), summarise, mean = mean(pAcc), min = min(pAcc), max = max(pAcc), sd = sd(pAcc))

# plot
sumld <- ddply(x, .(), summarise, mean = mean(pAcc), lb = lb(pAcc), ub = ub(pAcc))

p <- ggplot(sumld, aes(x = 1, y=mean)) +
  geom_bar(stat="identity", color="black", fill= "#C93312", position=position_dodge()) +
  geom_errorbar(aes(ymin=lb, ymax=ub), width=0, size= 2, position=position_dodge(.9)) +
  geom_point(data= x, aes(x = 1, y=pAcc), alpha= 0.2, position=position_jitter(width = 0.1, height = 0)) +
  geom_abline(intercept = 0.5, slope = 0, color="#899DA4", linetype="dashed") +
  scale_y_continuous(limits= c(0,1), breaks = c(0, 0.5, 1), labels = c("0", "0.5", "1")) +
  scale_x_continuous(limits= c(0,2), breaks = c(1), labels = c("")) +
  annotate("text", x = 1, y = 1, label = p_string2)

p <- p + theme_classic() +
  theme(text = element_text(size = 14),
        legend.position = "none") +
  labs(x="", y = "Accuracy")

## dprime
# check if above chance:
x <- dplyr::select(ActorHR_measures_onlyAccepted, dprime)
shapiro.test(x$dprime) # p-value = 0.16 so normal distribution
res <- t.test(x$dprime, mu = 0)
format(res$p.value, scientific = FALSE)

if (res$p.value < .001){p_string = "p < .001"} else {p_string = paste("p =", round(res$p.value, digits=3), sep = " ")}

coh <- cohens_d(data= x, dprime ~ 1, mu= 0)
p_string2 <- paste(p_string, ", d =", round(coh$effsize, digits = 3), sep = " ")

# plot
sumld <- ddply(x, .(), summarise, mean = mean(dprime), lb = lb(dprime), ub = ub(dprime))

d <- ggplot(sumld, aes(x = 1, y=mean)) +
  geom_bar(stat="identity", color="black", fill= "#C93312", position=position_dodge()) +
  geom_errorbar(aes(ymin=lb, ymax=ub), width=0, size= 2, position=position_dodge(.9)) +
  geom_point(data= x, aes(x = 1, y=dprime), alpha= 0.2, position=position_jitter(width = 0.1, height = 0)) +
  geom_abline(intercept = 0, slope = 0, color="#899DA4", linetype="dashed") +
  #scale_y_continuous(limits= c(0,1), breaks = c(0, 0.5, 1), labels = c("0", "0.5", "1")) +
  scale_x_continuous(limits= c(0,2), breaks = c(1), labels = c("")) +
  annotate("text", x = 1, y = 1.5, label = p_string2)

d <- d + theme_classic() +
  theme(text = element_text(size = 14),
        legend.position = "none") +
  labs(x="", y = "D Prime")

## bias
# check if above chance:
x <- dplyr::select(ActorHR_measures_onlyAccepted, bias)
shapiro.test(x$bias) # p-value = 0.005 -> normality violated
res <- t.test(x$bias, mu = 0)
format(res$p.value, scientific = FALSE)

if (res$p.value < .001){p_string = "p < .001"} else {p_string = paste("p =", round(res$p.value, digits=3), sep = " ")}

coh <- cohens_d(data= x, bias ~ 1, mu= 0)
p_string2 <- paste(p_string, ", d =", round(coh$effsize, digits = 3), sep = " ")

# plot
sumld <- ddply(x, .(), summarise, mean = mean(bias), lb = lb(bias), ub = ub(bias))

b <- ggplot(sumld, aes(x = 1, y=mean)) +
  geom_bar(stat="identity", color="black", fill= "#C93312", position=position_dodge()) +
  geom_errorbar(aes(ymin=lb, ymax=ub), width=0, size= 2, position=position_dodge(.9)) +
  geom_point(data= x, aes(x = 1, y=bias), alpha= 0.2, position=position_jitter(width = 0.1, height = 0)) +
  geom_abline(intercept = 0, slope = 0, color="#899DA4", linetype="dashed") +
  #scale_y_continuous(limits= c(0,1), breaks = c(0, 0.5, 1), labels = c("0", "0.5", "1")) +
  scale_x_continuous(limits= c(0,2), breaks = c(1), labels = c("")) +
  annotate("text", x = 1, y = 1, label = p_string2)

b <- b + theme_classic() +
  theme(text = element_text(size = 14),
        legend.position = "none") +
  labs(x="", y = "Bias")

## plot mean confidence
x <- dplyr::select(ActorHR_measures_onlyAccepted, mConfidence)
ddply(x, .(), summarise, mean = mean(mConfidence), min = min(mConfidence), max = max(mConfidence), sd = sd(mConfidence))

sumld <- ddply(x, .(), summarise, mean = mean(mConfidence), lb = lb(mConfidence), ub = ub(mConfidence))

con <- ggplot(sumld, aes(x = 1, y=mean)) +
  geom_bar(stat="identity", color="black", fill= "#C93312", position=position_dodge()) +
  geom_errorbar(aes(ymin=lb, ymax=ub), width=0, size= 2, position=position_dodge(.9)) +
  geom_point(data= x, aes(x = 1, y=mConfidence), alpha= 0.2, position=position_jitter(width = 0.1, height = 0)) +
  geom_abline(intercept = 0, slope = 0, color="#899DA4", linetype="dashed") +
  scale_y_continuous(limits= c(0,10), breaks = c(0, 5, 10), labels = c("0", "5", "10")) +
  scale_x_continuous(limits= c(0,2), breaks = c(1), labels = c(""))
  #annotate("text", x = 1, y = 1, label = p_string2)

con <- con + theme_classic() +
  theme(text = element_text(size = 14),
        legend.position = "none") +
  labs(x="", y = "Mean Confidence")

## correlation between dprime and accuracy:
c <- ggscatter(ActorHR_measures_onlyAccepted, x = "pAcc", y = "dprime", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Accuracy", ylab = "D Prime")

## confidence between accuracte and inaccurate:

# Paired sample between incorrect and correct
confdata_P <- aggregate(Confidence.Rating ~ Participant.Public.ID + acc_factor, data= data_wide_onlyAccepted, mean)
confdata <- ddply(confdata_P, c("acc_factor"), summarise, mean = mean(Confidence.Rating), lb = lb(Confidence.Rating), ub = ub(Confidence.Rating))

var.test(Confidence.Rating ~ acc_factor, data = confdata_P) # p=0.98 -> no difference in variance
wide <- spread(confdata_P, acc_factor, Confidence.Rating)
wide <- wide %>% mutate(differences = correct - incorrect)
shapiro_test(wide$differences)

res <- t.test(Confidence.Rating ~ acc_factor, data= confdata_P, paired = TRUE, var.equal = TRUE)
coh <- cohens_d(confdata_P, Confidence.Rating ~ acc_factor, paired= TRUE, var.equal= TRUE)

if (res$p.value < .001){p_string = "p < .001"} else {p_string = paste("p =", round(res$p.value, digits=3), sep = " ")}
p_string2 <- paste(p_string, ", d =", round(coh$effsize, digits = 3), sep = " ")

# plot:
con_levels <- ggplot(confdata, aes(x=acc_factor, y=mean)) +
  geom_bar(stat="identity", color="black", fill= "#C93312", position=position_dodge()) +
  geom_errorbar(aes(ymin=lb, ymax=ub), width=0, position=position_dodge(.9)) +
  geom_point(data= confdata_P, aes(x = acc_factor, y=Confidence.Rating), position=position_dodge(.9)) +
  geom_line(data= confdata_P, aes(x = acc_factor, y=Confidence.Rating, group = Participant.Public.ID), color="#899DA4", alpha = 0.5) +
  scale_y_continuous(limits= c(0,10.5), breaks = c(0, 5, 10), labels = c("0", "5", "10")) +
  annotate("text", x = 1.5, y = 10.5, label = p_string2)

con_levels <- con_levels + theme_classic() +
  theme(text = element_text(size = 14)) +
  labs(x="Accuracy", y = "Mean confidence")
con_levels

# correlation between accuracy and confidence
ggscatter(ActorHR_measures_onlyAccepted, x = "pAcc", y = "mConfidence", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Accuracy", ylab = "Confidence")

```

#### Plot all together:
```{r fig.width = 7, fig.height= 6}
g <- ggarrange(p, d, c, b, con, con_levels,
          labels = c("A", "B", "C", "D", "E", "F"),
          ncol = 3, nrow = 2)
suppressWarnings(print(g))

ggsave("ActorHR.png", g, width = 7, height = 6, dpi= 300)

```

#### Put conf difference into the main measures dataset:
```{r}
# this is in dataframe: wide, which was used above for Shaphiro

subs <- unique(ActorHR_measures_onlyAccepted$Participant)
subs_num <- length(subs)

for(r in 1:subs_num){
  ActorHR_measures_onlyAccepted$ConfDiff[ActorHR_measures_onlyAccepted$Participant == subs[r]] <- wide$differences[wide$Participant.Public.ID == subs[r]] # better participants -> more positive
}

```

##### Responses at each confidence level:
```{r fig.width = 4, fig.height= 2}
confdata_P <- ddply(data_wide_onlyAccepted, c("Participant.Public.ID","Confidence.Rating" ,"acc_factor"), summarise, n = length(acc_factor))
confdata_P$Confidence.Rating <- as.factor(confdata_P$Confidence.Rating)
confdata <- aggregate(n ~ Confidence.Rating + acc_factor, data= confdata_P, mean)

p <- ggplot(confdata, aes(x=Confidence.Rating, y=n, fill= acc_factor)) +
  geom_bar(stat="identity", color="black", position=position_dodge()) +
  scale_fill_manual(values = c("#899DA4", "#C93312"))
  #scale_y_continuous(limits= c(0,10), breaks = c(0, 5, 10), labels = c("0", "5", "10"))

p <- p + theme_classic() +
  theme(legend.position="top", 
        legend.title = element_blank(),
        text = element_text(size = 14)) +
  labs(x="Confidence", y = "Nr. of responses")
p

```

##### Add prompt as a factor:

```{r}
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="55fb380977f33b0012cb1fc2"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5c629b836e03a00001d47bdd"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5cf9179b8c98dc0001d5a431"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5d0f89123382180001624f48"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5d7f460632ee8a0018dc7502"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5d8cef3c28e183001a335ab0"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5e4bc6e3a767d8018bd8e2be"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5e5e3f5c9dad80156c98b89c"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5e7d09e7f0a5a00c4a1ccf96"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5ebc2b0a9b711a04722d7382"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5ebfa146d86a5137c31b105d"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5ef1bb10c673fd7d2d14e439"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5f3013e31c8a690aacb02c31"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5f8cbc5c355ea745e6cef2ca"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5faff8d93849f12f7e013042"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5fbb7aae04da87a3fe5f129c"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60021cc6d5be39201d34f6bf"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="601952130cd928000a796a8b"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="6023f94d1951e70ae21770ec"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60445f787075a64dbae085c5"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="6086a082cfd8e051845166e0"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="609592f5c75f5c00c1fcc87e"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="609720f77227ed736f8426cf"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="609d2b711c0593de2807d045"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60b535024ca96f70d41dc881"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60b553c5d946760d7983c009"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60eb841bc608d3c01a7c5582"] <- "breathing"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5c81b804b5bfcb00015aee82"] <- "breathing"

ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5dd1919051c6d2208e27fbc1"] <- "eye movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5dd72d2883e3096d755c0f14"] <- "eye movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5ee232f2b970662cfa352567"] <- "eye movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5ef39ea1e9a3511219951cc6"] <- "eye movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5f50191209e6d018aeb925f5"] <- "eye movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5f56506b2a8fb805ac024015"] <- "eye movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5f600669b846780f0fe45709"] <- "eye movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5f60ec315bd9c0011edd8b8f"] <- "eye movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5fa458b62713510a43fa06a6"] <- "eye movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5fa949031fdafd084c4d0812"] <- "eye movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5fad8f592f488e1271524b06"] <- "eye movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5fb53bab484613000a4fa361"] <- "eye movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5fc951a3fa107d0fcee036e9"] <- "eye movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="6076ddaec7fce6e8befa9ace"] <- "eye movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60e3fa63e9b13df2a6cef41c"] <- "eye movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60e3fa63e9b13df2a6cef41c"] <- "eye movements"

ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="575b2b408b705300078ae5e6"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5ae203d63cb5b0000185ccc7"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5aeb063b2f05b500013028a0"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5d35989e71b4880017d5cc81"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5d3e3541fd9694001a2d1789"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5ebaf261b69880094c6363ac"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5f18739d7dae940372d3e1d2"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5f244e0d0d7f44018faa3938"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5f32c91f649a5d04b32ff063"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5fe8c20bad8fba7bebe85d0e"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5ff458933803bbb00107e417"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="601f00e7c33dab4182151cc5"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="602bbb43cfca8a33d87378c7"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="603d0e0e5b0386b034e93bf5"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="607071077825ce1b96d83505"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60850f02822cdda28b5ecfcb"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60a37b4e514b606e0a822a0c"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60a90be1be2d42fba2368523"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60abef0280e8ef0e8a28497c"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60b4d4a21330fa73d200fa22"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60b60d67bbc65b38b155536e"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60b80ef4dcda79b9665c8c79"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60c67f7c98690351d580de6c"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60dafc1958e64bd5621cbef7"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60dcb2b6886dab98e5b8249a"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60e3029ab54bc58254e23a34"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60e49c6274c1be146fa85140"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60eb0d38fbe20e4ffe7505d6"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="qx6r0c7g"] <- "general movements"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="zzpkfztt"] <- "general movements"

ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5a9b20c535237b0001129820"] <- "skin color"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5eaaec78a563dc0724c63b98"] <- "skin color"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5f2d14d99d93bf265393b8ac"] <- "skin color"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60180a6c16d7314fec02e99f"] <- "skin color"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="6022dfbafb748f0ca0385db9"] <- "skin color"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="602d965dc8c74282fc222c7e"] <- "skin color"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60368b837f900be76ef6c9db"] <- "skin color"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="603f6e643234e512fc197ae1"] <- "skin color"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="604b169fe4b7991ec08da3a6"] <- "skin color"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60ab235a8a3d9b42f0817c27"] <- "skin color"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60ab235a8a3d9b42f0817c27"] <- "skin color"

ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="568d0641b5a2c2000cb657d0"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="588093c6704f1100014a3d01"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5bf1ecfcaf38d100016c1171"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5d07fc124e753800168ccafe"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5dbc435b78b8d81ec088fb40"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5e0d4d2d7605fe4d7fba6f5e"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5eb4909c2f46f82f9280a49b"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5f00fa2353b5c10c934298fa"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5f6ea775bc475b407020431f"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5fd9e1d7f35a0e508fd433d1"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="601129f77e0c21000b0c408a"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60338f35010951035cca4a91"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="603862f99e00971c55fe0874"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="603c124974df2e8f9f375fa8"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="603ffa13fa433c1989bff9e3"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60432be2ffdadc2d2b9a90e4"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60527c19066274811cb7ca77"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="6086a11397234e7f83e4e793"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="609478fa9e5b4d075246cfaf"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60a272d70db564387c61ede5"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60a2dffd4d05d87faf96873b"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60b9b93577a388a2ed3ac8ae"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60c07a36ba668880b8010450"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60dc9d77f88945d66d46966c"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60dc9d77f88945d66d46966c"] <- "person's state"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60a0dfc6f9936b0d30dfea15"] <- "person's state"

ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5d3587a13e11900001093ae8"] <- "pulse at neck"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5d88b1c27250e90001c40cfc"] <- "pulse at neck"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5e81c7b87412d48be61aaaab"] <- "pulse at neck"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5e92f26b444572122fdfe44d"] <- "pulse at neck"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5f9dbe7b71894b333e8722f7"] <- "pulse at neck"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5fc92eb719e43600082952d9"] <- "pulse at neck"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="605d90aeb58f606babd7a55b"] <- "pulse at neck"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60f9b14b819ae6fbff693bb2"] <- "pulse at neck"

ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5d5ee4b5b3e1bf0001a46a7d"] <- "physique"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5e28e735ea776009d4d15c34"] <- "physique"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5e3e11a36a0b8a000c609d5e"] <- "physique"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="604c9833900727300680726b"] <- "physique"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="6074b929f753216d88c77e88"] <- "physique"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="6074b929f753216d88c77e88"] <- "physique"

ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5d68c8aa40524c00189e8ac2"] <- "association"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5e15e7a61d4607bd245169d9"] <- "association"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5e4a1730c94447480594cea4"] <- "association"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5ea9916c3b32cf0dda50f621"] <- "association"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5ec4e3db7e31c83dfc851b83"] <- "association"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="603ecc7968ff0bf9b25e4bf1"] <- "association"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="6054effde12cd6b1052a4f1c"] <- "association"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60b405631fbdf499c48838ca"] <- "association"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60dc758b1fb5b747a605e4f4"] <- "association"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="5ee93ab8a93d8b15baf72fc5"] <- "association"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="60b769d44a48c12976a5f699"] <- "association"
ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant =="kiqaak2s"] <- "association"

# replace NA values in promnt with none
ActorHR_measures_onlyAccepted$prompt[is.na(ActorHR_measures_onlyAccepted$prompt)] <- "none"

# make promt factor and change order, so none is last:
ActorHR_measures_onlyAccepted$prompt <- factor(ActorHR_measures_onlyAccepted$prompt, levels = c("general movements", "breathing", "person's state", "eye movements", "association", "skin color",  "pulse at neck", "physique",  "none"))

# set the color scheme, we need 9 colors
colors_9 <- c("#FF0000", "#00A08A", "#F98400", "#5BBCD6", "#046C9A", "#F2AD00","#ABDDDE", "#D69C4E", "#000000")

# plot
## pAcc
# check if above chance:
x <- dplyr::select(ActorHR_measures_onlyAccepted, pAcc, prompt)

# plot
p <- ggplot(x, aes(x = prompt, y=pAcc, fill = prompt)) +
  geom_point(size= 2, shape = 21, colour = "black", alpha = 0.8, position=position_jitter(width = 0.4, height = 0)) +
  #geom_flat_violin(data= x, aes(x = prompt, y = pAcc, fill = prompt), position = position_nudge(x = 0, y = 0), alpha = 0.3, color = NA) +
  geom_abline(intercept = 0.4, slope = 0, color="#899DA4", linetype="dashed") +
  geom_abline(intercept = 0.5, slope = 0, color="#899DA4", linetype="dashed") +
  geom_abline(intercept = 0.6, slope = 0, color="#899DA4", linetype="dashed") +
  geom_abline(intercept = 0.7, slope = 0, color="#899DA4", linetype="dashed") +
  scale_y_continuous(limits= c(0.3,0.82), breaks = c(0.3, 0.4, 0.5, 0.6, 0.7, 1), labels = c("0.3","0.4", "0.5", "0.6","0.7","0.8")) +
  #scale_x_continuous(limits= c(0,2), breaks = c(1), labels = c("")) +
  scale_fill_manual(values = colors_9)

p <- p + theme_classic() +
  theme(text = element_text(size = 12),
        axis.text.x = element_blank()) +
  labs(x="", y = "Accuracy")

p

ggsave("ActorHR_prompt.png", p, width = 6, height = 3, dpi= 300)

# analysis
res.aov <- aov(pAcc ~ prompt, data = ActorHR_measures_onlyAccepted)
summary(res.aov)

check_model(res.aov)

oneway.test(pAcc ~ prompt, data = ActorHR_measures_onlyAccepted)

```

#### Actor-specific analysis:

___________
(1) Add a small adjustment factor, e.g. adj_f = 1/(length(nR_S1), to each 
% input vector:
% 
% adj_f = 1/length(nR_S1);
% nR_S1_adj = nR_S1 + adj_f;
% nR_S2_adj = nR_S2 + adj_f;
% 
% This is a generalization of the correction for similar estimation issues of
% type 1 d' as recommended in
% 
% Hautus, M. J. (1995). Corrections for extreme proportions and their biasing 
%     effects on estimated values of d'. Behavior Research Methods, Instruments, 
%     & Computers, 27, 46-51.
____________

```{r}
subs <- unique(data_wide_onlyAccepted$Participant.Public.ID)
subs_num <- length(subs)

# Actor A:
target_actor <- "A"
x <- subset(data_wide_onlyAccepted, left_actor==target_actor | right_actor==target_actor, -c(H,F,acc,acc_factor))

actor_data <- matrix(, nrow = subs_num, ncol = 6)
actor_data[,1] <- target_actor

# recode the resp and correct in terms of the actor rather than the side of HB
  x$Actor.Resp[x$left_actor == target_actor & x$resp== "left"] <- "targetActor"  # did the subject pick the target actor and the other actor
  x$Actor.Resp[x$left_actor == target_actor & x$resp== "right"] <- "otherActor"
  x$Actor.Resp[x$left_actor != target_actor & x$resp== "left"] <- "otherActor"
  x$Actor.Resp[x$left_actor != target_actor & x$resp== "right"] <- "targetActor"

  x$Actor.Cor[x$left_actor == target_actor & x$correct== "left"] <- "targetActor" # did the HB belong to the target actor and the other actor
  x$Actor.Cor[x$left_actor == target_actor & x$correct== "right"] <- "otherActor"
  x$Actor.Cor[x$left_actor != target_actor & x$correct== "left"] <- "otherActor"
  x$Actor.Cor[x$left_actor != target_actor & x$correct== "right"] <- "targetActor"

# Now hit rate is calculated in terms of target actor
# H <- response == target & HB == target
# F <- response == target & HB == other
for(r in 1:nrow(x)) {

  if(x$Actor.Resp[r]== "targetActor" & x$Actor.Cor[r]== "targetActor"){
    x$H[r] <- 1
    x$acc[r] <- 1
    x$F[r] <- 0}
  else if(x$Actor.Resp[r]== "targetActor" & x$Actor.Cor[r]== "otherActor"){
    x$H[r] <- 0
    x$acc[r] <- 0
    x$F[r] <- 1}
  else if(x$Actor.Resp[r]== "otherActor" & x$Actor.Cor[r]== "otherActor"){
    x$H[r] <- 0
    x$acc[r] <- 1
    x$F[r] <- 0}
  else if(x$Actor.Resp[r]== "otherActor" & x$Actor.Cor[r]== "targetActor"){
    x$H[r] <- 0
    x$acc[r] <- 0
    x$F[r] <- 0}
}

x$H <- as.numeric(x$H) # just in case, make sure variables are numeric
x$F <- as.numeric(x$F)

x$acc_factor[x$acc==0] <- 1
x$acc_factor[x$acc==1] <- 2
x$acc_factor <- factor(x$acc_factor, levels=c(1,2), labels=c("incorrect", "correct"))

x$Actor.Cor[x$Actor.Cor=="targetActor"] <- 1
x$Actor.Cor[x$Actor.Cor=="otherActor"] <- 2
x$Actor.Resp[x$Actor.Resp=="targetActor"] <- 1
x$Actor.Resp[x$Actor.Resp=="otherActor"] <- 2

x$Actor.Cor <- as.numeric(x$Actor.Cor)
x$Actor.Resp <- as.numeric(x$Actor.Resp)

for(subj in 1:subs_num) {

  work <- subset(x, Participant.Public.ID==subs[subj])

  df <- sdt_counts(work, stimulus = Actor.Cor, response = Actor.Resp, split_resp = FALSE)

  SDT_1 <- type_1_sdt(df, stimulus = Actor.Cor, response = Actor.Resp, counts = total, s = 1, add_constant = TRUE)

  actor_data[subj, 2] <- sum(work$acc)/24
  actor_data[subj, 3] <- mean(work$Confidence)
  actor_data[subj, 4] <- SDT_1$d_prime
  actor_data[subj, 5] <- SDT_1$c_raw
  actor_data[subj, 6] <- work$Participant.Public.ID[1]
}

# Actor B:
target_actor <- "B"
x <- subset(data_wide_onlyAccepted, left_actor==target_actor | right_actor==target_actor, -c(H,F,acc,acc_factor))

actor_data2 <- matrix(, nrow = subs_num, ncol = 6)
actor_data2[,1] <- target_actor

# recode the resp and correct in terms of the actor rather than the side of HB
x$Actor.Resp[x$left_actor == target_actor & x$resp== "left"] <- "targetActor"  # did the subject pick the target actor and the other actor
  x$Actor.Resp[x$left_actor == target_actor & x$resp== "right"] <- "otherActor"
  x$Actor.Resp[x$left_actor != target_actor & x$resp== "left"] <- "otherActor"
  x$Actor.Resp[x$left_actor != target_actor & x$resp== "right"] <- "targetActor"

  x$Actor.Cor[x$left_actor == target_actor & x$correct== "left"] <- "targetActor" # did the HB belong to the target actor and the other actor
  x$Actor.Cor[x$left_actor == target_actor & x$correct== "right"] <- "otherActor"
  x$Actor.Cor[x$left_actor != target_actor & x$correct== "left"] <- "otherActor"
  x$Actor.Cor[x$left_actor != target_actor & x$correct== "right"] <- "targetActor"

# Now hit rate is calculated in terms of target actor
# H <- response == target & HB == target
# F <- response == target & HB == other
for(r in 1:nrow(x)) {

  if(x$Actor.Resp[r]== "targetActor" & x$Actor.Cor[r]== "targetActor"){
    x$H[r] <- 1
    x$acc[r] <- 1
    x$F[r] <- 0}
  else if(x$Actor.Resp[r]== "targetActor" & x$Actor.Cor[r]== "otherActor"){
    x$H[r] <- 0
    x$acc[r] <- 0
    x$F[r] <- 1}
  else if(x$Actor.Resp[r]== "otherActor" & x$Actor.Cor[r]== "otherActor"){
    x$H[r] <- 0
    x$acc[r] <- 1
    x$F[r] <- 0}
  else if(x$Actor.Resp[r]== "otherActor" & x$Actor.Cor[r]== "targetActor"){
    x$H[r] <- 0
    x$acc[r] <- 0
    x$F[r] <- 0}
}

x$H <- as.numeric(x$H) # just in case, make sure variables are numeric
x$F <- as.numeric(x$F)

x$acc_factor[x$acc==0] <- 1
x$acc_factor[x$acc==1] <- 2
x$acc_factor <- factor(x$acc_factor, levels=c(1,2), labels=c("incorrect", "correct"))

x$Actor.Cor[x$Actor.Cor=="targetActor"] <- 1
x$Actor.Cor[x$Actor.Cor=="otherActor"] <- 2
x$Actor.Resp[x$Actor.Resp=="targetActor"] <- 1
x$Actor.Resp[x$Actor.Resp=="otherActor"] <- 2

x$Actor.Cor <- as.numeric(x$Actor.Cor)
x$Actor.Resp <- as.numeric(x$Actor.Resp)

for(subj in 1:subs_num) {

  work <- subset(x, Participant.Public.ID==subs[subj])

  df <- sdt_counts(work, stimulus = Actor.Cor, response = Actor.Resp, split_resp = FALSE)

  SDT_1 <- type_1_sdt(df, stimulus = Actor.Cor, response = Actor.Resp, counts = total, s = 1, add_constant = TRUE)

  actor_data2[subj, 2] <- sum(work$acc)/24
  actor_data2[subj, 3] <- mean(work$Confidence)
  actor_data2[subj, 4] <- SDT_1$d_prime
  actor_data2[subj, 5] <- SDT_1$c_raw
  actor_data2[subj, 6] <- work$Participant.Public.ID[1]
}

actor_data <- rbind(actor_data, actor_data2)

# Actor C:
target_actor <- "C"
x <- subset(data_wide_onlyAccepted, left_actor==target_actor | right_actor==target_actor, -c(H,F,acc,acc_factor))

actor_data2 <- matrix(, nrow = subs_num, ncol = 6)
actor_data2[,1] <- target_actor

# recode the resp and correct in terms of the actor rather than the side of HB
x$Actor.Resp[x$left_actor == target_actor & x$resp== "left"] <- "targetActor"  # did the subject pick the target actor and the other actor
  x$Actor.Resp[x$left_actor == target_actor & x$resp== "right"] <- "otherActor"
  x$Actor.Resp[x$left_actor != target_actor & x$resp== "left"] <- "otherActor"
  x$Actor.Resp[x$left_actor != target_actor & x$resp== "right"] <- "targetActor"

  x$Actor.Cor[x$left_actor == target_actor & x$correct== "left"] <- "targetActor" # did the HB belong to the target actor and the other actor
  x$Actor.Cor[x$left_actor == target_actor & x$correct== "right"] <- "otherActor"
  x$Actor.Cor[x$left_actor != target_actor & x$correct== "left"] <- "otherActor"
  x$Actor.Cor[x$left_actor != target_actor & x$correct== "right"] <- "targetActor"

# Now hit rate is calculated in terms of target actor
# H <- response == target & HB == target
# F <- response == target & HB == other
for(r in 1:nrow(x)) {

  if(x$Actor.Resp[r]== "targetActor" & x$Actor.Cor[r]== "targetActor"){
    x$H[r] <- 1
    x$acc[r] <- 1
    x$F[r] <- 0}
  else if(x$Actor.Resp[r]== "targetActor" & x$Actor.Cor[r]== "otherActor"){
    x$H[r] <- 0
    x$acc[r] <- 0
    x$F[r] <- 1}
  else if(x$Actor.Resp[r]== "otherActor" & x$Actor.Cor[r]== "otherActor"){
    x$H[r] <- 0
    x$acc[r] <- 1
    x$F[r] <- 0}
  else if(x$Actor.Resp[r]== "otherActor" & x$Actor.Cor[r]== "targetActor"){
    x$H[r] <- 0
    x$acc[r] <- 0
    x$F[r] <- 0}
}

x$H <- as.numeric(x$H) # just in case, make sure variables are numeric
x$F <- as.numeric(x$F)

x$acc_factor[x$acc==0] <- 1
x$acc_factor[x$acc==1] <- 2
x$acc_factor <- factor(x$acc_factor, levels=c(1,2), labels=c("incorrect", "correct"))

x$Actor.Cor[x$Actor.Cor=="targetActor"] <- 1
x$Actor.Cor[x$Actor.Cor=="otherActor"] <- 2
x$Actor.Resp[x$Actor.Resp=="targetActor"] <- 1
x$Actor.Resp[x$Actor.Resp=="otherActor"] <- 2

x$Actor.Cor <- as.numeric(x$Actor.Cor)
x$Actor.Resp <- as.numeric(x$Actor.Resp)

for(subj in 1:subs_num) {

  work <- subset(x, Participant.Public.ID==subs[subj])

  df <- sdt_counts(work, stimulus = Actor.Cor, response = Actor.Resp, split_resp = FALSE)

  SDT_1 <- type_1_sdt(df, stimulus = Actor.Cor, response = Actor.Resp, counts = total, s = 1, add_constant = TRUE)

  actor_data2[subj, 2] <- sum(work$acc)/24
  actor_data2[subj, 3] <- mean(work$Confidence)
  actor_data2[subj, 4] <- SDT_1$d_prime
  actor_data2[subj, 5] <- SDT_1$c_raw
  actor_data2[subj, 6] <- work$Participant.Public.ID[1]
}

actor_data <- rbind(actor_data, actor_data2)

# Actor D:
target_actor <- "D"
x <- subset(data_wide_onlyAccepted, left_actor==target_actor | right_actor==target_actor, -c(H,F,acc,acc_factor))

actor_data2 <- matrix(, nrow = subs_num, ncol = 6)
actor_data2[,1] <- target_actor

# recode the resp and correct in terms of the actor rather than the side of HB
x$Actor.Resp[x$left_actor == target_actor & x$resp== "left"] <- "targetActor"  # did the subject pick the target actor and the other actor
  x$Actor.Resp[x$left_actor == target_actor & x$resp== "right"] <- "otherActor"
  x$Actor.Resp[x$left_actor != target_actor & x$resp== "left"] <- "otherActor"
  x$Actor.Resp[x$left_actor != target_actor & x$resp== "right"] <- "targetActor"

  x$Actor.Cor[x$left_actor == target_actor & x$correct== "left"] <- "targetActor" # did the HB belong to the target actor and the other actor
  x$Actor.Cor[x$left_actor == target_actor & x$correct== "right"] <- "otherActor"
  x$Actor.Cor[x$left_actor != target_actor & x$correct== "left"] <- "otherActor"
  x$Actor.Cor[x$left_actor != target_actor & x$correct== "right"] <- "targetActor"

# Now hit rate is calculated in terms of target actor
# H <- response == target & HB == target
# F <- response == target & HB == other
for(r in 1:nrow(x)) {

  if(x$Actor.Resp[r]== "targetActor" & x$Actor.Cor[r]== "targetActor"){
    x$H[r] <- 1
    x$acc[r] <- 1
    x$F[r] <- 0}
  else if(x$Actor.Resp[r]== "targetActor" & x$Actor.Cor[r]== "otherActor"){
    x$H[r] <- 0
    x$acc[r] <- 0
    x$F[r] <- 1}
  else if(x$Actor.Resp[r]== "otherActor" & x$Actor.Cor[r]== "otherActor"){
    x$H[r] <- 0
    x$acc[r] <- 1
    x$F[r] <- 0}
  else if(x$Actor.Resp[r]== "otherActor" & x$Actor.Cor[r]== "targetActor"){
    x$H[r] <- 0
    x$acc[r] <- 0
    x$F[r] <- 0}
}

x$H <- as.numeric(x$H) # just in case, make sure variables are numeric
x$F <- as.numeric(x$F)

x$acc_factor[x$acc==0] <- 1
x$acc_factor[x$acc==1] <- 2
x$acc_factor <- factor(x$acc_factor, levels=c(1,2), labels=c("incorrect", "correct"))

x$Actor.Cor[x$Actor.Cor=="targetActor"] <- 1
x$Actor.Cor[x$Actor.Cor=="otherActor"] <- 2
x$Actor.Resp[x$Actor.Resp=="targetActor"] <- 1
x$Actor.Resp[x$Actor.Resp=="otherActor"] <- 2

x$Actor.Cor <- as.numeric(x$Actor.Cor)
x$Actor.Resp <- as.numeric(x$Actor.Resp)

for(subj in 1:subs_num) {

  work <- subset(x, Participant.Public.ID==subs[subj])

  df <- sdt_counts(work, stimulus = Actor.Cor, response = Actor.Resp, split_resp = FALSE)

  SDT_1 <- type_1_sdt(df, stimulus = Actor.Cor, response = Actor.Resp, counts = total, s = 1, add_constant = TRUE)

  actor_data2[subj, 2] <- sum(work$acc)/24
  actor_data2[subj, 3] <- mean(work$Confidence)
  actor_data2[subj, 4] <- SDT_1$d_prime
  actor_data2[subj, 5] <- SDT_1$c_raw
  actor_data2[subj, 6] <- work$Participant.Public.ID[1]
}

actor_data <- rbind(actor_data, actor_data2)

# Actor E:
target_actor <- "E"
x <- subset(data_wide_onlyAccepted, left_actor==target_actor | right_actor==target_actor, -c(H,F,acc,acc_factor))

actor_data2 <- matrix(, nrow = subs_num, ncol = 6)
actor_data2[,1] <- target_actor

# recode the resp and correct in terms of the actor rather than the side of HB
x$Actor.Resp[x$left_actor == target_actor & x$resp== "left"] <- "targetActor"  # did the subject pick the target actor and the other actor
  x$Actor.Resp[x$left_actor == target_actor & x$resp== "right"] <- "otherActor"
  x$Actor.Resp[x$left_actor != target_actor & x$resp== "left"] <- "otherActor"
  x$Actor.Resp[x$left_actor != target_actor & x$resp== "right"] <- "targetActor"

  x$Actor.Cor[x$left_actor == target_actor & x$correct== "left"] <- "targetActor" # did the HB belong to the target actor and the other actor
  x$Actor.Cor[x$left_actor == target_actor & x$correct== "right"] <- "otherActor"
  x$Actor.Cor[x$left_actor != target_actor & x$correct== "left"] <- "otherActor"
  x$Actor.Cor[x$left_actor != target_actor & x$correct== "right"] <- "targetActor"

# Now hit rate is calculated in terms of target actor
# H <- response == target & HB == target
# F <- response == target & HB == other
for(r in 1:nrow(x)) {

  if(x$Actor.Resp[r]== "targetActor" & x$Actor.Cor[r]== "targetActor"){
    x$H[r] <- 1
    x$acc[r] <- 1
    x$F[r] <- 0}
  else if(x$Actor.Resp[r]== "targetActor" & x$Actor.Cor[r]== "otherActor"){
    x$H[r] <- 0
    x$acc[r] <- 0
    x$F[r] <- 1}
  else if(x$Actor.Resp[r]== "otherActor" & x$Actor.Cor[r]== "otherActor"){
    x$H[r] <- 0
    x$acc[r] <- 1
    x$F[r] <- 0}
  else if(x$Actor.Resp[r]== "otherActor" & x$Actor.Cor[r]== "targetActor"){
    x$H[r] <- 0
    x$acc[r] <- 0
    x$F[r] <- 0}
}

x$H <- as.numeric(x$H) # just in case, make sure variables are numeric
x$F <- as.numeric(x$F)

x$acc_factor[x$acc==0] <- 1
x$acc_factor[x$acc==1] <- 2
x$acc_factor <- factor(x$acc_factor, levels=c(1,2), labels=c("incorrect", "correct"))

x$Actor.Cor[x$Actor.Cor=="targetActor"] <- 1
x$Actor.Cor[x$Actor.Cor=="otherActor"] <- 2
x$Actor.Resp[x$Actor.Resp=="targetActor"] <- 1
x$Actor.Resp[x$Actor.Resp=="otherActor"] <- 2

x$Actor.Cor <- as.numeric(x$Actor.Cor)
x$Actor.Resp <- as.numeric(x$Actor.Resp)

for(subj in 1:subs_num) {

  work <- subset(x, Participant.Public.ID==subs[subj])

  df <- sdt_counts(work, stimulus = Actor.Cor, response = Actor.Resp, split_resp = FALSE)

  SDT_1 <- type_1_sdt(df, stimulus = Actor.Cor, response = Actor.Resp, counts = total, s = 1, add_constant = TRUE)

  actor_data2[subj, 2] <- sum(work$acc)/24
  actor_data2[subj, 3] <- mean(work$Confidence)
  actor_data2[subj, 4] <- SDT_1$d_prime
  actor_data2[subj, 5] <- SDT_1$c_raw
  actor_data2[subj, 6] <- work$Participant.Public.ID[1]
}

actor_data <- rbind(actor_data, actor_data2)

# Actor G:
target_actor <- "G"
x <- subset(data_wide_onlyAccepted, left_actor==target_actor | right_actor==target_actor, -c(H,F,acc,acc_factor))

actor_data2 <- matrix(, nrow = subs_num, ncol = 6)
actor_data2[,1] <- target_actor

# recode the resp and correct in terms of the actor rather than the side of HB
x$Actor.Resp[x$left_actor == target_actor & x$resp== "left"] <- "targetActor"  # did the subject pick the target actor and the other actor
  x$Actor.Resp[x$left_actor == target_actor & x$resp== "right"] <- "otherActor"
  x$Actor.Resp[x$left_actor != target_actor & x$resp== "left"] <- "otherActor"
  x$Actor.Resp[x$left_actor != target_actor & x$resp== "right"] <- "targetActor"

  x$Actor.Cor[x$left_actor == target_actor & x$correct== "left"] <- "targetActor" # did the HB belong to the target actor and the other actor
  x$Actor.Cor[x$left_actor == target_actor & x$correct== "right"] <- "otherActor"
  x$Actor.Cor[x$left_actor != target_actor & x$correct== "left"] <- "otherActor"
  x$Actor.Cor[x$left_actor != target_actor & x$correct== "right"] <- "targetActor"

# Now hit rate is calculated in terms of target actor
# H <- response == target & HB == target
# F <- response == target & HB == other
for(r in 1:nrow(x)) {

  if(x$Actor.Resp[r]== "targetActor" & x$Actor.Cor[r]== "targetActor"){
    x$H[r] <- 1
    x$acc[r] <- 1
    x$F[r] <- 0}
  else if(x$Actor.Resp[r]== "targetActor" & x$Actor.Cor[r]== "otherActor"){
    x$H[r] <- 0
    x$acc[r] <- 0
    x$F[r] <- 1}
  else if(x$Actor.Resp[r]== "otherActor" & x$Actor.Cor[r]== "otherActor"){
    x$H[r] <- 0
    x$acc[r] <- 1
    x$F[r] <- 0}
  else if(x$Actor.Resp[r]== "otherActor" & x$Actor.Cor[r]== "targetActor"){
    x$H[r] <- 0
    x$acc[r] <- 0
    x$F[r] <- 0}
}

x$H <- as.numeric(x$H) # just in case, make sure variables are numeric
x$F <- as.numeric(x$F)

x$acc_factor[x$acc==0] <- 1
x$acc_factor[x$acc==1] <- 2
x$acc_factor <- factor(x$acc_factor, levels=c(1,2), labels=c("incorrect", "correct"))

x$Actor.Cor[x$Actor.Cor=="targetActor"] <- 1
x$Actor.Cor[x$Actor.Cor=="otherActor"] <- 2
x$Actor.Resp[x$Actor.Resp=="targetActor"] <- 1
x$Actor.Resp[x$Actor.Resp=="otherActor"] <- 2

x$Actor.Cor <- as.numeric(x$Actor.Cor)
x$Actor.Resp <- as.numeric(x$Actor.Resp)

for(subj in 1:subs_num) {

  work <- subset(x, Participant.Public.ID==subs[subj])

  df <- sdt_counts(work, stimulus = Actor.Cor, response = Actor.Resp, split_resp = FALSE)

  SDT_1 <- type_1_sdt(df, stimulus = Actor.Cor, response = Actor.Resp, counts = total, s = 1, add_constant = TRUE)

  actor_data2[subj, 2] <- sum(work$acc)/24
  actor_data2[subj, 3] <- mean(work$Confidence)
  actor_data2[subj, 4] <- SDT_1$d_prime
  actor_data2[subj, 5] <- SDT_1$c_raw
  actor_data2[subj, 6] <- work$Participant.Public.ID[1]
}

actor_data <- rbind(actor_data, actor_data2)

# Actor H:
target_actor <- "H"
x <- subset(data_wide_onlyAccepted, left_actor==target_actor | right_actor==target_actor, -c(H,F,acc,acc_factor))

actor_data2 <- matrix(, nrow = subs_num, ncol = 6)
actor_data2[,1] <- target_actor

# recode the resp and correct in terms of the actor rather than the side of HB
x$Actor.Resp[x$left_actor == target_actor & x$resp== "left"] <- "targetActor"  # did the subject pick the target actor and the other actor
  x$Actor.Resp[x$left_actor == target_actor & x$resp== "right"] <- "otherActor"
  x$Actor.Resp[x$left_actor != target_actor & x$resp== "left"] <- "otherActor"
  x$Actor.Resp[x$left_actor != target_actor & x$resp== "right"] <- "targetActor"

  x$Actor.Cor[x$left_actor == target_actor & x$correct== "left"] <- "targetActor" # did the HB belong to the target actor and the other actor
  x$Actor.Cor[x$left_actor == target_actor & x$correct== "right"] <- "otherActor"
  x$Actor.Cor[x$left_actor != target_actor & x$correct== "left"] <- "otherActor"
  x$Actor.Cor[x$left_actor != target_actor & x$correct== "right"] <- "targetActor"

# Now hit rate is calculated in terms of target actor
# H <- response == target & HB == target
# F <- response == target & HB == other
for(r in 1:nrow(x)) {

  if(x$Actor.Resp[r]== "targetActor" & x$Actor.Cor[r]== "targetActor"){
    x$H[r] <- 1
    x$acc[r] <- 1
    x$F[r] <- 0}
  else if(x$Actor.Resp[r]== "targetActor" & x$Actor.Cor[r]== "otherActor"){
    x$H[r] <- 0
    x$acc[r] <- 0
    x$F[r] <- 1}
  else if(x$Actor.Resp[r]== "otherActor" & x$Actor.Cor[r]== "otherActor"){
    x$H[r] <- 0
    x$acc[r] <- 1
    x$F[r] <- 0}
  else if(x$Actor.Resp[r]== "otherActor" & x$Actor.Cor[r]== "targetActor"){
    x$H[r] <- 0
    x$acc[r] <- 0
    x$F[r] <- 0}
}

x$H <- as.numeric(x$H) # just in case, make sure variables are numeric
x$F <- as.numeric(x$F)

x$acc_factor[x$acc==0] <- 1
x$acc_factor[x$acc==1] <- 2
x$acc_factor <- factor(x$acc_factor, levels=c(1,2), labels=c("incorrect", "correct"))

x$Actor.Cor[x$Actor.Cor=="targetActor"] <- 1
x$Actor.Cor[x$Actor.Cor=="otherActor"] <- 2
x$Actor.Resp[x$Actor.Resp=="targetActor"] <- 1
x$Actor.Resp[x$Actor.Resp=="otherActor"] <- 2

x$Actor.Cor <- as.numeric(x$Actor.Cor)
x$Actor.Resp <- as.numeric(x$Actor.Resp)

for(subj in 1:subs_num) {

  work <- subset(x, Participant.Public.ID==subs[subj])

  df <- sdt_counts(work, stimulus = Actor.Cor, response = Actor.Resp, split_resp = FALSE)

  SDT_1 <- type_1_sdt(df, stimulus = Actor.Cor, response = Actor.Resp, counts = total, s = 1, add_constant = TRUE)

  actor_data2[subj, 2] <- sum(work$acc)/24
  actor_data2[subj, 3] <- mean(work$Confidence)
  actor_data2[subj, 4] <- SDT_1$d_prime
  actor_data2[subj, 5] <- SDT_1$c_raw
  actor_data2[subj, 6] <- work$Participant.Public.ID[1]
}

actor_data <- rbind(actor_data, actor_data2)

```

##### Put into a dataframe:
```{r}
actor_data <- as.data.frame(actor_data)
names(actor_data) <- c("Target.Actor","pAcc", "Confidence", "DPrime", "Bias", "Participant")
actor_data$Target.Actor <- as.factor(actor_data$Target.Actor)
actor_data$pAcc <- as.numeric(actor_data$pAcc)
actor_data$Confidence <- as.numeric(actor_data$Confidence)
actor_data$DPrime <- as.numeric(actor_data$DPrime)
actor_data$Bias <- as.numeric(actor_data$Bias)
actor_data$Participant <- as.factor(actor_data$Participant)

```

##### Plot measures for each actor and run a one-way Anova:
```{r}
# Accuracy:
x <- dplyr::select(actor_data, pAcc, Target.Actor, Participant)

# one-way ANOVA to see if there is an effect of actor:
result <- ezANOVA(data = x, dv = . (pAcc), wid = . (Participant), 
                within = . (Target.Actor), detailed = TRUE, type = 3) 
result # no need for correction
result <- aovEffectSize(result, "pes")
aovDispTable(result)

if (result[["ANOVA"]][["p"]][2] < .001){pvalue = "p< .001"} else {pvalue = paste("p=", round(res$p.value, digits=3), sep = " ")}

df1 = result[["ANOVA"]][["DFn"]][2]
df2 = result[["ANOVA"]][["DFd"]][2]
Fvalue= round(result[["ANOVA"]][["F"]][2], digits = 2)
nvalue= round(result[["ANOVA"]][["pes"]][2], digits = 2)

stringF = paste("F(", df1, ",", df2, ")= ", Fvalue, ", ", pvalue, ", n= ", nvalue, sep="")

# pair-wise tests to follow-up the effect:
pairwise.t.test(x$pAcc, x$Target.Actor,
                paired= TRUE, p.adjust.method = "bonferroni")
# C vs A: p < .001
# C vs B: p < .001
# C vs D: p = .005
# C vs G: p = .04
# C vs H: p = .001
string_pairwise <- "B-corrected tests: actor C vs. others"

# plot:
sumld <- ddply(x, c("Target.Actor"), summarise, mean = mean(pAcc), lb = lb(pAcc), ub = ub(pAcc))

a <- ggplot(sumld, aes(x = Target.Actor, y = mean)) + 
  geom_bar(stat="identity", color="black", fill= "#C93312", position=position_dodge()) +
  geom_errorbar(aes(ymin=lb, ymax=ub), width=0, position=position_dodge(.9)) +
  geom_point(data= x, aes(x = Target.Actor, y=pAcc), alpha= 0.2, position=position_jitter(width = 0.1, height = 0)) +
  #geom_line(data= x, aes(x = Target.Actor, y=pAcc, group = Participant), color="#899DA4", alpha = 0.5) +
  geom_abline(intercept = 0.5, slope = 0, color="#899DA4", linetype="dashed") +
  scale_y_continuous(limits= c(0,1), breaks = c(0, 0.5, 1), labels = c("0", "0.5", "1")) +
  annotate("text", x = 2.6, y = 1, label = stringF, size = 3) +
  annotate("text", x = 2.8, y = 0.92, label = string_pairwise, size = 3)

a <- a + theme_classic() +
  theme(text = element_text(size = 12)) +
  labs(x="Actor", y = "Accuracy")

# DPrime
x <- dplyr::select(actor_data, DPrime, Target.Actor, Participant)

# one-way ANOVA to see if there is an effect of actor:
result <- ezANOVA(data = x, dv = . (DPrime), wid = . (Participant), 
                within = . (Target.Actor), detailed = TRUE, type = 3) 
#result
result <- aovEffectSize(result, "pes")
#aovDispTable(result)

if (result[["ANOVA"]][["p"]][2] < .001){pvalue = "p< .001"} else {pvalue = paste("p=", round(res$p.value, digits=3), sep = " ")}

df1 = result[["ANOVA"]][["DFn"]][2]
df2 = result[["ANOVA"]][["DFd"]][2]
Fvalue= round(result[["ANOVA"]][["F"]][2], digits = 2)
nvalue= round(result[["ANOVA"]][["pes"]][2], digits = 2)

stringF = paste("F(", df1, ",", df2, ")= ", Fvalue, ", ", pvalue, ", n= ", nvalue, sep="")

# pair-wise tests to follow-up the effect:
pairwise.t.test(x$DPrime, x$Target.Actor,
                paired= TRUE, p.adjust.method = "bonferroni")
# C vs A: p = .001
# C vs B: p = .002
# C vs D: p = .002
# C vs G: p = .04
# C vs H: p = .001
string_pairwise <- "B-corrected tests: actor C vs. others"

# plot:
sumld <- ddply(x, c("Target.Actor"), summarise, mean = mean(DPrime), lb = lb(DPrime), ub = ub(DPrime))

d <- ggplot(sumld, aes(x = Target.Actor, y = mean)) + 
  geom_bar(stat="identity", color="black", fill= "#C93312", position=position_dodge()) +
  geom_errorbar(aes(ymin=lb, ymax=ub), width=0, position=position_dodge(.9)) +
  geom_point(data= x, aes(x = Target.Actor, y=DPrime), alpha= 0.2, position=position_jitter(width = 0.1, height = 0)) +
  #geom_line(data= x, aes(x = Target.Actor, y=DPrime, group = Participant), color="#899DA4", alpha = 0.5) +
  geom_abline(intercept = 0, slope = 0, color="#899DA4", linetype="dashed") +
  #scale_y_continuous(limits= c(0,1), breaks = c(0, 0.5, 1), labels = c("0", "0.5", "1"))
  annotate("text", x = 2.6, y = 4, label = stringF, size = 3) +
  annotate("text", x = 2.8, y = 3.55, label = string_pairwise, size = 3)

d <- d + theme_classic() +
  theme(text = element_text(size = 12)) +
  labs(x="Actor", y = "D Prime")

# Bias
x <- dplyr::select(actor_data, Bias, Target.Actor, Participant)

# one-way ANOVA to see if there is an effect of actor:
result <- ezANOVA(data = x, dv = . (Bias), wid = . (Participant), 
                within = . (Target.Actor), detailed = TRUE, type = 3) 
#result
result <- aovEffectSize(result, "pes")
#aovDispTable(result)

if (result[["ANOVA"]][["p"]][2] < .001){pvalue = "p< .001"} else {pvalue = paste("p=", round(res$p.value, digits=3), sep = " ")}

df1 = result[["ANOVA"]][["DFn"]][2]
df2 = result[["ANOVA"]][["DFd"]][2]
Fvalue= round(result[["ANOVA"]][["F"]][2], digits = 2)
nvalue= round(result[["ANOVA"]][["pes"]][2], digits = 2)

stringF = paste("F(", df1, ",", df2, ")= ", Fvalue, ", ", pvalue, ", n= ", nvalue, sep="")

# pair-wise tests to follow-up the effect:
pairwise.t.test(x$Bias, x$Target.Actor,
                paired= TRUE, p.adjust.method = "bonferroni")
# D vs B: p = .001
# D vs G: p = .002

string_pairwise <- "B-corrected tests: actor D vs. others"

## t-tests against 0:
# A:
y <- filter(x, Target.Actor=="A")
y <- dplyr::select(y, -Target.Actor)
t.test(y$Bias, mu = 0) # p = .97

# B:
y <- filter(x, Target.Actor=="B")
y <- dplyr::select(y, -Target.Actor)
t.test(y$Bias, mu = 0) # p = .22

# C: 
y <- filter(x, Target.Actor=="C")
y <- dplyr::select(y, -Target.Actor)
t.test(y$Bias, mu = 0) # p = .32

# D:
y <- filter(x, Target.Actor=="D")
y <- dplyr::select(y, -Target.Actor)
t.test(y$Bias, mu = 0) # p < .001

# E:
y <- filter(x, Target.Actor=="E")
y <- dplyr::select(y, -Target.Actor)
t.test(y$Bias, mu = 0) # p = .23

# G:
y <- filter(x, Target.Actor=="G")
y <- dplyr::select(y, -Target.Actor)
t.test(y$Bias, mu = 0) # p = .001

# H:
y <- filter(x, Target.Actor=="H")
y <- dplyr::select(y, -Target.Actor)
t.test(y$Bias, mu = 0) # p = .06

# plot:
sumld <- ddply(x, c("Target.Actor"), summarise, mean = mean(Bias), lb = lb(Bias), ub = ub(Bias))

b <- ggplot(sumld, aes(x = Target.Actor, y = mean)) + 
  geom_bar(stat="identity", color="black", fill= "#C93312", position=position_dodge()) +
  geom_errorbar(aes(ymin=lb, ymax=ub), width=0, position=position_dodge(.9)) +
  geom_point(data= x, aes(x = Target.Actor, y=Bias), alpha= 0.2, position=position_jitter(width = 0.1, height = 0)) +
  #geom_line(data= x, aes(x = Target.Actor, y=Bias, group = Participant), color="#899DA4", alpha = 0.5) +
  geom_abline(intercept = 0, slope = 0, color="#899DA4", linetype="dashed") +
  #scale_y_continuous(limits= c(0,1), breaks = c(0, 0.5, 1), labels = c("0", "0.5", "1"))
  annotate("text", x = 2.6, y = 3, label = stringF, size = 3) +
  annotate("text", x = 2.8, y = 2.60, label = string_pairwise, size = 3) + 
  annotate("text", x = 4, y = 1.7, label = "**", fontface = 'bold', size = 5) +
  annotate("text", x = 6, y = 1.7, label = "*", fontface = 'bold', size = 5) +
  annotate("text", x = 1.7, y = 1.7, label = "t-tests against 0:", size = 3)

b <- b + theme_classic() +
  theme(text = element_text(size = 12)) +
  labs(x="Actor", y = "Bias")

# Confidence
x <- dplyr::select(actor_data, Confidence, Target.Actor, Participant)

# one-way ANOVA to see if there is an effect of actor:
result <- ezANOVA(data = x, dv = . (Confidence), wid = . (Participant), 
                within = . (Target.Actor), detailed = TRUE, type = 3) 
#result # no need for correction
result <- aovEffectSize(result, "pes")
#aovDispTable(result)

if (result[["ANOVA"]][["p"]][2] < .001){pvalue = "p< .001"} else {pvalue = paste("p=", round(res$p.value, digits=3), sep = " ")}

df1 = result[["ANOVA"]][["DFn"]][2]
df2 = result[["ANOVA"]][["DFd"]][2]
Fvalue= round(result[["ANOVA"]][["F"]][2], digits = 2)
nvalue= round(result[["ANOVA"]][["pes"]][2], digits = 2)

stringF = paste("F(", df1, ",", df2, ")= ", Fvalue, ", ", pvalue, ", n= ", nvalue, sep="")

# pair-wise tests to follow-up the effect:
pairwise.t.test(x$Confidence, x$Target.Actor,
                paired= TRUE, p.adjust.method = "bonferroni")
# B vs G: p = .04
# C vs H: p = .01

# plot:
sumld <- ddply(x, c("Target.Actor"), summarise, mean = mean(Confidence), lb = lb(Confidence), ub = ub(Confidence))

c <- ggplot(sumld, aes(x = Target.Actor, y = mean)) + 
  geom_bar(stat="identity", color="black", fill= "#C93312", position=position_dodge()) +
  geom_errorbar(aes(ymin=lb, ymax=ub), width=0, position=position_dodge(.9)) +
  geom_point(data= x, aes(x = Target.Actor, y=Confidence), alpha= 0.2, position=position_jitter(width = 0.1, height = 0)) +
  #geom_line(data= x, aes(x = Target.Actor, y=pAcc, group = Participant), color="#899DA4", alpha = 0.5) +
  geom_abline(intercept = 5, slope = 0, color="#899DA4", linetype="dashed") +
  scale_y_continuous(limits= c(0,10), breaks = c(0, 5, 10), labels = c("0", "5", "10")) +
  annotate("text", x = 2.6, y = 10, label = stringF, size = 3)

c <- c + theme_classic() +
  theme(text = element_text(size = 12)) +
  labs(x="Actor", y = "Confidence")

```

##### Put the plots together:
```{r fig.width = 7, fig.height= 5}
g <- ggarrange(a, d, b, c,
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2)
suppressWarnings(print(g))

ggsave("Actor-specific.png", g, width = 7, height = 5, dpi= 300)

```

## Analysis: IAS, SI and ActorHR

### Add the scores to the ActorHR main measures:
```{r}
subs <- unique(ActorHR_measures_onlyAccepted$Participant)
subs_num <- length(subs)

for(r in 1:subs_num){
  # IAS total
  ActorHR_measures_onlyAccepted$IAS_score[ActorHR_measures_onlyAccepted$Participant == subs[r]] <- Murphy_scores2$Response[Murphy_scores2$Participant.Public.ID == subs[r] & Murphy_scores2$Question.Key == "Total"]
  ActorHR_measures_onlyAccepted$Processing[ActorHR_measures_onlyAccepted$Participant == subs[r]] <- SI_scores$Response[SI_scores$Participant.Public.ID == subs[r] & SI_scores$Question.Key == "SP_total"]
  ActorHR_measures_onlyAccepted$Awareness[ActorHR_measures_onlyAccepted$Participant == subs[r]] <- SI_scores$Response[SI_scores$Participant.Public.ID == subs[r] & SI_scores$Question.Key == "SA_total"]
  ActorHR_measures_onlyAccepted$Skill[ActorHR_measures_onlyAccepted$Participant == subs[r]] <- SI_scores$Response[SI_scores$Participant.Public.ID == subs[r] & SI_scores$Question.Key == "SS_total"]
  ActorHR_measures_onlyAccepted$SI_score[ActorHR_measures_onlyAccepted$Participant == subs[r]] <- SI_scores$Response[SI_scores$Participant.Public.ID == subs[r] & SI_scores$Question.Key == "total"]
   ActorHR_measures_onlyAccepted$IAS_Heart_score[ActorHR_measures_onlyAccepted$Participant == subs[r]] <- Murphy_scores2$Response[Murphy_scores2$Participant.Public.ID == subs[r] & Murphy_scores2$Question.Key == "FastHeart"]
}

```

### Correlation between ActorHR task performance and questionnaire scores:
```{r}
# needs to be in long format -> each column a variable

acc <- dplyr::select(ActorHR_measures_onlyAccepted, pAcc, mConfidence, ConfDiff, IAS_score, Processing, Awareness, Skill)

res <- rcorr(as.matrix(acc)) # this gives both: r and p values
round(res$P, 3)

# produce and save the plot (saving [png and dev.off] is commented to not overwrite existing save)

pdf(file="ActorHR_conf_corrs.pdf", width = 4, height = 4)

corrplot(res$r, type="upper", 
         p.mat = res$P, sig.level = 0.05, 
         tl.col = "black", tl.srt = 45, tl.cex = .8, cl.align = "l")

dev.off() # only works when chunks are displayed in console and not inline!!

# explore the correlations
ggscatter(ActorHR_measures_onlyAccepted, x = "pAcc", y = "IAS_Heart_score", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "pAcc", ylab = "IAS_Heart")

ggsave("fig.pdf", width = 3, height = 3, dpi= 300)

```

## Analysis on reduced sample: IAcc, IAS, SI on ActorHR

### Get the scores form Actor-measures and put into Intero:
```{r}
subs <- unique(Schandry_onlyaccepted$Subj.ID)
subs_num <- length(subs)

for(s in 1:subs_num) {

Intero_perf$SI_score[Intero_perf$Subj== subs[s]] <- SI_scores$Response[SI_scores$Participant.Public.ID == subs[s] & SI_scores$Question.Key == "total"]
Intero_perf$Actor_Acc[Intero_perf$Subj==subs[s]] <- ActorHR_measures_onlyAccepted$pAcc[ActorHR_measures_onlyAccepted$Participant==subs[s]]
Intero_perf$Actor_ConfDiff[Intero_perf$Subj==subs[s]] <- ActorHR_measures_onlyAccepted$ConfDiff[ActorHR_measures_onlyAccepted$Participant==subs[s]]
}

```

### Big correlation matrix:
```{r}
res <- rcorr(as.matrix(Intero_perf[ ,2:9])) # this gives both: r and p values
round(res$P, 3)

# produce and save the plot (saving [png and dev.off] is commented to not overwrite existing save)

pdf(file="Big_corr.pdf", width = 4, height = 4)

corrplot(res$r, type="upper", 
         p.mat = res$P, sig.level = 0.05, 
         tl.col = "black", tl.srt = 45, tl.cex = .8, cl.align = "l")

dev.off() # only works when chunks are displayed in console and not inline!!

# explore the correlations
ggscatter(Intero_perf, x = "IAcc", y = "Actor_ConfDiff", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "I_Acc", ylab = "Actor_ConfDiff")

# ggsave("fig.png", width = 3, height = 3, units = "in" , dpi= 300)
ggscatter(Intero_perf, x = "Iawareness", y = "Actor_ConfDiff", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Iawareness", ylab = "Actor_ConfDiff")

```

### Get the average heartrate and estimated heartrate
```{r}
subs <- unique(Schandry_onlyaccepted$Subj.ID)
subs_num <- length(subs)
HR <- matrix(NA, nrow = subs_num, ncol = 3)

for(r in 1:subs_num){
  x <- subset(Schandry_onlyaccepted, Subj.ID == subs[r])
  HR[r, 1] <- x$Subj.ID[1]
  HR[r, 2] <- mean(x$smoothy)
  HR[r, 3] <- x$estimated_HR[1]
}

HR <- as.data.frame(HR)
names(HR) = c("Subj", "meanHR", "estimatedHR")
HR$Subj <- as.factor(HR$Subj)
HR$meanHR <- as.numeric(HR$meanHR)

```

### Add the control variables:
```{r}
exel_file <- paste(work_dir, "Participants2.xlsx", sep="/")
demo <- read.xlsx(xlsxFile= exel_file, sheet = "Schandry_included")

subs <- unique(Intero_perf$Subj)
subs_num <- length(subs)

for(s in 1:subs_num) {

Intero_perf$Gender[Intero_perf$Subj==subs[s]] <- demo$Gender[demo$Subj.ID==subs[s]]
Intero_perf$BMI[Intero_perf$Subj==subs[s]] <- demo$BMI[demo$Subj.ID==subs[s]]
Intero_perf$promt[Intero_perf$Subj==subs[s]] <- ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant==subs[s]]
Intero_perf$meanHR[Intero_perf$Subj==subs[s]] <- HR$meanHR[HR$Subj==subs[s]]
Intero_perf$estimatedHR[Intero_perf$Subj==subs[s]] <- demo$estimatedHR[demo$Subj.ID==subs[s]]

}

Intero_perf$estimated_true <- abs(Intero_perf$estimatedHR - Intero_perf$meanHR)

#ggscatter(Intero_perf, x = "IAcc", y = "estimated_true", 
#          add = "reg.line", conf.int = TRUE, 
#          cor.coef = TRUE, cor.method = "pearson",
#          xlab = "I_Acc", ylab = "estimated_true")

```

### Multiple regression ActorHR_Acc = IAS + I_Acc
```{r}
x <- Intero_perf

# mean-center all variables
x['IAcc'] <- as.data.frame(scale(x$IAcc, center = TRUE, scale = TRUE)) # mean center and z transform - need to do this way otherwise saves it in a weird format
x['Iawareness'] <- as.data.frame(scale(x$Iawareness, center = TRUE, scale = TRUE)) 
x['SubjvsObj'] <- as.data.frame(scale(x$SubjvsObj, center = TRUE, scale = TRUE)) 
x['IAS'] <- as.data.frame(scale(x$IAS, center = TRUE, scale = TRUE)) 
x['SI_score'] <- as.data.frame(scale(x$SI_score, center = TRUE, scale = TRUE)) 
x['Actor_Acc'] <- as.data.frame(scale(x$Actor_Acc, center = TRUE, scale = TRUE)) 
x['Actor_ConfDiff'] <- as.data.frame(scale(x$Actor_ConfDiff, center = TRUE, scale = TRUE)) 
x['BMI'] <- as.data.frame(scale(x$BMI, center = TRUE, scale = TRUE)) 
x['meanHR'] <- as.data.frame(scale(x$meanHR, center = TRUE, scale = TRUE)) 
x['estimated_true'] <- as.data.frame(scale(x$estimated_true, center = TRUE, scale = TRUE)) 
x$Gender <- factor(x$Gender, levels=c(0,1), labels=c("male", "female"))

# 
model <- lm(Actor_Acc ~ IAcc*IAS*SI_score + Gender + BMI + meanHR + estimated_true, data = x)
# model <- lm(Actor_Acc ~ SubjvsObj*SI_score + Gender + BMI + meanHR + estimated_true, data = x)

Anova(model)
summary(model)

check_model(model)

coffs <- confint(model_soc, level = 0.95)
coffs <- as.matrix(coffs)
mean_coffs <- model_soc$coefficients
mean_coffs <- as.vector(mean_coffs)

# plot the coefficients for each model:
coeffs <- data.frame("predictor"= c("I_Acc", "IAS", "SI_Processing", "SI_Awareness", "SI_Skill", "Gender", "BMI", "restingHR", "HR_knowledge"), "value"= mean_coffs[2:10], "lb"= coffs[2:10,1], "ub"= coffs[2:10,2])
coeffs$predictor <- factor(coeffs$predictor, levels = c("HR_knowledge", "restingHR", "BMI", "Gender", "SI_Skill", "SI_Awareness", "SI_Processing",  "IAS", "I_Acc"))

p <- ggplot(coeffs, aes(x=predictor, y=value, ymin=lb, ymax=ub)) +
        geom_pointrange(fatten = 3, size = 0.3) + 
        geom_hline(yintercept=0, lty=2) +
        coord_flip() +  # flip coordinates (puts labels on y axis)
        xlab("Predictors") + ylab("Beta (95% CI)")

p <- p + theme_bw() +
  theme(text = element_text(size = 10))

p
ggsave("reg.pdf", p, width = 2.5, height = 3.5, dpi= 300)

```

### Follow-up of the interaction
```{r}
int <- sim_slopes(model, pred = IAS, modx = IAcc, johnson_neyman = FALSE, jnplot = TRUE)
plot(int)

i <- interact_plot(model, pred = IAS, modx = IAcc, centered = "all", plot.points = TRUE, colors = c("#fde725", "#21918c", "#440154"),
              y.label = "accuracy on other-HR task", x.label = "total mean IAS score", legend.main = "level of IAcc")
# ggsave("simple_slopes.pdf", i, width = 2.5, height = 2.5, dpi= 300)

# ggplot(Intero_perf, aes(IAS, Actor_Acc, colour = IAcc, fill = IAcc)) + 
#    geom_point(shape=21, size = 2) +
#   scale_color_viridis(discrete=FALSE, option="magma") +
#   scale_fill_viridis(discrete=FALSE, option="magma")

```

### Median-split analysis according to IAcc
```{r}
ddply(x, .(group), summarise, mean = mean(Actor_Acc), median = median(Actor_Acc), min = min(Actor_Acc), max = max(Actor_Acc), sd = sd(Actor_Acc))

x <- Intero_perf

x$group[x$IAcc > 0.80] <- 1
x$group[x$IAcc < 0.80] <- 2

# remove NA values
x <- filter(x, group != "NA")

x$group <- factor(x$group, levels = c(1,2), labels = c("better","worse"))

var.test(Actor_Acc ~ group, data = x) # p=0.9 so no differene in variance
t.test(Actor_Acc ~ group, data= x, var.equal = TRUE)
cohens_d(x, Actor_Acc ~ group, var.equal= TRUE)

```

# What if you exclude the biasing actors: D G C
```{r}
# filter out the corresponding actors
data_wide_noActor <- filter(data_wide_onlyAccepted, left_actor != "D" & left_actor != "G" & left_actor != "C"
                            & right_actor != "D" & right_actor != "G" & right_actor != "C")

# get the mean measures
subs <- unique(data_wide_noActor$Participant.Public.ID)
subs_num <- length(subs)
ActorHR_measures <- matrix(NA, nrow = subs_num, ncol = 3)

for(r in 1:subs_num){
  x <- subset(data_wide_noActor, Participant.Public.ID==subs[r]) # we now have 24 trials per participant, instead of 84

  ActorHR_measures[r, 1] <- subs[r]
  ActorHR_measures[r, 2] <- round(sum(x$acc)/24, digits = 2) # accuray - proportion correct
  ActorHR_measures[r, 3] <- round(mean(x$Confidence.Rating), digits = 2)
}

# make into a dataframe:
ActorHR_measures <- as.data.frame(ActorHR_measures)
names(ActorHR_measures) <- c("Participant", "pAcc", "mConfidence")
ActorHR_measures$pAcc <- as.numeric(ActorHR_measures$pAcc)
ActorHR_measures$mConfidence <- as.numeric(ActorHR_measures$mConfidence)

# put eveyrthing into a single dataframe
subs <- unique(Schandry_onlyaccepted$Subj.ID)
subs_num <- length(subs)

for(s in 1:subs_num) {

Intero_perf$SI_score[Intero_perf$Subj== subs[s]] <- SI_scores$Response[SI_scores$Participant.Public.ID == subs[s] & SI_scores$Question.Key == "total"]
Intero_perf$Actor_Acc[Intero_perf$Subj==subs[s]] <- ActorHR_measures_onlyAccepted$pAcc[ActorHR_measures_onlyAccepted$Participant==subs[s]]
}

# Get the average HR and estimated HR
subs <- unique(Schandry_onlyaccepted$Subj.ID)
subs_num <- length(subs)
HR <- matrix(NA, nrow = subs_num, ncol = 3)

for(r in 1:subs_num){
  x <- subset(Schandry_onlyaccepted, Subj.ID == subs[r])
  HR[r, 1] <- x$Subj.ID[1]
  HR[r, 2] <- mean(x$smoothy)
  HR[r, 3] <- x$estimated_HR[1]
}

HR <- as.data.frame(HR)
names(HR) = c("Subj", "meanHR", "estimatedHR")
HR$Subj <- as.factor(HR$Subj)
HR$meanHR <- as.numeric(HR$meanHR)

# Add the control variables
exel_file <- paste(work_dir, "Participants2.xlsx", sep="/")
demo <- read.xlsx(xlsxFile= exel_file, sheet = "Schandry_included")

subs <- unique(Intero_perf$Subj)
subs_num <- length(subs)

for(s in 1:subs_num) {

Intero_perf$Gender[Intero_perf$Subj==subs[s]] <- demo$Gender[demo$Subj.ID==subs[s]]
Intero_perf$BMI[Intero_perf$Subj==subs[s]] <- demo$BMI[demo$Subj.ID==subs[s]]
Intero_perf$promt[Intero_perf$Subj==subs[s]] <- ActorHR_measures_onlyAccepted$prompt[ActorHR_measures_onlyAccepted$Participant==subs[s]]
Intero_perf$meanHR[Intero_perf$Subj==subs[s]] <- HR$meanHR[HR$Subj==subs[s]]
Intero_perf$estimatedHR[Intero_perf$Subj==subs[s]] <- demo$estimatedHR[demo$Subj.ID==subs[s]]

}

Intero_perf$estimated_true <- abs(Intero_perf$estimatedHR - Intero_perf$meanHR)

# Run the main regression:
x <- Intero_perf

# mean-center all variables
x['IAcc'] <- as.data.frame(scale(x$IAcc, center = TRUE, scale = TRUE)) # mean center and z transform - need to do this way otherwise saves it in a weird format
x['Iawareness'] <- as.data.frame(scale(x$Iawareness, center = TRUE, scale = TRUE)) 
x['SubjvsObj'] <- as.data.frame(scale(x$SubjvsObj, center = TRUE, scale = TRUE)) 
x['IAS'] <- as.data.frame(scale(x$IAS, center = TRUE, scale = TRUE)) 
x['SI_score'] <- as.data.frame(scale(x$SI_score, center = TRUE, scale = TRUE)) 
x['Actor_Acc'] <- as.data.frame(scale(x$Actor_Acc, center = TRUE, scale = TRUE)) 
x['BMI'] <- as.data.frame(scale(x$BMI, center = TRUE, scale = TRUE)) 
x['meanHR'] <- as.data.frame(scale(x$meanHR, center = TRUE, scale = TRUE)) 
x['estimated_true'] <- as.data.frame(scale(x$estimated_true, center = TRUE, scale = TRUE)) 
x$Gender <- factor(x$Gender, levels=c(0,1), labels=c("male", "female"))

# 
model <- lm(Actor_Acc ~ IAcc*IAS*SI_score + Gender + BMI + meanHR + estimated_true, data = x)
# model <- lm(Actor_Acc ~ SubjvsObj*SI_score + Gender + BMI + meanHR + estimated_true, data = x)

Anova(model)
summary(model)

```

### 2024-02-26 analysis/study1.qmd
separate 2 studies into 2 files

---
title: "Meta-analysis of the Interoceptive Accuracy Scale"
subtitle: "Study 1"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: true
    toc: true
    fig-dpi: 100
    fig-width: 11.33
execute: 
  cache: true
---

```{r}
#| message: false
#| warning: false

library(tidyverse)
library(easystats)
library(patchwork)
library(lavaan)
library(ggraph)
library(tidySEM)
library(EGAnet)
```

## Data Preparation

::: {.panel-tabset}

### Sample 1

Murphy (https://osf.io/3m5nh)

```{r}
df1a <- haven::read_sav("../data/Murphy2020/Study 1.sav") |>
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(Gender == 1, "Male", ifelse(Gender == 2, "Female", "Other"))))

df1b <- haven::read_sav("../data/Murphy2020/Study 6 IAS.sav") |>
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(Gender == 1, "Male", ifelse(Gender == 2, "Female", "Other"))))
```

### Sample 2

Gaggero (2021) (https://osf.io/5x9sg)

```{r}
load("../data/Gaggero2021/data.rda")
df2 <- data |> 
  mutate(Gender = as.character(gender)) |> 
  rename(
    Age=age, Heart = `IAS 1`, Hungry = `IAS 2`, Breathing = `IAS 3`, Thirsty = `IAS 4`,
    Urinate = `IAS 5`, Defecate = `IAS 6`, Taste = `IAS 7`, Vomit = `IAS 8`, Sneeze = `IAS 9`,
    Cough = `IAS 10`, Temp = `IAS 11`, Sex_arousal = `IAS 12`, Wind = `IAS 13`, Burp = `IAS 14`,
    Muscles = `IAS 15`, Bruise = `IAS 16`, Pain = `IAS 17`, Blood_Sugar = `IAS 18`,
    Affective_touch = `IAS 19`, Tickle = `IAS 20`, Itch = `IAS 21`)
rm(data)
```

### Sample 3

Campos (2022) - Study 1 (https://osf.io/j6ef3)

```{r}
df3 <- haven::read_sav("../data/Campos2022/Dataset_Test.sav") |>
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(Sex == 1, "Male", ifelse(Sex == 0, "Female", "Other")))) |>
  rename(
    Heart = IAS1, Hungry = IAS2, Breathing = IAS3, Thirsty = IAS4,
    Urinate = IAS5, Defecate = IAS6, Taste = IAS7, Vomit = IAS8, Sneeze = IAS9,
    Cough = IAS10, Temp = IAS11, Sex_arousal = IAS12, Wind = IAS13, Burp = IAS14,
    Muscles = IAS15, Bruise = IAS16, Pain = IAS17, Blood_Sugar = IAS18,
    Affective_touch = IAS19, Tickle = IAS20, Itch = IAS21
  )
```

### Sample 4

Todd (2022) - https://osf.io/ms354/

```{r}
df4 <- haven::read_sav("../data/Todd2022/CompleteData_new.sav") |>
  rename_with(\(x) str_remove(x, "IAS_"), .cols = starts_with("IAS_")) |>
  rename(
    Heart = IAS1, Hungry = IAS2, Breathing = IAS3, Thirsty = IAS4,
    Urinate = IAS5, Defecate = IAS6, Taste = IAS7, Vomit = IAS8, Sneeze = IAS9,
    Cough = IAS10, Temp = IAS11, Sex_arousal = IAS12, Wind = IAS13, Burp = IAS14,
    Muscles = IAS15, Bruise = IAS16, Pain = IAS17, Blood_Sugar = IAS18,
    Affective_touch = IAS19, Tickle = IAS20, Itch = IAS21
  )
```

### Sample 5

Arslanova (2022) - https://osf.io/mp3cy/

```{r}
df5 <- readxl::read_excel("../data/Arslanova2022/Murphy_Iacc_scale.xlsx")  |> 
  filter(str_detect(Question.Key, "IAC_")) |> 
  filter(str_detect(Question.Key, "-quantised")) |> 
  pivot_wider(names_from = Question.Key, values_from = Response) |>
  rename_with(\(x) str_remove(x, "IAC_"), .cols = starts_with("IAC_")) |> 
  rename_with(\(x) str_remove(x, "-quantised"), .cols = everything()) |> 
  rename(Sex_arousal = SexuallyAroused, Itch = Itchy, Sex_arousal = SexuallyAroused,
         Temp = HotCold, Tickle = Ticklish, Breathing= BreatheFast, 
         Affective_touch= PleasantAffectionate, Blood_Sugar= BloodSugar, 
         Muscles=TiredMuscles, Heart= FastHeart, Taste=Tastes) |> 
  select(-starts_with("Participant")) |> 
  mutate_all(as.numeric)
```

### Sample 6

Brand (2022) - https://osf.io/xwz6g/

```{r}
df6 <- haven::read_sav("../data/Brand2022/LatentVariableApproach.sav") |> 
  select(-SERIAL) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  )
```

### Sample 7

Brand (2023) - https://osf.io/3f2h6/

```{r}
df7a <- haven::read_sav("../data/Brand2023/Data_Giessen.sav") |> 
  select(-COUNTRY_OTHER) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(SEX == 1, "Male", ifelse(SEX == 2, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  )

df7b <- haven::read_sav("../data/Brand2023/Data_Mainz.sav") |> 
  select(-COUNTRY_OTHER, -EDUCATION_OTHER, -Sample) |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  )

df7c <- haven::read_sav("../data/Brand2023/Data_PotVie.sav") |> 
  select(-ID) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IA02_01, Hungry = IA02_02, Breathing = IA02_03, Thirsty = IA02_04,
    Urinate = IA02_05, Defecate = IA02_06, Taste = IA02_07, Vomit = IA02_08, Sneeze = IA02_09,
    Cough = IA02_10, Temp = IA02_11, Sex_arousal = IA02_12, Wind = IA02_13, Burp = IA02_14,
    Muscles = IA02_15, Bruise = IA02_16, Pain = IA02_17, Blood_Sugar = IA02_18,
    Affective_touch = IA02_19, Tickle = IA02_20, Itch = IA02_21
  )
```

### Sample 8

Lin (2023) - https://osf.io/3eztd
- Note: No tickle because same Chinese character

```{r}
df8a <- haven::read_sav("../data/Lin2023/Study 1 & 3.sav") |>
  select(-sex) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(sex_dummy == 1, "Male", ifelse(sex_dummy == 0, "Female", "Other")))) |>
  rename(
    Age = age,
    Heart = Heart, Hungry = HUNGR, Breathing = BREAT, Thirsty = Thirs,
    Urinate = URINA, Defecate = Defec, Taste = TASTE, Vomit = VOMIT, Sneeze = Sneez,
    Cough = COUGH, Temp = TEMPE, Sex_arousal = SEXAR, Wind = WIND, Burp = Burp,
    Muscles = MUSCL, Bruise = Bruis, Pain = PAIN, Blood_Sugar = BloSu,
    Affective_touch = Touch, Itch = ITCH
  )

df8b <- haven::read_sav("../data/Lin2023/Study 2.sav") |>
  mutate(Gender = as.character(ifelse(Sex == "男", "Male", ifelse(Sex == "女", "Female", "Other")))) |>
  rename(
    Heart = Heart, Hungry = HUNGR, Breathing = BREAT, Thirsty = Thirs,
    Urinate = URINA, Defecate = Defec, Taste = TASTE, Vomit = VOMIT, Sneeze = Sneez,
    Cough = COUGH, Temp = TEMPE, Sex_arousal = SEXAR, Wind = WIND, Burp = Burp,
    Muscles = MUSCL, Bruise = Bruis, Pain = PAIN, Blood_Sugar = BloSu,
    Affective_touch = Touch, Itch = ITCH)
```

### Sample 9

VonMohr (2023) - Study 3 (https://osf.io/7p9u5/)

```{r}
df9 <- read.csv("../data/VonMohr2023/DataSet_study3.csv")
df9 <- df9[complete.cases(select(df9, starts_with("IAS_"))), ]
df9 <- df9 |>
  mutate(Gender = as.character(ifelse(GENDER == "Man", "Male", ifelse(GENDER == "Woman", "Female", "Other")))) |>
  rename(
    Age=AGE, Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  )
```

<!-- ##### Sample 10 -->

<!-- Bowling (2024) - https://osf.io/tx8h9/ -->

<!-- ```{r} -->
<!-- df10 <- haven::read_sav("../data/Bowling2024/TouchAttitudesData.sav") |> -->
<!--   mutate_all(as.numeric) |> -->
<!--   mutate(Gender = as.character(ifelse(Gender_coded == 1, "Male", ifelse(Gender_coded == 2, "Female", "Other")))) |> -->
<!--   rename( -->
<!--     Heart = IAS1, Hungry = IAS2, Breathing = IAS3, Thirsty = IAS4, -->
<!--     Urinate = IAS5, Defecate = IAS6, Taste = IAS7, Vomit = IAS8, Sneeze = IAS9, -->
<!--     Cough = IAS10, Temp = IAS11, Sex_arousal = IAS12, Wind = IAS13, Burp = IAS14, -->
<!--     Muscles = IAS15, Bruise = IAS16, Pain = IAS17, Blood_Sugar = IAS18, -->
<!--     Affective_touch = IAS19, Tickle = IAS20, Itch = IAS21 -->
<!--   )  -->

<!-- ``` -->

### Sample 10

Makowski

- Note: First sample has some missing items
- Note: Analog scales

```{r}
df10a <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |>
  rename(
    Gender = Sex, Heart = Item_IAS_Interoception_1, Hungry = Item_IAS_Interoception_2,
    Breathing = Item_IAS_Interoception_3, Thirsty = Item_IAS_Interoception_4,
    Temp = Item_IAS_Interoception_5, Sex_arousal = Item_IAS_Interoception_6,
    Urinate = Item_IAS_Elimination_1, Defecate = Item_IAS_Elimination_2,
    Vomit = Item_IAS_Elimination_3, Wind = Item_IAS_Expulsion_1,
    Burp = Item_IAS_Expulsion_2, Sneeze = Item_IAS_Expulsion_3,
    Muscles = Item_IAS_Nociception_1, Bruise = Item_IAS_Nociception_2,
    Pain = Item_IAS_Nociception_3, Affective_touch = Item_IAS_Skin_1,
    Tickle = Item_IAS_Skin_2, Itch = Item_IAS_Skin_3
  ) |>
  filter(!is.na(Urinate))

df10b <- read.csv("https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv") |>
  rename(
    Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  )

# Save all
data <- list(df1a=df1a, df1b=df1b, df2=df2, df3=df3, df4=df4, df5=df5, df6=df6, df7a=df7a, df7b=df7b, df7c=df7c, df8a=df8a, df8b=df8b, df9=df9, df10a=df10a, df10b=df10b)
save(data, file = "../data/data.RData")
```

:::

## Participants

- **Sample 1a**: Data from [Murphy's (2020)](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) study 1, downloaded from OSF, included `r report::report_participants(df1a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 1b**: Data from [Murphy's (2020)](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) study 6, downloaded from OSF, included `r report::report_participants(df1b, age = "Age", sex = NA, gender = "Gender")`.
- **TODO: ADD INFO**

Total N = `r nrow(df1a) + nrow(df1b) + nrow(df2) + nrow(df3) + nrow(df4) + nrow(df5) + nrow(df6) + nrow(df7a) + nrow(df7b) + nrow(df7c) + nrow(df8a) + nrow(df8b) + nrow(df9) + nrow(df10a) + nrow(df10b)`.

## Descriptive

### Distribution

The items with the differing distribution pattern (with a lower mode around 2/5) are "Affective Touch", "Blood Sugar" and "Bruise".

```{r}
vars <- c(
  "Heart", "Hungry", "Breathing", "Thirsty", "Urinate", "Defecate", "Taste", "Vomit", "Sneeze", "Cough", "Temp",
  "Sex_arousal", "Wind", "Burp", "Muscles", "Bruise", "Pain", "Blood_Sugar", "Affective_touch", "Tickle", "Itch"
)

dens1a <- estimate_density(select(df1a, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 1a")
dens1b <- estimate_density(select(df1b, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 1b")
dens2 <- estimate_density(select(df2, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 2")
dens3 <- estimate_density(select(df3, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 3")
dens4 <- estimate_density(select(df4, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 4")
dens5 <- estimate_density(select(df5, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 5")
dens6 <- estimate_density(select(df6, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 6")
dens7a <- estimate_density(select(df7a, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 7a")
dens7b <- estimate_density(select(df7b, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 7b")
dens7c <- estimate_density(select(df7c, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 7c")
dens8a <- estimate_density(select(df8a, all_of(setdiff(vars, "Tickle"))), method = "kernSmooth") |>
  mutate(Sample = "Sample 8a")
dens8b <- estimate_density(select(df8b, all_of(setdiff(vars, "Tickle"))), method = "kernSmooth") |>
  mutate(Sample = "Sample 8b")
dens9 <- estimate_density(select(df9, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 9")
dens10a <- estimate_density(select(df10a, all_of(setdiff(vars, c("Taste", "Cough", "Blood_Sugar")))), method = "kernSmooth") |>
  mutate(Sample = "Sample 10a",
         x = datawizard::rescale(x, to=c(1, 5), range=c(0, 1)))
dens10b <- estimate_density(select(df10b, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 10b",
         x = datawizard::rescale(x, to=c(1, 5), range=c(0, 1)))

p1 <- rbind(dens1a, dens1b, dens2, dens3, dens4, dens5, dens6, dens7a, dens7b, dens7c, dens8a, dens8b, dens9, dens10a, dens10b) |>
  mutate(Sample = fct_relevel(Sample, "Sample 1a", "Sample 1b", "Sample 2", "Sample 3", "Sample 4", "Sample 5", "Sample 6", "Sample 7a", "Sample 7b", "Sample 7c", "Sample 8a", "Sample 8b", "Sample 9", "Sample 10a", "Sample 10b")) |>
  # mutate(Dashed = ifelse(Parameter %in% c("Affective_touch", "Blood_Sugar", "Bruise"), TRUE, FALSE)) |> 
  ggplot(aes(x = x, y = y, color = Parameter)) +
  geom_line() +
  scale_color_material_d() +
  scale_linetype_manual(values = c("solid", "dashed"), guide="none") +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        plot.title = element_text(face="bold")) +
  labs(title = "Distribution of responses for all items across various datasets", x = "Response", y = "Density", color = "Item") +
  facet_wrap(~Sample, scales = "free_y", nrow = 5)

ggsave("figures/Figure1.png", p1, width=10, height=10, dpi=200, bg="white")
p1
```

```{r}
data1a <- normalize(select(df1a, all_of(dens1a$Parameter)), range = c(1, 5))
data1b <- normalize(select(df1b, all_of(dens1b$Parameter)), range = c(1, 5))
data2 <- normalize(select(df2, all_of(dens2$Parameter)), range = c(1, 5))
data3 <- normalize(select(df3, all_of(dens3$Parameter)), range = c(1, 5))
data4 <- normalize(select(df4, all_of(dens4$Parameter)), range = c(1, 5))
data5 <- normalize(select(df5, all_of(dens5$Parameter)), range = c(1, 5))
data6 <- normalize(select(df6, all_of(dens6$Parameter)), range = c(1, 5))
data7a <- normalize(select(df7a, all_of(dens7a$Parameter)), range = c(1, 5))
data7b <- normalize(select(df7b, all_of(dens7b$Parameter)), range = c(1, 5))
data7c <- normalize(select(df7c, all_of(dens7c$Parameter)), range = c(1, 5))
data8a <- normalize(select(df8a, all_of(dens8a$Parameter)), range = c(1, 5))
data8b <- normalize(select(df8b, all_of(dens8b$Parameter)), range = c(1, 5))
data9 <- normalize(select(df9, all_of(dens9$Parameter)), range = c(1, 5))
data10a <- select(df10a, all_of(dens10a$Parameter))
data10b <- select(df10b, all_of(dens10b$Parameter))

data_all <- rbind(
  data1a, data1b, data2, data3, data4, data5, data6, data7a, data7b, data7c,
  mutate(data8a, Tickle = NA), mutate(data8b, Tickle = NA), data9,
  mutate(data10a, Taste = NA, Cough = NA, Blood_Sugar = NA), data10b
) 
```

### Correlations

An overall positive intercorrelation pattern, with no clear structure emerging.

::: {.panel-tabset}

#### All data

```{r}
make_correlation <- function(df) {
  correlation::correlation(df, redundant = TRUE) |>
    correlation::cor_sort() |>
    correlation::cor_lower() |>
    mutate(val = paste0(insight::format_value(r), format_p(p, stars_only = TRUE))) |>
    mutate(Parameter2 = fct_rev(Parameter2)) |>
    ggplot(aes(x = Parameter1, y = Parameter2)) +
    geom_tile(aes(fill = r), color = "white") +
    geom_text(aes(label = val), size = 3) +
    labs(title = "Correlation Matrix") +
    scale_fill_metro_c(limit = c(0, 0.75), guide = guide_colourbar(ticks = FALSE)) +
    theme_minimal() +
    theme(
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      axis.text.x = element_text(angle = 45, hjust = 1)
    )
}

make_correlation(data_all)
```

#### Sample 1a

```{r}
make_correlation(data1a)
```

#### Sample 1b

```{r}
make_correlation(data1b)
```

#### Sample 2

```{r}
make_correlation(data2)
```

#### Sample 3

```{r}
make_correlation(data3)
```

#### Sample 4

```{r}
make_correlation(data4)
```

#### Sample 5

```{r}
make_correlation(data5)
```

#### Sample 6

```{r}
make_correlation(data6)
```

#### Sample 7a

```{r}
make_correlation(data7a)
```

#### Sample 7b

```{r}
make_correlation(data7b)
```

#### Sample 7c

```{r}
make_correlation(data7c)
```

#### Sample 8a

```{r}
make_correlation(data8a)
```

#### Sample 8b

```{r}
make_correlation(data8b)
```

#### Sample 9

```{r}
make_correlation(data9)
```

#### Sample 10a

```{r}
make_correlation(data10a)
```

#### Sample 10b

```{r}
make_correlation(data10b)
```

:::

## Graph Analysis

Exploratory Graph Analysis (EGA) is a recently developed framework for psychometric assessment, that can be used to estimate the number of dimensions in questionnaire data using network estimation methods and community detection algorithms, and assess the stability of dimensions and items using bootstrapping.
See https://r-ega.net/articles/ega.html for details.

### Unique Variable Analysis (UVA)

Unique Variable Analysis (Christensen, Garrido, & Golino, 2023) uses the weighted topological overlap measure (Nowick et al., 2009) on an estimated network. Values greater than 0.25 are determined to have considerable local dependence (i.e., redundancy) that should be handled (variables with the highest maximum weighted topological overlap to all other variables (other than the one it is redundant with) should be removed).

::: {.panel-tabset}

#### All data

```{r}
uva <- EGAnet::UVA(data = data_all, cut.off = 0.3)
uva
uva$keep_remove
```

#### Sample 1a

```{r}
uva <- EGAnet::UVA(data = data1a, cut.off = 0.3)
uva
uva$keep_remove
```

#### Sample 1b

```{r}
uva <- EGAnet::UVA(data = data1b, cut.off = 0.3)
uva
uva$keep_remove
```

#### Sample 3

```{r}
uva <- EGAnet::UVA(data = data3, cut.off = 0.3)
uva
uva$keep_remove
```

#### Sample 4

```{r}
uva <- EGAnet::UVA(data = data4, cut.off = 0.3)
uva
uva$keep_remove
```

#### Sample 5

```{r}
uva <- EGAnet::UVA(data = data5, cut.off = 0.3)
uva
uva$keep_remove
```

#### Sample 6

```{r}
uva <- EGAnet::UVA(data = data6, cut.off = 0.3)
uva
uva$keep_remove
```

#### Sample 7a

```{r}
uva <- EGAnet::UVA(data = data7a, cut.off = 0.3)
uva
uva$keep_remove
```

#### Sample 7b

```{r}
uva <- EGAnet::UVA(data = data7b, cut.off = 0.3)
uva
uva$keep_remove
```

#### Sample 7c

```{r}
uva <- EGAnet::UVA(data = data7c, cut.off = 0.3)
uva
uva$keep_remove
```

#### Sample 8a

```{r}
uva <- EGAnet::UVA(data = data8a, cut.off = 0.3)
uva
uva$keep_remove
```

#### Sample 8b

```{r}
uva <- EGAnet::UVA(data = data8b, cut.off = 0.3)
uva
uva$keep_remove
```

#### Sample 9

```{r}
uva <- EGAnet::UVA(data = data9, cut.off = 0.3)
uva
uva$keep_remove
```

#### Sample 10a

```{r}
uva <- EGAnet::UVA(data = data10a, cut.off = 0.3)
uva
uva$keep_remove
```

#### Sample 10b

```{r}
uva <- EGAnet::UVA(data = data10b, cut.off = 0.3)
uva
uva$keep_remove
```

:::

### Networks

::: {.panel-tabset}

#### All data

```{r ega_all}
#| fig-height: 20
#| fig-width: 12

make_egas <- function(data) {
  egas <- list()
  for (model in c("glasso")) {  # , "TMFG"
    for (algo in c("walktrap", "louvain")) {
      for (type in c("ega", "ega.fit")) { # "" # "hierega"
        if (type == "ega.fit" & algo == "louvain") next # Too slow
        egas[[paste0(model, "_", algo, "_", type)]] <- EGAnet::bootEGA(
          data = data,
          seed = 123,
          model = model,
          algorithm = algo,
          EGA.type = type,
          type = "resampling",
          plot.itemStability = FALSE,
          verbose = FALSE
        )
      }
    }
  }

  p <- EGAnet::compare.EGA.plots(
    egas$glasso_walktrap_ega, 
    # egas$glasso_walktrap_ega.fit,
    egas$glasso_louvain_ega, 
    # egas$TMFG_louvain_ega,
    # egas$TMFG_walktrap_ega, 
    # egas$TMFG_walktrap_ega.fit,
    labels = c(
      "glasso_walktrap_ega", 
      # "glasso_walktrap_ega.fit",
      "glasso_louvain_ega" 
      # "TMFG_louvain_ega",
      # "TMFG_walktrap_ega", 
      # "TMFG_walktrap_ega.fit"
    ),
    rows = 3,
    plot.all = FALSE
  )$all
  list(egas = egas, p = p)
}

egas_all <- make_egas(data_all)
egas_all$p
```

#### Sample 1a

```{r ega1a}
#| fig-height: 20
#| fig-width: 12

egas1a <- make_egas(data1a)
egas1a$p
```

#### Sample 1b

```{r ega1b}
#| fig-height: 20
#| fig-width: 12

egas1b <- make_egas(data1b)
egas1b$p
```

#### Sample 2

```{r ega2}
#| fig-height: 20
#| fig-width: 12

egas2 <- make_egas(data2)
egas2$p
```

#### Sample 3

```{r ega3}
#| fig-height: 20
#| fig-width: 12

egas3 <- make_egas(data3)
egas3$p
```

#### Sample 4

```{r ega4}
#| fig-height: 20
#| fig-width: 12

egas4 <- make_egas(data4)
egas4$p
```

#### Sample 5

```{r ega5}
#| fig-height: 20
#| fig-width: 12

egas5 <- make_egas(data5)
egas5$p
```

#### Sample 6

```{r ega6}
#| fig-height: 20
#| fig-width: 12

egas6 <- make_egas(data6)
egas6$p
```

#### Sample 7a

```{r ega7&}
#| fig-height: 20
#| fig-width: 12

egas7a <- make_egas(data7a)
egas7a$p
```

#### Sample 7b

```{r ega7b}
#| fig-height: 20
#| fig-width: 12

egas7b <- make_egas(data7b)
egas7b$p
```

#### Sample 7c

```{r ega7c}
#| fig-height: 20
#| fig-width: 12

egas7c <- make_egas(data7c)
egas7c$p
```

#### Sample 8a

```{r ega8a}
#| fig-height: 20
#| fig-width: 12

egas8a <- make_egas(data8a)
egas8a$p
```

#### Sample 8b

```{r ega8b}
#| fig-height: 20
#| fig-width: 12

egas8b <- make_egas(data8b)
egas8b$p
```

#### Sample 9

```{r ega9}
#| fig-height: 20
#| fig-width: 12

egas9 <- make_egas(data9)
egas9$p
```

#### Sample 10a

```{r ega10a}
#| fig-height: 20
#| fig-width: 12

egas10a <- make_egas(data10a)
egas10a$p
```

#### Sample 10b

```{r ega10b}
#| fig-height: 20
#| fig-width: 12

egas10b <- make_egas(data10b)
egas10b$p
```

:::

### Structure Stability

::: {.panel-tabset}

#### All data

```{r}
#| fig-height: 20
#| fig-width: 12

patchwork::wrap_plots(lapply(egas_all$egas, plot), nrow = 3)
```

#### Sample 1a

```{r}
#| fig-height: 20
#| fig-width: 12

patchwork::wrap_plots(lapply(egas1a$egas, plot), nrow = 3)
```

#### Sample 1b

```{r}
#| fig-height: 20
#| fig-width: 12

patchwork::wrap_plots(lapply(egas1b$egas, plot), nrow = 3)
```

#### Sample 2

```{r}
#| fig-height: 20
#| fig-width: 12

patchwork::wrap_plots(lapply(egas2$egas, plot), nrow = 3)
```

#### Sample 3

```{r}
#| fig-height: 20
#| fig-width: 12

patchwork::wrap_plots(lapply(egas3$egas, plot), nrow = 3)
```

#### Sample 4

```{r}
#| fig-height: 20
#| fig-width: 12

patchwork::wrap_plots(lapply(egas4$egas, plot), nrow = 3)
```

#### Sample 5

```{r}
#| fig-height: 20
#| fig-width: 12

patchwork::wrap_plots(lapply(egas5$egas, plot), nrow = 3)
```

#### Sample 6

```{r}
#| fig-height: 20
#| fig-width: 12

patchwork::wrap_plots(lapply(egas6$egas, plot), nrow = 3)
```

#### Sample 7a

```{r}
#| fig-height: 20
#| fig-width: 12

patchwork::wrap_plots(lapply(egas7a$egas, plot), nrow = 3)
```

#### Sample 7b

```{r}
#| fig-height: 20
#| fig-width: 12

patchwork::wrap_plots(lapply(egas7b$egas, plot), nrow = 3)
```

#### Sample 7c

```{r}
#| fig-height: 20
#| fig-width: 12

patchwork::wrap_plots(lapply(egas7c$egas, plot), nrow = 3)
```

#### Sample 8a

```{r}
#| fig-height: 20
#| fig-width: 12

patchwork::wrap_plots(lapply(egas8a$egas, plot), nrow = 3)
```

#### Sample 8b

```{r}
#| fig-height: 20
#| fig-width: 12

patchwork::wrap_plots(lapply(egas8b$egas, plot), nrow = 3)
```

#### Sample 9

```{r}
#| fig-height: 20
#| fig-width: 12

patchwork::wrap_plots(lapply(egas9$egas, plot), nrow = 3)
```

#### Sample 10a

```{r}
#| fig-height: 20
#| fig-width: 12

patchwork::wrap_plots(lapply(egas10a$egas, plot), nrow = 3)
```

#### Sample 10b

```{r}
#| fig-height: 20
#| fig-width: 12

patchwork::wrap_plots(lapply(egas10b$egas, plot), nrow = 3)
```

:::

### Scores

```{r}
ega <- egas_all$egas$glasso_louvain_ega$EGA
plot(ega)

get_scores <- function(data, ega) {
  EGAnet::net.scores(data, ega)$scores$std.scores |>
    as.data.frame() |>
    setNames(c("EGA1", "EGA2", "EGA3", "EGA4"))
}

ega_scores_1a <- get_scores(data1a, ega)
ega_scores_1b <- get_scores(data1b, ega)
ega_scores_2 <- get_scores(data2, ega)
ega_scores_3 <- get_scores(data3, ega)
ega_scores_4 <- get_scores(data4, ega)
ega_scores_5 <- get_scores(data5, ega)
ega_scores_6 <- get_scores(data6, ega)
ega_scores_7a <- get_scores(data7a, ega)
ega_scores_7b <- get_scores(data7b, ega)
ega_scores_7c <- get_scores(data7c, ega)
ega_scores_8a <- get_scores(data8a, ega)
ega_scores_8b <- get_scores(data8b, ega)
ega_scores_9 <- get_scores(data9, ega)
ega_scores_10a <- get_scores(data10a, ega)
ega_scores_10b <- get_scores(data10b, ega)
```

## Factor Analysis

### How Many Factors

::: {.panel-tabset}

#### All data

```{r}
n <- parameters::n_factors(data_all, n_max = 12)

plot(n)
knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
```

#### Sample 1a

```{r}
n <- parameters::n_factors(data1a, n_max = 12)

plot(n)
knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
```

#### Sample 1b

```{r}
n <- parameters::n_factors(data1b, n_max = 12)

plot(n)
knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
```

#### Sample 2

```{r}
n <- parameters::n_factors(data2, n_max = 12)

plot(n)
knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
```

#### Sample 3

```{r}
n <- parameters::n_factors(data3, n_max = 12)

plot(n)
knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
```

#### Sample 4

```{r}
n <- parameters::n_factors(data4, n_max = 12)

plot(n)
knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
```

#### Sample 5

```{r}
n <- parameters::n_factors(data5, n_max = 12)

plot(n)
knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
```

#### Sample 6

```{r}
n <- parameters::n_factors(data6, n_max = 12)

plot(n)
knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
```

#### Sample 7a

```{r}
n <- parameters::n_factors(data7a, n_max = 12)

plot(n)
knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
```

#### Sample 7b

```{r}
n <- parameters::n_factors(data7b, n_max = 12)

plot(n)
knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
```

#### Sample 7c

```{r}
n <- parameters::n_factors(data7c, n_max = 12)

plot(n)
knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
```

#### Sample 8a

```{r}
n <- parameters::n_factors(data8a, n_max = 12)

plot(n)
knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
```

#### Sample 8b

```{r}
n <- parameters::n_factors(data8b, n_max = 12)

plot(n)
knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
```

#### Sample 9

```{r}
n <- parameters::n_factors(data9, n_max = 12)

plot(n)
knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
```

#### Sample 10a

```{r}
n <- parameters::n_factors(data10a, n_max = 12)

plot(n)
knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
```

#### Sample 10b

```{r}
n <- parameters::n_factors(data10b, n_max = 12)

plot(n)
knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
```

:::

### EFA

::: {.panel-tabset}

#### All data

```{r}
#| fig-height: 10

efa5 <- parameters::factor_analysis(data_all, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa5)

display(efa5)
```

#### Sample 1a

```{r}
#| fig-height: 10

efa4 <- parameters::factor_analysis(data1a, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

display(efa4)
```

#### Sample 1b

```{r}
#| fig-height: 10

efa4 <- parameters::factor_analysis(data1b, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

display(efa4)
```

:::

## CFA

We discarded the following items:
- Tickle: not present in the same dataset and consistently flagged as redundant.
<!-- - Blood_Sugar -->

Ambiguous:
- Temp
- Vomit
- Affective_touch
- Sex_arousal
- Taste

### Lower-Level Factors

::: {.panel-tabset}

#### All data

```{r}
m1 <- "
Interoception =~ Hungry + Thirsty + Urinate + Defecate + Itch + Bruise + Muscles + Pain + Breathing + Heart + Cough + Sneeze + Wind + Burp
"

m4 <- "
Sustenance =~ Hungry + Thirsty + Urinate + Defecate + Muscles + Pain
Skin =~ Itch + Bruise
HeartBreathing =~ Breathing + Heart
Expulsion =~ Cough + Sneeze + Wind + Burp
"

m5 <- "
Sustenance =~ Hungry + Thirsty + Pain
UrinateDefecate =~ Urinate + Defecate
Skin =~ Itch + Bruise + Muscles
HeartBreathing =~ Breathing + Heart
Expulsion =~ Cough + Sneeze + Wind + Burp
"

m6 <- "
HungryThirsty =~ Hungry + Thirsty
UrinateDefecate =~ Urinate + Defecate
ItchBruise =~ Itch + Bruise
MusclesPain =~ Muscles + Pain
HeartBreathing =~ Breathing + Heart
Expulsion =~ Cough + Sneeze + Wind + Burp
"

m7 <- "
HungryThirsty =~ Hungry + Thirsty
UrinateDefecate =~ Urinate + Defecate
ItchBruise =~ Itch + Bruise
MusclesPain =~ Muscles + Pain
HeartBreathing =~ Breathing + Heart
CoughSneeze =~ Cough + Sneeze
WindBurp =~ Wind + Burp
"

is_converged <- function(m) {
  ev <- eigen(lavaan::lavTech(m, "cov.lv")[[1]], symmetric=TRUE, only.values=TRUE)$values
  if (any(ev < -1 * .Machine$double.eps^(3/4))) {
    "Not converged"
  } else {
    ""
  }
}

compare_mods <- function(data) {
  m1 <- lavaan::cfa(m1, data = data)
  m4 <- lavaan::cfa(m4, data = data)
  m5 <- lavaan::cfa(m5, data = data)
  m6 <- lavaan::cfa(m6, data = data)
  m7 <- lavaan::cfa(m7, data = data)

  anova(m1, m4, m5, m6, m7) |>
    parameters::parameters() |>
    mutate(AIC = format(round(AIC, 0), nsmall = 0),
           BIC = format(round(BIC, 0), nsmall = 0),
           Chi2 = format(round(Chi2, 2), nsmall = 2),
           Converged = sapply(list(m1, m4, m5, m6, m7), is_converged))
}

display(compare_mods(data_all))

m7_all <- lavaan::cfa(m7, data = data_all)
parameters::parameters(m7_all, standardize=TRUE) |>
  display()
```

#### Sample 1a

```{r}
#| warning: false

display(compare_mods(data1a))
```

:::

Conclusion: The 7th factor solution was preferred in most datasets, including by indices that penalize increased number of parameters (such as BIC).

### Higher Order Factors

::: {.panel-tabset}

#### All data

```{r}
m7h1 <- paste0(m7, "
              Interoception =~ HungryThirsty + UrinateDefecate + ItchBruise + MusclesPain + HeartBreathing + CoughSneeze + WindBurp
              ")

m7h2 <- paste0(m7, "
              Expulsion =~ CoughSneeze + WindBurp
              Interoception =~ HungryThirsty + UrinateDefecate + HeartBreathing
              ")

m7h3 <- paste0(m7, "
              Valenced =~ MusclesPain + HeartBreathing + ItchBruise
              Expulsion =~ CoughSneeze + WindBurp
              Homeostasis =~ HungryThirsty + UrinateDefecate
              ")

compare_mods_h <- function(data) {
  m7 <- lavaan::cfa(m7, data = data)
  m7h2 <- lavaan::cfa(m7h2, data = data)
  m7h1 <- lavaan::cfa(m7h1, data = data)
  m7h3 <- lavaan::cfa(m7h3, data = data)

  anova(m7, m7h1, m7h2, m7h3) |>
    parameters::parameters() |>
    mutate(AIC = format(round(AIC, 0), nsmall = 0),
           BIC = format(round(BIC, 0), nsmall = 0),
           Chi2 = format(round(Chi2, 2), nsmall = 2),
           Converged = sapply(list(m7, m7h1, m7h2, m7h3), is_converged))
}

display(compare_mods_h(data_all))
```

No evidence for higher order factors.

#### Sample 1a

```{r}
display(compare_mods_h(data1a))
```

:::

### Model Performance

```{r}
#| warning: false

rbind(
  performance::performance(m7_all, metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "All"),
  performance::performance(update(m7_all, data = data1a), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 1a"),
  performance::performance(update(m7_all, data = data1b), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 1b"),
  performance::performance(update(m7_all, data = data2), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 2"),
  performance::performance(update(m7_all, data = data3), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 3"),
  performance::performance(update(m7_all, data = data4), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 4"),
  performance::performance(update(m7_all, data = data5), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 5"),
  performance::performance(update(m7_all, data = data6), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 6"),
  performance::performance(update(m7_all, data = data7a), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 7a"),
  performance::performance(update(m7_all, data = data7b), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 7b"),
  performance::performance(update(m7_all, data = data7c), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 7c"),
  performance::performance(update(m7_all, data = data8a), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 8a"),
  performance::performance(update(m7_all, data = data8b), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 8b"),
  performance::performance(update(m7_all, data = data9), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 9"),
  performance::performance(lavaan::cfa(str_remove(m7, fixed("\nCoughSneeze =~ Cough + Sneeze")), data = data10a), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 10a"),
  performance::performance(update(m7_all, data = data10b), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
    mutate(Sample = "Sample 10b")
) |>
  display()
```

## Scores

Note the usage of descriptive factor names relating directly to the items to avoid abstraction.

```{r}
#| warning: false

# Add empirical variables
add_empirical <- function(data, df) {
  x <- data |>
    mutate(
      HungryThirsty = (df$Hungry + df$Thirsty) / 2,
      UrinateDefecate = (df$Urinate + df$Defecate) / 2,
      MusclesPain = (df$Muscles + df$Pain) / 2,
      HeartBreathing = (df$Heart + df$Breathing) / 2,
      ItchBruise = (df$Itch + df$Bruise) / 2,
      WindBurp = (df$Wind + df$Burp) / 2)
  if("Cough" %in% names(df)) {
    mutate(x, CoughSneeze = (df$Cough + df$Sneeze) / 2)
  } else {
    mutate(x, CoughSneeze = df$Sneeze)
  }
}

# Deal with missing data
temp <- predict(m7_all, newdata=data7c)
scores7c <- data.frame(matrix(ncol = 7, nrow = nrow(ega_scores_7c))) 
scores7c[!is.na(ega_scores_7c$EGA1), ] <- temp
names(scores7c) <- names(as.data.frame(temp))

scores <- list(
  sample1a = cbind(ega_scores_1a, data_addprefix(as.data.frame(predict(m7_all, newdata=data1a)), "CFA_")) |>
    add_empirical(data1a) |> 
    mutate(Sample = "Sample 1a"),
  sample1b = cbind(ega_scores_1b, data_addprefix(as.data.frame(predict(m7_all, newdata=data1b)), "CFA_")) |>
    add_empirical(data1b) |> 
    mutate(Sample = "Sample 1b"),
  sample2 = cbind(ega_scores_2, data_addprefix(as.data.frame(predict(m7_all, newdata=data2)), "CFA_")) |>
    add_empirical(data2) |> 
    mutate(Sample = "Sample 2"),
  sample3 = cbind(ega_scores_3, data_addprefix(as.data.frame(predict(m7_all, newdata=data3)), "CFA_")) |>
    add_empirical(data3) |> 
    mutate(Sample = "Sample 3"),
  sample4 = cbind(ega_scores_4, data_addprefix(as.data.frame(predict(m7_all, newdata=data4)), "CFA_")) |>
    add_empirical(data4) |> 
    mutate(Sample = "Sample 4"),
  sample5 = cbind(ega_scores_5, data_addprefix(as.data.frame(predict(m7_all, newdata=data5)), "CFA_")) |>
    add_empirical(data5) |> 
    mutate(Sample = "Sample 5"),
  sample6 = cbind(ega_scores_6, data_addprefix(as.data.frame(predict(m7_all, newdata=data6)), "CFA_")) |>
    add_empirical(data6) |> 
    mutate(Sample = "Sample 6"),
  sample7a = cbind(ega_scores_7a, data_addprefix(as.data.frame(predict(m7_all, newdata=data7a)), "CFA_")) |>
    add_empirical(data7a) |> 
    mutate(Sample = "Sample 7a"),
  sample7b = cbind(ega_scores_7b, data_addprefix(as.data.frame(predict(m7_all, newdata=data7b)), "CFA_")) |>
    add_empirical(data7b) |> 
    mutate(Sample = "Sample 7b"),
  sample7c = cbind(ega_scores_7c, data_addprefix(scores7c, "CFA_")) |> 
    add_empirical(data7c) |> 
    mutate(Sample = "Sample 7c"),
  sample8a = cbind(ega_scores_8a, data_addprefix(as.data.frame(predict(m7_all, newdata=data8a)), "CFA_")) |>
    add_empirical(data8a) |> 
    mutate(Sample = "Sample 8a"),
  sample8b = cbind(ega_scores_8b, data_addprefix(as.data.frame(predict(m7_all, newdata=data8b)), "CFA_")) |>
    add_empirical(data8b) |> 
    mutate(Sample = "Sample 8b"),
  sample9 = cbind(ega_scores_9, data_addprefix(as.data.frame(predict(m7_all, newdata=data9)), "CFA_")) |>
    add_empirical(data9) |> 
    mutate(Sample = "Sample 9"),
  sample10a = cbind(ega_scores_10a, data_addprefix(as.data.frame(predict(lavaan::cfa(str_remove(m7, fixed("\nCoughSneeze =~ Cough + Sneeze")), data = data_all), newdata=data10a)), "CFA_")) |>
    add_empirical(data10a) |> 
    mutate(Sample = "Sample 10a", CFA_CoughSneeze = NA),
  sample10b = cbind(ega_scores_10b, data_addprefix(as.data.frame(predict(m7_all, newdata=data10b)), "CFA_")) |>
    add_empirical(data10b) |> 
    mutate(Sample = "Sample 10b")
)

save(scores, file = "../data/scores.RData")
```

### 2024-02-26 analysis/study2.qmd
separate 2 studies into 2 files

---
title: "Meta-analysis of the Interoceptive Accuracy Scale"
subtitle: "Study 2"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: true
    toc: true
    fig-dpi: 300
    fig-width: 11.33
execute: 
  cache: true
---

```{r}
#| message: false
#| warning: false

library(tidyverse)
library(easystats)
library(patchwork)
library(lavaan)
library(ggraph)
library(tidySEM)
library(EGAnet)
```

## Data Preparation

```{r}
#| warning: false

load("../data/data.RData")
load("../data/scores.RData")

df1a <- cbind(data$df1a, scores$sample1a)
df1b <- cbind(data$df1b, scores$sample1b)
df2 <- cbind(data$df2, scores$sample2)
df3 <- cbind(data$df3, scores$sample3)
df4 <- cbind(data$df4, scores$sample4)
df5 <- cbind(data$df5, scores$sample5)
df6 <- cbind(data$df6, scores$sample6)
df7a <- cbind(data$df7a, scores$sample7a)
df7b <- cbind(data$df7b, scores$sample7b)
df7c <- cbind(data$df7c, scores$sample7c)
df8a <- cbind(data$df8a, scores$sample8a)
df8b <- cbind(data$df8b, scores$sample8b)
df9 <- cbind(data$df9, scores$sample9)
df10a <- cbind(data$df10a, scores$sample10a)
df10b <- cbind(data$df10b, scores$sample10b)

vars_intero <- names(select(scores$sample1a, -Sample, -starts_with("CFA_"), -starts_with("EGA")))
# vars_cfa <- names(select(scores$sample1a, -Sample, -starts_with("EGA")))
# vars_cfa7 <- vars_cfa[vars_cfa != "CoughSneeze"]

# names(df1a)
# names(df1b)
# names(df2)  # BPQ, BVAQ, MAIA, ICQ, TAS
# names(df3)  # TAS, BPQ
# names(df4)  # BAQ, BPQ, MAIA, BPCS
# names(df5)  
# names(df6)  # IATS, SSS, GAD, PHQ2
# names(df7a)  # MAIA, STAI, FFMQ, NEOFFI, CES
# names(df7b)  # MAIA, STAIT, BPQ, PHQ15, PHQ9
# names(df7c)  # TAS, BPQ, TAS, ASI, BDI, IASV
# names(df8a)  # EDI, BPQ
# names(df8b)  # TAS,PHQ15, PHQ9
# names(df9)  # BFI, STQ, EQ, ECR, 
# names(df10a)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
# names(df10n)  # BDI, STAI, PHQ4
```

## Empirical Scores vs. Model-based

```{r}
#| warning: false

vars_scores <- names(select(scores$sample1a, -Sample))
df_scores <- rbind(
  select(df1a, all_of(vars_scores)),
  select(df1b, all_of(vars_scores)),
  select(df2, all_of(vars_scores)),
  select(df3, all_of(vars_scores)),
  select(df4, all_of(vars_scores)),
  select(df5, all_of(vars_scores)),
  select(df6, all_of(vars_scores)),
  select(df7a, all_of(vars_scores)),
  select(df7b, all_of(vars_scores)),
  select(df7c, all_of(vars_scores)),
  select(df8a, all_of(vars_scores)),
  select(df8b, all_of(vars_scores)),
  select(df9, all_of(vars_scores)),
  select(df10a, all_of(vars_scores)),
  select(df10b, all_of(vars_scores))
)

order <- c("WindBurp", "CoughSneeze", "MusclesPain", "ItchBruise", "HeartBreathing", "HungryThirsty", "UrinateDefecate")

correlation::correlation(select(df_scores, -all_of(vars_intero)),
                         select(df_scores, all_of(vars_intero))) |> 
  mutate(val = paste0(insight::format_value(r), format_p(p, stars_only = TRUE))) |>
    mutate(Parameter2 = fct_relevel(Parameter2, rev(order)),
           Parameter1 = fct_relevel(Parameter1, paste0("CFA_", order), "EGA3", "EGA2", "EGA4", "EGA1")) |>
    ggplot(aes(x = Parameter1, y = Parameter2)) +
    geom_tile(aes(fill = r), color = "white") +
    geom_text(aes(label = val), size = 3) +
    labs(title = "Correlation Matrix") +
    scale_fill_gradient(low="blue", high="red", limit = c(0.1, 1), guide = guide_colourbar(ticks = FALSE)) +
    theme_minimal() +
    theme(
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      axis.text.x = element_text(angle = 45, hjust = 1)
    )
```

Even EGA components capture pairs or groupings of pairs of items.

## Demographics

```{r}
make_diff <- function(df, vars, component=NA) {
  df <- select(df, all_of(c("Gender", "Sample", vars)))
  df <- df[complete.cases(df), ]
  dat <- data.frame()
  for (resp in vars) {
    f <- as.formula(paste0(resp, "~ Gender"))
    d <- filter(df, Gender %in% c("Male", "Female")) |>
      mutate(Gender = fct_relevel(Gender, "Male", "Female"))
    dat <- effectsize::cohens_d(f, data=d) |>
      as.data.frame() |>
      mutate(var_Correlate = "Gender", 
             var_Interoception = resp,
             p=t.test(f, data=d)$p.val) |>
      rbind(dat)
  }

  dat$r <- effectsize::d_to_r(dat$Cohens_d, n1=sum(df$Gender=="Male"), n2=sum(df$Gender=="Female"))
  dat$CI_low <- effectsize::d_to_r(dat$CI_low, n1=sum(df$Gender=="Male"), n2=sum(df$Gender=="Female"))
  dat$CI_high <- effectsize::d_to_r(dat$CI_high, n1=sum(df$Gender=="Male"), n2=sum(df$Gender=="Female"))
  dat$Sample <- unique(df$Sample)
  dat$Component <- component
  select(dat, -Cohens_d)
}

data <- rbind(
  make_diff(df1a, vars_intero, component="Demographic"),
  make_diff(df1b, vars_intero, component="Demographic"),
  make_diff(df2, vars_intero, component="Demographic"),
  make_diff(df3, vars_intero, component="Demographic"),
  # make_diff(df4, vars_intero, component="Demographic"),
  # make_diff(df5, vars_intero, component="Demographic"),
  make_diff(df6, vars_intero, component="Demographic"),
  make_diff(df7a, vars_intero, component="Demographic"),
  make_diff(df7b, vars_intero, component="Demographic"),
  make_diff(df7c, vars_intero, component="Demographic"),
  make_diff(df8a, vars_intero, component="Demographic"),
  make_diff(df8b, vars_intero, component="Demographic"),
  make_diff(df9, vars_intero, component="Demographic"),
  make_diff(df10a, vars_intero, component="Demographic"),
  make_diff(df10b, vars_intero, component="Demographic")
) |>
  mutate(var_Correlate = "Gender (Male vs. Female)")
```

```{r}
make_cor <- function(df, vars, with = "Age", component=NA) {
  df <- select(df, all_of(c(with, "Sample", vars)))
  df <- df[complete.cases(df), ]

  dat <- data.frame()
  for (v in vars) {
    dat <- correlation::cor_test(df, v, with) |>
      rename(var_Interoception = Parameter1, var_Correlate = Parameter2) |>
      as.data.frame() |>
      rbind(dat)
  }

  dat$Sample <- unique(df$Sample)
  dat$Component <- component
  select(dat, -df_error, -t, -Method, -n_Obs)
}

data <- rbind(
  data,
  make_cor(df1a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df1b, vars_intero, with = "Age", component="Demographic"),
  make_cor(df2, vars_intero, with = "Age", component="Demographic"),
  make_cor(df3, vars_intero, with = "Age", component="Demographic"),
  # make_cor(df4, vars_intero, with = "Age", component="Demographic"),
  # make_cor(df5, vars_intero, with = "Age", component="Demographic"),
  make_cor(df6, vars_intero, with = "Age", component="Demographic"),
  make_cor(df7a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df7b, vars_intero, with = "Age", component="Demographic"),
  make_cor(df7c, vars_intero, with = "Age", component="Demographic"),
  make_cor(df8a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df8b, vars_intero, with = "Age", component="Demographic"),
  make_cor(df9, vars_intero, with = "Age", component="Demographic"),
  make_cor(df10a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df10b, vars_intero, with = "Age", component="Demographic")
)
```

### Body

```{r}
# df3$BPQ_BodyAwareness <- -1*normalize(df3$BPQ_BodyAwareness)
# df3$BPQ_AutonomicReactivity <- -1*normalize(df3$BPQ_AutonomicReactivity)
names(df2)  # BPQ_R_Supra and _Sub?
names(df3)
names(df4)  # individual items 1-26
names(df7b)  # BPQ sum
names(df8a)  # individual items

data <- rbind(
  data,
  make_cor(df2, vars_intero, with = "BPQ_A", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df2, vars_intero, with = "BPQ_R", component="Body") |>
    mutate(var_Correlate = "Autonomic Reactivity (BPQ)"),
  make_cor(df3, vars_intero, with = "BPQ_BodyAwareness", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df3, vars_intero, with = "BPQ_AutonomicReactivity", component="Body") |>
    mutate(var_Correlate = "Autonomic Reactivity (BPQ)")
)
```

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_AttentionRegulation", component="MAIA")  |>  -->
<!--     mutate(var_Correlate = "Attention Regulation"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_BodyListening", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Body Listening"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_EmotionalAwareness", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Emotional Awareness"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_NotDistracting", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Not Distracting"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_Noticing", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Noticing"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_NotWorrying", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Not Worrying"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_SelfRegulation", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Self Regulation"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_Trusting", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Trusting") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # names(df3)[str_detect(names(df3), "TAS")] -->
<!-- # names(df4b)[str_starts(names(df4b), "TAS")] -->

<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df3, vars_cfa, with = "TAS_IdentifyingFeelings", component="Body") |>  -->
<!--     mutate(var_Correlate = "Difficulties Identifying Feelings"), -->
<!--   make_cor(df3, vars_cfa, with = "TAS_DescribingFeelings", component="Body") |>  -->
<!--     mutate(var_Correlate = "Difficulties Describing Feelings"), -->
<!--   make_cor(df3, vars_cfa, with = "TAS_ExternallyOrientedThinking", component="Body") |>  -->
<!--     mutate(var_Correlate = "External Thinking"), -->
<!--   make_cor(df4b, vars_cfa, with = "TAS_DIF", component="Body") |>  -->
<!--     mutate(var_Correlate = "Difficulties Identifying Feelings"), -->
<!--   make_cor(df4b, vars_cfa, with = "TAS_DDF", component="Body") |>  -->
<!--     mutate(var_Correlate = "Difficulties Describing Feelings") -->
<!-- ) -->
<!-- ``` -->

<!-- ### Mood -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df4b, vars_cfa, with = "PHQ15_sum", component="Mood") |>  -->
<!--     mutate(var_Correlate = "Somatic Concerns (PHQ-15)"), -->
<!--   make_cor(df4b, vars_cfa, with = "PHQ9_sum", component="Mood")|>  -->
<!--     mutate(var_Correlate = "Depression (PHQ-9)"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PHQ4_Depression", component="Mood") |>  -->
<!--     mutate(var_Correlate = "Depression (PHQ-4)"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PHQ4_Anxiety", component="Mood") |>  -->
<!--     mutate(var_Correlate = "Anxiety (PHQ-4)") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5b, vars_cfa, with = "BDI2_Total", component="Mood") |>  -->
<!--     mutate(var_Correlate = "Depression (BDI-II)") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5b, vars_cfa, with = "STAI5_General", component="Mood") |>  -->
<!--     mutate(var_Correlate = "Anxiety (STAI-5)") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "BPD", component="Mood") |>  -->
<!--     mutate(var_Correlate = "Boderline Personality") -->
<!-- ) -->
<!-- ``` -->

<!-- ### Psychopathology -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "PID5_Antagonism", component="Maladaptive") |>  -->
<!--     mutate(var_Correlate = "Antagonism"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PID5_Detachment", component="Maladaptive") |>  -->
<!--     mutate(var_Correlate = "Detachment"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PID5_Disinhibition", component="Maladaptive") |>  -->
<!--     mutate(var_Correlate = "Disinhibition"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PID5_NegativeAffect", component="Maladaptive") |>  -->
<!--     mutate(var_Correlate = "Negative Affect"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PID5_Psychoticism", component="Maladaptive") |>  -->
<!--     mutate(var_Correlate = "Psychoticism") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_ConstrictedAffect", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Constricted Affect"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_Eccentric", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Eccentric"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_MagicalThinking", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Magical Thinking"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_NoCloseFriends", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "No Close Friends"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_OddSpeech", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Odd Speech"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_Reference", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Reference"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_SocialAnxiety", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Social Anxiety"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_Suspiciousness", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Suspiciousness"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_UnusualPerceptions", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Unusual Perceptions") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- #  names(select(df5a, starts_with("ASQ"))) -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "ASQ_Imagination", component="Autistic") |>  -->
<!--     mutate(var_Correlate = "Imagination"), -->
<!--   make_cor(df5a, vars_cfa7, with = "ASQ_LackSocialSkills", component="Autistic") |> -->
<!--     mutate(var_Correlate = "Lack of Social Skills"), -->
<!--   make_cor(df5a, vars_cfa7, with = "ASQ_LowAttentionalSwitching", component="Autistic") |> -->
<!--     mutate(var_Correlate = "Low Attentional Switching"), -->
<!--   make_cor(df5a, vars_cfa7, with = "ASQ_Patterns", component="Autistic") |> -->
<!--     mutate(var_Correlate = "Patterns and Numbers"), -->
<!--   make_cor(df5a, vars_cfa7, with = "ASQ_Routine", component="Autistic") |> -->
<!--     mutate(var_Correlate = "Routines") -->
<!-- ) -->
<!-- ``` -->

<!-- ### Personality -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Agreeableness", component="Personality") |>  -->
<!--     mutate(var_Correlate = "Agreeableness"), -->
<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Conscientiousness", component="Personality") |> -->
<!--     mutate(var_Correlate = "Conscientiousness"), -->
<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Neuroticism", component="Personality") |> -->
<!--     mutate(var_Correlate = "Neuroticism"), -->
<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Openness", component="Personality") |> -->
<!--     mutate(var_Correlate = "Openness"), -->
<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Extraversion", component="Personality") |> -->
<!--     mutate(var_Correlate = "Extraversion"), -->
<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_HonestyHumility", component="Personality") |> -->
<!--     mutate(var_Correlate = "Honesty-Humility") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "PI_Alive", component="World Beliefs") |>  -->
<!--     mutate(var_Correlate = "Alive"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PI_Changing", component="World Beliefs") |> -->
<!--     mutate(var_Correlate = "Changing"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PI_Enticing", component="World Beliefs") |> -->
<!--     mutate(var_Correlate = "Enticing"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PI_Good", component="World Beliefs") |> -->
<!--     mutate(var_Correlate = "Good"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PI_Hierarchical", component="World Beliefs") |> -->
<!--     mutate(var_Correlate = "Hierarchical"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PI_Safe", component="World Beliefs") |> -->
<!--     mutate(var_Correlate = "Safe") -->
<!--   # TODO: Add understanble -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "GCBS_Extraterrestrial", component="Conspiracy Beliefs") |>  -->
<!--     mutate(var_Correlate = "Extraterrestrial"), -->
<!--   make_cor(df5a, vars_cfa7, with = "GCBS_GlobalConspiracies", component="Conspiracy Beliefs") |> -->
<!--     mutate(var_Correlate = "Global Conspiracies"), -->
<!--   make_cor(df5a, vars_cfa7, with = "GCBS_GovernmentMalfeasance", component="Conspiracy Beliefs") |> -->
<!--     mutate(var_Correlate = "Government Malfeasance"), -->
<!--   make_cor(df5a, vars_cfa7, with = "GCBS_InformationControl", component="Conspiracy Beliefs") |> -->
<!--     mutate(var_Correlate = "Information Control"), -->
<!--   make_cor(df5a, vars_cfa7, with = "GCBS_PersonalWellbeing", component="Conspiracy Beliefs") |> -->
<!--     mutate(var_Correlate = "Personal Wellbeing") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "LIE_Ability", component="Lying Profile") |>  -->
<!--     mutate(var_Correlate = "Ability"), -->
<!--   make_cor(df5a, vars_cfa7, with = "LIE_Frequency", component="Lying Profile") |> -->
<!--     mutate(var_Correlate = "Frequency"), -->
<!--   make_cor(df5a, vars_cfa7, with = "LIE_Contextuality", component="Lying Profile") |> -->
<!--     mutate(var_Correlate = "Contextuality"), -->
<!--   make_cor(df5a, vars_cfa7, with = "LIE_Negativity", component="Lying Profile") |> -->
<!--     mutate(var_Correlate = "Negativity") -->
<!-- ) -->
<!-- ``` -->

### Summary

```{r}
#| fig-height: 20
#| fig-width: 15

p <- data |>
  mutate(sig = ifelse(p < .01, "p < .01", ifelse(p < .001, "p < .001", "N.S.")),
         dir = sign(r),
         var_Interoception = str_replace(var_Interoception, "CoughSneeze", "Cough/Sneeze"),
         var_Interoception = str_replace(var_Interoception, "HeartBreathing", "Heart/Breathing"),
         var_Interoception = str_replace(var_Interoception, "HungryThirsty", "Hungry/Thirsty"),
         var_Interoception = str_replace(var_Interoception, "ItchBruise", "Itch/Bruise"),
         var_Interoception = str_replace(var_Interoception, "MusclesPain", "Muscles/Pain"),
         var_Interoception = str_replace(var_Interoception, "UrinateDefecate", "Urinate/Defecate"),
         var_Interoception = str_replace(var_Interoception, "WindBurp", "Wind/Burp"),
         var_Interoception = str_replace(var_Interoception, "Expulsion_Sudden", "Expulsion - Sudden"),
         var_Interoception = fct_relevel(var_Interoception, "Heart/Breathing", "Muscles/Pain", "Itch/Bruise", "Hungry/Thirsty", "Urinate/Defecate", "Wind/Burp", "Cough/Sneeze")) |>
         # Component = fct_relevel(
         #   Component, "Demographic", "MAIA", "Body", "Mood", "Maladaptive",
         #   "Schizotypic", "Autistic", "Personality", "Conspiracy Beliefs", "World Beliefs", "Lying Profile")) |>
  ggplot(aes(x = var_Correlate)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  # geom_bar(aes(fill=Sample, alpha=sig, y=r, group=Sample), stat="identity", position = position_dodge2(width = 0.8)) +
  geom_linerange(aes(color=dir, alpha=sig, ymin=0, ymax=r, group=Sample), position = position_dodge2(width = 0.7), linewidth=2.5) +
  geom_linerange(aes(ymin = CI_low, ymax = CI_high, color = dir, alpha=sig, group=Sample), position = position_dodge2(width = 0.7)) +
  scale_fill_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_color_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_alpha_discrete(range = c(0.2, 0.7), guide = "none") +
  scale_y_continuous(expand = c(0, 0), breaks = c(-0.3, 0, 0.3)) +
  facet_grid(Component ~ var_Interoception, scales = "free_y", switch = "y") +
  coord_flip(ylim = c(-0.45, 0.45)) +
  theme_modern(axis.title.space = 5) +
  theme(panel.grid.major.y = element_line(),
        axis.title.y = element_blank(),
        axis.line.x = element_blank(),
        axis.text.y = element_text(size = rel(0.5)),
        axis.text.x = element_text(size = rel(0.8)),
        plot.title = element_text(face = "bold", hjust = 0),
        strip.placement = "outside",
        strip.background.y = element_rect(fill = "#E0E0E0", color = "white"),
        strip.background.x = element_rect(fill = "#F8BBD0", color = "white"))
p
ggsave("figures/Figure2.png", p, width=21*0.6, height=29.7*0.45, dpi=200, bg="white")
```

## Discussion

Benefits of the IAS:
- Straightforward and sensation-centered items

Recommendations:
- Remove Itch (redundant + issue in Chinese)
- Use analog scales

Limitations:
- Not much clear theorethical or empirical structure (small grouping of items)
- Limited variability (clear mode at 4/5), very low prevalence of 5/5 responses.
- Ambiguous items which grouping depends on the context (and its awareness)
  - E.g., heart beating fast, vomit when nauseaous
- Few items for some modalities (e.g., 1 for heart)
- Positive phrasing: benefits but also might exacerbate positivity bias (and thus unidimensionality)

Need for context-specific items (cross-modal when possible, i.E., cardioception, respiroception, etc.).

New Scale: Multimodal Interoceptive Sensitivity Scale (MISS)

### 2024-02-26 analysis/study2.qmd
update study 2

@@
 # vars_cfa <- names(select(scores$sample1a, -Sample, -starts_with("EGA")))
-# vars_cfa7 <- vars_cfa[vars_cfa != "CoughSneeze"]
+# vars_intero <- vars_cfa[vars_cfa != "CoughSneeze"]
 
@@
 # names(df1b)
-# names(df2)  # BPQ, BVAQ, MAIA, ICQ, TAS
+# names(df2)  # BPQ, BVAQ, MAIA, ICQ (?), TAS
 # names(df3)  # TAS, BPQ
-# names(df4)  # BAQ, BPQ, MAIA, BPCS
+# names(df4)  # BAQ (?), BPQ, MAIA, BRS (resilience?), PBCS (private bodily consciousness?)
 # names(df5)  
@@
 # names(df7a)  # MAIA, STAI, FFMQ, NEOFFI, CES
-# names(df7b)  # MAIA, STAIT, BPQ, PHQ15, PHQ9
+# names(df7b)  # MAIA, STAI, BPQ, PHQ15, PHQ9
 # names(df7c)  # TAS, BPQ, TAS, ASI, BDI, IASV
 # names(df8a)  # EDI, BPQ
-# names(df8b)  # TAS,PHQ15, PHQ9
+# names(df8b)  # TAS, PHQ15, PHQ9
 # names(df9)  # BFI, STQ, EQ, ECR, 
 # names(df10a)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
-# names(df10n)  # BDI, STAI, PHQ4
+# names(df10b)  # BDI, STAI, PHQ4
 ```
@@
 
+### Gender
+
 ```{r}
@@
 
+### Age
+
 ```{r}
@@
 
-### Body
+## Body
+
+### MAIA
+
+```{r}
+names(df2)[str_detect(names(df2), "MAIA")]  
+names(df4)[str_detect(names(df4), "MAIA")]  # ?
+names(df7a)[str_detect(names(df7a), "MAIA")]  
+names(df7b)[str_detect(names(df7b), "maia")] 
+names(df10a)[str_detect(names(df10b), "MAIA")]
+
+data <- rbind(
+  data,
+  make_cor(df2, vars_intero, with = "MAIA_AttentionReg", component="MAIA")  |>
+    mutate(var_Correlate = "Attention Regulation"),
+  make_cor(df2, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
+    mutate(var_Correlate = "Listening"),
+  make_cor(df2, vars_intero, with = "MAIA_BodyTrusting", component="MAIA") |>
+    mutate(var_Correlate = "Trusting"),
+  make_cor(df2, vars_intero, with = "MAIA_EmoAwareness", component="MAIA") |>
+    mutate(var_Correlate = "Emotional Awareness"),
+  make_cor(df2, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
+    mutate(var_Correlate = "Not Distracting"),
+  make_cor(df2, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
+    mutate(var_Correlate = "Noticing"),
+  make_cor(df2, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
+    mutate(var_Correlate = "Not Worrying"),
+  make_cor(df2, vars_intero, with = "MAIA_SelfReg", component="MAIA") |>
+    mutate(var_Correlate = "Self Regulation"),
+  # df4
+  # df7a
+  make_cor(df7a, vars_intero, with = "mAIA_ATTENTION_REGULATION", component="MAIA") |>
+    mutate(var_Correlate = "Attention Regulation"),
+  make_cor(df7a, vars_intero, with = "MAIA_NOTICING", component="MAIA") |>
+    mutate(var_Correlate = "Noticing"),
+  make_cor(df7a, vars_intero, with = "MAIA_NON_DISTRACTING", component="MAIA") |>
+    mutate(var_Correlate = "Not Distracting"),
+  make_cor(df7a, vars_intero, with = "MAIA_NON_DISTRACTING", component="MAIA") |>
+    mutate(var_Correlate = "Not Distracting"),
+  make_cor(df7a, vars_intero, with = "MAIA_NOT_WORRYING", component="MAIA") |>
+    mutate(var_Correlate = "Not Worrying"),
+  make_cor(df7a, vars_intero, with = "MAIA_EMOTIONAL_AWARENESS", component="MAIA") |>
+    mutate(var_Correlate = "Emotional Awareness"),
+  make_cor(df7a, vars_intero, with = "MAIA_SELF_REGULATION", component="MAIA") |>
+    mutate(var_Correlate = "Self Regulation"),
+  make_cor(df7a, vars_intero, with = "MAIA_BODY_LISTENING", component="MAIA") |>
+    mutate(var_Correlate = "Listening"),
+  make_cor(df7a, vars_intero, with = "MAIA_TRUSTING", component="MAIA") |>
+    mutate(var_Correlate = "Trusting"),
+
+  # df7b
+  make_cor(df7b, vars_intero, with = "maiaNotice", component="MAIA") |>
+    mutate(var_Correlate = "Noticing"),
+  make_cor(df7b, vars_intero, with = "maiaNonDistracting", component="MAIA") |>
+    mutate(var_Correlate = "Not Distracting"),
+  make_cor(df7b, vars_intero, with = "maiaNotWorrying", component="MAIA") |>
+    mutate(var_Correlate = "Not Worrying"),
+  make_cor(df7b, vars_intero, with = "maiaAttentionRegulation", component="MAIA") |>
+    mutate(var_Correlate = "Attention Regulation"),
+  make_cor(df7b, vars_intero, with = "maiaEmotionalAwareness", component="MAIA") |>
+    mutate(var_Correlate = "Emotional Awareness"),
+  make_cor(df7b, vars_intero, with = "maiaSelfRegulation", component="MAIA") |>
+    mutate(var_Correlate = "Self Regulation"),
+  make_cor(df7b, vars_intero, with = "maiaBodyListening", component="MAIA") |>
+    mutate(var_Correlate = "Listening"),
+  make_cor(df7b, vars_intero, with = "maiaTrusting", component="MAIA") |>
+    mutate(var_Correlate = "Trusting"),
+
+  # df10a
+  make_cor(df10a, vars_intero, with = "MAIA_AttentionRegulation", component="MAIA")  |>
+    mutate(var_Correlate = "Attention Regulation"),
+  make_cor(df10a, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
+    mutate(var_Correlate = "Listening"),
+  make_cor(df10a, vars_intero, with = "MAIA_EmotionalAwareness", component="MAIA") |>
+    mutate(var_Correlate = "Emotional Awareness"),
+  make_cor(df10a, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
+    mutate(var_Correlate = "Not Distracting"),
+  make_cor(df10a, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
+    mutate(var_Correlate = "Noticing"),
+  make_cor(df10a, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
+    mutate(var_Correlate = "Not Worrying"),
+  make_cor(df10a, vars_intero, with = "MAIA_SelfRegulation", component="MAIA") |>
+    mutate(var_Correlate = "Self Regulation"),
+  make_cor(df10a, vars_intero, with = "MAIA_Trusting", component="MAIA") |>
+    mutate(var_Correlate = "Trusting")
+)
+```
+
+### BPQ
 
@@
 # df3$BPQ_AutonomicReactivity <- -1*normalize(df3$BPQ_AutonomicReactivity)
-names(df2)  # BPQ_R_Supra and _Sub?
-names(df3)
-names(df4)  # individual items 1-26
-names(df7b)  # BPQ sum
-names(df8a)  # individual items
+names(df2)[str_detect(names(df2), "BPQ")]  # BPQ_R_Supra and _Sub?
+names(df3)[str_detect(names(df3), "BPQ")]  
+names(df4)[str_detect(names(df4), "BPQ")]   # individual items 1-26
+names(df7b)[str_detect(names(df7b), "BPQ")]  # BPQ sum
+names(df8a)[str_detect(names(df8a), "BPQ")]  # individual items
 
@@
   data,
-  make_cor(df2, vars_intero, with = "BPQ_A", component="Body") |>
+  make_cor(df2, vars_intero, with = "BPQ_A", component="BPQ") |>
     mutate(var_Correlate = "Body Awareness (BPQ)"),
-  make_cor(df2, vars_intero, with = "BPQ_R", component="Body") |>
+  make_cor(df2, vars_intero, with = "BPQ_R", component="BPQ") |>
     mutate(var_Correlate = "Autonomic Reactivity (BPQ)"),
-  make_cor(df3, vars_intero, with = "BPQ_BodyAwareness", component="Body") |>
+  make_cor(df3, vars_intero, with = "BPQ_BodyAwareness", component="BPQ") |>
     mutate(var_Correlate = "Body Awareness (BPQ)"),
-  make_cor(df3, vars_intero, with = "BPQ_AutonomicReactivity", component="Body") |>
+  make_cor(df3, vars_intero, with = "BPQ_AutonomicReactivity", component="BPQ") |>
     mutate(var_Correlate = "Autonomic Reactivity (BPQ)")
@@
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5a, vars_cfa7, with = "MAIA_AttentionRegulation", component="MAIA")  |>  -->
-<!--     mutate(var_Correlate = "Attention Regulation"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "MAIA_BodyListening", component="MAIA") |>  -->
-<!--     mutate(var_Correlate = "Body Listening"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "MAIA_EmotionalAwareness", component="MAIA") |>  -->
-<!--     mutate(var_Correlate = "Emotional Awareness"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "MAIA_NotDistracting", component="MAIA") |>  -->
-<!--     mutate(var_Correlate = "Not Distracting"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "MAIA_Noticing", component="MAIA") |>  -->
-<!--     mutate(var_Correlate = "Noticing"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "MAIA_NotWorrying", component="MAIA") |>  -->
-<!--     mutate(var_Correlate = "Not Worrying"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "MAIA_SelfRegulation", component="MAIA") |>  -->
-<!--     mutate(var_Correlate = "Self Regulation"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "MAIA_Trusting", component="MAIA") |>  -->
-<!--     mutate(var_Correlate = "Trusting") -->
-<!-- ) -->
-<!-- ``` -->
+### Alexithymia
 
-<!-- ```{r} -->
-<!-- # names(df3)[str_detect(names(df3), "TAS")] -->
-<!-- # names(df4b)[str_starts(names(df4b), "TAS")] -->
+```{r}
+names(df2)[str_detect(names(df2), "TAS")]
+names(df3)[str_starts(names(df3), "TAS")]
+names(df7c)[str_starts(names(df7c), "TAS")]
+names(df8b)[str_starts(names(df8b), "TAS")]
 
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df3, vars_cfa, with = "TAS_IdentifyingFeelings", component="Body") |>  -->
-<!--     mutate(var_Correlate = "Difficulties Identifying Feelings"), -->
-<!--   make_cor(df3, vars_cfa, with = "TAS_DescribingFeelings", component="Body") |>  -->
-<!--     mutate(var_Correlate = "Difficulties Describing Feelings"), -->
-<!--   make_cor(df3, vars_cfa, with = "TAS_ExternallyOrientedThinking", component="Body") |>  -->
-<!--     mutate(var_Correlate = "External Thinking"), -->
-<!--   make_cor(df4b, vars_cfa, with = "TAS_DIF", component="Body") |>  -->
-<!--     mutate(var_Correlate = "Difficulties Identifying Feelings"), -->
-<!--   make_cor(df4b, vars_cfa, with = "TAS_DDF", component="Body") |>  -->
-<!--     mutate(var_Correlate = "Difficulties Describing Feelings") -->
-<!-- ) -->
-<!-- ``` -->
+data <- rbind(
+  data,
+  make_cor(df2, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
+    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
+  make_cor(df2, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
+    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
+  make_cor(df2, vars_intero, with = "TAS_EOT", component="Alexithymia") |>
+    mutate(var_Correlate = "External Thinking (TAS)"),
+  make_cor(df3, vars_intero, with = "TAS_DescribingFeelings", component="Alexithymia") |>
+    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
+  make_cor(df3, vars_intero, with = "TAS_IdentifyingFeelings", component="Alexithymia") |> 
+    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
+  make_cor(df3, vars_intero, with = "TAS_ExternallyOrientedThinking", component="Alexithymia") |>
+    mutate(var_Correlate = "External Thinking (TAS)"),
+  make_cor(df7c, vars_intero, with = "TAS_des", component="Alexithymia") |>
+    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
+  make_cor(df7c, vars_intero, with = "TAS_ident", component="Alexithymia") |>
+    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
+  make_cor(df7c, vars_intero, with = "TAS_ext", component="Alexithymia") |>
+    mutate(var_Correlate = "External Thinking (TAS)"),
+  make_cor(df8b, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
+    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
+  make_cor(df8b, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
+    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
+  # BVAQ
+  make_cor(df2, vars_intero, with = "BVAQ_Affective", component="Alexithymia") |>
+    mutate(var_Correlate = "Affective (BVAQ)"),
+  make_cor(df2, vars_intero, with = "BVAQ_Cognitive", component="Alexithymia") |>
+    mutate(var_Correlate = "Cognitive (BVAQ)")
+)
+```
 
-<!-- ### Mood -->
+## Mood
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df4b, vars_cfa, with = "PHQ15_sum", component="Mood") |>  -->
-<!--     mutate(var_Correlate = "Somatic Concerns (PHQ-15)"), -->
-<!--   make_cor(df4b, vars_cfa, with = "PHQ9_sum", component="Mood")|>  -->
-<!--     mutate(var_Correlate = "Depression (PHQ-9)"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PHQ4_Depression", component="Mood") |>  -->
-<!--     mutate(var_Correlate = "Depression (PHQ-4)"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PHQ4_Anxiety", component="Mood") |>  -->
-<!--     mutate(var_Correlate = "Anxiety (PHQ-4)") -->
-<!-- ) -->
-<!-- ``` -->
+### Depression
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5b, vars_cfa, with = "BDI2_Total", component="Mood") |>  -->
-<!--     mutate(var_Correlate = "Depression (BDI-II)") -->
-<!-- ) -->
-<!-- ``` -->
+```{r}
+names(df6)[str_detect(names(df6), "PHQ")] 
+names(df7b)[str_detect(names(df7b), "PHQ")]
+names(df7c)[str_detect(names(df7c), "BDI")]
+names(df8b)[str_detect(names(df8b), "PHQ")]
+names(df9)
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5b, vars_cfa, with = "STAI5_General", component="Mood") |>  -->
-<!--     mutate(var_Correlate = "Anxiety (STAI-5)") -->
-<!-- ) -->
-<!-- ``` -->
+data <- rbind(
+  data,
+  make_cor(df6, vars_intero, with = "PHQ2_sum", component="Mood") |>
+    mutate(var_Correlate = "Depression (PHQ-2)"),
+  make_cor(df7b, vars_intero, with = "PHQ15_Sum", component="Mood") |>
+    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
+  make_cor(df7b, vars_intero, with = "PHQ9_Sum", component="Mood")|>
+    mutate(var_Correlate = "Depression (PHQ-9)"),
+  make_cor(df7c, vars_intero, with = "BDI_sum", component="Mood") |>
+    mutate(var_Correlate = "Depression (BDI)"),
+  make_cor(df8b, vars_intero, with = "PHQ15_sum", component="Mood") |>
+    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
+  make_cor(df8b, vars_intero, with = "PHQ9_sum", component="Mood") |>
+    mutate(var_Correlate = "Depression (PHQ-9)"),
+  make_cor(df10a, vars_intero, with = "PHQ4_Depression", component="Mood") |>
+    mutate(var_Correlate = "Depression (PHQ-2)"),
+  make_cor(df10b, vars_intero, with = "BDI2_Total", component="Mood") |>
+    mutate(var_Correlate = "Depression (BDI)")
+)
+```
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5a, vars_cfa7, with = "BPD", component="Mood") |>  -->
-<!--     mutate(var_Correlate = "Boderline Personality") -->
-<!-- ) -->
-<!-- ``` -->
+### Anxiety
 
-<!-- ### Psychopathology -->
+```{r}
+names(df6)[str_detect(names(df6), "GAD")] 
+names(df7a)[str_detect(names(df7a), "STAI")] 
+names(df7b)[str_detect(names(df7b), "STAI")] 
+names(df7c)[str_detect(names(df7c), "STAI")]
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5a, vars_cfa7, with = "PID5_Antagonism", component="Maladaptive") |>  -->
-<!--     mutate(var_Correlate = "Antagonism"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PID5_Detachment", component="Maladaptive") |>  -->
-<!--     mutate(var_Correlate = "Detachment"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PID5_Disinhibition", component="Maladaptive") |>  -->
-<!--     mutate(var_Correlate = "Disinhibition"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PID5_NegativeAffect", component="Maladaptive") |>  -->
-<!--     mutate(var_Correlate = "Negative Affect"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PID5_Psychoticism", component="Maladaptive") |>  -->
-<!--     mutate(var_Correlate = "Psychoticism") -->
-<!-- ) -->
-<!-- ``` -->
+data <- rbind(
+  data,
+  make_cor(df6, vars_intero, with = "GAD2_sum", component="Mood") |>
+    mutate(var_Correlate = "Anxiety (GAD-2)"),
+  make_cor(df7a, vars_intero, with = "STAI_T_Sumscore", component="Mood") |>
+    mutate(var_Correlate = "Anxiety (STAI)"),
+  make_cor(df7b, vars_intero, with = "STAIT_Sum", component="Mood") |>
+    mutate(var_Correlate = "Anxiety (STAI)"),
+  make_cor(df7c, vars_intero, with = "STAIT_sum", component="Mood") |>
+    mutate(var_Correlate = "Anxiety (STAI)"),
+  make_cor(df10a, vars_intero, with = "PHQ4_Anxiety", component="Mood") |>
+    mutate(var_Correlate = "Anxiety (GAD-2)"),
+  make_cor(df10b, vars_intero, with = "PHQ4_Anxiety", component="Mood") |>
+    mutate(var_Correlate = "Anxiety (GAD-2)"),
+  make_cor(df10b, vars_intero, with = "STAI5_General", component="Mood") |>
+    mutate(var_Correlate = "Anxiety (STAI)")
+)
+```
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5a, vars_cfa7, with = "SPQ_ConstrictedAffect", component="Schizotypic") |>  -->
-<!--     mutate(var_Correlate = "Constricted Affect"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "SPQ_Eccentric", component="Schizotypic") |>  -->
-<!--     mutate(var_Correlate = "Eccentric"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "SPQ_MagicalThinking", component="Schizotypic") |>  -->
-<!--     mutate(var_Correlate = "Magical Thinking"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "SPQ_NoCloseFriends", component="Schizotypic") |>  -->
-<!--     mutate(var_Correlate = "No Close Friends"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "SPQ_OddSpeech", component="Schizotypic") |>  -->
-<!--     mutate(var_Correlate = "Odd Speech"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "SPQ_Reference", component="Schizotypic") |>  -->
-<!--     mutate(var_Correlate = "Reference"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "SPQ_SocialAnxiety", component="Schizotypic") |>  -->
-<!--     mutate(var_Correlate = "Social Anxiety"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "SPQ_Suspiciousness", component="Schizotypic") |>  -->
-<!--     mutate(var_Correlate = "Suspiciousness"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "SPQ_UnusualPerceptions", component="Schizotypic") |>  -->
-<!--     mutate(var_Correlate = "Unusual Perceptions") -->
-<!-- ) -->
-<!-- ``` -->
+## Psychopathology
 
-<!-- ```{r} -->
-<!-- #  names(select(df5a, starts_with("ASQ"))) -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5a, vars_cfa7, with = "ASQ_Imagination", component="Autistic") |>  -->
-<!--     mutate(var_Correlate = "Imagination"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "ASQ_LackSocialSkills", component="Autistic") |> -->
-<!--     mutate(var_Correlate = "Lack of Social Skills"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "ASQ_LowAttentionalSwitching", component="Autistic") |> -->
-<!--     mutate(var_Correlate = "Low Attentional Switching"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "ASQ_Patterns", component="Autistic") |> -->
-<!--     mutate(var_Correlate = "Patterns and Numbers"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "ASQ_Routine", component="Autistic") |> -->
-<!--     mutate(var_Correlate = "Routines") -->
-<!-- ) -->
-<!-- ``` -->
+```{r}
+data <- rbind(
+  data,
+  make_cor(df10a, vars_intero, with = "BPD", component="Mood") |>
+    mutate(var_Correlate = "Boderline Personality")
+)
+```
 
-<!-- ### Personality -->
+```{r}
+data <- rbind(
+  data,
+  make_cor(df10a, vars_intero, with = "PID5_Antagonism", component="Maladaptive") |>
+    mutate(var_Correlate = "Antagonism"),
+  make_cor(df10a, vars_intero, with = "PID5_Detachment", component="Maladaptive") |>
+    mutate(var_Correlate = "Detachment"),
+  make_cor(df10a, vars_intero, with = "PID5_Disinhibition", component="Maladaptive") |>
+    mutate(var_Correlate = "Disinhibition"),
+  make_cor(df10a, vars_intero, with = "PID5_NegativeAffect", component="Maladaptive") |>
+    mutate(var_Correlate = "Negative Affect"),
+  make_cor(df10a, vars_intero, with = "PID5_Psychoticism", component="Maladaptive") |>
+    mutate(var_Correlate = "Psychoticism")
+)
+```
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Agreeableness", component="Personality") |>  -->
-<!--     mutate(var_Correlate = "Agreeableness"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Conscientiousness", component="Personality") |> -->
-<!--     mutate(var_Correlate = "Conscientiousness"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Neuroticism", component="Personality") |> -->
-<!--     mutate(var_Correlate = "Neuroticism"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Openness", component="Personality") |> -->
-<!--     mutate(var_Correlate = "Openness"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Extraversion", component="Personality") |> -->
-<!--     mutate(var_Correlate = "Extraversion"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_HonestyHumility", component="Personality") |> -->
-<!--     mutate(var_Correlate = "Honesty-Humility") -->
-<!-- ) -->
-<!-- ``` -->
+```{r}
+data <- rbind(
+  data,
+  make_cor(df10a, vars_intero, with = "SPQ_ConstrictedAffect", component="Schizotypic") |>
+    mutate(var_Correlate = "Constricted Affect"),
+  make_cor(df10a, vars_intero, with = "SPQ_Eccentric", component="Schizotypic") |>
+    mutate(var_Correlate = "Eccentric"),
+  make_cor(df10a, vars_intero, with = "SPQ_MagicalThinking", component="Schizotypic") |>
+    mutate(var_Correlate = "Magical Thinking"),
+  make_cor(df10a, vars_intero, with = "SPQ_NoCloseFriends", component="Schizotypic") |>
+    mutate(var_Correlate = "No Close Friends"),
+  make_cor(df10a, vars_intero, with = "SPQ_OddSpeech", component="Schizotypic") |>
+    mutate(var_Correlate = "Odd Speech"),
+  make_cor(df10a, vars_intero, with = "SPQ_Reference", component="Schizotypic") |>
+    mutate(var_Correlate = "Reference"),
+  make_cor(df10a, vars_intero, with = "SPQ_SocialAnxiety", component="Schizotypic") |>
+    mutate(var_Correlate = "Social Anxiety"),
+  make_cor(df10a, vars_intero, with = "SPQ_Suspiciousness", component="Schizotypic") |>
+    mutate(var_Correlate = "Suspiciousness"),
+  make_cor(df10a, vars_intero, with = "SPQ_UnusualPerceptions", component="Schizotypic") |>
+    mutate(var_Correlate = "Unusual Perceptions")
+)
+```
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5a, vars_cfa7, with = "PI_Alive", component="World Beliefs") |>  -->
-<!--     mutate(var_Correlate = "Alive"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PI_Changing", component="World Beliefs") |> -->
-<!--     mutate(var_Correlate = "Changing"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PI_Enticing", component="World Beliefs") |> -->
-<!--     mutate(var_Correlate = "Enticing"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PI_Good", component="World Beliefs") |> -->
-<!--     mutate(var_Correlate = "Good"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PI_Hierarchical", component="World Beliefs") |> -->
-<!--     mutate(var_Correlate = "Hierarchical"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PI_Safe", component="World Beliefs") |> -->
-<!--     mutate(var_Correlate = "Safe") -->
-<!--   # TODO: Add understanble -->
-<!-- ) -->
-<!-- ``` -->
+```{r}
+#  names(select(df10a, starts_with("ASQ")))
+data <- rbind(
+  data,
+  make_cor(df10a, vars_intero, with = "ASQ_Imagination", component="Autistic") |>
+    mutate(var_Correlate = "Imagination"),
+  make_cor(df10a, vars_intero, with = "ASQ_LackSocialSkills", component="Autistic") |>
+    mutate(var_Correlate = "Lack of Social Skills"),
+  make_cor(df10a, vars_intero, with = "ASQ_LowAttentionalSwitching", component="Autistic") |>
+    mutate(var_Correlate = "Low Attentional Switching"),
+  make_cor(df10a, vars_intero, with = "ASQ_Patterns", component="Autistic") |>
+    mutate(var_Correlate = "Patterns and Numbers"),
+  make_cor(df10a, vars_intero, with = "ASQ_Routine", component="Autistic") |>
+    mutate(var_Correlate = "Routines")
+)
+```
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5a, vars_cfa7, with = "GCBS_Extraterrestrial", component="Conspiracy Beliefs") |>  -->
-<!--     mutate(var_Correlate = "Extraterrestrial"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "GCBS_GlobalConspiracies", component="Conspiracy Beliefs") |> -->
-<!--     mutate(var_Correlate = "Global Conspiracies"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "GCBS_GovernmentMalfeasance", component="Conspiracy Beliefs") |> -->
-<!--     mutate(var_Correlate = "Government Malfeasance"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "GCBS_InformationControl", component="Conspiracy Beliefs") |> -->
-<!--     mutate(var_Correlate = "Information Control"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "GCBS_PersonalWellbeing", component="Conspiracy Beliefs") |> -->
-<!--     mutate(var_Correlate = "Personal Wellbeing") -->
-<!-- ) -->
-<!-- ``` -->
+## Personality
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5a, vars_cfa7, with = "LIE_Ability", component="Lying Profile") |>  -->
-<!--     mutate(var_Correlate = "Ability"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "LIE_Frequency", component="Lying Profile") |> -->
-<!--     mutate(var_Correlate = "Frequency"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "LIE_Contextuality", component="Lying Profile") |> -->
-<!--     mutate(var_Correlate = "Contextuality"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "LIE_Negativity", component="Lying Profile") |> -->
-<!--     mutate(var_Correlate = "Negativity") -->
-<!-- ) -->
-<!-- ``` -->
+```{r}
+names(df7a)[str_detect(names(df7a), "NEO")]
+names(df9)[str_detect(names(df9), "BFI_")]
 
-### Summary
+data <- rbind(
+  data,
+  make_cor(df9, vars_intero, with = "BFI_AGREEABLENESS", component="Personality") |>
+    mutate(var_Correlate = "Agreeableness"),
+  make_cor(df9, vars_intero, with = "BFI_CONSCIENTIOUSNESS", component="Personality") |>
+    mutate(var_Correlate = "Conscientiousness"),
+  make_cor(df9, vars_intero, with = "BFI_NEUROTICISM", component="Personality") |>
+    mutate(var_Correlate = "Neuroticism"),
+  make_cor(df9, vars_intero, with = "BFI_OPENNESS", component="Personality") |>
+    mutate(var_Correlate = "Openness"),
+  make_cor(df9, vars_intero, with = "BFI_EXTROVERSION", component="Personality") |>
+    mutate(var_Correlate = "Extraversion"),
+  make_cor(df10a, vars_intero, with = "IPIP6_Agreeableness", component="Personality") |>
+    mutate(var_Correlate = "Agreeableness"),
+  make_cor(df10a, vars_intero, with = "IPIP6_Conscientiousness", component="Personality") |>
+    mutate(var_Correlate = "Conscientiousness"),
+  make_cor(df10a, vars_intero, with = "IPIP6_Neuroticism", component="Personality") |>
+    mutate(var_Correlate = "Neuroticism"),
+  make_cor(df10a, vars_intero, with = "IPIP6_Openness", component="Personality") |>
+    mutate(var_Correlate = "Openness"),
+  make_cor(df10a, vars_intero, with = "IPIP6_Extraversion", component="Personality") |>
+    mutate(var_Correlate = "Extraversion"),
+  make_cor(df10a, vars_intero, with = "IPIP6_HonestyHumility", component="Personality") |>
+    mutate(var_Correlate = "Honesty-Humility")
+)
+```
+
+## Others
+
+```{r}
+data <- rbind(
+  data,
+  make_cor(df10a, vars_intero, with = "PI_Alive", component="World Beliefs") |>
+    mutate(var_Correlate = "Alive"),
+  make_cor(df10a, vars_intero, with = "PI_Changing", component="World Beliefs") |>
+    mutate(var_Correlate = "Changing"),
+  make_cor(df10a, vars_intero, with = "PI_Enticing", component="World Beliefs") |>
+    mutate(var_Correlate = "Enticing"),
+  make_cor(df10a, vars_intero, with = "PI_Good", component="World Beliefs") |>
+    mutate(var_Correlate = "Good"),
+  make_cor(df10a, vars_intero, with = "PI_Hierarchical", component="World Beliefs") |>
+    mutate(var_Correlate = "Hierarchical"),
+  make_cor(df10a, vars_intero, with = "PI_Safe", component="World Beliefs") |>
+    mutate(var_Correlate = "Safe"),
+  make_cor(df10a, vars_intero, with = "PI_Understandable", component="World Beliefs") |>
+    mutate(var_Correlate = "Understandable")
+)
+```
+
+```{r}
+data <- rbind(
+  data,
+  make_cor(df10a, vars_intero, with = "GCBS_Extraterrestrial", component="Conspiracy Beliefs") |>
+    mutate(var_Correlate = "Extraterrestrial"),
+  make_cor(df10a, vars_intero, with = "GCBS_GlobalConspiracies", component="Conspiracy Beliefs") |>
+    mutate(var_Correlate = "Global Conspiracies"),
+  make_cor(df10a, vars_intero, with = "GCBS_GovernmentMalfeasance", component="Conspiracy Beliefs") |>
+    mutate(var_Correlate = "Government Malfeasance"),
+  make_cor(df10a, vars_intero, with = "GCBS_InformationControl", component="Conspiracy Beliefs") |>
+    mutate(var_Correlate = "Information Control"),
+  make_cor(df10a, vars_intero, with = "GCBS_PersonalWellbeing", component="Conspiracy Beliefs") |>
+    mutate(var_Correlate = "Personal Wellbeing")
+)
+```
+
+```{r}
+data <- rbind(
+  data,
+  make_cor(df10a, vars_intero, with = "LIE_Ability", component="Lying Profile") |>
+    mutate(var_Correlate = "Ability"),
+  make_cor(df10a, vars_intero, with = "LIE_Frequency", component="Lying Profile") |>
+    mutate(var_Correlate = "Frequency"),
+  make_cor(df10a, vars_intero, with = "LIE_Contextuality", component="Lying Profile") |>
+    mutate(var_Correlate = "Contextuality"),
+  make_cor(df10a, vars_intero, with = "LIE_Negativity", component="Lying Profile") |>
+    mutate(var_Correlate = "Negativity")
+)
+```
+
+## Summary
 

### 2024-02-26 analysis/study2.qmd
Update study2.qmd

--- 2024-02-26 analysis/study2.qmd
@@
 # names(df3)  # TAS, BPQ
-# names(df4)  # BAQ, BPQ, MAIA, BPCS
+# names(df4)  # BAQ, BPQ, MAIA, BRS, PBCS
 # names(df5)  
 # names(df6)  # IATS, SSS, GAD, PHQ2
-# names(df7a)  # MAIA, STAI, FFMQ, NEOFFI, CES
-# names(df7b)  # MAIA, STAIT, BPQ, PHQ15, PHQ9
-# names(df7c)  # TAS, BPQ, TAS, ASI, BDI, IASV
-# names(df8a)  # EDI, BPQ
-# names(df8b)  # TAS,PHQ15, PHQ9
-# names(df9)  # BFI, STQ, EQ, ECR, 
+# names(df7a)  # MAIA, STAI, FFMQ, NEOFFI, CES (?)
+# names(df7b)  # MAIA, STAI, BPQ, PHQ15, PHQ9
+# names(df7c)  # TAS, BPQ, ASI, BDI, CI (?), IASV (?), IASP (?)
+# names(df8a)  # EDI (eating disorder inventory?), BPQ
+# names(df8b)  # TAS, PHQ15, PHQ9
+# names(df9)  # BFI, STQ (?), EQ (?), ECR (?), TEAQ (?), UCLA (?), TACSEN (?)
 # names(df10a)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
-# names(df10n)  # BDI, STAI, PHQ4
+# names(df10b)  # BDI, STAI, PHQ4
 ```
@@
 
-data <- rbind(
+rez_gender <- rbind(
   make_diff(df1a, vars_intero, component="Demographic"),
@@
   mutate(var_Correlate = "Gender (Male vs. Female)")
+
+display_sig <- function(rez) {
+  rez |> 
+    arrange(var_Interoception, var_Correlate, desc(abs(r))) |> 
+    mutate(CI = insight::format_ci(CI_low, CI_high, ci=CI)) |>
+    select(Sample, var_Correlate, var_Interoception, r, CI, p) |>
+    gt::gt() |> 
+    gt::data_color(
+      columns = r,
+      rows = p < 0.5,
+      method = "numeric",
+      palette = c("blue", "red")
+    ) |> 
+    gt::fmt_number(decimals=3) |> 
+    gt::opt_stylize() |> 
+    gt::opt_interactive(use_compact_mode = TRUE) 
+}
+
+display_sig(rez_gender)
 ```
+
+### Age
 
@@
 
-data <- rbind(
-  data,
+rez_age <- rbind(
   make_cor(df1a, vars_intero, with = "Age", component="Demographic"),
@@
 )
+
+display_sig(rez_age)
+```
+
+## Body
+
+### MAIA
+
+```{r}
+# names(df2)[str_detect(names(df2), "MAIA")]  
+# names(df4)[str_detect(names(df4), "MAIA")] 
+# names(df7a)[str_detect(names(df7a), "MAIA")]  
+# names(df7b)[str_detect(names(df7b), "maia")] 
+# names(df10a)[str_detect(names(df10b), "MAIA")]
+
+df4$MAIA_BL <- rowMeans(df4[grep("MAIA_BL", names(df4))])
+df4$MAIA_TR <- rowMeans(df4[grep("MAIA_TR", names(df4))])
+df4$MAIA_AR <- rowMeans(df4[grep("MAIA_AR", names(df4))])
+df4$MAIA_SR <- rowMeans(df4[grep("MAIA_SR", names(df4))])
+df4$MAIA_EA <- rowMeans(df4[grep("MAIA_EA", names(df4))])
+df4$MAIA_NT <- rowMeans(df4[grep("MAIA_NT", names(df4))])
+
+rez_maia <- rbind(
+  make_cor(df2, vars_intero, with = "MAIA_AttentionReg", component="MAIA")  |>
+    mutate(var_Correlate = "Attention Regulation"),
+  make_cor(df2, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
+    mutate(var_Correlate = "Listening"),
+  make_cor(df2, vars_intero, with = "MAIA_BodyTrusting", component="MAIA") |>
+    mutate(var_Correlate = "Trusting"),
+  make_cor(df2, vars_intero, with = "MAIA_EmoAwareness", component="MAIA") |>
+    mutate(var_Correlate = "Emotional Awareness"),
+  make_cor(df2, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
+    mutate(var_Correlate = "Not Distracting"),
+  make_cor(df2, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
+    mutate(var_Correlate = "Noticing"),
+  make_cor(df2, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
+    mutate(var_Correlate = "Not Worrying"),
+  make_cor(df2, vars_intero, with = "MAIA_SelfReg", component="MAIA") |>
+    mutate(var_Correlate = "Self Regulation"),
+  # df4
+  make_cor(df4, vars_intero, with = "MAIA_BL", component="MAIA") |>
+    mutate(var_Correlate = "Listening"),
+  make_cor(df4, vars_intero, with = "MAIA_TR", component="MAIA") |>
+    mutate(var_Correlate = "Trusting"),
+  make_cor(df4, vars_intero, with = "MAIA_AR", component="MAIA") |>
+    mutate(var_Correlate = "Attention Regulation"),
+  make_cor(df4, vars_intero, with = "MAIA_SR", component="MAIA") |>
+    mutate(var_Correlate = "Self Regulation"),
+  make_cor(df4, vars_intero, with = "MAIA_EA", component="MAIA") |>
+    mutate(var_Correlate = "Emotional Awareness"),
+  make_cor(df4, vars_intero, with = "MAIA_NT", component="MAIA") |>
+    mutate(var_Correlate = "Noticing"),
+  # df7a
+  make_cor(df7a, vars_intero, with = "mAIA_ATTENTION_REGULATION", component="MAIA") |>
+    mutate(var_Correlate = "Attention Regulation"),
+  make_cor(df7a, vars_intero, with = "MAIA_NOTICING", component="MAIA") |>
+    mutate(var_Correlate = "Noticing"),
+  make_cor(df7a, vars_intero, with = "MAIA_NON_DISTRACTING", component="MAIA") |>
+    mutate(var_Correlate = "Not Distracting"),
+  make_cor(df7a, vars_intero, with = "MAIA_NON_DISTRACTING", component="MAIA") |>
+    mutate(var_Correlate = "Not Distracting"),
+  make_cor(df7a, vars_intero, with = "MAIA_NOT_WORRYING", component="MAIA") |>
+    mutate(var_Correlate = "Not Worrying"),
+  make_cor(df7a, vars_intero, with = "MAIA_EMOTIONAL_AWARENESS", component="MAIA") |>
+    mutate(var_Correlate = "Emotional Awareness"),
+  make_cor(df7a, vars_intero, with = "MAIA_SELF_REGULATION", component="MAIA") |>
+    mutate(var_Correlate = "Self Regulation"),
+  make_cor(df7a, vars_intero, with = "MAIA_BODY_LISTENING", component="MAIA") |>
+    mutate(var_Correlate = "Listening"),
+  make_cor(df7a, vars_intero, with = "MAIA_TRUSTING", component="MAIA") |>
+    mutate(var_Correlate = "Trusting"),
+
+  # df7b
+  make_cor(df7b, vars_intero, with = "maiaNotice", component="MAIA") |>
+    mutate(var_Correlate = "Noticing"),
+  make_cor(df7b, vars_intero, with = "maiaNonDistracting", component="MAIA") |>
+    mutate(var_Correlate = "Not Distracting"),
+  make_cor(df7b, vars_intero, with = "maiaNotWorrying", component="MAIA") |>
+    mutate(var_Correlate = "Not Worrying"),
+  make_cor(df7b, vars_intero, with = "maiaAttentionRegulation", component="MAIA") |>
+    mutate(var_Correlate = "Attention Regulation"),
+  make_cor(df7b, vars_intero, with = "maiaEmotionalAwareness", component="MAIA") |>
+    mutate(var_Correlate = "Emotional Awareness"),
+  make_cor(df7b, vars_intero, with = "maiaSelfRegulation", component="MAIA") |>
+    mutate(var_Correlate = "Self Regulation"),
+  make_cor(df7b, vars_intero, with = "maiaBodyListening", component="MAIA") |>
+    mutate(var_Correlate = "Listening"),
+  make_cor(df7b, vars_intero, with = "maiaTrusting", component="MAIA") |>
+    mutate(var_Correlate = "Trusting"),
+
+  # df10a
+  make_cor(df10a, vars_intero, with = "MAIA_AttentionRegulation", component="MAIA")  |>
+    mutate(var_Correlate = "Attention Regulation"),
+  make_cor(df10a, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
+    mutate(var_Correlate = "Listening"),
+  make_cor(df10a, vars_intero, with = "MAIA_EmotionalAwareness", component="MAIA") |>
+    mutate(var_Correlate = "Emotional Awareness"),
+  make_cor(df10a, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
+    mutate(var_Correlate = "Not Distracting"),
+  make_cor(df10a, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
+    mutate(var_Correlate = "Noticing"),
+  make_cor(df10a, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
+    mutate(var_Correlate = "Not Worrying"),
+  make_cor(df10a, vars_intero, with = "MAIA_SelfRegulation", component="MAIA") |>
+    mutate(var_Correlate = "Self Regulation"),
+  make_cor(df10a, vars_intero, with = "MAIA_Trusting", component="MAIA") |>
+    mutate(var_Correlate = "Trusting")
+)
+
+display_sig(rez_maia)
 ```
@@
 # df3$BPQ_AutonomicReactivity <- -1*normalize(df3$BPQ_AutonomicReactivity)
-names(df2)  # BPQ_R_Supra and _Sub?
-names(df3)
-names(df4)  # individual items 1-26
-names(df7b)  # BPQ sum
-names(df8a)  # individual items
+# names(df2)[str_detect(names(df2), "BPQ")]  # BPQ_R_Supra and _Sub?
+# names(df3)[str_detect(names(df3), "BPQ")]  
+# names(df4)[str_detect(names(df4), "BPQ")]   # individual items 1-26
+# names(df7b)[str_detect(names(df7b), "BPQ")]  # BPQ sum
+# names(df8a)[str_detect(names(df8a), "BPQ")]  # individual items
 
-data <- rbind(
-  data,
+df4$BPQ_A <- rowMeans(df4[str_detect(names(df4), "BPQ_")])
+df4$BAQ <- rowMeans(df4[,str_detect(names(df4), "BAQ")], na.rm = TRUE)
+df4$PBCS <- rowMeans(df4[,str_detect(names(df4), "PBCS")], na.rm = TRUE)
+df4$BRS <- rowMeans(df4[,str_detect(names(df4), "BRS")], na.rm = TRUE)
+df8a$BPQ_A <- -1*normalize(df8a$BPQ_A)
+
+rez_bpq <- rbind(
+  # df2
   make_cor(df2, vars_intero, with = "BPQ_A", component="Body") |>
@@
     mutate(var_Correlate = "Autonomic Reactivity (BPQ)"),
+  make_cor(df2, vars_intero, with = "ICQ", component="Body") |>
+    mutate(var_Correlate = "Interoceptive Confusion (ICQ)"),
+  # df3
   make_cor(df3, vars_intero, with = "BPQ_BodyAwareness", component="Body") |>
@@
   make_cor(df3, vars_intero, with = "BPQ_AutonomicReactivity", component="Body") |>
-    mutate(var_Correlate = "Autonomic Reactivity (BPQ)")
+    mutate(var_Correlate = "Autonomic Reactivity (BPQ)"),
+  # df4
+  make_cor(df4, vars_intero, with = "BPQ_A", component="Body") |>
+    mutate(var_Correlate = "Body Awareness (BPQ)"),
+  make_cor(df4, vars_intero, with = "BAQ", component="Body") |>
+    mutate(var_Correlate = "Body Awareness (BAQ)"),
+  make_cor(df4, vars_intero, with = "PBCS", component="Body") |>
+    mutate(var_Correlate = "Body Consciousness (PBCS)"),
+  make_cor(df4, vars_intero, with = "BRS", component="Body") |>
+    mutate(var_Correlate = "Body Responsiveness (BRS)"),
+  # df 6
+  make_cor(df6, vars_intero, with = "IATS_sum", component="Body") |>
+    mutate(var_Correlate = "Interoceptive Attention (IATS)"),
+  make_cor(df6, vars_intero, with = "SSS8_sum", component="Body") |>
+    mutate(var_Correlate = "Somatic Burden (SSS-8)"),
+  # df 7b
+  make_cor(df7b, vars_intero, with = "BPQ_Sum", component="Body") |>
+    mutate(var_Correlate = "Body Awareness (BPQ)"),
+  make_cor(df7b, vars_intero, with = "PHQ15_Sum", component="Mood") |>
+    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
+  # df 7c
+  make_cor(df7c, vars_intero, with = "BPQ_sum", component="Body") |>
+    mutate(var_Correlate = "Body Awareness (BPQ)"),
+  make_cor(df7c, vars_intero, with = "ICQ_sum", component="Body") |>
+    mutate(var_Correlate = "Interoceptive Confusion (ICQ)"),
+  # df8a
+  make_cor(df8a, vars_intero, with = "BPQ_A", component="Body") |>
+    mutate(var_Correlate = "Body Awareness (BPQ)")
 )
+
+display_sig(rez_bpq)
 ```
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5a, vars_cfa7, with = "MAIA_AttentionRegulation", component="MAIA")  |>  -->
-<!--     mutate(var_Correlate = "Attention Regulation"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "MAIA_BodyListening", component="MAIA") |>  -->
-<!--     mutate(var_Correlate = "Body Listening"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "MAIA_EmotionalAwareness", component="MAIA") |>  -->
-<!--     mutate(var_Correlate = "Emotional Awareness"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "MAIA_NotDistracting", component="MAIA") |>  -->
-<!--     mutate(var_Correlate = "Not Distracting"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "MAIA_Noticing", component="MAIA") |>  -->
-<!--     mutate(var_Correlate = "Noticing"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "MAIA_NotWorrying", component="MAIA") |>  -->
-<!--     mutate(var_Correlate = "Not Worrying"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "MAIA_SelfRegulation", component="MAIA") |>  -->
-<!--     mutate(var_Correlate = "Self Regulation"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "MAIA_Trusting", component="MAIA") |>  -->
-<!--     mutate(var_Correlate = "Trusting") -->
-<!-- ) -->
-<!-- ``` -->
+### Alexithymia
 
-<!-- ```{r} -->
-<!-- # names(df3)[str_detect(names(df3), "TAS")] -->
-<!-- # names(df4b)[str_starts(names(df4b), "TAS")] -->
+```{r}
+# names(df2)[str_detect(names(df2), "TAS")]
+# names(df3)[str_starts(names(df3), "TAS")]
+# names(df7c)[str_starts(names(df7c), "TAS")]
+# names(df8b)[str_starts(names(df8b), "TAS")]
 
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df3, vars_cfa, with = "TAS_IdentifyingFeelings", component="Body") |>  -->
-<!--     mutate(var_Correlate = "Difficulties Identifying Feelings"), -->
-<!--   make_cor(df3, vars_cfa, with = "TAS_DescribingFeelings", component="Body") |>  -->
-<!--     mutate(var_Correlate = "Difficulties Describing Feelings"), -->
-<!--   make_cor(df3, vars_cfa, with = "TAS_ExternallyOrientedThinking", component="Body") |>  -->
-<!--     mutate(var_Correlate = "External Thinking"), -->
-<!--   make_cor(df4b, vars_cfa, with = "TAS_DIF", component="Body") |>  -->
-<!--     mutate(var_Correlate = "Difficulties Identifying Feelings"), -->
-<!--   make_cor(df4b, vars_cfa, with = "TAS_DDF", component="Body") |>  -->
-<!--     mutate(var_Correlate = "Difficulties Describing Feelings") -->
-<!-- ) -->
-<!-- ``` -->
+rez_alexi <- rbind(
+  make_cor(df2, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
+    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
+  make_cor(df2, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
+    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
+  make_cor(df2, vars_intero, with = "TAS_EOT", component="Alexithymia") |>
+    mutate(var_Correlate = "External Thinking (TAS)"),
+  make_cor(df3, vars_intero, with = "TAS_DescribingFeelings", component="Alexithymia") |>
+    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
+  make_cor(df3, vars_intero, with = "TAS_IdentifyingFeelings", component="Alexithymia") |> 
+    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
+  make_cor(df3, vars_intero, with = "TAS_ExternallyOrientedThinking", component="Alexithymia") |>
+    mutate(var_Correlate = "External Thinking (TAS)"),
+  make_cor(df7c, vars_intero, with = "TAS_des", component="Alexithymia") |>
+    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
+  make_cor(df7c, vars_intero, with = "TAS_ident", component="Alexithymia") |>
+    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
+  make_cor(df7c, vars_intero, with = "TAS_ext", component="Alexithymia") |>
+    mutate(var_Correlate = "External Thinking (TAS)"),
+  make_cor(df8b, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
+    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
+  make_cor(df8b, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
+    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
+  # BVAQ
+  make_cor(df2, vars_intero, with = "BVAQ_Affective", component="Alexithymia") |>
+    mutate(var_Correlate = "Affective (BVAQ)"),
+  make_cor(df2, vars_intero, with = "BVAQ_Cognitive", component="Alexithymia") |>
+    mutate(var_Correlate = "Cognitive (BVAQ)")
+)
 
-<!-- ### Mood -->
+display_sig(rez_bpq)
+```
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df4b, vars_cfa, with = "PHQ15_sum", component="Mood") |>  -->
-<!--     mutate(var_Correlate = "Somatic Concerns (PHQ-15)"), -->
-<!--   make_cor(df4b, vars_cfa, with = "PHQ9_sum", component="Mood")|>  -->
-<!--     mutate(var_Correlate = "Depression (PHQ-9)"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PHQ4_Depression", component="Mood") |>  -->
-<!--     mutate(var_Correlate = "Depression (PHQ-4)"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PHQ4_Anxiety", component="Mood") |>  -->
-<!--     mutate(var_Correlate = "Anxiety (PHQ-4)") -->
-<!-- ) -->
-<!-- ``` -->
+## Mood
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5b, vars_cfa, with = "BDI2_Total", component="Mood") |>  -->
-<!--     mutate(var_Correlate = "Depression (BDI-II)") -->
-<!-- ) -->
-<!-- ``` -->
+### Depression
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5b, vars_cfa, with = "STAI5_General", component="Mood") |>  -->
-<!--     mutate(var_Correlate = "Anxiety (STAI-5)") -->
-<!-- ) -->
-<!-- ``` -->
+```{r}
+# names(df6)[str_detect(names(df6), "PHQ")] 
+# names(df7b)[str_detect(names(df7b), "PHQ")]
+# names(df7c)[str_detect(names(df7c), "BDI")]
+# names(df8b)[str_detect(names(df8b), "PHQ")]
+# names(df9)
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5a, vars_cfa7, with = "BPD", component="Mood") |>  -->
-<!--     mutate(var_Correlate = "Boderline Personality") -->
-<!-- ) -->
-<!-- ``` -->
+rez_dep <- rbind(
+  make_cor(df6, vars_intero, with = "PHQ2_sum", component="Mood") |>
+    mutate(var_Correlate = "Depression (PHQ-2)"),
+  make_cor(df7b, vars_intero, with = "PHQ9_Sum", component="Mood")|>
+    mutate(var_Correlate = "Depression (PHQ-9)"),
+  make_cor(df7c, vars_intero, with = "BDI_sum", component="Mood") |>
+    mutate(var_Correlate = "Depression (BDI)"),
+  make_cor(df8b, vars_intero, with = "PHQ15_sum", component="Mood") |>
+    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
+  make_cor(df8b, vars_intero, with = "PHQ9_sum", component="Mood") |>
+    mutate(var_Correlate = "Depression (PHQ-9)"),
+  make_cor(df10a, vars_intero, with = "PHQ4_Depression", component="Mood") |>
+    mutate(var_Correlate = "Depression (PHQ-2)"),
+  make_cor(df10b, vars_intero, with = "BDI2_Total", component="Mood") |>
+    mutate(var_Correlate = "Depression (BDI)")
+)
 
-<!-- ### Psychopathology -->
+display_sig(rez_dep)
+```
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5a, vars_cfa7, with = "PID5_Antagonism", component="Maladaptive") |>  -->
-<!--     mutate(var_Correlate = "Antagonism"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PID5_Detachment", component="Maladaptive") |>  -->
-<!--     mutate(var_Correlate = "Detachment"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PID5_Disinhibition", component="Maladaptive") |>  -->
-<!--     mutate(var_Correlate = "Disinhibition"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PID5_NegativeAffect", component="Maladaptive") |>  -->
-<!--     mutate(var_Correlate = "Negative Affect"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PID5_Psychoticism", component="Maladaptive") |>  -->
-<!--     mutate(var_Correlate = "Psychoticism") -->
-<!-- ) -->
-<!-- ``` -->
+### Anxiety
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5a, vars_cfa7, with = "SPQ_ConstrictedAffect", component="Schizotypic") |>  -->
-<!--     mutate(var_Correlate = "Constricted Affect"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "SPQ_Eccentric", component="Schizotypic") |>  -->
-<!--     mutate(var_Correlate = "Eccentric"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "SPQ_MagicalThinking", component="Schizotypic") |>  -->
-<!--     mutate(var_Correlate = "Magical Thinking"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "SPQ_NoCloseFriends", component="Schizotypic") |>  -->
-<!--     mutate(var_Correlate = "No Close Friends"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "SPQ_OddSpeech", component="Schizotypic") |>  -->
-<!--     mutate(var_Correlate = "Odd Speech"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "SPQ_Reference", component="Schizotypic") |>  -->
-<!--     mutate(var_Correlate = "Reference"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "SPQ_SocialAnxiety", component="Schizotypic") |>  -->
-<!--     mutate(var_Correlate = "Social Anxiety"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "SPQ_Suspiciousness", component="Schizotypic") |>  -->
-<!--     mutate(var_Correlate = "Suspiciousness"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "SPQ_UnusualPerceptions", component="Schizotypic") |>  -->
-<!--     mutate(var_Correlate = "Unusual Perceptions") -->
-<!-- ) -->
-<!-- ``` -->
+```{r}
+# names(df6)[str_detect(names(df6), "GAD")] 
+# names(df7a)[str_detect(names(df7a), "STAI")] 
+# names(df7b)[str_detect(names(df7b), "STAI")] 
+# names(df7c)[str_detect(names(df7c), "STAI")]
 
-<!-- ```{r} -->
-<!-- #  names(select(df5a, starts_with("ASQ"))) -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5a, vars_cfa7, with = "ASQ_Imagination", component="Autistic") |>  -->
-<!--     mutate(var_Correlate = "Imagination"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "ASQ_LackSocialSkills", component="Autistic") |> -->
-<!--     mutate(var_Correlate = "Lack of Social Skills"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "ASQ_LowAttentionalSwitching", component="Autistic") |> -->
-<!--     mutate(var_Correlate = "Low Attentional Switching"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "ASQ_Patterns", component="Autistic") |> -->
-<!--     mutate(var_Correlate = "Patterns and Numbers"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "ASQ_Routine", component="Autistic") |> -->
-<!--     mutate(var_Correlate = "Routines") -->
-<!-- ) -->
-<!-- ``` -->
+rez_anx <- rbind(
+  make_cor(df6, vars_intero, with = "GAD2_sum", component="Mood") |>
+    mutate(var_Correlate = "Anxiety (GAD-2)"),
+  make_cor(df7a, vars_intero, with = "STAI_T_Sumscore", component="Mood") |>
+    mutate(var_Correlate = "Anxiety (STAI)"),
+  make_cor(df7b, vars_intero, with = "STAIT_Sum", component="Mood") |>
+    mutate(var_Correlate = "Anxiety (STAI)"),
+  make_cor(df7c, vars_intero, with = "STAIT_sum", component="Mood") |>
+    mutate(var_Correlate = "Anxiety (STAI)"),
+  make_cor(df10a, vars_intero, with = "PHQ4_Anxiety", component="Mood") |>
+    mutate(var_Correlate = "Anxiety (GAD-2)"),
+  make_cor(df10b, vars_intero, with = "PHQ4_Anxiety", component="Mood") |>
+    mutate(var_Correlate = "Anxiety (GAD-2)"),
+  make_cor(df10b, vars_intero, with = "STAI5_General", component="Mood") |>
+    mutate(var_Correlate = "Anxiety (STAI)")
+)
 
-<!-- ### Personality -->
+display_sig(rez_anx)
+```
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Agreeableness", component="Personality") |>  -->
-<!--     mutate(var_Correlate = "Agreeableness"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Conscientiousness", component="Personality") |> -->
-<!--     mutate(var_Correlate = "Conscientiousness"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Neuroticism", component="Personality") |> -->
-<!--     mutate(var_Correlate = "Neuroticism"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Openness", component="Personality") |> -->
-<!--     mutate(var_Correlate = "Openness"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Extraversion", component="Personality") |> -->
-<!--     mutate(var_Correlate = "Extraversion"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_HonestyHumility", component="Personality") |> -->
-<!--     mutate(var_Correlate = "Honesty-Humility") -->
-<!-- ) -->
-<!-- ``` -->
+## Psychopathology
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5a, vars_cfa7, with = "PI_Alive", component="World Beliefs") |>  -->
-<!--     mutate(var_Correlate = "Alive"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PI_Changing", component="World Beliefs") |> -->
-<!--     mutate(var_Correlate = "Changing"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PI_Enticing", component="World Beliefs") |> -->
-<!--     mutate(var_Correlate = "Enticing"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PI_Good", component="World Beliefs") |> -->
-<!--     mutate(var_Correlate = "Good"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PI_Hierarchical", component="World Beliefs") |> -->
-<!--     mutate(var_Correlate = "Hierarchical"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "PI_Safe", component="World Beliefs") |> -->
-<!--     mutate(var_Correlate = "Safe") -->
-<!--   # TODO: Add understanble -->
-<!-- ) -->
-<!-- ``` -->
+```{r}
+rez_bpd <- rbind(
+  make_cor(df10a, vars_intero, with = "BPD", component="Mood") |>
+    mutate(var_Correlate = "Boderline Personality")
+)
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5a, vars_cfa7, with = "GCBS_Extraterrestrial", component="Conspiracy Beliefs") |>  -->
-<!--     mutate(var_Correlate = "Extraterrestrial"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "GCBS_GlobalConspiracies", component="Conspiracy Beliefs") |> -->
-<!--     mutate(var_Correlate = "Global Conspiracies"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "GCBS_GovernmentMalfeasance", component="Conspiracy Beliefs") |> -->
-<!--     mutate(var_Correlate = "Government Malfeasance"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "GCBS_InformationControl", component="Conspiracy Beliefs") |> -->
-<!--     mutate(var_Correlate = "Information Control"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "GCBS_PersonalWellbeing", component="Conspiracy Beliefs") |> -->
-<!--     mutate(var_Correlate = "Personal Wellbeing") -->
-<!-- ) -->
-<!-- ``` -->
+display_sig(rez_bpd)
+```
 
-<!-- ```{r} -->
-<!-- data <- rbind( -->
-<!--   data, -->
-<!--   make_cor(df5a, vars_cfa7, with = "LIE_Ability", component="Lying Profile") |>  -->
-<!--     mutate(var_Correlate = "Ability"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "LIE_Frequency", component="Lying Profile") |> -->
-<!--     mutate(var_Correlate = "Frequency"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "LIE_Contextuality", component="Lying Profile") |> -->
-<!--     mutate(var_Correlate = "Contextuality"), -->
-<!--   make_cor(df5a, vars_cfa7, with = "LIE_Negativity", component="Lying Profile") |> -->
-<!--     mutate(var_Correlate = "Negativity") -->
-<!-- ) -->
-<!-- ``` -->
+```{r}
+rez_pid <- rbind(
+  make_cor(df10a, vars_intero, with = "PID5_Antagonism", component="Maladaptive") |>
+    mutate(var_Correlate = "Antagonism"),
+  make_cor(df10a, vars_intero, with = "PID5_Detachment", component="Maladaptive") |>
+    mutate(var_Correlate = "Detachment"),
+  make_cor(df10a, vars_intero, with = "PID5_Disinhibition", component="Maladaptive") |>
+    mutate(var_Correlate = "Disinhibition"),
+  make_cor(df10a, vars_intero, with = "PID5_NegativeAffect", component="Maladaptive") |>
+    mutate(var_Correlate = "Negative Affect"),
+  make_cor(df10a, vars_intero, with = "PID5_Psychoticism", component="Maladaptive") |>
+    mutate(var_Correlate = "Psychoticism")
+)
 
-### Summary
+display_sig(rez_pid)
+```
+
+```{r}
+rez_spq <- rbind(
+  make_cor(df10a, vars_intero, with = "SPQ_ConstrictedAffect", component="Schizotypic") |>
+    mutate(var_Correlate = "Constricted Affect"),
+  make_cor(df10a, vars_intero, with = "SPQ_Eccentric", component="Schizotypic") |>
+    mutate(var_Correlate = "Eccentric"),
+  make_cor(df10a, vars_intero, with = "SPQ_MagicalThinking", component="Schizotypic") |>
+    mutate(var_Correlate = "Magical Thinking"),
+  make_cor(df10a, vars_intero, with = "SPQ_NoCloseFriends", component="Schizotypic") |>
+    mutate(var_Correlate = "No Close Friends"),
+  make_cor(df10a, vars_intero, with = "SPQ_OddSpeech", component="Schizotypic") |>
+    mutate(var_Correlate = "Odd Speech"),
+  make_cor(df10a, vars_intero, with = "SPQ_Reference", component="Schizotypic") |>
+    mutate(var_Correlate = "Reference"),
+  make_cor(df10a, vars_intero, with = "SPQ_SocialAnxiety", component="Schizotypic") |>
+    mutate(var_Correlate = "Social Anxiety"),
+  make_cor(df10a, vars_intero, with = "SPQ_Suspiciousness", component="Schizotypic") |>
+    mutate(var_Correlate = "Suspiciousness"),
+  make_cor(df10a, vars_intero, with = "SPQ_UnusualPerceptions", component="Schizotypic") |>
+    mutate(var_Correlate = "Unusual Perceptions")
+)
+
+display_sig(rez_spq)
+```
+
+```{r}
+#  names(select(df10a, starts_with("ASQ")))
+rez_asq <- rbind(
+  make_cor(df10a, vars_intero, with = "ASQ_Imagination", component="Autistic") |>
+    mutate(var_Correlate = "Imagination"),
+  make_cor(df10a, vars_intero, with = "ASQ_LackSocialSkills", component="Autistic") |>
+    mutate(var_Correlate = "Lack of Social Skills"),
+  make_cor(df10a, vars_intero, with = "ASQ_LowAttentionalSwitching", component="Autistic") |>
+    mutate(var_Correlate = "Low Attentional Switching"),
+  make_cor(df10a, vars_intero, with = "ASQ_Patterns", component="Autistic") |>
+    mutate(var_Correlate = "Patterns and Numbers"),
+  make_cor(df10a, vars_intero, with = "ASQ_Routine", component="Autistic") |>
+    mutate(var_Correlate = "Routines")
+)
+
+display_sig(rez_asq)
+```
+
+## Personality
+
+```{r}
+# names(df7a)[str_detect(names(df7a), "NEO")]
+# names(df9)[str_detect(names(df9), "BFI_")]
+
+rez_pers <- rbind(
+  make_cor(df7a, vars_intero, with = "NEO_FFI_SUMSCORE", component="Personality") |>
+    mutate(var_Correlate = "Neuroticism"),
+  make_cor(df9, vars_intero, with = "BFI_AGREEABLENESS", component="Personality") |>
+    mutate(var_Correlate = "Agreeableness"),
+  make_cor(df9, vars_intero, with = "BFI_CONSCIENTIOUSNESS", component="Personality") |>
+    mutate(var_Correlate = "Conscientiousness"),
+  make_cor(df9, vars_intero, with = "BFI_NEUROTICISM", component="Personality") |>
+    mutate(var_Correlate = "Neuroticism"),
+  make_cor(df9, vars_intero, with = "BFI_OPENNESS", component="Personality") |>
+    mutate(var_Correlate = "Openness"),
+  make_cor(df9, vars_intero, with = "BFI_EXTROVERSION", component="Personality") |>
+    mutate(var_Correlate = "Extraversion"),
+  make_cor(df10a, vars_intero, with = "IPIP6_Agreeableness", component="Personality") |>
+    mutate(var_Correlate = "Agreeableness"),
+  make_cor(df10a, vars_intero, with = "IPIP6_Conscientiousness", component="Personality") |>
+    mutate(var_Correlate = "Conscientiousness"),
+  make_cor(df10a, vars_intero, with = "IPIP6_Neuroticism", component="Personality") |>
+    mutate(var_Correlate = "Neuroticism"),
+  make_cor(df10a, vars_intero, with = "IPIP6_Openness", component="Personality") |>
+    mutate(var_Correlate = "Openness"),
+  make_cor(df10a, vars_intero, with = "IPIP6_Extraversion", component="Personality") |>
+    mutate(var_Correlate = "Extraversion"),
+  make_cor(df10a, vars_intero, with = "IPIP6_HonestyHumility", component="Personality") |>
+    mutate(var_Correlate = "Honesty-Humility")
+)
+
+display_sig(rez_pers)
+```
+
+## Others
+
+```{r}
+# names(df7a)[str_detect(names(df7a), "FFMQ")]
+
+rez_ffmq <- rbind(
+  make_cor(df7a, vars_intero, with = "FFMQ_OBSERVATION", component="Mindfulness") |>
+    mutate(var_Correlate = "Observation (FFMQ)"),
+  make_cor(df7a, vars_intero, with = "FFMQ_DESCRIPTION", component="Mindfulness") |>
+    mutate(var_Correlate = "Description (FFMQ)")
+)
+
+display_sig(rez_ffmq)
+```
+
+```{r}
+rez_pi <- rbind(
+  make_cor(df10a, vars_intero, with = "PI_Alive", component="World Beliefs") |>
+    mutate(var_Correlate = "Alive"),
+  make_cor(df10a, vars_intero, with = "PI_Changing", component="World Beliefs") |>
+    mutate(var_Correlate = "Changing"),
+  make_cor(df10a, vars_intero, with = "PI_Enticing", component="World Beliefs") |>
+    mutate(var_Correlate = "Enticing"),
+  make_cor(df10a, vars_intero, with = "PI_Good", component="World Beliefs") |>
+    mutate(var_Correlate = "Good"),
+  make_cor(df10a, vars_intero, with = "PI_Hierarchical", component="World Beliefs") |>
+    mutate(var_Correlate = "Hierarchical"),
+  make_cor(df10a, vars_intero, with = "PI_Safe", component="World Beliefs") |>
+    mutate(var_Correlate = "Safe"),
+  make_cor(df10a, vars_intero, with = "PI_Understandable", component="World Beliefs") |>
+    mutate(var_Correlate = "Understandable")
+)
+
+display_sig(rez_pi)
+```
+
+```{r}
+rez_gcbs <- rbind(
+  make_cor(df10a, vars_intero, with = "GCBS_Extraterrestrial", component="Conspiracy Beliefs") |>
+    mutate(var_Correlate = "Extraterrestrial"),
+  make_cor(df10a, vars_intero, with = "GCBS_GlobalConspiracies", component="Conspiracy Beliefs") |>
+    mutate(var_Correlate = "Global Conspiracies"),
+  make_cor(df10a, vars_intero, with = "GCBS_GovernmentMalfeasance", component="Conspiracy Beliefs") |>
+    mutate(var_Correlate = "Government Malfeasance"),
+  make_cor(df10a, vars_intero, with = "GCBS_InformationControl", component="Conspiracy Beliefs") |>
+    mutate(var_Correlate = "Information Control"),
+  make_cor(df10a, vars_intero, with = "GCBS_PersonalWellbeing", component="Conspiracy Beliefs") |>
+    mutate(var_Correlate = "Personal Wellbeing")
+)
+
+display_sig(rez_gcbs)
+```
+
+```{r}
+rez_lie <- rbind(
+  make_cor(df10a, vars_intero, with = "LIE_Ability", component="Lying Profile") |>
+    mutate(var_Correlate = "Ability"),
+  make_cor(df10a, vars_intero, with = "LIE_Frequency", component="Lying Profile") |>
+    mutate(var_Correlate = "Frequency"),
+  make_cor(df10a, vars_intero, with = "LIE_Contextuality", component="Lying Profile") |>
+    mutate(var_Correlate = "Contextuality"),
+  make_cor(df10a, vars_intero, with = "LIE_Negativity", component="Lying Profile") |>
+    mutate(var_Correlate = "Negativity")
+)
+
+display_sig(rez_lie)
+```
+
+```{r}
+# names(df4)
+
+# rez_others <- rbind(
+#   make_cor(df2, vars_intero, with = "ICQ", component="Other") |>
+#     mutate(var_Correlate = "Interoceptive Confusion (ICQ)")
+# )
+# 
+# display_sig(rez_others)
+```
+
+## Summary
 
@@
 #| fig-width: 15
+
+data <- rbind(
+  rez_gender,
+  rez_age,
+  rez_maia,
+  rez_bpq,
+  rez_alexi,
+  rez_dep,
+  rez_anx,
+  rez_bpd,
+  rez_spq,
+  rez_asq,
+  rez_pers,
+  rez_ffmq,
+  rez_pi,
+  rez_gcbs,
+  rez_lie
+)
 
@@
          #   "Schizotypic", "Autistic", "Personality", "Conspiracy Beliefs", "World Beliefs", "Lying Profile")) |>
-  ggplot(aes(x = var_Correlate)) +
-  geom_hline(yintercept = 0, linetype = "dashed") +
+  ggplot(aes(y = var_Correlate)) +
+  geom_vline(xintercept = 0, linetype = "dashed") +
   # geom_bar(aes(fill=Sample, alpha=sig, y=r, group=Sample), stat="identity", position = position_dodge2(width = 0.8)) +
-  geom_linerange(aes(color=dir, alpha=sig, ymin=0, ymax=r, group=Sample), position = position_dodge2(width = 0.7), linewidth=2.5) +
-  geom_linerange(aes(ymin = CI_low, ymax = CI_high, color = dir, alpha=sig, group=Sample), position = position_dodge2(width = 0.7)) +
+  geom_linerange(aes(color=dir, alpha=sig, xmin=0, xmax=r, group=Sample), position = position_dodge2(width = 0.7), linewidth=2.5) +
+  geom_linerange(aes(xmin = CI_low, xmax = CI_high, color = dir, alpha=sig, group=Sample), position = position_dodge2(width = 0.7)) +
   scale_fill_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
@@
   scale_alpha_discrete(range = c(0.2, 0.7), guide = "none") +
-  scale_y_continuous(expand = c(0, 0), breaks = c(-0.3, 0, 0.3)) +
+  scale_x_continuous(expand = c(0, 0), breaks = c(-0.3, 0, 0.3)) +
   facet_grid(Component ~ var_Interoception, scales = "free_y", switch = "y") +
-  coord_flip(ylim = c(-0.45, 0.45)) +
+  coord_cartesian(xlim = c(-0.45, 0.45)) +
   theme_modern(axis.title.space = 5) +
+  # labs(x = "Correlation", title="Correlates of the Interoceptive Accuracy Scale (IAS)") +
   theme(panel.grid.major.y = element_line(),
         axis.title.y = element_blank(),
+        axis.title.x = element_blank(),
         axis.line.x = element_blank(),

### 2024-02-27 analysis/study1.qmd
update figs
@AnafNeves @magdapf I think we are close to a definitive version of the results, so we can focus on the paper
- TODO is to add the various samples tabs in study1 in some of the steps where I was too lazy to add them

@@
         plot.title = element_text(face="bold")) +
-  labs(title = "Distribution of responses for all items across various datasets", x = "Response", y = "Density", color = "Item") +
+  labs(x = "Response", y = "Density",
+       # title = "Distribution of responses for all items across various datasets", 
+       color = "Item") +
   facet_wrap(~Sample, scales = "free_y", nrow = 5)

### 2024-02-27 analysis/study2.qmd
update figs
@AnafNeves @magdapf I think we are close to a definitive version of the results, so we can focus on the paper
- TODO is to add the various samples tabs in study1 in some of the steps where I was too lazy to add them

@@
 # names(df6)  # IATS, SSS, GAD, PHQ2
-# names(df7a)  # MAIA, STAI, FFMQ, NEOFFI, CES (?)
+# names(df7a)  # MAIA, STAI, FFMQ, NEOFFI, CES
 # names(df7b)  # MAIA, STAI, BPQ, PHQ15, PHQ9
@@
 # names(df8b)  # TAS, PHQ15, PHQ9
-# names(df9)  # BFI, STQ (?), EQ (?), ECR (?), TEAQ (?), UCLA (?), TACSEN (?)
+# names(df9)  # BFI, STQ (?), EQ, ECR, TEAQ, UCLA, TACSEN
 # names(df10a)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
@@
 
-Even EGA components capture pairs or groupings of pairs of items.
+Very strong correlations between empirical scores (i.e., average of pairs of items) and dimensions derived from models. Even EGA components capture pairs or groupings of pairs of items.
 
@@
 
-## Body
+## Interoception
 
@@
 # names(df7b)[str_detect(names(df7b), "maia")] 
+# names(df8a)[str_detect(names(df8a), "EDI")] 
 # names(df10a)[str_detect(names(df10b), "MAIA")]
@@
 
-### Body
+### Body Awareness
 
@@
 
-rez_bpq <- rbind(
+rez_body <- rbind(
   # df2
@@
   make_cor(df8a, vars_intero, with = "BPQ_A", component="Body") |>
-    mutate(var_Correlate = "Body Awareness (BPQ)")
+    mutate(var_Correlate = "Body Awareness (BPQ)"),
+  make_cor(df8a, vars_intero, with = "EDI_IA", component="Body") |>
+    mutate(var_Correlate = "Interoceptive Awareness (EDI)")
 )
 
-display_sig(rez_bpq)
+display_sig(rez_body)
 ```
@@
   make_cor(df2, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
-    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
+    mutate(var_Correlate = "Diff. Identifying Feelings (TAS)"),
   make_cor(df2, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
-    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
+    mutate(var_Correlate = "Diff. Describing Feelings (TAS)"),
   make_cor(df2, vars_intero, with = "TAS_EOT", component="Alexithymia") |>
@@
   make_cor(df3, vars_intero, with = "TAS_DescribingFeelings", component="Alexithymia") |>
-    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
+    mutate(var_Correlate = "Diff. Describing Feelings (TAS)"),
   make_cor(df3, vars_intero, with = "TAS_IdentifyingFeelings", component="Alexithymia") |> 
-    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
+    mutate(var_Correlate = "Diff. Identifying Feelings (TAS)"),
   make_cor(df3, vars_intero, with = "TAS_ExternallyOrientedThinking", component="Alexithymia") |>
@@
   make_cor(df7c, vars_intero, with = "TAS_des", component="Alexithymia") |>
-    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
+    mutate(var_Correlate = "Diff. Describing Feelings (TAS)"),
   make_cor(df7c, vars_intero, with = "TAS_ident", component="Alexithymia") |>
-    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
+    mutate(var_Correlate = "Diff. Identifying Feelings (TAS)"),
   make_cor(df7c, vars_intero, with = "TAS_ext", component="Alexithymia") |>
@@
   make_cor(df8b, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
-    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
+    mutate(var_Correlate = "Diff. Identifying Feelings (TAS)"),
   make_cor(df8b, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
-    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
+    mutate(var_Correlate = "Diff. Describing Feelings (TAS)"),
   # BVAQ
@@
 
-display_sig(rez_bpq)
+display_sig(rez_alexi)
 ```
@@
 # names(df6)[str_detect(names(df6), "PHQ")] 
+# names(df7a)[str_detect(names(df7aa), "PHQ")]
 # names(df7b)[str_detect(names(df7b), "PHQ")]
@@
     mutate(var_Correlate = "Depression (PHQ-2)"),
+  make_cor(df7a, vars_intero, with = "CES_SUM", component="Mood")|>
+    mutate(var_Correlate = "Depression (CES)"),
   make_cor(df7b, vars_intero, with = "PHQ9_Sum", component="Mood")|>
@@
 ## Psychopathology
-
-```{r}
-rez_bpd <- rbind(
-  make_cor(df10a, vars_intero, with = "BPD", component="Mood") |>
-    mutate(var_Correlate = "Boderline Personality")
-)
-
-display_sig(rez_bpd)
-```
 
@@
 ```{r}
+# names(df9)[str_detect(names(df9), "UCLA")]
+# names(df9)[str_detect(names(df9), "EQ")]
+df9$EQ <- rowMeans(select(df9, starts_with("EQ")))
+
+rez_social <- rbind(
+  make_cor(df9, vars_intero, with = "UCLA_TOTAL", component="Interpersonal") |>
+    mutate(var_Correlate = "Loneliness (UCLA)"),
+  make_cor(df9, vars_intero, with = "EQ", component="Interpersonal") |>
+    mutate(var_Correlate = "Empathy (EQ)"),
+  make_cor(df9, vars_intero, with = "ECR_ANXIETY", component="Interpersonal") |>
+    mutate(var_Correlate = "Relationship Anxiety (ECR)"),
+  make_cor(df9, vars_intero, with = "ECR_AVOIDANCE", component="Interpersonal") |>
+    mutate(var_Correlate = "Relationship Avoidance (ECR)"),
+  make_cor(df10a, vars_intero, with = "BPD", component="Interpersonal") |>
+    mutate(var_Correlate = "Boderline Personality")
+)
+
+display_sig(rez_social)
+```
+
+```{r}
 rez_pi <- rbind(
@@
 rez_gcbs <- rbind(
-  make_cor(df10a, vars_intero, with = "GCBS_Extraterrestrial", component="Conspiracy Beliefs") |>
+  make_cor(df10a, vars_intero, with = "GCBS_Extraterrestrial", component="Conspiracy") |>
     mutate(var_Correlate = "Extraterrestrial"),
-  make_cor(df10a, vars_intero, with = "GCBS_GlobalConspiracies", component="Conspiracy Beliefs") |>
+  make_cor(df10a, vars_intero, with = "GCBS_GlobalConspiracies", component="Conspiracy") |>
     mutate(var_Correlate = "Global Conspiracies"),
-  make_cor(df10a, vars_intero, with = "GCBS_GovernmentMalfeasance", component="Conspiracy Beliefs") |>
+  make_cor(df10a, vars_intero, with = "GCBS_GovernmentMalfeasance", component="Conspiracy") |>
     mutate(var_Correlate = "Government Malfeasance"),
-  make_cor(df10a, vars_intero, with = "GCBS_InformationControl", component="Conspiracy Beliefs") |>
+  make_cor(df10a, vars_intero, with = "GCBS_InformationControl", component="Conspiracy") |>
     mutate(var_Correlate = "Information Control"),
-  make_cor(df10a, vars_intero, with = "GCBS_PersonalWellbeing", component="Conspiracy Beliefs") |>
+  make_cor(df10a, vars_intero, with = "GCBS_PersonalWellbeing", component="Conspiracy") |>
     mutate(var_Correlate = "Personal Wellbeing")
@@
 
-```{r}
-# names(df4)
-
-# rez_others <- rbind(
-#   make_cor(df2, vars_intero, with = "ICQ", component="Other") |>
-#     mutate(var_Correlate = "Interoceptive Confusion (ICQ)")
-# )
-# 
-# display_sig(rez_others)
-```
-
 ## Summary
@@
 ```{r}
-#| fig-height: 20
-#| fig-width: 15
+#| fig-height: 13.365
+#| fig-width: 9.45
+#| fig-cap: "Subjective Correlates of the Interoceptive Accuracy Scale (IAS).
+Each bar represents one sample (total N = **TODO**), and different samples using the same measures are grouped together, providing an intuition of the general trend.
+Blue and red bars represent positive and negative correlations, respectively, with their 95% CI.
+Transparent bars indicate non-significant correlations (p > .05)."
 
@@
   rez_maia,
-  rez_bpq,
+  rez_body,
   rez_alexi,
@@
   rez_anx,
-  rez_bpd,
   rez_spq,
   rez_asq,
+  rez_pid,
+  rez_social,
   rez_pers,
@@
          var_Interoception = str_replace(var_Interoception, "Expulsion_Sudden", "Expulsion - Sudden"),
-         var_Interoception = fct_relevel(var_Interoception, "Heart/Breathing", "Muscles/Pain", "Itch/Bruise", "Hungry/Thirsty", "Urinate/Defecate", "Wind/Burp", "Cough/Sneeze")) |>
-         # Component = fct_relevel(
-         #   Component, "Demographic", "MAIA", "Body", "Mood", "Maladaptive",
-         #   "Schizotypic", "Autistic", "Personality", "Conspiracy Beliefs", "World Beliefs", "Lying Profile")) |>
+         var_Interoception = fct_relevel(var_Interoception, "Heart/Breathing", "Muscles/Pain", "Itch/Bruise", "Hungry/Thirsty", "Urinate/Defecate", "Wind/Burp", "Cough/Sneeze"),
+         Component = fct_relevel(
+           Component, "Demographic", "MAIA", "Body", "Alexithymia", "Mood", "Maladaptive",
+           "Schizotypic", "Autistic", "Interpersonal", "Personality", "Conspiracy", "World Beliefs", "Lying Profile", "Mindfulness")) |>
   ggplot(aes(y = var_Correlate)) +
@@
   # geom_bar(aes(fill=Sample, alpha=sig, y=r, group=Sample), stat="identity", position = position_dodge2(width = 0.8)) +
-  geom_linerange(aes(color=dir, alpha=sig, xmin=0, xmax=r, group=Sample), position = position_dodge2(width = 0.7), linewidth=2.5) +
+  geom_linerange(aes(color=dir, alpha=sig, xmin=0, xmax=r, group=Sample), position = position_dodge2(width = 0.7), linewidth=2) +
   geom_linerange(aes(xmin = CI_low, xmax = CI_high, color = dir, alpha=sig, group=Sample), position = position_dodge2(width = 0.7)) +
@@
 p
-ggsave("figures/Figure2.png", p, width=21*0.6, height=29.7*0.45, dpi=200, bg="white")
+ggsave("figures/Figure2.png", p, width=21*0.45, height=29.7*0.45, dpi=200, bg="white")
 ```
-
-## Discussion
-
-Benefits of the IAS:
-- Straightforward and sensation-centered items
-
-Recommendations:
-- Remove Itch (redundant + issue in Chinese)
-- Use analog scales
-
-Limitations:
-- Not much clear theorethical or empirical structure (small grouping of items)
-- Limited variability (clear mode at 4/5), very low prevalence of 5/5 responses.
-- Ambiguous items which grouping depends on the context (and its awareness)
-  - E.g., heart beating fast, vomit when nauseaous
-- Few items for some modalities (e.g., 1 for heart)
-- Positive phrasing: benefits but also might exacerbate positivity bias (and thus unidimensionality)
-
-Need for context-specific items (cross-modal when possible, i.E., cardioception, respiroception, etc.).
-
-New Scale: Multimodal Interoceptive Sensitivity Scale (MISS)

### 2024-02-28 analysis/study1.qmd
sample tabs
Think its just this?

--- 2024-02-26 analysis/study1.qmd
@@
 
+#### Sample 2
+
+```{r}
+#| fig-height: 10
+
+efa4 <- parameters::factor_analysis(data2, n = 4, rotation = "oblimin", sort = TRUE)
+plot(efa4)
+
+display(efa4)
+
+```
+
+#### Sample 3
+
+```{r}
+#| fig-height: 10
+
+efa4 <- parameters::factor_analysis(data3, n = 4, rotation = "oblimin", sort = TRUE)
+plot(efa4)
+
+display(efa4)
+```
+
+#### sample 4
+
+```{r}
+#| fig-height: 10
+
+efa4 <- parameters::factor_analysis(data4, n = 4, rotation = "oblimin", sort = TRUE)
+plot(efa4)
+
+display(efa4)
+```
+
+#### Sample 5
+
+```{r}
+#| fig-height: 10
+
+efa4 <- parameters::factor_analysis(data5, n = 4, rotation = "oblimin", sort = TRUE)
+plot(efa4)
+
+display(efa4)
+```
+
+#### Sample 5
+
+```{r}
+#| fig-height: 10
+
+efa4 <- parameters::factor_analysis(data5, n = 4, rotation = "oblimin", sort = TRUE)
+plot(efa4)
+
+display(efa4)
+```
+
+#### Sample 6
+
+```{r}
+#| fig-height: 10
+
+efa4 <- parameters::factor_analysis(data6, n = 4, rotation = "oblimin", sort = TRUE)
+plot(efa4)
+
+display(efa4)
+```
+
+#### Sample 7a
+
+```{r}
+#| fig-height: 10
+
+efa4 <- parameters::factor_analysis(data7a, n = 4, rotation = "oblimin", sort = TRUE)
+plot(efa4)
+
+display(efa4)
+```
+
+#### Sample 7b
+
+```{r}
+#| fig-height: 10
+
+efa4 <- parameters::factor_analysis(data7b, n = 4, rotation = "oblimin", sort = TRUE)
+plot(efa4)
+
+display(efa4)
+```
+
+#### Sample 7c
+
+```{r}
+#| fig-height: 10
+
+efa4 <- parameters::factor_analysis(data7c, n = 4, rotation = "oblimin", sort = TRUE)
+plot(efa4)
+
+display(efa4)
+```
+
+#### Sample 8a
+
+```{r}
+#| fig-height: 10
+
+efa4 <- parameters::factor_analysis(data8a, n = 4, rotation = "oblimin", sort = TRUE)
+plot(efa4)
+
+display(efa4)
+```
+
+#### Sample 8b
+
+```{r}
+#| fig-height: 10
+
+efa4 <- parameters::factor_analysis(data8b, n = 4, rotation = "oblimin", sort = TRUE)
+plot(efa4)
+
+display(efa4)
+```
+
+#### Sample 9
+
+```{r}
+#| fig-height: 10
+
+efa4 <- parameters::factor_analysis(data9, n = 4, rotation = "oblimin", sort = TRUE)
+plot(efa4)
+
+display(efa4)
+```
+
+#### Sample 10a
+
+```{r}
+#| fig-height: 10
+
+efa4 <- parameters::factor_analysis(data10a, n = 4, rotation = "oblimin", sort = TRUE)
+plot(efa4)
+
+display(efa4)
+```
+
+#### Sample 10b
+
+```{r}
+#| fig-height: 10
+
+efa4 <- parameters::factor_analysis(data10b, n = 4, rotation = "oblimin", sort = TRUE)
+plot(efa4)
+
+display(efa4)
+```
+
 :::
@@
 
+#### Sample 1b
+
+```{r}
+#| warning: false
+
+display(compare_mods(data1b))
+
+```
+
+#### Sample 2
+
+```{r}
+#| warning: false
+
+display(compare_mods(data2))
+
+```
+
+#### Sample 3
+
+```{r}
+#| warning: false
+
+display(compare_mods(data3))
+
+```
+
+#### Sample 4
+
+```{r}
+#| warning: false
+
+display(compare_mods(data4))
+
+```
+
+#### Sample 5
+
+```{r}
+#| warning: false
+
+display(compare_mods(data5))
+
+```
+
+#### Sample 6
+
+```{r}
+#| warning: false
+
+display(compare_mods(data6))
+```
+
+#### Sample 7a
+
+```{r}
+#| warning: false
+
+display(compare_mods(data7a))
+```
+
+#### Sample 7b
+
+```{r}
+#| warning: false
+
+display(compare_mods(data7b))
+
+```
+
+#### Sample 7c
+
+```{r}
+#| warning: false
+
+display(compare_mods(data7c))
+
+```
+
+#### Sample 8a
+
+```{r}
+#| warning: false
+
+display(compare_mods(data8a))
+```
+
+#### Sample 8b
+
+```{r}
+#| warning: false
+
+display(compare_mods(data8b))
+```
+
+#### Sample 9
+
+```{r}
+#| warning: false
+
+display(compare_mods(data9))
+
+```
+
+#### Sample 10a
+
+```{r}
+#| warning: false
+
+display(compare_mods(data10a))
+
+```
+
+#### Sample 10b
+
+```{r}
+#| warning: false
+
+display(compare_mods(data10b))
+
+```
+
 :::
@@
 display(compare_mods_h(data1a))
+```
+
+#### Sample 1b
+
+```{r}
+display(compare_mods_h(data1b))
+```
+
+#### Sample 2
+
+```{r}
+display(compare_mods_h(data2))
+```
+
+#### Sample 3
+
+```{r}
+display(compare_mods_h(data3))
+```
+
+#### Sample 4
+
+```{r}
+display(compare_mods_h(data4))
+```
+
+#### Sample 5
+
+```{r}
+display(compare_mods_h(data5))
+```
+
+#### Sample 6
+
+```{r}
+display(compare_mods_h(data6))
+```
+
+#### Sample 7a
+
+```{r}
+display(compare_mods_h(data7a))
+```
+
+#### Sample 7b
+
+```{r}
+display(compare_mods_h(data7b))
+```
+
+#### Sample 7c
+
+```{r}
+display(compare_mods_h(data7c))
+```
+
+#### Sample 8a
+
+```{r}
+display(compare_mods_h(data8a))
+```
+
+#### Sample 8b
+
+```{r}
+display(compare_mods_h(data8b))
+```
+
+#### Sample 9
+
+```{r}
+display(compare_mods_h(data9))
+```
+
+#### Sample 10a
+
+```{r}
+display(compare_mods_h(data10a))
+```
+
+#### Sample 10b
+
+```{r}
+display(compare_mods_h(data10b))
 ```

### 2024-03-18 analysis/study1.qmd
Removed repeated sample
Updated participant's section
Did not add the link to Makowski's sample 10 data

@@
 - **Sample 1b**: Data from [Murphy's (2020)](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) study 6, downloaded from OSF, included `r report::report_participants(df1b, age = "Age", sex = NA, gender = "Gender")`.
-- **TODO: ADD INFO**
+- **Sample 2**: Data from [Gaggero's(2020)](https://osf.io/5x9sg/) study, downloaded from OSF, included `r report::report_participants(df2, age = "Age", sex = NA, gender = "Gender")`.
+- **Sample 3**: Data from [Campos's(2022)](https://osf.io/j6ef3) study, downloaded from OSF, included `r report::report_participants(df3, age = "Age", sex = NA, gender = "Gender")`.
+- **Sample 4**: Data from [Todd's(2022)]( https://osf.io/ms354/) study, downloaded from OSF, included `r report::report_participants(df4, age = "Age", sex = NA, gender = "Gender")`.
+- **Sample 5**: Data from [Arslanova (2022)](https://osf.io/mp3cy/) study, downloaded from OSF, included `r report::report_participants(df5, age = "Age", sex = NA, gender = "Gender")`.
+- **Sample 6**: Data from [Brand's(2022)](https://osf.io/xwz6g/) study, downloaded from OSF, included `r report::report_participants(df6, age = "Age", sex = NA, gender = "Gender")`.
+- **Sample 7a**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7a, age = "Age", sex = NA, gender = "Gender")`.
+- **Sample 7b**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7b, age = "Age", sex = NA, gender = "Gender")`.
+- **Sample 7c**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7c, age = "Age", sex = NA, gender = "Gender")`.
+- **Sample 8a**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8a, age = "Age", sex = NA, gender = "Gender")`.
+- **Sample 8b**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8a, age = "Age", sex = NA, gender = "Gender")`.
+- **Sample 9**: Data from [VonMohr's(2023)](https://osf.io/7p9u5/) study 3, downloaded from OSF, included `r report::report_participants(df9, age = "Age", sex = NA, gender = "Gender")`.
+- **Sample 10a**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10a, age = "Age", sex = NA, gender = "Gender")`.
+- **Sample 10b**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10b, age = "Age", sex = NA, gender = "Gender")`.
 
@@
 efa4 <- parameters::factor_analysis(data4, n = 4, rotation = "oblimin", sort = TRUE)
-plot(efa4)
-
-display(efa4)
-```
-
-#### Sample 5
-
-```{r}
-#| fig-height: 10
-
-efa4 <- parameters::factor_analysis(data5, n = 4, rotation = "oblimin", sort = TRUE)
 plot(efa4)

### 2024-04-05 analysis/study1.qmd
fixed df 8 mistake

@@
 - **Sample 8a**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8a, age = "Age", sex = NA, gender = "Gender")`.
-- **Sample 8b**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8a, age = "Age", sex = NA, gender = "Gender")`.
+- **Sample 8b**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8b, age = "Age", sex = NA, gender = "Gender")`.
 - **Sample 9**: Data from [VonMohr's(2023)](https://osf.io/7p9u5/) study 3, downloaded from OSF, included `r report::report_participants(df9, age = "Age", sex = NA, gender = "Gender")`.

### 2024-05-31 analysis/study1.qmd
Update study1.qmd

@@
 - **Sample 1b**: Data from [Murphy's (2020)](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) study 6, downloaded from OSF, included `r report::report_participants(df1b, age = "Age", sex = NA, gender = "Gender")`.
-- **Sample 2**: Data from [Gaggero's(2020)](https://osf.io/5x9sg/) study, downloaded from OSF, included `r report::report_participants(df2, age = "Age", sex = NA, gender = "Gender")`.
+- **Sample 2**: Data from [Gaggero's(2020)](https://osf.io/5x9sg/) study, downloaded from OSF, included `r report::report_participants(df2[c("Age", "Gender")], age = "Age", sex = NA, gender = "Gender")`.
 - **Sample 3**: Data from [Campos's(2022)](https://osf.io/j6ef3) study, downloaded from OSF, included `r report::report_participants(df3, age = "Age", sex = NA, gender = "Gender")`.

### 2024-06-04 analysis/study1_a.qmd
Study1_a
The version that renders on my laptop.

--- 2024-05-31 analysis/study1.qmd
@@
 ---
-
 ```{r}
@@
   mutate(Gender = as.character(gender)) |> 
+  mutate(across(starts_with("IAS "), as.numeric)) |>
   rename(
@@
 ```
-
-<!-- ##### Sample 10 -->
-
-<!-- Bowling (2024) - https://osf.io/tx8h9/ -->
-
-<!-- ```{r} -->
-<!-- df10 <- haven::read_sav("../data/Bowling2024/TouchAttitudesData.sav") |> -->
-<!--   mutate_all(as.numeric) |> -->
-<!--   mutate(Gender = as.character(ifelse(Gender_coded == 1, "Male", ifelse(Gender_coded == 2, "Female", "Other")))) |> -->
-<!--   rename( -->
-<!--     Heart = IAS1, Hungry = IAS2, Breathing = IAS3, Thirsty = IAS4, -->
-<!--     Urinate = IAS5, Defecate = IAS6, Taste = IAS7, Vomit = IAS8, Sneeze = IAS9, -->
-<!--     Cough = IAS10, Temp = IAS11, Sex_arousal = IAS12, Wind = IAS13, Burp = IAS14, -->
-<!--     Muscles = IAS15, Bruise = IAS16, Pain = IAS17, Blood_Sugar = IAS18, -->
-<!--     Affective_touch = IAS19, Tickle = IAS20, Itch = IAS21 -->
-<!--   )  -->
-
-<!-- ``` -->
 
@@
 :::
-
 ## Graph Analysis

### 2024-06-07 paper/1_Initial/manuscript.qmd
put paper in paper folder

@@
 ---
-title: "The Revised Interoceptive Accuracy Scale (IAS-R) Confirms Links between Interoception and Mental Health"
-blank-lines-above-title: 2  # Lines above title in .docx format
-shorttitle: "Revised Interoceptive Accuracy Scale (IAS-R)"
+title: "Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates"
+shorttitle: "IAS Factor structure and correlates"
 author:
-  - name: Dominique Makowski
+  - name: Magda Pfaff
     corresponding: true
-    orcid: "0000-0001-5375-9967"
-    email: D.Makowski@sussex.ac.uk
-    url: https://realitybending.github.io/
-    # Roles are optional (note: The two writing roles have en dashes, not hyphens. You can use their aliases, w)
-    # Select from the CRediT: Contributor Roles Taxonomy https://credit.niso.org/
-    # Conceptualization, Data curation, Formal Analysis, Funding acquisition, Investigation, 
-    # Methodology, Project administration, Resources, Software, Supervision, Validation, 
-    # Visualization, Writing – original draft, Writing – review & editing
-    roles:
-      - conceptualization: lead
-      - Writing - original draft
+    orcid: 0009-0006-2386-7936
+    # roles: 
+      # - Project administration
+      # - Data curation
+      # - Formal Analysis
+      # - Investigation
+      # - Visualization
+      # - Writing – original draft
+      # - Writing – review & editing
     affiliations:
@@
         name: "University of Sussex"
-        group: Reality Bending Lab
         department: School of Psychology
-        city: Brighton
-        region: UK
-        postal-code: "BN1 9RH"
-  - name: X. Y
+        # address: 1234 Capital St.
+        # city: New York
+        # region: NY
+        # country: USA
+        # postal-code: 12084-1234
+# author-note:
+#   status-changes: 
+#     affiliation-change: ~
+#     deceased: ~
+#   disclosures:
+#     study-registration: ~
+#     data-sharing: ~
+#     related-report: ~
+#     conflict-of-interest: ~
+#     financial-support: ~
+#     gratitude: ~
+#     authorship-agreements: ~
+  - name: Ana Neves
+    orcid: 0009-0006-0020-7599
     # roles:
-    #   - Project administration
-    #   - Formal Analysis
+    #   # - Project administration
+    #   # - Data curation
+    #   # - Formal Analysis
+    #   # - Investigation
+    #   # - Visualization
+    #   # - Writing – original draft
+    #   # - Writing – review & editing
     affiliations:
       - ref: id1 
-  - name: Annabel Chen
-    orcid: "0000-0002-1540-5516"
+  - name: Dominique Makowski
+    corresponding: true
+    orcid: 0000-0001-5375-9967
+    email: D.Makowski@sussex.ac.uk
+    url: https://realitybending.github.io/
+    # Roles are optional. 
+    # Select from the CRediT: Contributor Roles Taxonomy https://credit.niso.org/
+    # conceptualization, data curation, formal Analysis, funding acquisition, investigation, 
+    # methodology, project administration, resources, software, supervision, validation, 
+    # visualization, writing, editing
     # roles:
+    #   - Conceptualization
+    #   - Data curation
+    #   - formal Analysis
+    #   - Funding acquisition
+    #   - Investigation
+    #   - Methodology
+    #   - Project administration
     #   - Resources
-    #   - Project administration
+    #   - Software
+    #   - Supervision
+    #   - Validation
+    #   - Visualization
+    #   - Writing – original draft
+    #   - Writing – review & editing
     affiliations:
-      - name: "School of Social Sciences, Nanyang Technological University, Singapore"
-author-note:
-  blank-lines-above-author-note: 1
-abstract: "This document is a template demonstrating the apaquarto format."
-keywords: [Interoception, Accuracy, Scale, Questionnaire, Personality, Psychopathology, Validation]
+      - ref: id1 
+# Put as many keywords at you like, separated by commmas (e.g., [reliability, validity, generalizability])
+keywords: []
+# If true, tables and figures are mingled with the text instead of listed at the end of the document.
 floatsintext: true
-bibliography: "bibliography.bib"
+# Numbered lines (.pdf and .docx only)
+numbered-lines: true
+# File with references
+bibliography: bibliography.bib
+# Suppress title page
+suppress-title-page: false
+# Masks references that appear in the masked-citations list
+mask: false
+# Language options. See https://quarto.org/docs/authoring/language.html
+lang: en
+language:
+  citation-last-author-separator: "and"
+  citation-masked-author: "Masked Citation"
+  citation-masked-date: "n.d."
+  citation-masked-title: "Masked Title"
+  title-block-author-note: "Author Note"
+  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
+  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
+  references-meta-analysis:
 format:
-  apaquarto-docx:
-    numbered-lines: true
+  apaquarto-docx: default
+  apaquarto-html: default
+  apaquarto-pdf:
+    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
+    documentmode: man
 ---
 
-```{r}
-#| label: setup
-#| include: false
-library(conflicted)
-library(tidyverse)
-```
+Interoception is referred to the process of sensing, interpreting and integrating information pertaining to internal organs, such as the heart, the lungs or the gut [@khalsa2018].
+While recent research emphasizes a key role of interoception in a variety of processes (e.g., emotion regulation, decision making) and of outcomes (physical and psychological well being), the field remains clouded by concerns pertaining to how interoception is assessed.
 
-intro
+Various measures of interoception have been developed, forming a combination of “objective” and “subjective” assessments (i.e., physiological tasks such as the heart beat counting or tracking vs.
+questionnaires and subjective scales involving a metacognitive reflection), “implicit” or “explicit” paradigms (i.e., directing participant’s awareness and attention to interoceptive processes), various interoceptive modalities (e.g., cardioception, respiroception, gastroception) and theoretical dimensions (e.g., sensitivity, awareness, or accuracy) (see figure 1).
+While there is no consensus as to which particular approach provides the most accurate and “pure” measure of interoception and interoceptive abilities (assuming it is a unidimensional construct), it is instead plausible that each measure has strengths and limitations, and a utility dependent on the context and goal at hand [@jahedi2014].
 
-# Methods
+For instance, while the use of self-reports questionnaires might seem at odds with the concept of interoception (appearing at first as a deeply embodied - almost non-cognitive - sensory function), recent redefinitions of interoception, emphasizing the role of high-level and metacognitive elaboration of interoceptive information, has provided the theoretical grounding to support the hypothesis that facets of interoception can be assessed with subjective measures [@murphy2019].
+It is important to note that subjective interoceptive measures yield different results depending on which aspect of interoception is investigated, such as interoceptive attention compared to interoceptive accuracy [@murphy2019].
+The present paper focuses on interoceptive accuracy.
+Moreover, the current subjective measures do not correlate well with the objective measures [@murphy2019] .
+Nonetheless, measuring interoception subjectively is highly useful, as it indicates the participants’ view of their own interoceptive abilities.
 
-blabla
+![Figure 1. Different ways in which interoception can be measured.](images/measuring_interoception.png)
+
+### Introducing the IAS
+
+A recently developed scale with a rapidly growing popularity is the Interoceptive Accuracy Scale [IAS; @murphy2019].
+The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological mechanism such as respiration (“I can always accurately perceive when I am breathing fast”), heart (e.g “I can always accurately perceive when my heart is beating fast”), skin (e.g “I can always accurately perceive when something is going to be ticklish”), arousal or bodily functions like coughing (e.g “I can always accurately perceive when I am going to cough”), urinating (e.g.
+“I can always accurately perceive when I need to urinate”), etc.
+Interestingly, the IAS states specific examples, rather than broad claims, which is different to other interoception questionnaires, such as the multidimensional assessment of interoceptive awareness [MAIA, @mehling2012].
+
+Since its original publication, several studies have investigated the structure and validity of the IAS.
+@murphy2019 indicated a two-factor solution, measuring direct interoceptive signals, such as cardioception, and secondly, rather indirect factors such as bruising, which cannot be perceived by interoceptive signals alone.
+While the fit of the two-factor solution is passable, the fit was not perfect and requires further examination.
+In contrast, other studies have found unidimensional one-factor structures to be the best fit for the IAS ([@lin2023; @campos2021; @brand2023].
+However, @lin2023 also elaborate that their correlation analysis showed five locally dependent pairs in three items with exceptionally high difficulty and low discrimination making them subjects for reduction, proposing a shortened version of the IAS (IAS-SF) with 12 items, while @campos2021 found that item “tickle” is representing a more specific, rather than a general factor, they argue that all items should be retained, given that items for the IAS are largely associated with interoceptive information.
+Interestingly, @brand2023 analyzed data of four different translations (all in German) of the IAS, some of which were more formal, but did not find any significant differences between the different versions.
+The IAS in the given studies were done in Chinese, Portuguese and in German, respectively.
+All mentioned recent studies indicate good psychometric measures with good test-retest reliability of the IAS.
+
+Several measures have been used to assess convergent validity for the the IAS, including alexithymia, or neuroticism, or other interoception scales, such as the MAIA, which have previously correlated and used to validate each other [@brand2023].
+Recent findings by @campos2021 suggest a significant positive correlation between the BPQ Body Awareness (BPQ-BA) and the IAS, which contradict @murphy2019 findings of the 2x2 factorial model of interoception, in which attention and accuracy are conceptualized as dissociable interoceptive dimensions.
+
+As recent findings report the IAS structure controversially, it becomes evident that further analysis into the structure of the IAS is needed.
+Additionally, the IAS could be developed further from a structural standpoint to be able to capture interoceptive accuracy and abilities accurately (e.g., Brand, et al., 2023).
+The present paper is divided into two parts.
+Firstly, it is trying to leverage existing datasets to do a meta-analysis contrasting the traditional structure analysis approach (CFA/SEM) with new approaches Exploratory Graph Analysis (EGA).
+Secondly, the present study provides an overview of the correlates of the IAS.
+
+## Study 1
+
+The goal of study 1 is to re-analyse the factor structure of the IAS, using multiple data sets (Brand, et al., 2023; Campos, et al., 2021; Lin, et al., 2023; Murphy, et al., 2020).
+Getting a factor structure from these samples will help understand the IAS and the results this survey provides further, so that results will be more interpretable.
+Furthermore, it gives the chance to critically examine the IAS.
+The re-analysis is done using distribution, correlation and graph analyses.
+
+# Method
+
+Data collection utilized Google Scholar’s cited-by feature, identifying 136 papers.
+To qualify for inclusion, papers needed to (1) provide accessible data, (2) employ the IAS as a measure, and (3) report individual IAS scores.
+A total of 15 samples were obtained.
+
+## Participants
+
+The analysed sample contains 31317 participants, of which xxx are females.
+
+**Table 1.** Samples demographics
+
+| Samples                  |          | Sample Size | Mean age | SD      | Range   | Female % | Available at           |
+|---------|---------|---------|---------|---------|---------|---------|---------|
+| Murphy et al., (2020)    |          |             |          |         |         |          |                        |
+|                          | Sample 1 | 451         | 25.8     | 8.4     | 18-69   | 69.4%    |                        |
+|                          | Sample 2 | 375         | 35.3     | 16.9    | 18-91   | 70.1%    | <https://osf.io/3m5nh> |
+| Gaggero et al., (2021)   |          | 814         | 24.9     | 5.3     | 18-58   | 60.3%    | <https://osf.io/5x9sg> |
+| Campos et al., (2022)    |          | 515         | 30.7     | 10.5    | 18-72   | 59.6%    | <https://osf.io/j6ef3> |
+| Todd et al., (2022)      |          | 802         | 36.58\*  | 12.41\* | 18-92\* | NA       | <https://osf.io/ms354> |
+| Arslanova et al., (2022) |          | 96          | 28.78    | 27.5    | 18-73   | 46.8%    | <https://osf.io/mp3cy> |
+| Brand et al., (2022)     |          | 619         | 43.9     | 14.5    | 18-78   | 78.7%    | <https://osf.io/xwz6g> |
+| Brand et al., (2023)     |          |             |          |         |         |          |                        |
+|                          | Sample 1 | 522         | 23.4     | 6.7     | 18-79   | 79.5%    |                        |
+|                          | Sample 2 | 1993        | 32.0     | 12.6    | 16-81   | 77.7%    | <https://osf.io/3f2h6> |
+|                          | Sample 3 | 802         | 27.3     | 9.3     | 18-72   | 68.9%    |                        |
+| Lin et al., (2023)       |          |             |          |         |         |          |                        |
+|                          | Sample 1 | 1166        | 32.5     | 8.4     | 16-60   | 57.0%    |                        |
+|                          | Sample 2 | 500         | 37.4     | 7.4     | 20-60   | 56.2%    | <https://osf.io/3eztd> |
+| VonMohr et al., (2023)   |          | 21843       | 56.5     | 14.4    | 18-93   | 73.2%    | <https://osf.io/7p9u5> |
+| Makowski et al., (2023a) |          | 485         | 30.1     | 10.1    | 18-73   | 50.3%    | To be published\*\*    |
+| Makowski et al., (2023b) |          | 251         | 37.5     | 13.2    | 17-76   | 53.0%    | To be published\*\*    |
+
+## Statistical Analysis
+
+To examine the factor structure of the IAS, a two-step approach was employed.
+First, Exploratory Graph Analysis (EGA), was used to estimate the dimensions via network estimation and community detection, alongside assessing the stability of dimensions and items using the bootstrapping techniques.
+The selection of EGA was motivated by its capability to handle complex, multidimensional data and provide robust dimension estimates.
+Subsequently, exploratory factor analysis (EFA) was employed followed by confirmatory factor analysis (CFA).
 
@@
 
-blabla
+Visualizing the distribution of the items for all samples suggests the presence of a consistent modal value (Fig.
+X).
+In other words,  participants are most likely to answer 4/5 (i.e., agree) on most items (but “affective touch”, “blood sugar”, and “bruise” that exhibit a different distributional pattern).
+Additionally, one can note the low density on extreme values (1 and 5), meaning that the bulk of answers **(87% TODO: get the actual statistic: what’s the proportion of non 1&5 answers for the likert scale samples)** varies between 3 values.
+The interindividual variability seems improved in the samples using an analogue scale, displaying a more continuous and progressive spread of answers.
+
+![**Figure 1.** Distribution of responses for all items across all datasets.](images/clipboard-1080495164.png){width="723"}
+
+### Correlations
+
+The correlation analysis revealed that the items overall have positive intercorrelation patterns with no clear structure emerging.
+This remains the same across all samples.
+However, there are possibly some higher-order groupings emerging for the 2 analog-scale samples.
+
+### EGA
+
+The unique variable analysis revealed that there are two redundant variables when taking all samples into account.
+Namely, “itch” and “tickle”, where “tickle” should be removed, and “itch” should remain in the questionnaire.
+There are several more items that are moderately to largely redundant, namely, “wind” and “burp”, and “urinate” and “defecate”.
+On top of that, “sneeze" and “cough”, “heart” and “breathing”, and “hungry” and “thirsty” seem to have small to moderate redundancy.
+These findings are rather consistent across the samples with minor differences, such as that when the questionnaire had an analog scale, there seems to be no redundant items.
+
+According to the network analysis, a 4-factor structure fits the questionnaire best across all data sets.
+This is rather consistent within the data sets, where some samples indicate 3-factor structure, and some a 5-factor structure would fit well too.
+The 4-factor structure model with the best fit entails the following items per group: 1) itch, tickle, bruise, blood sugar; 2) burp, wind, cough, sneeze, vomit; 3) affective touch, sexual arousal, muscles, temperature, pain, and taste; 4) Heart, breathing, hungry, thirsty, urinate, and defecate.
+
+Stability analysis, employing 500 bootstrap iterations, also favoured the 4-factor solution for its greater stability.
+Most items, except for 'affective touch,' demonstrated stability levels exceeding 0.70, indicating structural consistency and reliability [@christensen2021].
+These findings underscore the robustness of the identified 4-dimensional structure.
+
+When accounting for all samples, the factor analysis reveals that a 4-factor structure fits best.
+The exploratory factor analysis revealed that 4 latent factors (oblimin rotation) accounted for 41.67% of 5the total variance of the original data (MR1 = 14.64%, MR3 = 11.59%, MR4 = 7.30%).
+Confirmatory factor analysis showed that the time “tickle” can be discarded, as it was flagged as redundant in the samples consistently.
+Some of the factors were ambiguous, namely, temperature, vomit, effective touch, sexual arousal, as well as taste.
+There was no evidence for higher order factors.
 
@@
 
-blabla
+In this study, several datasets were analyzed for a meta analysis of the structure of the IAS.
+The findings reveal that a 4-factor model fits the IAS best.
+Additionally, the lowest level structure (pairs of items) seem to be the most robust, especially for samples using Likert scales (some higher-order groupings might emerge for the 2 analog-scale samples).
+There was no clear evidence for higher-order factors.
+
+These findings contrast with previous research, which all found that a 2-factor model, or a 1-factor model fits the data best [@murphy2019, @lin2023, @campos2021, @brand2023].
+While this analysis also revealed an okay fit for the 1-factor model, the 4-factor model revealed the best fit.
+The 4-factor structure reveals different ‘hubs’ of items that are related, not only in this structure analysis, but also in underlying mechanisms.
+The ‘wind-burp-cough-sneeze-vomit’ category, for example, only entails items that are linked to excretion through the mouth.
+The other categories are organized similarly.
+This organization  and structure is useful for further analysis, as the data can be analyzed and interpreted according to a grouping that is coherent in result, as well as underlying mechanisms.
+
+There are several items that show redundancy suggesting that adapting the IAS would be beneficial for validity.
+Based on the given results, we suggest removing the tickle, while keeping the itch item (stats).
+Other items with slight redundancy were Hungry and Thirsty, Urinate and Defecate, and Sneeze and Cough.
+
+Interestingly, @lin2023 also found that tickle and itch were redundant, excluding one of them but the reason being that the character for both words is the same in the Chinese language.
+On top of that, they came up with a shortened version of the IAS, excluding further items, resulting in a 12-item IAS, which aligns with our findings, suggesting that further items are ambiguous as to whether they should be removed.  In contrast, other findings also found itch and tickle to be redundant but did not suggest excluding items .
+
+The findings indicate a high proportion of answers at 4 (see Figure 1), especially when using a 5-step scale.
+The analogue scale shows a more dispersed distribution, with some answers indicating the highest 5/5, which was not the case in the 5-step scale.
+Therefore, we recommend using an analog scale for the IAS.
+
+Before this paper, the IAS has not yet been used or analyzed with an analog scale, rather than a five step scale.
+Therefore, this study provides a novel approach to improving the IAS in a simple manner.
+
+## Limitations and Future Directions
+
+There are several limitations to the IAS; There are some redundant items, the 5-point scale does not provide great variability, and the structure could be improved.
+Therefore, improving the IAS, or creating a new questionnaire investigating interoception could be useful to achieving reliable and accurate indication of interoceptive awareness.
+
+## Study 2
+
+Study 2 aims to investigate correlates of the IAS.
+Correlations of the IAS will be computed to assess the relationship between subjective interoceptive accuracy and other subjective measures of interoception, mood, psychopathology, personality, and beliefs.
+Investigating correlates will help validate the IAS, as well as other interoceptive measures in the future.
+The
+
+## Methods
+
+### Materials
+
+The questionnaires used for the IAS correlates are listed in Table 2 (**TODO: add the rest of the questionnaires, sample items and references**).
+
+**Table 2.** Questionnaires used for the IAS correlates analysis.
+
+| Questionnaire              | Number of Dimensions | Assessment                              | Number of Items | Scoring                | Example Item  |
+|-----------------|------------|-------------------|-------------|-------------|-------------|
+| **Interoceptive Related**  |                      |                                         |                 |                        |               |
+| MAIA-2                     | 8                    | Interoception                           | 37              | 6-point Likert scale   |               |
+| BPQ                        | 2                    | Body awareness and autonomic reactivity | 49              | 5-point Likert scale   |               |
+| TAS-20                     | 3                    | Alexithymia                             | 20              | 5-point Likert scale   |               |
+| BVAQ                       | 2                    | Alexithymia                             | 40              | 5-point Likert scale   |               |
+| **Mood**                   |                      |                                         |                 |                        |               |
+| BDI-II                     | 1                    | Severity of depressive symptoms         | 21              | 0-to-3-point values    |               |
+| PHQ-4                      | 2                    | Anxiety and depressive symptoms         | 4               | 5-point Likert scale   |               |
+| STAI-T                     | 1                    | Trait anxiety                           | 20              | 4-point Likert scale   |               |
+| GAD-2                      | 1                    | General Anxiety                         | 2               | 4-point Likert scale   |               |
+| **Personality**            |                      |                                         |                 |                        |               |
+| NEO-FFI                    | 1                    | Neuroticism                             | 12              | 5-point Likert scale   |               |
+| Mini IPIP6                 | 6                    | Personality                             | 24              | Analogue scales        |               |
+| BFI                        | 5                    | Personality                             | 44              | 5-point Likert scale   |               |
+| PID-5-SF                   | 5                    | Dysfunctional personality traits        | 25              | 4-point Likert scale   |               |
+| **Psychopathology**        |                      |                                         |                 |                        |               |
+| SPQ-BRU                    | 4                    | Schizotypy                              | 32              | 5-point Likert scale   |               |
+| MSI-BPD                    | 1                    | Borderline personality disorder         | 10              | Analogue scales        |               |
+| ASQ - Short                | 5                    | Autistic Traits                         | 28              | 4-point Likert scale   |               |
+| **Beliefs and Misbeliefs** |                      |                                         |                 |                        |               |
+| GCB                        | 5                    | Conspiracy beliefs                      | 15              | 5-point Likert scale   |               |
+| PI-18                      | 1                    | Beliefs about the world                 | 99              | 6-point Likert scale   |               |
+| LIE scale                  | 4                    | Lying tendencies                        | 16              | Visual analogue scales |               |
+
+*Note.* MAIA-2 Multidimensional Assessment of Interoceptive Awareness Version-2; BPQ Body Perception Questionnaire (Mehling et al.
+2018); TAS-20 Toronto Alexithymia Scale (Bagby et al., 1994); BVAQ Bermond-Vorst Alexithymia Questionnaire (Vorst & Bermond, 2001); BDI-II Beck’s Depression Inventory (Dozois et al., 1998); PHQ-4 Patient Health Questionnaire (Kroenke et al., 2009); STAI-T State-Trait-Anxiety Inventory Trait-Version (Spielberger et al.
+1970); GAD- 2 Generalized Anxiety Disorder Scale – 2 (Spitzer et al., 2007); NEO-FFI NEO Five-Factor Inventory Neuroticism (Costa & McCrae, 2008); Mini IPIP6 Mini International Personality Item Pool (Sibley et al.
+2011); BFI Big Five Inventory (John et al., 2010); PID-5-SF Personality Inventory for DSM-5 Short Form (Thimm et al., 2016); SPQ-BRU Schizotypal Personality Questionnaire (Davidson et al., 2016); MSI-BPD Mclean Screening Instrument for Borderline Personality Disorder (Zanarini et al.
+2003); ASQ Short Autism-Spectrum Quotient (Hoekstra et al.
+2011); GCB Generic Conspiracist Beliefs scale (Brotherton et al.,  2013); PI-18 Primals Inventory (Clifton et al., 2021); LIE scale Lying Profile Questionnaire (Makowski, et al,.
+2023).
+
+### Statistical analysis
+
+Correlations will be computed using the correlation package under a Bayesian framework (ref).
+
+## Results
+
+The EGA components capture groupings of pairs of items, such as “wind” and “burp”, “cough” and “sneeze”, or “muscle” and “pain”.
+These groupings were used in the correlational analysis, to observe how much each group/pair correlates with other factors, such as Alexithymia, or the MAIA (see Figure 2).
+
+Alexithymia is negatively correlated with all interoceptive groups.
+Autistic traits are mostly negatively correlated with IAS measure, except for patterns and numbers (as an autistic trait), which is significantly and positively correlated with the “itch/bruise” pairing.
+The BPQ Body Awareness part is positively correlated with all IAS pairs, whereas the Autonomic Reactivity part is negatively correlated with all IAS groupings.
+Conspiracy Beliefs were all positively correlated with the IAS pairs, however, only Global Conspiracy with “hungry/thirsty”, “urinate/defecate” and “cough/sneeze”, as well as personal wellbeing with “hungry/thirsty”, and Information Control with “cough/sneeze” were significantly positively correlated.
+Demographic data is also mostly positively correlated with the IAS findings, where gender and age more strongly correlated with “hungry/thirsty”.
+In this analysis, lying profile is not strongly correlated with the IAS; Except for contextuality, which shows a significant negative correlation with “itch/bruise”.
+The MAIA has a strong positive correlation with most IAS pairings, except for the “not worrying” and “not distracting” items of the MAIA, which show less strong, or even negative correlations with all IAS item pairings.
+Maladaptiveness had mostly negative correlations with the IAS, with only a few significant correlations, namely “psychoticism”, “negative affect”, and “detachment” with “muscle/pain” and “hungry/thirsty”, as well as “negative affect” with “wind/burp”.
+Overall, mood was mostly negatively correlated with the IAS, where “hungry/thirsty” had the strongest negative correlation of all mood measures.
+Except for “neuroticism” and “honesty-humility”, personality traits, such as “openness” and “extraversion” were positively correlated with the IAS groupings.
+Shizotypic traits were mostly negatively correlated with the IAS, with “hungry/thirsty” showing the strongest negative correlation between schizotypic and the IAS.
+World beliefs were mostly positively correlated with the IAS, however, only a few were significant: “hierarchical”, “enticing”, and “alive” correlates significantly with “muscle/pain”; “Understandable” has a significant positive correlation with “heart/breathing”; And  “hierarchical” and “alive” has a significant positive correlation with “hungry/thirsty”.
+
+![**Figure 2.** Correlates of the IAS](images/clipboard-1619164537.png){width="911"}
+
+## Discussion
+
+Our findings confirmed that interception lies within an intricate network of correlates.
+ Alexithyma has the most negative correlation with the IAS, whereas, the MAIA questionnaire is most strongly positively correlated with the IAS.
+The correlates cannot only explain attributes of interoception, but can also be used to validate measures for interoception.
+
+While these results reveal correlations of different categories with the IAS, the findings are limited to the given questionnaire.
+However, they give a good indication of how interoception in general might be linked to the different categories, leading to interesting findings.
+The results show a consistent pattern of correlations with other interoception measures, psychopathology, and highlighting of interesting exploratory results, such as how primal world beliefs correlate with the IAS.
+
+The analysis revealed a negative correlation between alexithymia and scores in the IAS, which is in line with previous research [@herbert2011].
+A negative correlation between autism and interoceptive awareness, which has been found in this sample, has also been found in previous research [@dubois2016].
+Conspiracy Beliefs and IAS scores were not strongly correlated.
+However, there was a slight positive correlation.
+To the best of our knowledge, this interaction has not been investigated before.
+However, research shows correlations between (political) beliefs and interoception, which could underlie the same mechanism \[@ruisch2022\].
+Lying profile was also not strongly correlated with the IAS.
+Previous research provides some evidence for a relationshipbetween interoception and lying profile [@makowski2023a], indicating a contrast from the literature to the results at hand.
+The analysis showed that mood and the IAS scores have a strong negative correlation, which has been investigated in previous studies, finding a correlation between the two variables as well [@solanolópez2018].
+The analysis showed that personality is also correlated with interoceptive accuracy scores as retrieved by the IAS.
+While there are many aspects of personality, put simply, personality and interoception have been found to correlate in previous studies as well [@erle2021].
+Our findings show some negative correlations between schizotypy and interoception.
+Previous research has investigated this relationship and, similarly, found a negative correlation between interoceptive awareness and schizotypy, particularly at the onset of psychosis [@torregrossa2022].
+Lastly, World Beliefs and Interoception showed some significant positive correlations.
+World Beliefs have not been linked with interoception previously.
+As mentioned, other beliefs, such as political beliefs have been mentioned to interoception, where significant correlations were observed [@ruisch2022a].
+Further research is needed to understand this mechanism and validate whether world beliefs, which lay the framework through which we see the world [@clifton2020], is needed.
+
+The above findings show how interoception is correlated with many lifestyle and health factors, and is therefore an important concept to study.
+Here we showed many correlates of the IAS and lifestyle, as well as health factors.
+This is not only valuable to understand interception, and the role it plays in our lives, better, but also crucial to further validate the Ias, as well as other interoception measures.
+This analysis therefore lays the groundwork for validating new interoceptive measures and questionnaires needed to grasp interoception and its role in our life.
+
+## General Discussion
+
+The analyses revealed that the IAS has 4-factor structure, and a rather uneven distribution.
+The findings indicate that the IAS is measuring interoception in an acceptable manner, but there is also room for improvement.
+Furthermore, the results reveal different correlation measures with the IAS, giving space to further explore whether and how measures correlate with interoception/the IAS.
+In the following section, the IAS is discussed further to reveal shortcomings and strengths of the questionnaire.
+Finally, future steps will be revealed to improve the way in which we measure interoception.
+
+Overall, the IAS is straightforward with its sensation-centered items.
+There are several points of improvement to the IAS, which this work suggests.
+Firstly, removing redundant items, such as the itch item as shown in the above analysis.
+Previous work has also shown that the itch and tickle items are subject to redundancy [@lin2023, @campos2021] has shown.
+Interestingly, @campos2021 suggest removin the tickle item instead.
+@lin2023 on the other hand removed the itch item, because the sign for itch and tickle is the same.  Furthermore,  this work recommends using analog scales, instead of 5 point scales.
+In a 5-point scale, the variability is clearly limited with most people choosing ⅘.
+As visible in Figure X, the variability increases significantly, using an analog scale.
+However, it is important to note that even with an analog scale, the variability of the IAS is still limited.
+The more variability a scale shows, the more results can depict individual differences between participants.
+Therefore, good dispersion is essential for achieving relevant and usable results, and striving for more variability would be beneficial to this interoception scale, too.
+
+In this work, it becomes apparent that even with the mentioned improvements to the scale, there are limitations to the IAS, which reduce the accuracy of this scale.
+Those limitations include that there are few items for some modalities, such as only one item for heart perception.
+Having more modality is useful as each grouping can have more variability with increased modality, leading to more nuanced results.
+On top of that, there is no clear and theoretical, or empirical structure, as there is a very small grouping of items.
+Ideally, a scale would allow for an analysis showing different groupings so that different categories can be created based on which the data can be analyzed.
+The groupings in this analysis reveal that the IAS can only be grouped with two items per group, leading to low scores and variability in each group.
+On top of that, there are ambiguous items in the IAS, of which the grouping depends on the context.
+For example, one might indicate that they can perceive well how their heart is beating fast as well as vomiting, but both items can be linked to feeling anxious, and therefore might indicate different results than initially expected.
+Therefore, the grouping and structure of the IAS can be improved.
+
+Furthermore, all items are phrased positively, which might influence how participants answer the questions.
+While phrasing items in a positive manner can be beneficial, the benefits of positive phrasing might exacerbate a positive bias and thus lead to unidimensional results.
+Therefore, phrasing questions in a more diverse manner might lead to more accurate results and might thus be beneficial.
+
+Based on the given arguments, it becomes clear that there is a need for context-specific items, which are cross-modal when possible, such as integrating cardioception and respiroception.
+After establishing the clear need for a new scale to measure interoception, this study proposes the need for a new scale (Multimodal Interoceptive Sensitivity Scale, MISS) to adapt to the newest findings on the IAS and what we know about interoception to this day.
+The new scale will be able to be compared to the correlates of the IAS.
+
+## Conclusion
+
+The IAS is a good way of measuring interoception considering the current existing questionnaires and tools.
+However, revising, or even re-inventing a survey to measure interoception would lead to the best measure of interoception.
+Therefore, this study proposes that a new scale to measure interoception is needed to evolve the current research on interoception.
+This study revealed many correlates of the IAS, giving space for future analysis on what might be a good interoceptive measure, and therefore laying the groundwork for the creation of a new interoception survey.
 
@@
 
+<!-- References will auto-populate in the refs div below -->
+
 ::: {#refs}
 :::
+
+# Appendix
+
+# Title for Appendix

### 2024-06-07 analysis/study1.qmd
fix missing item
@AnafNeves it should work now - let me know if there are further issues

@@
 compare_mods <- function(data) {
-  m1 <- lavaan::cfa(m1, data = data)
-  m4 <- lavaan::cfa(m4, data = data)
-  m5 <- lavaan::cfa(m5, data = data)
-  m6 <- lavaan::cfa(m6, data = data)
-  m7 <- lavaan::cfa(m7, data = data)
-
-  anova(m1, m4, m5, m6, m7) |>
+
+  fit_model <- function(f, data) {
+    if(!"Cough" %in% names(data)) {
+      f <- str_remove(f, fixed("Cough +"))
+    }
+    lavaan::cfa(f, data = data)
+  }
+
+  cfa1 <- fit_model(m1, data = data)
+  cfa4 <- fit_model(m4, data = data)
+  cfa5 <- fit_model(m5, data = data)
+  cfa6 <- fit_model(m6, data = data)
+  cfa7 <- fit_model(m7, data = data)
+
+  anova(cfa1, cfa4, cfa5, cfa6, cfa7) |> 
     parameters::parameters() |>
@@
            Chi2 = format(round(Chi2, 2), nsmall = 2),
-           Converged = sapply(list(m1, m4, m5, m6, m7), is_converged))
+           Converged = sapply(list(cfa1, cfa4, cfa5, cfa6, cfa7), is_converged))
 }

### 2024-06-09 paper/1_Initial/manuscript.qmd
replace quotation symbols

@@
 author:
-  - name: Magda Pfaff
+  - name: Magdalena Pfaff
     corresponding: true
@@
 
+<!-- Interoception definition -->
 Interoception is referred to the process of sensing, interpreting and integrating information pertaining to internal organs, such as the heart, the lungs or the gut [@khalsa2018].
@@
 
-Various measures of interoception have been developed, forming a combination of “objective” and “subjective” assessments (i.e., physiological tasks such as the heart beat counting or tracking vs.
-questionnaires and subjective scales involving a metacognitive reflection), “implicit” or “explicit” paradigms (i.e., directing participant’s awareness and attention to interoceptive processes), various interoceptive modalities (e.g., cardioception, respiroception, gastroception) and theoretical dimensions (e.g., sensitivity, awareness, or accuracy) (see figure 1).
-While there is no consensus as to which particular approach provides the most accurate and “pure” measure of interoception and interoceptive abilities (assuming it is a unidimensional construct), it is instead plausible that each measure has strengths and limitations, and a utility dependent on the context and goal at hand [@jahedi2014].
+<!-- Interocetpion measure -->
+Various measures of interoception have been developed, forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking vs.
+questionnaires and subjective scales involving a metacognitive reflection), "implicit" or "explicit" paradigms (i.e., directing participant’s awareness and attention to interoceptive processes), various interoceptive modalities (e.g., cardioception, respiroception, gastroception) and theoretical dimensions (e.g., sensitivity, awareness, or accuracy) (see figure 1).
+While there is no consensus as to which particular approach provides the most accurate and "pure" measure of interoception and interoceptive abilities (assuming it is a unidimensional construct), it is instead plausible that each measure has strengths and limitations, and a utility dependent on the context and goal at hand [@jahedi2014].
 
@@
 A recently developed scale with a rapidly growing popularity is the Interoceptive Accuracy Scale [IAS; @murphy2019].
-The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological mechanism such as respiration (“I can always accurately perceive when I am breathing fast”), heart (e.g “I can always accurately perceive when my heart is beating fast”), skin (e.g “I can always accurately perceive when something is going to be ticklish”), arousal or bodily functions like coughing (e.g “I can always accurately perceive when I am going to cough”), urinating (e.g.
-“I can always accurately perceive when I need to urinate”), etc.
+The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological mechanism such as respiration ("I can always accurately perceive when I am breathing fast"), heart (e.g "I can always accurately perceive when my heart is beating fast"), skin (e.g "I can always accurately perceive when something is going to be ticklish"), arousal or bodily functions like coughing (e.g "I can always accurately perceive when I am going to cough"), urinating (e.g.
+"I can always accurately perceive when I need to urinate"), etc.
 Interestingly, the IAS states specific examples, rather than broad claims, which is different to other interoception questionnaires, such as the multidimensional assessment of interoceptive awareness [MAIA, @mehling2012].
@@
 In contrast, other studies have found unidimensional one-factor structures to be the best fit for the IAS ([@lin2023; @campos2021; @brand2023].
-However, @lin2023 also elaborate that their correlation analysis showed five locally dependent pairs in three items with exceptionally high difficulty and low discrimination making them subjects for reduction, proposing a shortened version of the IAS (IAS-SF) with 12 items, while @campos2021 found that item “tickle” is representing a more specific, rather than a general factor, they argue that all items should be retained, given that items for the IAS are largely associated with interoceptive information.
+However, @lin2023 also elaborate that their correlation analysis showed five locally dependent pairs in three items with exceptionally high difficulty and low discrimination making them subjects for reduction, proposing a shortened version of the IAS (IAS-SF) with 12 items, while @campos2021 found that item "tickle" is representing a more specific, rather than a general factor, they argue that all items should be retained, given that items for the IAS are largely associated with interoceptive information.
 Interestingly, @brand2023 analyzed data of four different translations (all in German) of the IAS, some of which were more formal, but did not find any significant differences between the different versions.
@@
 X).
-In other words,  participants are most likely to answer 4/5 (i.e., agree) on most items (but “affective touch”, “blood sugar”, and “bruise” that exhibit a different distributional pattern).
+In other words,  participants are most likely to answer 4/5 (i.e., agree) on most items (but "affective touch", "blood sugar", and "bruise" that exhibit a different distributional pattern).
 Additionally, one can note the low density on extreme values (1 and 5), meaning that the bulk of answers **(87% TODO: get the actual statistic: what’s the proportion of non 1&5 answers for the likert scale samples)** varies between 3 values.
@@
 The unique variable analysis revealed that there are two redundant variables when taking all samples into account.
-Namely, “itch” and “tickle”, where “tickle” should be removed, and “itch” should remain in the questionnaire.
-There are several more items that are moderately to largely redundant, namely, “wind” and “burp”, and “urinate” and “defecate”.
-On top of that, “sneeze" and “cough”, “heart” and “breathing”, and “hungry” and “thirsty” seem to have small to moderate redundancy.
+Namely, "itch" and "tickle", where "tickle" should be removed, and "itch" should remain in the questionnaire.
+There are several more items that are moderately to largely redundant, namely, "wind" and "burp", and "urinate" and "defecate".
+On top of that, "sneeze" and "cough", "heart" and "breathing", and "hungry" and "thirsty" seem to have small to moderate redundancy.
 These findings are rather consistent across the samples with minor differences, such as that when the questionnaire had an analog scale, there seems to be no redundant items.
@@
 The exploratory factor analysis revealed that 4 latent factors (oblimin rotation) accounted for 41.67% of 5the total variance of the original data (MR1 = 14.64%, MR3 = 11.59%, MR4 = 7.30%).
-Confirmatory factor analysis showed that the time “tickle” can be discarded, as it was flagged as redundant in the samples consistently.
+Confirmatory factor analysis showed that the time "tickle" can be discarded, as it was flagged as redundant in the samples consistently.
 Some of the factors were ambiguous, namely, temperature, vomit, effective touch, sexual arousal, as well as taste.
@@
 
-The EGA components capture groupings of pairs of items, such as “wind” and “burp”, “cough” and “sneeze”, or “muscle” and “pain”.
+The EGA components capture groupings of pairs of items, such as "wind" and "burp", "cough" and "sneeze", or "muscle" and "pain".
 These groupings were used in the correlational analysis, to observe how much each group/pair correlates with other factors, such as Alexithymia, or the MAIA (see Figure 2).
@@
 Alexithymia is negatively correlated with all interoceptive groups.
-Autistic traits are mostly negatively correlated with IAS measure, except for patterns and numbers (as an autistic trait), which is significantly and positively correlated with the “itch/bruise” pairing.
+Autistic traits are mostly negatively correlated with IAS measure, except for patterns and numbers (as an autistic trait), which is significantly and positively correlated with the "itch/bruise" pairing.
 The BPQ Body Awareness part is positively correlated with all IAS pairs, whereas the Autonomic Reactivity part is negatively correlated with all IAS groupings.
-Conspiracy Beliefs were all positively correlated with the IAS pairs, however, only Global Conspiracy with “hungry/thirsty”, “urinate/defecate” and “cough/sneeze”, as well as personal wellbeing with “hungry/thirsty”, and Information Control with “cough/sneeze” were significantly positively correlated.
-Demographic data is also mostly positively correlated with the IAS findings, where gender and age more strongly correlated with “hungry/thirsty”.
-In this analysis, lying profile is not strongly correlated with the IAS; Except for contextuality, which shows a significant negative correlation with “itch/bruise”.
-The MAIA has a strong positive correlation with most IAS pairings, except for the “not worrying” and “not distracting” items of the MAIA, which show less strong, or even negative correlations with all IAS item pairings.
-Maladaptiveness had mostly negative correlations with the IAS, with only a few significant correlations, namely “psychoticism”, “negative affect”, and “detachment” with “muscle/pain” and “hungry/thirsty”, as well as “negative affect” with “wind/burp”.
-Overall, mood was mostly negatively correlated with the IAS, where “hungry/thirsty” had the strongest negative correlation of all mood measures.
-Except for “neuroticism” and “honesty-humility”, personality traits, such as “openness” and “extraversion” were positively correlated with the IAS groupings.
-Shizotypic traits were mostly negatively correlated with the IAS, with “hungry/thirsty” showing the strongest negative correlation between schizotypic and the IAS.
-World beliefs were mostly positively correlated with the IAS, however, only a few were significant: “hierarchical”, “enticing”, and “alive” correlates significantly with “muscle/pain”; “Understandable” has a significant positive correlation with “heart/breathing”; And  “hierarchical” and “alive” has a significant positive correlation with “hungry/thirsty”.
+Conspiracy Beliefs were all positively correlated with the IAS pairs, however, only Global Conspiracy with "hungry/thirsty", "urinate/defecate" and "cough/sneeze", as well as personal wellbeing with "hungry/thirsty", and Information Control with "cough/sneeze" were significantly positively correlated.
+Demographic data is also mostly positively correlated with the IAS findings, where gender and age more strongly correlated with "hungry/thirsty".
+In this analysis, lying profile is not strongly correlated with the IAS; Except for contextuality, which shows a significant negative correlation with "itch/bruise".
+The MAIA has a strong positive correlation with most IAS pairings, except for the "not worrying" and "not distracting" items of the MAIA, which show less strong, or even negative correlations with all IAS item pairings.
+Maladaptiveness had mostly negative correlations with the IAS, with only a few significant correlations, namely "psychoticism", "negative affect", and "detachment" with "muscle/pain" and "hungry/thirsty", as well as "negative affect" with "wind/burp".
+Overall, mood was mostly negatively correlated with the IAS, where "hungry/thirsty" had the strongest negative correlation of all mood measures.
+Except for "neuroticism" and "honesty-humility", personality traits, such as "openness" and "extraversion" were positively correlated with the IAS groupings.
+Shizotypic traits were mostly negatively correlated with the IAS, with "hungry/thirsty" showing the strongest negative correlation between schizotypic and the IAS.
+World beliefs were mostly positively correlated with the IAS, however, only a few were significant: "hierarchical", "enticing", and "alive" correlates significantly with "muscle/pain"; "Understandable" has a significant positive correlation with "heart/breathing"; And  "hierarchical" and "alive" has a significant positive correlation with "hungry/thirsty".
 

### 2024-06-09 paper/1_Initial/manuscript.qmd
edits to intro

@@
 
-<!-- Interocetpion measure -->
-Various measures of interoception have been developed, forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking vs.
-questionnaires and subjective scales involving a metacognitive reflection), "implicit" or "explicit" paradigms (i.e., directing participant’s awareness and attention to interoceptive processes), various interoceptive modalities (e.g., cardioception, respiroception, gastroception) and theoretical dimensions (e.g., sensitivity, awareness, or accuracy) (see figure 1).
+<!-- Interoception measure -->
+Various measures of interoception have been developed (see **figure 1** [**TODO: add crossref**]), forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking vs.
+questionnaires and subjective scales involving a metacognitive reflection), "explicit" and "implicit" paradigms (i.e., directing participants' awareness and attention to interoceptive processes vs.
+measuring interoception unbeknownst to them), various interoceptive modalities (e.g., cardioception, respiroception, gastroception) and theoretical dimensions (e.g., sensitivity, awareness, accuracy).
 While there is no consensus as to which particular approach provides the most accurate and "pure" measure of interoception and interoceptive abilities (assuming it is a unidimensional construct), it is instead plausible that each measure has strengths and limitations, and a utility dependent on the context and goal at hand [@jahedi2014].
 
-For instance, while the use of self-reports questionnaires might seem at odds with the concept of interoception (appearing at first as a deeply embodied - almost non-cognitive - sensory function), recent redefinitions of interoception, emphasizing the role of high-level and metacognitive elaboration of interoceptive information, has provided the theoretical grounding to support the hypothesis that facets of interoception can be assessed with subjective measures [@murphy2019].
-It is important to note that subjective interoceptive measures yield different results depending on which aspect of interoception is investigated, such as interoceptive attention compared to interoceptive accuracy [@murphy2019].
-The present paper focuses on interoceptive accuracy.
-Moreover, the current subjective measures do not correlate well with the objective measures [@murphy2019] .
-Nonetheless, measuring interoception subjectively is highly useful, as it indicates the participants’ view of their own interoceptive abilities.
+<!-- self-reports -->
+For instance, while the use of self-reports questionnaires might seem at odds with the concept of interoception (appearing at first as a deeply embodied - almost non-cognitive - sensory function), recent redefinitions of interoception, emphasizing the role of high-level and metacognitive elaboration of interoceptive information, has provided the theoretical grounding to support the idea that some facets of interoception (including participants' metacognitive beliefs) can be assessed subjectively, providing useful and interesting measures [@murphy2019].
+However, understanding the exact nature of what is being measured with different questionnaires is crucial, as self-reports might not reflect the same processes as other measures, seemingly contributing to an apparent lack of convergence in the field.
 
-![Figure 1. Different ways in which interoception can be measured.](images/measuring_interoception.png)
+![Figure 1. Different ways in which interoception can be measured.](figures/measuring_interoception.png)
+<!-- TODO: replace with include_ _figure that allows for legend -->
 
-### Introducing the IAS
+<!-- Introducing the IAS -->
+A recently developed scale with a rapidly growing popularity is the Interoceptive Accuracy Scale [IAS; @murphy2019].
+The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological mechanism such as respiration (*"I can always accurately perceive when I am breathing fast"*), heart (e.g *"I can always accurately perceive when my heart is beating fast"*), skin (e.g *"I can always accurately perceive when something is going to be ticklish"*), arousal or bodily functions like coughing (e.g *"I can always accurately perceive when I am going to cough"*), urinating (e.g.
+*"I can always accurately perceive when I need to urinate"*).
+Interestingly, the IAS' statements are about specific interoceptive behaviours, which is notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012], which items are more general and metacognitive (e.g., **TODO: add representative examples**).
 
-A recently developed scale with a rapidly growing popularity is the Interoceptive Accuracy Scale [IAS; @murphy2019].
-The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological mechanism such as respiration ("I can always accurately perceive when I am breathing fast"), heart (e.g "I can always accurately perceive when my heart is beating fast"), skin (e.g "I can always accurately perceive when something is going to be ticklish"), arousal or bodily functions like coughing (e.g "I can always accurately perceive when I am going to cough"), urinating (e.g.
-"I can always accurately perceive when I need to urinate"), etc.
-Interestingly, the IAS states specific examples, rather than broad claims, which is different to other interoception questionnaires, such as the multidimensional assessment of interoceptive awareness [MAIA, @mehling2012].
-
+<!-- IAS structure  -->
 Since its original publication, several studies have investigated the structure and validity of the IAS.
 @murphy2019 indicated a two-factor solution, measuring direct interoceptive signals, such as cardioception, and secondly, rather indirect factors such as bruising, which cannot be perceived by interoceptive signals alone.
-While the fit of the two-factor solution is passable, the fit was not perfect and requires further examination.
+While the fit of the two-factor solution was passable, the fit was not perfect and requires further examination.
 In contrast, other studies have found unidimensional one-factor structures to be the best fit for the IAS ([@lin2023; @campos2021; @brand2023].
@@
 
+<!-- Convergent validity (correlates)  -->
 Several measures have been used to assess convergent validity for the the IAS, including alexithymia, or neuroticism, or other interoception scales, such as the MAIA, which have previously correlated and used to validate each other [@brand2023].
 Recent findings by @campos2021 suggest a significant positive correlation between the BPQ Body Awareness (BPQ-BA) and the IAS, which contradict @murphy2019 findings of the 2x2 factorial model of interoception, in which attention and accuracy are conceptualized as dissociable interoceptive dimensions.
+<!-- Moreover, the current subjective measures do not correlate well with the objective measures [@murphy2019]. -->
 
@@
 
-Data collection utilized Google Scholar’s cited-by feature, identifying 136 papers.
+Data collection utilized Google Scholar's cited-by feature, identifying 136 papers.
 To qualify for inclusion, papers needed to (1) provide accessible data, (2) employ the IAS as a measure, and (3) report individual IAS scores.
@@
 In other words,  participants are most likely to answer 4/5 (i.e., agree) on most items (but "affective touch", "blood sugar", and "bruise" that exhibit a different distributional pattern).
-Additionally, one can note the low density on extreme values (1 and 5), meaning that the bulk of answers **(87% TODO: get the actual statistic: what’s the proportion of non 1&5 answers for the likert scale samples)** varies between 3 values.
+Additionally, one can note the low density on extreme values (1 and 5), meaning that the bulk of answers **(87% TODO: get the actual statistic: what's the proportion of non 1&5 answers for the likert scale samples)** varies between 3 values.
 The interindividual variability seems improved in the samples using an analogue scale, displaying a more continuous and progressive spread of answers.
 
-![**Figure 1.** Distribution of responses for all items across all datasets.](images/clipboard-1080495164.png){width="723"}
+![**Figure 1.** Distribution of responses for all items across all datasets.](figures/clipboard-1080495164.png){width="723"}
 
@@
 While this analysis also revealed an okay fit for the 1-factor model, the 4-factor model revealed the best fit.
-The 4-factor structure reveals different ‘hubs’ of items that are related, not only in this structure analysis, but also in underlying mechanisms.
-The ‘wind-burp-cough-sneeze-vomit’ category, for example, only entails items that are linked to excretion through the mouth.
+The 4-factor structure reveals different ‘hubs' of items that are related, not only in this structure analysis, but also in underlying mechanisms.
+The ‘wind-burp-cough-sneeze-vomit' category, for example, only entails items that are linked to excretion through the mouth.
 The other categories are organized similarly.
@@
 *Note.* MAIA-2 Multidimensional Assessment of Interoceptive Awareness Version-2; BPQ Body Perception Questionnaire (Mehling et al.
-2018); TAS-20 Toronto Alexithymia Scale (Bagby et al., 1994); BVAQ Bermond-Vorst Alexithymia Questionnaire (Vorst & Bermond, 2001); BDI-II Beck’s Depression Inventory (Dozois et al., 1998); PHQ-4 Patient Health Questionnaire (Kroenke et al., 2009); STAI-T State-Trait-Anxiety Inventory Trait-Version (Spielberger et al.
+2018); TAS-20 Toronto Alexithymia Scale (Bagby et al., 1994); BVAQ Bermond-Vorst Alexithymia Questionnaire (Vorst & Bermond, 2001); BDI-II Beck's Depression Inventory (Dozois et al., 1998); PHQ-4 Patient Health Questionnaire (Kroenke et al., 2009); STAI-T State-Trait-Anxiety Inventory Trait-Version (Spielberger et al.
 1970); GAD- 2 Generalized Anxiety Disorder Scale – 2 (Spitzer et al., 2007); NEO-FFI NEO Five-Factor Inventory Neuroticism (Costa & McCrae, 2008); Mini IPIP6 Mini International Personality Item Pool (Sibley et al.
@@
 
-![**Figure 2.** Correlates of the IAS](images/clipboard-1619164537.png){width="911"}
+![**Figure 2.** Correlates of the IAS](figures/clipboard-1619164537.png){width="911"}
 

### 2024-06-09 analysis/Stud1_a.qmd
Study1_a qmd and html
The one that works on my laptop

--- 2024-06-07 analysis/study1.qmd
@@
 ---
+
 ```{r}
@@
 
-Murphy (https://osf.io/3m5nh)
+Murphy (<https://osf.io/3m5nh)>
 
@@
 
-Gaggero (2021) (https://osf.io/5x9sg)
+Gaggero (2021) (<https://osf.io/5x9sg)>
 
@@
 
-Campos (2022) - Study 1 (https://osf.io/j6ef3)
+Campos (2022) - Study 1 (<https://osf.io/j6ef3)>
 
@@
 
-Todd (2022) - https://osf.io/ms354/
+Todd (2022) - <https://osf.io/ms354/>
 
@@
 
-Arslanova (2022) - https://osf.io/mp3cy/
+Arslanova (2022) - <https://osf.io/mp3cy/>
 
@@
 
-Brand (2022) - https://osf.io/xwz6g/
+Brand (2022) - <https://osf.io/xwz6g/>
 
@@
 
-Brand (2023) - https://osf.io/3f2h6/
+Brand (2023) - <https://osf.io/3f2h6/>
 
@@
 
-Lin (2023) - https://osf.io/3eztd
-- Note: No tickle because same Chinese character
+Lin (2023) - <https://osf.io/3eztd> - Note: No tickle because same Chinese character
 
@@
 
-VonMohr (2023) - Study 3 (https://osf.io/7p9u5/)
+VonMohr (2023) - Study 3 (<https://osf.io/7p9u5/)>
 
@@
 :::
+
 ## Graph Analysis
@@
 compare_mods_h <- function(data) {
-  m7 <- lavaan::cfa(m7, data = data)
-  m7h2 <- lavaan::cfa(m7h2, data = data)
-  m7h1 <- lavaan::cfa(m7h1, data = data)
-  m7h3 <- lavaan::cfa(m7h3, data = data)
+
+  fit_model_h <- function(f, data) {
+    if(!"Cough" %in% names(data)) {
+      f <- str_remove(f, fixed("Cough +"))
+    }
+    lavaan::cfa(f, data = data)
+  }
+
+  m7 <- fit_model_h(m7, data = data)
+  m7h2 <- fit_model_h(m7h2, data = data)
+  m7h1 <- fit_model_h(m7h1, data = data)
+  m7h3 <- fit_model_h(m7h3, data = data)
 

### 2024-06-09 paper/1_Initial/manuscript.qmd
break lines for every sentence
@AnafNeves it is useful to break lines between sentences to help the git change tracker (otherwise when you make a change it highlights the whole paragraph)
Update manuscript.qmd

@@
 <!-- IAS structure  -->
-Since its original publication, several studies have investigated the structure and validity of the IAS.
-@murphy2019 indicated a two-factor solution, measuring direct interoceptive signals, such as cardioception, and secondly, rather indirect factors such as bruising, which cannot be perceived by interoceptive signals alone.
-While the fit of the two-factor solution was passable, the fit was not perfect and requires further examination.
-In contrast, other studies have found unidimensional one-factor structures to be the best fit for the IAS ([@lin2023; @campos2021; @brand2023].
-However, @lin2023 also elaborate that their correlation analysis showed five locally dependent pairs in three items with exceptionally high difficulty and low discrimination making them subjects for reduction, proposing a shortened version of the IAS (IAS-SF) with 12 items, while @campos2021 found that item "tickle" is representing a more specific, rather than a general factor, they argue that all items should be retained, given that items for the IAS are largely associated with interoceptive information.
-Interestingly, @brand2023 analyzed data of four different translations (all in German) of the IAS, some of which were more formal, but did not find any significant differences between the different versions.
-The IAS in the given studies were done in Chinese, Portuguese and in German, respectively.
-All mentioned recent studies indicate good psychometric measures with good test-retest reliability of the IAS.
+The original validation study suggested a two-factor solution structure, the authors decided...
+**what?**, and underline the need for further investigation of the scale's factor structure [@murphy2019, *p.
+XX*].
+Most follow-up studies, using a confirmatory factor analysis approach (CFA) **(is that correct?)**, report unidimensional structures to be the best fit [@lin2023; @campos2021; @brand2023], although with some discussions about specific items.
+For instance, @murphy2019 does mention that some items might be measuring direct interoceptive signals such as cardioception, while others, for instance "bruising", might capture phenomena that cannot be perceived through interoceptive signals alone (**Can you double check that this paper said this**).
+@lin2023 also highlights their correlation analysis showing five locally dependent pairs in three items with exceptionally high difficulty and low discrimination, and @campos2021 suggests that the "tickle" item is representing a more specific factor.
+Recently, **@blabla** used a new approach, namely Exploratory Graph Analysis (EGA), and found that **TODO**.
 

### 2024-06-09 paper/1_Initial/manuscript.qmd
Update manuscript.qmd

@@
 ![Figure 1. Different ways in which interoception can be measured.](figures/measuring_interoception.png)
-<!-- TODO: replace with include_ _figure that allows for legend -->
+<!-- TODO: replace with a code chunk that allows for legend -->
 
@@
 <!-- Convergent validity (correlates)  -->
-Several measures have been used to assess convergent validity for the the IAS, including alexithymia, or neuroticism, or other interoception scales, such as the MAIA, which have previously correlated and used to validate each other [@brand2023].
-Recent findings by @campos2021 suggest a significant positive correlation between the BPQ Body Awareness (BPQ-BA) and the IAS, which contradict @murphy2019 findings of the 2x2 factorial model of interoception, in which attention and accuracy are conceptualized as dissociable interoceptive dimensions.
+While the assessment of the validity of an interoception scale can be conceived as theoretically challenging, several traits have been used to assess convergent validity for the the IAS, including expected negative associations with alexithymia [@REF], and positive with neuroticism [@ref].
+**anything else?**.
+The IAS has also been compared to other interoception scales, yielding a positive correlation with most facets of the MAIA, with the notable exception of **TODO** [@brand2023], and the **TODO** dimension of the Body Perception Questionnaire [BPQ; @campos2021].
 <!-- Moreover, the current subjective measures do not correlate well with the objective measures [@murphy2019]. -->
 
-As recent findings report the IAS structure controversially, it becomes evident that further analysis into the structure of the IAS is needed.
-Additionally, the IAS could be developed further from a structural standpoint to be able to capture interoceptive accuracy and abilities accurately (e.g., Brand, et al., 2023).
-The present paper is divided into two parts.
-Firstly, it is trying to leverage existing datasets to do a meta-analysis contrasting the traditional structure analysis approach (CFA/SEM) with new approaches Exploratory Graph Analysis (EGA).
-Secondly, the present study provides an overview of the correlates of the IAS.
+The current study aims at 1) clarifying the structure of the IAS with a meta-analytic approach that leverages existing data and contrasts the traditional CFA/SEM factor-based analyses with graph-based ones such as EGA.
+2) The second part will provide an overview of the dispositional correlates of the IAS, sketching a pattern of associations that is key to better understand the nature, place and role of interoception questionnaires within a larger context.
 

### 2024-06-09 paper/1_Initial/manuscript.qmd
Update manuscript.qmd

@@
 
-The goal of study 1 is to re-analyse the factor structure of the IAS, using multiple data sets (Brand, et al., 2023; Campos, et al., 2021; Lin, et al., 2023; Murphy, et al., 2020).
-Getting a factor structure from these samples will help understand the IAS and the results this survey provides further, so that results will be more interpretable.
-Furthermore, it gives the chance to critically examine the IAS.
-The re-analysis is done using distribution, correlation and graph analyses.
+The goal of study 1 is to re-analyse and assess the factor structure of the IAS by taking advantage of the large number of open-access datasets **(Brand, et al., 2023; Campos, et al., 2021; Lin, et al., 2023; Murphy, et al., 2020)** **[REDO REFS]**.
+While combining these studies might provide a more robust and generalizable understanding of the IAS' factor structure, it is important to note that the studies differ in their sample sizes, demographics, language, and the way they collected the data.
+Thus, providing additionally a individual analysis (i.e., on all samples individually) will help adding nuance to the general picture.
 
-# Method
+### Method
 
-Data collection utilized Google Scholar's cited-by feature, identifying 136 papers.
-To qualify for inclusion, papers needed to (1) provide accessible data, (2) employ the IAS as a measure, and (3) report individual IAS scores.
-A total of 15 samples were obtained.
+#### Datasets
 
-## Participants
-
-The analysed sample contains 31317 participants, of which xxx are females.
+Our search focused on studies citing the original IAS validation paper [@murphy2019], identifying 136 papers (as of **XX/XX/2024**). 
+To qualify for inclusion, papers needed to (1) provide accessible data in open-access, (2) employ the IAS as a measure, and (3) report individual IAS items scores. 
+A total of 9 studies was included. 
+Additionally, we added datasets of two unpublished (but already open-access) studies from our lab.
+**See Table 1 (add crossref link)** for a summary of the samples demographics.
 
@@
 | VonMohr et al., (2023)   |          | 21843       | 56.5     | 14.4    | 18-93   | 73.2%    | <https://osf.io/7p9u5> |
-| Makowski et al., (2023a) |          | 485         | 30.1     | 10.1    | 18-73   | 50.3%    | To be published\*\*    |
-| Makowski et al., (2023b) |          | 251         | 37.5     | 13.2    | 17-76   | 53.0%    | To be published\*\*    |
+| Makowski et al., (2023a) |          | 485         | 30.1     | 10.1    | 18-73   | 50.3%    | In preparation\*\*    |
+| Makowski et al., (2023b) |          | 251         | 37.5     | 13.2    | 17-76   | 53.0%    | In preparation\*\*    |
+
+**TODO: add row for Total N, average age etc.**
+**TODO: add language also, as well as maybe something like "difference" from the original validation (which could acctually be language, and for our the type of scale / less items)**
+**TODO: add links to GH for our studies**
+
+The analysed sample contains 31,317 participants, of which xxx are females.
 

### 2024-06-10 analysis/Stud1_a.qmd
Updated qmd and docx with total demographics

@@
 Total N = `r nrow(df1a) + nrow(df1b) + nrow(df2) + nrow(df3) + nrow(df4) + nrow(df5) + nrow(df6) + nrow(df7a) + nrow(df7b) + nrow(df7c) + nrow(df8a) + nrow(df8b) + nrow(df9) + nrow(df10a) + nrow(df10b)`.
+
+```{r}
+
+desc <- function(df){
+  summary <- df |> summarise(
+      n = n(),
+      mean = mean(Age, na.rm = TRUE),
+      sd = sd(Age, na.rm = TRUE),
+      min = min(Age, na.rm = TRUE),
+      max = max(Age, na.rm = TRUE),
+      female = sum(Gender == "Female", na.rm = TRUE)
+    )
+    return(summary)
+}
+
+desc_df1a <- desc(df1a)
+desc_df1b <- desc(df1b)
+desc_df2 <- desc(df2)
+desc_df3 <- desc(df3)
+#desc_df4 <- desc(df4)
+#desc_df5 <- desc(df5)
+desc_df6 <- desc(df6)
+desc_df7a <- desc(df7a)
+desc_df7b <- desc(df7b)
+desc_df7c <- desc(df7c)
+desc_df8a <- desc(df8a)
+desc_df8b <- desc(df8b)
+desc_df9 <- desc(df9)
+desc_df10a <- desc(df10a)
+desc_df10b <- desc(df10b)
+
+desc_total <- rbind(desc_df1a, desc_df1b, desc_df2, desc_df3, desc_df6, desc_df7a, desc_df7b, desc_df7c, desc_df8a, desc_df8b, desc_df9, desc_df10a, desc_df10b)
+
+## calculate weighted mean
+
+total_mean = sum(desc_total$mean * desc_total$n) / sum(desc_total$n)
+total_sd = sum(desc_total$sd * desc_total$n) / sum(desc_total$n)
+perce_female = sum(desc_total$female)/sum(desc_total$n) *100
+
+```
 
@@
 p1
+
 ```

### 2024-06-10 paper/1_Initial/manuscript.qmd
Updated qmd and docx with total demographics

@@
 
-| Samples                  |          | Sample Size | Mean age | SD      | Range   | Female % | Available at           |
-|---------|---------|---------|---------|---------|---------|---------|---------|
+| Samples                  |          | Language of Items|  Sample Size | Mean age | SD      | Range   | Female % | Available at           |
+|---------|---------|---------|---------|---------|---------|---------|---------|---------|
 | Murphy et al., (2020)    |          |             |          |         |         |          |                        |
-|                          | Sample 1 | 451         | 25.8     | 8.4     | 18-69   | 69.4%    |                        |
-|                          | Sample 2 | 375         | 35.3     | 16.9    | 18-91   | 70.1%    | <https://osf.io/3m5nh> |
-| Gaggero et al., (2021)   |          | 814         | 24.9     | 5.3     | 18-58   | 60.3%    | <https://osf.io/5x9sg> |
-| Campos et al., (2022)    |          | 515         | 30.7     | 10.5    | 18-72   | 59.6%    | <https://osf.io/j6ef3> |
-| Todd et al., (2022)      |          | 802         | 36.58\*  | 12.41\* | 18-92\* | NA       | <https://osf.io/ms354> |
-| Arslanova et al., (2022) |          | 96          | 28.78    | 27.5    | 18-73   | 46.8%    | <https://osf.io/mp3cy> |
-| Brand et al., (2022)     |          | 619         | 43.9     | 14.5    | 18-78   | 78.7%    | <https://osf.io/xwz6g> |
-| Brand et al., (2023)     |          |             |          |         |         |          |                        |
-|                          | Sample 1 | 522         | 23.4     | 6.7     | 18-79   | 79.5%    |                        |
-|                          | Sample 2 | 1993        | 32.0     | 12.6    | 16-81   | 77.7%    | <https://osf.io/3f2h6> |
-|                          | Sample 3 | 802         | 27.3     | 9.3     | 18-72   | 68.9%    |                        |
-| Lin et al., (2023)       |          |             |          |         |         |          |                        |
-|                          | Sample 1 | 1166        | 32.5     | 8.4     | 16-60   | 57.0%    |                        |
-|                          | Sample 2 | 500         | 37.4     | 7.4     | 20-60   | 56.2%    | <https://osf.io/3eztd> |
-| VonMohr et al., (2023)   |          | 21843       | 56.5     | 14.4    | 18-93   | 73.2%    | <https://osf.io/7p9u5> |
-| Makowski et al., (2023a) |          | 485         | 30.1     | 10.1    | 18-73   | 50.3%    | In preparation\*\*    |
-| Makowski et al., (2023b) |          | 251         | 37.5     | 13.2    | 17-76   | 53.0%    | In preparation\*\*    |
-
-**TODO: add row for Total N, average age etc.**
-**TODO: add language also, as well as maybe something like "difference" from the original validation (which could acctually be language, and for our the type of scale / less items)**
+|                          | Sample 1 | English     |451         | 25.8     | 8.4     | 18-69   | 69.4%    |                        |
+|                          | Sample 2 | English     | 375         | 35.3     | 16.9    | 18-91   | 70.1%    | <https://osf.io/3m5nh> |
+| Gaggero et al., (2021)   |          | English and Italian   | 814         | 24.9     | 5.3     | 18-58   | 60.3%    | <https://osf.io/5x9sg> |
+| Campos et al., (2022)    |          | Portuguese  | 515         | 30.7     | 10.5    | 18-72   | 59.6%    | <https://osf.io/j6ef3> |
+| Todd et al., (2022)      |          | English     | 802         | 36.58\*  | 12.41\* | 18-92\* | NA       | <https://osf.io/ms354> |
+| Arslanova et al., (2022) |          | English     | 96          | 28.78    | 27.5    | 18-73   | 46.8%    | <https://osf.io/mp3cy> |
+| Brand et al., (2022)     |          | German      | 619         | 43.9     | 14.5    | 18-78   | 78.7%    | <https://osf.io/xwz6g> |
+| Brand et al., (2023)     |          |             |             |          |         |         |          |                        |
+|                          | Sample 1 | German      | 522         | 23.4     | 6.7     | 18-79   | 79.5%    |                        |
+|                          | Sample 2 | German      |1993        | 32.0     | 12.6    | 16-81   | 77.7%    | <https://osf.io/3f2h6> |
+|                          | Sample 3 | German      | 802         | 27.3     | 9.3     | 18-72   | 68.9%    |                        |
+| Lin et al., (2023)       |          |             |             |          |         |         |          |                        |
+|                          | Sample 1 | Chinese     | 1166        | 32.5     | 8.4     | 16-60   | 57.0%    |                        |
+|                          | Sample 2 | Chinese     | 500         | 37.4     | 7.4     | 20-60   | 56.2%    | <https://osf.io/3eztd> |
+| VonMohr et al., (2023)   |          | English     | 21843       | 56.5     | 14.4    | 18-93   | 73.2%    | <https://osf.io/7p9u5> |
+| Makowski et al., (2023a) |          | English     | 485         | 30.1     | 10.1    | 18-73   | 50.3%    | In preparation \*\*    |
+| Makowski et al., (2023b) |          | English     |251         | 37.5     | 13.2    | 17-76   | 53.0%    | In preparation \*\*    |
+| Total                    |          |             |31317       | 49.5     | 13.2    | 17 - 93 | 71.5%    | |
+**Note**.
+\* Numbers were sourced from the original paper rather than independently calculated.
+\*\* Data for Makowski et al., 2023a: <https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv> and Makowski et al., 2013b: <https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv>
+<!-- **TODO: add row for Total N, average age etc.** -->
+**TODO: add language also, as well as maybe something like "difference" from the original validation (which could actually be language, and for our the type of scale / less items)**
 **TODO: add links to GH for our studies**
 
-The analysed sample contains 31,317 participants, of which xxx are females.
+The analysed sample contains 31,317 participants, of which 71.5% are females.
 

### 2024-06-10 paper/1_Initial/manuscript.qmd
updated docx and qmd

--- 2024-06-09 paper/1_Initial/manuscript.qmd
@@
 #   status-changes: 
-#     affiliation-change: ~
-#     deceased: ~
+#     affiliation-change: null
+#     deceased: null
 #   disclosures:
-#     study-registration: ~
-#     data-sharing: ~
-#     related-report: ~
-#     conflict-of-interest: ~
-#     financial-support: ~
-#     gratitude: ~
-#     authorship-agreements: ~
-  - name: Ana Neves
-    orcid: 0009-0006-0020-7599
-    # roles:
+#     study-registration: null
+#     data-sharing: null
+#     related-report: null
+#     conflict-of-interest: null
+#     financial-support: null
+#     gratitude: null
+#     authorship-agreements: null
     #   # - Project administration
@@
     #   # - Writing – review & editing
-    affiliations:
-      - ref: id1 
-  - name: Dominique Makowski
-    corresponding: true
-    orcid: 0000-0001-5375-9967
-    email: D.Makowski@sussex.ac.uk
-    url: https://realitybending.github.io/
     # Roles are optional. 
-    # Select from the CRediT: Contributor Roles Taxonomy https://credit.niso.org/
     # conceptualization, data curation, formal Analysis, funding acquisition, investigation, 
@@
     # visualization, writing, editing
-    # roles:
     #   - Conceptualization
@@
     #   - Writing – review & editing
+  - name: Ana Neves
+    orcid: 0009-0006-0020-7599
+    # roles:
     affiliations:
       - ref: id1 
-# Put as many keywords at you like, separated by commmas (e.g., [reliability, validity, generalizability])
+  - name: Dominique Makowski
+    corresponding: true
+    orcid: 0000-0001-5375-9967
+    email: D.Makowski@sussex.ac.uk
+    url: https://realitybending.github.io/
+    # Select from the CRediT: Contributor Roles Taxonomy https://credit.niso.org/
+    # roles:
+    affiliations:
+      - ref: id1 
 keywords: []
-# If true, tables and figures are mingled with the text instead of listed at the end of the document.
 floatsintext: true
-# Numbered lines (.pdf and .docx only)
 numbered-lines: true
-# File with references
 bibliography: bibliography.bib
-# Suppress title page
 suppress-title-page: false
-# Masks references that appear in the masked-citations list
 mask: false
@@
     documentmode: man
+editor: 
+  markdown: 
+    wrap: sentence
 ---
@@
 <!-- Interoception definition -->
+
 Interoception is referred to the process of sensing, interpreting and integrating information pertaining to internal organs, such as the heart, the lungs or the gut [@khalsa2018].
@@
 <!-- Interoception measure -->
-Various measures of interoception have been developed (see **figure 1** [**TODO: add crossref**]), forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking vs.
+
+Various measures of interoception have been developed (see **figure 1** \[**TODO: add crossref**\]), forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking vs.
 questionnaires and subjective scales involving a metacognitive reflection), "explicit" and "implicit" paradigms (i.e., directing participants' awareness and attention to interoceptive processes vs.
@@
 <!-- self-reports -->
+
 For instance, while the use of self-reports questionnaires might seem at odds with the concept of interoception (appearing at first as a deeply embodied - almost non-cognitive - sensory function), recent redefinitions of interoception, emphasizing the role of high-level and metacognitive elaboration of interoceptive information, has provided the theoretical grounding to support the idea that some facets of interoception (including participants' metacognitive beliefs) can be assessed subjectively, providing useful and interesting measures [@murphy2019].
@@
 
-![Figure 1. Different ways in which interoception can be measured.](figures/measuring_interoception.png)
-<!-- TODO: replace with a code chunk that allows for legend -->
+**Figure 1**
+
+Different ways in which interoception can be measured.
+
+![Figure 1. Different ways in which interoception can be measured.](figures/measuring_interoception.png) <!-- TODO: replace with a code chunk that allows for legend -->
 
 <!-- Introducing the IAS -->
+
 A recently developed scale with a rapidly growing popularity is the Interoceptive Accuracy Scale [IAS; @murphy2019].
@@
 *"I can always accurately perceive when I need to urinate"*).
-Interestingly, the IAS' statements are about specific interoceptive behaviours, which is notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012], which items are more general and metacognitive (e.g., **TODO: add representative examples**).
+Interestingly, the IAS' statements are about specific interoceptive behaviours, which is notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012], which items are more general and metacognitive (e.g., ***"I trust my body sensations"***, ***"I can notice an unpleasant body sensation without worrying about it"***).
 
 <!-- IAS structure  -->
-The original validation study suggested a two-factor solution structure, the authors decided...
-**what?**, and underline the need for further investigation of the scale's factor structure [@murphy2019, *p.
-XX*].
-Most follow-up studies, using a confirmatory factor analysis approach (CFA) **(is that correct?)**, report unidimensional structures to be the best fit [@lin2023; @campos2021; @brand2023], although with some discussions about specific items.
-For instance, @murphy2019 does mention that some items might be measuring direct interoceptive signals such as cardioception, while others, for instance "bruising", might capture phenomena that cannot be perceived through interoceptive signals alone (**Can you double check that this paper said this**).
-@lin2023 also highlights their correlation analysis showing five locally dependent pairs in three items with exceptionally high difficulty and low discrimination, and @campos2021 suggests that the "tickle" item is representing a more specific factor.
-Recently, **@blabla** used a new approach, namely Exploratory Graph Analysis (EGA), and found that **TODO**.
+
+<!-- The original validation study suggested a two-factor solution structure, the authors decided...
+**what?**, and underline the need for further investigation of the scale's factor structure [@murphy2019, *p. 127*].
+Most follow-up studies, using a confirmatory factor analysis approach (CFA) and exploratory structural equation modeling (**all used CFA but Campos also used ESEM**), report unidimensional structures to be the best fit [@lin2023; @campos2021; @brand2023], although with some discussions about specific items.
+-->
+<!-- For instance, @murphy2019 does mention that some items might be measuring direct interoceptive signals such as cardioception, while others, for instance "bruising", might capture phenomena that cannot be perceived through interoceptive signals alone (*yes* p.119).
+-->
+<!-- @lin2023 also highlights their correlation analysis showing five locally dependent pairs in three items with exceptionally high difficulty and low discrimination, and @campos2021 suggests that the "tickle" item is representing a more specific factor.
+-->
+<!-- Recently, @blabla used a new approach, namely Exploratory Graph Analysis (EGA), and found that **TODO**. -->
+
+The original validation study suggested a two-factor solution structure, the authors however underline the need for further investigation of the scale's factor structure, as it provided acceptable but imperfect explanation of the data [@murphy2019; p.
+127].
+Notably, the only other validation study to report a 2-factor solution was conducted by @koike2023, who performed an exploratory factor analysis assuming 2 factors to align with the findings from the original validation paper.
+Other follow-up studies using confirmatory factor analysis (CFA) and exploratory structural modeling [@morin2016] have identified different optimal solutions.
+Some studies, like @brand2023, reported a 1-factor solution, while @lin2023 and @campos2021 found bifactor solutions to be the best fit.
+These studies included discussions on specific items.
+For instance, @murphy2019 notes that some items might measure direct interoceptive signals such as cardioception, while others, like “bruising,” might capture phenomena not perceivable through interoceptive signals alone (yes p.119).
+@lin2023 also highlights their correlation analysis, showing five locally dependent pairs and three items with exceptionally high difficulty and low discrimination.
+Additionally, @campos2021 suggests that the “tickle” item represents a more specific factor.
+Interestingly, @lin2023 reported that all items of the IAS grouped together using a new approach, Exploratory Graph Analysis (EGA), to assess convergent and discriminant validity, which suggests unidimensionality.
+<!-- TO BE COMPLETED -->
 
 <!-- Convergent validity (correlates)  -->
-While the assessment of the validity of an interoception scale can be conceived as theoretically challenging, several traits have been used to assess convergent validity for the the IAS, including expected negative associations with alexithymia [@REF], and positive with neuroticism [@ref].
-**anything else?**.
-The IAS has also been compared to other interoception scales, yielding a positive correlation with most facets of the MAIA, with the notable exception of **TODO** [@brand2023], and the **TODO** dimension of the Body Perception Questionnaire [BPQ; @campos2021].
+
+While the assessment of the validity of an interoception scale can be conceived as theoretically challenging, several traits have been used to assess convergent validity for the the IAS, including expected negative associations with alexithymia [@brand2023; @koike2023; @campos2023, @murphy2019], somatic symptoms [@brand2023; @koike2023], depressive symptoms [@brand2023; @koike2023], anxiety [@brand2023], neuroticism [@brand2023].
+<!-- **anything else?**. TO BE COMPLETED -->
+The IAS has also been compared to other interoception scales (and interoceptive related scales), yielding a positive correlation with most facets of the MAIA, with the notable exception of *Non distracting* and *Not worrying* subscales [@brand2023], the body awareness dimension of the Body Perception Questionnaire [BPQ-A; @brand2023; @campos2021; @koike2023; @lin2023], the observation and description scales of the Five Facet Mindfulness Questionnaire [@ref, @brand2023], the interoceptive awareness subscale of the Eating Disorder Inventory [@lin2023] and a negative correlation with interoceptive confusion questionnaire [@brand2023], IATS [@lin2023; @murphy2019].
+<!-- TO BE COMPLETED -->
+
 <!-- Moreover, the current subjective measures do not correlate well with the objective measures [@murphy2019]. -->
@@
 
-The goal of study 1 is to re-analyse and assess the factor structure of the IAS by taking advantage of the large number of open-access datasets **(Brand, et al., 2023; Campos, et al., 2021; Lin, et al., 2023; Murphy, et al., 2020)** **[REDO REFS]**.
+The goal of study 1 is to re-analyse and assess the factor structure of the IAS by taking advantage of the large number of open-access datasets [@brand2023; @campos2021; @lin2023; @murphy2019; @arslanova2022; @todd2022; @gaggero2021; @brand2022; @von2023].
 While combining these studies might provide a more robust and generalizable understanding of the IAS' factor structure, it is important to note that the studies differ in their sample sizes, demographics, language, and the way they collected the data.
@@
 
-**Table 1.** Samples demographics
+**Table 1**
 
-| Samples                  |          | Sample Size | Mean age | SD      | Range   | Female % | Available at           |
-|---------|---------|---------|---------|---------|---------|---------|---------|
-| Murphy et al., (2020)    |          |             |          |         |         |          |                        |
-|                          | Sample 1 | 451         | 25.8     | 8.4     | 18-69   | 69.4%    |                        |
-|                          | Sample 2 | 375         | 35.3     | 16.9    | 18-91   | 70.1%    | <https://osf.io/3m5nh> |
-| Gaggero et al., (2021)   |          | 814         | 24.9     | 5.3     | 18-58   | 60.3%    | <https://osf.io/5x9sg> |
-| Campos et al., (2022)    |          | 515         | 30.7     | 10.5    | 18-72   | 59.6%    | <https://osf.io/j6ef3> |
-| Todd et al., (2022)      |          | 802         | 36.58\*  | 12.41\* | 18-92\* | NA       | <https://osf.io/ms354> |
-| Arslanova et al., (2022) |          | 96          | 28.78    | 27.5    | 18-73   | 46.8%    | <https://osf.io/mp3cy> |
-| Brand et al., (2022)     |          | 619         | 43.9     | 14.5    | 18-78   | 78.7%    | <https://osf.io/xwz6g> |
-| Brand et al., (2023)     |          |             |          |         |         |          |                        |
-|                          | Sample 1 | 522         | 23.4     | 6.7     | 18-79   | 79.5%    |                        |
-|                          | Sample 2 | 1993        | 32.0     | 12.6    | 16-81   | 77.7%    | <https://osf.io/3f2h6> |
-|                          | Sample 3 | 802         | 27.3     | 9.3     | 18-72   | 68.9%    |                        |
-| Lin et al., (2023)       |          |             |          |         |         |          |                        |
-|                          | Sample 1 | 1166        | 32.5     | 8.4     | 16-60   | 57.0%    |                        |
-|                          | Sample 2 | 500         | 37.4     | 7.4     | 20-60   | 56.2%    | <https://osf.io/3eztd> |
-| VonMohr et al., (2023)   |          | 21843       | 56.5     | 14.4    | 18-93   | 73.2%    | <https://osf.io/7p9u5> |
-| Makowski et al., (2023a) |          | 485         | 30.1     | 10.1    | 18-73   | 50.3%    | In preparation\*\*    |
-| Makowski et al., (2023b) |          | 251         | 37.5     | 13.2    | 17-76   | 53.0%    | In preparation\*\*    |
+Samples demographics.
+![Figure 1. Different ways in which interoception can be measured.](figures/table1.png){width="580"}
 
-**TODO: add row for Total N, average age etc.**
-**TODO: add language also, as well as maybe something like "difference" from the original validation (which could acctually be language, and for our the type of scale / less items)**
-**TODO: add links to GH for our studies**
+<!-- **Table 1.** Samples demographics -->
 
-The analysed sample contains 31,317 participants, of which xxx are females.
+<!-- | Samples                  |          | Language of Items|  Sample Size | Mean age | SD      | Range   | Female % | Available at           | -->
+
+<!-- |---------|---------|---------|---------|---------|---------|---------|---------|---------| -->
+
+<!-- | Murphy et al., (2020)    |          |             |          |         |         |          |                        | -->
+
+<!-- |                          | Sample 1 | English     |451         | 25.8     | 8.4     | 18-69   | 69.4%    |                        | -->
+
+<!-- |                          | Sample 2 | English     | 375         | 35.3     | 16.9    | 18-91   | 70.1%    | <https://osf.io/3m5nh> | -->
+
+<!-- | Gaggero et al., (2021)   |          | English and Italian   | 814         | 24.9     | 5.3     | 18-58   | 60.3%    | <https://osf.io/5x9sg> | -->
+
+<!-- | Campos et al., (2022)    |          | Portuguese  | 515         | 30.7     | 10.5    | 18-72   | 59.6%    | <https://osf.io/j6ef3> | -->
+
+<!-- | Todd et al., (2022)      |          | English     | 802         | 36.58\*  | 12.41\* | 18-92\* | NA       | <https://osf.io/ms354> | -->
+
+<!-- | Arslanova et al., (2022) |          | English     | 96          | 28.78    | 27.5    | 18-73   | 46.8%    | <https://osf.io/mp3cy> | -->
+
+<!-- | Brand et al., (2022)     |          | German      | 619         | 43.9     | 14.5    | 18-78   | 78.7%    | <https://osf.io/xwz6g> | -->
+
+<!-- | Brand et al., (2023)     |          |             |             |          |         |         |          |                        | -->
+
+<!-- |                          | Sample 1 | German      | 522         | 23.4     | 6.7     | 18-79   | 79.5%    |                        | -->
+
+<!-- |                          | Sample 2 | German      |1993        | 32.0     | 12.6    | 16-81   | 77.7%    | <https://osf.io/3f2h6> | -->
+
+<!-- |                          | Sample 3 | German      | 802         | 27.3     | 9.3     | 18-72   | 68.9%    |                        |instaiin -->
+
+<!-- | Lin et al., (2023)       |          |             |             |          |         |         |          |                        | -->
+
+<!-- |                          | Sample 1 | Chinese     | 1166        | 32.5     | 8.4     | 16-60   | 57.0%    |                        | -->
+
+<!-- |                          | Sample 2 | Chinese     | 500         | 37.4     | 7.4     | 20-60   | 56.2%    | <https://osf.io/3eztd> | -->
+
+<!-- | VonMohr et al., (2023)   |          | English     | 21843       | 56.5     | 14.4    | 18-93   | 73.2%    | <https://osf.io/7p9u5> | -->
+
+<!-- | Makowski et al., (2023a) |          | English     | 485         | 30.1     | 10.1    | 18-73   | 50.3%    | In preparation \*\*    | -->
+
+<!-- | Makowski et al., (2023b) |          | English     |251         | 37.5     | 13.2    | 17-76   | 53.0%    | In preparation \*\*    | -->
+
+<!-- | Total                    |          |             |31317       | 49.5     | 13.2    | 17 - 93 | 71.5%    | | -->
+
+**Note**.
+\* Numbers were sourced from the original paper rather than independently calculated.
+\*\* Data for Makowski et al., 2023a: <https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv> and Makowski et al., 2013b: <https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv>
+
+<!-- **TODO: add row for Total N, average age etc.** -->
+
+**TODO: add language also, as well as maybe something like "difference" from the original validation (which could actually be language, and for our the type of scale / less items)** <!-- **TODO: add links to GH for our studies** -->
+
+The analysed sample contains 31,317 participants, of which 71.5% are females.
 
@@
 
-Visualizing the distribution of the items for all samples suggests the presence of a consistent modal value (Fig.
-X).
+Visualizing the distribution of the items for all samples suggests the presence of a consistent modal value (Fig. X).
 In other words,  participants are most likely to answer 4/5 (i.e., agree) on most items (but "affective touch", "blood sugar", and "bruise" that exhibit a different distributional pattern).
@@
 Interestingly, @lin2023 also found that tickle and itch were redundant, excluding one of them but the reason being that the character for both words is the same in the Chinese language.
-On top of that, they came up with a shortened version of the IAS, excluding further items, resulting in a 12-item IAS, which aligns with our findings, suggesting that further items are ambiguous as to whether they should be removed.  In contrast, other findings also found itch and tickle to be redundant but did not suggest excluding items .
+On top of that, they came up with a shortened version of the IAS, excluding further items, resulting in a 12-item IAS, which aligns with our findings, suggesting that further items are ambiguous as to whether they should be removed.
+In contrast, other findings also found itch and tickle to be redundant but did not suggest excluding items .
 
@@
 | Questionnaire              | Number of Dimensions | Assessment                              | Number of Items | Scoring                | Example Item |
-|-----------------|------------|-------------------|-------------|-------------|-------------|
+|------------|------------|------------|------------|------------|------------|
 | **Interoceptive Related**  |                      |                                         |                 |                        |              |
@@
 To the best of our knowledge, this interaction has not been investigated before.
-However, research shows correlations between (political) beliefs and interoception, which could underlie the same mechanism \[@ruisch2022\].
+However, research shows correlations between (political) beliefs and interoception, which could underlie the same mechanism [@ruisch2022].
 Lying profile was also not strongly correlated with the IAS.
@@
 Interestingly, @campos2021 suggest removin the tickle item instead.
-@lin2023 on the other hand removed the itch item, because the sign for itch and tickle is the same.  Furthermore,  this work recommends using analog scales, instead of 5 point scales.
+@lin2023 on the other hand removed the itch item, because the sign for itch and tickle is the same. 
+Furthermore,  this work recommends using analog scales, instead of 5 point scales.
 In a 5-point scale, the variability is clearly limited with most people choosing ⅘.

### 2024-06-10 analysis/Stud1_a.qmd
table1 code

@@
 
+```
+
+```{r}
+#| output: false
+#| warning: false
+
+library(gt)
+library(tidyverse)
+
+# APA style ####
+apa_style <- function(data) {
+  data %>%
+    opt_table_lines(extent = "none") %>%
+    tab_options(
+      heading.border.bottom.width = 2,
+      heading.border.bottom.color = "black",
+      heading.border.bottom.style = "solid",
+      table.border.top.color = "black",
+      table.border.top.style = "solid",
+      table.border.top.width = 2,  
+      table_body.hlines.color = "white",
+      table_body.border.top.color = "black",
+      table_body.border.top.style = "solid",
+      table_body.border.top.width = 2,
+      heading.title.font.size = 12,
+      table.font.size = 12,
+      heading.subtitle.font.size = 12,
+      table_body.border.bottom.color = "black",
+      table_body.border.bottom.width = 2,
+      table_body.border.bottom.style = "solid",
+      column_labels.border.bottom.color = "black",
+      column_labels.border.bottom.style = "solid",
+      column_labels.border.bottom.width = 1
+    ) %>%
+      opt_table_font(font = "times")
+}
+
+# Create the dataframe
+table <- data.frame(
+  Samples = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Total'),
+  Number_of_Sample = c('', 'Sample 1', 'Sample 2', '', '', '', '', '', '', 'Sample 1', 'Sample 2', 'Sample 3', '', 'Sample 1', 'Sample 2', '', '', '', ''),   
+  Items_Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', ''),
+  Sample_Size = c('', 451, 375, 814, 515, 802, 96, 619,'', 522, 1993, 802,'', 1166, 500, 21843, 485, 251, 31317),
+  Mean_age = c('', 25.8, 35.3, 24.9, 30.7, 36.58, 28.78, 43.9,'', 23.4, 32.0, 27.3,'', 32.5, 37.4, 56.5, 30.1, 37.5, 49.5),
+  SD = c('', 8.4, 16.9, 5.3, 10.5, 12.41, 27.5, 14.5,'',  6.7, 12.6, 9.3, '', 8.4, 7.4, 14.4, 10.1, 13.2, 13.2),
+  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76', '17 - 93'),
+  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', NA, '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '71.5%'),
+  Available_at= c('', '', 'https://osf.io/3m5nh', 'https://osf.io/5x9sg', 'https://osf.io/j6ef3', 'https://osf.io/ms354', 'https://osf.io/mp3cy', 'https://osf.io/xwz6g', '', '', 'https://osf.io/3f2h6', '','','', 'https://osf.io/3eztd', 'https://osf.io/7p9u5', 'In preparation **', 'In preparation **', '')
+)
+
+table_apa <- table |> gt() |>
+  cols_label(Number_of_Sample = "Number of Sample", Items_Language = "Items Language", Sample_Size = "Sample Size", Mean_age = "Mean Age", Female_Percentage = "Female %", Available_at = "Available at")
+
+table_apa <- apa_style(table_apa)
+
+# Save as image for IPPE google docs workflow
+gtsave(data = table_apa, path = "../paper/1_Initial/figures", filename = "table1.png")
 ```

### 2024-06-11 paper/1_Initial/manuscript.qmd
let's not use gt

@@
     wrap: sentence
+editor_options: 
+  chunk_output_type: console
 ---
@@
 
-![Figure 1. Different ways in which interoception can be measured.](figures/measuring_interoception.png) <!-- TODO: replace with a code chunk that allows for legend -->
+![Figure 1. Different ways in which interoception can be measured.](figures/measuring_interoception.png) 
+<!-- TODO: replace with a code chunk that allows for legend -->
 
@@
 *"I can always accurately perceive when I need to urinate"*).
-Interestingly, the IAS' statements are about specific interoceptive behaviours, which is notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012], which items are more general and metacognitive (e.g., ***"I trust my body sensations"***, ***"I can notice an unpleasant body sensation without worrying about it"***).
+Interestingly, the IAS' statements are about specific interoceptive behaviours, which is notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012], which items are more general and metacognitive (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*).
 
@@
 
+```{r}
+#| warning: false
+#| label: tbl-samples
+#| tbl-cap: "Blabla caption fds Samples demographics"
+# #| apa-note: "Some note bedlow the table"
+
+table <- data.frame(
+  Studies = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', '***Total***'),
+  Samples = c('', 'Sample 1', 'Sample 2', '', '', '', '', '', '', 'Sample 1', 'Sample 2', 'Sample 3', '', 'Sample 1', 'Sample 2', '', '', '', ''),   
+  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', ''),
+  N = c('', 451, 375, 814, 515, 802, 96, 619,'', 522, 1993, 802,'', 1166, 500, 21843, 485, 251, "\\textbf{31317}"),
+  Age = c('', "25.8 ± 8.4 [18-69]", 35.3, 24.9, 30.7, 36.58, 28.78, 43.9,'', 23.4, 32.0, 27.3,'', 32.5, 37.4, 56.5, 30.1, 37.5, 49.5),
+  SD = c('', 8.4, 16.9, 5.3, 10.5, 12.41, 27.5, 14.5,'',  6.7, 12.6, 9.3, '', 8.4, 7.4, 14.4, 10.1, 13.2, 13.2),
+  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76', '17 - 93'),
+  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', NA, '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '71.5%'),
+  Link= c('', '', 'https://osf.io/3m5nh', 'https://osf.io/5x9sg', 'https://osf.io/j6ef3', 'https://osf.io/ms354', 'https://osf.io/mp3cy', 'https://osf.io/xwz6g', '', '', 'https://osf.io/3f2h6', '','','', 'https://osf.io/3eztd', 'https://osf.io/7p9u5', 'In preparation **', 'In preparation **', '')
+)
+
+knitr::kable(table, format = "latex", booktabs = TRUE, longtable = TRUE, col.names = stringr::str_replace(names(table), "Female_Percentage", "Female %")) |> 
+  kableExtra::kable_styling(font_size = 7)
+```
+
 Our search focused on studies citing the original IAS validation paper [@murphy2019], identifying 136 papers (as of **XX/XX/2024**).
@@
 Additionally, we added datasets of two unpublished (but already open-access) studies from our lab.
-**See Table 1 (add crossref link)** for a summary of the samples demographics.
-
-**Table 1**
-
-Samples demographics.
-![Figure 1. Different ways in which interoception can be measured.](figures/table1.png){width="580"}
+**See @tbl-samples** for a summary of the samples demographics.
 

### 2024-06-11 paper/1_Initial/manuscript.qmd
fix bold

@@
 table <- data.frame(
-  Studies = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', '***Total***'),
+  Studies = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Total'),
   Samples = c('', 'Sample 1', 'Sample 2', '', '', '', '', '', '', 'Sample 1', 'Sample 2', 'Sample 3', '', 'Sample 1', 'Sample 2', '', '', '', ''),   
   Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', ''),
-  N = c('', 451, 375, 814, 515, 802, 96, 619,'', 522, 1993, 802,'', 1166, 500, 21843, 485, 251, "\\textbf{31317}"),
+  N = c('', 451, 375, 814, 515, 802, 96, 619,'', 522, 1993, 802,'', 1166, 500, 21843, 485, 251, "31317"),
   Age = c('', "25.8 ± 8.4 [18-69]", 35.3, 24.9, 30.7, 36.58, 28.78, 43.9,'', 23.4, 32.0, 27.3,'', 32.5, 37.4, 56.5, 30.1, 37.5, 49.5),
@@
 
-knitr::kable(table, format = "latex", booktabs = TRUE, longtable = TRUE, col.names = stringr::str_replace(names(table), "Female_Percentage", "Female %")) |> 
-  kableExtra::kable_styling(font_size = 7)
+knitr::kable(table, format = "latex", booktabs = TRUE, longtable = TRUE, 
+             col.names = stringr::str_replace(names(table), "Female_Percentage", "Female %")) |> 
+  kableExtra::kable_styling(font_size = 7) |> 
+  kableExtra::row_spec(0, bold=TRUE) |> 
+  kableExtra::row_spec(nrow(table), bold=TRUE, italic=TRUE)
 ```

### 2024-11-17 analysis/Stud1_a.qmd
let's not use gt
Minor: format links

@@
 ---
-title: "Meta-analysis of the Interoceptive Accuracy Scale"
+title: "Meta-analysis of the Interoceptive Accuracy Scale (IAS)"
 subtitle: "Study 1"
@@
 
-Murphy (<https://osf.io/3m5nh)>
+- Murphy (2020)
+  - https://osf.io/3m5nh
 
@@
 
-Gaggero (2021) (<https://osf.io/5x9sg)>
+- Gaggero (2021) 
+  - https://osf.io/5x9sg
 
@@
 
-Campos (2022) - Study 1 (<https://osf.io/j6ef3)>
+- Campos (2022) - Study 1 
+  - https://osf.io/j6ef3
 
@@
 
-Todd (2022) - <https://osf.io/ms354/>
+- Todd (2022) 
+  - https://osf.io/ms354/
 
@@
 
-Arslanova (2022) - <https://osf.io/mp3cy/>
+- Arslanova (2022)
+  - https://osf.io/mp3cy/
 
@@
 
-Brand (2022) - <https://osf.io/xwz6g/>
+- Brand (2022) 
+  - https://osf.io/xwz6g/
 
@@
 
-Brand (2023) - <https://osf.io/3f2h6/>
+- Brand (2023) 
+  - https://osf.io/3f2h6/
 
@@
 
-Lin (2023) - <https://osf.io/3eztd> - Note: No tickle because same Chinese character
+- Lin (2023)
+  - https://osf.io/3eztd
+  - Note: No tickle because same Chinese character
 
@@
 
-VonMohr (2023) - Study 3 (<https://osf.io/7p9u5/)>
+- VonMohr (2023) - Study 3 
+  - https://osf.io/7p9u5/
 
@@
 
-Makowski
-
+- Makowski
   - Note: First sample has some missing items
@@
 library(gt)
-library(tidyverse)
 
@@
 
-table_apa <- table |> gt() |>
+table_apa <- table |> 
+  gt() |>
   cols_label(Number_of_Sample = "Number of Sample", Items_Language = "Items Language", Sample_Size = "Sample Size", Mean_age = "Mean Age", Female_Percentage = "Female %", Available_at = "Available at")
@@
 table_apa <- apa_style(table_apa) 
-
-# Save as image for IPPE google docs workflow
-gtsave(data = table_apa, path = "../paper/1_Initial/figures", filename = "table1.png")
+table_apa
 ```

### 2024-11-17 analysis/Stud1_a.qmd
make table1 more reproducible
@AnafNeves  :
- just noticed the sample size for df5 and df7c that we had written vs. the recomputed doesn't match, not sure if  that's expected
- The mean age is probably wrong too

--- 2024-06-10 analysis/Stud1_a.qmd
@@
 
+```
+
+```{r}
+#| output: false
+#| warning: false
+
+library(gt)
+
+# APA style ####
+gt_apastyle <- function(gt_table, font.size=12) {
+  gt_table  |> 
+    gt::opt_table_lines(extent = "none") %>%
+    gt::tab_options(
+      heading.border.bottom.width = 2,
+      heading.border.bottom.color = "black",
+      heading.border.bottom.style = "solid",
+      table.border.top.color = "black",
+      table.border.top.style = "solid",
+      table.border.top.width = 2,  
+      table_body.hlines.color = "white",
+      table_body.border.top.color = "black",
+      table_body.border.top.style = "solid",
+      table_body.border.top.width = 2,
+      heading.title.font.size = font.size,
+      table.font.size = font.size,
+      heading.subtitle.font.size = font.size,
+      table_body.border.bottom.color = "black",
+      table_body.border.bottom.width = 2,
+      table_body.border.bottom.style = "solid",
+      column_labels.border.bottom.color = "black",
+      column_labels.border.bottom.style = "solid",
+      column_labels.border.bottom.width = 1
+    ) |> 
+      gt::opt_table_font(font = "times")
+}
+
+make_age <- function(age) {
+  age <- as.numeric(age)
+
+  mean(age, na.rm = TRUE) |> 
+    insight::format_value(digits=1) |> 
+    paste0(" ± ", 
+           insight::format_value(sd(age, na.rm = TRUE), digits=1)) 
+}
+
+# Create the dataframe
+table <- data.frame(
+  Sample = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Total'),
+  Subsample = c('', 'Sample 1', 'Sample 2', '', '', '', '', '', '', 'Sample 1', 'Sample 2', 'Sample 3', '', 'Sample 1', 'Sample 2', '', '', '', ''),   
+  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', ''),
+  N = c('', nrow(df1a), nrow(df1b), nrow(df2), nrow(df3), nrow(df4), 96, nrow(df6),'', nrow(df7a), nrow(df7b), 802,'', nrow(df8a), nrow(df8b), nrow(df9), nrow(df10a), nrow(df10b), 31317),
+  Age = c('', make_age(df1a$Age), make_age(df1b$Age), make_age(df2$Age), make_age(df3$Age), "TODO*", "TODO*", make_age(df6$Age),'', make_age(df7a$Age), make_age(df7b$Age), make_age(df7c$Age),'', make_age(df8a$Age), make_age(df8b$Age), make_age(df9$Age), make_age(df10a$Age), make_age(df10b$Age), 49.5),
+  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76', '17 - 93'),
+  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', NA, '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '71.5%'),
+  Availability= c('', '', 'https://osf.io/3m5nh', 'https://osf.io/5x9sg', 'https://osf.io/j6ef3', 'https://osf.io/ms354', 'https://osf.io/mp3cy', 'https://osf.io/xwz6g', '', '', 'https://osf.io/3f2h6', '','','', 'https://osf.io/3eztd', 'https://osf.io/7p9u5', 'https://github.com/RealityBending/IllusionGameReliability', 'https://github.com/DominiqueMakowski/PHQ4R', '')
+)
+
+table_apa <- table |> 
+  gt() |>
+  cols_align(align = c("right"), columns = "Age") |> 
+  cols_label(Age = "Age (Mean  ± SD)", Female_Percentage = "Female %") |> 
+  tab_footnote("* Information copied from the sample description rather than recomputed.") |> 
+  gt_apastyle()
+
+table_apa
+gtsave(table_apa, "figures/table1.tex")
 ```

### 2024-11-17 analysis/figures/table1.tex
make table1 more reproducible
@AnafNeves  :
- just noticed the sample size for df5 and df7c that we had written vs. the recomputed doesn't match, not sure if  that's expected
- The mean age is probably wrong too

\setlength{\LTpost}{0mm}
\begin{longtable}{lllrrrrl}
\toprule
Sample & Subsample & Language & N & Age (Mean  ± SD) & Range & Female \% & Availability \\ 
\midrule\addlinespace[2.5pt]
Murphy et al., (2020) &  &  &  &  &  &  &  \\ 
 & Sample 1 & English & 451 & 25.8 ± 8.4 & 18-69 & 69.4\% &  \\ 
 & Sample 2 & English & 375 & 35.3 ± 16.9 & 18-91 & 70.1\% & https://osf.io/3m5nh \\ 
Gaggero et al., (2021) &  & English and Italian & 814 & 24.9 ± 5.3 & 18-58 & 60.3\% & https://osf.io/5x9sg \\ 
Campos et al., (2022) &  & Portuguese & 515 & 30.7 ± 10.5 & 18-72 & 59.6\% & https://osf.io/j6ef3 \\ 
Todd et al., (2022) &  & English & 802 & TODO* & 18-92* & NA & https://osf.io/ms354 \\ 
Arslanova et al., (2022) &  & English & 96 & TODO* & 18-73 & 46.8\% & https://osf.io/mp3cy \\ 
Brand et al., (2022) &  & German & 619 & 43.9 ± 14.5 & 18-78 & 78.7\% & https://osf.io/xwz6g \\ 
Brand et al., (2023) &  &  &  &  &  &  &  \\ 
 & Sample 1 & German & 522 & 23.4 ± 6.7 & 18-79 & 79.5\% &  \\ 
 & Sample 2 & German & 1993 & 32.0 ± 12.6 & 16-81 & 77.7\% & https://osf.io/3f2h6 \\ 
 & Sample 3 & German & 802 & 27.3 ± 9.3 & 18-72 & 68.9\% &  \\ 
Lin et al., (2023) &  &  &  &  &  &  &  \\ 
 & Sample 1 & Chinese & 1166 & 32.5 ± 8.4 & 16-60 & 57.0\% &  \\ 
 & Sample 2 & Chinese & 500 & 37.4 ± 7.4 & 20-60 & 56.2\% & https://osf.io/3eztd \\ 
VonMohr et al., (2023) &  & English & 21843 & 56.5 ± 14.4 & 18-93 & 73.2\% & https://osf.io/7p9u5 \\ 
Makowski et al., (2023a) &  & English & 485 & 30.1 ± 10.1 & 18-73 & 50.3\% & https://github.com/RealityBending/IllusionGameReliability \\ 
Makowski et al., (2023b) &  & English & 251 & 37.5 ± 13.2 & 17-76 & 53.0\% & https://github.com/DominiqueMakowski/PHQ4R \\ 
Total &  &  & 31317 & 49.5 & 17 - 93 & 71.5\% &  \\ 
\bottomrule
\end{longtable}
\begin{minipage}{\linewidth}
* Information copied from the sample description rather than recomputed.\\
\end{minipage}

### 2024-11-17 paper/1_Initial/manuscript.qmd
make table1 more reproducible
@AnafNeves  :
- just noticed the sample size for df5 and df7c that we had written vs. the recomputed doesn't match, not sure if  that's expected
- The mean age is probably wrong too

--- 2024-06-11 paper/1_Initial/manuscript.qmd
@@
 title: "Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates"
-shorttitle: "IAS Factor structure and correlates"
+shorttitle: "IAS Meta-analysis"
 author:
-  - name: Magdalena Pfaff
+  - name: Ana Neves
     corresponding: true
-    orcid: 0009-0006-2386-7936
+    orcid: 0009-0006-0020-7599
     # roles: 
@@
     #   - Writing – review & editing
-  - name: Ana Neves
-    orcid: 0009-0006-0020-7599
-    # roles:
+  - name: Magdalena Pfaff
+    corresponding: true
+    orcid: 0009-0006-2386-7936
     affiliations:
@@
 
-```{r}
-#| warning: false
-#| label: tbl-samples
-#| tbl-cap: "Blabla caption fds Samples demographics"
-# #| apa-note: "Some note bedlow the table"
-
-table <- data.frame(
-  Studies = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', '***Total***'),
-  Samples = c('', 'Sample 1', 'Sample 2', '', '', '', '', '', '', 'Sample 1', 'Sample 2', 'Sample 3', '', 'Sample 1', 'Sample 2', '', '', '', ''),   
-  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', ''),
-  N = c('', 451, 375, 814, 515, 802, 96, 619,'', 522, 1993, 802,'', 1166, 500, 21843, 485, 251, "\\textbf{31317}"),
-  Age = c('', "25.8 ± 8.4 [18-69]", 35.3, 24.9, 30.7, 36.58, 28.78, 43.9,'', 23.4, 32.0, 27.3,'', 32.5, 37.4, 56.5, 30.1, 37.5, 49.5),
-  SD = c('', 8.4, 16.9, 5.3, 10.5, 12.41, 27.5, 14.5,'',  6.7, 12.6, 9.3, '', 8.4, 7.4, 14.4, 10.1, 13.2, 13.2),
-  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76', '17 - 93'),
-  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', NA, '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '71.5%'),
-  Link= c('', '', 'https://osf.io/3m5nh', 'https://osf.io/5x9sg', 'https://osf.io/j6ef3', 'https://osf.io/ms354', 'https://osf.io/mp3cy', 'https://osf.io/xwz6g', '', '', 'https://osf.io/3f2h6', '','','', 'https://osf.io/3eztd', 'https://osf.io/7p9u5', 'In preparation **', 'In preparation **', '')
-)
-
-knitr::kable(table, format = "latex", booktabs = TRUE, longtable = TRUE, col.names = stringr::str_replace(names(table), "Female_Percentage", "Female %")) |> 
-  kableExtra::kable_styling(font_size = 7)
-```
-
 Our search focused on studies citing the original IAS validation paper [@murphy2019], identifying 136 papers (as of **XX/XX/2024**).
@@
 Additionally, we added datasets of two unpublished (but already open-access) studies from our lab.
-**See @tbl-samples** for a summary of the samples demographics.
+See @tbl-samples for a summary of the samples demographics.
 
-<!-- **Table 1.** Samples demographics -->
+```{r}
+#| warning: false
+#| label: tbl-samples
+#| tbl-cap: "Blabla caption for Samples demographics"
+# #| apa-note: "Some note bedlow the table"
 
-<!-- | Samples                  |          | Language of Items|  Sample Size | Mean age | SD      | Range   | Female % | Available at           | -->
+```
 
-<!-- |---------|---------|---------|---------|---------|---------|---------|---------|---------| -->
-
-<!-- | Murphy et al., (2020)    |          |             |          |         |         |          |                        | -->
-
-<!-- |                          | Sample 1 | English     |451         | 25.8     | 8.4     | 18-69   | 69.4%    |                        | -->
-
-<!-- |                          | Sample 2 | English     | 375         | 35.3     | 16.9    | 18-91   | 70.1%    | <https://osf.io/3m5nh> | -->
-
-<!-- | Gaggero et al., (2021)   |          | English and Italian   | 814         | 24.9     | 5.3     | 18-58   | 60.3%    | <https://osf.io/5x9sg> | -->
-
-<!-- | Campos et al., (2022)    |          | Portuguese  | 515         | 30.7     | 10.5    | 18-72   | 59.6%    | <https://osf.io/j6ef3> | -->
-
-<!-- | Todd et al., (2022)      |          | English     | 802         | 36.58\*  | 12.41\* | 18-92\* | NA       | <https://osf.io/ms354> | -->
-
-<!-- | Arslanova et al., (2022) |          | English     | 96          | 28.78    | 27.5    | 18-73   | 46.8%    | <https://osf.io/mp3cy> | -->
-
-<!-- | Brand et al., (2022)     |          | German      | 619         | 43.9     | 14.5    | 18-78   | 78.7%    | <https://osf.io/xwz6g> | -->
-
-<!-- | Brand et al., (2023)     |          |             |             |          |         |         |          |                        | -->
-
-<!-- |                          | Sample 1 | German      | 522         | 23.4     | 6.7     | 18-79   | 79.5%    |                        | -->
-
-<!-- |                          | Sample 2 | German      |1993        | 32.0     | 12.6    | 16-81   | 77.7%    | <https://osf.io/3f2h6> | -->
-
-<!-- |                          | Sample 3 | German      | 802         | 27.3     | 9.3     | 18-72   | 68.9%    |                        |instaiin -->
-
-<!-- | Lin et al., (2023)       |          |             |             |          |         |         |          |                        | -->
-
-<!-- |                          | Sample 1 | Chinese     | 1166        | 32.5     | 8.4     | 16-60   | 57.0%    |                        | -->
-
-<!-- |                          | Sample 2 | Chinese     | 500         | 37.4     | 7.4     | 20-60   | 56.2%    | <https://osf.io/3eztd> | -->
-
-<!-- | VonMohr et al., (2023)   |          | English     | 21843       | 56.5     | 14.4    | 18-93   | 73.2%    | <https://osf.io/7p9u5> | -->
-
-<!-- | Makowski et al., (2023a) |          | English     | 485         | 30.1     | 10.1    | 18-73   | 50.3%    | In preparation \*\*    | -->
-
-<!-- | Makowski et al., (2023b) |          | English     |251         | 37.5     | 13.2    | 17-76   | 53.0%    | In preparation \*\*    | -->
-
-<!-- | Total                    |          |             |31317       | 49.5     | 13.2    | 17 - 93 | 71.5%    | | -->
+\tiny 
+\input{../../analysis/figures/table1.tex}
+\normalsize
 
@@
 \*\* Data for Makowski et al., 2023a: <https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv> and Makowski et al., 2013b: <https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv>
-
-<!-- **TODO: add row for Total N, average age etc.** -->
 

### 2024-11-17 paper/1_Initial/manuscript.qmd
removes notes (now int able)

@@
 To qualify for inclusion, papers needed to (1) provide accessible data in open-access, (2) employ the IAS as a measure, and (3) report individual IAS items scores.
-A total of 9 studies was included.
-Additionally, we added datasets of two unpublished (but already open-access) studies from our lab.
+A total of **XX** studies was included.
+We also included the data of two unpublished (but already open-access) studies from the authors.
+The total N participants was 31,317 participants (Mean SD, 71.5% Female).
 See @tbl-samples for a summary of the samples demographics.
@@
 
-**Note**.
-\* Numbers were sourced from the original paper rather than independently calculated.
-\*\* Data for Makowski et al., 2023a: <https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv> and Makowski et al., 2013b: <https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv>
-
 **TODO: add language also, as well as maybe something like "difference" from the original validation (which could actually be language, and for our the type of scale / less items)** <!-- **TODO: add links to GH for our studies** -->
-
-The analysed sample contains 31,317 participants, of which 71.5% are females.
 

### 2024-11-17 paper/1_Initial/manuscript.qmd
Correct way of including a figure

@@
 Interoception is referred to the process of sensing, interpreting and integrating information pertaining to internal organs, such as the heart, the lungs or the gut [@khalsa2018].
-While recent research emphasizes a key role of interoception in a variety of processes (e.g., emotion regulation, decision making) and of outcomes (physical and psychological well being), the field remains clouded by concerns pertaining to how interoception is assessed.
+While recent research emphasizes a key role of interoception in a variety of processes (e.g., emotion regulation, decision making) and of outcomes (physical and psychological well being), the field remains clouded by concerns about how interoception is assessed.
 
@@
 
-Various measures of interoception have been developed (see **figure 1** \[**TODO: add crossref**\]), forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking vs.
-questionnaires and subjective scales involving a metacognitive reflection), "explicit" and "implicit" paradigms (i.e., directing participants' awareness and attention to interoceptive processes vs.
-measuring interoception unbeknownst to them), various interoceptive modalities (e.g., cardioception, respiroception, gastroception) and theoretical dimensions (e.g., sensitivity, awareness, accuracy).
+Various measures of interoception have been developed (see **@fig-measures**), forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking vs.
+questionnaires and subjective scales involving a metacognitive reflection), "explicit" and "implicit" paradigms (i.e., directing participants' awareness and attention to interoceptive processes *vs.* measuring interoception unbeknownst to them), various interoceptive modalities (e.g., cardioception, respiroception, gastroception) and theoretical dimensions (e.g., accuracy, sensitivity, awareness).
 While there is no consensus as to which particular approach provides the most accurate and "pure" measure of interoception and interoceptive abilities (assuming it is a unidimensional construct), it is instead plausible that each measure has strengths and limitations, and a utility dependent on the context and goal at hand [@jahedi2014].
@@
 
-For instance, while the use of self-reports questionnaires might seem at odds with the concept of interoception (appearing at first as a deeply embodied - almost non-cognitive - sensory function), recent redefinitions of interoception, emphasizing the role of high-level and metacognitive elaboration of interoceptive information, has provided the theoretical grounding to support the idea that some facets of interoception (including participants' metacognitive beliefs) can be assessed subjectively, providing useful and interesting measures [@murphy2019].
-However, understanding the exact nature of what is being measured with different questionnaires is crucial, as self-reports might not reflect the same processes as other measures, seemingly contributing to an apparent lack of convergence in the field.
+For instance, while the use of self-reports questionnaires to measure an embodied function might seem paradoxical, recent redefinitions of interoception, emphasizing the role of high-level and metacognitive elaboration of interoceptive information, has provided the theoretical grounding to support the idea that some facets of interoception (including participants' metacognitive beliefs) can be assessed subjectively, providing useful and interesting measures [@murphy2019] [**TODO: also cite the most recent paper**].
+The notion that self-reports might not reflect the same processes as other interoception measures is important to contextualize the apparent lack of convergence between measures in the field **(REF)**.
+Still, a better understanding of what is being measured with different questionnaires and dimensions, as well their potential overlaps with other constructs (e.g., alexithymia, body awareness) is needed to clarify the role of self-reports in the assessment of interoception.
 
-**Figure 1**
+```{r}
+#| label: "fig-measures"
+#| fig-cap: "Different ways in which interoception can be measured."
 
-Different ways in which interoception can be measured.
+knitr::include_graphics("figures/measuring_interoception.png")
+```
 
-![Figure 1. Different ways in which interoception can be measured.](figures/measuring_interoception.png) 
 <!-- TODO: replace with a code chunk that allows for legend -->

### 2024-11-17 paper/1_Initial/manuscript.qmd
Update manuscript.qmd

@@
 
-<!-- self-reports -->
-
-For instance, while the use of self-reports questionnaires to measure an embodied function might seem paradoxical, recent redefinitions of interoception, emphasizing the role of high-level and metacognitive elaboration of interoceptive information, has provided the theoretical grounding to support the idea that some facets of interoception (including participants' metacognitive beliefs) can be assessed subjectively, providing useful and interesting measures [@murphy2019] [**TODO: also cite the most recent paper**].
-The notion that self-reports might not reflect the same processes as other interoception measures is important to contextualize the apparent lack of convergence between measures in the field **(REF)**.
-Still, a better understanding of what is being measured with different questionnaires and dimensions, as well their potential overlaps with other constructs (e.g., alexithymia, body awareness) is needed to clarify the role of self-reports in the assessment of interoception.
-
 ```{r}
@@
 
-<!-- TODO: replace with a code chunk that allows for legend -->
+<!-- self-reports -->
+
+For instance, while the use of self-reports questionnaires to measure an embodied function might seem paradoxical, recent redefinitions of interoception, emphasizing the role of high-level and metacognitive elaboration of interoceptive information, has provided the theoretical grounding to support the idea that some facets of interoception (including participants' metacognitive beliefs) can be assessed subjectively, providing useful and interesting measures [@murphy2019] [**TODO: also cite the most recent paper**].
+The notion that self-reports might not reflect the same processes as other interoception measures is important to contextualize the apparent lack of convergence between measures in the field **(REF)**.
+Still, a better understanding of what is being measured with different questionnaires and dimensions, as well their potential overlaps with other constructs (e.g., alexithymia, body awareness) is needed to clarify the role of self-reports in the assessment of interoception.
 
@@
 *"I can always accurately perceive when I need to urinate"*).
-Interestingly, the IAS' statements are about specific interoceptive behaviours, which is notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012], which items are more general and metacognitive (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*).
+Interestingly, the IAS' statements are about specific interoceptive behaviours, which is notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012; **SECOND REF**], which contains more general and metacognitive items (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*).
 
@@
 Additionally, @campos2021 suggests that the “tickle” item represents a more specific factor.
-Interestingly, @lin2023 reported that all items of the IAS grouped together using a new approach, Exploratory Graph Analysis (EGA), to assess convergent and discriminant validity, which suggests unidimensionality.
+Interestingly, @lin2023 reported that all items of the IAS grouped together using a new approach, Exploratory Graph Analysis (EGA) **[REFS]**, to assess convergent and discriminant validity, which suggests unidimensionality.
 <!-- TO BE COMPLETED -->
@@
 <!-- **anything else?**. TO BE COMPLETED -->
-The IAS has also been compared to other interoception scales (and interoceptive related scales), yielding a positive correlation with most facets of the MAIA, with the notable exception of *Non distracting* and *Not worrying* subscales [@brand2023], the body awareness dimension of the Body Perception Questionnaire [BPQ-A; @brand2023; @campos2021; @koike2023; @lin2023], the observation and description scales of the Five Facet Mindfulness Questionnaire [@ref, @brand2023], the interoceptive awareness subscale of the Eating Disorder Inventory [@lin2023] and a negative correlation with interoceptive confusion questionnaire [@brand2023], IATS [@lin2023; @murphy2019].
+The IAS has also been compared to other interoception scales (and interoceptive related scales), yielding a positive correlation with most facets of the MAIA, with the notable exception of *Non distracting* and *Not worrying* subscales [@brand2023], the body awareness dimension of the Body Perception Questionnaire [BPQ-A; @brand2023; @campos2021; @koike2023; @lin2023], the observation and description scales of the Five Facet Mindfulness Questionnaire [@ref, @brand2023], the interoceptive awareness subscale of the Eating Disorder Inventory [@lin2023] and a negative correlation with interoceptive confusion questionnaire [@brand2023] **[I don't think this is the correct ref]**, IATS [@lin2023; @murphy2019].
 <!-- TO BE COMPLETED -->

### 2024-11-17 paper/1_Initial/manuscript.qmd
the structure and convergent validity paragraphs need rewriting

@@
 A recently developed scale with a rapidly growing popularity is the Interoceptive Accuracy Scale [IAS; @murphy2019].
-The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological mechanism such as respiration (*"I can always accurately perceive when I am breathing fast"*), heart (e.g *"I can always accurately perceive when my heart is beating fast"*), skin (e.g *"I can always accurately perceive when something is going to be ticklish"*), arousal or bodily functions like coughing (e.g *"I can always accurately perceive when I am going to cough"*), urinating (e.g.
+The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological modality such as respiration (*"I can always accurately perceive when I am breathing fast"*), heart (e.g *"I can always accurately perceive when my heart is beating fast"*), skin (e.g *"I can always accurately perceive when something is going to be ticklish"*), arousal or bodily functions like coughing (e.g *"I can always accurately perceive when I am going to cough"*) or urinating (e.g.
 *"I can always accurately perceive when I need to urinate"*).
-Interestingly, the IAS' statements are about specific interoceptive behaviours, which is notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012; **SECOND REF**], which contains more general and metacognitive items (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*).
+Interestingly, the IAS' statements are about specific interoceptive behaviours, which is a notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012; **SECOND REF**], which contains more general and metacognitive items (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*).
 
@@
 
-<!-- The original validation study suggested a two-factor solution structure, the authors decided...
-**what?**, and underline the need for further investigation of the scale's factor structure [@murphy2019, *p. 127*].
-Most follow-up studies, using a confirmatory factor analysis approach (CFA) and exploratory structural equation modeling (**all used CFA but Campos also used ESEM**), report unidimensional structures to be the best fit [@lin2023; @campos2021; @brand2023], although with some discussions about specific items.
--->
-<!-- For instance, @murphy2019 does mention that some items might be measuring direct interoceptive signals such as cardioception, while others, for instance "bruising", might capture phenomena that cannot be perceived through interoceptive signals alone (*yes* p.119).
--->
-<!-- @lin2023 also highlights their correlation analysis showing five locally dependent pairs in three items with exceptionally high difficulty and low discrimination, and @campos2021 suggests that the "tickle" item is representing a more specific factor.
--->
-<!-- Recently, @blabla used a new approach, namely Exploratory Graph Analysis (EGA), and found that **TODO**. -->
+Although the original validation study suggested a two-factor solution structure, the authors underlines the need for further investigation of the scale's factor structure, as it provided acceptable but imperfect explanation of the data [@murphy2019; p.
+127].
+Notably, the only other validation study to report a 2-factor solution was conducted by @koike2023, who performed an Exploratory Factor Analysis (EFA) assuming 2 factors to align with the findings from the original validation paper.
+Other follow-up studies using confirmatory factor analysis (CFA) and structural modeling [@morin2016] have identified different optimal solutions. 
+Some studies, like @brand2023, reported a 1-factor solution, while @lin2023 and @campos2021 found bifactor solutions **(i.e., QUICK DESCRIPTION)** to be the best fit.
 
-The original validation study suggested a two-factor solution structure, the authors however underline the need for further investigation of the scale's factor structure, as it provided acceptable but imperfect explanation of the data [@murphy2019; p.
-127].
-Notably, the only other validation study to report a 2-factor solution was conducted by @koike2023, who performed an exploratory factor analysis assuming 2 factors to align with the findings from the original validation paper.
-Other follow-up studies using confirmatory factor analysis (CFA) and exploratory structural modeling [@morin2016] have identified different optimal solutions.
-Some studies, like @brand2023, reported a 1-factor solution, while @lin2023 and @campos2021 found bifactor solutions to be the best fit.
-These studies included discussions on specific items.
-For instance, @murphy2019 notes that some items might measure direct interoceptive signals such as cardioception, while others, like “bruising,” might capture phenomena not perceivable through interoceptive signals alone (yes p.119).
-@lin2023 also highlights their correlation analysis, showing five locally dependent pairs and three items with exceptionally high difficulty and low discrimination.
-Additionally, @campos2021 suggests that the “tickle” item represents a more specific factor.
+Discussions have also been focused on specific items.
+For instance, @murphy2019 notes that some items might measure direct interoceptive signals such as cardioception, while others might capture phenomena not perceivable through interoceptive signals alone (e.g., "bruising"; p.
+119).
+@lin2023 also highlights their correlation analysis, showing five locally dependent pairs and three items **(WHICH ONES)** with exceptionally high difficulty and low discrimination. 
+Additionally, @campos2021 suggests that the "tickle" item represents a more specific factor.
 Interestingly, @lin2023 reported that all items of the IAS grouped together using a new approach, Exploratory Graph Analysis (EGA) **[REFS]**, to assess convergent and discriminant validity, which suggests unidimensionality.
+
 <!-- TO BE COMPLETED -->
@@
 <!-- **anything else?**. TO BE COMPLETED -->
-The IAS has also been compared to other interoception scales (and interoceptive related scales), yielding a positive correlation with most facets of the MAIA, with the notable exception of *Non distracting* and *Not worrying* subscales [@brand2023], the body awareness dimension of the Body Perception Questionnaire [BPQ-A; @brand2023; @campos2021; @koike2023; @lin2023], the observation and description scales of the Five Facet Mindfulness Questionnaire [@ref, @brand2023], the interoceptive awareness subscale of the Eating Disorder Inventory [@lin2023] and a negative correlation with interoceptive confusion questionnaire [@brand2023] **[I don't think this is the correct ref]**, IATS [@lin2023; @murphy2019].
+The IAS has also been compared to other interoception scales (and interoceptive related scales), yielding a positive correlation with most facets of the MAIA, with the notable exception of *Non distracting* and *Not worrying* subscales [@brand2023], the body awareness dimension of the Body Perception Questionnaire [BPQ-A; @brand2023; @campos2021; @koike2023; @lin2023], the observation and description scales of the Five Facet Mindfulness Questionnaire [FFMQ **what is ref?**; @ref, @brand2023], the interoceptive awareness subscale of the Eating Disorder Inventory [@lin2023] and a negative correlation with the interoceptive confusion questionnaire [@brand2023] **[I don't think this is the correct ref]**, IATS [@lin2023; @murphy2019].
+<!-- What about the iats? -->
 <!-- TO BE COMPLETED -->

### 2024-11-17 paper/1_Initial/manuscript.qmd
typos and headings

@@
   - name: Ana Neves
-    corresponding: true
     orcid: 0009-0006-0020-7599
@@
   - name: Magdalena Pfaff
-    corresponding: true
     orcid: 0009-0006-2386-7936
@@
 
-A recently developed scale with a rapidly growing popularity is the Interoceptive Accuracy Scale [IAS; @murphy2019].
+A recently developed scale with a rapidly growing popularity is the Interoceptive Accuracy Scale [IAS, @murphy2019].
 The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological modality such as respiration (*"I can always accurately perceive when I am breathing fast"*), heart (e.g *"I can always accurately perceive when my heart is beating fast"*), skin (e.g *"I can always accurately perceive when something is going to be ticklish"*), arousal or bodily functions like coughing (e.g *"I can always accurately perceive when I am going to cough"*) or urinating (e.g.
@@
 
-The current study aims at 1) clarifying the structure of the IAS with a meta-analytic approach that leverages existing data and contrasts the traditional CFA/SEM factor-based analyses with graph-based ones such as EGA.
-2) The second part will provide an overview of the dispositional correlates of the IAS, sketching a pattern of associations that is key to better understand the nature, place and role of interoception questionnaires within a larger context.
+The current study aims at 1) clarifying the structure of the IAS with a meta-analytic approach that leverages existing data and contrast the traditional CFA/SEM factor-based analyses with network-based ones such as EGA.
+2) The second part will provide an overview of the dispositional correlates of the IAS, providing an overview of the pattern of associations that is key to better understand the nature, place and role of interoception questionnaires within a larger context.
 
@@
 While combining these studies might provide a more robust and generalizable understanding of the IAS' factor structure, it is important to note that the studies differ in their sample sizes, demographics, language, and the way they collected the data.
-Thus, providing additionally a individual analysis (i.e., on all samples individually) will help adding nuance to the general picture.
+Thus, providing additionally an individual analysis (i.e., on all samples individually) will help adding nuance to the general picture.
 
-### Method
+### Methods
 
@@
 
-## Statistical Analysis
+### Statistical Analysis
 
@@
 
-# Results
+### Results
 
@@
 
-### Correlations
+#### Correlations
 
@@
 
-### EGA
+#### EGA
 
@@
 
-# Discussion
+### Discussion
 
@@
 
-## Limitations and Future Directions
+### Limitations and Future Directions
 
@@
 
-## Methods
+### Methods
 
-### Materials
+#### Materials
 
@@
 
-### Statistical analysis
+#### Statistical analysis
 
@@
 
-## Results
+### Results
 
@@
 
-## Discussion
+### Discussion
 
@@
 
-# References
+## References
 
@@
 :::
-
-# Appendix
-
-# Title for Appendix

### 2025-01-02 paper/1_Initial/manuscript.qmd
minor

@@
       - ref: id1 
-keywords: []
+author-note:
+  disclosures:
+    gratitude: |
+      ::: {.callout-note icon=false appearance="simple"}
+      This preprint is a non-peer-reviewed work from the [**Reality Bending Lab**](https://realitybending.github.io/).
+      ![](https://realitybending.github.io/media/ReBeL_LogoOnly_hu11484441381606756729.png){width=20% fig-align="center"}
+      :::
+abstract: |
+  Blabla the abstract blabla.
+keywords: [keyword1, keyword2, keyword3]
 floatsintext: true

### 2025-01-03 analysis/Stud1_a.qmd
added Giulias data
rendered html with added data

@@
   - https://osf.io/mp3cy/
-
-```{r}
+  - note: Final.xlsx includes information about which participants passed the attention checks
+
+```{r}
+
+df5_attention <- readxl::read_excel("C:/Users/asf25/Documents/studies/InteroceptionIAS/data/Arslanova2022/Participants2.xlsx", 
+    sheet = "FINAL") |>
+  filter(ActorHR == 1) |>
+  select(Subj.ID, Gender, Age) |>
+  mutate(Gender = as.numeric(Gender), Age = as.numeric(Age)) |>
+  filter(!is.na(Age)) |> #error on the documentation of this participant - attention check failed but not noted
+  mutate(Gender = case_when(
+    Gender== 0 ~ "Male",
+    Gender== 1 ~ "Female" # based on paper reporting 65 women
+  ))
+
 df5 <- readxl::read_excel("../data/Arslanova2022/Murphy_Iacc_scale.xlsx")  |>
@@
          Muscles=TiredMuscles, Heart= FastHeart, Taste=Tastes) |> 
-  select(-starts_with("Participant")) |> 
-  mutate_all(as.numeric)
+  rename(Subj.ID = "Participant.Public.ID") |>
+  select(-starts_with("Participant"))
+
+df5 <- df5 |>
+  filter(Subj.ID %in% df5_attention$Subj.ID) |>
+  select(-Subj.ID) |>
+  mutate(across(everything(), as.numeric))
+
 ```
@@
   - Note: Analog scales
+  - note df10c = primals data
 
@@
 
+df10c <- read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionPrimals/refs/heads/main/data/data_participants.csv") |>
+  select("Participant" = "participant_id", "Gender", "Age", "Ethnicity", starts_with("IAS")) |>
+   rename(
+    Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
+    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
+    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
+    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
+    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
+  ) |>
+  filter(!is.na(Heart)) # participant is outlier and had total IAS scores below 0.4
+
+```
+
+### Sample 11
+
+- Giulia
+
+```{r}
+
+df11a <- df11a <- haven::read_sav("../data/Giulia/Interoceptive Attention ESM.sav") |> 
+  select(AGE, GENDER, contains("IAS_ACC"), -IAS_ACC_20) |>
+  mutate_all(as.numeric) |>
+  rename(
+    Age = AGE, Gender = GENDER,
+    Heart = IAS_ACC_1, Hungry = IAS_ACC_2, Breathing = IAS_ACC_3, Thirsty = IAS_ACC_4,
+    Urinate = IAS_ACC_5, Defecate = IAS_ACC_6, Taste = IAS_ACC_7, Vomit = IAS_ACC_8, Sneeze = IAS_ACC_9,
+    Cough = IAS_ACC_10, Temp = IAS_ACC_11, Sex_arousal = IAS_ACC_12, Wind = IAS_ACC_13, Burp = IAS_ACC_14,
+    Muscles = IAS_ACC_15, Bruise = IAS_ACC_16, Pain = IAS_ACC_17, Blood_Sugar = IAS_ACC_18,
+    Affective_touch = IAS_ACC_19, Tickle =IAS_ACC_21, Itch = IAS_ACC_22
+  ) |>
+   mutate(Gender = case_when(
+    Gender == 1 ~ "Male",
+    Gender == 2 ~ "Female",
+    Gender %in% c(3, 5) ~ "Other",
+    Gender == 4 ~ "NA"
+  ))
+
+df11b <- haven::read_sav("../data/Giulia/Sleep and Exteroceptive Interoceptive Sensitivity.sav") |> # 165 participants
+  filter(Total_Attention_Fail == 0) |> # 32 participants removed based on failing one or more checks
+  select(AGE, GENDER, contains("IAS_ACC")) |> 
+  mutate_all(as.numeric) |> 
+  rename( Age = AGE, Gender = GENDER, 
+          Heart = IAS_ACC_1, Hungry = IAS_ACC_2, Breathing = IAS_ACC_3, Thirsty = IAS_ACC_4, Urinate = IAS_ACC_5, Defecate = IAS_ACC_6, Taste = IAS_ACC_7,
+          Vomit = IAS_ACC_8, Sneeze = IAS_ACC_9, Cough = IAS_ACC_10, Temp = IAS_ACC_11, Sex_arousal = IAS_ACC_12, Wind = IAS_ACC_13, Burp = IAS_ACC_14,
+          Muscles = IAS_ACC_15, Bruise = IAS_ACC_16, Pain = IAS_ACC_17, Blood_Sugar = IAS_ACC_18, Affective_touch = IAS_ACC_19, Tickle =IAS_ACC_20, 
+          Itch = IAS_ACC_21 )  |> 
+  mutate(Gender = case_when(
+    Gender == 1 ~ "Male", 
+    Gender == 2 ~"Female", 
+    Gender %in% c(3, 5) ~ "Other", 
+    Gender == 4 ~ "NA", ))
+
 # Save all
-data <- list(df1a=df1a, df1b=df1b, df2=df2, df3=df3, df4=df4, df5=df5, df6=df6, df7a=df7a, df7b=df7b, df7c=df7c, df8a=df8a, df8b=df8b, df9=df9, df10a=df10a, df10b=df10b)
+data <- list(df1a=df1a, df1b=df1b, df2=df2, df3=df3, df4=df4, df5=df5, df6=df6, df7a=df7a, df7b=df7b, df7c=df7c, df8a=df8a, df8b=df8b, df9=df9, df10a=df10a, df10b=df10b, df10c=df10c, df11a=df11a, df11b=df11b)
 save(data, file = "../data/data.RData")
@@
 - **Sample 4**: Data from [Todd's(2022)]( https://osf.io/ms354/) study, downloaded from OSF, included `r report::report_participants(df4, age = "Age", sex = NA, gender = "Gender")`.
-- **Sample 5**: Data from [Arslanova (2022)](https://osf.io/mp3cy/) study, downloaded from OSF, included `r report::report_participants(df5, age = "Age", sex = NA, gender = "Gender")`.
+- **Sample 5**: Data from [Arslanova (2022)](https://osf.io/mp3cy/) study, downloaded from OSF, included `r report::report_participants(df5_attention, age = "Age", sex = NA, gender = "Gender")`.
 - **Sample 6**: Data from [Brand's(2022)](https://osf.io/xwz6g/) study, downloaded from OSF, included `r report::report_participants(df6, age = "Age", sex = NA, gender = "Gender")`.
@@
 - **Sample 10b**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10b, age = "Age", sex = NA, gender = "Gender")`.
-
-Total N = `r nrow(df1a) + nrow(df1b) + nrow(df2) + nrow(df3) + nrow(df4) + nrow(df5) + nrow(df6) + nrow(df7a) + nrow(df7b) + nrow(df7c) + nrow(df8a) + nrow(df8b) + nrow(df9) + nrow(df10a) + nrow(df10b)`.
+- **Sample 10c**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10c, age = "Age", sex = NA, gender = "Gender")`.
+-- **Sample 11a**: Data from [Giulia's (2024)](https://osf.io/49wbv) study , included `r report::report_participants(df11a, age = "Age", sex = NA, gender = "Gender")`
+- **Sample 11b**: Data from [Giulia] study , included `r report::report_participants(df11b, age = "Age", sex = NA, gender = "Gender")`
+
+Total N = `r nrow(df1a) + nrow(df1b) + nrow(df2) + nrow(df3) + nrow(df4) + nrow(df5) + nrow(df6) + nrow(df7a) + nrow(df7b) + nrow(df7c) + nrow(df8a) + nrow(df8b) + nrow(df9) + nrow(df10a) + nrow(df10b) + nrow(df10c) +nrow(df11a) + nrow(df11b)`.
 
@@
 #desc_df4 <- desc(df4)
-#desc_df5 <- desc(df5)
+desc_df5 <- desc(df5_attention)
 desc_df6 <- desc(df6)
@@
 desc_df10b <- desc(df10b)
-
-desc_total <- rbind(desc_df1a, desc_df1b, desc_df2, desc_df3, desc_df6, desc_df7a, desc_df7b, desc_df7c, desc_df8a, desc_df8b, desc_df9, desc_df10a, desc_df10b)
+desc_df10c <- desc(df10c)
+desc_df11a <- desc(df11a)
+desc_df11b <- desc(df11b)
+
+desc_total <- rbind(desc_df1a, desc_df1b, desc_df2, desc_df3, desc_df5, desc_df6, desc_df7a, desc_df7b, desc_df7c, desc_df8a, desc_df8b, desc_df9, desc_df10a, desc_df10b, desc_df10c, desc_df11a, desc_df11b)
 
@@
 table <- data.frame(
-  Sample = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Total'),
-  Subsample = c('', 'Sample 1', 'Sample 2', '', '', '', '', '', '', 'Sample 1', 'Sample 2', 'Sample 3', '', 'Sample 1', 'Sample 2', '', '', '', ''),   
-  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', ''),
-  N = c('', nrow(df1a), nrow(df1b), nrow(df2), nrow(df3), nrow(df4), 96, nrow(df6),'', nrow(df7a), nrow(df7b), 802,'', nrow(df8a), nrow(df8b), nrow(df9), nrow(df10a), nrow(df10b), 31317),
-  Age = c('', make_age(df1a$Age), make_age(df1b$Age), make_age(df2$Age), make_age(df3$Age), "TODO*", "TODO*", make_age(df6$Age),'', make_age(df7a$Age), make_age(df7b$Age), make_age(df7c$Age),'', make_age(df8a$Age), make_age(df8b$Age), make_age(df9$Age), make_age(df10a$Age), make_age(df10b$Age), 49.5),
-  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76', '17 - 93'),
-  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', NA, '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '71.5%'),
-  Availability= c('', '', 'https://osf.io/3m5nh', 'https://osf.io/5x9sg', 'https://osf.io/j6ef3', 'https://osf.io/ms354', 'https://osf.io/mp3cy', 'https://osf.io/xwz6g', '', '', 'https://osf.io/3f2h6', '','','', 'https://osf.io/3eztd', 'https://osf.io/7p9u5', 'https://github.com/RealityBending/IllusionGameReliability', 'https://github.com/DominiqueMakowski/PHQ4R', '')
+   Sample = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Makowski et al., (2023c)', 'Poreiro et al., (2024)', 'Poreiro et al., unpublished', 'Total'),
+  Subsample = c('', 'Sample 1', 'Sample 2', '', '', '', '', '', '', 'Sample 1', 'Sample 2', 'Sample 3', '', 'Sample 1', 'Sample 2', '', '', '', '', '','', ''),   
+  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', 'English', 'English', 'English',''),
+  N = c('', nrow(df1a), nrow(df1b), nrow(df2), nrow(df3), nrow(df4), nrow(df5_attention), nrow(df6),'', nrow(df7a), nrow(df7b), 802,'', nrow(df8a), nrow(df8b), nrow(df9), nrow(df10a), nrow(df10b), nrow(df10c), nrow(df11a), nrow(df11b), 32216),
+  Age = c('', make_age(df1a$Age), make_age(df1b$Age), make_age(df2$Age), make_age(df3$Age), "48.6.6 ± 14.1*", make_age(df5_attention$Age), make_age(df6$Age),'', make_age(df7a$Age), make_age(df7b$Age), make_age(df7c$Age),'', make_age(df8a$Age), make_age(df8b$Age), make_age(df9$Age), make_age(df10a$Age), make_age(df10b$Age), make_age(df10c$Age), make_age(df11a$Age), make_age(df11b$Age), '48.6 ± 13.1'),
+  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76','18-50', '18-57', '18-60', '17-93'),
+  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', '50%*', '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '76%', '74.8%', '75.9%', '71.6'),
+  Availability= c('', '', 'https://osf.io/3m5nh', 'https://osf.io/5x9sg', 'https://osf.io/j6ef3', 'https://osf.io/ms354', 'https://osf.io/mp3cy', 'https://osf.io/xwz6g', '', '', 'https://osf.io/3f2h6', '','','', 'https://osf.io/3eztd', 'https://osf.io/7p9u5', 'https://github.com/RealityBending/IllusionGameReliability', 'https://github.com/DominiqueMakowski/PHQ4R', 'https://github.com/RealityBending/InteroceptionPrimals', 'https://osf.io/49wbv', '','')
 )
@@
   cols_label(Age = "Age (Mean  ± SD)", Female_Percentage = "Female %") |> 
-  tab_footnote("* Information copied from the sample description rather than recomputed.") |> 
+  tab_footnote("* Information taken from the sample description of relevant paper rather than recomputed.") |> 
   gt_apastyle()
@@
          x = datawizard::rescale(x, to=c(1, 5), range=c(0, 1)))
-
-p1 <- rbind(dens1a, dens1b, dens2, dens3, dens4, dens5, dens6, dens7a, dens7b, dens7c, dens8a, dens8b, dens9, dens10a, dens10b) |>
-  mutate(Sample = fct_relevel(Sample, "Sample 1a", "Sample 1b", "Sample 2", "Sample 3", "Sample 4", "Sample 5", "Sample 6", "Sample 7a", "Sample 7b", "Sample 7c", "Sample 8a", "Sample 8b", "Sample 9", "Sample 10a", "Sample 10b")) |>
+dens10c <- estimate_density(select(df10c, all_of(vars)), method = "kernSmooth") |>
+  mutate(Sample = "Sample 10c",
+         x = datawizard::rescale(x, to=c(1, 5), range=c(0, 1)))
+dens11a <- estimate_density(select(df11a, all_of(vars)), method = "kernSmooth") |>
+  mutate(Sample = "Sample 11a")
+dens11b <- estimate_density(select(df11b, all_of(vars)), method = "kernSmooth") |>
+  mutate(Sample = "Sample 11b")
+
+p1 <- rbind(dens1a, dens1b, dens2, dens3, dens4, dens5, dens6, dens7a, dens7b, dens7c, dens8a, dens8b, dens9, dens10a, dens10b, dens10c, dens11a, dens11b) |>
+  mutate(Sample = fct_relevel(Sample, "Sample 1a", "Sample 1b", "Sample 2", "Sample 3", "Sample 4", "Sample 5", "Sample 6", "Sample 7a", "Sample 7b", "Sample 7c", "Sample 8a", "Sample 8b", "Sample 9", "Sample 10a", "Sample 10b", "Sample 10c", "Sample 11a", "Sample 11b")) |>
   # mutate(Dashed = ifelse(Parameter %in% c("Affective_touch", "Blood_Sugar", "Bruise"), TRUE, FALSE)) |> 
@@
 data10b <- select(df10b, all_of(dens10b$Parameter))
+data10c <- select(df10c, all_of(dens10c$Parameter))
+data11a <- normalize(select(df11a, all_of(dens11a$Parameter)), range = c(1, 5))
+data11b <- na.omit(normalize(select(df11b, all_of(dens11b$Parameter)), range = c(1, 5)))
+row.names(data11b) <- NULL
 
@@
   mutate(data8a, Tickle = NA), mutate(data8b, Tickle = NA), data9,
-  mutate(data10a, Taste = NA, Cough = NA, Blood_Sugar = NA), data10b
+  mutate(data10a, Taste = NA, Cough = NA, Blood_Sugar = NA),  data10b,  data10c, data11a, data11b
 ) 
@@
 
+#### Sample 10c
+
+```{r}
+make_correlation(data10c)
+```
+
+#### Sample 11a
+
+```{r}
+make_correlation(data11a)
+```
+
+#### Sample 11b
+
+```{r}
+make_correlation(data11b)
+```
+
 :::
@@
 uva <- EGAnet::UVA(data = data10b, cut.off = 0.3)
+uva
+uva$keep_remove
+```
+
+#### Sample 10c
+
+```{r}
+uva <- EGAnet::UVA(data = data10c, cut.off = 0.3)
+uva
+uva$keep_remove
+```
+
+#### Sample 11a
+
+```{r}
+uva <- EGAnet::UVA(data = data11a, cut.off = 0.3)
+uva
+uva$keep_remove
+```
+
+#### Sample 11b
+
+```{r}
+uva <- EGAnet::UVA(data = data11b, cut.off = 0.3)
 uva
@@
 
+#### Sample 10c
+
+```{r ega10c}
+#| fig-height: 20
+#| fig-width: 12
+
+egas10c <- make_egas(data10c)
+egas10c$p
+```
+
+#### Sample 11a
+
+```{r ega11a}
+#| fig-height: 20
+#| fig-width: 12
+
+egas11a <- make_egas(data11a)
+egas11a$p
+```
+
+#### Sample 11b
+
+```{r ega11c}
+#| fig-height: 20
+#| fig-width: 12
+
+egas11b <- make_egas(data11b)
+egas11b$p
+```
+
 :::
@@
 patchwork::wrap_plots(lapply(egas10b$egas, plot), nrow = 3)
+```
+
+#### Sample 10c
+
+```{r}
+#| fig-height: 20
+#| fig-width: 12
+
+patchwork::wrap_plots(lapply(egas10c$egas, plot), nrow = 3)
+```
+
+#### Sample 11a
+
+```{r}
+#| fig-height: 20
+#| fig-width: 12
+
+patchwork::wrap_plots(lapply(egas11a$egas, plot), nrow = 3)
+```
+
+#### Sample 11b
+
+```{r}
+#| fig-height: 20
+#| fig-width: 12
+
+patchwork::wrap_plots(lapply(egas11b$egas, plot), nrow = 3)
 ```
@@
 ega_scores_10b <- get_scores(data10b, ega)
+ega_scores_10c <- get_scores(data10c, ega)
+ega_scores_11a <- get_scores(data11a, ega)
+ega_scores_11b <- na.omit(get_scores(data11b, ega)) # remove two rows with NAS
+row.names(ega_scores_11b) <- NULL
 ```
@@
 
+#### Sample 10c
+
+```{r}
+n <- parameters::n_factors(data10c, n_max = 12)
+
+plot(n)
+knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
+```
+
+#### Sample 11a
+
+```{r}
+n <- parameters::n_factors(data11a, n_max = 12)
+
+plot(n)
+knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
+```
+
+#### Sample 11b
+
+```{r}
+n <- parameters::n_factors(data11b, n_max = 12)
+
+plot(n)
+knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
+```
 :::
@@
 efa4 <- parameters::factor_analysis(data10b, n = 4, rotation = "oblimin", sort = TRUE)
+plot(efa4)
+
+display(efa4)
+```
+
+#### Sample 10c
+
+```{r}
+#| fig-height: 10
+
+efa4 <- parameters::factor_analysis(data10c, n = 4, rotation = "oblimin", sort = TRUE)
+plot(efa4)
+
+display(efa4)
+```
+
+#### Sample 11a
+
+```{r}
+#| fig-height: 10
+
+efa4 <- parameters::factor_analysis(data11a, n = 4, rotation = "oblimin", sort = TRUE)
+plot(efa4)
+
+display(efa4)
+```
+
+#### Sample 11b
+
+```{r}
+#| fig-height: 10
+
+efa4 <- parameters::factor_analysis(data11b, n = 4, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
+#### Sample 10c
+
+```{r}
+#| warning: false
+
+display(compare_mods(data10c))
+
+```
+
+#### Sample 11a
+
+```{r}
+#| warning: false
+
+display(compare_mods(data11a))
+
+```
+
+#### Sample 11b
+
+```{r}
+#| warning: false
+
+display(compare_mods(data11b))
+
+```
+
 :::
@@
 display(compare_mods_h(data10b))
+```
+
+#### Sample 10c
+
+```{r}
+display(compare_mods_h(data10c))
+```
+
+#### Sample 11a
+
+```{r}
+display(compare_mods_h(data11a))
+```
+
+#### Sample 11b
+
+```{r}
+display(compare_mods_h(data11b))
 ```
@@
   performance::performance(update(m7_all, data = data10b), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
-    mutate(Sample = "Sample 10b")
+    mutate(Sample = "Sample 10b"),
+  performance::performance(update(m7_all, data = data10c), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
+    mutate(Sample = "Sample 10c"),
+  performance::performance(update(m7_all, data = data11a), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
+    mutate(Sample = "Sample 11a"),
+  performance::performance(update(m7_all, data = data11b), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
+    mutate(Sample = "Sample 11b")
 ) |>
@@
     add_empirical(data10b) |> 
-    mutate(Sample = "Sample 10b")
+    mutate(Sample = "Sample 10b"),
+  sample10c = cbind(ega_scores_10c, data_addprefix(as.data.frame(predict(m7_all, newdata=data10c)), "CFA_")) |>
+    add_empirical(data10c) |> 
+    mutate(Sample = "Sample 10c"),
+  sample11a = cbind(ega_scores_11a, data_addprefix(as.data.frame(predict(m7_all, newdata=data11a)), "CFA_")) |>
+    add_empirical(data11a) |> 
+    mutate(Sample = "Sample 11a"),
+  sample11b = cbind(ega_scores_11b, data_addprefix(as.data.frame(predict(m7_all, newdata=data11b)), "CFA_")) |>
+    add_empirical(data11b) |> 
+    mutate(Sample = "Sample 11b")
 )

### 2025-01-03 analysis/figures/table1.tex
rendered html with added data

@@
-\setlength{\LTpost}{0mm}
-\begin{longtable}{lllrrrrl}
+\begin{table}[!t]
+\fontsize{9.0pt}{10.8pt}\selectfont
+\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}lllrrrrl}
 \toprule
@@
 Campos et al., (2022) &  & Portuguese & 515 & 30.7 ± 10.5 & 18-72 & 59.6\% & https://osf.io/j6ef3 \\ 
-Todd et al., (2022) &  & English & 802 & TODO* & 18-92* & NA & https://osf.io/ms354 \\ 
-Arslanova et al., (2022) &  & English & 96 & TODO* & 18-73 & 46.8\% & https://osf.io/mp3cy \\ 
+Todd et al., (2022) &  & English & 802 & 48.6.6 ± 14.1* & 18-92* & 50\%* & https://osf.io/ms354 \\ 
+Arslanova et al., (2022) &  & English & 143 & 28.5 ± 7.6 & 18-73 & 46.8\% & https://osf.io/mp3cy \\ 
 Brand et al., (2022) &  & German & 619 & 43.9 ± 14.5 & 18-78 & 78.7\% & https://osf.io/xwz6g \\ 
@@
 Makowski et al., (2023a) &  & English & 485 & 30.1 ± 10.1 & 18-73 & 50.3\% & https://github.com/RealityBending/IllusionGameReliability \\ 
-Makowski et al., (2023b) &  & English & 251 & 37.5 ± 13.2 & 17-76 & 53.0\% & https://github.com/DominiqueMakowski/PHQ4R \\ 
-Total &  &  & 31317 & 49.5 & 17 - 93 & 71.5\% &  \\ 
+Makowski et al., (2023b) &  & English & 836 & 25.1 ± 11.3 & 17-76 & 53.0\% & https://github.com/DominiqueMakowski/PHQ4R \\ 
+Makowski et al., (2023c) &  & English & 104 & 21.6 ± 5.0 & 18-50 & 76\% & https://github.com/RealityBending/InteroceptionPrimals \\ 
+Poreiro et al., (2024) &  & English & 107 & 26.8 ± 9.2 & 18-57 & 74.8\% & https://osf.io/49wbv \\ 
+Poreiro et al., unpublished &  & English & 133 & 30.8 ± 12.0 & 18-60 & 75.9\% &  \\ 
+Total &  &  & 32216 & 48.6 ± 13.1 & 17-93 & 71.6 &  \\ 
 \bottomrule
-\end{longtable}
+\end{tabular*}
 \begin{minipage}{\linewidth}
-* Information copied from the sample description rather than recomputed.\\
+* Information taken from the sample description of relevant paper rather than recomputed.\\
 \end{minipage}
+\end{table}

### 2025-01-06 analysis/figures/table1.tex
rendered correlation html + added data to correlations script

@@
 Poreiro et al., (2024) &  & English & 107 & 26.8 ± 9.2 & 18-57 & 74.8\% & https://osf.io/49wbv \\ 
-Poreiro et al., unpublished &  & English & 133 & 30.8 ± 12.0 & 18-60 & 75.9\% &  \\ 
+Poreiro et al., unpublished &  & English & 131 & 30.9 ± 12.0 & 18-60 & 75.9\% &  \\ 
 Total &  &  & 32216 & 48.6 ± 13.1 & 17-93 & 71.6 &  \\ 

### 2025-01-06 analysis/study2.qmd
rendered correlation html + added data to correlations script

--- 2024-02-26 analysis/study2.qmd
@@
 df10b <- cbind(data$df10b, scores$sample10b)
+df10c <- cbind(data$df10c, scores$sample10c)
+df11a <- cbind(data$df11a, scores$sample11a)
+df11b <- cbind(data$df11b, scores$sample11b)
 
@@
 # names(df10b)  # BDI, STAI, PHQ4
+# names(df10c) # PI, MAIA
+# names(df11a) # MAIA, TAS, MFQ(DEP), STAI(ANX)
+# names(df11b) 
 ```
@@
   select(df10a, all_of(vars_scores)),
-  select(df10b, all_of(vars_scores))
+  select(df10b, all_of(vars_scores)),
+  select(df10c, all_of(vars_scores)),
+  select(df11a, all_of(vars_scores)),
+  select(df11b, all_of(vars_scores))
 )
@@
   make_diff(df3, vars_intero, component="Demographic"),
-  # make_diff(df4, vars_intero, component="Demographic"),
-  # make_diff(df5, vars_intero, component="Demographic"),
+  #make_diff(df4, vars_intero, component="Demographic"),
+  #make_diff(df5_attention, vars_intero, component="Demographic"),
   make_diff(df6, vars_intero, component="Demographic"),
@@
   make_diff(df10a, vars_intero, component="Demographic"),
-  make_diff(df10b, vars_intero, component="Demographic")
+  make_diff(df10b, vars_intero, component="Demographic"),
+  make_diff(df10c, vars_intero, component="Demographic"),
+  make_diff(df11a, vars_intero, component="Demographic"),
+  make_diff(df11b, vars_intero, component="Demographic")
 ) |>
@@
   make_cor(df10a, vars_intero, with = "Age", component="Demographic"),
-  make_cor(df10b, vars_intero, with = "Age", component="Demographic")
+  make_cor(df10b, vars_intero, with = "Age", component="Demographic"),
+  make_cor(df10c, vars_intero, with = "Age", component="Demographic"),
+  make_cor(df11a, vars_intero, with = "Age", component="Demographic"),
+  make_cor(df11b, vars_intero, with = "Age", component="Demographic")
 )
@@
 names(df10a)[str_detect(names(df10b), "MAIA")]
+names(df10c)[str_detect(names(df10c), "MAIA")]
+names(df11a)[str_detect(names(df11b), "MAIA")]
 
@@
   make_cor(df10a, vars_intero, with = "MAIA_Trusting", component="MAIA") |>
+    mutate(var_Correlate = "Trusting"),
+
+  # df10c 
+  make_cor(df10c, vars_intero, with = "MAIA_AttentionRegulation", component="MAIA")  |>
+    mutate(var_Correlate = "Attention Regulation"),
+  make_cor(df10c, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
+    mutate(var_Correlate = "Listening"),
+  make_cor(df10c, vars_intero, with = "MAIA_EmotionalAwareness", component="MAIA") |>
+    mutate(var_Correlate = "Emotional Awareness"),
+  make_cor(df10c, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
+    mutate(var_Correlate = "Not Distracting"),
+  make_cor(df10c, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
+    mutate(var_Correlate = "Noticing"),
+  make_cor(df10c, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
+    mutate(var_Correlate = "Not Worrying"),
+  make_cor(df10c, vars_intero, with = "MAIA_SelfRegulation", component="MAIA") |>
+    mutate(var_Correlate = "Self Regulation"),
+  make_cor(df10c, vars_intero, with = "MAIA_Trusting", component="MAIA") |>
+    mutate(var_Correlate = "Trusting"),
+
+    # df11a
+  make_cor(df11a, vars_intero, with = "MAIA_Attention", component="MAIA")  |>
+    mutate(var_Correlate = "Attention Regulation"),
+  make_cor(df11a, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
+    mutate(var_Correlate = "Listening"),
+  make_cor(df11a, vars_intero, with = "MAIA_Emotional", component="MAIA") |>
+    mutate(var_Correlate = "Emotional Awareness"),
+  make_cor(df11a, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
+    mutate(var_Correlate = "Not Distracting"),
+  make_cor(df11a, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
+    mutate(var_Correlate = "Noticing"),
+  make_cor(df11a, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
+    mutate(var_Correlate = "Not Worrying"),
+  make_cor(df11a, vars_intero, with = "MAIA_SelfRegulation", component="MAIA") |>
+    mutate(var_Correlate = "Self Regulation"),
+  make_cor(df11a, vars_intero, with = "MAIA_Trusting", component="MAIA") |>
     mutate(var_Correlate = "Trusting")
@@
 names(df8b)[str_starts(names(df8b), "TAS")]
+names(df11a)[str_starts(names(df11a), "TAS")]
 
@@
     mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
+  make_cor(df11a, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
+    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
+  make_cor(df11a, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
+    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
+  make_cor(df11a, vars_intero, with = "TAS_EOT", component="Alexithymia") |>
+    mutate(var_Correlate = "External Thinking (TAS)"),
   # BVAQ
@@
 names(df9)
+names(df11a)
 
@@
   make_cor(df10b, vars_intero, with = "BDI2_Total", component="Mood") |>
-    mutate(var_Correlate = "Depression (BDI)")
+    mutate(var_Correlate = "Depression (BDI)"),
+  make_cor(df11a, vars_intero, with = "DEP", component = "Mood") |>
+    mutate(var_Correlate = "Depression (MFQ)")
 )
@@
   make_cor(df10b, vars_intero, with = "STAI5_General", component="Mood") |>
+    mutate(var_Correlate = "Anxiety (STAI)"),
+  make_cor(df11a, vars_intero, with =  "ANX", component = "Mood") |>
     mutate(var_Correlate = "Anxiety (STAI)")
@@
   make_cor(df10a, vars_intero, with = "PI_Understandable", component="World Beliefs") |>
+    mutate(var_Correlate = "Understandable"),
+  make_cor(df10c, vars_intero, with = "PI_Alive", component="World Beliefs") |>
+    mutate(var_Correlate = "Alive"),
+  make_cor(df10c, vars_intero, with = "PI_Changing", component="World Beliefs") |>
+    mutate(var_Correlate = "Changing"),
+  make_cor(df10c, vars_intero, with = "PI_Enticing", component="World Beliefs") |>
+    mutate(var_Correlate = "Enticing"),
+  make_cor(df10c, vars_intero, with = "PI_Good", component="World Beliefs") |>
+    mutate(var_Correlate = "Good"),
+  make_cor(df10c, vars_intero, with = "PI_Hierarchical", component="World Beliefs") |>
+    mutate(var_Correlate = "Hierarchical"),
+  make_cor(df10c, vars_intero, with = "PI_Safe", component="World Beliefs") |>
+    mutate(var_Correlate = "Safe"),
+  make_cor(df10c, vars_intero, with = "PI_Understandable", component="World Beliefs") |>
     mutate(var_Correlate = "Understandable")
@@
   facet_grid(Component ~ var_Interoception, scales = "free_y", switch = "y") +
-  coord_flip(ylim = c(-0.45, 0.45)) +
+  coord_flip(ylim = c(-0.7, 0.7)) +
   theme_modern(axis.title.space = 5) +

### 2025-01-06 analysis/Stud1_a.qmd
Update Stud1_a.qmd

@@
     Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
-    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
+    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
+    typeSample = Sample
   )
@@
 df10c <- read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionPrimals/refs/heads/main/data/data_participants.csv") |>
-  select("Participant" = "participant_id", "Gender", "Age", "Ethnicity", starts_with("IAS")) |>
+  select("Participant" = "participant_id", "Gender", "Age", "Ethnicity", starts_with(c("IAS","MAIA","PI"))) |>
    rename(
@@
 
+```{r}
+pi_vars <- c("PI_Enticing", "PI_Alive", "PI_Safe", "PI_Good", "PI_Changing", 
+             "PI_Hierarchical", "PI_Understandable", "PI_AboutMe", "PI_Abundant", 
+             "PI_Acceptable", "PI_Beautiful", "PI_Cooperative", "PI_Funny", 
+             "PI_Harmless", "PI_Improvable", "PI_Intentional", "PI_Interconnected", 
+             "PI_Interesting", "PI_Just", "PI_Meaningful", "PI_NeedsMe", 
+             "PI_Pleasurable", "PI_Progressing", "PI_Regenerative", "PI_Stable", 
+             "PI_WorthExploring")
+
+correlation::correlation(
+  df10c[, "IAS_Total", drop = FALSE],  
+  data2 = select(df10c, all_of(pi_vars)), 
+) |> 
+  # Formatting correlation results
+  mutate(val = paste0(insight::format_value(r), format_p(p, stars_only = TRUE))) |>
+
+  # Releveling factors for visualization
+  mutate(Parameter2 = fct_relevel(Parameter2, rev(pi_vars)),
+         Parameter1 = fct_relevel(Parameter1, "IAS_Total")) |>
+
+  # Plotting the correlation matrix
+  ggplot(aes(x = Parameter1, y = Parameter2)) +
+  geom_tile(aes(fill = r), color = "white") +  
+  geom_text(aes(label = val), size = 3) +  
+  labs(title = "Correlation Matrix") +
+  scale_fill_gradient2(low = "blue", high = "red", mid = "white", limit = c(-1, 1), midpoint = 0, guide = guide_colourbar(ticks = FALSE)) +  
+  theme_minimal() +
+  theme(
+    legend.title = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank(),
+    axis.text.x = element_text(hjust = 1)
+  )
+```
+
 ### Sample 11
@@
 - Giulia
-
-```{r}
-
-df11a <- df11a <- haven::read_sav("../data/Giulia/Interoceptive Attention ESM.sav") |> 
-  select(AGE, GENDER, contains("IAS_ACC"), -IAS_ACC_20) |>
+  - note: anx_21 , tas20_21 are attention checks
+
+```{r}
+
+df11a <- haven::read_sav("../data/Giulia/Interoceptive Attention ESM.sav") |> 
+  select(AGE, GENDER, contains("IAS_ACC"), -IAS_ACC_20, starts_with(c("MAIA", "TAS20", "DEP", "ANX")),  -ANX_21, -TAS20_21) |>
   mutate_all(as.numeric) |>
@@
     Gender == 4 ~ "NA"
-  ))
+  )) |> ## compute dimensions for the TAS
+  mutate(TAS_DIF = TAS20_1 + TAS20_3 + TAS20_6 + TAS20_7 + TAS20_9 + TAS20_13 + TAS20_14,
+         TAS_DDF = TAS20_2 + (1-TAS20_4) + TAS20_11 + TAS20_12 + TAS20_17,
+         TAS_EOT = (1-TAS20_5) + TAS20_8 + (1-TAS20_10) + TAS20_15 + TAS20_16 + (1-TAS20_18) + (1-TAS20_19) + TAS20_20)
 
@@
   filter(Total_Attention_Fail == 0) |> # 32 participants removed based on failing one or more checks
-  select(AGE, GENDER, contains("IAS_ACC")) |> 
+  select(AGE, GENDER, contains("IAS_ACC"), ) |> 
   mutate_all(as.numeric) |> 
@@
     Gender %in% c(3, 5) ~ "Other", 
-    Gender == 4 ~ "NA", ))
+    Gender == 4 ~ "NA", )) |>
+  na.omit()
 
@@
 data11a <- normalize(select(df11a, all_of(dens11a$Parameter)), range = c(1, 5))
-data11b <- na.omit(normalize(select(df11b, all_of(dens11b$Parameter)), range = c(1, 5)))
+data11b <- na.omit(normalize(select(df11b, all_of(dens11b$Parameter)), range = c(1, 5))) # remove NAS
 row.names(data11b) <- NULL

### 2025-01-06 analysis/Stud1_a.qmd
quick changes

@@
 
-- Giulia
-  - note: anx_21 , tas20_21 are attention checks
+- Poreiro et al., 
+  - Study 1: https://osf.io/49wbv
+  - Study 2: unpublished
 
@@
 df11a <- haven::read_sav("../data/Giulia/Interoceptive Attention ESM.sav") |> 
-  select(AGE, GENDER, contains("IAS_ACC"), -IAS_ACC_20, starts_with(c("MAIA", "TAS20", "DEP", "ANX")),  -ANX_21, -TAS20_21) |>
+  select(AGE, GENDER, contains("IAS_ACC"), -IAS_ACC_20, starts_with(c("MAIA", "TAS20", "DEP", "ANX")),  -ANX_21, -TAS20_21) |> #anx_21 , tas20_21 are attention checks
   mutate_all(as.numeric) |>
@@
 - **Sample 10c**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10c, age = "Age", sex = NA, gender = "Gender")`.
--- **Sample 11a**: Data from [Giulia's (2024)](https://osf.io/49wbv) study , included `r report::report_participants(df11a, age = "Age", sex = NA, gender = "Gender")`
+- **Sample 11a**: Data from [Giulia's (2024)](https://osf.io/49wbv) study , included `r report::report_participants(df11a, age = "Age", sex = NA, gender = "Gender")`
 - **Sample 11b**: Data from [Giulia] study , included `r report::report_participants(df11b, age = "Age", sex = NA, gender = "Gender")`

### 2025-01-07 analysis/figures/table1.tex
Update table1.tex

@@
 Poreiro et al., unpublished &  & English & 131 & 30.9 ± 12.0 & 18-60 & 75.9\% &  \\ 
-Total &  &  & 32216 & 48.6 ± 13.1 & 17-93 & 71.6 &  \\ 
+Total &  &  & 32214 & 48.6 ± 13.1 & 17-93 & 71.6 &  \\ 
 \bottomrule

### 2025-01-08 paper/1_Initial/manuscript.qmd
update to the manuscript

@@
 
-knitr::include_graphics("figures/measuring_interoception.png")
+knitr::include_graphics("1_Initial/figures/MeasuringInteroception.png")
 ```
@@
 
+<!-- what most recent paper? -->
+
 For instance, while the use of self-reports questionnaires to measure an embodied function might seem paradoxical, recent redefinitions of interoception, emphasizing the role of high-level and metacognitive elaboration of interoceptive information, has provided the theoretical grounding to support the idea that some facets of interoception (including participants' metacognitive beliefs) can be assessed subjectively, providing useful and interesting measures [@murphy2019] [**TODO: also cite the most recent paper**].
-The notion that self-reports might not reflect the same processes as other interoception measures is important to contextualize the apparent lack of convergence between measures in the field **(REF)**.
+The notion that self-reports might not reflect the same processes as other interoception measures is important to contextualize the apparent lack of convergence between measures in the field [@desmedt2022measures].
 Still, a better understanding of what is being measured with different questionnaires and dimensions, as well their potential overlaps with other constructs (e.g., alexithymia, body awareness) is needed to clarify the role of self-reports in the assessment of interoception.
@@
 
+<!-- was the second reference asked for the MAIA, the MAIA-2 ? -->
+
 A recently developed scale with a rapidly growing popularity is the Interoceptive Accuracy Scale [IAS, @murphy2019].
@@
 *"I can always accurately perceive when I need to urinate"*).
-Interestingly, the IAS' statements are about specific interoceptive behaviours, which is a notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012; **SECOND REF**], which contains more general and metacognitive items (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*).
+Interestingly, the IAS' statements are about specific interoceptive behaviours, which is a notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012; MAIA-2, @mehling2018multidimensional], which contains more general and metacognitive items (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*).
 
@@
 Other follow-up studies using confirmatory factor analysis (CFA) and structural modeling [@morin2016] have identified different optimal solutions. 
-Some studies, like @brand2023, reported a 1-factor solution, while @lin2023 and @campos2021 found bifactor solutions **(i.e., QUICK DESCRIPTION)** to be the best fit.
+Some studies, like @brand2023, reported a 1-factor solution, while @lin2023 and @campos2021 found bifactor solutions - one general factor and a set of lowe-level factors (@rodriguez2016evaluating) - to be the best fit.
 
@@
 119).
-@lin2023 also highlights their correlation analysis, showing five locally dependent pairs and three items **(WHICH ONES)** with exceptionally high difficulty and low discrimination. 
+@lin2023 also highlights their correlation analysis, showing five locally dependent pairs and three items (touch, blood sugar, bruise) with exceptionally high difficulty and low discrimination. 
 Additionally, @campos2021 suggests that the "tickle" item represents a more specific factor.
-Interestingly, @lin2023 reported that all items of the IAS grouped together using a new approach, Exploratory Graph Analysis (EGA) **[REFS]**, to assess convergent and discriminant validity, which suggests unidimensionality.
+Interestingly, @lin2023 reported that all items of the IAS grouped together using a new approach, Exploratory Graph Analysis [EGA; @golino2017exploratory], to assess convergent and discriminant validity, which suggests unidimensionality.
 
@@
 
-While the assessment of the validity of an interoception scale can be conceived as theoretically challenging, several traits have been used to assess convergent validity for the the IAS, including expected negative associations with alexithymia [@brand2023; @koike2023; @campos2023, @murphy2019], somatic symptoms [@brand2023; @koike2023], depressive symptoms [@brand2023; @koike2023], anxiety [@brand2023], neuroticism [@brand2023].
-<!-- **anything else?**. TO BE COMPLETED -->
-The IAS has also been compared to other interoception scales (and interoceptive related scales), yielding a positive correlation with most facets of the MAIA, with the notable exception of *Non distracting* and *Not worrying* subscales [@brand2023], the body awareness dimension of the Body Perception Questionnaire [BPQ-A; @brand2023; @campos2021; @koike2023; @lin2023], the observation and description scales of the Five Facet Mindfulness Questionnaire [FFMQ **what is ref?**; @ref, @brand2023], the interoceptive awareness subscale of the Eating Disorder Inventory [@lin2023] and a negative correlation with the interoceptive confusion questionnaire [@brand2023] **[I don't think this is the correct ref]**, IATS [@lin2023; @murphy2019].
-<!-- What about the iats? -->
+While the assessment of the validity of an interoception scale can be conceived as theoretically challenging, several traits have been used to assess convergent validity for the the IAS, including expected negative associations with alexithymia [@brand2023; @koike2023; @campos2023, @murphy2019; @lin2023], somatic symptoms [@brand2023; @koike2023], depressive symptoms [@brand2023; @koike2023], anxiety [@brand2023], neuroticism [@brand2023].
+<!-- **anything else?**. TO BE COMPLETED -- to be determined -->
+
+The IAS has also been compared to other interoception scales (and interoceptive related scales),generally showing positive correlations with most facets of the MAIA, except for the Non-Distracting and Not-Worrying subscales [@brand2023].
+Findings on the correlation between the IAS and the body awareness dimension of the Body Perception Questionnaire (BPQ-A; @porges1993body) have been mixed: some studies report small positive correlations [@brand2023; @campos; @koike2023], while others find small negative correlations [@lin2023] or no correlation at all [@murphy2019].
+Small positive correlations have also been observed with the observation and description subscales of the Five Facet Mindfulness Questionnaire (FFMQ, @baer2006using; @brand2023; @koike2023), as well as with the nonreactivity and acting with awareness subscales [@koike2023].
+Additionally, the IAS has shown a positive correlation with the interoceptive awareness subscale of the Eating Disorder Inventory [@lin2023] and a negative correlation with the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia; @brand2023; @murphy2019].
+Lastly, small positive correlations have been reported between the Interoceptive Attention Scale (IATS, @gabriele2022dissociations) and the IAS [@lin2023; @koike2023], though studies have also found no correlation between these measures [@gabriele2022dissociations].
+
 <!-- TO BE COMPLETED -->
@@
 
-*Note.* MAIA-2 Multidimensional Assessment of Interoceptive Awareness Version-2; BPQ Body Perception Questionnaire (Mehling et al.
-2018); TAS-20 Toronto Alexithymia Scale (Bagby et al., 1994); BVAQ Bermond-Vorst Alexithymia Questionnaire (Vorst & Bermond, 2001); BDI-II Beck's Depression Inventory (Dozois et al., 1998); PHQ-4 Patient Health Questionnaire (Kroenke et al., 2009); STAI-T State-Trait-Anxiety Inventory Trait-Version (Spielberger et al.
+*Note.* MAIA-2 Multidimensional Assessment of Interoceptive Awareness Version-2 (Mehling et al.
+2018); BPQ Body Perception Questionnaire; TAS-20 Toronto Alexithymia Scale (Bagby et al., 1994); BVAQ Bermond-Vorst Alexithymia Questionnaire (Vorst & Bermond, 2001); BDI-II Beck's Depression Inventory (Dozois et al., 1998); PHQ-4 Patient Health Questionnaire (Kroenke et al., 2009); STAI-T State-Trait-Anxiety Inventory Trait-Version (Spielberger et al.
 1970); GAD- 2 Generalized Anxiety Disorder Scale – 2 (Spitzer et al., 2007); NEO-FFI NEO Five-Factor Inventory Neuroticism (Costa & McCrae, 2008); Mini IPIP6 Mini International Personality Item Pool (Sibley et al.

### 2025-01-10 analysis/Stud1_a.qmd

@@
 
-df5_attention <- readxl::read_excel("C:/Users/asf25/Documents/studies/InteroceptionIAS/data/Arslanova2022/Participants2.xlsx", 
+df5_attention <- readxl::read_excel("../data/Arslanova2022/Participants2.xlsx", 
     sheet = "FINAL") |>
@@
   df10c[, "IAS_Total", drop = FALSE],  
-  data2 = select(df10c, all_of(pi_vars)), 
+  data2 = select(df10c, all_of(pi_vars)), p_adjust = "none"
 ) |> 
@@
 - **Sample 10c**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10c, age = "Age", sex = NA, gender = "Gender")`.
-- **Sample 11a**: Data from [Giulia's (2024)](https://osf.io/49wbv) study , included `r report::report_participants(df11a, age = "Age", sex = NA, gender = "Gender")`
-- **Sample 11b**: Data from [Giulia] study , included `r report::report_participants(df11b, age = "Age", sex = NA, gender = "Gender")`
+- **Sample 11a**: Data from [Poreiro's(2024)](https://osf.io/49wbv) study , included `r report::report_participants(df11a, age = "Age", sex = NA, gender = "Gender")`
+- **Sample 11b**: Data from [Poreiro's] study , included `r report::report_participants(df11b, age = "Age", sex = NA, gender = "Gender")`
 

### 2025-01-14 analysis/Stud1_a.qmd
updated manuscript

@@
   Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', 'English', 'English', 'English',''),
-  N = c('', nrow(df1a), nrow(df1b), nrow(df2), nrow(df3), nrow(df4), nrow(df5_attention), nrow(df6),'', nrow(df7a), nrow(df7b), 802,'', nrow(df8a), nrow(df8b), nrow(df9), nrow(df10a), nrow(df10b), nrow(df10c), nrow(df11a), nrow(df11b), 32216),
+  N = c('', nrow(df1a), nrow(df1b), nrow(df2), nrow(df3), nrow(df4), nrow(df5_attention), nrow(df6),'', nrow(df7a), nrow(df7b), 802,'', nrow(df8a), nrow(df8b), nrow(df9), nrow(df10a), nrow(df10b), nrow(df10c), nrow(df11a), nrow(df11b), 32214),
+  'Difference' = c('','', '', '', '', '', '', '', '', '', '', '', '', 'Collapsed "Itch" and "Tingling"', 'Collapsed "Itch" and "Tingling"', '', 'Analog scales', 'Analog scales', 'Analog scales', '', '', ''),
   Age = c('', make_age(df1a$Age), make_age(df1b$Age), make_age(df2$Age), make_age(df3$Age), "48.6.6 ± 14.1*", make_age(df5_attention$Age), make_age(df6$Age),'', make_age(df7a$Age), make_age(df7b$Age), make_age(df7c$Age),'', make_age(df8a$Age), make_age(df8b$Age), make_age(df9$Age), make_age(df10a$Age), make_age(df10b$Age), make_age(df10c$Age), make_age(df11a$Age), make_age(df11b$Age), '48.6 ± 13.1'),
   Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76','18-50', '18-57', '18-60', '17-93'),
-  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', '50%*', '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '76%', '74.8%', '75.9%', '71.6'),
+  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', '50%*', '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '76%', '74.8%', '75.9%', '71.6%'),
   Availability= c('', '', 'https://osf.io/3m5nh', 'https://osf.io/5x9sg', 'https://osf.io/j6ef3', 'https://osf.io/ms354', 'https://osf.io/mp3cy', 'https://osf.io/xwz6g', '', '', 'https://osf.io/3f2h6', '','','', 'https://osf.io/3eztd', 'https://osf.io/7p9u5', 'https://github.com/RealityBending/IllusionGameReliability', 'https://github.com/DominiqueMakowski/PHQ4R', 'https://github.com/RealityBending/InteroceptionPrimals', 'https://osf.io/49wbv', '','')
@@
 gtsave(table_apa, "figures/table1.tex")
+gtsave(table_apa, "figures/table1.png")
 ```
@@
 
-p1 <- rbind(dens1a, dens1b, dens2, dens3, dens4, dens5, dens6, dens7a, dens7b, dens7c, dens8a, dens8b, dens9, dens10a, dens10b, dens10c, dens11a, dens11b) |>
+p1_data <- rbind(dens1a, dens1b, dens2, dens3, dens4, dens5, dens6, dens7a, dens7b, dens7c, dens8a, dens8b, dens9, dens10a, dens10b, dens10c, dens11a, dens11b)
+
+# proportion of non-1 and non-5 values 
+p1_data |>
+  filter(x > 1 & x < 5) |>  # Keep only x values strictly between 1 and 5
+  summarise(proportion = sum(y) / sum(p1_data$y))  # Normalize by total density
+
+p1 <- p1_data |>
   mutate(Sample = fct_relevel(Sample, "Sample 1a", "Sample 1b", "Sample 2", "Sample 3", "Sample 4", "Sample 5", "Sample 6", "Sample 7a", "Sample 7b", "Sample 7c", "Sample 8a", "Sample 8b", "Sample 9", "Sample 10a", "Sample 10b", "Sample 10c", "Sample 11a", "Sample 11b")) |>
@@
         plot.title = element_text(face="bold")) +
-  labs(title = "Distribution of responses for all items across various datasets", x = "Response", y = "Density", color = "Item") +
+  labs(x = "Response", y = "Density", color = "Item") +
   facet_wrap(~Sample, scales = "free_y", nrow = 5)

### 2025-01-14 analysis/figures/table1.tex
changes to script
updated manuscript

@@
-\begin{table}[!t]
+\begin{table}
 \fontsize{9.0pt}{10.8pt}\selectfont
-\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}lllrrrrl}
+\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}lllrlrrrl}
 \toprule
-Sample & Subsample & Language & N & Age (Mean  ± SD) & Range & Female \% & Availability \\ 
+Sample & Subsample & Language & N & Difference & Age (Mean  ± SD) & Range & Female \% & Availability \\ 
 \midrule\addlinespace[2.5pt]
-Murphy et al., (2020) &  &  &  &  &  &  &  \\ 
- & Sample 1 & English & 451 & 25.8 ± 8.4 & 18-69 & 69.4\% &  \\ 
- & Sample 2 & English & 375 & 35.3 ± 16.9 & 18-91 & 70.1\% & https://osf.io/3m5nh \\ 
-Gaggero et al., (2021) &  & English and Italian & 814 & 24.9 ± 5.3 & 18-58 & 60.3\% & https://osf.io/5x9sg \\ 
-Campos et al., (2022) &  & Portuguese & 515 & 30.7 ± 10.5 & 18-72 & 59.6\% & https://osf.io/j6ef3 \\ 
-Todd et al., (2022) &  & English & 802 & 48.6.6 ± 14.1* & 18-92* & 50\%* & https://osf.io/ms354 \\ 
-Arslanova et al., (2022) &  & English & 143 & 28.5 ± 7.6 & 18-73 & 46.8\% & https://osf.io/mp3cy \\ 
-Brand et al., (2022) &  & German & 619 & 43.9 ± 14.5 & 18-78 & 78.7\% & https://osf.io/xwz6g \\ 
-Brand et al., (2023) &  &  &  &  &  &  &  \\ 
- & Sample 1 & German & 522 & 23.4 ± 6.7 & 18-79 & 79.5\% &  \\ 
- & Sample 2 & German & 1993 & 32.0 ± 12.6 & 16-81 & 77.7\% & https://osf.io/3f2h6 \\ 
- & Sample 3 & German & 802 & 27.3 ± 9.3 & 18-72 & 68.9\% &  \\ 
-Lin et al., (2023) &  &  &  &  &  &  &  \\ 
- & Sample 1 & Chinese & 1166 & 32.5 ± 8.4 & 16-60 & 57.0\% &  \\ 
- & Sample 2 & Chinese & 500 & 37.4 ± 7.4 & 20-60 & 56.2\% & https://osf.io/3eztd \\ 
-VonMohr et al., (2023) &  & English & 21843 & 56.5 ± 14.4 & 18-93 & 73.2\% & https://osf.io/7p9u5 \\ 
-Makowski et al., (2023a) &  & English & 485 & 30.1 ± 10.1 & 18-73 & 50.3\% & https://github.com/RealityBending/IllusionGameReliability \\ 
-Makowski et al., (2023b) &  & English & 836 & 25.1 ± 11.3 & 17-76 & 53.0\% & https://github.com/DominiqueMakowski/PHQ4R \\ 
-Makowski et al., (2023c) &  & English & 104 & 21.6 ± 5.0 & 18-50 & 76\% & https://github.com/RealityBending/InteroceptionPrimals \\ 
-Poreiro et al., (2024) &  & English & 107 & 26.8 ± 9.2 & 18-57 & 74.8\% & https://osf.io/49wbv \\ 
-Poreiro et al., unpublished &  & English & 131 & 30.9 ± 12.0 & 18-60 & 75.9\% &  \\ 
-Total &  &  & 32214 & 48.6 ± 13.1 & 17-93 & 71.6 &  \\ 
+Murphy et al., (2020) &  &  &  &  &  &  &  &  \\ 
+ & Sample 1 & English & 451 &  & 25.8 ± 8.4 & 18-69 & 69.4\% &  \\ 
+ & Sample 2 & English & 375 &  & 35.3 ± 16.9 & 18-91 & 70.1\% & https://osf.io/3m5nh \\ 
+Gaggero et al., (2021) &  & English and Italian & 814 &  & 24.9 ± 5.3 & 18-58 & 60.3\% & https://osf.io/5x9sg \\ 
+Campos et al., (2022) &  & Portuguese & 515 &  & 30.7 ± 10.5 & 18-72 & 59.6\% & https://osf.io/j6ef3 \\ 
+Todd et al., (2022) &  & English & 802 &  & 48.6.6 ± 14.1* & 18-92* & 50\%* & https://osf.io/ms354 \\ 
+Arslanova et al., (2022) &  & English & 143 &  & 28.5 ± 7.6 & 18-73 & 46.8\% & https://osf.io/mp3cy \\ 
+Brand et al., (2022) &  & German & 619 &  & 43.9 ± 14.5 & 18-78 & 78.7\% & https://osf.io/xwz6g \\ 
+Brand et al., (2023) &  &  &  &  &  &  &  &  \\ 
+ & Sample 1 & German & 522 &  & 23.4 ± 6.7 & 18-79 & 79.5\% &  \\ 
+ & Sample 2 & German & 1993 &  & 32.0 ± 12.6 & 16-81 & 77.7\% & https://osf.io/3f2h6 \\ 
+ & Sample 3 & German & 802 &  & 27.3 ± 9.3 & 18-72 & 68.9\% &  \\ 
+Lin et al., (2023) &  &  &  &  &  &  &  &  \\ 
+ & Sample 1 & Chinese & 1166 & Collapsed "Itch" and "Tingling" & 32.5 ± 8.4 & 16-60 & 57.0\% &  \\ 
+ & Sample 2 & Chinese & 500 & Collapsed "Itch" and "Tingling" & 37.4 ± 7.4 & 20-60 & 56.2\% & https://osf.io/3eztd \\ 
+VonMohr et al., (2023) &  & English & 21843 &  & 56.5 ± 14.4 & 18-93 & 73.2\% & https://osf.io/7p9u5 \\ 
+Makowski et al., (2023a) &  & English & 485 & Analog scales & 30.1 ± 10.1 & 18-73 & 50.3\% & https://github.com/RealityBending/IllusionGameReliability \\ 
+Makowski et al., (2023b) &  & English & 836 & Analog scales & 25.1 ± 11.3 & 17-76 & 53.0\% & https://github.com/DominiqueMakowski/PHQ4R \\ 
+Makowski et al., (2023c) &  & English & 104 & Analog scales & 21.6 ± 5.0 & 18-50 & 76\% & https://github.com/RealityBending/InteroceptionPrimals \\ 
+Poreiro et al., (2024) &  & English & 107 &  & 26.8 ± 9.2 & 18-57 & 74.8\% & https://osf.io/49wbv \\ 
+Poreiro et al., unpublished &  & English & 131 &  & 30.9 ± 12.0 & 18-60 & 75.9\% &  \\ 
+Total &  &  & 32214 &  & 48.6 ± 13.1 & 17-93 & 71.6\% &  \\ 
 \bottomrule

### 2025-01-14 paper/1_Initial/manuscript.qmd
updated manuscript

@@
 
-knitr::include_graphics("1_Initial/figures/MeasuringInteroception.png")
+knitr::include_graphics("figures/MeasuringInteroception.jpg")
 ```
@@
 
-While the assessment of the validity of an interoception scale can be conceived as theoretically challenging, several traits have been used to assess convergent validity for the the IAS, including expected negative associations with alexithymia [@brand2023; @koike2023; @campos2023, @murphy2019; @lin2023], somatic symptoms [@brand2023; @koike2023], depressive symptoms [@brand2023; @koike2023], anxiety [@brand2023], neuroticism [@brand2023].
+While the assessment of the validity of an interoception scale can be conceived as theoretically challenging, several traits have been used to assess convergent validity for the the IAS, including expected negative associations with alexithymia [@brand2023; @koike2023; @campos2021, @murphy2019; @lin2023], somatic symptoms [@brand2023; @koike2023], depressive symptoms [@brand2023; @koike2023], anxiety [@brand2023], neuroticism [@brand2023].
 <!-- **anything else?**. TO BE COMPLETED -- to be determined -->
@@
 The IAS has also been compared to other interoception scales (and interoceptive related scales),generally showing positive correlations with most facets of the MAIA, except for the Non-Distracting and Not-Worrying subscales [@brand2023].
-Findings on the correlation between the IAS and the body awareness dimension of the Body Perception Questionnaire (BPQ-A; @porges1993body) have been mixed: some studies report small positive correlations [@brand2023; @campos; @koike2023], while others find small negative correlations [@lin2023] or no correlation at all [@murphy2019].
+Findings on the correlation between the IAS and the body awareness dimension of the Body Perception Questionnaire (BPQ-A; @porges1993body) have been mixed: some studies report small positive correlations [@brand2023; @campos2021; @koike2023], while others find small negative correlations [@lin2023] or no correlation at all [@murphy2019].
 Small positive correlations have also been observed with the observation and description subscales of the Five Facet Mindfulness Questionnaire (FFMQ, @baer2006using; @brand2023; @koike2023), as well as with the nonreactivity and acting with awareness subscales [@koike2023].
@@
 
-Our search focused on studies citing the original IAS validation paper [@murphy2019], identifying 136 papers (as of **XX/XX/2024**).
+Our search focused on studies citing the original IAS validation paper [@murphy2019], identifying 136 papers (as of 01/05/2024).
 To qualify for inclusion, papers needed to (1) provide accessible data in open-access, (2) employ the IAS as a measure, and (3) report individual IAS items scores.
-A total of **XX** studies was included.
-We also included the data of two unpublished (but already open-access) studies from the authors.
-The total N participants was 31,317 participants (Mean SD, 71.5% Female).
+A total of 10  studies was included.
+We also included the data of two unpublished (but already open-access) studies from the authors and one from another author.
+The total N participants was 32,214 participants (*Mean* = 48.6 years, *SD* = 13.1, 71.6% Female).
 See @tbl-samples for a summary of the samples demographics.
@@
 #| label: tbl-samples
-#| tbl-cap: "Blabla caption for Samples demographics"
-# #| apa-note: "Some note bedlow the table"
+#| tbl-cap: "Samples demographics"
+#| apa-note: "Some note bedlow the table"
+
+knitr::include_graphics("figures/table1.png")
 
@@
 
+<!-- This only works when redering to pdf right? -->
 \tiny 
@@
 
-**TODO: add language also, as well as maybe something like "difference" from the original validation (which could actually be language, and for our the type of scale / less items)** <!-- **TODO: add links to GH for our studies** -->
-
 ### Statistical Analysis
@@
 To examine the factor structure of the IAS, a two-step approach was employed.
-First, Exploratory Graph Analysis (EGA), was used to estimate the dimensions via network estimation and community detection, alongside assessing the stability of dimensions and items using the bootstrapping techniques.
+First, Exploratory Graph Analysis (EGA), was used to estimate the dimensions via network estimation and community detection, alongside assessing the stability of dimensions and items using the bootstrapping techniques [@golino2017exploratory].
 The selection of EGA was motivated by its capability to handle complex, multidimensional data and provide robust dimension estimates.
+A novel network psychometrics - Unique variable analysis [UVA; @christensen2023unique] - approach based on the weighted topological overlap will be computed to evaluate which items have substantial local dependence (> 0.25).
 Subsequently, exploratory factor analysis (EFA) was employed followed by confirmatory factor analysis (CFA).
@@
 
-Visualizing the distribution of the items for all samples suggests the presence of a consistent modal value (Fig. X).
+Visualizing the distribution of the items for all samples suggests the presence of a consistent modal value (@fig-distributions).
 In other words, participants are most likely to answer 4/5 (i.e., agree) on most items (but "affective touch", "blood sugar", and "bruise" that exhibit a different distributional pattern).
-Additionally, one can note the low density on extreme values (1 and 5), meaning that the bulk of answers **(87% TODO: get the actual statistic: what's the proportion of non 1&5 answers for the likert scale samples)** varies between 3 values.
+Additionally, one can note the low density on extreme values (1 and 5), meaning that the bulk of answers (i.e., 99%%) varies between 3 values.
 The interindividual variability seems improved in the samples using an analogue scale, displaying a more continuous and progressive spread of answers.
 
-![**Figure 1.** Distribution of responses for all items across all datasets.](figures/clipboard-1080495164.png){width="723"}
+```{r}
+#| warning: false
+#| label: fig-distributions
+#| fig-cap: "Distribution of responses for all items across various datasets."
+# #| fig-width:
+# #| apa-note: "Some note bedlow the table"
+
+knitr::include_graphics("figures/Figure1.png")
+
+```
 
@@
 
-The unique variable analysis revealed that there are two redundant variables when taking all samples into account.
-Namely, "itch" and "tickle", where "tickle" should be removed, and "itch" should remain in the questionnaire.
+The UVA revealed that there are two large to very large redundant variables when taking all samples into account.
+Namely, "itch" and "tickle", where "tickle" should be removed, and "itch" should be kept. 
 There are several more items that are moderately to largely redundant, namely, "wind" and "burp", and "urinate" and "defecate".
 On top of that, "sneeze" and "cough", "heart" and "breathing", and "hungry" and "thirsty" seem to have small to moderate redundancy.
-These findings are rather consistent across the samples with minor differences, such as that when the questionnaire had an analog scale, there seems to be no redundant items.
+These findings are rather consistent across the samples with minor differences, such as that when the questionnaire had an analog scale, there seems to be no large to very large redundant items but "itch" and "tickle" remain moderately to largely redundant and "heart" and "breathing" small to moderately redundant in one sample.
 
-According to the network analysis, a 4-factor structure fits the questionnaire best across all data sets.
+According to the network analysis, using the Walktrap and Louvain algorithms applied to Glasso networks, a 4-factor structure fits the questionnaire best across all data sets.
 This is rather consistent within the data sets, where some samples indicate 3-factor structure, and some a 5-factor structure would fit well too.
@@
 Stability analysis, employing 500 bootstrap iterations, also favoured the 4-factor solution for its greater stability.
-Most items, except for 'affective touch,' demonstrated stability levels exceeding 0.70, indicating structural consistency and reliability [@christensen2021].
+Most items, except for 'affective touch,' demonstrated stability levels exceeding 0.90, indicating structural consistency and reliability [@christensen2021].
 These findings underscore the robustness of the identified 4-dimensional structure.
@@
 When accounting for all samples, the factor analysis reveals that a 4-factor structure fits best.
-The exploratory factor analysis revealed that 4 latent factors (oblimin rotation) accounted for 41.67% of 5the total variance of the original data (MR1 = 14.64%, MR3 = 11.59%, MR4 = 7.30%).
-Confirmatory factor analysis showed that the time "tickle" can be discarded, as it was flagged as redundant in the samples consistently.
-Some of the factors were ambiguous, namely, temperature, vomit, effective touch, sexual arousal, as well as taste.
+The exploratory factor analysis revealed that 4 latent factors (oblimin rotation) accounted for 51.95% of the total variance of the original data (MR2 = 19.08%, MR1 = 17.78%, MR4 = 9.34%, MR3 = 5.75%).
+Since UVA identified "tickle" as the item to be removed—and it also had the lowest uniqueness value in factor analysis with a similar loading to "itch"—"tickle" was excluded from subsequent analyses.
+
+Confirmatory factor analysis compared 5 models: a single-factor solution, a 4-factor solution, a 5-factor solution, a 6-factor solution and a 7-factor solution.
+The latter was preferred in most datasets, including with indices that penalise increased number of parameters (such as BIC).
 There was no evidence for higher order factors.
@@
 Previous work has also shown that the itch and tickle items are subject to redundancy [@lin2023, @campos2021] has shown.
-Interestingly, @campos2021 suggest removin the tickle item instead.
+Interestingly, @campos2021 suggest removing the tickle item instead.
 @lin2023 on the other hand removed the itch item, because the sign for itch and tickle is the same.

### 2025-01-14 paper/1_Initial/manuscript.qmd
remove weird characters

@@
 format:
+  apaquarto-pdf:
+    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
+    documentmode: jou
   apaquarto-docx: default
   apaquarto-html: default
-  apaquarto-pdf:
-    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
-    documentmode: man
 editor: 
@@
 #| fig-cap: "Different ways in which interoception can be measured."
+#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
+#| out-width: "100%"
 
@@
 
-For instance, while the use of self-reports questionnaires to measure an embodied function might seem paradoxical, recent redefinitions of interoception, emphasizing the role of high-level and metacognitive elaboration of interoceptive information, has provided the theoretical grounding to support the idea that some facets of interoception (including participants' metacognitive beliefs) can be assessed subjectively, providing useful and interesting measures [@murphy2019] [**TODO: also cite the most recent paper**].
+For instance, while the use of self-reports questionnaires to measure an embodied function might seem paradoxical, recent redefinitions of interoception, emphasizing the role of high-level and metacognitive elaboration of interoceptive information, has provided the theoretical grounding to support the idea that some facets of interoception (including participants' metacognitive beliefs) can be assessed subjectively, providing useful and interesting measures [@murphy2019] [**TODO: also cite the most recent paper OF MURPHY with the chinese**].
 The notion that self-reports might not reflect the same processes as other interoception measures is important to contextualize the apparent lack of convergence between measures in the field [@desmedt2022measures].
@@
 ```{r}
-#| warning: false
 #| label: tbl-samples
 #| tbl-cap: "Samples demographics"
-#| apa-note: "Some note bedlow the table"
+#| apa-note: "Some note below the table"
 
 knitr::include_graphics("figures/table1.png")
-
 ```

### 2025-01-15 analysis/Stud1_a.qmd
remove https

@@
       column_labels.border.bottom.style = "solid",
-      column_labels.border.bottom.width = 1
+      column_labels.border.bottom.width = 1,
+      latex.use_longtable = FALSE
     ) |> 
@@
   Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', '50%*', '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '76%', '74.8%', '75.9%', '71.6%'),
-  Availability= c('', '', 'https://osf.io/3m5nh', 'https://osf.io/5x9sg', 'https://osf.io/j6ef3', 'https://osf.io/ms354', 'https://osf.io/mp3cy', 'https://osf.io/xwz6g', '', '', 'https://osf.io/3f2h6', '','','', 'https://osf.io/3eztd', 'https://osf.io/7p9u5', 'https://github.com/RealityBending/IllusionGameReliability', 'https://github.com/DominiqueMakowski/PHQ4R', 'https://github.com/RealityBending/InteroceptionPrimals', 'https://osf.io/49wbv', '','')
+  Availability= c('', '', 'osf.io/3m5nh', 'osf.io/5x9sg', 'osf.io/j6ef3', 'osf.io/ms354', 'osf.io/mp3cy', 'osf.io/xwz6g', '', '', 'osf.io/3f2h6', '','','', 'osf.io/3eztd', 'osf.io/7p9u5', 'github.com/RealityBending/IllusionGameReliability', 'github.com/DominiqueMakowski/PHQ4R', 'github.com/RealityBending/InteroceptionPrimals', 'osf.io/49wbv', '','')
 )
@@
   cols_label(Age = "Age (Mean  ± SD)", Female_Percentage = "Female %") |> 
-  tab_footnote("* Information taken from the sample description of relevant paper rather than recomputed.") |> 
-  gt_apastyle()
-
-table_apa
-gtsave(table_apa, "figures/table1.tex")
-gtsave(table_apa, "figures/table1.png")
+  tab_footnote("* Information taken from the sample description of relevant paper rather than recomputed.")
+
+gt_apastyle(table_apa, font.size=12)
+gtsave(gt_apastyle(table_apa, font.size=9), "figures/table1.tex")
+
+# gtsave(table_apa, "figures/table1.png")
 ```

### 2025-01-15 analysis/Stud1_a.qmd
put links as first

@@
   Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', '50%*', '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '76%', '74.8%', '75.9%', '71.6%'),
-  Availability= c('', '', 'osf.io/3m5nh', 'osf.io/5x9sg', 'osf.io/j6ef3', 'osf.io/ms354', 'osf.io/mp3cy', 'osf.io/xwz6g', '', '', 'osf.io/3f2h6', '','','', 'osf.io/3eztd', 'osf.io/7p9u5', 'github.com/RealityBending/IllusionGameReliability', 'github.com/DominiqueMakowski/PHQ4R', 'github.com/RealityBending/InteroceptionPrimals', 'osf.io/49wbv', '','')
+  Availability= c('osf.io/3m5nh', '', '', 'osf.io/5x9sg', 'osf.io/j6ef3', 'osf.io/ms354', 'osf.io/mp3cy', 'osf.io/xwz6g', 'osf.io/3f2h6', '', '', '','osf.io/3eztd','', '', 'osf.io/7p9u5', 'github.com/RealityBending/IllusionGameReliability', 'github.com/DominiqueMakowski/PHQ4R', 'github.com/RealityBending/InteroceptionPrimals', 'osf.io/49wbv', '','')
 )

### 2025-01-15 analysis/figures/table1.tex
put links as first

@@
-\begin{table}
-\fontsize{9.0pt}{10.8pt}\selectfont
+\begin{table}[!t]
+\fontsize{6.8pt}{8.1pt}\selectfont
 \begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}lllrlrrrl}
@@
 \midrule\addlinespace[2.5pt]
-Murphy et al., (2020) &  &  &  &  &  &  &  &  \\ 
+Murphy et al., (2020) &  &  &  &  &  &  &  & osf.io/3m5nh \\ 
  & Sample 1 & English & 451 &  & 25.8 ± 8.4 & 18-69 & 69.4\% &  \\ 
- & Sample 2 & English & 375 &  & 35.3 ± 16.9 & 18-91 & 70.1\% & https://osf.io/3m5nh \\ 
-Gaggero et al., (2021) &  & English and Italian & 814 &  & 24.9 ± 5.3 & 18-58 & 60.3\% & https://osf.io/5x9sg \\ 
-Campos et al., (2022) &  & Portuguese & 515 &  & 30.7 ± 10.5 & 18-72 & 59.6\% & https://osf.io/j6ef3 \\ 
-Todd et al., (2022) &  & English & 802 &  & 48.6.6 ± 14.1* & 18-92* & 50\%* & https://osf.io/ms354 \\ 
-Arslanova et al., (2022) &  & English & 143 &  & 28.5 ± 7.6 & 18-73 & 46.8\% & https://osf.io/mp3cy \\ 
-Brand et al., (2022) &  & German & 619 &  & 43.9 ± 14.5 & 18-78 & 78.7\% & https://osf.io/xwz6g \\ 
-Brand et al., (2023) &  &  &  &  &  &  &  &  \\ 
+ & Sample 2 & English & 375 &  & 35.3 ± 16.9 & 18-91 & 70.1\% &  \\ 
+Gaggero et al., (2021) &  & English and Italian & 814 &  & 24.9 ± 5.3 & 18-58 & 60.3\% & osf.io/5x9sg \\ 
+Campos et al., (2022) &  & Portuguese & 515 &  & 30.7 ± 10.5 & 18-72 & 59.6\% & osf.io/j6ef3 \\ 
+Todd et al., (2022) &  & English & 802 &  & 48.6.6 ± 14.1* & 18-92* & 50\%* & osf.io/ms354 \\ 
+Arslanova et al., (2022) &  & English & 143 &  & 28.5 ± 7.6 & 18-73 & 46.8\% & osf.io/mp3cy \\ 
+Brand et al., (2022) &  & German & 619 &  & 43.9 ± 14.5 & 18-78 & 78.7\% & osf.io/xwz6g \\ 
+Brand et al., (2023) &  &  &  &  &  &  &  & osf.io/3f2h6 \\ 
  & Sample 1 & German & 522 &  & 23.4 ± 6.7 & 18-79 & 79.5\% &  \\ 
- & Sample 2 & German & 1993 &  & 32.0 ± 12.6 & 16-81 & 77.7\% & https://osf.io/3f2h6 \\ 
+ & Sample 2 & German & 1993 &  & 32.0 ± 12.6 & 16-81 & 77.7\% &  \\ 
  & Sample 3 & German & 802 &  & 27.3 ± 9.3 & 18-72 & 68.9\% &  \\ 
-Lin et al., (2023) &  &  &  &  &  &  &  &  \\ 
+Lin et al., (2023) &  &  &  &  &  &  &  & osf.io/3eztd \\ 
  & Sample 1 & Chinese & 1166 & Collapsed "Itch" and "Tingling" & 32.5 ± 8.4 & 16-60 & 57.0\% &  \\ 
- & Sample 2 & Chinese & 500 & Collapsed "Itch" and "Tingling" & 37.4 ± 7.4 & 20-60 & 56.2\% & https://osf.io/3eztd \\ 
-VonMohr et al., (2023) &  & English & 21843 &  & 56.5 ± 14.4 & 18-93 & 73.2\% & https://osf.io/7p9u5 \\ 
-Makowski et al., (2023a) &  & English & 485 & Analog scales & 30.1 ± 10.1 & 18-73 & 50.3\% & https://github.com/RealityBending/IllusionGameReliability \\ 
-Makowski et al., (2023b) &  & English & 836 & Analog scales & 25.1 ± 11.3 & 17-76 & 53.0\% & https://github.com/DominiqueMakowski/PHQ4R \\ 
-Makowski et al., (2023c) &  & English & 104 & Analog scales & 21.6 ± 5.0 & 18-50 & 76\% & https://github.com/RealityBending/InteroceptionPrimals \\ 
-Poreiro et al., (2024) &  & English & 107 &  & 26.8 ± 9.2 & 18-57 & 74.8\% & https://osf.io/49wbv \\ 
+ & Sample 2 & Chinese & 500 & Collapsed "Itch" and "Tingling" & 37.4 ± 7.4 & 20-60 & 56.2\% &  \\ 
+VonMohr et al., (2023) &  & English & 21843 &  & 56.5 ± 14.4 & 18-93 & 73.2\% & osf.io/7p9u5 \\ 
+Makowski et al., (2023a) &  & English & 485 & Analog scales & 30.1 ± 10.1 & 18-73 & 50.3\% & github.com/RealityBending/IllusionGameReliability \\ 
+Makowski et al., (2023b) &  & English & 836 & Analog scales & 25.1 ± 11.3 & 17-76 & 53.0\% & github.com/DominiqueMakowski/PHQ4R \\ 
+Makowski et al., (2023c) &  & English & 104 & Analog scales & 21.6 ± 5.0 & 18-50 & 76\% & github.com/RealityBending/InteroceptionPrimals \\ 
+Poreiro et al., (2024) &  & English & 107 &  & 26.8 ± 9.2 & 18-57 & 74.8\% & osf.io/49wbv \\ 
 Poreiro et al., unpublished &  & English & 131 &  & 30.9 ± 12.0 & 18-60 & 75.9\% &  \\ 

### 2025-01-15 paper/1_Initial/manuscript.qmd
format

@@
     # Can be jou (journal), man (manuscript), stu (student), or doc (document)
-    documentmode: jou
+    documentmode: man
   apaquarto-docx: default
@@
 To qualify for inclusion, papers needed to (1) provide accessible data in open-access, (2) employ the IAS as a measure, and (3) report individual IAS items scores.
-A total of 10  studies was included.
+A total of 10 studies was included (see **Table 1**).
 We also included the data of two unpublished (but already open-access) studies from the authors and one from another author.
 The total N participants was 32,214 participants (*Mean* = 48.6 years, *SD* = 13.1, 71.6% Female).
-See @tbl-samples for a summary of the samples demographics.
-
-```{r}
-#| label: tbl-samples
-#| tbl-cap: "Samples demographics"
-#| apa-note: "Some note below the table"
-
-knitr::include_graphics("figures/table1.png")
-```
 
 <!-- This only works when redering to pdf right? -->
-\tiny 
 \input{../../analysis/figures/table1.tex}
-\normalsize
 
-### Statistical Analysis
+#### Statistical Analysis
 
@@
 In other words, participants are most likely to answer 4/5 (i.e., agree) on most items (but "affective touch", "blood sugar", and "bruise" that exhibit a different distributional pattern).
-Additionally, one can note the low density on extreme values (1 and 5), meaning that the bulk of answers (i.e., 99%%) varies between 3 values.
+Additionally, one can note the low density on extreme values (1 and 5), meaning that the bulk of answers (i.e., 99\%) varies between 3 values.
 The interindividual variability seems improved in the samples using an analogue scale, displaying a more continuous and progressive spread of answers.
@@
 #| fig-cap: "Distribution of responses for all items across various datasets."
-# #| fig-width:
-# #| apa-note: "Some note bedlow the table"
 
 knitr::include_graphics("figures/Figure1.png")
-
 ```

### 2025-01-15 paper/1_Initial/manuscript.qmd
intro points

@@
 
-For instance, while the use of self-reports questionnaires to measure an embodied function might seem paradoxical, recent redefinitions of interoception, emphasizing the role of high-level and metacognitive elaboration of interoceptive information, has provided the theoretical grounding to support the idea that some facets of interoception (including participants' metacognitive beliefs) can be assessed subjectively, providing useful and interesting measures [@murphy2019] [**TODO: also cite the most recent paper OF MURPHY with the chinese**].
-The notion that self-reports might not reflect the same processes as other interoception measures is important to contextualize the apparent lack of convergence between measures in the field [@desmedt2022measures].
-Still, a better understanding of what is being measured with different questionnaires and dimensions, as well their potential overlaps with other constructs (e.g., alexithymia, body awareness) is needed to clarify the role of self-reports in the assessment of interoception.
+For instance, while the use of subjective self-reports questionnaires to measure deeply embodied functions might seem paradoxical, recent redefinitions of interoception, emphasizing the role of high-level and metacognitive elaboration of interoceptive information, has provided the theoretical grounding to support the idea that some facets of interoception (including participants' metacognitive beliefs) can be assessed subjectively, providing useful and interesting measures [@murphy2019] [**TODO: also cite the most recent paper OF MURPHY with the chinese**].
+**TODO: that's a long sentence consider splitting**
+The notion that self-reports might not reflect the same processes as other interoception measures is important to contextualize the apparent lack of convergence between various measures in the field [@desmedt2022measures].
+A better understanding of what is being measured with different questionnaires and dimensions, as well their potential overlaps with other constructs (e.g., alexithymia, body awareness), is thus needed to clarify the role of self-reports in the assessment of interoception.
 
@@
 
-Although the original validation study suggested a two-factor solution structure, the authors underlines the need for further investigation of the scale's factor structure, as it provided acceptable but imperfect explanation of the data [@murphy2019; p.
-127].
+Although the original validation study suggested a two-factor structure for the IAS (**TODO: what are they?**), the authors underline its acceptable but imperfect fit [@murphy2019; p.
+127], calling on further investigation of the scale's factor structure.
 Notably, the only other validation study to report a 2-factor solution was conducted by @koike2023, who performed an Exploratory Factor Analysis (EFA) assuming 2 factors to align with the findings from the original validation paper.
+**TODO: this above is not really a validation study showing 2 factors is good if they prespecified two to match the original?**
 Other follow-up studies using confirmatory factor analysis (CFA) and structural modeling [@morin2016] have identified different optimal solutions. 
-Some studies, like @brand2023, reported a 1-factor solution, while @lin2023 and @campos2021 found bifactor solutions - one general factor and a set of lowe-level factors (@rodriguez2016evaluating) - to be the best fit.
+Some studies, like @brand2023, reported a 1-factor solution, while @lin2023 and @campos2021 found bifactor solutions - one general factor and a set of lower-level factors [@rodriguez2016evaluating] - to be the best fit.
+**TODO: what does morin2016 found? I would cite it after saying what they found rather than here**
 
@@
 @lin2023 also highlights their correlation analysis, showing five locally dependent pairs and three items (touch, blood sugar, bruise) with exceptionally high difficulty and low discrimination. 
-Additionally, @campos2021 suggests that the "tickle" item represents a more specific factor.
-Interestingly, @lin2023 reported that all items of the IAS grouped together using a new approach, Exploratory Graph Analysis [EGA; @golino2017exploratory], to assess convergent and discriminant validity, which suggests unidimensionality.
+Additionally, @campos2021 suggests that the "tickle" item represents a more specific *(separate?*) factor.
+Interestingly, @lin2023 reported that all items of the IAS grouped together using a new approach, Exploratory Graph Analysis [EGA; @golino2017exploratory], to assess convergent and discriminant validity, providing further evidence for unidimensionality.
 

### 2025-01-15 analysis/Study1.qmd
updated manuscript + added extension

--- 2025-01-15 analysis/Stud1_a.qmd
@@
 desc_df3 <- desc(df3)
-#desc_df4 <- desc(df4)
+#desc_df4 <- desc(df4) # no demographic data available
 desc_df5 <- desc(df5_attention)

### 2025-01-15 analysis/study2.qmd
updated manuscript + added extension

@@
 library(EGAnet)
+```
+
+## Measures used
+
+```{r}
+library(gt)
+
+# APA style ####
+gt_apastyle <- function(gt_table, font.size=12) {
+  gt_table  |> 
+    gt::opt_table_lines(extent = "none") %>%
+    gt::tab_options(
+      heading.border.bottom.width = 2,
+      heading.border.bottom.color = "black",
+      heading.border.bottom.style = "solid",
+      table.border.top.color = "black",
+      table.border.top.style = "solid",
+      table.border.top.width = 2,  
+      table_body.hlines.color = "white",
+      table_body.border.top.color = "black",
+      table_body.border.top.style = "solid",
+      table_body.border.top.width = 2,
+      heading.title.font.size = font.size,
+      table.font.size = font.size,
+      heading.subtitle.font.size = font.size,
+      table_body.border.bottom.color = "black",
+      table_body.border.bottom.width = 2,
+      table_body.border.bottom.style = "solid",
+      column_labels.border.bottom.color = "black",
+      column_labels.border.bottom.style = "solid",
+      column_labels.border.bottom.width = 1,
+      latex.use_longtable = FALSE
+    ) |> 
+      gt::opt_table_font(font = "times")
+}
+
+table <- data.frame(
+  Questionnaire = c("Interoceptive Related", "MAIA-2", "BPQ", "TAS-20", "BVAQ",
+                    "Mood", "BDI-II", "PHQ-4", "STAI-T", "GAD-2",
+                    "Personality", "NEO-FFI", "Mini IPIP6", "BFI", "PID-5-SF",
+                    "Psychopathology", "SPQ-BRU", "MSI-BPD", "ASQ - Short",
+                    "Beliefs and Misbeliefs", "GCB", "PI-18", "LIE scale"),
+  Number_of_Dimensions = c('', 8, 2, 3, 2, 
+                           '', 1, 2, 1, 1, 
+                           '', 1, 6, 5, 5, 
+                           '', 4, 1, 5, 
+                           '', 5, 1, 4),
+  Assessment = c('', "Interoception", "Body awareness and autonomic reactivity", "Alexithymia", "Alexithymia",
+                 '',"Severity of depressive symptoms", "Anxiety and depressive symptoms", "Trait anxiety", "General Anxiety",
+                 '', "Neuroticism", "Personality", "Personality", "Dysfunctional personality traits",
+                 '', "Schizotypy", "Borderline personality disorder", "Autistic Traits",
+                 '', "Conspiracy beliefs", "Beliefs about the world", "Lying tendencies"),
+  Number_of_Items = c('',37, 49, 20, 40, 
+                      '',21, 4, 20, 2, 
+                      '',12, 24, 44, 25, 
+                      '',32, 10, 28, 
+                      '',15, 99, 16),
+  Scoring = c('',"6-point Likert scale", "5-point Likert scale", "5-point Likert scale", "5-point Likert scale", 
+              '',"0-to-3-point values", "5-point Likert scale", "4-point Likert scale", "4-point Likert scale", 
+              '',"5-point Likert scale", "Analogue scales", "5-point Likert scale", "4-point Likert scale", 
+              '',"5-point Likert scale", "Analogue scales", "4-point Likert scale", 
+              '',"5-point Likert scale", "6-point Likert scale", "Visual analogue scales"), 
+  stringsAsFactors = FALSE
+)
+
+table_apa <- table |> 
+  gt() |>
+  cols_align(align = c("right"), columns = "Scoring") |> 
+  cols_label(Number_of_Dimensions = "Number of Dimensions", Number_of_Items = "Number of Items")  |>
+  # tab_footnote("* Information taken from the sample description of relevant paper rather than recomputed.") 
+  tab_style( style = list(cell_text(weight = "bold")), locations = cells_body(columns = Questionnaire, rows = Questionnaire %in% c("Interoceptive Related", "Mood", "Personality", "Psychopathology", "Beliefs and Misbeliefs")))
+
+gt_apastyle(table_apa, font.size=12)
+gtsave(gt_apastyle(table_apa, font.size=9), "figures/table2.tex")
 ```

### 2025-01-15 paper/1_Initial/manuscript.tex
updated manuscript + added extension

@@
 \documentclass[
-  jou,
+  man,
   floatsintext,
   longtable,
+  nolmodern,
+  notxfonts,
+  notimes,
   colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{apa7}
 
+\usepackage{amsmath}
+\usepackage{amssymb}
+
+\usepackage[bidi=default]{babel}
+\babelprovide[main,import]{english}
+
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+
 \RequirePackage{longtable}
-% \setlength\LTleft{0pt}
 \RequirePackage{threeparttablex}
-
-% %
 
@@
 
-\usepackage{amsmath}
+\usepackage{longtable, booktabs, multirow, multicol, colortbl, hhline, caption, array, float, xpatch}
+\setcounter{topnumber}{2}
+\setcounter{bottomnumber}{2}
+\setcounter{totalnumber}{4}
+\renewcommand{\topfraction}{0.85}
+\renewcommand{\bottomfraction}{0.85}
+\renewcommand{\textfraction}{0.15}
+\renewcommand{\floatpagefraction}{0.7}
 
-\usepackage{longtable, booktabs, multirow, multicol, colortbl, hhline, caption, array, float, tcolorbox}
+\usepackage{tcolorbox}
+\tcbuselibrary{listings,theorems, breakable, skins}
+\usepackage{fontawesome5}
 
-%
+\definecolor{quarto-callout-color}{HTML}{909090}
+\definecolor{quarto-callout-note-color}{HTML}{0758E5}
+\definecolor{quarto-callout-important-color}{HTML}{CC1914}
+\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
+\definecolor{quarto-callout-tip-color}{HTML}{00A047}
+\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
+\definecolor{quarto-callout-color-frame}{HTML}{ACACAC}
+\definecolor{quarto-callout-note-color-frame}{HTML}{4582EC}
+\definecolor{quarto-callout-important-color-frame}{HTML}{D9534F}
+\definecolor{quarto-callout-warning-color-frame}{HTML}{F0AD4E}
+\definecolor{quarto-callout-tip-color-frame}{HTML}{02B875}
+\definecolor{quarto-callout-caution-color-frame}{HTML}{FD7E14}
 
-\newlength\Oldarrayrulewidth
-\newlength\Oldtabcolsep
+%\newlength\Oldarrayrulewidth
+%\newlength\Oldtabcolsep
 
 \usepackage{hyperref}
-\usepackage{float}
 
@@
 
-\usepackage{times}
+\usepackage[nolongtablepatch]{lineno}
+\linenumbers
 
-\usepackage{lineno}
+\usepackage{newtx}
 
-\title{The Revised Interoceptive Accuracy Scale (IAS-R) Confirms Links
-between Interoception and Mental Health}
-\shorttitle{Revised Interoceptive Accuracy Scale (IAS-R)}
+\defaultfontfeatures{Scale=MatchLowercase}
+\defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+
+\title{Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure
+and its Subjective Correlates}
+
+\shorttitle{IAS Meta-analysis}
 
@@
 
-\course{Introduction to Assessment}
-\professor{W. Joel Schneider}
-\duedate{12/22/2024}
+\authorsnames{Ana Neves,Magdalena Pfaff,Dominique Makowski}
 
-\authorsnames[{1},{1},{2}]{
-Dominique Makowski,X. Y,Annabel Chen
+\affiliation{
+{School of Psychology, University of Sussex}}
+
+\leftheader{Neves, Pfaff and Makowski}
+
+\abstract{Blabla the abstract blabla.}
+
+\keywords{keyword1, keyword2, keyword3}
+
+\authornote{\par{\addORCIDlink{Ana
+Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{Magdalena
+Pfaff}{0009-0006-2386-7936}}\par{\addORCIDlink{Dominique
+Makowski}{0000-0001-5375-9967}}
+
+\par{     \begin{tcolorbox}[enhanced jigsaw, colback=white, breakable, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, arc=.35mm, toprule=.15mm, rightrule=.15mm, opacityback=0, left=2mm, leftrule=.75mm]
+
+This preprint is a non-peer-reviewed work from the
+\href{https://realitybending.github.io/}{\textbf{Reality Bending Lab}}.
+\begin{center}
+\includegraphics[width=0.2\textwidth,height=\textheight]{manuscript_files/mediabag/ReBeL_LogoOnly_hu114.png}
+\end{center}
+
+\end{tcolorbox}  }
+\par{Correspondence concerning this article should be addressed
+to Dominique Makowski, Email: D.Makowski@sussex.ac.uk}
 }
-
-\authorsaffiliations{
-{School of Psychology, University of Sussex},{School of Social Sciences,
-Nanyang Technological University, Singapore}}
-
-\leftheader{Makowski, Y and Chen}
-
-\abstract{This document is a template demonstrating the apaquarto
-format.}
-% % \addbibresource{bibliography.bib}
-% 
-\keywords{Interoception, Accuracy, Scale, Questionnaire, Personality, Psychopathology, Validation}
-
-\authornote{\par{\addORCIDlink{Dominique
-Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{Annabel
-Chen}{0000-0002-1540-5516}}
-\par{ }
-\par{       Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows: Dominique
-Makowski:   conceptualization, Writing - original draft}
-\par{Correspondence concerning this article should be addressed to Dominique
-Makowski, Email: D.Makowski@sussex.ac.uk}
-}
-
-\usepackage{float}
-\makeatletter
-\let\oldtpt\ThreePartTable
-\let\endoldtpt\endThreePartTable
-\def\ThreePartTable{\@ifnextchar[\ThreePartTable@i \ThreePartTable@ii}
-\def\ThreePartTable@i[#1]{\begin{figure}
-\onecolumn
-\begin{minipage}{0.5\textwidth}
-\oldtpt[#1]
-}
-\def\ThreePartTable@ii{\begin{figure}
-\onecolumn
-\begin{minipage}{0.5\textwidth}
-\oldtpt
-}
-\def\endThreePartTable{
-\endoldtpt
-\end{minipage}
-\twocolumn
-\end{figure}}
-\makeatother
 
@@
 \hline
-\endoldlt}
+\endoldlt
+}
 \makeatother
-
-\newenvironment{twocolumntable}% environment name
-{% begin code
-\begin{table*}%
-\onecolumn%
-}%
-{%
-\twocolumn%
-\end{table*}%
-}% end code
 
@@
 
+\makeatletter
+\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
+\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
+\definecolor{quarto-callout-color}{HTML}{909090}
+\definecolor{quarto-callout-note-color}{HTML}{0758E5}
+\definecolor{quarto-callout-important-color}{HTML}{CC1914}
+\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
+\definecolor{quarto-callout-tip-color}{HTML}{00A047}
+\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
+\definecolor{quarto-callout-color-frame}{HTML}{acacac}
+\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
+\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
+\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
+\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
+\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\AtBeginDocument{%
+\ifdefined\contentsname
+  \renewcommand*\contentsname{Table of contents}
+\else
+  \newcommand\contentsname{Table of contents}
+\fi
+\ifdefined\listfigurename
+  \renewcommand*\listfigurename{List of Figures}
+\else
+  \newcommand\listfigurename{List of Figures}
+\fi
+\ifdefined\listtablename
+  \renewcommand*\listtablename{List of Tables}
+\else
+  \newcommand\listtablename{List of Tables}
+\fi
+\ifdefined\figurename
+  \renewcommand*\figurename{Figure}
+\else
+  \newcommand\figurename{Figure}
+\fi
+\ifdefined\tablename
+  \renewcommand*\tablename{Table}
+\else
+  \newcommand\tablename{Table}
+\fi
+}
+\@ifpackageloaded{float}{}{\usepackage{float}}
+\floatstyle{ruled}
+\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
+\floatname{codelisting}{Listing}
+\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
+\makeatother
+
+% From https://tex.stackexchange.com/a/645996/211326
+%%% apa7 doesn't want to add appendix section titles in the toc
+%%% let's make it do it
+\makeatletter
+\xpatchcmd{\appendix}
+  {\par}
+  {\addcontentsline{toc}{section}{\@currentlabelname}\par}
+  {}{}
+\makeatother
+
+%% Disable longtable counter
+%% https://tex.stackexchange.com/a/248395/211326
+
+\usepackage{etoolbox}
+
+\makeatletter
+\patchcmd{\LT@caption}
+  {\bgroup}
+  {\bgroup\global\LTpatch@captiontrue}
+  {}{}
+\patchcmd{\longtable}
+  {\par}
+  {\par\global\LTpatch@captionfalse}
+  {}{}
+\apptocmd{\endlongtable}
+  {\ifLTpatch@caption\else\addtocounter{table}{-1}\fi}
+  {}{}
+\newif\ifLTpatch@caption
+\makeatother
+
 \begin{document}
+
 \maketitle
+
 \setcounter{secnumdepth}{-\maxdimen} % remove section numbering
@@
 
-intro
+\resetlinenumber[1]
 
-\section{Methods}\label{methods}
+Interoception is referred to the process of sensing, interpreting and
+integrating information pertaining to internal organs, such as the
+heart, the lungs or the gut (\citeproc{ref-khalsa2018}{Khalsa et al.,
+2018}). While recent research emphasizes a key role of interoception in
+a variety of processes (e.g., emotion regulation, decision making) and
+of outcomes (physical and psychological well being), the field remains
+clouded by concerns about how interoception is assessed.
 
-blabla
+{[}\textbf{TO DO}: add - previous work suggests the importance of
+physiological contexts (Vlemincx et al., 2021){]}
 
-\section{Results}\label{results}
+Various measures of interoception have been developed (see
+\textbf{Figure~\ref{fig-measures}}), forming a combination of
+``objective'' and ``subjective'' assessments (i.e., physiological tasks
+such as the heart beat counting or tracking vs.~questionnaires and
+subjective scales involving a metacognitive reflection), ``explicit''
+and ``implicit'' paradigms (i.e., directing participants' awareness and
+attention to interoceptive processes \emph{vs.} measuring interoception
+unbeknownst to them), various interoceptive modalities (e.g.,
+cardioception, respiroception, gastroception) and theoretical dimensions
+(e.g., accuracy, sensitivity, awareness). While there is no consensus as
+to which particular approach provides the most accurate and ``pure''
+measure of interoception and interoceptive abilities (assuming it is a
+unidimensional construct), it is instead plausible that each measure has
+strengths and limitations, and a utility dependent on the context and
+goal at hand (\citeproc{ref-jahedi2014}{Jahedi \& Méndez, 2014}).
 
-blabla
+\begin{figure*}[!htbp]
 
-\section{Discussion}\label{discussion}
+{\caption{{Different ways in which interoception can be
+measured.}{\label{fig-measures}}}}
 
-blabla
+\includegraphics[width=1\textwidth,height=\textheight]{figures/MeasuringInteroception.jpg}
 
-\section{References}\label{references}
+\end{figure*}
+
+For instance, while the use of self-reports questionnaires to measure an
+embodied function might seem paradoxical, recent redefinitions of
+interoception, emphasizing the role of high-level and metacognitive
+elaboration of interoceptive information, has provided the theoretical
+grounding to support the idea that some facets of interoception
+(including participants' metacognitive beliefs) can be assessed
+subjectively, providing useful and interesting measures
+(\citeproc{ref-lin2023}{Lin et al., 2023};
+\citeproc{ref-murphy2019}{Murphy et al., 2019}). The notion that
+self-reports might not reflect the same processes as other interoception
+measures is important to contextualize the apparent lack of convergence
+between measures in the field
+(\citeproc{ref-desmedt2022measures}{Desmedt et al., 2022}). Still, a
+better understanding of what is being measured with different
+questionnaires and dimensions, as well their potential overlaps with
+other constructs (e.g., alexithymia, body awareness) is needed to
+clarify the role of self-reports in the assessment of interoception.
+
+A recently developed scale with a rapidly growing popularity is the
+Interoceptive Accuracy Scale (IAS, \citeproc{ref-murphy2019}{Murphy et
+al., 2019}). The IAS consists of 21 Likert-scale items that query how
+accurately one can perceive different bodily signals, with one item per
+physiological modality such as respiration (\emph{``I can always
+accurately perceive when I am breathing fast''}), heart (e.g \emph{``I
+can always accurately perceive when my heart is beating fast''}), skin
+(e.g \emph{``I can always accurately perceive when something is going to
+be ticklish''}), arousal or bodily functions like coughing (e.g
+\emph{``I can always accurately perceive when I am going to cough''}) or
+urinating (e.g.~\emph{``I can always accurately perceive when I need to
+urinate''}). Interestingly, the IAS' statements are about specific
+interoceptive behaviours, which is a notable difference with other
+popular interoception questionnaires, such as the Multidimensional
+Assessment of Interoceptive Awareness scale (MAIA,
+\citeproc{ref-mehling2012}{Mehling et al., 2012}; MAIA-2,
+\citeproc{ref-mehling2018multidimensional}{Mehling et al., 2018}), which
+contains more general and metacognitive items (e.g., \emph{``I trust my
+body sensations''}, \emph{``I can notice an unpleasant body sensation
+without worrying about it''}).
+
+Although the original validation study suggested a two-factor solution
+structure, the authors underlines the need for further investigation of
+the scale's factor structure, as it provided acceptable but imperfect
+explanation of the data {[}Murphy et al.
+(\citeproc{ref-murphy2019}{2019}); p.~127{]}. Notably, the only other
+validation study to report a 2-factor solution was conducted by Koike
+and Nomura (\citeproc{ref-koike2023}{2023}), who performed an
+Exploratory Factor Analysis (EFA) assuming 2 factors to align with the
+findings from the original validation paper. Other follow-up studies
+using confirmatory factor analysis (CFA) and structural modeling
+(\citeproc{ref-morin2016}{Morin et al., 2015}) have identified different
+optimal solutions. Some studies, like Brand et al.
+(\citeproc{ref-brand2023}{2023}), reported a 1-factor solution, while
+Lin et al. (\citeproc{ref-lin2023}{2023}) and Campos et al.
+(\citeproc{ref-campos2021}{2021}) found bifactor solutions - one general
+factor and a set of loweroike -level factors (Rodriguez et al.
+(\citeproc{ref-rodriguez2016evaluating}{2016})) - to be the best fit.
+
+Discussions have also been focused on specific items. For instance,
+Murphy et al. (\citeproc{ref-murphy2019}{2019}) notes that some items
+might measure direct interoceptive signals such as cardioception, while
+others might capture phenomena not perceivable through interoceptive
+signals alone (e.g., ``bruising''; p.~119). Lin et al.
+(\citeproc{ref-lin2023}{2023}) also highlights their correlation
+analysis, showing five locally dependent pairs and three items (touch,
+blood sugar, bruise) with exceptionally high difficulty and low
+discrimination. Additionally, Campos et al.
+(\citeproc{ref-campos2021}{2021}) suggests that the ``tickle'' item
+represents a more specific factor. Interestingly, Lin et al.
+(\citeproc{ref-lin2023}{2023}) reported that all items of the IAS
+grouped together using a new approach, Exploratory Graph Analysis
+{[}EGA; Golino and Epskamp
+(\citeproc{ref-golino2017exploratory}{2017}){]}, to assess convergent
+and discriminant validity, which suggests unidimensionality.
+
+While the assessment of the validity of an interoception scale can be
+conceived as theoretically challenging, several traits have been used to
+assess convergent validity for the the IAS, including expected negative
+associations with alexithymia Murphy et al.
+(\citeproc{ref-murphy2019}{2019}), somatic symptoms Lin et al.
+(\citeproc{ref-lin2023}{2023}), depressive symptoms
+(\citeproc{ref-brand2023}{Brand et al., 2023};
+\citeproc{ref-koike2023}{Koike \& Nomura, 2023};
+\citeproc{ref-lin2023}{Lin et al., 2023}), anxiety
+(\citeproc{ref-brand2023}{Brand et al., 2023}), neuroticism
+(\citeproc{ref-brand2023}{Brand et al., 2023}) and self-esteem
+(\citeproc{ref-murphy2019}{Murphy et al., 2019}).
+
+The IAS has also been compared to other interoception scales (and
+interoceptive related scales),generally showing positive correlations
+with most facets of the MAIA, except for the Non-Distracting and
+Not-Worrying subscales (\citeproc{ref-brand2023}{Brand et al., 2023}).
+Findings on the correlation between the IAS and the body awareness
+dimension of the Body Perception Questionnaire (BPQ-A; Porges
+(\citeproc{ref-porges1993body}{1993})) have been mixed: some studies
+report small positive correlations (\citeproc{ref-brand2023}{Brand et
+al., 2023}; \citeproc{ref-campos2021}{Campos et al., 2021};
+\citeproc{ref-koike2023}{Koike \& Nomura, 2023}), while others find
+small negative correlations (\citeproc{ref-lin2023}{Lin et al., 2023})
+or no correlation at all (\citeproc{ref-murphy2019}{Murphy et al.,
+2019}). Small positive correlations have also been observed with the
+observation and description subscales of the Five Facet Mindfulness
+Questionnaire (FFMQ, Baer et al. (\citeproc{ref-baer2006using}{2006});
+Brand et al. (\citeproc{ref-brand2023}{2023}); Koike and Nomura
+(\citeproc{ref-koike2023}{2023})), as well as with the nonreactivity and
+acting with awareness subscales (\citeproc{ref-koike2023}{Koike \&
+Nomura, 2023}). Additionally, the IAS has shown a positive correlation
+with the interoceptive awareness subscale of the Eating Disorder
+Inventory (\citeproc{ref-lin2023}{Lin et al., 2023}) and a negative
+correlation with the Interoceptive Confusion Questionnaire
+(\citeproc{ref-brand2023}{Brand et al., 2023}; ICQ,
+\citeproc{ref-brewer2016alexithymia}{Brewer et al., 2016};
+\citeproc{ref-murphy2019}{Murphy et al., 2019}). Lastly, small positive
+correlations have been reported between the Interoceptive Attention
+Scale (IATS, Gabriele et al.
+(\citeproc{ref-gabriele2022dissociations}{2022})) and the IAS
+(\citeproc{ref-koike2023}{Koike \& Nomura, 2023};
+\citeproc{ref-lin2023}{Lin et al., 2023}), though studies have also
+found no correlation between these measures
+(\citeproc{ref-gabriele2022dissociations}{Gabriele et al., 2022}).
+
+Few studies have examined the correlation between objective
+interoceptive measures, such as the Heartbeat Counting Task (HCT;
+Schandry, 1981) and the Heartbeat Detection Task (HDT; Kleckner et al.,
+2015). Existing findings report weak correlations for the HCT (Murphy et
+al., 2019), no correlations except for the sensitivity variable of the
+HCT (Brand et al., 2023), and small correlations for the HDT (Brand et
+al., 2023). These results suggest that the IAS, a subjective measure,
+does not strongly align with objective interoceptive assessments.
+
+The current study aims at 1) clarifying the structure of the IAS with a
+meta-analytic approach that leverages existing data and contrast the
+traditional CFA/SEM factor-based analyses with network-based ones such
+as EGA. 2) The second part will provide an overview of the dispositional
+correlates of the IAS, providing an overview of the pattern of
+associations that is key to better understand the nature, place and role
+of interoception questionnaires within a larger context.
+
+\subsection{Study 1}\label{study-1}
+
+The goal of study 1 is to re-analyse and assess the factor structure of
+the IAS by taking advantage of the large number of open-access datasets
+(\citeproc{ref-arslanova2022}{Arslanova et al., 2022};
+\citeproc{ref-brand2022}{Brand et al., 2022};
+\citeproc{ref-brand2023}{Brand et al., 2023};
+\citeproc{ref-campos2021}{Campos et al., 2021};
+\citeproc{ref-gaggero2021}{Gaggero et al., 2021};
+\citeproc{ref-lin2023}{Lin et al., 2023};
+\citeproc{ref-murphy2019}{Murphy et al., 2019};
+\citeproc{ref-todd2022}{Todd et al., 2022}; \citeproc{ref-von2023}{Von
+Mohr et al., 2023}). While combining these studies might provide a more
+robust and generalizable understanding of the IAS' factor structure, it
+is important to note that the studies differ in their sample sizes,
+demographics, language, and the way they collected the data. Thus,
+providing additionally an individual analysis (i.e., on all samples
+individually) will help adding nuance to the general picture.
+
+\subsubsection{Methods}\label{methods}
+
+\paragraph{Datasets.}\label{datasets}
+
+Our search focused on studies citing the original IAS validation paper
+(\citeproc{ref-murphy2019}{Murphy et al., 2019}), identifying 136 papers
+(as of 01/05/2024). To qualify for inclusion, papers needed to (1)
+provide accessible data in open-access, (2) employ the IAS as a measure,
+and (3) report individual IAS items scores. A total of 10 studies was
+included (see \textbf{Table 1}). We also included the data of two
+unpublished (but already open-access) studies from the authors and one
+from another author. The total N participants was 32,214 participants
+(\emph{Mean} = 48.6 years, \emph{SD} = 13.1, 71.6\% Female).
+
+\input{../../analysis/figures/table1.tex}
+
+\paragraph{Statistical Analysis.}\label{statistical-analysis}
+
+To examine the factor structure of the IAS, a two-step approach was
+employed. First, Exploratory Graph Analysis (EGA), was used to estimate
+the dimensions via network estimation and community detection, alongside
+assessing the stability of dimensions and items using the bootstrapping
+techniques (\citeproc{ref-golino2017exploratory}{Golino \& Epskamp,
+2017}). The selection of EGA was motivated by its capability to handle
+complex, multidimensional data and provide robust dimension estimates. A
+novel network psychometrics - Unique variable analysis {[}UVA;
+Christensen et al. (\citeproc{ref-christensen2023unique}{2023}){]} -
+approach based on the weighted topological overlap will be computed to
+evaluate which items have substantial local dependence (\textgreater{}
+0.25). Subsequently, exploratory factor analysis (EFA) was employed
+followed by confirmatory factor analysis (CFA).
+
+\subsubsection{Results}\label{results}
+
+Visualizing the distribution of the items for all samples suggests the
+presence of a consistent modal value (Figure~\ref{fig-distributions}).
+In other words, participants are most likely to answer 4/5 (i.e., agree)
+on most items (but ``affective touch'', ``blood sugar'', and ``bruise''
+that exhibit a different distributional pattern). Additionally, one can
+note the low density on extreme values (1 and 5), meaning that the bulk
+of answers (i.e., 99\%) varies between 3 values. The interindividual
+variability seems improved in the samples using an analogue scale,
+displaying a more continuous and progressive spread of answers.
+
+\begin{figure}
+
+\caption{\label{fig-distributions}Distribution of responses for all
+items across various datasets.}
+
+\centering{
+
+\includegraphics[width=6.67in,height=\textheight]{figures/Figure1.png}
+
+}
+
+\end{figure}%
+
+\paragraph{Correlations.}\label{correlations}
+
+The correlation analysis revealed that the items overall have positive
+intercorrelation patterns with no clear structure emerging. This remains
+the same across all samples. However, there are possibly some
+higher-order groupings emerging for the 2 analog-scale samples.
+
+\paragraph{EGA.}\label{ega}
+
+The UVA revealed that there are two large to very large redundant
+variables when taking all samples into account. Namely, ``itch'' and
+``tickle'', where ``tickle'' should be removed, and ``itch'' should be
+kept. There are several more items that are moderately to largely
+redundant, namely, ``wind'' and ``burp'', and ``urinate'' and
+``defecate''. On top of that, ``sneeze'' and ``cough'', ``heart'' and
+``breathing'', and ``hungry'' and ``thirsty'' seem to have small to
+moderate redundancy. These findings are rather consistent across the
+samples with minor differences, such as that when the questionnaire had
+an analog scale, there seems to be no large to very large redundant
+items but ``itch'' and ``tickle'' remain moderately to largely redundant
+and ``heart'' and ``breathing'' small to moderately redundant in one
+sample.
+
+According to the network analysis, using the Walktrap and Louvain
+algorithms applied to Glasso networks, a 4-factor structure fits the
+questionnaire best across all data sets. This is rather consistent
+within the data sets, where some samples indicate 3-factor structure,
+and some a 5-factor structure would fit well too. The 4-factor structure
+model with the best fit entails the following items per group: 1) itch,
+tickle, bruise, blood sugar; 2) burp, wind, cough, sneeze, vomit; 3)
+affective touch, sexual arousal, muscles, temperature, pain, and taste;
+4) Heart, breathing, hungry, thirsty, urinate, and defecate.
+
+Stability analysis, employing 500 bootstrap iterations, also favoured
+the 4-factor solution for its greater stability. Most items, except for
+`affective touch,' demonstrated stability levels exceeding 0.90,
+indicating structural consistency and reliability
+(\citeproc{ref-christensen2021}{Christensen \& Golino, 2021}). These
+findings underscore the robustness of the identified 4-dimensional
+structure.
+
+When accounting for all samples, the factor analysis reveals that a
+4-factor structure fits best. The exploratory factor analysis revealed
+that 4 latent factors (oblimin rotation) accounted for 51.95\% of the
+total variance of the original data (MR2 = 19.08\%, MR1 = 17.78\%, MR4 =
+9.34\%, MR3 = 5.75\%). Since UVA identified ``tickle'' as the item to be
+removed---and it also had the lowest uniqueness value in factor analysis
+with a similar loading to ``itch''---``tickle'' was excluded from
+subsequent analyses.
+
+Confirmatory factor analysis compared 5 models: a single-factor
+solution, a 4-factor solution, a 5-factor solution, a 6-factor solution
+and a 7-factor solution. The latter was preferred in most datasets,
+including with indices that penalise increased number of parameters
+(such as BIC). There was no evidence for higher order factors.
+
+\subsubsection{Discussion}\label{discussion}
+
+In this study, several datasets were analyzed for a meta analysis of the
+structure of the IAS. The findings reveal that a 4-factor model fits the
+IAS best. Additionally, the lowest level structure (pairs of items) seem
+to be the most robust, especially for samples using Likert scales (some
+higher-order groupings might emerge for the 2 analog-scale samples).
+There was no clear evidence for higher-order factors.
+
+These findings contrast with previous research, which all found that
+2-factor model(\citeproc{ref-koike2023}{Koike \& Nomura, 2023};
+\citeproc{ref-murphy2019}{Murphy et al., 2019}), 1-factor model
+(\citeproc{ref-brand2023}{Brand et al., 2023}) and bifactor model
+(\citeproc{ref-campos2021}{Campos et al., 2021};
+\citeproc{ref-lin2023}{Lin et al., 2023}) fits the data best. While this
+analysis also revealed an okay fit for the 1-factor model, the 4-factor
+model revealed the best fit. The 4-factor structure reveals different
+`hubs' of items that are related, not only in this structure analysis,
+but also in underlying mechanisms. The `wind-burp-cough-sneeze-vomit'
+category, for example, only entails items that are linked to excretion
+through the mouth. The other categories are organized similarly. This
+organization and structure is useful for further analysis, as the data
+can be analyzed and interpreted according to a grouping that is coherent
+in result, as well as underlying mechanisms.
+
+There are several items that show redundancy suggesting that adapting
+the IAS would be beneficial for validity. Based on the given results, we
+suggest removing the tickle, while keeping the itch item
+{[}\textbf{todo}: stats?{]}. Other items with slight redundancy were
+Hungry and Thirsty, Urinate and Defecate, and Sneeze and Cough.
+
+Interestingly, Lin et al. (\citeproc{ref-lin2023}{2023}) also found that
+tickle and itch were redundant, excluding one of them but the reason
+being that the character for both words is the same in the Chinese
+language. On top of that, they came up with a shortened version of the
+IAS, excluding further items, resulting in a 12-item IAS, which aligns
+with our findings, suggesting that further items are ambiguous as to
+whether they should be removed. In contrast, other findings also found
+itch and tickle to be redundant but did not suggest excluding items
+(\citeproc{ref-campos2021}{Campos et al., 2021}).
+
+The findings indicate a high proportion of answers at 4 (see Figure 1),
+especially when using a 5-step scale. The analogue scale shows a more
+dispersed distribution, with some answers indicating the highest 5/5,
+which was not the case in the 5-step scale. Therefore, we recommend
+using an analog scale for the IAS.
+
+Before this paper, the IAS has not yet been used or analyzed with an
+analog scale, rather than a five step scale. Therefore, this study
+provides a novel approach to improving the IAS in a simple manner.
+
+\subsubsection{Limitations and Future
+Directions}\label{limitations-and-future-directions}
+
+There are several limitations to the IAS; There are some redundant
+items, the 5-point scale does not provide great variability, and the
+structure could be improved. Therefore, improving the IAS, or creating a
+new questionnaire investigating interoception could be useful to
+achieving reliable and accurate indication of interoceptive awareness.
+
+\subsection{Study 2}\label{study-2}
+
+Study 2 aims to investigate correlates of the IAS. Correlations of the
+IAS will be computed to assess the relationship between subjective
+interoceptive accuracy and other subjective measures of interoception,
+mood, psychopathology, personality, and beliefs. Investigating
+correlates will help validate the IAS, as well as other interoceptive
+measures in the future. The
+
+\subsubsection{Methods}\label{methods-1}
+
+\paragraph{Materials.}\label{materials}
+
+The questionnaires used for the IAS correlates are listed in
+\textbf{Table 2} (\textbf{TODO: add the rest of the questionnaires,
+sample items and references}).
+
+\input{../../analysis/figures/table2.tex}
+
+\paragraph{Statistical analysis.}\label{statistical-analysis-1}
+
+Correlations will be computed using the correlation package under a
+Bayesian framework (ref).
+
+\subsubsection{Results}\label{results-1}
+
+The EGA components capture groupings of pairs of items, such as ``wind''
+and ``burp'', ``cough'' and ``sneeze'', or ``muscle'' and ``pain''.
+These groupings were used in the correlational analysis, to observe how
+much each group/pair correlates with other factors, such as Alexithymia,
+or the MAIA (see Figure 2).
+
+Alexithymia is negatively correlated with all interoceptive groups.
+Autistic traits are mostly negatively correlated with IAS measure,
+except for patterns and numbers (as an autistic trait), which is
+significantly and positively correlated with the ``itch/bruise''
+pairing. The BPQ Body Awareness part is positively correlated with all
+IAS pairs, whereas the Autonomic Reactivity part is negatively
+correlated with all IAS groupings. Conspiracy Beliefs were all
+positively correlated with the IAS pairs, however, only Global
+Conspiracy with ``hungry/thirsty'', ``urinate/defecate'' and
+``cough/sneeze'', as well as personal wellbeing with ``hungry/thirsty'',
+and Information Control with ``cough/sneeze'' were significantly
+positively correlated. Demographic data is also mostly positively
+correlated with the IAS findings, where gender and age more strongly
+correlated with ``hungry/thirsty''. In this analysis, lying profile is
+not strongly correlated with the IAS; Except for contextuality, which
+shows a significant negative correlation with ``itch/bruise''. The MAIA
+has a strong positive correlation with most IAS pairings, except for the
+``not worrying'' and ``not distracting'' items of the MAIA, which show
+less strong, or even negative correlations with all IAS item pairings.
+Maladaptiveness had mostly negative correlations with the IAS, with only
+a few significant correlations, namely ``psychoticism'', ``negative
+affect'', and ``detachment'' with ``muscle/pain'' and
+``hungry/thirsty'', as well as ``negative affect'' with ``wind/burp''.
+Overall, mood was mostly negatively correlated with the IAS, where
+``hungry/thirsty'' had the strongest negative correlation of all mood
+measures. Except for ``neuroticism'' and ``honesty-humility'',
+personality traits, such as ``openness'' and ``extraversion'' were
+positively correlated with the IAS groupings. Shizotypic traits were
+mostly negatively correlated with the IAS, with ``hungry/thirsty''
+showing the strongest negative correlation between schizotypic and the
+IAS. World beliefs were mostly positively correlated with the IAS,
+however, only a few were significant: ``hierarchical'', ``enticing'',
+and ``alive'' correlates significantly with ``muscle/pain'';
+``Understandable'' has a significant positive correlation with
+``heart/breathing''; And ``hierarchical'' and ``alive'' has a
+significant positive correlation with ``hungry/thirsty''.
+
+\begin{figure}[H]
+
+\caption{\textbf{Figure 2.} Correlates of the IAS}
+
+{\centering \includegraphics[width=9.48958in,height=\textheight]{figures/clipboard-1619164537.png}
+
+}
+
+\end{figure}%
+
+\subsubsection{Discussion}\label{discussion-1}
+
+Our findings confirmed that interception lies within an intricate
+network of correlates. Alexithyma has the most negative correlation with
+the IAS, whereas, the MAIA questionnaire is most strongly positively
+correlated with the IAS. The correlates cannot only explain attributes
+of interoception, but can also be used to validate measures for
+interoception.
+
+While these results reveal correlations of different categories with the
+IAS, the findings are limited to the given questionnaire. However, they
+give a good indication of how interoception in general might be linked
+to the different categories, leading to interesting findings. The
+results show a consistent pattern of correlations with other
+interoception measures, psychopathology, and highlighting of interesting
+exploratory results, such as how primal world beliefs correlate with the
+IAS.
+
+The analysis revealed a negative correlation between alexithymia and
+scores in the IAS, which is in line with previous research
+(\citeproc{ref-herbert2011}{Herbert et al., 2011}). A negative
+correlation between autism and interoceptive awareness, which has been
+found in this sample, has also been found in previous research
+(\citeproc{ref-dubois2016}{DuBois et al., 2016}). Conspiracy Beliefs and
+IAS scores were not strongly correlated. However, there was a slight
+positive correlation. To the best of our knowledge, this interaction has
+not been investigated before. However, research shows correlations
+between (political) beliefs and interoception, which could underlie the
+same mechanism (\citeproc{ref-ruisch2022}{Ruisch et al., 2022a}). Lying
+profile was also not strongly correlated with the IAS. Previous research
+provides some evidence for a relationshipbetween interoception and lying
+profile (\citeproc{ref-makowski2023a}{Makowski et al., 2023}),
+indicating a contrast from the literature to the results at hand. The
+analysis showed that mood and the IAS scores have a strong negative
+correlation, which has been investigated in previous studies, finding a
+correlation between the two variables as well
+(\citeproc{ref-solanoluxf3pez2018}{Solano López \& Moore, 2018}). The
+analysis showed that personality is also correlated with interoceptive
+accuracy scores as retrieved by the IAS. While there are many aspects of
+personality, put simply, personality and interoception have been found
+to correlate in previous studies as well (\citeproc{ref-erle2021}{Erle
+et al., 2021}). Our findings show some negative correlations between
+schizotypy and interoception. Previous research has investigated this
+relationship and, similarly, found a negative correlation between
+interoceptive awareness and schizotypy, particularly at the onset of
+psychosis (\citeproc{ref-torregrossa2022}{Torregrossa et al., 2022}).
+Lastly, World Beliefs and Interoception showed some significant positive
+correlations. World Beliefs have not been linked with interoception
+previously. As mentioned, other beliefs, such as political beliefs have
+been mentioned to interoception, where significant correlations were
+observed (\citeproc{ref-ruisch2022a}{Ruisch et al., 2022b}). Further
+research is needed to understand this mechanism and validate whether
+world beliefs, which lay the framework through which we see the world
+(\citeproc{ref-clifton2020}{Clifton, 2020}), is needed.
+
+The above findings show how interoception is correlated with many
+lifestyle and health factors, and is therefore an important concept to
+study. Here we showed many correlates of the IAS and lifestyle, as well
+as health factors. This is not only valuable to understand interception,
+and the role it plays in our lives, better, but also crucial to further
+validate the Ias, as well as other interoception measures. This analysis
+therefore lays the groundwork for validating new interoceptive measures
+and questionnaires needed to grasp interoception and its role in our
+life.
+
+\subsection{General Discussion}\label{general-discussion}
+
+The analyses revealed that the IAS has 4-factor structure, and a rather
+uneven distribution. The findings indicate that the IAS is measuring
+interoception in an acceptable manner, but there is also room for
+improvement. Furthermore, the results reveal different correlation
+measures with the IAS, giving space to further explore whether and how
+measures correlate with interoception/the IAS. In the following section,
+the IAS is discussed further to reveal shortcomings and strengths of the
+questionnaire. Finally, future steps will be revealed to improve the way
+in which we measure interoception.
+
+Overall, the IAS is straightforward with its sensation-centered items.
+There are several points of improvement to the IAS, which this work
+suggests. Firstly, removing redundant items, such as the itch item as
+shown in the above analysis. Previous work has also shown that the itch
+and tickle items are subject to redundancy Campos et al.
+(\citeproc{ref-campos2021}{2021}) has shown. Interestingly, Campos et
+al. (\citeproc{ref-campos2021}{2021}) suggest removing the tickle item
+instead. Lin et al. (\citeproc{ref-lin2023}{2023}) on the other hand
+removed the itch item, because the sign for itch and tickle is the same.
+Furthermore, this work recommends using analog scales, instead of 5
+point scales. In a 5-point scale, the variability is clearly limited
+with most people choosing ⅘. As visible in Figure X, the variability
+increases significantly, using an analog scale. However, it is important
+to note that even with an analog scale, the variability of the IAS is
+still limited. The more variability a scale shows, the more results can
+depict individual differences between participants. Therefore, good
+dispersion is essential for achieving relevant and usable results, and
+striving for more variability would be beneficial to this interoception
+scale, too.
+
+In this work, it becomes apparent that even with the mentioned
+improvements to the scale, there are limitations to the IAS, which
+reduce the accuracy of this scale. Those limitations include that there
+are few items for some modalities, such as only one item for heart
+perception. Having more modality is useful as each grouping can have
+more variability with increased modality, leading to more nuanced
+results. On top of that, there is no clear and theoretical, or empirical
+structure, as there is a very small grouping of items. Ideally, a scale
+would allow for an analysis showing different groupings so that
+different categories can be created based on which the data can be
+analyzed. The groupings in this analysis reveal that the IAS can only be
+grouped with two items per group, leading to low scores and variability
+in each group. On top of that, there are ambiguous items in the IAS, of
+which the grouping depends on the context. For example, one might
+indicate that they can perceive well how their heart is beating fast as
+well as vomiting, but both items can be linked to feeling anxious, and
+therefore might indicate different results than initially expected.
+Therefore, the grouping and structure of the IAS can be improved.
+
+Furthermore, all items are phrased positively, which might influence how
+participants answer the questions. While phrasing items in a positive
+manner can be beneficial, the benefits of positive phrasing might
+exacerbate a positive bias and thus lead to unidimensional results.
+Therefore, phrasing questions in a more diverse manner might lead to
+more accurate results and might thus be beneficial.
+
+Based on the given arguments, it becomes clear that there is a need for
+context-specific items, which are cross-modal when possible, such as
+integrating cardioception and respiroception. After establishing the
+clear need for a new scale to measure interoception, this study proposes
+the need for a new scale (Multimodal Interoceptive Sensitivity Scale,
+MISS) to adapt to the newest findings on the IAS and what we know about
+interoception to this day. The new scale will be able to be compared to
+the correlates of the IAS.
+
+\subsection{Conclusion}\label{conclusion}
+
+The IAS is a good way of measuring interoception considering the current
+existing questionnaires and tools. However, revising, or even
+re-inventing a survey to measure interoception would lead to the best
+measure of interoception. Therefore, this study proposes that a new
+scale to measure interoception is needed to evolve the current research
+on interoception. This study revealed many correlates of the IAS, giving
+space for future analysis on what might be a good interoceptive measure,
+and therefore laying the groundwork for the creation of a new
+interoception survey.
+
+\subsection{References}\label{references}
 
 \phantomsection\label{refs}
-\begin{CSLReferences}{0}{1}
+\begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-arslanova2022}
+Arslanova, I., Galvez-Pol, A., Kilner, J., Finotti, G., \& Tsakiris, M.
+(2022). Seeing through each other's hearts: Inferring others' heart rate
+as a function of own heart rate perception and perceived social
+intelligence. \emph{Affective Science}, \emph{3}(4), 862--877.
+
+\bibitem[\citeproctext]{ref-baer2006using}
+Baer, R. A., Smith, G. T., Hopkins, J., Krietemeyer, J., \& Toney, L.
+(2006). Using self-report assessment methods to explore facets of
+mindfulness. \emph{Assessment}, \emph{13}(1), 27--45.
+
+\bibitem[\citeproctext]{ref-brand2023}
+Brand, S., Meis, A. C., Tünte, M. R., Murphy, J., Woller, J. P.,
+Jungmann, S. M., Witthöft, M., Hoehl, S., Weymar, M., Hermann, C., \&
+Ventura-Bort, C. (2023). A multi-site German validation of the
+Interoceptive Accuracy Scale and its relation to psychopathological
+symptom burden. \emph{Communications Psychology}, \emph{1}(1).
+\url{https://doi.org/10.1038/s44271-023-00016-x}
+
+\bibitem[\citeproctext]{ref-brand2022}
+Brand, S., Petzke, T. M., \& Witthöft, M. (2022). The differential
+relationship between self-reported interoceptive accuracy and attention
+with psychopathology. \emph{Zeitschrift f{ü}r Klinische Psychologie Und
+Psychotherapie}.
+
+\bibitem[\citeproctext]{ref-brewer2016alexithymia}
+Brewer, R., Cook, R., \& Bird, G. (2016). Alexithymia: A general deficit
+of interoception. \emph{Royal Society Open Science}, \emph{3}(10),
+150664.
+
+\bibitem[\citeproctext]{ref-campos2021}
+Campos, C., Rocha, N. B., \& Barbosa, F. (2021). \emph{Untangling
+self-reported interoceptive attention and accuracy: Evidence from the
+european portuguese validation of the body perception questionnaire and
+the interoceptive accuracy scale}.
+\url{http://dx.doi.org/10.31234/osf.io/a7wdj}
+
+\bibitem[\citeproctext]{ref-christensen2023unique}
+Christensen, A. P., Garrido, L. E., \& Golino, H. (2023). Unique
+variable analysis: A network psychometrics method to detect local
+dependence. \emph{Multivariate Behavioral Research}, \emph{58}(6),
+1165--1182.
+
+\bibitem[\citeproctext]{ref-christensen2021}
+Christensen, A. P., \& Golino, H. (2021). Estimating the Stability of
+Psychological Dimensions via Bootstrap Exploratory Graph Analysis: A
+Monte Carlo Simulation and Tutorial. \emph{Psych}, \emph{3}(3),
+479--500. \url{https://doi.org/10.3390/psych3030032}
+
+\bibitem[\citeproctext]{ref-clifton2020}
+Clifton, J. D. W. (2020). Testing if primal world beliefs reflect
+experiences{\textemdash}or at least some experiences identified ad hoc.
+\emph{Frontiers in Psychology}, \emph{11}.
+\url{https://doi.org/10.3389/fpsyg.2020.01145}
+
+\bibitem[\citeproctext]{ref-desmedt2022measures}
+Desmedt, O., Heeren, A., Corneille, O., \& Luminet, O. (2022). What do
+measures of self-report interoception measure? Insights from a
+systematic review, latent factor analysis, and network approach.
+\emph{Biological Psychology}, \emph{169}, 108289.
+
+\bibitem[\citeproctext]{ref-dubois2016}
+DuBois, D., Ameis, S. H., Lai, M.-C., Casanova, M. F., \& Desarkar, P.
+(2016). Interoception in Autism Spectrum Disorder: A review.
+\emph{International Journal of Developmental Neuroscience},
+\emph{52}(1), 104--111.
+\url{https://doi.org/10.1016/j.ijdevneu.2016.05.001}
+
+\bibitem[\citeproctext]{ref-erle2021}
+Erle, T. M., Mitschke, V., \& Schultchen, D. (2021). Did my heart just
+leap or sink? The role of personality for the relation between cardiac
+interoception and well-being. \emph{Personality and Individual
+Differences}, \emph{170}, 110493.
+\url{https://doi.org/10.1016/j.paid.2020.110493}
+
+\bibitem[\citeproctext]{ref-gabriele2022dissociations}
+Gabriele, E., Spooner, R., Brewer, R., \& Murphy, J. (2022).
+Dissociations between self-reported interoceptive accuracy and
+attention: Evidence from the interoceptive attention scale.
+\emph{Biological Psychology}, \emph{168}, 108243.
+
+\bibitem[\citeproctext]{ref-gaggero2021}
+Gaggero, G., Bizzego, A., Dellantonio, S., Pastore, L., Lim, M., \&
+Esposito, G. (2021). Clarifying the relationship between alexithymia and
+subjective interoception. \emph{PLoS One}, \emph{16}(12), e0261126.
+
+\bibitem[\citeproctext]{ref-golino2017exploratory}
+Golino, H. F., \& Epskamp, S. (2017). Exploratory graph analysis: A new
+approach for estimating the number of dimensions in psychological
+research. \emph{PloS One}, \emph{12}(6), e0174035.
+
+\bibitem[\citeproctext]{ref-herbert2011}
+Herbert, B. M., Herbert, C., \& Pollatos, O. (2011). On the Relationship
+Between Interoceptive Awareness and Alexithymia: Is Interoceptive
+Awareness Related to Emotional Awareness? \emph{Journal of Personality},
+\emph{79}(5), 1149--1175.
+\url{https://doi.org/10.1111/j.1467-6494.2011.00717.x}
+
+\bibitem[\citeproctext]{ref-jahedi2014}
+Jahedi, S., \& Méndez, F. (2014). On the advantages and disadvantages of
+subjective measures. \emph{Journal of Economic Behavior \&
+Organization}, \emph{98}, 97--114.
+\url{https://doi.org/10.1016/j.jebo.2013.12.016}
+
+\bibitem[\citeproctext]{ref-khalsa2018}
+Khalsa, S. S., Adolphs, R., Cameron, O. G., Critchley, H. D., Davenport,
+P. W., Feinstein, J. S., Feusner, J. D., Garfinkel, S. N., Lane, R. D.,
+Mehling, W. E., Meuret, A. E., Nemeroff, C. B., Oppenheimer, S.,
+Petzschner, F. H., Pollatos, O., Rhudy, J. L., Schramm, L. P., Simmons,
+W. K., Stein, M. B., \ldots{} Zucker, N. (2018). Interoception and
+Mental Health: A Roadmap. \emph{Biological Psychiatry: Cognitive
+Neuroscience and Neuroimaging}, \emph{3}(6), 501--513.
+\url{https://doi.org/10.1016/j.bpsc.2017.12.004}
+
+\bibitem[\citeproctext]{ref-koike2023}
+Koike, H., \& Nomura, M. (2023). Development and validation of japanese
+versions of the interoceptive accuracy scale and interoceptive attention
+scale. \emph{SAGE Open}, \emph{13}(4), 21582440231214639.
+
+\bibitem[\citeproctext]{ref-lin2023}
+Lin, X.-X., Shen, H.-R., Lin, J.-X., Zhang, Y.-H., Murphy, J., Wang,
+Y.-Z., Sun, Y.-B., Wang, N., Wang, J.-Y., Wei, G.-X., \& Luo, F. (2023).
+Psychometric validation and refinement of the Chinese Interoceptive
+Accuracy Scale (IAS) in general population and patients with chronic
+pain. \emph{Journal of Psychosomatic Research}, \emph{175}, 111541.
+\url{https://doi.org/10.1016/j.jpsychores.2023.111541}
+
+\bibitem[\citeproctext]{ref-makowski2023a}
+Makowski, D., Lau, Z. J., Pham, T., Te, A., Kirk, S., \& Liauw Yong
+Tong, C. (2023). \emph{The heart can lie: The role of interoception and
+theory of mind in deception}.
+\url{http://dx.doi.org/10.31234/osf.io/p342w}
+
+\bibitem[\citeproctext]{ref-mehling2018multidimensional}
+Mehling, W. E., Acree, M., Stewart, A., Silas, J., \& Jones, A. (2018).
+The multidimensional assessment of interoceptive awareness, version 2
+(MAIA-2). \emph{PloS One}, \emph{13}(12), e0208034.
+
+\bibitem[\citeproctext]{ref-mehling2012}
+Mehling, W. E., Price, C., Daubenmier, J. J., Acree, M., Bartmess, E.,
+\& Stewart, A. (2012). The Multidimensional Assessment of Interoceptive
+Awareness (MAIA). \emph{PLoS ONE}, \emph{7}(11), e48230.
+\url{https://doi.org/10.1371/journal.pone.0048230}
+
+\bibitem[\citeproctext]{ref-morin2016}
+Morin, A. J. S., Arens, A. K., \& Marsh, H. W. (2015). A bifactor
+exploratory structural equation modeling framework for the
+identification of distinct sources of construct-relevant psychometric
+multidimensionality. \emph{Structural Equation Modeling: A
+Multidisciplinary Journal}, \emph{23}(1), 116--139.
+\url{https://doi.org/10.1080/10705511.2014.961800}
+
+\bibitem[\citeproctext]{ref-murphy2019}
+Murphy, J., Brewer, R., Plans, D., Khalsa, S. S., Catmur, C., \& Bird,
+G. (2019). Testing the independence of self-reported interoceptive
+accuracy and attention. \emph{Quarterly Journal of Experimental
+Psychology}, \emph{73}(1), 115--133.
+\url{https://doi.org/10.1177/1747021819879826}
+
+\bibitem[\citeproctext]{ref-porges1993body}
+Porges, S. (1993). Body perception questionnaire. \emph{Laboratory of
+Developmental Assessment, University of Maryland}, \emph{10},
+s15327752jpa5304\_1.
+
+\bibitem[\citeproctext]{ref-rodriguez2016evaluating}
+Rodriguez, A., Reise, S. P., \& Haviland, M. G. (2016). Evaluating
+bifactor models: Calculating and interpreting statistical indices.
+\emph{Psychological Methods}, \emph{21}(2), 137.
+
+\bibitem[\citeproctext]{ref-ruisch2022}
+Ruisch, B. C., Von Mohr, M., Naber, M., Tsakiris, M., Fazio, R. H., \&
+Scheepers, D. T. (2022a). Sensitive liberals and unfeeling
+conservatives? {\emph{Interoceptive sensitivity predicts political
+liberalism}}. \emph{Politics and the Life Sciences}, \emph{41}(2),
+256--275. \url{https://doi.org/10.1017/pls.2022.18}
+
+\bibitem[\citeproctext]{ref-ruisch2022a}
+Ruisch, B. C., Von Mohr, M., Naber, M., Tsakiris, M., Fazio, R. H., \&
+Scheepers, D. T. (2022b). Sensitive liberals and unfeeling
+conservatives? {\emph{Interoceptive sensitivity predicts political
+liberalism}}. \emph{Politics and the Life Sciences}, \emph{41}(2),
+256--275. \url{https://doi.org/10.1017/pls.2022.18}
+
+\bibitem[\citeproctext]{ref-solanoluxf3pez2018}
+Solano López, A. L., \& Moore, S. (2018). Dimensions of Body-Awareness
+and Depressed Mood and Anxiety. \emph{Western Journal of Nursing
+Research}, \emph{41}(6), 834--853.
+\url{https://doi.org/10.1177/0193945918798374}
+
+\bibitem[\citeproctext]{ref-todd2022}
+Todd, J., Swami, V., Aspell, J. E., Furnham, A., Horne, G., \& Stieger,
+S. (2022). Are some interoceptive sensibility components more central
+than others? Using item pool visualisation to understand the
+psychometric representation of interoception. \emph{Plos One},
+\emph{17}(12), e0277894.
+
+\bibitem[\citeproctext]{ref-torregrossa2022}
+Torregrossa, L. J., Amedy, A., Roig, J., Prada, A., \& Park, S. (2022).
+Interoceptive functioning in schizophrenia and schizotypy.
+\emph{Schizophrenia Research}, \emph{239}, 151--159.
+\url{https://doi.org/10.1016/j.schres.2021.11.046}
+
+\bibitem[\citeproctext]{ref-von2023}
+Von Mohr, M., Silva, P. C., Vagnoni, E., Bracher, A., Bertoni, T.,
+Serino, A., Banissy, M. J., Jenkinson, P. M., \& Fotopoulou, A. (2023).
+My social comfort zone: Attachment anxiety shapes peripersonal and
+interpersonal space. \emph{Iscience}, \emph{26}(2).
+
 \end{CSLReferences}

### 2025-01-16 paper/1_Initial/manuscript.qmd
fix conflicts @AnafNeves

@@
 
+[**TO DO**: add - previous work suggests the importance of physiological contexts (Vlemincx et al., 2021)]
+**I  would rather put that in the discussion in the suggestions for better scales**
+
 <!-- Interoception measure -->
@@
 
-<!-- what most recent paper? -->
-
-For instance, while the use of subjective self-reports questionnaires to measure deeply embodied functions might seem paradoxical, recent redefinitions of interoception, emphasizing the role of high-level and metacognitive elaboration of interoceptive information, has provided the theoretical grounding to support the idea that some facets of interoception (including participants' metacognitive beliefs) can be assessed subjectively, providing useful and interesting measures [@murphy2019] [**TODO: also cite the most recent paper OF MURPHY with the chinese**].
+For instance, while the use of subjective self-reports questionnaires to measure deeply embodied functions might seem paradoxical, recent redefinitions of interoception, emphasizing the role of high-level and metacognitive elaboration of interoceptive information, has provided the theoretical grounding to support the idea that some facets of interoception (including participants' metacognitive beliefs) can be assessed subjectively, providing useful and interesting measures [@murphy2019; @lin2023].
 **TODO: that's a long sentence consider splitting**
-The notion that self-reports might not reflect the same processes as other interoception measures is important to contextualize the apparent lack of convergence between various measures in the field [@desmedt2022measures].
-A better understanding of what is being measured with different questionnaires and dimensions, as well their potential overlaps with other constructs (e.g., alexithymia, body awareness), is thus needed to clarify the role of self-reports in the assessment of interoception.
+The notion that self-reports might not reflect the same processes as other interoception measures is important to contextualize the apparent lack of convergence between measures in the field [@desmedt2022measures].
+A better understanding of what is being measured with different questionnaires and dimensions, as well as their potential overlaps with other constructs (e.g., alexithymia, body awareness), is thus needed to clarify the role of self-reports in the assessment of interoception.
 
@@
 
-While the assessment of the validity of an interoception scale can be conceived as theoretically challenging, several traits have been used to assess convergent validity for the the IAS, including expected negative associations with alexithymia [@brand2023; @koike2023; @campos2021, @murphy2019; @lin2023], somatic symptoms [@brand2023; @koike2023], depressive symptoms [@brand2023; @koike2023], anxiety [@brand2023], neuroticism [@brand2023].
+While the assessment of the validity of an interoception scale can be conceived as theoretically challenging, several traits have been used to assess convergent validity for the the IAS, including expected negative associations with alexithymia [@brand2023; @koike2023; @campos2021, @murphy2019; @lin2023], somatic symptoms [@brand2023; @koike2023, @lin2023], depressive symptoms [@brand2023; @koike2023; @lin2023], anxiety [@brand2023], neuroticism [@brand2023] and self-esteem [@murphy2019].
 <!-- **anything else?**. TO BE COMPLETED -- to be determined -->
@@
 <!-- Moreover, the current subjective measures do not correlate well with the objective measures [@murphy2019]. -->
+
+Few studies have examined the correlation between objective interoceptive measures, such as the Heartbeat Counting Task (HCT; Schandry, 1981) and the Heartbeat Detection Task (HDT; Kleckner et al., 2015).
+Existing findings report weak correlations for the HCT (Murphy et al., 2019), no correlations except for the sensitivity variable of the HCT (Brand et al., 2023), and small correlations for the HDT (Brand et al., 2023).
+These results suggest that the IAS, a subjective measure, does not strongly align with objective interoceptive assessments.
+
+<!-- current study -->
 
@@
 
+<!-- Distibutions of items -->
+
 Visualizing the distribution of the items for all samples suggests the presence of a consistent modal value (@fig-distributions).
@@
 
+<!-- Univariate analysis -->
+
 The UVA revealed that there are two large to very large redundant variables when taking all samples into account.
@@
 
+<!-- Network analysis -->
+
 According to the network analysis, using the Walktrap and Louvain algorithms applied to Glasso networks, a 4-factor structure fits the questionnaire best across all data sets.
@@
 The 4-factor structure model with the best fit entails the following items per group: 1) itch, tickle, bruise, blood sugar; 2) burp, wind, cough, sneeze, vomit; 3) affective touch, sexual arousal, muscles, temperature, pain, and taste; 4) Heart, breathing, hungry, thirsty, urinate, and defecate.
+
+<!-- Stability analysis -->
 
@@
 
+<!-- Factor analysis -->
+
 When accounting for all samples, the factor analysis reveals that a 4-factor structure fits best.
@@
 Since UVA identified "tickle" as the item to be removed—and it also had the lowest uniqueness value in factor analysis with a similar loading to "itch"—"tickle" was excluded from subsequent analyses.
+
+<!-- Confirmatory factor analysis -->
 
@@
 
+<!-- Ias structure -->
+
 In this study, several datasets were analyzed for a meta analysis of the structure of the IAS.
@@
 
-These findings contrast with previous research, which all found that a 2-factor model, or a 1-factor model fits the data best [@murphy2019, @lin2023, @campos2021, @brand2023].
+<!-- linking findings to previous research -->
+
+These findings contrast with previous research, which all found that 2-factor model[@murphy2019; @koike2023], 1-factor model [@brand2023] and bifactor model [@lin2023; @campos2021] fits the data best.
 While this analysis also revealed an okay fit for the 1-factor model, the 4-factor model revealed the best fit.
@@
 
+<!-- Items redundancy -->
+
 There are several items that show redundancy suggesting that adapting the IAS would be beneficial for validity.
-Based on the given results, we suggest removing the tickle, while keeping the itch item (stats).
+Based on the given results, we suggest removing the tickle, while keeping the itch item [**todo**: stats?].
 Other items with slight redundancy were Hungry and Thirsty, Urinate and Defecate, and Sneeze and Cough.
+
+<!-- Lins short IAs kept: Hunger, Breath, Urinate, Taste, Vomit, Cough, Temperature, Sexual Arousal, Wind, Muscle, Pain, Itch -->
 
@@
 On top of that, they came up with a shortened version of the IAS, excluding further items, resulting in a 12-item IAS, which aligns with our findings, suggesting that further items are ambiguous as to whether they should be removed.
-In contrast, other findings also found itch and tickle to be redundant but did not suggest excluding items .
+In contrast, other findings also found itch and tickle to be redundant but did not suggest excluding items [@campos2021].
+
+<!-- low density on extreme values (1 and 5) -->
 
@@
 
-The questionnaires used for the IAS correlates are listed in Table 2 (**TODO: add the rest of the questionnaires, sample items and references**).
+The questionnaires used for the IAS correlates are listed in **Table 2** (**TODO: add the rest of the questionnaires, sample items and references**).
 
-**Table 2.** Questionnaires used for the IAS correlates analysis.
-
-| Questionnaire              | Number of Dimensions | Assessment                              | Number of Items | Scoring                | Example Item |
-|------------|------------|------------|------------|------------|------------|
-| **Interoceptive Related**  |                      |                                         |                 |                        |              |
-| MAIA-2                     | 8                    | Interoception                           | 37              | 6-point Likert scale   |              |
-| BPQ                        | 2                    | Body awareness and autonomic reactivity | 49              | 5-point Likert scale   |              |
-| TAS-20                     | 3                    | Alexithymia                             | 20              | 5-point Likert scale   |              |
-| BVAQ                       | 2                    | Alexithymia                             | 40              | 5-point Likert scale   |              |
-| **Mood**                   |                      |                                         |                 |                        |              |
-| BDI-II                     | 1                    | Severity of depressive symptoms         | 21              | 0-to-3-point values    |              |
-| PHQ-4                      | 2                    | Anxiety and depressive symptoms         | 4               | 5-point Likert scale   |              |
-| STAI-T                     | 1                    | Trait anxiety                           | 20              | 4-point Likert scale   |              |
-| GAD-2                      | 1                    | General Anxiety                         | 2               | 4-point Likert scale   |              |
-| **Personality**            |                      |                                         |                 |                        |              |
-| NEO-FFI                    | 1                    | Neuroticism                             | 12              | 5-point Likert scale   |              |
-| Mini IPIP6                 | 6                    | Personality                             | 24              | Analogue scales        |              |
-| BFI                        | 5                    | Personality                             | 44              | 5-point Likert scale   |              |
-| PID-5-SF                   | 5                    | Dysfunctional personality traits        | 25              | 4-point Likert scale   |              |
-| **Psychopathology**        |                      |                                         |                 |                        |              |
-| SPQ-BRU                    | 4                    | Schizotypy                              | 32              | 5-point Likert scale   |              |
-| MSI-BPD                    | 1                    | Borderline personality disorder         | 10              | Analogue scales        |              |
-| ASQ - Short                | 5                    | Autistic Traits                         | 28              | 4-point Likert scale   |              |
-| **Beliefs and Misbeliefs** |                      |                                         |                 |                        |              |
-| GCB                        | 5                    | Conspiracy beliefs                      | 15              | 5-point Likert scale   |              |
-| PI-18                      | 1                    | Beliefs about the world                 | 99              | 6-point Likert scale   |              |
-| LIE scale                  | 4                    | Lying tendencies                        | 16              | Visual analogue scales |              |
-
-*Note.* MAIA-2 Multidimensional Assessment of Interoceptive Awareness Version-2 (Mehling et al.
-2018); BPQ Body Perception Questionnaire; TAS-20 Toronto Alexithymia Scale (Bagby et al., 1994); BVAQ Bermond-Vorst Alexithymia Questionnaire (Vorst & Bermond, 2001); BDI-II Beck's Depression Inventory (Dozois et al., 1998); PHQ-4 Patient Health Questionnaire (Kroenke et al., 2009); STAI-T State-Trait-Anxiety Inventory Trait-Version (Spielberger et al.
-1970); GAD- 2 Generalized Anxiety Disorder Scale – 2 (Spitzer et al., 2007); NEO-FFI NEO Five-Factor Inventory Neuroticism (Costa & McCrae, 2008); Mini IPIP6 Mini International Personality Item Pool (Sibley et al.
-2011); BFI Big Five Inventory (John et al., 2010); PID-5-SF Personality Inventory for DSM-5 Short Form (Thimm et al., 2016); SPQ-BRU Schizotypal Personality Questionnaire (Davidson et al., 2016); MSI-BPD Mclean Screening Instrument for Borderline Personality Disorder (Zanarini et al.
-2003); ASQ Short Autism-Spectrum Quotient (Hoekstra et al.
-2011); GCB Generic Conspiracist Beliefs scale (Brotherton et al., 2013); PI-18 Primals Inventory (Clifton et al., 2021); LIE scale Lying Profile Questionnaire (Makowski, et al,.
-2023).
+\input{../../analysis/figures/table2.tex}
 

### 2025-01-16 paper/1_Initial/manuscript.qmd
horizontal table

@@
     documentmode: man
+    include-in-header:
+      - text: |
+          \usepackage{lscape}
   apaquarto-docx: default
@@
 
-<!-- This only works when redering to pdf right? -->
+\begin{landscape}
 \input{../../analysis/figures/table1.tex}
+\end{landscape}
 

### 2025-01-16 paper/1_Initial/manuscript.qmd
more paragraph up

@@
 
+<!-- Relationship with other interoception measures -->
+
+The IAS has naturally been compared to other interoception-related scales, and shows a positive correlations with most facets of the MAIA **(TODO: MAIA should be introduced before)**, except for the Non-Distracting and Not-Worrying subscales [@brand2023].
+Interestingly, findings on the correlation between the IAS and the body awareness dimension of the Body Perception Questionnaire [BPQ-A, @porges1993body] have been mixed: some studies report small positive correlations [@brand2023; @campos2021; @koike2023], while others find small negative correlations [@lin2023] or no correlation at all [@murphy2019].
+Small positive correlations have also been observed with the "observation" and "description" subscales of the Five Facet Mindfulness Questionnaire [FFMQ, @baer2006using; @brand2023; @koike2023], as well as with the "non-reactivity" and "acting with awareness" subscales [@koike2023].
+Additionally, the IAS has shown a positive correlation with the interoceptive awareness subscale of the Eating Disorder Inventory [@lin2023] and a negative correlation with the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia; @brand2023; @murphy2019].
+Lastly, small positive correlations have also been reported with the Interoceptive Attention Scale [IATS, @gabriele2022dissociations], though studies have also found no correlation between these measures [@gabriele2022dissociations] **(TODO: why same reference for two contradictory claims?)**.
+
 <!-- TO BE COMPLETED -->
@@
 
-While the assessment of the validity of an interoception scale can be conceived as theoretically challenging, several traits have been used to assess convergent validity for the the IAS, including expected negative associations with alexithymia [@brand2023; @koike2023; @campos2021, @murphy2019; @lin2023], somatic symptoms [@brand2023; @koike2023, @lin2023], depressive symptoms [@brand2023; @koike2023; @lin2023], anxiety [@brand2023], neuroticism [@brand2023] and self-esteem [@murphy2019].
+While assessing the validity of an interoception scale can be conceived as theoretically challenging, several measures have been used to assess convergent validity for the the IAS, including expected negative associations with alexithymia [@brand2023; @koike2023; @campos2021, @murphy2019; @lin2023], somatic symptoms [@brand2023; @koike2023, @lin2023], depressive symptoms [@brand2023; @koike2023; @lin2023], anxiety [@brand2023], neuroticism [@brand2023] and self-esteem [@murphy2019].
 <!-- **anything else?**. TO BE COMPLETED -- to be determined -->
-
-The IAS has also been compared to other interoception scales (and interoceptive related scales),generally showing positive correlations with most facets of the MAIA, except for the Non-Distracting and Not-Worrying subscales [@brand2023].
-Findings on the correlation between the IAS and the body awareness dimension of the Body Perception Questionnaire (BPQ-A; @porges1993body) have been mixed: some studies report small positive correlations [@brand2023; @campos2021; @koike2023], while others find small negative correlations [@lin2023] or no correlation at all [@murphy2019].
-Small positive correlations have also been observed with the observation and description subscales of the Five Facet Mindfulness Questionnaire (FFMQ, @baer2006using; @brand2023; @koike2023), as well as with the nonreactivity and acting with awareness subscales [@koike2023].
-Additionally, the IAS has shown a positive correlation with the interoceptive awareness subscale of the Eating Disorder Inventory [@lin2023] and a negative correlation with the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia; @brand2023; @murphy2019].
-Lastly, small positive correlations have been reported between the Interoceptive Attention Scale (IATS, @gabriele2022dissociations) and the IAS [@lin2023; @koike2023], though studies have also found no correlation between these measures [@gabriele2022dissociations].
-
-<!-- TO BE COMPLETED -->
 

### 2025-01-16 paper/1_Initial/manuscript.qmd
Update manuscript.qmd

@@
 The notion that self-reports might not reflect the same processes as other interoception measures is important to contextualize the apparent lack of convergence between measures in the field [@desmedt2022measures].
+**(TODO: I would talk here a bit more about the relationship and lack thereof with intero tasks rather than later)**
 A better understanding of what is being measured with different questionnaires and dimensions, as well as their potential overlaps with other constructs (e.g., alexithymia, body awareness), is thus needed to clarify the role of self-reports in the assessment of interoception.

### 2025-01-16 paper/1_Initial/manuscript.qmd
Update manuscript.qmd

@@
 The goal of study 1 is to re-analyse and assess the factor structure of the IAS by taking advantage of the large number of open-access datasets [@brand2023; @campos2021; @lin2023; @murphy2019; @arslanova2022; @todd2022; @gaggero2021; @brand2022; @von2023].
-While combining these studies might provide a more robust and generalizable understanding of the IAS' factor structure, it is important to note that the studies differ in their sample sizes, demographics, language, and the way they collected the data.
-Thus, providing additionally an individual analysis (i.e., on all samples individually) will help adding nuance to the general picture.
+While combining these studies might provide a more robust and generalizable understanding of the IAS' factor structure, we also additionally provide an individual analysis (i.e., on all samples separately) to add nuance to the general picture, as all studies differ in their sample sizes, demographics, language, and procedure.
 

### 2025-01-16 paper/1_Initial/manuscript.qmd
remove stuff

@@
     orcid: 0009-0006-0020-7599
-    # roles: 
-      # - Project administration
-      # - Data curation
-      # - Formal Analysis
-      # - Investigation
-      # - Visualization
-      # - Writing – original draft
-      # - Writing – review & editing
+    roles:
+      - Project administration
+      - Data curation
+      - Formal Analysis
+      - Investigation
+      - Visualization
+      - Writing – original draft
+      - Writing – review & editing
     affiliations:
-      - id: id1
+      - id: "id1"
         name: "University of Sussex"
-        department: School of Psychology
-        # address: 1234 Capital St.
-        # city: New York
-        # region: NY
-        # country: USA
-        # postal-code: 12084-1234
+        department: "School of Psychology"
+        city: "Brighton"
+        country: "UK"
+        postal-code: "BN1 9RH"
 # author-note:
@@
     affiliations:
-      - ref: id1 
+      - ref: "id1" 
   - name: Dominique Makowski
@@
     url: https://realitybending.github.io/
-    # Select from the CRediT: Contributor Roles Taxonomy https://credit.niso.org/
-    # roles:
+    roles:
+      - Conceptualization
+      - Data curation
+      - Formal Analysis
+      - Funding acquisition
+      - Investigation
+      - Methodology
+      - Project administration
+      - Resources
+      - Software
+      - Supervision
+      - Validation
+      - Visualization
+      - Writing – original draft
     affiliations:
-      - ref: id1 
+      - ref: "id1"
+      - name: "University of Sussex"
+        department:  "Sussex Centre for Consciousness Science"
 author-note:
@@
       ::: {.callout-note icon=false appearance="simple"}
+      :::
       This preprint is a non-peer-reviewed work from the [**Reality Bending Lab**](https://realitybending.github.io/).
       ![](https://realitybending.github.io/media/ReBeL_LogoOnly_hu11484441381606756729.png){width=20% fig-align="center"}
-      :::
 abstract: |
@@
 Subsequently, exploratory factor analysis (EFA) was employed followed by confirmatory factor analysis (CFA).
-
-### Results
-
-<!-- Distibutions of items -->
-
-Visualizing the distribution of the items for all samples suggests the presence of a consistent modal value (@fig-distributions).
-In other words, participants are most likely to answer 4/5 (i.e., agree) on most items (but "affective touch", "blood sugar", and "bruise" that exhibit a different distributional pattern).
-Additionally, one can note the low density on extreme values (1 and 5), meaning that the bulk of answers (i.e., 99\%) varies between 3 values.
-The interindividual variability seems improved in the samples using an analogue scale, displaying a more continuous and progressive spread of answers.
-
-```{r}
-#| warning: false
-#| label: fig-distributions
-#| fig-cap: "Distribution of responses for all items across various datasets."
-
-knitr::include_graphics("figures/Figure1.png")
-```
-
-#### Correlations
-
-The correlation analysis revealed that the items overall have positive intercorrelation patterns with no clear structure emerging.
-This remains the same across all samples.
-However, there are possibly some higher-order groupings emerging for the 2 analog-scale samples.
-
-#### EGA
-
-<!-- Univariate analysis -->
-
-The UVA revealed that there are two large to very large redundant variables when taking all samples into account.
-Namely, "itch" and "tickle", where "tickle" should be removed, and "itch" should be kept. 
-There are several more items that are moderately to largely redundant, namely, "wind" and "burp", and "urinate" and "defecate".
-On top of that, "sneeze" and "cough", "heart" and "breathing", and "hungry" and "thirsty" seem to have small to moderate redundancy.
-These findings are rather consistent across the samples with minor differences, such as that when the questionnaire had an analog scale, there seems to be no large to very large redundant items but "itch" and "tickle" remain moderately to largely redundant and "heart" and "breathing" small to moderately redundant in one sample.
-
-<!-- Network analysis -->
-
-According to the network analysis, using the Walktrap and Louvain algorithms applied to Glasso networks, a 4-factor structure fits the questionnaire best across all data sets.
-This is rather consistent within the data sets, where some samples indicate 3-factor structure, and some a 5-factor structure would fit well too.
-The 4-factor structure model with the best fit entails the following items per group: 1) itch, tickle, bruise, blood sugar; 2) burp, wind, cough, sneeze, vomit; 3) affective touch, sexual arousal, muscles, temperature, pain, and taste; 4) Heart, breathing, hungry, thirsty, urinate, and defecate.
-
-<!-- Stability analysis -->
-
-Stability analysis, employing 500 bootstrap iterations, also favoured the 4-factor solution for its greater stability.
-Most items, except for 'affective touch,' demonstrated stability levels exceeding 0.90, indicating structural consistency and reliability [@christensen2021].
-These findings underscore the robustness of the identified 4-dimensional structure.
-
-<!-- Factor analysis -->
-
-When accounting for all samples, the factor analysis reveals that a 4-factor structure fits best.
-The exploratory factor analysis revealed that 4 latent factors (oblimin rotation) accounted for 51.95% of the total variance of the original data (MR2 = 19.08%, MR1 = 17.78%, MR4 = 9.34%, MR3 = 5.75%).
-Since UVA identified "tickle" as the item to be removed—and it also had the lowest uniqueness value in factor analysis with a similar loading to "itch"—"tickle" was excluded from subsequent analyses.
-
-<!-- Confirmatory factor analysis -->
-
-Confirmatory factor analysis compared 5 models: a single-factor solution, a 4-factor solution, a 5-factor solution, a 6-factor solution and a 7-factor solution.
-The latter was preferred in most datasets, including with indices that penalise increased number of parameters (such as BIC).
-There was no evidence for higher order factors.
-
-### Discussion
-
-<!-- Ias structure -->
-
-In this study, several datasets were analyzed for a meta analysis of the structure of the IAS.
-The findings reveal that a 4-factor model fits the IAS best.
-Additionally, the lowest level structure (pairs of items) seem to be the most robust, especially for samples using Likert scales (some higher-order groupings might emerge for the 2 analog-scale samples).
-There was no clear evidence for higher-order factors.
-
-<!-- linking findings to previous research -->
-
-These findings contrast with previous research, which all found that 2-factor model[@murphy2019; @koike2023], 1-factor model [@brand2023] and bifactor model [@lin2023; @campos2021] fits the data best.
-While this analysis also revealed an okay fit for the 1-factor model, the 4-factor model revealed the best fit.
-The 4-factor structure reveals different ‘hubs' of items that are related, not only in this structure analysis, but also in underlying mechanisms.
-The ‘wind-burp-cough-sneeze-vomit' category, for example, only entails items that are linked to excretion through the mouth.
-The other categories are organized similarly.
-This organization and structure is useful for further analysis, as the data can be analyzed and interpreted according to a grouping that is coherent in result, as well as underlying mechanisms.
-
-<!-- Items redundancy -->
-
-There are several items that show redundancy suggesting that adapting the IAS would be beneficial for validity.
-Based on the given results, we suggest removing the tickle, while keeping the itch item [**todo**: stats?].
-Other items with slight redundancy were Hungry and Thirsty, Urinate and Defecate, and Sneeze and Cough.
-
-<!-- Lins short IAs kept: Hunger, Breath, Urinate, Taste, Vomit, Cough, Temperature, Sexual Arousal, Wind, Muscle, Pain, Itch -->
-
-Interestingly, @lin2023 also found that tickle and itch were redundant, excluding one of them but the reason being that the character for both words is the same in the Chinese language.
-On top of that, they came up with a shortened version of the IAS, excluding further items, resulting in a 12-item IAS, which aligns with our findings, suggesting that further items are ambiguous as to whether they should be removed.
-In contrast, other findings also found itch and tickle to be redundant but did not suggest excluding items [@campos2021].
-
-<!-- low density on extreme values (1 and 5) -->
-
-The findings indicate a high proportion of answers at 4 (see Figure 1), especially when using a 5-step scale.
-The analogue scale shows a more dispersed distribution, with some answers indicating the highest 5/5, which was not the case in the 5-step scale.
-Therefore, we recommend using an analog scale for the IAS.
-
-Before this paper, the IAS has not yet been used or analyzed with an analog scale, rather than a five step scale.
-Therefore, this study provides a novel approach to improving the IAS in a simple manner.
-
-### Limitations and Future Directions
-
-There are several limitations to the IAS; There are some redundant items, the 5-point scale does not provide great variability, and the structure could be improved.
-Therefore, improving the IAS, or creating a new questionnaire investigating interoception could be useful to achieving reliable and accurate indication of interoceptive awareness.
-
-## Study 2
-
-Study 2 aims to investigate correlates of the IAS.
-Correlations of the IAS will be computed to assess the relationship between subjective interoceptive accuracy and other subjective measures of interoception, mood, psychopathology, personality, and beliefs.
-Investigating correlates will help validate the IAS, as well as other interoceptive measures in the future.
-The
-
-### Methods
-
-#### Materials
-
-The questionnaires used for the IAS correlates are listed in **Table 2** (**TODO: add the rest of the questionnaires, sample items and references**).
-
-\input{../../analysis/figures/table2.tex}
-
-#### Statistical analysis
-
-Correlations will be computed using the correlation package under a Bayesian framework (ref).
-
-### Results
-
-The EGA components capture groupings of pairs of items, such as "wind" and "burp", "cough" and "sneeze", or "muscle" and "pain".
-These groupings were used in the correlational analysis, to observe how much each group/pair correlates with other factors, such as Alexithymia, or the MAIA (see Figure 2).
-
-Alexithymia is negatively correlated with all interoceptive groups.
-Autistic traits are mostly negatively correlated with IAS measure, except for patterns and numbers (as an autistic trait), which is significantly and positively correlated with the "itch/bruise" pairing.
-The BPQ Body Awareness part is positively correlated with all IAS pairs, whereas the Autonomic Reactivity part is negatively correlated with all IAS groupings.
-Conspiracy Beliefs were all positively correlated with the IAS pairs, however, only Global Conspiracy with "hungry/thirsty", "urinate/defecate" and "cough/sneeze", as well as personal wellbeing with "hungry/thirsty", and Information Control with "cough/sneeze" were significantly positively correlated.
-Demographic data is also mostly positively correlated with the IAS findings, where gender and age more strongly correlated with "hungry/thirsty".
-In this analysis, lying profile is not strongly correlated with the IAS; Except for contextuality, which shows a significant negative correlation with "itch/bruise".
-The MAIA has a strong positive correlation with most IAS pairings, except for the "not worrying" and "not distracting" items of the MAIA, which show less strong, or even negative correlations with all IAS item pairings.
-Maladaptiveness had mostly negative correlations with the IAS, with only a few significant correlations, namely "psychoticism", "negative affect", and "detachment" with "muscle/pain" and "hungry/thirsty", as well as "negative affect" with "wind/burp".
-Overall, mood was mostly negatively correlated with the IAS, where "hungry/thirsty" had the strongest negative correlation of all mood measures.
-Except for "neuroticism" and "honesty-humility", personality traits, such as "openness" and "extraversion" were positively correlated with the IAS groupings.
-Shizotypic traits were mostly negatively correlated with the IAS, with "hungry/thirsty" showing the strongest negative correlation between schizotypic and the IAS.
-World beliefs were mostly positively correlated with the IAS, however, only a few were significant: "hierarchical", "enticing", and "alive" correlates significantly with "muscle/pain"; "Understandable" has a significant positive correlation with "heart/breathing"; And "hierarchical" and "alive" has a significant positive correlation with "hungry/thirsty".
-
-![**Figure 2.** Correlates of the IAS](figures/clipboard-1619164537.png){width="911"}
-
-### Discussion
-
-Our findings confirmed that interception lies within an intricate network of correlates.
-Alexithyma has the most negative correlation with the IAS, whereas, the MAIA questionnaire is most strongly positively correlated with the IAS.
-The correlates cannot only explain attributes of interoception, but can also be used to validate measures for interoception.
-
-While these results reveal correlations of different categories with the IAS, the findings are limited to the given questionnaire.
-However, they give a good indication of how interoception in general might be linked to the different categories, leading to interesting findings.
-The results show a consistent pattern of correlations with other interoception measures, psychopathology, and highlighting of interesting exploratory results, such as how primal world beliefs correlate with the IAS.
-
-The analysis revealed a negative correlation between alexithymia and scores in the IAS, which is in line with previous research [@herbert2011].
-A negative correlation between autism and interoceptive awareness, which has been found in this sample, has also been found in previous research [@dubois2016].
-Conspiracy Beliefs and IAS scores were not strongly correlated.
-However, there was a slight positive correlation.
-To the best of our knowledge, this interaction has not been investigated before.
-However, research shows correlations between (political) beliefs and interoception, which could underlie the same mechanism [@ruisch2022].
-Lying profile was also not strongly correlated with the IAS.
-Previous research provides some evidence for a relationshipbetween interoception and lying profile [@makowski2023a], indicating a contrast from the literature to the results at hand.
-The analysis showed that mood and the IAS scores have a strong negative correlation, which has been investigated in previous studies, finding a correlation between the two variables as well [@solanolópez2018].
-The analysis showed that personality is also correlated with interoceptive accuracy scores as retrieved by the IAS.
-While there are many aspects of personality, put simply, personality and interoception have been found to correlate in previous studies as well [@erle2021].
-Our findings show some negative correlations between schizotypy and interoception.
-Previous research has investigated this relationship and, similarly, found a negative correlation between interoceptive awareness and schizotypy, particularly at the onset of psychosis [@torregrossa2022].
-Lastly, World Beliefs and Interoception showed some significant positive correlations.
-World Beliefs have not been linked with interoception previously.
-As mentioned, other beliefs, such as political beliefs have been mentioned to interoception, where significant correlations were observed [@ruisch2022a].
-Further research is needed to understand this mechanism and validate whether world beliefs, which lay the framework through which we see the world [@clifton2020], is needed.
-
-The above findings show how interoception is correlated with many lifestyle and health factors, and is therefore an important concept to study.
-Here we showed many correlates of the IAS and lifestyle, as well as health factors.
-This is not only valuable to understand interception, and the role it plays in our lives, better, but also crucial to further validate the Ias, as well as other interoception measures.
-This analysis therefore lays the groundwork for validating new interoceptive measures and questionnaires needed to grasp interoception and its role in our life.
-
-## General Discussion
-
-The analyses revealed that the IAS has 4-factor structure, and a rather uneven distribution.
-The findings indicate that the IAS is measuring interoception in an acceptable manner, but there is also room for improvement.
-Furthermore, the results reveal different correlation measures with the IAS, giving space to further explore whether and how measures correlate with interoception/the IAS.
-In the following section, the IAS is discussed further to reveal shortcomings and strengths of the questionnaire.
-Finally, future steps will be revealed to improve the way in which we measure interoception.
-
-Overall, the IAS is straightforward with its sensation-centered items.
-There are several points of improvement to the IAS, which this work suggests.
-Firstly, removing redundant items, such as the itch item as shown in the above analysis.
-Previous work has also shown that the itch and tickle items are subject to redundancy [@lin2023, @campos2021] has shown.
-Interestingly, @campos2021 suggest removing the tickle item instead.
-@lin2023 on the other hand removed the itch item, because the sign for itch and tickle is the same.
-Furthermore, this work recommends using analog scales, instead of 5 point scales.
-In a 5-point scale, the variability is clearly limited with most people choosing ⅘.
-As visible in Figure X, the variability increases significantly, using an analog scale.
-However, it is important to note that even with an analog scale, the variability of the IAS is still limited.
-The more variability a scale shows, the more results can depict individual differences between participants.
-Therefore, good dispersion is essential for achieving relevant and usable results, and striving for more variability would be beneficial to this interoception scale, too.
-
-In this work, it becomes apparent that even with the mentioned improvements to the scale, there are limitations to the IAS, which reduce the accuracy of this scale.
-Those limitations include that there are few items for some modalities, such as only one item for heart perception.
-Having more modality is useful as each grouping can have more variability with increased modality, leading to more nuanced results.
-On top of that, there is no clear and theoretical, or empirical structure, as there is a very small grouping of items.
-Ideally, a scale would allow for an analysis showing different groupings so that different categories can be created based on which the data can be analyzed.
-The groupings in this analysis reveal that the IAS can only be grouped with two items per group, leading to low scores and variability in each group.
-On top of that, there are ambiguous items in the IAS, of which the grouping depends on the context.
-For example, one might indicate that they can perceive well how their heart is beating fast as well as vomiting, but both items can be linked to feeling anxious, and therefore might indicate different results than initially expected.
-Therefore, the grouping and structure of the IAS can be improved.
-
-Furthermore, all items are phrased positively, which might influence how participants answer the questions.
-While phrasing items in a positive manner can be beneficial, the benefits of positive phrasing might exacerbate a positive bias and thus lead to unidimensional results.
-Therefore, phrasing questions in a more diverse manner might lead to more accurate results and might thus be beneficial.
-
-Based on the given arguments, it becomes clear that there is a need for context-specific items, which are cross-modal when possible, such as integrating cardioception and respiroception.
-After establishing the clear need for a new scale to measure interoception, this study proposes the need for a new scale (Multimodal Interoceptive Sensitivity Scale, MISS) to adapt to the newest findings on the IAS and what we know about interoception to this day.
-The new scale will be able to be compared to the correlates of the IAS.
-
-## Conclusion
-
-The IAS is a good way of measuring interoception considering the current existing questionnaires and tools.
-However, revising, or even re-inventing a survey to measure interoception would lead to the best measure of interoception.
-Therefore, this study proposes that a new scale to measure interoception is needed to evolve the current research on interoception.
-This study revealed many correlates of the IAS, giving space for future analysis on what might be a good interoceptive measure, and therefore laying the groundwork for the creation of a new interoception survey.
-
-## References
-
-<!-- References will auto-populate in the refs div below -->
-
-::: {#refs}
-:::

### 2025-01-27 paper/1_Initial/manuscript.qmd
minor changes

@@
     #   - Writing – original draft
-    #   - Writing – review & editing
-  - name: Magdalena Pfaff
-    orcid: 0009-0006-2386-7936
-    affiliations:
-      - ref: "id1" 
-  - name: Dominique Makowski
-    corresponding: true
-    orcid: 0000-0001-5375-9967
-    email: D.Makowski@sussex.ac.uk
-    url: https://realitybending.github.io/
-    roles:
-      - Conceptualization
-      - Data curation
-      - Formal Analysis
-      - Funding acquisition
-      - Investigation
-      - Methodology
-      - Project administration
-      - Resources
-      - Software
-      - Supervision
-      - Validation
-      - Visualization
-      - Writing – original draft
-    affiliations:
-      - ref: "id1"
-      - name: "University of Sussex"
-        department:  "Sussex Centre for Consciousness Science"
+  #   #   - Writing – review & editing
+  # - name: Magdalena Pfaff
+  #   orcid: 0009-0006-2386-7936
+  #   affiliations:
+  #     - ref: "id1" 
+  # - name: Dominique Makowski
+  #   corresponding: true
+  #   orcid: 0000-0001-5375-9967
+  #   email: D.Makowski@sussex.ac.uk
+  #   url: https://realitybending.github.io/
+  #   roles:
+  #     - Conceptualization
+  #     - Data curation
+  #     - Formal Analysis
+  #     - Funding acquisition
+  #     - Investigation
+  #     - Methodology
+  #     - Project administration
+  #     - Resources
+  #     - Software
+  #     - Supervision
+  #     - Validation
+  #     - Visualization
+  #     - Writing – original draft
+  #   affiliations:
+  #     - ref: "id1"
+  #     - name: "University of Sussex"
+  #       department:  "Sussex Centre for Consciousness Science"
 author-note:
@@
 
-[**TO DO**: add - previous work suggests the importance of physiological contexts (Vlemincx et al., 2021)]
-**I  would rather put that in the discussion in the suggestions for better scales**
-
 <!-- Interoception measure -->
@@
 
-For instance, while the use of subjective self-reports questionnaires to measure deeply embodied functions might seem paradoxical, recent redefinitions of interoception, emphasizing the role of high-level and metacognitive elaboration of interoceptive information, has provided the theoretical grounding to support the idea that some facets of interoception (including participants' metacognitive beliefs) can be assessed subjectively, providing useful and interesting measures [@murphy2019; @lin2023].
-**TODO: that's a long sentence consider splitting**
+The use of subjective self-report questionnaires to measure deeply embodied functions might seem paradoxical.
+However, recent redefinitions of interoception emphasize the role of high-level and metacognitive elaboration of interoceptive information.
+These redefinitions provide theoretical grounding to support the idea that some facets of interoception, including participants' metacognitive beliefs, can be assessed subjectively.
+This approach offers useful and interesting measures [@murphy2019; @lin2023].
+
 The notion that self-reports might not reflect the same processes as other interoception measures is important to contextualize the apparent lack of convergence between measures in the field [@desmedt2022measures].
-**(TODO: I would talk here a bit more about the relationship and lack thereof with intero tasks rather than later)**
+
+<!-- lack of convergence between self-reported questionnaires -->
+
+A recent systematic review by @desmedt2022measures examined whether various questionnaires designed to measure "interoceptive sensibility" truly assess the same construct.
+Notably, @garfinkel2015knowing defines interoceptive sensibility as the self-reported tendency to focus on and detect internal sensations, whereas @khalsa2018interoception defines it more narrowly, excluding the ability to detect these signals.
+According to @desmedt2022measures, most authors adopt the latter definition.
+The review found that these questionnaires measure related but distinct constructs, leading researchers to commit the 'jingle fallacy'—mistakenly treating them as equivalent measures of interoceptive sensibility.
+
+**TODO: do a better job**
+
+<!-- Moreover, the current subjective measures do not correlate well with the objective measures [@murphy2019]. -->
+
+Few studies have examined the correlation between objective interoceptive measures, such as the Heartbeat Counting Task (HCT; Schandry, 1981) and the Heartbeat Detection Task (HDT; Kleckner et al., 2015).
+Existing findings report weak correlations for the HCT (Murphy et al., 2019), no correlations except for the sensitivity variable of the HCT (Brand et al., 2023), and small correlations for the HDT (Brand et al., 2023).
+These results suggest that the IAS, a subjective measure, does not strongly align with objective interoceptive assessments.
+
 A better understanding of what is being measured with different questionnaires and dimensions, as well as their potential overlaps with other constructs (e.g., alexithymia, body awareness), is thus needed to clarify the role of self-reports in the assessment of interoception.
@@
 
-Although the original validation study suggested a two-factor structure for the IAS (**TODO: what are they?**), the authors underline its acceptable but imperfect fit [@murphy2019; p.
+Although the original validation study suggested a two-factor structure for the IAS, the authors underline its acceptable but imperfect fit [@murphy2019; p.
 127], calling on further investigation of the scale's factor structure.
-Notably, the only other validation study to report a 2-factor solution was conducted by @koike2023, who performed an Exploratory Factor Analysis (EFA) assuming 2 factors to align with the findings from the original validation paper.
-**TODO: this above is not really a validation study showing 2 factors is good if they prespecified two to match the original?**
-Other follow-up studies using confirmatory factor analysis (CFA) and structural modeling [@morin2016] have identified different optimal solutions. 
+Notably, the authors did not define these factors, as no clear explanations were evident.
+They suggested that the first factor reflects the perception of interoceptive signals, while the second pertains to signals that may be difficult to perceive solely through interoceptive information.
+
+<!-- [@morin2016] is a methodological paper on ESEM -->
+
+Other follow-up studies using confirmatory factor analysis (CFA) and structural modeling have identified different optimal solutions. 
 Some studies, like @brand2023, reported a 1-factor solution, while @lin2023 and @campos2021 found bifactor solutions - one general factor and a set of lower-level factors [@rodriguez2016evaluating] - to be the best fit.
-**TODO: what does morin2016 found? I would cite it after saying what they found rather than here**
+Notably, the only other study to report a 2-factor solution was conducted by @koike2023, who performed an Exploratory Factor Analysis (EFA) assuming 2 factors to align with the findings from the original validation paper.
 
@@
 @lin2023 also highlights their correlation analysis, showing five locally dependent pairs and three items (touch, blood sugar, bruise) with exceptionally high difficulty and low discrimination. 
-Additionally, @campos2021 suggests that the "tickle" item represents a more specific *(separate?*) factor.
+Additionally, @campos2021 reported "tickle" to be the only item that reflected more specific factors than the general factor. 
 Interestingly, @lin2023 reported that all items of the IAS grouped together using a new approach, Exploratory Graph Analysis [EGA; @golino2017exploratory], to assess convergent and discriminant validity, providing further evidence for unidimensionality.
@@
 <!-- Relationship with other interoception measures --> 
+<!-- The MAIA was introduced above -->
 
-The IAS has naturally been compared to other interoception-related scales, and shows a positive correlations with most facets of the MAIA **(TODO: MAIA should be introduced before)**, except for the Non-Distracting and Not-Worrying subscales [@brand2023].
+The IAS has naturally been compared to other interoception-related scales, and shows a positive correlations with most facets of the MAIA [@mehling2018multidimensional], except for the Non-Distracting and Not-Worrying subscales [@brand2023].
 Interestingly, findings on the correlation between the IAS and the body awareness dimension of the Body Perception Questionnaire [BPQ-A, @porges1993body] have been mixed: some studies report small positive correlations [@brand2023; @campos2021; @koike2023], while others find small negative correlations [@lin2023] or no correlation at all [@murphy2019].
@@
 Additionally, the IAS has shown a positive correlation with the interoceptive awareness subscale of the Eating Disorder Inventory [@lin2023] and a negative correlation with the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia; @brand2023; @murphy2019].
-Lastly, small positive correlations have also been reported with the Interoceptive Attention Scale [IATS, @gabriele2022dissociations], though studies have also found no correlation between these measures [@gabriele2022dissociations] **(TODO: why same reference for two contradictory claims?)**.
+Lastly, small positive correlations have also been reported with the Interoceptive Attention Scale [IATS, @lin2023; @koike2023], though studies have also found no correlation between these measures [@gabriele2022dissociations].
 
@@
 <!-- **anything else?**. TO BE COMPLETED -- to be determined -->
-
-<!-- Moreover, the current subjective measures do not correlate well with the objective measures [@murphy2019]. -->
-
-Few studies have examined the correlation between objective interoceptive measures, such as the Heartbeat Counting Task (HCT; Schandry, 1981) and the Heartbeat Detection Task (HDT; Kleckner et al., 2015).
-Existing findings report weak correlations for the HCT (Murphy et al., 2019), no correlations except for the sensitivity variable of the HCT (Brand et al., 2023), and small correlations for the HDT (Brand et al., 2023).
-These results suggest that the IAS, a subjective measure, does not strongly align with objective interoceptive assessments.
 
@@
 
-\begin{landscape}
-\input{../../analysis/figures/table1.tex}
-\end{landscape}
+<!-- \begin{landscape} -->
+<!-- \input{../../analysis/figures/table1.tex} -->
+<!-- \end{landscape} -->
 
@@
 
-\input{../../analysis/figures/table2.tex}
+<!-- \input{../../analysis/figures/table2.tex} -->
 
@@
 ### Results
+**todo:  compute average correlations **
 
@@
 
+[**TO DO**: add - previous work suggests the importance of physiological contexts (Vlemincx et al., 2021)]
+**I  would rather put that in the discussion in the suggestions for better scales**
+
 ## References

### 2025-01-27 paper/1_Initial/manuscript.tex
minor changes

@@
 
-\authorsnames{Ana Neves,Magdalena Pfaff,Dominique Makowski}
+\author{Ana Neves}
 
@@
 
-\leftheader{Neves, Pfaff and Makowski}
+\leftheader{Neves}
 
@@
 
-\authornote{\par{\addORCIDlink{Ana
-Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{Magdalena
-Pfaff}{0009-0006-2386-7936}}\par{\addORCIDlink{Dominique
-Makowski}{0000-0001-5375-9967}}
-
-\par{     \begin{tcolorbox}[enhanced jigsaw, colback=white, breakable, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, arc=.35mm, toprule=.15mm, rightrule=.15mm, opacityback=0, left=2mm, leftrule=.75mm]
+\authornote{\par{\addORCIDlink{Ana Neves}{0009-0006-0020-7599}}
+
+\par{     \begin{tcolorbox}[enhanced jigsaw, breakable, bottomrule=.15mm, rightrule=.15mm, toprule=.15mm, left=2mm, colback=white, arc=.35mm, colframe=quarto-callout-note-color-frame, leftrule=.75mm, opacityback=0]
+
+\end{tcolorbox}
 
@@
 \includegraphics[width=0.2\textwidth,height=\textheight]{manuscript_files/mediabag/ReBeL_LogoOnly_hu114.png}
-\end{center}
-
-\end{tcolorbox}  }
-\par{Correspondence concerning this article should be addressed
-to Dominique Makowski, Email: D.Makowski@sussex.ac.uk}
+\end{center}  Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows: Ana
+Neves:   Project administration, Data curation, Formal
+Analysis, Investigation, Visualization, Writing -- original
+draft, Writing -- review \& editing}
+\par{Correspondence concerning this article should be addressed to }
 }
@@
 
+\usepackage{lscape}
 \makeatletter
@@
 
-{[}\textbf{TO DO}: add - previous work suggests the importance of
-physiological contexts (Vlemincx et al., 2021){]}
-
 Various measures of interoception have been developed (see
@@
 
-For instance, while the use of self-reports questionnaires to measure an
-embodied function might seem paradoxical, recent redefinitions of
-interoception, emphasizing the role of high-level and metacognitive
-elaboration of interoceptive information, has provided the theoretical
-grounding to support the idea that some facets of interoception
-(including participants' metacognitive beliefs) can be assessed
-subjectively, providing useful and interesting measures
-(\citeproc{ref-lin2023}{Lin et al., 2023};
-\citeproc{ref-murphy2019}{Murphy et al., 2019}). The notion that
-self-reports might not reflect the same processes as other interoception
-measures is important to contextualize the apparent lack of convergence
-between measures in the field
-(\citeproc{ref-desmedt2022measures}{Desmedt et al., 2022}). Still, a
-better understanding of what is being measured with different
-questionnaires and dimensions, as well their potential overlaps with
-other constructs (e.g., alexithymia, body awareness) is needed to
+The use of subjective self-report questionnaires to measure deeply
+embodied functions might seem paradoxical. However, recent redefinitions
+of interoception emphasize the role of high-level and metacognitive
+elaboration of interoceptive information. These redefinitions provide
+theoretical grounding to support the idea that some facets of
+interoception, including participants' metacognitive beliefs, can be
+assessed subjectively. This approach offers useful and interesting
+measures (\citeproc{ref-lin2023}{Lin et al., 2023};
+\citeproc{ref-murphy2019}{Murphy et al., 2019}).
+
+The notion that self-reports might not reflect the same processes as
+other interoception measures is important to contextualize the apparent
+lack of convergence between measures in the field
+(\citeproc{ref-desmedt2022measures}{Desmedt et al., 2022}).
+
+A recent systematic review by Desmedt et al.
+(\citeproc{ref-desmedt2022measures}{2022}) examined whether various
+questionnaires designed to measure ``interoceptive sensibility'' truly
+assess the same construct. Notably, Garfinkel et al.
+(\citeproc{ref-garfinkel2015knowing}{2015}) defines interoceptive
+sensibility as the self-reported tendency to focus on and detect
+internal sensations, whereas
+(\citeproc{ref-khalsa2018interoception}{\textbf{khalsa2018interoception?}})
+defines it more narrowly, excluding the ability to detect these signals.
+According to Desmedt et al. (\citeproc{ref-desmedt2022measures}{2022}),
+most authors adopt the latter definition. The review found that these
+questionnaires measure related but distinct constructs, leading
+researchers to commit the `jingle fallacy'---mistakenly treating them as
+equivalent measures of interoceptive sensibility.
+
+\textbf{TODO: do a better job}
+
+Few studies have examined the correlation between objective
+interoceptive measures, such as the Heartbeat Counting Task (HCT;
+Schandry, 1981) and the Heartbeat Detection Task (HDT; Kleckner et al.,
+2015). Existing findings report weak correlations for the HCT (Murphy et
+al., 2019), no correlations except for the sensitivity variable of the
+HCT (Brand et al., 2023), and small correlations for the HDT (Brand et
+al., 2023). These results suggest that the IAS, a subjective measure,
+does not strongly align with objective interoceptive assessments.
+
+A better understanding of what is being measured with different
+questionnaires and dimensions, as well as their potential overlaps with
+other constructs (e.g., alexithymia, body awareness), is thus needed to
 clarify the role of self-reports in the assessment of interoception.
@@
 
-Although the original validation study suggested a two-factor solution
-structure, the authors underlines the need for further investigation of
-the scale's factor structure, as it provided acceptable but imperfect
-explanation of the data {[}Murphy et al.
-(\citeproc{ref-murphy2019}{2019}); p.~127{]}. Notably, the only other
-validation study to report a 2-factor solution was conducted by Koike
-and Nomura (\citeproc{ref-koike2023}{2023}), who performed an
-Exploratory Factor Analysis (EFA) assuming 2 factors to align with the
-findings from the original validation paper. Other follow-up studies
-using confirmatory factor analysis (CFA) and structural modeling
-(\citeproc{ref-morin2016}{Morin et al., 2015}) have identified different
-optimal solutions. Some studies, like Brand et al.
-(\citeproc{ref-brand2023}{2023}), reported a 1-factor solution, while
-Lin et al. (\citeproc{ref-lin2023}{2023}) and Campos et al.
-(\citeproc{ref-campos2021}{2021}) found bifactor solutions - one general
-factor and a set of loweroike -level factors (Rodriguez et al.
-(\citeproc{ref-rodriguez2016evaluating}{2016})) - to be the best fit.
+Although the original validation study suggested a two-factor structure
+for the IAS, the authors underline its acceptable but imperfect fit
+{[}Murphy et al. (\citeproc{ref-murphy2019}{2019}); p.~127{]}, calling
+on further investigation of the scale's factor structure. Notably, the
+authors did not define these factors, as no clear explanations were
+evident. They suggested that the first factor reflects the perception of
+interoceptive signals, while the second pertains to signals that may be
+difficult to perceive solely through interoceptive information.
+
+Other follow-up studies using confirmatory factor analysis (CFA) and
+structural modeling have identified different optimal solutions. Some
+studies, like Brand et al. (\citeproc{ref-brand2023}{2023}), reported a
+1-factor solution, while Lin et al. (\citeproc{ref-lin2023}{2023}) and
+Campos et al. (\citeproc{ref-campos2021}{2021}) found bifactor solutions
+- one general factor and a set of lower-level factors
+(\citeproc{ref-rodriguez2016evaluating}{Rodriguez et al., 2016}) - to be
+the best fit. Notably, the only other study to report a 2-factor
+solution was conducted by Koike and Nomura
+(\citeproc{ref-koike2023}{2023}), who performed an Exploratory Factor
+Analysis (EFA) assuming 2 factors to align with the findings from the
+original validation paper.
 
@@
 discrimination. Additionally, Campos et al.
-(\citeproc{ref-campos2021}{2021}) suggests that the ``tickle'' item
-represents a more specific factor. Interestingly, Lin et al.
-(\citeproc{ref-lin2023}{2023}) reported that all items of the IAS
-grouped together using a new approach, Exploratory Graph Analysis
-{[}EGA; Golino and Epskamp
+(\citeproc{ref-campos2021}{2021}) reported ``tickle'' to be the only
+item that reflected more specific factors than the general factor.
+Interestingly, Lin et al. (\citeproc{ref-lin2023}{2023}) reported that
+all items of the IAS grouped together using a new approach, Exploratory
+Graph Analysis {[}EGA; Golino and Epskamp
 (\citeproc{ref-golino2017exploratory}{2017}){]}, to assess convergent
-and discriminant validity, which suggests unidimensionality.
-
-While the assessment of the validity of an interoception scale can be
-conceived as theoretically challenging, several traits have been used to
-assess convergent validity for the the IAS, including expected negative
+and discriminant validity, providing further evidence for
+unidimensionality.
+
+The IAS has naturally been compared to other interoception-related
+scales, and shows a positive correlations with most facets of the MAIA
+(\citeproc{ref-mehling2018multidimensional}{Mehling et al., 2018}),
+except for the Non-Distracting and Not-Worrying subscales
+(\citeproc{ref-brand2023}{Brand et al., 2023}). Interestingly, findings
+on the correlation between the IAS and the body awareness dimension of
+the Body Perception Questionnaire (BPQ-A,
+\citeproc{ref-porges1993body}{Porges, 1993}) have been mixed: some
+studies report small positive correlations
+(\citeproc{ref-brand2023}{Brand et al., 2023};
+\citeproc{ref-campos2021}{Campos et al., 2021};
+\citeproc{ref-koike2023}{Koike \& Nomura, 2023}), while others find
+small negative correlations (\citeproc{ref-lin2023}{Lin et al., 2023})
+or no correlation at all (\citeproc{ref-murphy2019}{Murphy et al.,
+2019}). Small positive correlations have also been observed with the
+``observation'' and ``description'' subscales of the Five Facet
+Mindfulness Questionnaire (FFMQ, \citeproc{ref-baer2006using}{Baer et
+al., 2006}; \citeproc{ref-brand2023}{Brand et al., 2023};
+\citeproc{ref-koike2023}{Koike \& Nomura, 2023}), as well as with the
+``non-reactivity'' and ``acting with awareness'' subscales
+(\citeproc{ref-koike2023}{Koike \& Nomura, 2023}). Additionally, the IAS
+has shown a positive correlation with the interoceptive awareness
+subscale of the Eating Disorder Inventory (\citeproc{ref-lin2023}{Lin et
+al., 2023}) and a negative correlation with the Interoceptive Confusion
+Questionnaire (\citeproc{ref-brand2023}{Brand et al., 2023}; ICQ,
+\citeproc{ref-brewer2016alexithymia}{Brewer et al., 2016};
+\citeproc{ref-murphy2019}{Murphy et al., 2019}). Lastly, small positive
+correlations have also been reported with the Interoceptive Attention
+Scale (\citeproc{ref-koike2023}{Koike \& Nomura, 2023}; IATS,
+\citeproc{ref-lin2023}{Lin et al., 2023}), though studies have also
+found no correlation between these measures
+(\citeproc{ref-gabriele2022dissociations}{Gabriele et al., 2022}).
+
+While assessing the validity of an interoception scale can be conceived
+as theoretically challenging, several measures have been used to assess
+convergent validity for the the IAS, including expected negative
 associations with alexithymia Murphy et al.
@@
 (\citeproc{ref-murphy2019}{Murphy et al., 2019}).
-
-The IAS has also been compared to other interoception scales (and
-interoceptive related scales),generally showing positive correlations
-with most facets of the MAIA, except for the Non-Distracting and
-Not-Worrying subscales (\citeproc{ref-brand2023}{Brand et al., 2023}).
-Findings on the correlation between the IAS and the body awareness
-dimension of the Body Perception Questionnaire (BPQ-A; Porges
-(\citeproc{ref-porges1993body}{1993})) have been mixed: some studies
-report small positive correlations (\citeproc{ref-brand2023}{Brand et
-al., 2023}; \citeproc{ref-campos2021}{Campos et al., 2021};
-\citeproc{ref-koike2023}{Koike \& Nomura, 2023}), while others find
-small negative correlations (\citeproc{ref-lin2023}{Lin et al., 2023})
-or no correlation at all (\citeproc{ref-murphy2019}{Murphy et al.,
-2019}). Small positive correlations have also been observed with the
-observation and description subscales of the Five Facet Mindfulness
-Questionnaire (FFMQ, Baer et al. (\citeproc{ref-baer2006using}{2006});
-Brand et al. (\citeproc{ref-brand2023}{2023}); Koike and Nomura
-(\citeproc{ref-koike2023}{2023})), as well as with the nonreactivity and
-acting with awareness subscales (\citeproc{ref-koike2023}{Koike \&
-Nomura, 2023}). Additionally, the IAS has shown a positive correlation
-with the interoceptive awareness subscale of the Eating Disorder
-Inventory (\citeproc{ref-lin2023}{Lin et al., 2023}) and a negative
-correlation with the Interoceptive Confusion Questionnaire
-(\citeproc{ref-brand2023}{Brand et al., 2023}; ICQ,
-\citeproc{ref-brewer2016alexithymia}{Brewer et al., 2016};
-\citeproc{ref-murphy2019}{Murphy et al., 2019}). Lastly, small positive
-correlations have been reported between the Interoceptive Attention
-Scale (IATS, Gabriele et al.
-(\citeproc{ref-gabriele2022dissociations}{2022})) and the IAS
-(\citeproc{ref-koike2023}{Koike \& Nomura, 2023};
-\citeproc{ref-lin2023}{Lin et al., 2023}), though studies have also
-found no correlation between these measures
-(\citeproc{ref-gabriele2022dissociations}{Gabriele et al., 2022}).
-
-Few studies have examined the correlation between objective
-interoceptive measures, such as the Heartbeat Counting Task (HCT;
-Schandry, 1981) and the Heartbeat Detection Task (HDT; Kleckner et al.,
-2015). Existing findings report weak correlations for the HCT (Murphy et
-al., 2019), no correlations except for the sensitivity variable of the
-HCT (Brand et al., 2023), and small correlations for the HDT (Brand et
-al., 2023). These results suggest that the IAS, a subjective measure,
-does not strongly align with objective interoceptive assessments.
 
@@
 Mohr et al., 2023}). While combining these studies might provide a more
-robust and generalizable understanding of the IAS' factor structure, it
-is important to note that the studies differ in their sample sizes,
-demographics, language, and the way they collected the data. Thus,
-providing additionally an individual analysis (i.e., on all samples
-individually) will help adding nuance to the general picture.
+robust and generalizable understanding of the IAS' factor structure, we
+also additionally provide an individual analysis (i.e., on all samples
+separately) to add nuance to the general picture, as all studies differ
+in their sample sizes, demographics, language, and procedure.
 
@@
 (\emph{Mean} = 48.6 years, \emph{SD} = 13.1, 71.6\% Female).
-
-\input{../../analysis/figures/table1.tex}
 
@@
 
-\input{../../analysis/figures/table2.tex}
-
 \paragraph{Statistical analysis.}\label{statistical-analysis-1}
@@
 \subsubsection{Results}\label{results-1}
+
+\textbf{todo: compute average correlations }
 
@@
 
+{[}\textbf{TO DO}: add - previous work suggests the importance of
+physiological contexts (Vlemincx et al., 2021){]} \textbf{I would rather
+put that in the discussion in the suggestions for better scales}
+
 \subsection{References}\label{references}
@@
 subjective interoception. \emph{PLoS One}, \emph{16}(12), e0261126.
+
+\bibitem[\citeproctext]{ref-garfinkel2015knowing}
+Garfinkel, S. N., Seth, A. K., Barrett, A. B., Suzuki, K., \& Critchley,
+H. D. (2015). Knowing your own heart: Distinguishing interoceptive
+accuracy from interoceptive awareness. \emph{Biological Psychology},
+\emph{104}, 65--74.
 
@@
 
-\bibitem[\citeproctext]{ref-morin2016}
-Morin, A. J. S., Arens, A. K., \& Marsh, H. W. (2015). A bifactor
-exploratory structural equation modeling framework for the
-identification of distinct sources of construct-relevant psychometric
-multidimensionality. \emph{Structural Equation Modeling: A
-Multidisciplinary Journal}, \emph{23}(1), 116--139.
-\url{https://doi.org/10.1080/10705511.2014.961800}
-
 \bibitem[\citeproctext]{ref-murphy2019}

### 2025-01-28 paper/1_Initial/manuscript2.qmd
updated manuscript

--- 2025-01-27 paper/1_Initial/manuscript.qmd
@@
     #   - Writing – original draft
-  #   #   - Writing – review & editing
   # - name: Magdalena Pfaff
@@
   #   roles:
-  #     - Conceptualization
-  #     - Data curation
-  #     - Formal Analysis
-  #     - Funding acquisition
-  #     - Investigation
-  #     - Methodology
-  #     - Project administration
-  #     - Resources
-  #     - Software
-  #     - Supervision
-  #     - Validation
-  #     - Visualization
-  #     - Writing – original draft
   #   affiliations:
@@
 However, recent redefinitions of interoception emphasize the role of high-level and metacognitive elaboration of interoceptive information.
-These redefinitions provide theoretical grounding to support the idea that some facets of interoception, including participants' metacognitive beliefs, can be assessed subjectively.
+These redefinitions provide theoretical grounding to support the idea that some facets of interoception, including participants' metacognitive beliefs, can be assessed subjectively [@murphy2019; @khalsa2018interoception].
 This approach offers useful and interesting measures [@murphy2019; @lin2023].
@@
 
-<!-- lack of convergence between self-reported questionnaires -->
+<!-- A better understanding of what is being measured with different questionnaires and dimensions, as well as their potential overlaps with other constructs (e.g., alexithymia, body awareness), is thus needed to clarify the role of self-reports in the assessment of interoception.
+-->
 
-A recent systematic review by @desmedt2022measures examined whether various questionnaires designed to measure "interoceptive sensibility" truly assess the same construct.
-Notably, @garfinkel2015knowing defines interoceptive sensibility as the self-reported tendency to focus on and detect internal sensations, whereas @khalsa2018interoception defines it more narrowly, excluding the ability to detect these signals.
-According to @desmedt2022measures, most authors adopt the latter definition.
-The review found that these questionnaires measure related but distinct constructs, leading researchers to commit the 'jingle fallacy'—mistakenly treating them as equivalent measures of interoceptive sensibility.
-
-**TODO: do a better job**
-
-<!-- Moreover, the current subjective measures do not correlate well with the objective measures [@murphy2019]. -->
-
-Few studies have examined the correlation between objective interoceptive measures, such as the Heartbeat Counting Task (HCT; Schandry, 1981) and the Heartbeat Detection Task (HDT; Kleckner et al., 2015).
-Existing findings report weak correlations for the HCT (Murphy et al., 2019), no correlations except for the sensitivity variable of the HCT (Brand et al., 2023), and small correlations for the HDT (Brand et al., 2023).
-These results suggest that the IAS, a subjective measure, does not strongly align with objective interoceptive assessments.
-
-A better understanding of what is being measured with different questionnaires and dimensions, as well as their potential overlaps with other constructs (e.g., alexithymia, body awareness), is thus needed to clarify the role of self-reports in the assessment of interoception.
+<!-- WHATS THE ARGUMENT ?? -->
+<!--   1. lack of relationship between different explicit measures of Interoception?  -->
+<!--   2. lack of convergence bettween different self-report measures of interoception? -->
+<!--   3. lack of correlation between subjective vs objective accuracy? -->
 
 <!-- Introducing the IAS -->
-
-<!-- was the second reference asked for the MAIA, the MAIA-2 ? -->
 
@@
 
-<!-- [@morin2016] is a methodological paper on ESEM -->
+**note to dom**:@morin2016] is a methodological paper on ESEM
 
@@
 <!-- Relationship with other interoception measures --> 
-<!-- The MAIA was introduced above -->
+**note to dom**: the maia was introduced above
 

### 2025-01-28 paper/1_Initial/manuscript2.tex
updated manuscript

--- 2025-01-27 paper/1_Initial/manuscript.tex
@@
 
-\par{     \begin{tcolorbox}[enhanced jigsaw, breakable, bottomrule=.15mm, rightrule=.15mm, toprule=.15mm, left=2mm, colback=white, arc=.35mm, colframe=quarto-callout-note-color-frame, leftrule=.75mm, opacityback=0]
+\par{     \begin{tcolorbox}[enhanced jigsaw, leftrule=.75mm, rightrule=.15mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, left=2mm, toprule=.15mm, arc=.35mm, breakable, opacityback=0, colback=white]
 
@@
 \begin{center}
-\includegraphics[width=0.2\textwidth,height=\textheight]{manuscript_files/mediabag/ReBeL_LogoOnly_hu114.png}
+\includegraphics[width=0.2\textwidth,height=\textheight]{manuscript2_files/mediabag/ReBeL_LogoOnly_hu114.png}
 \end{center}  Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows: Ana
@@
 integrating information pertaining to internal organs, such as the
-heart, the lungs or the gut (\citeproc{ref-khalsa2018}{Khalsa et al.,
-2018}). While recent research emphasizes a key role of interoception in
-a variety of processes (e.g., emotion regulation, decision making) and
-of outcomes (physical and psychological well being), the field remains
-clouded by concerns about how interoception is assessed.
+heart, the lungs or the gut (\citeproc{ref-khalsa2018}{Khalsa, Adolphs,
+Cameron, Critchley, Davenport, Feinstein, Feusner, Garfinkel, Lane,
+Mehling, Meuret, et al., 2018}). While recent research emphasizes a key
+role of interoception in a variety of processes (e.g., emotion
+regulation, decision making) and of outcomes (physical and psychological
+well being), the field remains clouded by concerns about how
+interoception is assessed.
 
@@
 interoception, including participants' metacognitive beliefs, can be
-assessed subjectively. This approach offers useful and interesting
-measures (\citeproc{ref-lin2023}{Lin et al., 2023};
+assessed subjectively (\citeproc{ref-khalsa2018interoception}{Khalsa,
+Adolphs, Cameron, Critchley, Davenport, Feinstein, Feusner, Garfinkel,
+Lane, Mehling, \& others, 2018}; \citeproc{ref-murphy2019}{Murphy et
+al., 2019}). This approach offers useful and interesting measures
+(\citeproc{ref-lin2023}{Lin et al., 2023};
 \citeproc{ref-murphy2019}{Murphy et al., 2019}).
@@
 (\citeproc{ref-desmedt2022measures}{Desmedt et al., 2022}).
-
-A recent systematic review by Desmedt et al.
-(\citeproc{ref-desmedt2022measures}{2022}) examined whether various
-questionnaires designed to measure ``interoceptive sensibility'' truly
-assess the same construct. Notably, Garfinkel et al.
-(\citeproc{ref-garfinkel2015knowing}{2015}) defines interoceptive
-sensibility as the self-reported tendency to focus on and detect
-internal sensations, whereas
-(\citeproc{ref-khalsa2018interoception}{\textbf{khalsa2018interoception?}})
-defines it more narrowly, excluding the ability to detect these signals.
-According to Desmedt et al. (\citeproc{ref-desmedt2022measures}{2022}),
-most authors adopt the latter definition. The review found that these
-questionnaires measure related but distinct constructs, leading
-researchers to commit the `jingle fallacy'---mistakenly treating them as
-equivalent measures of interoceptive sensibility.
-
-\textbf{TODO: do a better job}
-
-Few studies have examined the correlation between objective
-interoceptive measures, such as the Heartbeat Counting Task (HCT;
-Schandry, 1981) and the Heartbeat Detection Task (HDT; Kleckner et al.,
-2015). Existing findings report weak correlations for the HCT (Murphy et
-al., 2019), no correlations except for the sensitivity variable of the
-HCT (Brand et al., 2023), and small correlations for the HDT (Brand et
-al., 2023). These results suggest that the IAS, a subjective measure,
-does not strongly align with objective interoceptive assessments.
-
-A better understanding of what is being measured with different
-questionnaires and dimensions, as well as their potential overlaps with
-other constructs (e.g., alexithymia, body awareness), is thus needed to
-clarify the role of self-reports in the assessment of interoception.
 
@@
 
+\textbf{note to dom}:Morin et al. (\citeproc{ref-morin2016}{2015}){]} is
+a methodological paper on ESEM
+
 Other follow-up studies using confirmatory factor analysis (CFA) and
@@
 unidimensionality.
+
+\textbf{note to dom}: the maia was introduced above
 
@@
 
-\bibitem[\citeproctext]{ref-garfinkel2015knowing}
-Garfinkel, S. N., Seth, A. K., Barrett, A. B., Suzuki, K., \& Critchley,
-H. D. (2015). Knowing your own heart: Distinguishing interoceptive
-accuracy from interoceptive awareness. \emph{Biological Psychology},
-\emph{104}, 65--74.
-
 \bibitem[\citeproctext]{ref-golino2017exploratory}
@@
 \url{https://doi.org/10.1016/j.jebo.2013.12.016}
+
+\bibitem[\citeproctext]{ref-khalsa2018interoception}
+Khalsa, S. S., Adolphs, R., Cameron, O. G., Critchley, H. D., Davenport,
+P. W., Feinstein, J. S., Feusner, J. D., Garfinkel, S. N., Lane, R. D.,
+Mehling, W. E., et al. (2018). Interoception and mental health: A
+roadmap. \emph{Biological Psychiatry: Cognitive Neuroscience and
+Neuroimaging}, \emph{3}(6), 501--513.
 
@@
 
+\bibitem[\citeproctext]{ref-morin2016}
+Morin, A. J. S., Arens, A. K., \& Marsh, H. W. (2015). A bifactor
+exploratory structural equation modeling framework for the
+identification of distinct sources of construct-relevant psychometric
+multidimensionality. \emph{Structural Equation Modeling: A
+Multidisciplinary Journal}, \emph{23}(1), 116--139.
+\url{https://doi.org/10.1080/10705511.2014.961800}
+
 \bibitem[\citeproctext]{ref-murphy2019}

### 2025-01-29 analysis/study2.qmd
started average correlations analysis

@@
 Even EGA components capture pairs or groupings of pairs of items.
+
+## Average Correlations
+
+```{r}
+
+# names(df1a)
+# names(df1b)
+# names(df2)  # BPQ, BVAQ, MAIA, ICQ (?), TAS
+# names(df3)  # TAS, BPQ
+# names(df4)  # BAQ (?), BPQ, MAIA, BRS (resilience?), PBCS (private bodily consciousness?)
+# names(df5)
+# names(df6)  # IATS, SSS, GAD, PHQ2
+# names(df7a)  # MAIA, STAI, FFMQ, NEOFFI, CES
+# names(df7b)  # MAIA, STAI, BPQ, PHQ15, PHQ9
+# names(df7c)  # TAS, BPQ, TAS, ASI, BDI, IASV
+# names(df8a)  # EDI, BPQ
+# names(df8b)  # TAS, PHQ15, PHQ9
+# names(df9)  # BFI, STQ, EQ, ECR,
+# names(df10a)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
+# names(df10b)  # BDI, STAI, PHQ4
+# names(df10c) # PI, MAIA
+# names(df11a) # MAIA, TAS, MFQ(DEP), STAI(ANX)
+# names(df11b)
+
+# Compute total IAS scores for each dataset 
+df1a$total_IAS <- rowSums(df1a[, c(3:23)])
+```
 

### 2025-01-31 paper/1_Initial/manuscript.qmd
changes to manuscript

@@
 
-Various measures of interoception have been developed (see **@fig-measures**), forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking vs.
+Various measures of interoception have been developed (see @fig-measures), forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking vs.
 questionnaires and subjective scales involving a metacognitive reflection), "explicit" and "implicit" paradigms (i.e., directing participants' awareness and attention to interoceptive processes *vs.* measuring interoception unbeknownst to them), various interoceptive modalities (e.g., cardioception, respiroception, gastroception) and theoretical dimensions (e.g., accuracy, sensitivity, awareness).
@@
 ```{r}
+#| warning: false 
 #| label: "fig-measures"
@@
 #| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
-#| out-width: "100%"
+## | out-width: "100%"
 
@@
 However, recent redefinitions of interoception emphasize the role of high-level and metacognitive elaboration of interoceptive information.
-These redefinitions provide theoretical grounding to support the idea that some facets of interoception, including participants' metacognitive beliefs, can be assessed subjectively.
+These redefinitions provide theoretical grounding to support the idea that some facets of interoception, including participants' metacognitive beliefs, can be assessed subjectively [@khalsa2018interoception; @suksasilp2022towards].
 This approach offers useful and interesting measures [@murphy2019; @lin2023].
 
+<!-- lack of correlation between objective and subjective measures + lack of correlation between self-report measures-->
+
 The notion that self-reports might not reflect the same processes as other interoception measures is important to contextualize the apparent lack of convergence between measures in the field [@desmedt2022measures].
+While few studies have explored the correlation between objective interoceptive measures,  such as the Heartbeat Counting Task [HCT, @schandry1981heart] and the Heartbeat Detection Task [HDT, @kleckner2015methodological], and correspondent self-report measures, existing findings typically show weak or no correlations [e.g., task-based accuracy vs.
+self-reported accuracy, @murphy2019; @brand2023].
 
-<!-- lack of convergence between self-reported questionnaires -->
-
-A recent systematic review by @desmedt2022measures examined whether various questionnaires designed to measure "interoceptive sensibility" truly assess the same construct.
+Even among self-report measures low correlations have been observed, suggesting that these measures, while group in the same umbrella term of self-report assess different facets of interoception. 
+A recent systematic review by @desmedt2022measures examined whether various questionnaires designed to assess "interoceptive sensibility" truly measure the same construct. 
 Notably, @garfinkel2015knowing defines interoceptive sensibility as the self-reported tendency to focus on and detect internal sensations, whereas @khalsa2018interoception defines it more narrowly, excluding the ability to detect these signals.
 According to @desmedt2022measures, most authors adopt the latter definition.
-The review found that these questionnaires measure related but distinct constructs, leading researchers to commit the 'jingle fallacy'—mistakenly treating them as equivalent measures of interoceptive sensibility.
-
-**TODO: do a better job**
-
-<!-- Moreover, the current subjective measures do not correlate well with the objective measures [@murphy2019]. -->
-
-Few studies have examined the correlation between objective interoceptive measures, such as the Heartbeat Counting Task (HCT; Schandry, 1981) and the Heartbeat Detection Task (HDT; Kleckner et al., 2015).
-Existing findings report weak correlations for the HCT (Murphy et al., 2019), no correlations except for the sensitivity variable of the HCT (Brand et al., 2023), and small correlations for the HDT (Brand et al., 2023).
-These results suggest that the IAS, a subjective measure, does not strongly align with objective interoceptive assessments.
-
+The review found that these questionnaires measure related but distinct constructs, leading researchers to mistakenly treating them as equivalent measures of interoceptive sensibility. 
 A better understanding of what is being measured with different questionnaires and dimensions, as well as their potential overlaps with other constructs (e.g., alexithymia, body awareness), is thus needed to clarify the role of self-reports in the assessment of interoception.
@@
 <!-- Introducing the IAS -->
-
-<!-- was the second reference asked for the MAIA, the MAIA-2 ? -->
 
@@
 
-Although the original validation study suggested a two-factor structure for the IAS, the authors underline its acceptable but imperfect fit [@murphy2019; p.
+Although the original validation study suggested a two-factor structure for the IAS, the authors underline its acceptable but imperfect fit [@murphy2019, p.
 127], calling on further investigation of the scale's factor structure.
@@
 
-<!-- [@morin2016] is a methodological paper on ESEM -->
+**note to dom**:@morin2016 is a methodological paper on ESEM
 
@@
 Additionally, @campos2021 reported "tickle" to be the only item that reflected more specific factors than the general factor.
-Interestingly, @lin2023 reported that all items of the IAS grouped together using a new approach, Exploratory Graph Analysis [EGA; @golino2017exploratory], to assess convergent and discriminant validity, providing further evidence for unidimensionality.
+Interestingly, @lin2023 reported that all items of the IAS grouped together using a new approach, Exploratory Graph Analysis [EGA, @golino2017exploratory], to assess convergent and discriminant validity, providing further evidence for unidimensionality.
 
 <!-- Relationship with other interoception measures -->
-<!-- The MAIA was introduced above -->
 
@@
 Lastly, small positive correlations have also been reported with the Interoceptive Attention Scale [IATS, @lin2023; @koike2023], though studies have also found no correlation between these measures [@gabriele2022dissociations].
+Interestingly, the IAS and the IATS supposedly measure two different interoceptive processes (i.e., accuracy and attention, respectively) which contradict @murphy2019 proposed 2x2 framework.
 
@@
 
-While assessing the validity of an interoception scale can be conceived as theoretically challenging, several measures have been used to assess convergent validity for the the IAS, including expected negative associations with alexithymia [@brand2023; @koike2023; @campos2021, @murphy2019; @lin2023], somatic symptoms [@brand2023; @koike2023, @lin2023], depressive symptoms [@brand2023; @koike2023; @lin2023], anxiety [@brand2023], neuroticism [@brand2023] and self-esteem [@murphy2019].
+While assessing the validity of an interoception scale can be conceived as theoretically challenging, several measures have been used to assess convergent validity for the the IAS, including expected negative associations with alexithymia [@brand2023; @koike2023; @campos2021; @murphy2019; @lin2023], somatic symptoms [@brand2023; @koike2023; @lin2023], depressive symptoms [@brand2023; @koike2023; @lin2023], anxiety [@brand2023], neuroticism [@brand2023] and self-esteem [@murphy2019].
 <!-- **anything else?**. TO BE COMPLETED -- to be determined -->
@@
 
-The current study aims at 1) clarifying the structure of the IAS with a meta-analytic approach that leverages existing data and contrast the traditional CFA/SEM factor-based analyses with network-based ones such as EGA.
-2) The second part will provide an overview of the dispositional correlates of the IAS, providing an overview of the pattern of associations that is key to better understand the nature, place and role of interoception questionnaires within a larger context.
+The current study aims at 1) clarifying the structure of the IAS with a meta-analytic approach that leverages existing data and contrast the traditional CFA/SEM factor-based analyses with network-based ones such as EGA;
+2) the second part will provide an overview of the dispositional correlates of the IAS, clarifying the pattern of associations which is key to better understand the nature, place and role of interoception questionnaires within a larger context.
 
@@
 A total of 10 studies was included (see **Table 1**).
-We also included the data of two unpublished (but already open-access) studies from the authors and one from another author.
+We also included the data of two unpublished (but already open-access) studies from the authors and one from another researcher.
 The total N participants was 32,214 participants (*Mean* = 48.6 years, *SD* = 13.1, 71.6% Female).
 
-<!-- \begin{landscape} -->
-<!-- \input{../../analysis/figures/table1.tex} -->
-<!-- \end{landscape} -->
+\begin{landscape}
+
+\input{../../analysis/figures/table1.tex}
+
+\end{landscape}
 
@@
 The selection of EGA was motivated by its capability to handle complex, multidimensional data and provide robust dimension estimates.
-A novel network psychometrics - Unique variable analysis [UVA; @christensen2023unique] - approach based on the weighted topological overlap will be computed to evaluate which items have substantial local dependence (> 0.25).
+A novel network psychometrics - Unique variable analysis [UVA, @christensen2023unique] - approach based on the weighted topological overlap will be computed to evaluate which items have substantial local dependence (\> 0.25).
 Subsequently, exploratory factor analysis (EFA) was employed followed by confirmatory factor analysis (CFA).
@@
 In other words, participants are most likely to answer 4/5 (i.e., agree) on most items (but "affective touch", "blood sugar", and "bruise" that exhibit a different distributional pattern).
-Additionally, one can note the low density on extreme values (1 and 5), meaning that the bulk of answers (i.e., 99\%) varies between 3 values.
+Additionally, one can note the low density on extreme values (1 and 5), meaning that the bulk of answers (i.e., 99%) varies between 3 values.
 The interindividual variability seems improved in the samples using an analogue scale, displaying a more continuous and progressive spread of answers.
@@
 
+<!-- check EFA results again -->
+
 When accounting for all samples, the factor analysis reveals that a 4-factor structure fits best.
-The exploratory factor analysis revealed that 4 latent factors (oblimin rotation) accounted for 51.95% of the total variance of the original data (MR2 = 19.08%, MR1 = 17.78%, MR4 = 9.34%, MR3 = 5.75%).
-Since UVA identified "tickle" as the item to be removed—and it also had the lowest uniqueness value in factor analysis with a similar loading to "itch"—"tickle" was excluded from subsequent analyses.
+The exploratory factor analysis revealed that 4 latent factors (oblimin rotation) accounted for  41.58% of the total variance of the original data (MR1 = 14.45%, MR3 = 11.76%, MR2 = 8.09%, MR4 = 7.28%).
+Since UVA identified "tickle" as the item to be removed—and it also had the lowest uniqueness value in factor analysis with a similar loading to "itch"—" it was excluded from subsequent analyses.
 
@@
 
-Confirmatory factor analysis compared 5 models: a single-factor solution, a 4-factor solution, a 5-factor solution, a 6-factor solution and a 7-factor solution.
+CFA was computed with the removal of the item "tickle" as it was constantly flagged as redundant.
+This analysis compared 5 models: a single-factor solution, a 4-factor solution, a 5-factor solution, a 6-factor solution and a 7-factor solution.
 The latter was preferred in most datasets, including with indices that penalise increased number of parameters (such as BIC).
@@
 
-These findings contrast with previous research, which all found that 2-factor model[@murphy2019; @koike2023], 1-factor model [@brand2023] and bifactor model [@lin2023; @campos2021] fits the data best.
-While this analysis also revealed an okay fit for the 1-factor model, the 4-factor model revealed the best fit.
+These findings contrast with previous research, which all found that 2-factor model [@murphy2019; @koike2023], 1-factor model [@brand2023] and bifactor model [@lin2023; @campos2021] fits the data best.
+While this analysis also revealed an okay fit for the 1-factor model, the 4-factor model was superior.
 The 4-factor structure reveals different ‘hubs' of items that are related, not only in this structure analysis, but also in underlying mechanisms.
@@
 
+**note to dom**: what stats do you mean here? the UVA one?
+
 There are several items that show redundancy suggesting that adapting the IAS would be beneficial for validity.
-Based on the given results, we suggest removing the tickle, while keeping the itch item [**todo**: stats?].
-Other items with slight redundancy were Hungry and Thirsty, Urinate and Defecate, and Sneeze and Cough.
+Based on the given results, we suggest removing the tickle, while keeping the itch item  \[**todo**: stats?\].
+Other items with slight redundancy were "hungry" and "thirsty", "urinate" and "defecate", and "sneeze" and "cough".
 
@@
 
-Interestingly, @lin2023 also found that tickle and itch were redundant, excluding one of them but the reason being that the character for both words is the same in the Chinese language.
+Interestingly, @lin2023 also found that "tickle" and "itch" were redundant, which led them to excludw one of them.
+Although, the reason being that the character for both words is the same in the Chinese language.
 On top of that, they came up with a shortened version of the IAS, excluding further items, resulting in a 12-item IAS, which aligns with our findings, suggesting that further items are ambiguous as to whether they should be removed.
-In contrast, other findings also found itch and tickle to be redundant but did not suggest excluding items [@campos2021].
+Their 12-item IAS included the "hunger", "breath", "urinate", "taste", "vomit", "cough", "temperature", "sexual arousa", "wind", "muscle", "pain", "itch" items.  
+In contrast, other findings also found "tickle" to be redundant but did not suggest excluding items [@campos2021].
 
@@
 The findings indicate a high proportion of answers at 4 (see Figure 1), especially when using a 5-step scale.
-The analogue scale shows a more dispersed distribution, with some answers indicating the highest 5/5, which was not the case in the 5-step scale.
+The analogue scale shows a more dispersed distribution, with some answers indicating the highest 5/5, which was not the case in Likert-scales. 
 Therefore, we recommend using an analog scale for the IAS.
 
-Before this paper, the IAS has not yet been used or analyzed with an analog scale, rather than a five step scale.
+Before this paper, the IAS had not yet been used or analyzed with an analog scale, rather than a five-step scale.
 Therefore, this study provides a novel approach to improving the IAS in a simple manner.
@@
 
-There are several limitations to the IAS; There are some redundant items, the 5-point scale does not provide great variability, and the structure could be improved.
+<!-- pooor arguments --> 
+There are several limitations to the IAS. There are some redundant items, the 5-point scale does not provide great variability, and the structure could be improved.
 Therefore, improving the IAS, or creating a new questionnaire investigating interoception could be useful to achieving reliable and accurate indication of interoceptive awareness.
@@
 Investigating correlates will help validate the IAS, as well as other interoceptive measures in the future.
-The
 
@@
 
+**note to dom** how do you want to present the questionnaires? in text format or in the table with their references on a footnote?
+
 The questionnaires used for the IAS correlates are listed in **Table 2** (**TODO: add the rest of the questionnaires, sample items and references**).
 
-<!-- \input{../../analysis/figures/table2.tex} -->
+\input{../../analysis/figures/table2.tex}
+
+##### Interoceptive Measures
 
@@
 
-Correlations will be computed using the correlation package under a Bayesian framework (ref).
+Correlations will be computed using the correlation package under a Bayesian framework [@ben2020effectsize].
 
 ### Results
-**todo:  compute average correlations **
 
-The EGA components capture groupings of pairs of items, such as "wind" and "burp", "cough" and "sneeze", or "muscle" and "pain".
+**todo: compute average correlations**
+
+The EGA components capture groupings of pairs of items, such as "wind" and "burp", "cough" and "sneeze", and "muscle" and "pain".
 These groupings were used in the correlational analysis, to observe how much each group/pair correlates with other factors, such as Alexithymia, or the MAIA (see Figure 2).
@@
 Autistic traits are mostly negatively correlated with IAS measure, except for patterns and numbers (as an autistic trait), which is significantly and positively correlated with the "itch/bruise" pairing.
+
 The BPQ Body Awareness part is positively correlated with all IAS pairs, whereas the Autonomic Reactivity part is negatively correlated with all IAS groupings.
 Conspiracy Beliefs were all positively correlated with the IAS pairs, however, only Global Conspiracy with "hungry/thirsty", "urinate/defecate" and "cough/sneeze", as well as personal wellbeing with "hungry/thirsty", and Information Control with "cough/sneeze" were significantly positively correlated.
+
 Demographic data is also mostly positively correlated with the IAS findings, where gender and age more strongly correlated with "hungry/thirsty".
-In this analysis, lying profile is not strongly correlated with the IAS; Except for contextuality, which shows a significant negative correlation with "itch/bruise".
-The MAIA has a strong positive correlation with most IAS pairings, except for the "not worrying" and "not distracting" items of the MAIA, which show less strong, or even negative correlations with all IAS item pairings.
+
+In this analysis, lying profile is not strongly correlated with the IAS, except for contextuality which shows a significant negative correlation with "itch/bruise".
+The MAIA has a strong positive correlation with most IAS pairings, except for the Not Worrying and Not Distracting items of the MAIA, which show less strong, or even negative correlations with all IAS item pairings.
+
 Maladaptiveness had mostly negative correlations with the IAS, with only a few significant correlations, namely "psychoticism", "negative affect", and "detachment" with "muscle/pain" and "hungry/thirsty", as well as "negative affect" with "wind/burp".
+
 Overall, mood was mostly negatively correlated with the IAS, where "hungry/thirsty" had the strongest negative correlation of all mood measures.
@@
 Shizotypic traits were mostly negatively correlated with the IAS, with "hungry/thirsty" showing the strongest negative correlation between schizotypic and the IAS.
+
 World beliefs were mostly positively correlated with the IAS, however, only a few were significant: "hierarchical", "enticing", and "alive" correlates significantly with "muscle/pain"; "Understandable" has a significant positive correlation with "heart/breathing"; And "hierarchical" and "alive" has a significant positive correlation with "hungry/thirsty".
@@
 
-Our findings confirmed that interception lies within an intricate network of correlates.
-Alexithyma has the most negative correlation with the IAS, whereas, the MAIA questionnaire is most strongly positively correlated with the IAS.
-The correlates cannot only explain attributes of interoception, but can also be used to validate measures for interoception.
+<!-- strongest and weakest correlations with the IAS--> 
+Our findings confirm that interoception exists within a complex network of correlates. 
+Among these, alexithymia exhibits the strongest negative correlation with the IAS, whereas the MAIA questionnaire shows the strongest positive correlation. 
+These correlates not only help explain different aspects of interoception but also serve as valuable tools for validating interoceptive measures.
 
-While these results reveal correlations of different categories with the IAS, the findings are limited to the given questionnaire.
-However, they give a good indication of how interoception in general might be linked to the different categories, leading to interesting findings.
-The results show a consistent pattern of correlations with other interoception measures, psychopathology, and highlighting of interesting exploratory results, such as how primal world beliefs correlate with the IAS.
+<!-- consistent pattern of results and interesting exprolatory analysis --> 
+While our results reveal various correlations with the IAS, they are limited to the scope of the given questionnaire.
+Nonetheless, they provide valuable insights into how interoception may relate to different psychological and personality traits. 
+The results show a consistent pattern of correlations with other measures and highlight interesting exploratory results, such as correlations between primal world beliefs with the IAS.
 
-The analysis revealed a negative correlation between alexithymia and scores in the IAS, which is in line with previous research [@herbert2011].
-A negative correlation between autism and interoceptive awareness, which has been found in this sample, has also been found in previous research [@dubois2016].
-Conspiracy Beliefs and IAS scores were not strongly correlated.
-However, there was a slight positive correlation.
-To the best of our knowledge, this interaction has not been investigated before.
-However, research shows correlations between (political) beliefs and interoception, which could underlie the same mechanism [@ruisch2022].
-Lying profile was also not strongly correlated with the IAS.
-Previous research provides some evidence for a relationshipbetween interoception and lying profile [@makowski2023a], indicating a contrast from the literature to the results at hand.
-The analysis showed that mood and the IAS scores have a strong negative correlation, which has been investigated in previous studies, finding a correlation between the two variables as well [@solanolópez2018].
-The analysis showed that personality is also correlated with interoceptive accuracy scores as retrieved by the IAS.
-While there are many aspects of personality, put simply, personality and interoception have been found to correlate in previous studies as well [@erle2021].
-Our findings show some negative correlations between schizotypy and interoception.
-Previous research has investigated this relationship and, similarly, found a negative correlation between interoceptive awareness and schizotypy, particularly at the onset of psychosis [@torregrossa2022].
-Lastly, World Beliefs and Interoception showed some significant positive correlations.
-World Beliefs have not been linked with interoception previously.
-As mentioned, other beliefs, such as political beliefs have been mentioned to interoception, where significant correlations were observed [@ruisch2022a].
-Further research is needed to understand this mechanism and validate whether world beliefs, which lay the framework through which we see the world [@clifton2020], is needed.
+<!-- negative correlation with alexithymia and autism --> 
+Our analysis found a strong negative correlation between alexithymia and IAS scores, aligning with previous research [@herbert2011; @brand2023; @murphy2019]. 
+Similarly, a negative correlation between autism and interoceptive awareness was observed in our sample, consistent with prior findings [@dubois2016].
 
-The above findings show how interoception is correlated with many lifestyle and health factors, and is therefore an important concept to study.
-Here we showed many correlates of the IAS and lifestyle, as well as health factors.
-This is not only valuable to understand interception, and the role it plays in our lives, better, but also crucial to further validate the Ias, as well as other interoception measures.
-This analysis therefore lays the groundwork for validating new interoceptive measures and questionnaires needed to grasp interoception and its role in our life.
+<!-- weak correlation with conspiracy beliefs --> 
+Conspiracy beliefs did not strongly correlate with IAS scores, though a slight positive correlation was present. 
+To our knowledge, this relationship has not been previously explored. 
+However, prior studies have suggested connections between interoception and (political) beliefs, potentially pointing to shared underlying mechanisms [@ruisch2022].
+
+<!-- weak correlation with lying profiles --> 
+The relationship between interoception and lying profiles was also weak. 
+This contrasts with previous research suggesting associations between interoception and deception [@makowski2023a], warranting further investigation.
+
+<!-- stroong negative correlations with Mood --> 
+Mood and IAS scores exhibited a strong negative correlation, consistent with prior studies that have documented similar findings [@solanolópez2018]. 
+Additionally, personality traits correlated with interoceptive accuracy scores, reinforcing existing research linking personality and interoception [@erle2021].
+
+<!-- negative correlations with schizotypy --> 
+We also observed negative correlations between schizotypy and interoception, in line with previous studies that identified a similar relationship with interoceptive awareness, particularly in individuals at risk for psychosis [@torregrossa2022].
+
+<!-- positive correlations with some Primal World Beliefs --> 
+Interestingly, world beliefs demonstrated significant positive correlations with interoception. 
+While this relationship has not been previously documented, other forms of belief, such as political ideology, have been linked to interoception [@ruisch2022a]. 
+Further research is needed to determine whether world beliefs, which shape our perception of reality [@clifton2020], are meaningfully connected to interoception.
+
+<!--Summary -->
+
+Overall, our findings highlight the broad relevance of interoception across various cognitive and affective traits, underscoring its significance in both research and clinical contexts. 
+By identifying numerous correlates of the IAS, we contribute not only to a deeper understanding of interoception’s role in daily life but also to the ongoing validation of the IAS and other interoceptive measures.
+This analysis lays an important foundation for the development of new interoceptive assessment tools, further advancing our comprehension of interoception and its impact on human experience.
 
@@
 
-The analyses revealed that the IAS has 4-factor structure, and a rather uneven distribution.
-The findings indicate that the IAS is measuring interoception in an acceptable manner, but there is also room for improvement.
-Furthermore, the results reveal different correlation measures with the IAS, giving space to further explore whether and how measures correlate with interoception/the IAS.
-In the following section, the IAS is discussed further to reveal shortcomings and strengths of the questionnaire.
-Finally, future steps will be revealed to improve the way in which we measure interoception.
+<!-- factor structure -->
 
-Overall, the IAS is straightforward with its sensation-centered items.
-There are several points of improvement to the IAS, which this work suggests.
-Firstly, removing redundant items, such as the itch item as shown in the above analysis.
-Previous work has also shown that the itch and tickle items are subject to redundancy [@lin2023, @campos2021] has shown.
-Interestingly, @campos2021 suggest removing the tickle item instead.
-@lin2023 on the other hand removed the itch item, because the sign for itch and tickle is the same.
-Furthermore, this work recommends using analog scales, instead of 5 point scales.
-In a 5-point scale, the variability is clearly limited with most people choosing ⅘.
-As visible in Figure X, the variability increases significantly, using an analog scale.
-However, it is important to note that even with an analog scale, the variability of the IAS is still limited.
-The more variability a scale shows, the more results can depict individual differences between participants.
-Therefore, good dispersion is essential for achieving relevant and usable results, and striving for more variability would be beneficial to this interoception scale, too.
+Our analyses revealed that the IAS follows a four-factor structure with an uneven distribution. 
+While the findings indicate that the IAS measures interoception adequately, there is room for improvement. 
+Additionally, different correlation measures with the IAS suggest opportunities for further exploration of how interoception is assessed.
+In the following section, we discuss the strengths and shortcomings of the IAS, followed by proposed steps to enhance interoception measurement.
 
-In this work, it becomes apparent that even with the mentioned improvements to the scale, there are limitations to the IAS, which reduce the accuracy of this scale.
-Those limitations include that there are few items for some modalities, such as only one item for heart perception.
-Having more modality is useful as each grouping can have more variability with increased modality, leading to more nuanced results.
-On top of that, there is no clear and theoretical, or empirical structure, as there is a very small grouping of items.
-Ideally, a scale would allow for an analysis showing different groupings so that different categories can be created based on which the data can be analyzed.
-The groupings in this analysis reveal that the IAS can only be grouped with two items per group, leading to low scores and variability in each group.
-On top of that, there are ambiguous items in the IAS, of which the grouping depends on the context.
-For example, one might indicate that they can perceive well how their heart is beating fast as well as vomiting, but both items can be linked to feeling anxious, and therefore might indicate different results than initially expected.
-Therefore, the grouping and structure of the IAS can be improved.
+<!-- redundancy of tickle and other items -->
 
-Furthermore, all items are phrased positively, which might influence how participants answer the questions.
-While phrasing items in a positive manner can be beneficial, the benefits of positive phrasing might exacerbate a positive bias and thus lead to unidimensional results.
-Therefore, phrasing questions in a more diverse manner might lead to more accurate results and might thus be beneficial.
+Overall, the IAS is straightforward in its sensation-centered items.
+However, several areas for improvement emerge from this study. Firstly, redundant items should be removed, such as the "itch" item, as highlighted in our analysis. 
+Previous research also suggests redundancy between itch and tickle items [@lin2023, @campos2021]. 
+Interestingly, while @campos2021 does not recommend the removal of either, @lin2023 argues for removing the itch item due to their overlapping character representation.
 
-Based on the given arguments, it becomes clear that there is a need for context-specific items, which are cross-modal when possible, such as integrating cardioception and respiroception.
-After establishing the clear need for a new scale to measure interoception, this study proposes the need for a new scale (Multimodal Interoceptive Sensitivity Scale, MISS) to adapt to the newest findings on the IAS and what we know about interoception to this day.
-The new scale will be able to be compared to the correlates of the IAS.
+<!-- benefit of analog scales -->
+
+Furthermore, this study recommends using analog scales instead of 5-point scales. 
+The limited variability of the 5-point scale often results in most responses clustering around 3 or 4. 
+As shown in @fig-distributions, adopting an analog scale significantly increases variability. However, even with an analog scale, IAS variability remains constrained. 
+Greater variability allows for better differentiation among participants, making dispersion an essential factor for obtaining meaningful results. 
+Enhancing variability would therefore be beneficial for the IAS.
+
+<!-- Underrepresentation of modalities -->
+
+Despite these improvements, certain limitations persist in the IAS that affect its accuracy. 
+Notably, some modalities are underrepresented—for instance, heart perception is measured by only one item. 
+Expanding modality coverage would enhance variability within each category, leading to more nuanced results. 
+Moreover, the IAS lacks a clear theoretical or empirical structure, with only small item groupings. 
+Ideally, a scale should allow for clear groupings that support meaningful data analysis. 
+In this study, each group contained only two items, resulting in low scores and limited variability. 
+Additionally, some IAS items are ambiguous, with their interpretation depending on context. 
+For example, an item about perceiving heartbeats and another about vomiting could both relate to anxiety, leading to results that may differ from initial expectations. 
+Thus, the grouping and structure of the IAS require refinement.
+
+<!-- positve response bias from only positive worded items -->
+
+Another concern is that all IAS items are phrased positively, which may influence participant responses. 
+While positive phrasing has advantages, it can also introduce response bias, leading to unidimensional results.
+A more balanced phrasing approach, incorporating both positively and negatively framed items, could yield more accurate responses.
+
+<!-- suggestion for more context-specific -->
+
+Given these considerations, it is clear that context-specific, cross-modal items—such as integrating cardioception and respiroception—are needed. 
+Recognizing the necessity for a refined interoception scale, this study proposes the development of the Multidimensional Interoceptive Inventory (MInt). 
+This new scale will be designed to align with recent findings on the IAS and interoception research while allowing for direct comparison with IAS correlates.
+
+\[**TO DO**: add - previous work suggests the importance of physiological contexts (Vlemincx et al., 2021)\] **I would rather put that in the discussion in the suggestions for better scales**
 
@@
 
-The IAS is a good way of measuring interoception considering the current existing questionnaires and tools.
-However, revising, or even re-inventing a survey to measure interoception would lead to the best measure of interoception.
-Therefore, this study proposes that a new scale to measure interoception is needed to evolve the current research on interoception.
-This study revealed many correlates of the IAS, giving space for future analysis on what might be a good interoceptive measure, and therefore laying the groundwork for the creation of a new interoception survey.
-
-[**TO DO**: add - previous work suggests the importance of physiological contexts (Vlemincx et al., 2021)]
-**I  would rather put that in the discussion in the suggestions for better scales**
+The IAS is a valuable tool for measuring interoception compared to existing questionnaires and methods. 
+However, refining or even redesigning the questionnaire could lead to a more precise and comprehensive assessment. 
+This study highlights the need for a new interoception scale to advance research in the field.
+By identifying various correlates of the IAS, this work paves the way for future investigations into optimal interoceptive measures, ultimately laying the foundation for the development of a more effective interoception survey.
 

### 2025-02-03 analysis/study2.qmd
used scales
till df10a (need to check the ones after)

--- 2025-01-15 analysis/study2.qmd
@@
 
+## Average Correlations
+
+- BPQ - sf - Body perception questionnaire short form
+- BPQ - vsf - Body perception questionnaire very short form 
+- BVAQ - Bermond–Vorst Alexithymia Questionnaire 
+- MAIA-2 - Multidimensional Assessment of Interoceptive Awareness , Version-2
+- ICQ  - Interocpetive Confusion Questionnaire
+- TAS - Toronto Alexithymia Scale 
+- BAQ - Body awareness questionnaire
+- BRS - the body responsiveness scale 
+- PHQ-2 - Patient Health Questionnaire 2 items on major depressive episodes 
+- PHQ-4 - atient Health Questionnaire 4 items assessing anxiety and depression 
+- PHQ-9 - Patient Health Questionnaire 9-Item Version assesses depressive symptoms
+- PHQ-15 - Patient Health Questionnaire 15-Item Version assesses Somatic symptom distress 
+- SSS-8 - Somatic Symptom Scale 
+- IATS - Interoceptive Attention Scale
+- GAD-2 - Generalized Anxiety Disorder Scale 2 items on anxiety disorder 
+- STAIT - State-Trait-Anxiety Inventory Trait subscale
+- FFMQ - Observation and Description subscales of the Five Facet Mindfulness Questionnaire
+- NEOFFI - Neuroticism Neo Five-Factor Inventory Neuroticism subscale
+- ASI - Anxiety Sensitivity Inventory 3
+- BDI - The Beck Depression Inventory
+- EDI_IA - Eating Disorder Inventory, interoceptive awareness subscale
+- BFI -  Big Five inventory-10
+- ASQ -  Autism-Spectrum Quotient
+- MSI-BPD - Mclean Screening Instrument for Borderline Personality Disorder
+- GCB - Generic Conspiracist Beliefs scale
+- IPIP6 - Mini International Personality Item Pool
+- PI - Primal Inventory 18 items and 99 items 
+- PID5-sf - Personality Inventory for DSM-5 Short Form 
+- SPQ-BRU - Schizotypal Personality Questionnaire, brief revised updated
+- LIE - Lying Profile Questionnaire
+
 ## Summary

### 2025-02-04 analysis/study2.qmd
Update study2.qmd

@@
 # names(df1b)
-# names(df2)  # BPQ, BVAQ, MAIA, ICQ (?), TAS
+# names(df2)  #TAS, MAIA, ICQ, BPQ, BVAQ
 # names(df3)  # TAS, BPQ
-# names(df4)  # BAQ (?), BPQ, MAIA, BRS (resilience?), PBCS (private bodily consciousness?)
+# names(df4)  # BPQ, PBCS (private bodily consciousness?), MAIA, BAQ, BRS
 # names(df5)  
-# names(df6)  # IATS, SSS, GAD, PHQ2
-# names(df7a)  # MAIA, STAI, FFMQ, NEOFFI, CES
-# names(df7b)  # MAIA, STAI, BPQ, PHQ15, PHQ9
-# names(df7c)  # TAS, BPQ, TAS, ASI, BDI, IASV
+# names(df6)  # PHQ2, GAD2, SSS8, IATS
+# names(df7a)  # STAIT, MAIA, CES (not reported in the paper), FFMQ, NEOFFI
+# names(df7b)  # BPQ, PHQ15, PHQ9, MAIA, STAIT, 
+# names(df7c)  # CI01 (not reported in the paper), TAS, BPQ, MAIA, ASI, ICQ 
 # names(df8a)  # EDI, BPQ
-# names(df8b)  # TAS, PHQ15, PHQ9
-# names(df9)  # BFI, STQ, EQ, ECR, 
-# names(df10a)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
-# names(df10b)  # BDI, STAI, PHQ4
-# names(df10c) # PI, MAIA
+# names(df8b)  # PHQ9, PHQ15, TAS
+# names(df9)  # ECR (Experience in Close Relationship Scale), TEAQ (touch experiences and attitudes questionnaire), STQ, TACSEN, UCLA, BFI, DBIA, BO, EQ
+# names(df10a)  # ASQ, BPD, GCBS, IPIP6, LIE, MAIA, PHQ4, PI, PID, SPQ
+# names(df10b)  # PHQ4, STAIT5, BDI, MAIA
+# names(df10c) # MAIA, PI, 
 # names(df11a) # MAIA, TAS, MFQ(DEP), STAI(ANX)
@@
 names(df2)[str_detect(names(df2), "MAIA")]  
-names(df4)[str_detect(names(df4), "MAIA")]  # ?
+names(df4)[str_detect(names(df4), "MAIA")]  # individual items
 names(df7a)[str_detect(names(df7a), "MAIA")]  
 names(df7b)[str_detect(names(df7b), "maia")] 
-names(df10a)[str_detect(names(df10b), "MAIA")]
+names(df7c)[str_detect(names(df7c), "MAIA")]
+names(df10a)[str_detect(names(df10a), "MAIA")]
+names(df10b)[str_detect(names(df10b), "MAIA2")] # all columns with NA values 
 names(df10c)[str_detect(names(df10c), "MAIA")]
@@
     mutate(var_Correlate = "Self Regulation"),
+
   # df4
+
   # df7a
@@
 
+  # df7c
+   make_cor(df7c, vars_intero, with = "MAIA_noticing", component="MAIA") |>
+    mutate(var_Correlate = "Noticing"),
+  make_cor(df7c, vars_intero, with = "MAIA_notdis", component="MAIA") |>
+    mutate(var_Correlate = "Not Distracting"),
+  make_cor(df7c, vars_intero, with = "MAIA_notwor", component="MAIA") |>
+    mutate(var_Correlate = "Not Worrying"),
+  make_cor(df7c, vars_intero, with = "MAIA_attreg", component="MAIA") |>
+    mutate(var_Correlate = "Attention Regulation"),
+  make_cor(df7c, vars_intero, with = "MAIA_emoaw", component="MAIA") |>
+    mutate(var_Correlate = "Emotional Awareness"),
+  make_cor(df7c, vars_intero, with = "MAIA_selfreg", component="MAIA") |>
+    mutate(var_Correlate = "Self Regulation"),
+  make_cor(df7c, vars_intero, with = "MAIA_bodlis", component="MAIA") |>
+    mutate(var_Correlate = "Listening"),
+  make_cor(df7c, vars_intero, with = "MAIA_trust", component="MAIA") |>
+    mutate(var_Correlate = "Trusting"),
+
   # df10a
@@
     mutate(var_Correlate = "Trusting"),
+
+  #df10b
 
@@
 ```{r}
+#  only one study assess alexithymia with BVAQ (df2)
 names(df2)[str_detect(names(df2), "TAS")]
@@
   data,
+
+  #df2 
   make_cor(df2, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
@@
     mutate(var_Correlate = "External Thinking (TAS)"),
+
+  #df3 
   make_cor(df3, vars_intero, with = "TAS_DescribingFeelings", component="Alexithymia") |>

### 2025-02-07 analysis/study2.qmd
updated manuscript

@@
 
+```{r}
+# names(df1a)
+# names(df1b)
+# names(df2)  #TAS, MAIA, ICQ, BPQ, BVAQ
+# names(df3)  # TAS, BPQ
+# names(df4)  # BPQ, PBCS (private bodily consciousness?), MAIA, BAQ, BRS
+# names(df5)  
+# names(df6)  # PHQ2, GAD2, SSS8, IATS
+# names(df7a)  # STAIT, MAIA, CES (not reported in the paper), FFMQ, NEOFFI
+# names(df7b)  # BPQ, PHQ15, PHQ9, MAIA, STAIT, 
+# names(df7c)  # CI01 (not reported in the paper), TAS, BPQ, MAIA, ASI, ICQ 
+# names(df8a)  # EDI, BPQ
+# names(df8b)  # PHQ9, PHQ15, TAS
+# names(df9)  # ECR (Experience in Close Relationship Scale), TEAQ (touch experiences and attitudes questionnaire), STQ, TACSEN, UCLA, BFI, DBIA, BO, EQ
+# names(df10a)  # ASQ, BPD, GCBS, IPIP6, LIE, MAIA, PHQ4, PI, PID, SPQ
+# names(df10b)  # PHQ4, STAIT5, BDI, MAIA
+# names(df10c) # MAIA, PI, 
+# names(df11a) # MAIA, TAS, MFQ(DEP), STAI(ANX)
+# names(df11b)
+
+average_corr <- data |>
+    summarise(mean_r = mean(r, na.rm = TRUE), .by=c("Component", "var_Correlate", "var_Interoception"))
+
+# Alexithymia
+average_corr |>
+  filter(Component == "Alexithymia") |>
+  group_by(var_Correlate) |>
+  summarise(min = min(mean_r),
+             max = max(mean_r))
+#BPQ
+average_corr |>
+  filter(Component == "BPQ") |>
+  group_by(var_Correlate) |>
+  summarise(min = min(mean_r),
+             max = max(mean_r))
+
+```
+
 ## Summary

### 2025-02-07 paper/1_Initial/manuscript.qmd
updated manuscript

@@
 
-**note to dom** how do you want to present the questionnaires? in text format or in the table with their references on a footnote?
-
 The questionnaires used for the IAS correlates are listed in **Table 2** (**TODO: add the rest of the questionnaires, sample items and references**).
@@
 
-**todo: compute average correlations**
+## Average correlations
+
+**compute internal consistency**
+
+### Correlations with body measures
+<!-- Alexithymia -->
+Alexithymia was assessed in the samples with the Bermond–Vorst Alexithymia Questionnaire [BVAQ; @vorst2001validity] and the Toronto Alexithymia Scale[TAS; @bagby1994twenty].
+
+<!-- BVAQ -->
+The BVAQ consists of 5 subscales - fantasising, idenitying, analysing; verbalising and emotionalising - assessed with 40 items on a 5-point Likert scale, from 'defnitely applies to me' to 'in no way applies to me'.
+Additionally, the BVAQ reduces these subscales into two high order factors, an affective component and a cognitive one, with high scores being indicative of high proneness to alexithymia.
+
+On average, the cognitive component of the BVAQ was weakly and negatively correlated with all IAS pairs of items with the biggest correlation being with the Itch/Bruise pair (r = -0.112) and the lowest correlation beeing with the Muscle/Pain pair (r = -0.244).
+The affective component of the BVAQ was positively, but very weak, correlated with all pairs, with the biggest correlation being with the Itch/Bruise pair (r = 0.107). 
+The only exception was a negative correlation with the Urinate/Defecate pair (r = -0.036).
+
+<!-- TAS -->
+The TAS contains 20-items rated on a 5-point forced scale, from 'strongly disagree' to 'strongly afree', divided into 3 dimensions - difficulty identiying feelings, difficulty describing feelings, and externally thinking.
+High scores on this scale also reflect higher alexithymia.
+
+All the three dimensions assessed with the TAS were on average negatively correlated with all pairs of IAS items.
+The difficulty describing feelings had its strongest correlation with Hungry/Thirsty (r = -0.179) and weakest with the Wind/Burp (r = -0.117).
+while, the difficulty describing feelings had its strongest correlation with Muscle/Pain (r = -0.247) and weakest with Itch/Bruise (r = -0.157).
+Lastly, the external thinking dimension was more correlated with the Cough/Sneeze pair (r = -0.138) and less correlated with the Hungry/Thirsty (r = -0.018).
+
+<!-- BPQ -->
+The studies within our sample used the Body Perception Questionnaire short-form (BPQ-SF) and the very-short form (BPQ-VSF) to assess interoception [@cabrera2018assessing]. 
+The BPQ-SF comprised of 46 items on a 5-point Likert scale assessing body awareness (26 items) and autonomic reactivity (21 items). 
+The BPQ-VSF comprises of 12 items from the body awareness subscale of the BPQ-SF.
+In this study, all scores assessing these two dimensions were grouped together, hence no disitintion is made between awareness measured with the BPQ-SF and the BPQ-VSF.
+
+**note to add:** discuss later
+
+In general, all pairs of the IAS were positively,and weakily, associated with the body awareness subscales, while negative and weakily correlated with the autonomic reactivity subscale. 
+The strongest correlation identified between the IAS pairs and the body awereness subscale was with the 	
+Heart/Breathing pair (r = 0.151) whilst the strongest correlation with the autonomic reactivity was with the Urinate/Defecate pair (r = -0.235). 
+The weakest correlation between the body awareness and the IAS was with the Hungry/Thirsty pair (r =  0.055) and between the autonomic reactivity and the IAS was with the Heart/Breathing pair (r = -0.106).
+
+<!-- MAIA -->
+
+<!-- MAIA -->
+
+## Correlations
 

### 2025-02-10 analysis/figures/table2.tex
updated manuscript and analysis script

\begin{table}
\fontsize{6.8pt}{8.1pt}\selectfont
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}lrlrr}
\toprule
Questionnaire & Number of Dimensions & Assessment & Number of Items & Scoring \\ 
\midrule\addlinespace[2.5pt]
{\bfseries Interoceptive Related} &  &  &  &  \\ 
MAIA-2 & 8 & Interoception & 37 & 6-point Likert scale \\ 
BPQ & 2 & Body awareness and autonomic reactivity & 49 & 5-point Likert scale \\ 
TAS-20 & 3 & Alexithymia & 20 & 5-point Likert scale \\ 
BVAQ & 2 & Alexithymia & 40 & 5-point Likert scale \\ 
{\bfseries Mood} &  &  &  &  \\ 
BDI-II & 1 & Severity of depressive symptoms & 21 & 0-to-3-point values \\ 
PHQ-4 & 2 & Anxiety and depressive symptoms & 4 & 5-point Likert scale \\ 
STAI-T & 1 & Trait anxiety & 20 & 4-point Likert scale \\ 
GAD-2 & 1 & General Anxiety & 2 & 4-point Likert scale \\ 
{\bfseries Personality} &  &  &  &  \\ 
NEO-FFI & 1 & Neuroticism & 12 & 5-point Likert scale \\ 
Mini IPIP6 & 6 & Personality & 24 & Analogue scales \\ 
BFI & 5 & Personality & 44 & 5-point Likert scale \\ 
PID-5-SF & 5 & Dysfunctional personality traits & 25 & 4-point Likert scale \\ 
{\bfseries Psychopathology} &  &  &  &  \\ 
SPQ-BRU & 4 & Schizotypy & 32 & 5-point Likert scale \\ 
MSI-BPD & 1 & Borderline personality disorder & 10 & Analogue scales \\ 
ASQ - Short & 5 & Autistic Traits & 28 & 4-point Likert scale \\ 
{\bfseries Beliefs and Misbeliefs} &  &  &  &  \\ 
GCB & 5 & Conspiracy beliefs & 15 & 5-point Likert scale \\ 
PI-18 & 1 & Beliefs about the world & 99 & 6-point Likert scale \\ 
LIE scale & 4 & Lying tendencies & 16 & Visual analogue scales \\ 
\bottomrule
\end{tabular*}
\end{table}

### 2025-02-10 analysis/study2.qmd
updated manuscript and analysis script

@@
 
+### ICQ
+```{r}
+
+names(df2)[str_detect(names(df2), "ICQ")] 
+names(df7c)[str_detect(names(df7c), "ICQ")]
+
+data <- rbind(
+  data,
+  make_cor(df2, vars_intero, with = "ICQ", component="ICQ") |>
+    mutate(var_Correlate = "ICQ"),
+  make_cor(df7c, vars_intero, with = "ICQ_sum", component="ICQ") |>
+    mutate(var_Correlate = "ICQ")
+)
+
+```
+
 ### BPQ
@@
 names(df7c)[str_detect(names(df7c), "STAI")]
+names(df10b)[str_detect(names(df10b), "STAI")] 
+names(df11a)[str_detect(names(df11a), "ANX")] # anx = stai-t
 
@@
   make_cor(df7a, vars_intero, with = "STAI_T_Sumscore", component="Mood") |>
-    mutate(var_Correlate = "Anxiety (STAI)"),
+    mutate(var_Correlate = "Anxiety (STAI-T)"),
   make_cor(df7b, vars_intero, with = "STAIT_Sum", component="Mood") |>
-    mutate(var_Correlate = "Anxiety (STAI)"),
+    mutate(var_Correlate = "Anxiety (STAI-T)"),
   make_cor(df7c, vars_intero, with = "STAIT_sum", component="Mood") |>
-    mutate(var_Correlate = "Anxiety (STAI)"),
+    mutate(var_Correlate = "Anxiety (STAI-T)"),
   make_cor(df10a, vars_intero, with = "PHQ4_Anxiety", component="Mood") |>
@@
   make_cor(df10b, vars_intero, with = "PHQ4_Anxiety", component="Mood") |>
-    mutate(var_Correlate = "Anxiety (GAD-2)"),
+    mutate(var_Correlate = "Anxiety (STAI-5)"),
   make_cor(df10b, vars_intero, with = "STAI5_General", component="Mood") |>
-    mutate(var_Correlate = "Anxiety (STAI)"),
+    mutate(var_Correlate = "Anxiety (STAI-T)"),
   make_cor(df11a, vars_intero, with =  "ANX", component = "Mood") |>
-    mutate(var_Correlate = "Anxiety (STAI)")
+    mutate(var_Correlate = "Anxiety (STAI-T)")
 )
@@
 
+#MAIA
+average_corr |>
+  filter(Component == "MAIA") |>
+  group_by(var_Correlate) |>
+  summarise(min = min(mean_r),
+             max = max(mean_r))
+#ICQ
+average_corr |>
+  filter(Component == "ICQ") |>
+  group_by(var_Correlate) |>
+  summarise(min = min(mean_r),
+             max = max(mean_r))
+#Mood
+average_corr |>
+  filter(Component == "Mood") |>
+  group_by(var_Correlate) |>
+  summarise(min = min(mean_r),
+             max = max(mean_r))
+
 ```

### 2025-02-10 paper/1_Initial/manuscript.qmd
updated manuscript and analysis script

@@
 
-##### Interoceptive Measures
-
 #### Statistical analysis
@@
 
-**compute internal consistency**
+The EGA components captured grouping of items such as 'wind' and 'burp, 'cough' and 'sneeze', 'muscle' and 'pain'. 
+These groupings were used in correlational analysis to analyse how much each pairing is associated with other factor such as Alexithymia and with Mood disorders (see figure 2).
 
-### Correlations with body measures
+**note**compute internal consistency
+
+#### Correlations with body measures
 <!-- Alexithymia -->
@@
 
-<!-- MAIA -->
+The MAIA was one of the most commonly used measures of interoception in our study, with nine samples reporting its use. 
+This 37-item questionnaire assesses eight state-trait dimensions of interoception: Noticing, Not-Distracting, Not-Worrying, Attention Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust.
+Responses are rated on a scale from 0 (Never) to 5 (Always).
 
-## Correlations
+On average, all MAIA dimensions were positively and weakly to moderately correlated with IAS pairings. 
+Notably, the strongest correlations were observed between the Noticing dimension and the Heart/Breathing pairing (r = 0.394), Trusting and Hungry/Thirsty (r = 0.347), and Attention Regulation and Heart/Breathing (r = 0.334).
+The Not-Distracting and Not-Worrying subscales were generally positively correlated with IAS pairings, with a few exceptions: Not-Distracting showed minimal correlation with Cough/Sneeze (r = 0.0206) and Heart/Breathing (r = -0.007), while Not-Worrying had a low correlation with Itch/Bruise (r = 0.031).
 
-The EGA components capture groupings of pairs of items, such as "wind" and "burp", "cough" and "sneeze", and "muscle" and "pain".
-These groupings were used in the correlational analysis, to observe how much each group/pair correlates with other factors, such as Alexithymia, or the MAIA (see Figure 2).
+<!-- ICQ -->
 
-Alexithymia is negatively correlated with all interoceptive groups.
-Autistic traits are mostly negatively correlated with IAS measure, except for patterns and numbers (as an autistic trait), which is significantly and positively correlated with the "itch/bruise" pairing.
+The Interoceptive Confusion Questionnaire (ICQ; @brewer2016alexithymia) was used to assess individuals' difficulties in interpreting non-affective physiological states, such as pain and hunger.
+The ICQ consists of 20 items rated on a scale from 1 ("Does not describe me") to 5 ("Describes me very well"), with higher scores indicating greater interoceptive confusion.
 
-The BPQ Body Awareness part is positively correlated with all IAS pairs, whereas the Autonomic Reactivity part is negatively correlated with all IAS groupings.
-Conspiracy Beliefs were all positively correlated with the IAS pairs, however, only Global Conspiracy with "hungry/thirsty", "urinate/defecate" and "cough/sneeze", as well as personal wellbeing with "hungry/thirsty", and Information Control with "cough/sneeze" were significantly positively correlated.
+The ICQ showed weak to moderate negative correlations with all IAS pairings.
+The strongest correlation was observed with the Hunger/Thirsty pairing (r = 0.348), while the weakest was with the Itch/Bruise pairing (r = 0.207).
 
-Demographic data is also mostly positively correlated with the IAS findings, where gender and age more strongly correlated with "hungry/thirsty".
+#### Correlations with mood measures
 
-In this analysis, lying profile is not strongly correlated with the IAS, except for contextuality which shows a significant negative correlation with "itch/bruise".
-The MAIA has a strong positive correlation with most IAS pairings, except for the Not Worrying and Not Distracting items of the MAIA, which show less strong, or even negative correlations with all IAS item pairings.
+Mood disorders were assessed using several standardized measures, including the General Anxiety Disorder-2 [GAD-2; @kroenke2007anxiety], the State-Trait Anxiety Inventory [STAI; @spielberger1970manual] and its shorter version, the STAI-5 [@zsido2020development], Beck’s Depression Inventory [BDI; @beck1996beck], and the Mood and Feelings Questionnaire [MFQ; @messer1995development].
+Additionally, the Patient Health Questionnaire (PHQ) was administered in its 2-item [PHQ-2; @kroenke2003patient], 9-item [PHQ-9; @kroenke2001phq], and 15-item [PHQ-15; @kroenke2002phq] versions.
+Finally, borderline personality traits were assessed using the McLean Screening Instrument for Borderline Personality Disorder [MSI-BPD; @zanarini2003zanarini].
 
-Maladaptiveness had mostly negative correlations with the IAS, with only a few significant correlations, namely "psychoticism", "negative affect", and "detachment" with "muscle/pain" and "hungry/thirsty", as well as "negative affect" with "wind/burp".
+<!-- Anxiety -->
+The GAD-2, a brief screening tool for generalized anxiety disorder, consists of two items rated on a scale from 0 (not at all) to 3 (nearly every day).
+The STAI, a 40-item questionnaire rated on a 4-point Likert scale (0 to 3), measures both state and trait anxiety. 
+However, in our study, most participants primarily completed the trait anxiety subscale. 
+In some samples, a shorter 5-item version (STAI-5) was used to assess both state and trait anxiety.
 
-Overall, mood was mostly negatively correlated with the IAS, where "hungry/thirsty" had the strongest negative correlation of all mood measures.
-Except for "neuroticism" and "honesty-humility", personality traits, such as "openness" and "extraversion" were positively correlated with the IAS groupings.
-Shizotypic traits were mostly negatively correlated with the IAS, with "hungry/thirsty" showing the strongest negative correlation between schizotypic and the IAS.
+On average, anxiety measures showed weak negative correlations with all IAS pairs. 
+Notably, the strongest correlations between the IAS pairings and the GAD-2, STAI-T and STAIT-5 were observed with the Hungry/Thirsty pair (r = -0.168, r = -0.270 and r =  -0.248, respectively).
 
-World beliefs were mostly positively correlated with the IAS, however, only a few were significant: "hierarchical", "enticing", and "alive" correlates significantly with "muscle/pain"; "Understandable" has a significant positive correlation with "heart/breathing"; And "hierarchical" and "alive" has a significant positive correlation with "hungry/thirsty".
+<!-- Depression -->
+The BDI consists of 21 items measuring the severity of depressive symptoms on a scale from 0 to 3. 
+The total score is calculated by summing the highest responses, which are then compared to six depression severity levels, ranging from 1–10 (normal fluctuations in mood) to over 40 (extreme depression).
+The PHQ-2 includes two items assessing the frequency of depressive symptoms and anhedonia. 
+The PHQ-2 is derived from the PHQ-9, a nine-item screening tool used to assess depression severity and monitor treatment response.
+Both questionnaires are measured on on a scale from 0 (not at all) to 3 (nearly every day)
+
+Depression measures showed weak to moderate negative correlations with IAS pairings. 
+The BDI (r = -0.372), PHQ-2 (r = -0.148), and PHQ-9 (r = -0.241) correlated most with the Hungry/Thirsty pair, while the MFQ correlated most with Heart/Breathing (r = -0.345) pair.
+
+<!-- Somatic concerns  -->
+
+The PHQ-15 also showed its strongest correlation with the Hungry/Thirsty pair (r = -0.241) but was, on average, weakly and negatively correlated with all other IAS pairings.
+
+<!-- Borderline personality -->
+
+Lastly, the MSI-BPD also showed its strongest negative correlation with the Hungry/Thirsty pair (r = -0.140) and was negatively correlated with all other pairings, except for Cough/Sneeze, which showed a slight positive correlation (r = 0.0219).
 

### 2025-02-10 paper/1_Initial/manuscript.tex
updated manuscript and analysis script

@@
 
-\par{     \begin{tcolorbox}[enhanced jigsaw, breakable, bottomrule=.15mm, rightrule=.15mm, toprule=.15mm, left=2mm, colback=white, arc=.35mm, colframe=quarto-callout-note-color-frame, leftrule=.75mm, opacityback=0]
+\par{     \begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colback=white, breakable, opacityback=0, leftrule=.75mm, arc=.35mm, bottomrule=.15mm, toprule=.15mm, left=2mm, colframe=quarto-callout-note-color-frame]
 
@@
 integrating information pertaining to internal organs, such as the
-heart, the lungs or the gut (\citeproc{ref-khalsa2018}{Khalsa et al.,
-2018}). While recent research emphasizes a key role of interoception in
-a variety of processes (e.g., emotion regulation, decision making) and
-of outcomes (physical and psychological well being), the field remains
-clouded by concerns about how interoception is assessed.
+heart, the lungs or the gut (\citeproc{ref-khalsa2018}{Khalsa, Adolphs,
+Cameron, Critchley, Davenport, Feinstein, Feusner, Garfinkel, Lane,
+Mehling, Meuret, et al., 2018}). While recent research emphasizes a key
+role of interoception in a variety of processes (e.g., emotion
+regulation, decision making) and of outcomes (physical and psychological
+well being), the field remains clouded by concerns about how
+interoception is assessed.
 
 Various measures of interoception have been developed (see
-\textbf{Figure~\ref{fig-measures}}), forming a combination of
-``objective'' and ``subjective'' assessments (i.e., physiological tasks
-such as the heart beat counting or tracking vs.~questionnaires and
-subjective scales involving a metacognitive reflection), ``explicit''
-and ``implicit'' paradigms (i.e., directing participants' awareness and
-attention to interoceptive processes \emph{vs.} measuring interoception
-unbeknownst to them), various interoceptive modalities (e.g.,
-cardioception, respiroception, gastroception) and theoretical dimensions
-(e.g., accuracy, sensitivity, awareness). While there is no consensus as
-to which particular approach provides the most accurate and ``pure''
+Figure~\ref{fig-measures}), forming a combination of ``objective'' and
+``subjective'' assessments (i.e., physiological tasks such as the heart
+beat counting or tracking vs.~questionnaires and subjective scales
+involving a metacognitive reflection), ``explicit'' and ``implicit''
+paradigms (i.e., directing participants' awareness and attention to
+interoceptive processes \emph{vs.} measuring interoception unbeknownst
+to them), various interoceptive modalities (e.g., cardioception,
+respiroception, gastroception) and theoretical dimensions (e.g.,
+accuracy, sensitivity, awareness). While there is no consensus as to
+which particular approach provides the most accurate and ``pure''
 measure of interoception and interoceptive abilities (assuming it is a
@@
 
-\includegraphics[width=1\textwidth,height=\textheight]{figures/MeasuringInteroception.jpg}
+\includegraphics[width=6.4in,height=\textheight]{figures/MeasuringInteroception.jpg}
 
@@
 interoception, including participants' metacognitive beliefs, can be
-assessed subjectively. This approach offers useful and interesting
-measures (\citeproc{ref-lin2023}{Lin et al., 2023};
+assessed subjectively (\citeproc{ref-khalsa2018interoception}{Khalsa,
+Adolphs, Cameron, Critchley, Davenport, Feinstein, Feusner, Garfinkel,
+Lane, Mehling, \& others, 2018};
+\citeproc{ref-suksasilp2022towards}{Suksasilp \& Garfinkel, 2022}). This
+approach offers useful and interesting measures
+(\citeproc{ref-lin2023}{Lin et al., 2023};
 \citeproc{ref-murphy2019}{Murphy et al., 2019}).
@@
 lack of convergence between measures in the field
-(\citeproc{ref-desmedt2022measures}{Desmedt et al., 2022}).
-
-A recent systematic review by Desmedt et al.
+(\citeproc{ref-desmedt2022measures}{Desmedt et al., 2022}). While few
+studies have explored the correlation between objective interoceptive
+measures, such as the Heartbeat Counting Task (HCT,
+\citeproc{ref-schandry1981heart}{Schandry, 1981}) and the Heartbeat
+Detection Task (HDT, \citeproc{ref-kleckner2015methodological}{Kleckner
+et al., 2015}), and correspondent self-report measures, existing
+findings typically show weak or no correlations
+(\citeproc{ref-brand2023}{Brand et al., 2023}; e.g., task-based accuracy
+vs.~self-reported accuracy, \citeproc{ref-murphy2019}{Murphy et al.,
+2019}).
+
+Even among self-report measures low correlations have been observed,
+suggesting that these measures, while group in the same umbrella term of
+self-report assess different facets of interoception. A recent
+systematic review by Desmedt et al.
 (\citeproc{ref-desmedt2022measures}{2022}) examined whether various
-questionnaires designed to measure ``interoceptive sensibility'' truly
-assess the same construct. Notably, Garfinkel et al.
+questionnaires designed to assess ``interoceptive sensibility'' truly
+measure the same construct. Notably, Garfinkel et al.
 (\citeproc{ref-garfinkel2015knowing}{2015}) defines interoceptive
 sensibility as the self-reported tendency to focus on and detect
-internal sensations, whereas
-(\citeproc{ref-khalsa2018interoception}{\textbf{khalsa2018interoception?}})
-defines it more narrowly, excluding the ability to detect these signals.
-According to Desmedt et al. (\citeproc{ref-desmedt2022measures}{2022}),
-most authors adopt the latter definition. The review found that these
-questionnaires measure related but distinct constructs, leading
-researchers to commit the `jingle fallacy'---mistakenly treating them as
-equivalent measures of interoceptive sensibility.
-
-\textbf{TODO: do a better job}
-
-Few studies have examined the correlation between objective
-interoceptive measures, such as the Heartbeat Counting Task (HCT;
-Schandry, 1981) and the Heartbeat Detection Task (HDT; Kleckner et al.,
-2015). Existing findings report weak correlations for the HCT (Murphy et
-al., 2019), no correlations except for the sensitivity variable of the
-HCT (Brand et al., 2023), and small correlations for the HDT (Brand et
-al., 2023). These results suggest that the IAS, a subjective measure,
-does not strongly align with objective interoceptive assessments.
-
-A better understanding of what is being measured with different
+internal sensations, whereas Khalsa, Adolphs, Cameron, Critchley,
+Davenport, Feinstein, Feusner, Garfinkel, Lane, Mehling, and others
+(\citeproc{ref-khalsa2018interoception}{2018}) defines it more narrowly,
+excluding the ability to detect these signals. According to Desmedt et
+al. (\citeproc{ref-desmedt2022measures}{2022}), most authors adopt the
+latter definition. The review found that these questionnaires measure
+related but distinct constructs, leading researchers to mistakenly
+treating them as equivalent measures of interoceptive sensibility. A
+better understanding of what is being measured with different
 questionnaires and dimensions, as well as their potential overlaps with
@@
 for the IAS, the authors underline its acceptable but imperfect fit
-{[}Murphy et al. (\citeproc{ref-murphy2019}{2019}); p.~127{]}, calling
-on further investigation of the scale's factor structure. Notably, the
+(\citeproc{ref-murphy2019}{Murphy et al., 2019, p. 127}), calling on
+further investigation of the scale's factor structure. Notably, the
 authors did not define these factors, as no clear explanations were
@@
 difficult to perceive solely through interoceptive information.
+
+\textbf{note to dom}:Morin et al. (\citeproc{ref-morin2016}{2015}) is a
+methodological paper on ESEM
 
@@
 all items of the IAS grouped together using a new approach, Exploratory
-Graph Analysis {[}EGA; Golino and Epskamp
-(\citeproc{ref-golino2017exploratory}{2017}){]}, to assess convergent
-and discriminant validity, providing further evidence for
-unidimensionality.
+Graph Analysis (EGA, \citeproc{ref-golino2017exploratory}{Golino \&
+Epskamp, 2017}), to assess convergent and discriminant validity,
+providing further evidence for unidimensionality.
 
@@
 (\citeproc{ref-gabriele2022dissociations}{Gabriele et al., 2022}).
+Interestingly, the IAS and the IATS supposedly measure two different
+interoceptive processes (i.e., accuracy and attention, respectively)
+which contradict Murphy et al. (\citeproc{ref-murphy2019}{2019})
+proposed 2x2 framework.
 
@@
 convergent validity for the the IAS, including expected negative
-associations with alexithymia Murphy et al.
-(\citeproc{ref-murphy2019}{2019}), somatic symptoms Lin et al.
-(\citeproc{ref-lin2023}{2023}), depressive symptoms
+associations with alexithymia (\citeproc{ref-brand2023}{Brand et al.,
+2023}; \citeproc{ref-campos2021}{Campos et al., 2021};
+\citeproc{ref-koike2023}{Koike \& Nomura, 2023};
+\citeproc{ref-lin2023}{Lin et al., 2023};
+\citeproc{ref-murphy2019}{Murphy et al., 2019}), somatic symptoms
+(\citeproc{ref-brand2023}{Brand et al., 2023};
+\citeproc{ref-koike2023}{Koike \& Nomura, 2023};
+\citeproc{ref-lin2023}{Lin et al., 2023}), depressive symptoms
 (\citeproc{ref-brand2023}{Brand et al., 2023};
@@
 traditional CFA/SEM factor-based analyses with network-based ones such
-as EGA. 2) The second part will provide an overview of the dispositional
-correlates of the IAS, providing an overview of the pattern of
-associations that is key to better understand the nature, place and role
-of interoception questionnaires within a larger context.
+as EGA; 2) the second part will provide an overview of the dispositional
+correlates of the IAS, clarifying the pattern of associations which is
+key to better understand the nature, place and role of interoception
+questionnaires within a larger context.
 
@@
 unpublished (but already open-access) studies from the authors and one
-from another author. The total N participants was 32,214 participants
-(\emph{Mean} = 48.6 years, \emph{SD} = 13.1, 71.6\% Female).
+from another researcher. The total N participants was 32,214
+participants (\emph{Mean} = 48.6 years, \emph{SD} = 13.1, 71.6\%
+Female).
+
+\begin{landscape}
+
+\input{../../analysis/figures/table1.tex}
+
+\end{landscape}
 
@@
 complex, multidimensional data and provide robust dimension estimates. A
-novel network psychometrics - Unique variable analysis {[}UVA;
-Christensen et al. (\citeproc{ref-christensen2023unique}{2023}){]} -
+novel network psychometrics - Unique variable analysis (UVA,
+\citeproc{ref-christensen2023unique}{Christensen et al., 2023}) -
 approach based on the weighted topological overlap will be computed to
@@
 4-factor structure fits best. The exploratory factor analysis revealed
-that 4 latent factors (oblimin rotation) accounted for 51.95\% of the
-total variance of the original data (MR2 = 19.08\%, MR1 = 17.78\%, MR4 =
-9.34\%, MR3 = 5.75\%). Since UVA identified ``tickle'' as the item to be
+that 4 latent factors (oblimin rotation) accounted for 41.58\% of the
+total variance of the original data (MR1 = 14.45\%, MR3 = 11.76\%, MR2 =
+8.09\%, MR4 = 7.28\%). Since UVA identified ``tickle'' as the item to be
 removed---and it also had the lowest uniqueness value in factor analysis
-with a similar loading to ``itch''---``tickle'' was excluded from
-subsequent analyses.
-
-Confirmatory factor analysis compared 5 models: a single-factor
-solution, a 4-factor solution, a 5-factor solution, a 6-factor solution
-and a 7-factor solution. The latter was preferred in most datasets,
-including with indices that penalise increased number of parameters
-(such as BIC). There was no evidence for higher order factors.
+with a similar loading to ``itch''---'' it was excluded from subsequent
+analyses.
+
+CFA was computed with the removal of the item ``tickle'' as it was
+constantly flagged as redundant. This analysis compared 5 models: a
+single-factor solution, a 4-factor solution, a 5-factor solution, a
+6-factor solution and a 7-factor solution. The latter was preferred in
+most datasets, including with indices that penalise increased number of
+parameters (such as BIC). There was no evidence for higher order
+factors.
 
@@
 These findings contrast with previous research, which all found that
-2-factor model(\citeproc{ref-koike2023}{Koike \& Nomura, 2023};
+2-factor model (\citeproc{ref-koike2023}{Koike \& Nomura, 2023};
 \citeproc{ref-murphy2019}{Murphy et al., 2019}), 1-factor model
@@
 analysis also revealed an okay fit for the 1-factor model, the 4-factor
-model revealed the best fit. The 4-factor structure reveals different
-`hubs' of items that are related, not only in this structure analysis,
-but also in underlying mechanisms. The `wind-burp-cough-sneeze-vomit'
-category, for example, only entails items that are linked to excretion
-through the mouth. The other categories are organized similarly. This
-organization and structure is useful for further analysis, as the data
-can be analyzed and interpreted according to a grouping that is coherent
-in result, as well as underlying mechanisms.
+model was superior. The 4-factor structure reveals different `hubs' of
+items that are related, not only in this structure analysis, but also in
+underlying mechanisms. The `wind-burp-cough-sneeze-vomit' category, for
+example, only entails items that are linked to excretion through the
+mouth. The other categories are organized similarly. This organization
+and structure is useful for further analysis, as the data can be
+analyzed and interpreted according to a grouping that is coherent in
+result, as well as underlying mechanisms.
+
+\textbf{note to dom}: what stats do you mean here? the UVA one?
 
@@
 {[}\textbf{todo}: stats?{]}. Other items with slight redundancy were
-Hungry and Thirsty, Urinate and Defecate, and Sneeze and Cough.
+``hungry'' and ``thirsty'', ``urinate'' and ``defecate'', and ``sneeze''
+and ``cough''.
 
 Interestingly, Lin et al. (\citeproc{ref-lin2023}{2023}) also found that
-tickle and itch were redundant, excluding one of them but the reason
-being that the character for both words is the same in the Chinese
-language. On top of that, they came up with a shortened version of the
-IAS, excluding further items, resulting in a 12-item IAS, which aligns
-with our findings, suggesting that further items are ambiguous as to
-whether they should be removed. In contrast, other findings also found
-itch and tickle to be redundant but did not suggest excluding items
-(\citeproc{ref-campos2021}{Campos et al., 2021}).
+``tickle'' and ``itch'' were redundant, which led them to excludw one of
+them. Although, the reason being that the character for both words is
+the same in the Chinese language. On top of that, they came up with a
+shortened version of the IAS, excluding further items, resulting in a
+12-item IAS, which aligns with our findings, suggesting that further
+items are ambiguous as to whether they should be removed. Their 12-item
+IAS included the ``hunger'', ``breath'', ``urinate'', ``taste'',
+``vomit'', ``cough'', ``temperature'', ``sexual arousa'', ``wind'',
+``muscle'', ``pain'', ``itch'' items.\\
+In contrast, other findings also found ``tickle'' to be redundant but
+did not suggest excluding items (\citeproc{ref-campos2021}{Campos et
+al., 2021}).
 
@@
 dispersed distribution, with some answers indicating the highest 5/5,
-which was not the case in the 5-step scale. Therefore, we recommend
-using an analog scale for the IAS.
-
-Before this paper, the IAS has not yet been used or analyzed with an
-analog scale, rather than a five step scale. Therefore, this study
+which was not the case in Likert-scales. Therefore, we recommend using
+an analog scale for the IAS.
+
+Before this paper, the IAS had not yet been used or analyzed with an
+analog scale, rather than a five-step scale. Therefore, this study
 provides a novel approach to improving the IAS in a simple manner.
@@
 
-There are several limitations to the IAS; There are some redundant
+There are several limitations to the IAS. There are some redundant
 items, the 5-point scale does not provide great variability, and the
@@
 correlates will help validate the IAS, as well as other interoceptive
-measures in the future. The
+measures in the future.
 
@@
 
+\input{../../analysis/figures/table2.tex}
+
 \paragraph{Statistical analysis.}\label{statistical-analysis-1}
@@
 Correlations will be computed using the correlation package under a
-Bayesian framework (ref).
+Bayesian framework (\citeproc{ref-ben2020effectsize}{Ben-Shachar et al.,
+2020}).
 
@@
 
-\textbf{todo: compute average correlations }
-
-The EGA components capture groupings of pairs of items, such as ``wind''
-and ``burp'', ``cough'' and ``sneeze'', or ``muscle'' and ``pain''.
-These groupings were used in the correlational analysis, to observe how
-much each group/pair correlates with other factors, such as Alexithymia,
-or the MAIA (see Figure 2).
-
-Alexithymia is negatively correlated with all interoceptive groups.
-Autistic traits are mostly negatively correlated with IAS measure,
-except for patterns and numbers (as an autistic trait), which is
-significantly and positively correlated with the ``itch/bruise''
-pairing. The BPQ Body Awareness part is positively correlated with all
-IAS pairs, whereas the Autonomic Reactivity part is negatively
-correlated with all IAS groupings. Conspiracy Beliefs were all
-positively correlated with the IAS pairs, however, only Global
-Conspiracy with ``hungry/thirsty'', ``urinate/defecate'' and
-``cough/sneeze'', as well as personal wellbeing with ``hungry/thirsty'',
-and Information Control with ``cough/sneeze'' were significantly
-positively correlated. Demographic data is also mostly positively
-correlated with the IAS findings, where gender and age more strongly
-correlated with ``hungry/thirsty''. In this analysis, lying profile is
-not strongly correlated with the IAS; Except for contextuality, which
-shows a significant negative correlation with ``itch/bruise''. The MAIA
-has a strong positive correlation with most IAS pairings, except for the
-``not worrying'' and ``not distracting'' items of the MAIA, which show
-less strong, or even negative correlations with all IAS item pairings.
-Maladaptiveness had mostly negative correlations with the IAS, with only
-a few significant correlations, namely ``psychoticism'', ``negative
-affect'', and ``detachment'' with ``muscle/pain'' and
-``hungry/thirsty'', as well as ``negative affect'' with ``wind/burp''.
-Overall, mood was mostly negatively correlated with the IAS, where
-``hungry/thirsty'' had the strongest negative correlation of all mood
-measures. Except for ``neuroticism'' and ``honesty-humility'',
-personality traits, such as ``openness'' and ``extraversion'' were
-positively correlated with the IAS groupings. Shizotypic traits were
-mostly negatively correlated with the IAS, with ``hungry/thirsty''
-showing the strongest negative correlation between schizotypic and the
-IAS. World beliefs were mostly positively correlated with the IAS,
-however, only a few were significant: ``hierarchical'', ``enticing'',
-and ``alive'' correlates significantly with ``muscle/pain'';
-``Understandable'' has a significant positive correlation with
-``heart/breathing''; And ``hierarchical'' and ``alive'' has a
-significant positive correlation with ``hungry/thirsty''.
+\subsection{Average correlations}\label{average-correlations}
+
+The EGA components captured grouping of items such as `wind' and `burp,
+'cough' and `sneeze', `muscle' and `pain'. These groupings were used in
+correlational analysis to analyse how much each pairing is associated
+with other factor such as Alexithymia and with Mood disorders (see
+figure 2).
+
+\textbf{note}compute internal consistency
+
+\paragraph{Correlations with body
+measures.}\label{correlations-with-body-measures}
+
+Alexithymia was assessed in the samples with the Bermond--Vorst
+Alexithymia Questionnaire {[}BVAQ; Vorst and Bermond
+(\citeproc{ref-vorst2001validity}{2001}){]} and the Toronto Alexithymia
+Scale{[}TAS; Bagby et al. (\citeproc{ref-bagby1994twenty}{1994}){]}.
+
+The BVAQ consists of 5 subscales - fantasising, idenitying, analysing;
+verbalising and emotionalising - assessed with 40 items on a 5-point
+Likert scale, from `defnitely applies to me' to `in no way applies to
+me'. Additionally, the BVAQ reduces these subscales into two high order
+factors, an affective component and a cognitive one, with high scores
+being indicative of high proneness to alexithymia.
+
+On average, the cognitive component of the BVAQ was weakly and
+negatively correlated with all IAS pairs of items with the biggest
+correlation being with the Itch/Bruise pair (r = -0.112) and the lowest
+correlation beeing with the Muscle/Pain pair (r = -0.244). The affective
+component of the BVAQ was positively, but very weak, correlated with all
+pairs, with the biggest correlation being with the Itch/Bruise pair (r =
+0.107). The only exception was a negative correlation with the
+Urinate/Defecate pair (r = -0.036).
+
+The TAS contains 20-items rated on a 5-point forced scale, from
+`strongly disagree' to `strongly afree', divided into 3 dimensions -
+difficulty identiying feelings, difficulty describing feelings, and
+externally thinking. High scores on this scale also reflect higher
+alexithymia.
+
+All the three dimensions assessed with the TAS were on average
+negatively correlated with all pairs of IAS items. The difficulty
+describing feelings had its strongest correlation with Hungry/Thirsty (r
+= -0.179) and weakest with the Wind/Burp (r = -0.117). while, the
+difficulty describing feelings had its strongest correlation with
+Muscle/Pain (r = -0.247) and weakest with Itch/Bruise (r = -0.157).
+Lastly, the external thinking dimension was more correlated with the
+Cough/Sneeze pair (r = -0.138) and less correlated with the
+Hungry/Thirsty (r = -0.018).
+
+The studies within our sample used the Body Perception Questionnaire
+short-form (BPQ-SF) and the very-short form (BPQ-VSF) to assess
+interoception (\citeproc{ref-cabrera2018assessing}{Cabrera et al.,
+2018}). The BPQ-SF comprised of 46 items on a 5-point Likert scale
+assessing body awareness (26 items) and autonomic reactivity (21 items).
+The BPQ-VSF comprises of 12 items from the body awareness subscale of
+the BPQ-SF. In this study, all scores assessing these two dimensions
+were grouped together, hence no disitintion is made between awareness
+measured with the BPQ-SF and the BPQ-VSF.
+
+\textbf{note to add:} discuss later
+
+In general, all pairs of the IAS were positively,and weakily, associated
+with the body awareness subscales, while negative and weakily correlated
+with the autonomic reactivity subscale. The strongest correlation
+identified between the IAS pairs and the body awereness subscale was
+with the\\
+Heart/Breathing pair (r = 0.151) whilst the strongest correlation with
+the autonomic reactivity was with the Urinate/Defecate pair (r =
+-0.235). The weakest correlation between the body awareness and the IAS
+was with the Hungry/Thirsty pair (r = 0.055) and between the autonomic
+reactivity and the IAS was with the Heart/Breathing pair (r = -0.106).
+
+The MAIA was one of the most commonly used measures of interoception in
+our study, with nine samples reporting its use. This 37-item
+questionnaire assesses eight state-trait dimensions of interoception:
+Noticing, Not-Distracting, Not-Worrying, Attention Regulation, Emotional
+Awareness, Self-Regulation, Body Listening, and Trust. Responses are
+rated on a scale from 0 (Never) to 5 (Always).
+
+On average, all MAIA dimensions were positively and weakly to moderately
+correlated with IAS pairings. Notably, the strongest correlations were
+observed between the Noticing dimension and the Heart/Breathing pairing
+(r = 0.394), Trusting and Hungry/Thirsty (r = 0.347), and Attention
+Regulation and Heart/Breathing (r = 0.334). The Not-Distracting and
+Not-Worrying subscales were generally positively correlated with IAS
+pairings, with a few exceptions: Not-Distracting showed minimal
+correlation with Cough/Sneeze (r = 0.0206) and Heart/Breathing (r =
+-0.007), while Not-Worrying had a low correlation with Itch/Bruise (r =
+0.031).
+
+The Interoceptive Confusion Questionnaire (ICQ; Brewer et al.
+(\citeproc{ref-brewer2016alexithymia}{2016})) was used to assess
+individuals' difficulties in interpreting non-affective physiological
+states, such as pain and hunger. The ICQ consists of 20 items rated on a
+scale from 1 (``Does not describe me'') to 5 (``Describes me very
+well''), with higher scores indicating greater interoceptive confusion.
+
+The ICQ showed weak to moderate negative correlations with all IAS
+pairings. The strongest correlation was observed with the Hunger/Thirsty
+pairing (r = 0.348), while the weakest was with the Itch/Bruise pairing
+(r = 0.207).
+
+\paragraph{Correlations with mood
+measures.}\label{correlations-with-mood-measures}
+
+Mood disorders were assessed using several standardized measures,
+including the General Anxiety Disorder-2 {[}GAD-2; Kroenke et al.
+(\citeproc{ref-kroenke2007anxiety}{2007}){]}, the State-Trait Anxiety
+Inventory {[}STAI; Spielberger
+(\citeproc{ref-spielberger1970manual}{1970}){]} and its shorter version,
+the STAI-5 (\citeproc{ref-zsido2020development}{Zsido et al., 2020}),
+Beck's Depression Inventory {[}BDI; Beck et al.
+(\citeproc{ref-beck1996beck}{1996}){]}, and the Mood and Feelings
+Questionnaire {[}MFQ; Messer et al.
+(\citeproc{ref-messer1995development}{1995}){]}. Additionally, the
+Patient Health Questionnaire (PHQ) was administered in its 2-item
+{[}PHQ-2; Kroenke et al. (\citeproc{ref-kroenke2003patient}{2003}){]},
+9-item {[}PHQ-9; Kroenke et al.
+(\citeproc{ref-kroenke2001phq}{2001}){]}, and 15-item {[}PHQ-15; Kroenke
+et al. (\citeproc{ref-kroenke2002phq}{2002}){]} versions. Finally,
+borderline personality traits were assessed using the McLean Screening
+Instrument for Borderline Personality Disorder {[}MSI-BPD; Zanarini
+(\citeproc{ref-zanarini2003zanarini}{2003}){]}.
+
+The GAD-2, a brief screening tool for generalized anxiety disorder,
+consists of two items rated on a scale from 0 (not at all) to 3 (nearly
+every day). The STAI, a 40-item questionnaire rated on a 4-point Likert
+scale (0 to 3), measures both state and trait anxiety. However, in our
+study, most participants primarily completed the trait anxiety subscale.
+In some samples, a shorter 5-item version (STAI-5) was used to assess
+both state and trait anxiety.
+
+On average, anxiety measures showed weak negative correlations with all
+IAS pairs. Notably, the strongest correlations between the IAS pairings
+and the GAD-2, STAI-T and STAIT-5 were observed with the Hungry/Thirsty
+pair (r = -0.168, r = -0.270 and r = -0.248, respectively).
+
+The BDI consists of 21 items measuring the severity of depressive
+symptoms on a scale from 0 to 3. The total score is calculated by
+summing the highest responses, which are then compared to six depression
+severity levels, ranging from 1--10 (normal fluctuations in mood) to
+over 40 (extreme depression). The PHQ-2 includes two items assessing the
+frequency of depressive symptoms and anhedonia. The PHQ-2 is derived
+from the PHQ-9, a nine-item screening tool used to assess depression
+severity and monitor treatment response. Both questionnaires are
+measured on on a scale from 0 (not at all) to 3 (nearly every day)
+
+Depression measures showed weak to moderate negative correlations with
+IAS pairings. The BDI (r = -0.372), PHQ-2 (r = -0.148), and PHQ-9 (r =
+-0.241) correlated most with the Hungry/Thirsty pair, while the MFQ
+correlated most with Heart/Breathing (r = -0.345) pair.
+
+The PHQ-15 also showed its strongest correlation with the Hungry/Thirsty
+pair (r = -0.241) but was, on average, weakly and negatively correlated
+with all other IAS pairings.
+
+Lastly, the MSI-BPD also showed its strongest negative correlation with
+the Hungry/Thirsty pair (r = -0.140) and was negatively correlated with
+all other pairings, except for Cough/Sneeze, which showed a slight
+positive correlation (r = 0.0219).
 
@@
 
-Our findings confirmed that interception lies within an intricate
-network of correlates. Alexithyma has the most negative correlation with
-the IAS, whereas, the MAIA questionnaire is most strongly positively
-correlated with the IAS. The correlates cannot only explain attributes
-of interoception, but can also be used to validate measures for
-interoception.
-
-While these results reveal correlations of different categories with the
-IAS, the findings are limited to the given questionnaire. However, they
-give a good indication of how interoception in general might be linked
-to the different categories, leading to interesting findings. The
-results show a consistent pattern of correlations with other
-interoception measures, psychopathology, and highlighting of interesting
-exploratory results, such as how primal world beliefs correlate with the
-IAS.
-
-The analysis revealed a negative correlation between alexithymia and
-scores in the IAS, which is in line with previous research
-(\citeproc{ref-herbert2011}{Herbert et al., 2011}). A negative
-correlation between autism and interoceptive awareness, which has been
-found in this sample, has also been found in previous research
-(\citeproc{ref-dubois2016}{DuBois et al., 2016}). Conspiracy Beliefs and
-IAS scores were not strongly correlated. However, there was a slight
-positive correlation. To the best of our knowledge, this interaction has
-not been investigated before. However, research shows correlations
-between (political) beliefs and interoception, which could underlie the
-same mechanism (\citeproc{ref-ruisch2022}{Ruisch et al., 2022a}). Lying
-profile was also not strongly correlated with the IAS. Previous research
-provides some evidence for a relationshipbetween interoception and lying
-profile (\citeproc{ref-makowski2023a}{Makowski et al., 2023}),
-indicating a contrast from the literature to the results at hand. The
-analysis showed that mood and the IAS scores have a strong negative
-correlation, which has been investigated in previous studies, finding a
-correlation between the two variables as well
-(\citeproc{ref-solanoluxf3pez2018}{Solano López \& Moore, 2018}). The
-analysis showed that personality is also correlated with interoceptive
-accuracy scores as retrieved by the IAS. While there are many aspects of
-personality, put simply, personality and interoception have been found
-to correlate in previous studies as well (\citeproc{ref-erle2021}{Erle
-et al., 2021}). Our findings show some negative correlations between
-schizotypy and interoception. Previous research has investigated this
-relationship and, similarly, found a negative correlation between
-interoceptive awareness and schizotypy, particularly at the onset of
-psychosis (\citeproc{ref-torregrossa2022}{Torregrossa et al., 2022}).
-Lastly, World Beliefs and Interoception showed some significant positive
-correlations. World Beliefs have not been linked with interoception
-previously. As mentioned, other beliefs, such as political beliefs have
-been mentioned to interoception, where significant correlations were
-observed (\citeproc{ref-ruisch2022a}{Ruisch et al., 2022b}). Further
-research is needed to understand this mechanism and validate whether
-world beliefs, which lay the framework through which we see the world
-(\citeproc{ref-clifton2020}{Clifton, 2020}), is needed.
-
-The above findings show how interoception is correlated with many
-lifestyle and health factors, and is therefore an important concept to
-study. Here we showed many correlates of the IAS and lifestyle, as well
-as health factors. This is not only valuable to understand interception,
-and the role it plays in our lives, better, but also crucial to further
-validate the Ias, as well as other interoception measures. This analysis
-therefore lays the groundwork for validating new interoceptive measures
-and questionnaires needed to grasp interoception and its role in our
-life.
+Our findings confirm that interoception exists within a complex network
+of correlates. Among these, alexithymia exhibits the strongest negative
+correlation with the IAS, whereas the MAIA questionnaire shows the
+strongest positive correlation. These correlates not only help explain
+different aspects of interoception but also serve as valuable tools for
+validating interoceptive measures.
+
+While our results reveal various correlations with the IAS, they are
+limited to the scope of the given questionnaire. Nonetheless, they
+provide valuable insights into how interoception may relate to different
+psychological and personality traits. The results show a consistent
+pattern of correlations with other measures and highlight interesting
+exploratory results, such as correlations between primal world beliefs
+with the IAS.
+
+Our analysis found a strong negative correlation between alexithymia and
+IAS scores, aligning with previous research
+(\citeproc{ref-brand2023}{Brand et al., 2023};
+\citeproc{ref-herbert2011}{Herbert et al., 2011};
+\citeproc{ref-murphy2019}{Murphy et al., 2019}). Similarly, a negative
+correlation between autism and interoceptive awareness was observed in
+our sample, consistent with prior findings
+(\citeproc{ref-dubois2016}{DuBois et al., 2016}).
+
+Conspiracy beliefs did not strongly correlate with IAS scores, though a
+slight positive correlation was present. To our knowledge, this
+relationship has not been previously explored. However, prior studies
+have suggested connections between interoception and (political)
+beliefs, potentially pointing to shared underlying mechanisms
+(\citeproc{ref-ruisch2022}{Ruisch et al., 2022a}).
+
+The relationship between interoception and lying profiles was also weak.
+This contrasts with previous research suggesting associations between
+interoception and deception (\citeproc{ref-makowski2023a}{Makowski et
+al., 2023}), warranting further investigation.
+
+Mood and IAS scores exhibited a strong negative correlation, consistent
+with prior studies that have documented similar findings
+(\citeproc{ref-solanoluxf3pez2018}{Solano López \& Moore, 2018}).
+Additionally, personality traits correlated with interoceptive accuracy
+scores, reinforcing existing research linking personality and
+interoception (\citeproc{ref-erle2021}{Erle et al., 2021}).
+
+We also observed negative correlations between schizotypy and
+interoception, in line with previous studies that identified a similar
+relationship with interoceptive awareness, particularly in individuals
+at risk for psychosis (\citeproc{ref-torregrossa2022}{Torregrossa et
+al., 2022}).
+
+Interestingly, world beliefs demonstrated significant positive
+correlations with interoception. While this relationship has not been
+previously documented, other forms of belief, such as political
+ideology, have been linked to interoception
+(\citeproc{ref-ruisch2022a}{Ruisch et al., 2022b}). Further research is
+needed to determine whether world beliefs, which shape our perception of
+reality (\citeproc{ref-clifton2020}{Clifton, 2020}), are meaningfully
+connected to interoception.
+
+Overall, our findings highlight the broad relevance of interoception
+across various cognitive and affective traits, underscoring its
+significance in both research and clinical contexts. By identifying
+numerous correlates of the IAS, we contribute not only to a deeper
+understanding of interoception's role in daily life but also to the
+ongoing validation of the IAS and other interoceptive measures. This
+analysis lays an important foundation for the development of new
+interoceptive assessment tools, further advancing our comprehension of
+interoception and its impact on human experience.
 
@@
 
-The analyses revealed that the IAS has 4-factor structure, and a rather
-uneven distribution. The findings indicate that the IAS is measuring
-interoception in an acceptable manner, but there is also room for
-improvement. Furthermore, the results reveal different correlation
-measures with the IAS, giving space to further explore whether and how
-measures correlate with interoception/the IAS. In the following section,
-the IAS is discussed further to reveal shortcomings and strengths of the
-questionnaire. Finally, future steps will be revealed to improve the way
-in which we measure interoception.
-
-Overall, the IAS is straightforward with its sensation-centered items.
-There are several points of improvement to the IAS, which this work
-suggests. Firstly, removing redundant items, such as the itch item as
-shown in the above analysis. Previous work has also shown that the itch
-and tickle items are subject to redundancy Campos et al.
-(\citeproc{ref-campos2021}{2021}) has shown. Interestingly, Campos et
-al. (\citeproc{ref-campos2021}{2021}) suggest removing the tickle item
-instead. Lin et al. (\citeproc{ref-lin2023}{2023}) on the other hand
-removed the itch item, because the sign for itch and tickle is the same.
-Furthermore, this work recommends using analog scales, instead of 5
-point scales. In a 5-point scale, the variability is clearly limited
-with most people choosing ⅘. As visible in Figure X, the variability
-increases significantly, using an analog scale. However, it is important
-to note that even with an analog scale, the variability of the IAS is
-still limited. The more variability a scale shows, the more results can
-depict individual differences between participants. Therefore, good
-dispersion is essential for achieving relevant and usable results, and
-striving for more variability would be beneficial to this interoception
-scale, too.
-
-In this work, it becomes apparent that even with the mentioned
-improvements to the scale, there are limitations to the IAS, which
-reduce the accuracy of this scale. Those limitations include that there
-are few items for some modalities, such as only one item for heart
-perception. Having more modality is useful as each grouping can have
-more variability with increased modality, leading to more nuanced
-results. On top of that, there is no clear and theoretical, or empirical
-structure, as there is a very small grouping of items. Ideally, a scale
-would allow for an analysis showing different groupings so that
-different categories can be created based on which the data can be
-analyzed. The groupings in this analysis reveal that the IAS can only be
-grouped with two items per group, leading to low scores and variability
-in each group. On top of that, there are ambiguous items in the IAS, of
-which the grouping depends on the context. For example, one might
-indicate that they can perceive well how their heart is beating fast as
-well as vomiting, but both items can be linked to feeling anxious, and
-therefore might indicate different results than initially expected.
-Therefore, the grouping and structure of the IAS can be improved.
-
-Furthermore, all items are phrased positively, which might influence how
-participants answer the questions. While phrasing items in a positive
-manner can be beneficial, the benefits of positive phrasing might
-exacerbate a positive bias and thus lead to unidimensional results.
-Therefore, phrasing questions in a more diverse manner might lead to
-more accurate results and might thus be beneficial.
-
-Based on the given arguments, it becomes clear that there is a need for
-context-specific items, which are cross-modal when possible, such as
-integrating cardioception and respiroception. After establishing the
-clear need for a new scale to measure interoception, this study proposes
-the need for a new scale (Multimodal Interoceptive Sensitivity Scale,
-MISS) to adapt to the newest findings on the IAS and what we know about
-interoception to this day. The new scale will be able to be compared to
-the correlates of the IAS.
-
-\subsection{Conclusion}\label{conclusion}
-
-The IAS is a good way of measuring interoception considering the current
-existing questionnaires and tools. However, revising, or even
-re-inventing a survey to measure interoception would lead to the best
-measure of interoception. Therefore, this study proposes that a new
-scale to measure interoception is needed to evolve the current research
-on interoception. This study revealed many correlates of the IAS, giving
-space for future analysis on what might be a good interoceptive measure,
-and therefore laying the groundwork for the creation of a new
-interoception survey.
+Our analyses revealed that the IAS follows a four-factor structure with
+an uneven distribution. While the findings indicate that the IAS
+measures interoception adequately, there is room for improvement.
+Additionally, different correlation measures with the IAS suggest
+opportunities for further exploration of how interoception is assessed.
+In the following section, we discuss the strengths and shortcomings of
+the IAS, followed by proposed steps to enhance interoception
+measurement.
+
+Overall, the IAS is straightforward in its sensation-centered items.
+However, several areas for improvement emerge from this study. Firstly,
+redundant items should be removed, such as the ``itch'' item, as
+highlighted in our analysis. Previous research also suggests redundancy
+between itch and tickle items Campos et al.
+(\citeproc{ref-campos2021}{2021}). Interestingly, while Campos et al.
+(\citeproc{ref-campos2021}{2021}) does not recommend the removal of
+either, Lin et al. (\citeproc{ref-lin2023}{2023}) argues for removing
+the itch item due to their overlapping character representation.
+
+Furthermore, this study recommends using analog scales instead of
+5-point scales. The limited variability of the 5-point scale often
+results in most responses clustering around 3 or 4. As shown in
+Figure~\ref{fig-distributions}, adopting an analog scale significantly
+increases variability. However, even with an analog scale, IAS
+variability remains constrained. Greater variability allows for better
+differentiation among participants, making dispersion an essential
+factor for obtaining meaningful results. Enhancing variability would
+therefore be beneficial for the IAS.
+
+Despite these improvements, certain limitations persist in the IAS that
+affect its accuracy. Notably, some modalities are underrepresented---for
+instance, heart perception is measured by only one item. Expanding
+modality coverage would enhance variability within each category,
+leading to more nuanced results. Moreover, the IAS lacks a clear
+theoretical or empirical structure, with only small item groupings.
+Ideally, a scale should allow for clear groupings that support
+meaningful data analysis. In this study, each group contained only two
+items, resulting in low scores and limited variability. Additionally,
+some IAS items are ambiguous, with their interpretation depending on
+context. For example, an item about perceiving heartbeats and another
+about vomiting could both relate to anxiety, leading to results that may
+differ from initial expectations. Thus, the grouping and structure of
+the IAS require refinement.
+
+Another concern is that all IAS items are phrased positively, which may
+influence participant responses. While positive phrasing has advantages,
+it can also introduce response bias, leading to unidimensional results.
+A more balanced phrasing approach, incorporating both positively and
+negatively framed items, could yield more accurate responses.
+
+Given these considerations, it is clear that context-specific,
+cross-modal items---such as integrating cardioception and
+respiroception---are needed. Recognizing the necessity for a refined
+interoception scale, this study proposes the development of the
+Multidimensional Interoceptive Inventory (MInt). This new scale will be
+designed to align with recent findings on the IAS and interoception
+research while allowing for direct comparison with IAS correlates.
 
@@
 put that in the discussion in the suggestions for better scales}
+
+\subsection{Conclusion}\label{conclusion}
+
+The IAS is a valuable tool for measuring interoception compared to
+existing questionnaires and methods. However, refining or even
+redesigning the questionnaire could lead to a more precise and
+comprehensive assessment. This study highlights the need for a new
+interoception scale to advance research in the field. By identifying
+various correlates of the IAS, this work paves the way for future
+investigations into optimal interoceptive measures, ultimately laying
+the foundation for the development of a more effective interoception
+survey.
 
@@
 
+\bibitem[\citeproctext]{ref-bagby1994twenty}
+Bagby, R. M., Parker, J. D., \& Taylor, G. J. (1994). The twenty-item
+toronto alexithymia scale---i. Item selection and cross-validation of
+the factor structure. \emph{Journal of Psychosomatic Research},
+\emph{38}(1), 23--32.
+
+\bibitem[\citeproctext]{ref-beck1996beck}
+Beck, A. T., Steer, R. A., \& Brown, G. (1996). Beck depression
+inventory--II. \emph{Psychological Assessment}.
+
+\bibitem[\citeproctext]{ref-ben2020effectsize}
+Ben-Shachar, M. S., Lüdecke, D., \& Makowski, D. (2020). Effectsize:
+Estimation of effect size indices and standardized parameters.
+\emph{Journal of Open Source Software}, \emph{5}(56), 2815.
+
 \bibitem[\citeproctext]{ref-brand2023}
@@
 
+\bibitem[\citeproctext]{ref-cabrera2018assessing}
+Cabrera, A., Kolacz, J., Pailhez, G., Bulbena-Cabre, A., Bulbena, A., \&
+Porges, S. W. (2018). Assessing body awareness and autonomic reactivity:
+Factor structure and psychometric properties of the body perception
+questionnaire-short form (BPQ-SF). \emph{International Journal of
+Methods in Psychiatric Research}, \emph{27}(2), e1596.
+
 \bibitem[\citeproctext]{ref-campos2021}
@@
 
+\bibitem[\citeproctext]{ref-kleckner2015methodological}
+Kleckner, I. R., Wormwood, J. B., Simmons, W. K., Barrett, L. F., \&
+Quigley, K. S. (2015). Methodological recommendations for a heartbeat
+detection-based measure of interoceptive sensitivity.
+\emph{Psychophysiology}, \emph{52}(11), 1432--1440.
+
 \bibitem[\citeproctext]{ref-koike2023}
@@
 scale. \emph{SAGE Open}, \emph{13}(4), 21582440231214639.
+
+\bibitem[\citeproctext]{ref-kroenke2001phq}
+Kroenke, K., Spitzer, R. L., \& Williams, J. B. (2001). The PHQ-9:
+Validity of a brief depression severity measure. \emph{Journal of
+General Internal Medicine}, \emph{16}(9), 606--613.
+
+\bibitem[\citeproctext]{ref-kroenke2002phq}
+Kroenke, K., Spitzer, R. L., \& Williams, J. B. (2002). The PHQ-15:
+Validity of a new measure for evaluating the severity of somatic
+symptoms. \emph{Psychosomatic Medicine}, \emph{64}(2), 258--266.
+
+\bibitem[\citeproctext]{ref-kroenke2003patient}
+Kroenke, K., Spitzer, R. L., \& Williams, J. B. (2003). The patient
+health questionnaire-2: Validity of a two-item depression screener.
+\emph{Medical Care}, \emph{41}(11), 1284--1292.
+
+\bibitem[\citeproctext]{ref-kroenke2007anxiety}
+Kroenke, K., Spitzer, R. L., Williams, J. B., Monahan, P. O., \& Löwe,
+B. (2007). Anxiety disorders in primary care: Prevalence, impairment,
+comorbidity, and detection. \emph{Annals of Internal Medicine},
+\emph{146}(5), 317--325.
 
@@
 
+\bibitem[\citeproctext]{ref-messer1995development}
+Messer, S. C., Angold, A., Costello, E. J., Loeber, R., Van Kammen, W.,
+\& Stouthamer-Loeber, M. (1995). Development of a short questionnaire
+for use in epidemiological studies of depression in children and
+adolescents: Factor composition and structure across development.
+\emph{International Journal of Methods in Psychiatric Research},
+\emph{5}, 251--262.
+
+\bibitem[\citeproctext]{ref-morin2016}
+Morin, A. J. S., Arens, A. K., \& Marsh, H. W. (2015). A bifactor
+exploratory structural equation modeling framework for the
+identification of distinct sources of construct-relevant psychometric
+multidimensionality. \emph{Structural Equation Modeling: A
+Multidisciplinary Journal}, \emph{23}(1), 116--139.
+\url{https://doi.org/10.1080/10705511.2014.961800}
+
 \bibitem[\citeproctext]{ref-murphy2019}
@@
 
+\bibitem[\citeproctext]{ref-schandry1981heart}
+Schandry, R. (1981). Heart beat perception and emotional experience.
+\emph{Psychophysiology}, \emph{18}(4), 483--488.
+
 \bibitem[\citeproctext]{ref-solanoluxf3pez2018}
@@
 \url{https://doi.org/10.1177/0193945918798374}
+
+\bibitem[\citeproctext]{ref-spielberger1970manual}
+Spielberger, C. D. (1970). Manual for the state-trait anxiety inventory
+(self-evaluation questionnaire). \emph{(No Title)}.
+
+\bibitem[\citeproctext]{ref-suksasilp2022towards}
+Suksasilp, C., \& Garfinkel, S. N. (2022). Towards a comprehensive
+assessment of interoception in a multi-dimensional framework.
+\emph{Biological Psychology}, \emph{168}, 108262.
 
@@
 
+\bibitem[\citeproctext]{ref-vorst2001validity}
+Vorst, H. C., \& Bermond, B. (2001). Validity and reliability of the
+bermond--vorst alexithymia questionnaire. \emph{Personality and
+Individual Differences}, \emph{30}(3), 413--434.
+
+\bibitem[\citeproctext]{ref-zanarini2003zanarini}
+Zanarini, M. C. (2003). Zanarini rating scale for borderline personality
+disorder (ZAN-BPD): A continuous measure of DSM-IV borderline
+psychopathology. \emph{Journal of Personality Disorders}, \emph{17}(3),
+233--242.
+
+\bibitem[\citeproctext]{ref-zsido2020development}
+Zsido, A. N., Teleki, S. A., Csokasi, K., Rozsa, S., \& Bandi, S. A.
+(2020). Development of the short version of the spielberger
+state---trait anxiety inventory. \emph{Psychiatry Research}, \emph{291},
+113223.
+
 \end{CSLReferences}

### 2025-02-12 paper/1_Initial/manuscript.qmd
manuscript updated

@@
 <!-- MAIA -->
-
 The MAIA was one of the most commonly used measures of interoception in our study, with nine samples reporting its use. 
@@
 <!-- ICQ -->
-
 The Interoceptive Confusion Questionnaire (ICQ; @brewer2016alexithymia) was used to assess individuals' difficulties in interpreting non-affective physiological states, such as pain and hunger.
@@
 <!-- Somatic concerns  -->
-
-The PHQ-15 also showed its strongest correlation with the Hungry/Thirsty pair (r = -0.241) but was, on average, weakly and negatively correlated with all other IAS pairings.
+The PHQ-15 is a 15-item questionnaire that assesses somatic symptoms on a 3-point scale (e.g., back pain). 
+It exhibited its strongest correlation with the Hungry/Thirsty pair (r = -0.241) and, on average, showed weak negative correlations with all other IAS pairings.
 
 <!-- Borderline personality -->
+Lastly, the MSI-BPD is a 10-item questionnaire used to assess personality disorder, where items are rated on a dichotomous scale of 1 (present) and 0 (absent). 
+The MSI-BPD also showed its strongest negative correlation with the Hungry/Thirsty pair (r = -0.140) and was negatively correlated with all other pairings, except for Cough/Sneeze, which showed a slight positive correlation (r = 0.0219).
 
-Lastly, the MSI-BPD also showed its strongest negative correlation with the Hungry/Thirsty pair (r = -0.140) and was negatively correlated with all other pairings, except for Cough/Sneeze, which showed a slight positive correlation (r = 0.0219).
+#### Correlations with psychopathology measures
+
+<!-- Maladaptive  -->
+Maladaptive personality traits were assessed using the Personality Inventory for DSM-5 Short Form [PID-5-SF; @thimm2016personality], which measures five domains: disinhibition, antagonism, detachment, negative affect, and psychoticism.
+The scale consists of 25 items rated on a 4-point Likert scale, ranging from 0 (very false or often false) to 3 (very true or often true).
+
+On average, all maladaptive personality traits assessed by the PID-5-SF were weakly and negatively correlated with IAS pairings.
+The strongest correlation was observed between the psychoticism dimension and the Muscle/Pain pairing (r = -0.173).
+
+<!-- Schyzoty -->
+Schizotypy was assessed using the Schizotypal Personality Questionnaire – Brief Revised Updated (SPQ-BRU; @davidson2016schizotypal), which consists of 32 items rated on a 5-point Likert scale ranging from strongly agree to strongly disagree.
+This questionnaire evaluates four primary dimensions: cognitive-perceptual (positive), interpersonal (negative), disorganized, and social anxiety. 
+These dimensions are further divided into nine secondary factors: constricted affect, eccentricity, magical thinking, lack of close friends, odd speech, referential thinking, social anxiety, suspiciousness, and unusual perceptions.
+
+On average, all nine factors were weakly and negatively correlated with IAS pairings, with correlations ranging from r = -0.170 (between lack of close friends and Muscles/Pain) to r = 0.102 (between magical thinking and Itch/Bruise).
+
+<!-- Autism -->
+The short version of the Autism-Spectrum Quotient (ASQ-Short; Hoekstra et al., 2011) was used to assess five autistic traits: social skills, adherence to routines, cognitive flexibility (switching), imagination, and patterns/numbers.
+The questionnaire consists of 28 items rated on a 4-point Likert scale, ranging from 1 (definitely agree) to 4 (definitely disagree).
+
+Overall, all pairings were weakly and negatively correlated with the ASQ dimensions, except for the Itch/Bruise and Heart/Breathing pairings, which showed weak positive correlations with the patterns/numbers trait (r = 0.184 and r = 0.038, respectively).
+The strongest correlation was observed between the imagination trait and the Wind/Burp pairing (r = -0.218).
+
+#### Correlations with personality measures
+
+The Big Five Inventory-Short Form [BFI-S; @lang2011short] and the Mini International Personality Item Pool [Mini-IPIP6; @sibley2011mini] were used to assess general personality traits. 
+The BFI-S consists of 15 items rated on a 7-point Likert scale, ranging from 1 (strongly disagree) to 7 (strongly agree), measuring five personality factors: Openness, Conscientiousness, Extraversion, Agreeableness, and Neuroticism.
+The Mini-IPIP6 assesses six personality traits—Extraversion, Agreeableness, Conscientiousness, Neuroticism, Openness, and Honesty-Humility—using 24 items. 
+While this questionnaire is typically scored on a 7-point Likert scale from 1 (very inaccurate) to 7 (very accurate), an analogous scale was used in the respective sample. 
+Lastly, the Neuroticism subscale of the NEO Five-Factor Inventory [Neo-FFI; @costa1992normal] was used to assess Neuroticism, consisting of 12 items rated on a 5-point Likert scale from 1 (strongly disagree) to 5 (strongly agree).
+
+To assess correlations with the IAS pairings, scores were grouped across personality dimensions due to the overlap among these traits (with the exception of Honesty-Humility). 
+On average, IAS pairings were positively associated with most personality dimensions, though these correlations were generally weak.
+The strongest correlation was observed between Conscientiousness and the Hungry/Thirsty pairing (r = 0.164).
+Both Honesty-Humility and Neuroticism were weakly and negatively correlated with the IAS pairings, with the highest correlations observed for the Hungry/Thirsty pairing (r = -0.217 and r = -0.200, respectively).
+
+#### Correlations with other measures
+
+<!-- PI -->
+
+The IAS was also correlated with primal world beliefs, as measured by the Primal Inventory [PI-18; @clifton2021brief], which assesses beliefs about the world being alive, good, safe, and enticing. 
+Items that evaluate neutral beliefs about the hierarchical order of importance in the world (i.e., hierarchical), as well as beliefs about the comprehensibility of most things and situations (i.e., understandable), and the belief that the world is characterized by flux (i.e., changing) were added as well.
+
+Overall, most primal beliefs show weak positive correlations with all pairings of the IAS. The strongest correlation is between the hierarchical belief and the Hungry/Thirsty pairing (r = 0.181). 
+Some beliefs, however, exhibit negative correlations with certain pairings. 
+These negative correlations range from r = -0.0940 between the changing belief and the Hungry/Thirsty pairing, to r = -0.00490 between the Enticing belief and the Itch/Bruise pairing.
+
+<!-- GCBS -->
+
+<!-- LIE -->
 

### 2025-02-12 analysis/study2.qmd
manuscript updated
started Internal reliability

@@
 ```{r}
+#| output: false
+
 library(gt)
@@
 ### ICQ
+
 ```{r}
@@
 names(df9)[str_detect(names(df9), "BFI_")]
+names(df10a)[str_detect(names(df10a), "IPIP6_")]
 
@@
   data,
+  make_cor(df7a, vars_intero, with = "NEO_FFI_SUMSCORE", component = "Personality") |>
+      mutate(var_Correlate = "Neuroticism"),
   make_cor(df9, vars_intero, with = "BFI_AGREEABLENESS", component="Personality") |>
@@
 
+## Internal Reliability
+
+### BPQ
+
+- sample df7c does not have individual BPQ items
+
+```{r}
+
+# BPQ 46 Items SV
+df2_BPQ <- df2 |> select(contains("BPQ ")) 
+df3_BPQ <- df3 |> select(contains("BPQ"), -contains("BPQ_"))
+
+# BPQ 26 items - awareness subscale
+
+df4_BPQ_A <- df4 |> select(contains("BPQ_"))
+
+# BPQ 12 items VSF
+df7a_BPQVSF <- df7b |> select(contains("BPQ_"), -BPQ_Sum)
+df8a_BPQVSF <- df8a |> select(contains("BPQ"), -BPQ_A)
+
+```
+
 ```{r}
@@
 
-# Alexithymia
 average_corr |>
@@
              max = max(mean_r))
-#BPQ
+
 average_corr |>
@@
 
-#MAIA
 average_corr |>
@@
              max = max(mean_r))
-#ICQ
+
 average_corr |>
@@
              max = max(mean_r))
-#Mood
+
 average_corr |>
@@
   group_by(var_Correlate) |>
+  summarise(min = min(mean_r),
+             max = max(mean_r))
+
+average_corr |>
+  filter(Component == "Maladaptive") |>
+  group_by(var_Correlate) |>
+  summarise(min = min(mean_r),
+             max = max(mean_r))
+
+average_corr |>
+  filter(Component == "Schizotypic") |>
+  group_by(var_Correlate) |>
+  summarise(min = min(mean_r),
+             max = max(mean_r))
+
+average_corr |>
+  filter(Component == "Autistic") |>
+  group_by(var_Correlate) |>
+  summarise(min = min(mean_r),
+             max = max(mean_r))
+
+average_corr |>
+  filter(Component == "Personality") |>
+  group_by(var_Correlate) |>
+  summarise(min = min(mean_r),
+             max = max(mean_r))
+
+average_corr |>
+  filter(Component == "World Beliefs") |>
+  # group_by(var_Correlate) |>
   summarise(min = min(mean_r),
@@
 
-Benefits of the IAS:
-- Straightforward and sensation-centered items
+Benefits of the IAS: - Straightforward and sensation-centered items
 
-Recommendations:
-- Remove Itch (redundant + issue in Chinese)
-- Use analog scales
+Recommendations: - Remove Itch (redundant + issue in Chinese) - Use analog scales
 
-Limitations:
-- Not much clear theorethical or empirical structure (small grouping of items)
-- Limited variability (clear mode at 4/5), very low prevalence of 5/5 responses.
-- Ambiguous items which grouping depends on the context (and its awareness)
-  - E.g., heart beating fast, vomit when nauseaous
-- Few items for some modalities (e.g., 1 for heart)
-- Positive phrasing: benefits but also might exacerbate positivity bias (and thus unidimensionality)
+Limitations: - Not much clear theorethical or empirical structure (small grouping of items) - Limited variability (clear mode at 4/5), very low prevalence of 5/5 responses.
+- Ambiguous items which grouping depends on the context (and its awareness) - E.g., heart beating fast, vomit when nauseaous - Few items for some modalities (e.g., 1 for heart) - Positive phrasing: benefits but also might exacerbate positivity bias (and thus unidimensionality)
 

### 2025-02-12 paper/1_Initial/manuscript.qmd
started Internal reliability

@@
 The BPQ-VSF comprises of 12 items from the body awareness subscale of the BPQ-SF.
-In this study, all scores assessing these two dimensions were grouped together, hence no disitintion is made between awareness measured with the BPQ-SF and the BPQ-VSF.
+In this study, all scores assessing these two dimensions were grouped together, hence no disitintion is made between awareness measured with the BPQ-SF and the BPQ-VSF, or eith scores obtained only using the awareness subscale.
 

### 2025-02-13 paper/1_Initial/manuscript.qmd
updated manuscript

@@
 Items that evaluate neutral beliefs about the hierarchical order of importance in the world (i.e., hierarchical), as well as beliefs about the comprehensibility of most things and situations (i.e., understandable), and the belief that the world is characterized by flux (i.e., changing) were added as well.
+The scale contains 18 items ranging from 5 (Strongly agree) to 0 (strongly disagree).
 
@@
 
+The Generic Conspiracist Beliefs Scale [GCBS; @brotherton2013measuring] was used to assess five facets of conspiracy beliefs: Extraterrestrial, Global Conspiracies, Government Malfeasance, Information Control, and Personal Wellbeing.
+The scale comprises 15 items rated on a 5-point Likert scale, ranging from definitely not true (1) to definitely true (5).
+
+Overall, the GCBS showed a weak but positive correlation with all facets of the IAS, with the strongest correlation observed between Global Conspiracies and Hungry/Thirsty (r = 0.140). 
+Negative correlations were found within the Global Conspiracies, Extraterrestrial, and Information Control facets, though these were small, ranging from r = -0.0101 to r = -0.0167.
+
 <!-- LIE -->
+
+Lastly, the Lying Profile Questionnaire [LIE; @makowski2023structure] a 16 item visual analog scale was used to assess 4 dispositional lying simensions: ability; negativity, contextuality, and frequency.
+
+Overall, most lying profile dimensions show weak correlations with IAS pairings. 
+Ability exhibits primarily weak positive correlations, with the strongest observed for Wind/Burp (r = 0.082).
+In contrast, Frequency tends to show weak negative correlations, ranging from Wind/Burp (r = -0.062) to Muscles/Pain (r = -0.088).
+Contextuality displays mixed correlations, with Itch/Bruise showing the strongest negative association (r = -0.127), while Urinate/Defecate has a small positive correlation (r = 0.045).
+Finally, Negativity is consistently positively correlated with all pairings, with the strongest relationship found for Hungry/Thirsty (r = 0.090).
 

### 2025-02-13 paper/1_Initial/manuscript.tex
updated manuscript

@@
 \makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\newsavebox\pandoc@box
+\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
+  \sbox\pandoc@box{#1}%
+  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
+  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
+  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
+  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
+  \else\usebox{\pandoc@box}%
+  \fi%
+}
 % Set default figure placement to htbp
-\makeatletter
 \def\fps@figure{htbp}
@@
 
-\par{     \begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colback=white, breakable, opacityback=0, leftrule=.75mm, arc=.35mm, bottomrule=.15mm, toprule=.15mm, left=2mm, colframe=quarto-callout-note-color-frame]
+\par{     \begin{tcolorbox}[enhanced jigsaw, colback=white, colframe=quarto-callout-note-color-frame, leftrule=.75mm, opacityback=0, arc=.35mm, toprule=.15mm, breakable, rightrule=.15mm, left=2mm, bottomrule=.15mm]
 
@@
 \begin{center}
-\includegraphics[width=0.2\textwidth,height=\textheight]{manuscript_files/mediabag/ReBeL_LogoOnly_hu114.png}
+\includegraphics[width=0.2\linewidth,height=\textheight,keepaspectratio]{manuscript_files/mediabag/ReBeL_LogoOnly_hu114.png}
 \end{center}  Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows: Ana
@@
 
-\includegraphics[width=6.4in,height=\textheight]{figures/MeasuringInteroception.jpg}
+\includegraphics[width=6.4in,height=\textheight,keepaspectratio]{figures/MeasuringInteroception.jpg}
 
@@
 
-\includegraphics[width=6.67in,height=\textheight]{figures/Figure1.png}
+\includegraphics[width=6.67in,height=\textheight,keepaspectratio]{figures/Figure1.png}
 
@@
 were grouped together, hence no disitintion is made between awareness
-measured with the BPQ-SF and the BPQ-VSF.
+measured with the BPQ-SF and the BPQ-VSF, or eith scores obtained only
+using the awareness subscale.
 
@@
 
-The PHQ-15 also showed its strongest correlation with the Hungry/Thirsty
-pair (r = -0.241) but was, on average, weakly and negatively correlated
-with all other IAS pairings.
-
-Lastly, the MSI-BPD also showed its strongest negative correlation with
-the Hungry/Thirsty pair (r = -0.140) and was negatively correlated with
-all other pairings, except for Cough/Sneeze, which showed a slight
-positive correlation (r = 0.0219).
+The PHQ-15 is a 15-item questionnaire that assesses somatic symptoms on
+a 3-point scale (e.g., back pain). It exhibited its strongest
+correlation with the Hungry/Thirsty pair (r = -0.241) and, on average,
+showed weak negative correlations with all other IAS pairings.
+
+Lastly, the MSI-BPD is a 10-item questionnaire used to assess
+personality disorder, where items are rated on a dichotomous scale of 1
+(present) and 0 (absent). The MSI-BPD also showed its strongest negative
+correlation with the Hungry/Thirsty pair (r = -0.140) and was negatively
+correlated with all other pairings, except for Cough/Sneeze, which
+showed a slight positive correlation (r = 0.0219).
+
+\paragraph{Correlations with psychopathology
+measures.}\label{correlations-with-psychopathology-measures}
+
+Maladaptive personality traits were assessed using the Personality
+Inventory for DSM-5 Short Form {[}PID-5-SF; Thimm et al.
+(\citeproc{ref-thimm2016personality}{2016}){]}, which measures five
+domains: disinhibition, antagonism, detachment, negative affect, and
+psychoticism. The scale consists of 25 items rated on a 4-point Likert
+scale, ranging from 0 (very false or often false) to 3 (very true or
+often true).
+
+On average, all maladaptive personality traits assessed by the PID-5-SF
+were weakly and negatively correlated with IAS pairings. The strongest
+correlation was observed between the psychoticism dimension and the
+Muscle/Pain pairing (r = -0.173).
+
+Schizotypy was assessed using the Schizotypal Personality Questionnaire
+-- Brief Revised Updated (SPQ-BRU; Davidson et al.
+(\citeproc{ref-davidson2016schizotypal}{2016})), which consists of 32
+items rated on a 5-point Likert scale ranging from strongly agree to
+strongly disagree. This questionnaire evaluates four primary dimensions:
+cognitive-perceptual (positive), interpersonal (negative), disorganized,
+and social anxiety. These dimensions are further divided into nine
+secondary factors: constricted affect, eccentricity, magical thinking,
+lack of close friends, odd speech, referential thinking, social anxiety,
+suspiciousness, and unusual perceptions.
+
+On average, all nine factors were weakly and negatively correlated with
+IAS pairings, with correlations ranging from r = -0.170 (between lack of
+close friends and Muscles/Pain) to r = 0.102 (between magical thinking
+and Itch/Bruise).
+
+The short version of the Autism-Spectrum Quotient (ASQ-Short; Hoekstra
+et al., 2011) was used to assess five autistic traits: social skills,
+adherence to routines, cognitive flexibility (switching), imagination,
+and patterns/numbers. The questionnaire consists of 28 items rated on a
+4-point Likert scale, ranging from 1 (definitely agree) to 4 (definitely
+disagree).
+
+Overall, all pairings were weakly and negatively correlated with the ASQ
+dimensions, except for the Itch/Bruise and Heart/Breathing pairings,
+which showed weak positive correlations with the patterns/numbers trait
+(r = 0.184 and r = 0.038, respectively). The strongest correlation was
+observed between the imagination trait and the Wind/Burp pairing (r =
+-0.218).
+
+\paragraph{Correlations with personality
+measures.}\label{correlations-with-personality-measures}
+
+The Big Five Inventory-Short Form {[}BFI-S; Lang et al.
+(\citeproc{ref-lang2011short}{2011}){]} and the Mini International
+Personality Item Pool {[}Mini-IPIP6; Sibley et al.
+(\citeproc{ref-sibley2011mini}{2011}){]} were used to assess general
+personality traits. The BFI-S consists of 15 items rated on a 7-point
+Likert scale, ranging from 1 (strongly disagree) to 7 (strongly agree),
+measuring five personality factors: Openness, Conscientiousness,
+Extraversion, Agreeableness, and Neuroticism. The Mini-IPIP6 assesses
+six personality traits---Extraversion, Agreeableness, Conscientiousness,
+Neuroticism, Openness, and Honesty-Humility---using 24 items. While this
+questionnaire is typically scored on a 7-point Likert scale from 1 (very
+inaccurate) to 7 (very accurate), an analogous scale was used in the
+respective sample. Lastly, the Neuroticism subscale of the NEO
+Five-Factor Inventory {[}Neo-FFI; Costa and McCrae
+(\citeproc{ref-costa1992normal}{1992}){]} was used to assess
+Neuroticism, consisting of 12 items rated on a 5-point Likert scale from
+1 (strongly disagree) to 5 (strongly agree).
+
+To assess correlations with the IAS pairings, scores were grouped across
+personality dimensions due to the overlap among these traits (with the
+exception of Honesty-Humility). On average, IAS pairings were positively
+associated with most personality dimensions, though these correlations
+were generally weak. The strongest correlation was observed between
+Conscientiousness and the Hungry/Thirsty pairing (r = 0.164). Both
+Honesty-Humility and Neuroticism were weakly and negatively correlated
+with the IAS pairings, with the highest correlations observed for the
+Hungry/Thirsty pairing (r = -0.217 and r = -0.200, respectively).
+
+\paragraph{Correlations with other
+measures.}\label{correlations-with-other-measures}
+
+The IAS was also correlated with primal world beliefs, as measured by
+the Primal Inventory {[}PI-18; J. D. Clifton and Yaden
+(\citeproc{ref-clifton2021brief}{2021}){]}, which assesses beliefs about
+the world being alive, good, safe, and enticing. Items that evaluate
+neutral beliefs about the hierarchical order of importance in the world
+(i.e., hierarchical), as well as beliefs about the comprehensibility of
+most things and situations (i.e., understandable), and the belief that
+the world is characterized by flux (i.e., changing) were added as well.
+The scale contains 18 items ranging from 5 (Strongly agree) to 0
+(strongly disagree).
+
+Overall, most primal beliefs show weak positive correlations with all
+pairings of the IAS. The strongest correlation is between the
+hierarchical belief and the Hungry/Thirsty pairing (r = 0.181). Some
+beliefs, however, exhibit negative correlations with certain pairings.
+These negative correlations range from r = -0.0940 between the changing
+belief and the Hungry/Thirsty pairing, to r = -0.00490 between the
+Enticing belief and the Itch/Bruise pairing.
+
+The Generic Conspiracist Beliefs Scale {[}GCBS; Brotherton et al.
+(\citeproc{ref-brotherton2013measuring}{2013}){]} was used to assess
+five facets of conspiracy beliefs: Extraterrestrial, Global
+Conspiracies, Government Malfeasance, Information Control, and Personal
+Wellbeing. The scale comprises 15 items rated on a 5-point Likert scale,
+ranging from definitely not true (1) to definitely true (5).
+
+Overall, the GCBS showed a weak but positive correlation with all facets
+of the IAS, with the strongest correlation observed between Global
+Conspiracies and Hungry/Thirsty (r = 0.140). Negative correlations were
+found within the Global Conspiracies, Extraterrestrial, and Information
+Control facets, though these were small, ranging from r = -0.0101 to r =
+-0.0167.
+
+Lastly, the Lying Profile Questionnaire {[}LIE; Makowski, Pham, et al.
+(\citeproc{ref-makowski2023structure}{2023}){]} a 16 item visual analog
+scale was used to assess 4 dispositional lying simensions: ability;
+negativity, contextuality, and frequency.
+
+Overall, most lying profile dimensions show weak correlations with IAS
+pairings. Ability exhibits primarily weak positive correlations, with
+the strongest observed for Wind/Burp (r = 0.082). In contrast, Frequency
+tends to show weak negative correlations, ranging from Wind/Burp (r =
+-0.062) to Muscles/Pain (r = -0.088). Contextuality displays mixed
+correlations, with Itch/Bruise showing the strongest negative
+association (r = -0.127), while Urinate/Defecate has a small positive
+correlation (r = 0.045). Finally, Negativity is consistently positively
+correlated with all pairings, with the strongest relationship found for
+Hungry/Thirsty (r = 0.090).
 
@@
 
-{\centering \includegraphics[width=9.48958in,height=\textheight]{figures/clipboard-1619164537.png}
+{\centering \includegraphics[width=9.48958in,height=\textheight,keepaspectratio]{figures/clipboard-1619164537.png}
 
@@
 This contrasts with previous research suggesting associations between
-interoception and deception (\citeproc{ref-makowski2023a}{Makowski et
-al., 2023}), warranting further investigation.
+interoception and deception (\citeproc{ref-makowski2023a}{Makowski, Lau,
+et al., 2023}), warranting further investigation.
 
@@
 needed to determine whether world beliefs, which shape our perception of
-reality (\citeproc{ref-clifton2020}{Clifton, 2020}), are meaningfully
-connected to interoception.
+reality (\citeproc{ref-clifton2020}{J. D. W. Clifton, 2020}), are
+meaningfully connected to interoception.
 
@@
 
+\bibitem[\citeproctext]{ref-brotherton2013measuring}
+Brotherton, R., French, C. C., \& Pickering, A. D. (2013). Measuring
+belief in conspiracy theories: The generic conspiracist beliefs scale.
+\emph{Frontiers in Psychology}, \emph{4}, 279.
+
 \bibitem[\citeproctext]{ref-cabrera2018assessing}
@@
 \url{https://doi.org/10.3389/fpsyg.2020.01145}
+
+\bibitem[\citeproctext]{ref-clifton2021brief}
+Clifton, J. D., \& Yaden, D. B. (2021). Brief measures of the four
+highest-order primal world beliefs. \emph{Psychological Assessment},
+\emph{33}(12), 1267.
+
+\bibitem[\citeproctext]{ref-costa1992normal}
+Costa, P. T., \& McCrae, R. R. (1992). Normal personality assessment in
+clinical practice: The NEO personality inventory. \emph{Psychological
+Assessment}, \emph{4}(1), 5.
+
+\bibitem[\citeproctext]{ref-davidson2016schizotypal}
+Davidson, C. A., Hoffman, L., \& Spaulding, W. D. (2016). Schizotypal
+personality questionnaire--brief revised (updated): An update of norms,
+factor structure, and item content in a large non-clinical young adult
+sample. \emph{Psychiatry Research}, \emph{238}, 345--355.
 
@@
 
+\bibitem[\citeproctext]{ref-lang2011short}
+Lang, F. R., John, D., Lüdtke, O., Schupp, J., \& Wagner, G. G. (2011).
+Short assessment of the big five: Robust across survey methods except
+telephone interviewing. \emph{Behavior Research Methods}, \emph{43},
+548--567.
+
 \bibitem[\citeproctext]{ref-lin2023}
@@
 
+\bibitem[\citeproctext]{ref-makowski2023structure}
+Makowski, D., Pham, T., Lau, Z. J., Raine, A., \& Chen, S. A. (2023).
+The structure of deception: Validation of the lying profile
+questionnaire. \emph{Current Psychology}, \emph{42}(5), 4001--4016.
+
 \bibitem[\citeproctext]{ref-mehling2018multidimensional}
@@
 
+\bibitem[\citeproctext]{ref-sibley2011mini}
+Sibley, C. G., Luyten, N., Purnomo, M., Mobberley, A., Wootton, L. W.,
+Hammond, M. D., Sengupta, N., Perry, R., West-Newman, T., Wilson, M. S.,
+et al. (2011). The mini-IPIP6: Validation and extension of a short
+measure of the big-six factors of personality in new zealand. \emph{New
+Zealand Journal of Psychology}, \emph{40}(3).
+
 \bibitem[\citeproctext]{ref-solanoluxf3pez2018}
@@
 \emph{Biological Psychology}, \emph{168}, 108262.
+
+\bibitem[\citeproctext]{ref-thimm2016personality}
+Thimm, J. C., Jordan, S., \& Bach, B. (2016). The personality inventory
+for DSM-5 short form (PID-5-SF): Psychometric properties and association
+with big five traits and pathological beliefs in a norwegian population.
+\emph{BMC Psychology}, \emph{4}, 1--11.
 

### 2025-02-13 paper/1_Initial/manuscript.qmd
works

@@
       ::: {.callout-note icon=false appearance="simple"}
-      :::
       This preprint is a non-peer-reviewed work from the [**Reality Bending Lab**](https://realitybending.github.io/).
       ![](https://realitybending.github.io/media/ReBeL_LogoOnly_hu11484441381606756729.png){width=20% fig-align="center"}
+      :::
 abstract: |
@@
 #| fig-cap: "Different ways in which interoception can be measured."
-#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
-## | out-width: "100%"
+#| apa-twocolumn: false  # A Figure Spanning Two Columns When in Journal Mode
+#| out-width: "100%"
 
@@
 To qualify for inclusion, papers needed to (1) provide accessible data in open-access, (2) employ the IAS as a measure, and (3) report individual IAS items scores.
+We also included the data of two unpublished (but already open-access) studies.
 A total of 10 studies was included (see **Table 1**).
-We also included the data of two unpublished (but already open-access) studies from the authors and one from another researcher.
-The total N participants was 32,214 participants (*Mean* = 48.6 years, *SD* = 13.1, 71.6% Female).
+
+The total number of participants was 32,214 participants (Mean = 48.6 $\pm$ 13.1, 71.6\% Female).
 
@@
 
-To examine the factor structure of the IAS, a two-step approach was employed.
+To examine the factor structure of the IAS, a two-steps approach was employed.
 First, Exploratory Graph Analysis (EGA), was used to estimate the dimensions via network estimation and community detection, alongside assessing the stability of dimensions and items using the bootstrapping techniques [@golino2017exploratory].

### 2025-02-13 paper/1_Initial/manuscript.qmd
consistency

@@
 
-Various measures of interoception have been developed (see @fig-measures), forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking vs.
-questionnaires and subjective scales involving a metacognitive reflection), "explicit" and "implicit" paradigms (i.e., directing participants' awareness and attention to interoceptive processes *vs.* measuring interoception unbeknownst to them), various interoceptive modalities (e.g., cardioception, respiroception, gastroception) and theoretical dimensions (e.g., accuracy, sensitivity, awareness).
+Various measures of interoception have been developed (see @fig-measures), forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking *vs.* questionnaires and subjective scales involving a metacognitive reflection), "explicit" and "implicit" paradigms (i.e., directing participants' awareness and attention to interoceptive processes *vs.* measuring interoception unbeknownst to them), various interoceptive modalities (e.g., cardioception, respiroception, gastroception) and theoretical dimensions (e.g., accuracy, sensitivity, awareness).
 While there is no consensus as to which particular approach provides the most accurate and "pure" measure of interoception and interoceptive abilities (assuming it is a unidimensional construct), it is instead plausible that each measure has strengths and limitations, and a utility dependent on the context and goal at hand [@jahedi2014].
@@
 
-The use of subjective self-report questionnaires to measure deeply embodied functions might seem paradoxical.
-However, recent redefinitions of interoception emphasize the role of high-level and metacognitive elaboration of interoceptive information.
+Although the use of subjective self-report questionnaires to measure deeply embodied functions might seem paradoxical at first, recent redefinitions of interoception emphasize the role of high-level and metacognitive elaboration of interoceptive information.
 These redefinitions provide theoretical grounding to support the idea that some facets of interoception, including participants' metacognitive beliefs, can be assessed subjectively [@khalsa2018interoception; @suksasilp2022towards].
+
 This approach offers useful and interesting measures [@murphy2019; @lin2023].

### 2025-02-13 paper/1_Initial/manuscript.qmd
uninformative  sentence
reorganize

@@
 These redefinitions provide theoretical grounding to support the idea that some facets of interoception, including participants' metacognitive beliefs, can be assessed subjectively [@khalsa2018interoception; @suksasilp2022towards].
-
-This approach offers useful and interesting measures [@murphy2019; @lin2023].
-
 <!-- lack of correlation between objective and subjective measures + lack of correlation between self-report measures-->
-
-The notion that self-reports might not reflect the same processes as other interoception measures is important to contextualize the apparent lack of convergence between measures in the field [@desmedt2022measures].
-While few studies have explored the correlation between objective interoceptive measures,  such as the Heartbeat Counting Task [HCT, @schandry1981heart] and the Heartbeat Detection Task [HDT, @kleckner2015methodological], and correspondent self-report measures, existing findings typically show weak or no correlations [e.g., task-based accuracy vs.
-self-reported accuracy, @murphy2019; @brand2023].
+Moreover, the notion that self-reports might not reflect the same processes as other interoception tasks might be important to contextualize the apparent lack of convergence between measures in the field [@desmedt2022measures].
+For instance, existing findings typically show weak or no correlations between questionnaires and objective measures [including for measures of the same theorethical dimensions, e.g., task-based accuracy vs.
+self-reported accuracy, @murphy2019; @brand2023], such as the Heartbeat Counting Task [HCT, @schandry1981heart] and the Heartbeat Detection Task [HDT, @kleckner2015methodological].
 

### 2025-02-13 paper/1_Initial/manuscript.qmd
rephrase

@@
 These redefinitions provide theoretical grounding to support the idea that some facets of interoception, including participants' metacognitive beliefs, can be assessed subjectively [@khalsa2018interoception; @suksasilp2022towards].
-<!-- lack of correlation between objective and subjective measures + lack of correlation between self-report measures-->
 Moreover, the notion that self-reports might not reflect the same processes as other interoception tasks might be important to contextualize the apparent lack of convergence between measures in the field [@desmedt2022measures].
@@
 self-reported accuracy, @murphy2019; @brand2023], such as the Heartbeat Counting Task [HCT, @schandry1981heart] and the Heartbeat Detection Task [HDT, @kleckner2015methodological].
+Perhaps more surprisingly, low correlations have been observed even among questionnaires, suggesting the targeting of different facets related to interoception.
 
-Even among self-report measures low correlations have been observed, suggesting that these measures, while group in the same umbrella term of self-report assess different facets of interoception. 
-A recent systematic review by @desmedt2022measures examined whether various questionnaires designed to assess "interoceptive sensibility" truly measure the same construct. 
-Notably, @garfinkel2015knowing defines interoceptive sensibility as the self-reported tendency to focus on and detect internal sensations, whereas @khalsa2018interoception defines it more narrowly, excluding the ability to detect these signals.
-According to @desmedt2022measures, most authors adopt the latter definition.
-The review found that these questionnaires measure related but distinct constructs, leading researchers to mistakenly treating them as equivalent measures of interoceptive sensibility. 
-A better understanding of what is being measured with different questionnaires and dimensions, as well as their potential overlaps with other constructs (e.g., alexithymia, body awareness), is thus needed to clarify the role of self-reports in the assessment of interoception.
+One striking example concerns the assessment of "interoceptive sensibility", defined as the self-reported tendency to focus on and detect internal sensations [@garfinkel2015knowing], or more narrowly as the subjective ability to focus on interoceptive signals [@khalsa2018interoception].
+**TODO: ANA check if the definitions are correct**.
+A recent systematic review suggested that various questionnaires [**WHICH ONES**] designed to assess this dimension actually measure distinct constructs, leading researchers to mistakenly treating them as equivalent measures [@desmedt2022measures].
+This underlines the need for a more comprehensive understanding of what is being measured with different questionnaires and dimensions, as well as their potential overlaps with other constructs (e.g., alexithymia, body awareness).
 
@@
 A recently developed scale with a rapidly growing popularity is the Interoceptive Accuracy Scale [IAS, @murphy2019].
-The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological modality such as respiration (*"I can always accurately perceive when I am breathing fast"*), heart (e.g *"I can always accurately perceive when my heart is beating fast"*), skin (e.g *"I can always accurately perceive when something is going to be ticklish"*), arousal or bodily functions like coughing (e.g *"I can always accurately perceive when I am going to cough"*) or urinating (e.g.
-*"I can always accurately perceive when I need to urinate"*).
+The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological modality such as respiration (*"I can always accurately perceive when I am breathing fast"*), heart (*"I can always accurately perceive when my heart is beating fast"*), skin (*"I can always accurately perceive when something is going to be ticklish"*), arousal or bodily functions like coughing (*"I can always accurately perceive when I am going to cough"*) or urinating (*"I can always accurately perceive when I need to urinate"*).
 Interestingly, the IAS' statements are about specific interoceptive behaviours, which is a notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012; MAIA-2, @mehling2018multidimensional], which contains more general and metacognitive items (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*).

### 2025-02-13 paper/1_Initial/manuscript.qmd
Update manuscript.qmd

@@
 The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological modality such as respiration (*"I can always accurately perceive when I am breathing fast"*), heart (*"I can always accurately perceive when my heart is beating fast"*), skin (*"I can always accurately perceive when something is going to be ticklish"*), arousal or bodily functions like coughing (*"I can always accurately perceive when I am going to cough"*) or urinating (*"I can always accurately perceive when I need to urinate"*).
-Interestingly, the IAS' statements are about specific interoceptive behaviours, which is a notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012; MAIA-2, @mehling2018multidimensional], which contains more general and metacognitive items (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*).
+Notably, the IAS' statements are about specific interoceptive behaviours, which is a notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012; MAIA-2, @mehling2018multidimensional], which contains more general and metacognitive items (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*), as well as dimensions related to attention regulation (e.g., Not-distracting) or emotion regulation (e.g., Not-worrying).
 

### 2025-02-13 paper/1_Initial/manuscript.qmd
Update manuscript.qmd

@@
 
-Although the original validation study suggested a two-factor structure for the IAS, the authors underline its acceptable but imperfect fit [@murphy2019, p.
+Although the original validation study suggested a two-factor structure for the IAS, reflecting the perception of [**general?**] interoceptive signals, and that of signals that may be difficult to perceive solely through interoceptive information.
+However, the authors underline its acceptable but imperfect fit [@murphy2019, p.
 127], calling on further investigation of the scale's factor structure.
-Notably, the authors did not define these factors, as no clear explanations were evident.
-They suggested that the first factor reflects the perception of interoceptive signals, while the second pertains to signals that may be difficult to perceive solely through interoceptive information.
 

### 2025-02-17 paper/1_Initial/manuscript.qmd
update @AnafNeves

@@
 Although the original validation study suggested a two-factor structure for the IAS, reflecting the perception of [**general?**] interoceptive signals, and that of signals that may be difficult to perceive solely through interoceptive information.
-However, the authors underline its acceptable but imperfect fit [@murphy2019, p.
-127], calling on further investigation of the scale's factor structure.
-
-**note to dom**:@morin2016 is a methodological paper on ESEM
-
-Other follow-up studies using confirmatory factor analysis (CFA) and structural modeling have identified different optimal solutions.
-Some studies, like @brand2023, reported a 1-factor solution, while @lin2023 and @campos2021 found bifactor solutions - one general factor and a set of lower-level factors [@rodriguez2016evaluating] - to be the best fit.
-Notably, the only other study to report a 2-factor solution was conducted by @koike2023, who performed an Exploratory Factor Analysis (EFA) assuming 2 factors to align with the findings from the original validation paper.
-
+The authors however underlined its acceptable but imperfect fit [@murphy2019, p. 127], and several follow-up studies have indeed identified different optimal solutions. 
+For instance, @brand2023 and @golino2017exploratory (the latter using a new approach to structure analysis, Exploratory Graph Analysis), reported a 1-factor solution, while @lin2023 and @campos2021 found bifactor solutions - one general factor above a set of lower-level factors [@rodriguez2016evaluating] - to be the best fit.
 Discussions have also been focused on specific items.
@@
 119).
-@lin2023 also highlights their correlation analysis, showing five locally dependent pairs and three items (touch, blood sugar, bruise) with exceptionally high difficulty and low discrimination.
-Additionally, @campos2021 reported "tickle" to be the only item that reflected more specific factors than the general factor.
-Interestingly, @lin2023 reported that all items of the IAS grouped together using a new approach, Exploratory Graph Analysis [EGA, @golino2017exploratory], to assess convergent and discriminant validity, providing further evidence for unidimensionality.
+@lin2023 also highlights their correlation analysis, showing five locally dependent pairs and three items (touch, blood sugar, bruise) with exceptionally high difficulty and low discrimination, and @campos2021 reported "tickle" to be the only item that reflected more specific factors than the general factor.
+Localization issues also arisen with two items, **TODO** (talk about chinese stuff)
+
+<!-- Notably, the only other study to report a 2-factor solution was conducted by @koike2023, who performed an Exploratory Factor Analysis (EFA) assuming 2 factors to align with the findings from the original validation paper.
+-->
+**TODO: how did koike2023 interpret the two factors? Do they say?**
 
@@
 
-The IAS has naturally been compared to other interoception-related scales, and shows a positive correlations with most facets of the MAIA [@mehling2018multidimensional], except for the Non-Distracting and Not-Worrying subscales [@brand2023].
+Regarding its validity, the IAS has naturally been compared to other interoception-related measures, and shows a positive correlations with most facets of the MAIA [@mehling2018multidimensional], except for the Not-Distracting and Not-Worrying subscales [@brand2023] - which were highlighted previously as related to non-interoceptive abilities [**do we have a ref to say that?
+will also be useful for our MINT paper to back up our claims that these 2 dims are something else**].
 Interestingly, findings on the correlation between the IAS and the body awareness dimension of the Body Perception Questionnaire [BPQ-A, @porges1993body] have been mixed: some studies report small positive correlations [@brand2023; @campos2021; @koike2023], while others find small negative correlations [@lin2023] or no correlation at all [@murphy2019].
@@
 Interestingly, the IAS and the IATS supposedly measure two different interoceptive processes (i.e., accuracy and attention, respectively) which contradict @murphy2019 proposed 2x2 framework.
-
-<!-- TO BE COMPLETED -->
+**TODO: how so?
+Elaborate**
 
@@
 
-While assessing the validity of an interoception scale can be conceived as theoretically challenging, several measures have been used to assess convergent validity for the the IAS, including expected negative associations with alexithymia [@brand2023; @koike2023; @campos2021; @murphy2019; @lin2023], somatic symptoms [@brand2023; @koike2023; @lin2023], depressive symptoms [@brand2023; @koike2023; @lin2023], anxiety [@brand2023], neuroticism [@brand2023] and self-esteem [@murphy2019].
+While assessing the predictive validity of an interoception scale can be conceived as theoretically challenging, expected negative associations were observed between the IAS and alexithymia [@brand2023; @koike2023; @campos2021; @murphy2019; @lin2023], somatic symptoms [@brand2023; @koike2023; @lin2023], depressive symptoms [@brand2023; @koike2023; @lin2023], anxiety [@brand2023], neuroticism [@brand2023] and self-esteem [@murphy2019].
+
+**TODO: can you update the fig. 1's box (assessmeent of related traits) to remove the question marks and put the the stronger interoception correlates**
+
 <!-- **anything else?**. TO BE COMPLETED -- to be determined -->
@@
 
-The current study aims at 1) clarifying the structure of the IAS with a meta-analytic approach that leverages existing data and contrast the traditional CFA/SEM factor-based analyses with network-based ones such as EGA;
+Given The current study aims at 1) clarifying the structure of the IAS with a meta-analytic approach that leverages existing data and contrast the traditional CFA/SEM factor-based analyses with network-based ones such as EGA;
 2) the second part will provide an overview of the dispositional correlates of the IAS, clarifying the pattern of associations which is key to better understand the nature, place and role of interoception questionnaires within a larger context.

### 2025-02-17 paper/1_Initial/manuscript.qmd
minor

@@
 
+<!-- 
+Garfinkel - sensibility-> Self-perceived dispositional tendency to be internally self-focused and interoceptively cognisant,
+Khalsa - sensibility -> Self-perceived tendency to focus on interoceptive stimuli (trait measure)
+ -->
+
+**todo**: reframe paragraph to reflect that review focus on looking at whether the self-report scales and interoceptive sensibility, which are both assessed with questionnaires tap onto a common or different construct
+
 One striking example concerns the assessment of "interoceptive sensibility", defined as the self-reported tendency to focus on and detect internal sensations [@garfinkel2015knowing], or more narrowly as the subjective ability to focus on interoceptive signals [@khalsa2018interoception].
-**TODO: ANA check if the definitions are correct**.
-A recent systematic review suggested that various questionnaires [**WHICH ONES**] designed to assess this dimension actually measure distinct constructs, leading researchers to mistakenly treating them as equivalent measures [@desmedt2022measures].
+A recent systematic review suggested that various questionnaires (e.g., MAIA, Body Perception Questionnaire, Body Awareness Questionnaire, Eating Disorder Inventory) designed to assess this dimension actually measure distinct constructs, leading researchers to mistakenly treating them as equivalent measures [@desmedt2022measures].
 This underlines the need for a more comprehensive understanding of what is being measured with different questionnaires and dimensions, as well as their potential overlaps with other constructs (e.g., alexithymia, body awareness).

### 2025-02-21 paper/1_Initial/manuscript.qmd
changes to script
@DominiqueMakowski changes have been made please check as there are some comments for you.

--- 2025-02-17 paper/1_Initial/manuscript.qmd
@@
 
-One striking example concerns the assessment of "interoceptive sensibility", defined as the self-reported tendency to focus on and detect internal sensations [@garfinkel2015knowing], or more narrowly as the subjective ability to focus on interoceptive signals [@khalsa2018interoception].
-**TODO: ANA check if the definitions are correct**.
-A recent systematic review suggested that various questionnaires [**WHICH ONES**] designed to assess this dimension actually measure distinct constructs, leading researchers to mistakenly treating them as equivalent measures [@desmedt2022measures].
-This underlines the need for a more comprehensive understanding of what is being measured with different questionnaires and dimensions, as well as their potential overlaps with other constructs (e.g., alexithymia, body awareness).
+<!-- 
+Garfinkel - sensibility-> Self-perceived dispositional tendency to be internally self-focused and interoceptively cognisant,
+Khalsa - sensibility -> Self-perceived tendency to focus on interoceptive stimuli (trait measure)
+Khalsa self-report scales -> The ability to reflect upon one’s autobiographical experiences of interoceptive states, make judgments about their outcomes, and describe them through verbal or motor responses.
+-->
+
+One striking example concerns the assessment of "interoceptive sensibility," defined as the self-reported tendency to focus on and detect internal sensations [@garfinkel2015knowing], or more narrowly as the subjective ability to focus on interoceptive signals [@khalsa2018interoception].
+A recent systematic review suggested that various questionnaires designed to assess this dimension actually measure distinct constructs, leading researchers to mistakenly treat them as equivalent measures [@desmedt2022measures].
+Notably, sensibility in this review also included self-report scales from @khalsa2018interoception's 8-facet model of interoception, which divides self-report measures into sensibility and self-report scales as the capacity to evaluate one's personal experiences of internal bodily states, assess their consequences, and express them through speech or movement.
+Some of the studies included the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012; MAIA-2, @mehling2018multidimensional], Body Perception Questionnaire [BPQ; @porges1993body], Private subscale of the Body Consciousness Questionnaire [PBCS, @miller1981consciousness], Body Awareness Questionnaire [BAQ, @shields1989body], and Eating Disorder Inventory [EDI, @garner1991eating; @garner1983].
+The inexistent to moderate correlations between these questionnaires underlines the need for a more comprehensive understanding of what is being measured with different questionnaires and dimensions, as well as their potential overlaps with other constructs (e.g., alexithymia, body awareness).
 
@@
 The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological modality such as respiration (*"I can always accurately perceive when I am breathing fast"*), heart (*"I can always accurately perceive when my heart is beating fast"*), skin (*"I can always accurately perceive when something is going to be ticklish"*), arousal or bodily functions like coughing (*"I can always accurately perceive when I am going to cough"*) or urinating (*"I can always accurately perceive when I need to urinate"*).
-Notably, the IAS' statements are about specific interoceptive behaviours, which is a notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012; MAIA-2, @mehling2018multidimensional], which contains more general and metacognitive items (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*), as well as dimensions related to attention regulation (e.g., Not-distracting) or emotion regulation (e.g., Not-worrying).
+Notably, the IAS' statements are about specific interoceptive behaviours, which is a notable difference with other popular interoception questionnaires, such as the MAIA-2, which contains more general and metacognitive items (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*), as well as dimensions related to attention regulation (e.g., Not-distracting) or emotion regulation (e.g., Not-worrying).
 
@@
 
-Although the original validation study suggested a two-factor structure for the IAS, reflecting the perception of [**general?**] interoceptive signals, and that of signals that may be difficult to perceive solely through interoceptive information.
+**note to dom**: review this. 
+1. yes I think they are general interoceptive signals (I added the items that loaded to both factors for Murphy's and Koike's validation)
+2. Do we want to add that lin created a short verison of the scale?
+3. Yes kioke  did named their factors
+
+Although the original validation study suggested a two-factor structure for the IAS, reflecting the perception of general interoceptive signals (i.e., urinate, hungry, defecate, thirsty, pain, heart, taste, breathing, temperature, mulscles, affective touch, vomit, sexual arousal), and that of signals that may be difficult to perceive solely through interoceptive information (i.e., itch, tickle, cough, burp, bruise, blood sugar, sneeze, wind).
 The authors however underlined its acceptable but imperfect fit [@murphy2019, p. 127], and several follow-up studies have indeed identified different optimal solutions. 
@@
 @lin2023 also highlights their correlation analysis, showing five locally dependent pairs and three items (touch, blood sugar, bruise) with exceptionally high difficulty and low discrimination, and @campos2021 reported "tickle" to be the only item that reflected more specific factors than the general factor.
-Localization issues also arisen with two items, **TODO** (talk about chinese stuff)
-
-<!-- Notably, the only other study to report a 2-factor solution was conducted by @koike2023, who performed an Exploratory Factor Analysis (EFA) assuming 2 factors to align with the findings from the original validation paper.
--->
-**TODO: how did koike2023 interpret the two factors? Do they say?**
+Localization issues also arose in @lin2023 validation of the IAS, where both "itch" and "tickle" correspond to the same Chinese character, leading to their collapse into a single item. 
+Notably, the only other study to report a 2-factor solution was conducted by @koike2023, who performed an Exploratory Factor Analysis (EFA) assuming 2 factors to align with the findings from the original validation paper.
+According to the authors, the first factor appears to reflect cutaneous sensations (e.g., itching, tickling, coughing, burping, affective touch, bruising, passing gas, sneezing, muscle sensations, sexual arousal, and taste), while the second factor seems to represent visceral sensations (e.g., urination, defecation, hunger, thirst, pain, breathing, fatigue/blood sugar, temperature, vomiting, and heartbeat).
 
@@
 
-Regarding its validity, the IAS has naturally been compared to other interoception-related measures, and shows a positive correlations with most facets of the MAIA [@mehling2018multidimensional], except for the Not-Distracting and Not-Worrying subscales [@brand2023] - which were highlighted previously as related to non-interoceptive abilities [**do we have a ref to say that?
-will also be useful for our MINT paper to back up our claims that these 2 dims are something else**].
+**Note to dom**: @ferentzi2021examining suggests that all MAIA dimensions, except for Not-Worrying and Not-Distracting, relate to a general interoceptive awareness factor.
+The low correlations of NW and ND with this general factor indicate that these dimensions do not contribute significantly to the measurement of general interoceptive awareness.
+Instead, NW appears to measure low emotionality or neuroticism, while ND does not capture a coherent underlying structure.
+
+Regarding its validity, the IAS has naturally been compared to other interoception-related measures, and shows a positive correlations with most facets of the MAIA [@mehling2018multidimensional], except for the Not-Distracting and Not-Worrying subscales [@brand2023] - which were highlighted previously as related to non-interoceptive abilities [@ferentzi2021examining]
 Interestingly, findings on the correlation between the IAS and the body awareness dimension of the Body Perception Questionnaire [BPQ-A, @porges1993body] have been mixed: some studies report small positive correlations [@brand2023; @campos2021; @koike2023], while others find small negative correlations [@lin2023] or no correlation at all [@murphy2019].
@@
 Lastly, small positive correlations have also been reported with the Interoceptive Attention Scale [IATS, @lin2023; @koike2023], though studies have also found no correlation between these measures [@gabriele2022dissociations].
-Interestingly, the IAS and the IATS supposedly measure two different interoceptive processes (i.e., accuracy and attention, respectively) which contradict @murphy2019 proposed 2x2 framework.
-**TODO: how so?
-Elaborate**
 
@@
 
-**TODO: can you update the fig. 1's box (assessmeent of related traits) to remove the question marks and put the the stronger interoception correlates**
+**TODO: can you update the fig. 1's box (assessmeent of related traits) to remove the question marks and put the the stronger interoception correlates** - as in with what?
 

### 2025-02-27 paper/1_Initial/manuscript.qmd
minor

@@
 
-Interoception is referred to the process of sensing, interpreting and integrating information pertaining to internal organs, such as the heart, the lungs or the gut [@khalsa2018].
+Interoception is referred to the process of sensing, interpreting and integrating information pertaining to internal organs, such as the heart, the lungs or the gut [@khalsa2018interoception].
 While recent research emphasizes a key role of interoception in a variety of processes (e.g., emotion regulation, decision making) and of outcomes (physical and psychological well being), the field remains clouded by concerns about how interoception is assessed.
@@
 A recent systematic review suggested that various questionnaires designed to assess this dimension actually measure distinct constructs, leading researchers to mistakenly treat them as equivalent measures [@desmedt2022measures].
-Notably, sensibility in this review also included self-report scales from @khalsa2018interoception's 8-facet model of interoception, which divides self-report measures into sensibility and self-report scales as the capacity to evaluate one's personal experiences of internal bodily states, assess their consequences, and express them through speech or movement.
+
+Notably, 'sensibility' in this review also included self-report scales based on @khalsa2018interoception's 8-facet model of interoception, which divides self-report measures into sensibility and self-report scales as the capacity to evaluate one's personal experiences of internal bodily states, assess their consequences, and express them through speech or movement.
 Some of the studies included the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012; MAIA-2, @mehling2018multidimensional], Body Perception Questionnaire [BPQ; @porges1993body], Private subscale of the Body Consciousness Questionnaire [PBCS, @miller1981consciousness], Body Awareness Questionnaire [BAQ, @shields1989body], and Eating Disorder Inventory [EDI, @garner1991eating; @garner1983].
@@
 The authors however underlined its acceptable but imperfect fit [@murphy2019, p. 127], and several follow-up studies have indeed identified different optimal solutions. 
-For instance, @brand2023 and @golino2017exploratory (the latter using a new approach to structure analysis, Exploratory Graph Analysis), reported a 1-factor solution, while @lin2023 and @campos2021 found bifactor solutions - one general factor above a set of lower-level factors [@rodriguez2016evaluating] - to be the best fit.
+For instance, @brand2023 reported a 1-factor solution, while @lin2023 and @campos2021 [the former using a new approach to structure analysis, Exploratory Graph Analysis; @golino2017exploratory] found bifactor solutions - one general factor above a set of lower-level factors [@rodriguez2016evaluating] - to be the best fit.
+
 Discussions have also been focused on specific items.

### 2025-02-27 paper/1_Initial/manuscript.qmd
minor

@@
 
-One striking example concerns the assessment of "interoceptive sensibility," defined as the self-reported tendency to focus on and detect internal sensations [@garfinkel2015knowing], or more narrowly as the subjective ability to focus on interoceptive signals [@khalsa2018interoception].
+One striking example concerns the assessment of "interoceptive sensibility" defined as the self-reported tendency to focus on and detect internal sensations [@garfinkel2015knowing], or more narrowly as the subjective ability to focus on interoceptive signals [@khalsa2018interoception].
 A recent systematic review suggested that various questionnaires designed to assess this dimension actually measure distinct constructs, leading researchers to mistakenly treat them as equivalent measures [@desmedt2022measures].
@@
 Notably, 'sensibility' in this review also included self-report scales based on @khalsa2018interoception's 8-facet model of interoception, which divides self-report measures into sensibility and self-report scales as the capacity to evaluate one's personal experiences of internal bodily states, assess their consequences, and express them through speech or movement.
-Some of the studies included the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012; MAIA-2, @mehling2018multidimensional], Body Perception Questionnaire [BPQ; @porges1993body], Private subscale of the Body Consciousness Questionnaire [PBCS, @miller1981consciousness], Body Awareness Questionnaire [BAQ, @shields1989body], and Eating Disorder Inventory [EDI, @garner1991eating; @garner1983].
+Some of the studies included the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012; MAIA-2, @mehling2018multidimensional], Body Perception Questionnaire [BPQ, @porges1993body], Private subscale of the Body Consciousness Questionnaire [PBCS, @miller1981consciousness], Body Awareness Questionnaire [BAQ, @shields1989body], and Eating Disorder Inventory [EDI; @garner1991eating, @garner1983].
 The inexistent to moderate correlations between these questionnaires underlines the need for a more comprehensive understanding of what is being measured with different questionnaires and dimensions, as well as their potential overlaps with other constructs (e.g., alexithymia, body awareness).
@@
 The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological modality such as respiration (*"I can always accurately perceive when I am breathing fast"*), heart (*"I can always accurately perceive when my heart is beating fast"*), skin (*"I can always accurately perceive when something is going to be ticklish"*), arousal or bodily functions like coughing (*"I can always accurately perceive when I am going to cough"*) or urinating (*"I can always accurately perceive when I need to urinate"*).
-Notably, the IAS' statements are about specific interoceptive behaviours, which is a notable difference with other popular interoception questionnaires, such as the MAIA-2, which contains more general and metacognitive items (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*), as well as dimensions related to attention regulation (e.g., Not-distracting) or emotion regulation (e.g., Not-worrying).
+Notably, the IAS' statements are about specific interoceptive behaviours, which is a distinct difference with other popular interoception questionnaires, such as the MAIA-2, which contains more general and metacognitive items (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*), as well as dimensions related to attention regulation (e.g., Not-distracting) or emotion regulation (e.g., Not-worrying).
 
@@
 
-**note to dom**: review this. 
-1. yes I think they are general interoceptive signals (I added the items that loaded to both factors for Murphy's and Koike's validation)
-2. Do we want to add that lin created a short verison of the scale?
-3. Yes kioke  did named their factors
+**note to dom review this.
+1.
+yes I think they are general interoceptive signals (I added the items that loaded to both factors for Murphy's and Koike's validation) 2.
+Do we want to add that lin created a short verison of the scale?
+3.
+Yes kioke  did named their factors**
 
@@
 The authors however underlined its acceptable but imperfect fit [@murphy2019, p. 127], and several follow-up studies have indeed identified different optimal solutions. 
-For instance, @brand2023 reported a 1-factor solution, while @lin2023 and @campos2021 [the former using a new approach to structure analysis, Exploratory Graph Analysis; @golino2017exploratory] found bifactor solutions - one general factor above a set of lower-level factors [@rodriguez2016evaluating] - to be the best fit.
+For instance, @brand2023 reported a 1-factor solution, while @lin2023 and @campos2021 [the former using a new approach to structure analysis, Exploratory Graph Analysis, @golino2017exploratory] found bifactor solutions - one general factor above a set of lower-level factors [@rodriguez2016evaluating] - to be the best fit.
 
@@
 @lin2023 also highlights their correlation analysis, showing five locally dependent pairs and three items (touch, blood sugar, bruise) with exceptionally high difficulty and low discrimination, and @campos2021 reported "tickle" to be the only item that reflected more specific factors than the general factor.
+
 Localization issues also arose in @lin2023 validation of the IAS, where both "itch" and "tickle" correspond to the same Chinese character, leading to their collapse into a single item. 
@@
 
-**Note to dom**: @ferentzi2021examining suggests that all MAIA dimensions, except for Not-Worrying and Not-Distracting, relate to a general interoceptive awareness factor.
+**Note to dom: @ferentzi2021examining suggests that all MAIA dimensions, except for Not-Worrying and Not-Distracting, relate to a general interoceptive awareness factor.
 The low correlations of NW and ND with this general factor indicate that these dimensions do not contribute significantly to the measurement of general interoceptive awareness.
-Instead, NW appears to measure low emotionality or neuroticism, while ND does not capture a coherent underlying structure.
+Instead, NW appears to measure low emotionality or neuroticism, while ND does not capture a coherent underlying structure.**
 
-Regarding its validity, the IAS has naturally been compared to other interoception-related measures, and shows a positive correlations with most facets of the MAIA [@mehling2018multidimensional], except for the Not-Distracting and Not-Worrying subscales [@brand2023] - which were highlighted previously as related to non-interoceptive abilities [@ferentzi2021examining]
+Regarding its validity, the IAS has naturally been compared to other interoception-related measures, and shows a positive correlations with most facets of the MAIA [@mehling2018multidimensional], except for the Not-Distracting and Not-Worrying subscales [@brand2023] - which were highlighted previously as related to non-interoceptive abilities [@ferentzi2021examining].
 Interestingly, findings on the correlation between the IAS and the body awareness dimension of the Body Perception Questionnaire [BPQ-A, @porges1993body] have been mixed: some studies report small positive correlations [@brand2023; @campos2021; @koike2023], while others find small negative correlations [@lin2023] or no correlation at all [@murphy2019].
 Small positive correlations have also been observed with the "observation" and "description" subscales of the Five Facet Mindfulness Questionnaire [FFMQ, @baer2006using; @brand2023; @koike2023], as well as with the "non-reactivity" and "acting with awareness" subscales [@koike2023].
-Additionally, the IAS has shown a positive correlation with the interoceptive awareness subscale of the Eating Disorder Inventory [@lin2023] and a negative correlation with the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia; @brand2023; @murphy2019].
-Lastly, small positive correlations have also been reported with the Interoceptive Attention Scale [IATS, @lin2023; @koike2023], though studies have also found no correlation between these measures [@gabriele2022dissociations].
+Additionally, the IAS has shown a positive correlation with the interoceptive awareness subscale of the Eating Disorder Inventory [@lin2023] and a negative correlation with the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia, @brand2023; @murphy2019].
+Lastly, small positive correlations have also been reported with the Interoceptive Attention Scale [IATS, @lin2023, @koike2023], though studies have also found no correlation between these measures [@gabriele2022dissociations].
 
@@
 
-Given The current study aims at 1) clarifying the structure of the IAS with a meta-analytic approach that leverages existing data and contrast the traditional CFA/SEM factor-based analyses with network-based ones such as EGA;
+The current study aims at 1) clarifying the structure of the IAS with a meta-analytic approach that leverages existing data and contrast the traditional CFA/SEM factor-based analyses with network-based ones such as EGA;
 2) the second part will provide an overview of the dispositional correlates of the IAS, clarifying the pattern of associations which is key to better understand the nature, place and role of interoception questionnaires within a larger context.

### 2025-02-28 paper/1_Initial/manuscript.qmd
changes to manuscript

@@
 
-Various measures of interoception have been developed (see @fig-measures), forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking *vs.* questionnaires and subjective scales involving a metacognitive reflection), "explicit" and "implicit" paradigms (i.e., directing participants' awareness and attention to interoceptive processes *vs.* measuring interoception unbeknownst to them), various interoceptive modalities (e.g., cardioception, respiroception, gastroception) and theoretical dimensions (e.g., accuracy, sensitivity, awareness).
-While there is no consensus as to which particular approach provides the most accurate and "pure" measure of interoception and interoceptive abilities (assuming it is a unidimensional construct), it is instead plausible that each measure has strengths and limitations, and a utility dependent on the context and goal at hand [@jahedi2014].
+<!-- Various measures of interoception have been developed (see @fig-measures), forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking *vs.* questionnaires and subjective scales involving a metacognitive reflection), "explicit" and "implicit" paradigms (i.e., directing participants' awareness and attention to interoceptive processes *vs.* measuring interoception unbeknownst to them), various interoceptive modalities (e.g., cardioception, respiroception, gastroception) and theoretical dimensions (e.g., accuracy, sensitivity, awareness).
+-->
+
+<!-- While this is longer it breaks it down a bit more -->
+Various measures of interoception have been developed (see @fig-measures), combining different approaches, including both “objective” and “subjective” assessments—physiological tasks, such as  Heartbeat Counting Task [HCT, @schandry1981heart] or the Heartbeat Detection Task [HDT, @kleckner2015methodological], versus questionnaires and rating scales that require metacognitive reflection.
+A further distinction can be made between “explicit” and “implicit” paradigms, where explicit measures direct participants’ awareness toward interoceptive processes, while implicit measures assess interoception unbeknownst to them.
+Additionally, interoceptive measures vary across different modalities, such as cardioception, respiroception, and gastroception. 
+Finally, these measures assess various theoretical dimensions, including accuracy, sensitivity, awareness, and magnitude.
+While there is no consensus as to which particular approach provides the most accurate and "pure" measure of interoception and interoceptive abilities (assuming it is a unidimensional construct), it is instead plausible that each measure has strengths and limitations, and a utility dependent on the context and goal at hand [@jahedi2014; @Desmedt2023accuracy].
 
@@
 For instance, existing findings typically show weak or no correlations between questionnaires and objective measures [including for measures of the same theorethical dimensions, e.g., task-based accuracy vs.
-self-reported accuracy, @murphy2019; @brand2023], such as the Heartbeat Counting Task [HCT, @schandry1981heart] and the Heartbeat Detection Task [HDT, @kleckner2015methodological].
+self-reported accuracy, @murphy2019; @brand2023; @arslanova2022], such as the HCT and the HDT.
+Additionally, objective measures assessing the same interoceptive dimension, such as accuracy, either show no correlation [e.g., @brand2023] or only weak correlations [e.g., @hickman2020relationship].
 Perhaps more surprisingly, low correlations have been observed even among questionnaires, suggesting the targeting of different facets related to interoception.
@@
 
-One striking example concerns the assessment of "interoceptive sensibility" defined as the self-reported tendency to focus on and detect internal sensations [@garfinkel2015knowing], or more narrowly as the subjective ability to focus on interoceptive signals [@khalsa2018interoception].
-A recent systematic review suggested that various questionnaires designed to assess this dimension actually measure distinct constructs, leading researchers to mistakenly treat them as equivalent measures [@desmedt2022measures].
+One striking example concerns the assessment of interoceptive sensibility, which is broadly defined as the self-reported tendency to focus on and detect internal sensations [@garfinkel2015knowing], but more narrowly as the subjective tendency to focus on interoceptive signals, without necessarily implying detection ability [@khalsa2018interoception].
+A recent systematic review suggested that various questionnaires designed to assess interoceptive sensibility may, in fact, measure distinct constructs, leading researchers to treat them as equivalent despite overall low convergence [@desmedt2022measures].
 
-Notably, 'sensibility' in this review also included self-report scales based on @khalsa2018interoception's 8-facet model of interoception, which divides self-report measures into sensibility and self-report scales as the capacity to evaluate one's personal experiences of internal bodily states, assess their consequences, and express them through speech or movement.
-Some of the studies included the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012; MAIA-2, @mehling2018multidimensional], Body Perception Questionnaire [BPQ, @porges1993body], Private subscale of the Body Consciousness Questionnaire [PBCS, @miller1981consciousness], Body Awareness Questionnaire [BAQ, @shields1989body], and Eating Disorder Inventory [EDI; @garner1991eating, @garner1983].
-The inexistent to moderate correlations between these questionnaires underlines the need for a more comprehensive understanding of what is being measured with different questionnaires and dimensions, as well as their potential overlaps with other constructs (e.g., alexithymia, body awareness).
+Notably, this review adopted a broad definition of 'sensibility,' incorporating both interoceptive sensibility and interoceptive self-report scales, as described in @khalsa2018interoception's eight-facet model.
+In this framework, self-report measures are categorized into interoceptive sensibility and interoceptive self-report scales (i.e., the ability to evaluate one's personal experiences of internal bodily states, assess their consequences, and articulate them through speech or movement).
+Several widely used questionnaires were included in the review, such as the Multidimensional Assessment of Interoceptive Awareness [MAIA, @mehling2012; MAIA-2, @mehling2018multidimensional], the Body Perception Questionnaire [BPQ, @porges1993body], the Private subscale of the Body Consciousness Questionnaire [PBCS, @miller1981consciousness], the Body Awareness Questionnaire [BAQ, @shields1989body], and the Eating Disorder Inventory [EDI, @garner1991eating; @garner1983].
+The lack of correlations to moderate correlations among these questionnaires highlight the need for greater conceptual clarity regarding what each measure captures, how they relate to different dimensions of interoception, and their potential overlaps with other constructs, such as alexithymia and body awareness.
 

### 2025-03-03 paper/1_Initial/manuscript.qmd
changes to manuscript

@@
 <!-- While this is longer it breaks it down a bit more -->
-Various measures of interoception have been developed (see @fig-measures), combining different approaches, including both “objective” and “subjective” assessments—physiological tasks, such as  Heartbeat Counting Task [HCT, @schandry1981heart] or the Heartbeat Detection Task [HDT, @kleckner2015methodological], versus questionnaires and rating scales that require metacognitive reflection.
+Various measures of interoception have been developed (see @fig-measures), combining different approaches, including both “objective” and “subjective” assessments—physiological tasks, such as  Heartbeat Counting Task [HCT, @schandry1981heart] or the Heartbeat Detection Task [HDT, @kleckner2015methodological]- versus questionnaires and rating scales that require metacognitive reflection.
 A further distinction can be made between “explicit” and “implicit” paradigms, where explicit measures direct participants’ awareness toward interoceptive processes, while implicit measures assess interoception unbeknownst to them.
-Additionally, interoceptive measures vary across different modalities, such as cardioception, respiroception, and gastroception. 
-Finally, these measures assess various theoretical dimensions, including accuracy, sensitivity, awareness, and magnitude.
+Additionally, interoceptive measures vary across different modalities, such as cardioception, respiroception, and gastroception, and assess various theoretical dimensions, including accuracy, sensitivity, awareness, and magnitude.
 While there is no consensus as to which particular approach provides the most accurate and "pure" measure of interoception and interoceptive abilities (assuming it is a unidimensional construct), it is instead plausible that each measure has strengths and limitations, and a utility dependent on the context and goal at hand [@jahedi2014; @Desmedt2023accuracy].
@@
 <!-- IAS structure  --> 
-
-**note to dom review this.
-1.
-yes I think they are general interoceptive signals (I added the items that loaded to both factors for Murphy's and Koike's validation) 2.
-Do we want to add that lin created a short verison of the scale?
-3.
-Yes kioke  did named their factors**
-
-Although the original validation study suggested a two-factor structure for the IAS, reflecting the perception of general interoceptive signals (i.e., urinate, hungry, defecate, thirsty, pain, heart, taste, breathing, temperature, mulscles, affective touch, vomit, sexual arousal), and that of signals that may be difficult to perceive solely through interoceptive information (i.e., itch, tickle, cough, burp, bruise, blood sugar, sneeze, wind).
+Although the original validation study suggested a two-factor structure for the IAS: one reflecting the perception of general interoceptive signals (i.e., urinate, hungry, defecate, thirsty, pain, heart, taste, breathing, temperature, mulscles, affective touch, vomit, sexual arousal), and other relating to signals that may be difficult to perceive solely through interoceptive information (i.e., itch, tickle, cough, burp, bruise, blood sugar, sneeze, wind).
 The authors however underlined its acceptable but imperfect fit [@murphy2019, p. 127], and several follow-up studies have indeed identified different optimal solutions. 
-For instance, @brand2023 reported a 1-factor solution, while @lin2023 and @campos2021 [the former using a new approach to structure analysis, Exploratory Graph Analysis, @golino2017exploratory] found bifactor solutions - one general factor above a set of lower-level factors [@rodriguez2016evaluating] - to be the best fit.
+For instance, @brand2023 reported a 1-factor solution, while @lin2023 - using a new approach to structure analysis, namely Exploratory Graph Analysis [EGA, @golino2017exploratory]- and @campos2021 found bifactor solutions, that is one general factor above a set of lower-level factors [@rodriguez2016evaluating],  to be the best fit.
 
@@
 Notably, the only other study to report a 2-factor solution was conducted by @koike2023, who performed an Exploratory Factor Analysis (EFA) assuming 2 factors to align with the findings from the original validation paper.
-According to the authors, the first factor appears to reflect cutaneous sensations (e.g., itching, tickling, coughing, burping, affective touch, bruising, passing gas, sneezing, muscle sensations, sexual arousal, and taste), while the second factor seems to represent visceral sensations (e.g., urination, defecation, hunger, thirst, pain, breathing, fatigue/blood sugar, temperature, vomiting, and heartbeat).
+According to the authors, the first factor appears to reflect cutaneous sensations (i.e., itching, tickling, coughing, burping, affective touch, bruising, passing gas, sneezing, muscle sensations, sexual arousal, and taste), while the second factor seems to represent visceral sensations (i.e., urination, defecation, hunger, thirst, pain, breathing, fatigue/blood sugar, temperature, vomiting, and heartbeat).
 
@@
 Regarding its validity, the IAS has naturally been compared to other interoception-related measures, and shows a positive correlations with most facets of the MAIA [@mehling2018multidimensional], except for the Not-Distracting and Not-Worrying subscales [@brand2023] - which were highlighted previously as related to non-interoceptive abilities [@ferentzi2021examining].
-Interestingly, findings on the correlation between the IAS and the body awareness dimension of the Body Perception Questionnaire [BPQ-A, @porges1993body] have been mixed: some studies report small positive correlations [@brand2023; @campos2021; @koike2023], while others find small negative correlations [@lin2023] or no correlation at all [@murphy2019].
+Interestingly, findings on the correlation between the IAS and the body awareness dimension of the BPQ (i.e., BPQ-A) have been mixed: some studies report small positive correlations [@brand2023; @campos2021; @koike2023], while others find small negative correlations [@lin2023] or no correlation at all [@murphy2019].
 Small positive correlations have also been observed with the "observation" and "description" subscales of the Five Facet Mindfulness Questionnaire [FFMQ, @baer2006using; @brand2023; @koike2023], as well as with the "non-reactivity" and "acting with awareness" subscales [@koike2023].
-Additionally, the IAS has shown a positive correlation with the interoceptive awareness subscale of the Eating Disorder Inventory [@lin2023] and a negative correlation with the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia, @brand2023; @murphy2019].
-Lastly, small positive correlations have also been reported with the Interoceptive Attention Scale [IATS, @lin2023, @koike2023], though studies have also found no correlation between these measures [@gabriele2022dissociations].
+Additionally, the IAS has shown a positive correlation with the interoceptive awareness subscale of the EDI [@lin2023] and a negative correlation with the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia], as reported by @brand2023 and @murphy2019.
+Lastly, no correlations have also been reported with the Interoceptive Attention Scale [IATS, @gabriele2022dissociations], though studies have also found small positive correlation between these measures [@lin2023; @koike2023].
 
@@
 
-**TODO: can you update the fig. 1's box (assessmeent of related traits) to remove the question marks and put the the stronger interoception correlates** - as in with what?
+**TODO: can you update the fig.
+1's box (assessmeent of related traits) to remove the question marks and put the the stronger interoception correlates.
+-- > I have put somatic symptoms but can also change to anxiety or depression?**
 
@@
 
-The current study aims at 1) clarifying the structure of the IAS with a meta-analytic approach that leverages existing data and contrast the traditional CFA/SEM factor-based analyses with network-based ones such as EGA;
+Given the conflicting findings surrounding the IAS, the current study aims at 1) clarifying its structure with a meta-analytic approach that leverages existing data and contrast the traditional confirmatory factor analysis (CFA)/structural equation modeling (SEM) factor-based analyses with network-based ones such as EGA;
 2) the second part will provide an overview of the dispositional correlates of the IAS, clarifying the pattern of associations which is key to better understand the nature, place and role of interoception questionnaires within a larger context.
@@
 
-The goal of study 1 is to re-analyse and assess the factor structure of the IAS by taking advantage of the large number of open-access datasets [@brand2023; @campos2021; @lin2023; @murphy2019; @arslanova2022; @todd2022; @gaggero2021; @brand2022; @von2023].
+Study 1 will re-analyse and assess the factor structure of the IAS by taking advantage of the large number of open-access datasets [@brand2023; @campos2021; @lin2023; @murphy2019; @arslanova2022; @todd2022; @gaggero2021; @brand2022; @von2023].
 While combining these studies might provide a more robust and generalizable understanding of the IAS' factor structure, we also additionally provide an individual analysis (i.e., on all samples separately) to add nuance to the general picture, as all studies differ in their sample sizes, demographics, language, and procedure.
@@
 
+**Note to dom: just to confirm all of your samples are from unpublished papers tight ?**
+
 Our search focused on studies citing the original IAS validation paper [@murphy2019], identifying 136 papers (as of 01/05/2024).
 To qualify for inclusion, papers needed to (1) provide accessible data in open-access, (2) employ the IAS as a measure, and (3) report individual IAS items scores.
-We also included the data of two unpublished (but already open-access) studies.
-A total of 10 studies was included (see **Table 1**).
+We also included the data of four unpublished (but already open-access) studies.
+A total of 14 studies was included (see **Table 1**).
 
@@
 To examine the factor structure of the IAS, a two-steps approach was employed.
-First, Exploratory Graph Analysis (EGA), was used to estimate the dimensions via network estimation and community detection, alongside assessing the stability of dimensions and items using the bootstrapping techniques [@golino2017exploratory].
+First, EGA  was used to estimate the dimensions via network estimation and community detection, alongside assessing the stability of dimensions and items using the bootstrapping techniques [@golino2017exploratory].
 The selection of EGA was motivated by its capability to handle complex, multidimensional data and provide robust dimension estimates.
 A novel network psychometrics - Unique variable analysis [UVA, @christensen2023unique] - approach based on the weighted topological overlap will be computed to evaluate which items have substantial local dependence (\> 0.25).
-Subsequently, exploratory factor analysis (EFA) was employed followed by confirmatory factor analysis (CFA).
+Subsequently, exploratory factor analysis (EFA) was employed followed by CFA.
 
@@
 #### EGA
-
 <!-- Univariate analysis -->
-
 The UVA revealed that there are two large to very large redundant variables when taking all samples into account.
@@
 <!-- Network analysis -->
-
 According to the network analysis, using the Walktrap and Louvain algorithms applied to Glasso networks, a 4-factor structure fits the questionnaire best across all data sets.
-This is rather consistent within the data sets, where some samples indicate 3-factor structure, and some a 5-factor structure would fit well too.
-The 4-factor structure model with the best fit entails the following items per group: 1) itch, tickle, bruise, blood sugar; 2) burp, wind, cough, sneeze, vomit; 3) affective touch, sexual arousal, muscles, temperature, pain, and taste; 4) Heart, breathing, hungry, thirsty, urinate, and defecate.
+This is generally consistent within the data sets, although some samples suggest that a 3-factor or 5-factor structure might also be a good fit.
+The 4-factor structure model with the best fit entails the following items per group: 1)"itch", "tickle", "bruise", "blood sugar"; 2) "burp", "wind", "cough", "sneeze", "vomit"; 3) "affective touch", "sexual arousal", "muscles", "temperature", "pain", and "taste"; 4) "heart", "breathing", "hungry", "thirsty", "urinate", and "defecate".
 
 <!-- Stability analysis -->
-
 Stability analysis, employing 500 bootstrap iterations, also favoured the 4-factor solution for its greater stability.
@@
 <!-- Factor analysis -->
-
-<!-- check EFA results again -->
-
 When accounting for all samples, the factor analysis reveals that a 4-factor structure fits best.
 The exploratory factor analysis revealed that 4 latent factors (oblimin rotation) accounted for  41.58% of the total variance of the original data (MR1 = 14.45%, MR3 = 11.76%, MR2 = 8.09%, MR4 = 7.28%).
-Since UVA identified "tickle" as the item to be removed—and it also had the lowest uniqueness value in factor analysis with a similar loading to "itch"—" it was excluded from subsequent analyses.
+
+<!-- Removal of items before the CFA -->
+Since UVA identified "tickle" as the item to be removed—and it had the lowest uniqueness value in factor analysis, with a loading similar to "itch"—it was excluded from subsequent analyses.
+Additionally, several items were removed due to ambiguity, in which ....
+**need to add reasoning for the removal of 'ambiguous items'**
 
 <!-- Confirmatory factor analysis -->
-
-CFA was computed with the removal of the item "tickle" as it was constantly flagged as redundant.
-This analysis compared 5 models: a single-factor solution, a 4-factor solution, a 5-factor solution, a 6-factor solution and a 7-factor solution.
-The latter was preferred in most datasets, including with indices that penalise increased number of parameters (such as BIC).
-There was no evidence for higher order factors.
+CFA analysis compared 5 models: a single-factor solution, a 4-factor solution, a 5-factor solution, a 6-factor solution and a 7-factor solution. 
+The latter, which composed of pairs of itmes was preferred in most datasets, including with indices that penalise increased number of parameters (such as BIC).
+Lastly, there was no evidence for higher order factors.
 
@@
 <!-- Ias structure -->
-
 In this study, several datasets were analyzed for a meta analysis of the structure of the IAS.
@@
 
-Interestingly, @lin2023 also found that "tickle" and "itch" were redundant, which led them to excludw one of them.
+Interestingly, @lin2023 also found that "tickle" and "itch" were redundant, which led them to exclude one of them.
 Although, the reason being that the character for both words is the same in the Chinese language.
@@
 
-The findings indicate a high proportion of answers at 4 (see Figure 1), especially when using a 5-step scale.
+The findings indicate a high proportion of answers at 4 (see @fig-distributions), especially when using a 5-step scale.
 The analogue scale shows a more dispersed distribution, with some answers indicating the highest 5/5, which was not the case in Likert-scales. 
@@
 
-**note**compute internal consistency
-
 #### Correlations with body measures
 <!-- Alexithymia -->
-Alexithymia was assessed in the samples with the Bermond–Vorst Alexithymia Questionnaire [BVAQ; @vorst2001validity] and the Toronto Alexithymia Scale[TAS; @bagby1994twenty].
+Alexithymia was assessed in the samples with the Bermond–Vorst Alexithymia Questionnaire [BVAQ, @vorst2001validity] and the Toronto Alexithymia Scale [TAS, @bagby1994twenty].
 

### 2025-03-03 paper/1_Initial/manuscript.qmd
minor

@@
 <!-- ICQ -->
-The Interoceptive Confusion Questionnaire (ICQ; @brewer2016alexithymia) was used to assess individuals' difficulties in interpreting non-affective physiological states, such as pain and hunger.
+The Interoceptive Confusion Questionnaire was used to assess individuals' difficulties in interpreting non-affective physiological states, such as pain and hunger.
 The ICQ consists of 20 items rated on a scale from 1 ("Does not describe me") to 5 ("Describes me very well"), with higher scores indicating greater interoceptive confusion.
@@
 
-Mood disorders were assessed using several standardized measures, including the General Anxiety Disorder-2 [GAD-2; @kroenke2007anxiety], the State-Trait Anxiety Inventory [STAI; @spielberger1970manual] and its shorter version, the STAI-5 [@zsido2020development], Beck’s Depression Inventory [BDI; @beck1996beck], and the Mood and Feelings Questionnaire [MFQ; @messer1995development].
-Additionally, the Patient Health Questionnaire (PHQ) was administered in its 2-item [PHQ-2; @kroenke2003patient], 9-item [PHQ-9; @kroenke2001phq], and 15-item [PHQ-15; @kroenke2002phq] versions.
+Mood disorders were assessed using several standardized measures, including the General Anxiety Disorder-2 [GAD-2, @kroenke2007anxiety], the State-Trait Anxiety Inventory [STAI, @spielberger1970manual] and its shorter version, the STAI-5 [@zsido2020development], Beck’s Depression Inventory [BDI, @beck1996beck], and the Mood and Feelings Questionnaire [MFQ; @messer1995development].
+Additionally, the Patient Health Questionnaire (PHQ) was administered in its 2-item [PHQ-2; @kroenke2003patient], 9-item [PHQ-9; @kroenke2001phq], and 15-item [PHQ-15, @kroenke2002phq] versions.
 Finally, borderline personality traits were assessed using the McLean Screening Instrument for Borderline Personality Disorder [MSI-BPD; @zanarini2003zanarini].

### 2025-03-03 paper/1_Initial/manuscript.qmd
minor

--- 2025-02-28 paper/1_Initial/manuscript.qmd
@@
 
-Interoception is referred to the process of sensing, interpreting and integrating information pertaining to internal organs, such as the heart, the lungs or the gut [@khalsa2018interoception].
+Interoception is referred to the process of sensing, interpreting and integrating information pertaining to internal organs, such as the heart, the lungs or the gut [@khalsa2018].
 While recent research emphasizes a key role of interoception in a variety of processes (e.g., emotion regulation, decision making) and of outcomes (physical and psychological well being), the field remains clouded by concerns about how interoception is assessed.
@@
 
-<!-- Various measures of interoception have been developed (see @fig-measures), forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking *vs.* questionnaires and subjective scales involving a metacognitive reflection), "explicit" and "implicit" paradigms (i.e., directing participants' awareness and attention to interoceptive processes *vs.* measuring interoception unbeknownst to them), various interoceptive modalities (e.g., cardioception, respiroception, gastroception) and theoretical dimensions (e.g., accuracy, sensitivity, awareness).
--->
-
-<!-- While this is longer it breaks it down a bit more -->
-Various measures of interoception have been developed (see @fig-measures), combining different approaches, including both “objective” and “subjective” assessments—physiological tasks, such as  Heartbeat Counting Task [HCT, @schandry1981heart] or the Heartbeat Detection Task [HDT, @kleckner2015methodological], versus questionnaires and rating scales that require metacognitive reflection.
-A further distinction can be made between “explicit” and “implicit” paradigms, where explicit measures direct participants’ awareness toward interoceptive processes, while implicit measures assess interoception unbeknownst to them.
-Additionally, interoceptive measures vary across different modalities, such as cardioception, respiroception, and gastroception. 
-Finally, these measures assess various theoretical dimensions, including accuracy, sensitivity, awareness, and magnitude.
-While there is no consensus as to which particular approach provides the most accurate and "pure" measure of interoception and interoceptive abilities (assuming it is a unidimensional construct), it is instead plausible that each measure has strengths and limitations, and a utility dependent on the context and goal at hand [@jahedi2014; @Desmedt2023accuracy].
+Various measures of interoception have been developed (see @fig-measures), forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking *vs.* questionnaires and subjective scales involving a metacognitive reflection), "explicit" and "implicit" paradigms (i.e., directing participants' awareness and attention to interoceptive processes *vs.* measuring interoception unbeknownst to them), various interoceptive modalities (e.g., cardioception, respiroception, gastroception) and theoretical dimensions (e.g., accuracy, sensitivity, awareness).
+While there is no consensus as to which particular approach provides the most accurate and "pure" measure of interoception and interoceptive abilities (assuming it is a unidimensional construct), it is instead plausible that each measure has strengths and limitations, and a utility dependent on the context and goal at hand [@jahedi2014].
 
@@
 For instance, existing findings typically show weak or no correlations between questionnaires and objective measures [including for measures of the same theorethical dimensions, e.g., task-based accuracy vs.
-self-reported accuracy, @murphy2019; @brand2023; @arslanova2022], such as the HCT and the HDT.
-Additionally, objective measures assessing the same interoceptive dimension, such as accuracy, either show no correlation [e.g., @brand2023] or only weak correlations [e.g., @hickman2020relationship].
+self-reported accuracy, @murphy2019; @brand2023], such as the Heartbeat Counting Task [HCT, @schandry1981heart] and the Heartbeat Detection Task [HDT, @kleckner2015methodological].
 Perhaps more surprisingly, low correlations have been observed even among questionnaires, suggesting the targeting of different facets related to interoception.
 
-<!-- 
-Garfinkel - sensibility-> Self-perceived dispositional tendency to be internally self-focused and interoceptively cognisant,
-Khalsa - sensibility -> Self-perceived tendency to focus on interoceptive stimuli (trait measure)
-Khalsa self-report scales -> The ability to reflect upon one’s autobiographical experiences of interoceptive states, make judgments about their outcomes, and describe them through verbal or motor responses.
--->
-
-One striking example concerns the assessment of interoceptive sensibility, which is broadly defined as the self-reported tendency to focus on and detect internal sensations [@garfinkel2015knowing], but more narrowly as the subjective tendency to focus on interoceptive signals, without necessarily implying detection ability [@khalsa2018interoception].
-A recent systematic review suggested that various questionnaires designed to assess interoceptive sensibility may, in fact, measure distinct constructs, leading researchers to treat them as equivalent despite overall low convergence [@desmedt2022measures].
-
-Notably, this review adopted a broad definition of 'sensibility,' incorporating both interoceptive sensibility and interoceptive self-report scales, as described in @khalsa2018interoception's eight-facet model.
-In this framework, self-report measures are categorized into interoceptive sensibility and interoceptive self-report scales (i.e., the ability to evaluate one's personal experiences of internal bodily states, assess their consequences, and articulate them through speech or movement).
-Several widely used questionnaires were included in the review, such as the Multidimensional Assessment of Interoceptive Awareness [MAIA, @mehling2012; MAIA-2, @mehling2018multidimensional], the Body Perception Questionnaire [BPQ, @porges1993body], the Private subscale of the Body Consciousness Questionnaire [PBCS, @miller1981consciousness], the Body Awareness Questionnaire [BAQ, @shields1989body], and the Eating Disorder Inventory [EDI, @garner1991eating; @garner1983].
-The lack of correlations to moderate correlations among these questionnaires highlight the need for greater conceptual clarity regarding what each measure captures, how they relate to different dimensions of interoception, and their potential overlaps with other constructs, such as alexithymia and body awareness.
+One striking example concerns the assessment of "interoceptive sensibility", defined as the self-reported tendency to focus on and detect internal sensations [@garfinkel2015knowing], or more narrowly as the subjective ability to focus on interoceptive signals [@khalsa2018interoception].
+**TODO: ANA check if the definitions are correct**.
+A recent systematic review suggested that various questionnaires [**WHICH ONES**] designed to assess this dimension actually measure distinct constructs, leading researchers to mistakenly treating them as equivalent measures [@desmedt2022measures].
+This underlines the need for a more comprehensive understanding of what is being measured with different questionnaires and dimensions, as well as their potential overlaps with other constructs (e.g., alexithymia, body awareness).
 
@@
 The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological modality such as respiration (*"I can always accurately perceive when I am breathing fast"*), heart (*"I can always accurately perceive when my heart is beating fast"*), skin (*"I can always accurately perceive when something is going to be ticklish"*), arousal or bodily functions like coughing (*"I can always accurately perceive when I am going to cough"*) or urinating (*"I can always accurately perceive when I need to urinate"*).
-Notably, the IAS' statements are about specific interoceptive behaviours, which is a distinct difference with other popular interoception questionnaires, such as the MAIA-2, which contains more general and metacognitive items (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*), as well as dimensions related to attention regulation (e.g., Not-distracting) or emotion regulation (e.g., Not-worrying).
+Notably, the IAS' statements are about specific interoceptive behaviours, which is a notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012; MAIA-2, @mehling2018multidimensional], which contains more general and metacognitive items (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*), as well as dimensions related to attention regulation (e.g., Not-distracting) or emotion regulation (e.g., Not-worrying).
 
@@
 
-**note to dom review this.
-1.
-yes I think they are general interoceptive signals (I added the items that loaded to both factors for Murphy's and Koike's validation) 2.
-Do we want to add that lin created a short verison of the scale?
-3.
-Yes kioke  did named their factors**
-
-Although the original validation study suggested a two-factor structure for the IAS, reflecting the perception of general interoceptive signals (i.e., urinate, hungry, defecate, thirsty, pain, heart, taste, breathing, temperature, mulscles, affective touch, vomit, sexual arousal), and that of signals that may be difficult to perceive solely through interoceptive information (i.e., itch, tickle, cough, burp, bruise, blood sugar, sneeze, wind).
+Although the original validation study suggested a two-factor structure for the IAS, reflecting the perception of [**general?**] interoceptive signals, and that of signals that may be difficult to perceive solely through interoceptive information.
 The authors however underlined its acceptable but imperfect fit [@murphy2019, p. 127], and several follow-up studies have indeed identified different optimal solutions. 
-For instance, @brand2023 reported a 1-factor solution, while @lin2023 and @campos2021 [the former using a new approach to structure analysis, Exploratory Graph Analysis, @golino2017exploratory] found bifactor solutions - one general factor above a set of lower-level factors [@rodriguez2016evaluating] - to be the best fit.
-
+For instance, @brand2023 and @golino2017exploratory (the latter using a new approach to structure analysis, Exploratory Graph Analysis), reported a 1-factor solution, while @lin2023 and @campos2021 found bifactor solutions - one general factor above a set of lower-level factors [@rodriguez2016evaluating] - to be the best fit.
 Discussions have also been focused on specific items.
@@
 @lin2023 also highlights their correlation analysis, showing five locally dependent pairs and three items (touch, blood sugar, bruise) with exceptionally high difficulty and low discrimination, and @campos2021 reported "tickle" to be the only item that reflected more specific factors than the general factor.
+Localization issues also arisen with two items, **TODO** (talk about chinese stuff)
 
-Localization issues also arose in @lin2023 validation of the IAS, where both "itch" and "tickle" correspond to the same Chinese character, leading to their collapse into a single item. 
-Notably, the only other study to report a 2-factor solution was conducted by @koike2023, who performed an Exploratory Factor Analysis (EFA) assuming 2 factors to align with the findings from the original validation paper.
-According to the authors, the first factor appears to reflect cutaneous sensations (e.g., itching, tickling, coughing, burping, affective touch, bruising, passing gas, sneezing, muscle sensations, sexual arousal, and taste), while the second factor seems to represent visceral sensations (e.g., urination, defecation, hunger, thirst, pain, breathing, fatigue/blood sugar, temperature, vomiting, and heartbeat).
+<!-- Notably, the only other study to report a 2-factor solution was conducted by @koike2023, who performed an Exploratory Factor Analysis (EFA) assuming 2 factors to align with the findings from the original validation paper.
+-->
+**TODO: how did koike2023 interpret the two factors? Do they say?**
 
@@
 
-**Note to dom: @ferentzi2021examining suggests that all MAIA dimensions, except for Not-Worrying and Not-Distracting, relate to a general interoceptive awareness factor.
-The low correlations of NW and ND with this general factor indicate that these dimensions do not contribute significantly to the measurement of general interoceptive awareness.
-Instead, NW appears to measure low emotionality or neuroticism, while ND does not capture a coherent underlying structure.**
-
-Regarding its validity, the IAS has naturally been compared to other interoception-related measures, and shows a positive correlations with most facets of the MAIA [@mehling2018multidimensional], except for the Not-Distracting and Not-Worrying subscales [@brand2023] - which were highlighted previously as related to non-interoceptive abilities [@ferentzi2021examining].
+Regarding its validity, the IAS has naturally been compared to other interoception-related measures, and shows a positive correlations with most facets of the MAIA [@mehling2018multidimensional], except for the Not-Distracting and Not-Worrying subscales [@brand2023] - which were highlighted previously as related to non-interoceptive abilities [**do we have a ref to say that?
+will also be useful for our MINT paper to back up our claims that these 2 dims are something else**].
 Interestingly, findings on the correlation between the IAS and the body awareness dimension of the Body Perception Questionnaire [BPQ-A, @porges1993body] have been mixed: some studies report small positive correlations [@brand2023; @campos2021; @koike2023], while others find small negative correlations [@lin2023] or no correlation at all [@murphy2019].
 Small positive correlations have also been observed with the "observation" and "description" subscales of the Five Facet Mindfulness Questionnaire [FFMQ, @baer2006using; @brand2023; @koike2023], as well as with the "non-reactivity" and "acting with awareness" subscales [@koike2023].
-Additionally, the IAS has shown a positive correlation with the interoceptive awareness subscale of the Eating Disorder Inventory [@lin2023] and a negative correlation with the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia, @brand2023; @murphy2019].
-Lastly, small positive correlations have also been reported with the Interoceptive Attention Scale [IATS, @lin2023, @koike2023], though studies have also found no correlation between these measures [@gabriele2022dissociations].
+Additionally, the IAS has shown a positive correlation with the interoceptive awareness subscale of the Eating Disorder Inventory [@lin2023] and a negative correlation with the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia; @brand2023; @murphy2019].
+Lastly, small positive correlations have also been reported with the Interoceptive Attention Scale [IATS, @lin2023; @koike2023], though studies have also found no correlation between these measures [@gabriele2022dissociations].
+Interestingly, the IAS and the IATS supposedly measure two different interoceptive processes (i.e., accuracy and attention, respectively) which contradict @murphy2019 proposed 2x2 framework.
+**TODO: how so?
+Elaborate**
 
@@
 
-**TODO: can you update the fig. 1's box (assessmeent of related traits) to remove the question marks and put the the stronger interoception correlates** - as in with what?
+**TODO: can you update the fig. 1's box (assessmeent of related traits) to remove the question marks and put the the stronger interoception correlates**
 

### 2025-03-03 paper/1_Initial/manuscript.qmd

--- 2025-03-03 paper/1_Initial/manuscript.qmd
@@
 
-Given the conflicting findings surrounding the IAS, the current study aims at 1) clarifying its structure with a meta-analytic approach that leverages existing data and contrast the traditional confirmatory factor analysis (CFA)/structural equation modeling (SEM) factor-based analyses with network-based ones such as EGA;
+The current study aims at 1) clarifying the structure of the IAS with a meta-analytic approach that leverages existing data and contrast the traditional CFA/SEM factor-based analyses with network-based ones such as EGA;
 2) the second part will provide an overview of the dispositional correlates of the IAS, clarifying the pattern of associations which is key to better understand the nature, place and role of interoception questionnaires within a larger context.

### 2025-03-03 paper/1_Initial/manuscript.qmd
fix hierarchy

@@
 While there is no consensus as to which particular approach provides the most accurate and "pure" measure of interoception and interoceptive abilities (assuming it is a unidimensional construct), it is instead plausible that each measure has strengths and limitations, and a utility dependent on the context and goal at hand [@jahedi2014; @Desmedt2023accuracy].
+
+**TODO: more detailed caption for the graph below.
+A good caption typically repeats and summarizes info from the text.
+E.g., "The different modalities of interoception can be measured in a variety of ways, directly and indirectly, ..."**
 
@@
 
-**Note to dom: @ferentzi2021examining suggests that all MAIA dimensions, except for Not-Worrying and Not-Distracting, relate to a general interoceptive awareness factor.
-The low correlations of NW and ND with this general factor indicate that these dimensions do not contribute significantly to the measurement of general interoceptive awareness.
-Instead, NW appears to measure low emotionality or neuroticism, while ND does not capture a coherent underlying structure.**
-
 Regarding its validity, the IAS has naturally been compared to other interoception-related measures, and shows a positive correlations with most facets of the MAIA [@mehling2018multidimensional], except for the Not-Distracting and Not-Worrying subscales [@brand2023] - which were highlighted previously as related to non-interoceptive abilities [@ferentzi2021examining].
@@
 While assessing the predictive validity of an interoception scale can be conceived as theoretically challenging, expected negative associations were observed between the IAS and alexithymia [@brand2023; @koike2023; @campos2021; @murphy2019; @lin2023], somatic symptoms [@brand2023; @koike2023; @lin2023], depressive symptoms [@brand2023; @koike2023; @lin2023], anxiety [@brand2023], neuroticism [@brand2023] and self-esteem [@murphy2019].
-
-**TODO: can you update the fig.
-1's box (assessmeent of related traits) to remove the question marks and put the the stronger interoception correlates.
--- > I have put somatic symptoms but can also change to anxiety or depression?**
-
-<!-- **anything else?**. TO BE COMPLETED -- to be determined -->
 
@@
 #### Datasets
-
-**Note to dom: just to confirm all of your samples are from unpublished papers tight ?**
 
@@
 
+<!-- Note: this table is generated during data analysis -->
 \input{../../analysis/figures/table2.tex}
 
-#### Statistical analysis
+#### Data Analysis
 
@@
 
-## Average correlations
+#### Average correlations
 
@@
 
-#### Correlations with body measures
+##### Correlations with body measures
+
 <!-- Alexithymia -->
@@
 
-#### Correlations with mood measures
+##### Correlations with mood measures
 
@@
 
-#### Correlations with psychopathology measures
+##### Correlations with psychopathology measures
 
@@
 
-#### Correlations with personality measures
+##### Correlations with personality measures
 
@@
 
-#### Correlations with other measures
+##### Correlations with other measures
 
@@
 These correlates not only help explain different aspects of interoception but also serve as valuable tools for validating interoceptive measures.
+
+**TODO: integrate the following**
+**Note to dom: @ferentzi2021examining suggests that all MAIA dimensions, except for Not-Worrying and Not-Distracting, relate to a general interoceptive awareness factor.
+The low correlations of NW and ND with this general factor indicate that these dimensions do not contribute significantly to the measurement of general interoceptive awareness.
+Instead, NW appears to measure low emotionality or neuroticism, while ND does not capture a coherent underlying structure.**
 

### 2025-03-03 paper/1_Initial/manuscript.qmd
@AnafNeves added todo in data analysis

@@
 Study 1 will re-analyse and assess the factor structure of the IAS by taking advantage of the large number of open-access datasets [@brand2023; @campos2021; @lin2023; @murphy2019; @arslanova2022; @todd2022; @gaggero2021; @brand2022; @von2023].
-While combining these studies might provide a more robust and generalizable understanding of the IAS' factor structure, we also additionally provide an individual analysis (i.e., on all samples separately) to add nuance to the general picture, as all studies differ in their sample sizes, demographics, language, and procedure.
+While combining these studies might provide a more robust and generalizable understanding of the IAS' factor structure, we also additionally provide an individual analysis (i.e., on all samples separately) to add nuance to the general picture, as all studies differ in their sample size, demographic characteristics, language, and procedure.
 
@@
 
+<!-- Note: this table is generated during data analysis -->
+
 \begin{landscape}
@@
 
-#### Statistical Analysis
+#### Data Analysis
 
-To examine the factor structure of the IAS, a two-steps approach was employed.
-First, EGA  was used to estimate the dimensions via network estimation and community detection, alongside assessing the stability of dimensions and items using the bootstrapping techniques [@golino2017exploratory].
-The selection of EGA was motivated by its capability to handle complex, multidimensional data and provide robust dimension estimates.
-A novel network psychometrics - Unique variable analysis [UVA, @christensen2023unique] - approach based on the weighted topological overlap will be computed to evaluate which items have substantial local dependence (\> 0.25).
-Subsequently, exploratory factor analysis (EFA) was employed followed by CFA.
+In order to obtain a comprehensive view, we will examine the factor structure of the IAS using two different approaches, namely Exploratory Graph Analysis (EGA) and traditional exploratory and confirmatory Factor Analysis (EFA/CFA).
+
+**TODO: Explain EGA. Rework the following paraphraph**.
+
+<!-- was used to estimate the dimensions via network estimation and community detection, alongside assessing the stability of dimensions and items using the bootstrapping techniques [@golino2017exploratory].
+-->
+<!-- The selection of EGA was motivated by its capability to handle complex, multidimensional data and provide robust dimension estimates. -->
+<!-- A novel network psychometrics - Unique variable analysis [UVA, @christensen2023unique] - approach based on the weighted topological overlap will be computed to evaluate which items have substantial local dependence (\> 0.25).
+-->
+
+In contrast, the factor analsyis framework... **TODO**. 
+We will first apply EFA to... and then identify the best fitting models using CFA.
 
@@
 
-<!-- Distibutions of items -->
+<!-- Distributions of items -->
 
@@
 
-<!-- Note: this table is generated during data analysis -->
 \input{../../analysis/figures/table2.tex}

### 2025-03-03 paper/1_Initial/manuscript.qmd
comments for results 1

@@
 
-In order to obtain a comprehensive view, we will examine the factor structure of the IAS using two different approaches, namely Exploratory Graph Analysis (EGA) and traditional exploratory and confirmatory Factor Analysis (EFA/CFA).
+Psychometrically good items should exhibit various qualities, such as validity and reliability, and one of the contributing factors is the amount of variability captured by an item.
+Items to which all participants' answers are concentrated around one option - i.e., exhibiting a narrow distribution - should be flagged as potentially problematic.
+
+After examining the distributions to all IAS items, we will analyze the factor structure using two different approaches, namely Exploratory Graph Analysis (EGA) and traditional exploratory and confirmatory Factor Analysis (EFA/CFA).
 
@@
 
-Visualizing the distribution of the items for all samples suggests the presence of a consistent modal value (@fig-distributions).
-In other words, participants are most likely to answer 4/5 (i.e., agree) on most items (but "affective touch", "blood sugar", and "bruise" that exhibit a different distributional pattern).
-Additionally, one can note the low density on extreme values (1 and 5), meaning that the bulk of answers (i.e., 99%) varies between 3 values.
-The interindividual variability seems improved in the samples using an analogue scale, displaying a more continuous and progressive spread of answers.
+The distribution of the items for all samples suggests the presence of a consistent modal value (@fig-distributions).
+In other words, participants are most likely to answer 4/5 (i.e., agree) on most items, with the exception of "affective touch" (**TODO: this one only seem off in ssames 8 no?
+could it be a language thing?**), "blood sugar", and "bruise", which exhibit a different distributional pattern with a lower mode (\~2/5).
+Additionally, one can note the low occurence of extreme values (1 and 5), meaning that the bulk of answers varies between 3 values (assuming the IAS is implemented as a 5-point Likert scale following its validation).
+The samples using an analogue scale (samples 10a, 10b and 10c in the figure **what about 11?**) displaying a more continuous and progressive spread of answers, seemingly improving the interindividual variability, although potentially suggesting a second lower mode at \~2.
+
+**TODO: add more information to the caption to highlight some interesting things.
+What are the two items that stand out.
+Mention caveat that for most samples the undelying data is disrete (Likert scales), and hence the density plots are not the most accurate visualization method but have been chosen as the clearer to highlight what we are interested in.**
+
+**TODO: change the number of rows/cols of the figure to make it nicer (e.g., 3x6). And add x-axis on all subplots. Consider making the problematic items dashed.**.
 

### 2025-03-03 paper/1_Initial/manuscript.qmd
more

@@
 
-**TODO: Explain EGA. Rework the following paraphraph**.
+**TODO: Explain EGA. Explain UVA. Rework the following paragraph**.
 
@@
 
-The distribution of the items for all samples suggests the presence of a consistent modal value (@fig-distributions).
+The distribution of the items across samples suggests the presence of a consistent modal value (@fig-distributions).
 In other words, participants are most likely to answer 4/5 (i.e., agree) on most items, with the exception of "affective touch" (**TODO: this one only seem off in ssames 8 no?
 could it be a language thing?**), "blood sugar", and "bruise", which exhibit a different distributional pattern with a lower mode (\~2/5).
-Additionally, one can note the low occurence of extreme values (1 and 5), meaning that the bulk of answers varies between 3 values (assuming the IAS is implemented as a 5-point Likert scale following its validation).
+Additionally, one can note the low occurrence of extreme values (1 and 5), meaning that the bulk of answers varies between 3 values (assuming the IAS is implemented as a 5-point Likert scale following its validation).
 The samples using an analogue scale (samples 10a, 10b and 10c in the figure **what about 11?**) displaying a more continuous and progressive spread of answers, seemingly improving the interindividual variability, although potentially suggesting a second lower mode at \~2.
@@
 
-#### Correlations
-
-The correlation analysis revealed that the items overall have positive intercorrelation patterns with no clear structure emerging.
-This remains the same across all samples.
-However, there are possibly some higher-order groupings emerging for the 2 analog-scale samples.
-
-#### EGA
 <!-- Univariate analysis -->
-The UVA revealed that there are two large to very large redundant variables when taking all samples into account.
-Namely, "itch" and "tickle", where "tickle" should be removed, and "itch" should be kept.
-There are several more items that are moderately to largely redundant, namely, "wind" and "burp", and "urinate" and "defecate".
-On top of that, "sneeze" and "cough", "heart" and "breathing", and "hungry" and "thirsty" seem to have small to moderate redundancy.
-These findings are rather consistent across the samples with minor differences, such as that when the questionnaire had an analog scale, there seems to be no large to very large redundant items but "itch" and "tickle" remain moderately to largely redundant and "heart" and "breathing" small to moderately redundant in one sample.
+The UVA flagged two strongly redundant variables.
+Namely, "itch" and "tickle" - suggesting to remove the latter.
+Several more pairs of items were flagged as moderately redundant ("wind" and "burp"; "urinate" and "defecate") and mildly redundant ("sneeze" and "cough"; "heart" and "breathing"; "hungry" and "thirsty").
+These patterns consistently appeared in most samples when considered individually.
 
@@
 <!-- Factor analysis -->
+**TODO: explain how we obtained the optimal number of factors**
+
 When accounting for all samples, the factor analysis reveals that a 4-factor structure fits best.

### 2025-03-04 paper/1_Initial/manuscript.qmd
minor

@@
 
-**TODO: more detailed caption for the graph below.
-A good caption typically repeats and summarizes info from the text.
-E.g., "The different modalities of interoception can be measured in a variety of ways, directly and indirectly, ..."**
-
 ```{r}
@@
 #| label: "fig-measures"
-#| fig-cap: "Different ways in which interoception can be measured."
 #| apa-twocolumn: false  # A Figure Spanning Two Columns When in Journal Mode
 #| out-width: "100%"
+#| fig-cap: "The different modalities of interoception can be assessed through both direct and indirect methods.
+Direct measures are classified as subjective or objective, depending on whether they involve conscious metacognitive interpretation.
+Objective measures are further divided into implicit and explicit, based on whether they bypass participants' conscious awareness and metacognitive processes.
+Indirect assessments evaluate interoception by examining its relationship with psychological traits (reflecting ability level) or physiological indices (reflecting underlying mechanisms)."
 
@@
 
-After examining the distributions to all IAS items, we will analyze the factor structure using two different approaches, namely Exploratory Graph Analysis (EGA) and traditional exploratory and confirmatory Factor Analysis (EFA/CFA).
+After examining the distributions to all IAS items, we will analyze the factor structure using two different approaches, namely EGA and traditional exploratory and confirmatory Factor Analysis (EFA/CFA).
+
+<!-- EGA -->
+EGA is a network-based approach for estimating the number of dimensions in psychological data while also identifying which items belong to each dimension [@golino2017exploratory]. 
+It was developed to address limitations of traditional methods like parallel analysis, minimum average partial procedure, and the Kaiser-Guttman rule, which can either underestimate or overestimate factor numbers depending on factors such as sample size and item correlations.
+Rooted in the network psychometric perspective, EGA integrates network analysis with psychometric methods to model relationships between psychological variables[@golino2020investigating]. 
+Specifically, it combines the Gaussian Graphical Model with the walktrap clustering algorithm to determine the dimensional structure of psychological constructs.
 

### 2025-03-11 paper/1_Initial/manuscript.qmd
added section on EGA

@@
 <!-- EGA -->
-EGA is a network-based approach for estimating the number of dimensions in psychological data while also identifying which items belong to each dimension [@golino2017exploratory]. 
-It was developed to address limitations of traditional methods like parallel analysis, minimum average partial procedure, and the Kaiser-Guttman rule, which can either underestimate or overestimate factor numbers depending on factors such as sample size and item correlations.
-Rooted in the network psychometric perspective, EGA integrates network analysis with psychometric methods to model relationships between psychological variables[@golino2020investigating]. 
-Specifically, it combines the Gaussian Graphical Model with the walktrap clustering algorithm to determine the dimensional structure of psychological constructs.
+EGA is a powerful network-based approach for estimating the number of dimensions in psychological data while identifying which items belong to each dimension, both crucial for understanding the structure of complex constructs and improving the validity of psychological assessments [@golino2017exploratory; @markos2024dimensionality].
+This new approach addresses limitations of traditional methods which can either underestimate or overestimate factor numbers depending on factors such as sample size and item correlations.
+By combining network analysis with psychometric methods, EGA offers a unique perspective for modeling relationships between psychological variables [@golino2020investigating]. 
+For instance, unlike factor analysis, which assumes a common cause for observed variables, EGA conceptualizes variables as nodes in a network, with connections (edges) reflecting associations between them [@christensen2021equivalency].
+Clustering these nodes reveals distinct communities of related items, which resemble latent factors without explicitly assuming their presence. 
+EGA has shown strong performance with binary, continuous [@cosemans2022exploratory], and more recently, ordinal data [@markos2024dimensionality], providing a flexible and reliable alternative for exploring data dimensionality.
+Given the IAS's unclear factor structure and EGA's proven accuracy with complex psychological constructs, it is a suitable technique for this analysis.
 
-**TODO: Explain EGA. Explain UVA. Rework the following paragraph**.
+**TODO: Explain UVA. Rework the following paragraph**.
 
 <!-- was used to estimate the dimensions via network estimation and community detection, alongside assessing the stability of dimensions and items using the bootstrapping techniques [@golino2017exploratory].
--->
-<!-- The selection of EGA was motivated by its capability to handle complex, multidimensional data and provide robust dimension estimates. -->
-<!-- A novel network psychometrics - Unique variable analysis [UVA, @christensen2023unique] - approach based on the weighted topological overlap will be computed to evaluate which items have substantial local dependence (\> 0.25).
+The selection of EGA was motivated by its capability to handle complex, multidimensional data and provide robust dimension estimates.
+A novel network psychometrics - Unique variable analysis [UVA, @christensen2023unique] - approach based on the weighted topological overlap will be computed to evaluate which items have substantial local dependence (\> 0.25).
 -->

### 2025-03-14 paper/1_Initial/manuscript.qmd
streamline
@AnafNeves 1. I preferred the concise version of the "multimodal" paragraph and added more examples as figure caption
2. Reworked the EGA paragraph

--- 2025-03-03 paper/1_Initial/manuscript.qmd
@@
 
-<!-- Various measures of interoception have been developed (see @fig-measures), forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking *vs.* questionnaires and subjective scales involving a metacognitive reflection), "explicit" and "implicit" paradigms (i.e., directing participants' awareness and attention to interoceptive processes *vs.* measuring interoception unbeknownst to them), various interoceptive modalities (e.g., cardioception, respiroception, gastroception) and theoretical dimensions (e.g., accuracy, sensitivity, awareness).
--->
-
-<!-- While this is longer it breaks it down a bit more -->
-Various measures of interoception have been developed (see @fig-measures), combining different approaches, including both “objective” and “subjective” assessments—physiological tasks, such as  Heartbeat Counting Task [HCT, @schandry1981heart] or the Heartbeat Detection Task [HDT, @kleckner2015methodological]- versus questionnaires and rating scales that require metacognitive reflection.
-A further distinction can be made between “explicit” and “implicit” paradigms, where explicit measures direct participants’ awareness toward interoceptive processes, while implicit measures assess interoception unbeknownst to them.
-Additionally, interoceptive measures vary across different modalities, such as cardioception, respiroception, and gastroception, and assess various theoretical dimensions, including accuracy, sensitivity, awareness, and magnitude.
+Various measures of interoception have been developed (see @fig-measures), forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking *vs.* questionnaires and subjective scales involving a metacognitive reflection), "explicit" and "implicit" paradigms (i.e., directing participants' awareness and attention to interoceptive processes *vs.* measuring interoception unbeknownst to them), various interoceptive modalities (e.g., cardioception, respiroception, gastroception) and theoretical dimensions (e.g., accuracy, sensitivity, awareness).
 While there is no consensus as to which particular approach provides the most accurate and "pure" measure of interoception and interoceptive abilities (assuming it is a unidimensional construct), it is instead plausible that each measure has strengths and limitations, and a utility dependent on the context and goal at hand [@jahedi2014; @Desmedt2023accuracy].
-
-**TODO: more detailed caption for the graph below.
-A good caption typically repeats and summarizes info from the text.
-E.g., "The different modalities of interoception can be measured in a variety of ways, directly and indirectly, ..."**
 
@@
 #| label: "fig-measures"
-#| fig-cap: "Different ways in which interoception can be measured."
 #| apa-twocolumn: false  # A Figure Spanning Two Columns When in Journal Mode
 #| out-width: "100%"
+#| fig-cap: "The different modalities of interoception (e.g., cardioception) can be assessed directly or indirectly.
+Direct assessments can further be subjective or objective, depending on whether they involve conscious metacognitive appraisals or more performance-based indices.
+Interoceptive tasks can be explicit (the participant is aware of the interoceptive nature of the task and must consciously attend to interoceptive signals; e.g., the heartbeat counting task) or implicit (measurements of interoception done unbeknowst to the participant; e.g., heartbeat evoked potentials measured during resting state).
+Indirect assessments evaluate constructs typically related (and ideally dependent on) to interoceptive processes or ability (or its deficit)."
 
@@
 Moreover, the notion that self-reports might not reflect the same processes as other interoception tasks might be important to contextualize the apparent lack of convergence between measures in the field [@desmedt2022measures].
-For instance, existing findings typically show weak or no correlations between questionnaires and objective measures [including for measures of the same theorethical dimensions, e.g., task-based accuracy vs.
-self-reported accuracy, @murphy2019; @brand2023; @arslanova2022], such as the HCT and the HDT.
+For instance, existing findings typically show weak or no correlations between questionnaires and objective measures [including for measures of the same theoretical dimensions, e.g., task-based accuracy vs.
+self-reported accuracy, @murphy2019; @brand2023; @arslanova2022], such as the Heartbeat Counting Task [HCT, @schandry1981heart] and the Heartbeat Detection Task [HDT, @kleckner2015methodological].
 Additionally, objective measures assessing the same interoceptive dimension, such as accuracy, either show no correlation [e.g., @brand2023] or only weak correlations [e.g., @hickman2020relationship].
@@
 The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological modality such as respiration (*"I can always accurately perceive when I am breathing fast"*), heart (*"I can always accurately perceive when my heart is beating fast"*), skin (*"I can always accurately perceive when something is going to be ticklish"*), arousal or bodily functions like coughing (*"I can always accurately perceive when I am going to cough"*) or urinating (*"I can always accurately perceive when I need to urinate"*).
-Notably, the IAS' statements are about specific interoceptive behaviours, which is a distinct difference with other popular interoception questionnaires, such as the MAIA-2, which contains more general and metacognitive items (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*), as well as dimensions related to attention regulation (e.g., Not-distracting) or emotion regulation (e.g., Not-worrying).
+Appealingly, the IAS' statements are about specific interoceptive behaviours, which is a distinct difference with other popular interoception questionnaires, such as the MAIA-2, which contains more general and metacognitive items (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*), as well as dimensions related to attention regulation (e.g., Not-distracting) or emotion regulation (e.g., Not-worrying).
 
@@
 
-The current study aims at 1) clarifying the structure of the IAS with a meta-analytic approach that leverages existing data and contrast the traditional CFA/SEM factor-based analyses with network-based ones such as EGA;
+The current study aims at 1) clarifying the structure of the IAS with a meta-analytic approach that leverages existing data and contrast the traditional CFA/SEM factor-based analyses with network-based ones (Exploratory Graph Analysis);
 2) the second part will provide an overview of the dispositional correlates of the IAS, clarifying the pattern of associations which is key to better understand the nature, place and role of interoception questionnaires within a larger context.
@@
 
-After examining the distributions to all IAS items, we will analyze the factor structure using two different approaches, namely Exploratory Graph Analysis (EGA) and traditional exploratory and confirmatory Factor Analysis (EFA/CFA).
+After examining the distributions to all IAS items, we will analyze the factor structure using two different approaches, namely traditional exploratory and confirmatory Factor Analysis (EFA/CFA) as well as Exploratory Graph Analysis (EGA).
 
-**TODO: Explain EGA. Explain UVA. Rework the following paragraph**.
+<!-- EGA -->
+<!-- EGA is a powerful network-based approach for estimating the number of dimensions in psychological data while identifying which items belong to each dimension, both crucial for understanding the structure of complex constructs and improving the validity of psychological assessments [@golino2017exploratory; @markos2024dimensionality].
+-->
+<!-- This new approach addresses limitations of traditional methods which can either underestimate or overestimate factor numbers depending on factors such as sample size and item correlations. -->
+<!-- By combining network analysis with psychometric methods, EGA offers a unique perspective for modeling relationships between psychological variables [@golino2020investigating].  -->
+<!-- For instance, unlike factor analysis, which assumes a common cause for observed variables, EGA conceptualizes variables as nodes in a network, with connections (edges) reflecting associations between them [@christensen2021equivalency].
+-->
+<!-- Clustering these nodes reveals distinct communities of related items, which resemble latent factors without explicitly assuming their presence.  -->
+<!-- EGA has shown strong performance with binary, continuous [@cosemans2022exploratory], and more recently, ordinal data [@markos2024dimensionality], providing a flexible and reliable alternative for exploring data dimensionality.
+-->
+<!-- Given the IAS's unclear factor structure and EGA's proven accuracy with complex psychological constructs, it is a suitable technique for this analysis. -->
+
+By combining network analysis with psychometric methods, the recently-developed EGA framework that allows to jointly estimate the number of dimensions (i.e., groups of items), the structure as well as its stability [@golino2017exploratory; @golino2020investigating].
+Evidence has underlined its suitability as an alternative to traditional factor analysis, addressing some of its limitations such as the assumption of a "latent" source of variability, possible biasing in the estimation of the optimal factor numbers depending on sample size, and **TODO: a third example would be nice?** **REF**, while remaining comparable and interpretable [@christensen2021equivalency].
+At a fundamental level, EGA conceptualizes variables as nodes in a network, with connections (edges) reflecting associations between them.
+Clustering these nodes reveals distinct communities of related items, in practice akin to traditional latent factors - but without explicitly assuming their presence [@christensen2021equivalency].
+
+**TODO: Explain UVA. Rework the following paragraph**.
 
 <!-- was used to estimate the dimensions via network estimation and community detection, alongside assessing the stability of dimensions and items using the bootstrapping techniques [@golino2017exploratory].
--->
-<!-- The selection of EGA was motivated by its capability to handle complex, multidimensional data and provide robust dimension estimates. -->
-<!-- A novel network psychometrics - Unique variable analysis [UVA, @christensen2023unique] - approach based on the weighted topological overlap will be computed to evaluate which items have substantial local dependence (\> 0.25).
+The selection of EGA was motivated by its capability to handle complex, multidimensional data and provide robust dimension estimates.
+A novel network psychometrics - Unique variable analysis [UVA, @christensen2023unique] - approach based on the weighted topological overlap will be computed to evaluate which items have substantial local dependence (\> 0.25).
 -->

### 2025-03-14 paper/1_Initial/manuscript.qmd
minor

@@
 
-By combining network analysis with psychometric methods, the recently-developed EGA framework that allows to jointly estimate the number of dimensions (i.e., groups of items), the structure as well as its stability [@golino2017exploratory; @golino2020investigating].
+By combining network analysis with psychometric methods, the recently-developed EGA framework allows to jointly estimate the number of dimensions (i.e., groups of items), the structure as well as its stability [@golino2017exploratory; @golino2020investigating].
 Evidence has underlined its suitability as an alternative to traditional factor analysis, addressing some of its limitations such as the assumption of a "latent" source of variability, possible biasing in the estimation of the optimal factor numbers depending on sample size, and **TODO: a third example would be nice?** **REF**, while remaining comparable and interpretable [@christensen2021equivalency].

### 2025-03-17 paper/1_Initial/manuscript.qmd
comments for study 1 are mostly done @AnafNeves

@@
 ---
-title: "Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates"
+title: "Mega-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates"
 shorttitle: "IAS Meta-analysis"
@@
 
-The current study aims at 1) clarifying the structure of the IAS with a meta-analytic approach that leverages existing data and contrast the traditional CFA/SEM factor-based analyses with network-based ones (Exploratory Graph Analysis);
+The current study aims at 1) clarifying the structure of the IAS with a mega-analytic (which involves a re-analysis at the raw data level by aggregating datasets) approach that leverages existing data and contrast the traditional CFA/SEM factor-based analyses with network-based ones (Exploratory Graph Analysis);
 2) the second part will provide an overview of the dispositional correlates of the IAS, clarifying the pattern of associations which is key to better understand the nature, place and role of interoception questionnaires within a larger context.
@@
 
-In contrast, the factor analsyis framework... **TODO**. 
+In contrast, the factor analsyis framework... **TODO**. **Meention rotation and how number of factors is selected**
 We will first apply EFA to... and then identify the best fitting models using CFA.
@@
 The distribution of the items across samples suggests the presence of a consistent modal value (@fig-distributions).
-In other words, participants are most likely to answer 4/5 (i.e., agree) on most items, with the exception of "affective touch" (**TODO: this one only seem off in ssames 8 no?
+In other words, participants are most likely to answer 4/5 (i.e., agree) on most items, with the exception of "affective touch" (**TODO: this one only seem off in samples 8 no?
 could it be a language thing?**), "blood sugar", and "bruise", which exhibit a different distributional pattern with a lower mode (\~2/5).
@@
 <!-- Univariate analysis -->
-The UVA flagged two strongly redundant variables.
-Namely, "itch" and "tickle" - suggesting to remove the latter.
+UVA flagged two strongly redundant variables, "itch" and "tickle" - suggesting to remove the latter.
 Several more pairs of items were flagged as moderately redundant ("wind" and "burp"; "urinate" and "defecate") and mildly redundant ("sneeze" and "cough"; "heart" and "breathing"; "hungry" and "thirsty").
@@
 <!-- Network analysis -->
-According to the network analysis, using the Walktrap and Louvain algorithms applied to Glasso networks, a 4-factor structure fits the questionnaire best across all data sets.
-This is generally consistent within the data sets, although some samples suggest that a 3-factor or 5-factor structure might also be a good fit.
-The 4-factor structure model with the best fit entails the following items per group: 1)"itch", "tickle", "bruise", "blood sugar"; 2) "burp", "wind", "cough", "sneeze", "vomit"; 3) "affective touch", "sexual arousal", "muscles", "temperature", "pain", and "taste"; 4) "heart", "breathing", "hungry", "thirsty", "urinate", and "defecate".
-
-<!-- Stability analysis -->
-Stability analysis, employing 500 bootstrap iterations, also favoured the 4-factor solution for its greater stability.
-Most items, except for 'affective touch,' demonstrated stability levels exceeding 0.90, indicating structural consistency and reliability [@christensen2021].
-These findings underscore the robustness of the identified 4-dimensional structure.
+Applying EGA to all data sets yielded 4 clusters as the optimal solution; C1.
+"itch", "tickle", "bruise", "blood sugar"; C2.
+"burp", "wind", "cough", "sneeze", "vomit"; C3.
+"affective touch", "sexual arousal", "muscles", "temperature", "pain", and "taste"; C4.
+"heart", "breathing", "hungry", "thirsty", "urinate", and "defecate".
+**TODO: if these clusters are consistent with the factor dimensions below, consider naming them**
+Most items, except for "affective touch", demonstrated a high structural stability **what that means needs to be explained in the section above**.
+This solution was generally consistent within the data sets, although some samples yielded 3- or 5- clusters as the optimal structure.
 
@@
 **TODO: explain how we obtained the optimal number of factors**
+Across all samples, the Method Agreement Procedure to find the optimal number of latent factors suggested a 4-factors solution, accounting for 41.58% of the total variance.
+**describe the loading items** **does it match the clusters above?** (MR1 = 14.45%, MR3 = 11.76%, MR2 = 8.09%, MR4 = 7.28%).
 
-When accounting for all samples, the factor analysis reveals that a 4-factor structure fits best.
-The exploratory factor analysis revealed that 4 latent factors (oblimin rotation) accounted for  41.58% of the total variance of the original data (MR1 = 14.45%, MR3 = 11.76%, MR2 = 8.09%, MR4 = 7.28%).
+**TODO: rework the CFA part below**
 
@@
 CFA analysis compared 5 models: a single-factor solution, a 4-factor solution, a 5-factor solution, a 6-factor solution and a 7-factor solution. 
-The latter, which composed of pairs of itmes was preferred in most datasets, including with indices that penalise increased number of parameters (such as BIC).
+The latter, which composed of pairs of items was preferred in most datasets, including with indices that penalise increased number of parameters (such as BIC).
 Lastly, there was no evidence for higher order factors.
@@
 <!-- Ias structure -->
-In this study, several datasets were analyzed for a meta analysis of the structure of the IAS.
-The findings reveal that a 4-factor model fits the IAS best.
-Additionally, the lowest level structure (pairs of items) seem to be the most robust, especially for samples using Likert scales (some higher-order groupings might emerge for the 2 analog-scale samples).
-There was no clear evidence for higher-order factors.
+The comprehensive structural analysis of a large body of IAS item-level datasets revealed a 4-factor model as the most appropriate solution - consisting of strongly-related pairs of items - including **TODO: list the dimensions?**
+There was no clear evidence in favour of higher-order general factors (relative to other solutions).
+
+<!-- Additionally, the lowest level structure (pairs of items) seem to be the most robust, especially for samples using Likert scales (some higher-order groupings might emerge for the 2 analog-scale samples).
+-->
 
@@
 This organization and structure is useful for further analysis, as the data can be analyzed and interpreted according to a grouping that is coherent in result, as well as underlying mechanisms.
+
+**Reorganize the below following the order of the analysis. Group all of it into one section which would be "recommendations for improvement"**
 
@@
 Therefore, this study provides a novel approach to improving the IAS in a simple manner.
-
-### Limitations and Future Directions
-
-<!-- pooor arguments --> 
-There are several limitations to the IAS. There are some redundant items, the 5-point scale does not provide great variability, and the structure could be improved.
-Therefore, improving the IAS, or creating a new questionnaire investigating interoception could be useful to achieving reliable and accurate indication of interoceptive awareness.
 
@@
 
+## Limitations and Future Directions
+
+<!-- pooor arguments --> 
+There are several limitations to the IAS. There are some redundant items, the 5-point scale does not provide great variability, and the structure could be improved.
+Therefore, improving the IAS, or creating a new questionnaire investigating interoception could be useful to achieving reliable and accurate indication of interoceptive awareness.
+
 ## Conclusion

### 2025-03-17 paper/1_Initial/manuscript.qmd
other study 2 comments

@@
 
-Study 2 aims to investigate correlates of the IAS.
+The second study focuses on the dispositional correlates of the IAS.
+
 Correlations of the IAS will be computed to assess the relationship between subjective interoceptive accuracy and other subjective measures of interoception, mood, psychopathology, personality, and beliefs.
@@
 The EGA components captured grouping of items such as 'wind' and 'burp, 'cough' and 'sneeze', 'muscle' and 'pain'. 
+**TODO: but that's not true, we used only pairs, not EGA clusters?J**
+
 These groupings were used in correlational analysis to analyse how much each pairing is associated with other factor such as Alexithymia and with Mood disorders (see figure 2).
+
+**TODO: Massively streamline. It can be all summarize in one or two paragraphs max.**
 
@@
 <!-- strongest and weakest correlations with the IAS--> 
-Our findings confirm that interoception exists within a complex network of correlates. 
+Our findings underline how subjective measures of interoception exist within a complex network of correlates.
+
+**TODO:: Firstly, talk about the link with other interoceptive measures.**
+**Then, discuss other correlates by order of importance**
+
+**TODO: this discussion is too much descriptive for now. Discuss that from a larger perspective. What does it mean in general.**
+
 Among these, alexithymia exhibits the strongest negative correlation with the IAS, whereas the MAIA questionnaire shows the strongest positive correlation. 
@@
 ## General Discussion
+
+**The present study aimed... [always start with a description of the study]**.
 

### 2025-03-17 analysis/figures/table1.tex
major changes to manuscript
@DominiqueMakowski

please check the latest changes (lot has been done till end of result section on study 1)

@@
 Makowski et al., (2023b) &  & English & 836 & Analog scales & 25.1 ± 11.3 & 17-76 & 53.0\% & github.com/DominiqueMakowski/PHQ4R \\ 
-Makowski et al., (2023c) &  & English & 104 & Analog scales & 21.6 ± 5.0 & 18-50 & 76\% & github.com/RealityBending/InteroceptionPrimals \\ 
-Poreiro et al., (2024) &  & English & 107 &  & 26.8 ± 9.2 & 18-57 & 74.8\% & osf.io/49wbv \\ 
-Poreiro et al., unpublished &  & English & 131 &  & 30.9 ± 12.0 & 18-60 & 75.9\% &  \\ 
+Makowski et al., (2023c) &  & English & 146 & Analog scales & 21.1 ± 4.3 & 18-50 & 76\% & github.com/RealityBending/InteroceptionPrimals \\ 
+Poerio et al., (2024) &  & English & 107 &  & 26.8 ± 9.2 & 18-57 & 74.8\% & osf.io/49wbv \\ 
+Poerio et al., unpublished &  & English & 131 &  & 30.9 ± 12.0 & 18-60 & 75.9\% &  \\ 
 Total &  &  & 32214 &  & 48.6 ± 13.1 & 17-93 & 71.6\% &  \\ 

### 2025-03-17 paper/1_Initial/manuscript.qmd
major changes to manuscript
@DominiqueMakowski

please check the latest changes (lot has been done till end of result section on study 1)

@@
 <!-- EGA -->
-<!-- EGA is a powerful network-based approach for estimating the number of dimensions in psychological data while identifying which items belong to each dimension, both crucial for understanding the structure of complex constructs and improving the validity of psychological assessments [@golino2017exploratory; @markos2024dimensionality].
--->
-<!-- This new approach addresses limitations of traditional methods which can either underestimate or overestimate factor numbers depending on factors such as sample size and item correlations. -->
-<!-- By combining network analysis with psychometric methods, EGA offers a unique perspective for modeling relationships between psychological variables [@golino2020investigating].  -->
-<!-- For instance, unlike factor analysis, which assumes a common cause for observed variables, EGA conceptualizes variables as nodes in a network, with connections (edges) reflecting associations between them [@christensen2021equivalency].
--->
-<!-- Clustering these nodes reveals distinct communities of related items, which resemble latent factors without explicitly assuming their presence.  -->
-<!-- EGA has shown strong performance with binary, continuous [@cosemans2022exploratory], and more recently, ordinal data [@markos2024dimensionality], providing a flexible and reliable alternative for exploring data dimensionality.
--->
-<!-- Given the IAS's unclear factor structure and EGA's proven accuracy with complex psychological constructs, it is a suitable technique for this analysis. -->
-
 By combining network analysis with psychometric methods, the recently-developed EGA framework allows to jointly estimate the number of dimensions (i.e., groups of items), the structure as well as its stability [@golino2017exploratory; @golino2020investigating].
-Evidence has underlined its suitability as an alternative to traditional factor analysis, addressing some of its limitations such as the assumption of a "latent" source of variability, possible biasing in the estimation of the optimal factor numbers depending on sample size, and **TODO: a third example would be nice?** **REF**, while remaining comparable and interpretable [@christensen2021equivalency].
+Evidence has underlined its suitability as an alternative to traditional factor analysis, addressing some of its limitations such as the assumption of a "latent" source of variability, possible biasing in the estimation of the optimal factor numbers depending on sample size, and the poor performance of other methods in complex population structures, while remaining comparable and interpretable [@christensen2021equivalency; @jimenez2023dimensionality].
 At a fundamental level, EGA conceptualizes variables as nodes in a network, with connections (edges) reflecting associations between them. 
 Clustering these nodes reveals distinct communities of related items, in practice akin to traditional latent factors - but without explicitly assuming their presence [@christensen2021equivalency].
+<!-- By applying UVA, the analysis can maintain the integrity of the IAS while improving its efficiency and reducing redundancy. -->
 
-**TODO: Explain UVA. Rework the following paragraph**.
+<!-- UVA -->
+To assess whether the IAS contains redundant items (e.g., due to multicollinearity or local dependency), Unique Variable Analysis [UVA, @christensen2023unique] will be employed. 
+UVA is another novel network psychometric method designed to identify and merge items that share substantial variance, effectively reducing datasets to a set of unique variables. 
+Unlike other reduction methods that aim to minimize variables broadly, UVA targets redundancy specifically, preserving meaningful information that may otherwise be lost [@merritt2022experimental]. 
+By focusing on statistically redundant variables, UVA offers a middle ground between no reduction and extensive reduction approaches. 
+Simulation studies have demonstrated that using a threshold of 0.25 optimally balances accuracy and false positives, ensuring that only genuinely redundant items are combined.
 
-<!-- was used to estimate the dimensions via network estimation and community detection, alongside assessing the stability of dimensions and items using the bootstrapping techniques [@golino2017exploratory].
-The selection of EGA was motivated by its capability to handle complex, multidimensional data and provide robust dimension estimates.
-A novel network psychometrics - Unique variable analysis [UVA, @christensen2023unique] - approach based on the weighted topological overlap will be computed to evaluate which items have substantial local dependence (\> 0.25).
--->
+<!-- Factor Analysis -->
 
-In contrast, the factor analsyis framework... **TODO**. **Meention rotation and how number of factors is selected**
-We will first apply EFA to... and then identify the best fitting models using CFA.
+While EGA offers a robust alternative to traditional factor analysis, factor analysis remains a widely used method for dimensionality assessment, hence it will be also be computed in this analysis. 
+Unlike EGA, factor analysis assumes a latent source of variability — a common latent variable — underlies the observed set of manifest variables [@cosemans2022exploratory].
+A critical step in factor analysis is determining the optimal number of factors, typically achieved by examining eigenvalue patterns and applying stopping rules, such as the Kaiser-Guttman criterion (eigenvalues greater than 1) or parallel analysis.
+These methods aim to identify the most meaningful factor structure, though their performance can vary depending on sample size and data complexity [@christensen2023unique].
+
+To determine the appropriate number of factors to retain during factor analysis, the n_factors function from the performance package will be used [@ludecke2021performance]. 
+This function runs multiple established procedures for factor retention and identifies the optimal number of factors based on the maximum consensus across methods - i.e., Method Agreement Procedure. 
+These methods include the Kaiser criterion, parallel analysis,  Velicer's MAP, and others.
+Following this, EFA with the optimal number of factors identified, using 'oblimin' rotation, will be aplied. 
+Model fit using CFA to identify the best-fitting model will then be computed.
 
@@
 The distribution of the items across samples suggests the presence of a consistent modal value (@fig-distributions).
-In other words, participants are most likely to answer 4/5 (i.e., agree) on most items, with the exception of "affective touch" (**TODO: this one only seem off in samples 8 no?
-could it be a language thing?**), "blood sugar", and "bruise", which exhibit a different distributional pattern with a lower mode (\~2/5).
+In other words, participants are most likely to answer 4/5 (i.e., agree) on most items, with the exception of "blood sugar" and "bruise", which exhibit a different distributional pattern with a lower mode (\~2/5).
+This pattern persists across most samples, except for "affective touch" in samples 8a and 8b, where it deviates from the general trend. 
+In these samples, "affective touch" follows a distribution similar to that of "blood sugar" and "bruise".  **-could it be a language thing?**
 Additionally, one can note the low occurrence of extreme values (1 and 5), meaning that the bulk of answers varies between 3 values (assuming the IAS is implemented as a 5-point Likert scale following its validation).
-The samples using an analogue scale (samples 10a, 10b and 10c in the figure **what about 11?**) displaying a more continuous and progressive spread of answers, seemingly improving the interindividual variability, although potentially suggesting a second lower mode at \~2.
+The samples using an analogue scale (samples 10a, 10b and 10c in the figure) displaying a more continuous and progressive spread of answers, seemingly improving the interindividual variability, although potentially suggesting a second lower mode at \~2.
+**- sample 11's were rated on a liker-scale**
 
-**TODO: add more information to the caption to highlight some interesting things.
-What are the two items that stand out.
-Mention caveat that for most samples the undelying data is disrete (Likert scales), and hence the density plots are not the most accurate visualization method but have been chosen as the clearer to highlight what we are interested in.**
-
-**TODO: change the number of rows/cols of the figure to make it nicer (e.g., 3x6). And add x-axis on all subplots. Consider making the problematic items dashed.**.
+**TODO: And add x-axis on all subplots. Consider making the problematic items dashed.**.
 
@@
 #| label: fig-distributions
-#| fig-cap: "Distribution of responses for all items across various datasets."
-
+#| fig-cap: "Distribution of responses across datasets reveals a consistent modal value, typically around 4 or 5 (indicating agreement), except for 'blood sugar' and 'bruise,' which have lower modes.
+Most responses cluster around the middle values, with few extreme scores (1 and 5).
+Samples using an analogue scale (10a, 10b, 10c) show a more continuous distribution and increased interindividual variability.
+Since most samples use Likert scales (discrete), the density plots may not be the most accurate representation but were chosen to clearly highlight variability patterns in the data."
+#|
 knitr::include_graphics("figures/Figure1.png")
@@
 
-<!-- Network analysis -->
-Applying EGA to all data sets yielded 4 clusters as the optimal solution; C1.
+<!-- Network analysis and Strcuture stability -->
+
+**TO DOM: I put a bunch of info from the fucntion you created an the package documentation. Let me know what you want to keep from this information**
+
+The EGA analysis employed a sparse Gaussian graphical model with the graphical lasso (glasso) method. 
+To identify community structures, both the Louvain and Walktrap algorithms were applied.
+The Walktrap algorithm identified an optimal solution with five clusters, whereas the Louvain algorithm indicated an optimal solution with four clusters. 
+To assess the stability of these solutions, a bootstrap resampling approach was implemented, evaluating stability based on the proportion of bootstrap samples in which the original structure was replicated.
+The four-cluster solution demonstrated greater item stability, with a higher proportion of items consistently appearing within the same dimension across bootstrap samples.
+In this solution, item stability for all variables exceeded 0.91, with the exception of "affective touch" in the four-cluster solution, which showed comparatively lower stability.
+Nevertheless, this solution was considered the most optimal; C1.
 "itch", "tickle", "bruise", "blood sugar"; C2.
@@
 "heart", "breathing", "hungry", "thirsty", "urinate", and "defecate".
-**TODO: if these clusters are consistent with the factor dimensions below, consider naming them**
-Most items, except for "affective touch", demonstrated a high structural stability **what that means needs to be explained in the section above**.
 This solution was generally consistent within the data sets, although some samples yielded 3- or 5- clusters as the optimal structure.
 
+**EGA Clusters not consistent with FA dimensions**
+<!-- EGA clusters 
+c1- "itch", "tickle", "bruise", "blood sugar
+c2- burp", "wind", "cough", "sneeze", "vomit"
+c3 - affective touch", "sexual arousal", "muscles", "temperature", "pain", and "taste"
+c4- "heart", "breathing", "hungry", "thirsty", "urinate", and "defecate"
+
+<!-- FA clusters -->
+<!-- c1 - burp, cough, wind, sneeze, vomit, temp, sexual arousal, taste
+c2 - breathing, hungry, heart, thirsty, pain, muscles , blood sugar, bruise
+c3 - tickle, itch, affective touch,
+c4 - urinate, defecate -->
+
 <!-- Factor analysis -->
-**TODO: explain how we obtained the optimal number of factors**
-Across all samples, the Method Agreement Procedure to find the optimal number of latent factors suggested a 4-factors solution, accounting for 41.58% of the total variance.
-**describe the loading items** **does it match the clusters above?** (MR1 = 14.45%, MR3 = 11.76%, MR2 = 8.09%, MR4 = 7.28%).
 
-**TODO: rework the CFA part below**
+**TODO: explain how we obtained the optimal number of factors** -->  **I think i explained it above on the analysis bit, please confirm whether there needs to be more info** 
+Across all samples, the Method Agreement Procedure recommended a four-factor solution. 
+Approximately 30% of the tested methods — the Beta method, Optimal Coordinates, Parallel Analysis, and the Kaiser criterion — converged on this as the optimal number of factors to retain.
 
-<!-- Removal of items before the CFA -->
-Since UVA identified "tickle" as the item to be removed—and it had the lowest uniqueness value in factor analysis, with a loading similar to "itch"—it was excluded from subsequent analyses.
-Additionally, several items were removed due to ambiguity, in which ....
+In line with the Method Agreement Procedure's recommendation, a four-factor solution was extracted using an oblimin rotation, accounting for 41.58% of the total variance.
+The first factor included items "burp," "cough," "wind," "sneeze," "vomit," "temperature," "sexual arousal," and "taste," explaining 14.45% of the total variance. 
+The second factor incuded "breathing," "hungry," "heart," "thirsty," "pain," "muscles," "blood sugar," and "bruise," accounting for 11.76% of the variance. 
+The third factor contained "tickle," "itch," and "affective touch," explaining 8.09% of the total variance. 
+Lastly, the fourth factor included "urinate" and "defecate," accounting for only 7.28% of the total variance.
+Notably this grouping differs from that of the EGA's four cluster optimal solution.
+
+<!-- CFA -->
+Throughout the EGA and EFA analyses, the item "tickle" was consistently identified as redundant and was flagged for removal in the UVA analysis. 
+It also demonstrated the lowest uniqueness value in the factor analysis, leading to its exclusion from further analysis.
+SSimilarly, several "ambiguous" items — such as "temp", "vomit", "affective touch", "sexual arousal", and "taste" — were removed due to their context-dependent nature, which may compromise measurement consistency and reduce the clarity of factor structure.
 **need to add reasoning for the removal of 'ambiguous items'**
 
+**TO DOM: HELP WITH AMBIGUOUS REASONING PLEASE**
+
 <!-- Confirmatory factor analysis -->
-CFA analysis compared 5 models: a single-factor solution, a 4-factor solution, a 5-factor solution, a 6-factor solution and a 7-factor solution. 
-The latter, which composed of pairs of items was preferred in most datasets, including with indices that penalise increased number of parameters (such as BIC).
-Lastly, there was no evidence for higher order factors.
+CFA was performed to identify the best-fitting model for the data. 
+A total of five models were computed: Model 1 assumed a general interoception factor (1-factor solution), Model 2 proposed four factors, Model 3 assumed five factors, Model 4 proposed six factors, and Model 5, the most refined model, separated the factors into smaller, more specific groups, resulting in a 7-factor solution.
+
+<!-- Model Fit + lower-level factors + high-order factors-->
+The results of model comparison indicate that the Model 5 - with 7 factors  - had the best fit among all the models (AIC = -171638, BIC = -171228, χ² (56) = 2195.20, p < .001). 
+Parameter estimates for the model with 7 factors were also analyzed, with all factor loadings found to be significant (p < .001) and standardized coefficients ranging from 0.50 to 0.82. 
+Furthermore, the correlations between latent factors were all significant, ranging from 0.43 to 0.80, with the strongest correlation observed between ItchBruise and MusclesPain (0.80).
+
+<!-- higher- level factors -->
+To assess whether the inclusion of higher-order factors was justified, three models were evaluated. 
+Model 1 assumed one higher-order factor. 
+Model 2 introduced two higher-order factors, while Model 3 included three higher-order factors. 
+The baseline model, which consisted of 7 factors, was compared with these alternative models. 
+The results indicated that the baseline model provided the best fit (AIC = -171638, BIC = -171228, χ²(56) = 2195.20, p < .001), suggesting no evidence to support the inclusion of higher-order factors.
+
+<!-- Model Performance -->
+When taking acount all the samples, the fit statistics indicated a very good model fit (χ²(56) = 2195.20, p < .001, RMSEA = 0.03, CFI= 0.98 SRMR = 0.92) for the model with 7-factors.
+These fit statistics collectively suggest that the model adequately represents the data structure.
+Overall, the CFA results suggest that Model 7 provides the best fit for the data, with significant factor loadings and strong correlations between the factors.
 
@@
 <!-- Ias structure -->
-The comprehensive structural analysis of a large body of IAS item-level datasets revealed a 4-factor model as the most appropriate solution - consisting of strongly-related pairs of items - including **TODO: list the dimensions?**
+The comprehensive structural analysis of a large body of IAS item-level datasets revealed a 4-factor model as the most appropriate solution - consisting of strongly-related pairs of items - including including Hungry/Thirsty, Urinate/Defecate, ItchBruise, Muscles/Pain, Heart/Breathing, Cough/Sneeze, and Wind/Burp,
 There was no clear evidence in favour of higher-order general factors (relative to other solutions).

### 2025-03-19 paper/1_Initial/manuscript.qmd
big changes to manuscript

@@
 **TODO: explain how we obtained the optimal number of factors** -->  **I think i explained it above on the analysis bit, please confirm whether there needs to be more info**
+
 Across all samples, the Method Agreement Procedure recommended a four-factor solution. 
@@
 It also demonstrated the lowest uniqueness value in the factor analysis, leading to its exclusion from further analysis.
-SSimilarly, several "ambiguous" items — such as "temp", "vomit", "affective touch", "sexual arousal", and "taste" — were removed due to their context-dependent nature, which may compromise measurement consistency and reduce the clarity of factor structure.
-**need to add reasoning for the removal of 'ambiguous items'**
-
-**TO DOM: HELP WITH AMBIGUOUS REASONING PLEASE**
+Similarly, several "ambiguous" items — such as "temp", "vomit", "affective touch", "sexual arousal", and "taste" — were removed due to their context-dependent nature as well as weak loadings on multiple factors, which may compromise measurement consistency and reduce the clarity of factor structure.
 
@@
 
-<!-- Ias structure -->
-The comprehensive structural analysis of a large body of IAS item-level datasets revealed a 4-factor model as the most appropriate solution - consisting of strongly-related pairs of items - including including Hungry/Thirsty, Urinate/Defecate, ItchBruise, Muscles/Pain, Heart/Breathing, Cough/Sneeze, and Wind/Burp,
-There was no clear evidence in favour of higher-order general factors (relative to other solutions).
+The comprehensive structural analysis of a large body of IAS item-level datasets revealed a 4-factor model as the most appropriate solution when taking into account all the items in the scale. 
+These findings contrast with previous research which all found that 2-factor model [@murphy2019; @koike2023], 1-factor model [@brand2023] and bifactor model [@lin2023; @campos2021] fits the data best.
+While this analysis also revealed an okay fit for the 1-factor model, the 4-factor model was ultimately superior.
+Notably, this 4-factor solution was found in both the EGA and EFA analysis, altough groupings differed.
 
-<!-- Additionally, the lowest level structure (pairs of items) seem to be the most robust, especially for samples using Likert scales (some higher-order groupings might emerge for the 2 analog-scale samples).
--->
+<!-- EGA groupings -->
+The EGA analysis revealed different ‘hubs' of items that are related, not only in this structure analysis, but also in underlying mechanisms.
+The ‘wind-burp-cough-sneeze-vomit' category, for example, only entails items that are linked to excretion through the mouth. 
+The 'heart-breathing-hungry-urinate-defecate' category includes items linked to basic physiological functions essential for homeostasis and survival.
+The 'affective-touch-sexual arousal-temperature-pain-taste-muscles' category represents sensations closely tied to both affective experiences and bodily awareness.
+Lastly, the 'tickle-itch-bruise-blood-sugar' category includes items that reflect more localized or transient bodily sensations, often linked to surface-level or metabolic responses.
 
-<!-- linking findings to previous research -->
+<!-- EFA groupings -->
+The EFA groupings, in contrast, revealed a less balanced division of items into clusters.
+One factor consisted of just two items—'urinate' and 'defecate'—while another contained three items—'tickle', 'itch', and 'affective touch'.
+Of notice is the loading for 'affective touch' as 0.33, barely meeting the acceptable threshold of >0.32 [@costello2005best], while the other items in this factor had loadings above 0.75.
 
-These findings contrast with previous research, which all found that 2-factor model [@murphy2019; @koike2023], 1-factor model [@brand2023] and bifactor model [@lin2023; @campos2021] fits the data best.
-While this analysis also revealed an okay fit for the 1-factor model, the 4-factor model was superior.
-The 4-factor structure reveals different ‘hubs' of items that are related, not only in this structure analysis, but also in underlying mechanisms.
-The ‘wind-burp-cough-sneeze-vomit' category, for example, only entails items that are linked to excretion through the mouth.
-The other categories are organized similarly.
-This organization and structure is useful for further analysis, as the data can be analyzed and interpreted according to a grouping that is coherent in result, as well as underlying mechanisms.
+<!-- CFA -->
+While the 4-factor structure repeatedely showed up reagrdless of the dimensionality method, some items were flagged as redudant and in particular 'tickle' was suggested to be removed. 
+Additionally, some items appear to be ambiguous, as their interpretation and grouping may be contextually dependent.
+For instance, sensations such as feeling one's heart beat faster and experiencing nausea-related urges to vomit often co-occur.
+This overlap is not merely coincidental; these sensations may reflect interconnected physiological processes, such as autonomic arousal or the body's stress response. 
+Such interdependencies challenge the assumption that IAS items neatly map onto distinct bodily sensations. 
+Empirical evidence further highlights item ambiguity. 
+Items such as 'taste' showed similarly weak loadings across multiple factors (0.24 for Factor 1 and 0.20 for Factor 3), falling below the commonly accepted threshold for meaningful loadings. 
+Likewise, 'temperature' loaded weakly on both Factor 1 (0.26) and Factor 3 (0.25), while 'sexual arousal' demonstrated similarly low and split loadings (0.25 to Factor 1 and 0.23 to Factor 3). 
+Although 'vomit' showed a slightly stronger loading on Factor 1, its context-dependent nature further complicates its conceptual clarity.
+Consequently, refining the scale by removing items with overlapping or ambiguous content could enhance its precision, ensuring that each item captures a unique and meaningful aspect of interoceptive awareness.
+Based on this, the CFA was conducted with 14 items out of the 21, suggetsing that 7-factors (i.e., pairs of items) is the model with the best fit for the data.
 
-**Reorganize the below following the order of the analysis. Group all of it into one section which would be "recommendations for improvement"**
-
-<!-- Items redundancy -->
-
-**note to dom**: what stats do you mean here? the UVA one?
-
-There are several items that show redundancy suggesting that adapting the IAS would be beneficial for validity.
-Based on the given results, we suggest removing the tickle, while keeping the itch item  \[**todo**: stats?\].
-Other items with slight redundancy were "hungry" and "thirsty", "urinate" and "defecate", and "sneeze" and "cough".
-
-<!-- Lins short IAs kept: Hunger, Breath, Urinate, Taste, Vomit, Cough, Temperature, Sexual Arousal, Wind, Muscle, Pain, Itch -->
-
-Interestingly, @lin2023 also found that "tickle" and "itch" were redundant, which led them to exclude one of them.
-Although, the reason being that the character for both words is the same in the Chinese language.
-On top of that, they came up with a shortened version of the IAS, excluding further items, resulting in a 12-item IAS, which aligns with our findings, suggesting that further items are ambiguous as to whether they should be removed.
-Their 12-item IAS included the "hunger", "breath", "urinate", "taste", "vomit", "cough", "temperature", "sexual arousa", "wind", "muscle", "pain", "itch" items.
-In contrast, other findings also found "tickle" to be redundant but did not suggest excluding items [@campos2021].
-
-<!-- low density on extreme values (1 and 5) -->
-
+<!-- Recomendations -->
+There are couple recomendations that follow from this mega-analysis on the IAS.
 The findings indicate a high proportion of answers at 4 (see @fig-distributions), especially when using a 5-step scale.
 The analogue scale shows a more dispersed distribution, with some answers indicating the highest 5/5, which was not the case in Likert-scales.
-Therefore, we recommend using an analog scale for the IAS.
+Therefore, we recommend using an analog scale for the IAS, which provides a novel approach to improving the scale in a simple manner.
 
-Before this paper, the IAS had not yet been used or analyzed with an analog scale, rather than a five-step scale.
-Therefore, this study provides a novel approach to improving the IAS in a simple manner.
+<!-- removal of tickle and potential for a short version of the IAS -->
+Secondly, there are several items that show redundancy suggesting that adapting the IAS would be beneficial for validity.
+Based on the given results, we suggest removing the tickle, while keeping the itch item  \[wTO = 0.364\].
+Other items with moderate redundancy include 'wind' and 'burp', as well as 'urinate' and 'defecate'. 
+Additionally, there are pairs with slight redundancy, such as 'hungry' and 'thirsty', 'sneeze' and 'cough', and 'heart' and 'breathing'.
+Interestingly, @lin2023 also found redundancy between 'tickle' and 'itch', ultimately deciding to exclude the former due to the fact that the characters for both terms are identical in the Chinese language.
+In contrast, @campos2021 also found 'tickle' to be redudant but did not suggest excluding it from the analysis.
+@lin2023 also developed a shortened version of the IAS, removing additional items to create a 12-item scale, including the following items:'hunger', 'breath', 'urinate', 'taste', 'vomit', 'cough', 'temperature', 'sexual arousal', 'wind', 'muscle', 'pain', and 'itch'.
+As demonstrated by @lin2023, reducing redundancy and streamlining the scale through a short-form IAS can improve the model fit and enhance the scale's unidimensionality, ultimately making it a more efficient tool for assessing interoceptive accuracy.
+<!-- ...aligns with our findings, suggesting that further items are ambiguous as to whether they should be removed. -->
+
+<!-- Context-specific items -->
+
+The IAS aims to measure subjective interoceptive accuracy by assessing individuals' self-reported ability to detect internal bodily sensations. 
+However, the interpretation of these sensations is highly dependent on their physiological context. 
+Sensations such as heart rate acceleration, breathing changes, or muscle soreness can arise in diverse contexts — for instance, during exercise, emotional arousal, or illness. 
+Without considering the underlying physiological context, individuals may misattribute these sensations to different causes, potentially confounding their self-assessments.
+For example, a fast heartbeat may be accurately detected but interpreted as anxiety rather than exertion.
+Similarly, sensations like nausea or sexual arousal may fluctuate in intensity depending on contextual factors such as stress, fatigue, or hormonal cycles.
+In fact, previous research has highlighted the need for interoceptive questionnaires to prioritize neutral bodily sensations that are less susceptible to cognitive or emotional reinterpretation [@vlemincx2023novel].
+
+<!-- Conclusion -->
+In conclusion this study provided valuable insights into the structure and content of the IAS. 
+While the original factor structure was not replicated, our findings revealed a more stable 4-factor model that emerged across both EGA and EFA approaches. 
+This structure highlights meaningful item clusters that align with underlying physiological processes, improving our understanding of subjective interoceptive accuracy.
+However, our analysis also uncovered several limitations that warrant further attention. 
+The presence of redundant items (e.g., ‘tickle’) and items with ambiguous or weak factor loadings (e.g., ‘taste’ and ‘temperature’) suggests a need for scale refinement. 
+Adopting an analog scale format may further enhance variability and improve response accuracy. 
+Additionally, the observed overlap between context-dependent sensations underscores the importance of developing items that account for physiological contexts to minimize misattributions.
 
@@
 Investigating correlates will help validate the IAS, as well as other interoceptive measures in the future.
+
+<!-- what factor structure to choose -->
 

### 2025-06-19 paper/1_Initial/manuscript.qmd
more edits to intro

@@
     roles:
-      - Project administration
       - Data curation
@@
     #   - Writing – original draft
-  # - name: Magdalena Pfaff
-  #   orcid: 0009-0006-2386-7936
-  #   affiliations:
-  #     - ref: "id1" 
-  # - name: Dominique Makowski
-  #   corresponding: true
-  #   orcid: 0000-0001-5375-9967
-  #   email: D.Makowski@sussex.ac.uk
-  #   url: https://realitybending.github.io/
-  #   roles:
-  #   affiliations:
-  #     - ref: "id1"
-  #     - name: "University of Sussex"
-  #       department:  "Sussex Centre for Consciousness Science"
+  - name: Magdalena Pfaff
+    orcid: 0009-0006-2386-7936
+    roles:
+      - Data curation
+      - Writing – original draft
+    affiliations:
+      - ref: "id1"
+  - name: Dominique Makowski
+    corresponding: true
+    orcid: 0000-0001-5375-9967
+    email: D.Makowski@sussex.ac.uk
+    url: https://realitybending.github.io/
+    roles:
+      - Project administration
+      - Data curation
+      - Formal Analysis
+      - Investigation
+      - Visualization
+      - Writing – original draft
+      - Writing – review & editing
+    affiliations:
+      - ref: "id1"
+      - name: "University of Sussex"
+        department:  "Sussex Centre for Consciousness Science"
 author-note:
@@
     # Can be jou (journal), man (manuscript), stu (student), or doc (document)
-    documentmode: man
+    documentmode: jou
     include-in-header:
@@
 
+## Introduction
+
 <!-- Interoception definition -->
@@
 
+### The Interoceptive Assessment Puzzle
+
 <!-- Interoception measure -->
 
-Various measures of interoception have been developed (see @fig-measures), forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking *vs.* questionnaires and subjective scales involving a metacognitive reflection), "explicit" and "implicit" paradigms (i.e., directing participants' awareness and attention to interoceptive processes *vs.* measuring interoception unbeknownst to them), various interoceptive modalities (e.g., cardioception, respiroception, gastroception) and theoretical dimensions (e.g., accuracy, sensitivity, awareness).
+Various measures of interoception have been developed (see @fig-measures), forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking *vs.* questionnaires and subjective scales involving metacognitive judgments), "explicit" and "implicit" paradigms (i.e., directing participants' awareness and attention to interoceptive processes *vs.* measuring interoception unbeknownst to them), various interoceptive modalities (e.g., cardioception, respiroception, gastroception) and theoretical dimensions (e.g., accuracy, sensitivity, awareness).
 While there is no consensus as to which particular approach provides the most accurate and "pure" measure of interoception and interoceptive abilities (assuming it is a unidimensional construct), it is instead plausible that each measure has strengths and limitations, and a utility dependent on the context and goal at hand [@jahedi2014; @Desmedt2023accuracy].
@@
 #| label: "fig-measures"
-#| apa-twocolumn: false  # A Figure Spanning Two Columns When in Journal Mode
+#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
 #| out-width: "100%"
-#| fig-cap: "The different modalities of interoception (e.g., cardioception) can be assessed directly or indirectly.
+#| fig-cap: "The Interoceptive Assessment Puzzle.
+The different modalities of interoception (e.g., cardioception) can be assessed directly or indirectly.
 Direct assessments can further be subjective or objective, depending on whether they involve conscious metacognitive appraisals or more performance-based indices.
@@
 
-knitr::include_graphics("figures/MeasuringInteroception.jpg")
+knitr::include_graphics("figures/MeasuringInteroception.png")
 ```
@@
 Moreover, the notion that self-reports might not reflect the same processes as other interoception tasks might be important to contextualize the apparent lack of convergence between measures in the field [@desmedt2022measures].
-For instance, existing findings typically show weak or no correlations between questionnaires and objective measures [including for measures of the same theoretical dimensions, e.g., task-based accuracy vs.
-self-reported accuracy, @murphy2019; @brand2023; @arslanova2022], such as the Heartbeat Counting Task [HCT, @schandry1981heart] and the Heartbeat Detection Task [HDT, @kleckner2015methodological].
-Additionally, objective measures assessing the same interoceptive dimension, such as accuracy, either show no correlation [e.g., @brand2023] or only weak correlations [e.g., @hickman2020relationship].
-Perhaps more surprisingly, low correlations have been observed even among questionnaires, suggesting the targeting of different facets related to interoception.
-
-<!-- 
-Garfinkel - sensibility-> Self-perceived dispositional tendency to be internally self-focused and interoceptively cognisant,
-Khalsa - sensibility -> Self-perceived tendency to focus on interoceptive stimuli (trait measure)
-Khalsa self-report scales -> The ability to reflect upon one’s autobiographical experiences of interoceptive states, make judgments about their outcomes, and describe them through verbal or motor responses.
--->
+For instance, existing findings typically show weak or no correlations between questionnaires and objective measures, such as the Heartbeat Counting Task [HCT, @schandry1981heart] and the Heartbeat Detection Task [HDT, @kleckner2015methodological], including for measures of the same theoretical dimensions [e.g., task-based accuracy vs.
+self-reported accuracy, @murphy2019; @brand2023; @arslanova2022].
+Additionally, even various objective measures assessing in theory the same interoceptive dimension, such as accuracy, either show no or weak correlation [respectively, @brand2023; @hickman2020relationship].
+Perhaps more surprisingly, low correlations have been observed even among questionnaires, suggesting (in parallel to major validity concerns) the potential targeting of different facets related to interoception.
 
 One striking example concerns the assessment of interoceptive sensibility, which is broadly defined as the self-reported tendency to focus on and detect internal sensations [@garfinkel2015knowing], but more narrowly as the subjective tendency to focus on interoceptive signals, without necessarily implying detection ability [@khalsa2018interoception].
-A recent systematic review suggested that various questionnaires designed to assess interoceptive sensibility may, in fact, measure distinct constructs, leading researchers to treat them as equivalent despite overall low convergence [@desmedt2022measures].
-
-Notably, this review adopted a broad definition of 'sensibility,' incorporating both interoceptive sensibility and interoceptive self-report scales, as described in @khalsa2018interoception's eight-facet model.
-In this framework, self-report measures are categorized into interoceptive sensibility and interoceptive self-report scales (i.e., the ability to evaluate one's personal experiences of internal bodily states, assess their consequences, and articulate them through speech or movement).
+A recent systematic review suggested that various questionnaires designed to assess interoceptive sensibility may, in fact, measure distinct constructs, with the risk of researchers treating them as equivalent despite overall low convergence [@desmedt2022measures].
+Notably, this review adopted a broad definition of sensibility, incorporating both interoceptive sensibility and interoceptive self-report scales, following the eight-facet model by @khalsa2018interoception.
+<!-- In this framework, self-report measures are categorized into interoceptive sensibility and interoceptive self-report scales (i.e., the ability to evaluate one's personal experiences of internal bodily states, assess their consequences, and articulate them through speech or movement).
+-->
 Several widely used questionnaires were included in the review, such as the Multidimensional Assessment of Interoceptive Awareness [MAIA, @mehling2012; MAIA-2, @mehling2018multidimensional], the Body Perception Questionnaire [BPQ, @porges1993body], the Private subscale of the Body Consciousness Questionnaire [PBCS, @miller1981consciousness], the Body Awareness Questionnaire [BAQ, @shields1989body], and the Eating Disorder Inventory [EDI, @garner1991eating; @garner1983].
@@
 
+### The Interoceptive Accuracy Scale (IAS)
+
 <!-- Introducing the IAS -->
 
-A recently developed scale with a rapidly growing popularity is the Interoceptive Accuracy Scale [IAS, @murphy2019].
+Focusing on another dimension of interoception, a recently developed scale with a rapidly growing popularity is the Interoceptive Accuracy Scale [IAS, @murphy2019].
 The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological modality such as respiration (*"I can always accurately perceive when I am breathing fast"*), heart (*"I can always accurately perceive when my heart is beating fast"*), skin (*"I can always accurately perceive when something is going to be ticklish"*), arousal or bodily functions like coughing (*"I can always accurately perceive when I am going to cough"*) or urinating (*"I can always accurately perceive when I need to urinate"*).
@@
 <!-- IAS structure  --> 
-Although the original validation study suggested a two-factor structure for the IAS: one reflecting the perception of general interoceptive signals (i.e., urinate, hungry, defecate, thirsty, pain, heart, taste, breathing, temperature, mulscles, affective touch, vomit, sexual arousal), and other relating to signals that may be difficult to perceive solely through interoceptive information (i.e., itch, tickle, cough, burp, bruise, blood sugar, sneeze, wind).
+The original validation study suggested a two-factor structure for the IAS, one reflecting the perception of general interoceptive signals (urinate, hungry, defecate, thirsty, pain, heart, taste, breathing, temperature, muscles, affective touch, vomit, sexual arousal), and other relating to signals that may be difficult to perceive solely through interoceptive information (itch, tickle, cough, burp, bruise, blood sugar, sneeze, wind).
 The authors however underlined its acceptable but imperfect fit [@murphy2019, p. 127], and several follow-up studies have indeed identified different optimal solutions. 
-For instance, @brand2023 reported a 1-factor solution, while @lin2023 - using a new approach to structure analysis, namely Exploratory Graph Analysis [EGA, @golino2017exploratory]- and @campos2021 found bifactor solutions, that is one general factor above a set of lower-level factors [@rodriguez2016evaluating],  to be the best fit.
+For instance, @brand2023 reported a 1-factor solution, while @lin2023 - using Exploratory Graph Analysis [EGA, @golino2017exploratory] - and @campos2021 found bifactor solutions [i.e., one general factor above a set of lower-level factors, @rodriguez2016evaluating] to be the best fit.
+Using a 2-factors Exploratory Factor Analysis (EFA), @koike2023 suggested that the items could be grouped into cutaneous (itching, tickling, coughing, burping, affective touch, bruising, passing gas, sneezing, muscle sensations, sexual arousal, and taste) and visceral sensations (urination, defecation, hunger, thirst, pain, breathing, fatigue/blood sugar, temperature, vomiting, and heartbeat).
 
@@
 119).
-@lin2023 also highlights their correlation analysis, showing five locally dependent pairs and three items (touch, blood sugar, bruise) with exceptionally high difficulty and low discrimination, and @campos2021 reported "tickle" to be the only item that reflected more specific factors than the general factor.
-
-Localization issues also arose in @lin2023 validation of the IAS, where both "itch" and "tickle" correspond to the same Chinese character, leading to their collapse into a single item. 
-Notably, the only other study to report a 2-factor solution was conducted by @koike2023, who performed an Exploratory Factor Analysis (EFA) assuming 2 factors to align with the findings from the original validation paper.
-According to the authors, the first factor appears to reflect cutaneous sensations (i.e., itching, tickling, coughing, burping, affective touch, bruising, passing gas, sneezing, muscle sensations, sexual arousal, and taste), while the second factor seems to represent visceral sensations (i.e., urination, defecation, hunger, thirst, pain, breathing, fatigue/blood sugar, temperature, vomiting, and heartbeat).
+@lin2023 additionally highlights five locally dependent pairs and three items (touch, blood sugar, bruise) with exceptionally high difficulty and low discrimination, and @campos2021 reported "tickle" to be the only item that reflected more specific factors than the general factor.
+Furthermore, localization issues also arose, with both "itch" and "tickle" corresponding to the same Chinese character, leading to their collapse into a single item [@lin2023].
 
@@
 
-Regarding its validity, the IAS has naturally been compared to other interoception-related measures, and shows a positive correlations with most facets of the MAIA [@mehling2018multidimensional], except for the Not-Distracting and Not-Worrying subscales [@brand2023] - which were highlighted previously as related to non-interoceptive abilities [@ferentzi2021examining].
+Regarding its validity, the IAS has naturally been compared to other interoception-related measures, and shows a positive correlations with most facets of the MAIA [@mehling2018multidimensional], except for the Not-Distracting and Not-Worrying subscales [@brand2023] - which were previously highlighted as related to non-interoceptive abilities [@ferentzi2021examining].
 Interestingly, findings on the correlation between the IAS and the body awareness dimension of the BPQ (i.e., BPQ-A) have been mixed: some studies report small positive correlations [@brand2023; @campos2021; @koike2023], while others find small negative correlations [@lin2023] or no correlation at all [@murphy2019].
 Small positive correlations have also been observed with the "observation" and "description" subscales of the Five Facet Mindfulness Questionnaire [FFMQ, @baer2006using; @brand2023; @koike2023], as well as with the "non-reactivity" and "acting with awareness" subscales [@koike2023].
-Additionally, the IAS has shown a positive correlation with the interoceptive awareness subscale of the EDI [@lin2023] and a negative correlation with the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia], as reported by @brand2023 and @murphy2019.
-Lastly, no correlations have also been reported with the Interoceptive Attention Scale [IATS, @gabriele2022dissociations], though studies have also found small positive correlation between these measures [@lin2023; @koike2023].
+Additionally, the IAS has shown a positive correlation with the interoceptive awareness subscale of the EDI **Write full name** [EDI, @lin2023] and a negative correlation with the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia], as reported by @brand2023 and @murphy2019.
+Lastly, the correlation with the Interoceptive Attention Scale [IATS, @gabriele2022dissociations] **is that the ref for the scale validation?** appears rather small [@lin2023; @koike2023].
 
@@
 While assessing the predictive validity of an interoception scale can be conceived as theoretically challenging, expected negative associations were observed between the IAS and alexithymia [@brand2023; @koike2023; @campos2021; @murphy2019; @lin2023], somatic symptoms [@brand2023; @koike2023; @lin2023], depressive symptoms [@brand2023; @koike2023; @lin2023], anxiety [@brand2023], neuroticism [@brand2023] and self-esteem [@murphy2019].
+Taken together, these findings support the IAS as measuring an adaptive aspect of interoception, although its pattern of associations with other interoception (or interoception-related) questionnaires points towards some overlap across various theoretical dimensions, casting some doubt on the orthogonal models of interoception and the possibility of its faithful capture by questionnaires.
 
@@
 The current study aims at 1) clarifying the structure of the IAS with a mega-analytic (which involves a re-analysis at the raw data level by aggregating datasets) approach that leverages existing data and contrast the traditional CFA/SEM factor-based analyses with network-based ones (Exploratory Graph Analysis);
-2) the second part will provide an overview of the dispositional correlates of the IAS, clarifying the pattern of associations which is key to better understand the nature, place and role of interoception questionnaires within a larger context.
+2) provide an overview of the dispositional correlates of the IAS, clarifying its general pattern of associations, which is key to better understand the nature, place and role of interoception questionnaires within a larger context.
 

### 2025-06-21 analysis/Study1.qmd
edits to paper

@@
 ---
-title: "Meta-analysis of the Interoceptive Accuracy Scale (IAS)"
+title: "Mega-analysis of the Interoceptive Accuracy Scale (IAS)"
 subtitle: "Study 1"
@@
 table <- data.frame(
-   Sample = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Makowski et al., (2023c)', 'Poreiro et al., (2024)', 'Poreiro et al., unpublished', 'Total'),
+   Sample = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Makowski et al., (2023c)', 'Poerio et al., (2024)', 'Poerio et al., unpublished', 'Total'),
   Subsample = c('', 'Sample 1', 'Sample 2', '', '', '', '', '', '', 'Sample 1', 'Sample 2', 'Sample 3', '', 'Sample 1', 'Sample 2', '', '', '', '', '','', ''),   
@@
 
+linetype <- setNames(rep("solid", length(vars)), vars)
+linetype["Affective touch"] <- "dotted"
+linetype["Blood sugar"] <- "dashed"
+linetype["Sex arousal"] <- "solid"
+linetype["Bruise"] <- "dashed"
+
 # proportion of non-1 and non-5 values 
@@
 p1 <- p1_data |>
-  mutate(Sample = fct_relevel(Sample, "Sample 1a", "Sample 1b", "Sample 2", "Sample 3", "Sample 4", "Sample 5", "Sample 6", "Sample 7a", "Sample 7b", "Sample 7c", "Sample 8a", "Sample 8b", "Sample 9", "Sample 10a", "Sample 10b", "Sample 10c", "Sample 11a", "Sample 11b")) |>
+  mutate(Sample = fct_relevel(Sample, "Sample 1a", "Sample 1b", "Sample 2", "Sample 3", "Sample 4", "Sample 5", "Sample 6", "Sample 7a", "Sample 7b", "Sample 7c", "Sample 8a", "Sample 8b", "Sample 9", "Sample 10a", "Sample 10b", "Sample 10c", "Sample 11a", "Sample 11b"),
+         Parameter = ifelse(Parameter == "Affective_touch", "Affective touch", Parameter),
+         Parameter = ifelse(Parameter == "Blood_Sugar", "Blood sugar", Parameter),
+         Parameter = ifelse(Parameter == "Sex_arousal", "Sex arousal", Parameter)) |>
   # mutate(Dashed = ifelse(Parameter %in% c("Affective_touch", "Blood_Sugar", "Bruise"), TRUE, FALSE)) |> 
   ggplot(aes(x = x, y = y, color = Parameter)) +
-  geom_line() +
+  geom_line(aes(linetype = Parameter), linewidth = 0.7) +
   scale_color_material_d() +
-  scale_linetype_manual(values = c("solid", "dashed"), guide="none") +
+  scale_linetype_manual(values = linetype) +
   theme_minimal() +
@@
         plot.title = element_text(face="bold")) +
-  labs(x = "Response", y = "Density", color = "Item") +
-  facet_wrap(~Sample, scales = "free_y", nrow = 5)
-
-ggsave("figures/Figure1.png", p1, width=10, height=10, dpi=200, bg="white")
+  labs(x = "Response", y = "Distribution", color = "Item", linetype = "Item") +
+  facet_wrap(~Sample, scales = "free_y", nrow = 3)
+
+ggsave("figures/Figure1.png", p1, width=12, height=7, dpi=300, bg="white")
 p1
-
 ```

### 2025-06-21 paper/1_Initial/manuscript.qmd
edits to paper

@@
 
-## Introduction
+# Introduction
 
@@
 
-### The Interoceptive Assessment Puzzle
+## The Interoceptive Assessment Puzzle
 
@@
 
-### The Interoceptive Accuracy Scale (IAS)
+## The Interoceptive Accuracy Scale (IAS)
 
@@
 
-## Study 1
+# Study 1
 
 Study 1 will re-analyse and assess the factor structure of the IAS by taking advantage of the large number of open-access datasets [@brand2023; @campos2021; @lin2023; @murphy2019; @arslanova2022; @todd2022; @gaggero2021; @brand2022; @von2023].
-While combining these studies might provide a more robust and generalizable understanding of the IAS' factor structure, we also additionally provide an individual analysis (i.e., on all samples separately) to add nuance to the general picture, as all studies differ in their sample size, demographic characteristics, language, and procedure.
+While combining these studies might provide a more robust and generalizable understanding of the IAS' factor structure, we also additionally provide an individual analysis (i.e., applying the same method on all samples separately) to add nuance to the general picture, as all studies differ in their sample size, demographic characteristics, language, and procedure.
 
-### Methods
+## Methods
 
-#### Datasets
+### Datasets
 
@@
 To qualify for inclusion, papers needed to (1) provide accessible data in open-access, (2) employ the IAS as a measure, and (3) report individual IAS items scores.
-We also included the data of four unpublished (but already open-access) studies.
-A total of 14 studies was included (see **Table 1**).
+We also included the data of four unpublished studies.
+A total of 14 datasets was included (see **Table 1**).
 
@@
 
-#### Data Analysis
+### Data Analysis
 
-Psychometrically good items should exhibit various qualities, such as validity and reliability, and one of the contributing factors is the amount of variability captured by an item.
-Items to which all participants' answers are concentrated around one option - i.e., exhibiting a narrow distribution - should be flagged as potentially problematic.
+Psychometrically good items should exhibit various qualities, such as validity, reliability and discrimination, to which one of the contributing factors is the amount of inter-individual variability captured by an item.
+Items to which all participants' answers are concentrated around one option - i.e., exhibiting a narrow distribution - will be flagged as potentially problematic.
 
-After examining the distributions to all IAS items, we will analyze the factor structure using two different approaches, namely traditional exploratory and confirmatory Factor Analysis (EFA/CFA) as well as Exploratory Graph Analysis (EGA).
+<!-- UVA -->
+After examining the distributions to all IAS items, we will test for "redundant" items (e.g., due to multicollinearity or local dependency) using Unique Variable Analysis [UVA, @christensen2023unique], a novel method derived from network psychometric designed to identify and merge items that share substantial variance (which can distort the structure estimation).
+We will use a threshold of 0.25, suggested to optimally balances accuracy and false positives **[REF NEEDED]**.
 
 <!-- EGA -->
+Following the analysis of items, we will analyze the factor structure of the IAS using two different approaches, namely traditional exploratory and confirmatory Factor Analysis (EFA/CFA) and Exploratory Graph Analysis (EGA).
 By combining network analysis with psychometric methods, the recently-developed EGA framework allows to jointly estimate the number of dimensions (i.e., groups of items), the structure as well as its stability [@golino2017exploratory; @golino2020investigating].
@@
 Clustering these nodes reveals distinct communities of related items, in practice akin to traditional latent factors - but without explicitly assuming their presence [@christensen2021equivalency].
-<!-- By applying UVA, the analysis can maintain the integrity of the IAS while improving its efficiency and reducing redundancy. -->
-
-<!-- UVA -->
-To assess whether the IAS contains redundant items (e.g., due to multicollinearity or local dependency), Unique Variable Analysis [UVA, @christensen2023unique] will be employed. 
-UVA is another novel network psychometric method designed to identify and merge items that share substantial variance, effectively reducing datasets to a set of unique variables. 
-Unlike other reduction methods that aim to minimize variables broadly, UVA targets redundancy specifically, preserving meaningful information that may otherwise be lost [@merritt2022experimental]. 
-By focusing on statistically redundant variables, UVA offers a middle ground between no reduction and extensive reduction approaches. 
-Simulation studies have demonstrated that using a threshold of 0.25 optimally balances accuracy and false positives, ensuring that only genuinely redundant items are combined.
 
 <!-- Factor Analysis -->
+While EGA offers a robust alternative to traditional factor analysis, factor analysis remains a widely used method for dimensionality assessment.
+As our goal is to provide a general - yet nuanced - picture, with room to show potential discrepancies emerging from the methods used, we will also include it in the present study.
+Unlike EGA, factor analysis assumes that  a latent source of variability — a common latent variable — underlies the observed set of manifest variables [@cosemans2022exploratory].
+A critical step in factor analysis is determining the optimal number of factors, for which we will used the Method Agreement Procedure [@ludecke2021performance], which involves a consensus-based decision based on multiple factor estimation methods applied concurrently.
 
-While EGA offers a robust alternative to traditional factor analysis, factor analysis remains a widely used method for dimensionality assessment, hence it will be also be computed in this analysis. 
-Unlike EGA, factor analysis assumes a latent source of variability — a common latent variable — underlies the observed set of manifest variables [@cosemans2022exploratory].
-A critical step in factor analysis is determining the optimal number of factors, typically achieved by examining eigenvalue patterns and applying stopping rules, such as the Kaiser-Guttman criterion (eigenvalues greater than 1) or parallel analysis.
-These methods aim to identify the most meaningful factor structure, though their performance can vary depending on sample size and data complexity [@christensen2023unique].
-
-To determine the appropriate number of factors to retain during factor analysis, the n_factors function from the performance package will be used [@ludecke2021performance]. 
-This function runs multiple established procedures for factor retention and identifies the optimal number of factors based on the maximum consensus across methods - i.e., Method Agreement Procedure. 
-These methods include the Kaiser criterion, parallel analysis,  Velicer's MAP, and others.
-Following this, EFA with the optimal number of factors identified, using 'oblimin' rotation, will be aplied. 
-Model fit using CFA to identify the best-fitting model will then be computed.
-
-### Results
+## Results
 
@@
 In other words, participants are most likely to answer 4/5 (i.e., agree) on most items, with the exception of "blood sugar" and "bruise", which exhibit a different distributional pattern with a lower mode (\~2/5).
-This pattern persists across most samples, except for "affective touch" in samples 8a and 8b, where it deviates from the general trend. 
-In these samples, "affective touch" follows a distribution similar to that of "blood sugar" and "bruise".  **-could it be a language thing?**
+This is also the case for "affective touch" in samples 8a and 8b (the Chinese validation samples), which might indicate localisation issues.
 Additionally, one can note the low occurrence of extreme values (1 and 5), meaning that the bulk of answers varies between 3 values (assuming the IAS is implemented as a 5-point Likert scale following its validation).
-The samples using an analogue scale (samples 10a, 10b and 10c in the figure) displaying a more continuous and progressive spread of answers, seemingly improving the interindividual variability, although potentially suggesting a second lower mode at \~2.
-**- sample 11's were rated on a liker-scale**
-
-**TODO: And add x-axis on all subplots. Consider making the problematic items dashed.**.
+The samples using an analogue scale (samples 10a, 10b and 10c in the figure) display a more continuous and progressive spread of answers, seemingly improving the interindividual variability, although potentially displaying a secondary lower mode at \~2 (which might be suggesting the existence of potential clusters of participants).
 
@@
 #| label: fig-distributions
-#| fig-cap: "Distribution of responses across datasets reveals a consistent modal value, typically around 4 or 5 (indicating agreement), except for 'blood sugar' and 'bruise,' which have lower modes.
+#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
+#| out-width: "100%"
+#| fig-cap: "Distribution of responses across datasets reveals a consistent modal value, typically around 4 or 5 (indicating agreement), except for 'blood sugar' and 'bruise' - in dashed lines - and 'affective touch' (dotted lines) in the Chinese validation sample, which have lower modes.
 Most responses cluster around the middle values, with few extreme scores (1 and 5).
@@
 Since most samples use Likert scales (discrete), the density plots may not be the most accurate representation but were chosen to clearly highlight variability patterns in the data."
-#|
-knitr::include_graphics("figures/Figure1.png")
+
+knitr::include_graphics("../../analysis/figures/Figure1.png")
 ```
 
-<!-- Univariate analysis -->
+<!-- UVA -->
 UVA flagged two strongly redundant variables, "itch" and "tickle" - suggesting to remove the latter.
@@
 
-<!-- Network analysis and Strcuture stability -->
+<!-- Network analysis and Structure stability -->
+The EGA analysis employed a sparse Gaussian graphical model (GGM) with the graphical lasso (glasso) method.
+We applied the Walktrap (**REF**) and the Louvain (**REF**) algorithms for clusters identification, which yielded a five and four clusters solution, respectively.
+The four-cluster solution appeared as being more stable (based on the bootstrapped stability analysis: it had a higher proportion of items consistently assigned to the same cluster across bootstrap samples).
+In this solution, item stability for all variables exceeded 0.90, except for "affective touch".
+The first cluster included skin-related items "itch", "tickle", "bruise", and "blood sugar"; the second cluster contained expulsion-related items "burp", "wind", "cough", "sneeze", and "vomit"; the third cluster (**NAME or interpretation?**) comprised "affective touch", "sexual arousal", "muscles", "temperature", "pain", and "taste"; and the fourth cluster included visceroceptive items like "heart", "breathing", "hungry", "thirsty", "urinate", and "defecate".
+This solution was generally consistent when applied to samples separately.
 
-**TO DOM: I put a bunch of info from the fucntion you created an the package documentation. Let me know what you want to keep from this information**
+<!-- Factor analysis -->
 
-The EGA analysis employed a sparse Gaussian graphical model with the graphical lasso (glasso) method. 
-To identify community structures, both the Louvain and Walktrap algorithms were applied.
-The Walktrap algorithm identified an optimal solution with five clusters, whereas the Louvain algorithm indicated an optimal solution with four clusters. 
-To assess the stability of these solutions, a bootstrap resampling approach was implemented, evaluating stability based on the proportion of bootstrap samples in which the original structure was replicated.
-The four-cluster solution demonstrated greater item stability, with a higher proportion of items consistently appearing within the same dimension across bootstrap samples.
-In this solution, item stability for all variables exceeded 0.91, with the exception of "affective touch" in the four-cluster solution, which showed comparatively lower stability.
-Nevertheless, this solution was considered the most optimal; C1.
-"itch", "tickle", "bruise", "blood sugar"; C2.
-"burp", "wind", "cough", "sneeze", "vomit"; C3.
-"affective touch", "sexual arousal", "muscles", "temperature", "pain", and "taste"; C4.
-"heart", "breathing", "hungry", "thirsty", "urinate", and "defecate".
-This solution was generally consistent within the data sets, although some samples yielded 3- or 5- clusters as the optimal structure.
+Regarding Factor Analysis, the Method Agreement Procedure recommended a four-factor solution for the whole sample.
+A four-factor solution was extracted using an *oblimin* rotation, accounting for 41.58% of the total variance.
+The first factor (14.45%) included items "burp", "cough", "wind", "sneeze", "vomit", "temperature", "sexual arousal" and "taste".
+The second factor (11.76%) included "breathing", "hungry", "heart", "thirsty", "pain", "muscles", "blood sugar", and "bruise".
+The third factor (8.09%) contained skin-related items "tickle", "itch" and "affective touch", and the final factor (7.28%) included "urinate" and "defecate".
+Notably, this structure differed from that suggested by EGA.
 
-**EGA Clusters not consistent with FA dimensions**
 <!-- EGA clusters 
@@
 
-<!-- Factor analysis -->
-
-**TODO: explain how we obtained the optimal number of factors** -->  **I think i explained it above on the analysis bit, please confirm whether there needs to be more info**
-
-Across all samples, the Method Agreement Procedure recommended a four-factor solution. 
-Approximately 30% of the tested methods — the Beta method, Optimal Coordinates, Parallel Analysis, and the Kaiser criterion — converged on this as the optimal number of factors to retain.
-
-In line with the Method Agreement Procedure's recommendation, a four-factor solution was extracted using an oblimin rotation, accounting for 41.58% of the total variance.
-The first factor included items "burp," "cough," "wind," "sneeze," "vomit," "temperature," "sexual arousal," and "taste," explaining 14.45% of the total variance. 
-The second factor incuded "breathing," "hungry," "heart," "thirsty," "pain," "muscles," "blood sugar," and "bruise," accounting for 11.76% of the variance. 
-The third factor contained "tickle," "itch," and "affective touch," explaining 8.09% of the total variance. 
-Lastly, the fourth factor included "urinate" and "defecate," accounting for only 7.28% of the total variance.
-Notably this grouping differs from that of the EGA's four cluster optimal solution.
+<!-- Item selection -->
+**UVA**, then re-run EGA and EFA. Then CFA.
 
 <!-- CFA -->
+We then attempted at testing various candidate structures using confirmatory factor analysis (CFA).
+
 Throughout the EGA and EFA analyses, the item "tickle" was consistently identified as redundant and was flagged for removal in the UVA analysis. 
@@
 
-### Discussion
+## Discussion
 
@@
 
-## Study 2
+# Study 2
 
@@
 
-### Methods
+## Methods
 
-#### Materials
+### Materials
 
@@
 
-#### Data Analysis
+### Data Analysis
 
@@
 
-### Results
+## Results
 
-#### Average correlations
+### Average correlations
 
@@
 
-##### Correlations with body measures
+#### Correlations with body measures
 
@@
 
-##### Correlations with mood measures
+#### Correlations with mood measures
 
@@
 
-##### Correlations with psychopathology measures
+#### Correlations with psychopathology measures
 
@@
 
-##### Correlations with personality measures
+#### Correlations with personality measures
 
@@
 
-##### Correlations with other measures
+#### Correlations with other measures
 
@@
 
-## General Discussion
+# General Discussion
 
@@
 
-## Limitations and Future Directions
+# Limitations and Future Directions
 
@@
 
-## Conclusion
+# Conclusion
 
@@
 
-## References
+# References
 

### 2025-07-01 analysis/Study1.qmd
updated EGA andEFA analysis
removed item

@@
 
+Discarded the following items:
+- Tickle: not present in the same dataset and consistently flagged as redundant in UVA analysis.
+
+Ambiguous:
+- Temp
+- Vomit
+- Affective_touch
+- Sex_arousal
+- Taste
+- Blood Sugar
+
 ```{r ega_all}
@@
           plot.itemStability = FALSE,
-          verbose = FALSE
+          verbose = FALSE, 
         )
@@
 egas_all$p
-```
 
@@
 
-```{r}
+We discarded the following items: 
+- Tickle
+- Blood Sugar
+- Temp
+- Vomit
+- Affective_touch
+- Sex_arousal
+- Taste
+
+```{r}
+cols_to_remove <- c("Temp", "Vomit", "Affective_touch", "Sex_arousal", "Taste", "Tickle", "Bloo")
+```
+
+```{r}
+data_all <- data_all |>
+  select(-any_of(cols_to_remove))
+
 n <- parameters::n_factors(data_all, n_max = 12)
@@
 ```{r}
+data1a <- data1a |>
+  select(-any_of(cols_to_remove))
+
 n <- parameters::n_factors(data1a, n_max = 12)
@@
 ```{r}
+data1b <- data1b |>
+  select(-any_of(cols_to_remove))
+
 n <- parameters::n_factors(data1b, n_max = 12)
@@
 ```{r}
+data2 <- data2 |>
+  select(-any_of(cols_to_remove))
+
 n <- parameters::n_factors(data2, n_max = 12)
@@
 ```{r}
+data3 <- data3 |>
+  select(-any_of(cols_to_remove))
+
 n <- parameters::n_factors(data3, n_max = 12)
@@
 ```{r}
+data4 <- data4 |>
+  select(-any_of(cols_to_remove))
+
 n <- parameters::n_factors(data4, n_max = 12)
@@
 ```{r}
+data5 <- data5 |>
+  select(-any_of(cols_to_remove))
+
 n <- parameters::n_factors(data5, n_max = 12)
@@
 ```{r}
+data6 <- data6 |>
+  select(-any_of(cols_to_remove))
+
 n <- parameters::n_factors(data6, n_max = 12)
@@
 ```{r}
+data7a <- data7a |>
+  select(-any_of(cols_to_remove))
+
 n <- parameters::n_factors(data7a, n_max = 12)
@@
 ```{r}
+data7b <- data7b |>
+  select(-any_of(cols_to_remove))
+
 n <- parameters::n_factors(data7b, n_max = 12)
@@
 ```{r}
+data7c <- data7c |>
+  select(-any_of(cols_to_remove))
+
 n <- parameters::n_factors(data7c, n_max = 12)
@@
 ```{r}
+data8a <- data8a |>
+  select(-any_of(cols_to_remove))
+
 n <- parameters::n_factors(data8a, n_max = 12)
@@
 ```{r}
+data8b <- data8b |>
+  select(-any_of(cols_to_remove))
+
 n <- parameters::n_factors(data8b, n_max = 12)
@@
 ```{r}
+data9 <- data9 |>
+  select(-any_of(cols_to_remove))
+
 n <- parameters::n_factors(data9, n_max = 12)
@@
 ```{r}
+data10a <- data10a |>
+  select(-any_of(cols_to_remove))
+
 n <- parameters::n_factors(data10a, n_max = 12)
@@
 ```{r}
+data10b <- data10b |>
+  select(-any_of(cols_to_remove))
+
 n <- parameters::n_factors(data10b, n_max = 12)
@@
 ```{r}
+data10c <- data10c |>
+  select(-any_of(cols_to_remove))
+
 n <- parameters::n_factors(data10c, n_max = 12)
@@
 ```{r}
+data11a <- data11a |>
+  select(-any_of(cols_to_remove))
+
 n <- parameters::n_factors(data11a, n_max = 12)
@@
 ```{r}
+data11b <- data11b |>
+  select(-any_of(cols_to_remove))
+
 n <- parameters::n_factors(data11b, n_max = 12)
@@
 
-efa5 <- parameters::factor_analysis(data_all, n = 4, rotation = "oblimin", sort = TRUE)
+efa5 <- parameters::factor_analysis(data_all, n = 3, rotation = "oblimin", sort = TRUE)
 plot(efa5)
@@
 
-efa4 <- parameters::factor_analysis(data1a, n = 4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data1a, n = 3, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
-efa4 <- parameters::factor_analysis(data1b, n = 4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data1b, n = 3, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
-efa4 <- parameters::factor_analysis(data2, n = 4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data2, n = 3, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
-efa4 <- parameters::factor_analysis(data3, n = 4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data3, n = 3, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
-efa4 <- parameters::factor_analysis(data4, n = 4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data4, n = 3, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
-efa4 <- parameters::factor_analysis(data5, n = 4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data5, n = 3, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
-efa4 <- parameters::factor_analysis(data6, n = 4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data6, n = 3, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
-efa4 <- parameters::factor_analysis(data7a, n = 4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data7a, n = 3, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
-efa4 <- parameters::factor_analysis(data7b, n = 4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data7b, n = 3, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
-efa4 <- parameters::factor_analysis(data7c, n = 4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data7c, n = 3, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
-efa4 <- parameters::factor_analysis(data8a, n = 4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data8a, n = 3, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
-efa4 <- parameters::factor_analysis(data8b, n = 4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data8b, n = 3, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
-efa4 <- parameters::factor_analysis(data9, n = 4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data9, n = 3, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
-efa4 <- parameters::factor_analysis(data10a, n = 4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data10a, n = 3, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
-efa4 <- parameters::factor_analysis(data10b, n = 4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data10b, n = 3, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
-efa4 <- parameters::factor_analysis(data10c, n = 4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data10c, n = 3, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
-efa4 <- parameters::factor_analysis(data11a, n = 4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data11a, n = 3, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 
-efa4 <- parameters::factor_analysis(data11b, n = 4, rotation = "oblimin", sort = TRUE)
+efa4 <- parameters::factor_analysis(data11b, n = 3, rotation = "oblimin", sort = TRUE)
 plot(efa4)
@@
 We discarded the following items: 
-- Tickle: not present in the same dataset and consistently flagged as redundant.
-<!-- - Blood_Sugar -->
-
-Ambiguous:
+- Tickle
+- Blood Sugar
 - Temp

### 2025-07-06 analysis/Study1.qmd
update

--- 2025-06-21 analysis/Study1.qmd
@@
     Muscles = `IAS 15`, Bruise = `IAS 16`, Pain = `IAS 17`, Blood_Sugar = `IAS 18`,
-    Affective_touch = `IAS 19`, Tickle = `IAS 20`, Itch = `IAS 21`)
+    Affective_touch = `IAS 19`, Tickle = `IAS 20`, Itch = `IAS 21`,
+    MAIA_AttentionRegulation = MAIA_AttentionReg, MAIA_BodyListening = MAIA_BodyListening,
+    MAIA_Trusting = MAIA_BodyTrusting, MAIA_EmotionalAwareness = MAIA_EmoAwareness,
+    MAIA_NonDistracting=MAIA_NotDistracting, MAIA_NotWorrying=MAIA_NotWorrying,
+    MAIA_SelfRegulation=MAIA_SelfReg, MAIA_Noticing=MAIA_Noticing)
 rm(data)
@@
   )
+df4$MAIA_AttentionRegulation <- rowMeans(select(df4, starts_with("MAIA_AR")), na.rm = TRUE)
+df4$MAIA_BodyListening <- rowMeans(select(df4, starts_with("MAIA_BL")), na.rm = TRUE)
+df4$MAIA_Trusting <- rowMeans(select(df4, starts_with("MAIA_TR")), na.rm = TRUE)
+df4$MAIA_EmotionalAwareness <- rowMeans(select(df4, starts_with("MAIA_EA")), na.rm = TRUE)
+df4$MAIA_SelfRegulation <- rowMeans(select(df4, starts_with("MAIA_SR")), na.rm = TRUE)
+# TODO: what is NT?
+# Check if that's all
 ```
@@
   mutate(across(everything(), as.numeric))
-
 ```
@@
     Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
-    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
+    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
+    MAIA_Noticing = MAIA_NOTICING, MAIA_NonDistracting = MAIA_NON_DISTRACTING,
+    MAIA_NotWorrying = MAIA_NOT_WORRYING, MAIA_AttentionRegulation = mAIA_ATTENTION_REGULATION,
+    MAIA_SelfRegulation = MAIA_SELF_REGULATION, MAIA_BodyListening = MAIA_BODY_LISTENING,
+    MAIA_Trusting = MAIA_TRUSTING, MAIA_EmotionalAwareness = MAIA_EMOTIONAL_AWARENESS
   )
@@
     Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
-    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
+    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
+    MAIA_Noticing = maiaNotice, MAIA_NonDistracting = maiaNonDistracting,
+    MAIA_NotWorrying = maiaNotWorrying, MAIA_AttentionRegulation = maiaAttentionRegulation,
+    MAIA_SelfRegulation = maiaSelfRegulation, MAIA_BodyListening = maiaBodyListening,
+    MAIA_Trusting = maiaTrusting, MAIA_EmotionalAwareness = maiaEmotionalAwareness
   )
@@
     Muscles = IA02_15, Bruise = IA02_16, Pain = IA02_17, Blood_Sugar = IA02_18,
-    Affective_touch = IA02_19, Tickle = IA02_20, Itch = IA02_21
+    Affective_touch = IA02_19, Tickle = IA02_20, Itch = IA02_21,
+    MAIA_Noticing = MAIA_noticing, MAIA_NonDistracting = MAIA_notdis, 
+    MAIA_NotWorrying = MAIA_notwor, MAIA_AttentionRegulation = MAIA_attreg,
+    MAIA_SelfRegulation = MAIA_selfreg, MAIA_BodyListening = MAIA_bodlis,
+    MAIA_Trusting = MAIA_trust, MAIA_EmotionalAwareness = MAIA_emoaw,
+    ICQ = ICQ_sum
   )
@@
 - Makowski
-  - Note: First sample has some missing items
+  - Note: First sample has some missing items (No Taste, Cough, Blood_Sugar)
   - Note: Analog scales
@@
 
+# TODO: Sanitize MAIA names / Compute dimensions.
+
 df10b <- read.csv("https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv") |>
@@
   )
+
+# TODO: Sanitize MAIA names / Compute dimensions.
 
@@
 
-```
-
-```{r}
-pi_vars <- c("PI_Enticing", "PI_Alive", "PI_Safe", "PI_Good", "PI_Changing", 
-             "PI_Hierarchical", "PI_Understandable", "PI_AboutMe", "PI_Abundant", 
-             "PI_Acceptable", "PI_Beautiful", "PI_Cooperative", "PI_Funny", 
-             "PI_Harmless", "PI_Improvable", "PI_Intentional", "PI_Interconnected", 
-             "PI_Interesting", "PI_Just", "PI_Meaningful", "PI_NeedsMe", 
-             "PI_Pleasurable", "PI_Progressing", "PI_Regenerative", "PI_Stable", 
-             "PI_WorthExploring")
-
-correlation::correlation(
-  df10c[, "IAS_Total", drop = FALSE],  
-  data2 = select(df10c, all_of(pi_vars)), p_adjust = "none"
+# TODO: Sanitize MAIA names / Compute dimensions.
+
+df10d <- read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionScale/refs/heads/main/study2/data/rawdata_participants.csv") |>
+  select("Participant", "Gender", "Age", "Ethnicity", starts_with(c("IAS","MAIA","PI", "PHQ4"))) |>
+   rename(
+    Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
+    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
+    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
+    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
+    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
   ) |> 
-  # Formatting correlation results
-  mutate(val = paste0(insight::format_value(r), format_p(p, stars_only = TRUE))) |>
-
-  # Releveling factors for visualization
-  mutate(Parameter2 = fct_relevel(Parameter2, rev(pi_vars)),
-         Parameter1 = fct_relevel(Parameter1, "IAS_Total")) |>
-
-  # Plotting the correlation matrix
-  ggplot(aes(x = Parameter1, y = Parameter2)) +
-  geom_tile(aes(fill = r), color = "white") +  
-  geom_text(aes(label = val), size = 3) +  
-  labs(title = "Correlation Matrix") +
-  scale_fill_gradient2(low = "blue", high = "red", mid = "white", limit = c(-1, 1), midpoint = 0, guide = guide_colourbar(ticks = FALSE)) +  
-  theme_minimal() +
-  theme(
-    legend.title = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank(),
-    axis.text.x = element_text(hjust = 1)
-  )
+  filter(Participant %in% read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionScale/refs/heads/main/study2/data/data_participants.csv")$Participant)
+
+# TODO: Sanitize MAIA names / Compute dimensions.
+
+```
+
+```{r}
+# pi_vars <- c("PI_Enticing", "PI_Alive", "PI_Safe", "PI_Good", "PI_Changing", 
+#              "PI_Hierarchical", "PI_Understandable", "PI_AboutMe", "PI_Abundant", 
+#              "PI_Acceptable", "PI_Beautiful", "PI_Cooperative", "PI_Funny", 
+#              "PI_Harmless", "PI_Improvable", "PI_Intentional", "PI_Interconnected", 
+#              "PI_Interesting", "PI_Just", "PI_Meaningful", "PI_NeedsMe", 
+#              "PI_Pleasurable", "PI_Progressing", "PI_Regenerative", "PI_Stable", 
+#              "PI_WorthExploring")
+# 
+# 
+# correlation::correlation(
+#   df10c[, "IAS_Total", drop = FALSE],  
+#   data2 = select(df10c, all_of(pi_vars)), p_adjust = "none"
+# ) |> 
+#   # Formatting correlation results
+#   mutate(val = paste0(insight::format_value(r), format_p(p, stars_only = TRUE))) |>
+#   
+#   # Releveling factors for visualization
+#   mutate(Parameter2 = fct_relevel(Parameter2, rev(pi_vars)),
+#          Parameter1 = fct_relevel(Parameter1, "IAS_Total")) |>
+#   
+#   # Plotting the correlation matrix
+#   ggplot(aes(x = Parameter1, y = Parameter2)) +
+#   geom_tile(aes(fill = r), color = "white") +  
+#   geom_text(aes(label = val), size = 3) +  
+#   labs(title = "Correlation Matrix") +
+#   scale_fill_gradient2(low = "blue", high = "red", mid = "white", limit = c(-1, 1), midpoint = 0, guide = guide_colourbar(ticks = FALSE)) +  
+#   theme_minimal() +
+#   theme(
+#     legend.title = element_blank(),
+#     axis.title.x = element_blank(),
+#     axis.title.y = element_blank(),
+#     axis.text.x = element_text(hjust = 1)
+#   )
 ```
@@
 
+# TODO: sanitize MAIA names / Compute dimensions.
+
 df11b <- haven::read_sav("../data/Giulia/Sleep and Exteroceptive Interoceptive Sensitivity.sav") |> # 165 participants
@@
   na.omit()
+
+# TODO: sanitize MAIA names / Compute dimensions.
 
@@
 table <- data.frame(
-   Sample = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Makowski et al., (2023c)', 'Poerio et al., (2024)', 'Poerio et al., unpublished', 'Total'),
-  Subsample = c('', 'Sample 1', 'Sample 2', '', '', '', '', '', '', 'Sample 1', 'Sample 2', 'Sample 3', '', 'Sample 1', 'Sample 2', '', '', '', '', '','', ''),   
+  Reference = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Makowski et al., (2023c)', 'Poerio et al., (2024)', 'Poerio et al., unpublished', 'Total'),
+  Sample = c('', 'Sample 1a', 'Sample 1b', 'Sample 2', 'Sample 3', 'Sample 4', 'Sample 5', 'Sample 6', '', 'Sample 7a', 'Sample 7b', 'Sample 7c', '', 'Sample 8a', 'Sample 8b', 'Sample 9', 'Sample 10', 'Sample 11', 'Sample 12', 'Sample 13', 'Sample 14', 'Sample 15'),
   Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', 'English', 'English', 'English',''),
   N = c('', nrow(df1a), nrow(df1b), nrow(df2), nrow(df3), nrow(df4), nrow(df5_attention), nrow(df6),'', nrow(df7a), nrow(df7b), 802,'', nrow(df8a), nrow(df8b), nrow(df9), nrow(df10a), nrow(df10b), nrow(df10c), nrow(df11a), nrow(df11b), 32214),
-  'Difference' = c('','', '', '', '', '', '', '', '', '', '', '', '', 'Collapsed "Itch" and "Tingling"', 'Collapsed "Itch" and "Tingling"', '', 'Analog scales', 'Analog scales', 'Analog scales', '', '', ''),
+  'Difference' = c('','', '', '', '', '', '', '', '', '', '', '', '', 'Collapsed "Itch" and "Tickling"', 'Collapsed "Itch" and "Tickling"', '', 'Analog scales', 'Analog scales', 'Analog scales', '', '', ''),
   Age = c('', make_age(df1a$Age), make_age(df1b$Age), make_age(df2$Age), make_age(df3$Age), "48.6.6 ± 14.1*", make_age(df5_attention$Age), make_age(df6$Age),'', make_age(df7a$Age), make_age(df7b$Age), make_age(df7c$Age),'', make_age(df8a$Age), make_age(df8b$Age), make_age(df9$Age), make_age(df10a$Age), make_age(df10b$Age), make_age(df10c$Age), make_age(df11a$Age), make_age(df11b$Age), '48.6 ± 13.1'),
@@
 
-## Descriptive
+## Item Selection
 
@@
   scale_linetype_manual(values = linetype)  +
+  labs(x = "Response", y = "Distribution", color = "Item", linetype = "Item", title = "Item Distribution") +
+  guides(color = guide_legend(ncol = 1)) +
+  facet_wrap(~Sample, scales = "free_y", nrow = 3) +
   theme_minimal() +
   theme(axis.text.y = element_blank(),
-        plot.title = element_text(face="bold")) +
-  labs(x = "Response", y = "Distribution", color = "Item", linetype = "Item") +
-  facet_wrap(~Sample, scales = "free_y", nrow = 3)
-
-ggsave("figures/Figure1.png", p1, width=12, height=7, dpi=300, bg="white")
+        axis.title.y = element_blank(),
+        plot.title = element_text(face="bold"))
+
 p1
@@
   data1a, data1b, data2, data3, data4, data5, data6, data7a, data7b, data7c,
-  mutate(data8a, Tickle = NA), mutate(data8b, Tickle = NA), data9,
-  mutate(data10a, Taste = NA, Cough = NA, Blood_Sugar = NA),  data10b,  data10c, data11a, data11b
+  mutate(data8a, Tickle = NA), 
+  mutate(data8b, Tickle = NA), data9,
+  mutate(data10a, Taste = NA, Cough = NA, Blood_Sugar = NA),  
+  data10b,  data10c, data11a, data11b
 ) 
@@
     correlation::cor_sort() |>
-    correlation::cor_lower() |>
-    mutate(val = paste0(insight::format_value(r), format_p(p, stars_only = TRUE))) |>
-    mutate(Parameter2 = fct_rev(Parameter2)) |>
-    ggplot(aes(x = Parameter1, y = Parameter2)) +
+    # correlation::cor_lower() |>
+    mutate(val = paste0(insight::format_value(r), format_p(p, stars_only = TRUE)),
+           r = ifelse(Parameter1 == Parameter2, NA, r),
+           lbl = ifelse(Parameter1 == Parameter2, "", format_value(r, zap_small = TRUE, lead_zero = FALSE)),
+           lbl = ifelse(p > .05, "", lbl),
+           Param1 = fct_relevel(str_replace(Parameter1, "_", " "), str_replace(levels(Parameter1), "_", " ")),
+           Param2 = fct_relevel(str_replace(Parameter2, "_", " "), str_replace(levels(Parameter2), "_", " "))) |>
+    # mutate(Parameter2 = fct_rev(Parameter2)) |>
+    ggplot(aes(x = Param1, y = Param2)) +
     geom_tile(aes(fill = r), color = "white") +
-    geom_text(aes(label = val), size = 3) +
-    labs(title = "Correlation Matrix") +
-    scale_fill_metro_c(limit = c(0, 0.75), guide = guide_colourbar(ticks = FALSE)) +
+    geom_text(aes(label = lbl), size = 3) +
+    labs(title = "Correlation Matrix", subtitle = paste0("N = ", nrow(df))) +
+    scale_fill_gradientn(
+      colors = c("white", "#FFF9C4", "#FFF59D", "#FFEB3B", "#FFCA28", "#FF9800", "#FF5722", "#F44336", "#E91E63", "#9C27B0", "#673AB7", "#512DA8", "#311B92"),
+      na.value = "#311B92",
+      limits = c(0, 0.8),
+      guide = guide_colorbar(ticks.colour = NA)
+    ) +
+    # scale_fill_metro_c(limit = c(0, 0.75), guide = guide_colourbar(ticks = FALSE)) +
     theme_minimal() +
@@
       axis.title.y = element_blank(),
-      axis.text.x = element_text(angle = 45, hjust = 1)
+      axis.text.x = element_text(angle = 45, hjust = 1),
+      plot.title = element_text(face = "bold")
     )
@@
 
-make_correlation(data_all)
+p2 <- make_correlation(data_all)
+p2
+
+fig1 <- p1 / p2
+ggsave("figures/Figure1.png", fig1, width=10, height=12, dpi=300, bg="white")
 ```
@@
 :::
-
-## Graph Analysis
-
-Exploratory Graph Analysis (EGA) is a recently developed framework for psychometric assessment, that can be used to estimate the number of dimensions in questionnaire data using network estimation methods and community detection algorithms, and assess the stability of dimensions and items using bootstrapping.
-See https://r-ega.net/articles/ega.html for details.
 
@@
 ```{r}
-uva <- EGAnet::UVA(data = data_all, cut.off = 0.3)
-uva
-uva$keep_remove
+uva0 <- EGAnet::UVA(data = data_all, cut.off = 0.3)
+uva0
+uva0$keep_remove
 ```
@@
 ```{r}
-uva <- EGAnet::UVA(data = data1a, cut.off = 0.3)
-uva
-uva$keep_remove
+uva1a <- EGAnet::UVA(data = data1a, cut.off = 0.3)
+uva1a
+uva1a$keep_remove
 ```
@@
 ```{r}
-uva <- EGAnet::UVA(data = data1b, cut.off = 0.3)
-uva
-uva$keep_remove
+uva1b <- EGAnet::UVA(data = data1b, cut.off = 0.3)
+uva1b
+uva1b$keep_remove
+```
+
+#### Sample 2
+
+```{r}
+uva2 <- EGAnet::UVA(data = data2, cut.off = 0.3)
+uva2
+uva2$keep_remove
 ```
@@
 ```{r}
-uva <- EGAnet::UVA(data = data3, cut.off = 0.3)
-uva
-uva$keep_remove
+uva3 <- EGAnet::UVA(data = data3, cut.off = 0.3)
+uva3
+uva3$keep_remove
 ```
@@
 ```{r}
-uva <- EGAnet::UVA(data = data4, cut.off = 0.3)
-uva
-uva$keep_remove
+uva4 <- EGAnet::UVA(data = data4, cut.off = 0.3)
+uva4
+uva4$keep_remove
 ```
@@
 ```{r}
-uva <- EGAnet::UVA(data = data5, cut.off = 0.3)
-uva
-uva$keep_remove
+uva5 <- EGAnet::UVA(data = data5, cut.off = 0.3)
+uva5
+uva5$keep_remove
 ```
@@
 ```{r}
-uva <- EGAnet::UVA(data = data6, cut.off = 0.3)
-uva
-uva$keep_remove
+uva6 <- EGAnet::UVA(data = data6, cut.off = 0.3)
+uva6
+uva6$keep_remove
 ```
@@
 ```{r}
-uva <- EGAnet::UVA(data = data7a, cut.off = 0.3)
-uva
-uva$keep_remove
+uva7a <- EGAnet::UVA(data = data7a, cut.off = 0.3)
+uva7a
+uva7a$keep_remove
 ```
@@
 ```{r}
-uva <- EGAnet::UVA(data = data7b, cut.off = 0.3)
-uva
-uva$keep_remove
+uva7b <- EGAnet::UVA(data = data7b, cut.off = 0.3)
+uva7b
+uva7b$keep_remove
 ```
@@
 ```{r}
-uva <- EGAnet::UVA(data = data7c, cut.off = 0.3)
-uva
-uva$keep_remove
+uva7c <- EGAnet::UVA(data = data7c, cut.off = 0.3)
+uva7c
+uva7c$keep_remove
 ```
@@
 ```{r}
-uva <- EGAnet::UVA(data = data8a, cut.off = 0.3)
-uva
-uva$keep_remove
+uva8a <- EGAnet::UVA(data = data8a, cut.off = 0.3)
+uva8a
+uva8a$keep_remove
 ```
@@
 ```{r}
-uva <- EGAnet::UVA(data = data8b, cut.off = 0.3)
-uva
-uva$keep_remove
+uva8b <- EGAnet::UVA(data = data8b, cut.off = 0.3)
+uva8b
+uva8b$keep_remove
 ```
@@
 ```{r}
-uva <- EGAnet::UVA(data = data9, cut.off = 0.3)
-uva
-uva$keep_remove
+uva9 <- EGAnet::UVA(data = data9, cut.off = 0.3)
+uva9
+uva9$keep_remove
 ```
@@
 ```{r}
-uva <- EGAnet::UVA(data = data10a, cut.off = 0.3)
-uva
-uva$keep_remove
+uva10a <- EGAnet::UVA(data = data10a, cut.off = 0.3)
+uva10a
+uva10a$keep_remove
 ```
@@
 ```{r}
-uva <- EGAnet::UVA(data = data10b, cut.off = 0.3)
-uva
-uva$keep_remove
+uva10b <- EGAnet::UVA(data = data10b, cut.off = 0.3)
+uva10b
+uva10b$keep_remove
 ```
@@
 ```{r}
-uva <- EGAnet::UVA(data = data10c, cut.off = 0.3)
-uva
-uva$keep_remove
+uva10c <- EGAnet::UVA(data = data10c, cut.off = 0.3)
+uva10c
+uva10c$keep_remove
 ```
@@
 ```{r}
-uva <- EGAnet::UVA(data = data11a, cut.off = 0.3)
-uva
-uva$keep_remove
+uva11a <- EGAnet::UVA(data = data11a, cut.off = 0.3)
+uva11a
+uva11a$keep_remove
 ```
@@
 ```{r}
-uva <- EGAnet::UVA(data = data11b, cut.off = 0.3)
-uva
-uva$keep_remove
+uva11b <- EGAnet::UVA(data = data11b, cut.off = 0.3)
+uva11b
+uva11b$keep_remove
+```
+
+#### Summary
+
+```{r}
+rez_uva <- c(uva1a$keep_remove$remove,
+  uva1b$keep_remove$remove,
+  uva2$keep_remove$remove,
+  uva3$keep_remove$remove,
+  uva4$keep_remove$remove,
+  uva5$keep_remove$remove,
+  uva6$keep_remove$remove,
+  uva7a$keep_remove$remove,
+  uva7b$keep_remove$remove,
+  uva7c$keep_remove$remove,
+  uva8a$keep_remove$remove,
+  uva8b$keep_remove$remove,
+  uva9$keep_remove$remove,
+  uva10a$keep_remove$remove,
+  uva10b$keep_remove$remove,
+  uva10c$keep_remove$remove,
+  uva11a$keep_remove$remove,
+  uva11b$keep_remove$remove)
+
+sort(table(rez_uva), decreasing = TRUE) / length(rez_uva) 
 ```
@@
 
-### Networks
+### Structure Refinement
+
+Discarded the following items:
+- Tickle: not present in the same dataset and consistently flagged as redundant in UVA analysis.
+
+```{r}
+data_all <- select(data_all, -Tickle)
+data1a <- select(data1a, -Tickle)
+data1b <- select(data1b, -Tickle)
+data2 <- select(data2, -Tickle)
+data3 <- select(data3, -Tickle)
+data4 <- select(data4, -Tickle)
+data5 <- select(data5, -Tickle)
+data6 <- select(data6, -Tickle)
+data7a <- select(data7a, -Tickle)
+data7b <- select(data7b, -Tickle)
+data7c <- select(data7c, -Tickle)
+# data8a <- select(data8a, -Tickle)
+# data8b <- select(data8b, -Tickle)
+data9 <- select(data9, -Tickle)
+data10a <- select(data10a, -Tickle)
+data10b <- select(data10b, -Tickle)
+data10c <- select(data10c, -Tickle)
+data11a <- select(data11a, -Tickle)
+data11b <- select(data11b, -Tickle)
+```
+
+#### Initial
+
+```{r}
+colors <- c("Heart" = "#F44336", "Breathing" = "#FF5722",
+            "Hungry" = "#FF9800", "Thirsty" = "#FFC107",
+            "Burp" = "#4CAF50", "Wind" = "#009688",
+            "Urinate" = "#63824C", "Defecate" = "#795548",
+            "Cough" = "#8BC34A", "Sneeze" = "#CDDC39", 
+            "Bruise" = "#673AB7", "Blood Sugar" = "#3F51B5",
+            "Muscles" = "#2196F3", "Pain" = "#00BCD4",
+            "Sex arousal" = "#FF4081", "Temp" = "#9C27B0",
+            "Vomit" = "#76FF03", "Taste" = "#00E676",
+            "Affective touch" = "#FF1744", "Itch" = "#D500F9")
+```
 
@@
 
-#### All data
-
-```{r ega_all}
+##### HCA
+
+```{r}
+make_hclust <- function(data) {
+  rez_pvclust <- pvclust::pvclust(data,
+                 method.hclust = "complete",
+                 method.dist = "correlation",
+                 nboot = 1000, quiet=TRUE, parallel=TRUE)
+
+  dendrogram <- as.dist(1 - cor(data, use = "pairwise.complete.obs")) |> 
+  hclust(method = "complete") |> 
+  tidygraph::as_tbl_graph()
+
+  # Process Nodes
+  nodes <- as.list(dendrogram)$nodes |> 
+    mutate(
+      Size = ifelse(label != "", 10, NA),
+      Item = str_replace(label, "_", " "),
+      idx = 1:nrow(as.list(dendrogram)$nodes))
+
+  # Central node 
+  nodes[nodes$height == max(nodes$height), c("Item", "Size")] <- data.frame(Item="Central", Size=15)
+
+  # Process Edges
+  edges <- as.list(dendrogram)$edges
+  edges$linewidth = datawizard::rescale(nodes[edges$from, ]$height, to = c(0.1, 1))
+
+  p <- tidygraph::tbl_graph(nodes = nodes, edges = edges) |> 
+    ggraph(layout = "dendrogram", circular = TRUE) +
+    # geom_edge_diagonal(strength = 0.7, linewidth = 1) +
+    geom_edge_elbow2(aes(edge_width=linewidth), color="#212121") +
+    geom_node_point(aes(filter=Item %in% c("Central"), size = Size), color="#212121") +
+    # geom_node_point(aes(filter=Group %in% c("Visceroception", "Awareness", "Deficit"), color=Group, size = Size)) +
+    geom_node_text(aes(
+      label = ifelse(Item != "", Item, NA),
+      x = x * 1.10,
+      y = y * 1.10,
+      filter = label != "",
+      angle = ifelse(
+        x >= 0,
+        asin(y) * 360 / 2 / pi,
+        360 - asin(y) * 360 / 2 / pi
+      ),
+      hjust = ifelse(
+        x >= 0, 0, 1
+      ))) +
+    geom_node_point(aes(filter = label != "", color=Item, size=Size), alpha = 1) +
+    # geom_node_text(aes(label=idx)) +  # Debug
+    scale_edge_width_continuous(range=c(1, 3), guide = "none") +
+    scale_size_continuous(range=c(10, 10), guide = "none") +
+    scale_color_manual(values = colors,
+                       breaks = names(colors)) +
+    ggtitle("Hierarchical Clustering Analysis (HCA)", subtitle = "Method = Correlation") +
+    coord_equal(clip = "off", xlim = c(-1.25, 1.25), ylim = c(-1.25, 1.25)) +
+    theme_void() + 
+    # guides(color = guide_legend(override.aes = list(size = c(7.5, 5, 5, 3.5, 7.5, 5, 5, 3.5, 3.5, 3.5, 7.5, 5, 5, 3.5)))) +
+    theme(legend.text = ggtext::element_markdown(),
+          legend.title = element_blank(),
+          legend.position = "none",
+          # plot.title = element_blank(), 
+          # plot.subtitle = element_blank()
+          plot.title = element_text(face="bold"))
+
+  list(pvclust = rez_pvclust, p = p)
+}
+
+rez_hclust <- make_hclust(data_all)
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+rez_hclust$p
+```
+
+##### EGA
+
+```{r}
+#| message: false
+#| warning: false
+
+make_ega <- function(data, cols = c("C1" = "#F44336", "C2" = "#FF9800", "C3" = "#795548", "C4" = "#CDDC39", "C5" = "#2196F3", "C6" = "#009688", "C7" = "#9C27B0")) {
+  rez <- EGAnet::bootEGA(
+    data = data,
+    seed = 123,
+    model = "glasso",
+    algorithm = "leiden",
+    EGA.type = "hierEGA",
+    type = "resampling",
+    plot.itemStability = FALSE,
+    verbose = FALSE, 
+    allow.singleton = TRUE
+  )
+
+  table <- EGAnet::net.loads(rez$EGA$lower_order)$std |> 
+    as.data.frame() |> 
+    rownames_to_column("Item") |>
+    gt::gt() |>
+    gt::tab_header(title = "EGA Loadings") |>
+    gt::data_color(
+      columns = -Item,
+      method = "numeric",
+      colors = scales::col_numeric(
+        palette = c("red", "white", "green"),
+        domain = c(-1, 0, 1)
+      )) |> 
+    gt::fmt_auto()
+
+  nodes <- rez$EGA$lower_order$dim.variables |> 
+    rename(name = items) |> 
+    mutate(dimension = paste0("C", dimension),
+           size = apply(EGAnet::net.loads(rez$EGA$lower_order)$std, 1, max)[name])
+
+  loadings <- rez$EGA$lower_order$network |> 
+    as.data.frame() |> 
+    rownames_to_column("to") |>
+    pivot_longer(-c(to), names_to = "from", values_to = "Loading") |> 
+    filter(Loading > quantile(Loading, 1/3))
+
+  g <- tidygraph::tbl_graph(nodes = nodes, edges = loadings, directed = FALSE) |> 
+    mutate(name = str_replace(name, "_", " "),
+           name = ifelse(name == "Sex arousal", "Sex", name))
+
+  set.seed(1)
+  layout <- ggraph::create_layout(g, layout = "fr", weights = abs(loadings$Loading))
+
+  xrange <- max(layout$x) - min(layout$x)
+  yrange <- max(layout$y) - min(layout$y)
+  xmin <- min(layout$x) - xrange * 0.05
+  xmax <- max(layout$x) + xrange * 0.05
+  ymin <- min(layout$y) - yrange * 0.05
+  ymax <- max(layout$y) + yrange * 0.05
+
+  p <- layout |> 
+    ggraph() +
+    geom_edge_bend(aes(edge_width = Loading, edge_alpha = Loading), color = "#212121",
+                   strength = 0.3) +
+    geom_node_point(aes(size = size, color = dimension), alpha = 0.95) +
+    geom_node_text(aes(label = name), size = 3, color = "white", fontface = "bold") +
+    scale_size_continuous(range = c(23, 28)) +
+    scale_edge_width(range = c(0.3, 4)) +
+    scale_edge_alpha(range = c(0.1, 0.9)) +
+    scale_color_manual(values = cols) +
+    labs(title = "Exploratory Graph Analysis (EGA)", subtitle = "Method = Leiden") +
+    theme_void() +
+    theme(legend.position = "none",
+          plot.title = element_text(face="bold")) +
+    coord_cartesian(xlim =c(xmin, xmax), ylim = c(ymin, ymax))
+
+  list(rez = rez, table = table, p = p)
+}
+
+rez_ega <- make_ega(data_all, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]]))
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+rez_ega$p
+```
+
+##### EFA
+
+```{r}
+make_efa <- function(data, n = 3, cols = c("F1" = "#009688", "F2" = "#795548", "F3" = "red")) {
+  n_fac <- n_factors(data)
+
+  rez_efa <- factor_analysis(data, n = n, sort = TRUE, rotation = "oblimin")
+
+  # Exctract loadings
+  loadings <- attributes(rez_efa)$loadings_long |> 
+    select(from = Component, to=Variable, Loading) |> 
+    mutate(Type = "Loading",
+           to = str_replace(to, "_", " "),
+           from = str_replace(from, "MR", "F"))
+
+  # Reorder factors
+  fct_order <- c("Pain", "Muscles", "Blood Sugar", "Bruise",
+                 "Affective touch", "Sex arousal", "Temp", "Itch", "Tickle", 
+                 "Thirsty", "Hungry", "Breathing", "Heart", "Defecate", "Urinate",
+                 "Sneeze", "Cough",  "Wind", "Burp", "Vomit", "Taste")
+  loadings <- loadings |> 
+    mutate(to = fct_relevel(to, fct_order[fct_order %in% unique(loadings$to)])) |> 
+    arrange(to) |> 
+    mutate(to = as.character(to))
+
+  # Get correlations between factors
+  phi <- attributes(rez_efa)$model$Phi
+  phi[upper.tri(phi, diag = TRUE)] <- NA
+  phi <- phi |> 
+    as.data.frame() |> 
+    rownames_to_column("from") %>%
+    pivot_longer(-from, names_to = "to", values_to = "Loading") |> 
+    filter(!is.na(Loading)) |>
+    mutate(Type = "Correlation",
+           from = str_replace(from, "MR", "F"),
+           to = str_replace(to, "MR", "F"))
+
+  # Reverse so that arcs are on the same side
+  phi[paste(phi$from, phi$to) %in% c("F3 F1"), c("from", "to")] <- data.frame(from = "F1", to = "F3")
+  phi[paste(phi$from, phi$to) %in% c("F2 F1"), c("from", "to")] <- data.frame(from = "F1", to = "F2")
+  phi[paste(phi$from, phi$to) %in% c("F3 F2"), c("from", "to")] <- data.frame(from = "F2", to = "F3")
+  phi[paste(phi$from, phi$to) %in% c("F4 F1"), c("from", "to")] <- data.frame(from = "F1", to = "F4")
+  phi[paste(phi$from, phi$to) %in% c("F4 F2"), c("from", "to")] <- data.frame(from = "F2", to = "F4")
+  phi[paste(phi$from, phi$to) %in% c("F4 F3"), c("from", "to")] <- data.frame(from = "F3", to = "F4")
+
+  loadings <- rbind(loadings, phi)
+
+  # Make layout
+  factor_names <- unique(loadings$from[loadings$Type == "Loading"])
+  item_names <- unique(loadings$to[loadings$Type == "Loading"])
+
+  nodes <- tibble(name = unique(c(loadings$from, loadings$to))) |>
+    mutate(type = case_when(
+      name %in% factor_names ~ "Factor",
+      name %in% item_names ~ "Item",
+      TRUE ~ "Other"
+    ))
+
+  y_position <- seq(0.8, 0.2, length.out = length(factor_names))
+
+  layout <- nodes |>
+    mutate(x = ifelse(type == "Item", 0, 1),
+           y = case_when(
+            name == "F1" ~ y_position[1],
+            name == "F2" ~ y_position[2],
+            name == "F3" ~ y_position[3],
+            name == "F4" ~ y_position[4],
+            name == "F5" ~ y_position[5],
+            name == "F6" ~ y_position[6],
+            .default = NA
+          ))
+  layout[layout$type == "Item", "y"] <- seq(0, 1, length.out = sum(layout$type == "Item"))
+
+  g <- tidygraph::as_tbl_graph(loadings, directed = TRUE) |>
+    left_join(layout, by = c("name"))
+
+  p_efa <- ggraph(g, layout = as.data.frame(layout)[c("x", "y")]) + 
+    geom_edge_link(
+      aes(
+        edge_width = abs(Loading),
+        edge_alpha = abs(Loading),
+        # edge_color = Loading,
+        filter = Type == "Loading"
+        # label = insight::format_value(Loading, lead_zero = FALSE, zap_small = TRUE)
+      ),
+      color = "#212121",
+      arrow = arrow(length = unit(2.5, "mm"), type = "closed"),
+      end_cap = circle(5, 'mm')
+    ) +
+      geom_edge_arc(
+      aes(
+        edge_width = abs(Loading),
+        filter = Type == "Correlation",
+        label = insight::format_value(Loading, lead_zero = FALSE, zap_small = TRUE)
+      ),
+      edge_color = "forestgreen",
+      angle_calc = "along",
+      label_dodge = unit(2.5, "mm"),
+      force_flip = TRUE,
+      strength = 0.2  # controls curvature
+    ) +
+    geom_node_label(data=filter(layout, type == "Item"), 
+                    aes(fill = name), 
+                    label = paste(rep(" ", 20), collapse = ""),
+                    size = 3, 
+                    hjust = 0.5, 
+                    nudge_x = -0.05,
+                    label.r = unit(0.2, "lines"),
+                    label.padding = unit(0.5, "lines"),
+                    label.size = 0) +
+    geom_node_label(data=filter(layout, type == "Item"), 
+                    aes(label = name), 
+                    fill = NA,
+                    size = 3, 
+                    hjust = 0.5, 
+                    vjust = 0.5,
+                    color = "white",
+                    fontface = "bold",
+                    nudge_x = -0.05,
+                    label.size = 0) +
+    geom_node_point(data=filter(layout, type == "Factor"), 
+                    aes(color = name), 
+                    size = 12) +
+    geom_node_text(data=filter(layout, type == "Factor"), 
+                   aes(label = name), 
+                   size = 4, 
+                   color = "white", 
+                   fontface = "bold") +
+    scale_edge_width(range = c(0.3, 2)) +
+    scale_edge_alpha(range = c(0.1, 1)) +
+    scale_fill_manual(values = colors) +
+    scale_color_manual(values = cols) +
+    labs(title = "Exploratory Factor Analysis (EFA)", subtitle = "Method = Oblimin") +
+    theme_void() +
+    theme(legend.position = "none",
+          plot.title = element_text(face="bold")) +
+    coord_cartesian(xlim = c(-0.08, 1.08))
+
+  list(n_fac=n_fac, efa=rez_efa, p=p_efa)
+}
+
+rez_efa <- make_efa(data_all, n = 3, cols = c("F1" = colors[["Wind"]], 
+                                              "F2" = colors[["Defecate"]], 
+                                              "F3" = colors[["Heart"]]))
+plot(rez_efa$n_fac)
+rez_efa$p
+```
+
+:::
+
+#### Final
+
+We discarded:
+
+- Taste: Lone item + unstable
+- Affective_touch: Cross-loadings + unstable
+- Vomit: Less strongly associated
+- Itch: Less strongly associated, did not form consistent cluster
+- More controversial: Temp and Sex_arousal: similar cluster yet less reliable
+
+```{r}
+#| code-fold: false
+
+data_allf <- select(data_all, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
+data1af <- select(data1a, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
+data1bf <- select(data1b, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
+data2f <- select(data2, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
+data3f <- select(data3, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
+data4f <- select(data4, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
+data5f <- select(data5, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
+data6f <- select(data6, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
+data7af <- select(data7a, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
+data7bf <- select(data7b, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
+data7cf <- select(data7c, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
+data8af <- select(data8a, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
+data8bf <- select(data8b, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
+data9f <- select(data9, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
+data10af <- select(data10a, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
+data10bf <- select(data10b, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
+data10cf <- select(data10c, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
+data11af <- select(data11a, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
+data11bf <- select(data11b, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
+```
+
+::: {.panel-tabset}
+
+##### HCA
+
+```{r}
+#| warning: false
+#| message: false
+
+rez_hclust <- make_hclust(data_allf)
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+rez_hclust$p
+```
+
+##### EGA
+
+```{r}
+#| warning: false
+#| message: false
+
+rez_ega <- make_ega(data_allf, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+rez_ega$p
+```
+
+##### EFA
+
+```{r}
+rez_efa <- make_efa(data_allf, n = 3, cols = 
+                      c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                        "F3" = colors[["Heart"]]))
+plot(rez_efa$n_fac)
+rez_efa$p
+```
+
+##### CFA
+
+```{r}
 #| fig-height: 20
@@
 
-make_egas <- function(data) {
-  egas <- list()
-  for (model in c("glasso")) {  # , "TMFG"
-    for (algo in c("walktrap", "louvain")) {
-      for (type in c("ega", "ega.fit")) { # "" # "hierega"
-        if (type == "ega.fit" & algo == "louvain") next # Too slow
-        egas[[paste0(model, "_", algo, "_", type)]] <- EGAnet::bootEGA(
-          data = data,
-          seed = 123,
-          model = model,
-          algorithm = algo,
-          EGA.type = type,
-          type = "resampling",
-          plot.itemStability = FALSE,
-          verbose = FALSE
+make_cfa <- function(data) {
+
+  # Main models
+  m_g <- '
+IAS =~ Burp + Wind + Cough + Sneeze + Hungry + Thirsty  + Urinate + Defecate + Heart + Breathing + Pain + Muscles 
+  '
+  m_ega <- '
+    CoughSneeze =~ Cough + Sneeze
+    UrinateDefecate =~ Urinate + Defecate
+    BruiseBloodsugar =~ Bruise + Blood_Sugar
+    WindBurp =~ Wind + Burp
+    HeartBreath =~ Heart + Breathing
+    MusclesPain =~ Muscles + Pain
+    HungryThirsty =~ Hungry + Thirsty
+  '
+
+  m_efa <- '
+    UrinateDefecate =~ Urinate + Defecate
+    Sudden =~ Cough + Sneeze + Wind + Burp
+    Homeostasis =~ Heart + Breathing + Muscles + Pain + Hungry + Thirsty + Bruise + Blood_Sugar
+  '
+
+  m_hclust <- '
+    HeartBreath =~ Heart + Breathing
+    BruiseBloodsugar =~ Bruise + Blood_Sugar
+    HungryThirsty =~ Hungry + Thirsty
+    Sudden =~ Cough + Sneeze + Wind + Burp
+    Unpleasant =~ Urinate + Defecate + Muscles + Pain
+  '
+
+  # Test bifactor models
+  m_egag <- paste0(m_ega, "\nIAS =~ CoughSneeze + WindBurp + BruiseBloodsugar + UrinateDefecate + HeartBreath + MusclesPain")
+  m_efag <- paste0(m_efa, "\nIAS =~ UrinateDefecate + Sudden + Homeostasis")
+  m_hclustg <- paste0(m_hclust, "\nIAS =~ HeartBreath + BruiseBloodsugar + HungryThirsty + Sudden + Unpleasant")
+
+  fit_g <- lavaan::cfa(m_g, data = data, std.lv = TRUE)
+  fit_ega <- lavaan::cfa(m_ega, data = data, std.lv = TRUE)
+  fit_egag <- lavaan::cfa(m_egag, data = data, std.lv = TRUE)
+  fit_efa <- lavaan::cfa(m_efa, data = data, std.lv = TRUE)
+  fit_efag <- lavaan::cfa(m_efag, data = data, std.lv = TRUE)
+  fit_hclust <- lavaan::cfa(m_hclust, data = data, std.lv = TRUE)
+  fit_hclustg <- lavaan::cfa(m_hclustg, data = data, std.lv = TRUE)
+
+  # Test
+  bf <- test_bf(fit_ega, fit_g, fit_egag, fit_efa, fit_efag, fit_hclust, fit_hclustg) |> 
+    as.data.frame() |> 
+    select(Name = Model, BF)
+
+  # test <- lavaan::lavTestLRT(fit_g, fit_ega, fit_egag, fit_efa, fit_efag, fit_hclust, fit_hclustg)
+  test <- compare_performance(fit_g, fit_ega, fit_egag, fit_efa, fit_efag, fit_hclust, fit_hclustg,
+                      metrics = c("BIC", "RMSEA", "Chi2", "CFI")) |> 
+    select(-BIC_wt, -Model) |> 
+    merge(bf, by = "Name") |>
+    arrange(BIC) |> 
+    gt::gt() |> 
+    gt::tab_header(title = "CFA Model Comparison") |>
+    gt::data_color(
+      columns = c(BIC, Chi2, RMSEA),
+      method = "numeric",
+      palette = c("green", "white")) |>
+    gt::data_color(
+      columns = c(CFI),
+      method = "numeric",
+      palette = c("white", "green")) |>
+    gt::data_color(
+      columns = c(BF),
+      method = "numeric",
+      palette = c("red", "yellow", "white", "yellow", "green"),
+      domain = c(0, 0.3, 1, 3, 10000000)) |>
+    gt::fmt_number(columns = c(RMSEA, Chi2, CFI), decimals = 3)
+
+  param  <- parameters::parameters(fit_ega)
+  perf <- performance::performance(fit_ega)
+
+  # Graph
+  nodes <- tidySEM::get_nodes(fit_ega) |> 
+    mutate(name = str_replace(name, "_", " "))
+  edges <- tidySEM::get_edges(fit_ega) |> 
+    mutate(from = str_replace(from, "_", " "),
+           to = str_replace(to, "_", " "), 
+           est_std = as.numeric(est_std)) |> 
+    filter(from != to)
+
+  g <- tidygraph::tbl_graph(nodes = nodes, edges = edges, directed = TRUE) 
+  set.seed(1)
+  layout <- ggraph::create_layout(g, layout = "fr", weights = est_std)
+
+  p_cfa <- ggraph(layout) +
+    geom_edge_bend(aes(edge_width = abs(est_std), edge_alpha = abs(est_std),
+                       label = format_value(est_std, zap_small = TRUE, lead_zero = FALSE),
+                       filter = arrow == "none"), 
+                   color = "forestgreen",
+                   angle_calc = "along", 
+                   check_overlap = TRUE,
+                   label_dodge = unit(0, "mm"),
+                   label_size = unit(3, "mm"),
+                   strength = 0.3) +
+    geom_edge_link(aes(edge_width = abs(est_std), edge_color = abs(est_std), 
+                       label = format_value(est_std, zap_small = TRUE, lead_zero = FALSE),
+                      filter = arrow != "none"), 
+                   angle_calc = "along", 
+                   label_dodge = unit(3, "mm"),
+                   arrow = arrow(length = unit(2.5, "mm"), type = "open", ends = "first"), 
+                   lineend = "round",
+                   linejoin = "bevel",
+                   start_cap = circle(9, 'mm')) +
+    geom_node_point(aes(color = name, shape=shape), alpha = 0.97, size = 20) +
+    geom_node_text(data = filter(layout, shape == "rect"), aes(label = name), 
+                   size = 3, color = "white", fontface = "bold") +
+    scale_size_continuous(range = c(10, 20)) +
+    scale_edge_width(range = c(0.3, 4)) +
+    scale_edge_alpha(range = c(0.1, 0.9)) +
+    scale_edge_color_gradient(low = "#EEEEEE", high = "#212121") +
+    scale_color_manual(values = c(colors, 
+                               "CoughSneeze" = "#CDDC39", 
+                               "UrinateDefecate" = "#795548", "BruiseBloodsugar" = "#673AB7",
+                               "WindBurp" = "#009688", "HeartBreath" = "#F44336",
+                               "MusclesPain" = "#2196F3", "HungryThirsty" = "#FF9800")) +
+    scale_shape_manual(values = c("oval" = 16, "rect" = 15)) +
+    labs(title = "Confirmatory Factor Analysis (CFA)", subtitle = "Method = Maximum Likelihood") +
+    theme_void() +
+    theme(legend.position = "none",
+          plot.title = element_text(face="bold"))
+  p_cfa
+
+  list(test = test, param = param, perf = perf, p=p_cfa)
+}
+
+rez_cfa0 <- make_cfa(data_allf)
+rez_cfa0$test
+rez_cfa0$perf
+rez_cfa0$param
+rez_cfa0$p
+```
+
+:::
+
+#### Figure
+
+The structural analysis seem to converge on the idea of small clusters (of pairs or triplets) that are potentially inter-related parts of larger clusters (although with unstable associations).
+Best way to assess the values of this new granular structure is to assess its predictive value against convergent measures, and see if it's superior to a unique score (-> Study 2).
+
+```{r}
+#| eval: false
+
+fig2 <- (rez_hclust$p | rez_ega$p) / (rez_efa$p | rez_cfa0$p) 
+ggsave("figures/Figure2.png", fig2, width=14, height=14, dpi=300, bg="white")
+```
+
+## Structure Invariance
+
+::: {.panel-tabset}
+
+### Sample 1a
+
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data1a)
+rez_ega <- make_ega(data1a, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data1a, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data1af)
+rez_ega <- make_ega(data1af, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data1af, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_cfa1a  <- make_cfa(data1af)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cfa1a$test
+```
+
+::::
+
+### Sample 1b
+
+TODO.
+
+:::
+
+## Model Performance
+
+```{r}
+#| warning: false
+
+rbind(
+  mutate(rez_cfa0$perf, Sample = "All Samples"),
+  mutate(rez_cfa1a$perf, Sample = "Sample 1a")
+  # TODO
+) |> 
+  select(Sample, Chi2, RMSEA, CFI, "SRMR") 
+```
+
+## Scores
+
+Note the usage of descriptive factor names relating directly to the items to avoid abstraction.
+
+```{r}
+#| warning: false
+
+# Add empirical variables
+add_empirical <- function(data, sample = "Sample 1a") {
+  x <- data.frame(
+    Original = rowMeans(data),
+    HungryThirsty = (data$Hungry + data$Thirsty) / 2,
+    MusclesPain = (data$Muscles + data$Pain) / 2,
+    WindBurp = (data$Wind + data$Burp) / 2,
+    UrinateDefecate = (data$Urinate + data$Defecate) / 2,
+    BreathingHeart = (data$Heart + data$Breathing) / 2)
+
+  if("Blood_Sugar" %in% names(data)) {
+    x$BruiseBlood <- (data$Blood_Sugar + data$Bruise) / 2
+  } else {
+    x$BruiseBlood <- data$Bruise
+  }
+
+  if("Cough" %in% names(data)) {
+    x$CoughSneeze <- (data$Cough + data$Sneeze) / 2
+  } else {
+    x$CoughSneeze <- data$Sneeze
+  }
+  x$Sample <- sample
+  x
+}
+
+scores <- list(
+  sample1a = add_empirical(data1a, "Sample 1a"),
+  sample1b = add_empirical(data1b, "Sample 1b"),
+  sample2 = add_empirical(data2, "Sample 2"),
+  sample3 = add_empirical(data3, "Sample 3"),
+  sample4 = add_empirical(data4, "Sample 4"),
+  sample5 = add_empirical(data5, "Sample 5"),
+  sample6 = add_empirical(data6, "Sample 6"),
+  sample7a = add_empirical(data7a, "Sample 7a"),
+  sample7b = add_empirical(data7b, "Sample 7b"),
+  sample7c = add_empirical(data7c, "Sample 7c"),
+  sample8a = add_empirical(data8a, "Sample 8a"),
+  sample8b = add_empirical(data8b, "Sample 8b"),
+  sample9 = add_empirical(data9, "Sample 9"),
+  sample10a = add_empirical(data10a, "Sample 10a"),
+  sample10b = add_empirical(data10b, "Sample 10b"),
+  sample10c = add_empirical(data10c, "Sample 10c"),
+  sample11a = add_empirical(data11a, "Sample 11a"),
+  sample11b = add_empirical(data11b, "Sample 11b")
 )
-      }
-    }
-  }
-
-  p <- EGAnet::compare.EGA.plots(
-    egas$glasso_walktrap_ega, 
-    # egas$glasso_walktrap_ega.fit,
-    egas$glasso_louvain_ega, 
-    # egas$TMFG_louvain_ega,
-    # egas$TMFG_walktrap_ega, 
-    # egas$TMFG_walktrap_ega.fit,
-    labels = c(
-      "glasso_walktrap_ega", 
-      # "glasso_walktrap_ega.fit",
-      "glasso_louvain_ega" 
-      # "TMFG_louvain_ega",
-      # "TMFG_walktrap_ega", 
-      # "TMFG_walktrap_ega.fit"
-    ),
-    rows = 3,
-    plot.all = FALSE
-  )$all
-  list(egas = egas, p = p)
-}
-
-egas_all <- make_egas(data_all)
-egas_all$p
-```
-
-#### Sample 1a
-
-```{r ega1a}
-#| fig-height: 20
-#| fig-width: 12
-
-egas1a <- make_egas(data1a)
-egas1a$p
-```
-
-#### Sample 1b
-
-```{r ega1b}
-#| fig-height: 20
-#| fig-width: 12
-
-egas1b <- make_egas(data1b)
-egas1b$p
-```
-
-#### Sample 2
-
-```{r ega2}
-#| fig-height: 20
-#| fig-width: 12
-
-egas2 <- make_egas(data2)
-egas2$p
-```
-
-#### Sample 3
-
-```{r ega3}
-#| fig-height: 20
-#| fig-width: 12
-
-egas3 <- make_egas(data3)
-egas3$p
-```
-
-#### Sample 4
-
-```{r ega4}
-#| fig-height: 20
-#| fig-width: 12
-
-egas4 <- make_egas(data4)
-egas4$p
-```
-
-#### Sample 5
-
-```{r ega5}
-#| fig-height: 20
-#| fig-width: 12
-
-egas5 <- make_egas(data5)
-egas5$p
-```
-
-#### Sample 6
-
-```{r ega6}
-#| fig-height: 20
-#| fig-width: 12
-
-egas6 <- make_egas(data6)
-egas6$p
-```
-
-#### Sample 7a
-
-```{r ega7&}
-#| fig-height: 20
-#| fig-width: 12
-
-egas7a <- make_egas(data7a)
-egas7a$p
-```
-
-#### Sample 7b
-
-```{r ega7b}
-#| fig-height: 20
-#| fig-width: 12
-
-egas7b <- make_egas(data7b)
-egas7b$p
-```
-
-#### Sample 7c
-
-```{r ega7c}
-#| fig-height: 20
-#| fig-width: 12
-
-egas7c <- make_egas(data7c)
-egas7c$p
-```
-
-#### Sample 8a
-
-```{r ega8a}
-#| fig-height: 20
-#| fig-width: 12
-
-egas8a <- make_egas(data8a)
-egas8a$p
-```
-
-#### Sample 8b
-
-```{r ega8b}
-#| fig-height: 20
-#| fig-width: 12
-
-egas8b <- make_egas(data8b)
-egas8b$p
-```
-
-#### Sample 9
-
-```{r ega9}
-#| fig-height: 20
-#| fig-width: 12
-
-egas9 <- make_egas(data9)
-egas9$p
-```
-
-#### Sample 10a
-
-```{r ega10a}
-#| fig-height: 20
-#| fig-width: 12
-
-egas10a <- make_egas(data10a)
-egas10a$p
-```
-
-#### Sample 10b
-
-```{r ega10b}
-#| fig-height: 20
-#| fig-width: 12
-
-egas10b <- make_egas(data10b)
-egas10b$p
-```
-
-#### Sample 10c
-
-```{r ega10c}
-#| fig-height: 20
-#| fig-width: 12
-
-egas10c <- make_egas(data10c)
-egas10c$p
-```
-
-#### Sample 11a
-
-```{r ega11a}
-#| fig-height: 20
-#| fig-width: 12
-
-egas11a <- make_egas(data11a)
-egas11a$p
-```
-
-#### Sample 11b
-
-```{r ega11c}
-#| fig-height: 20
-#| fig-width: 12
-
-egas11b <- make_egas(data11b)
-egas11b$p
-```
-
-:::
-
-### Structure Stability
-
-::: {.panel-tabset}
-
-#### All data
-
-```{r}
-#| fig-height: 20
-#| fig-width: 12
-
-patchwork::wrap_plots(lapply(egas_all$egas, plot), nrow = 3)
-```
-
-#### Sample 1a
-
-```{r}
-#| fig-height: 20
-#| fig-width: 12
-
-patchwork::wrap_plots(lapply(egas1a$egas, plot), nrow = 3)
-```
-
-#### Sample 1b
-
-```{r}
-#| fig-height: 20
-#| fig-width: 12
-
-patchwork::wrap_plots(lapply(egas1b$egas, plot), nrow = 3)
-```
-
-#### Sample 2
-
-```{r}
-#| fig-height: 20
-#| fig-width: 12
-
-patchwork::wrap_plots(lapply(egas2$egas, plot), nrow = 3)
-```
-
-#### Sample 3
-
-```{r}
-#| fig-height: 20
-#| fig-width: 12
-
-patchwork::wrap_plots(lapply(egas3$egas, plot), nrow = 3)
-```
-
-#### Sample 4
-
-```{r}
-#| fig-height: 20
-#| fig-width: 12
-
-patchwork::wrap_plots(lapply(egas4$egas, plot), nrow = 3)
-```
-
-#### Sample 5
-
-```{r}
-#| fig-height: 20
-#| fig-width: 12
-
-patchwork::wrap_plots(lapply(egas5$egas, plot), nrow = 3)
-```
-
-#### Sample 6
-
-```{r}
-#| fig-height: 20
-#| fig-width: 12
-
-patchwork::wrap_plots(lapply(egas6$egas, plot), nrow = 3)
-```
-
-#### Sample 7a
-
-```{r}
-#| fig-height: 20
-#| fig-width: 12
-
-patchwork::wrap_plots(lapply(egas7a$egas, plot), nrow = 3)
-```
-
-#### Sample 7b
-
-```{r}
-#| fig-height: 20
-#| fig-width: 12
-
-patchwork::wrap_plots(lapply(egas7b$egas, plot), nrow = 3)
-```
-
-#### Sample 7c
-
-```{r}
-#| fig-height: 20
-#| fig-width: 12
-
-patchwork::wrap_plots(lapply(egas7c$egas, plot), nrow = 3)
-```
-
-#### Sample 8a
-
-```{r}
-#| fig-height: 20
-#| fig-width: 12
-
-patchwork::wrap_plots(lapply(egas8a$egas, plot), nrow = 3)
-```
-
-#### Sample 8b
-
-```{r}
-#| fig-height: 20
-#| fig-width: 12
-
-patchwork::wrap_plots(lapply(egas8b$egas, plot), nrow = 3)
-```
-
-#### Sample 9
-
-```{r}
-#| fig-height: 20
-#| fig-width: 12
-
-patchwork::wrap_plots(lapply(egas9$egas, plot), nrow = 3)
-```
-
-#### Sample 10a
-
-```{r}
-#| fig-height: 20
-#| fig-width: 12
-
-patchwork::wrap_plots(lapply(egas10a$egas, plot), nrow = 3)
-```
-
-#### Sample 10b
-
-```{r}
-#| fig-height: 20
-#| fig-width: 12
-
-patchwork::wrap_plots(lapply(egas10b$egas, plot), nrow = 3)
-```
-
-#### Sample 10c
-
-```{r}
-#| fig-height: 20
-#| fig-width: 12
-
-patchwork::wrap_plots(lapply(egas10c$egas, plot), nrow = 3)
-```
-
-#### Sample 11a
-
-```{r}
-#| fig-height: 20
-#| fig-width: 12
-
-patchwork::wrap_plots(lapply(egas11a$egas, plot), nrow = 3)
-```
-
-#### Sample 11b
-
-```{r}
-#| fig-height: 20
-#| fig-width: 12
-
-patchwork::wrap_plots(lapply(egas11b$egas, plot), nrow = 3)
-```
-
-:::
-
-### Scores
-
-```{r}
-ega <- egas_all$egas$glasso_louvain_ega$EGA
-plot(ega)
-
-get_scores <- function(data, ega) {
-  EGAnet::net.scores(data, ega)$scores$std.scores |>
-    as.data.frame() |>
-    setNames(c("EGA1", "EGA2", "EGA3", "EGA4"))
-}
-
-ega_scores_1a <- get_scores(data1a, ega)
-ega_scores_1b <- get_scores(data1b, ega)
-ega_scores_2 <- get_scores(data2, ega)
-ega_scores_3 <- get_scores(data3, ega)
-ega_scores_4 <- get_scores(data4, ega)
-ega_scores_5 <- get_scores(data5, ega)
-ega_scores_6 <- get_scores(data6, ega)
-ega_scores_7a <- get_scores(data7a, ega)
-ega_scores_7b <- get_scores(data7b, ega)
-ega_scores_7c <- get_scores(data7c, ega)
-ega_scores_8a <- get_scores(data8a, ega)
-ega_scores_8b <- get_scores(data8b, ega)
-ega_scores_9 <- get_scores(data9, ega)
-ega_scores_10a <- get_scores(data10a, ega)
-ega_scores_10b <- get_scores(data10b, ega)
-ega_scores_10c <- get_scores(data10c, ega)
-ega_scores_11a <- get_scores(data11a, ega)
-ega_scores_11b <- na.omit(get_scores(data11b, ega)) # remove two rows with NAS
-row.names(ega_scores_11b) <- NULL
-```
-
-## Factor Analysis
-
-### How Many Factors
-
-::: {.panel-tabset}
-
-#### All data
-
-```{r}
-n <- parameters::n_factors(data_all, n_max = 12)
-
-plot(n)
-knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
-```
-
-#### Sample 1a
-
-```{r}
-n <- parameters::n_factors(data1a, n_max = 12)
-
-plot(n)
-knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
-```
-
-#### Sample 1b
-
-```{r}
-n <- parameters::n_factors(data1b, n_max = 12)
-
-plot(n)
-knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
-```
-
-#### Sample 2
-
-```{r}
-n <- parameters::n_factors(data2, n_max = 12)
-
-plot(n)
-knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
-```
-
-#### Sample 3
-
-```{r}
-n <- parameters::n_factors(data3, n_max = 12)
-
-plot(n)
-knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
-```
-
-#### Sample 4
-
-```{r}
-n <- parameters::n_factors(data4, n_max = 12)
-
-plot(n)
-knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
-```
-
-#### Sample 5
-
-```{r}
-n <- parameters::n_factors(data5, n_max = 12)
-
-plot(n)
-knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
-```
-
-#### Sample 6
-
-```{r}
-n <- parameters::n_factors(data6, n_max = 12)
-
-plot(n)
-knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
-```
-
-#### Sample 7a
-
-```{r}
-n <- parameters::n_factors(data7a, n_max = 12)
-
-plot(n)
-knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
-```
-
-#### Sample 7b
-
-```{r}
-n <- parameters::n_factors(data7b, n_max = 12)
-
-plot(n)
-knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
-```
-
-#### Sample 7c
-
-```{r}
-n <- parameters::n_factors(data7c, n_max = 12)
-
-plot(n)
-knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
-```
-
-#### Sample 8a
-
-```{r}
-n <- parameters::n_factors(data8a, n_max = 12)
-
-plot(n)
-knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
-```
-
-#### Sample 8b
-
-```{r}
-n <- parameters::n_factors(data8b, n_max = 12)
-
-plot(n)
-knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
-```
-
-#### Sample 9
-
-```{r}
-n <- parameters::n_factors(data9, n_max = 12)
-
-plot(n)
-knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
-```
-
-#### Sample 10a
-
-```{r}
-n <- parameters::n_factors(data10a, n_max = 12)
-
-plot(n)
-knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
-```
-
-#### Sample 10b
-
-```{r}
-n <- parameters::n_factors(data10b, n_max = 12)
-
-plot(n)
-knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
-```
-
-#### Sample 10c
-
-```{r}
-n <- parameters::n_factors(data10c, n_max = 12)
-
-plot(n)
-knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
-```
-
-#### Sample 11a
-
-```{r}
-n <- parameters::n_factors(data11a, n_max = 12)
-
-plot(n)
-knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
-```
-
-#### Sample 11b
-
-```{r}
-n <- parameters::n_factors(data11b, n_max = 12)
-
-plot(n)
-knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 3, 4, 5), ], row.names = FALSE)
-```
-:::
-
-### EFA
-
-::: {.panel-tabset}
-
-#### All data
-
-```{r}
-#| fig-height: 10
-
-efa5 <- parameters::factor_analysis(data_all, n = 4, rotation = "oblimin", sort = TRUE)
-plot(efa5)
-
-display(efa5)
-```
-
-#### Sample 1a
-
-```{r}
-#| fig-height: 10
-
-efa4 <- parameters::factor_analysis(data1a, n = 4, rotation = "oblimin", sort = TRUE)
-plot(efa4)
-
-display(efa4)
-```
-
-#### Sample 1b
-
-```{r}
-#| fig-height: 10
-
-efa4 <- parameters::factor_analysis(data1b, n = 4, rotation = "oblimin", sort = TRUE)
-plot(efa4)
-
-display(efa4)
-```
-
-#### Sample 2
-
-```{r}
-#| fig-height: 10
-
-efa4 <- parameters::factor_analysis(data2, n = 4, rotation = "oblimin", sort = TRUE)
-plot(efa4)
-
-display(efa4)
-
-```
-
-#### Sample 3
-
-```{r}
-#| fig-height: 10
-
-efa4 <- parameters::factor_analysis(data3, n = 4, rotation = "oblimin", sort = TRUE)
-plot(efa4)
-
-display(efa4)
-```
-
-#### sample 4
-
-```{r}
-#| fig-height: 10
-
-efa4 <- parameters::factor_analysis(data4, n = 4, rotation = "oblimin", sort = TRUE)
-plot(efa4)
-
-display(efa4)
-```
-
-#### Sample 5
-
-```{r}
-#| fig-height: 10
-
-efa4 <- parameters::factor_analysis(data5, n = 4, rotation = "oblimin", sort = TRUE)
-plot(efa4)
-
-display(efa4)
-```
-
-#### Sample 6
-
-```{r}
-#| fig-height: 10
-
-efa4 <- parameters::factor_analysis(data6, n = 4, rotation = "oblimin", sort = TRUE)
-plot(efa4)
-
-display(efa4)
-```
-
-#### Sample 7a
-
-```{r}
-#| fig-height: 10
-
-efa4 <- parameters::factor_analysis(data7a, n = 4, rotation = "oblimin", sort = TRUE)
-plot(efa4)
-
-display(efa4)
-```
-
-#### Sample 7b
-
-```{r}
-#| fig-height: 10
-
-efa4 <- parameters::factor_analysis(data7b, n = 4, rotation = "oblimin", sort = TRUE)
-plot(efa4)
-
-display(efa4)
-```
-
-#### Sample 7c
-
-```{r}
-#| fig-height: 10
-
-efa4 <- parameters::factor_analysis(data7c, n = 4, rotation = "oblimin", sort = TRUE)
-plot(efa4)
-
-display(efa4)
-```
-
-#### Sample 8a
-
-```{r}
-#| fig-height: 10
-
-efa4 <- parameters::factor_analysis(data8a, n = 4, rotation = "oblimin", sort = TRUE)
-plot(efa4)
-
-display(efa4)
-```
-
-#### Sample 8b
-
-```{r}
-#| fig-height: 10
-
-efa4 <- parameters::factor_analysis(data8b, n = 4, rotation = "oblimin", sort = TRUE)
-plot(efa4)
-
-display(efa4)
-```
-
-#### Sample 9
-
-```{r}
-#| fig-height: 10
-
-efa4 <- parameters::factor_analysis(data9, n = 4, rotation = "oblimin", sort = TRUE)
-plot(efa4)
-
-display(efa4)
-```
-
-#### Sample 10a
-
-```{r}
-#| fig-height: 10
-
-efa4 <- parameters::factor_analysis(data10a, n = 4, rotation = "oblimin", sort = TRUE)
-plot(efa4)
-
-display(efa4)
-```
-
-#### Sample 10b
-
-```{r}
-#| fig-height: 10
-
-efa4 <- parameters::factor_analysis(data10b, n = 4, rotation = "oblimin", sort = TRUE)
-plot(efa4)
-
-display(efa4)
-```
-
-#### Sample 10c
-
-```{r}
-#| fig-height: 10
-
-efa4 <- parameters::factor_analysis(data10c, n = 4, rotation = "oblimin", sort = TRUE)
-plot(efa4)
-
-display(efa4)
-```
-
-#### Sample 11a
-
-```{r}
-#| fig-height: 10
-
-efa4 <- parameters::factor_analysis(data11a, n = 4, rotation = "oblimin", sort = TRUE)
-plot(efa4)
-
-display(efa4)
-```
-
-#### Sample 11b
-
-```{r}
-#| fig-height: 10
-
-efa4 <- parameters::factor_analysis(data11b, n = 4, rotation = "oblimin", sort = TRUE)
-plot(efa4)
-
-display(efa4)
-```
-
-:::
-
-## CFA
-
-We discarded the following items:
-- Tickle: not present in the same dataset and consistently flagged as redundant.
-<!-- - Blood_Sugar -->
-
-Ambiguous:
-- Temp
-- Vomit
-- Affective_touch
-- Sex_arousal
-- Taste
-
-### Lower-Level Factors
-
-::: {.panel-tabset}
-
-#### All data
-
-```{r}
-m1 <- "
-Interoception =~ Hungry + Thirsty + Urinate + Defecate + Itch + Bruise + Muscles + Pain + Breathing + Heart + Cough + Sneeze + Wind + Burp
-"
-
-m4 <- "
-Sustenance =~ Hungry + Thirsty + Urinate + Defecate + Muscles + Pain
-Skin =~ Itch + Bruise
-HeartBreathing =~ Breathing + Heart
-Expulsion =~ Cough + Sneeze + Wind + Burp
-"
-
-m5 <- "
-Sustenance =~ Hungry + Thirsty + Pain
-UrinateDefecate =~ Urinate + Defecate
-Skin =~ Itch + Bruise + Muscles
-HeartBreathing =~ Breathing + Heart
-Expulsion =~ Cough + Sneeze + Wind + Burp
-"
-
-m6 <- "
-HungryThirsty =~ Hungry + Thirsty
-UrinateDefecate =~ Urinate + Defecate
-ItchBruise =~ Itch + Bruise
-MusclesPain =~ Muscles + Pain
-HeartBreathing =~ Breathing + Heart
-Expulsion =~ Cough + Sneeze + Wind + Burp
-"
-
-m7 <- "
-HungryThirsty =~ Hungry + Thirsty
-UrinateDefecate =~ Urinate + Defecate
-ItchBruise =~ Itch + Bruise
-MusclesPain =~ Muscles + Pain
-HeartBreathing =~ Breathing + Heart
-CoughSneeze =~ Cough + Sneeze
-WindBurp =~ Wind + Burp
-"
-
-is_converged <- function(m) {
-  ev <- eigen(lavaan::lavTech(m, "cov.lv")[[1]], symmetric=TRUE, only.values=TRUE)$values
-  if (any(ev < -1 * .Machine$double.eps^(3/4))) {
-    "Not converged"
-  } else {
-    ""
-  }
-}
-
-compare_mods <- function(data) {
-
-  fit_model <- function(f, data) {
-    if(!"Cough" %in% names(data)) {
-      f <- str_remove(f, fixed("Cough +"))
-    }
-    lavaan::cfa(f, data = data)
-  }
-
-  cfa1 <- fit_model(m1, data = data)
-  cfa4 <- fit_model(m4, data = data)
-  cfa5 <- fit_model(m5, data = data)
-  cfa6 <- fit_model(m6, data = data)
-  cfa7 <- fit_model(m7, data = data)
-
-  anova(cfa1, cfa4, cfa5, cfa6, cfa7) |> 
-    parameters::parameters() |>
-    mutate(AIC = format(round(AIC, 0), nsmall = 0),
-           BIC = format(round(BIC, 0), nsmall = 0),
-           Chi2 = format(round(Chi2, 2), nsmall = 2),
-           Converged = sapply(list(cfa1, cfa4, cfa5, cfa6, cfa7), is_converged))
-}
-
-display(compare_mods(data_all))
-
-m7_all <- lavaan::cfa(m7, data = data_all)
-parameters::parameters(m7_all, standardize=TRUE) |>
-  display()
-```
-
-#### Sample 1a
-
-```{r}
-#| warning: false
-
-display(compare_mods(data1a))
-```
-
-#### Sample 1b
-
-```{r}
-#| warning: false
-
-display(compare_mods(data1b))
-
-```
-
-#### Sample 2
-
-```{r}
-#| warning: false
-
-display(compare_mods(data2))
-
-```
-
-#### Sample 3
-
-```{r}
-#| warning: false
-
-display(compare_mods(data3))
-
-```
-
-#### Sample 4
-
-```{r}
-#| warning: false
-
-display(compare_mods(data4))
-
-```
-
-#### Sample 5
-
-```{r}
-#| warning: false
-
-display(compare_mods(data5))
-
-```
-
-#### Sample 6
-
-```{r}
-#| warning: false
-
-display(compare_mods(data6))
-```
-
-#### Sample 7a
-
-```{r}
-#| warning: false
-
-display(compare_mods(data7a))
-```
-
-#### Sample 7b
-
-```{r}
-#| warning: false
-
-display(compare_mods(data7b))
-
-```
-
-#### Sample 7c
-
-```{r}
-#| warning: false
-
-display(compare_mods(data7c))
-
-```
-
-#### Sample 8a
-
-```{r}
-#| warning: false
-
-display(compare_mods(data8a))
-```
-
-#### Sample 8b
-
-```{r}
-#| warning: false
-
-display(compare_mods(data8b))
-```
-
-#### Sample 9
-
-```{r}
-#| warning: false
-
-display(compare_mods(data9))
-
-```
-
-#### Sample 10a
-
-```{r}
-#| warning: false
-
-display(compare_mods(data10a))
-
-```
-
-#### Sample 10b
-
-```{r}
-#| warning: false
-
-display(compare_mods(data10b))
-
-```
-
-#### Sample 10c
-
-```{r}
-#| warning: false
-
-display(compare_mods(data10c))
-
-```
-
-#### Sample 11a
-
-```{r}
-#| warning: false
-
-display(compare_mods(data11a))
-
-```
-
-#### Sample 11b
-
-```{r}
-#| warning: false
-
-display(compare_mods(data11b))
-
-```
-
-:::
-
-Conclusion: The 7th factor solution was preferred in most datasets, including by indices that penalize increased number of parameters (such as BIC).
-
-### Higher Order Factors
-
-::: {.panel-tabset}
-
-#### All data
-
-```{r}
-m7h1 <- paste0(m7, "
-              Interoception =~ HungryThirsty + UrinateDefecate + ItchBruise + MusclesPain + HeartBreathing + CoughSneeze + WindBurp
-              ")
-
-m7h2 <- paste0(m7, "
-              Expulsion =~ CoughSneeze + WindBurp
-              Interoception =~ HungryThirsty + UrinateDefecate + HeartBreathing
-              ")
-
-m7h3 <- paste0(m7, "
-              Valenced =~ MusclesPain + HeartBreathing + ItchBruise
-              Expulsion =~ CoughSneeze + WindBurp
-              Homeostasis =~ HungryThirsty + UrinateDefecate
-              ")
-
-compare_mods_h <- function(data) {
-
-  fit_model_h <- function(f, data) {
-    if(!"Cough" %in% names(data)) {
-      f <- str_remove(f, fixed("Cough +"))
-    }
-    lavaan::cfa(f, data = data)
-  }
-
-  m7 <- fit_model_h(m7, data = data)
-  m7h2 <- fit_model_h(m7h2, data = data)
-  m7h1 <- fit_model_h(m7h1, data = data)
-  m7h3 <- fit_model_h(m7h3, data = data)
-
-  anova(m7, m7h1, m7h2, m7h3) |>
-    parameters::parameters() |>
-    mutate(AIC = format(round(AIC, 0), nsmall = 0),
-           BIC = format(round(BIC, 0), nsmall = 0),
-           Chi2 = format(round(Chi2, 2), nsmall = 2),
-           Converged = sapply(list(m7, m7h1, m7h2, m7h3), is_converged))
-}
-
-display(compare_mods_h(data_all))
-```
-
-No evidence for higher order factors.
-
-#### Sample 1a
-
-```{r}
-display(compare_mods_h(data1a))
-```
-
-#### Sample 1b
-
-```{r}
-display(compare_mods_h(data1b))
-```
-
-#### Sample 2
-
-```{r}
-display(compare_mods_h(data2))
-```
-
-#### Sample 3
-
-```{r}
-display(compare_mods_h(data3))
-```
-
-#### Sample 4
-
-```{r}
-display(compare_mods_h(data4))
-```
-
-#### Sample 5
-
-```{r}
-display(compare_mods_h(data5))
-```
-
-#### Sample 6
-
-```{r}
-display(compare_mods_h(data6))
-```
-
-#### Sample 7a
-
-```{r}
-display(compare_mods_h(data7a))
-```
-
-#### Sample 7b
-
-```{r}
-display(compare_mods_h(data7b))
-```
-
-#### Sample 7c
-
-```{r}
-display(compare_mods_h(data7c))
-```
-
-#### Sample 8a
-
-```{r}
-display(compare_mods_h(data8a))
-```
-
-#### Sample 8b
-
-```{r}
-display(compare_mods_h(data8b))
-```
-
-#### Sample 9
-
-```{r}
-display(compare_mods_h(data9))
-```
-
-#### Sample 10a
-
-```{r}
-display(compare_mods_h(data10a))
-```
-
-#### Sample 10b
-
-```{r}
-display(compare_mods_h(data10b))
-```
-
-#### Sample 10c
-
-```{r}
-display(compare_mods_h(data10c))
-```
-
-#### Sample 11a
-
-```{r}
-display(compare_mods_h(data11a))
-```
-
-#### Sample 11b
-
-```{r}
-display(compare_mods_h(data11b))
-```
-
-:::
-
-### Model Performance
-
-```{r}
-#| warning: false
-
-rbind(
-  performance::performance(m7_all, metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
-    mutate(Sample = "All"),
-  performance::performance(update(m7_all, data = data1a), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
-    mutate(Sample = "Sample 1a"),
-  performance::performance(update(m7_all, data = data1b), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
-    mutate(Sample = "Sample 1b"),
-  performance::performance(update(m7_all, data = data2), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
-    mutate(Sample = "Sample 2"),
-  performance::performance(update(m7_all, data = data3), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
-    mutate(Sample = "Sample 3"),
-  performance::performance(update(m7_all, data = data4), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
-    mutate(Sample = "Sample 4"),
-  performance::performance(update(m7_all, data = data5), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
-    mutate(Sample = "Sample 5"),
-  performance::performance(update(m7_all, data = data6), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
-    mutate(Sample = "Sample 6"),
-  performance::performance(update(m7_all, data = data7a), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
-    mutate(Sample = "Sample 7a"),
-  performance::performance(update(m7_all, data = data7b), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
-    mutate(Sample = "Sample 7b"),
-  performance::performance(update(m7_all, data = data7c), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
-    mutate(Sample = "Sample 7c"),
-  performance::performance(update(m7_all, data = data8a), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
-    mutate(Sample = "Sample 8a"),
-  performance::performance(update(m7_all, data = data8b), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
-    mutate(Sample = "Sample 8b"),
-  performance::performance(update(m7_all, data = data9), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
-    mutate(Sample = "Sample 9"),
-  performance::performance(lavaan::cfa(str_remove(m7, fixed("\nCoughSneeze =~ Cough + Sneeze")), data = data10a), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
-    mutate(Sample = "Sample 10a"),
-  performance::performance(update(m7_all, data = data10b), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
-    mutate(Sample = "Sample 10b"),
-  performance::performance(update(m7_all, data = data10c), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
-    mutate(Sample = "Sample 10c"),
-  performance::performance(update(m7_all, data = data11a), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
-    mutate(Sample = "Sample 11a"),
-  performance::performance(update(m7_all, data = data11b), metrics = c("Chi2", "RMSEA", "CFI", "SRMR")) |>
-    mutate(Sample = "Sample 11b")
-) |>
-  display()
-```
-
-## Scores
-
-Note the usage of descriptive factor names relating directly to the items to avoid abstraction.
-
-```{r}
-#| warning: false
-
-# Add empirical variables
-add_empirical <- function(data, df) {
-  x <- data |>
-    mutate(
-      HungryThirsty = (df$Hungry + df$Thirsty) / 2,
-      UrinateDefecate = (df$Urinate + df$Defecate) / 2,
-      MusclesPain = (df$Muscles + df$Pain) / 2,
-      HeartBreathing = (df$Heart + df$Breathing) / 2,
-      ItchBruise = (df$Itch + df$Bruise) / 2,
-      WindBurp = (df$Wind + df$Burp) / 2)
-  if("Cough" %in% names(df)) {
-    mutate(x, CoughSneeze = (df$Cough + df$Sneeze) / 2)
-  } else {
-    mutate(x, CoughSneeze = df$Sneeze)
-  }
-}
-
-# Deal with missing data
-temp <- predict(m7_all, newdata=data7c)
-scores7c <- data.frame(matrix(ncol = 7, nrow = nrow(ega_scores_7c))) 
-scores7c[!is.na(ega_scores_7c$EGA1), ] <- temp
-names(scores7c) <- names(as.data.frame(temp))
-
-scores <- list(
-  sample1a = cbind(ega_scores_1a, data_addprefix(as.data.frame(predict(m7_all, newdata=data1a)), "CFA_")) |>
-    add_empirical(data1a) |> 
-    mutate(Sample = "Sample 1a"),
-  sample1b = cbind(ega_scores_1b, data_addprefix(as.data.frame(predict(m7_all, newdata=data1b)), "CFA_")) |>
-    add_empirical(data1b) |> 
-    mutate(Sample = "Sample 1b"),
-  sample2 = cbind(ega_scores_2, data_addprefix(as.data.frame(predict(m7_all, newdata=data2)), "CFA_")) |>
-    add_empirical(data2) |> 
-    mutate(Sample = "Sample 2"),
-  sample3 = cbind(ega_scores_3, data_addprefix(as.data.frame(predict(m7_all, newdata=data3)), "CFA_")) |>
-    add_empirical(data3) |> 
-    mutate(Sample = "Sample 3"),
-  sample4 = cbind(ega_scores_4, data_addprefix(as.data.frame(predict(m7_all, newdata=data4)), "CFA_")) |>
-    add_empirical(data4) |> 
-    mutate(Sample = "Sample 4"),
-  sample5 = cbind(ega_scores_5, data_addprefix(as.data.frame(predict(m7_all, newdata=data5)), "CFA_")) |>
-    add_empirical(data5) |> 
-    mutate(Sample = "Sample 5"),
-  sample6 = cbind(ega_scores_6, data_addprefix(as.data.frame(predict(m7_all, newdata=data6)), "CFA_")) |>
-    add_empirical(data6) |> 
-    mutate(Sample = "Sample 6"),
-  sample7a = cbind(ega_scores_7a, data_addprefix(as.data.frame(predict(m7_all, newdata=data7a)), "CFA_")) |>
-    add_empirical(data7a) |> 
-    mutate(Sample = "Sample 7a"),
-  sample7b = cbind(ega_scores_7b, data_addprefix(as.data.frame(predict(m7_all, newdata=data7b)), "CFA_")) |>
-    add_empirical(data7b) |> 
-    mutate(Sample = "Sample 7b"),
-  sample7c = cbind(ega_scores_7c, data_addprefix(scores7c, "CFA_")) |> 
-    add_empirical(data7c) |> 
-    mutate(Sample = "Sample 7c"),
-  sample8a = cbind(ega_scores_8a, data_addprefix(as.data.frame(predict(m7_all, newdata=data8a)), "CFA_")) |>
-    add_empirical(data8a) |> 
-    mutate(Sample = "Sample 8a"),
-  sample8b = cbind(ega_scores_8b, data_addprefix(as.data.frame(predict(m7_all, newdata=data8b)), "CFA_")) |>
-    add_empirical(data8b) |> 
-    mutate(Sample = "Sample 8b"),
-  sample9 = cbind(ega_scores_9, data_addprefix(as.data.frame(predict(m7_all, newdata=data9)), "CFA_")) |>
-    add_empirical(data9) |> 
-    mutate(Sample = "Sample 9"),
-  sample10a = cbind(ega_scores_10a, data_addprefix(as.data.frame(predict(lavaan::cfa(str_remove(m7, fixed("\nCoughSneeze =~ Cough + Sneeze")), data = data_all), newdata=data10a)), "CFA_")) |>
-    add_empirical(data10a) |> 
-    mutate(Sample = "Sample 10a", CFA_CoughSneeze = NA),
-  sample10b = cbind(ega_scores_10b, data_addprefix(as.data.frame(predict(m7_all, newdata=data10b)), "CFA_")) |>
-    add_empirical(data10b) |> 
-    mutate(Sample = "Sample 10b"),
-  sample10c = cbind(ega_scores_10c, data_addprefix(as.data.frame(predict(m7_all, newdata=data10c)), "CFA_")) |>
-    add_empirical(data10c) |> 
-    mutate(Sample = "Sample 10c"),
-  sample11a = cbind(ega_scores_11a, data_addprefix(as.data.frame(predict(m7_all, newdata=data11a)), "CFA_")) |>
-    add_empirical(data11a) |> 
-    mutate(Sample = "Sample 11a"),
-  sample11b = cbind(ega_scores_11b, data_addprefix(as.data.frame(predict(m7_all, newdata=data11b)), "CFA_")) |>
-    add_empirical(data11b) |> 
-    mutate(Sample = "Sample 11b")
-)
 

### 2025-07-06 analysis/figures/table1.tex
updated EGA andEFA analysis
removed item
update

@@
-\begin{table}[!t]
+\begin{table}
 \fontsize{6.8pt}{8.1pt}\selectfont
@@
 \toprule
-Sample & Subsample & Language & N & Difference & Age (Mean  ± SD) & Range & Female \% & Availability \\ 
+Reference & Sample & Language & N & Difference & Age (Mean  ± SD) & Range & Female \% & Availability \\ 
 \midrule\addlinespace[2.5pt]
 Murphy et al., (2020) &  &  &  &  &  &  &  & osf.io/3m5nh \\ 
- & Sample 1 & English & 451 &  & 25.8 ± 8.4 & 18-69 & 69.4\% &  \\ 
- & Sample 2 & English & 375 &  & 35.3 ± 16.9 & 18-91 & 70.1\% &  \\ 
-Gaggero et al., (2021) &  & English and Italian & 814 &  & 24.9 ± 5.3 & 18-58 & 60.3\% & osf.io/5x9sg \\ 
-Campos et al., (2022) &  & Portuguese & 515 &  & 30.7 ± 10.5 & 18-72 & 59.6\% & osf.io/j6ef3 \\ 
-Todd et al., (2022) &  & English & 802 &  & 48.6.6 ± 14.1* & 18-92* & 50\%* & osf.io/ms354 \\ 
-Arslanova et al., (2022) &  & English & 143 &  & 28.5 ± 7.6 & 18-73 & 46.8\% & osf.io/mp3cy \\ 
-Brand et al., (2022) &  & German & 619 &  & 43.9 ± 14.5 & 18-78 & 78.7\% & osf.io/xwz6g \\ 
+ & Sample 1a & English & 451 &  & 25.8 ± 8.4 & 18-69 & 69.4\% &  \\ 
+ & Sample 1b & English & 375 &  & 35.3 ± 16.9 & 18-91 & 70.1\% &  \\ 
+Gaggero et al., (2021) & Sample 2 & English and Italian & 814 &  & 24.9 ± 5.3 & 18-58 & 60.3\% & osf.io/5x9sg \\ 
+Campos et al., (2022) & Sample 3 & Portuguese & 515 &  & 30.7 ± 10.5 & 18-72 & 59.6\% & osf.io/j6ef3 \\ 
+Todd et al., (2022) & Sample 4 & English & 802 &  & 48.6.6 ± 14.1* & 18-92* & 50\%* & osf.io/ms354 \\ 
+Arslanova et al., (2022) & Sample 5 & English & 143 &  & 28.5 ± 7.6 & 18-73 & 46.8\% & osf.io/mp3cy \\ 
+Brand et al., (2022) & Sample 6 & German & 619 &  & 43.9 ± 14.5 & 18-78 & 78.7\% & osf.io/xwz6g \\ 
 Brand et al., (2023) &  &  &  &  &  &  &  & osf.io/3f2h6 \\ 
- & Sample 1 & German & 522 &  & 23.4 ± 6.7 & 18-79 & 79.5\% &  \\ 
- & Sample 2 & German & 1993 &  & 32.0 ± 12.6 & 16-81 & 77.7\% &  \\ 
- & Sample 3 & German & 802 &  & 27.3 ± 9.3 & 18-72 & 68.9\% &  \\ 
+ & Sample 7a & German & 522 &  & 23.4 ± 6.7 & 18-79 & 79.5\% &  \\ 
+ & Sample 7b & German & 1993 &  & 32.0 ± 12.6 & 16-81 & 77.7\% &  \\ 
+ & Sample 7c & German & 802 &  & 27.3 ± 9.3 & 18-72 & 68.9\% &  \\ 
 Lin et al., (2023) &  &  &  &  &  &  &  & osf.io/3eztd \\ 
- & Sample 1 & Chinese & 1166 & Collapsed "Itch" and "Tingling" & 32.5 ± 8.4 & 16-60 & 57.0\% &  \\ 
- & Sample 2 & Chinese & 500 & Collapsed "Itch" and "Tingling" & 37.4 ± 7.4 & 20-60 & 56.2\% &  \\ 
-VonMohr et al., (2023) &  & English & 21843 &  & 56.5 ± 14.4 & 18-93 & 73.2\% & osf.io/7p9u5 \\ 
-Makowski et al., (2023a) &  & English & 485 & Analog scales & 30.1 ± 10.1 & 18-73 & 50.3\% & github.com/RealityBending/IllusionGameReliability \\ 
-Makowski et al., (2023b) &  & English & 836 & Analog scales & 25.1 ± 11.3 & 17-76 & 53.0\% & github.com/DominiqueMakowski/PHQ4R \\ 
-Makowski et al., (2023c) &  & English & 146 & Analog scales & 21.1 ± 4.3 & 18-50 & 76\% & github.com/RealityBending/InteroceptionPrimals \\ 
-Poerio et al., (2024) &  & English & 107 &  & 26.8 ± 9.2 & 18-57 & 74.8\% & osf.io/49wbv \\ 
-Poerio et al., unpublished &  & English & 131 &  & 30.9 ± 12.0 & 18-60 & 75.9\% &  \\ 
-Total &  &  & 32214 &  & 48.6 ± 13.1 & 17-93 & 71.6\% &  \\ 
+ & Sample 8a & Chinese & 1166 & Collapsed "Itch" and "Tickling" & 32.5 ± 8.4 & 16-60 & 57.0\% &  \\ 
+ & Sample 8b & Chinese & 500 & Collapsed "Itch" and "Tickling" & 37.4 ± 7.4 & 20-60 & 56.2\% &  \\ 
+VonMohr et al., (2023) & Sample 9 & English & 21843 &  & 56.5 ± 14.4 & 18-93 & 73.2\% & osf.io/7p9u5 \\ 
+Makowski et al., (2023a) & Sample 10 & English & 485 & Analog scales & 30.1 ± 10.1 & 18-73 & 50.3\% & github.com/RealityBending/IllusionGameReliability \\ 
+Makowski et al., (2023b) & Sample 11 & English & 836 & Analog scales & 25.1 ± 11.3 & 17-76 & 53.0\% & github.com/DominiqueMakowski/PHQ4R \\ 
+Makowski et al., (2023c) & Sample 12 & English & 146 & Analog scales & 21.1 ± 4.3 & 18-50 & 76\% & github.com/RealityBending/InteroceptionPrimals \\ 
+Poerio et al., (2024) & Sample 13 & English & 107 &  & 26.8 ± 9.2 & 18-57 & 74.8\% & osf.io/49wbv \\ 
+Poerio et al., unpublished & Sample 14 & English & 131 &  & 30.9 ± 12.0 & 18-60 & 75.9\% &  \\ 
+Total & Sample 15 &  & 32214 &  & 48.6 ± 13.1 & 17-93 & 71.6\% &  \\ 
 \bottomrule

### 2025-07-06 analysis/study2.qmd
updated manuscript
update

@@
 library(patchwork)
-library(lavaan)
-library(ggraph)
-library(tidySEM)
-library(EGAnet)
 ```
@@
 
-vars_intero <- names(select(scores$sample1a, -Sample, -starts_with("CFA_"), -starts_with("EGA")))
-# vars_cfa <- names(select(scores$sample1a, -Sample, -starts_with("EGA")))
-# vars_intero <- vars_cfa[vars_cfa != "CoughSneeze"]
+vars_intero <- names(select(scores$sample1a, -Sample))
 
@@
 
-## Empirical Scores vs. Model-based
-
-```{r}
-#| warning: false
-
-vars_scores <- names(select(scores$sample1a, -Sample))
-df_scores <- rbind(
-  select(df1a, all_of(vars_scores)),
-  select(df1b, all_of(vars_scores)),
-  select(df2, all_of(vars_scores)),
-  select(df3, all_of(vars_scores)),
-  select(df4, all_of(vars_scores)),
-  select(df5, all_of(vars_scores)),
-  select(df6, all_of(vars_scores)),
-  select(df7a, all_of(vars_scores)),
-  select(df7b, all_of(vars_scores)),
-  select(df7c, all_of(vars_scores)),
-  select(df8a, all_of(vars_scores)),
-  select(df8b, all_of(vars_scores)),
-  select(df9, all_of(vars_scores)),
-  select(df10a, all_of(vars_scores)),
-  select(df10b, all_of(vars_scores)),
-  select(df10c, all_of(vars_scores)),
-  select(df11a, all_of(vars_scores)),
-  select(df11b, all_of(vars_scores))
-)
-
-order <- c("WindBurp", "CoughSneeze", "MusclesPain", "ItchBruise", "HeartBreathing", "HungryThirsty", "UrinateDefecate")
-
-correlation::correlation(select(df_scores, -all_of(vars_intero)),
-                         select(df_scores, all_of(vars_intero))) |> 
-  mutate(val = paste0(insight::format_value(r), format_p(p, stars_only = TRUE))) |>
-    mutate(Parameter2 = fct_relevel(Parameter2, rev(order)),
-           Parameter1 = fct_relevel(Parameter1, paste0("CFA_", order), "EGA3", "EGA2", "EGA4", "EGA1")) |>
-    ggplot(aes(x = Parameter1, y = Parameter2)) +
-    geom_tile(aes(fill = r), color = "white") +
-    geom_text(aes(label = val), size = 3) +
-    labs(title = "Correlation Matrix") +
-    scale_fill_gradient(low="blue", high="red", limit = c(0.1, 1), guide = guide_colourbar(ticks = FALSE)) +
-    theme_minimal() +
-    theme(
-      legend.title = element_blank(),
-      axis.title.x = element_blank(),
-      axis.title.y = element_blank(),
-      axis.text.x = element_text(angle = 45, hjust = 1)
-    )
-```
-
-Even EGA components capture pairs or groupings of pairs of items.
-
 ## Demographics
@@
 ```{r}
-make_diff <- function(df, vars, component=NA) {
-  df <- select(df, all_of(c("Gender", "Sample", vars)))
-  df <- df[complete.cases(df), ]
-  dat <- data.frame()
-  for (resp in vars) {
-    f <- as.formula(paste0(resp, "~ Gender"))
-    d <- filter(df, Gender %in% c("Male", "Female")) |>
-      mutate(Gender = fct_relevel(Gender, "Male", "Female"))
-    dat <- effectsize::cohens_d(f, data=d) |>
-      as.data.frame() |>
-      mutate(var_Correlate = "Gender", 
-             var_Interoception = resp,
-             p=t.test(f, data=d)$p.val) |>
-      rbind(dat)
+#| warning: false
+
+pool_coef <- function(with = "Age", component = "Demographic", standardize="within") {
+  rez <- data.frame()
+  for(intero in vars_intero) {
+    data <- data.frame() 
+    for(dataset in list(df1a, df1b, df2, df3, df4, 
+                     df5, df6, df7a, df7b, df7c, 
+                     df8a, df8b, df9, df10a, df10b, 
+                     df10c, df11a, df11b)) {
+      if (with %in% names(dataset)) {
+        d <- dataset[c(with, intero, "Sample")]
+        if(standardize == "within") d <- standardize(d)
+        data <- rbind(data, d)
+      }
     }
 
-  dat$r <- effectsize::d_to_r(dat$Cohens_d, n1=sum(df$Gender=="Male"), n2=sum(df$Gender=="Female"))
-  dat$CI_low <- effectsize::d_to_r(dat$CI_low, n1=sum(df$Gender=="Male"), n2=sum(df$Gender=="Female"))
-  dat$CI_high <- effectsize::d_to_r(dat$CI_high, n1=sum(df$Gender=="Male"), n2=sum(df$Gender=="Female"))
-  dat$Sample <- unique(df$Sample)
-  dat$Component <- component
-  select(dat, -Cohens_d)
+    if(standardize == "between") {
+      data <- standardize(data[complete.cases(data), ])
     }
 
-data <- rbind(
-  make_diff(df1a, vars_intero, component="Demographic"),
-  make_diff(df1b, vars_intero, component="Demographic"),
-  make_diff(df2, vars_intero, component="Demographic"),
-  make_diff(df3, vars_intero, component="Demographic"),
-  #make_diff(df4, vars_intero, component="Demographic"),
-  #make_diff(df5_attention, vars_intero, component="Demographic"),
-  make_diff(df6, vars_intero, component="Demographic"),
-  make_diff(df7a, vars_intero, component="Demographic"),
-  make_diff(df7b, vars_intero, component="Demographic"),
-  make_diff(df7c, vars_intero, component="Demographic"),
-  make_diff(df8a, vars_intero, component="Demographic"),
-  make_diff(df8b, vars_intero, component="Demographic"),
-  make_diff(df9, vars_intero, component="Demographic"),
-  make_diff(df10a, vars_intero, component="Demographic"),
-  make_diff(df10b, vars_intero, component="Demographic"),
-  make_diff(df10c, vars_intero, component="Demographic"),
-  make_diff(df11a, vars_intero, component="Demographic"),
-  make_diff(df11b, vars_intero, component="Demographic")
-) |>
-  mutate(var_Correlate = "Gender (Male vs. Female)")
+    if (with == "Gender") {
+      data <- data[data$Gender != "Other",]
+      data$Gender <- factor(data$Gender, levels = c("Male", "Female"))
+      f <- as.formula(paste0(intero, "~", with, " + (", with, "|Sample)"))
+      f2 <- as.formula(paste0(intero, "~", with, " + (1|Sample)"))
+    } else {
+      f <- as.formula(paste0(with, "~", intero, " + (", intero, "|Sample)"))
+      f2 <- as.formula(paste0(with, "~", intero, " + (1|Sample)"))
+    }
+
+    # if(length(unique(data$Sample)) == 1)
+    m <- glmmTMB::glmmTMB(f, data = data)
+    type <- "Full"
+    if(!insight::is_converged(m)) {
+      m <- glmmTMB::glmmTMB(f2, data = data)
+      type <- "Reduced"
+    }
+    out <- parameters::parameters(m)[2, ] |> 
+      select(r = Coefficient, CI_low, CI_high, p) |> 
+      as.data.frame()
+    out$var_Interoception <- intero
+    out$var_Correlate <- with
+    out$Component <- component
+    out$Method <- standardize
+    out$Type <- type
+    out$Converged <- insight::is_converged(m)
+    rez <- rbind(rez, out)
+
+  }
+  rez
+}
+
+make_rez <- function(with = "Gender", component = "Demographic", name = with) {
+  d <- rbind(
+    pool_coef(with = with, component = component, standardize="within"),
+    pool_coef(with = with, component = component, standardize="between")) 
+  d$var_Correlate <- name
+  d
+}
+
+data <- make_rez(with = "Gender", component = "Demographic", name = "Gender (Female - Male)")
 ```
@@
 ```{r}
-make_cor <- function(df, vars, with = "Age", component=NA) {
-  df <- select(df, all_of(c(with, "Sample", vars)))
-  df <- df[complete.cases(df), ]
+#| warning: false
 
-  dat <- data.frame()
-  for (v in vars) {
-    dat <- correlation::cor_test(df, v, with) |>
-      rename(var_Interoception = Parameter1, var_Correlate = Parameter2) |>
-      as.data.frame() |>
-      rbind(dat)
-  }
-
-  dat$Sample <- unique(df$Sample)
-  dat$Component <- component
-  select(dat, -df_error, -t, -Method, -n_Obs)
-}
-
-data <- rbind(
-  data,
-  make_cor(df1a, vars_intero, with = "Age", component="Demographic"),
-  make_cor(df1b, vars_intero, with = "Age", component="Demographic"),
-  make_cor(df2, vars_intero, with = "Age", component="Demographic"),
-  make_cor(df3, vars_intero, with = "Age", component="Demographic"),
-  # make_cor(df4, vars_intero, with = "Age", component="Demographic"),
-  # make_cor(df5, vars_intero, with = "Age", component="Demographic"),
-  make_cor(df6, vars_intero, with = "Age", component="Demographic"),
-  make_cor(df7a, vars_intero, with = "Age", component="Demographic"),
-  make_cor(df7b, vars_intero, with = "Age", component="Demographic"),
-  make_cor(df7c, vars_intero, with = "Age", component="Demographic"),
-  make_cor(df8a, vars_intero, with = "Age", component="Demographic"),
-  make_cor(df8b, vars_intero, with = "Age", component="Demographic"),
-  make_cor(df9, vars_intero, with = "Age", component="Demographic"),
-  make_cor(df10a, vars_intero, with = "Age", component="Demographic"),
-  make_cor(df10b, vars_intero, with = "Age", component="Demographic"),
-  make_cor(df10c, vars_intero, with = "Age", component="Demographic"),
-  make_cor(df11a, vars_intero, with = "Age", component="Demographic"),
-  make_cor(df11b, vars_intero, with = "Age", component="Demographic")
-)
+data <- rbind(data, make_rez(with = "Age", component = "Demographic"))
 ```
@@
 ```{r}
-names(df2)[str_detect(names(df2), "MAIA")]  
-names(df4)[str_detect(names(df4), "MAIA")]  # individual items
-names(df7a)[str_detect(names(df7a), "MAIA")]  
-names(df7b)[str_detect(names(df7b), "maia")] 
-names(df7c)[str_detect(names(df7c), "MAIA")]
-names(df10a)[str_detect(names(df10a), "MAIA")]
-names(df10b)[str_detect(names(df10b), "MAIA2")] # all columns with NA values 
-names(df10c)[str_detect(names(df10c), "MAIA")]
-names(df11a)[str_detect(names(df11b), "MAIA")]
+# names(df2)[str_detect(names(df2), "MAIA")]  
+# names(df4)[str_detect(names(df4), "MAIA")]  # individual items
+# names(df7a)[str_detect(names(df7a), "MAIA")]  
+# names(df7b)[str_detect(names(df7b), "maia")] 
+# names(df7c)[str_detect(names(df7c), "MAIA")]
+# names(df10a)[str_detect(names(df10a), "MAIA")]
+# names(df10b)[str_detect(names(df10b), "MAIA2")] # all columns with NA values 
+# names(df10c)[str_detect(names(df10c), "MAIA")]
+# names(df11a)[str_detect(names(df11b), "MAIA")]
 
-data <- rbind(
-  data,
-  make_cor(df2, vars_intero, with = "MAIA_AttentionReg", component="MAIA")  |>
-    mutate(var_Correlate = "Attention Regulation"),
-  make_cor(df2, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
-    mutate(var_Correlate = "Listening"),
-  make_cor(df2, vars_intero, with = "MAIA_BodyTrusting", component="MAIA") |>
-    mutate(var_Correlate = "Trusting"),
-  make_cor(df2, vars_intero, with = "MAIA_EmoAwareness", component="MAIA") |>
-    mutate(var_Correlate = "Emotional Awareness"),
-  make_cor(df2, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
-    mutate(var_Correlate = "Not Distracting"),
-  make_cor(df2, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
-    mutate(var_Correlate = "Noticing"),
-  make_cor(df2, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
-    mutate(var_Correlate = "Not Worrying"),
-  make_cor(df2, vars_intero, with = "MAIA_SelfReg", component="MAIA") |>
-    mutate(var_Correlate = "Self Regulation"),
+# data <- rbind(
+#   data,
+#   make_rez(with = "MAIA_AttentionReg", component = "MAIA", name = "Attention Regulation"),
+#   make_rez(with = "MAIA_BodyListening", component = "MAIA", name = "Listening"),
+#   make_rez(with = "MAIA_BodyTrusting", component = "MAIA", name = "Trusting"),
+#   make_rez(with = "MAIA_EmoAwareness", component = "MAIA", name = "Emotional Awareness"),
+#   make_rez(with = "MAIA_NotDistracting", component = "MAIA", name = "Not Distracting"),
+#   make_rez(with = "MAIA_Noticing", component = "MAIA", name = "Noticing"),
+#   make_rez(with = "MAIA_NotWorrying", component = "MAIA", name = "Not Worrying"),
+#   make_rez(with = "MAIA_SelfReg", component = "MAIA", name = "Self Regulation"),
+#   make_rez(with = "MAIA_Trusting", component = "MAIA", name = "Trusting")
+# )
 
-  # df4
-
-  # df7a
-  make_cor(df7a, vars_intero, with = "mAIA_ATTENTION_REGULATION", component="MAIA") |>
-    mutate(var_Correlate = "Attention Regulation"),
-  make_cor(df7a, vars_intero, with = "MAIA_NOTICING", component="MAIA") |>
-    mutate(var_Correlate = "Noticing"),
-  make_cor(df7a, vars_intero, with = "MAIA_NON_DISTRACTING", component="MAIA") |>
-    mutate(var_Correlate = "Not Distracting"),
-  make_cor(df7a, vars_intero, with = "MAIA_NON_DISTRACTING", component="MAIA") |>
-    mutate(var_Correlate = "Not Distracting"),
-  make_cor(df7a, vars_intero, with = "MAIA_NOT_WORRYING", component="MAIA") |>
-    mutate(var_Correlate = "Not Worrying"),
-  make_cor(df7a, vars_intero, with = "MAIA_EMOTIONAL_AWARENESS", component="MAIA") |>
-    mutate(var_Correlate = "Emotional Awareness"),
-  make_cor(df7a, vars_intero, with = "MAIA_SELF_REGULATION", component="MAIA") |>
-    mutate(var_Correlate = "Self Regulation"),
-  make_cor(df7a, vars_intero, with = "MAIA_BODY_LISTENING", component="MAIA") |>
-    mutate(var_Correlate = "Listening"),
-  make_cor(df7a, vars_intero, with = "MAIA_TRUSTING", component="MAIA") |>
-    mutate(var_Correlate = "Trusting"),
-
-  # df7b
-  make_cor(df7b, vars_intero, with = "maiaNotice", component="MAIA") |>
-    mutate(var_Correlate = "Noticing"),
-  make_cor(df7b, vars_intero, with = "maiaNonDistracting", component="MAIA") |>
-    mutate(var_Correlate = "Not Distracting"),
-  make_cor(df7b, vars_intero, with = "maiaNotWorrying", component="MAIA") |>
-    mutate(var_Correlate = "Not Worrying"),
-  make_cor(df7b, vars_intero, with = "maiaAttentionRegulation", component="MAIA") |>
-    mutate(var_Correlate = "Attention Regulation"),
-  make_cor(df7b, vars_intero, with = "maiaEmotionalAwareness", component="MAIA") |>
-    mutate(var_Correlate = "Emotional Awareness"),
-  make_cor(df7b, vars_intero, with = "maiaSelfRegulation", component="MAIA") |>
-    mutate(var_Correlate = "Self Regulation"),
-  make_cor(df7b, vars_intero, with = "maiaBodyListening", component="MAIA") |>
-    mutate(var_Correlate = "Listening"),
-  make_cor(df7b, vars_intero, with = "maiaTrusting", component="MAIA") |>
-    mutate(var_Correlate = "Trusting"),
-
-  # df7c
-   make_cor(df7c, vars_intero, with = "MAIA_noticing", component="MAIA") |>
-    mutate(var_Correlate = "Noticing"),
-  make_cor(df7c, vars_intero, with = "MAIA_notdis", component="MAIA") |>
-    mutate(var_Correlate = "Not Distracting"),
-  make_cor(df7c, vars_intero, with = "MAIA_notwor", component="MAIA") |>
-    mutate(var_Correlate = "Not Worrying"),
-  make_cor(df7c, vars_intero, with = "MAIA_attreg", component="MAIA") |>
-    mutate(var_Correlate = "Attention Regulation"),
-  make_cor(df7c, vars_intero, with = "MAIA_emoaw", component="MAIA") |>
-    mutate(var_Correlate = "Emotional Awareness"),
-  make_cor(df7c, vars_intero, with = "MAIA_selfreg", component="MAIA") |>
-    mutate(var_Correlate = "Self Regulation"),
-  make_cor(df7c, vars_intero, with = "MAIA_bodlis", component="MAIA") |>
-    mutate(var_Correlate = "Listening"),
-  make_cor(df7c, vars_intero, with = "MAIA_trust", component="MAIA") |>
-    mutate(var_Correlate = "Trusting"),
-
-  # df10a
-  make_cor(df10a, vars_intero, with = "MAIA_AttentionRegulation", component="MAIA")  |>
-    mutate(var_Correlate = "Attention Regulation"),
-  make_cor(df10a, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
-    mutate(var_Correlate = "Listening"),
-  make_cor(df10a, vars_intero, with = "MAIA_EmotionalAwareness", component="MAIA") |>
-    mutate(var_Correlate = "Emotional Awareness"),
-  make_cor(df10a, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
-    mutate(var_Correlate = "Not Distracting"),
-  make_cor(df10a, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
-    mutate(var_Correlate = "Noticing"),
-  make_cor(df10a, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
-    mutate(var_Correlate = "Not Worrying"),
-  make_cor(df10a, vars_intero, with = "MAIA_SelfRegulation", component="MAIA") |>
-    mutate(var_Correlate = "Self Regulation"),
-  make_cor(df10a, vars_intero, with = "MAIA_Trusting", component="MAIA") |>
-    mutate(var_Correlate = "Trusting"),
-
-  #df10b
-
-  # df10c 
-  make_cor(df10c, vars_intero, with = "MAIA_AttentionRegulation", component="MAIA")  |>
-    mutate(var_Correlate = "Attention Regulation"),
-  make_cor(df10c, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
-    mutate(var_Correlate = "Listening"),
-  make_cor(df10c, vars_intero, with = "MAIA_EmotionalAwareness", component="MAIA") |>
-    mutate(var_Correlate = "Emotional Awareness"),
-  make_cor(df10c, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
-    mutate(var_Correlate = "Not Distracting"),
-  make_cor(df10c, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
-    mutate(var_Correlate = "Noticing"),
-  make_cor(df10c, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
-    mutate(var_Correlate = "Not Worrying"),
-  make_cor(df10c, vars_intero, with = "MAIA_SelfRegulation", component="MAIA") |>
-    mutate(var_Correlate = "Self Regulation"),
-  make_cor(df10c, vars_intero, with = "MAIA_Trusting", component="MAIA") |>
-    mutate(var_Correlate = "Trusting"),
-
-    # df11a
-  make_cor(df11a, vars_intero, with = "MAIA_Attention", component="MAIA")  |>
-    mutate(var_Correlate = "Attention Regulation"),
-  make_cor(df11a, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
-    mutate(var_Correlate = "Listening"),
-  make_cor(df11a, vars_intero, with = "MAIA_Emotional", component="MAIA") |>
-    mutate(var_Correlate = "Emotional Awareness"),
-  make_cor(df11a, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
-    mutate(var_Correlate = "Not Distracting"),
-  make_cor(df11a, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
-    mutate(var_Correlate = "Noticing"),
-  make_cor(df11a, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
-    mutate(var_Correlate = "Not Worrying"),
-  make_cor(df11a, vars_intero, with = "MAIA_SelfRegulation", component="MAIA") |>
-    mutate(var_Correlate = "Self Regulation"),
-  make_cor(df11a, vars_intero, with = "MAIA_Trusting", component="MAIA") |>
-    mutate(var_Correlate = "Trusting")
-)
 ```
@@
 ```{r}
+# names(df2)[str_detect(names(df2), "ICQ")] 
+# names(df7c)[str_detect(names(df7c), "ICQ")]
 
-names(df2)[str_detect(names(df2), "ICQ")] 
-names(df7c)[str_detect(names(df7c), "ICQ")]
-
-data <- rbind(
-  data,
-  make_cor(df2, vars_intero, with = "ICQ", component="ICQ") |>
-    mutate(var_Correlate = "ICQ"),
-  make_cor(df7c, vars_intero, with = "ICQ_sum", component="ICQ") |>
-    mutate(var_Correlate = "ICQ")
-)
-
+data <- rbind(data, make_rez(with = "ICQ", component="ICQ", name = "ICQ"))
 ```
@@
 # df3$BPQ_AutonomicReactivity <- -1*normalize(df3$BPQ_AutonomicReactivity)
-names(df2)[str_detect(names(df2), "BPQ")]  # BPQ_R_Supra and _Sub?
-names(df3)[str_detect(names(df3), "BPQ")]  
-names(df4)[str_detect(names(df4), "BPQ")]   # individual items 1-26
-names(df7b)[str_detect(names(df7b), "BPQ")]  # BPQ sum
-names(df8a)[str_detect(names(df8a), "BPQ")]  # individual items
+# names(df2)[str_detect(names(df2), "BPQ")]  # BPQ_R_Supra and _Sub?
+# names(df3)[str_detect(names(df3), "BPQ")]  
+# names(df4)[str_detect(names(df4), "BPQ")]   # individual items 1-26
+# names(df7b)[str_detect(names(df7b), "BPQ")]  # BPQ sum
+# names(df8a)[str_detect(names(df8a), "BPQ")]  # individual items
 
@@
 #  only one study assess alexithymia with BVAQ (df2)
-names(df2)[str_detect(names(df2), "TAS")]
-names(df3)[str_starts(names(df3), "TAS")]
-names(df7c)[str_starts(names(df7c), "TAS")]
-names(df8b)[str_starts(names(df8b), "TAS")]
-names(df11a)[str_starts(names(df11a), "TAS")]
+# names(df2)[str_detect(names(df2), "TAS")]
+# names(df3)[str_starts(names(df3), "TAS")]
+# names(df7c)[str_starts(names(df7c), "TAS")]
+# names(df8b)[str_starts(names(df8b), "TAS")]
+# names(df11a)[str_starts(names(df11a), "TAS")]
 
@@
 ```{r}
-names(df6)[str_detect(names(df6), "PHQ")] 
-names(df7b)[str_detect(names(df7b), "PHQ")]
-names(df7c)[str_detect(names(df7c), "BDI")]
-names(df8b)[str_detect(names(df8b), "PHQ")]
-names(df9)
-names(df11a)
+# names(df6)[str_detect(names(df6), "PHQ")] 
+# names(df7b)[str_detect(names(df7b), "PHQ")]
+# names(df7c)[str_detect(names(df7c), "BDI")]
+# names(df8b)[str_detect(names(df8b), "PHQ")]
+# names(df9)
+# names(df11a)
 
@@
 ```{r}
-names(df6)[str_detect(names(df6), "GAD")] 
-names(df7a)[str_detect(names(df7a), "STAI")] 
-names(df7b)[str_detect(names(df7b), "STAI")] 
-names(df7c)[str_detect(names(df7c), "STAI")]
-names(df10b)[str_detect(names(df10b), "STAI")] 
-names(df11a)[str_detect(names(df11a), "ANX")] # anx = stai-t
+# names(df6)[str_detect(names(df6), "GAD")] 
+# names(df7a)[str_detect(names(df7a), "STAI")] 
+# names(df7b)[str_detect(names(df7b), "STAI")] 
+# names(df7c)[str_detect(names(df7c), "STAI")]
+# names(df10b)[str_detect(names(df10b), "STAI")] 
+# names(df11a)[str_detect(names(df11a), "ANX")] # anx = stai-t
 
@@
 ```{r}
-names(df7a)[str_detect(names(df7a), "NEO")]
-names(df9)[str_detect(names(df9), "BFI_")]
-names(df10a)[str_detect(names(df10a), "IPIP6_")]
+# names(df7a)[str_detect(names(df7a), "NEO")]
+# names(df9)[str_detect(names(df9), "BFI_")]
+# names(df10a)[str_detect(names(df10a), "IPIP6_")]
 
@@
 ```{r}
-data <- rbind(
-  data,
-  make_cor(df10a, vars_intero, with = "PI_Alive", component="World Beliefs") |>
-    mutate(var_Correlate = "Alive"),
-  make_cor(df10a, vars_intero, with = "PI_Changing", component="World Beliefs") |>
-    mutate(var_Correlate = "Changing"),
-  make_cor(df10a, vars_intero, with = "PI_Enticing", component="World Beliefs") |>
-    mutate(var_Correlate = "Enticing"),
-  make_cor(df10a, vars_intero, with = "PI_Good", component="World Beliefs") |>
-    mutate(var_Correlate = "Good"),
-  make_cor(df10a, vars_intero, with = "PI_Hierarchical", component="World Beliefs") |>
-    mutate(var_Correlate = "Hierarchical"),
-  make_cor(df10a, vars_intero, with = "PI_Safe", component="World Beliefs") |>
-    mutate(var_Correlate = "Safe"),
-  make_cor(df10a, vars_intero, with = "PI_Understandable", component="World Beliefs") |>
-    mutate(var_Correlate = "Understandable"),
-  make_cor(df10c, vars_intero, with = "PI_Alive", component="World Beliefs") |>
-    mutate(var_Correlate = "Alive"),
-  make_cor(df10c, vars_intero, with = "PI_Changing", component="World Beliefs") |>
-    mutate(var_Correlate = "Changing"),
-  make_cor(df10c, vars_intero, with = "PI_Enticing", component="World Beliefs") |>
-    mutate(var_Correlate = "Enticing"),
-  make_cor(df10c, vars_intero, with = "PI_Good", component="World Beliefs") |>
-    mutate(var_Correlate = "Good"),
-  make_cor(df10c, vars_intero, with = "PI_Hierarchical", component="World Beliefs") |>
-    mutate(var_Correlate = "Hierarchical"),
-  make_cor(df10c, vars_intero, with = "PI_Safe", component="World Beliefs") |>
-    mutate(var_Correlate = "Safe"),
-  make_cor(df10c, vars_intero, with = "PI_Understandable", component="World Beliefs") |>
-    mutate(var_Correlate = "Understandable")
-)
+
+data <- rbind(data, make_rez(with = "PI_Alive", component="World Beliefs", name = "Alive"))
+
+# data <- rbind(
+#   data,
+#   make_cor(df10a, vars_intero, with = "PI_Alive", component="World Beliefs") |>
+#     mutate(var_Correlate = "Alive"),
+#   make_cor(df10a, vars_intero, with = "PI_Changing", component="World Beliefs") |>
+#     mutate(var_Correlate = "Changing"),
+#   make_cor(df10a, vars_intero, with = "PI_Enticing", component="World Beliefs") |>
+#     mutate(var_Correlate = "Enticing"),
+#   make_cor(df10a, vars_intero, with = "PI_Good", component="World Beliefs") |>
+#     mutate(var_Correlate = "Good"),
+#   make_cor(df10a, vars_intero, with = "PI_Hierarchical", component="World Beliefs") |>
+#     mutate(var_Correlate = "Hierarchical"),
+#   make_cor(df10a, vars_intero, with = "PI_Safe", component="World Beliefs") |>
+#     mutate(var_Correlate = "Safe"),
+#   make_cor(df10a, vars_intero, with = "PI_Understandable", component="World Beliefs") |>
+#     mutate(var_Correlate = "Understandable"),
+#   make_cor(df10c, vars_intero, with = "PI_Alive", component="World Beliefs") |>
+#     mutate(var_Correlate = "Alive"),
+#   make_cor(df10c, vars_intero, with = "PI_Changing", component="World Beliefs") |>
+#     mutate(var_Correlate = "Changing"),
+#   make_cor(df10c, vars_intero, with = "PI_Enticing", component="World Beliefs") |>
+#     mutate(var_Correlate = "Enticing"),
+#   make_cor(df10c, vars_intero, with = "PI_Good", component="World Beliefs") |>
+#     mutate(var_Correlate = "Good"),
+#   make_cor(df10c, vars_intero, with = "PI_Hierarchical", component="World Beliefs") |>
+#     mutate(var_Correlate = "Hierarchical"),
+#   make_cor(df10c, vars_intero, with = "PI_Safe", component="World Beliefs") |>
+#     mutate(var_Correlate = "Safe"),
+#   make_cor(df10c, vars_intero, with = "PI_Understandable", component="World Beliefs") |>
+#     mutate(var_Correlate = "Understandable")
+# )
 ```
@@
 
-## Internal Reliability
-
-### BPQ
-
-- sample df7c does not have individual BPQ items
-
-```{r}
-
-# BPQ 46 Items SV
-df2_BPQ <- df2 |> select(contains("BPQ ")) 
-df3_BPQ <- df3 |> select(contains("BPQ"), -contains("BPQ_"))
-
-# BPQ 26 items - awareness subscale
-
-df4_BPQ_A <- df4 |> select(contains("BPQ_"))
-
-# BPQ 12 items VSF
-df7a_BPQVSF <- df7b |> select(contains("BPQ_"), -BPQ_Sum)
-df8a_BPQVSF <- df8a |> select(contains("BPQ"), -BPQ_A)
-
-```
-
 ```{r}
@@
 average_corr <- data |>
-    summarise(mean_r = mean(r, na.rm = TRUE), .by=c("Component", "var_Correlate", "var_Interoception"))
+  summarise(min_r = min(r, na.rm = TRUE), 
+            mean_r = mean(r, na.rm = TRUE),
+            max_r = max(r, na.rm = TRUE), 
+            Max = var_Interoception[which.max(abs(r))],
+            .by=c("Component", "var_Correlate"))
+
+sort(table(average_corr$Max), decreasing = TRUE)
 
 average_corr |> 
-  filter(Component == "Alexithymia") |>
-  group_by(var_Correlate) |>
-  summarise(min = min(mean_r),
-             max = max(mean_r))
-
-average_corr |>
-  filter(Component == "BPQ") |>
-  group_by(var_Correlate) |>
-  summarise(min = min(mean_r),
-             max = max(mean_r))
-
-average_corr |>
-  filter(Component == "MAIA") |>
-  group_by(var_Correlate) |>
-  summarise(min = min(mean_r),
-             max = max(mean_r))
-
-average_corr |>
-  filter(Component == "ICQ") |>
-  group_by(var_Correlate) |>
-  summarise(min = min(mean_r),
-             max = max(mean_r))
-
-average_corr |>
-  filter(Component == "Mood") |>
-  group_by(var_Correlate) |>
-  summarise(min = min(mean_r),
-             max = max(mean_r))
-
-average_corr |>
-  filter(Component == "Maladaptive") |>
-  group_by(var_Correlate) |>
-  summarise(min = min(mean_r),
-             max = max(mean_r))
-
-average_corr |>
-  filter(Component == "Schizotypic") |>
-  group_by(var_Correlate) |>
-  summarise(min = min(mean_r),
-             max = max(mean_r))
-
-average_corr |>
-  filter(Component == "Autistic") |>
-  group_by(var_Correlate) |>
-  summarise(min = min(mean_r),
-             max = max(mean_r))
-
-average_corr |>
-  filter(Component == "Personality") |>
-  group_by(var_Correlate) |>
-  summarise(min = min(mean_r),
-             max = max(mean_r))
-
-average_corr |>
-  filter(Component == "World Beliefs") |>
-  # group_by(var_Correlate) |>
-  summarise(min = min(mean_r),
-             max = max(mean_r))
-
+  gt::gt() |> 
+  gt::data_color(
+    columns = c(mean_r, min_r, max_r),
+    palette = c("#2196F3", "white", "#FF5722"),
+    domain = c(-0.7, 0, 0.7)
+  ) |>
+  gt::data_color(
+    columns = c(Component, Max)
+  ) |> 
+  gt::fmt_auto()
 ```
@@
 p <- data |>
+  filter(Method == "within") |> 
   mutate(sig = ifelse(p < .01, "p < .01", ifelse(p < .001, "p < .001", "N.S.")),
@@
          var_Interoception = str_replace(var_Interoception, "CoughSneeze", "Cough/Sneeze"),
-         var_Interoception = str_replace(var_Interoception, "HeartBreathing", "Heart/Breathing"),
          var_Interoception = str_replace(var_Interoception, "HungryThirsty", "Hungry/Thirsty"),
-         var_Interoception = str_replace(var_Interoception, "ItchBruise", "Itch/Bruise"),
+         var_Interoception = str_replace(var_Interoception, "BruiseBlood", "Bruise/Blood sugar"),
          var_Interoception = str_replace(var_Interoception, "MusclesPain", "Muscles/Pain"),
+         var_Interoception = str_replace(var_Interoception, "BreathingHeart", "Breathing/Heart"),
          var_Interoception = str_replace(var_Interoception, "UrinateDefecate", "Urinate/Defecate"),
          var_Interoception = str_replace(var_Interoception, "WindBurp", "Wind/Burp"),
-         var_Interoception = str_replace(var_Interoception, "Expulsion_Sudden", "Expulsion - Sudden"),
-         var_Interoception = fct_relevel(var_Interoception, "Heart/Breathing", "Muscles/Pain", "Itch/Bruise", "Hungry/Thirsty", "Urinate/Defecate", "Wind/Burp", "Cough/Sneeze")) |>
+         var_Interoception = fct_relevel(var_Interoception, "Original", "Hungry/Thirsty", "Bruise/Blood sugar", "Muscles/Pain", "Cough/Sneeze", "Wind/Burp", "Breathing/Heart", "Urinate/Defecate")) |>
          # Component = fct_relevel(
@@
   geom_hline(yintercept = 0, linetype = "dashed") +
+  geom_point2(aes(y=r, color = dir, alpha = sig), size = 3) +
+  geom_linerange(aes(color = dir, alpha = sig, ymin = CI_low, ymax = CI_high), linewidth = 2) +
   # geom_bar(aes(fill=Sample, alpha=sig, y=r, group=Sample), stat="identity", position = position_dodge2(width = 0.8)) +
-  geom_linerange(aes(color=dir, alpha=sig, ymin=0, ymax=r, group=Sample), position = position_dodge2(width = 0.7), linewidth=2.5) +
-  geom_linerange(aes(ymin = CI_low, ymax = CI_high, color = dir, alpha=sig, group=Sample), position = position_dodge2(width = 0.7)) +
+  # geom_linerange(aes(color=dir, alpha=sig, ymin=0, ymax=r, group=Sample), position = position_dodge2(width = 0.7), linewidth=2.5) +
+  # geom_linerange(aes(ymin = CI_low, ymax = CI_high, color = dir, alpha=sig, group=Sample), position = position_dodge2(width = 0.7),
+  #                linewidth = 1) +
+  facet_grid(Component ~ var_Interoception, scales = "free_y", switch = "y") +
   scale_fill_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
   scale_color_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
-  scale_alpha_discrete(range = c(0.2, 0.7), guide = "none") +
+  scale_alpha_discrete(range = c(0.2, 0.9), guide = "none") +
   scale_y_continuous(expand = c(0, 0), breaks = c(-0.3, 0, 0.3)) +
-  facet_grid(Component ~ var_Interoception, scales = "free_y", switch = "y") +
-  coord_flip(ylim = c(-0.7, 0.7)) +
+  coord_flip(ylim = c(-0.5, 0.5)) +
   theme_modern(axis.title.space = 5) +
+  labs(y = "Strength of Association (std. Beta)") +
   theme(panel.grid.major.y = element_line(),
@@
 p
-ggsave("figures/Figure2.png", p, width=21*0.6, height=29.7*0.45, dpi=200, bg="white")
+ggsave("figures/Figure3.png", p, width=21*0.5, height=29.7*0.5, dpi=300, bg="white")
 ```

### 2025-07-14 analysis/Study1.qmd
added MAIA dimensions

@@
   - https://osf.io/ms354/
+  - MAIA does not include items for not-worrying and not-distracting
 
@@
 df4$MAIA_SelfRegulation <- rowMeans(select(df4, starts_with("MAIA_SR")), na.rm = TRUE)
-# TODO: what is NT?
-# Check if that's all
+df4$MAI_Noticing < rowMeans(select(df4, starts_with("MAIA_NT")), na.rm = TRUE)
 ```
@@
 
-# TODO: Sanitize MAIA names / Compute dimensions.
-
 df10b <- read.csv("https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv") |>
@@
     typeSample = Sample
-  )
-
-# TODO: Sanitize MAIA names / Compute dimensions.
+  ) |>
+  mutate(
+    MAIA_NotDistracting_1_R = 1 - MAIA2_NotDistracting_1_R,
+    MAIA_NotDistracting_2_R = 1 - MAIA2_NotDistracting_2_R,
+    MAIA_NotDistracting_3_R = 1 - MAIA2_NotDistracting_3_R,
+    MAIA_NotDistracting_4_R = 1 - MAIA2_NotDistracting_4_R,
+    MAIA_NotDistracting_5_R = 1 - MAIA2_NotDistracting_5_R,
+    MAIA_NotDistracting_6_R = 1 - MAIA2_NotDistracting_6_R,
+    MAIA_NotWorrying_1_R = 1 - MAIA2_NotWorrying_1_R,
+    MAIA_NotWorrying_2_R = 1 - MAIA2_NotWorrying_2_R,
+    MAIA_NotWorrying_5_R = 1 - MAIA2_NotWorrying_5_R)
+
+# Compute subscales
+
+df10b$MAIA_AttentionRegulation <- rowMeans(select(df10b, starts_with("MAIA2_Attention")))
+df10b$MAIA_EmotionalAwareness <- rowMeans(select(df10b, starts_with("MAIA2_Emotional")))
+df10b$MAIA_Noticing <- rowMeans(select(df10b, starts_with("MAIA2_Noticing")))
+df10b$MAIA_BodyListening <- rowMeans(select(df10b, starts_with("MAIA2_BodyListening")))
+df10b$MAIA_NotDistracting<- rowMeans(select(df10b, starts_with("MAIA2_NotDistracting")))
+df10b$MAIA_NotWorrying<- rowMeans(select(df10b, starts_with("MAIA2_NotWorrying")))
+df10b$MAIA_SelfRegulation<- rowMeans(select(df10b, starts_with("MAIA2_SelfRegulation")))
+df10b$MAIA_Trusting<- rowMeans(select(df10b, starts_with("MAIA2_Trusting")))
 
@@
 
-# TODO: Sanitize MAIA names / Compute dimensions.
-
 df10d <- read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionScale/refs/heads/main/study2/data/rawdata_participants.csv") |>
@@
   ) |> 
-  filter(Participant %in% read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionScale/refs/heads/main/study2/data/data_participants.csv")$Participant)
-
-# TODO: Sanitize MAIA names / Compute dimensions.
+  filter(Participant %in% read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionScale/refs/heads/main/study2/data/data_participants.csv")$Participant) |>
+  mutate(
+    MAIA_NotDistracting_1_R = 1 - MAIA_NotDistracting_1_R,
+    MAIA_NotDistracting_2_R = 1 - MAIA_NotDistracting_2_R,
+    MAIA_NotDistracting_3_R = 1 - MAIA_NotDistracting_3_R,
+    MAIA_NotDistracting_4_R = 1 - MAIA_NotDistracting_4_R,
+    MAIA_NotDistracting_5_R = 1 - MAIA_NotDistracting_5_R,
+    MAIA_NotDistracting_6_R = 1 - MAIA_NotDistracting_6_R,
+    MAIA_NotWorrying_1_R = 1 - MAIA_NotWorrying_1_R,
+    MAIA_NotWorrying_2_R = 1 - MAIA_NotWorrying_2_R,
+    MAIA_NotWorrying_5_R = 1 - MAIA_NotWorrying_5_R)
+
+# Compute subscales
+
+df10b$MAIA_AttentionRegulation <- rowMeans(select(df10b, starts_with("MAIA2_Attention")))
+df10b$MAIA_EmotionalAwareness <- rowMeans(select(df10b, starts_with("MAIA2_Emotional")))
+df10b$MAIA_Noticing <- rowMeans(select(df10b, starts_with("MAIA2_Noticing")))
+df10b$MAIA_BodyListening <- rowMeans(select(df10b, starts_with("MAIA2_BodyListening")))
+df10b$MAIA_NotDistracting<- rowMeans(select(df10b, starts_with("MAIA2_NotDistracting")))
+df10b$MAIA_NotWorrying<- rowMeans(select(df10b, starts_with("MAIA2_NotWorrying")))
+df10b$MAIA_SelfRegulation<- rowMeans(select(df10b, starts_with("MAIA2_SelfRegulation")))
+df10b$MAIA_Trusting<- rowMeans(select(df10b, starts_with("MAIA2_Trusting")))
 
@@
 
-# TODO: sanitize MAIA names / Compute dimensions.
-
 df11b <- haven::read_sav("../data/Giulia/Sleep and Exteroceptive Interoceptive Sensitivity.sav") |> # 165 participants
@@
   na.omit()
-
-# TODO: sanitize MAIA names / Compute dimensions.
 
@@
   N = c('', nrow(df1a), nrow(df1b), nrow(df2), nrow(df3), nrow(df4), nrow(df5_attention), nrow(df6),'', nrow(df7a), nrow(df7b), 802,'', nrow(df8a), nrow(df8b), nrow(df9), nrow(df10a), nrow(df10b), nrow(df10c), nrow(df11a), nrow(df11b), 32214),
-  'Difference' = c('','', '', '', '', '', '', '', '', '', '', '', '', 'Collapsed "Itch" and "Tickling"', 'Collapsed "Itch" and "Tickling"', '', 'Analog scales', 'Analog scales', 'Analog scales', '', '', ''),
+  'Difference' = c('','', '', '', '', '', '', '', '', '', '', '', '', 'Collapsed "Itch" and "Tickling"', 'Collapsed "Itch" and "Tickling"', '', 'Analog scales.
+Does not include temperature, blood sugar and cough items.', 'Analog scales', 'Analog scales', '', '', ''),
   Age = c('', make_age(df1a$Age), make_age(df1b$Age), make_age(df2$Age), make_age(df3$Age), "48.6.6 ± 14.1*", make_age(df5_attention$Age), make_age(df6$Age),'', make_age(df7a$Age), make_age(df7b$Age), make_age(df7c$Age),'', make_age(df8a$Age), make_age(df8b$Age), make_age(df9$Age), make_age(df10a$Age), make_age(df10b$Age), make_age(df10c$Age), make_age(df11a$Age), make_age(df11b$Age), '48.6 ± 13.1'),
@@
   cols_label(Age = "Age (Mean  ± SD)", Female_Percentage = "Female %") |> 
-  tab_footnote("* Information taken from the sample description of relevant paper rather than recomputed.")
+  tab_footnote("Note.*Information taken from the sample description of relevant paper rather than recomputed.")
 

### 2025-07-14 analysis/figures/table1.tex
added MAIA dimensions

@@
-\begin{table}
+\begin{table}[!t]
 \fontsize{6.8pt}{8.1pt}\selectfont
@@
 \begin{minipage}{\linewidth}
-* Information taken from the sample description of relevant paper rather than recomputed.\\
+Note.*Information taken from the sample description of relevant paper rather than recomputed. Sample 10 does not include IAS items about temperature, blood sugar and cough.\\
 \end{minipage}

### 2025-07-14 analysis/study2.qmd
added new function

@@
 
-# data <- rbind(
-#   data,
-#   make_rez(with = "MAIA_AttentionReg", component = "MAIA", name = "Attention Regulation"),
-#   make_rez(with = "MAIA_BodyListening", component = "MAIA", name = "Listening"),
-#   make_rez(with = "MAIA_BodyTrusting", component = "MAIA", name = "Trusting"),
-#   make_rez(with = "MAIA_EmoAwareness", component = "MAIA", name = "Emotional Awareness"),
-#   make_rez(with = "MAIA_NotDistracting", component = "MAIA", name = "Not Distracting"),
-#   make_rez(with = "MAIA_Noticing", component = "MAIA", name = "Noticing"),
-#   make_rez(with = "MAIA_NotWorrying", component = "MAIA", name = "Not Worrying"),
-#   make_rez(with = "MAIA_SelfReg", component = "MAIA", name = "Self Regulation"),
-#   make_rez(with = "MAIA_Trusting", component = "MAIA", name = "Trusting")
-# )
+data <- rbind(
+  data,
+  make_rez(with = "MAIA_AttentionReg", component = "MAIA", name = "Attention Regulation"),
+  make_rez(with = "MAIA_BodyListening", component = "MAIA", name = "Listening"),
+  make_rez(with = "MAIA_BodyTrusting", component = "MAIA", name = "Trusting"),
+  make_rez(with = "MAIA_EmoAwareness", component = "MAIA", name = "Emotional Awareness"),
+  make_rez(with = "MAIA_NotDistracting", component = "MAIA", name = "Not Distracting"),
+  make_rez(with = "MAIA_Noticing", component = "MAIA", name = "Noticing"),
+  make_rez(with = "MAIA_NotWorrying", component = "MAIA", name = "Not Worrying"),
+  make_rez(with = "MAIA_SelfReg", component = "MAIA", name = "Self Regulation"),
+  make_rez(with = "MAIA_Trusting", component = "MAIA", name = "Trusting")
+)
 
@@
   data,
-  make_cor(df2, vars_intero, with = "BPQ_A", component="BPQ") |>
-    mutate(var_Correlate = "Body Awareness (BPQ)"),
-  make_cor(df2, vars_intero, with = "BPQ_R", component="BPQ") |>
-    mutate(var_Correlate = "Autonomic Reactivity (BPQ)"),
-  make_cor(df3, vars_intero, with = "BPQ_BodyAwareness", component="BPQ") |>
-    mutate(var_Correlate = "Body Awareness (BPQ)"),
-  make_cor(df3, vars_intero, with = "BPQ_AutonomicReactivity", component="BPQ") |>
-    mutate(var_Correlate = "Autonomic Reactivity (BPQ)")
+  make_rez(with = "BPQ_A", component="BPQ", name = "Body Awareness (BPQ)"),
+  make_rez(with = "BPQ_R", component="BPQ", name = "Autonomic Reactivity (BPQ)"),
+  make_rez(with = "BPQ_BodyAwareness", component="BPQ", name = "Body Awareness (BPQ)"),
+  make_rez(with = "BPQ_AutonomicReactivity", component="BPQ", name = "Autonomic Reactivity (BPQ)")
   )
@@
   data,
-
   #df2 
-  make_cor(df2, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
-    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
-  make_cor(df2, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
-    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
-  make_cor(df2, vars_intero, with = "TAS_EOT", component="Alexithymia") |>
-    mutate(var_Correlate = "External Thinking (TAS)"),
+  make_rez(with = "TAS_DIF", component="Alexithymia", name = "Difficulties Identifying Feelings (TAS)"),
+  make_rez(with = "TAS_DDF", component="Alexithymia", name = "Difficulties Describing Feelings (TAS)"),
+  make_rez(with = "TAS_EOT", component="Alexithymia", name = "External Thinking (TAS)"),
 
   #df3
-  make_cor(df3, vars_intero, with = "TAS_DescribingFeelings", component="Alexithymia") |>
-    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
-  make_cor(df3, vars_intero, with = "TAS_IdentifyingFeelings", component="Alexithymia") |> 
-    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
-  make_cor(df3, vars_intero, with = "TAS_ExternallyOrientedThinking", component="Alexithymia") |>
-    mutate(var_Correlate = "External Thinking (TAS)"),
-  make_cor(df7c, vars_intero, with = "TAS_des", component="Alexithymia") |>
-    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
-  make_cor(df7c, vars_intero, with = "TAS_ident", component="Alexithymia") |>
-    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
-  make_cor(df7c, vars_intero, with = "TAS_ext", component="Alexithymia") |>
-    mutate(var_Correlate = "External Thinking (TAS)"),
-  make_cor(df8b, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
-    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
-  make_cor(df8b, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
-    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
-  make_cor(df11a, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
-    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
-  make_cor(df11a, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
-    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
-  make_cor(df11a, vars_intero, with = "TAS_EOT", component="Alexithymia") |>
-    mutate(var_Correlate = "External Thinking (TAS)"),
-  # BVAQ
-  make_cor(df2, vars_intero, with = "BVAQ_Affective", component="Alexithymia") |>
-    mutate(var_Correlate = "Affective (BVAQ)"),
-  make_cor(df2, vars_intero, with = "BVAQ_Cognitive", component="Alexithymia") |>
-    mutate(var_Correlate = "Cognitive (BVAQ)")
+  make_rez(with = "TAS_DescribingFeelings", component="Alexithymia", name = "Difficulties Describing Feelings (TAS)"),
+  make_rez(with = "TAS_IdentifyingFeelings", component="Alexithymia", name ="Difficulties Identifying Feelings (TAS)"), 
+  make_rez(with = "TAS_ExternallyOrientedThinking", component="Alexithymia", name = "External Thinking (TAS)"), 
+  make_rez(with = "TAS_des", component="Alexithymia", name = "Difficulties Describing Feelings (TAS)"), 
+  make_rez(with = "TAS_ident", component="Alexithymia", name = "Difficulties Identifying Feelings (TAS)"), 
+  make_rez(with = "TAS_ext", component="Alexithymia", name = "External Thinking (TAS)"), 
+  make_rez(with = "TAS_DIF", component="Alexithymia", name = "Difficulties Identifying Feelings (TAS)"), 
+  make_rez(with = "BVAQ_Affective", component="Alexithymia", name = "Affective (BVAQ)"), 
+  make_rez(df2, vars_intero, with = "BVAQ_Cognitive", component="Alexithymia", name = "Cognitive (BVAQ)")
 )
@@
   data,
-  make_cor(df6, vars_intero, with = "PHQ2_sum", component="Mood") |>
-    mutate(var_Correlate = "Depression (PHQ-2)"),
-  make_cor(df7b, vars_intero, with = "PHQ15_Sum", component="Mood") |>
-    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
-  make_cor(df7b, vars_intero, with = "PHQ9_Sum", component="Mood")|>
-    mutate(var_Correlate = "Depression (PHQ-9)"),
-  make_cor(df7c, vars_intero, with = "BDI_sum", component="Mood") |>
-    mutate(var_Correlate = "Depression (BDI)"),
-  make_cor(df8b, vars_intero, with = "PHQ15_sum", component="Mood") |>
-    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
-  make_cor(df8b, vars_intero, with = "PHQ9_sum", component="Mood") |>
-    mutate(var_Correlate = "Depression (PHQ-9)"),
-  make_cor(df10a, vars_intero, with = "PHQ4_Depression", component="Mood") |>
-    mutate(var_Correlate = "Depression (PHQ-2)"),
-  make_cor(df10b, vars_intero, with = "BDI2_Total", component="Mood") |>
-    mutate(var_Correlate = "Depression (BDI)"),
-  make_cor(df11a, vars_intero, with = "DEP", component = "Mood") |>
-    mutate(var_Correlate = "Depression (MFQ)")
+  make_rez(with = "PHQ2_sum", component="Mood", name = "Depression (PHQ-2)"),
+  make_rez(with = "PHQ15_Sum", component="Mood", name = "Somatic Concerns (PHQ-15)"), 
+  make_rez(with = "PHQ9_Sum", component="Mood", name = "Depression (PHQ-9)"), 
+  make_rez(with = "BDI_sum", component="Mood", name = "Depression (BDI)"), 
+  make_rez(with = "PHQ15_sum", component="Mood", name = "Somatic Concerns (PHQ-15)"), 
+  make_rez(with = "PHQ9_sum", component="Mood", name = "Depression (PHQ-9)"), 
+  make_rez(with = "PHQ4_Depression", component="Mood", name = "Depression (PHQ-2)"),
+  make_rez(with = "BDI2_Total", component="Mood", name = "Depression (BDI)"),
+  make_cor(with = "DEP", component = "Mood", name = "Depression (MFQ)")
 )
@@
   data,
-  make_cor(df6, vars_intero, with = "GAD2_sum", component="Mood") |>
-    mutate(var_Correlate = "Anxiety (GAD-2)"),
-  make_cor(df7a, vars_intero, with = "STAI_T_Sumscore", component="Mood") |>
-    mutate(var_Correlate = "Anxiety (STAI-T)"),
-  make_cor(df7b, vars_intero, with = "STAIT_Sum", component="Mood") |>
-    mutate(var_Correlate = "Anxiety (STAI-T)"),
-  make_cor(df7c, vars_intero, with = "STAIT_sum", component="Mood") |>
-    mutate(var_Correlate = "Anxiety (STAI-T)"),
-  make_cor(df10a, vars_intero, with = "PHQ4_Anxiety", component="Mood") |>
-    mutate(var_Correlate = "Anxiety (GAD-2)"),
-  make_cor(df10b, vars_intero, with = "PHQ4_Anxiety", component="Mood") |>
-    mutate(var_Correlate = "Anxiety (STAI-5)"),
-  make_cor(df10b, vars_intero, with = "STAI5_General", component="Mood") |>
-    mutate(var_Correlate = "Anxiety (STAI-T)"),
-  make_cor(df11a, vars_intero, with =  "ANX", component = "Mood") |>
-    mutate(var_Correlate = "Anxiety (STAI-T)")
+  make_rez(with = "GAD2_sum", component="Mood", name = "Anxiety (GAD-2)"), 
+  make_rez(with = "STAI_T_Sumscore", component="Mood", name= "Anxiety (STAI-T)"), 
+  make_rez(with = "STAIT_Sum", component="Mood", name = "Anxiety (STAI-T)"), 
+  make_rez(with = "STAIT_sum", component="Mood", name = "Anxiety (STAI-T)"),
+  make_rez(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (GAD-2)"),
+  make_rez(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (STAI-5)"), 
+  make_rez(with = "STAI5_General", component="Mood", name = "Anxiety (STAI-T)"),
+  make_rez(with =  "ANX", component = "Mood", name = "Anxiety (STAI-T)")
 )
@@
   data,
-  make_cor(df10a, vars_intero, with = "BPD", component="Mood") |>
-    mutate(var_Correlate = "Boderline Personality")
+  make_rez(with = "BPD", component="Mood", name = "Boderline Personality")
 )
@@
   data,
-  make_cor(df10a, vars_intero, with = "PID5_Antagonism", component="Maladaptive") |>
-    mutate(var_Correlate = "Antagonism"),
-  make_cor(df10a, vars_intero, with = "PID5_Detachment", component="Maladaptive") |>
-    mutate(var_Correlate = "Detachment"),
-  make_cor(df10a, vars_intero, with = "PID5_Disinhibition", component="Maladaptive") |>
-    mutate(var_Correlate = "Disinhibition"),
-  make_cor(df10a, vars_intero, with = "PID5_NegativeAffect", component="Maladaptive") |>
-    mutate(var_Correlate = "Negative Affect"),
-  make_cor(df10a, vars_intero, with = "PID5_Psychoticism", component="Maladaptive") |>
-    mutate(var_Correlate = "Psychoticism")
+  make_rez(with = "PID5_Antagonism", component="Maladaptive", name = "Antagonism"),
+  make_rez(with = "PID5_Detachment", component="Maladaptive", name = "Detachment"), 
+  make_rez(with = "PID5_Disinhibition", component="Maladaptive", name = "Disinhibition"),
+  make_rez(with = "PID5_NegativeAffect", component="Maladaptive", name = "Negative Affect"),
+  make_rez(with = "PID5_Psychoticism", component="Maladaptive", name = "Psychoticism")
 )
@@
   data,
-  make_cor(df10a, vars_intero, with = "SPQ_ConstrictedAffect", component="Schizotypic") |>
-    mutate(var_Correlate = "Constricted Affect"),
-  make_cor(df10a, vars_intero, with = "SPQ_Eccentric", component="Schizotypic") |>
-    mutate(var_Correlate = "Eccentric"),
-  make_cor(df10a, vars_intero, with = "SPQ_MagicalThinking", component="Schizotypic") |>
-    mutate(var_Correlate = "Magical Thinking"),
-  make_cor(df10a, vars_intero, with = "SPQ_NoCloseFriends", component="Schizotypic") |>
-    mutate(var_Correlate = "No Close Friends"),
-  make_cor(df10a, vars_intero, with = "SPQ_OddSpeech", component="Schizotypic") |>
-    mutate(var_Correlate = "Odd Speech"),
-  make_cor(df10a, vars_intero, with = "SPQ_Reference", component="Schizotypic") |>
-    mutate(var_Correlate = "Reference"),
-  make_cor(df10a, vars_intero, with = "SPQ_SocialAnxiety", component="Schizotypic") |>
-    mutate(var_Correlate = "Social Anxiety"),
-  make_cor(df10a, vars_intero, with = "SPQ_Suspiciousness", component="Schizotypic") |>
-    mutate(var_Correlate = "Suspiciousness"),
-  make_cor(df10a, vars_intero, with = "SPQ_UnusualPerceptions", component="Schizotypic") |>
-    mutate(var_Correlate = "Unusual Perceptions")
+  make_rez(with = "SPQ_ConstrictedAffect", component="Schizotypic", name = "Constricted Affect"),
+  make_rez(with = "SPQ_Eccentric", component="Schizotypic", name = "Eccentric"),
+  make_rez(with = "SPQ_MagicalThinking", component="Schizotypic", name = "Magical Thinking"),
+  make_rez(with = "SPQ_NoCloseFriends", component="Schizotypic", name = "No Close Friends"),
+  make_rez(with = "SPQ_OddSpeech", component="Schizotypic", name = "Odd Speech"),
+  make_rez(with = "SPQ_Reference", component="Schizotypic", name = "Reference"),
+  make_rez(with = "SPQ_SocialAnxiety", component="Schizotypic", name = "Social Anxiety"),
+  make_rez(with = "SPQ_Suspiciousness", component="Schizotypic", name = "Suspiciousness"),
+  make_rez(with = "SPQ_UnusualPerceptions", component="Schizotypic", name = "Unusual Perceptions")
 )
@@
   data,
-  make_cor(df10a, vars_intero, with = "ASQ_Imagination", component="Autistic") |>
-    mutate(var_Correlate = "Imagination"),
-  make_cor(df10a, vars_intero, with = "ASQ_LackSocialSkills", component="Autistic") |>
-    mutate(var_Correlate = "Lack of Social Skills"),
-  make_cor(df10a, vars_intero, with = "ASQ_LowAttentionalSwitching", component="Autistic") |>
-    mutate(var_Correlate = "Low Attentional Switching"),
-  make_cor(df10a, vars_intero, with = "ASQ_Patterns", component="Autistic") |>
-    mutate(var_Correlate = "Patterns and Numbers"),
-  make_cor(df10a, vars_intero, with = "ASQ_Routine", component="Autistic") |>
-    mutate(var_Correlate = "Routines")
+  make_rez(with = "ASQ_Imagination", component="Autistic", name = "Imagination"),
+  make_rez(with = "ASQ_LackSocialSkills", component="Autistic", name = "Lack of Social Skills"), 
+  make_rez(with = "ASQ_LowAttentionalSwitching", component="Autistic", name = "Low Attentional Switching"),
+  make_rez(with = "ASQ_Patterns", component="Autistic", name = "Patterns and Numbers"),
+  make_rez(with = "ASQ_Routine", component="Autistic", name = "Routines")
 )
@@
   data,
-  make_cor(df7a, vars_intero, with = "NEO_FFI_SUMSCORE", component = "Personality") |>
-      mutate(var_Correlate = "Neuroticism"),
-  make_cor(df9, vars_intero, with = "BFI_AGREEABLENESS", component="Personality") |>
-    mutate(var_Correlate = "Agreeableness"),
-  make_cor(df9, vars_intero, with = "BFI_CONSCIENTIOUSNESS", component="Personality") |>
-    mutate(var_Correlate = "Conscientiousness"),
-  make_cor(df9, vars_intero, with = "BFI_NEUROTICISM", component="Personality") |>
-    mutate(var_Correlate = "Neuroticism"),
-  make_cor(df9, vars_intero, with = "BFI_OPENNESS", component="Personality") |>
-    mutate(var_Correlate = "Openness"),
-  make_cor(df9, vars_intero, with = "BFI_EXTROVERSION", component="Personality") |>
-    mutate(var_Correlate = "Extraversion"),
-  make_cor(df10a, vars_intero, with = "IPIP6_Agreeableness", component="Personality") |>
-    mutate(var_Correlate = "Agreeableness"),
-  make_cor(df10a, vars_intero, with = "IPIP6_Conscientiousness", component="Personality") |>
-    mutate(var_Correlate = "Conscientiousness"),
-  make_cor(df10a, vars_intero, with = "IPIP6_Neuroticism", component="Personality") |>
-    mutate(var_Correlate = "Neuroticism"),
-  make_cor(df10a, vars_intero, with = "IPIP6_Openness", component="Personality") |>
-    mutate(var_Correlate = "Openness"),
-  make_cor(df10a, vars_intero, with = "IPIP6_Extraversion", component="Personality") |>
-    mutate(var_Correlate = "Extraversion"),
-  make_cor(df10a, vars_intero, with = "IPIP6_HonestyHumility", component="Personality") |>
-    mutate(var_Correlate = "Honesty-Humility")
+  make_rez(with = "NEO_FFI_SUMSCORE", component = "Personality", name = "Neuroticism"),
+  make_rez(with = "BFI_AGREEABLENESS", component="Personality", name = "Agreeableness"),
+  make_rez(with = "BFI_CONSCIENTIOUSNESS", component="Personality", name = "Conscientiousness"), 
+  make_rez(with = "BFI_NEUROTICISM", component="Personality", name = "Neuroticism"),
+  make_rez(with = "BFI_OPENNESS", component="Personality", name = "Openness"),
+  make_rez(with = "BFI_EXTROVERSION", component="Personality", name = "Extraversion"),
+  make_rez(with = "IPIP6_Agreeableness", component="Personality", name = "Agreeableness"),
+  make_rez(with = "IPIP6_Conscientiousness", component="Personality", name = "Conscientiousness"), 
+  make_rez(with = "IPIP6_Neuroticism", component="Personality", name = "Neuroticism"),
+  make_rez(with = "IPIP6_Openness", component="Personality", name = "Openness"),
+  make_rez(with = "IPIP6_Extraversion", component="Personality", name = "Extraversion"), 
+  make_rez(with = "IPIP6_HonestyHumility", component="Personality", name = "Honesty-Humility")
 )
@@
 #   data,
-#   make_cor(df10a, vars_intero, with = "PI_Alive", component="World Beliefs") |>
-#     mutate(var_Correlate = "Alive"),
-#   make_cor(df10a, vars_intero, with = "PI_Changing", component="World Beliefs") |>
-#     mutate(var_Correlate = "Changing"),
-#   make_cor(df10a, vars_intero, with = "PI_Enticing", component="World Beliefs") |>
-#     mutate(var_Correlate = "Enticing"),
-#   make_cor(df10a, vars_intero, with = "PI_Good", component="World Beliefs") |>
-#     mutate(var_Correlate = "Good"),
-#   make_cor(df10a, vars_intero, with = "PI_Hierarchical", component="World Beliefs") |>
-#     mutate(var_Correlate = "Hierarchical"),
-#   make_cor(df10a, vars_intero, with = "PI_Safe", component="World Beliefs") |>
-#     mutate(var_Correlate = "Safe"),
-#   make_cor(df10a, vars_intero, with = "PI_Understandable", component="World Beliefs") |>
-#     mutate(var_Correlate = "Understandable"),
-#   make_cor(df10c, vars_intero, with = "PI_Alive", component="World Beliefs") |>
-#     mutate(var_Correlate = "Alive"),
-#   make_cor(df10c, vars_intero, with = "PI_Changing", component="World Beliefs") |>
-#     mutate(var_Correlate = "Changing"),
-#   make_cor(df10c, vars_intero, with = "PI_Enticing", component="World Beliefs") |>
-#     mutate(var_Correlate = "Enticing"),
-#   make_cor(df10c, vars_intero, with = "PI_Good", component="World Beliefs") |>
-#     mutate(var_Correlate = "Good"),
-#   make_cor(df10c, vars_intero, with = "PI_Hierarchical", component="World Beliefs") |>
-#     mutate(var_Correlate = "Hierarchical"),
-#   make_cor(df10c, vars_intero, with = "PI_Safe", component="World Beliefs") |>
-#     mutate(var_Correlate = "Safe"),
-#   make_cor(df10c, vars_intero, with = "PI_Understandable", component="World Beliefs") |>
-#     mutate(var_Correlate = "Understandable")
+#   make_rez(with = "PI_Alive", component="World Beliefs", name = "Alive"),
+#   make_rez(with = "PI_Changing", component="World Beliefs", name = "Changing"),
+#   make_rez(with = "PI_Enticing", component="World Beliefs", name = "Enticing"),
+#   make_rez(with = "PI_Good", component="World Beliefs", name = "Good"),
+#   make_rez(with = "PI_Hierarchical", component="World Beliefs", name = "Hierarchical"),
+#   make_rez(with = "PI_Safe", component="World Beliefs", name = "Safe"),
+#   make_rez(with = "PI_Understandable", component="World Beliefs", name = "Understandable"),
+#   make_rez(with = "PI_Alive", component="World Beliefs", name= "Alive"),
+#   make_rez(with = "PI_Changing", component="World Beliefs", name = "Changing"),
+#   make_rez(with = "PI_Enticing", component="World Beliefs", name = "Enticing"),
+#   make_rez(with = "PI_Good", component="World Beliefs", name = "Good"),
+#   make_rez(with = "PI_Hierarchical", component="World Beliefs", name = "Hierarchical"),
+#   make_rez(with = "PI_Safe", component="World Beliefs", name = "Safe"),
+#   make_rez(with = "PI_Understandable", component="World Beliefs", name = "Understandable")
 # )
@@
   data,
-  make_cor(df10a, vars_intero, with = "GCBS_Extraterrestrial", component="Conspiracy Beliefs") |>
-    mutate(var_Correlate = "Extraterrestrial"),
-  make_cor(df10a, vars_intero, with = "GCBS_GlobalConspiracies", component="Conspiracy Beliefs") |>
-    mutate(var_Correlate = "Global Conspiracies"),
-  make_cor(df10a, vars_intero, with = "GCBS_GovernmentMalfeasance", component="Conspiracy Beliefs") |>
-    mutate(var_Correlate = "Government Malfeasance"),
-  make_cor(df10a, vars_intero, with = "GCBS_InformationControl", component="Conspiracy Beliefs") |>
-    mutate(var_Correlate = "Information Control"),
-  make_cor(df10a, vars_intero, with = "GCBS_PersonalWellbeing", component="Conspiracy Beliefs") |>
-    mutate(var_Correlate = "Personal Wellbeing")
+  make_rez(with = "GCBS_Extraterrestrial", component="Conspiracy Beliefs", name = "Extraterrestrial"),
+  make_rez(with = "GCBS_GlobalConspiracies", component="Conspiracy Beliefs", name = "Global Conspiracies"),
+  make_rez(with = "GCBS_GovernmentMalfeasance", component="Conspiracy Beliefs", name  = "Government Malfeasance"),
+  make_rez(with = "GCBS_InformationControl", component="Conspiracy Beliefs", name = "Information Control"),
+  make_rez(with = "GCBS_PersonalWellbeing", component="Conspiracy Beliefs", name = "Personal Wellbeing")
 )
@@
   data,
-  make_cor(df10a, vars_intero, with = "LIE_Ability", component="Lying Profile") |>
-    mutate(var_Correlate = "Ability"),
-  make_cor(df10a, vars_intero, with = "LIE_Frequency", component="Lying Profile") |>
-    mutate(var_Correlate = "Frequency"),
-  make_cor(df10a, vars_intero, with = "LIE_Contextuality", component="Lying Profile") |>
-    mutate(var_Correlate = "Contextuality"),
-  make_cor(df10a, vars_intero, with = "LIE_Negativity", component="Lying Profile") |>
-    mutate(var_Correlate = "Negativity")
+  make_rez(with = "LIE_Ability", component="Lying Profile", name = "Ability"),
+  make_rez(with = "LIE_Frequency", component="Lying Profile", name = "Frequency"),
+  make_rez(with = "LIE_Contextuality", component="Lying Profile", name = "Contextuality"),
+  make_rez(with = "LIE_Negativity", component="Lying Profile", name = "Negativity")
 )

### 2025-07-17 analysis/Study1.qmd
updated scripts

--- 2025-07-06 analysis/Study1.qmd
@@
     MAIA_Trusting = MAIA_BodyTrusting, MAIA_EmotionalAwareness = MAIA_EmoAwareness,
-    MAIA_NonDistracting=MAIA_NotDistracting, MAIA_NotWorrying=MAIA_NotWorrying,
+    MAIA_NotDistracting=MAIA_NotDistracting, MAIA_NotWorrying=MAIA_NotWorrying,
     MAIA_SelfRegulation=MAIA_SelfReg, MAIA_Noticing=MAIA_Noticing)
@@
   )
-df4$MAIA_AttentionRegulation <- rowMeans(select(df4, starts_with("MAIA_AR")), na.rm = TRUE)
+
+df4$MAIA_AttentionReg <- rowMeans(select(df4, starts_with("MAIA_AR")), na.rm = TRUE)
 df4$MAIA_BodyListening <- rowMeans(select(df4, starts_with("MAIA_BL")), na.rm = TRUE)
-df4$MAIA_Trusting <- rowMeans(select(df4, starts_with("MAIA_TR")), na.rm = TRUE)
-df4$MAIA_EmotionalAwareness <- rowMeans(select(df4, starts_with("MAIA_EA")), na.rm = TRUE)
-df4$MAIA_SelfRegulation <- rowMeans(select(df4, starts_with("MAIA_SR")), na.rm = TRUE)
-# TODO: what is NT?
-# Check if that's all
+df4$MAIA_BodyTrusting <- rowMeans(select(df4, starts_with("MAIA_TR")), na.rm = TRUE)
+df4$MAIA_EmoAwareness <- rowMeans(select(df4, starts_with("MAIA_EA")), na.rm = TRUE)
+df4$MAIA_SelfReg<- rowMeans(select(df4, starts_with("MAIA_SR")), na.rm = TRUE)
+df4$MAIA_Noticing <- rowMeans(select(df4, starts_with("MAIA_NT")), na.rm = TRUE)
 ```
@@
     Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
-    MAIA_Noticing = MAIA_NOTICING, MAIA_NonDistracting = MAIA_NON_DISTRACTING,
-    MAIA_NotWorrying = MAIA_NOT_WORRYING, MAIA_AttentionRegulation = mAIA_ATTENTION_REGULATION,
-    MAIA_SelfRegulation = MAIA_SELF_REGULATION, MAIA_BodyListening = MAIA_BODY_LISTENING,
-    MAIA_Trusting = MAIA_TRUSTING, MAIA_EmotionalAwareness = MAIA_EMOTIONAL_AWARENESS
+    MAIA_Noticing = MAIA_NOTICING, MAIA_NotDistracting = MAIA_NON_DISTRACTING,
+    MAIA_NotWorrying = MAIA_NOT_WORRYING, MAIA_AttentionReg = mAIA_ATTENTION_REGULATION,
+    MAIA_SelfReg = MAIA_SELF_REGULATION, MAIA_BodyListening = MAIA_BODY_LISTENING,
+    MAIA_Trusting = MAIA_TRUSTING, MAIA_EmoAwareness = MAIA_EMOTIONAL_AWARENESS
   )
@@
     Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
-    MAIA_Noticing = maiaNotice, MAIA_NonDistracting = maiaNonDistracting,
-    MAIA_NotWorrying = maiaNotWorrying, MAIA_AttentionRegulation = maiaAttentionRegulation,
-    MAIA_SelfRegulation = maiaSelfRegulation, MAIA_BodyListening = maiaBodyListening,
-    MAIA_Trusting = maiaTrusting, MAIA_EmotionalAwareness = maiaEmotionalAwareness
+    MAIA_Noticing = maiaNotice, MAIA_NotDistracting = maiaNonDistracting,
+    MAIA_NotWorrying = maiaNotWorrying, MAIA_AttentionReg = maiaAttentionRegulation,
+    MAIA_SelfReg = maiaSelfRegulation, MAIA_BodyListening = maiaBodyListening,
+    MAIA_Trusting = maiaTrusting, MAIA_EmoAwareness = maiaEmotionalAwareness
   )
@@
     Affective_touch = IA02_19, Tickle = IA02_20, Itch = IA02_21,
-    MAIA_Noticing = MAIA_noticing, MAIA_NonDistracting = MAIA_notdis, 
-    MAIA_NotWorrying = MAIA_notwor, MAIA_AttentionRegulation = MAIA_attreg,
-    MAIA_SelfRegulation = MAIA_selfreg, MAIA_BodyListening = MAIA_bodlis,
-    MAIA_Trusting = MAIA_trust, MAIA_EmotionalAwareness = MAIA_emoaw,
+    MAIA_Noticing = MAIA_noticing, MAIA_NotDistracting = MAIA_notdis, 
+    MAIA_NotWorrying = MAIA_notwor, MAIA_AttentionReg = MAIA_attreg,
+    MAIA_SelfReg = MAIA_selfreg, MAIA_BodyListening = MAIA_bodlis,
+    MAIA_Trusting = MAIA_trust, MAIA_EmoAwareness = MAIA_emoaw,
     ICQ = ICQ_sum
@@
   - Note: Analog scales
-  - note df10c = primals data
-
-```{r}
-df10a <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |>
+  - note df12  = primals data
+
+```{r}
+df10 <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |>
   rename(
@@
     Pain = Item_IAS_Nociception_3, Affective_touch = Item_IAS_Skin_1,
-    Tickle = Item_IAS_Skin_2, Itch = Item_IAS_Skin_3
+    Tickle = Item_IAS_Skin_2, Itch = Item_IAS_Skin_3,
+    MAIA_EmoAwareness = MAIA_EmotionalAwareness, MAIA_AttentionReg = MAIA_AttentionRegulation,
+    MAIA_SelfReg = MAIA_SelfRegulation
   ) |>
@@
 
-# TODO: Sanitize MAIA names / Compute dimensions.
-
-df10b <- read.csv("https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv") |>
+```
+
+### Sample 11
+
+```{r}
+df11  <- read.csv("https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv") |>
   rename(
@@
     typeSample = Sample
-  )
-
-# TODO: Sanitize MAIA names / Compute dimensions.
-
-df10c <- read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionPrimals/refs/heads/main/data/data_participants.csv") |>
+  ) |>
+  mutate(
+    MAIA_NotDistracting_1_R = 1 - MAIA2_NotDistracting_1_R,
+    MAIA_NotDistracting_2_R = 1 - MAIA2_NotDistracting_2_R,
+    MAIA_NotDistracting_3_R = 1 - MAIA2_NotDistracting_3_R,
+    MAIA_NotDistracting_4_R = 1 - MAIA2_NotDistracting_4_R,
+    MAIA_NotDistracting_5_R = 1 - MAIA2_NotDistracting_5_R,
+    MAIA_NotDistracting_6_R = 1 - MAIA2_NotDistracting_6_R,
+    MAIA_NotWorrying_1_R = 1 - MAIA2_NotWorrying_1_R,
+    MAIA_NotWorrying_2_R = 1 - MAIA2_NotWorrying_2_R,
+    MAIA_NotWorrying_5_R = 1 - MAIA2_NotWorrying_5_R)
+
+# Compute subscales
+
+df11 $MAIA_AttentionReg <- rowMeans(select(df11 , starts_with("MAIA2_Attention")))
+df11 $MAIA_EmoAwareness <- rowMeans(select(df11 , starts_with("MAIA2_Emotional")))
+df11 $MAIA_Noticing <- rowMeans(select(df11 , starts_with("MAIA2_Noticing")))
+df11 $MAIA_BodyListening <- rowMeans(select(df11 , starts_with("MAIA2_BodyListening")))
+df11 $MAIA_NotDistracting<- rowMeans(select(df11 , starts_with("MAIA2_NotDistracting")))
+df11 $MAIA_NotWorrying<- rowMeans(select(df11 , starts_with("MAIA2_NotWorrying")))
+df11 $MAIA_SelfReg<- rowMeans(select(df11 , starts_with("MAIA2_SelfRegulation")))
+df11 $MAIA_Trusting<- rowMeans(select(df11 , starts_with("MAIA2_Trusting")))
+
+```
+
+### Sample 12
+
+```{r}
+df12  <- read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionPrimals/refs/heads/main/data/data_participants.csv") |>
   select("Participant" = "participant_id", "Gender", "Age", "Ethnicity", starts_with(c("IAS","MAIA","PI"))) |>
@@
     Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
-    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
+    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
+    MAIA_EmoAwareness = MAIA_EmotionalAwareness, MAIA_AttentionReg = MAIA_AttentionRegulation,
+    MAIA_SelfReg = MAIA_SelfRegulation
   ) |>
   filter(!is.na(Heart)) # participant is outlier and had total IAS scores below 0.4 
-
-# TODO: Sanitize MAIA names / Compute dimensions.
-
-df10d <- read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionScale/refs/heads/main/study2/data/rawdata_participants.csv") |>
+```
+
+### Sample 13
+
+```{r}
+
+df13  <- read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionScale/refs/heads/main/study2/data/rawdata_participants.csv") |>
   select("Participant", "Gender", "Age", "Ethnicity", starts_with(c("IAS","MAIA","PI", "PHQ4"))) |>
@@
   ) |> 
-  filter(Participant %in% read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionScale/refs/heads/main/study2/data/data_participants.csv")$Participant)
-
-# TODO: Sanitize MAIA names / Compute dimensions.
+  filter(Participant %in% read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionScale/refs/heads/main/study2/data/data_participants.csv")$Participant) |>
+  mutate(
+    MAIA_NotDistracting_1_R = 1 - MAIA_NotDistracting_1_R,
+    MAIA_NotDistracting_2_R = 1 - MAIA_NotDistracting_2_R,
+    MAIA_NotDistracting_3_R = 1 - MAIA_NotDistracting_3_R,
+    MAIA_NotDistracting_4_R = 1 - MAIA_NotDistracting_4_R,
+    MAIA_NotDistracting_5_R = 1 - MAIA_NotDistracting_5_R,
+    MAIA_NotDistracting_6_R = 1 - MAIA_NotDistracting_6_R,
+    MAIA_NotWorrying_1_R = 1 - MAIA_NotWorrying_1_R,
+    MAIA_NotWorrying_2_R = 1 - MAIA_NotWorrying_2_R,
+    MAIA_NotWorrying_5_R = 1 - MAIA_NotWorrying_5_R)
+
+# Compute subscales
+
+df13 $MAIA_AttentionReg <- rowMeans(select(df13 , starts_with("MAIA2_Attention")))
+df13 $MAIA_EmoAwareness <- rowMeans(select(df13 , starts_with("MAIA2_Emotional")))
+df13 $MAIA_Noticing <- rowMeans(select(df13 , starts_with("MAIA2_Noticing")))
+df13 $MAIA_BodyListening <- rowMeans(select(df13 , starts_with("MAIA2_BodyListening")))
+df13 $MAIA_NotDistracting<- rowMeans(select(df13 , starts_with("MAIA2_NotDistracting")))
+df13 $MAIA_NotWorrying<- rowMeans(select(df13 , starts_with("MAIA2_NotWorrying")))
+df13 $MAIA_SelfReg<- rowMeans(select(df13 , starts_with("MAIA2_SelfRegulation")))
+df13 $MAIA_Trusting<- rowMeans(select(df13 , starts_with("MAIA2_Trusting")))
 
@@
 # correlation::correlation(
-#   df10c[, "IAS_Total", drop = FALSE],  
-#   data2 = select(df10c, all_of(pi_vars)), p_adjust = "none"
+#   df12 [, "IAS_Total", drop = FALSE],  
+#   data2 = select(df12 , all_of(pi_vars)), p_adjust = "none"
 # ) |> 
@@
 
-### Sample 11
+### Sample 14
 
@@
   - Study 1: https://osf.io/49wbv
-  - Study 2: unpublished
-
-```{r}
-
-df11a <- haven::read_sav("../data/Giulia/Interoceptive Attention ESM.sav") |> 
+
+```{r}
+
+df14  <- haven::read_sav("../data/Giulia/Interoceptive Attention ESM.sav") |> 
   select(AGE, GENDER, contains("IAS_ACC"), -IAS_ACC_20, starts_with(c("MAIA", "TAS20", "DEP", "ANX")),  -ANX_21, -TAS20_21) |> #anx_21 , tas20_21 are attention checks
@@
     Muscles = IAS_ACC_15, Bruise = IAS_ACC_16, Pain = IAS_ACC_17, Blood_Sugar = IAS_ACC_18,
-    Affective_touch = IAS_ACC_19, Tickle =IAS_ACC_21, Itch = IAS_ACC_22
+    Affective_touch = IAS_ACC_19, Tickle =IAS_ACC_21, Itch = IAS_ACC_22,
+    MAIA_EmoAwareness =MAIA_Emotional, MAIA_SelfReg = MAIA_SelfRegulation, MAIA_AttentionReg = MAIA_Attention
   ) |>
@@
          TAS_EOT = (1-TAS20_5) + TAS20_8 + (1-TAS20_10) + TAS20_15 + TAS20_16 + (1-TAS20_18) + (1-TAS20_19) + TAS20_20) 
-
-# TODO: sanitize MAIA names / Compute dimensions.
-
-df11b <- haven::read_sav("../data/Giulia/Sleep and Exteroceptive Interoceptive Sensitivity.sav") |> # 165 participants
+```
+
+### Sample 15
+- Poreiro: unpublished
+
+```{r}
+
+df15   <- haven::read_sav("../data/Giulia/Sleep and Exteroceptive Interoceptive Sensitivity.sav") |> # 165 participants
   filter(Total_Attention_Fail == 0) |> # 32 participants removed based on failing one or more checks
@@
 
-# TODO: sanitize MAIA names / Compute dimensions.
-
 # Save all
-data <- list(df1a=df1a, df1b=df1b, df2=df2, df3=df3, df4=df4, df5=df5, df6=df6, df7a=df7a, df7b=df7b, df7c=df7c, df8a=df8a, df8b=df8b, df9=df9, df10a=df10a, df10b=df10b, df10c=df10c, df11a=df11a, df11b=df11b)
+data <- list(df1a=df1a, df1b=df1b, df2=df2, df3=df3, df4=df4, df5=df5, df6=df6, df7a=df7a, df7b=df7b, df7c=df7c, df8a=df8a, df8b=df8b, df9=df9, df10=df10, df11 =df11 , df12 =df12 , df13  = df13 , df14 =df14 , df15  =df15)
 save(data, file = "../data/data.RData")
@@
 - **Sample 9**: Data from [VonMohr's(2023)](https://osf.io/7p9u5/) study 3, downloaded from OSF, included `r report::report_participants(df9, age = "Age", sex = NA, gender = "Gender")`.
-- **Sample 10a**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10a, age = "Age", sex = NA, gender = "Gender")`.
-- **Sample 10b**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10b, age = "Age", sex = NA, gender = "Gender")`.
-- **Sample 10c**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10c, age = "Age", sex = NA, gender = "Gender")`.
-- **Sample 11a**: Data from [Poreiro's(2024)](https://osf.io/49wbv) study , included `r report::report_participants(df11a, age = "Age", sex = NA, gender = "Gender")`
-- **Sample 11b**: Data from [Poreiro's] study , included `r report::report_participants(df11b, age = "Age", sex = NA, gender = "Gender")`
-
-Total N = `r nrow(df1a) + nrow(df1b) + nrow(df2) + nrow(df3) + nrow(df4) + nrow(df5) + nrow(df6) + nrow(df7a) + nrow(df7b) + nrow(df7c) + nrow(df8a) + nrow(df8b) + nrow(df9) + nrow(df10a) + nrow(df10b) + nrow(df10c) +nrow(df11a) + nrow(df11b)`.
+- **Sample 10**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10, age = "Age", sex = NA, gender = "Gender")`.
+- **Sample 11**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df11 , age = "Age", sex = NA, gender = "Gender")`.
+- **Sample 12**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df12 , age = "Age", sex = NA, gender = "Gender")`.
+- **Sample 13**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df13 , age = "Age", sex = NA, gender = "Gender")`.
+- **Sample 14**: Data from [Poreiro's(2024)](https://osf.io/49wbv) study , included `r report::report_participants(df14 , age = "Age", sex = NA, gender = "Gender")`
+- **Sample 15 **: Data from [Poreiro's] study , included `r report::report_participants(df15 , age = "Age", sex = NA, gender = "Gender")`
+
+Total N = `r nrow(df1a) + nrow(df1b) + nrow(df2) + nrow(df3) + nrow(df4) + nrow(df5) + nrow(df6) + nrow(df7a) + nrow(df7b) + nrow(df7c) + nrow(df8a) + nrow(df8b) + nrow(df9) + nrow(df10) + nrow(df11) + nrow(df12) + nrow(df13) + nrow(df14) + nrow(df15)`.
 
@@
 desc_df9 <- desc(df9)
-desc_df10a <- desc(df10a)
-desc_df10b <- desc(df10b)
-desc_df10c <- desc(df10c)
-desc_df11a <- desc(df11a)
-desc_df11b <- desc(df11b)
-
-desc_total <- rbind(desc_df1a, desc_df1b, desc_df2, desc_df3, desc_df5, desc_df6, desc_df7a, desc_df7b, desc_df7c, desc_df8a, desc_df8b, desc_df9, desc_df10a, desc_df10b, desc_df10c, desc_df11a, desc_df11b)
+desc_df10 <- desc(df10)
+desc_df11  <- desc(df11)
+desc_df12  <- desc(df12)
+desc_df13  <- desc(df13)
+desc_df14  <- desc(df14)
+desc_df15   <- desc(df15)
+
+desc_total <- rbind(desc_df1a, desc_df1b, desc_df2, desc_df3, desc_df5, desc_df6, desc_df7a, desc_df7b, desc_df7c, desc_df8a, desc_df8b, desc_df9, desc_df10, desc_df11 , desc_df12 , desc_df13 , desc_df14 , desc_df15 )
 
@@
 table <- data.frame(
-  Reference = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Makowski et al., (2023c)', 'Poerio et al., (2024)', 'Poerio et al., unpublished', 'Total'),
-  Sample = c('', 'Sample 1a', 'Sample 1b', 'Sample 2', 'Sample 3', 'Sample 4', 'Sample 5', 'Sample 6', '', 'Sample 7a', 'Sample 7b', 'Sample 7c', '', 'Sample 8a', 'Sample 8b', 'Sample 9', 'Sample 10', 'Sample 11', 'Sample 12', 'Sample 13', 'Sample 14', 'Sample 15'),
-  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', 'English', 'English', 'English',''),
-  N = c('', nrow(df1a), nrow(df1b), nrow(df2), nrow(df3), nrow(df4), nrow(df5_attention), nrow(df6),'', nrow(df7a), nrow(df7b), 802,'', nrow(df8a), nrow(df8b), nrow(df9), nrow(df10a), nrow(df10b), nrow(df10c), nrow(df11a), nrow(df11b), 32214),
-  'Difference' = c('','', '', '', '', '', '', '', '', '', '', '', '', 'Collapsed "Itch" and "Tickling"', 'Collapsed "Itch" and "Tickling"', '', 'Analog scales', 'Analog scales', 'Analog scales', '', '', ''),
-  Age = c('', make_age(df1a$Age), make_age(df1b$Age), make_age(df2$Age), make_age(df3$Age), "48.6.6 ± 14.1*", make_age(df5_attention$Age), make_age(df6$Age),'', make_age(df7a$Age), make_age(df7b$Age), make_age(df7c$Age),'', make_age(df8a$Age), make_age(df8b$Age), make_age(df9$Age), make_age(df10a$Age), make_age(df10b$Age), make_age(df10c$Age), make_age(df11a$Age), make_age(df11b$Age), '48.6 ± 13.1'),
-  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76','18-50', '18-57', '18-60', '17-93'),
-  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', '50%*', '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '76%', '74.8%', '75.9%', '71.6%'),
-  Availability= c('osf.io/3m5nh', '', '', 'osf.io/5x9sg', 'osf.io/j6ef3', 'osf.io/ms354', 'osf.io/mp3cy', 'osf.io/xwz6g', 'osf.io/3f2h6', '', '', '','osf.io/3eztd','', '', 'osf.io/7p9u5', 'github.com/RealityBending/IllusionGameReliability', 'github.com/DominiqueMakowski/PHQ4R', 'github.com/RealityBending/InteroceptionPrimals', 'osf.io/49wbv', '','')
+  Reference = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Makowski et al., (2023c)', 'Makowski et al., (2024)', 'Poerio et al., (2024)', 'Poerio et al., unpublished', 'Total'),
+  Sample = c('', 'Sample 1a', 'Sample 1b', 'Sample 2', 'Sample 3', 'Sample 4', 'Sample 5', 'Sample 6', '', 'Sample 7a', 'Sample 7b', 'Sample 7c', '', 'Sample 8a', 'Sample 8b', 'Sample 9', 'Sample 10', 'Sample 11', 'Sample 12', 'Sample 13', 'Sample 14', 'Sample 15', 'Sample 16'),
+  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', 'English', 'English', 'English', 'English',''),
+  N = c('', nrow(df1a), nrow(df1b), nrow(df2), nrow(df3), nrow(df4), nrow(df5_attention), nrow(df6),'', nrow(df7a), nrow(df7b), 802,'', nrow(df8a), nrow(df8b), nrow(df9), nrow(df10), nrow(df11), nrow(df12), nrow(df13), nrow(df14), nrow(df15), 32993),
+  'Difference' = c('','', '', '', '', '', '', '', '', '', '', '', '', 'Collapsed "Itch" and "Tickling"', 'Collapsed "Itch" and "Tickling"', '', 'Analog scales.
+Does not include temperature, blood sugar and cough items.', 'Analog scales', 'Analog scales', '', '', '', ''),
+  Age = c('', make_age(df1a$Age), make_age(df1b$Age), make_age(df2$Age), make_age(df3$Age), "48.6.6 ± 14.1*", make_age(df5_attention$Age), make_age(df6$Age),'', make_age(df7a$Age), make_age(df7b$Age), make_age(df7c$Age),'', make_age(df8a$Age), make_age(df8b$Age), make_age(df9$Age), make_age(df10$Age), make_age(df11$Age), make_age(df12$Age), make_age(df13$Age), make_age(df14$Age), make_age(df15$Age), '48.6 ± 13.1'),
+  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76','18-50', '17, 87', '18-57', '18-60', '17-93'),
+  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', '50%*', '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '76%', '57.3%', '74.8%', '75.9%', '71.6%'),
+  Availability= c('osf.io/3m5nh', '', '', 'osf.io/5x9sg', 'osf.io/j6ef3', 'osf.io/ms354', 'osf.io/mp3cy', 'osf.io/xwz6g', 'osf.io/3f2h6', '', '', '','osf.io/3eztd','', '', 'osf.io/7p9u5', 'github.com/RealityBending/IllusionGameReliability', 'github.com/DominiqueMakowski/PHQ4R', 'github.com/RealityBending/InteroceptionPrimals',
+'github.com/RealityBending/InteroceptionScale',
+'osf.io/49wbv', '','')
 )
@@
   mutate(Sample = "Sample 9")
-dens10a <- estimate_density(select(df10a, all_of(setdiff(vars, c("Taste", "Cough", "Blood_Sugar")))), method = "kernSmooth") |>
-  mutate(Sample = "Sample 10a",
+dens10 <- estimate_density(select(df10, all_of(setdiff(vars, c("Taste", "Cough", "Blood_Sugar")))), method = "kernSmooth") |>
+  mutate(Sample = "Sample 10",
          x = datawizard::rescale(x, to=c(1, 5), range=c(0, 1)))
-dens10b <- estimate_density(select(df10b, all_of(vars)), method = "kernSmooth") |>
-  mutate(Sample = "Sample 10b",
+dens11<- estimate_density(select(df11, all_of(vars)), method = "kernSmooth") |>
+  mutate(Sample = "Sample 11",
          x = datawizard::rescale(x, to=c(1, 5), range=c(0, 1)))
-dens10c <- estimate_density(select(df10c, all_of(vars)), method = "kernSmooth") |>
-  mutate(Sample = "Sample 10c",
+dens12  <- estimate_density(select(df12, all_of(vars)), method = "kernSmooth") |>
+    mutate(Sample = "Sample 12",
          x = datawizard::rescale(x, to=c(1, 5), range=c(0, 1)))
-dens11a <- estimate_density(select(df11a, all_of(vars)), method = "kernSmooth") |>
-  mutate(Sample = "Sample 11a")
-dens11b <- estimate_density(select(df11b, all_of(vars)), method = "kernSmooth") |>
-  mutate(Sample = "Sample 11b")
-
-p1_data <- rbind(dens1a, dens1b, dens2, dens3, dens4, dens5, dens6, dens7a, dens7b, dens7c, dens8a, dens8b, dens9, dens10a, dens10b, dens10c, dens11a, dens11b)
+dens13  <- estimate_density(select(df13, all_of(vars)), method = "kernSmooth") |>
+  mutate(Sample = "Sample 13",
+         x = datawizard::rescale(x, to=c(1, 5), range=c(0, 1)))
+dens14  <- estimate_density(select(df14, all_of(vars)), method = "kernSmooth") |>
+  mutate(Sample = "Sample 14")
+dens15  <- estimate_density(select(df15, all_of(vars)), method = "kernSmooth") |>
+  mutate(Sample = "Sample 15")
+
+p1_data <- rbind(dens1a, dens1b, dens2, dens3, dens4, dens5, dens6, dens7a, dens7b, dens7c, dens8a, dens8b, dens9, dens10, dens11 , dens12, dens13, dens14, dens15)
 
@@
 p1 <- p1_data |>
-  mutate(Sample = fct_relevel(Sample, "Sample 1a", "Sample 1b", "Sample 2", "Sample 3", "Sample 4", "Sample 5", "Sample 6", "Sample 7a", "Sample 7b", "Sample 7c", "Sample 8a", "Sample 8b", "Sample 9", "Sample 10a", "Sample 10b", "Sample 10c", "Sample 11a", "Sample 11b"),
+  mutate(Sample = fct_relevel(Sample, "Sample 1a", "Sample 1b", "Sample 2", "Sample 3", "Sample 4", "Sample 5", "Sample 6", "Sample 7a", "Sample 7b", "Sample 7c", "Sample 8a", "Sample 8b", "Sample 9", "Sample 10", "Sample 11", "Sample 12", "Sample 13", "Sample 14", "Sample 15"),
          Parameter = ifelse(Parameter == "Affective_touch", "Affective touch", Parameter),
@@
 data9 <- normalize(select(df9, all_of(dens9$Parameter)), range = c(1, 5))
-data10a <- select(df10a, all_of(dens10a$Parameter))
-data10b <- select(df10b, all_of(dens10b$Parameter))
-data10c <- select(df10c, all_of(dens10c$Parameter))
-data11a <- normalize(select(df11a, all_of(dens11a$Parameter)), range = c(1, 5))
-data11b <- na.omit(normalize(select(df11b, all_of(dens11b$Parameter)), range = c(1, 5))) # remove NAS
-row.names(data11b) <- NULL
+data10 <- select(df10, all_of(dens10$Parameter))
+data11  <- select(df11, all_of(dens11$Parameter))
+data12  <- select(df12, all_of(dens12$Parameter))
+data13  <- select(df13, all_of(dens13$Parameter))
+data14  <- normalize(select(df14, all_of(dens14$Parameter)), range = c(1, 5))
+data15   <- na.omit(normalize(select(df15, all_of(dens15$Parameter)), range = c(1, 5))) # remove NAS
+row.names(data15) <- NULL
 
@@
   mutate(data8b, Tickle = NA), data9,
-  mutate(data10a, Taste = NA, Cough = NA, Blood_Sugar = NA),  
-  data10b,  data10c, data11a, data11b
+  mutate(data10, Taste = NA, Cough = NA, Blood_Sugar = NA),  
+  data11,  data12 , data13, data14 , data15  
 ) 
@@
     scale_fill_gradientn(
-      colors = c("white", "#FFF9C4", "#FFF59D", "#FFEB3B", "#FFCA28", "#FF9800", "#FF5722", "#F44336", "#E91E63", "#9C27B0", "#673AB7", "#512DA8", "#311B92"),
-      na.value = "#311B92",
+      colors = c("white", "#FFF9C4", "#FFF59D", "#FFEB3B", "#FFCA28", "#FF9800", "#FF5722", "#F44336", "#E91E63", "#9C27B0", "#673AB7", "#512DA8", "#315  92"),
+      na.value = "#315  92",
       limits = c(0, 0.8),
@@
 
-#### Sample 10a
-
-```{r}
-make_correlation(data10a)
-```
-
-#### Sample 10b
-
-```{r}
-make_correlation(data10b)
-```
-
-#### Sample 10c
-
-```{r}
-make_correlation(data10c)
-```
-
-#### Sample 11a
-
-```{r}
-make_correlation(data11a)
-```
-
-#### Sample 11b
-
-```{r}
-make_correlation(data11b)
+#### Sample 10
+
+```{r}
+make_correlation(data10)
+```
+
+#### Sample 11
+
+```{r}
+make_correlation(data11)
+```
+
+#### Sample 12
+
+```{r}
+make_correlation(data12)
+```
+
+#### Sample 13
+
+```{r}
+make_correlation(data13)
+```
+
+#### Sample 14
+
+```{r}
+make_correlation(data14)
+```
+
+#### Sample 15
+
+```{r}
+make_correlation(data15)
 ```
@@
 
-#### Sample 10a
-
-```{r}
-uva10a <- EGAnet::UVA(data = data10a, cut.off = 0.3)
-uva10a
-uva10a$keep_remove
-```
-
-#### Sample 10b
-
-```{r}
-uva10b <- EGAnet::UVA(data = data10b, cut.off = 0.3)
-uva10b
-uva10b$keep_remove
-```
-
-#### Sample 10c
-
-```{r}
-uva10c <- EGAnet::UVA(data = data10c, cut.off = 0.3)
-uva10c
-uva10c$keep_remove
-```
-
-#### Sample 11a
-
-```{r}
-uva11a <- EGAnet::UVA(data = data11a, cut.off = 0.3)
-uva11a
-uva11a$keep_remove
-```
-
-#### Sample 11b
-
-```{r}
-uva11b <- EGAnet::UVA(data = data11b, cut.off = 0.3)
-uva11b
-uva11b$keep_remove
+#### Sample 10
+
+```{r}
+uva10 <- EGAnet::UVA(data = data10, cut.off = 0.3)
+uva10
+uva10$keep_remove
+```
+
+#### Sample 11
+
+```{r}
+uva11  <- EGAnet::UVA(data = data11 , cut.off = 0.3)
+uva11 
+uva11$keep_remove
+```
+
+#### Sample 12
+
+```{r}
+uva12  <- EGAnet::UVA(data = data12, cut.off = 0.3)
+uva12 
+uva12$keep_remove
+```
+
+#### Sample 13
+
+```{r}
+uva13 <- EGAnet::UVA(data = data13, cut.off = 0.3)
+uva13 
+uva13$keep_remove
+```
+#### Sample 14
+
+```{r}
+uva14  <- EGAnet::UVA(data = data14 , cut.off = 0.3)
+uva14 
+uva14$keep_remove
+```
+
+#### Sample 15
+
+```{r}
+uva15   <- EGAnet::UVA(data = data15  , cut.off = 0.3)
+uva15  
+uva15$keep_remove
 ```
@@
   uva9$keep_remove$remove,
-  uva10a$keep_remove$remove,
-  uva10b$keep_remove$remove,
-  uva10c$keep_remove$remove,
-  uva11a$keep_remove$remove,
-  uva11b$keep_remove$remove)
+  uva10$keep_remove$remove,
+  uva11 $keep_remove$remove,
+  uva12 $keep_remove$remove,
+  uva13 $keep_remove$remove,
+  uva14 $keep_remove$remove,
+  uva15  $keep_remove$remove)
 
@@
 data9 <- select(data9, -Tickle)
-data10a <- select(data10a, -Tickle)
-data10b <- select(data10b, -Tickle)
-data10c <- select(data10c, -Tickle)
-data11a <- select(data11a, -Tickle)
-data11b <- select(data11b, -Tickle)
+data10 <- select(data10, -Tickle)
+data11  <- select(data11 , -Tickle)
+data12  <- select(data12 , -Tickle)
+data13  <- select(data13 , -Tickle)
+data14  <- select(data14 , -Tickle)
+data15   <- select(data15  , -Tickle)
 ```
@@
                    -Sex_arousal, -Temp)
-data10af <- select(data10a, -Affective_touch, -Vomit, -Itch,
+data10f <- select(data10, -Affective_touch, -Vomit, -Itch,
                    -Sex_arousal, -Temp)
-data10bf <- select(data10b, -Taste, -Affective_touch, -Vomit, -Itch,
+data11f <- select(data11, -Taste, -Affective_touch, -Vomit, -Itch,
                    -Sex_arousal, -Temp)
-data10cf <- select(data10c, -Taste, -Affective_touch, -Vomit, -Itch,
+data12f <- select(data12, -Taste, -Affective_touch, -Vomit, -Itch,
                    -Sex_arousal, -Temp)
-data11af <- select(data11a, -Taste, -Affective_touch, -Vomit, -Itch,
+data13f <- select(data13, -Taste, -Affective_touch, -Vomit, -Itch,
                    -Sex_arousal, -Temp)
-data11bf <- select(data11b, -Taste, -Affective_touch, -Vomit, -Itch,
+data14f <- select(data14, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
+data15f <- select(data15, -Taste, -Affective_touch, -Vomit, -Itch,
                    -Sex_arousal, -Temp)
@@
 
-TODO.
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data1b)
+rez_ega <- make_ega(data1b, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data1b, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data1bf)
+rez_ega <- make_ega(data1af, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data1af, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_cfa1b  <- make_cfa(data1bf)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cfa1b$test
+```
+
+::::
+
+### Sample 2
+
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data1b)
+rez_ega <- make_ega(data1b, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data1b, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data1bf)
+rez_ega <- make_ega(data1af, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data1af, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_cfa1b  <- make_cfa(data1bf)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cfa1b$test
+```
+
+::::
 
@@
   sample9 = add_empirical(data9, "Sample 9"),
-  sample10a = add_empirical(data10a, "Sample 10a"),
-  sample10b = add_empirical(data10b, "Sample 10b"),
-  sample10c = add_empirical(data10c, "Sample 10c"),
-  sample11a = add_empirical(data11a, "Sample 11a"),
-  sample11b = add_empirical(data11b, "Sample 11b")
+  sample10 = add_empirical(data10, "Sample 10"),
+  sample11  = add_empirical(data11 , "Sample 11 "),
+  sample12  = add_empirical(data12 , "Sample 12 "),
+  sample13 = add_empirical(data13, "Sample 13 "),
+  sample14  = add_empirical(data14 , "Sample 14 "),
+  sample15   = add_empirical(data15 , "Sample 15  ")
 )

### 2025-07-17 analysis/figures/table1.tex
updated scripts

--- 2025-07-06 analysis/figures/table1.tex
@@
 VonMohr et al., (2023) & Sample 9 & English & 21843 &  & 56.5 ± 14.4 & 18-93 & 73.2\% & osf.io/7p9u5 \\ 
-Makowski et al., (2023a) & Sample 10 & English & 485 & Analog scales & 30.1 ± 10.1 & 18-73 & 50.3\% & github.com/RealityBending/IllusionGameReliability \\ 
+Makowski et al., (2023a) & Sample 10 & English & 485 & Analog scales.
+Does not include temperature, blood sugar and cough items.
+& 30.1 ± 10.1 & 18-73 & 50.3\% & github.com/RealityBending/IllusionGameReliability \\
 Makowski et al., (2023b) & Sample 11 & English & 836 & Analog scales & 25.1 ± 11.3 & 17-76 & 53.0\% & github.com/DominiqueMakowski/PHQ4R \\ 
 Makowski et al., (2023c) & Sample 12 & English & 146 & Analog scales & 21.1 ± 4.3 & 18-50 & 76\% & github.com/RealityBending/InteroceptionPrimals \\ 
-Poerio et al., (2024) & Sample 13 & English & 107 &  & 26.8 ± 9.2 & 18-57 & 74.8\% & osf.io/49wbv \\ 
-Poerio et al., unpublished & Sample 14 & English & 131 &  & 30.9 ± 12.0 & 18-60 & 75.9\% &  \\ 
-Total & Sample 15 &  & 32214 &  & 48.6 ± 13.1 & 17-93 & 71.6\% &  \\ 
+Makowski et al., (2024) & Sample 13 & English & 737 &  & 36.8 ± 14.9 & 17, 87 & 57.3\% & github.com/RealityBending/InteroceptionScale \\ 
+Poerio et al., (2024) & Sample 14 & English & 107 &  & 26.8 ± 9.2 & 18-57 & 74.8\% & osf.io/49wbv \\ 
+Poerio et al., unpublished & Sample 15 & English & 131 &  & 30.9 ± 12.0 & 18-60 & 75.9\% &  \\ 
+Total & Sample 16 &  & 32993 &  & 48.6 ± 13.1 & 17-93 & 71.6\% &  \\ 
 \bottomrule
@@
 \begin{minipage}{\linewidth}
-* Information taken from the sample description of relevant paper rather than recomputed.\\
+Note.*Information taken from the sample description of relevant paper rather than recomputed.\\
 \end{minipage}

### 2025-07-17 analysis/study2.qmd
updated scripts

@@
 df9 <- cbind(data$df9, scores$sample9)
-df10a <- cbind(data$df10a, scores$sample10a)
-df10b <- cbind(data$df10b, scores$sample10b)
-df10c <- cbind(data$df10c, scores$sample10c)
-df11a <- cbind(data$df11a, scores$sample11a)
-df11b <- cbind(data$df11b, scores$sample11b)
+df10 <- cbind(data$df10, scores$sample10)
+df11 <- cbind(data$df11, scores$sample11)
+df12 <- cbind(data$df12, scores$sample12)
+df13 <- cbind(data$df13, scores$sample12)
+df14 <- cbind(data$df14, scores$sample14)
+df15 <- cbind(data$df15, scores$sample15)
 
@@
 # names(df9)  # ECR (Experience in Close Relationship Scale), TEAQ (touch experiences and attitudes questionnaire), STQ, TACSEN, UCLA, BFI, DBIA, BO, EQ
-# names(df10a)  # ASQ, BPD, GCBS, IPIP6, LIE, MAIA, PHQ4, PI, PID, SPQ
-# names(df10b)  # PHQ4, STAIT5, BDI, MAIA
-# names(df10c) # MAIA, PI, 
-# names(df11a) # MAIA, TAS, MFQ(DEP), STAI(ANX)
-# names(df11b) 
+# names(df10)  # ASQ, BPD, GCBS, IPIP6, LIE, MAIA, PHQ4, PI, PID, SPQ
+# names(df11)  # PHQ4, STAIT5, BDI, MAIA
+# names(df12) # MAIA, PI, 
+# names(df13) # 
+# names(df14) # MAIA, TAS, MFQ(DEP), STAI(ANX)
+# names(df15) 
 ```
@@
                      df5, df6, df7a, df7b, df7c, 
-                     df8a, df8b, df9, df10a, df10b, 
-                     df10c, df11a, df11b)) {
+                     df8a, df8b, df9, df10, df11, 
+                     df12, df14, df15)) {
       if (with %in% names(dataset)) {
@@
 # names(df7c)[str_detect(names(df7c), "MAIA")]
-# names(df10a)[str_detect(names(df10a), "MAIA")]
-# names(df10b)[str_detect(names(df10b), "MAIA2")] # all columns with NA values 
-# names(df10c)[str_detect(names(df10c), "MAIA")]
-# names(df11a)[str_detect(names(df11b), "MAIA")]
+# names(df10)[str_detect(names(df10), "MAIA")]
+# names(df11)[str_detect(names(df11), "MAIA2")] # all columns with NA values 
+# names(df12)[str_detect(names(df12), "MAIA")]
+# names(df14)[str_detect(names(df15), "MAIA")]
 
@@
 # names(df8b)[str_starts(names(df8b), "TAS")]
-# names(df11a)[str_starts(names(df11a), "TAS")]
+# names(df14)[str_starts(names(df14), "TAS")]
 
@@
 # names(df9)
-# names(df11a)
+# names(df14)
 
@@
 # names(df7c)[str_detect(names(df7c), "STAI")]
-# names(df10b)[str_detect(names(df10b), "STAI")] 
-# names(df11a)[str_detect(names(df11a), "ANX")] # anx = stai-t
+# names(df11)[str_detect(names(df11), "STAI")] 
+# names(df14)[str_detect(names(df14), "ANX")] # anx = stai-t
 
@@
 ```{r}
-#  names(select(df10a, starts_with("ASQ")))
+#  names(select(df10, starts_with("ASQ")))
 data <- rbind(
@@
 # names(df9)[str_detect(names(df9), "BFI_")]
-# names(df10a)[str_detect(names(df10a), "IPIP6_")]
+# names(df10)[str_detect(names(df10), "IPIP6_")]
 
@@
 # names(df9)  # ECR (Experience in Close Relationship Scale), TEAQ (touch experiences and attitudes questionnaire), STQ, TACSEN, UCLA, BFI, DBIA, BO, EQ
-# names(df10a)  # ASQ, BPD, GCBS, IPIP6, LIE, MAIA, PHQ4, PI, PID, SPQ
-# names(df10b)  # PHQ4, STAIT5, BDI, MAIA
-# names(df10c) # MAIA, PI, 
-# names(df11a) # MAIA, TAS, MFQ(DEP), STAI(ANX)
-# names(df11b)
+# names(df10)  # ASQ, BPD, GCBS, IPIP6, LIE, MAIA, PHQ4, PI, PID, SPQ
+# names(df11)  # PHQ4, STAIT5, BDI, MAIA
+# names(df12) # MAIA, PI, 
+# names(df14) # MAIA, TAS, MFQ(DEP), STAI(ANX)
+# names(df15)
 

### 2025-07-18 analysis/Study1.qmd
changes to script
done till 8a

@@
 data3 <- normalize(select(df3, all_of(dens3$Parameter)), range = c(1, 5))
-data4 <- normalize(select(df4, all_of(dens4$Parameter)), range = c(1, 5))
+data6 <- normalize(select(df4, all_of(dens4$Parameter)), range = c(1, 5))
 data5 <- normalize(select(df5, all_of(dens5$Parameter)), range = c(1, 5))
@@
 data_all <- rbind(
-  data1a, data1b, data2, data3, data4, data5, data6, data7a, data7b, data7c,
+  data1a, data1b, data2, data3, data6, data5, data6, data7a, data7b, data7c,
   mutate(data8a, Tickle = NA), 
@@
     scale_fill_gradientn(
-      colors = c("white", "#FFF9C4", "#FFF59D", "#FFEB3B", "#FFCA28", "#FF9800", "#FF5722", "#F44336", "#E91E63", "#9C27B0", "#673AB7", "#512DA8", "#315  92"),
-      na.value = "#315  92",
+      colors = c("white", "#FFF9C4", "#FFF59D", "#FFEB3B", "#FFCA28", "#FF9800", "#FF5722",
+        "#F44336", "#E91E63", "#9C27B0", "#673AB7", "#512DA8",  "#3F51B5", 
+        "#1976D2",  "#00ACC1","#00897B", "#00796B", "#31B192"),,
+      na.value = "#31B192",
       limits = c(0, 0.8),
@@
 ```{r}
-make_correlation(data4)
+make_correlation(data6)
 ```
@@
 ```{r}
-uva4 <- EGAnet::UVA(data = data4, cut.off = 0.3)
+uva4 <- EGAnet::UVA(data = data6, cut.off = 0.3)
 uva4
@@
 data3 <- select(data3, -Tickle)
-data4 <- select(data4, -Tickle)
+data6 <- select(data6, -Tickle)
 data5 <- select(data5, -Tickle)
@@
     verbose = FALSE, 
-    allow.singleton = TRUE
+    allow.singleton = TRUE,
+    loading.method = "original"
   )
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]]))
+
 stab <- EGAnet::itemStability(rez_ega$rez)
@@
                    -Sex_arousal, -Temp)
-data4f <- select(data4, -Taste, -Affective_touch, -Vomit, -Itch,
+data6f <- select(data6, -Taste, -Affective_touch, -Vomit, -Itch,
                    -Sex_arousal, -Temp)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data1af, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+rez_efa <- make_efa(data1bf, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
                                             "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
@@
 
-rez_hclust <- make_hclust(data1b)
-rez_ega <- make_ega(data1b, cols = c(
+rez_hclust <- make_hclust(data2)
+rez_ega <- make_ega(data2, cols = c(
   "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data1b, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+rez_efa <- make_efa(data2, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
                                             "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
@@
 
-rez_hclust <- make_hclust(data1bf)
-rez_ega <- make_ega(data1af, cols = c(
+rez_hclust <- make_hclust(data2f)
+rez_ega <- make_ega(data2f, cols = c(
   "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data1af, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+rez_efa <- make_efa(data2f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
                                             "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
-rez_cfa1b  <- make_cfa(data1bf)
+rez_cfa2  <- make_cfa(data2f)
 
@@
 
-rez_cfa1b$test
+rez_cfa2$test
 ```
@@
 
+### Sample 3
+
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data3)
+rez_ega <- make_ega(data3, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data3, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data3f)
+rez_ega <- make_ega(data3f, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data3f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_cf3  <- make_cfa(data3f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cfa3$test
+```
+
+::::
+
+### Sample 4
+
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data4)
+rez_ega <- make_ega(data4, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data4, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data4f)
+rez_ega <- make_ega(data4f, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data4f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_cf4  <- make_cfa(data4f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cf4$test
+```
+
+::::
+
+### Sample 5
+
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data5)
+rez_ega <- make_ega(data5, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data5, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data5f)
+rez_ega <- make_ega(data5f, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data5f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_cfa5  <- make_cfa(data5f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cf5$test
+```
+
+::::
+
+### Sample 6
+
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data6)
+rez_ega <- make_ega(data6, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data6, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data6f)
+rez_ega <- make_ega(data6f, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data6f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_cf6  <- make_cfa(data6f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cf6$test
+```
+
+::::
+
+### Sample 7a
+
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data7a)
+rez_ega <- make_ega(data7a, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data7a, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data7af)
+rez_ega <- make_ega(data7af, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data7af, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_cf7a  <- make_cfa(data7af)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cf7a$test
+```
+
+::::
+
+### Sample 7b
+
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data7b)
+rez_ega <- make_ega(data7b, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data7b, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data7bf)
+rez_ega <- make_ega(data7bf, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data7bf, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_cf7b  <- make_cfa(data7bf)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cf7b$test
+```
+
+::::
+
+### Sample 7c
+
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data7c)
+rez_ega <- make_ega(data7c, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data7c, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data7cf)
+rez_ega <- make_ega(data7cf, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data7cf, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_cf7c  <- make_cfa(data7cf)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cf7c$test
+```
+
+::::
+
+### Sample 8a
+
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data8a)
+rez_ega <- make_ega(data8a, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data8a, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data8af)
+rez_ega <- make_ega(data8af, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data8af, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_cf8a  <- make_cfa(data8af)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cf8$test
+```
+::::
+
+### Sample 8b
 :::
@@
   mutate(rez_cfa0$perf, Sample = "All Samples"),
-  mutate(rez_cfa1a$perf, Sample = "Sample 1a")
-  # TODO
+  mutate(rez_cfa1a$perf, Sample = "Sample 1a"),
+  mutate(rez_cfa1b$perf, Sample = "Sample 1b"),
+  mutate(rez_cfa2$perf, Sample = "Sample 2"),
+  mutate(rez_cfa3$perf, Sample = "Sample 3"),
+  mutate(rez_cfa4$perf, Sample = "Sample 4"),
+  mutate(rez_cfa5$perf, Sample = "Sample 5"),
+  mutate(rez_cfa6$perf, Sample = "Sample 6"),
+  mutate(rez_cfa7a$perf, Sample = "Sample 7a"),
+  mutate(rez_cfa7b$perf, Sample = "Sample 7b"),
+  mutate(rez_cfa7c$perf, Sample = "Sample 7c"),
+  mutate(rez_cfa8a$perf, Sample = "Sample 8a"),
+  mutate(rez_cfa8b$perf, Sample = "Sample 8b"),
+  mutate(rez_cfa9$perf, Sample = "Sample 9"),
+  mutate(rez_cfa10$perf, Sample = "Sample 10"),
+  mutate(rez_cfa11$perf, Sample = "Sample 11"),
+  mutate(rez_cfa12$perf, Sample = "Sample 12"),
+  mutate(rez_cfa13$perf, Sample = "Sample 13"),
+  mutate(rez_cfa14$perf, Sample = "Sample 14"),
+  mutate(rez_cfa15$perf, Sample = "Sample 15")
 ) |> 
@@
   sample3 = add_empirical(data3, "Sample 3"),
-  sample4 = add_empirical(data4, "Sample 4"),
+  sample4 = add_empirical(data6, "Sample 4"),
   sample5 = add_empirical(data5, "Sample 5"),

### 2025-07-21 analysis/Study1.qmd
added the rest of the 4 methods for the samples

@@
 data5 <- select(data5, -Tickle)
-data6 <- select(data6, -Tickle)
+# data6 <- select(data6, -Tickle)
 data7a <- select(data7a, -Tickle)
@@
 
-rez_cf8$test
+rez_cf8a$test
 ```
@@
 ### Sample 8b
-:::
+
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data8b)
+rez_ega <- make_ega(data8b, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data8b, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data8bf)
+rez_ega <- make_ega(data8bf, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data8bf, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_cf8b  <- make_cfa(data8bf)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cf8b$test
+```
+::::
+
+### Sample 9
+
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data9)
+rez_ega <- make_ega(data9, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data9, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data9f)
+rez_ega <- make_ega(data9f, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data9f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_cf9  <- make_cfa(data9f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cf9$test
+```
+::::
+
+### Sample 10
+
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data10)
+rez_ega <- make_ega(data10, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data10, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data10f)
+rez_ega <- make_ega(data10f, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data10f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_cf10  <- make_cfa(data10f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cf10$test
+```
+::::
+
+### Sample 11
+
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data11)
+rez_ega <- make_ega(data11, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data11, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data11f)
+rez_ega <- make_ega(data11f, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data8af, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_cf11  <- make_cfa(data11f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cf11$test
+```
+::::
+
+### Sample 12
+
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data12)
+rez_ega <- make_ega(data12, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data12, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data12f)
+rez_ega <- make_ega(data8af, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data12f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_cf12  <- make_cfa(data12f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cf12$test
+```
+::::
+
+### Sample 13
+
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data13)
+rez_ega <- make_ega(data13, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data13, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data13f)
+rez_ega <- make_ega(data13f, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data13f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_cf13  <- make_cfa(data13f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cf13$test
+```
+::::
+
+### Sample 14
+
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data14)
+rez_ega <- make_ega(data14, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data14, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data14f)
+rez_ega <- make_ega(data14f, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data8af, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_cf14  <- make_cfa(data14f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cf14$test
+```
+::::
+
+### Sample 15
+
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data15)
+rez_ega <- make_ega(data15, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data15, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data15f)
+rez_ega <- make_ega(data15f, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data8af, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_cf15  <- make_cfa(data15f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cf15$test
+```
+::::
 

### 2025-08-07 analysis/Study1.qmd
fix

@@
 library(EGAnet)
+
+ias_vars <- c(
+  "Heart", "Hungry", "Breathing", "Thirsty", "Urinate", "Defecate", "Taste", "Vomit", "Sneeze", "Cough", "Temp",
+  "Sex_arousal", "Wind", "Burp", "Muscles", "Bruise", "Pain", "Blood_Sugar", "Affective_touch", "Tickle", "Itch"
+)
 ```
@@
   ) |>
-  filter(!is.na(Urinate))
-
+  filter(!is.na(Urinate)) |> 
+  datawizard::rescale(select=ias_vars, to = c(0, 5), range = c(0, 1))
 ```
@@
   mutate(
-    MAIA_NotDistracting_1_R = 1 - MAIA2_NotDistracting_1_R,
-    MAIA_NotDistracting_2_R = 1 - MAIA2_NotDistracting_2_R,
-    MAIA_NotDistracting_3_R = 1 - MAIA2_NotDistracting_3_R,
-    MAIA_NotDistracting_4_R = 1 - MAIA2_NotDistracting_4_R,
-    MAIA_NotDistracting_5_R = 1 - MAIA2_NotDistracting_5_R,
-    MAIA_NotDistracting_6_R = 1 - MAIA2_NotDistracting_6_R,
-    MAIA_NotWorrying_1_R = 1 - MAIA2_NotWorrying_1_R,
-    MAIA_NotWorrying_2_R = 1 - MAIA2_NotWorrying_2_R,
-    MAIA_NotWorrying_5_R = 1 - MAIA2_NotWorrying_5_R)
+    MAIA2_NotDistracting_1_R = 1 - MAIA2_NotDistracting_1_R,
+    MAIA2_NotDistracting_2_R = 1 - MAIA2_NotDistracting_2_R,
+    MAIA2_NotDistracting_3_R = 1 - MAIA2_NotDistracting_3_R,
+    MAIA2_NotDistracting_4_R = 1 - MAIA2_NotDistracting_4_R,
+    MAIA2_NotDistracting_5_R = 1 - MAIA2_NotDistracting_5_R,
+    MAIA2_NotDistracting_6_R = 1 - MAIA2_NotDistracting_6_R,
+    MAIA2_NotWorrying_1_R = 1 - MAIA2_NotWorrying_1_R,
+    MAIA2_NotWorrying_2_R = 1 - MAIA2_NotWorrying_2_R,
+    MAIA2_NotWorrying_5_R = 1 - MAIA2_NotWorrying_5_R) |> 
+  datawizard::rescale(select=ias_vars, to = c(0, 5), range = c(0, 1))
 
@@
 
-df11 $MAIA_AttentionReg <- rowMeans(select(df11 , starts_with("MAIA2_Attention")))
-df11 $MAIA_EmoAwareness <- rowMeans(select(df11 , starts_with("MAIA2_Emotional")))
-df11 $MAIA_Noticing <- rowMeans(select(df11 , starts_with("MAIA2_Noticing")))
-df11 $MAIA_BodyListening <- rowMeans(select(df11 , starts_with("MAIA2_BodyListening")))
-df11 $MAIA_NotDistracting<- rowMeans(select(df11 , starts_with("MAIA2_NotDistracting")))
-df11 $MAIA_NotWorrying<- rowMeans(select(df11 , starts_with("MAIA2_NotWorrying")))
-df11 $MAIA_SelfReg<- rowMeans(select(df11 , starts_with("MAIA2_SelfRegulation")))
-df11 $MAIA_Trusting<- rowMeans(select(df11 , starts_with("MAIA2_Trusting")))
+df11$MAIA_AttentionReg <- rowMeans(select(df11 , starts_with("MAIA2_Attention")))
+df11$MAIA_EmoAwareness <- rowMeans(select(df11 , starts_with("MAIA2_Emotional")))
+df11$MAIA_Noticing <- rowMeans(select(df11 , starts_with("MAIA2_Noticing")))
+df11$MAIA_BodyListening <- rowMeans(select(df11 , starts_with("MAIA2_BodyListening")))
+df11$MAIA_NotDistracting<- rowMeans(select(df11 , starts_with("MAIA2_NotDistracting")))
+df11$MAIA_NotWorrying<- rowMeans(select(df11 , starts_with("MAIA2_NotWorrying")))
+df11$MAIA_SelfReg<- rowMeans(select(df11 , starts_with("MAIA2_SelfRegulation")))
+df11$MAIA_Trusting<- rowMeans(select(df11 , starts_with("MAIA2_Trusting")))
 
@@
     Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
-    MAIA_EmoAwareness = MAIA_EmotionalAwareness, MAIA_AttentionReg = MAIA_AttentionRegulation,
+    MAIA_EmoAwareness = MAIA_EmotionalAwareness, 
+    MAIA_AttentionReg = MAIA_AttentionRegulation,
     MAIA_SelfReg = MAIA_SelfRegulation
   ) |>
-  filter(!is.na(Heart)) # participant is outlier and had total IAS scores below 0.4 
+  filter(!is.na(Heart)) |>  # participant is outlier and had total IAS scores below 0.4 
+  datawizard::rescale(select=ias_vars, to = c(0, 5), range = c(0, 1))
 ```
@@
 # Compute subscales
-
-df13 $MAIA_AttentionReg <- rowMeans(select(df13 , starts_with("MAIA2_Attention")))
-df13 $MAIA_EmoAwareness <- rowMeans(select(df13 , starts_with("MAIA2_Emotional")))
-df13 $MAIA_Noticing <- rowMeans(select(df13 , starts_with("MAIA2_Noticing")))
-df13 $MAIA_BodyListening <- rowMeans(select(df13 , starts_with("MAIA2_BodyListening")))
-df13 $MAIA_NotDistracting<- rowMeans(select(df13 , starts_with("MAIA2_NotDistracting")))
-df13 $MAIA_NotWorrying<- rowMeans(select(df13 , starts_with("MAIA2_NotWorrying")))
-df13 $MAIA_SelfReg<- rowMeans(select(df13 , starts_with("MAIA2_SelfRegulation")))
-df13 $MAIA_Trusting<- rowMeans(select(df13 , starts_with("MAIA2_Trusting")))
-
+df13$MAIA_AttentionReg <- rowMeans(select(df13 , starts_with("MAIA_Attention")))
+df13$MAIA_EmoAwareness <- rowMeans(select(df13 , starts_with("MAIA_Emotional")))
+df13$MAIA_Noticing <- rowMeans(select(df13 , starts_with("MAIA_Noticing")))
+df13$MAIA_BodyListening <- rowMeans(select(df13 , starts_with("MAIA_BodyListening")))
+df13$MAIA_NotDistracting<- rowMeans(select(df13 , starts_with("MAIA_NotDistracting")))
+df13$MAIA_NotWorrying<- rowMeans(select(df13 , starts_with("MAIA_NotWorrying")))
+df13$MAIA_SelfReg<- rowMeans(select(df13 , starts_with("MAIA_SelfRegulation")))
+df13$MAIA_Trusting<- rowMeans(select(df13 , starts_with("MAIA_Trusting")))
 ```
@@
 ```{r}
-
 df14  <- haven::read_sav("../data/Giulia/Interoceptive Attention ESM.sav") |> 
@@
 ```{r}
-
 df15   <- haven::read_sav("../data/Giulia/Sleep and Exteroceptive Interoceptive Sensitivity.sav") |> # 165 participants
@@
   na.omit()
-
+```
+
+:::
+
+## Participants
+
+```{r}
 # Save all
@@
 ```
-
-:::
-
-## Participants
 
@@
 
-total_mean = sum(desc_total$mean * desc_total$n) / sum(desc_total$n)
-total_sd = sum(desc_total$sd * desc_total$n) / sum(desc_total$n)
-perce_female = sum(desc_total$female)/sum(desc_total$n) *100
+total_mean <- sum(desc_total$mean * desc_total$n) / sum(desc_total$n)
+total_sd <- sum(desc_total$sd * desc_total$n) / sum(desc_total$n)
+perce_female <- sum(desc_total$female)/sum(desc_total$n) * 100
 
@@
 ```{r}
-vars <- c(
-  "Heart", "Hungry", "Breathing", "Thirsty", "Urinate", "Defecate", "Taste", "Vomit", "Sneeze", "Cough", "Temp",
-  "Sex_arousal", "Wind", "Burp", "Muscles", "Bruise", "Pain", "Blood_Sugar", "Affective_touch", "Tickle", "Itch"
-)
-
-dens1a <- estimate_density(select(df1a, all_of(vars)), method = "kernSmooth") |>
+dens1a <- estimate_density(select(df1a, all_of(ias_vars)), method = "kernSmooth") |>
   mutate(Sample = "Sample 1a")
-dens1b <- estimate_density(select(df1b, all_of(vars)), method = "kernSmooth") |>
+dens1b <- estimate_density(select(df1b, all_of(ias_vars)), method = "kernSmooth") |>
   mutate(Sample = "Sample 1b")
-dens2 <- estimate_density(select(df2, all_of(vars)), method = "kernSmooth") |>
+dens2 <- estimate_density(select(df2, all_of(ias_vars)), method = "kernSmooth") |>
   mutate(Sample = "Sample 2")
-dens3 <- estimate_density(select(df3, all_of(vars)), method = "kernSmooth") |>
+dens3 <- estimate_density(select(df3, all_of(ias_vars)), method = "kernSmooth") |>
   mutate(Sample = "Sample 3")
-dens4 <- estimate_density(select(df4, all_of(vars)), method = "kernSmooth") |>
+dens4 <- estimate_density(select(df4, all_of(ias_vars)), method = "kernSmooth") |>
   mutate(Sample = "Sample 4")
-dens5 <- estimate_density(select(df5, all_of(vars)), method = "kernSmooth") |>
+dens5 <- estimate_density(select(df5, all_of(ias_vars)), method = "kernSmooth") |>
   mutate(Sample = "Sample 5")
-dens6 <- estimate_density(select(df6, all_of(vars)), method = "kernSmooth") |>
+dens6 <- estimate_density(select(df6, all_of(ias_vars)), method = "kernSmooth") |>
   mutate(Sample = "Sample 6")
-dens7a <- estimate_density(select(df7a, all_of(vars)), method = "kernSmooth") |>
+dens7a <- estimate_density(select(df7a, all_of(ias_vars)), method = "kernSmooth") |>
   mutate(Sample = "Sample 7a")
-dens7b <- estimate_density(select(df7b, all_of(vars)), method = "kernSmooth") |>
+dens7b <- estimate_density(select(df7b, all_of(ias_vars)), method = "kernSmooth") |>
   mutate(Sample = "Sample 7b")
-dens7c <- estimate_density(select(df7c, all_of(vars)), method = "kernSmooth") |>
+dens7c <- estimate_density(select(df7c, all_of(ias_vars)), method = "kernSmooth") |>
   mutate(Sample = "Sample 7c")
-dens8a <- estimate_density(select(df8a, all_of(setdiff(vars, "Tickle"))), method = "kernSmooth") |>
+dens8a <- estimate_density(select(df8a, all_of(setdiff(ias_vars, "Tickle"))), method = "kernSmooth") |>
   mutate(Sample = "Sample 8a")
-dens8b <- estimate_density(select(df8b, all_of(setdiff(vars, "Tickle"))), method = "kernSmooth") |>
+dens8b <- estimate_density(select(df8b, all_of(setdiff(ias_vars, "Tickle"))), method = "kernSmooth") |>
   mutate(Sample = "Sample 8b")
-dens9 <- estimate_density(select(df9, all_of(vars)), method = "kernSmooth") |>
+dens9 <- estimate_density(select(df9, all_of(ias_vars)), method = "kernSmooth") |>
   mutate(Sample = "Sample 9")
-dens10 <- estimate_density(select(df10, all_of(setdiff(vars, c("Taste", "Cough", "Blood_Sugar")))), method = "kernSmooth") |>
-  mutate(Sample = "Sample 10",
-         x = datawizard::rescale(x, to=c(1, 5), range=c(0, 1)))
-dens11<- estimate_density(select(df11, all_of(vars)), method = "kernSmooth") |>
-  mutate(Sample = "Sample 11",
-         x = datawizard::rescale(x, to=c(1, 5), range=c(0, 1)))
-dens12  <- estimate_density(select(df12, all_of(vars)), method = "kernSmooth") |>
-    mutate(Sample = "Sample 12",
-         x = datawizard::rescale(x, to=c(1, 5), range=c(0, 1)))
-dens13  <- estimate_density(select(df13, all_of(vars)), method = "kernSmooth") |>
-  mutate(Sample = "Sample 13",
-         x = datawizard::rescale(x, to=c(1, 5), range=c(0, 1)))
-dens14  <- estimate_density(select(df14, all_of(vars)), method = "kernSmooth") |>
+dens10 <- estimate_density(select(df10, all_of(setdiff(ias_vars, c("Taste", "Cough", "Blood_Sugar")))), method = "kernSmooth") |>
+  mutate(Sample = "Sample 10")
+dens11<- estimate_density(select(df11, all_of(ias_vars)), method = "kernSmooth") |>
+  mutate(Sample = "Sample 11")
+dens12  <- estimate_density(select(df12, all_of(ias_vars)), method = "kernSmooth") |>
+    mutate(Sample = "Sample 12")
+dens13  <- estimate_density(select(df13, all_of(ias_vars)), method = "kernSmooth") |>
+  mutate(Sample = "Sample 13")
+dens14  <- estimate_density(select(df14, all_of(ias_vars)), method = "kernSmooth") |>
   mutate(Sample = "Sample 14")
-dens15  <- estimate_density(select(df15, all_of(vars)), method = "kernSmooth") |>
+dens15  <- estimate_density(select(df15, all_of(ias_vars)), method = "kernSmooth") |>
   mutate(Sample = "Sample 15")
@@
 
-linetype <- setNames(rep("solid", length(vars)), vars)
+linetype <- setNames(rep("solid", length(ias_vars)), ias_vars)
 linetype["Affective touch"] <- "dotted"
@@
 ```{r}
-data1a <- normalize(select(df1a, all_of(dens1a$Parameter)), range = c(1, 5))
-data1b <- normalize(select(df1b, all_of(dens1b$Parameter)), range = c(1, 5))
-data2 <- normalize(select(df2, all_of(dens2$Parameter)), range = c(1, 5))
-data3 <- normalize(select(df3, all_of(dens3$Parameter)), range = c(1, 5))
-data6 <- normalize(select(df4, all_of(dens4$Parameter)), range = c(1, 5))
-data5 <- normalize(select(df5, all_of(dens5$Parameter)), range = c(1, 5))
-data6 <- normalize(select(df6, all_of(dens6$Parameter)), range = c(1, 5))
-data7a <- normalize(select(df7a, all_of(dens7a$Parameter)), range = c(1, 5))
-data7b <- normalize(select(df7b, all_of(dens7b$Parameter)), range = c(1, 5))
-data7c <- normalize(select(df7c, all_of(dens7c$Parameter)), range = c(1, 5))
-data8a <- normalize(select(df8a, all_of(dens8a$Parameter)), range = c(1, 5))
-data8b <- normalize(select(df8b, all_of(dens8b$Parameter)), range = c(1, 5))
-data9 <- normalize(select(df9, all_of(dens9$Parameter)), range = c(1, 5))
+#  ONLY IAS DATA
+data1a <- select(df1a, all_of(dens1a$Parameter))
+data1b <- select(df1b, all_of(dens1b$Parameter))
+data2 <- select(df2, all_of(dens2$Parameter))
+data3 <- select(df3, all_of(dens3$Parameter))
+data6 <- select(df4, all_of(dens4$Parameter))
+data5 <- select(df5, all_of(dens5$Parameter))
+data6 <- select(df6, all_of(dens6$Parameter))
+data7a <- select(df7a, all_of(dens7a$Parameter))
+data7b <- select(df7b, all_of(dens7b$Parameter))
+data7c <- select(df7c, all_of(dens7c$Parameter))
+data8a <- select(df8a, all_of(dens8a$Parameter))
+data8b <- select(df8b, all_of(dens8b$Parameter))
+data9 <- select(df9, all_of(dens9$Parameter))
 data10 <- select(df10, all_of(dens10$Parameter))
@@
 data13  <- select(df13, all_of(dens13$Parameter))
-data14  <- normalize(select(df14, all_of(dens14$Parameter)), range = c(1, 5))
-data15   <- na.omit(normalize(select(df15, all_of(dens15$Parameter)), range = c(1, 5))) # remove NAS
-row.names(data15) <- NULL
+data14  <- select(df14, all_of(dens14$Parameter))
+data15   <- select(df15, all_of(dens15$Parameter))
 
@@
   mutate(data10, Taste = NA, Cough = NA, Blood_Sugar = NA),  
-  data11,  data12 , data13, data14 , data15  
+  data11,  data12 , data13, data14, data15  
 ) 
@@
       colors = c("white", "#FFF9C4", "#FFF59D", "#FFEB3B", "#FFCA28", "#FF9800", "#FF5722",
-        "#F44336", "#E91E63", "#9C27B0", "#673AB7", "#512DA8",  "#3F51B5", 
-        "#1976D2",  "#00ACC1","#00897B", "#00796B", "#31B192"),,
-      na.value = "#31B192",
-      limits = c(0, 0.8),
+        "#F44336", "#E91E63", "#9C27B0", "#673AB7", "#512DA8", "#311B92"),
+      na.value = "#263238",
+      limits = c(0.05, 0.75),
       guide = guide_colorbar(ticks.colour = NA)
@@
       legend.title = element_blank(),
+      legend.position = "none",
       axis.title.x = element_blank(),

### 2025-08-10 analysis/Study1.qmd
typos

@@
 library(EGAnet)
+library(haven)
 
@@
 df4$MAIA_BodyListening <- rowMeans(select(df4, starts_with("MAIA_BL")), na.rm = TRUE)
-df4$MAIA_BodyTrusting <- rowMeans(select(df4, starts_with("MAIA_TR")), na.rm = TRUE)
+df4$MAIA_Trusting <- rowMeans(select(df4, starts_with("MAIA_TR")), na.rm = TRUE)
 df4$MAIA_EmoAwareness <- rowMeans(select(df4, starts_with("MAIA_EA")), na.rm = TRUE)
@@
     MAIA_Trusting = MAIA_TRUSTING, MAIA_EmoAwareness = MAIA_EMOTIONAL_AWARENESS
-  )
+  ) |> 
+  mutate(across(starts_with("MAIA_"), \(x) x - 1)) # Original scale 1-6
 
@@
     MAIA_Trusting = maiaTrusting, MAIA_EmoAwareness = maiaEmotionalAwareness
-  )
+  ) |> 
+  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5), range = c(1, 5)))) # Original scale 1-5
 
@@
     ICQ = ICQ_sum
-  )
+  ) |> 
+  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5), range = c(0, 6)))) # Original scale 0-6
 ```
@@
   filter(!is.na(Urinate)) |> 
-  datawizard::rescale(select=ias_vars, to = c(0, 5), range = c(0, 1))
+  datawizard::rescale(select=ias_vars, to = c(0, 5), range = c(0, 1)) |> 
+  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5)))) 
 ```
@@
 
+df11 <- mutate(df11, across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5))))
+
 ```
@@
   filter(!is.na(Heart)) |>  # participant is outlier and had total IAS scores below 0.4 
-  datawizard::rescale(select=ias_vars, to = c(0, 5), range = c(0, 1))
+  datawizard::rescale(select=ias_vars, to = c(0, 5), range = c(0, 1)) |> 
+  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5)))) 
 ```
@@
 data3 <- select(df3, all_of(dens3$Parameter))
-data6 <- select(df4, all_of(dens4$Parameter))
+data4 <- select(df4, all_of(dens4$Parameter))
 data5 <- select(df5, all_of(dens5$Parameter))
@@
 data_all <- rbind(
-  data1a, data1b, data2, data3, data6, data5, data6, data7a, data7b, data7c,
+  data1a, data1b, data2, data3, data4, data5, data6, data7a, data7b, data7c,
   mutate(data8a, Tickle = NA), 
@@
                    -Sex_arousal, -Temp)
-data6f <- select(data6, -Taste, -Affective_touch, -Vomit, -Itch,
+data4f <- select(data4, -Taste, -Affective_touch, -Vomit, -Itch,
                    -Sex_arousal, -Temp)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data1af, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data1af, n = 3, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]]))
 rez_cfa1a  <- make_cfa(data1af)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data1bf, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data1bf, n = 3, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Bruise"]], 
+                                            "F3" = colors[["Cough"]], "F4" = colors[["Itch"]]))
 rez_cfa1b  <- make_cfa(data1bf)
@@
 
-```{r}
+```{r data3}
 #| warning: false
@@
 
-```{r}
+```{r data3_details}
 #| warning: false
@@
 
-```{r}
+```{r data3f}
 #| warning: false
@@
                                             "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
-rez_cf3  <- make_cfa(data3f)
-
-rez_hclust$p / rez_ega$p / rez_efa$p
-```
-
-##### Details
-
-```{r}
+rez_cfa3  <- make_cfa(data3f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r data3f_details}
 #| warning: false
@@
 
-```{r}
+```{r data4}
 #| warning: false
@@
 
-```{r}
+```{r data4_details}
 #| warning: false
@@
 
-```{r}
+```{r data4f}
 #| warning: false
@@
 
-```{r}
+```{r data4f_details}
 #| warning: false
@@
 
-```{r}
+```{r data5}
 #| warning: false
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data5, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
-
-rez_hclust$p / rez_ega$p / rez_efa$p
-```
-
-##### Details
-
-```{r}
+rez_efa <- make_efa(data5, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Itch"]], 
+                                            "F3" = colors[["Breathing"]], "F4" = colors[["Urinate"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r data5_details}
 #| warning: false
@@
 
-```{r}
+Note: EGA errors.
+
+```{r data5f}
 #| warning: false
@@
 rez_hclust <- make_hclust(data5f)
-rez_ega <- make_ega(data5f, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data5f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+# rez_ega <- make_ega(data5f, cols = c(
+#   "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+#   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data5f, n = 5, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]],
+                                            "F5" = colors[["Urinate"]]))
 rez_cfa5  <- make_cfa(data5f)
 
-rez_hclust$p / rez_ega$p / rez_efa$p
-```
-
-##### Details
-
-```{r}
-#| warning: false
-#| message: false
-
-plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
-pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
-
-stab <- EGAnet::itemStability(rez_ega$rez)
-rez_ega$table
-
-plot(rez_efa$n_fac)
-
-rez_cf5$test
+rez_hclust$p / rez_efa$p
+```
+
+##### Details
+
+```{r data5f_details}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+plot(rez_efa$n_fac)
+
+rez_cfa5$test
 ```
@@
 
-```{r}
+```{r data6}
 #| warning: false
@@
 
-```{r}
+```{r data6_details}
 #| warning: false
@@
 
-```{r}
+```{r data6f}
 #| warning: false
@@
                                             "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
-rez_cf6  <- make_cfa(data6f)
-
-rez_hclust$p / rez_ega$p / rez_efa$p
-```
-
-##### Details
-
-```{r}
-#| warning: false
-#| message: false
-
-plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
-pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
-
-stab <- EGAnet::itemStability(rez_ega$rez)
-rez_ega$table
-
-plot(rez_efa$n_fac)
-
-rez_cf6$test
+rez_cfa6  <- make_cfa(data6f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r data6f_details}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cfa6$test
 ```
@@
 
-```{r}
+```{r data7a}
 #| warning: false
@@
 
-```{r}
+```{r data7a_details}
 #| warning: false
@@
 
-```{r}
+```{r data7af}
 #| warning: false
@@
 
-```{r}
+```{r data7af_details}
 #| warning: false
@@
 
-```{r}
+```{r data7b}
 #| warning: false
@@
 
-```{r}
+```{r data7b_details}
 #| warning: false
@@
 
-```{r}
+```{r data7bf}
 #| warning: false
@@
                                             "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
-rez_cf7b  <- make_cfa(data7bf)
-
-rez_hclust$p / rez_ega$p / rez_efa$p
-```
-
-##### Details
-
-```{r}
-#| warning: false
-#| message: false
-
-plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
-pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
-
-stab <- EGAnet::itemStability(rez_ega$rez)
-rez_ega$table
-
-plot(rez_efa$n_fac)
-
-rez_cf7b$test
+rez_cfa7b  <- make_cfa(data7bf)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r data7bf_details}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cfa7b$test
 ```
@@
 
-```{r}
+```{r data7c}
 #| warning: false
@@
 
-```{r}
+```{r data7c_details}
 #| warning: false
@@
 
-```{r}
+```{r data7cf}
 #| warning: false
@@
                                             "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
-rez_cf7c  <- make_cfa(data7cf)
-
-rez_hclust$p / rez_ega$p / rez_efa$p
-```
-
-##### Details
-
-```{r}
-#| warning: false
-#| message: false
-
-plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
-pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
-
-stab <- EGAnet::itemStability(rez_ega$rez)
-rez_ega$table
-
-plot(rez_efa$n_fac)
-
-rez_cf7c$test
+rez_cfa7c  <- make_cfa(data7cf)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r data7cf_details}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cfa7c$test
 ```
@@
 
-```{r}
+```{r data8a}
 #| warning: false
@@
 
-```{r}
-#| warning: false
-#| message: false
+```{r data8a_details}
+#| message: false
+#| warning: false
 
@@
 
-```{r}
-#| warning: false
-#| message: false
-#| fig-width: 12
-#| fig-height: 20
+```{r data8af}
+#| message: false
+#| warning: false
+#| fig-height: 20
+#| fig-width: 12
 
@@
                                             "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
-rez_cf8a  <- make_cfa(data8af)
-
-rez_hclust$p / rez_ega$p / rez_efa$p
-```
-
-##### Details
-
-```{r}
-#| warning: false
-#| message: false
-
-plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
-pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
-
-stab <- EGAnet::itemStability(rez_ega$rez)
-rez_ega$table
-
-plot(rez_efa$n_fac)
-
-rez_cf8a$test
+rez_cfa8a  <- make_cfa(data8af)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r data8af_details}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cfa8a$test
 ```
@@
 
-```{r}
+```{r data8b}
 #| warning: false
@@
 
-```{r}
+```{r data8b_details}
 #| warning: false
@@
 
-```{r}
+```{r data8bf}
 #| warning: false
@@
                                             "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
-rez_cf8b  <- make_cfa(data8bf)
-
-rez_hclust$p / rez_ega$p / rez_efa$p
-```
-
-##### Details
-
-```{r}
-#| warning: false
-#| message: false
-
-plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
-pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
-
-stab <- EGAnet::itemStability(rez_ega$rez)
-rez_ega$table
-
-plot(rez_efa$n_fac)
-
-rez_cf8b$test
+rez_cfa8b  <- make_cfa(data8bf)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r data8bf_details}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cfa8b$test
 ```
@@
 
-```{r}
+```{r data9}
 #| warning: false
@@
 
-```{r}
+```{r data9_details}
 #| warning: false
@@
 
-```{r}
+```{r data9f}
 #| warning: false
@@
                                             "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
-rez_cf9  <- make_cfa(data9f)
-
-rez_hclust$p / rez_ega$p / rez_efa$p
-```
-
-##### Details
-
-```{r}
-#| warning: false
-#| message: false
-
-plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
-pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
-
-stab <- EGAnet::itemStability(rez_ega$rez)
-rez_ega$table
-
-plot(rez_efa$n_fac)
-
-rez_cf9$test
+rez_cfa9  <- make_cfa(data9f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r data9f_details}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cfa9$test
 ```
@@
 
-```{r}
+```{r data10}
 #| warning: false
@@
 
-```{r}
+```{r data10_details}
 #| warning: false
@@
 
-```{r}
+Note: No CFA (missing items)
+
+```{r data10f}
 #| warning: false
@@
                                             "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
-rez_cf10  <- make_cfa(data10f)
-
-rez_hclust$p / rez_ega$p / rez_efa$p
-```
-
-##### Details
-
-```{r}
-#| warning: false
-#| message: false
-
-plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
-pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
-
-stab <- EGAnet::itemStability(rez_ega$rez)
-rez_ega$table
-
-plot(rez_efa$n_fac)
-
-rez_cf10$test
+# rez_cfa10  <- make_cfa(data10f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r data10f_details}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+# rez_cfa10$test
 ```
@@
 
-```{r}
+```{r data11}
 #| warning: false
@@
 
-```{r}
+```{r data11_details}
 #| warning: false
@@
 
-```{r}
+```{r data11f}
 #| warning: false
@@
                                             "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
-rez_cf11  <- make_cfa(data11f)
-
-rez_hclust$p / rez_ega$p / rez_efa$p
-```
-
-##### Details
-
-```{r}
-#| warning: false
-#| message: false
-
-plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
-pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
-
-stab <- EGAnet::itemStability(rez_ega$rez)
-rez_ega$table
-
-plot(rez_efa$n_fac)
-
-rez_cf11$test
+rez_cfa11  <- make_cfa(data11f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r data11f_details}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cfa11$test
 ```
@@
 
-```{r}
+```{r data12}
 #| warning: false
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data12, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+rez_efa <- make_efa(data12, n = 2, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
                                             "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
@@
 
-```{r}
+```{r data12_details}
 #| warning: false
@@
 
-```{r}
+Note: CFA errors.
+
+```{r data12f}
 #| warning: false
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data12f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+rez_efa <- make_efa(data12f, n = 5, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
                                              "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
-rez_cf12  <- make_cfa(data12f)
-
-rez_hclust$p / rez_ega$p / rez_efa$p
-```
-
-##### Details
-
-```{r}
-#| warning: false
-#| message: false
-
-plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
-pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
-
-stab <- EGAnet::itemStability(rez_ega$rez)
-rez_ega$table
-
-plot(rez_efa$n_fac)
-
-rez_cf12$test
+# rez_cfa12  <- make_cfa(data12f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r data12f_details}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+# rez_cfa12$test
 ```
@@
 
-```{r}
+```{r data13}
 #| warning: false
@@
 
-```{r}
+```{r data13_details}
 #| warning: false
@@
 
-```{r}
+```{r data13f}
 #| warning: false
@@
                                             "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
-rez_cf13  <- make_cfa(data13f)
-
-rez_hclust$p / rez_ega$p / rez_efa$p
-```
-
-##### Details
-
-```{r}
-#| warning: false
-#| message: false
-
-plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
-pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
-
-stab <- EGAnet::itemStability(rez_ega$rez)
-rez_ega$table
-
-plot(rez_efa$n_fac)
-
-rez_cf13$test
+rez_cfa13  <- make_cfa(data13f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r data13f_details}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cfa13$test
 ```
@@
 
-```{r}
+```{r data14}
 #| warning: false
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data14, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+rez_efa <- make_efa(data14, n = 3, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
                                             "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
@@
 
-```{r}
+```{r data14_details}
 #| warning: false
@@
 
-```{r}
+```{r data14f}
 #| warning: false
@@
                                              "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
-rez_cf14  <- make_cfa(data14f)
-
-rez_hclust$p / rez_ega$p / rez_efa$p
-```
-
-##### Details
-
-```{r}
-#| warning: false
-#| message: false
-
-plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
-pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
-
-stab <- EGAnet::itemStability(rez_ega$rez)
-rez_ega$table
-
-plot(rez_efa$n_fac)
-
-rez_cf14$test
+rez_cfa14  <- make_cfa(data14f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r data14f_details}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cfa14$test
 ```
@@
 
-```{r}
+```{r data15}
 #| warning: false
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data15, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+rez_efa <- make_efa(data15, n = 3, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
                                             "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
@@
 
-```{r}
+```{r data15_details}
 #| warning: false
@@
 
-```{r}
+```{r data15f}
 #| warning: false
@@
                                             "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
-rez_cf15  <- make_cfa(data15f)
-
-rez_hclust$p / rez_ega$p / rez_efa$p
-```
-
-##### Details
-
-```{r}
-#| warning: false
-#| message: false
-
-plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
-pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
-
-stab <- EGAnet::itemStability(rez_ega$rez)
-rez_ega$table
-
-plot(rez_efa$n_fac)
-
-rez_cf15$test
-```
-::::
-
-## Model Performance
-
-```{r}
-#| warning: false
-
-rbind(
-  mutate(rez_cfa0$perf, Sample = "All Samples"),
-  mutate(rez_cfa1a$perf, Sample = "Sample 1a"),
-  mutate(rez_cfa1b$perf, Sample = "Sample 1b"),
-  mutate(rez_cfa2$perf, Sample = "Sample 2"),
-  mutate(rez_cfa3$perf, Sample = "Sample 3"),
-  mutate(rez_cfa4$perf, Sample = "Sample 4"),
-  mutate(rez_cfa5$perf, Sample = "Sample 5"),
-  mutate(rez_cfa6$perf, Sample = "Sample 6"),
-  mutate(rez_cfa7a$perf, Sample = "Sample 7a"),
-  mutate(rez_cfa7b$perf, Sample = "Sample 7b"),
-  mutate(rez_cfa7c$perf, Sample = "Sample 7c"),
-  mutate(rez_cfa8a$perf, Sample = "Sample 8a"),
-  mutate(rez_cfa8b$perf, Sample = "Sample 8b"),
-  mutate(rez_cfa9$perf, Sample = "Sample 9"),
-  mutate(rez_cfa10$perf, Sample = "Sample 10"),
-  mutate(rez_cfa11$perf, Sample = "Sample 11"),
-  mutate(rez_cfa12$perf, Sample = "Sample 12"),
-  mutate(rez_cfa13$perf, Sample = "Sample 13"),
-  mutate(rez_cfa14$perf, Sample = "Sample 14"),
-  mutate(rez_cfa15$perf, Sample = "Sample 15")
-) |> 
-  select(Sample, Chi2, RMSEA, CFI, "SRMR") 
-```
+rez_cfa15  <- make_cfa(data15f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r data15f_details}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cfa15$test
+```
+::::
 
@@
 #| warning: false
+#| eval: true
 
@@
   sample3 = add_empirical(data3, "Sample 3"),
-  sample4 = add_empirical(data6, "Sample 4"),
+  sample4 = add_empirical(data4, "Sample 4"),
   sample5 = add_empirical(data5, "Sample 5"),

### 2025-08-10 analysis/study2.qmd
typos

@@
 df12 <- cbind(data$df12, scores$sample12)
-df13 <- cbind(data$df13, scores$sample12)
+df13 <- cbind(data$df13, scores$sample13)
 df14 <- cbind(data$df14, scores$sample14)
@@
 
-pool_coef <- function(with = "Age", component = "Demographic", standardize="within") {
+pool_coef <- function(with = "Age", component = "Demographic", name = with, unequalrange=FALSE) {
   rez <- data.frame()
@@
         d <- dataset[c(with, intero, "Sample")]
-        if(standardize == "within") d <- standardize(d)
         data <- rbind(data, d)
@@
 
-    if(standardize == "between") {
+    # Make sure that min-max of "with" is the equal across all samples
+    check <- summarize(data, 
+                       min = min(!!sym(with), na.rm = TRUE),  
+                       max = max(!!sym(with), na.rm = TRUE), .by = "Sample")
+    if (with != "Gender" && (any(check$min != min(check$min)) || any(check$max != max(check$max)))) {
+      if(unequalrange == FALSE) {
+        print(check)
+        stop(paste0("The range of '", with, "' is not equal across samples."))
+      }
+    }
+
     data <- standardize(data[complete.cases(data), ])
-    }
 
@@
     } else {
-      f <- as.formula(paste0(with, "~", intero, " + (", intero, "|Sample)"))
-      f2 <- as.formula(paste0(with, "~", intero, " + (1|Sample)"))
+      f <- as.formula(paste0(intero, "~", with, " + (", with, "|Sample)"))
+      f2 <- as.formula(paste0(intero, "~", with, " + (1|Sample)"))
     }
@@
     out$Component <- component
-    out$Method <- standardize
     out$Type <- type
     out$Converged <- insight::is_converged(m)
+    out$N <- nrow(data)
     rez <- rbind(rez, out)
@@
   }
+  rez$var_Correlate <- name
   rez
@@
 
-make_rez <- function(with = "Gender", component = "Demographic", name = with) {
-  d <- rbind(
-    pool_coef(with = with, component = component, standardize="within"),
-    pool_coef(with = with, component = component, standardize="between")) 
-  d$var_Correlate <- name
-  d
-}
-
-data <- make_rez(with = "Gender", component = "Demographic", name = "Gender (Female - Male)")
+data <- pool_coef(with = "Gender", component = "Demographic", name = "Gender (Female - Male)")
 ```
@@
 
-data <- rbind(data, make_rez(with = "Age", component = "Demographic"))
+data <- rbind(data, pool_coef(with = "Age", component = "Demographic", unequalrange=TRUE))
 ```
@@
   data,
-  make_rez(with = "MAIA_AttentionReg", component = "MAIA", name = "Attention Regulation"),
-  make_rez(with = "MAIA_BodyListening", component = "MAIA", name = "Listening"),
-  make_rez(with = "MAIA_BodyTrusting", component = "MAIA", name = "Trusting"),
-  make_rez(with = "MAIA_EmoAwareness", component = "MAIA", name = "Emotional Awareness"),
-  make_rez(with = "MAIA_NotDistracting", component = "MAIA", name = "Not Distracting"),
-  make_rez(with = "MAIA_Noticing", component = "MAIA", name = "Noticing"),
-  make_rez(with = "MAIA_NotWorrying", component = "MAIA", name = "Not Worrying"),
-  make_rez(with = "MAIA_SelfReg", component = "MAIA", name = "Self Regulation"),
-  make_rez(with = "MAIA_Trusting", component = "MAIA", name = "Trusting")
+  pool_coef(with = "MAIA_AttentionReg", component = "MAIA", name = "Attention Regulation", unequalrange=TRUE),
+  pool_coef(with = "MAIA_BodyListening", component = "MAIA", name = "Listening", unequalrange=TRUE),
+  pool_coef(with = "MAIA_Trusting", component = "MAIA", name = "Trusting", unequalrange=TRUE),
+  pool_coef(with = "MAIA_EmoAwareness", component = "MAIA", name = "Emotional Awareness", unequalrange=TRUE),
+  pool_coef(with = "MAIA_NotDistracting", component = "MAIA", name = "Not Distracting", unequalrange=TRUE),
+  pool_coef(with = "MAIA_Noticing", component = "MAIA", name = "Noticing", unequalrange=TRUE),
+  pool_coef(with = "MAIA_NotWorrying", component = "MAIA", name = "Not Worrying", unequalrange=TRUE),
+  pool_coef(with = "MAIA_SelfReg", component = "MAIA", name = "Self Regulation", unequalrange=TRUE)
 )
-
 ```
@@
 p <- data |>
-  filter(Method == "within") |> 
   mutate(sig = ifelse(p < .01, "p < .01", ifelse(p < .001, "p < .001", "N.S.")),
@@
   geom_hline(yintercept = 0, linetype = "dashed") +
-  geom_point2(aes(y=r, color = dir, alpha = sig), size = 3) +
-  geom_linerange(aes(color = dir, alpha = sig, ymin = CI_low, ymax = CI_high), linewidth = 2) +
-  # geom_bar(aes(fill=Sample, alpha=sig, y=r, group=Sample), stat="identity", position = position_dodge2(width = 0.8)) +
+  # geom_point2(aes(y=r, color = dir, alpha = sig), size = 3) +
+  geom_linerange(aes(color=dir, alpha=sig, ymax=r, ymin=0), linewidth = 1) +
+  geom_linerange(aes(color = dir, alpha = sig, ymin = CI_low, ymax = CI_high, linewidth = log(N))) +
   # geom_linerange(aes(color=dir, alpha=sig, ymin=0, ymax=r, group=Sample), position = position_dodge2(width = 0.7), linewidth=2.5) +
@@
   scale_y_continuous(expand = c(0, 0), breaks = c(-0.3, 0, 0.3)) +
-  coord_flip(ylim = c(-0.5, 0.5)) +
+  scale_linewidth_continuous(range = c(3, 7), guide = "none") +
+  coord_flip(ylim = c(-0.35, 0.35)) +
   theme_modern(axis.title.space = 5) +

### 2025-08-10 analysis/Study1.qmd
more

@@
     MAIA_NotDistracting=MAIA_NotDistracting, MAIA_NotWorrying=MAIA_NotWorrying,
-    MAIA_SelfRegulation=MAIA_SelfReg, MAIA_Noticing=MAIA_Noticing)
+    MAIA_SelfRegulation=MAIA_SelfReg, MAIA_Noticing=MAIA_Noticing,
+    BPQ_BodyAwareness = BPQ_A, BPQ_AutonomicReactivity = BPQ_R)
 rm(data)

### 2025-08-10 analysis/study2.qmd
more

@@
 
-data <- rbind(data, make_rez(with = "ICQ", component="ICQ", name = "ICQ"))
+data <- rbind(data, pool_coef(with = "ICQ", component="ICQ", name = "ICQ", unequalrange=TRUE))
 ```
@@
   data,
-  make_rez(with = "BPQ_A", component="BPQ", name = "Body Awareness (BPQ)"),
-  make_rez(with = "BPQ_R", component="BPQ", name = "Autonomic Reactivity (BPQ)"),
-  make_rez(with = "BPQ_BodyAwareness", component="BPQ", name = "Body Awareness (BPQ)"),
-  make_rez(with = "BPQ_AutonomicReactivity", component="BPQ", name = "Autonomic Reactivity (BPQ)")
+  # pool_coef(with = "BPQ_A", component="BPQ", name = "Body Awareness (BPQ)"),
+  # pool_coef(with = "BPQ_R", component="BPQ", name = "Autonomic Reactivity (BPQ)"),
+  pool_coef(with = "BPQ_BodyAwareness", component="BPQ", name = "Body Awareness (BPQ)"),
+  pool_coef(with = "BPQ_AutonomicReactivity", component="BPQ", name = "Autonomic Reactivity (BPQ)")
   )
@@
          #   "Schizotypic", "Autistic", "Personality", "Conspiracy Beliefs", "World Beliefs", "Lying Profile")) |>
-  ggplot(aes(x = var_Correlate)) +
-  geom_hline(yintercept = 0, linetype = "dashed") +
+  ggplot(aes(y = var_Correlate)) +
+  annotate(geom = "rect", xmin = -0.1, xmax = 0.1, ymin = -Inf, ymax=Inf, fill = "#FFF8E1") +
+  annotate(geom = "rect", xmin = c(-0.3, 0.1), xmax = c(-0.1, 0.3), ymin = -Inf, ymax=Inf, fill = "#F1F8E9") +
+  annotate(geom = "rect", xmin = c(-0.6, 0.3), xmax = c(-0.3, 0.6), ymin = -Inf, ymax=Inf, fill = "#E8F5E9") +
+  geom_vline(xintercept = 0, linetype = "dashed") +
   # geom_point2(aes(y=r, color = dir, alpha = sig), size = 3) +
-  geom_linerange(aes(color=dir, alpha=sig, ymax=r, ymin=0), linewidth = 1) +
-  geom_linerange(aes(color = dir, alpha = sig, ymin = CI_low, ymax = CI_high, linewidth = log(N))) +
+  geom_linerange(aes(color=dir, alpha=sig, xmax=r, xmin=0), linewidth = 1) +
+  geom_linerange(aes(color = dir, alpha = sig, xmin = CI_low, xmax = CI_high, linewidth = log(N))) +
   # geom_linerange(aes(color=dir, alpha=sig, ymin=0, ymax=r, group=Sample), position = position_dodge2(width = 0.7), linewidth=2.5) +
@@
   #                linewidth = 1) +
-  facet_grid(Component ~ var_Interoception, scales = "free_y", switch = "y") +
+  facet_grid(Component ~ var_Interoception, scales = "free", space ="free", switch = "y") +
   scale_fill_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
@@
   scale_alpha_discrete(range = c(0.2, 0.9), guide = "none") +
-  scale_y_continuous(expand = c(0, 0), breaks = c(-0.3, 0, 0.3)) +
+  scale_x_continuous(expand = c(0, 0), breaks = c(-0.3, 0, 0.3)) +
   scale_linewidth_continuous(range = c(3, 7), guide = "none") +
-  coord_flip(ylim = c(-0.35, 0.35)) +
+  coord_cartesian(xlim = c(-0.4, 0.4)) +
   theme_modern(axis.title.space = 5) +
-  labs(y = "Strength of Association (std. Beta)") +
+  labs(x = "Strength of Association (std. Beta)") +
   theme(panel.grid.major.y = element_line(),

### 2025-08-12 analysis/Study1.qmd
added data + updated dimensions/columns across samples

--- 2025-08-10 analysis/Study1.qmd
@@
     Affective_touch = `IAS 19`, Tickle = `IAS 20`, Itch = `IAS 21`,
-    MAIA_AttentionRegulation = MAIA_AttentionReg, MAIA_BodyListening = MAIA_BodyListening,
-    MAIA_Trusting = MAIA_BodyTrusting, MAIA_EmotionalAwareness = MAIA_EmoAwareness,
-    MAIA_NotDistracting=MAIA_NotDistracting, MAIA_NotWorrying=MAIA_NotWorrying,
-    MAIA_SelfRegulation=MAIA_SelfReg, MAIA_Noticing=MAIA_Noticing)
+    MAIA_Trusting = MAIA_BodyTrusting,
+    BPQ_BodyAwareness = BPQ_A, BPQ_AutonomicReactivity = BPQ_R)
 rm(data)
@@
     Muscles = IAS15, Bruise = IAS16, Pain = IAS17, Blood_Sugar = IAS18,
-    Affective_touch = IAS19, Tickle = IAS20, Itch = IAS21
+    Affective_touch = IAS19, Tickle = IAS20, Itch = IAS21,
+    TAS_EOT = TAS_ExternallyOrientedThinking, TAS_DIF = TAS_IdentifyingFeelings, TAS_DDF = TAS_DescribingFeelings
   )
@@
   - MAIA does not include items for not-worrying and not-distracting 
+  - BPQ 26 - body awareness
 
@@
 df4$MAIA_Noticing <- rowMeans(select(df4, starts_with("MAIA_NT")), na.rm = TRUE)
+
+df4$BPQ_BodyAwareness <- rowMeans(select(df4, starts_with("BPQ")), na.rm = TRUE)
 ```
@@
     Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
-    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
+    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
+    PHQ2_Sum= PHQ2_sum,
+    GAD2_Sum = GAD2_sum
   )
@@
     MAIA_SelfReg = MAIA_SELF_REGULATION, MAIA_BodyListening = MAIA_BODY_LISTENING,
-    MAIA_Trusting = MAIA_TRUSTING, MAIA_EmoAwareness = MAIA_EMOTIONAL_AWARENESS
+    MAIA_Trusting = MAIA_TRUSTING, MAIA_EmoAwareness = MAIA_EMOTIONAL_AWARENESS,
+    STAIT_Sum = STAI_T_Sumscore
   ) |> 
@@
     MAIA_SelfReg = maiaSelfRegulation, MAIA_BodyListening = maiaBodyListening,
-    MAIA_Trusting = maiaTrusting, MAIA_EmoAwareness = maiaEmotionalAwareness
+    MAIA_Trusting = maiaTrusting, MAIA_EmoAwareness = maiaEmotionalAwareness,
+    BPQ_BodyAwareness =BPQ_Sum
+
   ) |> 
@@
     MAIA_Trusting = MAIA_trust, MAIA_EmoAwareness = MAIA_emoaw,
-    ICQ = ICQ_sum
+    ICQ = ICQ_sum,
+    STAIT_Sum = STAIT_sum
   ) |> 
@@
 
+df8a$BPQ_BodyAwareness <- rowMeans(select(df8a, starts_with("BPQ")), na.rm = TRUE)
+
 df8b <- haven::read_sav("../data/Lin2023/Study 2.sav") |>
@@
     Muscles = MUSCL, Bruise = Bruis, Pain = PAIN, Blood_Sugar = BloSu,
-    Affective_touch = Touch, Itch = ITCH)
+    Affective_touch = Touch, Itch = ITCH,
+    PHQ15_Sum = PHQ15_sum,
+    PHQ9_Sum = PHQ9_sum)
 ```
@@
     Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
+  ) |>
+  mutate(
+    BFI_NEUROTICISM = (BFI_1 + BFI_2 + BFI_3)/3,
+    BFI_AGREEABLENESS = (BFI_10R + BFI_11 + BFI_12)/3,
+    BFI_EXTROVERSION = (BFI_4 + BFI_5 + BFI_6),
+    BFI_CONSCIENTIOUSNESS = (BFI_13 + BFI_14 + BFI_15R)/3,
+    BFI_OPENNESS = (BFI_7 + BFI_8 + BFI_9)/3
     )
@@
     Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
-    typeSample = Sample
+    typeSample = Sample,
+    STAIT_Sum = STAI5_General,
+    BDI_Sum = BDI2_Total
   ) |>
@@
 df13$MAIA_Trusting<- rowMeans(select(df13 , starts_with("MAIA_Trusting")))
+
+df13$PHQ4_Depression <- (df13$PHQ4_Depression_4 + df13$PHQ4_Depression_3)/2
+df13$PHQ4_Anxiety <- (df13$PHQ4_Anxiety_2 + df13$PHQ4_Anxiety_1)/2
 ```
@@
     Affective_touch = IAS_ACC_19, Tickle =IAS_ACC_21, Itch = IAS_ACC_22,
-    MAIA_EmoAwareness =MAIA_Emotional, MAIA_SelfReg = MAIA_SelfRegulation, MAIA_AttentionReg = MAIA_Attention
+    MAIA_EmoAwareness =MAIA_Emotional, MAIA_SelfReg = MAIA_SelfRegulation, MAIA_AttentionReg = MAIA_Attention,
+    STAIT_Sum = ANX
   ) |>
@@
     Gender %in% c(3, 5) ~ "Other",
-    Gender == 4 ~ "NA"
-  )) |> ## compute dimensions for the TAS
-  mutate(TAS_DIF = TAS20_1 + TAS20_3 + TAS20_6 + TAS20_7 + TAS20_9 + TAS20_13 + TAS20_14,
+    Gender == 4 ~ "NA"),
+    TAS_DIF = TAS20_1 + TAS20_3 + TAS20_6 + TAS20_7 + TAS20_9 + TAS20_13 + TAS20_14,
     TAS_DDF = TAS20_2 + (1-TAS20_4) + TAS20_11 + TAS20_12 + TAS20_17,
@@
   na.omit()
+```
+
+### Sample 16
+
+- Raquel Arjona and Robyn Scharte data
+
+```{r}
+
+df16 <- read.csv("../data/Scharte2025/data_IAS_rs.csv") |>
+  rename(Age= age, Gender = gender_identity,
+         Heart = ias1, Hungry = ias2, Breathing = ias3, Thirsty = ias4, Urinate = ias5, 
+         Defecate=ias6, Taste = ias7,Vomit = ias8, Sneeze = ias9, Cough = ias10, 
+         Temp = ias11, Sex_arousal = ias12, Wind = ias13, Burp = ias14,Muscles = ias15, 
+         Bruise = ias16, Pain = ias17, Blood_Sugar = ias18, Affective_touch = ias19, 
+         Tickle =ias20, Itch = ias21,
+         ) |>
+  mutate(Gender = case_when(
+    Gender == "1" ~ "Male",
+    Gender == 2 ~ "Female",
+    Gender %in% c(3, 4, 5) ~ "Other",
+    Gender == 6 ~ "NA"),
+    MAIA_Noticing = (maia1 + maia2 + maia3 + maia4)/4,
+    MAIA_NotDistracting = (maia5_rev + maia6_rev + maia7_rev +maia8_rev + maia9_rev + maia10_rev)/6, 
+    MAIA_NotWorrying = (maia11_rev +maia12_rev  + maia13)/3,
+    MAIA_AttentionReg = (maia16 + maia17 + maia18 + maia19 + maia20 + maia21 + maia22)/7,
+    MAIA_EmoAwareness = (maia23 + maia24 + maia25 + maia26 +maia27)/5,
+    MAIA_SelfReg = (maia28 + maia29 + maia30 + maia31)/4,
+    MAIA_BodyListening = (maia32 + maia33 +maia34)/3,
+    MAIA_Trusting = (maia35 + maia36 + maia37)/3 ,
+    GAD7_Sum = rowSums(across(starts_with("gad1_")), na.rm = TRUE),
+    PHQ9_Sum = rowSums(across(starts_with("phq1_")), na.rm = TRUE))
+
 ```

### 2025-08-12 analysis/study2.qmd
added data + updated dimensions/columns across samples

@@
 
-  #df3
-  make_rez(with = "TAS_DescribingFeelings", component="Alexithymia", name = "Difficulties Describing Feelings (TAS)"),
-  make_rez(with = "TAS_IdentifyingFeelings", component="Alexithymia", name ="Difficulties Identifying Feelings (TAS)"), 
-  make_rez(with = "TAS_ExternallyOrientedThinking", component="Alexithymia", name = "External Thinking (TAS)"), 
   make_rez(with = "TAS_des", component="Alexithymia", name = "Difficulties Describing Feelings (TAS)"), 
@@
   data,
-  make_rez(with = "PHQ2_sum", component="Mood", name = "Depression (PHQ-2)"),
+  make_rez(with = "PHQ2_Sum", component="Mood", name = "Depression (PHQ-2)"),
   make_rez(with = "PHQ15_Sum", component="Mood", name = "Somatic Concerns (PHQ-15)"), 
   make_rez(with = "PHQ9_Sum", component="Mood", name = "Depression (PHQ-9)"), 
-  make_rez(with = "BDI_sum", component="Mood", name = "Depression (BDI)"), 
-  make_rez(with = "PHQ15_sum", component="Mood", name = "Somatic Concerns (PHQ-15)"), 
-  make_rez(with = "PHQ9_sum", component="Mood", name = "Depression (PHQ-9)"), 
+  make_rez(with = "BDI_Sum", component="Mood", name = "Depression (BDI)"), 
   make_rez(with = "PHQ4_Depression", component="Mood", name = "Depression (PHQ-2)"),
-  make_rez(with = "BDI2_Total", component="Mood", name = "Depression (BDI)"),
   make_cor(with = "DEP", component = "Mood", name = "Depression (MFQ)")
@@
 # names(df7c)[str_detect(names(df7c), "STAI")]
+# names(df10)[]
 # names(df11)[str_detect(names(df11), "STAI")] 
@@
   data,
-  make_rez(with = "GAD2_sum", component="Mood", name = "Anxiety (GAD-2)"), 
-  make_rez(with = "STAI_T_Sumscore", component="Mood", name= "Anxiety (STAI-T)"), 
+  make_rez(with = "GAD2_Sum", component="Mood", name = "Anxiety (GAD-2)"), 
   make_rez(with = "STAIT_Sum", component="Mood", name = "Anxiety (STAI-T)"), 
-  make_rez(with = "STAIT_sum", component="Mood", name = "Anxiety (STAI-T)"),
-  make_rez(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (GAD-2)"),
-  make_rez(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (STAI-5)"), 
-  make_rez(with = "STAI5_General", component="Mood", name = "Anxiety (STAI-T)"),
-  make_rez(with =  "ANX", component = "Mood", name = "Anxiety (STAI-T)")
+  make_rez(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (PHQ-4)"),
+  # make_rez(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (STAI-5)"),
+  make_rez(with = "GAD7_Sum", component="Mood", name = "Anxiety (GAD-9)")
 )

### 2025-08-12 analysis/Study1.qmd
cleaned data

@@
 df16 <- read.csv("../data/Scharte2025/data_IAS_rs.csv") |>
-  rename(Age= age, Gender = gender_identity,
+  rename(Age= age, Gender = gender_identity, Education = education,
          Heart = ias1, Hungry = ias2, Breathing = ias3, Thirsty = ias4, Urinate = ias5, 
@@
          Tickle =ias20, Itch = ias21,
+         GAD2_Sum = gad2,
+         PHQ2_Sum = phq2
          ) |>
   mutate(Gender = case_when(
-    Gender == "1" ~ "Male",
+    Gender == 1 ~ "Male",
     Gender == 2 ~ "Female",
@@
     Gender == 6 ~ "NA"),
+    Education = case_when(
+      Education == 6 ~ "Bachelor",
+      Education == 7 ~ "Master",
+      Education == 8 ~ "Doctorate",
+      Education == 2 | Education == 3 ~ "High School", # GCSE + A-levels (16-18 years old)
+      Education == 4 | Education == 5 ~ "Other",       # NVQ and foundation year
+      Education == 1 ~ "No education"),
     MAIA_Noticing = (maia1 + maia2 + maia3 + maia4)/4,
@@
     GAD7_Sum = rowSums(across(starts_with("gad1_")), na.rm = TRUE),
-    PHQ9_Sum = rowSums(across(starts_with("phq1_")), na.rm = TRUE))
+    PHQ9_Sum = rowSums(across(starts_with("phq1_")), na.rm = TRUE)) |>
+  filter (!Age == 2004.00, !Age == 1999.00, # misreported age
+          att == 2) # only those that select 'no' the attention check
 
@@
 # Save all
-data <- list(df1a=df1a, df1b=df1b, df2=df2, df3=df3, df4=df4, df5=df5, df6=df6, df7a=df7a, df7b=df7b, df7c=df7c, df8a=df8a, df8b=df8b, df9=df9, df10=df10, df11 =df11 , df12 =df12 , df13  = df13 , df14 =df14 , df15  =df15)
+data <- list(df1a=df1a, df1b=df1b, df2=df2, df3=df3, df4=df4, df5=df5, df6=df6, df7a=df7a, df7b=df7b, df7c=df7c, df8a=df8a, df8b=df8b, df9=df9, df10=df10, df11 =df11 , df12 =df12 , df13  = df13 , df14 =df14 , df15  =df15, df16 = df16)
 save(data, file = "../data/data.RData")
@@
 - **Sample 15 **: Data from [Poreiro's] study , included `r report::report_participants(df15 , age = "Age", sex = NA, gender = "Gender")`
+- **Sample 16 **: Data from [Poreiro's] study , included `r report::report_participants(df16 , age = "Age", gender = "Gender")`
 

### 2025-08-12 analysis/Study1.qmd
added sample 16 + computed BPQ dimensions

@@
     MAIA_Trusting = maiaTrusting, MAIA_EmoAwareness = maiaEmotionalAwareness,
-    BPQ_BodyAwareness =BPQ_Sum
-
-  ) |> 
+    BPQ_BodyAwareness =BPQ_Sum) |> 
   mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5), range = c(1, 5)))) # Original scale 1-5
@@
 
-Total N = `r nrow(df1a) + nrow(df1b) + nrow(df2) + nrow(df3) + nrow(df4) + nrow(df5) + nrow(df6) + nrow(df7a) + nrow(df7b) + nrow(df7c) + nrow(df8a) + nrow(df8b) + nrow(df9) + nrow(df10) + nrow(df11) + nrow(df12) + nrow(df13) + nrow(df14) + nrow(df15)`.
+Total N = `r nrow(df1a) + nrow(df1b) + nrow(df2) + nrow(df3) + nrow(df4) + nrow(df5) + nrow(df6) + nrow(df7a) + nrow(df7b) + nrow(df7c) + nrow(df8a) + nrow(df8b) + nrow(df9) + nrow(df10) + nrow(df11) + nrow(df12) + nrow(df13) + nrow(df14) + nrow(df15) +nrow(df16)`.
 
@@
 desc_df15 <- desc(df15)
-
-desc_total <- rbind(desc_df1a, desc_df1b, desc_df2, desc_df3, desc_df5, desc_df6, desc_df7a, desc_df7b, desc_df7c, desc_df8a, desc_df8b, desc_df9, desc_df10, desc_df11 , desc_df12 , desc_df13 , desc_df14 , desc_df15 )
+desc_df16 <- desc(df16)
+
+desc_total <- rbind(desc_df1a, desc_df1b, desc_df2, desc_df3, desc_df5, desc_df6, desc_df7a, desc_df7b, desc_df7c, desc_df8a, desc_df8b, desc_df9, desc_df10, desc_df11 , desc_df12 , desc_df13 , desc_df14 , desc_df15, desc_df16)
 
@@
   mutate(Sample = "Sample 15")
-
-p1_data <- rbind(dens1a, dens1b, dens2, dens3, dens4, dens5, dens6, dens7a, dens7b, dens7c, dens8a, dens8b, dens9, dens10, dens11 , dens12, dens13, dens14, dens15)
+dens16  <- estimate_density(select(df16, all_of(ias_vars)), method = "kernSmooth") |>
+  mutate(Sample = "Sample 16")
+
+p1_data <- rbind(dens1a, dens1b, dens2, dens3, dens4, dens5, dens6, dens7a, dens7b, dens7c, dens8a, dens8b, dens9, dens10, dens11 , dens12, dens13, dens14, dens15, dens16)
 
@@
 data15   <- select(df15, all_of(dens15$Parameter))
+data16   <- select(df16, all_of(dens16$Parameter))
 
@@
   mutate(data10, Taste = NA, Cough = NA, Blood_Sugar = NA),  
-  data11,  data12 , data13, data14, data15  
+  data11,  data12 , data13, data14, data15, data16  
 ) 
@@
 
+#### Sample 16
+
+```{r}
+make_correlation(data16)
+```
+
 :::
@@
 ```{r}
-uva14  <- EGAnet::UVA(data = data14 , cut.off = 0.3)
+uva14  <- EGAnet::UVA(data = data14, cut.off = 0.3)
 uva14 
@@
 ```{r}
-uva15   <- EGAnet::UVA(data = data15  , cut.off = 0.3)
+uva15   <- EGAnet::UVA(data = data15, cut.off = 0.3)
 uva15  
 uva15$keep_remove
+```
+
+#### Sample 16
+
+```{r}
+uva16  <- EGAnet::UVA(data = data16, cut.off = 0.3)
+uva16  
+uva16$keep_remove
 ```
@@
   uva10$keep_remove$remove,
-  uva11 $keep_remove$remove,
-  uva12 $keep_remove$remove,
-  uva13 $keep_remove$remove,
-  uva14 $keep_remove$remove,
-  uva15  $keep_remove$remove)
+  uva11$keep_remove$remove,
+  uva12$keep_remove$remove,
+  uva13$keep_remove$remove,
+  uva14$keep_remove$remove,
+  uva15$keep_remove$remove,
+  uva16$keep_remove$remove)
 
@@
 data15 <- select(data15 , -Tickle)
+data16 <- select(data16 , -Tickle)
 ```
@@
                    -Sex_arousal, -Temp)
+data16f <- select(data16, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
 ```
@@
 
+### Sample 16
+
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data16)
+rez_ega <- make_ega(data16, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data16, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data16f)
+rez_ega <- make_ega(data16f, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data16f, n = 3, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Heart"]]))
+rez_cfa16  <- make_cfa(data16f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cfa16$test
+```
+
+::::
+
 ## Scores

### 2025-08-12 analysis/Study1.qmd
started changing colours for EGA

@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data2, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data2, n = 4, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Bruise"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Sex arousal"]]))
 
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data2f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data2f, n = 3, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Bruise"]], 
+                                            "F3" = colors[["Hungry"]]))
 rez_cfa2  <- make_cfa(data2f)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data3, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data3, n = 3, cols = c("F1" = colors[["Sneeze"]], "F2" = colors[["Hungry"]], 
+                                            "F3" = colors[["Blood Sugar"]]))
 
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data3f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data3f, n = 3, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Hungry"]], 
+                                            "F3" = colors[["Blood Sugar"]]))
 rez_cfa3  <- make_cfa(data3f)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data4, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data4, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Itch"]], 
+                                            "F3" = colors[["Breathing"]], "F4" = colors[["Urinate"]]))
 
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data4f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data4f, n = 3, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Breathing"]], 
+                                            "F3" = colors[["Urinate"]]))
 rez_cf4  <- make_cfa(data4f)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data5, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Itch"]], 
-                                            "F3" = colors[["Breathing"]], "F4" = colors[["Urinate"]]))
+rez_efa <- make_efa(data5, n = 8, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Itch"]], 
+                                            "F3" = colors[["Breathing"]], "F4" = colors[["Urinate"]], "F5" = colors[["Burp"]], "F6" = colors[["Taste"]], "F7" = colors[["Heart"]], "F8" = colors[["Vomit"]]))
 

### 2025-08-13 analysis/Study1.qmd
changes rest of dimensions/ variable names

@@
     ICQ = ICQ_sum,
-    STAIT_Sum = STAIT_sum
+    STAIT_Sum = STAIT_sum,
+    TAS_DIF = TAS_ident, TAS_EOT = TAS_ext, TAS_DDF = TAS_des,
+    BPQ_BodyAwareness = BPQ_sum
   ) |> 
@@
     MAIA_EmoAwareness = MAIA_EmotionalAwareness, MAIA_AttentionReg = MAIA_AttentionRegulation,
-    MAIA_SelfReg = MAIA_SelfRegulation
+    MAIA_SelfReg = MAIA_SelfRegulation,
   ) |>
@@
 df13$PHQ4_Anxiety <- (df13$PHQ4_Anxiety_2 + df13$PHQ4_Anxiety_1)/2
+
 ```
@@
          Tickle =ias20, Itch = ias21,
-         GAD2_Sum = gad2,
-         PHQ2_Sum = phq2
          ) |>

### 2025-08-13 analysis/study2.qmd
changes rest of dimensions/ variable names

@@
   data,
-  # pool_coef(with = "BPQ_A", component="BPQ", name = "Body Awareness (BPQ)"),
-  # pool_coef(with = "BPQ_R", component="BPQ", name = "Autonomic Reactivity (BPQ)"),
   pool_coef(with = "BPQ_BodyAwareness", component="BPQ", name = "Body Awareness (BPQ)"),
@@
   make_rez(with = "TAS_EOT", component="Alexithymia", name = "External Thinking (TAS)"),
-
-  make_rez(with = "TAS_des", component="Alexithymia", name = "Difficulties Describing Feelings (TAS)"), 
-  make_rez(with = "TAS_ident", component="Alexithymia", name = "Difficulties Identifying Feelings (TAS)"), 
-  make_rez(with = "TAS_ext", component="Alexithymia", name = "External Thinking (TAS)"), 
-  make_rez(with = "TAS_DIF", component="Alexithymia", name = "Difficulties Identifying Feelings (TAS)"), 
   make_rez(with = "BVAQ_Affective", component="Alexithymia", name = "Affective (BVAQ)"), 
@@
   make_rez(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (PHQ-4)"),
-  # make_rez(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (STAI-5)"),
-  make_rez(with = "GAD7_Sum", component="Mood", name = "Anxiety (GAD-9)")
+  make_rez(with = "GAD7_Sum", component="Mood", name = "Anxiety (GAD-7)")
 )

### 2025-08-13 analysis/Study1.qmd
updated ranges from scales

@@
     BPQ_BodyAwareness =BPQ_Sum) |> 
-  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5), range = c(1, 5)))) # Original scale 1-5
+  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5), range = c(1, 5))),# Original scale 1-5
+         across(starts_with("PHQ15_"), \(x) datawizard::rescale(x, to = c(0,2), range =c(1,3))),
+          across(starts_with("PHQ9_"), \(x) datawizard::rescale(x, to = c(0,3), range =c(1,4))))
 
@@
   filter(!is.na(Urinate)) |> 
-  datawizard::rescale(select=ias_vars, to = c(0, 5), range = c(0, 1)) |> 
+  datawizard::rescale(select=ias_vars, to = c(1, 5), range = c(0, 1)) |> 
   mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5)))) 
@@
     typeSample = Sample,
-    STAIT_Sum = STAI5_General,
     BDI_Sum = BDI2_Total
@@
     MAIA2_NotWorrying_5_R = 1 - MAIA2_NotWorrying_5_R) |> 
-  datawizard::rescale(select=ias_vars, to = c(0, 5), range = c(0, 1))
+  mutate(across(starts_with("MAIA2_"), \(x) datawizard::rescale(x, to = c(0, 5))))  |>
+  datawizard::rescale(select=ias_vars, to = c(1, 5), range = c(0, 1))
 
@@
 df11$MAIA_Trusting<- rowMeans(select(df11 , starts_with("MAIA2_Trusting")))
-
-df11 <- mutate(df11, across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5))))
 
@@
   filter(!is.na(Heart)) |>  # participant is outlier and had total IAS scores below 0.4 
-  datawizard::rescale(select=ias_vars, to = c(0, 5), range = c(0, 1)) |> 
+  datawizard::rescale(select=ias_vars, to = c(1, 5), range = c(0, 1)) |> 
   mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5)))) 
@@
     MAIA_NotWorrying_2_R = 1 - MAIA_NotWorrying_2_R,
-    MAIA_NotWorrying_5_R = 1 - MAIA_NotWorrying_5_R)
+    MAIA_NotWorrying_5_R = 1 - MAIA_NotWorrying_5_R) |>
+    mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5))))
 

### 2025-08-13 analysis/study2.qmd
updated ranges from scales

@@
   make_rez(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (PHQ-4)"),
+  make_rez(with = "STAI5_General", component="Mood", name = "Anxiety (STAI-5)"),
   make_rez(with = "GAD7_Sum", component="Mood", name = "Anxiety (GAD-7)")

### 2025-08-13 analysis/Study1.qmd
added colours + fixed mistakes + added positions

@@
             name == "F6" ~ y_position[6],
+            name == "F7" ~ y_position[7],
+            name == "F8" ~ y_position[8],
             .default = NA
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data1a, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data1a, n = 4, cols = c("F1" = colors[["Itch"]], "F2" = colors[["Burp"]], 
+                                            "F3" = colors[["Defecate"]], "F4" = colors[["Hungry"]]))
 
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data1af, n = 3, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]]))
+rez_efa <- make_efa(data1af, n = 3, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Urinate"]], 
+                                            "F3" = colors[["Bruise"]]))
 rez_cfa1a  <- make_cfa(data1af)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data1b, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data1b, n = 4, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Bruise"]], 
+                                            "F3" = colors[["Sneeze"]], "F4" = colors[["Wind"]]))
 
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data3, n = 3, cols = c("F1" = colors[["Sneeze"]], "F2" = colors[["Hungry"]], 
-                                            "F3" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data3, n = 4, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Urinate"]], 
+                                            "F3" = colors[["Blood Sugar"]], "F4" = colors[["Sex arousal"]]))
 
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data5, n = 8, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Itch"]], 
-                                            "F3" = colors[["Breathing"]], "F4" = colors[["Urinate"]], "F5" = colors[["Burp"]], "F6" = colors[["Taste"]], "F7" = colors[["Heart"]], "F8" = colors[["Vomit"]]))
+rez_efa <- make_efa(data5, n = 8, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Itch"]], 
+                                            "F3" = colors[["Burp"]], "F4" = colors[["Hungry"]], 
+                                           "F5" = colors[["Affective touch"]], "F6" = colors[["Breathing"]], "F7" = colors[["Sex arousal"]], "F8" = colors[["Taste"]]))
 
@@
 #   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data5f, n = 5, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]],
-                                            "F5" = colors[["Urinate"]]))
+rez_efa <- make_efa(data5f, n = 5, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Burp"]], 
+                                            "F3" = colors[["Wind"]], "F4" = colors[["Thirsty"]],
+                                            "F5" = colors[["Sneeze"]]))
 rez_cfa5  <- make_cfa(data5f)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data6, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data6, n = 3, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Hungry"]]))
 
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data6f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data6f, n = 3, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Thirsty"]]))
 rez_cfa6  <- make_cfa(data6f)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data7a, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data7a, n = 4, cols = c("F1" = colors[["Pain"]], "F2" = colors[["Sneeze"]], 
+                                            "F3" = colors[["Burp"]], "F4" = colors[["Urinate"]]))
 
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data7af, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data7af, n = 4, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Pain"]], 
+                                            "F3" = colors[["Sneeze"]], "F4" = colors[["Urinate"]]))
 rez_cf7a  <- make_cfa(data7af)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data7b, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data7b, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Urinate"]], 
+                                            "F3" = colors[["Heart"]], "F4" = colors[["Sneeze"]]))
 
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data7bf, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data7bf, n = 3, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Urinate"]], 
+                                            "F3" = colors[["Breathing"]]))
 rez_cfa7b  <- make_cfa(data7bf)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data7c, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data7c, n = 3, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Urinate"]], 
+                                            "F3" = colors[["Bruise"]]))
 
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data7cf, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data7cf, n = 4, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Hungry"]], 
+                                            "F3" = colors[["Bruise"]], "F4" = colors[["Breathing"]]))
 rez_cfa7c  <- make_cfa(data7cf)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data8a, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data8a, n = 5, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Thirsty"]], 
+                                            "F3" = colors[["Bruise"]], "F4" = colors[["Heart"]], "F5" = colors[["Urinate"]]))
 
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data8af, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data8af, n = 4, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Thirsty"]], 
+                                            "F3" = colors[["Bruise"]], "F4" = colors[["Heart"]]))
 rez_cfa8a  <- make_cfa(data8af)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data8b, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data8b, n = 5, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Thirsty"]], 
+                                            "F3" = colors[["Breathing"]], "F4" = colors[["Bruise"]], "F5" = colors[["Urinate"]]))
 
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data8bf, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data8bf, n = 4, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Heart"]], 
+                                            "F3" = colors[["Thirsty"]], "F4" = colors[["Bruise"]]))
 rez_cfa8b  <- make_cfa(data8bf)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data9, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data9, n = 3, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Thirsty"]], 
+                                            "F3" = colors[["Bruise"]]))
 
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data9f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data9f, n = 3, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Urinate"]], 
+                                            "F3" = colors[["Pain"]]))
 rez_cfa9  <- make_cfa(data9f)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data10, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data10, n = 4, cols = c("F1" = colors[["Hungry"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Itch"]], "F4" = colors[["Breathing"]]))
 
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data10f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data10f, n = 3, cols = c("F1" = colors[["Breathing"]], "F2" = colors[["Defecate"]], 
+                                            "F3" = colors[["Hungry"]]))
 # rez_cfa10  <- make_cfa(data10f)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data11, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data11, n = 4, cols = c("F1" = colors[["Hungry"]], "F2" = colors[["Wind"]], 
+                                            "F3" = colors[["Bruise"]], "F4" = colors[["Breathing"]]))
 
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data8af, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data11f, n = 3, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Hungry"]], 
+                                            "F3" = colors[["Breathing"]]))
 rez_cfa11  <- make_cfa(data11f)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data12, n = 2, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data12, n = 2, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Bruise"]]))
 
@@
 rez_hclust <- make_hclust(data12f)
-rez_ega <- make_ega(data8af, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data12f, n = 5, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                             "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_ega <- make_ega(data12f, cols = c(
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data12f, n = 5, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Burp"]], 
+                                             "F3" = colors[["Heart"]], "F4" = colors[["Pain"]], "F5" = colors[["Sneeze"]]))
 # rez_cfa12  <- make_cfa(data12f)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data13, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data13, n = 4, cols = c("F1" = colors[["Thirsty"]], "F2" = colors[["Heart"]], 
+                                            "F3" = colors[["Burp"]], "F4" = colors[["Bruise"]]))
 
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data13f, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data13f, n = 4, cols = c("F1" = colors[["Thirsty"]], "F2" = colors[["Heart"]], 
+                                            "F3" = colors[["Burp"]], "F4" = colors[["Bruise"]]))
 rez_cfa13  <- make_cfa(data13f)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data14, n = 3, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data14, n = 7, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Thirsty"]], 
+                                            "F3" = colors[["Bruise"]], "F4" = colors[["Temp"]], 
+                                            "F5" = colors[["Pain"]], "F6" = colors[["Sneeze"]],
+                                            "F7" = colors[["Heart"]]))
 
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data8af, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                             "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data14f, n = 5, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Defecate"]], 
+                                             "F3" = colors[["Thirsty"]], "F4" = colors[["Heart"]], 
+                                             "F5" = colors[["Muscles"]]))
 rez_cfa14  <- make_cfa(data14f)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data15, n = 3, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data15, n = 3, cols = c("F1" = colors[["Sneeze"]], "F2" = colors[["Hungry"]], 
+                                            "F3" = colors[["Bruise"]]))
 
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data8af, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data15f, n = 3, cols = c("F1" = colors[["Hungry"]], "F2" = colors[["Burp"]], 
+                                            "F3" = colors[["Blood Sugar"]]))
 rez_cfa15  <- make_cfa(data15f)
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data16, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]], "F4" = colors[["Itch"]]))
+rez_efa <- make_efa(data16, n = 4, cols = c("F1" = colors[["Thirsty"]], "F2" = colors[["Sneeze"]], 
+                                            "F3" = colors[["Blood Sugar"]], "F4" = colors[["Burp"]]))
 
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data16f, n = 3, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Defecate"]], 
-                                            "F3" = colors[["Heart"]]))
+rez_efa <- make_efa(data16f, n = 4, cols = c("F1" = colors[["Thirsty"]], "F2" = colors[["Cough"]], 
+                                            "F3" = colors[["Bruise"]], "F4" = colors[["Wind"]]))
 rez_cfa16  <- make_cfa(data16f)
@@
   sample10 = add_empirical(data10, "Sample 10"),
-  sample11  = add_empirical(data11 , "Sample 11 "),
-  sample12  = add_empirical(data12 , "Sample 12 "),
-  sample13 = add_empirical(data13, "Sample 13 "),
+  sample11 = add_empirical(data11 , "Sample 11"),
+  sample12 = add_empirical(data12 , "Sample 12"),
+  sample13 = add_empirical(data13, "Sample 13"),
   sample14 = add_empirical(data14 , "Sample 14 "),
-  sample15   = add_empirical(data15 , "Sample 15  ")
+  sample15 = add_empirical(data15 , "Sample 15"),
+  sample16 = add_empirical(data16, "Sample 16")
 )

### 2025-08-14 analysis/Study1.qmd
EGA| colours data 1-3

@@
 rez_ega <- make_ega(data1af, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data1af, n = 3, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Urinate"]], 
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Wind"]], "C6" = colors[["Pain"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data1af, n = 3, cols = c("F1"  colors[["Burp"]], "F2" = colors[["Urinate"]], 
                                             "F3" = colors[["Bruise"]]))
@@
 rez_ega <- make_ega(data1b, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Defecate"]], "C3" = colors[["Bruise"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Wind"]], "C6" = colors[["Temp"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data1b, n = 4, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Bruise"]], 
@@
 rez_ega <- make_ega(data1af, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Wind"]], "C6" = colors[["Pain"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data1bf, n = 3, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Bruise"]], 
@@
 rez_ega <- make_ega(data2, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Urinate"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Pain"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data2, n = 4, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Bruise"]], 
@@
 rez_ega <- make_ega(data2f, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Wind"]], "C6" = colors[["Pain"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data2f, n = 3, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Bruise"]], 
@@
 rez_ega <- make_ega(data3, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Urinate"]], "C3" = colors[["Pain"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Wind"]], "C6" = colors[["Bruise"]], "C7" = colors[["Muscles"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data3, n = 4, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Urinate"]], 
@@
 rez_ega <- make_ega(data3f, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Urinate"]], "C3" = colors[["Sneeze"]], "C4" = colors[["Wind"]], 
+  "C5" = colors[["Pain"]], "C6" = colors[["Bruise"]], "C7" = colors[["Muscles"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data3f, n = 3, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Hungry"]], 
@@
 rez_hclust <- make_hclust(data12f)
-rez_ega <- make_ega(data12f, cols = c(
+rez_ega <- make_ega(data8af, cols = c(
   "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 

### 2025-08-14 analysis/Study1.qmd
EGA colours data 4-6

@@
 rez_ega <- make_ega(data4, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Pain"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Affective touch"]]))
 rez_efa <- make_efa(data4, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Itch"]], 
@@
 rez_ega <- make_ega(data4f, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Wind"]], "C6" = colors[["Pain"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data4f, n = 3, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Breathing"]], 
@@
 rez_ega <- make_ega(data5, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Sneeze"]], "C3" = colors[["Vomit"]], "C4" = colors[["Cough"]], 
+  "C5" = colors[["Defecate"]], "C6" = colors[["Muscles"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data5, n = 8, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Itch"]], 
@@
   "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C5" = colors[["Cough"]], "C6" = colors[["Itch"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data6, n = 3, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Defecate"]], 
@@
 rez_ega <- make_ega(data6f, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Wind"]], "C6" = colors[["Bruise"]], "C7" = colors[["Pain"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data6f, n = 3, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Defecate"]], 

### 2025-08-15 analysis/Study1.qmd
EGA colours data 7a-9

@@
 rez_ega <- make_ega(data7a, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Defecate"]], "C3" = colors[["Itch"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Wind"]], "C6" = colors[["Bruise"]], "C7" = colors[["Pain"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data7a, n = 4, cols = c("F1" = colors[["Pain"]], "F2" = colors[["Sneeze"]], 
@@
 rez_ega <- make_ega(data7af, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Pain"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Wind"]], "C6" = colors[["Bruise"]], "C7" = colors[["Burp"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data7af, n = 4, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Pain"]], 
@@
 rez_ega <- make_ega(data7b, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Pain"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data7b, n = 4, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Urinate"]], 
@@
 rez_ega <- make_ega(data7bf, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Wind"]], "C6" = colors[["Pain"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data7bf, n = 3, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Urinate"]], 
@@
 rez_ega <- make_ega(data7c, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Pain"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Sex arousal"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data7c, n = 3, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Urinate"]], 
@@
 rez_ega <- make_ega(data7cf, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Wind"]], "C6" = colors[["Pain"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data7cf, n = 4, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Hungry"]], 
@@
 rez_ega <- make_ega(data8a, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Wind"]], "C6" = colors[["Bruise"]], "C7" = colors[["Itch"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data8a, n = 5, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Thirsty"]], 
@@
 rez_ega <- make_ega(data8af, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Wind"]], "C6" = colors[["Bruise"]], "C7" = colors[["Pain"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data8af, n = 4, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Thirsty"]], 
@@
 rez_ega <- make_ega(data8b, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Cough"]], 
+  "C5" = colors[["Pain"]], "C6" = colors[["Bruise"]], "C7" = colors[["Itch"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data8b, n = 5, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Thirsty"]], 
@@
 rez_ega <- make_ega(data8bf, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Cough"]], 
+  "C5" = colors[["Pain"]], "C6" = colors[["Bruise"]], "C7" = colors[["Itch"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data8bf, n = 4, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Heart"]], 
@@
 rez_ega <- make_ega(data9f, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Wind"]], "C6" = colors[["Pain"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data9f, n = 3, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Urinate"]], 

### 2025-08-15 analysis/Study1.qmd
EGA colours data 10-13

@@
 rez_ega <- make_ega(data10, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Bruise"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data10, n = 4, cols = c("F1" = colors[["Hungry"]], "F2" = colors[["Defecate"]], 
@@
 rez_ega <- make_ega(data10f, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Wind"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Pain"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data10f, n = 3, cols = c("F1" = colors[["Breathing"]], "F2" = colors[["Defecate"]], 
@@
 rez_ega <- make_ega(data11, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Bruise"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Pain"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data11, n = 4, cols = c("F1" = colors[["Hungry"]], "F2" = colors[["Wind"]], 
@@
 rez_ega <- make_ega(data11f, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Bruise"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Pain"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data11f, n = 3, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Hungry"]], 
@@
 rez_ega <- make_ega(data12, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Bruise"]], 
+  "C5" = colors[["Cough"]], "C6" = colors[["Pain"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data12, n = 2, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Bruise"]]))
@@
 rez_ega <- make_ega(data8af, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Wind"]], "C6" = colors[["Bruise"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data12f, n = 5, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Burp"]], 
@@
   "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C5" = colors[["Sex arousal"]], "C6" = colors[["Sneeze"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data13, n = 4, cols = c("F1" = colors[["Thirsty"]], "F2" = colors[["Heart"]], 
@@
 rez_ega <- make_ega(data13f, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Bruise"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data13f, n = 4, cols = c("F1" = colors[["Thirsty"]], "F2" = colors[["Heart"]], 

### 2025-08-15 analysis/Study1.qmd
EGA colours data 14-16

@@
 rez_ega <- make_ega(data14f, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Wind"]], "C6" = colors[["Pain"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data14f, n = 5, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Defecate"]], 
@@
 rez_ega <- make_ega(data15, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Sex arousal"]], "C4" = colors[["Sneeze"]], 
+  "C5" = colors[["Muscles"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data15, n = 3, cols = c("F1" = colors[["Sneeze"]], "F2" = colors[["Hungry"]], 
@@
 rez_ega <- make_ega(data15f, cols = c(
-  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Sneeze"]], "C4" = colors[["Wind"]], 
+  "C5" = colors[["Bruise"]], "C6" = colors[["Wind"]], "C7" = colors[["Pain"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data15f, n = 3, cols = c("F1" = colors[["Hungry"]], "F2" = colors[["Burp"]], 
@@
   "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
-  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+  "C5" = colors[["Cough"]], "C6" = colors[["Bruise"]], "C7" = colors[["Wind"]], "C8" = colors[["Blood Sugar"]]))
 rez_efa <- make_efa(data16, n = 4, cols = c("F1" = colors[["Thirsty"]], "F2" = colors[["Sneeze"]], 

### 2025-08-15 analysis/study2.qmd
pool coefficients BPQ- Depression
@DominiqueMakowski I am not sure this is correct

@@
   data,
-  pool_coef(with = "BPQ_BodyAwareness", component="BPQ", name = "Body Awareness (BPQ)"),
-  pool_coef(with = "BPQ_AutonomicReactivity", component="BPQ", name = "Autonomic Reactivity (BPQ)")
+  pool_coef(with = "BPQ_BodyAwareness", component="BPQ", name = "Body Awareness (BPQ)",unequalrange=TRUE),
+  pool_coef(with = "BPQ_AutonomicReactivity", component="BPQ", name = "Autonomic Reactivity (BPQ)",unequalrange=TRUE)
   )
@@
   data,
-  #df2 
-  make_rez(with = "TAS_DIF", component="Alexithymia", name = "Difficulties Identifying Feelings (TAS)"),
-  make_rez(with = "TAS_DDF", component="Alexithymia", name = "Difficulties Describing Feelings (TAS)"),
-  make_rez(with = "TAS_EOT", component="Alexithymia", name = "External Thinking (TAS)"),
-  make_rez(with = "BVAQ_Affective", component="Alexithymia", name = "Affective (BVAQ)"), 
-  make_rez(df2, vars_intero, with = "BVAQ_Cognitive", component="Alexithymia", name = "Cognitive (BVAQ)")
+  pool_coef(with = "TAS_DIF", component="Alexithymia", name = "Difficulties Identifying Feelings (TAS)", unequalrange=TRUE),
+  pool_coef(with = "TAS_DDF", component="Alexithymia", name = "Difficulties Describing Feelings (TAS)", unequalrange=TRUE),
+  pool_coef(with = "TAS_EOT", component="Alexithymia", name = "External Thinking (TAS)",unequalrange=TRUE),
+  pool_coef(with = "BVAQ_Affective", component="Alexithymia", name = "Affective (BVAQ)"), 
+  pool_coef(with = "BVAQ_Cognitive", component="Alexithymia", name = "Cognitive (BVAQ)")
 )
@@
   data,
-  make_rez(with = "PHQ2_Sum", component="Mood", name = "Depression (PHQ-2)"),
-  make_rez(with = "PHQ15_Sum", component="Mood", name = "Somatic Concerns (PHQ-15)"), 
-  make_rez(with = "PHQ9_Sum", component="Mood", name = "Depression (PHQ-9)"), 
-  make_rez(with = "BDI_Sum", component="Mood", name = "Depression (BDI)"), 
-  make_rez(with = "PHQ4_Depression", component="Mood", name = "Depression (PHQ-2)"),
-  make_cor(with = "DEP", component = "Mood", name = "Depression (MFQ)")
+  pool_coef(with = "PHQ2_Sum", component="Mood", name = "Depression (PHQ-2)"),
+  pool_coef(with = "PHQ15_Sum", component="Mood", name = "Somatic Concerns (PHQ-15)",unequalrange=TRUE), 
+  pool_coef(with = "PHQ9_Sum", component="Mood", name = "Depression (PHQ-9)"), 
+  pool_coef(with = "BDI_Sum", component="Mood", name = "Depression (BDI)"), 
+  pool_coef(with = "PHQ4_Depression", component="Mood", name = "Depression (PHQ-2)"),
+  pool_coef(with = "DEP", component = "Mood", name = "Depression (MFQ)")
 )

### 2025-08-18 analysis/Study1.qmd
updated scales and pool_coef function

@@
   - https://osf.io/5x9sg
+  - BPQ_A = autonomic symptoms
 
@@
     Affective_touch = `IAS 19`, Tickle = `IAS 20`, Itch = `IAS 21`,
-    MAIA_Trusting = MAIA_BodyTrusting,
-    BPQ_BodyAwareness = BPQ_A, BPQ_AutonomicReactivity = BPQ_R)
+    MAIA_Trusting = MAIA_BodyTrusting)
 rm(data)
+
+df2$BPQ_BodyAwareness <- rowMeans(select(df2, `BPQ 1`:`BPQ 26`), na.rm = TRUE)
+df2$BPQ_AutonomicReactivity <- rowMeans(select(df2, `BPQ 27`:`BPQ 46`), na.rm = TRUE)
+
 ```
@@
   )
+
+df3$BPQ_BodyAwareness <- rowMeans(select(df3, BPQ1:BPQ26), na.rm = TRUE)
+df3$BPQ_AutonomicReactivity <- rowMeans(select(df3, BPQ27:BPQ46), na.rm = TRUE)
+
 ```
@@
 
-df4$BPQ_BodyAwareness <- rowMeans(select(df4, starts_with("BPQ")), na.rm = TRUE)
+df4$BPQ_BodyAwareness <- rowMeans(select(df4, starts_with("BPQ_")), na.rm = TRUE)
 ```
@@
     MAIA_SelfReg = maiaSelfRegulation, MAIA_BodyListening = maiaBodyListening,
-    MAIA_Trusting = maiaTrusting, MAIA_EmoAwareness = maiaEmotionalAwareness,
-    BPQ_BodyAwareness =BPQ_Sum) |> 
+    MAIA_Trusting = maiaTrusting, MAIA_EmoAwareness = maiaEmotionalAwareness) |> 
   mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5), range = c(1, 5))),# Original scale 1-5
-         across(starts_with("PHQ15_"), \(x) datawizard::rescale(x, to = c(0,2), range =c(1,3))),
-          across(starts_with("PHQ9_"), \(x) datawizard::rescale(x, to = c(0,3), range =c(1,4))))
+          across(PHQ15_01:PHQ15_15recode, \(x) datawizard::rescale(x, to = c(0,2), range =c(1,3))),
+           across(PHQ9_01:PHQ9_09, \(x) datawizard::rescale(x, to = c(0,3), range =c(1,4))))
+
+df7b$BPQ_BodyAwareness <- rowMeans(select(df7b, BPQ_01:BPQ_12), na.rm = TRUE)
+df7b$PHQ15_Sum <-rowSums(select(df7b,PHQ15_01:PHQ15_15recode), na.rm = TRUE)
+df7b$PHQ9_Sum <- rowMeans(select(df7b, PHQ9_01:PHQ9_09), , na.rm = TRUE)
 
@@
     STAIT_Sum = STAIT_sum,
-    TAS_DIF = TAS_ident, TAS_EOT = TAS_ext, TAS_DDF = TAS_des,
-    BPQ_BodyAwareness = BPQ_sum
-  ) |> 
+    TAS_DIF = TAS_ident, TAS_EOT = TAS_ext, TAS_DDF = TAS_des) |> 
   mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5), range = c(0, 6)))) # Original scale 0-6
+
+df7c$BPQ_BodyAwareness <- df7c$BPQ_sum / 26
+
 ```
@@
   - Note: No tickle because same Chinese character
+  - missing phq9_9 item
 
@@
 
-df8a$BPQ_BodyAwareness <- rowMeans(select(df8a, starts_with("BPQ")), na.rm = TRUE)
+df8a$BPQ_BodyAwareness <- rowMeans(select(df8a,BPQ1:BPQ12), na.rm = FALSE)
 
@@
     Affective_touch = Touch, Itch = ITCH,
-    PHQ15_Sum = PHQ15_sum,
-    PHQ9_Sum = PHQ9_sum)
+    PHQ15_Sum = PHQ15_sum, PHQ9_sum = PHQ9_sum)
+
+df8b$PHQ9_Sum <- df8b$PHQ9_sum / 9
+df8b$PHQ15_Sum <- df8b$PHQ15_Sum/ 15
+
 ```
@@
   datawizard::rescale(select=ias_vars, to = c(1, 5), range = c(0, 1)) |> 
-  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5)))) 
+  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5))),
+         across(starts_with("PI_"), \(x) datawizard::rescale(x, to = c(0, 1))))
 ```
@@
   mutate(across(starts_with("MAIA2_"), \(x) datawizard::rescale(x, to = c(0, 5))))  |>
+   mutate(across(starts_with("PHQ4_Depression_"), \(x) datawizard::rescale(x, to = c(0, 4))),
+          across(starts_with("PHQ4_Anxiety_"), \(x) datawizard::rescale(x, to = c(0, 4)))) |>
+   mutate(PHQ4_Depression = (PHQ4_Depression_3 + PHQ4_Depression_4)/2,
+          PHQ4_Anxiety = (PHQ4_Anxiety_1 + PHQ4_Anxiety_2)/2) |>
   datawizard::rescale(select=ias_vars, to = c(1, 5), range = c(0, 1))
@@
     TAS_DIF = TAS20_1 + TAS20_3 + TAS20_6 + TAS20_7 + TAS20_9 + TAS20_13 + TAS20_14,
-    TAS_DDF = TAS20_2 + (1-TAS20_4) + TAS20_11 + TAS20_12 + TAS20_17,
-    TAS_EOT = (1-TAS20_5) + TAS20_8 + (1-TAS20_10) + TAS20_15 + TAS20_16 + (1-TAS20_18) + (1-TAS20_19) + TAS20_20) 
+    TAS_DDF = TAS20_2 + (6-TAS20_4) + TAS20_11 + TAS20_12 + TAS20_17,
+    TAS_EOT = (6-TAS20_5) + TAS20_8 + (6-TAS20_10) + TAS20_15 + TAS20_16 + (6-TAS20_18) + (6-TAS20_19) + TAS20_20) 
 ```
@@
   "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data1a, n = 4, cols = c("F1" = colors[["Itch"]], "F2" = colors[["Burp"]], 
-                                            "F3" = colors[["Defecate"]], "F4" = colors[["Hungry"]]))
+rez_efa <- make_efa(data1a, n = 4, cols = c("F1" = colors[["Itch"]], "F2" = colors[["Burp"]], "F3" = colors[["Defecate"]], "F4" = colors[["Hungry"]]))
 
@@
   "C5" = colors[["Wind"]], "C6" = colors[["Pain"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
-rez_efa <- make_efa(data1af, n = 3, cols = c("F1"  colors[["Burp"]], "F2" = colors[["Urinate"]], 
-                                            "F3" = colors[["Bruise"]]))
+rez_efa <- make_efa(data1af, n = 3, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Urinate"]], "F3" = colors[["Bruise"]]))
 rez_cfa1a  <- make_cfa(data1af)
@@
 ##### Summary
+- cfa did not converge
 
@@
                                             "F3" = colors[["Cough"]], "F4" = colors[["Itch"]]))
-rez_cfa1b  <- make_cfa(data1bf)
-
-rez_hclust$p / rez_ega$p / rez_efa$p
-```
-
-##### Details
-
-```{r}
-#| warning: false
-#| message: false
-
-plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
-pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
-
-stab <- EGAnet::itemStability(rez_ega$rez)
-rez_ega$table
-
-plot(rez_efa$n_fac)
-
-rez_cfa1b$test
+# rez_cfa1b  <- make_cfa(data1bf)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+# rez_cfa1b$test
 ```
@@
                                             "F3" = colors[["Hungry"]]))
-rez_cfa2  <- make_cfa(data2f)
-
-rez_hclust$p / rez_ega$p / rez_efa$p
-```
-
-##### Details
-
-```{r}
-#| warning: false
-#| message: false
-
-plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
-pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
-
-stab <- EGAnet::itemStability(rez_ega$rez)
-rez_ega$table
-
-plot(rez_efa$n_fac)
-
-rez_cfa2$test
+# rez_cfa2  <- make_cfa(data2f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+# rez_cfa2$test
 ```
@@
                                             "F3" = colors[["Blood Sugar"]]))
-rez_cfa3  <- make_cfa(data3f)
+# rez_cfa3  <- make_cfa(data3f)
 
@@
 
-rez_cfa3$test
+# rez_cfa3$test
 ```
@@
                                             "F5" = colors[["Sneeze"]]))
-rez_cfa5  <- make_cfa(data5f)
+# rez_cfa5  <- make_cfa(data5f)
 
@@
 
-rez_cfa5$test
+# rez_cfa5$test
 ```
@@
                                             "F3" = colors[["Blood Sugar"]]))
-rez_cfa15  <- make_cfa(data15f)
+# rez_cfa15  <- make_cfa(data15f)
 
@@
 
-rez_cfa15$test
+# rez_cfa15$test
 ```
@@
                                             "F3" = colors[["Bruise"]], "F4" = colors[["Wind"]]))
-rez_cfa16  <- make_cfa(data16f)
-
-rez_hclust$p / rez_ega$p / rez_efa$p
-```
-
-##### Details
-
-```{r}
-#| warning: false
-#| message: false
-
-plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
-pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
-
-stab <- EGAnet::itemStability(rez_ega$rez)
-rez_ega$table
-
-plot(rez_efa$n_fac)
-
-rez_cfa16$test
+# rez_cfa16  <- make_cfa(data16f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+# rez_cfa16$test
 ```

### 2025-08-18 analysis/study2.qmd
updated scales and pool_coef function

@@
 df15 <- cbind(data$df15, scores$sample15)
+df16 <- cbind(data$df16, scores$sample16)
 
@@
                      df8a, df8b, df9, df10, df11, 
-                     df12, df14, df15)) {
+                     df12, df14, df15, df16)) {
       if (with %in% names(dataset)) {
@@
   pool_coef(with = "PHQ15_Sum", component="Mood", name = "Somatic Concerns (PHQ-15)",unequalrange=TRUE), 
-  pool_coef(with = "PHQ9_Sum", component="Mood", name = "Depression (PHQ-9)"), 
+  pool_coef(with = "PHQ9_Sum", component="Mood", name = "Depression (PHQ-9)",unequalrange=TRUE), 
   pool_coef(with = "BDI_Sum", component="Mood", name = "Depression (BDI)"), 
@@
   data,
-  make_rez(with = "GAD2_Sum", component="Mood", name = "Anxiety (GAD-2)"), 
-  make_rez(with = "STAIT_Sum", component="Mood", name = "Anxiety (STAI-T)"), 
-  make_rez(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (PHQ-4)"),
-  make_rez(with = "STAI5_General", component="Mood", name = "Anxiety (STAI-5)"),
-  make_rez(with = "GAD7_Sum", component="Mood", name = "Anxiety (GAD-7)")
+  pool_coef(with = "GAD2_Sum", component="Mood", name = "Anxiety (GAD-2)"), 
+  pool_coef(with = "STAIT_Sum", component="Mood", name = "Anxiety (STAI-T)",unequalrange=TRUE), 
+  pool_coef(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (PHQ-4)"),
+  pool_coef(with = "STAI5_General", component="Mood", name = "Anxiety (STAI-5)"),
+  pool_coef(with = "GAD7_Sum", component="Mood", name = "Anxiety (GAD-7)")
 )
@@
   data,
-  make_rez(with = "BPD", component="Mood", name = "Boderline Personality")
+  pool_coef(with = "BPD", component="Mood", name = "Boderline Personality")
 )
@@
   data,
-  make_rez(with = "PID5_Antagonism", component="Maladaptive", name = "Antagonism"),
-  make_rez(with = "PID5_Detachment", component="Maladaptive", name = "Detachment"), 
-  make_rez(with = "PID5_Disinhibition", component="Maladaptive", name = "Disinhibition"),
-  make_rez(with = "PID5_NegativeAffect", component="Maladaptive", name = "Negative Affect"),
-  make_rez(with = "PID5_Psychoticism", component="Maladaptive", name = "Psychoticism")
+  pool_coef(with = "PID5_Antagonism", component="Maladaptive", name = "Antagonism"),
+  pool_coef(with = "PID5_Detachment", component="Maladaptive", name = "Detachment"), 
+  pool_coef(with = "PID5_Disinhibition", component="Maladaptive", name = "Disinhibition"),
+  pool_coef(with = "PID5_NegativeAffect", component="Maladaptive", name = "Negative Affect"),
+  pool_coef(with = "PID5_Psychoticism", component="Maladaptive", name = "Psychoticism")
 )
@@
   data,
-  make_rez(with = "SPQ_ConstrictedAffect", component="Schizotypic", name = "Constricted Affect"),
-  make_rez(with = "SPQ_Eccentric", component="Schizotypic", name = "Eccentric"),
-  make_rez(with = "SPQ_MagicalThinking", component="Schizotypic", name = "Magical Thinking"),
-  make_rez(with = "SPQ_NoCloseFriends", component="Schizotypic", name = "No Close Friends"),
-  make_rez(with = "SPQ_OddSpeech", component="Schizotypic", name = "Odd Speech"),
-  make_rez(with = "SPQ_Reference", component="Schizotypic", name = "Reference"),
-  make_rez(with = "SPQ_SocialAnxiety", component="Schizotypic", name = "Social Anxiety"),
-  make_rez(with = "SPQ_Suspiciousness", component="Schizotypic", name = "Suspiciousness"),
-  make_rez(with = "SPQ_UnusualPerceptions", component="Schizotypic", name = "Unusual Perceptions")
+  pool_coef(with = "SPQ_ConstrictedAffect", component="Schizotypic", name = "Constricted Affect"),
+  pool_coef(with = "SPQ_Eccentric", component="Schizotypic", name = "Eccentric"),
+  pool_coef(with = "SPQ_MagicalThinking", component="Schizotypic", name = "Magical Thinking"),
+  pool_coef(with = "SPQ_NoCloseFriends", component="Schizotypic", name = "No Close Friends"),
+  pool_coef(with = "SPQ_OddSpeech", component="Schizotypic", name = "Odd Speech"),
+  pool_coef(with = "SPQ_Reference", component="Schizotypic", name = "Reference"),
+  pool_coef(with = "SPQ_SocialAnxiety", component="Schizotypic", name = "Social Anxiety"),
+  pool_coef(with = "SPQ_Suspiciousness", component="Schizotypic", name = "Suspiciousness"),
+  pool_coef(with = "SPQ_UnusualPerceptions", component="Schizotypic", name = "Unusual Perceptions")
 )
@@
   data,
-  make_rez(with = "ASQ_Imagination", component="Autistic", name = "Imagination"),
-  make_rez(with = "ASQ_LackSocialSkills", component="Autistic", name = "Lack of Social Skills"), 
-  make_rez(with = "ASQ_LowAttentionalSwitching", component="Autistic", name = "Low Attentional Switching"),
-  make_rez(with = "ASQ_Patterns", component="Autistic", name = "Patterns and Numbers"),
-  make_rez(with = "ASQ_Routine", component="Autistic", name = "Routines")
+  pool_coef(with = "ASQ_Imagination", component="Autistic", name = "Imagination"),
+  pool_coef(with = "ASQ_LackSocialSkills", component="Autistic", name = "Lack of Social Skills"), 
+  pool_coef(with = "ASQ_LowAttentionalSwitching", component="Autistic", name = "Low Attentional Switching"),
+  pool_coef(with = "ASQ_Patterns", component="Autistic", name = "Patterns and Numbers"),
+  pool_coef(with = "ASQ_Routine", component="Autistic", name = "Routines")
 )
@@
   data,
-  make_rez(with = "NEO_FFI_SUMSCORE", component = "Personality", name = "Neuroticism"),
-  make_rez(with = "BFI_AGREEABLENESS", component="Personality", name = "Agreeableness"),
-  make_rez(with = "BFI_CONSCIENTIOUSNESS", component="Personality", name = "Conscientiousness"), 
-  make_rez(with = "BFI_NEUROTICISM", component="Personality", name = "Neuroticism"),
-  make_rez(with = "BFI_OPENNESS", component="Personality", name = "Openness"),
-  make_rez(with = "BFI_EXTROVERSION", component="Personality", name = "Extraversion"),
-  make_rez(with = "IPIP6_Agreeableness", component="Personality", name = "Agreeableness"),
-  make_rez(with = "IPIP6_Conscientiousness", component="Personality", name = "Conscientiousness"), 
-  make_rez(with = "IPIP6_Neuroticism", component="Personality", name = "Neuroticism"),
-  make_rez(with = "IPIP6_Openness", component="Personality", name = "Openness"),
-  make_rez(with = "IPIP6_Extraversion", component="Personality", name = "Extraversion"), 
-  make_rez(with = "IPIP6_HonestyHumility", component="Personality", name = "Honesty-Humility")
+  pool_coef(with = "NEO_FFI_SUMSCORE", component = "Personality", name = "Neuroticism"),
+  pool_coef(with = "BFI_AGREEABLENESS", component="Personality", name = "Agreeableness"),
+  pool_coef(with = "BFI_CONSCIENTIOUSNESS", component="Personality", name = "Conscientiousness"), 
+  pool_coef(with = "BFI_NEUROTICISM", component="Personality", name = "Neuroticism"),
+  pool_coef(with = "BFI_OPENNESS", component="Personality", name = "Openness"),
+  pool_coef(with = "BFI_EXTROVERSION", component="Personality", name = "Extraversion"),
+  pool_coef(with = "IPIP6_Agreeableness", component="Personality", name = "Agreeableness"),
+  pool_coef(with = "IPIP6_Conscientiousness", component="Personality", name = "Conscientiousness"), 
+  pool_coef(with = "IPIP6_Neuroticism", component="Personality", name = "Neuroticism"),
+  pool_coef(with = "IPIP6_Openness", component="Personality", name = "Openness"),
+  pool_coef(with = "IPIP6_Extraversion", component="Personality", name = "Extraversion"), 
+  pool_coef(with = "IPIP6_HonestyHumility", component="Personality", name = "Honesty-Humility")
 )
@@
 
-data <- rbind(data, make_rez(with = "PI_Alive", component="World Beliefs", name = "Alive"))
+data <- rbind(data, pool_coef(with = "PI_Alive", component="World Beliefs", name = "Alive"))
 
@@
   data,
-  make_rez(with = "GCBS_Extraterrestrial", component="Conspiracy Beliefs", name = "Extraterrestrial"),
-  make_rez(with = "GCBS_GlobalConspiracies", component="Conspiracy Beliefs", name = "Global Conspiracies"),
-  make_rez(with = "GCBS_GovernmentMalfeasance", component="Conspiracy Beliefs", name  = "Government Malfeasance"),
-  make_rez(with = "GCBS_InformationControl", component="Conspiracy Beliefs", name = "Information Control"),
-  make_rez(with = "GCBS_PersonalWellbeing", component="Conspiracy Beliefs", name = "Personal Wellbeing")
+  pool_coef(with = "GCBS_Extraterrestrial", component="Conspiracy Beliefs", name = "Extraterrestrial"),
+  pool_coef(with = "GCBS_GlobalConspiracies", component="Conspiracy Beliefs", name = "Global Conspiracies"),
+  pool_coef(with = "GCBS_GovernmentMalfeasance", component="Conspiracy Beliefs", name  = "Government Malfeasance"),
+  pool_coef(with = "GCBS_InformationControl", component="Conspiracy Beliefs", name = "Information Control"),
+  pool_coef(with = "GCBS_PersonalWellbeing", component="Conspiracy Beliefs", name = "Personal Wellbeing")
 )
@@
   data,
-  make_rez(with = "LIE_Ability", component="Lying Profile", name = "Ability"),
-  make_rez(with = "LIE_Frequency", component="Lying Profile", name = "Frequency"),
-  make_rez(with = "LIE_Contextuality", component="Lying Profile", name = "Contextuality"),
-  make_rez(with = "LIE_Negativity", component="Lying Profile", name = "Negativity")
+  pool_coef(with = "LIE_Ability", component="Lying Profile", name = "Ability"),
+  pool_coef(with = "LIE_Frequency", component="Lying Profile", name = "Frequency"),
+  pool_coef(with = "LIE_Contextuality", component="Lying Profile", name = "Contextuality"),
+  pool_coef(with = "LIE_Negativity", component="Lying Profile", name = "Negativity")
 )
@@
 # names(df14) # MAIA, TAS, MFQ(DEP), STAI(ANX)
-# names(df15)
+# names(df15) #
+# names(df16) #
 

### 2025-08-18 analysis/Study1.qmd
calculated PI_Alive dimension for  df13

@@
     MAIA_NotWorrying_5_R = 1 - MAIA_NotWorrying_5_R) |>
-    mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5))))
+    mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5))),
+           across(starts_with("PI18_"), \(x) datawizard::rescale(x, to = c(0,1)))) |>
+  mutate(
+    PI_Alive = (PI18_GA_2 + PI18_GA_14 + (1-PI18_A_12_R) + PI18_A_16 + PI18_A_4)/5)
 

### 2025-08-18 analysis/study2.qmd
study2 html

@@
 ```{r}
+# names(df10)[str_detect(names(df10), "PI_Alive")]
+# names(df12)[str_detect(names(df12), "PI_Alive")]
+# names(df13)[str_detect(names(df13), "PI_Alive")]
 
-data <- rbind(data, pool_coef(with = "PI_Alive", component="World Beliefs", name = "Alive"))
+data <- rbind(
+  data, 
+  pool_coef(with = "PI_Alive", component="World Beliefs", name = "Alive", unequalrange=TRUE))
 

### 2025-08-18 analysis/study2.qmd
updated html

@@
 ```{r}
+#| warning: false
+
 # names(df2)[str_detect(names(df2), "MAIA")]  
@@
 ```{r}
+#| warning: false
+
 # names(df2)[str_detect(names(df2), "ICQ")] 
@@
 ```{r}
+#| warning: false
+
 # df3$BPQ_BodyAwareness <- -1*normalize(df3$BPQ_BodyAwareness)
@@
 ```{r}
+#| warning: false
+
 #  only one study assess alexithymia with BVAQ (df2)
@@
 ```{r}
+#| warning: false
+
 # names(df6)[str_detect(names(df6), "PHQ")] 
@@
 ```{r}
+#| warning: false
+
 # names(df6)[str_detect(names(df6), "GAD")] 
@@
 ```{r}
+#| warning: false
+
 data <- rbind(
@@
 ```{r}
+#| warning: false
+
 #  names(select(df10, starts_with("ASQ")))
+
 data <- rbind(
@@
 ```{r}
+#| warning: false
+
 # names(df7a)[str_detect(names(df7a), "NEO")]
@@
 ```{r}
+#| warning: false
+
 # names(df10)[str_detect(names(df10), "PI_Alive")]
@@
 ```{r}
+#| warning: false
 #| fig-height: 20

### 2025-08-19 analysis/study2.qmd
commented-out scales not used in correlations

@@
 #  only one study assess alexithymia with BVAQ (df2)
-# names(df2)[str_detect(names(df2), "TAS")]
+# names(df2)[str_detect(names(df2), "TAS", "BVAQ)]
 # names(df3)[str_starts(names(df3), "TAS")]
@@
 -   BAQ - Body awareness questionnaire
--   BRS - the body responsiveness scale
+<!-- -   PBCS - The Private Bodily Consciousness Scale -->
+<!-- -   BRS - the body responsiveness scale -->
 -   PHQ-2 - Patient Health Questionnaire 2 items on major depressive episodes
@@
 -   PHQ-15 - Patient Health Questionnaire 15-Item Version assesses Somatic symptom distress
--   SSS-8 - Somatic Symptom Scale
--   IATS - Interoceptive Attention Scale
+<!-- -   SSS-8 - Somatic Symptom Scale -->
+<!-- -   IATS - Interoceptive Attention Scale -->
 -   GAD-2 - Generalized Anxiety Disorder Scale 2 items on anxiety disorder
@@
 -   NEOFFI - Neuroticism Neo Five-Factor Inventory Neuroticism subscale
--   ASI - Anxiety Sensitivity Inventory 3
+<!-- -   ASI - Anxiety Sensitivity Inventory 3 -->
 -   BDI - The Beck Depression Inventory
--   EDI_IA - Eating Disorder Inventory, interoceptive awareness subscale
+<!-- -   EDI_IA - Eating Disorder Inventory, interoceptive awareness subscale -->
 -   BFI - Big Five inventory-10
 -   ASQ - Autism-Spectrum Quotient
--   MSI-BPD - Mclean Screening Instrument for Borderline Personality Disorder
+<!-- -   MSI-BPD - Mclean Screening Instrument for Borderline Personality Disorder -->
 -   GCB - Generic Conspiracist Beliefs scale

### 2025-08-24 analysis/Study1.qmd
minor

@@
 table <- data.frame(
+  Sample = c('', 'Sample 1a', 'Sample 1b', 'Sample 2', 'Sample 3', 'Sample 4', 'Sample 5', 'Sample 6', '', 'Sample 7a', 'Sample 7b', 'Sample 7c', '', 'Sample 8a', 'Sample 8b', 'Sample 9', 'Sample 10', 'Sample 11', 'Sample 12', 'Sample 13', 'Sample 14', 'Sample 15', 'Sample 16'),
   Reference = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Makowski et al., (2023c)', 'Makowski et al., (2024)', 'Poerio et al., (2024)', 'Poerio et al., unpublished', 'Total'),
-  Sample = c('', 'Sample 1a', 'Sample 1b', 'Sample 2', 'Sample 3', 'Sample 4', 'Sample 5', 'Sample 6', '', 'Sample 7a', 'Sample 7b', 'Sample 7c', '', 'Sample 8a', 'Sample 8b', 'Sample 9', 'Sample 10', 'Sample 11', 'Sample 12', 'Sample 13', 'Sample 14', 'Sample 15', 'Sample 16'),
   Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', 'English', 'English', 'English', 'English',''),
@@
 gt_apastyle(table_apa, font.size=12)
-gtsave(gt_apastyle(table_apa, font.size=9), "figures/table1.tex")
+# gtsave(gt_apastyle(table_apa, font.size=9), "figures/table1.tex")
+saveRDS(table, "figures/table1.rds")
 
@@
   ggplot(aes(x = x, y = y, color = Parameter)) +
-  geom_line(aes(linetype = Parameter), linewidth = 0.7) +
+  geom_line(aes(linetype = Parameter), linewidth = 0.5) +
   scale_color_material_d() +
@@
   guides(color = guide_legend(ncol = 1)) +
-  facet_wrap(~Sample, scales = "free_y", nrow = 3) +
+  facet_wrap(~Sample, scales = "free_y", nrow = 4) +
   theme_minimal() +

### 2025-08-24 paper/1_Initial/manuscript.qmd
update
minor

@@
 Small positive correlations have also been observed with the "observation" and "description" subscales of the Five Facet Mindfulness Questionnaire [FFMQ, @baer2006using; @brand2023; @koike2023], as well as with the "non-reactivity" and "acting with awareness" subscales [@koike2023].
-Additionally, the IAS has shown a positive correlation with the interoceptive awareness subscale of the EDI **Write full name** [EDI, @lin2023] and a negative correlation with the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia], as reported by @brand2023 and @murphy2019.
-Lastly, the correlation with the Interoceptive Attention Scale [IATS, @gabriele2022dissociations] **is that the ref for the scale validation?** appears rather small [@lin2023; @koike2023].
+Additionally, the IAS has shown a positive correlation with the interoceptive awareness subscale of the EDI [**ANA Write full name**] [EDI, @lin2023] and a negative correlation with the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia], as reported by @brand2023 and @murphy2019.
+Lastly, the correlation with the Interoceptive Attention Scale [IATS, @gabriele2022dissociations] [**ANA is that the ref for the scale validation?**] appears rather small [@lin2023; @koike2023].
 
@@
 We also included the data of four unpublished studies.
-A total of 14 datasets was included (see **Table 1**).
+A total of 16 datasets was included (see **Table 1**).
 
@@
 
-\begin{landscape}
+<!-- \begin{landscape} -->
 
-\input{../../analysis/figures/table1.tex}
+<!-- \input{../../analysis/figures/table1.tex} -->
 
-\end{landscape}
+<!-- \end{landscape} -->
+
+```{r}
+#| label: tbl-table1
+#| tbl-cap: My Table
+#| apa-note: "*Information taken from the sample description of relevant paper rather than recomputed."
+#| apa-twocolumn: true
+
+library(flextable)
+set_flextable_defaults(font.size = 7)
+
+table <- readRDS("../../analysis/figures/table1.rds")
+
+table |> 
+  dplyr::rename("Age (Mean  ± SD)" = Age,  "Female %" = Female_Percentage)  |> 
+  flextable() |> 
+  theme_apa() 
+```
 
@@
 In other words, participants are most likely to answer 4/5 (i.e., agree) on most items, with the exception of "blood sugar" and "bruise", which exhibit a different distributional pattern with a lower mode (\~2/5).
+While it is not a problem *per se*, the contrasting distribution might be indicative of items with non-homogeneous psychometric "difficulty".
 This is also the case for "affective touch" in samples 8a and 8b (the Chinese validation samples), which might indicate localisation issues.
@@
 These patterns consistently appeared in most samples when considered individually.
+We removed "tickle" from further analysis due to its high redundancy (and because it is absent from some datasets due to translation issues).
 
@@
 
-![**Figure 2.** Correlates of the IAS](figures/clipboard-1619164537.png){width="911"}
-
 ## Discussion

### 2025-08-25 analysis/Study1.qmd
update

@@
   'Difference' = c('','', '', '', '', '', '', '', '', '', '', '', '', 'Collapsed "Itch" and "Tickling"', 'Collapsed "Itch" and "Tickling"', '', 'Analog scales.
-Does not include temperature, blood sugar and cough items.', 'Analog scales', 'Analog scales', '', '', '', ''),
+No Temp, Blood sugar and Cough', 'Analog scales', 'Analog scales', '', '', '', ''),
   Age = c('', make_age(df1a$Age), make_age(df1b$Age), make_age(df2$Age), make_age(df3$Age), "48.6.6 ± 14.1*", make_age(df5_attention$Age), make_age(df6$Age),'', make_age(df7a$Age), make_age(df7b$Age), make_age(df7c$Age),'', make_age(df8a$Age), make_age(df8b$Age), make_age(df9$Age), make_age(df10$Age), make_age(df11$Age), make_age(df12$Age), make_age(df13$Age), make_age(df14$Age), make_age(df15$Age), '48.6 ± 13.1'),
@@
 ```{r}
+#| fig.width: 8
+#| fig.height: 12
+
 make_hclust <- function(data) {
@@
 #| warning: false
+#| fig.width: 8
+#| fig.height: 12
 
@@
 ```{r}
+#| fig.width: 8
+#| fig.height: 12
+
 make_efa <- function(data, n = 3, cols = c("F1" = "#009688", "F2" = "#795548", "F3" = "red")) {
@@
 #| message: false
+#| fig.width: 8
+#| fig.height: 12
 
@@
 ```{r}
+#| fig.width: 8
+#| fig.height: 12
+
 rez_efa <- make_efa(data_allf, n = 3, cols = 

### 2025-08-25 analysis/study2.qmd
update

@@
 
-data <- rbind(data, pool_coef(with = "ICQ", component="ICQ", name = "ICQ", unequalrange=TRUE))
+data <- rbind(data, pool_coef(with = "ICQ", component="Alexithymia", name = "ICQ", unequalrange=TRUE))
 ```
@@
   scale_linewidth_continuous(range = c(3, 7), guide = "none") +
-  coord_cartesian(xlim = c(-0.4, 0.4)) +
+  coord_cartesian(xlim = c(-0.45, 0.45)) +
   theme_modern(axis.title.space = 5) +

### 2025-08-25 paper/1_Initial/manuscript.qmd
update

@@
 floatsintext: true
-numbered-lines: true
+numbered-lines: false
 bibliography: bibliography.bib
@@
 #| label: tbl-table1
-#| tbl-cap: My Table
+#| tbl-cap: "Description of the samples used in the study."
 #| apa-note: "*Information taken from the sample description of relevant paper rather than recomputed."
@@
 library(flextable)
-set_flextable_defaults(font.size = 7)
+set_flextable_defaults(font.size = 6)
 
@@
   flextable() |> 
+  set_table_properties(layout = "autofit", opts_pdf=list(arraystretch=1)) |> 
   theme_apa() 
@@
 <!-- UVA -->
-After examining the distributions to all IAS items, we will test for "redundant" items (e.g., due to multicollinearity or local dependency) using Unique Variable Analysis [UVA, @christensen2023unique], a novel method derived from network psychometric designed to identify and merge items that share substantial variance (which can distort the structure estimation).
-We will use a threshold of 0.25, suggested to optimally balances accuracy and false positives **[REF NEEDED]**.
+After examining the distributions and correlations of all IAS items, we will test for "redundant" items (e.g., due to multicollinearity or local dependency) using Unique Variable Analysis [UVA, @christensen2023unique], a novel method derived from network psychometric designed to identify and merge items that share substantial variance (which can distort the structure estimation).
+We will use a threshold of 0.30 that detects large to very large overlap.
+
+Following the analysis of items, we will analyze the factor structure of the IAS using three different approaches, each with particular trade-offs and assumptions, to provide a multi-verse picture of likely solutions.
+Namely, we will apply traditional exploratory and confirmatory Factor Analysis (EFA/CFA), hierarchical clustering (HCA), and Exploratory Graph Analysis (EGA), to the whole sample, as well as to each dataset separately (details being available in the analysis document at https://github.com/RealityBending/InteroceptionIAS), and our decisions and conclusions will try to take into account both levels of analysis.
 
 <!-- EGA -->
-Following the analysis of items, we will analyze the factor structure of the IAS using two different approaches, namely traditional exploratory and confirmatory Factor Analysis (EFA/CFA) and Exploratory Graph Analysis (EGA).
 By combining network analysis with psychometric methods, the recently-developed EGA framework allows to jointly estimate the number of dimensions (i.e., groups of items), the structure as well as its stability [@golino2017exploratory; @golino2020investigating].
@@
 Clustering these nodes reveals distinct communities of related items, in practice akin to traditional latent factors - but without explicitly assuming their presence [@christensen2021equivalency]. 
+We used the EGAnet package [@christensen2021estimating] to fit a hierachical EGA with the Leiden community detection algorithm.
 
@@
 A critical step in factor analysis is determining the optimal number of factors, for which we will used the Method Agreement Procedure [@ludecke2021performance], which involves a consensus-based decision based on multiple factor estimation methods applied concurrently.
+
+<!-- HCA -->
+Finally, we will also apply Hierarchical Clustering Analysis [HCA, @murtagh2014ward], which differs from factor analysis in that it does not assume any latent source of variability, but instead iteratively groups items based on their similarity (e.g., correlation) into a hierarchy of clusters.
+The benefits of HCA include its interpretability and ability to capture complex relationships among items without relying on strict assumptions about data distribution or latent variables.
+
+<!-- CFA -->
+In a typical 2-step fashion, this first analysis run will be followed by a structure refinement with a further selection of items, and the final pool of items will be tested again.
+Additionally, various solutions (e.g., adding general factors) will be statistically compared using Confirmatory Factor Analysis (CFA).
 
@@
 The samples using an analogue scale (samples 10a, 10b and 10c in the figure) display a more continuous and progressive spread of answers, seemingly improving the interindividual variability, although potentially displaying a secondary lower mode at \~2 (which might be suggesting the existence of potential clusters of participants).
+The correlation matrix between all items shows an overall positive correlation pattern, with highly correlated pairs of items (e.g., Tickle-Itch, Urinate-Defecate, Pain-Wind, Hungry-Thursty) or triplets (Vomit-Sneeze-Cough, Temperature-Muscles-Pain).
 
@@
 #| out-width: "100%"
-#| fig-cap: "Distribution of responses across datasets reveals a consistent modal value, typically around 4 or 5 (indicating agreement), except for 'blood sugar' and 'bruise' - in dashed lines - and 'affective touch' (dotted lines) in the Chinese validation sample, which have lower modes.
+#| fig-cap: "Top: Distribution of responses across datasets reveals a consistent modal value, typically around 4 or 5 (indicating agreement), except for 'blood sugar' and 'bruise' - in dashed lines - and 'affective touch' (dotted lines) in the Chinese validation sample, which have lower modes.
 Most responses cluster around the middle values, with few extreme scores (1 and 5).
 Samples using an analogue scale (10a, 10b, 10c) show a more continuous distribution and increased interindividual variability.
-Since most samples use Likert scales (discrete), the density plots may not be the most accurate representation but were chosen to clearly highlight variability patterns in the data."
+Since most samples use Likert scales (discrete), density plots may not be the most accurate representation but were chosen to clearly highlight variability patterns in the data.
+Bottom: The correlation matrix between all items shows an overall positive correlation pattern, with correlated pairs (e.g., Wind, Burp) of items or triplets (e.g., Vomit, Sneeze and Cough)."
 
@@
 
-<!-- Network analysis and Structure stability -->
-The EGA analysis employed a sparse Gaussian graphical model (GGM) with the graphical lasso (glasso) method.
-We applied the Walktrap (**REF**) and the Louvain (**REF**) algorithms for clusters identification, which yielded a five and four clusters solution, respectively.
-The four-cluster solution appeared as being more stable (based on the bootstrapped stability analysis: it had a higher proportion of items consistently assigned to the same cluster across bootstrap samples).
-In this solution, item stability for all variables exceeded 0.90, except for "affective touch".
-The first cluster included skin-related items "itch", "tickle", "bruise", and "blood sugar"; the second cluster contained expulsion-related items "burp", "wind", "cough", "sneeze", and "vomit"; the third cluster (**NAME or interpretation?**) comprised "affective touch", "sexual arousal", "muscles", "temperature", "pain", and "taste"; and the fourth cluster included visceroceptive items like "heart", "breathing", "hungry", "thirsty", "urinate", and "defecate".
-This solution was generally consistent when applied to samples separately.
+<!-- Initial run -->
+The HCA highlighted pairs and triplets of items consistently grouped together across samples, such as "wind" and "burp", "sneeze" and "cough", "itch" and "bruise", "urinate" and "defecate", and "pain", "muscles", and "temperature".
+This pattern was largely replicated by the EGA, with the additional presence of a unique cluster comprising "Sex arousal", "Affective touch", "Temperature", "Pain", "Muscles", and "Taste".
+EFA suggested the optimal number of factors to be 3, yielding one dimension with expulsion-related items ("burp", "wind", "cough", "sneeze", and "vomit"), a second dimension with visceroceptive items ("heart", "breathing", "hungry", "thirsty", "urinate", and "defecate"), and a third dimension with skin-related items ("bruise" and "blood sugar").
 
-<!-- Factor analysis -->
+<!-- We discarded: -->
 
-Regarding Factor Analysis, the Method Agreement Procedure recommended a four-factor solution for the whole sample.
-A four-factor solution was extracted using an *oblimin* rotation, accounting for 41.58% of the total variance.
-The first factor (14.45%) included items "burp", "cough", "wind", "sneeze", "vomit", "temperature", "sexual arousal" and "taste".
-The second factor (11.76%) included "breathing", "hungry", "heart", "thirsty", "pain", "muscles", "blood sugar", and "bruise".
-The third factor (8.09%) contained skin-related items "tickle", "itch" and "affective touch", and the final factor (7.28%) included "urinate" and "defecate".
-Notably, this structure differed from that suggested by EGA.
+<!-- Taste: Lone item + unstable -->
+<!-- Affective_touch: Cross-loadings + unstable -->
+<!-- Vomit: Less strongly associated -->
+<!-- Itch: Less strongly associated, did not form consistent cluster -->
+<!-- More controversial: Temp and Sex_arousal: similar cluster yet less reliable -->
 
-<!-- EGA clusters 
-c1- "itch", "tickle", "bruise", "blood sugar
-c2- burp", "wind", "cough", "sneeze", "vomit"
-c3 - affective touch", "sexual arousal", "muscles", "temperature", "pain", and "taste"
-c4- "heart", "breathing", "hungry", "thirsty", "urinate", and "defecate"
+Importantly, this initial structure analysis run highlighted some problematic items: "taste" typically displayed a lone or unstable pattern of associations, "affective touch" exhibited cross-loadings and instability, "vomit" was less strongly associated with other items, and "itch" did not form a consistent cluster.
+Finally, "temperature" and "sexual arousal" showed redundant patterns of associations but were less reliable.
+These 6 items were thus removed, and a second run of structure analysis was performed on the remaining 14 items.
 
-<!-- FA clusters -->
-<!-- c1 - burp, cough, wind, sneeze, vomit, temp, sexual arousal, taste
-c2 - breathing, hungry, heart, thirsty, pain, muscles , blood sugar, bruise
-c3 - tickle, itch, affective touch,
-c4 - urinate, defecate -->
+```{r}
+#| warning: false
+#| label: fig-structure
+#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
+#| out-width: "100%"
+#| fig-cap: "TODO."
 
-<!-- Item selection -->
-**UVA**, then re-run EGA and EFA. Then CFA.
+knitr::include_graphics("../../analysis/figures/Figure2.png")
+```
+
+<!-- Second run -->
+HCA and EGA yielded highly consistent results, emphasizing pairs of items, namely Hungry-Thirsty, Bruise-Blood sugar, Urinate-Defecate, Muscles-Pain, Breathing-Heart, Cough-Sneeze, Wind-Burp.
+HCA also significantly grouped the Urinate-Defecate and Muscles-Pain pairs, as well as expulsion items (Wind-Burp and Cough-Sneeze).
+EFA suggested once again 3 factors as the optimal solution, with the first factor including expulsion-related items ("burp", "wind", "cough", "sneeze"), the second factor being related to the Urinate-Defecate pair, and the third factor comprising the remaining items.
+
+<!-- CFA Model Comparison -->
+<!-- Name	BIC	RMSEA	Chi2	CFI	BF -->
+<!-- fit_g	933909.6	0.124	27,249.398	0.783	Inf -->
+<!-- fit_ega	1101773.3	0.035	2,306.303	0.984	NA -->
+<!-- fit_egag	1106163.9	0.054	6,842.382	0.952	0 -->
+<!-- fit_hclust	1112649.0	0.078	13,296.328	0.907	0 -->
+<!-- fit_hclustg	1113829.4	0.078	14,528.732	0.898	0 -->
+<!-- fit_efag	1115871.0	0.083	16,591.054	0.883	0 -->
+<!-- fit_efa	1115871.0	0.083	16,591.054	0.883	0 -->
 
 <!-- CFA -->
-We then attempted at testing various candidate structures using confirmatory factor analysis (CFA).
+We then fitted and compared using CFA various candidate structures emerging from the previous analyses, including a 1-factor model (the G-model), a 3-factor model (EFA), a 3+1 model (EFA + general factor), a 5-factor model (HCA), a 5+1 model (HCA + general factor), a 7-factor model (EGA), and a 7+1 model (EGA + general factor).
+The EGA model with 7 factors of item pairs provided the best fit with the lowest RMSEA (0.035), lowest $\chi^2$ (2306.30), highest CFI (0.984).
+It was followed by the EGA + general factor model (RMSEA = 0.054, $\chi^2$ = 6842.38, CFI = 0.952), and the HCA model with 5 factors (RMSEA = 0.078, $\chi^2$ = 13296.33, CFI = 0.907).
+The other models performed poorly, with RMSEA > 0.08 and CFI < 0.90.
+The unique-factor model yielded the lowest BIC (which takes into account the number of factors), followed by the EGA model.
+All the other models displayed significantly (BIC-based Bayes Factor < 1/100) lower evidence compared to the EGA model.
 
-Throughout the EGA and EFA analyses, the item "tickle" was consistently identified as redundant and was flagged for removal in the UVA analysis. 
-It also demonstrated the lowest uniqueness value in the factor analysis, leading to its exclusion from further analysis.
-Similarly, several "ambiguous" items — such as "temp", "vomit", "affective touch", "sexual arousal", and "taste" — were removed due to their context-dependent nature as well as weak loadings on multiple factors, which may compromise measurement consistency and reduce the clarity of factor structure.
-
-<!-- Confirmatory factor analysis -->
-CFA was performed to identify the best-fitting model for the data. 
-A total of five models were computed: Model 1 assumed a general interoception factor (1-factor solution), Model 2 proposed four factors, Model 3 assumed five factors, Model 4 proposed six factors, and Model 5, the most refined model, separated the factors into smaller, more specific groups, resulting in a 7-factor solution.
-
-<!-- Model Fit + lower-level factors + high-order factors-->
-The results of model comparison indicate that the Model 5 - with 7 factors  - had the best fit among all the models (AIC = -171638, BIC = -171228, χ² (56) = 2195.20, p < .001). 
-Parameter estimates for the model with 7 factors were also analyzed, with all factor loadings found to be significant (p < .001) and standardized coefficients ranging from 0.50 to 0.82. 
-Furthermore, the correlations between latent factors were all significant, ranging from 0.43 to 0.80, with the strongest correlation observed between ItchBruise and MusclesPain (0.80).
-
-<!-- higher- level factors -->
-To assess whether the inclusion of higher-order factors was justified, three models were evaluated. 
-Model 1 assumed one higher-order factor. 
-Model 2 introduced two higher-order factors, while Model 3 included three higher-order factors. 
-The baseline model, which consisted of 7 factors, was compared with these alternative models. 
-The results indicated that the baseline model provided the best fit (AIC = -171638, BIC = -171228, χ²(56) = 2195.20, p < .001), suggesting no evidence to support the inclusion of higher-order factors.
-
-<!-- Model Performance -->
-When taking acount all the samples, the fit statistics indicated a very good model fit (χ²(56) = 2195.20, p < .001, RMSEA = 0.03, CFI= 0.98 SRMR = 0.92) for the model with 7-factors.
-These fit statistics collectively suggest that the model adequately represents the data structure.
-Overall, the CFA results suggest that Model 7 provides the best fit for the data, with significant factor loadings and strong correlations between the factors.
+**ANA TODO: This result was relatively consistent across unique datasets, ...**
 
@@
 
-The comprehensive structural analysis of a large body of IAS item-level datasets revealed a 4-factor model as the most appropriate solution when taking into account all the items in the scale. 
-These findings contrast with previous research which all found that 2-factor model [@murphy2019; @koike2023], 1-factor model [@brand2023] and bifactor model [@lin2023; @campos2021] fits the data best.
-While this analysis also revealed an okay fit for the 1-factor model, the 4-factor model was ultimately superior.
-Notably, this 4-factor solution was found in both the EGA and EFA analysis, altough groupings differed.
-
-<!-- EGA groupings -->
-The EGA analysis revealed different ‘hubs' of items that are related, not only in this structure analysis, but also in underlying mechanisms.
-The ‘wind-burp-cough-sneeze-vomit' category, for example, only entails items that are linked to excretion through the mouth. 
-The 'heart-breathing-hungry-urinate-defecate' category includes items linked to basic physiological functions essential for homeostasis and survival.
-The 'affective-touch-sexual arousal-temperature-pain-taste-muscles' category represents sensations closely tied to both affective experiences and bodily awareness.
-Lastly, the 'tickle-itch-bruise-blood-sugar' category includes items that reflect more localized or transient bodily sensations, often linked to surface-level or metabolic responses.
-
-<!-- EFA groupings -->
-The EFA groupings, in contrast, revealed a less balanced division of items into clusters.
-One factor consisted of just two items—'urinate' and 'defecate'—while another contained three items—'tickle', 'itch', and 'affective touch'.
-Of notice is the loading for 'affective touch' as 0.33, barely meeting the acceptable threshold of >0.32 [@costello2005best], while the other items in this factor had loadings above 0.75.
-
-<!-- CFA -->
-While the 4-factor structure repeatedely showed up reagrdless of the dimensionality method, some items were flagged as redudant and in particular 'tickle' was suggested to be removed. 
-Additionally, some items appear to be ambiguous, as their interpretation and grouping may be contextually dependent.
-For instance, sensations such as feeling one's heart beat faster and experiencing nausea-related urges to vomit often co-occur.
-This overlap is not merely coincidental; these sensations may reflect interconnected physiological processes, such as autonomic arousal or the body's stress response. 
-Such interdependencies challenge the assumption that IAS items neatly map onto distinct bodily sensations. 
-Empirical evidence further highlights item ambiguity. 
-Items such as 'taste' showed similarly weak loadings across multiple factors (0.24 for Factor 1 and 0.20 for Factor 3), falling below the commonly accepted threshold for meaningful loadings. 
-Likewise, 'temperature' loaded weakly on both Factor 1 (0.26) and Factor 3 (0.25), while 'sexual arousal' demonstrated similarly low and split loadings (0.25 to Factor 1 and 0.23 to Factor 3). 
-Although 'vomit' showed a slightly stronger loading on Factor 1, its context-dependent nature further complicates its conceptual clarity.
-Consequently, refining the scale by removing items with overlapping or ambiguous content could enhance its precision, ensuring that each item captures a unique and meaningful aspect of interoceptive awareness.
-Based on this, the CFA was conducted with 14 items out of the 21, suggetsing that 7-factors (i.e., pairs of items) is the model with the best fit for the data.
-
-<!-- Recomendations -->
-There are couple recomendations that follow from this mega-analysis on the IAS.
-The findings indicate a high proportion of answers at 4 (see @fig-distributions), especially when using a 5-step scale.
-The analogue scale shows a more dispersed distribution, with some answers indicating the highest 5/5, which was not the case in Likert-scales.
-Therefore, we recommend using an analog scale for the IAS, which provides a novel approach to improving the scale in a simple manner.
-
-<!-- removal of tickle and potential for a short version of the IAS -->
-Secondly, there are several items that show redundancy suggesting that adapting the IAS would be beneficial for validity.
-Based on the given results, we suggest removing the tickle, while keeping the itch item  \[wTO = 0.364\].
-Other items with moderate redundancy include 'wind' and 'burp', as well as 'urinate' and 'defecate'. 
-Additionally, there are pairs with slight redundancy, such as 'hungry' and 'thirsty', 'sneeze' and 'cough', and 'heart' and 'breathing'.
-Interestingly, @lin2023 also found redundancy between 'tickle' and 'itch', ultimately deciding to exclude the former due to the fact that the characters for both terms are identical in the Chinese language.
-In contrast, @campos2021 also found 'tickle' to be redudant but did not suggest excluding it from the analysis.
-@lin2023 also developed a shortened version of the IAS, removing additional items to create a 12-item scale, including the following items:'hunger', 'breath', 'urinate', 'taste', 'vomit', 'cough', 'temperature', 'sexual arousal', 'wind', 'muscle', 'pain', and 'itch'.
-As demonstrated by @lin2023, reducing redundancy and streamlining the scale through a short-form IAS can improve the model fit and enhance the scale's unidimensionality, ultimately making it a more efficient tool for assessing interoceptive accuracy.
-<!-- ...aligns with our findings, suggesting that further items are ambiguous as to whether they should be removed. -->
-
-<!-- Context-specific items -->
-
-The IAS aims to measure subjective interoceptive accuracy by assessing individuals' self-reported ability to detect internal bodily sensations. 
-However, the interpretation of these sensations is highly dependent on their physiological context. 
-Sensations such as heart rate acceleration, breathing changes, or muscle soreness can arise in diverse contexts — for instance, during exercise, emotional arousal, or illness. 
-Without considering the underlying physiological context, individuals may misattribute these sensations to different causes, potentially confounding their self-assessments.
-For example, a fast heartbeat may be accurately detected but interpreted as anxiety rather than exertion.
-Similarly, sensations like nausea or sexual arousal may fluctuate in intensity depending on contextual factors such as stress, fatigue, or hormonal cycles.
-In fact, previous research has highlighted the need for interoceptive questionnaires to prioritize neutral bodily sensations that are less susceptible to cognitive or emotional reinterpretation [@vlemincx2023novel].
-
-<!-- Conclusion -->
-In conclusion this study provided valuable insights into the structure and content of the IAS. 
-While the original factor structure was not replicated, our findings revealed a more stable 4-factor model that emerged across both EGA and EFA approaches. 
-This structure highlights meaningful item clusters that align with underlying physiological processes, improving our understanding of subjective interoceptive accuracy.
-However, our analysis also uncovered several limitations that warrant further attention. 
-The presence of redundant items (e.g., ‘tickle’) and items with ambiguous or weak factor loadings (e.g., ‘taste’ and ‘temperature’) suggests a need for scale refinement. 
-Adopting an analog scale format may further enhance variability and improve response accuracy. 
-Additionally, the observed overlap between context-dependent sensations underscores the importance of developing items that account for physiological contexts to minimize misattributions.
+**TODO.**
 
@@
 
-The second study focuses on the dispositional correlates of the IAS.
+<!-- The goal of study 2 is two-fold, 1) provide a robust overview of the dispositional correlates of the IAS by leveraging the large number of datasets available, and 2) assess the practical benefits of using a refined version of the IAS (i.e., the 14-item version identified in study 1) compared to the original 21-item one general factor version.
+-->
 
-Correlations of the IAS will be computed to assess the relationship between subjective interoceptive accuracy and other subjective measures of interoception, mood, psychopathology, personality, and beliefs.
-Investigating correlates will help validate the IAS, as well as other interoceptive measures in the future.
-
-<!-- what factor structure to choose -->
+**TODO**
 
@@
 ### Data Analysis
-
-Correlations will be computed using the correlation package under a Bayesian framework [@ben2020effectsize].
 

### 2025-08-26 analysis/study2.qmd
updated script with changes made in study1

@@
   data,
-  pool_coef(with = "PHQ2_Sum", component="Mood", name = "Depression (PHQ-2)"),
   pool_coef(with = "PHQ15_Sum", component="Mood", name = "Somatic Concerns (PHQ-15)",unequalrange=TRUE), 
@@
   pool_coef(with = "BDI_Sum", component="Mood", name = "Depression (BDI)"), 
-  pool_coef(with = "PHQ4_Depression", component="Mood", name = "Depression (PHQ-2)"),
+  pool_coef(with = "PHQ4_Depression", component="Mood", name = "Depression (PHQ-4)"),
   pool_coef(with = "DEP", component = "Mood", name = "Depression (MFQ)")
@@
   data,
-  pool_coef(with = "GAD2_Sum", component="Mood", name = "Anxiety (GAD-2)"), 
-  pool_coef(with = "STAIT_Sum", component="Mood", name = "Anxiety (STAI-T)",unequalrange=TRUE), 
+  pool_coef(with = "STAIT_Mean", component="Mood", name = "Anxiety (STAI-T)",unequalrange=TRUE), 
   pool_coef(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (PHQ-4)"),
-  pool_coef(with = "STAI5_General", component="Mood", name = "Anxiety (STAI-5)"),
   pool_coef(with = "GAD7_Sum", component="Mood", name = "Anxiety (GAD-7)")
@@
 #   data,
-#   make_rez(with = "PI_Alive", component="World Beliefs", name = "Alive"),
-#   make_rez(with = "PI_Changing", component="World Beliefs", name = "Changing"),
-#   make_rez(with = "PI_Enticing", component="World Beliefs", name = "Enticing"),
-#   make_rez(with = "PI_Good", component="World Beliefs", name = "Good"),
-#   make_rez(with = "PI_Hierarchical", component="World Beliefs", name = "Hierarchical"),
-#   make_rez(with = "PI_Safe", component="World Beliefs", name = "Safe"),
-#   make_rez(with = "PI_Understandable", component="World Beliefs", name = "Understandable"),
-#   make_rez(with = "PI_Alive", component="World Beliefs", name= "Alive"),
-#   make_rez(with = "PI_Changing", component="World Beliefs", name = "Changing"),
-#   make_rez(with = "PI_Enticing", component="World Beliefs", name = "Enticing"),
-#   make_rez(with = "PI_Good", component="World Beliefs", name = "Good"),
-#   make_rez(with = "PI_Hierarchical", component="World Beliefs", name = "Hierarchical"),
-#   make_rez(with = "PI_Safe", component="World Beliefs", name = "Safe"),
-#   make_rez(with = "PI_Understandable", component="World Beliefs", name = "Understandable")
+#   pool_coef(with = "PI_Alive", component="World Beliefs", name = "Alive"),
+#   pool_coef(with = "PI_Changing", component="World Beliefs", name = "Changing"),
+#   pool_coef(with = "PI_Enticing", component="World Beliefs", name = "Enticing"),
+#   pool_coef(with = "PI_Good", component="World Beliefs", name = "Good"),
+#   pool_coef(with = "PI_Hierarchical", component="World Beliefs", name = "Hierarchical"),
+#   pool_coef(with = "PI_Safe", component="World Beliefs", name = "Safe"),
+#   pool_coef(with = "PI_Understandable", component="World Beliefs", name = "Understandable"),
 # )

### 2025-08-26 paper/1_Initial/manuscript.qmd
added authors

@@
   flextable() |>
-  set_table_properties(layout = "autofit", opts_pdf=list(arraystretch=1)) |> 
+  set_table_properties(layout = "autofit", opts_pdf = list(arraystretch = 1)) |>
   theme_apa()

### 2025-08-26 analysis/Study1.qmd
minor

@@
     Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
-    PHQ2_Sum= PHQ2_sum,
-    GAD2_Sum = GAD2_sum
+    PHQ4_Depression= PHQ2_sum,
+    PHQ4_Anxiety = GAD2_sum
   ) 
@@
 
+df7a$STAIT_Mean <- df7a$STAIT_Sum/20
+
 df7b <- haven::read_sav("../data/Brand2023/Data_Mainz.sav") |> 
@@
 df7b$PHQ15_Sum <-rowSums(select(df7b,PHQ15_01:PHQ15_15recode), na.rm = TRUE)
-df7b$PHQ9_Sum <- rowMeans(select(df7b, PHQ9_01:PHQ9_09), , na.rm = TRUE)
+df7b$PHQ9_Sum <- rowMeans(select(df7b, PHQ9_01:PHQ9_09), na.rm = TRUE)
+df7b$STAIT_Mean <- df7b$STAIT_Sum/20
 
@@
 df7c$BPQ_BodyAwareness <- df7c$BPQ_sum / 26
+df7c$STAIT_Mean <- df7c$STAIT_Sum/20
 
@@
   mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5))),
-         across(starts_with("PI_"), \(x) datawizard::rescale(x, to = c(0, 1))))
+         across(starts_with("PI_"), \(x) datawizard::rescale(x, to = c(0, 1))),
+         across(starts_with("Item_PHQ4_Depression_"), \(x) datawizard::rescale(x, to = c(1,4))),
+        across(starts_with("Item_PHQ4_Anxiety_"), \(x) datawizard::rescale(x, to = c(1,4)))) |>
+  mutate(PHQ4_Depression = Item_PHQ4_Depression_3 + Item_PHQ4_Depression_4,
+          PHQ4_Anxiety = Item_PHQ4_Anxiety_1 + Item_PHQ4_Anxiety_2)
 ```
@@
     typeSample = Sample,
-    BDI_Sum = BDI2_Total
-  ) |>
+    BDI_Sum = BDI2_Total) |>
   mutate(
@@
     MAIA2_NotWorrying_5_R = 1 - MAIA2_NotWorrying_5_R) |> 
-  mutate(across(starts_with("MAIA2_"), \(x) datawizard::rescale(x, to = c(0, 5))))  |>
-   mutate(across(starts_with("PHQ4_Depression_"), \(x) datawizard::rescale(x, to = c(0, 4))),
-          across(starts_with("PHQ4_Anxiety_"), \(x) datawizard::rescale(x, to = c(0, 4)))) |>
-   mutate(PHQ4_Depression = (PHQ4_Depression_3 + PHQ4_Depression_4)/2,
-          PHQ4_Anxiety = (PHQ4_Anxiety_1 + PHQ4_Anxiety_2)/2) |>
+  mutate(across(starts_with("MAIA2_"), \(x) datawizard::rescale(x, to = c(0, 5))),
+         across(starts_with("PHQ4_Depression_"), \(x) datawizard::rescale(x, to = c(1,4))),
+         across(starts_with("PHQ4_Anxiety_"), \(x) datawizard::rescale(x, to = c(1,4))),
+         across(starts_with("STAI5_"), \(x) datawizard::rescale(x, to = c(1, 4)))) |>
+   mutate(PHQ4_Depression = PHQ4_Depression_3 + PHQ4_Depression_4,
+          PHQ4_Anxiety = PHQ4_Anxiety_1 + PHQ4_Anxiety_2,
+          STAIT_Mean = (STAI5_1 + STAI5_2 + STAI5_3 + STAI5_4 + STAI5_4 + STAI5_5)/5) |>
   datawizard::rescale(select=ias_vars, to = c(1, 5), range = c(0, 1))
@@
     TAS_EOT = (6-TAS20_5) + TAS20_8 + (6-TAS20_10) + TAS20_15 + TAS20_16 + (6-TAS20_18) + (6-TAS20_19) + TAS20_20)
+
+df14$STAIT_Mean <- df14$STAIT_Sum/20
+
 ```
@@
 - **Sample 15 **: Data from [Poreiro's] study , included `r report::report_participants(df15 , age = "Age", sex = NA, gender = "Gender")`
-- **Sample 16 **: Data from [Poreiro's] study , included `r report::report_participants(df16 , age = "Age", gender = "Gender")`
-
-Total N = `r nrow(df1a) + nrow(df1b) + nrow(df2) + nrow(df3) + nrow(df4) + nrow(df5) + nrow(df6) + nrow(df7a) + nrow(df7b) + nrow(df7c) + nrow(df8a) + nrow(df8b) + nrow(df9) + nrow(df10) + nrow(df11) + nrow(df12) + nrow(df13) + nrow(df14) + nrow(df15) +nrow(df16)`.
+- **Sample 16 **: Data from [Arjona's] study , included `r report::report_participants(df16 , age = "Age", gender = "Gender")`
+
+Total N = `r nrow(df1a) + nrow(df1b) + nrow(df2) + nrow(df3) + nrow(df4) + nrow(df5) + nrow(df6) + nrow(df7a) + nrow(df7b) + nrow(df7c) + nrow(df8a) + nrow(df8b) + nrow(df9) + nrow(df10) + nrow(df11) + nrow(df12) + nrow(df13) + nrow(df14) + nrow(df15) + nrow(df16)`.
 
@@
 table <- data.frame(
-  Sample = c('', 'Sample 1a', 'Sample 1b', 'Sample 2', 'Sample 3', 'Sample 4', 'Sample 5', 'Sample 6', '', 'Sample 7a', 'Sample 7b', 'Sample 7c', '', 'Sample 8a', 'Sample 8b', 'Sample 9', 'Sample 10', 'Sample 11', 'Sample 12', 'Sample 13', 'Sample 14', 'Sample 15', 'Sample 16'),
-  Reference = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Makowski et al., (2023c)', 'Makowski et al., (2024)', 'Poerio et al., (2024)', 'Poerio et al., unpublished', 'Total'),
-  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', 'English', 'English', 'English', 'English',''),
-  N = c('', nrow(df1a), nrow(df1b), nrow(df2), nrow(df3), nrow(df4), nrow(df5_attention), nrow(df6),'', nrow(df7a), nrow(df7b), 802,'', nrow(df8a), nrow(df8b), nrow(df9), nrow(df10), nrow(df11), nrow(df12), nrow(df13), nrow(df14), nrow(df15), 32993),
+  Sample = c('', 'Sample 1a', 'Sample 1b', 'Sample 2', 'Sample 3', 'Sample 4', 'Sample 5', 'Sample 6', '', 'Sample 7a', 'Sample 7b', 'Sample 7c', '', 'Sample 8a', 'Sample 8b', 'Sample 9', 'Sample 10', 'Sample 11', 'Sample 12', 'Sample 13', 'Sample 14', 'Sample 15', 'Sample 16', 'Sample 17'),
+  Reference = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Makowski et al., (2023c)', 'Makowski et al., (2024)', 'Poerio et al., (2024)', 'Poerio et al., unpublished', 'Arjona et al., unpublished', 'Total'),
+  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', 'English', 'English', 'English', 'English','English', ''),
+  N = c('', nrow(df1a), nrow(df1b), nrow(df2), nrow(df3), nrow(df4), nrow(df5_attention), nrow(df6),'', nrow(df7a), nrow(df7b), 802,'', nrow(df8a), nrow(df8b), nrow(df9), nrow(df10), nrow(df11), nrow(df12), nrow(df13), nrow(df14), nrow(df15), nrow(df16), 33272),
   'Difference' = c('','', '', '', '', '', '', '', '', '', '', '', '', 'Collapsed "Itch" and "Tickling"', 'Collapsed "Itch" and "Tickling"', '', 'Analog scales.
-No Temp, Blood sugar and Cough', 'Analog scales', 'Analog scales', '', '', '', ''),
-  Age = c('', make_age(df1a$Age), make_age(df1b$Age), make_age(df2$Age), make_age(df3$Age), "48.6.6 ± 14.1*", make_age(df5_attention$Age), make_age(df6$Age),'', make_age(df7a$Age), make_age(df7b$Age), make_age(df7c$Age),'', make_age(df8a$Age), make_age(df8b$Age), make_age(df9$Age), make_age(df10$Age), make_age(df11$Age), make_age(df12$Age), make_age(df13$Age), make_age(df14$Age), make_age(df15$Age), '48.6 ± 13.1'),
-  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76','18-50', '17, 87', '18-57', '18-60', '17-93'),
-  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', '50%*', '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '76%', '57.3%', '74.8%', '75.9%', '71.6%'),
+No Temperature, Blood sugar and Cough items', 'Analog scales', 'Analog scales', '', '', '', '', ''),
+  Age = c('', make_age(df1a$Age), make_age(df1b$Age), make_age(df2$Age), make_age(df3$Age), "48.6.6 ± 14.1*", make_age(df5_attention$Age), make_age(df6$Age),'', make_age(df7a$Age), make_age(df7b$Age), make_age(df7c$Age),'', make_age(df8a$Age), make_age(df8b$Age), make_age(df9$Age), make_age(df10$Age), make_age(df11$Age), make_age(df12$Age), make_age(df13$Age), make_age(df14$Age), make_age(df15$Age), make_age(df16$Age), '48.09 ± 13.1'),
+  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76','18-50', '17, 87', '18-57', '18-60', '18-79', '17-93'),
+  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', '50%*', '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '76%', '57.3%', '74.8%', '75.9%', '67.7%', '71.3%'),
   Availability= c('osf.io/3m5nh', '', '', 'osf.io/5x9sg', 'osf.io/j6ef3', 'osf.io/ms354', 'osf.io/mp3cy', 'osf.io/xwz6g', 'osf.io/3f2h6', '', '', '','osf.io/3eztd','', '', 'osf.io/7p9u5', 'github.com/RealityBending/IllusionGameReliability', 'github.com/DominiqueMakowski/PHQ4R', 'github.com/RealityBending/InteroceptionPrimals',
 'github.com/RealityBending/InteroceptionScale',
-'osf.io/49wbv', '','')
+'osf.io/49wbv', '','', '')
 )
@@
 gt_apastyle(table_apa, font.size=12)
-# gtsave(gt_apastyle(table_apa, font.size=9), "figures/table1.tex")
+gtsave(gt_apastyle(table_apa, font.size=9), "figures/table1.tex")
 saveRDS(table, "figures/table1.rds")
 
-# gtsave(table_apa, "figures/table1.png")
+gtsave(table_apa, "figures/table1.png")
 ```
@@
 ##### Summary
-- cfa did not converge
+
+Note: CFA did not converge
 
@@
 
+Note: CFA did not converge
+
 ```{r}
@@
 
+Note: CFA did not converge
+
 ```{r data3f}
@@
 Note: EGA errors.
+Note: CFA did not converge
 
@@
 ##### Summary
+
+Note: CFA errors.
 

### 2025-08-26 paper/1_Initial/manuscript.qmd
minor

@@
         postal-code: "BN1 9RH"
+        author:
+  - name: Giulia Poerio
+    orcid: 0000-0002-2343-5109
+    roles: 
+    affiliations:
+      affiliations:
+      - ref: "id1"
+      - name: "University of Sussex"
+        department:  "Sussex Centre for Consciousness Science"
+  - name: Magdalena Pfaff
+    orcid: 0009-0006-2386-7936
+    roles:
+      - Data curation
+      - Writing – original draft
+    affiliations:
+      - ref: "id1"
+  - name: Robyn Scharte
+      orcid: 
+      roles: 
+      affiliations:
+        - ref: "id1"
+  - name: Raquel Nogueira Arjona
+      orcid: 0000-0002-5998-701X
+      roles: 
+      affiliations:
+        - ref: "id1"
+        - name: "University of Sussex"
+          department: "Sussex Addictions Research and Intervention Centre"
 # author-note:
@@
     #   - Writing – original draft
-  - name: Magdalena Pfaff
-    orcid: 0009-0006-2386-7936
-    roles:
-      - Data curation
-      - Writing – original draft
-    affiliations:
-      - ref: "id1"
   - name: Dominique Makowski
@@
 To qualify for inclusion, papers needed to (1) provide accessible data in open-access, (2) employ the IAS as a measure, and (3) report individual IAS items scores.
-We also included the data of four unpublished studies.
+We also included the data of five unpublished studies.
 A total of 16 datasets was included (see **Table 1**).
 
-The total number of participants was 32,214 participants (Mean = 48.6 $\pm$ 13.1, 71.6\% Female).
+The total number of participants was 33,272 participants (Mean = 48.09 $\pm$ 13.1, 71.3\% Female).
 
@@
 
-**ANA TODO: This result was relatively consistent across unique datasets, ...**
+**ANA TODO:**
+
+This result was relatively consistent across unique datasets,
+
+<!-- did not converge: df1b, df2, df3, df5, df10 (missing items), df12 (errors), df15 (errors), df16,  -->
 

### 2025-08-27 paper/1_Initial/manuscript.qmd
completed study 1 discussion

@@
 Small positive correlations have also been observed with the "observation" and "description" subscales of the Five Facet Mindfulness Questionnaire [FFMQ, @baer2006using; @brand2023; @koike2023], as well as with the "non-reactivity" and "acting with awareness" subscales [@koike2023].
-Additionally, the IAS has shown a positive correlation with the interoceptive awareness subscale of the EDI [**ANA Write full name**] [EDI, @lin2023] and a negative correlation with the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia], as reported by @brand2023 and @murphy2019.
-Lastly, the correlation with the Interoceptive Attention Scale [IATS, @gabriele2022dissociations] [**ANA is that the ref for the scale validation?**] appears rather small [@lin2023; @koike2023].
+Additionally, the IAS has shown a positive correlation with the interoceptive awareness subscale of the Eating Disorder Inventory [EDI-IA; @lin2023] and a negative correlation with the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia], as reported by @brand2023 and @murphy2019.
+Lastly, the correlation with the Interoceptive Attention Scale [IATS, @gabriele2022dissociations] appears rather small [@lin2023; @koike2023].
 
@@
 The current study aims at 1) clarifying the structure of the IAS with a mega-analytic (which involves a re-analysis at the raw data level by aggregating datasets) approach that leverages existing data and contrast the traditional CFA/SEM factor-based analyses with network-based ones (Exploratory Graph Analysis);
-2) provide an overview of the dispositional correlates of the IAS, clarifying its general pattern of associations, which is key to better understand the nature, place and role of interoception questionnaires within a larger context.
+1) provide an overview of the dispositional correlates of the IAS, clarifying its general pattern of associations, which is key to better understand the nature, place and role of interoception questionnaires within a larger context.
 
@@
 
-**ANA TODO:**
-
-This result was relatively consistent across unique datasets,
+This result was relatively consistent across unique datasets with the EGA model providing the best fit.
+In all samples where CFA converged, it showed excellent performance with low RMSEA (≈ 0.025–0.046), high CFI (≥ 0.97), and substantially lower $\chi^2$ compared to alternative models.
+Adding a general factor systematically worsened fit, while hierarchical clustering and EFA-based models showed poorer performance (RMSEA > 0.06, CFI < 0.93).
+Although BIC values occasionally favored alternative specifications, Bayes factor comparisons overwhelmingly supported the EGA solution, confirming its robustness across datasets.
 
@@
 
-**TODO.**
+<!-- Aim of the study and previous factor structures -->
+
+The first study aimed to clarify the factor structure of the IAS, a widely used subjective measure of interoception whose dimensionality remains contested.
+Previous validation and psychometric studies have proposed conflicting models ranging from a single general factor [@brand2023] to bifactor [@campos2021; @lin2023], and two-factor solutions [@murphy2019; @koike2023].
+At the same time, network-based approaches such as EGA emphasize local dependencies between items, identifying clusters at the item level that may not map neatly onto broader latent constructs [@christensen2023; @desmedt2022measures].
+By leveraging open-access datasets and reanalyzing them both in aggregate and individually using a mega-analytic approach, and by contrasting traditional factor-analytic models with network-based methods, this study provides the most comprehensive test of the IAS structure to date.
+
+<!-- 7-pairs of items as optimal model -->
+
+Overall, the findings converge on a robust yet novel picture.
+Exploratory and confirmatory analyses indicated that the IAS is best characterized by seven pairs of closely related items, consistently identified by EGA and supported by HCA.
+These pairs (e.g., hunger–thirst, urinate–defecate, cough–sneeze) were highly replicable across independent samples and yielded superior fit indices in CFA compared to one-factor, three-factor, three-factor with ageneral factor, five-factor, a five-factor with a general factor, a 7-factor or a seven factor with a general factor alternatives.
+Although the one-factor model occasionally achieved lower BIC, Bayes factor comparisons overwhelmingly supported the EGA structure, underlining its empirical robustness.
+
+<!-- IAS not higher-order, but item-level dependencies -->
+
+This pattern has several important implications.
+First, it suggests that the IAS does not capture a broad latent construct of interoceptive accuracy as originally intended, but rather reflects a set of tightly coupled item clusters tied to specific bodily sensations.
+In other words, the IAS may function more as a checklist of bodily signal detection items than as a scale measuring a coherent higher-order dimension.
+This stands in contrast to the original two-factor proposal [@murphy2019], where the factors were highly correlated and often collapsed into a unidimensional score, and helps explain why subsequent studies diverged in their conclusions: the psychometric structure of the IAS appears to be driven more by local dependencies than by robust latent factors.
+Second, the presence of redundant or unstable items (e.g., tickle, taste, affective touch), already highlighted in prior validation studies [@campos2021; @lin2023], undermines the interpretability of the scale, as their contributions appear inconsistent or overlapping.
+Together, these findings help explain why previous research has struggled to converge on a stable factor structure: the IAS lacks the psychometric properties required for strong latent modeling and may overstate its dimensionality by conflating redundancy with structure.
+
+**[ADD THAT LIN CREATED A SHORT VERSION OF THE IAS??]**
+
+<!-- Improvements for the scale + proposal of a new scale-->
+
+At the same time, the results do not render the IAS unusable.
+The consistent emergence of item pairs highlights intuitive bodily domains (e.g., visceral, expulsion, musculoskeletal) that align with everyday interoceptive experiences, supporting its ecological validity.
+However, the limited breadth of these pairings, the redundancy across items, and the reliance on a narrow 5-point scale all restrict the scale’s ability to differentiate between individuals and to capture the multidimensional nature of interoception [@desmedt2022measures].
+These findings therefore call for refinement—either through targeted revisions of the IAS (e.g., removing redundant items, expanding modality coverage, adopting analogue response formats) or through the development of a new questionnaire that better balances theoretical coherence with empirical validity.
+
+<!-- Summary -->
+
+In sum, Study 1 demonstrates that the IAS structure is best described by clusters of tightly coupled item pairs reflecting local dependencies, rather than by a broad latent dimension.
+While this solution is replicable and statistically robust, it highlights the conceptual and psychometric limitations of the IAS in its current form.
+These insights help contextualize the mixed findings on the scale’s validity and correlations with other interoceptive measures [@murphy2019; @brand2023; @lin2023] and provide a crucial foundation for Study 2, where we  to the dispositional correlates of the IAS to further evaluate its construct validity and situate it within the broader network of interoceptive and psychological traits.
 
@@
 
-**TODO**
+## Study 2
+
+Building on the structural findings from Study 1, the second study turns to the validity of the IAS by examining its dispositional correlates.
+Although the IAS has been widely used, evidence regarding its associations with personality traits, affective dispositions, and related psychological constructs remains scattered and inconsistent.
+Study 2 therefore had two primary goals.
+First, to provide a robust overview of the dispositional correlates of the IAS by leveraging the large number of available datasets.
+Second, to evaluate the practical benefits of using the refined 14-item version of the scale identified in Study 1, compared to the original 21-item unidimensional version, in order to assess whether structural improvements translate into clearer and more reliable external associations.
 

### 2025-08-27 analysis/Study1.qmd
table 1 update

@@
   - Note: Analog scales
-  - note df12  = primals data
 
@@
 gt_apastyle(table_apa, font.size=12)
-gtsave(gt_apastyle(table_apa, font.size=9), "figures/table1.tex")
+# gtsave(gt_apastyle(table_apa, font.size=9), "figures/table1.tex")
 saveRDS(table, "figures/table1.rds")
 
-gtsave(table_apa, "figures/table1.png")
+# gtsave(table_apa, "figures/table1.png")
 ```

### 2025-08-27 analysis/figures/table1.tex
added sample 16 + computed BPQ dimensions
table 1 update

@@
 \toprule
-Reference & Sample & Language & N & Difference & Age (Mean  ± SD) & Range & Female \% & Availability \\ 
+Sample & Reference & Language & N & Difference & Age (Mean  ± SD) & Range & Female \% & Availability \\ 
 \midrule\addlinespace[2.5pt]
-Murphy et al., (2020) &  &  &  &  &  &  &  & osf.io/3m5nh \\ 
- & Sample 1a & English & 451 &  & 25.8 ± 8.4 & 18-69 & 69.4\% &  \\ 
- & Sample 1b & English & 375 &  & 35.3 ± 16.9 & 18-91 & 70.1\% &  \\ 
-Gaggero et al., (2021) & Sample 2 & English and Italian & 814 &  & 24.9 ± 5.3 & 18-58 & 60.3\% & osf.io/5x9sg \\ 
-Campos et al., (2022) & Sample 3 & Portuguese & 515 &  & 30.7 ± 10.5 & 18-72 & 59.6\% & osf.io/j6ef3 \\ 
-Todd et al., (2022) & Sample 4 & English & 802 &  & 48.6.6 ± 14.1* & 18-92* & 50\%* & osf.io/ms354 \\ 
-Arslanova et al., (2022) & Sample 5 & English & 143 &  & 28.5 ± 7.6 & 18-73 & 46.8\% & osf.io/mp3cy \\ 
-Brand et al., (2022) & Sample 6 & German & 619 &  & 43.9 ± 14.5 & 18-78 & 78.7\% & osf.io/xwz6g \\ 
-Brand et al., (2023) &  &  &  &  &  &  &  & osf.io/3f2h6 \\ 
- & Sample 7a & German & 522 &  & 23.4 ± 6.7 & 18-79 & 79.5\% &  \\ 
- & Sample 7b & German & 1993 &  & 32.0 ± 12.6 & 16-81 & 77.7\% &  \\ 
- & Sample 7c & German & 802 &  & 27.3 ± 9.3 & 18-72 & 68.9\% &  \\ 
-Lin et al., (2023) &  &  &  &  &  &  &  & osf.io/3eztd \\ 
- & Sample 8a & Chinese & 1166 & Collapsed "Itch" and "Tickling" & 32.5 ± 8.4 & 16-60 & 57.0\% &  \\ 
- & Sample 8b & Chinese & 500 & Collapsed "Itch" and "Tickling" & 37.4 ± 7.4 & 20-60 & 56.2\% &  \\ 
-VonMohr et al., (2023) & Sample 9 & English & 21843 &  & 56.5 ± 14.4 & 18-93 & 73.2\% & osf.io/7p9u5 \\ 
-Makowski et al., (2023a) & Sample 10 & English & 485 & Analog scales.
-Does not include temperature, blood sugar and cough items.
-& 30.1 ± 10.1 & 18-73 & 50.3\% & github.com/RealityBending/IllusionGameReliability \\
-Makowski et al., (2023b) & Sample 11 & English & 836 & Analog scales & 25.1 ± 11.3 & 17-76 & 53.0\% & github.com/DominiqueMakowski/PHQ4R \\ 
-Makowski et al., (2023c) & Sample 12 & English & 146 & Analog scales & 21.1 ± 4.3 & 18-50 & 76\% & github.com/RealityBending/InteroceptionPrimals \\ 
-Makowski et al., (2024) & Sample 13 & English & 737 &  & 36.8 ± 14.9 & 17, 87 & 57.3\% & github.com/RealityBending/InteroceptionScale \\ 
-Poerio et al., (2024) & Sample 14 & English & 107 &  & 26.8 ± 9.2 & 18-57 & 74.8\% & osf.io/49wbv \\ 
-Poerio et al., unpublished & Sample 15 & English & 131 &  & 30.9 ± 12.0 & 18-60 & 75.9\% &  \\ 
-Total & Sample 16 &  & 32993 &  & 48.6 ± 13.1 & 17-93 & 71.6\% &  \\ 
+ & Murphy et al., (2020) &  &  &  &  &  &  & osf.io/3m5nh \\ 
+Sample 1a &  & English & 451 &  & 25.8 ± 8.4 & 18-69 & 69.4\% &  \\ 
+Sample 1b &  & English & 375 &  & 35.3 ± 16.9 & 18-91 & 70.1\% &  \\ 
+Sample 2 & Gaggero et al., (2021) & English and Italian & 814 &  & 24.9 ± 5.3 & 18-58 & 60.3\% & osf.io/5x9sg \\ 
+Sample 3 & Campos et al., (2022) & Portuguese & 515 &  & 30.7 ± 10.5 & 18-72 & 59.6\% & osf.io/j6ef3 \\ 
+Sample 4 & Todd et al., (2022) & English & 802 &  & 48.6.6 ± 14.1* & 18-92* & 50\%* & osf.io/ms354 \\ 
+Sample 5 & Arslanova et al., (2022) & English & 143 &  & 28.5 ± 7.6 & 18-73 & 46.8\% & osf.io/mp3cy \\ 
+Sample 6 & Brand et al., (2022) & German & 619 &  & 43.9 ± 14.5 & 18-78 & 78.7\% & osf.io/xwz6g \\ 
+ & Brand et al., (2023) &  &  &  &  &  &  & osf.io/3f2h6 \\ 
+Sample 7a &  & German & 522 &  & 23.4 ± 6.7 & 18-79 & 79.5\% &  \\ 
+Sample 7b &  & German & 1993 &  & 32.0 ± 12.6 & 16-81 & 77.7\% &  \\ 
+Sample 7c &  & German & 802 &  & 27.3 ± 9.3 & 18-72 & 68.9\% &  \\ 
+ & Lin et al., (2023) &  &  &  &  &  &  & osf.io/3eztd \\ 
+Sample 8a &  & Chinese & 1166 & Collapsed "Itch" and "Tickling" & 32.5 ± 8.4 & 16-60 & 57.0\% &  \\ 
+Sample 8b &  & Chinese & 500 & Collapsed "Itch" and "Tickling" & 37.4 ± 7.4 & 20-60 & 56.2\% &  \\ 
+Sample 9 & VonMohr et al., (2023) & English & 21843 &  & 56.5 ± 14.4 & 18-93 & 73.2\% & osf.io/7p9u5 \\ 
+Sample 10 & Makowski et al., (2023a) & English & 485 & Analog scales. No Temperature, Blood sugar and Cough items & 30.1 ± 10.1 & 18-73 & 50.3\% & github.com/RealityBending/IllusionGameReliability \\ 
+Sample 11 & Makowski et al., (2023b) & English & 836 & Analog scales & 25.1 ± 11.3 & 17-76 & 53.0\% & github.com/DominiqueMakowski/PHQ4R \\ 
+Sample 12 & Makowski et al., (2023c) & English & 146 & Analog scales & 21.1 ± 4.3 & 18-50 & 76\% & github.com/RealityBending/InteroceptionPrimals \\ 
+Sample 13 & Makowski et al., (2024) & English & 737 &  & 36.8 ± 14.9 & 17, 87 & 57.3\% & github.com/RealityBending/InteroceptionScale \\ 
+Sample 14 & Poerio et al., (2024) & English & 107 &  & 26.8 ± 9.2 & 18-57 & 74.8\% & osf.io/49wbv \\ 
+Sample 15 & Poerio et al., unpublished & English & 131 &  & 30.9 ± 12.0 & 18-60 & 75.9\% &  \\ 
+Sample 16 & Arjona et al., unpublished & English & 279 &  & 26.4 ± 13.2 & 18-79 & 67.7\% &  \\ 
+Sample 17 & Total &  & 33272 &  & 48.09 ± 13.1 & 17-93 & 71.3\% &  \\ 
 \bottomrule

### 2025-08-27 analysis/figures/table2.tex
manuscript updated
collapsed 1) phq2/GAD into PHQ4 ; 2) STAI5-T into STAIT  + Updated sample table
table 2 updated
need to add references

@@
-\begin{table}
+\begin{table}[t]
 \fontsize{6.8pt}{8.1pt}\selectfont
-\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}lrlrr}
+\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}lrlrrl}
 \toprule
-Questionnaire & Number of Dimensions & Assessment & Number of Items & Scoring \\ 
+Questionnaire & Number of Dimensions & Assessment & Number of Items & Scoring & Example\_Items \\ 
 \midrule\addlinespace[2.5pt]
-{\bfseries Interoceptive Related} &  &  &  &  \\ 
-MAIA-2 & 8 & Interoception & 37 & 6-point Likert scale \\ 
-BPQ & 2 & Body awareness and autonomic reactivity & 49 & 5-point Likert scale \\ 
-TAS-20 & 3 & Alexithymia & 20 & 5-point Likert scale \\ 
-BVAQ & 2 & Alexithymia & 40 & 5-point Likert scale \\ 
-{\bfseries Mood} &  &  &  &  \\ 
-BDI-II & 1 & Severity of depressive symptoms & 21 & 0-to-3-point values \\ 
-PHQ-4 & 2 & Anxiety and depressive symptoms & 4 & 5-point Likert scale \\ 
-STAI-T & 1 & Trait anxiety & 20 & 4-point Likert scale \\ 
-GAD-2 & 1 & General Anxiety & 2 & 4-point Likert scale \\ 
-{\bfseries Personality} &  &  &  &  \\ 
-NEO-FFI & 1 & Neuroticism & 12 & 5-point Likert scale \\ 
-Mini IPIP6 & 6 & Personality & 24 & Analogue scales \\ 
-BFI & 5 & Personality & 44 & 5-point Likert scale \\ 
-PID-5-SF & 5 & Dysfunctional personality traits & 25 & 4-point Likert scale \\ 
-{\bfseries Psychopathology} &  &  &  &  \\ 
-SPQ-BRU & 4 & Schizotypy & 32 & 5-point Likert scale \\ 
-MSI-BPD & 1 & Borderline personality disorder & 10 & Analogue scales \\ 
-ASQ - Short & 5 & Autistic Traits & 28 & 4-point Likert scale \\ 
-{\bfseries Beliefs and Misbeliefs} &  &  &  &  \\ 
-GCB & 5 & Conspiracy beliefs & 15 & 5-point Likert scale \\ 
-PI-18 & 1 & Beliefs about the world & 99 & 6-point Likert scale \\ 
-LIE scale & 4 & Lying tendencies & 16 & Visual analogue scales \\ 
+{\bfseries Interoceptive Related} &  &  &  &  &  \\ 
+MAIA-2 & 8 & Interoceptive awareness & 37 & 6-point Likert scale & I notice when I am uncomfortable in my body \\ 
+BPQ-SF & 2 & Body awareness and autonomic reactivity & 46 & 5-point Likert scale & My heart often beats irregularily \\ 
+BPQ-VSF & 1 & Body awareness & 12 & 5-point Likert scale & My mouth being dry \\ 
+ICQ & 3 & Interoceptive confusion & 20 & 5-point Likert scale &  I cannot tell when my muscles are sore or tight \\ 
+TAS-20 & 3 & Alexithymia & 20 & 5-point Likert scale & I have feelings I can't quite identify \\ 
+BVAQ & 5 & Alexithymia & 40 & 5-point Likert scale & I like to tell others how I feel \\ 
+{\bfseries Mood} &  &  &  &  &  \\ 
+BDI-II & 2 & Depressive symptoms severity & 21 & 4-point scale & I feel sad much of the time \\ 
+PHQ-4 & 2 & Depression and Anxiety & 4 & 4-point Likert scale & Little interest or pleasure in doing things \\ 
+PHQ-9 & 1 & Depressive symptoms & 9 & 4-point Likert scale & Feeling tired or having little energy? \\ 
+PHQ-15 & 1 & Somatic symptom distress & 15 & 3-point scale & Over the last week, how often have you been bothered by back pain? \\ 
+MFQ & 1 & Mood and affect & 13 & 3-point scale & I felt miserable or unhappy \\ 
+STAI-T & 1 & Trait anxiety & 20 & 4-point Likert scale & I worry too much about something that really doesn't matter \\ 
+GAD-7 & 1 & General anxiety disorder symptoms & 7 & 4-point Likert scale & Not being able to stop or control worrying \\ 
+{\bfseries Personality} &  &  &  &  &  \\ 
+NEO-FFI (neuroticism subscale) & 1 & Neuroticism & 12 & 5-point Likert scale & I often feel inferior to others \\ 
+Mini IPIP6 & 6 & Personality traits & 24 & Visual analogue scales & Am the life of the party \\ 
+BFI-S & 5 & Personality traits & 10 & 7-point Likert scale & I see myself as someone who ...is considerate and kind to almost everyone \\ 
+{\bfseries Psychopathology} &  &  &  &  &  \\ 
+PID-5-SFF & 5 & Maladaptive personality traits & 25 & 4-point Likert scale & Plenty of people are out to get me \\ 
+SPQ-BR & 9 & Schizotypy & 32 & 5-point Likert scale & I am an odd, unusual person \\ 
+MSI-BPD & 1 & Borderline personality disorder & 9 & Dichotomous (yes/no) & Have any of your closest relationships been troubled by a lot of arguments or repeated breakups? \\ 
+ASQ - Short & 5 & Autistic traits & 28 & 4-point Likert scale & I find it difficult to work out people’s intentions \\ 
+{\bfseries Beliefs and Misbeliefs} &  &  &  &  &  \\ 
+GCBS & 5 & Conspiracy beliefs & 15 & 5-point Likert scale & Secret organizations communicate with extraterrestrials, but keep this fact from the public \\ 
+PI-18 & 3 & Primal world beliefs & 18 & 5-point Likert scale & Nearly everything in the world is beautiful \\ 
+LIE scale & 4 & Lying tendencies & 16 & Visual analogue scales & I am a good liar \\ 
 \bottomrule

### 2025-08-27 analysis/study2.qmd
table 2 updated
need to add references

@@
 ## Measures used
+
+- Note, GAD2 and PHQ2 were collapsed into phq4
+- PI-99 was collapsed into PI-18
 
@@
 table <- data.frame(
-  Questionnaire = c("Interoceptive Related", "MAIA-2", "BPQ", "TAS-20", "BVAQ",
-                    "Mood", "BDI-II", "PHQ-4", "STAI-T", "GAD-2",
-                    "Personality", "NEO-FFI", "Mini IPIP6", "BFI", "PID-5-SF",
-                    "Psychopathology", "SPQ-BRU", "MSI-BPD", "ASQ - Short",
-                    "Beliefs and Misbeliefs", "GCB", "PI-18", "LIE scale"),
-  Number_of_Dimensions = c('', 8, 2, 3, 2, 
-                           '', 1, 2, 1, 1, 
-                           '', 1, 6, 5, 5, 
-                           '', 4, 1, 5, 
-                           '', 5, 1, 4),
-  Assessment = c('', "Interoception", "Body awareness and autonomic reactivity", "Alexithymia", "Alexithymia",
-                 '',"Severity of depressive symptoms", "Anxiety and depressive symptoms", "Trait anxiety", "General Anxiety",
-                 '', "Neuroticism", "Personality", "Personality", "Dysfunctional personality traits",
-                 '', "Schizotypy", "Borderline personality disorder", "Autistic Traits",
-                 '', "Conspiracy beliefs", "Beliefs about the world", "Lying tendencies"),
-  Number_of_Items = c('',37, 49, 20, 40, 
-                      '',21, 4, 20, 2, 
-                      '',12, 24, 44, 25, 
-                      '',32, 10, 28, 
-                      '',15, 99, 16),
-  Scoring = c('',"6-point Likert scale", "5-point Likert scale", "5-point Likert scale", "5-point Likert scale", 
-              '',"0-to-3-point values", "5-point Likert scale", "4-point Likert scale", "4-point Likert scale", 
-              '',"5-point Likert scale", "Analogue scales", "5-point Likert scale", "4-point Likert scale", 
-              '',"5-point Likert scale", "Analogue scales", "4-point Likert scale", 
-              '',"5-point Likert scale", "6-point Likert scale", "Visual analogue scales"), 
+  Questionnaire = c(
+    # Interoception
+    "Interoceptive Related", "MAIA-2", "BPQ-SF", "BPQ-VSF", "ICQ", "TAS-20", "BVAQ",
+    # Mood/Anxiety
+    "Mood", "BDI-II", "PHQ-4", "PHQ-9", "PHQ-15", "MFQ", "STAI-T", "GAD-7",
+    # Personality
+    "Personality", "NEO-FFI (neuroticism subscale)", "Mini IPIP6", "BFI-S",
+    # Psychopathology
+    "Psychopathology", "PID-5-SFF", "SPQ-BR", "MSI-BPD", "ASQ - Short",
+    # Beliefs and Misbeliefs
+    "Beliefs and Misbeliefs", "GCBS", "PI-18", "LIE scale"
+  ),
+  Number_of_Dimensions = c(
+    "", 8, 2, 1, 3, 3, 5,
+    "", 2, 2, 1, 1, 1, 1, 1,
+    "", 1, 6, 5,
+    "", 5, 9, 1, 5,
+    "", 5, 3, 4
+  ),
+  Assessment = c(
+    "", "Interoceptive awareness", "Body awareness and autonomic reactivity", "Body awareness", "Interoceptive confusion", "Alexithymia", "Alexithymia", 
+    "", "Depressive symptoms severity", "Depression and Anxiety", "Depressive symptoms", "Somatic symptom distress", "Mood and affect", "Trait anxiety", "General anxiety disorder symptoms",
+    "", "Neuroticism", "Personality traits", "Personality traits",
+    "", "Maladaptive personality traits", "Schizotypy", "Borderline personality disorder", "Autistic traits",
+    "", "Conspiracy beliefs", "Primal world beliefs", "Lying tendencies"
+  ),
+  Number_of_Items = c(
+    "", 37, 46, 12, 20, 20, 40,
+    "", 21, 4, 9, 15, 13, 20, 7,
+    "", 12, 24, 10,
+    "", 25, 32, 9, 28,
+    "", 15, 18, 16
+  ),
+  Scoring = c(
+    "", "6-point Likert scale", "5-point Likert scale", "5-point Likert scale", "5-point Likert scale", "5-point Likert scale", "5-point Likert scale",
+    "", "4-point scale", "4-point Likert scale", "4-point Likert scale", "3-point scale", "3-point scale", "4-point Likert scale", "4-point Likert scale",
+    "", "5-point Likert scale", "Visual analogue scales", "7-point Likert scale",
+    "", "4-point Likert scale", "5-point Likert scale", "Dichotomous (yes/no)", "4-point Likert scale",
+    "", "5-point Likert scale", "5-point Likert scale", "Visual analogue scales"
+  ),
+  Example_Items = c(
+    # Interoception
+    "", "I notice when I am uncomfortable in my body", "My heart often beats irregularily", "My mouth being dry", " I cannot tell when my muscles are sore or tight", "I have feelings I can't quite identify", "I like to tell others how I feel",
+    #Mood
+    "", "I feel sad much of the time","Little interest or pleasure in doing things", "Feeling tired or having little energy?", "Over the last week, how often have you been bothered by back pain?", "I felt miserable or unhappy", "I worry too much about something that really doesn't matter", "Not being able to stop or control worrying",
+    # Personality
+    "", "I often feel inferior to others", "Am the life of the party", "I see myself as someone who ...is considerate and kind to almost everyone", 
+   # Psychopathology
+    "", "Plenty of people are out to get me", "I am an odd, unusual person", "Have any of your closest relationships been troubled by a lot of arguments or repeated breakups?", "I find it difficult to work out people’s intentions",
+   # Beliefs and Misbeliefs
+    "", "Secret organizations communicate with extraterrestrials, but keep this fact from the public", "Nearly everything in the world is beautiful", "I am a good liar"
+),
   stringsAsFactors = FALSE
@@
 # names(df1b)
-# names(df2)  #TAS, MAIA, ICQ, BPQ, BVAQ
-# names(df3)  # TAS, BPQ
-# names(df4)  # BPQ, PBCS (private bodily consciousness?), MAIA, BAQ, BRS
+# names(df2)  #TAS(20 items), MAIA(37 items), ICQ (20 items), BPQ(46 items), BVAQ (40 items)
+# names(df3)  # TAS (20), BPQ (46)
+# names(df4)  # BPQ(26), PBCS (private bodily consciousness?), MAIA (37), BAQ (18), BRS (4)
 # names(df5)  
-# names(df6)  # PHQ2, GAD2, SSS8, IATS
-# names(df7a)  # STAIT, MAIA, CES (not reported in the paper), FFMQ, NEOFFI
-# names(df7b)  # BPQ, PHQ15, PHQ9, MAIA, STAIT, 
-# names(df7c)  # CI01 (not reported in the paper), TAS, BPQ, MAIA, ASI, ICQ 
-# names(df8a)  # EDI, BPQ
-# names(df8b)  # PHQ9, PHQ15, TAS
-# names(df9)  # ECR (Experience in Close Relationship Scale), TEAQ (touch experiences and attitudes questionnaire), STQ, TACSEN, UCLA, BFI, DBIA, BO, EQ
-# names(df10)  # ASQ, BPD, GCBS, IPIP6, LIE, MAIA, PHQ4, PI, PID, SPQ
-# names(df11)  # PHQ4, STAIT5, BDI, MAIA
-# names(df12) # MAIA, PI, 
-# names(df13) # 
-# names(df14) # MAIA, TAS, MFQ(DEP), STAI(ANX)
+# names(df6)  # PHQ2 (2 items), GAD2 (2 items), SSS8, IATS
+# names(df7a)  # STAIT (20), MAIA(37), CES (not reported in the paper), FFMQ (39), NEOFFI (12)
+# names(df7b)  # BPQ (12), PHQ15 (15), PHQ9 (9), MAIA (37), STAIT(20), 
+# names(df7c)  # CI01 (not reported in the paper), TAS, BPQ, MAIA, ASI, ICQ  - no individual items
+# names(df8a)  # EDI (10), BPQ (12)
+# names(df8b)  # PHQ9 (9), PHQ15 (15), TAS (20)
+# names(df9)  # ECR (Experience in Close Relationship Scale), TEAQ (touch experiences and attitudes questionnaire), STQ, TACSEN, UCLA, BFI (15), DBIA, BO, EQ
+# names(df10)  # ASQ(28), BPD(9), GCBS (15), IPIP6 (24), LIE (16), MAIA(37), PHQ4 (4), PI (32), PID (25), SPQ (32)
+# names(df11)  # PHQ4 (4), STAIT5 (5), BDI (21), MAIA (37)
+# names(df12) # MAIA (37), PI (99), 
+# names(df13) # PI (18), MAIA (37)
+# names(df14) # MAIA(37), TAS  (20), MFQ(DEP, 13), STAI(ANX, 20)
 # names(df15) 
+# names(df16) # MAIA (37), GAD (7), PHQ9 (9)
 ```

### 2025-08-28 paper/1_Initial/manuscript.qmd
updated manuscript

@@
 
-The questionnaires used for the IAS correlates are listed in **Table 2** (**TODO: add the rest of the questionnaires, sample items and references**).
+We selected measures that appeared in multiple datasets from Study 1 and/or were relevant given the scope of the study, merging scores of regular and abridged versions for conciseness where applicable.
+The measures include constructs related to interoception, mood, personality, psychopathology, and beliefs and misbeliefs.
 
-\input{../../analysis/figures/table2.tex}
+<!-- Interoception Related -->
+**Interoception Related**
+The Multidimensional Assessment of Interoceptive Awareness Version-2 [MAIA-2, @memehling2018multidimensional] is a 37-item questionnaire assessing eight dimensions of interoception: Noticing, Not-Distracting, Not-Worrying, Attention Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust.
+Responses are rated on a 6-point Likert scale (e.g., “I notice when I am uncomfortable in my body”).
+
+The Body Perception Questionnaire Short Form [BPQ-SF, @cabrera2018assessing] contains 46 items measuring body awareness and autonomic reactivity on a 5-point Likert scale (e.g., “My heart often beats irregularly”).
+The very-short form (BPQ-VSF) contains 12 items from the body awareness subscale.
+For this study, scores from both versions were combined.
+
+The Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia] consists of 20 items rated on a 5-point Likert scale (e.g., “I cannot tell when my muscles are sore or tight”) assessing difficulties in interpreting non-affective physiological states, such as pain or hunger.
+
+The Toronto Alexithymia Scale [TAS-20, @bagby1994twenty] contains 20 items rated on a 5-point forced-choice scale (e.g., “I have feelings I can’t quite identify”), divided into three dimensions: difficulty identifying feelings, difficulty describing feelings, and externally oriented thinking.
+
+The Bermond–Vorst Alexithymia Questionnaire [BVAQ, @vorst2001validity] consists of 40 items across five subscales: fantasising, identifying, analysing, verbalising, and emotionalising.
+Items are rated on a 5-point Likert scale.
+The BVAQ also provides two higher-order factors, namely affective and cognitive (e.g., “I like to tell others how I feel”).
+
+<!-- Mood and Anxiety -->
+**Mood and Anxiety Related**
+The Beck Depression Inventory-II [BDI-II, @beck1996beck] is a 21-item measure of depressive symptom severity, including psychological (e.g., guilt) and physiological (e.g., loss of energy) components.
+Items are rated on a 4-point scale (e.g., “I feel sad much of the time”).
+
+The Patient Health Questionnaire-4 [PHQ-4, @kroenke2009ultra] is a 4-item screening tool for depression and anxiety, rated on a 4-point Likert scale (e.g., “Little interest or pleasure in doing things”; “Not being able to stop or control worrying”).
+The PHQ-2 [PHQ-2; @kroenke2003patient] and General Anxiety Disorder-2 [GAD-2, @kroenke2007anxiety] scores were combined with the PHQ-4 scores.
+
+The Patient Health Questionnaire-9 [PHQ-9, @kroenke2001phq] includes 9 items assessing depressive symptoms on a 4-point Likert scale (e.g., “Feeling tired or having little energy?”).
+
+The Patient Health Questionnaire-15 [PHQ-15, @kroenke2002phq] assesses somatic symptom distress with 15 items rated on a 3-point scale (e.g., “Over the last week, how often have you been bothered by back pain?”).
+
+The Short Mood and Feelings Questionnaire [SMFQ, @angold1995development] is a 13-item measure of recent depressive symptoms in children aged 6–17, rated on a 3-point scale (e.g., “I felt miserable or unhappy”).
+
+The State–Trait Anxiety Inventory Trait Version [STAI-T, @spielberger1970manual] is a 20-item trait anxiety questionnaire rated on a 4-point Likert scale (e.g., “I worry too much about something that really doesn’t matter”).
+
+The Generalized Anxiety Disorder Scale [GAD-7, @spitzer2006brief] is a 7-item measure of generalized anxiety symptoms rated on a 4-point Likert scale (e.g., “Not being able to stop or control worrying”).
+
+<!-- Personality -->
+**Personality**
+The NEO Five-Factor Inventory, neuroticism subscale [NEO-FFI, @costa1989neoffi] is a 12-item measure of neuroticism, assessing the general tendency to experience negative emotions such as fear, sadness, or disgust.
+Items are rated on a 5-point Likert scale (e.g., “I often feel inferior to others”).
+
+The Mini International Personality Item Pool [MINI-IPIP6, @sibley2011mini] includes 24 items measuring six broad traits: Agreeableness, Conscientiousness, Neuroticism, Openness, Extraversion, and Honesty-Humility.
+Items were scored on visual analogue scales in our samples (originally 7-point Likert scales; e.g., “Have a vivid imagination”).
+
+The Big Five Inventory Short Form [BFI-S, @rammstedt2007measuring] is a 10-item measure of the Big Five traits, rated on a 7-point Likert scale (e.g., “I see myself as someone who … is considerate and kind to almost everyone”).
+
+<!-- Psychopathology -->
+**Psychopathology**
+The Personality Inventory for DSM-5 Short Form [PID-5-SF, @thimm2016personality] consists of 25 items rated on a 4-point Likert scale, measuring five domains: disinhibition, antagonism, detachment, negative affect, and psychoticism (e.g., “Plenty of people are out to get me”).
+
+The Schizotypal Personality Questionnaire – Brief Revised [SPQ-BR, @davidson2016schizotypal] contains 32 items rated on a 5-point Likert scale, assessing four primary dimensions: cognitive-perceptual, interpersonal, disorganized, and social anxiety.
+These are subdivided into nine secondary factors, including constricted affect, eccentricity, magical thinking, lack of close friends, odd speech, referential thinking, social anxiety, suspiciousness, and unusual perceptions (e.g., “Plenty of people are out to get me”).
+
+The McLean Screening Instrument for Borderline Personality Disorder [MSI-BPD, @zanarini2003zanarini] is a 10-item dichotomous screening measure for borderline personality disorder (present/absent; e.g., “Have any of your closest relationships been troubled by a lot of arguments or repeated breakups?”).
+
+The Autism Spectrum Quotient Short Form [ASQ-S, @Hoekstra et al., 2011] is a 28-item measure of five autistic traits: social skills, adherence to routines, cognitive flexibility, imagination, and patterns/numbers.
+Items are rated on a 4-point Likert scale (e.g., “I find it difficult to work out people’s intentions”).
+
+<!-- Beliefs and Misbeliefs -->
+**Beliefs and Misbeliefs**
+The Generic Conspiracist Beliefs Scale [GCBS, @brotherton2013measuring] is a 15-item measure assessing five dimensions of conspiracy beliefs: government malfeasance, extraterrestrial cover-up, malevolent global conspiracies, personal wellbeing, and control of information.
+Items are scored on a 5-point Likert scale (e.g., “Secret organizations communicate with extraterrestrials, but keep this fact from the public”).
+
+The Primal World Beliefs Inventory Short Form [PI-18, @lifton2021brief] is an 18-item measure assessing four high-order beliefs: the world is Good (vs.
+Bad) and its three dimensions: Safe (vs.
+Dangerous), Enticing (vs.
+Dull), and Alive (vs.
+Mechanistic).
+Items are scored on a 5-point Likert scale (e.g., “Nearly everything in the world is beautiful”).
+The PI-99 [@clifton2019primal] scores were combined with the 4 high-order beliefs of the PI-18.
+
+The Structure of Deception [SoD, @makowski2023structure] is a 16-item measure of lying tendencies across four components: Ability, Frequency, Negativity, and Contextuality.
+Items are scored on visual analogue scales (e.g., “I am a good liar”).
 
 ### Data Analysis
+
+<!-- Preprocessing and standardization -->
+
+All variables from the 16 open-access datasets will be extracted and standardized (z-scored).
+For continuous predictors, we will first ensure that their ranges are consistent across datasets; when necessary, ranges will be rescaled to achieve comparability.
+In cases where scales of different lengths measure the same construct, scores will be harmonised: when possible, means will be computed from overlapping individual items, while in other cases, total scores will be normalized by the number of items.
+Where redundant subscales exist (e.g., PHQ-2 and GAD-2 items contained within the PHQ-4), these will be collapsed into unified composite scores (e.g., PHQ-4 depression and PHQ-4 anxiety).
+Similarly, short forms of trait anxiety measures (e.g., STAI-5-trait) will be collapsed with their longer counterparts (STAI-T), with scores computed as the mean to ensure comparable ranges despite differing item counts.
+Additionally, longer formats of the PI (32 and 99 items) will be collapsed into its shorter versions PI-18.
+Missing data will be handled via listwise deletion prior to model fitting.
+
+<!-- Multilevel modelling approach -->
+
+Associations will be estimated using multilevel regression models implemented in the glmmTMB package [@glmmTMB].
+Each predictor will be entered separately, with IAS pair of ititems identified in Study 1 (i.e., "Hungry–Thirsty", "Muscles–Pain", "Wind–Burp", "Urinate–Defecate", "Breathing–Heart", "Bruise–Blood", "Cough–Sneeze") and the original IAS scale serving as outcomes.
+Models will include random intercepts and slopes by sample to account for between-study heterogeneity; when models fail to converge, a reduced structure with random intercepts only will be used.
+This approach will treat datasets as clusters, thereby providing a meta-analytic estimate of the pooled associations while simultaneously accounting for both within- and between-sample variability, an advantage over simple pooled correlations.
+
+<!-- Extraction of parameters -->
+
+From each fitted model, we will extract standardized regression coefficients (r), 95% confidence intervals, p-values, convergence status, and effective sample size.
+Gender will be modeled as a binary factor (Female vs.
+Male), with participants identifying as “Other” excluded from analyses due to limited representation.
 
@@
 
-The EGA components captured grouping of items such as 'wind' and 'burp, 'cough' and 'sneeze', 'muscle' and 'pain'. 
 **TODO: but that's not true, we used only pairs, not EGA clusters?J**

### 2025-08-28 analysis/study2.qmd
updated table 2

@@
 - PI-99 was collapsed into PI-18
+- STait-5 collapsed into STait-t
 
@@
   cols_align(align = c("right"), columns = "Scoring") |> 
-  cols_label(Number_of_Dimensions = "Number of Dimensions", Number_of_Items = "Number of Items")  |>
+  cols_label(Number_of_Dimensions = "Number of Dimensions", Number_of_Items = "Number of Items", Example_Items = "Example Items")  |>
   # tab_footnote("* Information taken from the sample description of relevant paper rather than recomputed.") 
@@
 gtsave(gt_apastyle(table_apa, font.size=9), "figures/table2.tex")
+saveRDS(table, "figures/table2.rds")
 ```

### 2025-08-28 analysis/Study1.qmd
computed means and rescaled personality dimensions

@@
 df7a$STAIT_Mean <- df7a$STAIT_Sum/20
+df7a$NEO_FFI_Mean <- rowMeans(select(df7a,NEOFFI_01:NEOFFI_12))
 
@@
     BFI_CONSCIENTIOUSNESS = (BFI_13 + BFI_14 + BFI_15R)/3,
-    BFI_OPENNESS = (BFI_7 + BFI_8 + BFI_9)/3
-    )
+    BFI_OPENNESS = (BFI_7 + BFI_8 + BFI_9)/3) |>
+  mutate(across(starts_with("BFI_"), \(x) datawizard::rescale(x, to = c(0, 1))))
+
 ```
@@
          across(starts_with("Item_PHQ4_Depression_"), \(x) datawizard::rescale(x, to = c(1,4))),
-        across(starts_with("Item_PHQ4_Anxiety_"), \(x) datawizard::rescale(x, to = c(1,4)))) |>
+        across(starts_with("Item_PHQ4_Anxiety_"), \(x) datawizard::rescale(x, to = c(1,4))),
+        across(starts_with("IPIP6_"), \(x) datawizard::rescale(x, to = c(0,1)))) |>
   mutate(PHQ4_Depression = Item_PHQ4_Depression_3 + Item_PHQ4_Depression_4,

### 2025-08-28 analysis/study2.qmd
computed means and rescaled personality dimensions

@@
   data,
-  pool_coef(with = "NEO_FFI_SUMSCORE", component = "Personality", name = "Neuroticism"),
+  pool_coef(with = "NEO_FFI_Mean", component = "Personality", name = "Neuroticism"),
   pool_coef(with = "BFI_AGREEABLENESS", component="Personality", name = "Agreeableness"),
@@
 
+average_corr <- data |>
+  summarise(
+    min_r = min(r, na.rm = TRUE), 
+    mean_r = mean(r, na.rm = TRUE),
+    max_r = max(r, na.rm = TRUE), 
+    Max = var_Interoception[which.max(abs(r))],
+    n_sig_001 = sum(p < .001, na.rm = TRUE),
+    n_sig_01  = sum(p < .01 & p >= .001, na.rm = TRUE),
+    n_ns      = sum(p >= .01 | is.na(p)),
+    total     = dplyr::n(),
+    .by=c("Component", "var_Correlate")
+  ) |>
+  mutate(
+    perc_sig = (n_sig_001 + n_sig_01) / total
+  )
+sort(table(average_corr$Max), decreasing = TRUE)
+
 average_corr |> 

### 2025-08-28 paper/1_Initial/manuscript.qmd
Update manuscript.qmd
till results study 2

P.S. need to re-check personality associations

@@
 The State–Trait Anxiety Inventory Trait Version [STAI-T, @spielberger1970manual] is a 20-item trait anxiety questionnaire rated on a 4-point Likert scale (e.g., “I worry too much about something that really doesn’t matter”).
+Scores from the shorter version of the STAI-5 [STAIT-5, @zsido2020development] were combined with the STAI-T.
 
@@
 
-The Structure of Deception [SoD, @makowski2023structure] is a 16-item measure of lying tendencies across four components: Ability, Frequency, Negativity, and Contextuality.
+The Lie Scale [LIE, @makowski2023structure] is a 16-item measure of lying tendencies across four components: Ability, Frequency, Negativity, and Contextuality.
 Items are scored on visual analogue scales (e.g., “I am a good liar”).
@@
 <!-- Preprocessing and standardization -->
-
 All variables from the 16 open-access datasets will be extracted and standardized (z-scored).
-For continuous predictors, we will first ensure that their ranges are consistent across datasets; when necessary, ranges will be rescaled to achieve comparability.
-In cases where scales of different lengths measure the same construct, scores will be harmonised: when possible, means will be computed from overlapping individual items, while in other cases, total scores will be normalized by the number of items.
-Where redundant subscales exist (e.g., PHQ-2 and GAD-2 items contained within the PHQ-4), these will be collapsed into unified composite scores (e.g., PHQ-4 depression and PHQ-4 anxiety).
-Similarly, short forms of trait anxiety measures (e.g., STAI-5-trait) will be collapsed with their longer counterparts (STAI-T), with scores computed as the mean to ensure comparable ranges despite differing item counts.
-Additionally, longer formats of the PI (32 and 99 items) will be collapsed into its shorter versions PI-18.
-Missing data will be handled via listwise deletion prior to model fitting.
+For continuous predictors, we will first ensure consistent ranges across datasets; when necessary, ranges will be rescaled to achieve comparability.
+In cases where scales of different lengths measured the same construct, scores were harmonized: when possible, means were computed from overlapping items, while in other cases total scores were normalized by the number of items.
+Redundant subscales (e.g., PHQ-2 and GAD-2 within PHQ-4) were collapsed into unified composite scores.
+Similarly, short forms of trait anxiety (e.g., STAI-5-trait) were collapsed with their longer counterpart (STAI-T), with scores computed as the mean to ensure comparable ranges.
+Longer formats of the PI (PI-99) were collapsed into its shorter version (PI-18).
+Missing data were handled via listwise deletion on a per-model basis prior to fitting.
 
 <!-- Multilevel modelling approach -->
-
-Associations will be estimated using multilevel regression models implemented in the glmmTMB package [@glmmTMB].
-Each predictor will be entered separately, with IAS pair of ititems identified in Study 1 (i.e., "Hungry–Thirsty", "Muscles–Pain", "Wind–Burp", "Urinate–Defecate", "Breathing–Heart", "Bruise–Blood", "Cough–Sneeze") and the original IAS scale serving as outcomes.
-Models will include random intercepts and slopes by sample to account for between-study heterogeneity; when models fail to converge, a reduced structure with random intercepts only will be used.
-This approach will treat datasets as clusters, thereby providing a meta-analytic estimate of the pooled associations while simultaneously accounting for both within- and between-sample variability, an advantage over simple pooled correlations.
+Associations were estimated using multilevel regression models implemented in the glmmTMB package [@glmmTMB].
+Each predictor was entered separately, with the seven IAS item pairs identified in Study 1 (“Hungry–Thirsty”, “Muscles–Pain”, “Wind–Burp”, “Urinate–Defecate”, “Breathing–Heart”, “Bruise–Blood”, “Cough–Sneeze”) and the original IAS scale serving as outcomes.
+Models included random intercepts and slopes by sample to account for between-study heterogeneity; when models failed to converge, a reduced structure with random intercepts only was used.
+This approach treats datasets as clusters, thereby providing pooled estimates of the associations while accounting for both within- and between-sample variability, akin to a meta-analytic framework.
 
 <!-- Extraction of parameters -->
-
-From each fitted model, we will extract standardized regression coefficients (r), 95% confidence intervals, p-values, convergence status, and effective sample size.
-Gender will be modeled as a binary factor (Female vs.
-Male), with participants identifying as “Other” excluded from analyses due to limited representation.
+From each fitted model, we extracted standardized regression coefficients (β), 95% confidence intervals, p-values, convergence status, and effective sample size.
+Participants identifying as “Other” were excluded from analyses due to limited representation.
 
@@
 
-### Average correlations
+<!-- Demographic correlates -->
+Age showed consistent positive associations across tasks (mean r = .12), with all correlations significant.
+Gender differences were weaker (mean r = −.01), though a majority of effects reached significance.
 
-**TODO: but that's not true, we used only pairs, not EGA clusters?J**
+<!-- Interoceptive measures -->
+Several MAIA subscales showed moderate and consistently significant positive associations with IAS scores.
+Noticing (mean β = .259), Attention Regulation (β = .249), Trusting (β = .236), Emotional Awareness (β = .197), Listening (β = .176), and Self-Regulation (β = .189) were significant across all pairings and the original scale.
+Autonomic reactivity from the BPQ was negatively associated (β = −.173, 88% significant), whereas body awareness showed weaker and less reliable effects (β = .122, 25% significant).
+Alexithymia was consistently negative: ICQ (β = −.316), TAS subscales: Difficulties Identifying Feelings (βs = −.211) , Difficulties Describing Feelings (βs = −.150), External Thinking (βs = −.081, 75% significance), and the BVAQ cognitive component (β = −0.200) were significant for nearly all IAS correlates.
 
-These groupings were used in correlational analysis to analyse how much each pairing is associated with other factor such as Alexithymia and with Mood disorders (see figure 2).
+<!-- Mood questionnaires -->
 
-**TODO: Massively streamline. It can be all summarize in one or two paragraphs max.**
+Depression (BDI: β = −0.204) and anxiety (STAI-T: β = −0.189) showed reliably negative associations.
+PHQ-15 (β = −0.128, 75% significant) PHQ-4 (depression: β = −0.094, 75% significant; anxiety: β = −0.103, 88% significant), and GAD-7 (β =−0.187, 63% significance) also showed consistent negative effects.
+By contrast, PHQ-9 (β = −0.619) and MFQ (β = −0.139) were largely nonsignificant despite negative averages.
 
-#### Correlations with body measures
+<!-- Psychopathology and personality -->
 
-<!-- Alexithymia -->
-Alexithymia was assessed in the samples with the Bermond–Vorst Alexithymia Questionnaire [BVAQ, @vorst2001validity] and the Toronto Alexithymia Scale [TAS, @bagby1994twenty].
+Autistic traits showed the clearest pattern: Imagination (β = −0.184, 88% significant), Low Attentional Switching (β = −0.143, 63% significant), and Lack of Social Skills (β = −0.119, 63% significant) were reliably negative.
+Among maladaptive traits, Negative Affect (β = −0.111, 63% significant) was the only consistent correlate.
+Schizotypal traits showed generally weak and unreliable associations, with No Close Friends (β = −0.12, significant in 50% of models) being the only subscale to exhibit a small effect, and even this just at the threshold of consistency.
 
-<!-- BVAQ -->
-The BVAQ consists of 5 subscales - fantasising, idenitying, analysing; verbalising and emotionalising - assessed with 40 items on a 5-point Likert scale, from 'defnitely applies to me' to 'in no way applies to me'.
-Additionally, the BVAQ reduces these subscales into two high order factors, an affective component and a cognitive one, with high scores being indicative of high proneness to alexithymia.
+<!-- Personality and beliefs -->
 
-On average, the cognitive component of the BVAQ was weakly and negatively correlated with all IAS pairs of items with the biggest correlation being with the Itch/Bruise pair (r = -0.112) and the lowest correlation beeing with the Muscle/Pain pair (r = -0.244).
-The affective component of the BVAQ was positively, but very weak, correlated with all pairs, with the biggest correlation being with the Itch/Bruise pair (r = 0.107). 
-The only exception was a negative correlation with the Urinate/Defecate pair (r = -0.036).
+Of the Big Five, only Openness showed consistent positive associations (β = 0.123, 63% significant).
+Other traits were weak or mostly nonsignificant.
+Conspiracy, world belief, and lying profiles showed no reliable associations.
 
-<!-- TAS -->
-The TAS contains 20-items rated on a 5-point forced scale, from 'strongly disagree' to 'strongly afree', divided into 3 dimensions - difficulty identiying feelings, difficulty describing feelings, and externally thinking.
-High scores on this scale also reflect higher alexithymia.
-
-All the three dimensions assessed with the TAS were on average negatively correlated with all pairs of IAS items.
-The difficulty describing feelings had its strongest correlation with Hungry/Thirsty (r = -0.179) and weakest with the Wind/Burp (r = -0.117).
-while, the difficulty describing feelings had its strongest correlation with Muscle/Pain (r = -0.247) and weakest with Itch/Bruise (r = -0.157).
-Lastly, the external thinking dimension was more correlated with the Cough/Sneeze pair (r = -0.138) and less correlated with the Hungry/Thirsty (r = -0.018).
-
-<!-- BPQ -->
-The studies within our sample used the Body Perception Questionnaire short-form (BPQ-SF) and the very-short form (BPQ-VSF) to assess interoception [@cabrera2018assessing]. 
-The BPQ-SF comprised of 46 items on a 5-point Likert scale assessing body awareness (26 items) and autonomic reactivity (21 items). 
-The BPQ-VSF comprises of 12 items from the body awareness subscale of the BPQ-SF.
-In this study, all scores assessing these two dimensions were grouped together, hence no disitintion is made between awareness measured with the BPQ-SF and the BPQ-VSF, or eith scores obtained only using the awareness subscale.
-
-**note to add:** discuss later
-
-In general, all pairs of the IAS were positively,and weakily, associated with the body awareness subscales, while negative and weakily correlated with the autonomic reactivity subscale. 
-The strongest correlation identified between the IAS pairs and the body awereness subscale was with the 	
-Heart/Breathing pair (r = 0.151) whilst the strongest correlation with the autonomic reactivity was with the Urinate/Defecate pair (r = -0.235). 
-The weakest correlation between the body awareness and the IAS was with the Hungry/Thirsty pair (r =  0.055) and between the autonomic reactivity and the IAS was with the Heart/Breathing pair (r = -0.106).
-
-<!-- MAIA -->
-The MAIA was one of the most commonly used measures of interoception in our study, with nine samples reporting its use. 
-This 37-item questionnaire assesses eight state-trait dimensions of interoception: Noticing, Not-Distracting, Not-Worrying, Attention Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust.
-Responses are rated on a scale from 0 (Never) to 5 (Always).
-
-On average, all MAIA dimensions were positively and weakly to moderately correlated with IAS pairings. 
-Notably, the strongest correlations were observed between the Noticing dimension and the Heart/Breathing pairing (r = 0.394), Trusting and Hungry/Thirsty (r = 0.347), and Attention Regulation and Heart/Breathing (r = 0.334).
-The Not-Distracting and Not-Worrying subscales were generally positively correlated with IAS pairings, with a few exceptions: Not-Distracting showed minimal correlation with Cough/Sneeze (r = 0.0206) and Heart/Breathing (r = -0.007), while Not-Worrying had a low correlation with Itch/Bruise (r = 0.031).
-
-<!-- ICQ -->
-The Interoceptive Confusion Questionnaire was used to assess individuals' difficulties in interpreting non-affective physiological states, such as pain and hunger.
-The ICQ consists of 20 items rated on a scale from 1 ("Does not describe me") to 5 ("Describes me very well"), with higher scores indicating greater interoceptive confusion.
-
-The ICQ showed weak to moderate negative correlations with all IAS pairings.
-The strongest correlation was observed with the Hunger/Thirsty pairing (r = 0.348), while the weakest was with the Itch/Bruise pairing (r = 0.207).
-
-#### Correlations with mood measures
-
-Mood disorders were assessed using several standardized measures, including the General Anxiety Disorder-2 [GAD-2, @kroenke2007anxiety], the State-Trait Anxiety Inventory [STAI, @spielberger1970manual] and its shorter version, the STAI-5 [@zsido2020development], Beck’s Depression Inventory [BDI, @beck1996beck], and the Mood and Feelings Questionnaire [MFQ; @messer1995development].
-Additionally, the Patient Health Questionnaire (PHQ) was administered in its 2-item [PHQ-2; @kroenke2003patient], 9-item [PHQ-9; @kroenke2001phq], and 15-item [PHQ-15, @kroenke2002phq] versions.
-Finally, borderline personality traits were assessed using the McLean Screening Instrument for Borderline Personality Disorder [MSI-BPD; @zanarini2003zanarini].
-
-<!-- Anxiety -->
-The GAD-2, a brief screening tool for generalized anxiety disorder, consists of two items rated on a scale from 0 (not at all) to 3 (nearly every day).
-The STAI, a 40-item questionnaire rated on a 4-point Likert scale (0 to 3), measures both state and trait anxiety. 
-However, in our study, most participants primarily completed the trait anxiety subscale. 
-In some samples, a shorter 5-item version (STAI-5) was used to assess both state and trait anxiety.
-
-On average, anxiety measures showed weak negative correlations with all IAS pairs. 
-Notably, the strongest correlations between the IAS pairings and the GAD-2, STAI-T and STAIT-5 were observed with the Hungry/Thirsty pair (r = -0.168, r = -0.270 and r =  -0.248, respectively).
-
-<!-- Depression -->
-The BDI consists of 21 items measuring the severity of depressive symptoms on a scale from 0 to 3. 
-The total score is calculated by summing the highest responses, which are then compared to six depression severity levels, ranging from 1–10 (normal fluctuations in mood) to over 40 (extreme depression).
-The PHQ-2 includes two items assessing the frequency of depressive symptoms and anhedonia. 
-The PHQ-2 is derived from the PHQ-9, a nine-item screening tool used to assess depression severity and monitor treatment response.
-Both questionnaires are measured on on a scale from 0 (not at all) to 3 (nearly every day)
-
-Depression measures showed weak to moderate negative correlations with IAS pairings. 
-The BDI (r = -0.372), PHQ-2 (r = -0.148), and PHQ-9 (r = -0.241) correlated most with the Hungry/Thirsty pair, while the MFQ correlated most with Heart/Breathing (r = -0.345) pair.
-
-<!-- Somatic concerns  -->
-The PHQ-15 is a 15-item questionnaire that assesses somatic symptoms on a 3-point scale (e.g., back pain). 
-It exhibited its strongest correlation with the Hungry/Thirsty pair (r = -0.241) and, on average, showed weak negative correlations with all other IAS pairings.
-
-<!-- Borderline personality -->
-Lastly, the MSI-BPD is a 10-item questionnaire used to assess personality disorder, where items are rated on a dichotomous scale of 1 (present) and 0 (absent). 
-The MSI-BPD also showed its strongest negative correlation with the Hungry/Thirsty pair (r = -0.140) and was negatively correlated with all other pairings, except for Cough/Sneeze, which showed a slight positive correlation (r = 0.0219).
-
-#### Correlations with psychopathology measures
-
-<!-- Maladaptive  -->
-Maladaptive personality traits were assessed using the Personality Inventory for DSM-5 Short Form [PID-5-SF; @thimm2016personality], which measures five domains: disinhibition, antagonism, detachment, negative affect, and psychoticism.
-The scale consists of 25 items rated on a 4-point Likert scale, ranging from 0 (very false or often false) to 3 (very true or often true).
-
-On average, all maladaptive personality traits assessed by the PID-5-SF were weakly and negatively correlated with IAS pairings.
-The strongest correlation was observed between the psychoticism dimension and the Muscle/Pain pairing (r = -0.173).
-
-<!-- Schyzoty -->
-Schizotypy was assessed using the Schizotypal Personality Questionnaire – Brief Revised Updated (SPQ-BRU; @davidson2016schizotypal), which consists of 32 items rated on a 5-point Likert scale ranging from strongly agree to strongly disagree.
-This questionnaire evaluates four primary dimensions: cognitive-perceptual (positive), interpersonal (negative), disorganized, and social anxiety. 
-These dimensions are further divided into nine secondary factors: constricted affect, eccentricity, magical thinking, lack of close friends, odd speech, referential thinking, social anxiety, suspiciousness, and unusual perceptions.
-
-On average, all nine factors were weakly and negatively correlated with IAS pairings, with correlations ranging from r = -0.170 (between lack of close friends and Muscles/Pain) to r = 0.102 (between magical thinking and Itch/Bruise).
-
-<!-- Autism -->
-The short version of the Autism-Spectrum Quotient (ASQ-Short; Hoekstra et al., 2011) was used to assess five autistic traits: social skills, adherence to routines, cognitive flexibility (switching), imagination, and patterns/numbers.
-The questionnaire consists of 28 items rated on a 4-point Likert scale, ranging from 1 (definitely agree) to 4 (definitely disagree).
-
-Overall, all pairings were weakly and negatively correlated with the ASQ dimensions, except for the Itch/Bruise and Heart/Breathing pairings, which showed weak positive correlations with the patterns/numbers trait (r = 0.184 and r = 0.038, respectively).
-The strongest correlation was observed between the imagination trait and the Wind/Burp pairing (r = -0.218).
-
-#### Correlations with personality measures
-
-The Big Five Inventory-Short Form [BFI-S; @lang2011short] and the Mini International Personality Item Pool [Mini-IPIP6; @sibley2011mini] were used to assess general personality traits. 
-The BFI-S consists of 15 items rated on a 7-point Likert scale, ranging from 1 (strongly disagree) to 7 (strongly agree), measuring five personality factors: Openness, Conscientiousness, Extraversion, Agreeableness, and Neuroticism.
-The Mini-IPIP6 assesses six personality traits—Extraversion, Agreeableness, Conscientiousness, Neuroticism, Openness, and Honesty-Humility—using 24 items. 
-While this questionnaire is typically scored on a 7-point Likert scale from 1 (very inaccurate) to 7 (very accurate), an analogous scale was used in the respective sample. 
-Lastly, the Neuroticism subscale of the NEO Five-Factor Inventory [Neo-FFI; @costa1992normal] was used to assess Neuroticism, consisting of 12 items rated on a 5-point Likert scale from 1 (strongly disagree) to 5 (strongly agree).
-
-To assess correlations with the IAS pairings, scores were grouped across personality dimensions due to the overlap among these traits (with the exception of Honesty-Humility). 
-On average, IAS pairings were positively associated with most personality dimensions, though these correlations were generally weak.
-The strongest correlation was observed between Conscientiousness and the Hungry/Thirsty pairing (r = 0.164).
-Both Honesty-Humility and Neuroticism were weakly and negatively correlated with the IAS pairings, with the highest correlations observed for the Hungry/Thirsty pairing (r = -0.217 and r = -0.200, respectively).
-
-#### Correlations with other measures
-
-<!-- PI -->
-
-The IAS was also correlated with primal world beliefs, as measured by the Primal Inventory [PI-18; @clifton2021brief], which assesses beliefs about the world being alive, good, safe, and enticing. 
-Items that evaluate neutral beliefs about the hierarchical order of importance in the world (i.e., hierarchical), as well as beliefs about the comprehensibility of most things and situations (i.e., understandable), and the belief that the world is characterized by flux (i.e., changing) were added as well.
-The scale contains 18 items ranging from 5 (Strongly agree) to 0 (strongly disagree).
-
-Overall, most primal beliefs show weak positive correlations with all pairings of the IAS. The strongest correlation is between the hierarchical belief and the Hungry/Thirsty pairing (r = 0.181). 
-Some beliefs, however, exhibit negative correlations with certain pairings. 
-These negative correlations range from r = -0.0940 between the changing belief and the Hungry/Thirsty pairing, to r = -0.00490 between the Enticing belief and the Itch/Bruise pairing.
-
-<!-- GCBS -->
-
-The Generic Conspiracist Beliefs Scale [GCBS; @brotherton2013measuring] was used to assess five facets of conspiracy beliefs: Extraterrestrial, Global Conspiracies, Government Malfeasance, Information Control, and Personal Wellbeing.
-The scale comprises 15 items rated on a 5-point Likert scale, ranging from definitely not true (1) to definitely true (5).
-
-Overall, the GCBS showed a weak but positive correlation with all facets of the IAS, with the strongest correlation observed between Global Conspiracies and Hungry/Thirsty (r = 0.140). 
-Negative correlations were found within the Global Conspiracies, Extraterrestrial, and Information Control facets, though these were small, ranging from r = -0.0101 to r = -0.0167.
-
-<!-- LIE -->
-
-Lastly, the Lying Profile Questionnaire [LIE; @makowski2023structure] a 16 item visual analog scale was used to assess 4 dispositional lying simensions: ability; negativity, contextuality, and frequency.
-
-Overall, most lying profile dimensions show weak correlations with IAS pairings. 
-Ability exhibits primarily weak positive correlations, with the strongest observed for Wind/Burp (r = 0.082).
-In contrast, Frequency tends to show weak negative correlations, ranging from Wind/Burp (r = -0.062) to Muscles/Pain (r = -0.088).
-Contextuality displays mixed correlations, with Itch/Bruise showing the strongest negative association (r = -0.127), while Urinate/Defecate has a small positive correlation (r = 0.045).
-Finally, Negativity is consistently positively correlated with all pairings, with the strongest relationship found for Hungry/Thirsty (r = 0.090).
+[**ANA: Confirm personality**]
 

### 2025-08-28 analysis/Study1.qmd
renamed personality columns

--- 2025-08-27 analysis/Study1.qmd
@@
 df7a$STAIT_Mean <- df7a$STAIT_Sum/20
+df7a$Neuroticism <- rowMeans(select(df7a,NEOFFI_01:NEOFFI_12))
 
@@
   mutate(
-    BFI_NEUROTICISM = (BFI_1 + BFI_2 + BFI_3)/3,
-    BFI_AGREEABLENESS = (BFI_10R + BFI_11 + BFI_12)/3,
-    BFI_EXTROVERSION = (BFI_4 + BFI_5 + BFI_6),
-    BFI_CONSCIENTIOUSNESS = (BFI_13 + BFI_14 + BFI_15R)/3,
-    BFI_OPENNESS = (BFI_7 + BFI_8 + BFI_9)/3
-    )
+    Neuroticism = (BFI_1 + BFI_2 + BFI_3)/3,
+    Agreeableness = (BFI_10R + BFI_11 + BFI_12)/3,
+    Extraversion = (BFI_4 + BFI_5 + BFI_6),
+    Conscientiousness = (BFI_13 + BFI_14 + BFI_15R)/3,
+    Openness = (BFI_7 + BFI_8 + BFI_9)/3) |>
+  mutate(across(starts_with("BFI_"), \(x) datawizard::rescale(x, to = c(0, 1))))
+
 ```
@@
          across(starts_with("Item_PHQ4_Depression_"), \(x) datawizard::rescale(x, to = c(1,4))),
-        across(starts_with("Item_PHQ4_Anxiety_"), \(x) datawizard::rescale(x, to = c(1,4)))) |>
-  mutate(PHQ4_Depression = Item_PHQ4_Depression_3 + Item_PHQ4_Depression_4,
-          PHQ4_Anxiety = Item_PHQ4_Anxiety_1 + Item_PHQ4_Anxiety_2)
+        across(starts_with("Item_PHQ4_Anxiety_"), \(x) datawizard::rescale(x, to = c(1,4))),
+        across(starts_with("IPIP6_"), \(x) datawizard::rescale(x, to = c(0,1))),
+        PHQ4_Depression = Item_PHQ4_Depression_3 + Item_PHQ4_Depression_4,
+          PHQ4_Anxiety = Item_PHQ4_Anxiety_1 + Item_PHQ4_Anxiety_2) |>
+  rename(
+     Agreeableness = IPIP6_Agreeableness,
+    Conscientiousness = IPIP6_Conscientiousness,
+    Extraversion = IPIP6_Extraversion,
+    HonestyHumility = IPIP6_HonestyHumility,
+    Neuroticism = IPIP6_Neuroticism,
+    Openness = IPIP6_Openness
+  )
 ```

### 2025-08-28 analysis/study2.qmd
Update study2.qmd

@@
   data,
-  pool_coef(with = "NEO_FFI_Mean", component = "Personality", name = "Neuroticism"),
-  pool_coef(with = "BFI_AGREEABLENESS", component="Personality", name = "Agreeableness"),
-  pool_coef(with = "BFI_CONSCIENTIOUSNESS", component="Personality", name = "Conscientiousness"), 
-  pool_coef(with = "BFI_NEUROTICISM", component="Personality", name = "Neuroticism"),
-  pool_coef(with = "BFI_OPENNESS", component="Personality", name = "Openness"),
-  pool_coef(with = "BFI_EXTROVERSION", component="Personality", name = "Extraversion"),
-  pool_coef(with = "IPIP6_Agreeableness", component="Personality", name = "Agreeableness"),
-  pool_coef(with = "IPIP6_Conscientiousness", component="Personality", name = "Conscientiousness"), 
-  pool_coef(with = "IPIP6_Neuroticism", component="Personality", name = "Neuroticism"),
-  pool_coef(with = "IPIP6_Openness", component="Personality", name = "Openness"),
-  pool_coef(with = "IPIP6_Extraversion", component="Personality", name = "Extraversion"), 
-  pool_coef(with = "IPIP6_HonestyHumility", component="Personality", name = "Honesty-Humility")
+  pool_coef(with = "Neuroticism", component = "Personality", name = "Neuroticism"),
+  pool_coef(with = "Agreeableness", component="Personality", name = "Agreeableness"),
+  pool_coef(with = "Conscientiousness", component="Personality", name = "Conscientiousness"), 
+  pool_coef(with = "Openness", component="Personality", name = "Openness"),
+  pool_coef(with = "Extraversion", component="Personality", name = "Extraversion"),
+  pool_coef(with = "HonestyHumility", component="Personality", name = "Honesty-Humility")
 )

### 2025-08-29 analysis/Study1.qmd
fixed personality duplicates

@@
   ) |> 
-  mutate(across(starts_with("MAIA_"), \(x) x - 1)) # Original scale 1-6
+  mutate(across(starts_with("MAIA_"), \(x) x - 1),
+         across(starts_with("NEOFFI_"),  \(x) datawizard::rescale(x, to = c(0, 1)))) # Original scale 1-6
 
@@
   ) |>
+  mutate(across(starts_with("BFI_"), \(x) datawizard::rescale(x, to = c(0, 1)))) |>
   mutate(
@@
     Agreeableness = (BFI_10R + BFI_11 + BFI_12)/3,
-    Extraversion = (BFI_4 + BFI_5 + BFI_6),
+    Extraversion = (BFI_4 + BFI_5 + BFI_6)/3,
     Conscientiousness = (BFI_13 + BFI_14 + BFI_15R)/3,
-    Openness = (BFI_7 + BFI_8 + BFI_9)/3) |>
-  mutate(across(starts_with("BFI_"), \(x) datawizard::rescale(x, to = c(0, 1))))
+    Openness = (BFI_7 + BFI_8 + BFI_9)/3)
 

### 2025-08-29 analysis/study2.qmd
fixed personality duplicates

@@
   data,
-  pool_coef(with = "Neuroticism", component = "Personality", name = "Neuroticism"),
-  pool_coef(with = "Agreeableness", component="Personality", name = "Agreeableness"),
-  pool_coef(with = "Conscientiousness", component="Personality", name = "Conscientiousness"), 
-  pool_coef(with = "Openness", component="Personality", name = "Openness"),
-  pool_coef(with = "Extraversion", component="Personality", name = "Extraversion"),
-  pool_coef(with = "HonestyHumility", component="Personality", name = "Honesty-Humility")
+  pool_coef(with = "Neuroticism", component = "Personality", name = "Neuroticism",unequalrange=TRUE),
+  pool_coef(with = "Agreeableness", component="Personality", name = "Agreeableness",unequalrange=TRUE),
+  pool_coef(with = "Conscientiousness", component="Personality", name = "Conscientiousness",unequalrange=TRUE), 
+  pool_coef(with = "Openness", component="Personality", name = "Openness",unequalrange=TRUE),
+  pool_coef(with = "Extraversion", component="Personality", name = "Extraversion", unequalrange=TRUE),
+  pool_coef(with = "HonestyHumility", component="Personality", name = "Honesty-Humility",unequalrange=TRUE)
 )

### 2025-08-29 paper/1_Initial/manuscript.qmd
fixed indentations on YAML
results study 2 completed

@@
 <!-- Demographic correlates -->
-Age showed consistent positive associations across tasks (mean r = .12), with all correlations significant.
-Gender differences were weaker (mean r = −.01), though a majority of effects reached significance.
+Age was positively associated across Ias correlates (mean r = .12), with all correlations significant. Gender showed near-zero effects (mean r = −.01), with 63% reaching significance.
 
 <!-- Interoceptive measures -->
-Several MAIA subscales showed moderate and consistently significant positive associations with IAS scores.
-Noticing (mean β = .259), Attention Regulation (β = .249), Trusting (β = .236), Emotional Awareness (β = .197), Listening (β = .176), and Self-Regulation (β = .189) were significant across all pairings and the original scale.
-Autonomic reactivity from the BPQ was negatively associated (β = −.173, 88% significant), whereas body awareness showed weaker and less reliable effects (β = .122, 25% significant).
-Alexithymia was consistently negative: ICQ (β = −.316), TAS subscales: Difficulties Identifying Feelings (βs = −.211) , Difficulties Describing Feelings (βs = −.150), External Thinking (βs = −.081, 75% significance), and the BVAQ cognitive component (β = −0.200) were significant for nearly all IAS correlates.
+MAIA subscales showed consistent positive associations with IAS: Noticing (β = .259), Attention Regulation (β = .249), Trusting (β = .236), Emotional Awareness (β = .197), Listening (β = .176), and Self-Regulation (β = .189) were significant across IAS pairings and the full scale.
+Autonomic reactivity (BPQ) was negatively associated (β = −.173, 88% significant), while body awareness was weaker and unreliable (β = .122, 25%).
+Alexithymia was consistently negative: ICQ (β = −.316), TAS-DIF (β = −.211), TAS-DDF (β = −.150), TAS-EOT (β = −.081, 75%), and BVAQ-Cognitive (β = −.200) were robust.
+In contrast, BVAQ-Affective showed a weak and inconsistent positive effect (β = .042, 13%).
 
@@
 
-Depression (BDI: β = −0.204) and anxiety (STAI-T: β = −0.189) showed reliably negative associations.
-PHQ-15 (β = −0.128, 75% significant) PHQ-4 (depression: β = −0.094, 75% significant; anxiety: β = −0.103, 88% significant), and GAD-7 (β =−0.187, 63% significance) also showed consistent negative effects.
-By contrast, PHQ-9 (β = −0.619) and MFQ (β = −0.139) were largely nonsignificant despite negative averages.
+Depression (BDI: β = −.204) and anxiety (STAI-T: β = −.189) were reliably negative.
+Additional scales also showed consistent, though weaker, effects: PHQ-15 (β = −.128, 75%), PHQ-4 depression (β = −.094, 75%), PHQ-4 anxiety (β = −.103, 88%), and GAD-7 (β = −.187, 63%).
+By contrast, PHQ-9 (β = −.619, 25%) and MFQ (β = −.139, 13%) were largely nonsignificant despite negative averages.
 
-<!-- Psychopathology and personality -->
+<!-- Psychopathology -->
 
-Autistic traits showed the clearest pattern: Imagination (β = −0.184, 88% significant), Low Attentional Switching (β = −0.143, 63% significant), and Lack of Social Skills (β = −0.119, 63% significant) were reliably negative.
-Among maladaptive traits, Negative Affect (β = −0.111, 63% significant) was the only consistent correlate.
-Schizotypal traits showed generally weak and unreliable associations, with No Close Friends (β = −0.12, significant in 50% of models) being the only subscale to exhibit a small effect, and even this just at the threshold of consistency.
+Autistic traits showed the clearest pattern: Imagination (β = −.184, 88%), Low Attentional Switching (β = −.143, 63%), and Lack of Social Skills (β = −.119, 63%) were consistently negative.
+Among maladaptive traits, only Negative Affect (β = −.111, 63%) showed reliable associations.
+Schizotypal traits were generally weak, with only No Close Friends (β = −.122, 50%) approaching consistency.
 
@@
 
-Of the Big Five, only Openness showed consistent positive associations (β = 0.123, 63% significant).
-Other traits were weak or mostly nonsignificant.
-Conspiracy, world belief, and lying profiles showed no reliable associations.
-
-[**ANA: Confirm personality**]
+Within the Big Five, Openness (β = .143, 100%), Agreeableness (β = .053, 100%), and Conscientiousness (β = .028, 88%) were consistently positive; other traits were negligible.
+Conspiracy, world belief, and lying profiles showed no reliable effects, except a small and small and somewhat consistent association with the belief that the world is alive (β = .087, 63%).
 

### 2025-08-29 analysis/Study1.qmd
updated study 1 html

@@
 - Makowski
-  - Note: First sample has some missing items (No Taste, Cough, Blood_Sugar)
+  - Note: sample has some missing items (No Taste, Cough, Blood_Sugar)
   - Note: Analog scales
@@
 
-- Poreiro et al., 
+- Poerio et al., 
   - Study 1: https://osf.io/49wbv
@@
 ### Sample 15
-- Poreiro: unpublished
+- Poerio: unpublished
 
@@
 
-- Raquel Arjona and Robyn Scharte data
+- Raquel Arjona and Robyn Scharte data upublished
 

### 2025-08-29 analysis/study2.qmd
updated study 2 html
added other primals to the correlates

@@
 
+# data <- rbind(
+#   data, 
+#   pool_coef(with = "PI_Alive", component="World Beliefs", name = "Alive", unequalrange=TRUE))
+
 data <- rbind(
   data,
-  pool_coef(with = "PI_Alive", component="World Beliefs", name = "Alive", unequalrange=TRUE))
-
-# data <- rbind(
-#   data,
-#   pool_coef(with = "PI_Alive", component="World Beliefs", name = "Alive"),
-#   pool_coef(with = "PI_Changing", component="World Beliefs", name = "Changing"),
-#   pool_coef(with = "PI_Enticing", component="World Beliefs", name = "Enticing"),
-#   pool_coef(with = "PI_Good", component="World Beliefs", name = "Good"),
-#   pool_coef(with = "PI_Hierarchical", component="World Beliefs", name = "Hierarchical"),
-#   pool_coef(with = "PI_Safe", component="World Beliefs", name = "Safe"),
-#   pool_coef(with = "PI_Understandable", component="World Beliefs", name = "Understandable"),
-# )
+  pool_coef(with = "PI_Alive", component="World Beliefs", name = "Alive", unequalrange=TRUE),
+  pool_coef(with = "PI_Changing", component="World Beliefs", name = "Changing", unequalrange=TRUE),
+  pool_coef(with = "PI_Enticing", component="World Beliefs", name = "Enticing", unequalrange=TRUE),
+  pool_coef(with = "PI_Good", component="World Beliefs", name = "Good", unequalrange=TRUE),
+  pool_coef(with = "PI_Hierarchical", component="World Beliefs", name = "Hierarchical", unequalrange=TRUE),
+  pool_coef(with = "PI_Safe", component="World Beliefs", name = "Safe",unequalrange=TRUE),
+  pool_coef(with = "PI_Understandable", component="World Beliefs", name = "Understandable",unequalrange=TRUE)
+)
 ```

### 2025-08-29 paper/1_Initial/manuscript.qmd
updates manuscript

@@
     roles: 
+      - bla bla
     affiliations:
@@
   - name: Robyn Scharte
-    orcid: 
+    orcid: blabla
     roles: 
+      - bla bla
     affiliations:
@@
         department: "Sussex Addictions Research and Intervention Centre"
+  - name: Dominique Makowski
+    corresponding: true
+    orcid: 0000-0001-5375-9967
+    email: D.Makowski@sussex.ac.uk
+    url: https://realitybending.github.io/
+    roles:
+      - Project administration
+      - Data curation
+      - Formal Analysis
+      - Investigation
+      - Visualization
+      - Writing – original draft
+      - Writing – review & editing
+    affiliations:
+      - ref: "id1"
+      - name: "University of Sussex"
+        department:  "Sussex Centre for Consciousness Science"
 # author-note:
@@
     #   - Writing – original draft
-  - name: Dominique Makowski
-    corresponding: true
-    orcid: 0000-0001-5375-9967
-    email: D.Makowski@sussex.ac.uk
-    url: https://realitybending.github.io/
-    roles:
-      - Project administration
-      - Data curation
-      - Formal Analysis
-      - Investigation
-      - Visualization
-      - Writing – original draft
-      - Writing – review & editing
-    affiliations:
-      - ref: "id1"
-      - name: "University of Sussex"
-        department:  "Sussex Centre for Consciousness Science"
 author-note:
@@
 <!-- IAS structure  --> 
+**NOTES: todd 2022 found no correlation for MAIA and IAS except  with the non-worrying facet + Gaggero found positive correlations with IAS and MAIA (general).**
+
 The original validation study suggested a two-factor structure for the IAS, one reflecting the perception of general interoceptive signals (urinate, hungry, defecate, thirsty, pain, heart, taste, breathing, temperature, muscles, affective touch, vomit, sexual arousal), and other relating to signals that may be difficult to perceive solely through interoceptive information (itch, tickle, cough, burp, bruise, blood sugar, sneeze, wind).
@@
 Small positive correlations have also been observed with the "observation" and "description" subscales of the Five Facet Mindfulness Questionnaire [FFMQ, @baer2006using; @brand2023; @koike2023], as well as with the "non-reactivity" and "acting with awareness" subscales [@koike2023].
-Additionally, the IAS has shown a positive correlation with the interoceptive awareness subscale of the Eating Disorder Inventory [EDI-IA; @lin2023] and a negative correlation with the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia], as reported by @brand2023 and @murphy2019.
+Additionally, the IAS has shown a positive correlation with the interoceptive awareness subscale of the Eating Disorder Inventory [EDI-IA, @lin2023] and a negative correlation with the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia], as reported by @brand2023 and @murphy2019.
 Lastly, the correlation with the Interoceptive Attention Scale [IATS, @gabriele2022dissociations] appears rather small [@lin2023; @koike2023].
@@
 
-Study 1 will re-analyse and assess the factor structure of the IAS by taking advantage of the large number of open-access datasets [@brand2023; @campos2021; @lin2023; @murphy2019; @arslanova2022; @todd2022; @gaggero2021; @brand2022; @von2023].
+Study 1 will re-analyse and assess the factor structure of the IAS by taking advantage of the large number of open-access datasets [@brand2023; @campos2021; @lin2023; @murphy2019; @arslanova2022; @todd2022; @gaggero2021; @brand2022; @von2023; @makowski2025measuring; @poerio2024interoceptive].
 While combining these studies might provide a more robust and generalizable understanding of the IAS' factor structure, we also additionally provide an individual analysis (i.e., applying the same method on all samples separately) to add nuance to the general picture, as all studies differ in their sample size, demographic characteristics, language, and procedure.
@@
 
-The first study aimed to clarify the factor structure of the IAS, a widely used subjective measure of interoception whose dimensionality remains contested.
-Previous validation and psychometric studies have proposed conflicting models ranging from a single general factor [@brand2023] to bifactor [@campos2021; @lin2023], and two-factor solutions [@murphy2019; @koike2023].
-At the same time, network-based approaches such as EGA emphasize local dependencies between items, identifying clusters at the item level that may not map neatly onto broader latent constructs [@christensen2023; @desmedt2022measures].
-By leveraging open-access datasets and reanalyzing them both in aggregate and individually using a mega-analytic approach, and by contrasting traditional factor-analytic models with network-based methods, this study provides the most comprehensive test of the IAS structure to date.
+The first study aimed to provide the most systematic test of the IAS structure to date.
+Previous work has produced conflicting models, ranging from a single general factor [@brand2023], to bifactor solutions [@campos2021; @lin2023], and two-factor models [@murphy2019; @koike2023].
+Alongside these structural discrepancies, several studies have questioned the quality of specific items.
+@murphy2019 distinguished between items tapping direct interoceptive signals (e.g., heartbeat) and others reflecting phenomena less accessible to interoception (e.g., bruising).
+Additionally, @lin2023 identified locally dependent pairs and low-discrimination items with Network-based methods, while @campos2021 found that “tickle” did not load on the general factor.
+To address these open questions, we reanalyzed multiple open-access datasets using a mega-analytic framework, contrasting traditional factor-analytic approaches with network-based methods.
 
@@
 Overall, the findings converge on a robust yet novel picture.
+Initial analysis revealed issues in 6 items (e.g., instability, redudancy, low associations, less reliable) which led to the formation of a 14-item IAS.
 Exploratory and confirmatory analyses indicated that the IAS is best characterized by seven pairs of closely related items, consistently identified by EGA and supported by HCA.
-These pairs (e.g., hunger–thirst, urinate–defecate, cough–sneeze) were highly replicable across independent samples and yielded superior fit indices in CFA compared to one-factor, three-factor, three-factor with ageneral factor, five-factor, a five-factor with a general factor, a 7-factor or a seven factor with a general factor alternatives.
+These pairs (e.g., hunger–thirst, urinate–defecate, cough–sneeze) were highly replicable across independent samples and yielded superior fit indices in CFA compared to other solutions.
 Although the one-factor model occasionally achieved lower BIC, Bayes factor comparisons overwhelmingly supported the EGA structure, underlining its empirical robustness.
@@
 In other words, the IAS may function more as a checklist of bodily signal detection items than as a scale measuring a coherent higher-order dimension.
-This stands in contrast to the original two-factor proposal [@murphy2019], where the factors were highly correlated and often collapsed into a unidimensional score, and helps explain why subsequent studies diverged in their conclusions: the psychometric structure of the IAS appears to be driven more by local dependencies than by robust latent factors.
+This stands in contrast to the original two-factor proposal [@murphy2019], where the factors were highly correlated and collapsed into a unidimensional score, and helps explain why subsequent studies diverged in their conclusions: the psychometric structure of the IAS appears to be driven more by local dependencies than by robust latent factors.
 Second, the presence of redundant or unstable items (e.g., tickle, taste, affective touch), already highlighted in prior validation studies [@campos2021; @lin2023], undermines the interpretability of the scale, as their contributions appear inconsistent or overlapping.
 Together, these findings help explain why previous research has struggled to converge on a stable factor structure: the IAS lacks the psychometric properties required for strong latent modeling and may overstate its dimensionality by conflating redundancy with structure.
-
-**[ADD THAT LIN CREATED A SHORT VERSION OF THE IAS??]**
 
@@
 However, the limited breadth of these pairings, the redundancy across items, and the reliance on a narrow 5-point scale all restrict the scale’s ability to differentiate between individuals and to capture the multidimensional nature of interoception [@desmedt2022measures].
-These findings therefore call for refinement—either through targeted revisions of the IAS (e.g., removing redundant items, expanding modality coverage, adopting analogue response formats) or through the development of a new questionnaire that better balances theoretical coherence with empirical validity.
+These findings therefore call for refinement, either through targeted revisions of the IAS (e.g., removing redundant items, expanding modality coverage, adopting analogue response formats) or through the development of a new questionnaire that better balances theoretical coherence with empirical validity.
 
@@
 While this solution is replicable and statistically robust, it highlights the conceptual and psychometric limitations of the IAS in its current form.
-These insights help contextualize the mixed findings on the scale’s validity and correlations with other interoceptive measures [@murphy2019; @brand2023; @lin2023] and provide a crucial foundation for Study 2, where we  to the dispositional correlates of the IAS to further evaluate its construct validity and situate it within the broader network of interoceptive and psychological traits.
+These insights help contextualize the mixed findings on the scale’s validity and correlations with other interoceptive measures [@murphy2019; @brand2023; @lin2023] and provide a crucial foundation for Study 2, where we  do the dispositional correlates of the IAS to further evaluate its construct validity and situate it within the broader network of interoceptive and psychological traits.
 
@@
 <!-- Interoception Related -->
-**Interoception Related**
-The Multidimensional Assessment of Interoceptive Awareness Version-2 [MAIA-2, @memehling2018multidimensional] is a 37-item questionnaire assessing eight dimensions of interoception: Noticing, Not-Distracting, Not-Worrying, Attention Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust.
+**Interoception Related**.
+The Multidimensional Assessment of Interoceptive Awareness Version-2 [MAIA-2, @mehling2018multidimensional] is a 37-item questionnaire assessing eight dimensions of interoception: Noticing, Not-Distracting, Not-Worrying, Attention Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust.
 Responses are rated on a 6-point Likert scale (e.g., “I notice when I am uncomfortable in my body”).
@@
 <!-- Mood and Anxiety -->
-**Mood and Anxiety Related**
+**Mood and Anxiety Related**.
 The Beck Depression Inventory-II [BDI-II, @beck1996beck] is a 21-item measure of depressive symptom severity, including psychological (e.g., guilt) and physiological (e.g., loss of energy) components.
@@
 <!-- Personality -->
-**Personality**
-The NEO Five-Factor Inventory, neuroticism subscale [NEO-FFI, @costa1989neoffi] is a 12-item measure of neuroticism, assessing the general tendency to experience negative emotions such as fear, sadness, or disgust.
+**Personality**.
+The NEO Five-Factor Inventory, neuroticism subscale [NEO-FFI, @costa1992neo] is a 12-item measure of neuroticism, assessing the general tendency to experience negative emotions such as fear, sadness, or disgust.
 Items are rated on a 5-point Likert scale (e.g., “I often feel inferior to others”).
@@
 <!-- Psychopathology -->
-**Psychopathology**
+
+**Psychopathology**.
 The Personality Inventory for DSM-5 Short Form [PID-5-SF, @thimm2016personality] consists of 25 items rated on a 4-point Likert scale, measuring five domains: disinhibition, antagonism, detachment, negative affect, and psychoticism (e.g., “Plenty of people are out to get me”).
@@
 <!-- Beliefs and Misbeliefs -->
-**Beliefs and Misbeliefs**
+**Beliefs and Misbeliefs**.
 The Generic Conspiracist Beliefs Scale [GCBS, @brotherton2013measuring] is a 15-item measure assessing five dimensions of conspiracy beliefs: government malfeasance, extraterrestrial cover-up, malevolent global conspiracies, personal wellbeing, and control of information.
@@
 
-The Primal World Beliefs Inventory Short Form [PI-18, @lifton2021brief] is an 18-item measure assessing four high-order beliefs: the world is Good (vs.
+The Primal World Beliefs Inventory Short Form [PI-18, @clifton2021brief] is an 18-item measure assessing four high-order beliefs: the world is Good (vs.
 Bad) and its three dimensions: Safe (vs.
@@
 For continuous predictors, we will first ensure consistent ranges across datasets; when necessary, ranges will be rescaled to achieve comparability.
-In cases where scales of different lengths measured the same construct, scores were harmonized: when possible, means were computed from overlapping items, while in other cases total scores were normalized by the number of items.
-Redundant subscales (e.g., PHQ-2 and GAD-2 within PHQ-4) were collapsed into unified composite scores.
-Similarly, short forms of trait anxiety (e.g., STAI-5-trait) were collapsed with their longer counterpart (STAI-T), with scores computed as the mean to ensure comparable ranges.
-Longer formats of the PI (PI-99) were collapsed into its shorter version (PI-18).
-Missing data were handled via listwise deletion on a per-model basis prior to fitting.
+In cases where scales of different lengths measure the same construct, scores will be harmonized: when possible, means will be computed from overlapping items, while in other cases total scores will be normalized by the number of items.
+We will collapse redundant subscales (e.g., PHQ-2 and GAD-2 within PHQ-4) into unified composite scores.
+Similarly, short forms of trait anxiety (e.g., STAI-5-trait) will be collapsed with their longer counterpart (STAI-T), with scores computed as the mean to ensure comparable ranges.
+Longer formats of the PI (PI-99) will be collapsed into its shorter version (PI-18).
+Missing data will be handled via listwise deletion on a per-model basis prior to fitting.
 
 <!-- Multilevel modelling approach -->
-Associations were estimated using multilevel regression models implemented in the glmmTMB package [@glmmTMB].
-Each predictor was entered separately, with the seven IAS item pairs identified in Study 1 (“Hungry–Thirsty”, “Muscles–Pain”, “Wind–Burp”, “Urinate–Defecate”, “Breathing–Heart”, “Bruise–Blood”, “Cough–Sneeze”) and the original IAS scale serving as outcomes.
-Models included random intercepts and slopes by sample to account for between-study heterogeneity; when models failed to converge, a reduced structure with random intercepts only was used.
-This approach treats datasets as clusters, thereby providing pooled estimates of the associations while accounting for both within- and between-sample variability, akin to a meta-analytic framework.
+Associations will be estimated using multilevel regression models implemented in the glmmTMB package [@glmTMB].
+Each predictor will be entered separately, with the seven IAS item pairs identified in Study 1 (“Hungry–Thirsty”, “Muscles–Pain”, “Wind–Burp”, “Urinate–Defecate”, “Breathing–Heart”, “Bruise–Blood”, “Cough–Sneeze”) and the original IAS scale serving as outcomes.
+Models will include random intercepts and slopes by sample to account for between-study heterogeneity; when models fail to converge, a reduced structure with random intercepts only will be used.
+This approach will treat datasets as clusters, thereby providing pooled estimates of the associations while accounting for both within- and between-sample variability, akin to a meta-analytic framework.
 
 <!-- Extraction of parameters -->
-From each fitted model, we extracted standardized regression coefficients (β), 95% confidence intervals, p-values, convergence status, and effective sample size.
-Participants identifying as “Other” were excluded from analyses due to limited representation.
+From each fitted model, we will extract standardized regression coefficients (β), 95% confidence intervals, p-values, convergence status, and effective sample size.
+Participants identifying as “Other” will be excluded from analyses due to limited representation.
 
@@
 Within the Big Five, Openness (β = .143, 100%), Agreeableness (β = .053, 100%), and Conscientiousness (β = .028, 88%) were consistently positive; other traits were negligible.
-Conspiracy, world belief, and lying profiles showed no reliable effects, except a small and small and somewhat consistent association with the belief that the world is alive (β = .087, 63%).
+Conspiracy, world belief, and lying profiles showed no reliable effects, except a small and consistent association with the believe the world is readily comprehensible (β = .113, 75%) and a small and somewhat consistent association with the belief that the world is alive (β = .087, 63%)
+
+<!-- Number of correlations with the intero vars -->
+Across these pairs, the “Original” scale was most frequently the strongest correlate (25 instances), followed by Hungry/Thirsty (16), Bruise/Blood (11), Muscles/Pain (7), and smaller contributions from Breathing/Heart, Cough/Sneeze, Urinate/Defecate, and Wind/Burp.
 
@@
 
-<!-- strongest and weakest correlations with the IAS--> 
-Our findings underline how subjective measures of interoception exist within a complex network of correlates.
+<!-- Aims recap -->
+The second study set out to provide a comprehensive overview of the dispositional correlates of the IAS by pooling data across multiple datasets, while also testing whether the refined 14-item version identified in Study 1 confers practical advantages over the original 21-item scale.
 
-**TODO:: Firstly, talk about the link with other interoceptive measures.**
-**Then, discuss other correlates by order of importance**
+<!-- Convergence with interoceptive self-reports -->
+Consistent with prior research, the IAS showed strong positive associations with other interoceptive self-report measures, particularly the MAIA, with the exception of the Not Distracting and Not Worrying facets [@brand202].
+This pattern replicates earlier findings while contradicting [@todd2022], who reported only a near-zero correlation with Not Worrying.
+Similarly, while previous evidence on the BPQ was mixed, our results indicate more robust associations with the Autonomic Reactivity dimension compared to body awareness [@campos2021; @brand2023; @todd2022].
+The replication of negative associations with interoceptive confusion [@murphy2019; @brand2023] further supports the convergent and discriminant validity of the IAS.
 
-**TODO: this discussion is too much descriptive for now. Discuss that from a larger perspective. What does it mean in general.**
+<!-- Negative associations with alexithymia and mood -->
+Robust negative correlations were observed between the IAS and alexithymia, in line with prior studies [@murphy2019; @campos2021; @brand2023; @lin2023; @koike2023].
+Similarly, negative associations with depression and anxiety, as measured by the BDI and STAI-T, reinforce the clinical relevance of interoceptive accuracy [@brand2023; @lin2023].
+Somatic symptoms were also negatively related to the IAS, although effect sizes were small, echoing earlier findings [@brand2023; @lin2023; @koike2023].
+At the same time, more recent studies have reported null or inconsistent associations between interoception and mental-health symptomatology, suggesting that these links may not be universal and could depend on measurement choices or sample characteristics [**REF PRE_PRINT?**].
 
-Among these, alexithymia exhibits the strongest negative correlation with the IAS, whereas the MAIA questionnaire shows the strongest positive correlation. 
-These correlates not only help explain different aspects of interoception but also serve as valuable tools for validating interoceptive measures.
+<!-- Autism-related traits -->
+Clear negative associations also emerged with autism-related traits such as imagination, low attentional switching, and reduced social skills.
+These findings resonate with @dubois2016 review reporting interoceptive abnormalities in autism.
+Nonetheless, our findings are limited to a single dataset employing the ASQ, which constrains the generalisability of conclusions regarding the relationship between interoception and autistic traits.
 
-**TODO: integrate the following**
-**Note to dom: @ferentzi2021examining suggests that all MAIA dimensions, except for Not-Worrying and Not-Distracting, relate to a general interoceptive awareness factor.
-The low correlations of NW and ND with this general factor indicate that these dimensions do not contribute significantly to the measurement of general interoceptive awareness.
-Instead, NW appears to measure low emotionality or neuroticism, while ND does not capture a coherent underlying structure.**
+<!-- Personality dimensions -->
+The associations between interoception and personality traits were more nuanced.
+Whereas prior work suggested a negative link with neuroticism [@brand2023], we found this relationship to be inconsistent and even slightly positive, though near zero.
+By contrast, openness and agreeableness were consistently positively associated with the IAS, albeit with small effect sizes.
+These findings are consistent with emerging evidence linking openness to interoception as measured by the MAIA-2 [@simkute2025interoception], and complement reports of associations between objective interoceptive sensitivity and extraversion [@haustein2024interoception].
 
-<!-- consistent pattern of results and interesting exprolatory analysis --> 
-While our results reveal various correlations with the IAS, they are limited to the scope of the given questionnaire.
-Nonetheless, they provide valuable insights into how interoception may relate to different psychological and personality traits. 
-The results show a consistent pattern of correlations with other measures and highlight interesting exploratory results, such as correlations between primal world beliefs with the IAS.
+<!-- Exploratory findings -->
+Beyond established correlates, exploratory analyses revealed weak but positive associations between the IAS and primal world beliefs, specifically perceiving the world as alive and understandable.
+While preliminary, these effects suggest a possible link between one’s relationship with internal bodily signals and broader worldviews, raising intriguing questions about how interoception might shape existential or meaning-related beliefs.
 
-<!-- negative correlation with alexithymia and autism --> 
-Our analysis found a strong negative correlation between alexithymia and IAS scores, aligning with previous research [@herbert2011; @brand2023; @murphy2019]. 
-Similarly, a negative correlation between autism and interoceptive awareness was observed in our sample, consistent with prior findings [@dubois2016].
+<!-- Comparison of 14-item vs. 21-item IAS -->
+A central aim of Study 2 was to assess whether the refined 14-item IAS identified in Study 1 provides practical benefits over the original 21-item scale.
+Our results showed that while the full version was occasionally the stronger correlate, across dispositional measures, the shortened scale retained comparable validity while offering clearer psychometric structure and reduced redundancy as shown in study 1.
+This suggests that the 14-item IAS constitutes a more efficient tool without substantial loss of predictive power.
+In practice, the refined scale offers advantages for researchers and clinicians alike: it reduces participant burden, avoids problematic items flagged in Study 1 (e.g., “tickle,” “taste,” “vomit”), and provides a more coherent representation of interoceptive domains.
 
-<!-- weak correlation with conspiracy beliefs --> 
-Conspiracy beliefs did not strongly correlate with IAS scores, though a slight positive correlation was present. 
-To our knowledge, this relationship has not been previously explored. 
-However, prior studies have suggested connections between interoception and (political) beliefs, potentially pointing to shared underlying mechanisms [@ruisch2022].
-
-<!-- weak correlation with lying profiles --> 
-The relationship between interoception and lying profiles was also weak. 
-This contrasts with previous research suggesting associations between interoception and deception [@makowski2023a], warranting further investigation.
-
-<!-- stroong negative correlations with Mood --> 
-Mood and IAS scores exhibited a strong negative correlation, consistent with prior studies that have documented similar findings [@solanolópez2018]. 
-Additionally, personality traits correlated with interoceptive accuracy scores, reinforcing existing research linking personality and interoception [@erle2021].
-
-<!-- negative correlations with schizotypy --> 
-We also observed negative correlations between schizotypy and interoception, in line with previous studies that identified a similar relationship with interoceptive awareness, particularly in individuals at risk for psychosis [@torregrossa2022].
-
-<!-- positive correlations with some Primal World Beliefs --> 
-Interestingly, world beliefs demonstrated significant positive correlations with interoception. 
-While this relationship has not been previously documented, other forms of belief, such as political ideology, have been linked to interoception [@ruisch2022a]. 
-Further research is needed to determine whether world beliefs, which shape our perception of reality [@clifton2020], are meaningfully connected to interoception.
-
-<!--Summary -->
-
-Overall, our findings highlight the broad relevance of interoception across various cognitive and affective traits, underscoring its significance in both research and clinical contexts. 
-By identifying numerous correlates of the IAS, we contribute not only to a deeper understanding of interoception’s role in daily life but also to the ongoing validation of the IAS and other interoceptive measures.
-This analysis lays an important foundation for the development of new interoceptive assessment tools, further advancing our comprehension of interoception and its impact on human experience.
+<!-- Summary -->
+Overall, these findings provide converging evidence for the construct validity of the IAS, most strongly in relation to interoceptive self-report, alexithymia, mood, and autism-related traits.
+Other associations, particularly with personality and belief systems, were weaker and more exploratory, highlighting both the breadth and the limits of interoceptive awareness as captured by the IAS.
+Taken together, Study 2 advances our understanding of the dispositional landscape of interoception and provides evidence that the refined IAS is a reliable and efficient tool for capturing interoceptive awareness.
 

### 2025-08-29 analysis/Study1.qmd
updated analysis scripts

@@
 - **Sample 13**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df13 , age = "Age", sex = NA, gender = "Gender")`.
-- **Sample 14**: Data from [Poreiro's(2024)](https://osf.io/49wbv) study , included `r report::report_participants(df14 , age = "Age", sex = NA, gender = "Gender")`
-- **Sample 15 **: Data from [Poreiro's] study , included `r report::report_participants(df15 , age = "Age", sex = NA, gender = "Gender")`
+- **Sample 14**: Data from [Poerio's(2024)](https://osf.io/49wbv) study , included `r report::report_participants(df14 , age = "Age", sex = NA, gender = "Gender")`
+- **Sample 15 **: Data from [Poerio's] study , included `r report::report_participants(df15 , age = "Age", sex = NA, gender = "Gender")`
 - **Sample 16 **: Data from [Arjona's] study , included `r report::report_participants(df16 , age = "Age", gender = "Gender")`

### 2025-08-29 analysis/study2.qmd
updated analysis scripts

@@
             .by=c("Component", "var_Correlate")) 
+#   
+# average_corr <- data |>
+#   summarise(
+#     min_r = min(r, na.rm = TRUE), 
+#     mean_r = mean(r, na.rm = TRUE),
+#     max_r = max(r, na.rm = TRUE), 
+#     Max = var_Interoception[which.max(abs(r))],
+#     n_sig_001 = sum(p < .001, na.rm = TRUE),
+#     n_sig_01  = sum(p < .01 & p >= .001, na.rm = TRUE),
+#     n_ns      = sum(p >= .01 | is.na(p)),
+#     total     = dplyr::n(),
+#     .by=c("Component", "var_Correlate")
+#   ) |>
+#   mutate(
+#     perc_sig = (n_sig_001 + n_sig_01) / total
+#   )
 
-sort(table(average_corr$Max), decreasing = TRUE)
-
-average_corr <- data |>
-  summarise(
-    min_r = min(r, na.rm = TRUE), 
-    mean_r = mean(r, na.rm = TRUE),
-    max_r = max(r, na.rm = TRUE), 
-    Max = var_Interoception[which.max(abs(r))],
-    n_sig_001 = sum(p < .001, na.rm = TRUE),
-    n_sig_01  = sum(p < .01 & p >= .001, na.rm = TRUE),
-    n_ns      = sum(p >= .01 | is.na(p)),
-    total     = dplyr::n(),
-    .by=c("Component", "var_Correlate")
-  ) |>
-  mutate(
-    perc_sig = (n_sig_001 + n_sig_01) / total
-  )
 sort(table(average_corr$Max), decreasing = TRUE)

### 2025-08-29 paper/1_Initial/manuscript.qmd
updated manuscript

@@
 However, the limited breadth of these pairings, the redundancy across items, and the reliance on a narrow 5-point scale all restrict the scale’s ability to differentiate between individuals and to capture the multidimensional nature of interoception [@desmedt2022measures].
-These findings therefore call for refinement, either through targeted revisions of the IAS (e.g., removing redundant items, expanding modality coverage, adopting analogue response formats) or through the development of a new questionnaire that better balances theoretical coherence with empirical validity.
+These findings therefore call for refinement, either through targeted revisions of the IAS (e.g., removing redundant items, addition of context-specific items, adopting analogue response formats) or through the development of a new questionnaire that better balances theoretical coherence with empirical validity.
 
@@
 Items are scored on a 5-point Likert scale (e.g., “Nearly everything in the world is beautiful”).
-The PI-99 [@clifton2019primal] scores were combined with the 4 high-order beliefs of the PI-18.
+
+The Primal World Beliefs Inventory [PI-99; @clifton2019primal] is a 99-item measure assessing high-order beliefs about the world.
+Items are scored on a 5-point Likert scale (e.g., “Nearly everything in the world is beautiful”).The PI-18 [@clifton2021brief] is a short form of the orginal questionnaire assessing the 4 main world beliefs: the world is Good (vs.
+Bad) and its three dimensions: Safe (vs.
+Dangerous), Enticing (vs.
+Dull), and Alive (vs.
+Mechanistic).
+Scores from the PI-18 scores were combined with the PI-99.
 
@@
 Similarly, short forms of trait anxiety (e.g., STAI-5-trait) will be collapsed with their longer counterpart (STAI-T), with scores computed as the mean to ensure comparable ranges.
-Longer formats of the PI (PI-99) will be collapsed into its shorter version (PI-18).
+Shorter formats of the PI (PI-18) will be combined with scores of its longer version (PI-99).
 Missing data will be handled via listwise deletion on a per-model basis prior to fitting.
@@
 MAIA subscales showed consistent positive associations with IAS: Noticing (β = .259), Attention Regulation (β = .249), Trusting (β = .236), Emotional Awareness (β = .197), Listening (β = .176), and Self-Regulation (β = .189) were significant across IAS pairings and the full scale.
-Autonomic reactivity (BPQ) was negatively associated (β = −.173, 88% significant), while body awareness was weaker and unreliable (β = .122, 25%).
+Autonomic Reactivity (BPQ) was negatively associated (β = −.173, 88% significant), while Body Awareness (BPQ) was weaker and unreliable (β = .122, 25%).
 Alexithymia was consistently negative: ICQ (β = −.316), TAS-DIF (β = −.211), TAS-DDF (β = −.150), TAS-EOT (β = −.081, 75%), and BVAQ-Cognitive (β = −.200) were robust.
@@
 
-Autistic traits showed the clearest pattern: Imagination (β = −.184, 88%), Low Attentional Switching (β = −.143, 63%), and Lack of Social Skills (β = −.119, 63%) were consistently negative.
+Autistic traits showed a clear pattern: Imagination (β = −.184, 88%), Low Attentional Switching (β = −.143, 63%), and Lack of Social Skills (β = −.119, 63%) were consistently negative.
 Among maladaptive traits, only Negative Affect (β = −.111, 63%) showed reliable associations.
@@
 <!-- Number of correlations with the intero vars -->
-Across these pairs, the “Original” scale was most frequently the strongest correlate (25 instances), followed by Hungry/Thirsty (16), Bruise/Blood (11), Muscles/Pain (7), and smaller contributions from Breathing/Heart, Cough/Sneeze, Urinate/Defecate, and Wind/Burp.
+Across these pairs, the full scale was most frequently the strongest correlate (25 instances), followed by Hungry/Thirsty (16), Bruise/Blood (11), Muscles/Pain (7), and smaller contributions from Breathing/Heart, Cough/Sneeze, Urinate/Defecate, and Wind/Burp.
+
+[**NOTE* justify the choice of those specific primals ? higehr correlations with the IAS?]
 
@@
 <!-- Convergence with interoceptive self-reports -->
-Consistent with prior research, the IAS showed strong positive associations with other interoceptive self-report measures, particularly the MAIA, with the exception of the Not Distracting and Not Worrying facets [@brand202].
+Consistent with prior research, the IAS showed strong positive associations with other interoceptive self-report measures, particularly the MAIA, with the exception of the Not Distracting and Not Worrying facets [@brand2023].
 This pattern replicates earlier findings while contradicting [@todd2022], who reported only a near-zero correlation with Not Worrying.
 Similarly, while previous evidence on the BPQ was mixed, our results indicate more robust associations with the Autonomic Reactivity dimension compared to body awareness [@campos2021; @brand2023; @todd2022].
-The replication of negative associations with interoceptive confusion [@murphy2019; @brand2023] further supports the convergent and discriminant validity of the IAS.
+This pattern diverges from earlier findings that consistently reported significant positive associations with Body Awareness [@gaggero2021; @campos2021; @brand2023], while at the same time complementing reports of significant negative correlations with Autonomic Reactivity  [@gaggero2021].
+The replication of negative associations with interoceptive confusion [@murphy2019; @brand2023; @gaggero2021] further supports the convergent and discriminant validity of the IAS.
 
@@
 Somatic symptoms were also negatively related to the IAS, although effect sizes were small, echoing earlier findings [@brand2023; @lin2023; @koike2023].
-At the same time, more recent studies have reported null or inconsistent associations between interoception and mental-health symptomatology, suggesting that these links may not be universal and could depend on measurement choices or sample characteristics [**REF PRE_PRINT?**].
+At the same time, more recent studies have reported null or inconsistent associations between interoceptive sensitivity and mental-health symptomatology, suggesting that such links may not generalize across all interoceptive domains and could be contingent on measurement approaches or sample characteristics [**REF PRE_PRINT?**].
 
@@
 By contrast, openness and agreeableness were consistently positively associated with the IAS, albeit with small effect sizes.
-These findings are consistent with emerging evidence linking openness to interoception as measured by the MAIA-2 [@simkute2025interoception], and complement reports of associations between objective interoceptive sensitivity and extraversion [@haustein2024interoception].
+These findings are consistent with emerging evidence linking openness to interoception as measured by the MAIA-2 [@simkute2025interoception], and complement reports of associations between interoceptive sensitivity (i.e., the accuracy of reported heartbeat counts relative to actual heartbeats) and extraversion [@haustein2024interoception].
 

### 2025-08-31 paper/1_Initial/manuscript.qmd
updated manuscript

@@
 <!-- IAS structure  --> 
-**NOTES: todd 2022 found no correlation for MAIA and IAS except  with the non-worrying facet + Gaggero found positive correlations with IAS and MAIA (general).**
+[**NOTES**: todd 2022 found no correlation for MAIA and IAS except  with the non-worrying facet + Gaggero found positive correlations with IAS and MAIA (general)]
 
@@
 Overall, the findings converge on a robust yet novel picture.
-Initial analysis revealed issues in 6 items (e.g., instability, redudancy, low associations, less reliable) which led to the formation of a 14-item IAS.
+Initial analysis revealed issues in 7 items (e.g., instability, redudancy, low associations, less reliable) which led to the formation of a 14-item IAS.
 Exploratory and confirmatory analyses indicated that the IAS is best characterized by seven pairs of closely related items, consistently identified by EGA and supported by HCA.
@@
 While this solution is replicable and statistically robust, it highlights the conceptual and psychometric limitations of the IAS in its current form.
-These insights help contextualize the mixed findings on the scale’s validity and correlations with other interoceptive measures [@murphy2019; @brand2023; @lin2023] and provide a crucial foundation for Study 2, where we  do the dispositional correlates of the IAS to further evaluate its construct validity and situate it within the broader network of interoceptive and psychological traits.
+These insights help contextualize the mixed findings on the scale’s validity and provide a crucial foundation for Study 2, where we  do the dispositional correlates of the IAS to further evaluate its construct validity and situate it within the broader network of interoceptive and psychological traits.
 
@@
 Building on the structural findings from Study 1, the second study turns to the validity of the IAS by examining its dispositional correlates.
-Although the IAS has been widely used, evidence regarding its associations with personality traits, affective dispositions, and related psychological constructs remains scattered and inconsistent.
+Although the IAS has been widely used, evidence regarding its associations with personality traits, affective dispositions, and related psychological constructs remains scattered and inconsiste [@murphy2019; @brand2023; @lin2023; @todd2022].
 Study 2 therefore had two primary goals.
@@
 <!-- Interoception Related -->
-**Interoception Related**.
+#### Interoception Related
 The Multidimensional Assessment of Interoceptive Awareness Version-2 [MAIA-2, @mehling2018multidimensional] is a 37-item questionnaire assessing eight dimensions of interoception: Noticing, Not-Distracting, Not-Worrying, Attention Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust.
@@
 <!-- Mood and Anxiety -->
-**Mood and Anxiety Related**.
+#### Mood and Anxiety Related
 The Beck Depression Inventory-II [BDI-II, @beck1996beck] is a 21-item measure of depressive symptom severity, including psychological (e.g., guilt) and physiological (e.g., loss of energy) components.
@@
 The Patient Health Questionnaire-4 [PHQ-4, @kroenke2009ultra] is a 4-item screening tool for depression and anxiety, rated on a 4-point Likert scale (e.g., “Little interest or pleasure in doing things”; “Not being able to stop or control worrying”).
-The PHQ-2 [PHQ-2; @kroenke2003patient] and General Anxiety Disorder-2 [GAD-2, @kroenke2007anxiety] scores were combined with the PHQ-4 scores.
+The PHQ-2 [PHQ-2, @kroenke2003patient] and General Anxiety Disorder-2 [GAD-2, @kroenke2007anxiety] scores were combined with the PHQ-4 scores.
 
@@
 The State–Trait Anxiety Inventory Trait Version [STAI-T, @spielberger1970manual] is a 20-item trait anxiety questionnaire rated on a 4-point Likert scale (e.g., “I worry too much about something that really doesn’t matter”).
-Scores from the shorter version of the STAI-5 [STAIT-5, @zsido2020development] were combined with the STAI-T.
+Scores from the shorter version of the STAIT-5 [@zsido2020development] were combined with the STAI-T.
 
@@
 <!-- Personality -->
-**Personality**.
+#### Personality
 The NEO Five-Factor Inventory, neuroticism subscale [NEO-FFI, @costa1992neo] is a 12-item measure of neuroticism, assessing the general tendency to experience negative emotions such as fear, sadness, or disgust.
@@
 
-**Psychopathology**.
+#### Psychopathology
 The Personality Inventory for DSM-5 Short Form [PID-5-SF, @thimm2016personality] consists of 25 items rated on a 4-point Likert scale, measuring five domains: disinhibition, antagonism, detachment, negative affect, and psychoticism (e.g., “Plenty of people are out to get me”).
@@
 
-The Autism Spectrum Quotient Short Form [ASQ-S, @Hoekstra et al., 2011] is a 28-item measure of five autistic traits: social skills, adherence to routines, cognitive flexibility, imagination, and patterns/numbers.
+The Autism Spectrum Quotient Short Form [ASQ-S, @hoekstra2011construction] is a 28-item measure of five autistic traits: social skills, adherence to routines, cognitive flexibility, imagination, and patterns/numbers.
 Items are rated on a 4-point Likert scale (e.g., “I find it difficult to work out people’s intentions”).
@@
 <!-- Beliefs and Misbeliefs -->
-**Beliefs and Misbeliefs**.
+#### Beliefs and Misbeliefs
 The Generic Conspiracist Beliefs Scale [GCBS, @brotherton2013measuring] is a 15-item measure assessing five dimensions of conspiracy beliefs: government malfeasance, extraterrestrial cover-up, malevolent global conspiracies, personal wellbeing, and control of information.
@@
 
-The Primal World Beliefs Inventory Short Form [PI-18, @clifton2021brief] is an 18-item measure assessing four high-order beliefs: the world is Good (vs.
-Bad) and its three dimensions: Safe (vs.
-Dangerous), Enticing (vs.
-Dull), and Alive (vs.
-Mechanistic).
-Items are scored on a 5-point Likert scale (e.g., “Nearly everything in the world is beautiful”).
-
-The Primal World Beliefs Inventory [PI-99; @clifton2019primal] is a 99-item measure assessing high-order beliefs about the world.
-Items are scored on a 5-point Likert scale (e.g., “Nearly everything in the world is beautiful”).The PI-18 [@clifton2021brief] is a short form of the orginal questionnaire assessing the 4 main world beliefs: the world is Good (vs.
+The Primal World Beliefs Inventory [PI-99, @clifton2019primal] is a 99-item measure assessing 26 high-order beliefs about the world.
+Items are scored on a 5-point Likert scale (e.g., “Nearly everything in the world is beautiful”) The PI-18 [@clifton2021brief] is a short form of the orginal questionnaire assessing the 4 main world beliefs: the world is Good (vs.
 Bad) and its three dimensions: Safe (vs.
@@
 <!-- Interoceptive measures -->
-MAIA subscales showed consistent positive associations with IAS: Noticing (β = .259), Attention Regulation (β = .249), Trusting (β = .236), Emotional Awareness (β = .197), Listening (β = .176), and Self-Regulation (β = .189) were significant across IAS pairings and the full scale.
-Autonomic Reactivity (BPQ) was negatively associated (β = −.173, 88% significant), while Body Awareness (BPQ) was weaker and unreliable (β = .122, 25%).
-Alexithymia was consistently negative: ICQ (β = −.316), TAS-DIF (β = −.211), TAS-DDF (β = −.150), TAS-EOT (β = −.081, 75%), and BVAQ-Cognitive (β = −.200) were robust.
-In contrast, BVAQ-Affective showed a weak and inconsistent positive effect (β = .042, 13%).
+Several MAIA subscales showed consistent positive associations with the IAS: Noticing, Attention Regulation, Trusting, Emotional Awareness, Listening, and Self-Regulation (βs ≈ .18–.26).
+These effects were generally strongest for the full IAS, but often replicated with Hungry/Thirsty or Bruise/Blood pairings.
+By contrast, Autonomic Reactivity (BPQ; β = −.17) was reliably negative across most pairings, while Body Awareness (BPQ; β = .12) was weak and only reliable for Hungry/Thirsty and Bruise/Blood.
+Alexithymia measures were consistently negative, with robust effects across both the full IAS and pairings, except for the Affective dimension of the BVAQ which showed only a positive association with the Bruise/Blood sugar pairing (β = .04).
 
-<!-- Mood questionnaires -->
-
-Depression (BDI: β = −.204) and anxiety (STAI-T: β = −.189) were reliably negative.
-Additional scales also showed consistent, though weaker, effects: PHQ-15 (β = −.128, 75%), PHQ-4 depression (β = −.094, 75%), PHQ-4 anxiety (β = −.103, 88%), and GAD-7 (β = −.187, 63%).
-By contrast, PHQ-9 (β = −.619, 25%) and MFQ (β = −.139, 13%) were largely nonsignificant despite negative averages.
-
-<!-- Psychopathology -->
-
-Autistic traits showed a clear pattern: Imagination (β = −.184, 88%), Low Attentional Switching (β = −.143, 63%), and Lack of Social Skills (β = −.119, 63%) were consistently negative.
-Among maladaptive traits, only Negative Affect (β = −.111, 63%) showed reliable associations.
-Schizotypal traits were generally weak, with only No Close Friends (β = −.122, 50%) approaching consistency.
+<!-- Mood and psychopathology -->
+Depression (BDI; β = −.20) and anxiety (STAI-T; β = −.19) were consistently negative across the IAS and most pairings, with Hungry/Thirsty again emerging as a particularly sensitive correlate.
+Broader symptom indices (PHQ-15, PHQ-4, GAD-7) showed weaker but often reliable effects, although some were restricted to certain pairings (e.g., PHQ-15 with Hungry/Thirsty, Bruise/Blood).
+By contrast, PHQ-9 and MFQ averaged negatively but were largely nonsignificant, even with the full scale.
+Autistic traits were generally negative, especially Imagination (β = −.18), which showed broad consistency across pairings except Cough/Sneeze.
 
 <!-- Personality and beliefs -->
+Within the Big Five, Openness (β = .14), Agreeableness (β = .05), and Conscientiousness (β = .03) showed small but consistent positive associations, most reliably captured by the full IAS but also evident in pairings.
+Honesty–Humility was uniquely negative, with significant associations for both the full scale and Hungry/Thirsty.
+Worldview measures were generally null, though belief in a comprehensible world (β = .11) and an “alive” world (β = .09) showed small but consistent positive associations, mainly with the full IAS and Hungry/Thirsty.
 
-Within the Big Five, Openness (β = .143, 100%), Agreeableness (β = .053, 100%), and Conscientiousness (β = .028, 88%) were consistently positive; other traits were negligible.
-Conspiracy, world belief, and lying profiles showed no reliable effects, except a small and consistent association with the believe the world is readily comprehensible (β = .113, 75%) and a small and somewhat consistent association with the belief that the world is alive (β = .087, 63%)
+<!-- Differences between the full IAS and item pairings -->
+Overall, the full IAS yielded the largest number of significant associations (25), but the Hungry/Thirsty (16) and Bruise/Blood sugar (11) pairings frequently showed equally strong or stronger effects.
+These item-level pairings often captured variance that the full scale did not, particularly for interoceptive and mood measures.
+In contrast, other pairings (e.g., Cough/Sneeze, Wind/Burp, Urinate/Defecate) contributed little unique variance.
+Together, these results suggest that while the full IAS captures broad dispositional tendencies, select pairings may provide more fine-grained sensitivity to specific domains, particularly interoception and affect.
 
-<!-- Number of correlations with the intero vars -->
-Across these pairs, the full scale was most frequently the strongest correlate (25 instances), followed by Hungry/Thirsty (16), Bruise/Blood (11), Muscles/Pain (7), and smaller contributions from Breathing/Heart, Cough/Sneeze, Urinate/Defecate, and Wind/Burp.
-
-[**NOTE* justify the choice of those specific primals ? higehr correlations with the IAS?]
+[**NOTE** justify the choice of those specific primals ? higehr correlations with the IAS?]
 
@@
 These findings are consistent with emerging evidence linking openness to interoception as measured by the MAIA-2 [@simkute2025interoception], and complement reports of associations between interoceptive sensitivity (i.e., the accuracy of reported heartbeat counts relative to actual heartbeats) and extraversion [@haustein2024interoception].
+Personality effects more broadly were modest in size, and as such, warrant replication before firm conclusions can be drawn.
+In contrast, maladaptive personality dimensions and schizotypal traits showed only weak and inconsistent associations with the IAS, indicating that interoceptive accuracy may not play a central role in these domains.
 
@@
 Beyond established correlates, exploratory analyses revealed weak but positive associations between the IAS and primal world beliefs, specifically perceiving the world as alive and understandable.
-While preliminary, these effects suggest a possible link between one’s relationship with internal bodily signals and broader worldviews, raising intriguing questions about how interoception might shape existential or meaning-related beliefs.
+The inclusion of primal world beliefs was exploratory, motivated by their potential theoretical link to embodied cognition and meaning-making processes.
+Although effect sizes were small, the emergence of consistent associations with perceiving the world as alive and understandable suggests an intriguing avenue for future work at the intersection of interoception and worldview formation.
 
@@
 A central aim of Study 2 was to assess whether the refined 14-item IAS identified in Study 1 provides practical benefits over the original 21-item scale.
-Our results showed that while the full version was occasionally the stronger correlate, across dispositional measures, the shortened scale retained comparable validity while offering clearer psychometric structure and reduced redundancy as shown in study 1.
-This suggests that the 14-item IAS constitutes a more efficient tool without substantial loss of predictive power.
-In practice, the refined scale offers advantages for researchers and clinicians alike: it reduces participant burden, avoids problematic items flagged in Study 1 (e.g., “tickle,” “taste,” “vomit”), and provides a more coherent representation of interoceptive domains.
+While the full version most often emerged as the strongest correlate, the refined 14-item IAS performed largely comparably across dispositional measures.
+Importantly, specific item pairings — particularly Hungry/Thirsty and Bruise/Blood sugar — frequently captured associations as strong as, or occasionally stronger than, the full scale.
+This suggests that beyond efficiency, the refined IAS may offer more fine-grained sensitivity to certain dispositional domains, highlighting that interoceptive self-report is not unidimensional but may be differentially expressed across bodily contexts.
 
-<!-- Summary -->
+<!-- Summary + need for contextual dimensions-->
 Overall, these findings provide converging evidence for the construct validity of the IAS, most strongly in relation to interoceptive self-report, alexithymia, mood, and autism-related traits.
-Other associations, particularly with personality and belief systems, were weaker and more exploratory, highlighting both the breadth and the limits of interoceptive awareness as captured by the IAS.
-Taken together, Study 2 advances our understanding of the dispositional landscape of interoception and provides evidence that the refined IAS is a reliable and efficient tool for capturing interoceptive awareness.
+Other associations, particularly with personality and belief systems, were weaker and more exploratory, highlighting both the breadth and the limits of interoceptive accuracy as captured by the IAS.
+Taken together, Study 2 advances our understanding of the dispositional landscape of interoception.
+The findings provide strong support for the construct validity of the IAS, while also demonstrating that the refined version can capture comparable patterns of association.
+Moreover, the sensitivity of specific item pairings points to the possibility that different bodily contexts (e.g., hunger vs.
+pain) may differentially align with psychological traits, suggesting a promising direction for future research on the contextual dimensions of interoceptive accuracy.
 
@@
 
+<!-- IAS  sF -->
+This suggests that the 14-item IAS constitutes a more efficient tool without substantial loss of predictive power.
+In practice, the refined scale offers advantages for researchers and clinicians alike: it reduces participant burden, avoids problematic items flagged in Study 1 (e.g., “tickle,” “taste,” “vomit”), and provides a more coherent representation of interoceptive domains.
+
 # Limitations and Future Directions

### 2025-08-31 paper/1_Initial/manuscript.tex
manuscript pdf

--- 2025-02-10 paper/1_Initial/manuscript.tex
@@
 \documentclass[
-  man,
+  jou,
   floatsintext,
@@
 \usepackage{longtable, booktabs, multirow, multicol, colortbl, hhline, caption, array, float, xpatch}
+\usepackage{subcaption}
+
+\renewcommand\thesubfigure{\Alph{subfigure}}
 \setcounter{topnumber}{2}
@@
 
-\usepackage[nolongtablepatch]{lineno}
-\linenumbers
-
 \usepackage{newtx}
@@
 
-\title{Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure
+\title{Mega-analysis of the Interoceptive Accuracy Scale (IAS) Structure
 and its Subjective Correlates}
@@
 
-\author{Ana Neves}
-
-\affiliation{
-{School of Psychology, University of Sussex}}
-
-\leftheader{Neves}
-
-\abstract{Blabla the abstract blabla.}
+\authorsnames[{1},{2},{1},{1},{1,3},{1,4}]{Ana Neves,Giulia
+Poerio,Magdalena Pfaff,Robyn Scharte,Raquel Nogueira Arjona,Dominique
+Makowski}
+
+\authorsaffiliations{
+{School of Psychology, University of Sussex},{},{Sussex Addictions
+Research and Intervention Centre, University of Sussex},{Sussex Centre
+for Consciousness Science, University of Sussex}}
+
+\leftheader{Neves, Poerio, Pfaff, Scharte, Arjona and Makowski}
+
+\abstract{Blabla the abstract blabla. }
 
@@
 
-\authornote{\par{\addORCIDlink{Ana Neves}{0009-0006-0020-7599}}
-
-\par{     \begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colback=white, breakable, opacityback=0, leftrule=.75mm, arc=.35mm, bottomrule=.15mm, toprule=.15mm, left=2mm, colframe=quarto-callout-note-color-frame]
+\authornote{\par{\addORCIDlink{Ana
+Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{Giulia
+Poerio}{0000-0002-2343-5109}}\par{\addORCIDlink{Magdalena
+Pfaff}{0009-0006-2386-7936}}\par{\addORCIDlink{Robyn
+Scharte}{blabla}}\par{\addORCIDlink{Raquel Nogueira
+Arjona}{0000-0002-5998-701X}}\par{\addORCIDlink{Dominique
+Makowski}{0000-0001-5375-9967}}
+
+\par{     \begin{tcolorbox}[enhanced jigsaw, left=2mm, bottomrule=.15mm, breakable, leftrule=.75mm, opacityback=0, colframe=quarto-callout-note-color-frame, arc=.35mm, rightrule=.15mm, toprule=.15mm, colback=white]
 
@@
 \begin{center}
-\includegraphics[width=0.2\textwidth,height=\textheight]{manuscript_files/mediabag/ReBeL_LogoOnly_hu114.png}
-\end{center}  Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows: Ana
-Neves:   Project administration, Data curation, Formal
+\includegraphics[width=0.2\linewidth,height=\textheight,keepaspectratio]{manuscript_files/mediabag/ReBeL_LogoOnly_hu114.png}
+\end{center}  Author roles were classified using the Contributor Role
+Taxonomy (CRediT; https://credit.niso.org/) as follows:  Ana
+Neves:   Data curation, Formal
+Analysis, Investigation, Visualization, Writing -- original
+draft, Writing -- review \& editing; Giulia Poerio:   bla bla; Magdalena
+Pfaff:   Data curation, Writing -- original draft; Robyn Scharte:   bla
+bla; Raquel Nogueira Arjona:   bla bla; Dominique Makowski:   Project
+administration, Data curation, Formal
 Analysis, Investigation, Visualization, Writing -- original
 draft, Writing -- review \& editing}
-\par{Correspondence concerning this article should be addressed to }
+\par{Correspondence concerning this article should be addressed
+to Dominique
+Makowski, Email: \href{mailto:D.Makowski@sussex.ac.uk}{D.Makowski@sussex.ac.uk}}
 }
+
+\usepackage{pbalance}
+% \usepackage{float}
+\makeatletter
+\let\oldtpt\ThreePartTable
+\let\endoldtpt\endThreePartTable
+\def\ThreePartTable{\@ifnextchar[\ThreePartTable@i \ThreePartTable@ii}
+\def\ThreePartTable@i[#1]{\begin{figure}[!htbp]
+\onecolumn
+\begin{minipage}{0.485\textwidth}
+\oldtpt[#1]
+}
+\def\ThreePartTable@ii{\begin{figure}[!htbp]
+\onecolumn
+\begin{minipage}{0.48\textwidth}
+\oldtpt
+}
+\def\endThreePartTable{
+\endoldtpt
+\end{minipage}
+\twocolumn
+\end{figure}}
+\makeatother
 
@@
 \hline
-\endoldlt
-}
+\endoldlt}
 \makeatother
 
+\newenvironment{twocolumntable}% environment name
+{% begin code
+\begin{table*}[!htbp]%
+\onecolumn%
+}%
+{%
+\twocolumn%
+\end{table*}%
+}% end code
+
 \urlstyle{same}
 
+\usepackage{fontspec}
+\usepackage{multirow}
+\usepackage{multicol}
+\usepackage{colortbl}
+\usepackage{hhline}
+\newlength\Oldarrayrulewidth
+\newlength\Oldtabcolsep
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{hyperref}
+\usepackage{float}
+\usepackage{wrapfig}
 \usepackage{lscape}
@@
 
-\resetlinenumber[1]
+\section{Introduction}\label{introduction}
 
@@
 integrating information pertaining to internal organs, such as the
-heart, the lungs or the gut (\citeproc{ref-khalsa2018}{Khalsa, Adolphs,
-Cameron, Critchley, Davenport, Feinstein, Feusner, Garfinkel, Lane,
-Mehling, Meuret, et al., 2018}). While recent research emphasizes a key
-role of interoception in a variety of processes (e.g., emotion
-regulation, decision making) and of outcomes (physical and psychological
-well being), the field remains clouded by concerns about how
-interoception is assessed.
+heart, the lungs or the gut
+(\citeproc{ref-khalsa2018interoception}{Khalsa et al., 2018}). While
+recent research emphasizes a key role of interoception in a variety of
+processes (e.g., emotion regulation, decision making) and of outcomes
+(physical and psychological well being), the field remains clouded by
+concerns about how interoception is assessed.
+
+\subsection{The Interoceptive Assessment
+Puzzle}\label{the-interoceptive-assessment-puzzle}
 
@@
 ``subjective'' assessments (i.e., physiological tasks such as the heart
-beat counting or tracking vs.~questionnaires and subjective scales
-involving a metacognitive reflection), ``explicit'' and ``implicit''
+beat counting or tracking \emph{vs.} questionnaires and subjective
+scales involving metacognitive judgments), ``explicit'' and ``implicit''
 paradigms (i.e., directing participants' awareness and attention to
@@
 strengths and limitations, and a utility dependent on the context and
-goal at hand (\citeproc{ref-jahedi2014}{Jahedi \& Méndez, 2014}).
+goal at hand (\citeproc{ref-Desmedt2023accuracy}{Desmedt et al., 2023};
+\citeproc{ref-jahedi2014}{Jahedi \& Méndez, 2014}).
 
@@
 
-{\caption{{Different ways in which interoception can be
-measured.}{\label{fig-measures}}}}
-
-\includegraphics[width=6.4in,height=\textheight]{figures/MeasuringInteroception.jpg}
+{\caption{{The Interoceptive Assessment Puzzle. The different modalities
+of interoception (e.g., cardioception) can be assessed directly or
+indirectly. Direct assessments can further be subjective or objective,
+depending on whether they involve conscious metacognitive appraisals or
+more performance-based indices. Interoceptive tasks can be explicit (the
+participant is aware of the interoceptive nature of the task and must
+consciously attend to interoceptive signals; e.g., the heartbeat
+counting task) or implicit (measurements of interoception done
+unbeknowst to the participant; e.g., heartbeat evoked potentials
+measured during resting state). Indirect assessments evaluate constructs
+typically related (and ideally dependent on) to interoceptive processes
+or ability (or its deficit).}{\label{fig-measures}}}}
+
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{figures/MeasuringInteroception.png}
 
@@
 
-The use of subjective self-report questionnaires to measure deeply
-embodied functions might seem paradoxical. However, recent redefinitions
-of interoception emphasize the role of high-level and metacognitive
-elaboration of interoceptive information. These redefinitions provide
-theoretical grounding to support the idea that some facets of
-interoception, including participants' metacognitive beliefs, can be
-assessed subjectively (\citeproc{ref-khalsa2018interoception}{Khalsa,
-Adolphs, Cameron, Critchley, Davenport, Feinstein, Feusner, Garfinkel,
-Lane, Mehling, \& others, 2018};
-\citeproc{ref-suksasilp2022towards}{Suksasilp \& Garfinkel, 2022}). This
-approach offers useful and interesting measures
-(\citeproc{ref-lin2023}{Lin et al., 2023};
-\citeproc{ref-murphy2019}{Murphy et al., 2019}).
-
-The notion that self-reports might not reflect the same processes as
-other interoception measures is important to contextualize the apparent
-lack of convergence between measures in the field
-(\citeproc{ref-desmedt2022measures}{Desmedt et al., 2022}). While few
-studies have explored the correlation between objective interoceptive
-measures, such as the Heartbeat Counting Task (HCT,
-\citeproc{ref-schandry1981heart}{Schandry, 1981}) and the Heartbeat
-Detection Task (HDT, \citeproc{ref-kleckner2015methodological}{Kleckner
-et al., 2015}), and correspondent self-report measures, existing
-findings typically show weak or no correlations
-(\citeproc{ref-brand2023}{Brand et al., 2023}; e.g., task-based accuracy
+Although the use of subjective self-report questionnaires to measure
+deeply embodied functions might seem paradoxical at first, recent
+redefinitions of interoception emphasize the role of high-level and
+metacognitive elaboration of interoceptive information. These
+redefinitions provide theoretical grounding to support the idea that
+some facets of interoception, including participants' metacognitive
+beliefs, can be assessed subjectively
+(\citeproc{ref-khalsa2018interoception}{Khalsa et al., 2018};
+\citeproc{ref-suksasilp2022towards}{Suksasilp \& Garfinkel, 2022}).
+Moreover, the notion that self-reports might not reflect the same
+processes as other interoception tasks might be important to
+contextualize the apparent lack of convergence between measures in the
+field (\citeproc{ref-desmedt2022measures}{Desmedt et al., 2022}). For
+instance, existing findings typically show weak or no correlations
+between questionnaires and objective measures, such as the Heartbeat
+Counting Task (HCT, \citeproc{ref-schandry1981heart}{Schandry, 1981})
+and the Heartbeat Detection Task (HDT,
+\citeproc{ref-kleckner2015methodological}{Kleckner et al., 2015}),
+including for measures of the same theoretical dimensions
+(\citeproc{ref-arslanova2022}{Arslanova et al., 2022};
+\citeproc{ref-brand2023}{Brand et al., 2023}; e.g., task-based accuracy
 vs.~self-reported accuracy, \citeproc{ref-murphy2019}{Murphy et al.,
-2019}).
-
-Even among self-report measures low correlations have been observed,
-suggesting that these measures, while group in the same umbrella term of
-self-report assess different facets of interoception. A recent
-systematic review by Desmedt et al.
-(\citeproc{ref-desmedt2022measures}{2022}) examined whether various
-questionnaires designed to assess ``interoceptive sensibility'' truly
-measure the same construct. Notably, Garfinkel et al.
-(\citeproc{ref-garfinkel2015knowing}{2015}) defines interoceptive
-sensibility as the self-reported tendency to focus on and detect
-internal sensations, whereas Khalsa, Adolphs, Cameron, Critchley,
-Davenport, Feinstein, Feusner, Garfinkel, Lane, Mehling, and others
-(\citeproc{ref-khalsa2018interoception}{2018}) defines it more narrowly,
-excluding the ability to detect these signals. According to Desmedt et
-al. (\citeproc{ref-desmedt2022measures}{2022}), most authors adopt the
-latter definition. The review found that these questionnaires measure
-related but distinct constructs, leading researchers to mistakenly
-treating them as equivalent measures of interoceptive sensibility. A
-better understanding of what is being measured with different
-questionnaires and dimensions, as well as their potential overlaps with
-other constructs (e.g., alexithymia, body awareness), is thus needed to
-clarify the role of self-reports in the assessment of interoception.
-
-A recently developed scale with a rapidly growing popularity is the
-Interoceptive Accuracy Scale (IAS, \citeproc{ref-murphy2019}{Murphy et
-al., 2019}). The IAS consists of 21 Likert-scale items that query how
-accurately one can perceive different bodily signals, with one item per
-physiological modality such as respiration (\emph{``I can always
-accurately perceive when I am breathing fast''}), heart (e.g \emph{``I
-can always accurately perceive when my heart is beating fast''}), skin
-(e.g \emph{``I can always accurately perceive when something is going to
-be ticklish''}), arousal or bodily functions like coughing (e.g
-\emph{``I can always accurately perceive when I am going to cough''}) or
-urinating (e.g.~\emph{``I can always accurately perceive when I need to
-urinate''}). Interestingly, the IAS' statements are about specific
-interoceptive behaviours, which is a notable difference with other
-popular interoception questionnaires, such as the Multidimensional
-Assessment of Interoceptive Awareness scale (MAIA,
+2019}). Additionally, even various objective measures assessing in
+theory the same interoceptive dimension, such as accuracy, either show
+no or weak correlation (respectively, \citeproc{ref-brand2023}{Brand et
+al., 2023}; \citeproc{ref-hickman2020relationship}{Hickman et al.,
+2020}). Perhaps more surprisingly, low correlations have been observed
+even among questionnaires, suggesting (in parallel to major validity
+concerns) the potential targeting of different facets related to
+interoception.
+
+One striking example concerns the assessment of interoceptive
+sensibility, which is broadly defined as the self-reported tendency to
+focus on and detect internal sensations
+(\citeproc{ref-garfinkel2015knowing}{Garfinkel et al., 2015}), but more
+narrowly as the subjective tendency to focus on interoceptive signals,
+without necessarily implying detection ability
+(\citeproc{ref-khalsa2018interoception}{Khalsa et al., 2018}). A recent
+systematic review suggested that various questionnaires designed to
+assess interoceptive sensibility may, in fact, measure distinct
+constructs, with the risk of researchers treating them as equivalent
+despite overall low convergence
+(\citeproc{ref-desmedt2022measures}{Desmedt et al., 2022}). Notably,
+this review adopted a broad definition of sensibility, incorporating
+both interoceptive sensibility and interoceptive self-report scales,
+following the eight-facet model by Khalsa et al.
+(\citeproc{ref-khalsa2018interoception}{2018}). Several widely used
+questionnaires were included in the review, such as the Multidimensional
+Assessment of Interoceptive Awareness (MAIA,
 \citeproc{ref-mehling2012}{Mehling et al., 2012}; MAIA-2,
-\citeproc{ref-mehling2018multidimensional}{Mehling et al., 2018}), which
-contains more general and metacognitive items (e.g., \emph{``I trust my
-body sensations''}, \emph{``I can notice an unpleasant body sensation
-without worrying about it''}).
-
-Although the original validation study suggested a two-factor structure
-for the IAS, the authors underline its acceptable but imperfect fit
-(\citeproc{ref-murphy2019}{Murphy et al., 2019, p. 127}), calling on
-further investigation of the scale's factor structure. Notably, the
-authors did not define these factors, as no clear explanations were
-evident. They suggested that the first factor reflects the perception of
-interoceptive signals, while the second pertains to signals that may be
-difficult to perceive solely through interoceptive information.
-
-\textbf{note to dom}:Morin et al. (\citeproc{ref-morin2016}{2015}) is a
-methodological paper on ESEM
-
-Other follow-up studies using confirmatory factor analysis (CFA) and
-structural modeling have identified different optimal solutions. Some
-studies, like Brand et al. (\citeproc{ref-brand2023}{2023}), reported a
-1-factor solution, while Lin et al. (\citeproc{ref-lin2023}{2023}) and
-Campos et al. (\citeproc{ref-campos2021}{2021}) found bifactor solutions
-- one general factor and a set of lower-level factors
-(\citeproc{ref-rodriguez2016evaluating}{Rodriguez et al., 2016}) - to be
-the best fit. Notably, the only other study to report a 2-factor
-solution was conducted by Koike and Nomura
-(\citeproc{ref-koike2023}{2023}), who performed an Exploratory Factor
-Analysis (EFA) assuming 2 factors to align with the findings from the
-original validation paper.
+\citeproc{ref-mehling2018multidimensional}{Mehling et al., 2018}), the
+Body Perception Questionnaire (BPQ,
+\citeproc{ref-porges1993body}{Porges, 1993}), the Private subscale of
+the Body Consciousness Questionnaire (PBCS,
+\citeproc{ref-miller1981consciousness}{Miller et al., 1981}), the Body
+Awareness Questionnaire (BAQ, \citeproc{ref-shields1989body}{Shields et
+al., 1989}), and the Eating Disorder Inventory
+(\citeproc{ref-garner1983}{Garner et al., 1983}; EDI,
+\citeproc{ref-garner1991eating}{Garner, 1991}). The lack of correlations
+to moderate correlations among these questionnaires highlight the need
+for greater conceptual clarity regarding what each measure captures, how
+they relate to different dimensions of interoception, and their
+potential overlaps with other constructs, such as alexithymia and body
+awareness.
+
+\subsection{The Interoceptive Accuracy Scale
+(IAS)}\label{the-interoceptive-accuracy-scale-ias}
+
+Focusing on another dimension of interoception, a recently developed
+scale with a rapidly growing popularity is the Interoceptive Accuracy
+Scale (IAS, \citeproc{ref-murphy2019}{Murphy et al., 2019}). The IAS
+consists of 21 Likert-scale items that query how accurately one can
+perceive different bodily signals, with one item per physiological
+modality such as respiration (\emph{``I can always accurately perceive
+when I am breathing fast''}), heart (\emph{``I can always accurately
+perceive when my heart is beating fast''}), skin (\emph{``I can always
+accurately perceive when something is going to be ticklish''}), arousal
+or bodily functions like coughing (\emph{``I can always accurately
+perceive when I am going to cough''}) or urinating (\emph{``I can always
+accurately perceive when I need to urinate''}). Appealingly, the IAS'
+statements are about specific interoceptive behaviours, which is a
+distinct difference with other popular interoception questionnaires,
+such as the MAIA-2, which contains more general and metacognitive items
+(e.g., \emph{``I trust my body sensations''}, \emph{``I can notice an
+unpleasant body sensation without worrying about it''}), as well as
+dimensions related to attention regulation (e.g., Not-distracting) or
+emotion regulation (e.g., Not-worrying).
+
+{[}\textbf{NOTES}: todd 2022 found no correlation for MAIA and IAS
+except with the non-worrying facet + Gaggero found positive correlations
+with IAS and MAIA (general){]}
+
+The original validation study suggested a two-factor structure for the
+IAS, one reflecting the perception of general interoceptive signals
+(urinate, hungry, defecate, thirsty, pain, heart, taste, breathing,
+temperature, muscles, affective touch, vomit, sexual arousal), and other
+relating to signals that may be difficult to perceive solely through
+interoceptive information (itch, tickle, cough, burp, bruise, blood
+sugar, sneeze, wind). The authors however underlined its acceptable but
+imperfect fit (\citeproc{ref-murphy2019}{Murphy et al., 2019, p. 127}),
+and several follow-up studies have indeed identified different optimal
+solutions. For instance, Brand et al. (\citeproc{ref-brand2023}{2023})
+reported a 1-factor solution, while Lin et al.
+(\citeproc{ref-lin2023}{2023}) - using Exploratory Graph Analysis (EGA,
+\citeproc{ref-golino2017exploratory}{H. F. Golino \& Epskamp, 2017}) -
+and Campos et al. (\citeproc{ref-campos2021}{2021}) found bifactor
+solutions (i.e., one general factor above a set of lower-level factors,
+\citeproc{ref-rodriguez2016evaluating}{Rodriguez et al., 2016}) to be
+the best fit. Using a 2-factors Exploratory Factor Analysis (EFA), Koike
+and Nomura (\citeproc{ref-koike2023}{2023}) suggested that the items
+could be grouped into cutaneous (itching, tickling, coughing, burping,
+affective touch, bruising, passing gas, sneezing, muscle sensations,
+sexual arousal, and taste) and visceral sensations (urination,
+defecation, hunger, thirst, pain, breathing, fatigue/blood sugar,
+temperature, vomiting, and heartbeat).
 
@@
 signals alone (e.g., ``bruising''; p.~119). Lin et al.
-(\citeproc{ref-lin2023}{2023}) also highlights their correlation
-analysis, showing five locally dependent pairs and three items (touch,
-blood sugar, bruise) with exceptionally high difficulty and low
-discrimination. Additionally, Campos et al.
+(\citeproc{ref-lin2023}{2023}) additionally highlights five locally
+dependent pairs and three items (touch, blood sugar, bruise) with
+exceptionally high difficulty and low discrimination, and Campos et al.
 (\citeproc{ref-campos2021}{2021}) reported ``tickle'' to be the only
 item that reflected more specific factors than the general factor.
-Interestingly, Lin et al. (\citeproc{ref-lin2023}{2023}) reported that
-all items of the IAS grouped together using a new approach, Exploratory
-Graph Analysis (EGA, \citeproc{ref-golino2017exploratory}{Golino \&
-Epskamp, 2017}), to assess convergent and discriminant validity,
-providing further evidence for unidimensionality.
-
-The IAS has naturally been compared to other interoception-related
-scales, and shows a positive correlations with most facets of the MAIA
+Furthermore, localization issues also arose, with both ``itch'' and
+``tickle'' corresponding to the same Chinese character, leading to their
+collapse into a single item (\citeproc{ref-lin2023}{Lin et al., 2023}).
+
+Regarding its validity, the IAS has naturally been compared to other
+interoception-related measures, and shows a positive correlations with
+most facets of the MAIA
 (\citeproc{ref-mehling2018multidimensional}{Mehling et al., 2018}),
-except for the Non-Distracting and Not-Worrying subscales
-(\citeproc{ref-brand2023}{Brand et al., 2023}). Interestingly, findings
-on the correlation between the IAS and the body awareness dimension of
-the Body Perception Questionnaire (BPQ-A,
-\citeproc{ref-porges1993body}{Porges, 1993}) have been mixed: some
+except for the Not-Distracting and Not-Worrying subscales
+(\citeproc{ref-brand2023}{Brand et al., 2023}) - which were previously
+highlighted as related to non-interoceptive abilities
+(\citeproc{ref-ferentzi2021examining}{Ferentzi et al., 2021}).
+Interestingly, findings on the correlation between the IAS and the body
+awareness dimension of the BPQ (i.e., BPQ-A) have been mixed: some
 studies report small positive correlations
@@
 has shown a positive correlation with the interoceptive awareness
-subscale of the Eating Disorder Inventory (\citeproc{ref-lin2023}{Lin et
-al., 2023}) and a negative correlation with the Interoceptive Confusion
-Questionnaire (\citeproc{ref-brand2023}{Brand et al., 2023}; ICQ,
-\citeproc{ref-brewer2016alexithymia}{Brewer et al., 2016};
-\citeproc{ref-murphy2019}{Murphy et al., 2019}). Lastly, small positive
-correlations have also been reported with the Interoceptive Attention
-Scale (\citeproc{ref-koike2023}{Koike \& Nomura, 2023}; IATS,
-\citeproc{ref-lin2023}{Lin et al., 2023}), though studies have also
-found no correlation between these measures
-(\citeproc{ref-gabriele2022dissociations}{Gabriele et al., 2022}).
-Interestingly, the IAS and the IATS supposedly measure two different
-interoceptive processes (i.e., accuracy and attention, respectively)
-which contradict Murphy et al. (\citeproc{ref-murphy2019}{2019})
-proposed 2x2 framework.
-
-While assessing the validity of an interoception scale can be conceived
-as theoretically challenging, several measures have been used to assess
-convergent validity for the the IAS, including expected negative
-associations with alexithymia (\citeproc{ref-brand2023}{Brand et al.,
-2023}; \citeproc{ref-campos2021}{Campos et al., 2021};
+subscale of the Eating Disorder Inventory (EDI-IA,
+\citeproc{ref-lin2023}{Lin et al., 2023}) and a negative correlation
+with the Interoceptive Confusion Questionnaire (ICQ,
+\citeproc{ref-brewer2016alexithymia}{Brewer et al., 2016}), as reported
+by Brand et al. (\citeproc{ref-brand2023}{2023}) and Murphy et al.
+(\citeproc{ref-murphy2019}{2019}). Lastly, the correlation with the
+Interoceptive Attention Scale (IATS,
+\citeproc{ref-gabriele2022dissociations}{Gabriele et al., 2022}) appears
+rather small (\citeproc{ref-koike2023}{Koike \& Nomura, 2023};
+\citeproc{ref-lin2023}{Lin et al., 2023}).
+
+While assessing the predictive validity of an interoception scale can be
+conceived as theoretically challenging, expected negative associations
+were observed between the IAS and alexithymia
+(\citeproc{ref-brand2023}{Brand et al., 2023};
+\citeproc{ref-campos2021}{Campos et al., 2021};
 \citeproc{ref-koike2023}{Koike \& Nomura, 2023};
@@
 (\citeproc{ref-brand2023}{Brand et al., 2023}) and self-esteem
-(\citeproc{ref-murphy2019}{Murphy et al., 2019}).
+(\citeproc{ref-murphy2019}{Murphy et al., 2019}). Taken together, these
+findings support the IAS as measuring an adaptive aspect of
+interoception, although its pattern of associations with other
+interoception (or interoception-related) questionnaires points towards
+some overlap across various theoretical dimensions, casting some doubt
+on the orthogonal models of interoception and the possibility of its
+faithful capture by questionnaires.
 
 The current study aims at 1) clarifying the structure of the IAS with a
-meta-analytic approach that leverages existing data and contrast the
-traditional CFA/SEM factor-based analyses with network-based ones such
-as EGA; 2) the second part will provide an overview of the dispositional
-correlates of the IAS, clarifying the pattern of associations which is
-key to better understand the nature, place and role of interoception
-questionnaires within a larger context.
-
-\subsection{Study 1}\label{study-1}
-
-The goal of study 1 is to re-analyse and assess the factor structure of
-the IAS by taking advantage of the large number of open-access datasets
+mega-analytic (which involves a re-analysis at the raw data level by
+aggregating datasets) approach that leverages existing data and contrast
+the traditional CFA/SEM factor-based analyses with network-based ones
+(Exploratory Graph Analysis); 1) provide an overview of the
+dispositional correlates of the IAS, clarifying its general pattern of
+associations, which is key to better understand the nature, place and
+role of interoception questionnaires within a larger context.
+
+\section{Study 1}\label{study-1}
+
+Study 1 will re-analyse and assess the factor structure of the IAS by
+taking advantage of the large number of open-access datasets
 (\citeproc{ref-arslanova2022}{Arslanova et al., 2022};
@@
 \citeproc{ref-lin2023}{Lin et al., 2023};
+\citeproc{ref-makowski2025measuring}{Makowski et al., 2025};
 \citeproc{ref-murphy2019}{Murphy et al., 2019};
+\citeproc{ref-poerio2024interoceptive}{Poerio et al., 2024};
 \citeproc{ref-todd2022}{Todd et al., 2022}; \citeproc{ref-von2023}{Von
@@
 robust and generalizable understanding of the IAS' factor structure, we
-also additionally provide an individual analysis (i.e., on all samples
-separately) to add nuance to the general picture, as all studies differ
-in their sample sizes, demographics, language, and procedure.
-
-\subsubsection{Methods}\label{methods}
-
-\paragraph{Datasets.}\label{datasets}
+also additionally provide an individual analysis (i.e., applying the
+same method on all samples separately) to add nuance to the general
+picture, as all studies differ in their sample size, demographic
+characteristics, language, and procedure.
+
+\subsection{Methods}\label{methods}
+
+\subsubsection{Datasets}\label{datasets}
 
@@
 provide accessible data in open-access, (2) employ the IAS as a measure,
-and (3) report individual IAS items scores. A total of 10 studies was
-included (see \textbf{Table 1}). We also included the data of two
-unpublished (but already open-access) studies from the authors and one
-from another researcher. The total N participants was 32,214
-participants (\emph{Mean} = 48.6 years, \emph{SD} = 13.1, 71.6\%
-Female).
-
-\begin{landscape}
-
-\input{../../analysis/figures/table1.tex}
-
-\end{landscape}
-
-\paragraph{Statistical Analysis.}\label{statistical-analysis}
-
-To examine the factor structure of the IAS, a two-step approach was
-employed. First, Exploratory Graph Analysis (EGA), was used to estimate
-the dimensions via network estimation and community detection, alongside
-assessing the stability of dimensions and items using the bootstrapping
-techniques (\citeproc{ref-golino2017exploratory}{Golino \& Epskamp,
-2017}). The selection of EGA was motivated by its capability to handle
-complex, multidimensional data and provide robust dimension estimates. A
-novel network psychometrics - Unique variable analysis (UVA,
-\citeproc{ref-christensen2023unique}{Christensen et al., 2023}) -
-approach based on the weighted topological overlap will be computed to
-evaluate which items have substantial local dependence (\textgreater{}
-0.25). Subsequently, exploratory factor analysis (EFA) was employed
-followed by confirmatory factor analysis (CFA).
-
-\subsubsection{Results}\label{results}
-
-Visualizing the distribution of the items for all samples suggests the
-presence of a consistent modal value (Figure~\ref{fig-distributions}).
-In other words, participants are most likely to answer 4/5 (i.e., agree)
-on most items (but ``affective touch'', ``blood sugar'', and ``bruise''
-that exhibit a different distributional pattern). Additionally, one can
-note the low density on extreme values (1 and 5), meaning that the bulk
-of answers (i.e., 99\%) varies between 3 values. The interindividual
-variability seems improved in the samples using an analogue scale,
-displaying a more continuous and progressive spread of answers.
-
-\begin{figure}
-
-\caption{\label{fig-distributions}Distribution of responses for all
-items across various datasets.}
-
-\centering{
-
-\includegraphics[width=6.67in,height=\textheight]{figures/Figure1.png}
-
-}
-
-\end{figure}%
-
-\paragraph{Correlations.}\label{correlations}
-
-The correlation analysis revealed that the items overall have positive
-intercorrelation patterns with no clear structure emerging. This remains
-the same across all samples. However, there are possibly some
-higher-order groupings emerging for the 2 analog-scale samples.
-
-\paragraph{EGA.}\label{ega}
-
-The UVA revealed that there are two large to very large redundant
-variables when taking all samples into account. Namely, ``itch'' and
-``tickle'', where ``tickle'' should be removed, and ``itch'' should be
-kept. There are several more items that are moderately to largely
-redundant, namely, ``wind'' and ``burp'', and ``urinate'' and
-``defecate''. On top of that, ``sneeze'' and ``cough'', ``heart'' and
-``breathing'', and ``hungry'' and ``thirsty'' seem to have small to
-moderate redundancy. These findings are rather consistent across the
-samples with minor differences, such as that when the questionnaire had
-an analog scale, there seems to be no large to very large redundant
-items but ``itch'' and ``tickle'' remain moderately to largely redundant
-and ``heart'' and ``breathing'' small to moderately redundant in one
-sample.
-
-According to the network analysis, using the Walktrap and Louvain
-algorithms applied to Glasso networks, a 4-factor structure fits the
-questionnaire best across all data sets. This is rather consistent
-within the data sets, where some samples indicate 3-factor structure,
-and some a 5-factor structure would fit well too. The 4-factor structure
-model with the best fit entails the following items per group: 1) itch,
-tickle, bruise, blood sugar; 2) burp, wind, cough, sneeze, vomit; 3)
-affective touch, sexual arousal, muscles, temperature, pain, and taste;
-4) Heart, breathing, hungry, thirsty, urinate, and defecate.
-
-Stability analysis, employing 500 bootstrap iterations, also favoured
-the 4-factor solution for its greater stability. Most items, except for
-`affective touch,' demonstrated stability levels exceeding 0.90,
-indicating structural consistency and reliability
-(\citeproc{ref-christensen2021}{Christensen \& Golino, 2021}). These
-findings underscore the robustness of the identified 4-dimensional
-structure.
-
-When accounting for all samples, the factor analysis reveals that a
-4-factor structure fits best. The exploratory factor analysis revealed
-that 4 latent factors (oblimin rotation) accounted for 41.58\% of the
-total variance of the original data (MR1 = 14.45\%, MR3 = 11.76\%, MR2 =
-8.09\%, MR4 = 7.28\%). Since UVA identified ``tickle'' as the item to be
-removed---and it also had the lowest uniqueness value in factor analysis
-with a similar loading to ``itch''---'' it was excluded from subsequent
-analyses.
-
-CFA was computed with the removal of the item ``tickle'' as it was
-constantly flagged as redundant. This analysis compared 5 models: a
-single-factor solution, a 4-factor solution, a 5-factor solution, a
-6-factor solution and a 7-factor solution. The latter was preferred in
-most datasets, including with indices that penalise increased number of
-parameters (such as BIC). There was no evidence for higher order
-factors.
-
-\subsubsection{Discussion}\label{discussion}
-
-In this study, several datasets were analyzed for a meta analysis of the
-structure of the IAS. The findings reveal that a 4-factor model fits the
-IAS best. Additionally, the lowest level structure (pairs of items) seem
-to be the most robust, especially for samples using Likert scales (some
-higher-order groupings might emerge for the 2 analog-scale samples).
-There was no clear evidence for higher-order factors.
-
-These findings contrast with previous research, which all found that
-2-factor model (\citeproc{ref-koike2023}{Koike \& Nomura, 2023};
-\citeproc{ref-murphy2019}{Murphy et al., 2019}), 1-factor model
-(\citeproc{ref-brand2023}{Brand et al., 2023}) and bifactor model
+and (3) report individual IAS items scores. We also included the data of
+five unpublished studies. A total of 16 datasets was included (see
+\textbf{Table 1}).
+
+The total number of participants was 33,272 participants (Mean = 48.09
+\(\pm\) 13.1, 71.3\% Female).
+
+\begin{twocolumntable}
+
+\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
+
+\global\setlength{\Oldtabcolsep}{\tabcolsep}
+
+\setlength{\tabcolsep}{2pt}
+
+\renewcommand*{\arraystretch}{1}
+
+\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\begin{longtable}[c]{ccccccccc}
+
+\caption{\label{tbl-table1}Description of the samples used in the
+study.}
+
+\tabularnewline
+
+\ascline{0.75pt}{000000}{1-9}
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Reference}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Language}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{N}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Difference}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Age\ (Mean\ \ ±\ SD)}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Range}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Female\ \%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Availability}}}} \\
+
+\ascline{0.75pt}{000000}{1-9}\endfirsthead
+
+\ascline{0.75pt}{000000}{1-9}
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Reference}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Language}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{N}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Difference}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Age\ (Mean\ \ ±\ SD)}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Range}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Female\ \%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Availability}}}} \\
+
+\ascline{0.75pt}{000000}{1-9}\endhead
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Murphy\ et\ al.,\ (2020)}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{osf.io/3m5nh}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 1a}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{English}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{451}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{25.8\ ±\ 8.4}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{18-69}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{69.4\%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 1b}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{English}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{375}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{35.3\ ±\ 16.9}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{18-91}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{70.1\%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 2}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Gaggero\ et\ al.,\ (2021)}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{English\ and\ Italian}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{814}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{24.9\ ±\ 5.3}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{18-58}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{60.3\%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{osf.io/5x9sg}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 3}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Campos\ et\ al.,\ (2022)}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Portuguese}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{515}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{30.7\ ±\ 10.5}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{18-72}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{59.6\%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{osf.io/j6ef3}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 4}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Todd\ et\ al.,\ (2022)}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{English}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{802}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{48.6.6\ ±\ 14.1*}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{18-92*}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{50\%*}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{osf.io/ms354}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 5}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Arslanova\ et\ al.,\ (2022)}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{English}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{143}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{28.5\ ±\ 7.6}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{18-73}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{46.8\%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{osf.io/mp3cy}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 6}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Brand\ et\ al.,\ (2022)}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{German}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{619}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{43.9\ ±\ 14.5}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{18-78}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{78.7\%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{osf.io/xwz6g}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Brand\ et\ al.,\ (2023)}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{osf.io/3f2h6}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 7a}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{German}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{522}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{23.4\ ±\ 6.7}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{18-79}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{79.5\%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 7b}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{German}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{1993}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{32.0\ ±\ 12.6}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{16-81}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{77.7\%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 7c}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{German}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{802}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{27.3\ ±\ 9.3}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{18-72}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{68.9\%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Lin\ et\ al.,\ (2023)}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{osf.io/3eztd}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 8a}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Chinese}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{1166}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Collapsed\ "Itch"\ and\ "Tickling"}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{32.5\ ±\ 8.4}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{16-60}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{57.0\%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 8b}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Chinese}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{500}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Collapsed\ "Itch"\ and\ "Tickling"}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{37.4\ ±\ 7.4}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{20-60}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{56.2\%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 9}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{VonMohr\ et\ al.,\ (2023)}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{English}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{21843}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{56.5\ ±\ 14.4}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{18-93}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{73.2\%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{osf.io/7p9u5}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 10}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Makowski\ et\ al.,\ (2023a)}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{English}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{485}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Analog\ scales.\ No\ Temperature,\ Blood\ sugar\ and\ Cough\ items}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{30.1\ ±\ 10.1}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{18-73}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{50.3\%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{github.com/RealityBending/IllusionGameReliability}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 11}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Makowski\ et\ al.,\ (2023b)}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{English}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{836}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Analog\ scales}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{25.1\ ±\ 11.3}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{17-76}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{53.0\%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{github.com/DominiqueMakowski/PHQ4R}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 12}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Makowski\ et\ al.,\ (2023c)}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{English}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{146}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Analog\ scales}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{21.1\ ±\ 4.3}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{18-50}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{76\%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{github.com/RealityBending/InteroceptionPrimals}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 13}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Makowski\ et\ al.,\ (2024)}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{English}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{737}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{36.8\ ±\ 14.9}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{17,\ 87}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{57.3\%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{github.com/RealityBending/InteroceptionScale}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 14}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Poerio\ et\ al.,\ (2024)}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{English}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{107}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{26.8\ ±\ 9.2}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{18-57}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{74.8\%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{osf.io/49wbv}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 15}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Poerio\ et\ al.,\ unpublished}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{English}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{131}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{30.9\ ±\ 12.0}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{18-60}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{75.9\%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 16}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Arjona\ et\ al.,\ unpublished}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{English}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{279}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{26.4\ ±\ 13.2}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{18-79}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{67.7\%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} \\
+
+\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Sample\ 17}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{Total}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{33272}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{48.09\ ±\ 13.1}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{17-93}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{71.3\%}}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{6}{12}\selectfont{\global\setmainfont{Times New Roman}{}}}} \\
+
+\ascline{0.75pt}{000000}{1-9}
+
+\end{longtable}
+
+\arrayrulecolor[HTML]{000000}
+
+\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
+
+\global\setlength{\tabcolsep}{\Oldtabcolsep}
+
+\renewcommand*{\arraystretch}{1}
+
+*Information taken from the sample description of relevant paper rather
+than recomputed.
+
+\end{twocolumntable}
+
+\subsubsection{Data Analysis}\label{data-analysis}
+
+Psychometrically good items should exhibit various qualities, such as
+validity, reliability and discrimination, to which one of the
+contributing factors is the amount of inter-individual variability
+captured by an item. Items to which all participants' answers are
+concentrated around one option - i.e., exhibiting a narrow distribution
+- will be flagged as potentially problematic.
+
+After examining the distributions and correlations of all IAS items, we
+will test for ``redundant'' items (e.g., due to multicollinearity or
+local dependency) using Unique Variable Analysis (UVA,
+\citeproc{ref-christensen2023unique}{Christensen et al., 2023}), a novel
+method derived from network psychometric designed to identify and merge
+items that share substantial variance (which can distort the structure
+estimation). We will use a threshold of 0.30 that detects large to very
+large overlap.
+
+Following the analysis of items, we will analyze the factor structure of
+the IAS using three different approaches, each with particular
+trade-offs and assumptions, to provide a multi-verse picture of likely
+solutions. Namely, we will apply traditional exploratory and
+confirmatory Factor Analysis (EFA/CFA), hierarchical clustering (HCA),
+and Exploratory Graph Analysis (EGA), to the whole sample, as well as to
+each dataset separately (details being available in the analysis
+document at https://github.com/RealityBending/InteroceptionIAS), and our
+decisions and conclusions will try to take into account both levels of
+analysis.
+
+By combining network analysis with psychometric methods, the
+recently-developed EGA framework allows to jointly estimate the number
+of dimensions (i.e., groups of items), the structure as well as its
+stability (\citeproc{ref-golino2020investigating}{H. Golino et al.,
+2020}; \citeproc{ref-golino2017exploratory}{H. F. Golino \& Epskamp,
+2017}). Evidence has underlined its suitability as an alternative to
+traditional factor analysis, addressing some of its limitations such as
+the assumption of a ``latent'' source of variability, possible biasing
+in the estimation of the optimal factor numbers depending on sample
+size, and the poor performance of other methods in complex population
+structures, while remaining comparable and interpretable
+(\citeproc{ref-christensen2021equivalency}{Christensen \& Golino,
+2021b}; \citeproc{ref-jimenez2023dimensionality}{Jiménez et al., 2023}).
+At a fundamental level, EGA conceptualizes variables as nodes in a
+network, with connections (edges) reflecting associations between them.
+Clustering these nodes reveals distinct communities of related items, in
+practice akin to traditional latent factors - but without explicitly
+assuming their presence
+(\citeproc{ref-christensen2021equivalency}{Christensen \& Golino,
+2021b}). We used the EGAnet package
+(\citeproc{ref-christensen2021estimating}{Christensen \& Golino, 2021a})
+to fit a hierachical EGA with the Leiden community detection algorithm.
+
+While EGA offers a robust alternative to traditional factor analysis,
+factor analysis remains a widely used method for dimensionality
+assessment. As our goal is to provide a general - yet nuanced - picture,
+with room to show potential discrepancies emerging from the methods
+used, we will also include it in the present study. Unlike EGA, factor
+analysis assumes that a latent source of variability --- a common latent
+variable --- underlies the observed set of manifest variables
+(\citeproc{ref-cosemans2022exploratory}{Cosemans et al., 2022}). A
+critical step in factor analysis is determining the optimal number of
+factors, for which we will used the Method Agreement Procedure
+(\citeproc{ref-ludecke2021performance}{Lüdecke et al., 2021}), which
+involves a consensus-based decision based on multiple factor estimation
+methods applied concurrently.
+
+Finally, we will also apply Hierarchical Clustering Analysis (HCA,
+\citeproc{ref-murtagh2014ward}{Murtagh \& Legendre, 2014}), which
+differs from factor analysis in that it does not assume any latent
+source of variability, but instead iteratively groups items based on
+their similarity (e.g., correlation) into a hierarchy of clusters. The
+benefits of HCA include its interpretability and ability to capture
+complex relationships among items without relying on strict assumptions
+about data distribution or latent variables.
+
+In a typical 2-step fashion, this first analysis run will be followed by
+a structure refinement with a further selection of items, and the final
+pool of items will be tested again. Additionally, various solutions
+(e.g., adding general factors) will be statistically compared using
+Confirmatory Factor Analysis (CFA).
+
+\subsection{Results}\label{results}
+
+The distribution of the items across samples suggests the presence of a
+consistent modal value (Figure~\ref{fig-distributions}). In other words,
+participants are most likely to answer 4/5 (i.e., agree) on most items,
+with the exception of ``blood sugar'' and ``bruise'', which exhibit a
+different distributional pattern with a lower mode (\textasciitilde2/5).
+While it is not a problem \emph{per se}, the contrasting distribution
+might be indicative of items with non-homogeneous psychometric
+``difficulty''. This is also the case for ``affective touch'' in samples
+8a and 8b (the Chinese validation samples), which might indicate
+localisation issues. Additionally, one can note the low occurrence of
+extreme values (1 and 5), meaning that the bulk of answers varies
+between 3 values (assuming the IAS is implemented as a 5-point Likert
+scale following its validation). The samples using an analogue scale
+(samples 10a, 10b and 10c in the figure) display a more continuous and
+progressive spread of answers, seemingly improving the interindividual
+variability, although potentially displaying a secondary lower mode at
+\textasciitilde2 (which might be suggesting the existence of potential
+clusters of participants). The correlation matrix between all items
+shows an overall positive correlation pattern, with highly correlated
+pairs of items (e.g., Tickle-Itch, Urinate-Defecate, Pain-Wind,
+Hungry-Thursty) or triplets (Vomit-Sneeze-Cough,
+Temperature-Muscles-Pain).
+
+\begin{figure*}[!htbp]
+
+{\caption{{Top: Distribution of responses across datasets reveals a
+consistent modal value, typically around 4 or 5 (indicating agreement),
+except for `blood sugar' and `bruise' - in dashed lines - and `affective
+touch' (dotted lines) in the Chinese validation sample, which have lower
+modes. Most responses cluster around the middle values, with few extreme
+scores (1 and 5). Samples using an analogue scale (10a, 10b, 10c) show a
+more continuous distribution and increased interindividual variability.
+Since most samples use Likert scales (discrete), density plots may not
+be the most accurate representation but were chosen to clearly highlight
+variability patterns in the data. Bottom: The correlation matrix between
+all items shows an overall positive correlation pattern, with correlated
+pairs (e.g., Wind, Burp) of items or triplets (e.g., Vomit, Sneeze and
+Cough).}{\label{fig-distributions}}}}
+
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{../../analysis/figures/Figure1.png}
+
+\end{figure*}
+
+UVA flagged two strongly redundant variables, ``itch'' and ``tickle'' -
+suggesting to remove the latter. Several more pairs of items were
+flagged as moderately redundant (``wind'' and ``burp''; ``urinate'' and
+``defecate'') and mildly redundant (``sneeze'' and ``cough''; ``heart''
+and ``breathing''; ``hungry'' and ``thirsty''). These patterns
+consistently appeared in most samples when considered individually. We
+removed ``tickle'' from further analysis due to its high redundancy (and
+because it is absent from some datasets due to translation issues).
+
+The HCA highlighted pairs and triplets of items consistently grouped
+together across samples, such as ``wind'' and ``burp'', ``sneeze'' and
+``cough'', ``itch'' and ``bruise'', ``urinate'' and ``defecate'', and
+``pain'', ``muscles'', and ``temperature''. This pattern was largely
+replicated by the EGA, with the additional presence of a unique cluster
+comprising ``Sex arousal'', ``Affective touch'', ``Temperature'',
+``Pain'', ``Muscles'', and ``Taste''. EFA suggested the optimal number
+of factors to be 3, yielding one dimension with expulsion-related items
+(``burp'', ``wind'', ``cough'', ``sneeze'', and ``vomit''), a second
+dimension with visceroceptive items (``heart'', ``breathing'',
+``hungry'', ``thirsty'', ``urinate'', and ``defecate''), and a third
+dimension with skin-related items (``bruise'' and ``blood sugar'').
+
+Importantly, this initial structure analysis run highlighted some
+problematic items: ``taste'' typically displayed a lone or unstable
+pattern of associations, ``affective touch'' exhibited cross-loadings
+and instability, ``vomit'' was less strongly associated with other
+items, and ``itch'' did not form a consistent cluster. Finally,
+``temperature'' and ``sexual arousal'' showed redundant patterns of
+associations but were less reliable. These 6 items were thus removed,
+and a second run of structure analysis was performed on the remaining 14
+items.
+
+\begin{figure*}[!htbp]
+
+{\caption{{TODO.}{\label{fig-structure}}}}
+
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{../../analysis/figures/Figure2.png}
+
+\end{figure*}
+
+HCA and EGA yielded highly consistent results, emphasizing pairs of
+items, namely Hungry-Thirsty, Bruise-Blood sugar, Urinate-Defecate,
+Muscles-Pain, Breathing-Heart, Cough-Sneeze, Wind-Burp. HCA also
+significantly grouped the Urinate-Defecate and Muscles-Pain pairs, as
+well as expulsion items (Wind-Burp and Cough-Sneeze). EFA suggested once
+again 3 factors as the optimal solution, with the first factor including
+expulsion-related items (``burp'', ``wind'', ``cough'', ``sneeze''), the
+second factor being related to the Urinate-Defecate pair, and the third
+factor comprising the remaining items.
+
+We then fitted and compared using CFA various candidate structures
+emerging from the previous analyses, including a 1-factor model (the
+G-model), a 3-factor model (EFA), a 3+1 model (EFA + general factor), a
+5-factor model (HCA), a 5+1 model (HCA + general factor), a 7-factor
+model (EGA), and a 7+1 model (EGA + general factor). The EGA model with
+7 factors of item pairs provided the best fit with the lowest RMSEA
+(0.035), lowest \(\chi^2\) (2306.30), highest CFI (0.984). It was
+followed by the EGA + general factor model (RMSEA = 0.054, \(\chi^2\) =
+6842.38, CFI = 0.952), and the HCA model with 5 factors (RMSEA = 0.078,
+\(\chi^2\) = 13296.33, CFI = 0.907). The other models performed poorly,
+with RMSEA \textgreater{} 0.08 and CFI \textless{} 0.90. The
+unique-factor model yielded the lowest BIC (which takes into account the
+number of factors), followed by the EGA model. All the other models
+displayed significantly (BIC-based Bayes Factor \textless{} 1/100) lower
+evidence compared to the EGA model.
+
+This result was relatively consistent across unique datasets with the
+EGA model providing the best fit. In all samples where CFA converged, it
+showed excellent performance with low RMSEA (≈ 0.025--0.046), high CFI
+(≥ 0.97), and substantially lower \(\chi^2\) compared to alternative
+models. Adding a general factor systematically worsened fit, while
+hierarchical clustering and EFA-based models showed poorer performance
+(RMSEA \textgreater{} 0.06, CFI \textless{} 0.93). Although BIC values
+occasionally favored alternative specifications, Bayes factor
+comparisons overwhelmingly supported the EGA solution, confirming its
+robustness across datasets.
+
+\subsection{Discussion}\label{discussion}
+
+The first study aimed to provide the most systematic test of the IAS
+structure to date. Previous work has produced conflicting models,
+ranging from a single general factor (\citeproc{ref-brand2023}{Brand et
+al., 2023}), to bifactor solutions (\citeproc{ref-campos2021}{Campos et
+al., 2021}; \citeproc{ref-lin2023}{Lin et al., 2023}), and two-factor
+models (\citeproc{ref-koike2023}{Koike \& Nomura, 2023};
+\citeproc{ref-murphy2019}{Murphy et al., 2019}). Alongside these
+structural discrepancies, several studies have questioned the quality of
+specific items. Murphy et al. (\citeproc{ref-murphy2019}{2019})
+distinguished between items tapping direct interoceptive signals (e.g.,
+heartbeat) and others reflecting phenomena less accessible to
+interoception (e.g., bruising). Additionally, Lin et al.
+(\citeproc{ref-lin2023}{2023}) identified locally dependent pairs and
+low-discrimination items with Network-based methods, while Campos et al.
+(\citeproc{ref-campos2021}{2021}) found that ``tickle'' did not load on
+the general factor. To address these open questions, we reanalyzed
+multiple open-access datasets using a mega-analytic framework,
+contrasting traditional factor-analytic approaches with network-based
+methods.
+
+Overall, the findings converge on a robust yet novel picture. Initial
+analysis revealed issues in 7 items (e.g., instability, redudancy, low
+associations, less reliable) which led to the formation of a 14-item
+IAS. Exploratory and confirmatory analyses indicated that the IAS is
+best characterized by seven pairs of closely related items, consistently
+identified by EGA and supported by HCA. These pairs (e.g.,
+hunger--thirst, urinate--defecate, cough--sneeze) were highly replicable
+across independent samples and yielded superior fit indices in CFA
+compared to other solutions. Although the one-factor model occasionally
+achieved lower BIC, Bayes factor comparisons overwhelmingly supported
+the EGA structure, underlining its empirical robustness.
+
+This pattern has several important implications. First, it suggests that
+the IAS does not capture a broad latent construct of interoceptive
+accuracy as originally intended, but rather reflects a set of tightly
+coupled item clusters tied to specific bodily sensations. In other
+words, the IAS may function more as a checklist of bodily signal
+detection items than as a scale measuring a coherent higher-order
+dimension. This stands in contrast to the original two-factor proposal
+(\citeproc{ref-murphy2019}{Murphy et al., 2019}), where the factors were
+highly correlated and collapsed into a unidimensional score, and helps
+explain why subsequent studies diverged in their conclusions: the
+psychometric structure of the IAS appears to be driven more by local
+dependencies than by robust latent factors. Second, the presence of
+redundant or unstable items (e.g., tickle, taste, affective touch),
+already highlighted in prior validation studies
 (\citeproc{ref-campos2021}{Campos et al., 2021};
-\citeproc{ref-lin2023}{Lin et al., 2023}) fits the data best. While this
-analysis also revealed an okay fit for the 1-factor model, the 4-factor
-model was superior. The 4-factor structure reveals different `hubs' of
-items that are related, not only in this structure analysis, but also in
-underlying mechanisms. The `wind-burp-cough-sneeze-vomit' category, for
-example, only entails items that are linked to excretion through the
-mouth. The other categories are organized similarly. This organization
-and structure is useful for further analysis, as the data can be
-analyzed and interpreted according to a grouping that is coherent in
-result, as well as underlying mechanisms.
-
-\textbf{note to dom}: what stats do you mean here? the UVA one?
-
-There are several items that show redundancy suggesting that adapting
-the IAS would be beneficial for validity. Based on the given results, we
-suggest removing the tickle, while keeping the itch item
-{[}\textbf{todo}: stats?{]}. Other items with slight redundancy were
-``hungry'' and ``thirsty'', ``urinate'' and ``defecate'', and ``sneeze''
-and ``cough''.
-
-Interestingly, Lin et al. (\citeproc{ref-lin2023}{2023}) also found that
-``tickle'' and ``itch'' were redundant, which led them to excludw one of
-them. Although, the reason being that the character for both words is
-the same in the Chinese language. On top of that, they came up with a
-shortened version of the IAS, excluding further items, resulting in a
-12-item IAS, which aligns with our findings, suggesting that further
-items are ambiguous as to whether they should be removed. Their 12-item
-IAS included the ``hunger'', ``breath'', ``urinate'', ``taste'',
-``vomit'', ``cough'', ``temperature'', ``sexual arousa'', ``wind'',
-``muscle'', ``pain'', ``itch'' items.\\
-In contrast, other findings also found ``tickle'' to be redundant but
-did not suggest excluding items (\citeproc{ref-campos2021}{Campos et
-al., 2021}).
-
-The findings indicate a high proportion of answers at 4 (see Figure 1),
-especially when using a 5-step scale. The analogue scale shows a more
-dispersed distribution, with some answers indicating the highest 5/5,
-which was not the case in Likert-scales. Therefore, we recommend using
-an analog scale for the IAS.
-
-Before this paper, the IAS had not yet been used or analyzed with an
-analog scale, rather than a five-step scale. Therefore, this study
-provides a novel approach to improving the IAS in a simple manner.
-
-\subsubsection{Limitations and Future
-Directions}\label{limitations-and-future-directions}
-
-There are several limitations to the IAS. There are some redundant
-items, the 5-point scale does not provide great variability, and the
-structure could be improved. Therefore, improving the IAS, or creating a
-new questionnaire investigating interoception could be useful to
-achieving reliable and accurate indication of interoceptive awareness.
-
-\subsection{Study 2}\label{study-2}
-
-Study 2 aims to investigate correlates of the IAS. Correlations of the
-IAS will be computed to assess the relationship between subjective
-interoceptive accuracy and other subjective measures of interoception,
-mood, psychopathology, personality, and beliefs. Investigating
-correlates will help validate the IAS, as well as other interoceptive
-measures in the future.
-
-\subsubsection{Methods}\label{methods-1}
-
-\paragraph{Materials.}\label{materials}
-
-The questionnaires used for the IAS correlates are listed in
-\textbf{Table 2} (\textbf{TODO: add the rest of the questionnaires,
-sample items and references}).
-
-\input{../../analysis/figures/table2.tex}
-
-\paragraph{Statistical analysis.}\label{statistical-analysis-1}
-
-Correlations will be computed using the correlation package under a
-Bayesian framework (\citeproc{ref-ben2020effectsize}{Ben-Shachar et al.,
-2020}).
-
-\subsubsection{Results}\label{results-1}
-
-\subsection{Average correlations}\label{average-correlations}
-
-The EGA components captured grouping of items such as `wind' and `burp,
-'cough' and `sneeze', `muscle' and `pain'. These groupings were used in
-correlational analysis to analyse how much each pairing is associated
-with other factor such as Alexithymia and with Mood disorders (see
-figure 2).
-
-\textbf{note}compute internal consistency
-
-\paragraph{Correlations with body
-measures.}\label{correlations-with-body-measures}
-
-Alexithymia was assessed in the samples with the Bermond--Vorst
-Alexithymia Questionnaire {[}BVAQ; Vorst and Bermond
-(\citeproc{ref-vorst2001validity}{2001}){]} and the Toronto Alexithymia
-Scale{[}TAS; Bagby et al. (\citeproc{ref-bagby1994twenty}{1994}){]}.
-
-The BVAQ consists of 5 subscales - fantasising, idenitying, analysing;
-verbalising and emotionalising - assessed with 40 items on a 5-point
-Likert scale, from `defnitely applies to me' to `in no way applies to
-me'. Additionally, the BVAQ reduces these subscales into two high order
-factors, an affective component and a cognitive one, with high scores
-being indicative of high proneness to alexithymia.
-
-On average, the cognitive component of the BVAQ was weakly and
-negatively correlated with all IAS pairs of items with the biggest
-correlation being with the Itch/Bruise pair (r = -0.112) and the lowest
-correlation beeing with the Muscle/Pain pair (r = -0.244). The affective
-component of the BVAQ was positively, but very weak, correlated with all
-pairs, with the biggest correlation being with the Itch/Bruise pair (r =
-0.107). The only exception was a negative correlation with the
-Urinate/Defecate pair (r = -0.036).
-
-The TAS contains 20-items rated on a 5-point forced scale, from
-`strongly disagree' to `strongly afree', divided into 3 dimensions -
-difficulty identiying feelings, difficulty describing feelings, and
-externally thinking. High scores on this scale also reflect higher
-alexithymia.
-
-All the three dimensions assessed with the TAS were on average
-negatively correlated with all pairs of IAS items. The difficulty
-describing feelings had its strongest correlation with Hungry/Thirsty (r
-= -0.179) and weakest with the Wind/Burp (r = -0.117). while, the
-difficulty describing feelings had its strongest correlation with
-Muscle/Pain (r = -0.247) and weakest with Itch/Bruise (r = -0.157).
-Lastly, the external thinking dimension was more correlated with the
-Cough/Sneeze pair (r = -0.138) and less correlated with the
-Hungry/Thirsty (r = -0.018).
-
-The studies within our sample used the Body Perception Questionnaire
-short-form (BPQ-SF) and the very-short form (BPQ-VSF) to assess
-interoception (\citeproc{ref-cabrera2018assessing}{Cabrera et al.,
-2018}). The BPQ-SF comprised of 46 items on a 5-point Likert scale
-assessing body awareness (26 items) and autonomic reactivity (21 items).
-The BPQ-VSF comprises of 12 items from the body awareness subscale of
-the BPQ-SF. In this study, all scores assessing these two dimensions
-were grouped together, hence no disitintion is made between awareness
-measured with the BPQ-SF and the BPQ-VSF.
-
-\textbf{note to add:} discuss later
-
-In general, all pairs of the IAS were positively,and weakily, associated
-with the body awareness subscales, while negative and weakily correlated
-with the autonomic reactivity subscale. The strongest correlation
-identified between the IAS pairs and the body awereness subscale was
-with the\\
-Heart/Breathing pair (r = 0.151) whilst the strongest correlation with
-the autonomic reactivity was with the Urinate/Defecate pair (r =
--0.235). The weakest correlation between the body awareness and the IAS
-was with the Hungry/Thirsty pair (r = 0.055) and between the autonomic
-reactivity and the IAS was with the Heart/Breathing pair (r = -0.106).
-
-The MAIA was one of the most commonly used measures of interoception in
-our study, with nine samples reporting its use. This 37-item
-questionnaire assesses eight state-trait dimensions of interoception:
-Noticing, Not-Distracting, Not-Worrying, Attention Regulation, Emotional
-Awareness, Self-Regulation, Body Listening, and Trust. Responses are
-rated on a scale from 0 (Never) to 5 (Always).
-
-On average, all MAIA dimensions were positively and weakly to moderately
-correlated with IAS pairings. Notably, the strongest correlations were
-observed between the Noticing dimension and the Heart/Breathing pairing
-(r = 0.394), Trusting and Hungry/Thirsty (r = 0.347), and Attention
-Regulation and Heart/Breathing (r = 0.334). The Not-Distracting and
-Not-Worrying subscales were generally positively correlated with IAS
-pairings, with a few exceptions: Not-Distracting showed minimal
-correlation with Cough/Sneeze (r = 0.0206) and Heart/Breathing (r =
--0.007), while Not-Worrying had a low correlation with Itch/Bruise (r =
-0.031).
-
-The Interoceptive Confusion Questionnaire (ICQ; Brewer et al.
-(\citeproc{ref-brewer2016alexithymia}{2016})) was used to assess
-individuals' difficulties in interpreting non-affective physiological
-states, such as pain and hunger. The ICQ consists of 20 items rated on a
-scale from 1 (``Does not describe me'') to 5 (``Describes me very
-well''), with higher scores indicating greater interoceptive confusion.
-
-The ICQ showed weak to moderate negative correlations with all IAS
-pairings. The strongest correlation was observed with the Hunger/Thirsty
-pairing (r = 0.348), while the weakest was with the Itch/Bruise pairing
-(r = 0.207).
-
-\paragraph{Correlations with mood
-measures.}\label{correlations-with-mood-measures}
-
-Mood disorders were assessed using several standardized measures,
-including the General Anxiety Disorder-2 {[}GAD-2; Kroenke et al.
-(\citeproc{ref-kroenke2007anxiety}{2007}){]}, the State-Trait Anxiety
-Inventory {[}STAI; Spielberger
-(\citeproc{ref-spielberger1970manual}{1970}){]} and its shorter version,
-the STAI-5 (\citeproc{ref-zsido2020development}{Zsido et al., 2020}),
-Beck's Depression Inventory {[}BDI; Beck et al.
-(\citeproc{ref-beck1996beck}{1996}){]}, and the Mood and Feelings
-Questionnaire {[}MFQ; Messer et al.
-(\citeproc{ref-messer1995development}{1995}){]}. Additionally, the
-Patient Health Questionnaire (PHQ) was administered in its 2-item
-{[}PHQ-2; Kroenke et al. (\citeproc{ref-kroenke2003patient}{2003}){]},
-9-item {[}PHQ-9; Kroenke et al.
-(\citeproc{ref-kroenke2001phq}{2001}){]}, and 15-item {[}PHQ-15; Kroenke
-et al. (\citeproc{ref-kroenke2002phq}{2002}){]} versions. Finally,
-borderline personality traits were assessed using the McLean Screening
-Instrument for Borderline Personality Disorder {[}MSI-BPD; Zanarini
-(\citeproc{ref-zanarini2003zanarini}{2003}){]}.
-
-The GAD-2, a brief screening tool for generalized anxiety disorder,
-consists of two items rated on a scale from 0 (not at all) to 3 (nearly
-every day). The STAI, a 40-item questionnaire rated on a 4-point Likert
-scale (0 to 3), measures both state and trait anxiety. However, in our
-study, most participants primarily completed the trait anxiety subscale.
-In some samples, a shorter 5-item version (STAI-5) was used to assess
-both state and trait anxiety.
-
-On average, anxiety measures showed weak negative correlations with all
-IAS pairs. Notably, the strongest correlations between the IAS pairings
-and the GAD-2, STAI-T and STAIT-5 were observed with the Hungry/Thirsty
-pair (r = -0.168, r = -0.270 and r = -0.248, respectively).
-
-The BDI consists of 21 items measuring the severity of depressive
-symptoms on a scale from 0 to 3. The total score is calculated by
-summing the highest responses, which are then compared to six depression
-severity levels, ranging from 1--10 (normal fluctuations in mood) to
-over 40 (extreme depression). The PHQ-2 includes two items assessing the
-frequency of depressive symptoms and anhedonia. The PHQ-2 is derived
-from the PHQ-9, a nine-item screening tool used to assess depression
-severity and monitor treatment response. Both questionnaires are
-measured on on a scale from 0 (not at all) to 3 (nearly every day)
-
-Depression measures showed weak to moderate negative correlations with
-IAS pairings. The BDI (r = -0.372), PHQ-2 (r = -0.148), and PHQ-9 (r =
--0.241) correlated most with the Hungry/Thirsty pair, while the MFQ
-correlated most with Heart/Breathing (r = -0.345) pair.
-
-The PHQ-15 also showed its strongest correlation with the Hungry/Thirsty
-pair (r = -0.241) but was, on average, weakly and negatively correlated
-with all other IAS pairings.
-
-Lastly, the MSI-BPD also showed its strongest negative correlation with
-the Hungry/Thirsty pair (r = -0.140) and was negatively correlated with
-all other pairings, except for Cough/Sneeze, which showed a slight
-positive correlation (r = 0.0219).
-
-\begin{figure}[H]
-
-\caption{\textbf{Figure 2.} Correlates of the IAS}
-
-{\centering \includegraphics[width=9.48958in,height=\textheight]{figures/clipboard-1619164537.png}
-
-}
-
-\end{figure}%
-
-\subsubsection{Discussion}\label{discussion-1}
-
-Our findings confirm that interoception exists within a complex network
-of correlates. Among these, alexithymia exhibits the strongest negative
-correlation with the IAS, whereas the MAIA questionnaire shows the
-strongest positive correlation. These correlates not only help explain
-different aspects of interoception but also serve as valuable tools for
-validating interoceptive measures.
-
-While our results reveal various correlations with the IAS, they are
-limited to the scope of the given questionnaire. Nonetheless, they
-provide valuable insights into how interoception may relate to different
-psychological and personality traits. The results show a consistent
-pattern of correlations with other measures and highlight interesting
-exploratory results, such as correlations between primal world beliefs
-with the IAS.
-
-Our analysis found a strong negative correlation between alexithymia and
-IAS scores, aligning with previous research
+\citeproc{ref-lin2023}{Lin et al., 2023}), undermines the
+interpretability of the scale, as their contributions appear
+inconsistent or overlapping. Together, these findings help explain why
+previous research has struggled to converge on a stable factor
+structure: the IAS lacks the psychometric properties required for strong
+latent modeling and may overstate its dimensionality by conflating
+redundancy with structure.
+
+At the same time, the results do not render the IAS unusable. The
+consistent emergence of item pairs highlights intuitive bodily domains
+(e.g., visceral, expulsion, musculoskeletal) that align with everyday
+interoceptive experiences, supporting its ecological validity. However,
+the limited breadth of these pairings, the redundancy across items, and
+the reliance on a narrow 5-point scale all restrict the scale's ability
+to differentiate between individuals and to capture the multidimensional
+nature of interoception (\citeproc{ref-desmedt2022measures}{Desmedt et
+al., 2022}). These findings therefore call for refinement, either
+through targeted revisions of the IAS (e.g., removing redundant items,
+addition of context-specific items, adopting analogue response formats)
+or through the development of a new questionnaire that better balances
+theoretical coherence with empirical validity.
+
+In sum, Study 1 demonstrates that the IAS structure is best described by
+clusters of tightly coupled item pairs reflecting local dependencies,
+rather than by a broad latent dimension. While this solution is
+replicable and statistically robust, it highlights the conceptual and
+psychometric limitations of the IAS in its current form. These insights
+help contextualize the mixed findings on the scale's validity and
+provide a crucial foundation for Study 2, where we do the dispositional
+correlates of the IAS to further evaluate its construct validity and
+situate it within the broader network of interoceptive and psychological
+traits.
+
+\section{Study 2}\label{study-2}
+
+\subsection{Study 2}\label{study-2-1}
+
+Building on the structural findings from Study 1, the second study turns
+to the validity of the IAS by examining its dispositional correlates.
+Although the IAS has been widely used, evidence regarding its
+associations with personality traits, affective dispositions, and
+related psychological constructs remains scattered and inconsiste
 (\citeproc{ref-brand2023}{Brand et al., 2023};
-\citeproc{ref-herbert2011}{Herbert et al., 2011};
-\citeproc{ref-murphy2019}{Murphy et al., 2019}). Similarly, a negative
-correlation between autism and interoceptive awareness was observed in
-our sample, consistent with prior findings
-(\citeproc{ref-dubois2016}{DuBois et al., 2016}).
-
-Conspiracy beliefs did not strongly correlate with IAS scores, though a
-slight positive correlation was present. To our knowledge, this
-relationship has not been previously explored. However, prior studies
-have suggested connections between interoception and (political)
-beliefs, potentially pointing to shared underlying mechanisms
-(\citeproc{ref-ruisch2022}{Ruisch et al., 2022a}).
-
-The relationship between interoception and lying profiles was also weak.
-This contrasts with previous research suggesting associations between
-interoception and deception (\citeproc{ref-makowski2023a}{Makowski et
-al., 2023}), warranting further investigation.
-
-Mood and IAS scores exhibited a strong negative correlation, consistent
-with prior studies that have documented similar findings
-(\citeproc{ref-solanoluxf3pez2018}{Solano López \& Moore, 2018}).
-Additionally, personality traits correlated with interoceptive accuracy
-scores, reinforcing existing research linking personality and
-interoception (\citeproc{ref-erle2021}{Erle et al., 2021}).
-
-We also observed negative correlations between schizotypy and
-interoception, in line with previous studies that identified a similar
-relationship with interoceptive awareness, particularly in individuals
-at risk for psychosis (\citeproc{ref-torregrossa2022}{Torregrossa et
-al., 2022}).
-
-Interestingly, world beliefs demonstrated significant positive
-correlations with interoception. While this relationship has not been
-previously documented, other forms of belief, such as political
-ideology, have been linked to interoception
-(\citeproc{ref-ruisch2022a}{Ruisch et al., 2022b}). Further research is
-needed to determine whether world beliefs, which shape our perception of
-reality (\citeproc{ref-clifton2020}{Clifton, 2020}), are meaningfully
-connected to interoception.
-
-Overall, our findings highlight the broad relevance of interoception
-across various cognitive and affective traits, underscoring its
-significance in both research and clinical contexts. By identifying
-numerous correlates of the IAS, we contribute not only to a deeper
-understanding of interoception's role in daily life but also to the
-ongoing validation of the IAS and other interoceptive measures. This
-analysis lays an important foundation for the development of new
-interoceptive assessment tools, further advancing our comprehension of
-interoception and its impact on human experience.
-
-\subsection{General Discussion}\label{general-discussion}
+\citeproc{ref-lin2023}{Lin et al., 2023};
+\citeproc{ref-murphy2019}{Murphy et al., 2019};
+\citeproc{ref-todd2022}{Todd et al., 2022}). Study 2 therefore had two
+primary goals. First, to provide a robust overview of the dispositional
+correlates of the IAS by leveraging the large number of available
+datasets. Second, to evaluate the practical benefits of using the
+refined 14-item version of the scale identified in Study 1, compared to
+the original 21-item unidimensional version, in order to assess whether
+structural improvements translate into clearer and more reliable
+external associations.
+
+\subsection{Methods}\label{methods-1}
+
+\subsubsection{Materials}\label{materials}
+
+We selected measures that appeared in multiple datasets from Study 1
+and/or were relevant given the scope of the study, merging scores of
+regular and abridged versions for conciseness where applicable. The
+measures include constructs related to interoception, mood, personality,
+psychopathology, and beliefs and misbeliefs.
+
+\paragraph{Interoception Related.}\label{interoception-related}
+
+The Multidimensional Assessment of Interoceptive Awareness Version-2
+(MAIA-2, \citeproc{ref-mehling2018multidimensional}{Mehling et al.,
+2018}) is a 37-item questionnaire assessing eight dimensions of
+interoception: Noticing, Not-Distracting, Not-Worrying, Attention
+Regulation, Emotional Awareness, Self-Regulation, Body Listening, and
+Trust. Responses are rated on a 6-point Likert scale (e.g., ``I notice
+when I am uncomfortable in my body'').
+
+The Body Perception Questionnaire Short Form (BPQ-SF,
+\citeproc{ref-cabrera2018assessing}{Cabrera et al., 2018}) contains 46
+items measuring body awareness and autonomic reactivity on a 5-point
+Likert scale (e.g., ``My heart often beats irregularly''). The
+very-short form (BPQ-VSF) contains 12 items from the body awareness
+subscale. For this study, scores from both versions were combined.
+
+The Interoceptive Confusion Questionnaire (ICQ,
+\citeproc{ref-brewer2016alexithymia}{Brewer et al., 2016}) consists of
+20 items rated on a 5-point Likert scale (e.g., ``I cannot tell when my
+muscles are sore or tight'') assessing difficulties in interpreting
+non-affective physiological states, such as pain or hunger.
+
+The Toronto Alexithymia Scale (TAS-20,
+\citeproc{ref-bagby1994twenty}{Bagby et al., 1994}) contains 20 items
+rated on a 5-point forced-choice scale (e.g., ``I have feelings I can't
+quite identify''), divided into three dimensions: difficulty identifying
+feelings, difficulty describing feelings, and externally oriented
+thinking.
+
+The Bermond--Vorst Alexithymia Questionnaire (BVAQ,
+\citeproc{ref-vorst2001validity}{Vorst \& Bermond, 2001}) consists of 40
+items across five subscales: fantasising, identifying, analysing,
+verbalising, and emotionalising. Items are rated on a 5-point Likert
+scale. The BVAQ also provides two higher-order factors, namely affective
+and cognitive (e.g., ``I like to tell others how I feel'').
+
+\paragraph{Mood and Anxiety Related.}\label{mood-and-anxiety-related}
+
+The Beck Depression Inventory-II (BDI-II,
+\citeproc{ref-beck1996beck}{Beck et al., 1996}) is a 21-item measure of
+depressive symptom severity, including psychological (e.g., guilt) and
+physiological (e.g., loss of energy) components. Items are rated on a
+4-point scale (e.g., ``I feel sad much of the time'').
+
+The Patient Health Questionnaire-4 (PHQ-4,
+\citeproc{ref-kroenke2009ultra}{Kroenke et al., 2009}) is a 4-item
+screening tool for depression and anxiety, rated on a 4-point Likert
+scale (e.g., ``Little interest or pleasure in doing things''; ``Not
+being able to stop or control worrying''). The PHQ-2 (PHQ-2,
+\citeproc{ref-kroenke2003patient}{Kroenke et al., 2003}) and General
+Anxiety Disorder-2 (GAD-2, \citeproc{ref-kroenke2007anxiety}{Kroenke et
+al., 2007}) scores were combined with the PHQ-4 scores.
+
+The Patient Health Questionnaire-9 (PHQ-9,
+\citeproc{ref-kroenke2001phq}{Kroenke et al., 2001}) includes 9 items
+assessing depressive symptoms on a 4-point Likert scale (e.g., ``Feeling
+tired or having little energy?'').
+
+The Patient Health Questionnaire-15 (PHQ-15,
+\citeproc{ref-kroenke2002phq}{Kroenke et al., 2002}) assesses somatic
+symptom distress with 15 items rated on a 3-point scale (e.g., ``Over
+the last week, how often have you been bothered by back pain?'').
+
+The Short Mood and Feelings Questionnaire (SMFQ,
+\citeproc{ref-angold1995development}{Angold et al., 1995}) is a 13-item
+measure of recent depressive symptoms in children aged 6--17, rated on a
+3-point scale (e.g., ``I felt miserable or unhappy'').
+
+The State--Trait Anxiety Inventory Trait Version (STAI-T,
+\citeproc{ref-spielberger1970manual}{Spielberger, 1970}) is a 20-item
+trait anxiety questionnaire rated on a 4-point Likert scale (e.g., ``I
+worry too much about something that really doesn't matter''). Scores
+from the shorter version of the STAIT-5
+(\citeproc{ref-zsido2020development}{Zsido et al., 2020}) were combined
+with the STAI-T.
+
+The Generalized Anxiety Disorder Scale (GAD-7,
+\citeproc{ref-spitzer2006brief}{Spitzer et al., 2006}) is a 7-item
+measure of generalized anxiety symptoms rated on a 4-point Likert scale
+(e.g., ``Not being able to stop or control worrying'').
+
+\paragraph{Personality.}\label{personality}
+
+The NEO Five-Factor Inventory, neuroticism subscale (NEO-FFI,
+\citeproc{ref-costa1992neo}{Costa \& McCrae, 1992}) is a 12-item measure
+of neuroticism, assessing the general tendency to experience negative
+emotions such as fear, sadness, or disgust. Items are rated on a 5-point
+Likert scale (e.g., ``I often feel inferior to others'').
+
+The Mini International Personality Item Pool (MINI-IPIP6,
+\citeproc{ref-sibley2011mini}{Sibley et al., 2011}) includes 24 items
+measuring six broad traits: Agreeableness, Conscientiousness,
+Neuroticism, Openness, Extraversion, and Honesty-Humility. Items were
+scored on visual analogue scales in our samples (originally 7-point
+Likert scales; e.g., ``Have a vivid imagination'').
+
+The Big Five Inventory Short Form (BFI-S,
+\citeproc{ref-rammstedt2007measuring}{Rammstedt \& John, 2007}) is a
+10-item measure of the Big Five traits, rated on a 7-point Likert scale
+(e.g., ``I see myself as someone who \ldots{} is considerate and kind to
+almost everyone'').
+
+\paragraph{Psychopathology.}\label{psychopathology}
+
+The Personality Inventory for DSM-5 Short Form (PID-5-SF,
+\citeproc{ref-thimm2016personality}{Thimm et al., 2016}) consists of 25
+items rated on a 4-point Likert scale, measuring five domains:
+disinhibition, antagonism, detachment, negative affect, and psychoticism
+(e.g., ``Plenty of people are out to get me'').
+
+The Schizotypal Personality Questionnaire -- Brief Revised (SPQ-BR,
+\citeproc{ref-davidson2016schizotypal}{Davidson et al., 2016}) contains
+32 items rated on a 5-point Likert scale, assessing four primary
+dimensions: cognitive-perceptual, interpersonal, disorganized, and
+social anxiety. These are subdivided into nine secondary factors,
+including constricted affect, eccentricity, magical thinking, lack of
+close friends, odd speech, referential thinking, social anxiety,
+suspiciousness, and unusual perceptions (e.g., ``Plenty of people are
+out to get me'').
+
+The McLean Screening Instrument for Borderline Personality Disorder
+(MSI-BPD, \citeproc{ref-zanarini2003zanarini}{Zanarini, 2003}) is a
+10-item dichotomous screening measure for borderline personality
+disorder (present/absent; e.g., ``Have any of your closest relationships
+been troubled by a lot of arguments or repeated breakups?'').
+
+The Autism Spectrum Quotient Short Form (ASQ-S,
+\citeproc{ref-hoekstra2011construction}{Hoekstra et al., 2011}) is a
+28-item measure of five autistic traits: social skills, adherence to
+routines, cognitive flexibility, imagination, and patterns/numbers.
+Items are rated on a 4-point Likert scale (e.g., ``I find it difficult
+to work out people's intentions'').
+
+\paragraph{Beliefs and Misbeliefs.}\label{beliefs-and-misbeliefs}
+
+The Generic Conspiracist Beliefs Scale (GCBS,
+\citeproc{ref-brotherton2013measuring}{Brotherton et al., 2013}) is a
+15-item measure assessing five dimensions of conspiracy beliefs:
+government malfeasance, extraterrestrial cover-up, malevolent global
+conspiracies, personal wellbeing, and control of information. Items are
+scored on a 5-point Likert scale (e.g., ``Secret organizations
+communicate with extraterrestrials, but keep this fact from the
+public'').
+
+The Primal World Beliefs Inventory (PI-99,
+\citeproc{ref-clifton2019primal}{Clifton et al., 2019}) is a 99-item
+measure assessing 26 high-order beliefs about the world. Items are
+scored on a 5-point Likert scale (e.g., ``Nearly everything in the world
+is beautiful'') The PI-18 (\citeproc{ref-clifton2021brief}{Clifton \&
+Yaden, 2021}) is a short form of the orginal questionnaire assessing the
+4 main world beliefs: the world is Good (vs.~Bad) and its three
+dimensions: Safe (vs.~Dangerous), Enticing (vs.~Dull), and Alive
+(vs.~Mechanistic). Scores from the PI-18 scores were combined with the
+PI-99.
+
+The Lie Scale (LIE, \citeproc{ref-makowski2023structure}{Makowski et
+al., 2023}) is a 16-item measure of lying tendencies across four
+components: Ability, Frequency, Negativity, and Contextuality. Items are
+scored on visual analogue scales (e.g., ``I am a good liar'').
+
+\subsubsection{Data Analysis}\label{data-analysis-1}
+
+All variables from the 16 open-access datasets will be extracted and
+standardized (z-scored). For continuous predictors, we will first ensure
+consistent ranges across datasets; when necessary, ranges will be
+rescaled to achieve comparability. In cases where scales of different
+lengths measure the same construct, scores will be harmonized: when
+possible, means will be computed from overlapping items, while in other
+cases total scores will be normalized by the number of items. We will
+collapse redundant subscales (e.g., PHQ-2 and GAD-2 within PHQ-4) into
+unified composite scores. Similarly, short forms of trait anxiety (e.g.,
+STAI-5-trait) will be collapsed with their longer counterpart (STAI-T),
+with scores computed as the mean to ensure comparable ranges. Shorter
+formats of the PI (PI-18) will be combined with scores of its longer
+version (PI-99). Missing data will be handled via listwise deletion on a
+per-model basis prior to fitting.
+
+Associations will be estimated using multilevel regression models
+implemented in the glmmTMB package (\citeproc{ref-glmTMB}{McGillycuddy
+et al., 2025}). Each predictor will be entered separately, with the
+seven IAS item pairs identified in Study 1 (``Hungry--Thirsty'',
+``Muscles--Pain'', ``Wind--Burp'', ``Urinate--Defecate'',
+``Breathing--Heart'', ``Bruise--Blood'', ``Cough--Sneeze'') and the
+original IAS scale serving as outcomes. Models will include random
+intercepts and slopes by sample to account for between-study
+heterogeneity; when models fail to converge, a reduced structure with
+random intercepts only will be used. This approach will treat datasets
+as clusters, thereby providing pooled estimates of the associations
+while accounting for both within- and between-sample variability, akin
+to a meta-analytic framework.
+
+From each fitted model, we will extract standardized regression
+coefficients (β), 95\% confidence intervals, p-values, convergence
+status, and effective sample size. Participants identifying as ``Other''
+will be excluded from analyses due to limited representation.
+
+\subsection{Results}\label{results-1}
+
+Age was positively associated across Ias correlates (mean r = .12), with
+all correlations significant. Gender showed near-zero effects (mean r =
+−.01), with 63\% reaching significance.
+
+Several MAIA subscales showed consistent positive associations with the
+IAS: Noticing, Attention Regulation, Trusting, Emotional Awareness,
+Listening, and Self-Regulation (βs ≈ .18--.26). These effects were
+generally strongest for the full IAS, but often replicated with
+Hungry/Thirsty or Bruise/Blood pairings. By contrast, Autonomic
+Reactivity (BPQ; β = −.17) was reliably negative across most pairings,
+while Body Awareness (BPQ; β = .12) was weak and only reliable for
+Hungry/Thirsty and Bruise/Blood. Alexithymia measures were consistently
+negative, with robust effects across both the full IAS and pairings,
+except for the Affective dimension of the BVAQ which showed only a
+positive association with the Bruise/Blood sugar pairing (β = .04).
+
+Depression (BDI; β = −.20) and anxiety (STAI-T; β = −.19) were
+consistently negative across the IAS and most pairings, with
+Hungry/Thirsty again emerging as a particularly sensitive correlate.
+Broader symptom indices (PHQ-15, PHQ-4, GAD-7) showed weaker but often
+reliable effects, although some were restricted to certain pairings
+(e.g., PHQ-15 with Hungry/Thirsty, Bruise/Blood). By contrast, PHQ-9 and
+MFQ averaged negatively but were largely nonsignificant, even with the
+full scale. Autistic traits were generally negative, especially
+Imagination (β = −.18), which showed broad consistency across pairings
+except Cough/Sneeze.
+
+Within the Big Five, Openness (β = .14), Agreeableness (β = .05), and
+Conscientiousness (β = .03) showed small but consistent positive
+associations, most reliably captured by the full IAS but also evident in
+pairings. Honesty--Humility was uniquely negative, with significant
+associations for both the full scale and Hungry/Thirsty. Worldview
+measures were generally null, though belief in a comprehensible world (β
+= .11) and an ``alive'' world (β = .09) showed small but consistent
+positive associations, mainly with the full IAS and Hungry/Thirsty.
+
+Overall, the full IAS yielded the largest number of significant
+associations (25), but the Hungry/Thirsty (16) and Bruise/Blood sugar
+(11) pairings frequently showed equally strong or stronger effects.
+These item-level pairings often captured variance that the full scale
+did not, particularly for interoceptive and mood measures. In contrast,
+other pairings (e.g., Cough/Sneeze, Wind/Burp, Urinate/Defecate)
+contributed little unique variance. Together, these results suggest that
+while the full IAS captures broad dispositional tendencies, select
+pairings may provide more fine-grained sensitivity to specific domains,
+particularly interoception and affect.
+
+{[}\textbf{NOTE} justify the choice of those specific primals ? higehr
+correlations with the IAS?{]}
+
+\subsection{Discussion}\label{discussion-1}
+
+The second study set out to provide a comprehensive overview of the
+dispositional correlates of the IAS by pooling data across multiple
+datasets, while also testing whether the refined 14-item version
+identified in Study 1 confers practical advantages over the original
+21-item scale.
+
+Consistent with prior research, the IAS showed strong positive
+associations with other interoceptive self-report measures, particularly
+the MAIA, with the exception of the Not Distracting and Not Worrying
+facets (\citeproc{ref-brand2023}{Brand et al., 2023}). This pattern
+replicates earlier findings while contradicting
+(\citeproc{ref-todd2022}{Todd et al., 2022}), who reported only a
+near-zero correlation with Not Worrying. Similarly, while previous
+evidence on the BPQ was mixed, our results indicate more robust
+associations with the Autonomic Reactivity dimension compared to body
+awareness (\citeproc{ref-brand2023}{Brand et al., 2023};
+\citeproc{ref-campos2021}{Campos et al., 2021};
+\citeproc{ref-todd2022}{Todd et al., 2022}). This pattern diverges from
+earlier findings that consistently reported significant positive
+associations with Body Awareness (\citeproc{ref-brand2023}{Brand et al.,
+2023}; \citeproc{ref-campos2021}{Campos et al., 2021};
+\citeproc{ref-gaggero2021}{Gaggero et al., 2021}), while at the same
+time complementing reports of significant negative correlations with
+Autonomic Reactivity (\citeproc{ref-gaggero2021}{Gaggero et al., 2021}).
+The replication of negative associations with interoceptive confusion
+(\citeproc{ref-brand2023}{Brand et al., 2023};
+\citeproc{ref-gaggero2021}{Gaggero et al., 2021};
+\citeproc{ref-murphy2019}{Murphy et al., 2019}) further supports the
+convergent and discriminant validity of the IAS.
+
+Robust negative correlations were observed between the IAS and
+alexithymia, in line with prior studies (\citeproc{ref-brand2023}{Brand
+et al., 2023}; \citeproc{ref-campos2021}{Campos et al., 2021};
+\citeproc{ref-koike2023}{Koike \& Nomura, 2023};
+\citeproc{ref-lin2023}{Lin et al., 2023};
+\citeproc{ref-murphy2019}{Murphy et al., 2019}). Similarly, negative
+associations with depression and anxiety, as measured by the BDI and
+STAI-T, reinforce the clinical relevance of interoceptive accuracy
+(\citeproc{ref-brand2023}{Brand et al., 2023};
+\citeproc{ref-lin2023}{Lin et al., 2023}). Somatic symptoms were also
+negatively related to the IAS, although effect sizes were small, echoing
+earlier findings (\citeproc{ref-brand2023}{Brand et al., 2023};
+\citeproc{ref-koike2023}{Koike \& Nomura, 2023};
+\citeproc{ref-lin2023}{Lin et al., 2023}). At the same time, more recent
+studies have reported null or inconsistent associations between
+interoceptive sensitivity and mental-health symptomatology, suggesting
+that such links may not generalize across all interoceptive domains and
+could be contingent on measurement approaches or sample characteristics
+{[}\textbf{REF PRE\_PRINT?}{]}.
+
+Clear negative associations also emerged with autism-related traits such
+as imagination, low attentional switching, and reduced social skills.
+These findings resonate with DuBois et al.
+(\citeproc{ref-dubois2016}{2016}) review reporting interoceptive
+abnormalities in autism. Nonetheless, our findings are limited to a
+single dataset employing the ASQ, which constrains the generalisability
+of conclusions regarding the relationship between interoception and
+autistic traits.
+
+The associations between interoception and personality traits were more
+nuanced. Whereas prior work suggested a negative link with neuroticism
+(\citeproc{ref-brand2023}{Brand et al., 2023}), we found this
+relationship to be inconsistent and even slightly positive, though near
+zero. By contrast, openness and agreeableness were consistently
+positively associated with the IAS, albeit with small effect sizes.
+These findings are consistent with emerging evidence linking openness to
+interoception as measured by the MAIA-2
+(\citeproc{ref-simkute2025interoception}{Simkute et al., 2025}), and
+complement reports of associations between interoceptive sensitivity
+(i.e., the accuracy of reported heartbeat counts relative to actual
+heartbeats) and extraversion
+(\citeproc{ref-haustein2024interoception}{Haustein et al., 2024}).
+Personality effects more broadly were modest in size, and as such,
+warrant replication before firm conclusions can be drawn. In contrast,
+maladaptive personality dimensions and schizotypal traits showed only
+weak and inconsistent associations with the IAS, indicating that
+interoceptive accuracy may not play a central role in these domains.
+
+Beyond established correlates, exploratory analyses revealed weak but
+positive associations between the IAS and primal world beliefs,
+specifically perceiving the world as alive and understandable. The
+inclusion of primal world beliefs was exploratory, motivated by their
+potential theoretical link to embodied cognition and meaning-making
+processes. Although effect sizes were small, the emergence of consistent
+associations with perceiving the world as alive and understandable
+suggests an intriguing avenue for future work at the intersection of
+interoception and worldview formation.
+
+A central aim of Study 2 was to assess whether the refined 14-item IAS
+identified in Study 1 provides practical benefits over the original
+21-item scale. While the full version most often emerged as the
+strongest correlate, the refined 14-item IAS performed largely
+comparably across dispositional measures. Importantly, specific item
+pairings --- particularly Hungry/Thirsty and Bruise/Blood sugar ---
+frequently captured associations as strong as, or occasionally stronger
+than, the full scale. This suggests that beyond efficiency, the refined
+IAS may offer more fine-grained sensitivity to certain dispositional
+domains, highlighting that interoceptive self-report is not
+unidimensional but may be differentially expressed across bodily
+contexts.
+
+Overall, these findings provide converging evidence for the construct
+validity of the IAS, most strongly in relation to interoceptive
+self-report, alexithymia, mood, and autism-related traits. Other
+associations, particularly with personality and belief systems, were
+weaker and more exploratory, highlighting both the breadth and the
+limits of interoceptive accuracy as captured by the IAS. Taken together,
+Study 2 advances our understanding of the dispositional landscape of
+interoception. The findings provide strong support for the construct
+validity of the IAS, while also demonstrating that the refined version
+can capture comparable patterns of association. Moreover, the
+sensitivity of specific item pairings points to the possibility that
+different bodily contexts (e.g., hunger vs.~pain) may differentially
+align with psychological traits, suggesting a promising direction for
+future research on the contextual dimensions of interoceptive accuracy.
+
+\section{General Discussion}\label{general-discussion}
+
+\textbf{The present study aimed\ldots{} {[}always start with a
+description of the study{]}}.
 
@@
 
-\subsection{Conclusion}\label{conclusion}
+This suggests that the 14-item IAS constitutes a more efficient tool
+without substantial loss of predictive power. In practice, the refined
+scale offers advantages for researchers and clinicians alike: it reduces
+participant burden, avoids problematic items flagged in Study 1 (e.g.,
+``tickle,'' ``taste,'' ``vomit''), and provides a more coherent
+representation of interoceptive domains.
+
+\section{Limitations and Future
+Directions}\label{limitations-and-future-directions}
+
+There are several limitations to the IAS. There are some redundant
+items, the 5-point scale does not provide great variability, and the
+structure could be improved. Therefore, improving the IAS, or creating a
+new questionnaire investigating interoception could be useful to
+achieving reliable and accurate indication of interoceptive awareness.
+
+\section{Conclusion}\label{conclusion}
 
@@
 
-\subsection{References}\label{references}
+\section{References}\label{references}
 
@@
 \begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-angold1995development}
+Angold, A., Costello, E. J., Messer, S. C., \& Pickles, A. (1995).
+Development of a short questionnaire for use in epidemiological studies
+of depression in children and adolescents. \emph{International Journal
+of Methods in Psychiatric Research}.
+
 \bibitem[\citeproctext]{ref-arslanova2022}
@@
 inventory--II. \emph{Psychological Assessment}.
-
-\bibitem[\citeproctext]{ref-ben2020effectsize}
-Ben-Shachar, M. S., Lüdecke, D., \& Makowski, D. (2020). Effectsize:
-Estimation of effect size indices and standardized parameters.
-\emph{Journal of Open Source Software}, \emph{5}(56), 2815.
 
@@
 
-\bibitem[\citeproctext]{ref-christensen2021}
-Christensen, A. P., \& Golino, H. (2021). Estimating the Stability of
-Psychological Dimensions via Bootstrap Exploratory Graph Analysis: A
-Monte Carlo Simulation and Tutorial. \emph{Psych}, \emph{3}(3),
-479--500. \url{https://doi.org/10.3390/psych3030032}
-
-\bibitem[\citeproctext]{ref-clifton2020}
-Clifton, J. D. W. (2020). Testing if primal world beliefs reflect
-experiences{\textemdash}or at least some experiences identified ad hoc.
-\emph{Frontiers in Psychology}, \emph{11}.
-\url{https://doi.org/10.3389/fpsyg.2020.01145}
+\bibitem[\citeproctext]{ref-christensen2021estimating}
+Christensen, A. P., \& Golino, H. (2021a). Estimating the stability of
+psychological dimensions via bootstrap exploratory graph analysis: A
+monte carlo simulation and tutorial. \emph{Psych}, \emph{3}(3),
+479--500.
+
+\bibitem[\citeproctext]{ref-christensen2021equivalency}
+Christensen, A. P., \& Golino, H. (2021b). On the equivalency of factor
+and network loadings. \emph{Behavior Research Methods}, \emph{53}(4),
+1563--1580.
+
+\bibitem[\citeproctext]{ref-clifton2019primal}
+Clifton, J. D., Baker, J. D., Park, C. L., Yaden, D. B., Clifton, A. B.,
+Terni, P., Miller, J. L., Zeng, G., Giorgi, S., Schwartz, H. A., et al.
+(2019). Primal world beliefs. \emph{Psychological Assessment},
+\emph{31}(1), 82.
+
+\bibitem[\citeproctext]{ref-clifton2021brief}
+Clifton, J. D., \& Yaden, D. B. (2021). Brief measures of the four
+highest-order primal world beliefs. \emph{Psychological Assessment},
+\emph{33}(12), 1267.
+
+\bibitem[\citeproctext]{ref-cosemans2022exploratory}
+Cosemans, T., Rosseel, Y., \& Gelper, S. (2022). Exploratory graph
+analysis for factor retention: Simulation results for continuous and
+binary data. \emph{Educational and Psychological Measurement},
+\emph{82}(5), 880--910.
+
+\bibitem[\citeproctext]{ref-costa1992neo}
+Costa, P. T., \& McCrae, R. R. (1992). \emph{Revised NEO personality
+inventory (NEO PI-r) and NEO five-factor inventory (NEO-FFI)}.
+Psychological Assessment Resources.
+
+\bibitem[\citeproctext]{ref-davidson2016schizotypal}
+Davidson, C. A., Hoffman, L., \& Spaulding, W. D. (2016). Schizotypal
+personality questionnaire--brief revised (updated): An update of norms,
+factor structure, and item content in a large non-clinical young adult
+sample. \emph{Psychiatry Research}, \emph{238}, 345--355.
 
@@
 \emph{Biological Psychology}, \emph{169}, 108289.
+
+\bibitem[\citeproctext]{ref-Desmedt2023accuracy}
+Desmedt, O., Luminet, O., Walentynowicz, M., \& Corneille, O. (2023).
+The new measures of interoceptive accuracy: A systematic review and
+assessment. \emph{Neuroscience \& Biobehavioral Reviews}, \emph{153},
+105388.
+https://doi.org/\url{https://doi.org/10.1016/j.neubiorev.2023.105388}
 
@@
 
-\bibitem[\citeproctext]{ref-erle2021}
-Erle, T. M., Mitschke, V., \& Schultchen, D. (2021). Did my heart just
-leap or sink? The role of personality for the relation between cardiac
-interoception and well-being. \emph{Personality and Individual
-Differences}, \emph{170}, 110493.
-\url{https://doi.org/10.1016/j.paid.2020.110493}
+\bibitem[\citeproctext]{ref-ferentzi2021examining}
+Ferentzi, E., Olaru, G., Geiger, M., Vig, L., Köteles, F., \& Wilhelm,
+O. (2021). Examining the factor structure and validity of the
+multidimensional assessment of interoceptive awareness. \emph{Journal of
+Personality Assessment}, \emph{103}(5), 675--684.
 
@@
 
+\bibitem[\citeproctext]{ref-garner1991eating}
+Garner, D. M. (1991). Eating disorder inventory-2; pro-fessional manual.
+\emph{Psychological Assessment Resources}.
+
+\bibitem[\citeproctext]{ref-garner1983}
+Garner, D. M., Olmstead, M. P., \& Polivy, J. (1983). Development and
+validation of a multidimensional eating disorder inventory for anorexia
+nervosa and bulimia. \emph{International Journal of Eating Disorders},
+\emph{2}(2), 15--34.
+
 \bibitem[\citeproctext]{ref-golino2017exploratory}
@@
 
-\bibitem[\citeproctext]{ref-herbert2011}
-Herbert, B. M., Herbert, C., \& Pollatos, O. (2011). On the Relationship
-Between Interoceptive Awareness and Alexithymia: Is Interoceptive
-Awareness Related to Emotional Awareness? \emph{Journal of Personality},
-\emph{79}(5), 1149--1175.
-\url{https://doi.org/10.1111/j.1467-6494.2011.00717.x}
+\bibitem[\citeproctext]{ref-golino2020investigating}
+Golino, H., Shi, D., Christensen, A. P., Garrido, L. E., Nieto, M. D.,
+Sadana, R., Thiyagarajan, J. A., \& Martinez-Molina, A. (2020).
+Investigating the performance of exploratory graph analysis and
+traditional techniques to identify the number of latent factors: A
+simulation and tutorial. \emph{Psychological Methods}, \emph{25}(3),
+292.
+
+\bibitem[\citeproctext]{ref-haustein2024interoception}
+Haustein, M., Thomas, E. B., Scheer, K., \& Denburg, N. L. (2024).
+Interoception, affect, and cognition in older adults. \emph{Experimental
+Aging Research}, \emph{50}(3), 279--295.
+
+\bibitem[\citeproctext]{ref-hickman2020relationship}
+Hickman, L., Seyedsalehi, A., Cook, J. L., Bird, G., \& Murphy, J.
+(2020). The relationship between heartbeat counting and heartbeat
+discrimination: A meta-analysis. \emph{Biological Psychology},
+\emph{156}, 107949.
+
+\bibitem[\citeproctext]{ref-hoekstra2011construction}
+Hoekstra, R. A., Vinkhuyzen, A. A., Wheelwright, S., Bartels, M.,
+Boomsma, D. I., Baron-Cohen, S., Posthuma, D., \& Van Der Sluis, S.
+(2011). The construction and validation of an abridged version of the
+autism-spectrum quotient (AQ-short). \emph{Journal of Autism and
+Developmental Disorders}, \emph{41}, 589--596.
 
@@
 \url{https://doi.org/10.1016/j.jebo.2013.12.016}
+
+\bibitem[\citeproctext]{ref-jimenez2023dimensionality}
+Jiménez, M., Abad, F. J., Garcia-Garzon, E., Golino, H., Christensen, A.
+P., \& Garrido, L. E. (2023). Dimensionality assessment in bifactor
+structures with multiple general factors: A network psychometrics
+approach. \emph{Psychological Methods}.
 
@@
 
-\bibitem[\citeproctext]{ref-khalsa2018}
-Khalsa, S. S., Adolphs, R., Cameron, O. G., Critchley, H. D., Davenport,
-P. W., Feinstein, J. S., Feusner, J. D., Garfinkel, S. N., Lane, R. D.,
-Mehling, W. E., Meuret, A. E., Nemeroff, C. B., Oppenheimer, S.,
-Petzschner, F. H., Pollatos, O., Rhudy, J. L., Schramm, L. P., Simmons,
-W. K., Stein, M. B., \ldots{} Zucker, N. (2018). Interoception and
-Mental Health: A Roadmap. \emph{Biological Psychiatry: Cognitive
-Neuroscience and Neuroimaging}, \emph{3}(6), 501--513.
-\url{https://doi.org/10.1016/j.bpsc.2017.12.004}
-
 \bibitem[\citeproctext]{ref-kleckner2015methodological}
@@
 \emph{Medical Care}, \emph{41}(11), 1284--1292.
+
+\bibitem[\citeproctext]{ref-kroenke2009ultra}
+Kroenke, K., Spitzer, R. L., Williams, J. B., \& Löwe, B. (2009). An
+ultra-brief screening scale for anxiety and depression: The PHQ--4.
+\emph{Psychosomatics}, \emph{50}(6), 613--621.
 
@@
 
-\bibitem[\citeproctext]{ref-makowski2023a}
-Makowski, D., Lau, Z. J., Pham, T., Te, A., Kirk, S., \& Liauw Yong
-Tong, C. (2023). \emph{The heart can lie: The role of interoception and
-theory of mind in deception}.
-\url{http://dx.doi.org/10.31234/osf.io/p342w}
+\bibitem[\citeproctext]{ref-ludecke2021performance}
+Lüdecke, D., Ben-Shachar, M. S., Patil, I., Waggoner, P., \& Makowski,
+D. (2021). Performance: An r package for assessment, comparison and
+testing of statistical models. \emph{Journal of Open Source Software},
+\emph{6}(60).
+
+\bibitem[\citeproctext]{ref-makowski2023structure}
+Makowski, D., Pham, T., Lau, Z. J., Raine, A., \& Chen, S. A. (2023).
+The structure of deception: Validation of the lying profile
+questionnaire. \emph{Current Psychology}, \emph{42}(5), 4001--4016.
+
+\bibitem[\citeproctext]{ref-makowski2025measuring}
+Makowski, D., Te, A. S., Neves, A., \& Chen, S. A. (2025). Measuring
+depression and anxiety with 4 items? Adaptation of the PHQ-4 to increase
+its sensitivity to subclinical variability. \emph{Collabra: Psychology},
+\emph{11}(1), 143431.
+
+\bibitem[\citeproctext]{ref-glmTMB}
+McGillycuddy, M., Warton, D. I., Popovic, G., \& Bolker, B. M. (2025).
+Parsimoniously fitting large multivariate random effects in {glmmTMB}.
+\emph{Journal of Statistical Software}, \emph{112}(1), 1--19.
+\url{https://doi.org/10.18637/jss.v112.i01}
 
@@
 
-\bibitem[\citeproctext]{ref-messer1995development}
-Messer, S. C., Angold, A., Costello, E. J., Loeber, R., Van Kammen, W.,
-\& Stouthamer-Loeber, M. (1995). Development of a short questionnaire
-for use in epidemiological studies of depression in children and
-adolescents: Factor composition and structure across development.
-\emph{International Journal of Methods in Psychiatric Research},
-\emph{5}, 251--262.
-
-\bibitem[\citeproctext]{ref-morin2016}
-Morin, A. J. S., Arens, A. K., \& Marsh, H. W. (2015). A bifactor
-exploratory structural equation modeling framework for the
-identification of distinct sources of construct-relevant psychometric
-multidimensionality. \emph{Structural Equation Modeling: A
-Multidisciplinary Journal}, \emph{23}(1), 116--139.
-\url{https://doi.org/10.1080/10705511.2014.961800}
+\bibitem[\citeproctext]{ref-miller1981consciousness}
+Miller, L. C., Murphy, R., \& Buss, A. H. (1981). Consciousness of body:
+Private and public. \emph{Journal of Personality and Social Psychology},
+\emph{41}(2), 397.
 
@@
 
+\bibitem[\citeproctext]{ref-murtagh2014ward}
+Murtagh, F., \& Legendre, P. (2014). Ward's hierarchical agglomerative
+clustering method: Which algorithms implement ward's criterion?
+\emph{Journal of Classification}, \emph{31}(3), 274--295.
+
+\bibitem[\citeproctext]{ref-poerio2024interoceptive}
+Poerio, G. L., Klabunde, M., Bird, G., \& Murphy, J. (2024).
+Interoceptive attention and mood in daily life: An experience-sampling
+study. \emph{Philosophical Transactions of the Royal Society B},
+\emph{379}(1908), 20230256.
+
 \bibitem[\citeproctext]{ref-porges1993body}
@@
 
+\bibitem[\citeproctext]{ref-rammstedt2007measuring}
+Rammstedt, B., \& John, O. P. (2007). Measuring personality in one
+minute or less: A 10-item short version of the big five inventory in
+english and german. \emph{Journal of Research in Personality},
+\emph{41}(1), 203--212.
+
 \bibitem[\citeproctext]{ref-rodriguez2016evaluating}
@@
 
-\bibitem[\citeproctext]{ref-ruisch2022}
-Ruisch, B. C., Von Mohr, M., Naber, M., Tsakiris, M., Fazio, R. H., \&
-Scheepers, D. T. (2022a). Sensitive liberals and unfeeling
-conservatives? {\emph{Interoceptive sensitivity predicts political
-liberalism}}. \emph{Politics and the Life Sciences}, \emph{41}(2),
-256--275. \url{https://doi.org/10.1017/pls.2022.18}
-
-\bibitem[\citeproctext]{ref-ruisch2022a}
-Ruisch, B. C., Von Mohr, M., Naber, M., Tsakiris, M., Fazio, R. H., \&
-Scheepers, D. T. (2022b). Sensitive liberals and unfeeling
-conservatives? {\emph{Interoceptive sensitivity predicts political
-liberalism}}. \emph{Politics and the Life Sciences}, \emph{41}(2),
-256--275. \url{https://doi.org/10.1017/pls.2022.18}
-
 \bibitem[\citeproctext]{ref-schandry1981heart}
@@
 
-\bibitem[\citeproctext]{ref-solanoluxf3pez2018}
-Solano López, A. L., \& Moore, S. (2018). Dimensions of Body-Awareness
-and Depressed Mood and Anxiety. \emph{Western Journal of Nursing
-Research}, \emph{41}(6), 834--853.
-\url{https://doi.org/10.1177/0193945918798374}
+\bibitem[\citeproctext]{ref-shields1989body}
+Shields, S. A., Mallory, M. E., \& Simon, A. (1989). The body awareness
+questionnaire: Reliability and validity. \emph{Journal of Personality
+Assessment}, \emph{53}(4), 802--815.
+
+\bibitem[\citeproctext]{ref-sibley2011mini}
+Sibley, C. G., Luyten, N., Purnomo, M., Mobberley, A., Wootton, L. W.,
+Hammond, M. D., Sengupta, N., Perry, R., West-Newman, T., Wilson, M. S.,
+et al. (2011). The mini-IPIP6: Validation and extension of a short
+measure of the big-six factors of personality in new zealand. \emph{New
+Zealand Journal of Psychology}, \emph{40}(3).
+
+\bibitem[\citeproctext]{ref-simkute2025interoception}
+Simkute, D., Wang, G. Y., \& Griskova-Bulanova, I. (2025).
+Interoception, personality, and internet use: Preliminary insights into
+their association. \emph{PLoS One}, \emph{20}(7), e0328260.
 
@@
 (self-evaluation questionnaire). \emph{(No Title)}.
+
+\bibitem[\citeproctext]{ref-spitzer2006brief}
+Spitzer, R. L., Kroenke, K., Williams, J. B., \& Löwe, B. (2006). A
+brief measure for assessing generalized anxiety disorder: The GAD-7.
+\emph{Archives of Internal Medicine}, \emph{166}(10), 1092--1097.
 
@@
 
-\bibitem[\citeproctext]{ref-torregrossa2022}
-Torregrossa, L. J., Amedy, A., Roig, J., Prada, A., \& Park, S. (2022).
-Interoceptive functioning in schizophrenia and schizotypy.
-\emph{Schizophrenia Research}, \emph{239}, 151--159.
-\url{https://doi.org/10.1016/j.schres.2021.11.046}
-
 \bibitem[\citeproctext]{ref-von2023}

### 2025-08-31 paper/1_Initial/manuscript.qmd
draft of general conclusion

@@
 
-<!-- Aim of the study and previous factor structures -->
+<!-- Aim and previous factor structures -->
+Study 1 aimed to systematically evaluate the structure of the IAS.
+Previous research reported conflicting models, from unidimensional [@brand2023] to bifactor [@campos2021; @lin2023] or two-factor solutions [@murphy2019; @koike2023].
+Concerns about specific items (e.g., low discrimination, local dependencies, and items reflecting phenomena less accessible to interoception) prompted a mega-analytic approach using both factor-analytic and network-based methods.
 
-The first study aimed to provide the most systematic test of the IAS structure to date.
-Previous work has produced conflicting models, ranging from a single general factor [@brand2023], to bifactor solutions [@campos2021; @lin2023], and two-factor models [@murphy2019; @koike2023].
-Alongside these structural discrepancies, several studies have questioned the quality of specific items.
-@murphy2019 distinguished between items tapping direct interoceptive signals (e.g., heartbeat) and others reflecting phenomena less accessible to interoception (e.g., bruising).
-Additionally, @lin2023 identified locally dependent pairs and low-discrimination items with Network-based methods, while @campos2021 found that “tickle” did not load on the general factor.
-To address these open questions, we reanalyzed multiple open-access datasets using a mega-analytic framework, contrasting traditional factor-analytic approaches with network-based methods.
+<!-- Item pairs and optimal structure -->
+Analyses revealed that seven item pairs (e.g., Hunger–Thirst, Urinate–Defecate, Cough–Sneeze) provided a robust and replicable structure, leading to a refined 14-item IAS.
+These pairs consistently emerged across datasets and yielded superior fit indices compared to alternative models.
+This suggests that the IAS does not measure a broad latent construct of interoceptive accuracy but reflects clusters of tightly coupled items tied to specific bodily sensations.
 
-<!-- 7-pairs of items as optimal model -->
-
-Overall, the findings converge on a robust yet novel picture.
-Initial analysis revealed issues in 7 items (e.g., instability, redudancy, low associations, less reliable) which led to the formation of a 14-item IAS.
-Exploratory and confirmatory analyses indicated that the IAS is best characterized by seven pairs of closely related items, consistently identified by EGA and supported by HCA.
-These pairs (e.g., hunger–thirst, urinate–defecate, cough–sneeze) were highly replicable across independent samples and yielded superior fit indices in CFA compared to other solutions.
-Although the one-factor model occasionally achieved lower BIC, Bayes factor comparisons overwhelmingly supported the EGA structure, underlining its empirical robustness.
-
-<!-- IAS not higher-order, but item-level dependencies -->
-
-This pattern has several important implications.
-First, it suggests that the IAS does not capture a broad latent construct of interoceptive accuracy as originally intended, but rather reflects a set of tightly coupled item clusters tied to specific bodily sensations.
-In other words, the IAS may function more as a checklist of bodily signal detection items than as a scale measuring a coherent higher-order dimension.
-This stands in contrast to the original two-factor proposal [@murphy2019], where the factors were highly correlated and collapsed into a unidimensional score, and helps explain why subsequent studies diverged in their conclusions: the psychometric structure of the IAS appears to be driven more by local dependencies than by robust latent factors.
-Second, the presence of redundant or unstable items (e.g., tickle, taste, affective touch), already highlighted in prior validation studies [@campos2021; @lin2023], undermines the interpretability of the scale, as their contributions appear inconsistent or overlapping.
-Together, these findings help explain why previous research has struggled to converge on a stable factor structure: the IAS lacks the psychometric properties required for strong latent modeling and may overstate its dimensionality by conflating redundancy with structure.
-
-<!-- Improvements for the scale + proposal of a new scale-->
-
-At the same time, the results do not render the IAS unusable.
-The consistent emergence of item pairs highlights intuitive bodily domains (e.g., visceral, expulsion, musculoskeletal) that align with everyday interoceptive experiences, supporting its ecological validity.
-However, the limited breadth of these pairings, the redundancy across items, and the reliance on a narrow 5-point scale all restrict the scale’s ability to differentiate between individuals and to capture the multidimensional nature of interoception [@desmedt2022measures].
-These findings therefore call for refinement, either through targeted revisions of the IAS (e.g., removing redundant items, addition of context-specific items, adopting analogue response formats) or through the development of a new questionnaire that better balances theoretical coherence with empirical validity.
+<!-- Implications for scale interpretation -->
+The presence of redundant or unstable items (e.g., Tickle, Taste, Affective Touch) undermines interpretability and likely explains inconsistencies in prior factor-analytic findings [@campos2021; @lin2023].
+Nevertheless, the structured item pairs correspond to intuitive bodily domains—visceral, expulsion, musculoskeletal—supporting ecological validity.
+These findings highlight the need for targeted scale refinement and motivate future development of context-sensitive, multidimensional interoception measures.
 
 <!-- Summary -->
-
-In sum, Study 1 demonstrates that the IAS structure is best described by clusters of tightly coupled item pairs reflecting local dependencies, rather than by a broad latent dimension.
-While this solution is replicable and statistically robust, it highlights the conceptual and psychometric limitations of the IAS in its current form.
-These insights help contextualize the mixed findings on the scale’s validity and provide a crucial foundation for Study 2, where we  do the dispositional correlates of the IAS to further evaluate its construct validity and situate it within the broader network of interoceptive and psychological traits.
+Study 1 establishes that once probelamtic items are removed the IAS is best conceptualized as a set of item clusters rather than a unidimensional scale.
+This structural insight provides the foundation for Study 2, where dispositional correlates are examined to further evaluate the IAS’s construct validity.
 
@@
 
-<!-- Aims recap -->
-The second study set out to provide a comprehensive overview of the dispositional correlates of the IAS by pooling data across multiple datasets, while also testing whether the refined 14-item version identified in Study 1 confers practical advantages over the original 21-item scale.
+<!-- Aim and conceptual focus -->
+Study 2 examined the dispositional correlates of the IAS and tested whether the refined 14-item version offers practical advantages over the original 21-item scale.
+The study provides insight into the conceptual boundaries of interoceptive self-reported accuracy across psychological domains.
 
-<!-- Convergence with interoceptive self-reports -->
-Consistent with prior research, the IAS showed strong positive associations with other interoceptive self-report measures, particularly the MAIA, with the exception of the Not Distracting and Not Worrying facets [@brand2023].
-This pattern replicates earlier findings while contradicting [@todd2022], who reported only a near-zero correlation with Not Worrying.
-Similarly, while previous evidence on the BPQ was mixed, our results indicate more robust associations with the Autonomic Reactivity dimension compared to body awareness [@campos2021; @brand2023; @todd2022].
-This pattern diverges from earlier findings that consistently reported significant positive associations with Body Awareness [@gaggero2021; @campos2021; @brand2023], while at the same time complementing reports of significant negative correlations with Autonomic Reactivity  [@gaggero2021].
-The replication of negative associations with interoceptive confusion [@murphy2019; @brand2023; @gaggero2021] further supports the convergent and discriminant validity of the IAS.
+<!-- Interoception and mental health + context dependency -->
+The IAS converged robustly with other interoceptive self-report measures, particularly facets of the MAIA, and correlated more strongly with dynamic bodily monitoring (Autonomic Reactivity on the BPQ) than general body awareness [@brand2023; @campos2021; @todd2022].
+Item pairings reflecting visceral sensations, such as Hunger–Thirst, were consistently linked to lower depressive and anxiety symptoms [@brand2023; @lin2023], supporting theoretical models connecting interoception to emotion regulation and monitoring of internal bodily states [@khalsa2018interoception; @suksasilp2022towards].
 
-<!-- Negative associations with alexithymia and mood -->
-Robust negative correlations were observed between the IAS and alexithymia, in line with prior studies [@murphy2019; @campos2021; @brand2023; @lin2023; @koike2023].
-Similarly, negative associations with depression and anxiety, as measured by the BDI and STAI-T, reinforce the clinical relevance of interoceptive accuracy [@brand2023; @lin2023].
-Somatic symptoms were also negatively related to the IAS, although effect sizes were small, echoing earlier findings [@brand2023; @lin2023; @koike2023].
-At the same time, more recent studies have reported null or inconsistent associations between interoceptive sensitivity and mental-health symptomatology, suggesting that such links may not generalize across all interoceptive domains and could be contingent on measurement approaches or sample characteristics [**REF PRE_PRINT?**].
+At the same time, these associations were context-dependent: not all item pairings or bodily domains related equally to mood or somatic symptoms [@murphy2019; @koike2023].
+Emerging evidence suggests that interoceptive abilities (e.g., sensitivity, precision and metacognitive insight) may not uniformly predict mental health outcomes and may depend on measurement approach or sample characteristics [**REF PRE_PRINT?**].
 
-<!-- Autism-related traits -->
-Clear negative associations also emerged with autism-related traits such as imagination, low attentional switching, and reduced social skills.
-These findings resonate with @dubois2016 review reporting interoceptive abnormalities in autism.
-Nonetheless, our findings are limited to a single dataset employing the ASQ, which constrains the generalisability of conclusions regarding the relationship between interoception and autistic traits.
+<!-- Personality, worldview, and boundaries of interoception -->
+Associations with broader personality traits and high-order beliefs were modest.
+Small positive correlations with Openness and Agreeableness and weak associations with primal world beliefs (e.g., perceiving the world as alive or comprehensible) suggest that interoception may subtly interact with higher-level cognitive frameworks [@simkute2025interoception; @haustein2024interoception; @gabriele2022dissociations].
+However, the effects were weak and inconsistent, reinforcing that interoception primarily aligns with bodily self-perception rather than broad personality or worldview constructs.
 
-<!-- Personality dimensions -->
-The associations between interoception and personality traits were more nuanced.
-Whereas prior work suggested a negative link with neuroticism [@brand2023], we found this relationship to be inconsistent and even slightly positive, though near zero.
-By contrast, openness and agreeableness were consistently positively associated with the IAS, albeit with small effect sizes.
-These findings are consistent with emerging evidence linking openness to interoception as measured by the MAIA-2 [@simkute2025interoception], and complement reports of associations between interoceptive sensitivity (i.e., the accuracy of reported heartbeat counts relative to actual heartbeats) and extraversion [@haustein2024interoception].
-Personality effects more broadly were modest in size, and as such, warrant replication before firm conclusions can be drawn.
-In contrast, maladaptive personality dimensions and schizotypal traits showed only weak and inconsistent associations with the IAS, indicating that interoceptive accuracy may not play a central role in these domains.
+<!-- Contextual sensitivity and scale refinement -->
+Certain item pairings (e.g., Hunger–Thirst, Bruise–Blood sugar) captured associations with mood and interoception as strongly as, or stronger than, the full 21-item scale.
+This highlights the contextual nature of interoceptive accuracy: interoceptive tendencies manifest variably across bodily domains [@desmedt2022measures; @khalsa2018], emphasizing the need for context-specific items.
 
-<!-- Exploratory findings -->
-Beyond established correlates, exploratory analyses revealed weak but positive associations between the IAS and primal world beliefs, specifically perceiving the world as alive and understandable.
-The inclusion of primal world beliefs was exploratory, motivated by their potential theoretical link to embodied cognition and meaning-making processes.
-Although effect sizes were small, the emergence of consistent associations with perceiving the world as alive and understandable suggests an intriguing avenue for future work at the intersection of interoception and worldview formation.
+The refined 14-item IAS performed comparably to the original scale, and item pairings sometimes provided greater sensitivity to specific interoceptive or affective domains, demonstrating that structural refinement can enhance efficiency and interpretability without sacrificing validity.
 
-<!-- Comparison of 14-item vs. 21-item IAS -->
-A central aim of Study 2 was to assess whether the refined 14-item IAS identified in Study 1 provides practical benefits over the original 21-item scale.
-While the full version most often emerged as the strongest correlate, the refined 14-item IAS performed largely comparably across dispositional measures.
-Importantly, specific item pairings — particularly Hungry/Thirsty and Bruise/Blood sugar — frequently captured associations as strong as, or occasionally stronger than, the full scale.
-This suggests that beyond efficiency, the refined IAS may offer more fine-grained sensitivity to certain dispositional domains, highlighting that interoceptive self-report is not unidimensional but may be differentially expressed across bodily contexts.
-
-<!-- Summary + need for contextual dimensions-->
-Overall, these findings provide converging evidence for the construct validity of the IAS, most strongly in relation to interoceptive self-report, alexithymia, mood, and autism-related traits.
-Other associations, particularly with personality and belief systems, were weaker and more exploratory, highlighting both the breadth and the limits of interoceptive accuracy as captured by the IAS.
-Taken together, Study 2 advances our understanding of the dispositional landscape of interoception.
-The findings provide strong support for the construct validity of the IAS, while also demonstrating that the refined version can capture comparable patterns of association.
-Moreover, the sensitivity of specific item pairings points to the possibility that different bodily contexts (e.g., hunger vs.
-pain) may differentially align with psychological traits, suggesting a promising direction for future research on the contextual dimensions of interoceptive accuracy.
+<!-- Summary -->
+Study 2 shows that interoceptive self-report is adaptive, context-sensitive, and most predictive in relation to mood and dynamic bodily monitoring.
+The refined IAS preserves construct validity while enabling more targeted assessment of domain-specific interoceptive tendencies.
 
@@
 
-**The present study aimed... [always start with a description of the study]**.
+<!-- AIms -->
+The present study aimed to provide a comphrensive evaluation of the IAS, spanning both its structure (study 1) and its dispositional correlates (study 2).
+Together, these studies offer novel insights into the psychometric characteristics, conceptual interpretation, and practical applications of the IAS within the broader landscape of interoception research.
 
-<!-- factor structure -->
+<!-- Item Structure, Redundancy, and Scale Refinement -->
 
-Our analyses revealed that the IAS follows a four-factor structure with an uneven distribution. 
-While the findings indicate that the IAS measures interoception adequately, there is room for improvement. 
-Additionally, different correlation measures with the IAS suggest opportunities for further exploration of how interoception is assessed.
-In the following section, we discuss the strengths and shortcomings of the IAS, followed by proposed steps to enhance interoception measurement.
+Study 1 demonstrated that the IAS is best conceptualized as clusters of tightly coupled item pairs, reflecting discrete bodily domains such as visceral sensations, musculoskeletal cues, and expulsion phenomena.
+Several items (e.g., Tickle, Taste, Affective Touch) were unstable, redundant, or poorly associated with broader interoceptive tendencies, justifying their removal.
+The resulting 14-item refined IAS retained the psychometric integrity of the original scale while improving interpretability and efficiency.
+Crucially, the item clusters reveal that the IAS does not capture a unitary construct of interoception.
+Instead, interoceptive self-report appears domain-specific, with meaningful differences across bodily modalities.
+This challenges the assumption of unidimensionality [@murphy2019; @lin2023] and resonates with theoretical perspectives that describe interoception as a multimodal, context-sensitive process rather than a singular capacity [@khalsa2018interoception].
 
-<!-- redundancy of tickle and other items -->
+<!-- Context-Specific Sensitivity of Interoception -->
 
-Overall, the IAS is straightforward in its sensation-centered items.
-However, several areas for improvement emerge from this study. Firstly, redundant items should be removed, such as the "itch" item, as highlighted in our analysis. 
-Previous research also suggests redundancy between itch and tickle items [@lin2023, @campos2021]. 
-Interestingly, while @campos2021 does not recommend the removal of either, @lin2023 argues for removing the itch item due to their overlapping character representation.
+Study 2 reinforced this domain-specific view.
+Certain item pairings, particularly Hunger–Thirst and Bruise–Blood sugar, consistently predicted mood and interoceptive outcomes as well as, or better than, the full scale.
+These findings indicate that interoceptive self-report is most informative when tied to ecologically meaningful bodily signals, echoing prior suggestions that physiological context are important in the measurement of interoception[@vlemincx2023novel].
+At the same time, other pairings (e.g., cough–sneeze, wind–burp) provided little predictive value.
+Taken together with Study 1, this suggests that the strength of interoceptive reporting lies not in broad aggregation but in the careful targeting of specific bodily domains.
 
-<!-- benefit of analog scales -->
+<!-- Correlates Across Psychological Domains -->
 
-Furthermore, this study recommends using analog scales instead of 5-point scales. 
-The limited variability of the 5-point scale often results in most responses clustering around 3 or 4. 
-As shown in @fig-distributions, adopting an analog scale significantly increases variability. However, even with an analog scale, IAS variability remains constrained. 
-Greater variability allows for better differentiation among participants, making dispersion an essential factor for obtaining meaningful results. 
-Enhancing variability would therefore be beneficial for the IAS.
+The dispositional correlates of the IAS provide important conceptual boundaries for the construct.
+Interoceptive accuracy, as assessed by the IAS, was robustly associated with mood-related outcomes, particularly depression and anxiety, underscoring its relevance for affective regulation and bodily state monitoring [@brand2023; @lin2023].
+In contrast, associations with personality traits and higher-order beliefs were modest: small positive correlations emerged with Openness and Agreeableness, and weak associations with primal world beliefs.
+Consistent with recent work linking interoceptive self-report to personality dispositions [@simkute2025interoception; @haustein2024interoception], these results suggest that interoceptive accuracy primarily operates at the level of bodily self-perception, exerting modest influence on broader dispositional tendencies.
 
-<!-- Underrepresentation of modalities -->
+At the same time, recent studies have reported null or inconsistent associations between interoceptive abilities and mental health symptomatology, suggesting that such links may not generalize across all interoceptive domains or measurement approaches [**ref pre-print?**].
+A potential key reason for these discrepancies is the lack of a consistent theoretical framework for interoception, as dimensions are neither defined nor captured equally across questionnaires and experimental tasks [@Desmedt2023accuracy].
 
-Despite these improvements, certain limitations persist in the IAS that affect its accuracy. 
-Notably, some modalities are underrepresented—for instance, heart perception is measured by only one item. 
-Expanding modality coverage would enhance variability within each category, leading to more nuanced results. 
-Moreover, the IAS lacks a clear theoretical or empirical structure, with only small item groupings. 
-Ideally, a scale should allow for clear groupings that support meaningful data analysis. 
-In this study, each group contained only two items, resulting in low scores and limited variability. 
-Additionally, some IAS items are ambiguous, with their interpretation depending on context. 
-For example, an item about perceiving heartbeats and another about vomiting could both relate to anxiety, leading to results that may differ from initial expectations. 
-Thus, the grouping and structure of the IAS require refinement.
+<!-- IAS limitations and potential improvements -->
 
-<!-- positve response bias from only positive worded items -->
+The structural and correlational findings converge to highlight both limitations of the IAS and opportunities for scale refinement.
+Although the 14-item refined version improves interpretability and efficiency, the scale continues to underrepresent key interoceptive modalities such as cardiac, respiratory, and nuanced somatosensory signals (i.e., only one item each), reducing variability and potentially obscuring meaningful individual differences.
+Nevertheless, analogue-style items and item pairings offer clear advantages: they capture greater response variability, allow more precise differentiation among individuals, and provide efficient, domain-specific indicators that often outperform global scores in predictive value.
+Building on these insights, a next-generation interoception scale could balance breadth (multiple items per modality) with depth (domain-specific subscales), retain the benefits of analogue or wider rating ranges (e.g., 1–7 instead of 1–5), and optimize coverage across physiologically and psychologically relevant bodily domains.
+Such a scale would improve the interpretability, sensitivity, and practical utility of interoceptive self-report measures, ultimately allowing for a more nuanced mapping of interoceptive abilities to affective, cognitive, and health-related outcomes.
 
-Another concern is that all IAS items are phrased positively, which may influence participant responses. 
-While positive phrasing has advantages, it can also introduce response bias, leading to unidimensional results.
-A more balanced phrasing approach, incorporating both positively and negatively framed items, could yield more accurate responses.
+<!-- Conclusion -->
 
-<!-- suggestion for more context-specific -->
-
-Given these considerations, it is clear that context-specific, cross-modal items—such as integrating cardioception and respiroception—are needed. 
-Recognizing the necessity for a refined interoception scale, this study proposes the development of the Multidimensional Interoceptive Inventory (MInt). 
-This new scale will be designed to align with recent findings on the IAS and interoception research while allowing for direct comparison with IAS correlates.
-
-\[**TO DO**: add - previous work suggests the importance of physiological contexts (Vlemincx et al., 2021)\] **I would rather put that in the discussion in the suggestions for better scales**
-
-<!-- IAS  sF -->
-This suggests that the 14-item IAS constitutes a more efficient tool without substantial loss of predictive power.
-In practice, the refined scale offers advantages for researchers and clinicians alike: it reduces participant burden, avoids problematic items flagged in Study 1 (e.g., “tickle,” “taste,” “vomit”), and provides a more coherent representation of interoceptive domains.
-
-# Limitations and Future Directions
-
-<!-- pooor arguments --> 
-There are several limitations to the IAS. There are some redundant items, the 5-point scale does not provide great variability, and the structure could be improved.
-Therefore, improving the IAS, or creating a new questionnaire investigating interoception could be useful to achieving reliable and accurate indication of interoceptive awareness.
-
-# Conclusion
-
-The IAS is a valuable tool for measuring interoception compared to existing questionnaires and methods. 
-However, refining or even redesigning the questionnaire could lead to a more precise and comprehensive assessment. 
-This study highlights the need for a new interoception scale to advance research in the field.
-By identifying various correlates of the IAS, this work paves the way for future investigations into optimal interoceptive measures, ultimately laying the foundation for the development of a more effective interoception survey.
+Taken together, these studies advance understanding of the IAS and interoceptive self-report more broadly.
+The refined 14-item IAS provides a more efficient and interpretable measure, capturing domain-specific interoceptive signals that are differentially associated with psychological outcomes.
+Consistent associations with mood, alongside modest links to personality and beliefs, indicate that the IAS reflects adaptive, context-sensitive aspects of bodily self-perception rather than broad dispositional traits.
+At the same time, current findings highlight limitations in modality coverage and item specificity, suggesting that future scale development should incorporate multimodal, context-sensitive, and continuous analogue ratings or wider discrete scales, to better capture the richness of interoceptive processes and clarify their role in affective, cognitive, and health-related outcomes [@desmedt2022measures; @vlemincx2021].
 

### 2025-09-24 paper/1_Initial/manuscript.qmd
fixed some typos

@@
 <!-- Summary -->
-Study 1 establishes that once probelamtic items are removed the IAS is best conceptualized as a set of item clusters rather than a unidimensional scale.
+Study 1 establishes that once probeleamtic items are removed the IAS is best conceptualized as a set of item clusters rather than a unidimensional scale.
 This structural insight provides the foundation for Study 2, where dispositional correlates are examined to further evaluate the IAS’s construct validity.
-
 # Study 2
@@
 <!-- AIms -->
-The present study aimed to provide a comphrensive evaluation of the IAS, spanning both its structure (study 1) and its dispositional correlates (study 2).
+The present study aimed to provide a comprehensive evaluation of the IAS, spanning both its structure (study 1) and its dispositional correlates (study 2).
 Together, these studies offer novel insights into the psychometric characteristics, conceptual interpretation, and practical applications of the IAS within the broader landscape of interoception research.
@@
 Certain item pairings, particularly Hunger–Thirst and Bruise–Blood sugar, consistently predicted mood and interoceptive outcomes as well as, or better than, the full scale.
-These findings indicate that interoceptive self-report is most informative when tied to ecologically meaningful bodily signals, echoing prior suggestions that physiological context are important in the measurement of interoception[@vlemincx2023novel].
+These findings indicate that interoceptive self-report is most informative when tied to ecologically meaningful bodily signals, echoing prior suggestions that physiological context are important in the measurement of interoception [@vlemincx2023novel].
 At the same time, other pairings (e.g., cough–sneeze, wind–burp) provided little predictive value.
@@
 Consistent associations with mood, alongside modest links to personality and beliefs, indicate that the IAS reflects adaptive, context-sensitive aspects of bodily self-perception rather than broad dispositional traits.
-At the same time, current findings highlight limitations in modality coverage and item specificity, suggesting that future scale development should incorporate multimodal, context-sensitive, and continuous analogue ratings or wider discrete scales, to better capture the richness of interoceptive processes and clarify their role in affective, cognitive, and health-related outcomes [@desmedt2022measures; @vlemincx2021].
+At the same time, current findings highlight limitations in modality coverage and item specificity, suggesting that future scale development should incorporate multimodal, context-sensitive, and continuous analogue ratings or wider discrete scales, to better capture the richness of interoceptive processes and clarify their role in affective, cognitive, and health-related outcomes [@desmedt2022measures; @vlemincx2023novel].
 

### 2025-09-24 analysis/Study1.qmd
calculated the other primals

@@
   mutate(
-    PI_Alive = (PI18_GA_2 + PI18_GA_14 + (1-PI18_A_12_R) + PI18_A_16 + PI18_A_4)/5)
+    PI_Alive = (PI18_GA_2 + PI18_GA_14 + (1-PI18_A_12_R) + PI18_A_16 + PI18_A_4)/5, 
+    PI_Good = ((1-PI18_GE_5_R) + (1-PI18_GS_13_R) + PI18_GA_14 + PI18_GE_8 + PI18_GA_2 + PI18_GE_1 + (1-PI18_GE_9_R) + (1-PI18_GS_10_R) + (1-PI18_GE_6_R) + PI18_GS_15 + PI18_GS_17 + (1-PI18_GS_11_R) + PI18_GS_3 + PI18_GE_18 +  PI18_GE_7)/ 15,
+    PI_Safe = ((1-PI18_GS_13_R) + (1-PI18_GS_10_R) + PI18_GS_15 + PI18_GS_17 + (1-PI18_GS_11_R) + PI18_GS_3)/ 6,
+    PI_Enticing = ((1-PI18_GE_5_R) + PI18_GE_8 + PI18_GE_1 +(1-PI18_GE_9_R) + (1-PI18_GE_6_R) + PI18_GE_18 + PI18_GE_7)/7)
 

### 2025-09-24 analysis/study2.qmd
added all primals to the correlates
@DominiqueMakowski I don't really have a strong theoretical backing for the inclusion of only a few primals so I am looking at all and then write the discussion based on that

@@
   pool_coef(with = "PI_Safe", component="World Beliefs", name = "Safe",unequalrange=TRUE),
-  pool_coef(with = "PI_Understandable", component="World Beliefs", name = "Understandable",unequalrange=TRUE)
+  pool_coef(with = "PI_Understandable", component="World Beliefs", name = "Understandable",unequalrange=TRUE),
+
+  pool_coef(with = "PI_AboutMe", component="World Beliefs", name = "About me",unequalrange=TRUE),
+  pool_coef(with = "PI_Abundant", component="World Beliefs", name = "Abundant",unequalrange=TRUE),
+  pool_coef(with = "PI_Acceptable", component="World Beliefs", name = "Acceptable",unequalrange=TRUE),
+  pool_coef(with = "PI_Beautiful", component="World Beliefs", name = "Beautiful",unequalrange=TRUE),
+  pool_coef(with = "PI_Cooperative", component="World Beliefs", name = "Cooperative",unequalrange=TRUE),
+  pool_coef(with = "PI_Funny", component="World Beliefs", name = "Funny",unequalrange=TRUE),
+  pool_coef(with = "PI_Harmless", component="World Beliefs", name = "Harmless",unequalrange=TRUE),
+  pool_coef(with = "PI_Improvable", component="World Beliefs", name = "Improvable",unequalrange=TRUE),
+  pool_coef(with = "PI_Interconnected", component="World Beliefs", name = "Interconnected",unequalrange=TRUE),
+  pool_coef(with = "PI_Interesting", component="World Beliefs", name = "Interesting",unequalrange=TRUE),
+  pool_coef(with = "PI_Just", component="World Beliefs", name = "Just",unequalrange=TRUE),
+  pool_coef(with = "PI_Meaningful", component="World Beliefs", name = "Meaningful",unequalrange=TRUE),
+  pool_coef(with = "PI_NeedsMe", component="World Beliefs", name = "Needs Me",unequalrange=TRUE),
+  pool_coef(with = "PI_Pleasurable", component="World Beliefs", name = "Pleasurable",unequalrange=TRUE),
+  pool_coef(with = "PI_Progressing", component="World Beliefs", name = "Progressing",unequalrange=TRUE),
+  pool_coef(with = "PI_Regenerative", component="World Beliefs", name = "Regenerative",unequalrange=TRUE),
+  pool_coef(with = "PI_Stable", component="World Beliefs", name = "Stable",unequalrange=TRUE),
+  pool_coef(with = "PI_WorthExploring", component="World Beliefs", name = "WorthExploring",unequalrange=TRUE),
+  pool_coef(with = "PI_Intentional", component="World Beliefs", name = "Intentional", unequalrange=TRUE),
   )

### 2025-09-24 analysis/study2.qmd
minor

--- 2025-08-29 analysis/study2.qmd
@@
   pool_coef(with = "PI_Safe", component="World Beliefs", name = "Safe",unequalrange=TRUE),
-  pool_coef(with = "PI_Understandable", component="World Beliefs", name = "Understandable",unequalrange=TRUE)
+  pool_coef(with = "PI_Understandable", component="World Beliefs", name = "Understandable",unequalrange=TRUE),
+
+  pool_coef(with = "PI_AboutMe", component="World Beliefs", name = "About me",unequalrange=TRUE),
+  pool_coef(with = "PI_Abundant", component="World Beliefs", name = "Abundant",unequalrange=TRUE),
+  pool_coef(with = "PI_Acceptable", component="World Beliefs", name = "Acceptable",unequalrange=TRUE),
+  pool_coef(with = "PI_Beautiful", component="World Beliefs", name = "Beautiful",unequalrange=TRUE),
+  pool_coef(with = "PI_Cooperative", component="World Beliefs", name = "Cooperative",unequalrange=TRUE),
+  pool_coef(with = "PI_Funny", component="World Beliefs", name = "Funny",unequalrange=TRUE),
+  pool_coef(with = "PI_Harmless", component="World Beliefs", name = "Harmless",unequalrange=TRUE),
+  pool_coef(with = "PI_Improvable", component="World Beliefs", name = "Improvable",unequalrange=TRUE),
+  pool_coef(with = "PI_Interconnected", component="World Beliefs", name = "Interconnected",unequalrange=TRUE),
+  pool_coef(with = "PI_Interesting", component="World Beliefs", name = "Interesting",unequalrange=TRUE),
+  pool_coef(with = "PI_Just", component="World Beliefs", name = "Just",unequalrange=TRUE),
+  pool_coef(with = "PI_Meaningful", component="World Beliefs", name = "Meaningful",unequalrange=TRUE),
+  pool_coef(with = "PI_NeedsMe", component="World Beliefs", name = "Needs Me",unequalrange=TRUE),
+  pool_coef(with = "PI_Pleasurable", component="World Beliefs", name = "Pleasurable",unequalrange=TRUE),
+  pool_coef(with = "PI_Progressing", component="World Beliefs", name = "Progressing",unequalrange=TRUE),
+  pool_coef(with = "PI_Regenerative", component="World Beliefs", name = "Regenerative",unequalrange=TRUE),
+  pool_coef(with = "PI_Stable", component="World Beliefs", name = "Stable",unequalrange=TRUE),
+  pool_coef(with = "PI_WorthExploring", component="World Beliefs", name = "WorthExploring",unequalrange=TRUE),
+  pool_coef(with = "PI_Intentional", component="World Beliefs", name = "Intentional", unequalrange=TRUE)
   )

### 2025-09-29 analysis/study2.qmd
minor changes to study 2

--- 2025-08-29 analysis/study2.qmd
@@
   pool_coef(with = "PI_Safe", component="World Beliefs", name = "Safe",unequalrange=TRUE),
-  pool_coef(with = "PI_Understandable", component="World Beliefs", name = "Understandable",unequalrange=TRUE)
+  pool_coef(with = "PI_Understandable", component="World Beliefs", name = "Understandable",unequalrange=TRUE),
+
+  pool_coef(with = "PI_AboutMe", component="World Beliefs", name = "About me",unequalrange=TRUE),
+  pool_coef(with = "PI_Abundant", component="World Beliefs", name = "Abundant",unequalrange=TRUE),
+  pool_coef(with = "PI_Acceptable", component="World Beliefs", name = "Acceptable",unequalrange=TRUE),
+  pool_coef(with = "PI_Beautiful", component="World Beliefs", name = "Beautiful",unequalrange=TRUE),
+  pool_coef(with = "PI_Cooperative", component="World Beliefs", name = "Cooperative",unequalrange=TRUE),
+  pool_coef(with = "PI_Funny", component="World Beliefs", name = "Funny",unequalrange=TRUE),
+  pool_coef(with = "PI_Harmless", component="World Beliefs", name = "Harmless",unequalrange=TRUE),
+  pool_coef(with = "PI_Improvable", component="World Beliefs", name = "Improvable",unequalrange=TRUE),
+  pool_coef(with = "PI_Interconnected", component="World Beliefs", name = "Interconnected",unequalrange=TRUE),
+  pool_coef(with = "PI_Interesting", component="World Beliefs", name = "Interesting",unequalrange=TRUE),
+  pool_coef(with = "PI_Just", component="World Beliefs", name = "Just",unequalrange=TRUE),
+  pool_coef(with = "PI_Meaningful", component="World Beliefs", name = "Meaningful",unequalrange=TRUE),
+  pool_coef(with = "PI_NeedsMe", component="World Beliefs", name = "Needs Me",unequalrange=TRUE),
+  pool_coef(with = "PI_Pleasurable", component="World Beliefs", name = "Pleasurable",unequalrange=TRUE),
+  pool_coef(with = "PI_Progressing", component="World Beliefs", name = "Progressing",unequalrange=TRUE),
+  pool_coef(with = "PI_Regenerative", component="World Beliefs", name = "Regenerative",unequalrange=TRUE),
+  pool_coef(with = "PI_Stable", component="World Beliefs", name = "Stable",unequalrange=TRUE),
+  pool_coef(with = "PI_WorthExploring", component="World Beliefs", name = "Worth Exploring",unequalrange=TRUE),
+  pool_coef(with = "PI_Intentional", component="World Beliefs", name = "Intentional", unequalrange=TRUE)
   )

### 2025-09-29 analysis/Study1.qmd
Update Study1.qmd
minor

@@
   sample13 = add_empirical(data13, "Sample 13"),
-  sample14 = add_empirical(data14 , "Sample 14 "),
+  sample14 = add_empirical(data14 , "Sample 14"),
   sample15 = add_empirical(data15 , "Sample 15"),

### 2025-10-03 paper/1_Initial/manuscript.qmd
updated to manuscript

@@
 Together, these studies offer novel insights into the psychometric characteristics, conceptual interpretation, and practical applications of the IAS within the broader landscape of interoception research.
+<!-- Study 1 findings -->
+Study 1 demonstrated that the IAS is best conceptualised as clusters of tightly coupled item pairs, reflecting discrete bodily domains such as visceral sensations, musculoskeletal cues, and expulsion phenomena.
+The pairs emerged once several items (e.g., Tickle, Taste, Affective Touch) were removed due to their instability, redundancy or poor associations with the other items.
+The resulting 14-item refined IAS retained the psychometric integrity of the original scale while improving interpretability and efficiency.
 
-<!-- Item Structure, Redundancy, and Scale Refinement -->
+A short version of the IAS has been proposed before.
+@lin2023 suggested a 12-item version by removing items with local dependency, high difficulty, and/or low discrimination.
+Their parallel analysis suggested unidimensionality, although this method is known to underestimate factor numbers in multidimensional data [@markos2024dimensionality;@golino2017exploratory].
+In contrast, our study applied multiple methods, yet the same pairs consistently emerged across datasets and demonstrated superior fit compared to alternative models.This challenges the assumption of unidimensionality [@lin2023; @murphy2019] and resonates with theoretical perspectives that describe interoception as a multimodal, context-sensitive process rather than a singular capacity (@khalsa2018; @vlemincx2023novel].
 
-Study 1 demonstrated that the IAS is best conceptualized as clusters of tightly coupled item pairs, reflecting discrete bodily domains such as visceral sensations, musculoskeletal cues, and expulsion phenomena.
-Several items (e.g., Tickle, Taste, Affective Touch) were unstable, redundant, or poorly associated with broader interoceptive tendencies, justifying their removal.
-The resulting 14-item refined IAS retained the psychometric integrity of the original scale while improving interpretability and efficiency.
-Crucially, the item clusters reveal that the IAS does not capture a unitary construct of interoception.
-Instead, interoceptive self-report appears domain-specific, with meaningful differences across bodily modalities.
-This challenges the assumption of unidimensionality [@murphy2019; @lin2023] and resonates with theoretical perspectives that describe interoception as a multimodal, context-sensitive process rather than a singular capacity [@khalsa2018interoception].
+<!-- Study 2 findings -->
+Study 2 provided further evidence for a domain-specific perspective.
+Certain item pairings, particularly Hunger–Thirst and Bruise–Blood sugar, showed consistent negative correlations with depression and anxiety measures, in some cases approaching or even surpassing the strength of associations observed for the full IAS scale.
+Notably, these were also the only pairs, out of the seven examined, that displayed significant positive correlations with the BPQ Body Awareness, whereas the full IAS scale showed no such association.
+This pattern suggests that specific item pairings may show distinct patterns of association with other interoceptive measures and with mental health indices, whereas the aggregated IAS scale may obscures these relationships.
+This highlights that questionnaires like the IAS may capture multiple facets of interoception rather than a single underlying dimension, and that domain-specific approaches may provide greater construct validity.
 
-<!-- Context-Specific Sensitivity of Interoception -->
+These findings mirror broader inconsistencies in the literature concerning associations between the IAS and the BPQ-A.
+While some studies report significant negative associations [@lin2023], others have observed significant positive associations [@gaggero2021; @todd2022; @brand2022; @campos2021], and still others none at all [@murphy2019].
+In our study the full IAS was not associated with the BPQ-A.
+Interpretation is further complicated by conceptual debates: the BPQ Body Awareness is frequently treated as a measure of interoception, whereas the BPQ Autonomic Reactivity subscale has been criticized as indexing dysfunction in the nervous system rather than interoceptive sensitivity [@gaggero2021].
+Our results lend tentative support to this interpretation, as the full IAS scale and most item pairings showed significant negative associations with the BPQ Autonomic Reactivity, with the exception of the Bruise–Blood sugar pair.
+This pattern is consistent with the idea that this subscale may capture maladaptive bodily experiences or autonomic dysfunction, rather than interoceptive accuracy per se.
+However, the Body Awareness subscale of the BPQ has also been criticized for its ambiguous instructions.
+It is often unclear whether respondents should interpret the items as assessing attentional focus on bodily sensations, perceived accuracy in detecting them, or simply the frequency of experiencing such signals.
+As a result, studies have reported that observed associations vary depending on how the BPQ-A is construed [@campos2021; @gaggero2021; @gabriele2022dissociations].
+As such, it is unclear whether the lack of a relationship between the IAS and the BPQ-A reflects a genuine divergence between the constructs measured by the two scales, or instead arises from ambiguities in how the BPQ-A is operationalized and interpreted across studies.
 
-Study 2 reinforced this domain-specific view.
-Certain item pairings, particularly Hunger–Thirst and Bruise–Blood sugar, consistently predicted mood and interoceptive outcomes as well as, or better than, the full scale.
-These findings indicate that interoceptive self-report is most informative when tied to ecologically meaningful bodily signals, echoing prior suggestions that physiological context are important in the measurement of interoception [@vlemincx2023novel].
-At the same time, other pairings (e.g., cough–sneeze, wind–burp) provided little predictive value.
-Taken together with Study 1, this suggests that the strength of interoceptive reporting lies not in broad aggregation but in the careful targeting of specific bodily domains.
+Taken together with these debates, the discrepancies observed here highlight that some IAS pairings may capture interoceptive self-reported accuracy more effectively than the aggregated measure, raising questions about the interpretability of the full scale.
+By contrast, other pairings (e.g., Cough–Sneeze, Wind–Burp) were weakly or inconsistently related to external variables, raising concerns about their usefulness.
+Together, these findings indicate that the strength and relevance of interoceptive self-reported accuracy may vary systematically across physiological domains.
+At the same time, the interpretation of such associations is complicated by the lack of contextualisation in the items themselves.
+For example, anxiety is often experienced as heart racing (ref), yet similar sensations occur during exercise or heightened arousal more generally.
+Without contextual anchors, it remains unclear which bodily states participants are drawing upon when responding.
+In line with prior work emphasizing the importance of contextual factors in the measurement of interoception [@vlemincx2023novel], our results suggest that the value of self-report lies less in broad aggregation across domains and more in the targeted assessment of physiologically and situationally meaningful contexts.
 
-<!-- Correlates Across Psychological Domains -->
-
+<!-- Correlates of IAS Across Psychological Domains -->
 The dispositional correlates of the IAS provide important conceptual boundaries for the construct.
 Interoceptive accuracy, as assessed by the IAS, was robustly associated with mood-related outcomes, particularly depression and anxiety, underscoring its relevance for affective regulation and bodily state monitoring [@brand2023; @lin2023].
-In contrast, associations with personality traits and higher-order beliefs were modest: small positive correlations emerged with Openness and Agreeableness, and weak associations with primal world beliefs.
-Consistent with recent work linking interoceptive self-report to personality dispositions [@simkute2025interoception; @haustein2024interoception], these results suggest that interoceptive accuracy primarily operates at the level of bodily self-perception, exerting modest influence on broader dispositional tendencies.
+This is in line research consistently revealing the link between conditions, such as depression or anxiety and interoceptive measures.
+For example, divergent findings in subjective and objective measures of interoception have been linked with high anxiety symptomology [@garfinkel2016interoceptive].
+At the same time, recent studies have reported null or inconsistent associations between interoceptive abilities and mental health symptomatology, suggesting that such links may not generalize across all interoceptive domains or measurement approaches [ref pre-print?].
+This further highlights the need to examine interoceptive self-perception at the level of separate domains rather than aggregated scores.
 
-At the same time, recent studies have reported null or inconsistent associations between interoceptive abilities and mental health symptomatology, suggesting that such links may not generalize across all interoceptive domains or measurement approaches [**ref pre-print?**].
-A potential key reason for these discrepancies is the lack of a consistent theoretical framework for interoception, as dimensions are neither defined nor captured equally across questionnaires and experimental tasks [@Desmedt2023accuracy].
+In contrast, associations of IAS scores with personality traits and higher-order beliefs were modest: small positive correlations emerged with Openness and Agreeableness, and weak associations with primal world beliefs.
+Consistent with recent work linking interoceptive self-report to personality dispositions [@haustein2024interoception;@simkute2025interoception], these results suggest that interoceptive accuracy primarily operates at the level of bodily self-perception.
+This contrast reinforces the view that the IAS primarily indexes bodily self-perception, exerting only modest influence on broader dispositional traits.
+A potential key reason for these discrepancies is the lack of a consistent theoretical framework for interoception, as dimensions are neither defined nor captured equally across questionnaires and experimental tasks [@desmedt2022measures].[**complete paragraph**]
 
 <!-- IAS limitations and potential improvements -->
-
-The structural and correlational findings converge to highlight both limitations of the IAS and opportunities for scale refinement.
-Although the 14-item refined version improves interpretability and efficiency, the scale continues to underrepresent key interoceptive modalities such as cardiac, respiratory, and nuanced somatosensory signals (i.e., only one item each), reducing variability and potentially obscuring meaningful individual differences.
+These two studies revealed three main points.
+Firstly, a shortened, 14-item refined IAS retained greater psychometric integrity while removing unstable and/or redundant items.
+Secondly, item pairings combined with analogue-style ratings captured greater variability and allowed more precise differentiation among individuals, often outperforming global scores in predictive value.
+However, even the refined IAS has significant limitations.
+Although the 14-item version improves interpretability and efficiency, the scale continues to underrepresent key interoceptive modalities such as cardiac, respiratory, and nuanced somatosensory signals, limiting its ability to capture the full breadth of interoceptive processes.
+This shortcoming underscores the need for broader coverage in future scale development.
 Nevertheless, analogue-style items and item pairings offer clear advantages: they capture greater response variability, allow more precise differentiation among individuals, and provide efficient, domain-specific indicators that often outperform global scores in predictive value.
@@
 
+<!-- Limitations -->
+One limitation worth noting is that we did not evaluate the IAS alongside other widely used questionnaires, such as the BPQ or MAIA.
+Although both are frequently employed in interoception research, they present important limitations.
+For example, the MAIA-2 contains subscales (e.g., Not-Worrying, Not-Distracting) with weak reliability and minimal relation to a general interoception factor [@ferentzi2021examining; @rogowska2023validation].
+Several other subscales primarily reflect higher-level cognitive tendencies, such as mindfulness and attentional regulation, rather than interoceptive body awareness [@vig2023self; @todd2022].
+Similarly, the BPQ’s Body Awareness and Autonomic Reactivity subscales show conceptual and psychometric concerns, and BPQ scores often overlap substantially with negative affect, raising questions about their specificity as measures of interoceptive sensibility [@campos2021; @gabriele2022dissociations; @vig2023self].
+
+Because the IAS is a newly developed questionnaire and the only one designed to assess interoceptive self-reported accuracy - a dimension previously thought to require objective tasks such as the HDT and HCT - our focus was on evaluating its structure and correlates without introducing established measures with documented shortcomings.
+Nonetheless, future research should employ novel methods, such as Exploratory Graph Analysis, to clarify the convergent and divergent validity of these questionnaires across interoceptive domains.
+
+<!-- Future Outlook in the field -->
+
+Building on these limitations, a next-generation interoception scale should balance breadth (multiple items per modality, including underrepresented domains such as cardiac and respiratory) with depth (domain-specific subscales).
+Retaining analogue or wider rating ranges (e.g., 1–7 instead of 1–5) would further enhance sensitivity and coverage.
+Such a scale would improve the interpretability, sensitivity, and practical utility of interoceptive self-report measures, ultimately allowing for a more nuanced mapping of interoceptive abilities to affective, cognitive, and health-related outcomes.
+
 <!-- Conclusion -->
-
 Taken together, these studies advance understanding of the IAS and interoceptive self-report more broadly.
@@
 Consistent associations with mood, alongside modest links to personality and beliefs, indicate that the IAS reflects adaptive, context-sensitive aspects of bodily self-perception rather than broad dispositional traits.
-At the same time, current findings highlight limitations in modality coverage and item specificity, suggesting that future scale development should incorporate multimodal, context-sensitive, and continuous analogue ratings or wider discrete scales, to better capture the richness of interoceptive processes and clarify their role in affective, cognitive, and health-related outcomes [@desmedt2022measures; @vlemincx2023novel].
+At the same time, current findings highlight limitations in modality coverage and item specificity, suggesting that future scale development should incorporate multimodal, context-sensitive, and continuous analogue ratings or wider discrete scales to better capture the richness of interoceptive processes and clarify their role in affective, cognitive, and health-related outcomes [@desmedt2022measures; @vlemincx2023novel].
+Ultimately, these studies show that the IAS is most informative when treated as a set of domain-specific, context-sensitive indicators rather than as a broad global index, advancing both the measurement and theoretical understanding of interoception.
 

### 2025-10-13 paper/1_Initial/manuscript.qmd
updated manuscript

@@
 The authors however underlined its acceptable but imperfect fit [@murphy2019, p. 127], and several follow-up studies have indeed identified different optimal solutions. 
-For instance, @brand2023 reported a 1-factor solution, while @lin2023 - using Exploratory Graph Analysis [EGA, @golino2017exploratory] - and @campos2021 found bifactor solutions [i.e., one general factor above a set of lower-level factors, @rodriguez2016evaluating] to be the best fit.
+For instance, @brand2023 reported a 1-factor solution, while @lin2023 and @campos2021 found bifactor solutions [i.e., one general factor above a set of lower-level factors, @rodriguez2016evaluating] to be the best fit.
 Using a 2-factors Exploratory Factor Analysis (EFA), @koike2023 suggested that the items could be grouped into cutaneous (itching, tickling, coughing, burping, affective touch, bruising, passing gas, sneezing, muscle sensations, sexual arousal, and taste) and visceral sensations (urination, defecation, hunger, thirst, pain, breathing, fatigue/blood sugar, temperature, vomiting, and heartbeat).
@@
 <!-- EGA -->
-By combining network analysis with psychometric methods, the recently-developed EGA framework allows to jointly estimate the number of dimensions (i.e., groups of items), the structure as well as its stability [@golino2017exploratory; @golino2020investigating].
+By combining network analysis with psychometric methods, the recently-developed Exploratory Graph Analysis [EGA, @golino2017exploratory] framework allows to jointly estimate the number of dimensions (i.e., groups of items), the structure as well as its stability [@golino2017exploratory; @golino2020investigating].
 Evidence has underlined its suitability as an alternative to traditional factor analysis, addressing some of its limitations such as the assumption of a "latent" source of variability, possible biasing in the estimation of the optimal factor numbers depending on sample size, and the poor performance of other methods in complex population structures, while remaining comparable and interpretable [@christensen2021equivalency; @jimenez2023dimensionality].
@@
 Together, these studies offer novel insights into the psychometric characteristics, conceptual interpretation, and practical applications of the IAS within the broader landscape of interoception research.
+
 <!-- Study 1 findings -->
@@
 @lin2023 suggested a 12-item version by removing items with local dependency, high difficulty, and/or low discrimination.
-Their parallel analysis suggested unidimensionality, although this method is known to underestimate factor numbers in multidimensional data [@markos2024dimensionality;@golino2017exploratory].
-In contrast, our study applied multiple methods, yet the same pairs consistently emerged across datasets and demonstrated superior fit compared to alternative models.This challenges the assumption of unidimensionality [@lin2023; @murphy2019] and resonates with theoretical perspectives that describe interoception as a multimodal, context-sensitive process rather than a singular capacity (@khalsa2018; @vlemincx2023novel].
+Their parallel analysis suggested unidimensionality, although this method is known to underestimate factor numbers in multidimensional data [@golino2017exploratory; @markos2024dimensionality].
+In contrast, our study applied multiple methods such as EGA, FA, and HCA yet the same pairs consistently emerged across datasets and demonstrated superior fit compared to alternative models.
+This challenges the assumption of unidimensionality of the IAS [@murphy2019; @brand2023].
+Although the short version of the IAS by @lin2023 preferred a one-factor solution, their 12-item IAS was derived by removing locally dependent items identified through Item Response Theory (IRT).
+In our framework, these locally dependent items are instead interpreted as meaningful pairs (e.g., Heart–Breath), reflecting distinct bodily domains.
+However, because IRT assumes unidimensionality [@nguyen2014introduction], it may have treated these natural item clusters as sources of statistical dependency rather than as theoretically relevant structures within interoceptive accuracy.
 
@@
 Notably, these were also the only pairs, out of the seven examined, that displayed significant positive correlations with the BPQ Body Awareness, whereas the full IAS scale showed no such association.
-This pattern suggests that specific item pairings may show distinct patterns of association with other interoceptive measures and with mental health indices, whereas the aggregated IAS scale may obscures these relationships.
+This pattern suggests that specific item pairings may show distinct patterns of association with other interoceptive measures and with mental health indices, whereas the aggregated IAS scale may obscure these relationships.
 This highlights that questionnaires like the IAS may capture multiple facets of interoception rather than a single underlying dimension, and that domain-specific approaches may provide greater construct validity.
 
-These findings mirror broader inconsistencies in the literature concerning associations between the IAS and the BPQ-A.
-While some studies report significant negative associations [@lin2023], others have observed significant positive associations [@gaggero2021; @todd2022; @brand2022; @campos2021], and still others none at all [@murphy2019].
-In our study the full IAS was not associated with the BPQ-A.
+These findings mirror broader inconsistencies in the literature concerning associations between the IAS and the BPQ Body Awareness.
+While some studies report significant negative associations [@lin2023], others have observed significant positive associations [@brand2023; @campos2021; @gaggero2021; @todd2022], and still others none at all [@murphy2019].
+In our study the full IAS was not associated with the BPQ Body Awareness.
 Interpretation is further complicated by conceptual debates: the BPQ Body Awareness is frequently treated as a measure of interoception, whereas the BPQ Autonomic Reactivity subscale has been criticized as indexing dysfunction in the nervous system rather than interoceptive sensitivity [@gaggero2021].
@@
 It is often unclear whether respondents should interpret the items as assessing attentional focus on bodily sensations, perceived accuracy in detecting them, or simply the frequency of experiencing such signals.
-As a result, studies have reported that observed associations vary depending on how the BPQ-A is construed [@campos2021; @gaggero2021; @gabriele2022dissociations].
-As such, it is unclear whether the lack of a relationship between the IAS and the BPQ-A reflects a genuine divergence between the constructs measured by the two scales, or instead arises from ambiguities in how the BPQ-A is operationalized and interpreted across studies.
+As a result, studies have reported that observed associations vary depending on how the BPQ Body Awareness is constructed [@campos2021; @gabriele2022dissociations; @gaggero2021].
+As such, it is unclear whether the lack of a relationship between the IAS and the BPQ Body Awareness in this study reflects a genuine divergence between the constructs measured by the two scales, or instead arises from ambiguities in how the BPQ Body Awareness is operationalized and interpreted across studies.
 
@@
 Together, these findings indicate that the strength and relevance of interoceptive self-reported accuracy may vary systematically across physiological domains.
-At the same time, the interpretation of such associations is complicated by the lack of contextualisation in the items themselves.
-For example, anxiety is often experienced as heart racing (ref), yet similar sensations occur during exercise or heightened arousal more generally.
+At the same time, the interpretation of such associations is complicated by the lack of contextualisation in the items themselves.For example, a racing heart is often associated with anxiety, yet the same sensation can also arise during exercise or other forms of physiological arousal.
 Without contextual anchors, it remains unclear which bodily states participants are drawing upon when responding.
@@
 <!-- Correlates of IAS Across Psychological Domains -->
-The dispositional correlates of the IAS provide important conceptual boundaries for the construct.
-Interoceptive accuracy, as assessed by the IAS, was robustly associated with mood-related outcomes, particularly depression and anxiety, underscoring its relevance for affective regulation and bodily state monitoring [@brand2023; @lin2023].
-This is in line research consistently revealing the link between conditions, such as depression or anxiety and interoceptive measures.
-For example, divergent findings in subjective and objective measures of interoception have been linked with high anxiety symptomology [@garfinkel2016interoceptive].
-At the same time, recent studies have reported null or inconsistent associations between interoceptive abilities and mental health symptomatology, suggesting that such links may not generalize across all interoceptive domains or measurement approaches [ref pre-print?].
-This further highlights the need to examine interoceptive self-perception at the level of separate domains rather than aggregated scores.
+The dispositional correlates of the IAS help delineate the conceptual boundaries of interoceptive accuracy as a construct.
+Self-reported interoceptive accuracy, as assessed by the IAS, has been robustly associated with mood-related outcomes, particularly depression and anxiety, underscoring its relevance for affective regulation and bodily state monitoring (Benau et al., 2023; Brand et al., 2023).
+This aligns with a broader body of research linking affective conditions such as anxiety and depression with altered interoceptive processing (e.g., Garfinkel et al., 2016).
+However, recent findings have also reported null or inconsistent associations between interoceptive abilities and mental health symptomatology, suggesting that such relationships may not generalize across all interoceptive domains or measurement modalities [@banellis2025interoceptive; @jenkinson2024interoception].
+For instance, a recent review by @jenkinson2024interoception found no consistent evidence linking cardiac interoceptive accuracy tasks with anxiety or depression across multiple meta-analyses.
+Collectively, these findings underscore the importance of examining interoceptive self-perception at the level of distinct bodily domains rather than relying on aggregated or unidimensional measures.
 
 In contrast, associations of IAS scores with personality traits and higher-order beliefs were modest: small positive correlations emerged with Openness and Agreeableness, and weak associations with primal world beliefs.
-Consistent with recent work linking interoceptive self-report to personality dispositions [@haustein2024interoception;@simkute2025interoception], these results suggest that interoceptive accuracy primarily operates at the level of bodily self-perception.
-This contrast reinforces the view that the IAS primarily indexes bodily self-perception, exerting only modest influence on broader dispositional traits.
-A potential key reason for these discrepancies is the lack of a consistent theoretical framework for interoception, as dimensions are neither defined nor captured equally across questionnaires and experimental tasks [@desmedt2022measures].[**complete paragraph**]
+Consistent with recent work linking interoceptive self-report to personality dispositions [@haustein2024interoception; @simkute2025interoception], these results suggest that interoceptive accuracy primarily operates at the level of bodily self-perception.
+This contrast reinforces the view that the IAS primarily indexes bodily self-perception, displaying only modest associations with  broader dispositional traits.
+
+A potential key reason for these discrepancies is the lack of a consistent theoretical framework for interoception, as dimensions are neither defined nor captured equally across questionnaires and experimental tasks [@desmedt2022measures].
+**[complete paragraph]**
 
@@
 For example, the MAIA-2 contains subscales (e.g., Not-Worrying, Not-Distracting) with weak reliability and minimal relation to a general interoception factor [@ferentzi2021examining; @rogowska2023validation].
-Several other subscales primarily reflect higher-level cognitive tendencies, such as mindfulness and attentional regulation, rather than interoceptive body awareness [@vig2023self; @todd2022].
+Several other subscales primarily reflect higher-level cognitive tendencies, such as mindfulness and attentional regulation, rather than interoceptive body awareness [@todd2022; @vig2023self].
 Similarly, the BPQ’s Body Awareness and Autonomic Reactivity subscales show conceptual and psychometric concerns, and BPQ scores often overlap substantially with negative affect, raising questions about their specificity as measures of interoceptive sensibility [@campos2021; @gabriele2022dissociations; @vig2023self].
@@
 <!-- Future Outlook in the field -->
-
 Building on these limitations, a next-generation interoception scale should balance breadth (multiple items per modality, including underrepresented domains such as cardiac and respiratory) with depth (domain-specific subscales).

### 2025-10-17 paper/1_Initial/manuscript.qmd
changes to manuscript

@@
 
-# General Discussion
+# General DiscussionGeneral Discussion
 
@@
 Together, these studies offer novel insights into the psychometric characteristics, conceptual interpretation, and practical applications of the IAS within the broader landscape of interoception research.
+
+<!-- Study 1 findings -->
+Study 1 demonstrated that the IAS is best conceptualised as clusters of tightly coupled item pairs, reflecting discrete bodily domains such as visceral sensations, musculoskeletal cues, and expulsion phenomena.
+The pairs emerged once several items (e.g., Tickle, Taste, Affective Touch) were removed due to their instability, redundancy or poor associations with the other items.
+The resulting 14-item refined IAS retained the psychometric integrity of the original scale while improving interpretability and efficiency.
 
@@
 This challenges the assumption of unidimensionality of the IAS [@murphy2019; @brand2023].
-Although the short version of the IAS by @lin2023 preferred a one-factor solution, their 12-item IAS was derived by removing locally dependent items identified through Item Response Theory (IRT).
+Although the short version of the IAS by  @lin2023 preferred a one-factor solution, their 12-item IAS was derived by removing locally dependent items identified through Item Response Theory.
 In our framework, these locally dependent items are instead interpreted as meaningful pairs (e.g., Heart–Breath), reflecting distinct bodily domains.
@@
 Study 2 provided further evidence for a domain-specific perspective.
-Certain item pairings, particularly Hunger–Thirst and Bruise–Blood sugar, showed consistent negative correlations with depression and anxiety measures, in some cases approaching or even surpassing the strength of associations observed for the full IAS scale.
-Notably, these were also the only pairs, out of the seven examined, that displayed significant positive correlations with the BPQ Body Awareness, whereas the full IAS scale showed no such association.
+Certain item pairings, particularly Hunger–Thirst, Bruise–Blood sugar and Muscles-Pain, showed consistent negative correlations with depression and anxiety measures, in some cases approaching or even surpassing the strength of associations observed for the full IAS scale.
+Notably, Hunger-Thirst and Bruise-Blood sugar were also the only pairs, out of the seven examined, that displayed significant positive correlations with the BPQ Body Awareness, whereas the full IAS scale showed no such association.
 This pattern suggests that specific item pairings may show distinct patterns of association with other interoceptive measures and with mental health indices, whereas the aggregated IAS scale may obscure these relationships.
@@
 It is often unclear whether respondents should interpret the items as assessing attentional focus on bodily sensations, perceived accuracy in detecting them, or simply the frequency of experiencing such signals.
-As a result, studies have reported that observed associations vary depending on how the BPQ Body Awareness is constructed [@campos2021; @gabriele2022dissociations; @gaggero2021].
+As a result, studies have reported that observed associations vary depending on how the BPQ Body Awareness is interpreted [@campos2021; @gabriele2022dissociations; @gaggero2021].
 As such, it is unclear whether the lack of a relationship between the IAS and the BPQ Body Awareness in this study reflects a genuine divergence between the constructs measured by the two scales, or instead arises from ambiguities in how the BPQ Body Awareness is operationalized and interpreted across studies.
@@
 At the same time, the interpretation of such associations is complicated by the lack of contextualisation in the items themselves.For example, a racing heart is often associated with anxiety, yet the same sensation can also arise during exercise or other forms of physiological arousal.
-Without contextual anchors, it remains unclear which bodily states participants are drawing upon when responding.
+Without contextual anchors, it remains unclear which bodily states participants are drawing upon when responding, highlighting the interpretive ambiguity of self-reports.
 In line with prior work emphasizing the importance of contextual factors in the measurement of interoception [@vlemincx2023novel], our results suggest that the value of self-report lies less in broad aggregation across domains and more in the targeted assessment of physiologically and situationally meaningful contexts.
@@
 The dispositional correlates of the IAS help delineate the conceptual boundaries of interoceptive accuracy as a construct.
-Self-reported interoceptive accuracy, as assessed by the IAS, has been robustly associated with mood-related outcomes, particularly depression and anxiety, underscoring its relevance for affective regulation and bodily state monitoring (Benau et al., 2023; Brand et al., 2023).
-This aligns with a broader body of research linking affective conditions such as anxiety and depression with altered interoceptive processing (e.g., Garfinkel et al., 2016).
-However, recent findings have also reported null or inconsistent associations between interoceptive abilities and mental health symptomatology, suggesting that such relationships may not generalize across all interoceptive domains or measurement modalities [@banellis2025interoceptive; @jenkinson2024interoception].
-For instance, a recent review by @jenkinson2024interoception found no consistent evidence linking cardiac interoceptive accuracy tasks with anxiety or depression across multiple meta-analyses.
-Collectively, these findings underscore the importance of examining interoceptive self-perception at the level of distinct bodily domains rather than relying on aggregated or unidimensional measures.
+Self-reported interoceptive accuracy, as assessed by the IAS, has been robustly associated with mood-related outcomes, particularly depression and anxiety, underscoring its relevance for affective regulation and bodily state monitoring [@benau2023self; @brand2023].
+This aligns with a broader body of research linking affective conditions such as anxiety and depression with altered interoceptive processing [e.g.,@garfinkel2015knowing].
+However, recent findings have also reported null or inconsistent associations between interoceptive abilities and mental health symptomatology, suggesting that such relationships may not generalize across all interoceptive domains or measurement modalities (@banellis2025interoceptive; @jenkinson2024interoception).
+For instance, a recent review by @jenkinson2024interoception found no consistent evidence linking cardiac interoceptive accuracy tasks with anxiety or depression across multiple meta-analyses.Collectively, these findings indicate that relationships between interoceptive accuracy and mental health may vary across bodily domains and measurement modalities.
+This suggests that the IAS, while informative, may benefit from a more differentiated approach that accounts for domain-specific and contextual influences on self-reported interoceptive accuracy.
 
-In contrast, associations of IAS scores with personality traits and higher-order beliefs were modest: small positive correlations emerged with Openness and Agreeableness, and weak associations with primal world beliefs.
-Consistent with recent work linking interoceptive self-report to personality dispositions [@haustein2024interoception; @simkute2025interoception], these results suggest that interoceptive accuracy primarily operates at the level of bodily self-perception.
-This contrast reinforces the view that the IAS primarily indexes bodily self-perception, displaying only modest associations with  broader dispositional traits.
+In contrast to the relatively stronger associations observed with affective measures, correlations between IAS scores and personality traits were small but directionally consistent.
+Modest positive associations emerged with Openness, Agreeableness, and Conscientiousness, while Neuroticism and Extraversion showed near-zero relationships, and Honesty–Humility displayed weak negative correlations.
+This pattern suggests that self-reported interoceptive accuracy, as indexed by the IAS, shares limited but systematic overlap with broad dispositional tendencies -particularly those reflecting intellectual curiosity and creativity, patience and tolerance in interpersonal interactions, and diligence and organizational tendencies [@aashton2007empirical].
+Recent evidence supports the view that relationships between interoceptive measures and personality are multifaceted rather than uniform.
+For instance, @haustein2024interoception reported significant associations between interoceptive awareness (MAIA) and all personality traits except Agreeableness, with Openness showing positive correlations with Body Listening and Emotional Awareness, and Neuroticism showing negative correlations with Self- and Attention Regulation.
+Similarly, @simkute2025interoception found that task-based indices of interoceptive sensitivity related negatively to Extraversion.
+Collectively, these findings indicate that interoceptive constructs show distinct and sometimes opposing patterns of association across measurement modalities, suggesting that the IAS relates to a specific, self-evaluative aspect of interoceptive functioning rather than reflecting a general interoceptive or personality-based trait.
 
-A potential key reason for these discrepancies is the lack of a consistent theoretical framework for interoception, as dimensions are neither defined nor captured equally across questionnaires and experimental tasks [@desmedt2022measures].
-**[complete paragraph]**
+A potential key reason for discrepancies in observed associations, including those seen with the IAS, is that self-report questionnaires in interoception often tap into distinct constructs rather than a common underlying dimension [@desmedt2022measures].
+Measures labeled as interoceptive sensibility, awareness, or self-reported accuracy capture partially overlapping but empirically distinct facets, with low intercorrelations between questionnaires and items.
+Consequently, differences in associations with psychological outcomes or personality traits may reflect differences in what each questionnaire assesses rather than true variation in interoceptive functioning.
 
@@
 These two studies revealed three main points.
-Firstly, a shortened, 14-item refined IAS retained greater psychometric integrity while removing unstable and/or redundant items.
-Secondly, item pairings combined with analogue-style ratings captured greater variability and allowed more precise differentiation among individuals, often outperforming global scores in predictive value.
-However, even the refined IAS has significant limitations.
-Although the 14-item version improves interpretability and efficiency, the scale continues to underrepresent key interoceptive modalities such as cardiac, respiratory, and nuanced somatosensory signals, limiting its ability to capture the full breadth of interoceptive processes.
+First,  in the datasets that included analogue-style ratings, these scales captured greater variability, further enhancing the ability to detect individual differences.
+Second, a shortened, 14-item version of the IAS retained strong psychometric integrity while removing unstable or redundant items.
+Third, specific item pairings allowed more precise differentiation among individuals and often outperformed global scores in predictive value.
+Nevertheless, even this refined IAS has important limitations.
+While the 14-item version improves interpretability and efficiency, it continues to underrepresent key interoceptive modalities such as cardiac, respiratory, and nuanced somatosensory signals, limiting its ability to capture the full breadth of interoceptive processes.
 This shortcoming underscores the need for broader coverage in future scale development.
-Nevertheless, analogue-style items and item pairings offer clear advantages: they capture greater response variability, allow more precise differentiation among individuals, and provide efficient, domain-specific indicators that often outperform global scores in predictive value.
+At the same time, analogue-style items and item pairings offer clear advantages: they increase response variability, allow more precise differentiation among individuals, and provide domain-specific indicators that often outperform global scores.
 Building on these insights, a next-generation interoception scale could balance breadth (multiple items per modality) with depth (domain-specific subscales), retain the benefits of analogue or wider rating ranges (e.g., 1–7 instead of 1–5), and optimize coverage across physiologically and psychologically relevant bodily domains.
-Such a scale would improve the interpretability, sensitivity, and practical utility of interoceptive self-report measures, ultimately allowing for a more nuanced mapping of interoceptive abilities to affective, cognitive, and health-related outcomes.
+Such a scale would improve interpretability, sensitivity, and practical utility, ultimately enabling a more nuanced mapping of interoceptive abilities onto affective, cognitive, and health-related outcomes.
 
@@
 
-Because the IAS is a newly developed questionnaire and the only one designed to assess interoceptive self-reported accuracy - a dimension previously thought to require objective tasks such as the HDT and HCT - our focus was on evaluating its structure and correlates without introducing established measures with documented shortcomings.
+Because the IAS is a newly developed questionnaire and the only one designed to assess interoceptive self-reported accuracy - a dimension previously assessed solely through objective tasks such as the HDT and HCT - our focus was on evaluating its structure and correlates without introducing established measures with documented shortcomings.
 Nonetheless, future research should employ novel methods, such as Exploratory Graph Analysis, to clarify the convergent and divergent validity of these questionnaires across interoceptive domains.
-
-<!-- Future Outlook in the field -->
-Building on these limitations, a next-generation interoception scale should balance breadth (multiple items per modality, including underrepresented domains such as cardiac and respiratory) with depth (domain-specific subscales).
-Retaining analogue or wider rating ranges (e.g., 1–7 instead of 1–5) would further enhance sensitivity and coverage.
-Such a scale would improve the interpretability, sensitivity, and practical utility of interoceptive self-report measures, ultimately allowing for a more nuanced mapping of interoceptive abilities to affective, cognitive, and health-related outcomes.
 
@@
 Taken together, these studies advance understanding of the IAS and interoceptive self-report more broadly.
-The refined 14-item IAS provides a more efficient and interpretable measure, capturing domain-specific interoceptive signals that are differentially associated with psychological outcomes.
-Consistent associations with mood, alongside modest links to personality and beliefs, indicate that the IAS reflects adaptive, context-sensitive aspects of bodily self-perception rather than broad dispositional traits.
+The refined 14-item IAS provides a more efficient and interpretable measure, capturing domain-specific interoceptive signals that show differential associations with psychological outcomes.
+Associations were consistently stronger with mood measures and compared to personality and beliefs, indicating that self-reported interoceptive accuracy relates more closely to affective experience than to stable dispositional traits.
 At the same time, current findings highlight limitations in modality coverage and item specificity, suggesting that future scale development should incorporate multimodal, context-sensitive, and continuous analogue ratings or wider discrete scales to better capture the richness of interoceptive processes and clarify their role in affective, cognitive, and health-related outcomes [@desmedt2022measures; @vlemincx2023novel].
-Ultimately, these studies show that the IAS is most informative when treated as a set of domain-specific, context-sensitive indicators rather than as a broad global index, advancing both the measurement and theoretical understanding of interoception.
+Ultimately, these studies show that the IAS is most informative when treated as a set of domain-specific, context-sensitive indicators rather than as a broad global index, advancing both the measurement and conceptual understanding of interoception.
 

### 2025-10-17 paper/1_Initial/manuscript.qmd
minor

@@
 
-Study 1 will re-analyse and assess the factor structure of the IAS by taking advantage of the large number of open-access datasets [@brand2023; @campos2021; @lin2023; @murphy2019; @arslanova2022; @todd2022; @gaggero2021; @brand2022; @von2023; @makowski2025measuring; @poerio2024interoceptive].
+Study 1 will re-analyse and assess the factor structure of the IAS by taking advantage of the large number of open-access datasets [@brand2023; @campos2021; @lin2023; @murphy2019; @arslanova2022; @todd2022; @gaggero2021; @brand2022; @von2023; @poerio2024interoceptive].
 While combining these studies might provide a more robust and generalizable understanding of the IAS' factor structure, we also additionally provide an individual analysis (i.e., applying the same method on all samples separately) to add nuance to the general picture, as all studies differ in their sample size, demographic characteristics, language, and procedure.
@@
 #### Personality
-The NEO Five-Factor Inventory, neuroticism subscale [NEO-FFI, @costa1992neo] is a 12-item measure of neuroticism, assessing the general tendency to experience negative emotions such as fear, sadness, or disgust.
+The NEO Five-Factor Inventory, neuroticism subscale [NEO-FFI, @costa1992personality] is a 12-item measure of neuroticism, assessing the general tendency to experience negative emotions such as fear, sadness, or disgust.
 Items are rated on a 5-point Likert scale (e.g., “I often feel inferior to others”).
@@
 Modest positive associations emerged with Openness, Agreeableness, and Conscientiousness, while Neuroticism and Extraversion showed near-zero relationships, and Honesty–Humility displayed weak negative correlations.
-This pattern suggests that self-reported interoceptive accuracy, as indexed by the IAS, shares limited but systematic overlap with broad dispositional tendencies -particularly those reflecting intellectual curiosity and creativity, patience and tolerance in interpersonal interactions, and diligence and organizational tendencies [@aashton2007empirical].
+This pattern suggests that self-reported interoceptive accuracy, as indexed by the IAS, shares limited but systematic overlap with broad dispositional tendencies -particularly those reflecting intellectual curiosity and creativity, patience and tolerance in interpersonal interactions, and diligence and organizational tendencies [@ashton2007empirical].
 Recent evidence supports the view that relationships between interoceptive measures and personality are multifaceted rather than uniform.

### 2025-10-17 paper/1_Initial/manuscript.qmd
minor
added a reference

@@
 At the same time, these associations were context-dependent: not all item pairings or bodily domains related equally to mood or somatic symptoms [@murphy2019; @koike2023].
-Emerging evidence suggests that interoceptive abilities (e.g., sensitivity, precision and metacognitive insight) may not uniformly predict mental health outcomes and may depend on measurement approach or sample characteristics [**REF PRE_PRINT?**].
+Emerging evidence suggests that interoceptive abilities (e.g., sensitivity, precision and metacognitive insight) may not uniformly predict mental health outcomes and may depend on measurement approach or sample characteristics [@@banellis2025interoceptive].
 
@@
 
-# General DiscussionGeneral Discussion
+# General Discussion
 

### 2025-10-20 paper/1_Initial/manuscript.qmd
more intro typos

@@
         author:
-  - name: Giulia Poerio
-    orcid: 0000-0002-2343-5109
-    roles: 
-      - bla bla
-    affiliations:
-      affiliations:
-      - ref: "id1"
-      - name: "University of Sussex"
-        department:  "Sussex Centre for Consciousness Science"
   - name: Magdalena Pfaff
@@
         department: "Sussex Addictions Research and Intervention Centre"
+  - name: Giulia Poerio
+    orcid: 0000-0002-2343-5109
+    roles: 
+      - bla bla
+    affiliations:
+      affiliations:
+      - ref: "id1"
+      - name: "University of Sussex"
+        department:  "Sussex Centre for Consciousness Science"
   - name: Dominique Makowski
@@
 
-Interoception is referred to the process of sensing, interpreting and integrating information pertaining to internal organs, such as the heart, the lungs or the gut [@khalsa2018interoception].
+Interoception refers to the process of sensing, interpreting and integrating information pertaining to internal organs, such as the heart, the lungs or the gut [@khalsa2018interoception].
 While recent research emphasizes a key role of interoception in a variety of processes (e.g., emotion regulation, decision making) and of outcomes (physical and psychological well being), the field remains clouded by concerns about how interoception is assessed.
@@
 
-Focusing on another dimension of interoception, a recently developed scale with a rapidly growing popularity is the Interoceptive Accuracy Scale [IAS, @murphy2019].
+Focusing on the *accuracy* dimension of interoception, a recently developed scale with a rapidly growing popularity is the Interoceptive Accuracy Scale [IAS, @murphy2019].
 The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological modality such as respiration (*"I can always accurately perceive when I am breathing fast"*), heart (*"I can always accurately perceive when my heart is beating fast"*), skin (*"I can always accurately perceive when something is going to be ticklish"*), arousal or bodily functions like coughing (*"I can always accurately perceive when I am going to cough"*) or urinating (*"I can always accurately perceive when I need to urinate"*).
-Appealingly, the IAS' statements are about specific interoceptive behaviours, which is a distinct difference with other popular interoception questionnaires, such as the MAIA-2, which contains more general and metacognitive items (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*), as well as dimensions related to attention regulation (e.g., Not-distracting) or emotion regulation (e.g., Not-worrying).
+Appealingly, the IAS' statements are about specific interoceptive behaviours and "objective" experiences (although still subjective reports of them), which is a distinct difference with other popular interoception questionnaires, such as the MAIA-2, which contains more general and metacognitive items (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*), as well as dimensions related to attention regulation (e.g., Not-distracting) or emotion regulation (e.g., Not-worrying).
 
 <!-- IAS structure  --> 
-[**NOTES**: todd 2022 found no correlation for MAIA and IAS except  with the non-worrying facet + Gaggero found positive correlations with IAS and MAIA (general)]
-
 The original validation study suggested a two-factor structure for the IAS, one reflecting the perception of general interoceptive signals (urinate, hungry, defecate, thirsty, pain, heart, taste, breathing, temperature, muscles, affective touch, vomit, sexual arousal), and other relating to signals that may be difficult to perceive solely through interoceptive information (itch, tickle, cough, burp, bruise, blood sugar, sneeze, wind).
@@
 <!-- Relationship with other interoception measures -->
-
-Regarding its validity, the IAS has naturally been compared to other interoception-related measures, and shows a positive correlations with most facets of the MAIA [@mehling2018multidimensional], except for the Not-Distracting and Not-Worrying subscales [@brand2023] - which were previously highlighted as related to non-interoceptive abilities [@ferentzi2021examining].
+Regarding its validity, the IAS has naturally been compared to other interoception-related measures, and shows a positive correlations with most facets of the MAIA [@mehling2018multidimensional; @gaggero2021], except for the Not-Distracting and Not-Worrying subscales [@brand2023] - which were previously highlighted as related to non-interoceptive abilities [@ferentzi2021examining].
 Interestingly, findings on the correlation between the IAS and the body awareness dimension of the BPQ (i.e., BPQ-A) have been mixed: some studies report small positive correlations [@brand2023; @campos2021; @koike2023], while others find small negative correlations [@lin2023] or no correlation at all [@murphy2019].
-Small positive correlations have also been observed with the "observation" and "description" subscales of the Five Facet Mindfulness Questionnaire [FFMQ, @baer2006using; @brand2023; @koike2023], as well as with the "non-reactivity" and "acting with awareness" subscales [@koike2023].
+Positive correlations have also been observed with the "observation" and "description" subscales of the Five Facet Mindfulness Questionnaire [FFMQ, @baer2006using; @brand2023; @koike2023], as well as with the "non-reactivity" and "acting with awareness" subscales [@koike2023].
 Additionally, the IAS has shown a positive correlation with the interoceptive awareness subscale of the Eating Disorder Inventory [EDI-IA, @lin2023] and a negative correlation with the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia], as reported by @brand2023 and @murphy2019.
@@
 
-The current study aims at 1) clarifying the structure of the IAS with a mega-analytic (which involves a re-analysis at the raw data level by aggregating datasets) approach that leverages existing data and contrast the traditional CFA/SEM factor-based analyses with network-based ones (Exploratory Graph Analysis);
+Given the increasing relevance of interoception across psychology and neuroscience, and the growing use of the IAS as an interesting self-report measure of interoceptive accuracy, the current study aims at 1) clarifying the structure of the IAS with a mega-analytic (which involves a re-analysis at the raw data level by aggregating datasets) approach that leverages existing data and contrast the traditional CFA/SEM factor-based analyses with network-based ones (Exploratory Graph Analysis);
 1) provide an overview of the dispositional correlates of the IAS, clarifying its general pattern of associations, which is key to better understand the nature, place and role of interoception questionnaires within a larger context.
@@
     flextable() |>
-  set_table_properties(layout = "autofit", opts_pdf = list(arraystretch = 1)) |>
+    set_table_properties(
+        layout = "autofit",
+        opts_pdf = list(arraystretch = 1)
+    ) |>
     theme_apa()
@@
 Building on the structural findings from Study 1, the second study turns to the validity of the IAS by examining its dispositional correlates.
-Although the IAS has been widely used, evidence regarding its associations with personality traits, affective dispositions, and related psychological constructs remains scattered and inconsiste [@murphy2019; @brand2023; @lin2023; @todd2022].
+Although the IAS has been widely used, evidence regarding its associations with personality traits, affective dispositions, and related psychological constructs remains scattered and inconsistent [@murphy2019; @brand2023; @lin2023; @todd2022].
 Study 2 therefore had two primary goals.

### 2025-10-20 paper/1_Initial/manuscript.qmd
Update manuscript.qmd

@@
 After examining the distributions and correlations of all IAS items, we will test for "redundant" items (e.g., due to multicollinearity or local dependency) using Unique Variable Analysis [UVA, @christensen2023unique], a novel method derived from network psychometric designed to identify and merge items that share substantial variance (which can distort the structure estimation).
-We will use a threshold of 0.30 that detects large to very large overlap.
+We will use a threshold of 0.30 that detects large to very large overlap to remain conservative and only suggest scale modifications if strongly justified.
 
 Following the analysis of items, we will analyze the factor structure of the IAS using three different approaches, each with particular trade-offs and assumptions, to provide a multi-verse picture of likely solutions.
-Namely, we will apply traditional exploratory and confirmatory Factor Analysis (EFA/CFA), hierarchical clustering (HCA), and Exploratory Graph Analysis (EGA), to the whole sample, as well as to each dataset separately (details being available in the analysis document at https://github.com/RealityBending/InteroceptionIAS), and our decisions and conclusions will try to take into account both levels of analysis.
+Namely, we will apply traditional exploratory and confirmatory Factor Analysis (EFA/CFA), hierarchical clustering (HCA), and Exploratory Graph Analysis (EGA), to the whole sample, as well as to each dataset separately (details being available in the analysis document at https://github.com/RealityBending/InteroceptionIAS), and our decisions and conclusions will try to take into account both levels of the analysis.
 
@@
 #| out-width: "100%"
-#| fig-cap: "TODO."
+#| fig-cap: "Four structure analysis methods (HCA, EGA, EFA, CFA) were applied and converged on a consistent optimal solution of 14 items formed seven pairs: Hungry-Thirsty, Bruise-Blood sugar, Urinate-Defecate, Muscles-Pain, Breathing-Heart, Cough-Sneeze, Wind-Burp.
+While EFA suggested 3 factors, CFA confirmed the superiority of the 7-factor model over alternative structures."
 
@@
 <!-- Summary -->
-Study 1 establishes that once probeleamtic items are removed the IAS is best conceptualized as a set of item clusters rather than a unidimensional scale.
-This structural insight provides the foundation for Study 2, where dispositional correlates are examined to further evaluate the IAS’s construct validity.
+In summary, study 1 suggests that once problematic items are removed, the IAS is best conceptualized as a set of item clusters rather than a unidimensional scale.
+This structural insight provides the foundation for Study 2, where dispositional correlates are examined to further evaluate the IAS's construct validity.
+
 # Study 2
-
-<!-- The goal of study 2 is two-fold, 1) provide a robust overview of the dispositional correlates of the IAS by leveraging the large number of datasets available, and 2) assess the practical benefits of using a refined version of the IAS (i.e., the 14-item version identified in study 1) compared to the original 21-item one general factor version.
--->
-
-## Study 2
 
@@
 First, to provide a robust overview of the dispositional correlates of the IAS by leveraging the large number of available datasets.
-Second, to evaluate the practical benefits of using the refined 14-item version of the scale identified in Study 1, compared to the original 21-item unidimensional version, in order to assess whether structural improvements translate into clearer and more reliable external associations.
+Second, to evaluate the practical benefits of using the refined 14-item version of the scale identified in Study 1, compared to the original 21-item unidimensional solution, in order to assess whether structural improvements translate into clearer and more reliable external associations.
 
@@
 
-We selected measures that appeared in multiple datasets from Study 1 and/or were relevant given the scope of the study, merging scores of regular and abridged versions for conciseness where applicable.
-The measures include constructs related to interoception, mood, personality, psychopathology, and beliefs and misbeliefs.
+We selected measures that appeared in multiple datasets from Study 1 and/or were relevant given the scope of the study, i.e., constructs related to physiology, mood, personality, psychopathology, and beliefs and misbeliefs.
+We merged scores of regular and abridged versions for conciseness where applicable.
 
@@
 #### Interoception Related
+
 The Multidimensional Assessment of Interoceptive Awareness Version-2 [MAIA-2, @mehling2018multidimensional] is a 37-item questionnaire assessing eight dimensions of interoception: Noticing, Not-Distracting, Not-Worrying, Attention Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust.

### 2025-10-20 analysis/study2.qmd
Update study2.qmd

@@
 # names(df16) # MAIA (37), GAD (7), PHQ9 (9)
+
+alldata <- list(df1a=df1a, df1b=df1b, df2=df2, df3=df3, df4=df4, 
+                df5=df5, df6=df6, df7a=df7a, df7b=df7b, df7c=df7c, 
+                df8a=df8a, df8b=df8b, df9=df9, df10=df10, df11=df11, 
+                df12=df12, df14=df14, df15=df15, df16=df16)
 ```
@@
 
-pool_coef <- function(with = "Age", component = "Demographic", name = with, unequalrange=FALSE) {
+pool_coef <- function(with = "Age", component = "Demographic", category = "Demographic", name = with, unequalrange=FALSE) {
   rez <- data.frame()
@@
     data <- data.frame() 
-    for(dataset in list(df1a, df1b, df2, df3, df4, 
-                     df5, df6, df7a, df7b, df7c, 
-                     df8a, df8b, df9, df10, df11, 
-                     df12, df14, df15, df16)) {
+    for(dataset in alldata) {
       if (with %in% names(dataset)) {
@@
       f2 <- as.formula(paste0(intero, "~", with, " + (1|Sample)"))
+      f3 <- as.formula(paste0(intero, "~ Sample * ", with))
     } else {
@@
       f2 <- as.formula(paste0(intero, "~", with, " + (1|Sample)"))
+      f3 <- as.formula(paste0(intero, "~ Sample / ", with))
     }
 
-    # if(length(unique(data$Sample)) == 1)
-    m <- glmmTMB::glmmTMB(f, data = data)
+    # Mixed models
+    control1 <- glmmTMB::glmmTMBControl(parallel = list(n=4, autopar = TRUE))
+    control2 <- glmmTMB::glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS"), parallel = list(n=4, autopar = TRUE))
+    m <- glmmTMB::glmmTMB(f, data = data, control=control1)
     type <- "Full"
     if(!insight::is_converged(m)) {
-      m <- glmmTMB::glmmTMB(f2, data = data)
+      m <- glmmTMB::glmmTMB(f, data = data, control=control2)
+      type <- "Full"
+    }
+    if(!insight::is_converged(m)) {
+      m <- glmmTMB::glmmTMB(f2, data = data, control=control1)
       type <- "Reduced"
     }
+    if(!insight::is_converged(m)) {
+      m <- glmmTMB::glmmTMB(f2, data = data, control=control2)
+      type <- "Reduced"
+    }
+
+    # # Marginal
+    # m <- lm(f3, data = data)
+    # modelbased::estimate_slopes(m, trend = with)
+
     out <- parameters::parameters(m)[2, ] |> 
@@
     out$var_Correlate <- with
+    out$Category <- category
     out$Component <- component
@@
 
-data <- pool_coef(with = "Gender", component = "Demographic", name = "Gender (Female - Male)")
+check_ranges <- function(var = "Neuroticism") {
+  for(d in names(alldata)) {
+    dataset <- alldata[[d]]
+    if(!var %in% names(dataset)) next
+    print(paste0(d, ": ", paste(round(range(dataset[[var]], na.rm=TRUE), 2), collapse = "-")))
+  }
+}
+
+data <- pool_coef(with = "Gender", component = "Demographic", category = "General", name = "Gender (Female - Male)")
 ```
@@
 
-data <- rbind(data, pool_coef(with = "Age", component = "Demographic", unequalrange=TRUE))
+# check_ranges("Age")
+data <- rbind(data, pool_coef(with = "Age", component = "Demographic", category = "General", unequalrange=TRUE))
+```
+
+## Personality
+
+```{r}
+#| warning: false
+
+# names(df7a)[str_detect(names(df7a), "NEO")]
+# names(df9)[str_detect(names(df9), "BFI_")]
+# names(df10)[str_detect(names(df10), "IPIP6_")]
+
+# check_ranges("Neuroticism")
+# check_ranges("Agreeableness")
+# check_ranges("Conscientiousness")
+# check_ranges("HonestyHumility")
+
+data <- rbind(
+  data,
+  pool_coef(with = "Neuroticism", component = "Personality", category = "General", name = "Neuroticism", unequalrange=TRUE),
+  pool_coef(with = "Agreeableness", component="Personality", category = "General", name = "Agreeableness",unequalrange=TRUE),
+  pool_coef(with = "Conscientiousness", component="Personality", category = "General", name = "Conscientiousness",unequalrange=TRUE), 
+  pool_coef(with = "Openness", component="Personality", category = "General", name = "Openness",unequalrange=TRUE),
+  pool_coef(with = "Extraversion", component="Personality", category = "General", name = "Extraversion", unequalrange=TRUE),
+  pool_coef(with = "HonestyHumility", component="Personality", category = "General", name = "Honesty-Humility",unequalrange=TRUE)
+)
 ```
@@
   data,
-  pool_coef(with = "MAIA_AttentionReg", component = "MAIA", name = "Attention Regulation", unequalrange=TRUE),
-  pool_coef(with = "MAIA_BodyListening", component = "MAIA", name = "Listening", unequalrange=TRUE),
-  pool_coef(with = "MAIA_Trusting", component = "MAIA", name = "Trusting", unequalrange=TRUE),
-  pool_coef(with = "MAIA_EmoAwareness", component = "MAIA", name = "Emotional Awareness", unequalrange=TRUE),
-  pool_coef(with = "MAIA_NotDistracting", component = "MAIA", name = "Not Distracting", unequalrange=TRUE),
-  pool_coef(with = "MAIA_Noticing", component = "MAIA", name = "Noticing", unequalrange=TRUE),
-  pool_coef(with = "MAIA_NotWorrying", component = "MAIA", name = "Not Worrying", unequalrange=TRUE),
-  pool_coef(with = "MAIA_SelfReg", component = "MAIA", name = "Self Regulation", unequalrange=TRUE)
+  pool_coef(with = "MAIA_AttentionReg", component = "MAIA", category = "Interoception", name = "Attention Regulation - MAIA", unequalrange=TRUE),
+  pool_coef(with = "MAIA_BodyListening", component = "MAIA", category = "Interoception", name = "Listening - MAIA", unequalrange=TRUE),
+  pool_coef(with = "MAIA_Trusting", component = "MAIA", category = "Interoception", name = "Trusting - MAIA", unequalrange=TRUE),
+  pool_coef(with = "MAIA_EmoAwareness", component = "MAIA", category = "Interoception", name = "Emotional Awareness - MAIA", unequalrange=TRUE),
+  pool_coef(with = "MAIA_NotDistracting", component = "MAIA", category = "Interoception", name = "Not Distracting - MAIA", unequalrange=TRUE),
+  pool_coef(with = "MAIA_Noticing", component = "MAIA", category = "Interoception", name = "Noticing - MAIA", unequalrange=TRUE),
+  pool_coef(with = "MAIA_NotWorrying", component = "MAIA", category = "Interoception", name = "Not Worrying - MAIA", unequalrange=TRUE),
+  pool_coef(with = "MAIA_SelfReg", component = "MAIA", category = "Interoception", name = "Self Regulation - MAIA", unequalrange=TRUE)
 )
-```
-
-### ICQ
-
-```{r}
-#| warning: false
-
-# names(df2)[str_detect(names(df2), "ICQ")] 
-# names(df7c)[str_detect(names(df7c), "ICQ")]
-
-data <- rbind(data, pool_coef(with = "ICQ", component="Alexithymia", name = "ICQ", unequalrange=TRUE))
 ```
@@
   data,
-  pool_coef(with = "BPQ_BodyAwareness", component="BPQ", name = "Body Awareness (BPQ)",unequalrange=TRUE),
-  pool_coef(with = "BPQ_AutonomicReactivity", component="BPQ", name = "Autonomic Reactivity (BPQ)",unequalrange=TRUE)
+  pool_coef(with = "BPQ_BodyAwareness", component="Interoception", category = "Interoception", name = "Body Awareness - BPQ",unequalrange=TRUE),
+  pool_coef(with = "BPQ_AutonomicReactivity", component="Interoception", category = "Interoception", name = "Autonomic Reactivity - BPQ",unequalrange=TRUE)
   )
+```
+
+### ICQ
+
+```{r}
+#| warning: false
+
+# names(df2)[str_detect(names(df2), "ICQ")] 
+# names(df7c)[str_detect(names(df7c), "ICQ")]
+
+data <- rbind(data, pool_coef(with = "ICQ", component="Interoception", category = "Interoception", name = "Interoceptive Confusion - ICQ", unequalrange=TRUE))
 ```
@@
   data,
-  pool_coef(with = "TAS_DIF", component="Alexithymia", name = "Difficulties Identifying Feelings (TAS)", unequalrange=TRUE),
-  pool_coef(with = "TAS_DDF", component="Alexithymia", name = "Difficulties Describing Feelings (TAS)", unequalrange=TRUE),
-  pool_coef(with = "TAS_EOT", component="Alexithymia", name = "External Thinking (TAS)",unequalrange=TRUE),
-  pool_coef(with = "BVAQ_Affective", component="Alexithymia", name = "Affective (BVAQ)"), 
-  pool_coef(with = "BVAQ_Cognitive", component="Alexithymia", name = "Cognitive (BVAQ)")
+  pool_coef(with = "TAS_DIF", component="Interoception", category = "Interoception", name = "Difficulties Identifying Feelings - TAS", unequalrange=TRUE),
+  pool_coef(with = "TAS_DDF", component="Interoception", category = "Interoception", name = "Difficulties Describing Feelings - TAS", unequalrange=TRUE),
+  pool_coef(with = "TAS_EOT", component="Interoception", category = "Interoception", name = "External Thinking - TAS",unequalrange=TRUE),
+  pool_coef(with = "BVAQ_Affective", component="Interoception", category = "Interoception", name = "Affective - BVAQ"), 
+  pool_coef(with = "BVAQ_Cognitive", component="Interoception", category = "Interoception", name = "Cognitive - BVAQ")
 )
@@
 
+check_ranges("PHQ15_Sum")
+check_ranges("PHQ9_Sum")
+check_ranges("BDI_Sum")
+check_ranges("PHQ4_Depression")
+check_ranges("DEP")
+
 data <- rbind(
   data,
-  pool_coef(with = "PHQ15_Sum", component="Mood", name = "Somatic Concerns (PHQ-15)",unequalrange=TRUE), 
-  pool_coef(with = "PHQ9_Sum", component="Mood", name = "Depression (PHQ-9)",unequalrange=TRUE), 
-  pool_coef(with = "BDI_Sum", component="Mood", name = "Depression (BDI)"), 
-  pool_coef(with = "PHQ4_Depression", component="Mood", name = "Depression (PHQ-4)"),
-  pool_coef(with = "DEP", component = "Mood", name = "Depression (MFQ)")
+  pool_coef(with = "PHQ15_Sum", component="Mood", category = "Mood", name = "Somatic Concerns - PHQ-15",unequalrange=TRUE), 
+  pool_coef(with = "PHQ9_Sum", component="Mood", category = "Mood", name = "Depression - PHQ-9", unequalrange=TRUE), 
+  pool_coef(with = "BDI_Sum", component="Mood", category = "Mood", name = "Depression - BDI"), 
+  pool_coef(with = "PHQ4_Depression", component="Mood", category = "Mood", name = "Depression - PHQ-4"),
+  pool_coef(with = "DEP", component = "Mood", category = "Mood", name = "Depression - MFQ")
 )
@@
 
+# check_ranges("STAIT_Mean")
+# check_ranges("PHQ4_Anxiety")
+# check_ranges("GAD7_Sum")
+
 data <- rbind(
   data,
-  pool_coef(with = "STAIT_Mean", component="Mood", name = "Anxiety (STAI-T)",unequalrange=TRUE), 
-  pool_coef(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (PHQ-4)"),
-  pool_coef(with = "GAD7_Sum", component="Mood", name = "Anxiety (GAD-7)")
+  pool_coef(with = "STAIT_Mean", component="Mood", category = "Mood", name = "Anxiety (STAI-T)", unequalrange=TRUE), 
+  pool_coef(with = "PHQ4_Anxiety", component="Mood", category = "Mood", name = "Anxiety (PHQ-4)"),
+  pool_coef(with = "GAD7_Sum", component="Mood", category = "Mood", name = "Anxiety (GAD-7)")
 )
@@
 
+check_ranges("BPD")
+
 data <- rbind(
   data,
-  pool_coef(with = "BPD", component="Mood", name = "Boderline Personality")
+  pool_coef(with = "BPD", component="Mood", category = "Mood", name = "Boderline Personality")
 )
@@
 
-## Personality
-
-```{r}
-#| warning: false
-
-# names(df7a)[str_detect(names(df7a), "NEO")]
-# names(df9)[str_detect(names(df9), "BFI_")]
-# names(df10)[str_detect(names(df10), "IPIP6_")]
-
-data <- rbind(
-  data,
-  pool_coef(with = "Neuroticism", component = "Personality", name = "Neuroticism",unequalrange=TRUE),
-  pool_coef(with = "Agreeableness", component="Personality", name = "Agreeableness",unequalrange=TRUE),
-  pool_coef(with = "Conscientiousness", component="Personality", name = "Conscientiousness",unequalrange=TRUE), 
-  pool_coef(with = "Openness", component="Personality", name = "Openness",unequalrange=TRUE),
-  pool_coef(with = "Extraversion", component="Personality", name = "Extraversion", unequalrange=TRUE),
-  pool_coef(with = "HonestyHumility", component="Personality", name = "Honesty-Humility",unequalrange=TRUE)
-)
-```
-
-## Others
+## Beliefs
 
@@
          var_Interoception = str_replace(var_Interoception, "WindBurp", "Wind/Burp"),
-         var_Interoception = fct_relevel(var_Interoception, "Original", "Hungry/Thirsty", "Bruise/Blood sugar", "Muscles/Pain", "Cough/Sneeze", "Wind/Burp", "Breathing/Heart", "Urinate/Defecate")) |>
-         # Component = fct_relevel(
-         #   Component, "Demographic", "MAIA", "Body", "Mood", "Maladaptive",
-         #   "Schizotypic", "Autistic", "Personality", "Conspiracy Beliefs", "World Beliefs", "Lying Profile")) |>
+         var_Interoception = fct_relevel(var_Interoception, "Original", "Hungry/Thirsty", "Bruise/Blood sugar", "Muscles/Pain", "Cough/Sneeze", "Wind/Burp", "Breathing/Heart", "Urinate/Defecate"),
+         Category = fct_relevel(
+           Category, "General", "Interoception"),
+         Component = fct_relevel(Component, "Personality", "Demographic", "Interoception", "MAIA")) |> 
+  group_by(Component) |> 
+  mutate(var_Correlate = fct_reorder(var_Correlate, r, .fun=mean)) |>
+  ungroup() |>
   ggplot(aes(y = var_Correlate)) +
@@
   #                linewidth = 1) +
-  facet_grid(Component ~ var_Interoception, scales = "free", space ="free", switch = "y") +
+  facet_grid(Category ~ var_Interoception, scales = "free", space ="free", switch = "y") +
   scale_fill_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
@@
   scale_linewidth_continuous(range = c(3, 7), guide = "none") +
-  coord_cartesian(xlim = c(-0.45, 0.45)) +
+  coord_cartesian(xlim = c(-0.47, 0.47)) +
   theme_modern(axis.title.space = 5) +
@@
 p
-ggsave("figures/Figure3.png", p, width=21*0.5, height=29.7*0.5, dpi=300, bg="white")
+ggsave("figures/Figure3.png", p, width=21*1, height=29.7*1, dpi=300, bg="white")
 ```
@@
 
-Need for context-specific items (cross-modal when possible, i.E., cardioception, respiroception, etc.).
-
-New Scale: Multimodal Interoceptive Sensitivity Scale (MISS)
+Need for context-specific items (cross-modal when possible, i.e., cardioception, respiroception, etc.).

### 2025-10-20 analysis/study2.qmd
Update study2.qmd

@@
   data,
-  pool_coef(with = "PHQ15_Sum", component="Mood", category = "Mood", name = "Somatic Concerns - PHQ-15",unequalrange=TRUE), 
-  pool_coef(with = "PHQ9_Sum", component="Mood", category = "Mood", name = "Depression - PHQ-9", unequalrange=TRUE), 
-  pool_coef(with = "BDI_Sum", component="Mood", category = "Mood", name = "Depression - BDI"), 
-  pool_coef(with = "PHQ4_Depression", component="Mood", category = "Mood", name = "Depression - PHQ-4"),
-  pool_coef(with = "DEP", component = "Mood", category = "Mood", name = "Depression - MFQ")
+  pool_coef(with = "PHQ15_Sum", component="Depression", category = "Mood", name = "Somatic Concerns - PHQ-15",unequalrange=TRUE), 
+  pool_coef(with = "PHQ9_Sum", component="Depression", category = "Mood", name = "Depression - PHQ-9", unequalrange=TRUE), 
+  pool_coef(with = "BDI_Sum", component="Depression", category = "Mood", name = "Depression - BDI"), 
+  pool_coef(with = "PHQ4_Depression", component="Depression", category = "Mood", name = "Depression - PHQ-4"),
+  pool_coef(with = "DEP", component = "Depression", category = "Mood", name = "Depression - MFQ")
 )
@@
   data,
-  pool_coef(with = "STAIT_Mean", component="Mood", category = "Mood", name = "Anxiety (STAI-T)", unequalrange=TRUE), 
-  pool_coef(with = "PHQ4_Anxiety", component="Mood", category = "Mood", name = "Anxiety (PHQ-4)"),
-  pool_coef(with = "GAD7_Sum", component="Mood", category = "Mood", name = "Anxiety (GAD-7)")
+  pool_coef(with = "STAIT_Mean", component="Anxiety", category = "Mood", name = "Anxiety - STAI-T", unequalrange=TRUE), 
+  pool_coef(with = "PHQ4_Anxiety", component="Anxiety", category = "Mood", name = "Anxiety - PHQ-4"),
+  pool_coef(with = "GAD7_Sum", component="Anxiety", category = "Mood", name = "Anxiety - GAD-7")
 )
@@
 
-check_ranges("BPD")
+# check_ranges("BPD")
 
@@
   data,
-  pool_coef(with = "BPD", component="Mood", category = "Mood", name = "Boderline Personality")
+  pool_coef(with = "BPD", component="Maladaptive", category = "Psychopathology", name = "Boderline Personality")
+)
+```
+
+```{r}
+#| warning: false
+
+# check_ranges("PID5_Antagonism")
+
+data <- rbind(
+  data,
+  pool_coef(with = "PID5_Antagonism", component="Maladaptive", category = "Psychopathology", name = "Antagonism - PID-5"),
+  pool_coef(with = "PID5_Detachment", component="Maladaptive", category = "Psychopathology", name = "Detachment - PID-5"), 
+  pool_coef(with = "PID5_Disinhibition", component="Maladaptive", category = "Psychopathology", name = "Disinhibition - PID-5"),
+  pool_coef(with = "PID5_NegativeAffect", component="Maladaptive", category = "Psychopathology", name = "Negative Affect - PID-5"),
+  pool_coef(with = "PID5_Psychoticism", component="Maladaptive", category = "Psychopathology", name = "Psychoticism - PID-5")
 )
@@
   data,
-  pool_coef(with = "PID5_Antagonism", component="Maladaptive", name = "Antagonism"),
-  pool_coef(with = "PID5_Detachment", component="Maladaptive", name = "Detachment"), 
-  pool_coef(with = "PID5_Disinhibition", component="Maladaptive", name = "Disinhibition"),
-  pool_coef(with = "PID5_NegativeAffect", component="Maladaptive", name = "Negative Affect"),
-  pool_coef(with = "PID5_Psychoticism", component="Maladaptive", name = "Psychoticism")
-)
-```
-
-```{r}
-#| warning: false
-
-data <- rbind(
-  data,
-  pool_coef(with = "SPQ_ConstrictedAffect", component="Schizotypic", name = "Constricted Affect"),
-  pool_coef(with = "SPQ_Eccentric", component="Schizotypic", name = "Eccentric"),
-  pool_coef(with = "SPQ_MagicalThinking", component="Schizotypic", name = "Magical Thinking"),
-  pool_coef(with = "SPQ_NoCloseFriends", component="Schizotypic", name = "No Close Friends"),
-  pool_coef(with = "SPQ_OddSpeech", component="Schizotypic", name = "Odd Speech"),
-  pool_coef(with = "SPQ_Reference", component="Schizotypic", name = "Reference"),
-  pool_coef(with = "SPQ_SocialAnxiety", component="Schizotypic", name = "Social Anxiety"),
-  pool_coef(with = "SPQ_Suspiciousness", component="Schizotypic", name = "Suspiciousness"),
-  pool_coef(with = "SPQ_UnusualPerceptions", component="Schizotypic", name = "Unusual Perceptions")
+  pool_coef(with = "SPQ_ConstrictedAffect", component="Schizotypic", category = "Psychopathology", name = "Constricted Affect - SPQ"),
+  pool_coef(with = "SPQ_Eccentric", component="Schizotypic", category = "Psychopathology", name = "Eccentric - SPQ"),
+  pool_coef(with = "SPQ_MagicalThinking", component="Schizotypic", category = "Psychopathology", name = "Magical Thinking - SPQ"),
+  pool_coef(with = "SPQ_NoCloseFriends", component="Schizotypic", category = "Psychopathology", name = "No Close Friends - SPQ"),
+  pool_coef(with = "SPQ_OddSpeech", component="Schizotypic", category = "Psychopathology", name = "Odd Speech - SPQ"),
+  pool_coef(with = "SPQ_Reference", component="Schizotypic", category = "Psychopathology", name = "Reference - SPQ"),
+  pool_coef(with = "SPQ_SocialAnxiety", component="Schizotypic", category = "Psychopathology", name = "Social Anxiety - SPQ"),
+  pool_coef(with = "SPQ_Suspiciousness", component="Schizotypic", category = "Psychopathology", name = "Suspiciousness - SPQ"),
+  pool_coef(with = "SPQ_UnusualPerceptions", component="Schizotypic", category = "Psychopathology", name = "Unusual Perceptions - SPQ")
 )
@@
   data,
-  pool_coef(with = "ASQ_Imagination", component="Autistic", name = "Imagination"),
-  pool_coef(with = "ASQ_LackSocialSkills", component="Autistic", name = "Lack of Social Skills"), 
-  pool_coef(with = "ASQ_LowAttentionalSwitching", component="Autistic", name = "Low Attentional Switching"),
-  pool_coef(with = "ASQ_Patterns", component="Autistic", name = "Patterns and Numbers"),
-  pool_coef(with = "ASQ_Routine", component="Autistic", name = "Routines")
+  pool_coef(with = "ASQ_Imagination", component="Autistic", category = "Psychopathology", name = "Imagination - ASQ"),
+  pool_coef(with = "ASQ_LackSocialSkills", component="Autistic", category = "Psychopathology", name = "Lack of Social Skills - ASQ"), 
+  pool_coef(with = "ASQ_LowAttentionalSwitching", component="Autistic", category = "Psychopathology", name = "Low Attentional Switching - ASQ"),
+  pool_coef(with = "ASQ_Patterns", component="Autistic", category = "Psychopathology", name = "Patterns and Numbers - ASQ"),
+  pool_coef(with = "ASQ_Routine", component="Autistic", category = "Psychopathology", name = "Routines - ASQ")
 )
@@
          Category = fct_relevel(
-           Category, "General", "Interoception"),
-         Component = fct_relevel(Component, "Personality", "Demographic", "Interoception", "MAIA")) |> 
+           Category, "General", "Interoception", "Mood", "Psychopathology"),
+         Component = fct_relevel(Component, "Personality", "Demographic", "Interoception", "MAIA", "Anxiety", "Depression", "Schizotypic", "Autistic", "Maladaptive")) |> 
   group_by(Component) |> 

### 2025-10-21 analysis/Study1.qmd
Update Study1.qmd

@@
   mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5), range = c(1, 5))),# Original scale 1-5
-          across(PHQ15_01:PHQ15_15recode, \(x) datawizard::rescale(x, to = c(0,2), range =c(1,3))),
+          across(starts_with("PHQ15_"), \(x) datawizard::rescale(x, to = c(0,2), range = c(1,3))),
+
            across(PHQ9_01:PHQ9_09, \(x) datawizard::rescale(x, to = c(0,3), range =c(1,4))))
@@
 df7b$BPQ_BodyAwareness <- rowMeans(select(df7b, BPQ_01:BPQ_12), na.rm = TRUE)
-df7b$PHQ15_Sum <-rowSums(select(df7b,PHQ15_01:PHQ15_15recode), na.rm = TRUE)
+df7b$PHQ15_Sum <-rowMeans(select(df7b,PHQ15_01:PHQ15_15recode), na.rm = TRUE)
 df7b$PHQ9_Sum <- rowMeans(select(df7b, PHQ9_01:PHQ9_09), na.rm = TRUE)
@@
     GAD7_Sum = rowSums(across(starts_with("gad1_")), na.rm = TRUE),
-    PHQ9_Sum = rowSums(across(starts_with("phq1_")), na.rm = TRUE)) |>
+    PHQ9_Sum = rowMeans(across(starts_with("phq1_")), na.rm = TRUE)) |>
   filter (!Age == 2004.00, !Age == 1999.00, # misreported age

### 2025-10-21 analysis/Study1.qmd
BFI updated df9

@@
   mutate(
-    Neuroticism = (BFI_1 + BFI_2 + BFI_3)/3,
-    Agreeableness = (BFI_10R + BFI_11 + BFI_12)/3,
-    Extraversion = (BFI_4 + BFI_5 + BFI_6)/3,
-    Conscientiousness = (BFI_13 + BFI_14 + BFI_15R)/3,
-    Openness = (BFI_7 + BFI_8 + BFI_9)/3)
+    Neuroticism = (BFI_5 + BFI_10 + BFI_15)/3,
+    Agreeableness = (BFI_3 + BFI_6 + BFI_13)/3,
+    Extraversion = (BFI_2 + BFI_8 + BFI_12)/3,
+    Conscientiousness = (BFI_1 + BFI_7 + BFI_11)/3,
+    Openness = (BFI_4 + BFI_9 + BFI_14)/3)
 

### 2025-10-22 paper/1_Initial/manuscript.qmd
Update manuscript.qmd

@@
 
-[**NOTE** justify the choice of those specific primals ? higehr correlations with the IAS?]
-
 ## Discussion
@@
 <!-- AIms -->
-The present study aimed to provide a comprehensive evaluation of the IAS, spanning both its structure (study 1) and its dispositional correlates (study 2).
-Together, these studies offer novel insights into the psychometric characteristics, conceptual interpretation, and practical applications of the IAS within the broader landscape of interoception research.
+The present study provides a comprehensive evaluation of the IAS, examining both its structure (study 1) and its dispositional correlates (study 2).
+These studies offer novel insights into the psychometric characteristics, conceptual interpretation, and practical applications of the IAS.
+In this discussion, these findings are contextualized within the broader landscape of interoception research.
 
 <!-- Study 1 findings -->
-Study 1 demonstrated that the IAS is best conceptualised as clusters of tightly coupled item pairs, reflecting discrete bodily domains such as visceral sensations, musculoskeletal cues, and expulsion phenomena.
-The pairs emerged once several items (e.g., Tickle, Taste, Affective Touch) were removed due to their instability, redundancy or poor associations with the other items.
-The resulting 14-item refined IAS retained the psychometric integrity of the original scale while improving interpretability and efficiency.
-
-<!-- Study 1 findings -->
-Study 1 demonstrated that the IAS is best conceptualised as clusters of tightly coupled item pairs, reflecting discrete bodily domains such as visceral sensations, musculoskeletal cues, and expulsion phenomena.
-The pairs emerged once several items (e.g., Tickle, Taste, Affective Touch) were removed due to their instability, redundancy or poor associations with the other items.
-The resulting 14-item refined IAS retained the psychometric integrity of the original scale while improving interpretability and efficiency.
+Study 1 demonstrated that the IAS is best conceptualised as comprising tightly coupled item pairs, reflecting discrete bodily domains such as visceral sensations, musculoskeletal cues, and expulsion phenomena.
+The pairs emerged after several items (e.g., Tickle, Taste, Affective Touch) were removed due to their instability, redundancy, or poor associations with the other items.
+The resulting 14-item IAS retained the psychometric integrity of the original scale while improving interpretability and efficiency.
 
@@
 @lin2023 suggested a 12-item version by removing items with local dependency, high difficulty, and/or low discrimination.
-Their parallel analysis suggested unidimensionality, although this method is known to underestimate factor numbers in multidimensional data [@golino2017exploratory; @markos2024dimensionality].
-In contrast, our study applied multiple methods such as EGA, FA, and HCA yet the same pairs consistently emerged across datasets and demonstrated superior fit compared to alternative models.
-This challenges the assumption of unidimensionality of the IAS [@murphy2019; @brand2023].
-Although the short version of the IAS by  @lin2023 preferred a one-factor solution, their 12-item IAS was derived by removing locally dependent items identified through Item Response Theory.
-In our framework, these locally dependent items are instead interpreted as meaningful pairs (e.g., Heart–Breath), reflecting distinct bodily domains.
-However, because IRT assumes unidimensionality [@nguyen2014introduction], it may have treated these natural item clusters as sources of statistical dependency rather than as theoretically relevant structures within interoceptive accuracy.
+Their parallel analysis suggested unidimensionality, although parallel analysis is known to underestimate factor numbers in multidimensional data [@golino2017exploratory; @markos2024dimensionality].
+
+In contrast, our study applied multiple methods including EGA, FA, and HCA yet the same pairs consistently emerged across datasets and demonstrated superior fit compared to alternative models, which challenges the assumption of unidimensionality of the IAS [@murphy2019; @brand2023].
+Although the short version of the IAS by  @lin2023 favoured a one-factor solution, their 12-item IAS was derived by removing locally dependent items identified through Item Response Theory (IRT).
+
+We found that these locally dependent items can instead be interpreted as meaningful pairs (e.g., Heart–Breath), reflecting distinct bodily domains.
+Because IRT assumes unidimensionality [@nguyen2014introduction], it may have treated these natural item clusters as statistical artefacts rather than as theoretically relevant structures within interoceptive accuracy.
 
@@
 Study 2 provided further evidence for a domain-specific perspective.
-Certain item pairings, particularly Hunger–Thirst, Bruise–Blood sugar and Muscles-Pain, showed consistent negative correlations with depression and anxiety measures, in some cases approaching or even surpassing the strength of associations observed for the full IAS scale.
-Notably, Hunger-Thirst and Bruise-Blood sugar were also the only pairs, out of the seven examined, that displayed significant positive correlations with the BPQ Body Awareness, whereas the full IAS scale showed no such association.
-This pattern suggests that specific item pairings may show distinct patterns of association with other interoceptive measures and with mental health indices, whereas the aggregated IAS scale may obscure these relationships.
-This highlights that questionnaires like the IAS may capture multiple facets of interoception rather than a single underlying dimension, and that domain-specific approaches may provide greater construct validity.
+Certain item pairings, particularly Hunger-Thirst, Bruise-Blood sugar, and Muscles-Pain, showed consistent negative correlations with depression and anxiety measures, sometimes approaching or even surpassing the strength of associations observed for the full IAS scale.
+Notably, Hunger–Thirst and Bruise–Blood sugar were also the only pairs, out of the seven examined, that displayed significant positive correlations with the BPQ Body Awareness subscale, whereas the full IAS scale showed no such association.
 
-These findings mirror broader inconsistencies in the literature concerning associations between the IAS and the BPQ Body Awareness.
+Additionally, specific item pairings revealed distinct patterns of association with other interoceptive measures and mental health indices that were not captured by the full IAS.
+For instance, while the full IAS showed no significant associations with Borderline Personality, the Hunger-Thirst pair exhibited negative correlations.
+These findings collectively suggest that item-level analyses may uncover more nuanced relationships than those identified by the overall scale.
+This pattern highlights that questionnaires like the IAS may capture multiple facets of interoception rather than a single underlying dimension.
+Consequently, adopting a domain-specific approach could enhance construct validity by better reflecting the heterogeneity of interoceptive experiences.
+
+These findings are in line with inconsistencies in the literature concerning associations between the IAS and the BPQ Body Awareness.
 While some studies report significant negative associations [@lin2023], others have observed significant positive associations  [@brand2023; @campos2021; @gaggero2021; @todd2022], and still others none at all  [@murphy2019].
-In our study the full IAS was not associated with the BPQ Body Awareness.
-Interpretation is further complicated by conceptual debates: the BPQ Body Awareness is frequently treated as a measure of interoception, whereas the BPQ Autonomic Reactivity subscale has been criticized as indexing dysfunction in the nervous system rather than interoceptive sensitivity [@gaggero2021].
-Our results lend tentative support to this interpretation, as the full IAS scale and most item pairings showed significant negative associations with the BPQ Autonomic Reactivity, with the exception of the Bruise–Blood sugar pair.
+In our study the full IAS was also not associated with the BPQ Body Awareness.
+
 This pattern is consistent with the idea that this subscale may capture maladaptive bodily experiences or autonomic dysfunction, rather than interoceptive accuracy per se.
@@
 
-Taken together with these debates, the discrepancies observed here highlight that some IAS pairings may capture interoceptive self-reported accuracy more effectively than the aggregated measure, raising questions about the interpretability of the full scale.
-By contrast, other pairings (e.g., Cough–Sneeze, Wind–Burp) were weakly or inconsistently related to external variables, raising concerns about their usefulness.
+We highlight that some IAS pairings may capture interoceptive self-reported accuracy more effectively than the full IAS measure, raising questions about the interpretability of the full scale.
+In contrast , other pairings (e.g., Cough–Sneeze, Wind–Burp) were weakly or inconsistently related to other variables, raising concerns about their usefulness.
 Together, these findings indicate that the strength and relevance of interoceptive self-reported accuracy may vary systematically across physiological domains.
-At the same time, the interpretation of such associations is complicated by the lack of contextualisation in the items themselves.For example, a racing heart is often associated with anxiety, yet the same sensation can also arise during exercise or other forms of physiological arousal.
+
+At the same time, the interpretation of such associations is complicated by the lack of contextualisation in the items themselves.
+For example, a racing heart is often associated with anxiety, yet the same sensation can also arise during exercise or other forms of physiological arousal.
 Without contextual anchors, it remains unclear which bodily states participants are drawing upon when responding, highlighting the interpretive ambiguity of self-reports.
@@
 This aligns with a broader body of research linking affective conditions such as anxiety and depression with altered interoceptive processing [e.g.,@garfinkel2015knowing].
+
 However, recent findings have also reported null or inconsistent associations between interoceptive abilities and mental health symptomatology, suggesting that such relationships may not generalize across all interoceptive domains or measurement modalities (@banellis2025interoceptive; @jenkinson2024interoception).
@@
 This pattern suggests that self-reported interoceptive accuracy, as indexed by the IAS, shares limited but systematic overlap with broad dispositional tendencies -particularly those reflecting intellectual curiosity and creativity, patience and tolerance in interpersonal interactions, and diligence and organizational tendencies [@ashton2007empirical].
+
 Recent evidence supports the view that relationships between interoceptive measures and personality are multifaceted rather than uniform.
@@
 Nevertheless, even this refined IAS has important limitations.
+
 While the 14-item version improves interpretability and efficiency, it continues to underrepresent key interoceptive modalities such as cardiac, respiratory, and nuanced somatosensory signals, limiting its ability to capture the full breadth of interoceptive processes.
@@
 At the same time, analogue-style items and item pairings offer clear advantages: they increase response variability, allow more precise differentiation among individuals, and provide domain-specific indicators that often outperform global scores.
+
 Building on these insights, a next-generation interoception scale could balance breadth (multiple items per modality) with depth (domain-specific subscales), retain the benefits of analogue or wider rating ranges (e.g., 1–7 instead of 1–5), and optimize coverage across physiologically and psychologically relevant bodily domains.
@@
 Associations were consistently stronger with mood measures and compared to personality and beliefs, indicating that self-reported interoceptive accuracy relates more closely to affective experience than to stable dispositional traits.
+
 At the same time, current findings highlight limitations in modality coverage and item specificity, suggesting that future scale development should incorporate multimodal, context-sensitive, and continuous analogue ratings or wider discrete scales to better capture the richness of interoceptive processes and clarify their role in affective, cognitive, and health-related outcomes [@desmedt2022measures; @vlemincx2023novel].

### 2025-10-22 analysis/study2.qmd
update results

@@
     # Mixed models
-    control1 <- glmmTMB::glmmTMBControl(parallel = list(n=4, autopar = TRUE))
-    control2 <- glmmTMB::glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS"), parallel = list(n=4, autopar = TRUE))
+    control1 <- glmmTMB::glmmTMBControl()
+    control2 <- glmmTMB::glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS"))
     m <- glmmTMB::glmmTMB(f, data = data, control=control1)
     type <- "Full"
-    if(!insight::is_converged(m)) {
+    if(!insight::is_converged(m) || is.nan(insight::get_statistic(m)$Statistic[2])) {
       m <- glmmTMB::glmmTMB(f, data = data, control=control2)
@@
     }
-    if(!insight::is_converged(m)) {
+    if(!insight::is_converged(m)  || is.nan(insight::get_statistic(m)$Statistic[2])) {
       m <- glmmTMB::glmmTMB(f2, data = data, control=control1)
@@
     }
-    if(!insight::is_converged(m)) {
+    if(!insight::is_converged(m) || is.nan(insight::get_statistic(m)$Statistic[2])) {
       m <- glmmTMB::glmmTMB(f2, data = data, control=control2)
@@
 
-```{r}
+```{r perso}
 #| warning: false
@@
   pool_coef(with = "Extraversion", component="Personality", category = "General", name = "Extraversion", unequalrange=TRUE),
-  pool_coef(with = "HonestyHumility", component="Personality", category = "General", name = "Honesty-Humility",unequalrange=TRUE)
+  pool_coef(with = "HonestyHumility", component="Personality", category = "General", name = "Honesty-Humility", unequalrange=TRUE)
 )
@@
 
-```{r}
+```{r maia}
 #| warning: false
@@
 
-```{r}
+```{r bpq}
 #| warning: false
@@
 
-```{r}
+```{r icq}
 #| warning: false
@@
 
+data <- rbind(
+  data,
+  pool_coef(with = "GCBS_Extraterrestrial", component="Conspiracy Beliefs", category = "Beliefs", name = "Extraterrestrial - GCBS"),
+  pool_coef(with = "GCBS_GlobalConspiracies", component="Conspiracy Beliefs", category = "Beliefs", name = "Global Conspiracies - GCBS"),
+  pool_coef(with = "GCBS_GovernmentMalfeasance", component="Conspiracy Beliefs", category = "Beliefs", name  = "Government Malfeasance - GCBS"),
+  pool_coef(with = "GCBS_InformationControl", component="Conspiracy Beliefs", category = "Beliefs", name = "Information Control - GCBS"),
+  pool_coef(with = "GCBS_PersonalWellbeing", component="Conspiracy Beliefs", category = "Beliefs", name = "Personal Wellbeing - GCBS")
+)
+```
+
+```{r}
+#| warning: false
+
+data <- rbind(
+  data,
+  pool_coef(with = "LIE_Ability", component="Lying Profile", category = "Beliefs", name = "Lying Ability"),
+  pool_coef(with = "LIE_Frequency", component="Lying Profile", category = "Beliefs", name = "Lying Frequency"),
+  pool_coef(with = "LIE_Contextuality", component="Lying Profile", category = "Beliefs", name = "Lying Contextuality"),
+  pool_coef(with = "LIE_Negativity", component="Lying Profile", category = "Beliefs", name = "Lying Negativity")
+)
+```
+
+```{r}
+#| warning: false
+
 # names(df10)[str_detect(names(df10), "PI_Alive")]
@@
   data,
-  pool_coef(with = "PI_Alive", component="World Beliefs", name = "Alive", unequalrange=TRUE),
-  pool_coef(with = "PI_Changing", component="World Beliefs", name = "Changing", unequalrange=TRUE),
-  pool_coef(with = "PI_Enticing", component="World Beliefs", name = "Enticing", unequalrange=TRUE),
-  pool_coef(with = "PI_Good", component="World Beliefs", name = "Good", unequalrange=TRUE),
-  pool_coef(with = "PI_Hierarchical", component="World Beliefs", name = "Hierarchical", unequalrange=TRUE),
-  pool_coef(with = "PI_Safe", component="World Beliefs", name = "Safe",unequalrange=TRUE),
-  pool_coef(with = "PI_Understandable", component="World Beliefs", name = "Understandable",unequalrange=TRUE),
+  pool_coef(with = "PI_Alive", component="World Beliefs", category = "Beliefs", name = "Alive - Primal Belief", unequalrange=TRUE),
+  pool_coef(with = "PI_Changing", component="World Beliefs", category = "Beliefs", name = "Changing - Primal Belief", unequalrange=TRUE),
+  pool_coef(with = "PI_Enticing", component="World Beliefs", category = "Beliefs", name = "Enticing - Primal Belief", unequalrange=TRUE),
+  pool_coef(with = "PI_Good", component="World Beliefs", category = "Beliefs", name = "Good - Primal Belief", unequalrange=TRUE),
+  pool_coef(with = "PI_Hierarchical", component="World Beliefs", category = "Beliefs", name = "Hierarchical - Primal Belief", unequalrange=TRUE),
+  pool_coef(with = "PI_Safe", component="World Beliefs", category = "Beliefs", name = "Safe - Primal Belief",unequalrange=TRUE),
+  pool_coef(with = "PI_Understandable", component="World Beliefs", category = "Beliefs", name = "Understandable - Primal Belief",unequalrange=TRUE)
 
-  pool_coef(with = "PI_AboutMe", component="World Beliefs", name = "About me",unequalrange=TRUE),
-  pool_coef(with = "PI_Abundant", component="World Beliefs", name = "Abundant",unequalrange=TRUE),
-  pool_coef(with = "PI_Acceptable", component="World Beliefs", name = "Acceptable",unequalrange=TRUE),
-  pool_coef(with = "PI_Beautiful", component="World Beliefs", name = "Beautiful",unequalrange=TRUE),
-  pool_coef(with = "PI_Cooperative", component="World Beliefs", name = "Cooperative",unequalrange=TRUE),
-  pool_coef(with = "PI_Funny", component="World Beliefs", name = "Funny",unequalrange=TRUE),
-  pool_coef(with = "PI_Harmless", component="World Beliefs", name = "Harmless",unequalrange=TRUE),
-  pool_coef(with = "PI_Improvable", component="World Beliefs", name = "Improvable",unequalrange=TRUE),
-  pool_coef(with = "PI_Interconnected", component="World Beliefs", name = "Interconnected",unequalrange=TRUE),
-  pool_coef(with = "PI_Interesting", component="World Beliefs", name = "Interesting",unequalrange=TRUE),
-  pool_coef(with = "PI_Just", component="World Beliefs", name = "Just",unequalrange=TRUE),
-  pool_coef(with = "PI_Meaningful", component="World Beliefs", name = "Meaningful",unequalrange=TRUE),
-  pool_coef(with = "PI_NeedsMe", component="World Beliefs", name = "Needs Me",unequalrange=TRUE),
-  pool_coef(with = "PI_Pleasurable", component="World Beliefs", name = "Pleasurable",unequalrange=TRUE),
-  pool_coef(with = "PI_Progressing", component="World Beliefs", name = "Progressing",unequalrange=TRUE),
-  pool_coef(with = "PI_Regenerative", component="World Beliefs", name = "Regenerative",unequalrange=TRUE),
-  pool_coef(with = "PI_Stable", component="World Beliefs", name = "Stable",unequalrange=TRUE),
-  pool_coef(with = "PI_WorthExploring", component="World Beliefs", name = "Worth Exploring",unequalrange=TRUE),
-  pool_coef(with = "PI_Intentional", component="World Beliefs", name = "Intentional", unequalrange=TRUE)
-  )
-```
-
-```{r}
-#| warning: false
-
-data <- rbind(
-  data,
-  pool_coef(with = "GCBS_Extraterrestrial", component="Conspiracy Beliefs", name = "Extraterrestrial"),
-  pool_coef(with = "GCBS_GlobalConspiracies", component="Conspiracy Beliefs", name = "Global Conspiracies"),
-  pool_coef(with = "GCBS_GovernmentMalfeasance", component="Conspiracy Beliefs", name  = "Government Malfeasance"),
-  pool_coef(with = "GCBS_InformationControl", component="Conspiracy Beliefs", name = "Information Control"),
-  pool_coef(with = "GCBS_PersonalWellbeing", component="Conspiracy Beliefs", name = "Personal Wellbeing")
-)
-```
-
-```{r}
-#| warning: false
-
-data <- rbind(
-  data,
-  pool_coef(with = "LIE_Ability", component="Lying Profile", name = "Ability"),
-  pool_coef(with = "LIE_Frequency", component="Lying Profile", name = "Frequency"),
-  pool_coef(with = "LIE_Contextuality", component="Lying Profile", name = "Contextuality"),
-  pool_coef(with = "LIE_Negativity", component="Lying Profile", name = "Negativity")
+  # pool_coef(with = "PI_AboutMe", component="World Beliefs", name = "About me",unequalrange=TRUE),
+  # pool_coef(with = "PI_Abundant", component="World Beliefs", name = "Abundant",unequalrange=TRUE),
+  # pool_coef(with = "PI_Acceptable", component="World Beliefs", name = "Acceptable",unequalrange=TRUE),
+  # pool_coef(with = "PI_Beautiful", component="World Beliefs", name = "Beautiful",unequalrange=TRUE),
+  # pool_coef(with = "PI_Cooperative", component="World Beliefs", name = "Cooperative",unequalrange=TRUE),
+  # pool_coef(with = "PI_Funny", component="World Beliefs", name = "Funny",unequalrange=TRUE),
+  # pool_coef(with = "PI_Harmless", component="World Beliefs", name = "Harmless",unequalrange=TRUE),
+  # pool_coef(with = "PI_Improvable", component="World Beliefs", name = "Improvable",unequalrange=TRUE),
+  # pool_coef(with = "PI_Interconnected", component="World Beliefs", name = "Interconnected",unequalrange=TRUE),
+  # pool_coef(with = "PI_Interesting", component="World Beliefs", name = "Interesting",unequalrange=TRUE),
+  # pool_coef(with = "PI_Just", component="World Beliefs", name = "Just",unequalrange=TRUE),
+  # pool_coef(with = "PI_Meaningful", component="World Beliefs", name = "Meaningful",unequalrange=TRUE),
+  # pool_coef(with = "PI_NeedsMe", component="World Beliefs", name = "Needs Me",unequalrange=TRUE),
+  # pool_coef(with = "PI_Pleasurable", component="World Beliefs", name = "Pleasurable",unequalrange=TRUE),
+  # pool_coef(with = "PI_Progressing", component="World Beliefs", name = "Progressing",unequalrange=TRUE),
+  # pool_coef(with = "PI_Regenerative", component="World Beliefs", name = "Regenerative",unequalrange=TRUE),
+  # pool_coef(with = "PI_Stable", component="World Beliefs", name = "Stable",unequalrange=TRUE),
+  # pool_coef(with = "PI_WorthExploring", component="World Beliefs", name = "Worth Exploring",unequalrange=TRUE),
+  # pool_coef(with = "PI_Intentional", component="World Beliefs", name = "Intentional", unequalrange=TRUE)
   )
@@
          Category = fct_relevel(
-           Category, "General", "Interoception", "Mood", "Psychopathology"),
-         Component = fct_relevel(Component, "Personality", "Demographic", "Interoception", "MAIA", "Anxiety", "Depression", "Schizotypic", "Autistic", "Maladaptive")) |> 
+           Category, "General", "Interoception", "Mood", "Psychopathology", "Beliefs"),
+         Component = fct_relevel(Component, "Personality", "Demographic", "Interoception", "MAIA", "Anxiety", "Depression", "Schizotypic", "Autistic", "Maladaptive", "World Beliefs", "Conspiracy Beliefs", "Lying Profile")) |>
   group_by(Component) |> 
@@
 p
-ggsave("figures/Figure3.png", p, width=21*1, height=29.7*1, dpi=300, bg="white")
+ggsave("figures/Figure3.png", p, width=21*0.55, height=29.7*0.4, dpi=300, bg="white")
 ```
@@
 Need for context-specific items (cross-modal when possible, i.e., cardioception, respiroception, etc.).
+
+Neuroticism: effect unclear
+
+Openness (driven by Wind/burp): effect of response bias

### 2025-10-22 paper/1_Initial/manuscript.qmd
updated Results CFA

@@
 
-<!-- CFA Model Comparison -->
-<!-- Name	BIC	RMSEA	Chi2	CFI	BF -->
-<!-- fit_g	933909.6	0.124	27,249.398	0.783	Inf -->
-<!-- fit_ega	1101773.3	0.035	2,306.303	0.984	NA -->
-<!-- fit_egag	1106163.9	0.054	6,842.382	0.952	0 -->
-<!-- fit_hclust	1112649.0	0.078	13,296.328	0.907	0 -->
-<!-- fit_hclustg	1113829.4	0.078	14,528.732	0.898	0 -->
-<!-- fit_efag	1115871.0	0.083	16,591.054	0.883	0 -->
-<!-- fit_efa	1115871.0	0.083	16,591.054	0.883	0 -->
+<!-- CFA Model Comparison
+Name	BIC	RMSEA	Chi2	CFI	BF
+fit_g	13466.62	0.106	325.704	0.784	Inf
+fit_ega	15870.94	0.026	72.825	0.988	NA
+fit_egag	15892.96	0.059	180.403	0.924	1.654961e-05
+fit_hclustg	15911.16	0.065	210.828	0.905	1.846821e-09
+fit_hclust	15913.39	0.062	182.492	0.921	6.080789e-10
+fit_efa	15941.59	0.073	253.472	0.877	4.576430e-16
+fit_efag	15941.59	0.073	253.472	0.877	4.576430e-16 -->
+
+<!-- Samples where CFA converged
+fit_ega	15870.94	0.026	72.825	0.988	NA - sample 1a
+fit_ega	28320.01	0.025	83.537	0.991	NA - sample 4
+fit_ega	20224.33	0.046	130.586	0.978	NA - sample 6
+it_ega	17647.14	0.038	98.571	0.973	NA - sample 7a
+fit_ega	68203.78	0.033	178.485	0.982	NA - sample 7b
+fit_ega	23336.33	0.036	102.630	0.976	NA - sample 7c
+fit_ega	40816.35	0.033	128.727	0.976	NA - sample 8a
+fit_ega	18031.48	0.031	83.225	0.977	NA - sample 8b
+it_ega	720615.2	0.041	2,068.422	0.980	NA - sample 9
+fit_ega	29023.36	0.052	181.784	0.948	NA - sample 11 
+fit_ega	25899.23	0.038	116.734	0.977	NA - sample 13 
+fit_ega	3975.352	0.040	65.620	0.975	NA - sampple 14 -->
+
+<!-- did not converge: df1b, df2, df3, df5, df10 (missing items), df12 (errors), df15 (errors), df16,  -->
 
@@
 We then fitted and compared using CFA various candidate structures emerging from the previous analyses, including a 1-factor model (the G-model), a 3-factor model (EFA), a 3+1 model (EFA + general factor), a 5-factor model (HCA), a 5+1 model (HCA + general factor), a 7-factor model (EGA), and a 7+1 model (EGA + general factor).
-The EGA model with 7 factors of item pairs provided the best fit with the lowest RMSEA (0.035), lowest $\chi^2$ (2306.30), highest CFI (0.984).
-It was followed by the EGA + general factor model (RMSEA = 0.054, $\chi^2$ = 6842.38, CFI = 0.952), and the HCA model with 5 factors (RMSEA = 0.078, $\chi^2$ = 13296.33, CFI = 0.907).
+The EGA model with 7 factors of item pairs provided the best fit with the lowest RMSEA (0.026), lowest $\chi^2$ (72.825), highest CFI (0.988).
+It was followed by the EGA + general factor model (RMSEA = 0.059, $\chi^2$ = 180.403, CFI = 0.065), and the HCA model with 5 factors (RMSEA = 0.062, $\chi^2$ = 182.492, CFI = 0.921).
 The other models performed poorly, with RMSEA > 0.08 and CFI < 0.90.
@@
 This result was relatively consistent across unique datasets with the EGA model providing the best fit.
-In all samples where CFA converged, it showed excellent performance with low RMSEA (≈ 0.025–0.046), high CFI (≥ 0.97), and substantially lower $\chi^2$ compared to alternative models.
-Adding a general factor systematically worsened fit, while hierarchical clustering and EFA-based models showed poorer performance (RMSEA > 0.06, CFI < 0.93).
+In all samples where CFA converged, it showed excellent performance with low RMSEA (≈ 0.025–0.052), high CFI (≥ 0.95), and substantially lower $\chi^2$ compared to alternative models.
+Adding a general factor systematically worsened fit, while hierarchical clustering and EFA-based models showed poorer performance (RMSEA > 0.05, CFI < 0.95).
 Although BIC values occasionally favored alternative specifications, Bayes factor comparisons overwhelmingly supported the EGA solution, confirming its robustness across datasets.
-
-<!-- did not converge: df1b, df2, df3, df5, df10 (missing items), df12 (errors), df15 (errors), df16,  -->
 

### 2025-10-22 paper/1_Initial/manuscript.qmd
finished results study 2

@@
 Additionally, one can note the low occurrence of extreme values (1 and 5), meaning that the bulk of answers varies between 3 values (assuming the IAS is implemented as a 5-point Likert scale following its validation).
-The samples using an analogue scale (samples 10a, 10b and 10c in the figure) display a more continuous and progressive spread of answers, seemingly improving the interindividual variability, although potentially displaying a secondary lower mode at \~2 (which might be suggesting the existence of potential clusters of participants).
+The samples using an analogue scale (samples 10, 11 and 12 in the figure) display a more continuous and progressive spread of answers, seemingly improving the interindividual variability, although potentially displaying a secondary lower mode at \~2 (which might be suggesting the existence of potential clusters of participants).
 The correlation matrix between all items shows an overall positive correlation pattern, with highly correlated pairs of items (e.g., Tickle-Itch, Urinate-Defecate, Pain-Wind, Hungry-Thursty) or triplets (Vomit-Sneeze-Cough, Temperature-Muscles-Pain).
@@
 
-The Body Perception Questionnaire Short Form [BPQ-SF, @cabrera2018assessing] contains 46 items measuring body awareness and autonomic reactivity on a 5-point Likert scale (e.g., “My heart often beats irregularly”).
-The very-short form (BPQ-VSF) contains 12 items from the body awareness subscale.
+The Body Perception Questionnaire Short Form [BPQ-SF, @cabrera2018assessing] contains 46 items measuring Body Awareness and Autonomic Reactivity on a 5-point Likert scale (e.g., “My heart often beats irregularly”).
+The very-short form (BPQ-VSF) contains 12 items from the Body Awareness subscale.
 For this study, scores from both versions were combined.
@@
 Associations will be estimated using multilevel regression models implemented in the glmmTMB package [@glmTMB].
-Each predictor will be entered separately, with the seven IAS item pairs identified in Study 1 (“Hungry–Thirsty”, “Muscles–Pain”, “Wind–Burp”, “Urinate–Defecate”, “Breathing–Heart”, “Bruise–Blood”, “Cough–Sneeze”) and the original IAS scale serving as outcomes.
+Each predictor will be entered separately, with the seven IAS item pairs identified in Study 1 (Hungry–Thirsty, Muscles–Pain, Wind–Burp, Urinate–Defecate, Breathing–Heart, Bruise–Blood, Cough–Sneeze) and the original IAS scale serving as outcomes.
 Models will include random intercepts and slopes by sample to account for between-study heterogeneity; when models fail to converge, a reduced structure with random intercepts only will be used.
@@
 <!-- Demographic correlates -->
-Age was positively associated across Ias correlates (mean r = .12), with all correlations significant. Gender showed near-zero effects (mean r = −.01), with 63% reaching significance.
+Age was positively associated across Ias correlates (mean r = .13), with all correlations significant.
+Gender showed near-zero effects (mean r = −.06), reaching significance only with the Hungry-Thirsty, Wind-Burp and Urinate-Defecate pairings.
 
 <!-- Interoceptive measures -->
-Several MAIA subscales showed consistent positive associations with the IAS: Noticing, Attention Regulation, Trusting, Emotional Awareness, Listening, and Self-Regulation (βs ≈ .18–.26).
-These effects were generally strongest for the full IAS, but often replicated with Hungry/Thirsty or Bruise/Blood pairings.
-By contrast, Autonomic Reactivity (BPQ; β = −.17) was reliably negative across most pairings, while Body Awareness (BPQ; β = .12) was weak and only reliable for Hungry/Thirsty and Bruise/Blood.
-Alexithymia measures were consistently negative, with robust effects across both the full IAS and pairings, except for the Affective dimension of the BVAQ which showed only a positive association with the Bruise/Blood sugar pairing (β = .04).
+Several MAIA subscales showed consistent positive associations with the IAS: Noticing, Body Listening, Attention Regulation, Trusting, Emotional Awareness, and Self-Regulation (mean r ≈ .18–.26), with effects generally stronger for the full IAS, with the exception of the Body Listenig dimension whose associations were stronger with the Bruise-Blood pairing.
+The Not Distracting subscale was significantly associated with the whole scale and with three of the seven pairs, namely Hungry–Thirsty, Bruise–Blood sugar, and Muscles–Pain (mean r ≈ .19–.13).
+By contrast, the Not Worrying subscale was only significant for the full IAS and the Hungry–Thirsty and Urinate–Defecate pairings (mean r ≈ −.009–.108).
+
+Autonomic Reactivity (BPQ; mean r = −.19) was reliably negative across most pairings, while Body Awareness (BPQ; mean r = .12) was weak and only reliable for Bruise-Blood.
+
+In terms of interoceptive deficits, alexithymia measures were consistently negative, with robust effects across both the full IAS and pairings, except for the Affective dimension of the BVAQ, which showed a positive association only with the Bruise–Blood sugar pairing (r = .16).
+Interoceptive confusion assessed with the ICQ was also consistently negatively associated with all pairings and the full IAS (mean r ≈ −.49–.20).
 
 <!-- Mood and psychopathology -->
-Depression (BDI; β = −.20) and anxiety (STAI-T; β = −.19) were consistently negative across the IAS and most pairings, with Hungry/Thirsty again emerging as a particularly sensitive correlate.
-Broader symptom indices (PHQ-15, PHQ-4, GAD-7) showed weaker but often reliable effects, although some were restricted to certain pairings (e.g., PHQ-15 with Hungry/Thirsty, Bruise/Blood).
-By contrast, PHQ-9 and MFQ averaged negatively but were largely nonsignificant, even with the full scale.
-Autistic traits were generally negative, especially Imagination (β = −.18), which showed broad consistency across pairings except Cough/Sneeze.
+Depression (BDI; mean r = −.20) and anxiety (STAI-T; mean r = −.19) were consistently negative across the IAS and most pairings, with Hungry–Thirsty again emerging as a particularly sensitive correlate.
+Notably, different measures indexing similar constructs showed distinct association patterns: the MFQ was largely nonsignificant despite measuring depressive symptoms comparable to for instance the BDI.
+Similarly, PHQ-9 followed a weaker and less reliable pattern.
+Related symptom measures (PHQ-15, PHQ-4, GAD-7) showed weaker but often reliable effects, although some were restricted to specific pairings (e.g., PHQ-15 not significant with Wind–Burp and Breathing–Heart).
+Notably, most of the mood measures (PHQ-9, BDI, PHQ-4, STAI-T, GAD-7) displayed stronger associations with the Hungry-Thristy pairing than the full IAS.
+
+<!-- Psychopathologies -->
+Autistic traits were generally negatively associated with the IAS, with Imagination (mean r = −.18) showing the most consistent effects across pairings, except for Cough–Sneeze.
+Most of the significant associations between the full IAS and autistic traits were driven by the first three pairings—Hungry–Thirsty, Bruise–Blood sugar, and Muscles–Pain—which showed the strongest and most reliable negative correlations.
+Beyond these, effects tended to weaken and often became nonsignificant, particularly for Patterns and Numbers, which did not correlate with any IAS correlate.
+Borderline Personality was only significantly associated with the Hungry–Thirsty pairing (mean r = −.14).
+
+Lastly, schizotypal traits (SPQ) were also generally negative and non-significant, but several significant associations with the full IAS appeared to be driven by particular pairings.
+
+Autistic traits were generally negatively associated with the IAS, with Imagination (mean r = −.18) showing the most consistent effects across pairings, except for Cough–Sneeze.
+Across subscales, most associations observed for the full IAS were primarily driven by the first three pairings—Hungry–Thirsty, Bruise–Blood sugar, and Muscles–Pain— which showed the strongest and most reliable negative correlations.
+Beyond these, effects tended to weaken and often became nonsignificant, particularly for Patterns and Numbers, which did not correlate with any IAS correlate, while Borderline Personality only correlated with the Hungry–Thirsty pairing (mean r = −.14).
+
+Schizotypal traits were generally negatively associated with the IAS, with Social Anxiety (mean r = −.11) and No Close Friends (mean r = −.12) showing the most consistent negative effects across pairings.
+Notably, although some facets did not show consistent associations with the overall IAS, they were significantly related to specific pairings.
+For example, Unusual Perceptions was associated with the Muscles–Pain and Urinate–Defecate pairings, whereas Eccentric was associated with the Hungry–Thirsty and Urinate–Defecate pairings.
 
 <!-- Personality and beliefs -->
-Within the Big Five, Openness (β = .14), Agreeableness (β = .05), and Conscientiousness (β = .03) showed small but consistent positive associations, most reliably captured by the full IAS but also evident in pairings.
-Honesty–Humility was uniquely negative, with significant associations for both the full scale and Hungry/Thirsty.
-Worldview measures were generally null, though belief in a comprehensible world (β = .11) and an “alive” world (β = .09) showed small but consistent positive associations, mainly with the full IAS and Hungry/Thirsty.
+Within the Big Five, Openness (mean r = .14), Agreeableness (mean r = .05), and Conscientiousness (mean r = .03) showed small but consistent positive associations, most reliably captured by the full IAS but also evident in pairings.
+Honesty–Humility showed a unique negative association with the full IAS scale, largely driven by the Hunger–Thirst and Bruise–Blood sugar item pairings.
+Similarly, Neuroticism was negatively associated with the full IAS, but this relationship was primarily attributable to the Hunger–Thirst and Wind–Burp pairings, with the strongest correlation observed for Hunger–Thirst (r = −.23).
+
+Worldview measures were largely null, but certain beliefs showed small yet consistent associations with specific IAS item pairings.
+Belief in a comprehensible world (“Understandable”) correlated positively with most pairings except Urinate–Defecate and Cough–Sneeze, while beliefs that the world is “Alive” and “Hierarchical” were associated with the full IAS and Hunger–Thirsty, and “Good” was uniquely linked to Muscles–Pain (mean r = .09).
+For the Lying Profile, only Lying Contextuality showed a notable negative association with the Bruise–Blood sugar pairing (r = −.12).
+
+Conspiracy Beliefs showed selective associations, with Global Conspiracies linked to the full IAS and several pairings (Original, Hunger–Thirsty, Cough–Sneeze, Urinate–Defecate; mean r = .103), Personal Wellbeing to the full IAS and Hunger–Thirsty (mean r = .086), and Information Control to Cough–Sneeze (mean r =  .06).
 
 <!-- Differences between the full IAS and item pairings -->
-Overall, the full IAS yielded the largest number of significant associations (25), but the Hungry/Thirsty (16) and Bruise/Blood sugar (11) pairings frequently showed equally strong or stronger effects.
-These item-level pairings often captured variance that the full scale did not, particularly for interoceptive and mood measures.
-In contrast, other pairings (e.g., Cough/Sneeze, Wind/Burp, Urinate/Defecate) contributed little unique variance.
-Together, these results suggest that while the full IAS captures broad dispositional tendencies, select pairings may provide more fine-grained sensitivity to specific domains, particularly interoception and affect.
+Overall, the full IAS yielded the largest number of significant associations (29), but these were often driven by specific item pairings rather than reflecting uniform effects across the scale.
+The Hungry–Thirsty (17) and Bruise–Blood sugar (10) pairings consistently produced equally strong or stronger effects, particularly for interoceptive, mood, and psychopathology measures.
+In contrast, other pairings (e.g., Cough–Sneeze, Wind–Burp, Urinate–Defecate) contributed little unique variance and rarely produced meaningful associations.
 
@@
 <!-- Study 2 findings -->
+
+<!-- - is the IAS really assessing interoception (lack of relationship with BPQ-awareness)
+- breathing - heart the most interoceptive items but less correlated (image figure 3?#)
+- Together, these results indicate that while the full IAS captures broad dispositional tendencies, its significant associations with external measures are frequently underpinned by a subset of item pairings, which appear more sensitive to specific interoceptive and affective domains.
+-->
+
 Study 2 provided further evidence for a domain-specific perspective.

### 2025-10-24 paper/1_Initial/manuscript.qmd
manuscript updated

@@
 Autistic traits were generally negatively associated with the IAS, with Imagination (mean r = −.18) showing the most consistent effects across pairings, except for Cough–Sneeze.
-Most of the significant associations between the full IAS and autistic traits were driven by the first three pairings—Hungry–Thirsty, Bruise–Blood sugar, and Muscles–Pain—which showed the strongest and most reliable negative correlations.
-Beyond these, effects tended to weaken and often became nonsignificant, particularly for Patterns and Numbers, which did not correlate with any IAS correlate.
-Borderline Personality was only significantly associated with the Hungry–Thirsty pairing (mean r = −.14).
-
-Lastly, schizotypal traits (SPQ) were also generally negative and non-significant, but several significant associations with the full IAS appeared to be driven by particular pairings.
-
-Autistic traits were generally negatively associated with the IAS, with Imagination (mean r = −.18) showing the most consistent effects across pairings, except for Cough–Sneeze.
 Across subscales, most associations observed for the full IAS were primarily driven by the first three pairings—Hungry–Thirsty, Bruise–Blood sugar, and Muscles–Pain— which showed the strongest and most reliable negative correlations.
@@
 
-Worldview measures were largely null, but certain beliefs showed small yet consistent associations with specific IAS item pairings.
+Primal world beliefs measures were largely null, but certain beliefs showed small yet consistent associations with specific IAS item pairings.
 Belief in a comprehensible world (“Understandable”) correlated positively with most pairings except Urinate–Defecate and Cough–Sneeze, while beliefs that the world is “Alive” and “Hierarchical” were associated with the full IAS and Hunger–Thirsty, and “Good” was uniquely linked to Muscles–Pain (mean r = .09).

### 2025-10-24 paper/1_Initial/manuscript.qmd
updated discussion study 2

@@
 <!-- Aim and conceptual focus -->
-Study 2 examined the dispositional correlates of the IAS and tested whether the refined 14-item version offers practical advantages over the original 21-item scale.
-The study provides insight into the conceptual boundaries of interoceptive self-reported accuracy across psychological domains.
+Study 2 examined the dispositional correlates of the IAS and evaluated whether the refined 14-item version offers practical advantages over the original 21-item scale.
+The findings clarify the conceptual boundaries of self-reported interoceptive accuracy across psychological domains and highlight the domain-specific nature of these associations.
 
-<!-- Interoception and mental health + context dependency -->
-The IAS converged robustly with other interoceptive self-report measures, particularly facets of the MAIA, and correlated more strongly with dynamic bodily monitoring (Autonomic Reactivity on the BPQ) than general body awareness [@brand2023; @campos2021; @todd2022].
-Item pairings reflecting visceral sensations, such as Hunger–Thirst, were consistently linked to lower depressive and anxiety symptoms [@brand2023; @lin2023], supporting theoretical models connecting interoception to emotion regulation and monitoring of internal bodily states [@khalsa2018interoception; @suksasilp2022towards].
+<!-- Interoception and correlates - item specific -->
+The IAS correlated robustly with other self-report interoceptive measures, particularly MAIA facets reflecting awareness, regulation, and trust in bodily signals.
+These associations were stronger with monitoring of autonomic reactivity (BPQ) than with general body awareness (BPQ) replicating previosu findings [@brand2023; @campos2021; @todd2022].
 
-At the same time, these associations were context-dependent: not all item pairings or bodily domains related equally to mood or somatic symptoms [@murphy2019; @koike2023].
-Emerging evidence suggests that interoceptive abilities (e.g., sensitivity, precision and metacognitive insight) may not uniformly predict mental health outcomes and may depend on measurement approach or sample characteristics [@@banellis2025interoceptive].
+Across mood and interoceptive measures, most item pairings showed at least moderate correlations, suggesting that the IAS shares variance with affective and bodily awareness constructs.
+In contrast, associations with psychopathology were more selective: significant correlations were mainly observed for visceral pairings such as Hunger–Thirsty and Bruise–Blood sugar, while other pairings were weak or nonsignificant.
+This pattern points to variation in how different interoceptive domains relate to affective and clinical traits [@murphy2019; @koike2023].
 
 <!-- Personality, worldview, and boundaries of interoception -->
-Associations with broader personality traits and high-order beliefs were modest.
-Small positive correlations with Openness and Agreeableness and weak associations with primal world beliefs (e.g., perceiving the world as alive or comprehensible) suggest that interoception may subtly interact with higher-level cognitive frameworks [@simkute2025interoception; @haustein2024interoception; @gabriele2022dissociations].
-However, the effects were weak and inconsistent, reinforcing that interoception primarily aligns with bodily self-perception rather than broad personality or worldview constructs.
+Associations with personality traits showed similar pattern.
+Effects for the full IAS often reflected contributions from specific pairings: Breathing–Heart correlated most strongly with Openness; Bruise–Blood sugar and Muscles–Pain with Extraversion; and Hunger–Thirsty with Neuroticism.
+Additionally, the negative correlation with Honesty–Humility in the full scale was mainly attributable to the Hunger–Thirsty and Bruise–Blood sugar pairings.
+These findings indicate that the strength of associations between interoceptive self-report and personality traits depends on the bodily domain represented by the items.
+
+Correlations with belief systems were small and inconsistent.
+Some primal world beliefs (e.g., perceiving the world as alive or comprehensible) showed weak positive associations with the full IAS and with certain pairings [@simkute2025interoception; @haustein2024interoception; @gabriele2022dissociations].
+These associations were not uniform across items, again reflecting variability in how interoceptive self-reports relate to broader cognitive or worldview constructs.
+
+Correlations with broader belief systems, including conspiracy beliefs and primal world beliefs, were generally small and inconsistent.
+Some weak positive associations were observed between the IAS and beliefs that the world is comprehensible or alive, and with certain conspiracy belief dimensions, particularly Global Conspiracies and Personal Wellbeing.
+These effects were largely limited to specific pairings, most notably Hunger–Thirsty and Bruise–Blood sugar, suggesting that any links between interoceptive self-report and belief systems are modest and not uniform across bodily domains.
 
 <!-- Contextual sensitivity and scale refinement -->
-Certain item pairings (e.g., Hunger–Thirst, Bruise–Blood sugar) captured associations with mood and interoception as strongly as, or stronger than, the full 21-item scale.
-This highlights the contextual nature of interoceptive accuracy: interoceptive tendencies manifest variably across bodily domains [@desmedt2022measures; @khalsa2018], emphasizing the need for context-specific items.
+Certain item pairings, notably Hunger–Thirsty and Bruise–Blood sugar, correlated with mood and interoceptive measures as strongly as, or more strongly than, the full IAS.
+These pairings accounted for many of the significant relationships observed across variables, whereas others (e.g., Cough–Sneeze, Wind–Burp) showed few consistent effects.
 
-The refined 14-item IAS performed comparably to the original scale, and item pairings sometimes provided greater sensitivity to specific interoceptive or affective domains, demonstrating that structural refinement can enhance efficiency and interpretability without sacrificing validity.
+The refined 14-item IAS performed comparably to the original 21-item version, maintaining similar patterns of association while reducing item redundancy.
+This supports the practical utility of the shortened version, which captures the same correlational structure with improved efficiency and interpretability.
 
 <!-- Summary -->
-Study 2 shows that interoceptive self-report is adaptive, context-sensitive, and most predictive in relation to mood and dynamic bodily monitoring.
-The refined IAS preserves construct validity while enabling more targeted assessment of domain-specific interoceptive tendencies.
+Overall, correlations between the IAS and external measures were not uniform but varied across bodily domains.
+The results indicate that some interoceptive item pairings, especially those representing visceral sensations, show stronger and more consistent relationships with interoceptive, affective, and personality measures.
+The refined 14-item IAS retains these patterns while providing a more concise and interpretable assessment of self-reported interoceptive accuracy.
 
@@
 
-<!-- AIms -->
+<!-- Aims -->
 The present study provides a comprehensive evaluation of the IAS, examining both its structure (study 1) and its dispositional correlates (study 2).

### 2025-10-24 paper/1_Initial/manuscript.qmd
Update manuscript.qmd

@@
 <!-- Study 1 findings -->
-Study 1 demonstrated that the IAS is best conceptualised as comprising tightly coupled item pairs, reflecting discrete bodily domains such as visceral sensations, musculoskeletal cues, and expulsion phenomena.
-The pairs emerged after several items (e.g., Tickle, Taste, Affective Touch) were removed due to their instability, redundancy, or poor associations with the other items.
-The resulting 14-item IAS retained the psychometric integrity of the original scale while improving interpretability and efficiency.
+A short version of the IAS was previously proposed by @lin2023, who suggested a 12-item version by removing items with local dependency, high difficulty, and/or low discrimination.
+Their parallel analysis supported a unidimensional structure, although this method tends to underestimate factor numbers in multidimensional data [@golino2017exploratory; @markos2024dimensionality].
+Consequently, the 12-item IAS was interpreted as reflecting a single underlying factor of interoceptive accuracy.
 
-A short version of the IAS has been proposed before.
-@lin2023 suggested a 12-item version by removing items with local dependency, high difficulty, and/or low discrimination.
-Their parallel analysis suggested unidimensionality, although parallel analysis is known to underestimate factor numbers in multidimensional data [@golino2017exploratory; @markos2024dimensionality].
+In contrast, Study 1 applied multiple complementary methods, including EGA, FA, and HCA.
+Across datasets and methods, the same tightly coupled item pairs consistently emerged, representing distinct bodily domains such as visceral sensations, musculoskeletal cues, and expulsion phenomena.
+Several items (e.g., Tickle, Taste, Affective Touch) were removed due to instability, redundancy, or weak associations, resulting in a refined 14-item IAS that retained psychometric robustness while improving interpretability and efficiency.
 
-In contrast, our study applied multiple methods including EGA, FA, and HCA yet the same pairs consistently emerged across datasets and demonstrated superior fit compared to alternative models, which challenges the assumption of unidimensionality of the IAS [@murphy2019; @brand2023].
-Although the short version of the IAS by  @lin2023 favoured a one-factor solution, their 12-item IAS was derived by removing locally dependent items identified through Item Response Theory (IRT).
-
-We found that these locally dependent items can instead be interpreted as meaningful pairs (e.g., Heart–Breath), reflecting distinct bodily domains.
-Because IRT assumes unidimensionality [@nguyen2014introduction], it may have treated these natural item clusters as statistical artefacts rather than as theoretically relevant structures within interoceptive accuracy.
+These findings challenge the assumption of IAS unidimensionality [@murphy2019; @brand2023].
+Whereas @lin2023 ’s IRT-based approach treated locally dependent items as artefacts to be removed, our results suggest that such dependencies may reflect theoretically meaningful pairs (e.g., Heart–Breath).
+Because IRT assumes unidimensionality [@nguyen2014introduction], it may have obscured these structured item clusters rather than as theoretically relevant structures within interoceptive accuracy.
 
@@
 This pattern highlights that questionnaires like the IAS may capture multiple facets of interoception rather than a single underlying dimension.
-Consequently, adopting a domain-specific approach could enhance construct validity by better reflecting the heterogeneity of interoceptive experiences.
 
-These findings are in line with inconsistencies in the literature concerning associations between the IAS and the BPQ Body Awareness.
-While some studies report significant negative associations [@lin2023], others have observed significant positive associations  [@brand2023; @campos2021; @gaggero2021; @todd2022], and still others none at all  [@murphy2019].
+These findings are in line with inconsistencies found in the literature concerning associations between the IAS and the BPQ Body Awareness.
+While some studies report significant negative associations [@lin2023], others have observed significant positive associations  [@brand2023; @campos2021; @gaggero2021; @todd2022], and others none at all [@murphy2019].
 In our study the full IAS was also not associated with the BPQ Body Awareness.
+This pattern is consistent with the idea that this subscale may capture maladaptive bodily experiences or autonomic dysfunction, rather than interoceptive accuracy per se.
 
-This pattern is consistent with the idea that this subscale may capture maladaptive bodily experiences or autonomic dysfunction, rather than interoceptive accuracy per se.
 However, the Body Awareness subscale of the BPQ has also been criticized for its ambiguous instructions.
@@
 
+<!-- Limitations -->
+One limitation worth noting is that we did not evaluate the IAS alongside other widely used questionnaires, such as the BPQ or MAIA.
+Although both are frequently employed in interoception research, they present important limitations.
+For example, the MAIA-2 contains subscales (e.g., Not-Worrying, Not-Distracting) with weak reliability and minimal relation to a general interoception factor [@ferentzi2021examining; @rogowska2023validation].
+Several other subscales primarily reflect higher-level cognitive tendencies, such as mindfulness and attentional regulation, rather than interoceptive body awareness [@todd2022; @vig2023self].
+Similarly, the BPQ’s Body Awareness and Autonomic Reactivity subscales show conceptual and psychometric concerns, and BPQ scores often overlap substantially with negative affect, raising questions about their specificity as measures of interoceptive sensibility [@campos2021; @gabriele2022dissociations; @vig2023self].
+
+Because the IAS is a newly developed questionnaire and the only one designed to assess interoceptive self-reported accuracy - a dimension previously assessed solely through objective tasks such as the HDT and HCT - our focus was on evaluating its structure and correlates without introducing established measures with documented shortcomings.
+Nonetheless, future research should employ novel methods, such as Exploratory Graph Analysis, to clarify the convergent and divergent validity of these questionnaires across interoceptive domains.
+
 <!-- IAS limitations and potential improvements -->
-These two studies revealed three main points.
+Nevertheless, these two studies revealed three main points.
 First,  in the datasets that included analogue-style ratings, these scales captured greater variability, further enhancing the ability to detect individual differences.
@@
 Such a scale would improve interpretability, sensitivity, and practical utility, ultimately enabling a more nuanced mapping of interoceptive abilities onto affective, cognitive, and health-related outcomes.
-
-<!-- Limitations -->
-One limitation worth noting is that we did not evaluate the IAS alongside other widely used questionnaires, such as the BPQ or MAIA.
-Although both are frequently employed in interoception research, they present important limitations.
-For example, the MAIA-2 contains subscales (e.g., Not-Worrying, Not-Distracting) with weak reliability and minimal relation to a general interoception factor [@ferentzi2021examining; @rogowska2023validation].
-Several other subscales primarily reflect higher-level cognitive tendencies, such as mindfulness and attentional regulation, rather than interoceptive body awareness [@todd2022; @vig2023self].
-Similarly, the BPQ’s Body Awareness and Autonomic Reactivity subscales show conceptual and psychometric concerns, and BPQ scores often overlap substantially with negative affect, raising questions about their specificity as measures of interoceptive sensibility [@campos2021; @gabriele2022dissociations; @vig2023self].
-
-Because the IAS is a newly developed questionnaire and the only one designed to assess interoceptive self-reported accuracy - a dimension previously assessed solely through objective tasks such as the HDT and HCT - our focus was on evaluating its structure and correlates without introducing established measures with documented shortcomings.
-Nonetheless, future research should employ novel methods, such as Exploratory Graph Analysis, to clarify the convergent and divergent validity of these questionnaires across interoceptive domains.
 

### 2025-10-27 paper/1_Initial/manuscript.qmd
results section re-written

@@
 The presence of redundant or unstable items (e.g., Tickle, Taste, Affective Touch) undermines interpretability and likely explains inconsistencies in prior factor-analytic findings [@campos2021; @lin2023].
-Nevertheless, the structured item pairs correspond to intuitive bodily domains—visceral, expulsion, musculoskeletal—supporting ecological validity.
+Nevertheless, the structured item pairs correspond to intuitive bodily domains - visceral, expulsion, musculoskeletal - supporting ecological validity.
 These findings highlight the need for targeted scale refinement and motivate future development of context-sensitive, multidimensional interoception measures.
@@
 <!-- Demographic correlates -->
-Age was positively associated across Ias correlates (mean r = .13), with all correlations significant.
-Gender showed near-zero effects (mean r = −.06), reaching significance only with the Hungry-Thirsty, Wind-Burp and Urinate-Defecate pairings.
+
+Age showed consistent positive standardized associations across IAS correlates (mean β = .13), with all effects significant.
+Gender displayed near-zero effects (mean β = −.06), significant only for the Hungry–Thirsty, Wind–Burp, and Urinate–Defecate pairings.
 
 <!-- Interoceptive measures -->
-Several MAIA subscales showed consistent positive associations with the IAS: Noticing, Body Listening, Attention Regulation, Trusting, Emotional Awareness, and Self-Regulation (mean r ≈ .18–.26), with effects generally stronger for the full IAS, with the exception of the Body Listenig dimension whose associations were stronger with the Bruise-Blood pairing.
-The Not Distracting subscale was significantly associated with the whole scale and with three of the seven pairs, namely Hungry–Thirsty, Bruise–Blood sugar, and Muscles–Pain (mean r ≈ .19–.13).
-By contrast, the Not Worrying subscale was only significant for the full IAS and the Hungry–Thirsty and Urinate–Defecate pairings (mean r ≈ −.009–.108).
 
-Autonomic Reactivity (BPQ; mean r = −.19) was reliably negative across most pairings, while Body Awareness (BPQ; mean r = .12) was weak and only reliable for Bruise-Blood.
+MAIA subscales showed robust positive standardized effects with the IAS.
+Noticing yielded the strongest association (mean β = .26), followed by Emotional Awareness (β = .20) and related subscales—Body Listening, Attention Regulation, Trusting, and Self-Regulation—each in the .20–.26 range, all significant.
+Effects were generally strongest for the full IAS, except for Body Listening, which peaked for the Bruise–Blood pairing.
+Not Distracting was weakly but significantly positive (mean β = .06), primarily for Hungry–Thirsty, Bruise–Blood, and Muscles–Pain.
+Not Worrying was significant only for the full IAS and the Hungry–Thirsty and Urinate–Defecate pairings (β ≈ −.01 to .11).
 
-In terms of interoceptive deficits, alexithymia measures were consistently negative, with robust effects across both the full IAS and pairings, except for the Affective dimension of the BVAQ, which showed a positive association only with the Bruise–Blood sugar pairing (r = .16).
-Interoceptive confusion assessed with the ICQ was also consistently negatively associated with all pairings and the full IAS (mean r ≈ −.49–.20).
+Autonomic Reactivity (BPQ; mean β = −.19) was reliably negative across pairings, reaching significance for all except the Bruise–Blood sugar and Breathing–Heart pairings.
+In contrast, Body Awareness (BPQ; mean β = .12) was weakly positive and significant only for Bruise–Blood.
+
+Interoceptive deficits showed consistent negative standardized effects.
+Alexithymia measures (TAS, BVAQ) were robustly negative (β ≈ −.18 to −.24), except for the BVAQ Affective subscale, which was positive for Bruise–Blood (β = .16).
+Interoceptive confusion (ICQ) was also strongly negative across all IAS measures (mean β ≈ −.42; range = −.49 to −.20).
 
 <!-- Mood and psychopathology -->
-Depression (BDI; mean r = −.20) and anxiety (STAI-T; mean r = −.19) were consistently negative across the IAS and most pairings, with Hungry–Thirsty again emerging as a particularly sensitive correlate.
-Notably, different measures indexing similar constructs showed distinct association patterns: the MFQ was largely nonsignificant despite measuring depressive symptoms comparable to for instance the BDI.
-Similarly, PHQ-9 followed a weaker and less reliable pattern.
-Related symptom measures (PHQ-15, PHQ-4, GAD-7) showed weaker but often reliable effects, although some were restricted to specific pairings (e.g., PHQ-15 not significant with Wind–Burp and Breathing–Heart).
-Notably, most of the mood measures (PHQ-9, BDI, PHQ-4, STAI-T, GAD-7) displayed stronger associations with the Hungry-Thristy pairing than the full IAS.
+
+Depression (BDI; mean β = −.20) and anxiety (STAI-T; mean β = −.19) showed consistent negative associations across the IAS and pairings, strongest for Hungry–Thirsty.
+Related constructs diverged somewhat: MFQ was largely nonsignificant; PHQ-9 and other mood indices (PHQ-15, PHQ-4, GAD-7) produced weaker but often reliable negative βs (typically −.10 to −.15), with effects sometimes limited to particular pairings (e.g., PHQ-15 nonsignificant for Wind–Burp and Breathing–Heart).
+Hungry–Thirsty consistently yielded the strongest standardized effects.
 
 <!-- Psychopathologies -->
-Autistic traits were generally negatively associated with the IAS, with Imagination (mean r = −.18) showing the most consistent effects across pairings, except for Cough–Sneeze.
-Across subscales, most associations observed for the full IAS were primarily driven by the first three pairings—Hungry–Thirsty, Bruise–Blood sugar, and Muscles–Pain— which showed the strongest and most reliable negative correlations.
-Beyond these, effects tended to weaken and often became nonsignificant, particularly for Patterns and Numbers, which did not correlate with any IAS correlate, while Borderline Personality only correlated with the Hungry–Thirsty pairing (mean r = −.14).
 
-Schizotypal traits were generally negatively associated with the IAS, with Social Anxiety (mean r = −.11) and No Close Friends (mean r = −.12) showing the most consistent negative effects across pairings.
-Notably, although some facets did not show consistent associations with the overall IAS, they were significantly related to specific pairings.
-For example, Unusual Perceptions was associated with the Muscles–Pain and Urinate–Defecate pairings, whereas Eccentric was associated with the Hungry–Thirsty and Urinate–Defecate pairings.
+Autistic traits were generally negatively associated with IAS scores.
+Imagination (mean β = −.18) showed the most consistent pattern across pairings except Cough–Sneeze.
+Most full-IAS associations were driven by Hungry–Thirsty, Bruise–Blood sugar, and Muscles–Pain, which yielded the largest negative coefficients.
+Beyond these, effects weakened or became nonsignificant- Patterns and Numbers showed none, and Borderline Personality was associated only with Hungry–Thirsty (mean β = −.14).
+
+Schizotypal traits showed similarly negative coefficients, with Social Anxiety (mean β = −.11) and No Close Friends (mean β = −.12) most consistent.
+Some facets were unrelated to the overall IAS but linked to specific pairings: Unusual Perceptions with Muscles–Pain and Urinate–Defecate, and Eccentric with Hungry–Thirsty and Urinate–Defecate.
 
 <!-- Personality and beliefs -->
-Within the Big Five, Openness (mean r = .14), Agreeableness (mean r = .05), and Conscientiousness (mean r = .03) showed small but consistent positive associations, most reliably captured by the full IAS but also evident in pairings.
-Honesty–Humility showed a unique negative association with the full IAS scale, largely driven by the Hunger–Thirst and Bruise–Blood sugar item pairings.
-Similarly, Neuroticism was negatively associated with the full IAS, but this relationship was primarily attributable to the Hunger–Thirst and Wind–Burp pairings, with the strongest correlation observed for Hunger–Thirst (r = −.23).
 
-Primal world beliefs measures were largely null, but certain beliefs showed small yet consistent associations with specific IAS item pairings.
-Belief in a comprehensible world (“Understandable”) correlated positively with most pairings except Urinate–Defecate and Cough–Sneeze, while beliefs that the world is “Alive” and “Hierarchical” were associated with the full IAS and Hunger–Thirsty, and “Good” was uniquely linked to Muscles–Pain (mean r = .09).
-For the Lying Profile, only Lying Contextuality showed a notable negative association with the Bruise–Blood sugar pairing (r = −.12).
+Among Big Five traits, Openness (mean β = .10), Agreeableness (β = .08), and Conscientiousness (β = .11) showed small but consistent positive effects, most evident for the full IAS.
+Honesty–Humility (mean β = −.10) showed a small negative effect, primarily for Hungry–Thirsty and Bruise–Blood sugar.
+Neuroticism (mean β = −.13) was negatively associated with the IAS, with the strongest β for Bruise–Blood (β = −.23).
 
-Conspiracy Beliefs showed selective associations, with Global Conspiracies linked to the full IAS and several pairings (Original, Hunger–Thirsty, Cough–Sneeze, Urinate–Defecate; mean r = .103), Personal Wellbeing to the full IAS and Hunger–Thirsty (mean r = .086), and Information Control to Cough–Sneeze (mean r =  .06).
+Primal world beliefs were largely null, with small positive standardized coefficients for certain beliefs: “Understandable,” “Alive,” and “Hierarchical” were weakly positive for the full IAS and Hungry–Thirsty (β ≈ .05–.10), while “Good” was uniquely positive for Muscles–Pain (β ≈ .09).
+Within the Lying Profile, only Lying Contextuality showed a modest negative coefficient for Bruise–Blood (β = −.12).
+
+Conspiracy Beliefs produced selective small positive effects.
+Global Conspiracies (GCBS) were associated with the full IAS and several pairings (mean β = .10), Government Malfeasance (β = .05) with Cough–Sneeze, and Extraterrestrial beliefs (β = .03) with Muscles–Pain.
 
 <!-- Differences between the full IAS and item pairings -->
-Overall, the full IAS yielded the largest number of significant associations (29), but these were often driven by specific item pairings rather than reflecting uniform effects across the scale.
-The Hungry–Thirsty (17) and Bruise–Blood sugar (10) pairings consistently produced equally strong or stronger effects, particularly for interoceptive, mood, and psychopathology measures.
-In contrast, other pairings (e.g., Cough–Sneeze, Wind–Burp, Urinate–Defecate) contributed little unique variance and rarely produced meaningful associations.
+
+Overall, the full IAS produced the greatest number of significant standardized effects (29), though many were driven by specific pairings rather than uniform scale-wide associations.
+Hungry–Thirsty (17) and Bruise–Blood sugar (10) consistently yielded the strongest standardized coefficients, especially for interoceptive, mood, and psychopathology measures.
+Other pairings (Cough–Sneeze, Wind–Burp, Urinate–Defecate) contributed little unique variance and rarely yielded meaningful standardized effects.
 

### 2025-10-27 paper/1_Initial/manuscript.qmd
updated results study 1

@@
 Regarding its validity, the IAS has naturally been compared to other interoception-related measures, and shows a positive correlations with most facets of the MAIA [@mehling2018multidimensional; @gaggero2021], except for the Not-Distracting and Not-Worrying subscales [@brand2023] - which were previously highlighted as related to non-interoceptive abilities [@ferentzi2021examining].
-Interestingly, findings on the correlation between the IAS and the body awareness dimension of the BPQ (i.e., BPQ-A) have been mixed: some studies report small positive correlations [@brand2023; @campos2021; @koike2023], while others find small negative correlations [@lin2023] or no correlation at all [@murphy2019].
+Interestingly, findings on the correlation between the IAS and the body awareness dimension of the BPQ, have been mixed: some studies report small positive correlations [@brand2023; @campos2021; @koike2023], while others find small negative correlations [@lin2023] or no correlation at all [@murphy2019; @gaggero2021].
 Positive correlations have also been observed with the "observation" and "description" subscales of the Five Facet Mindfulness Questionnaire [FFMQ, @baer2006using; @brand2023; @koike2023], as well as with the "non-reactivity" and "acting with awareness" subscales [@koike2023].
@@
 MAIA subscales showed robust positive standardized effects with the IAS.
-Noticing yielded the strongest association (mean β = .26), followed by Emotional Awareness (β = .20) and related subscales—Body Listening, Attention Regulation, Trusting, and Self-Regulation—each in the .20–.26 range, all significant.
+Noticing yielded the strongest association (mean β = .26), followed by Emotional Awareness (β = .20) and related subscales - Body Listening, Attention Regulation, Trusting, and Self-Regulation, each in the .20–.26 range, all significant.
 Effects were generally strongest for the full IAS, except for Body Listening, which peaked for the Bruise–Blood pairing.
@@
 
-Autistic traits were generally negatively associated with IAS scores.
+Autistic traits (ASQ) were generally negatively associated with IAS scores.
 Imagination (mean β = −.18) showed the most consistent pattern across pairings except Cough–Sneeze.
@@
 <!-- Aim and conceptual focus -->
-Study 2 examined the dispositional correlates of the IAS and evaluated whether the refined 14-item version offers practical advantages over the original 21-item scale.
-The findings clarify the conceptual boundaries of self-reported interoceptive accuracy across psychological domains and highlight the domain-specific nature of these associations.
+
+Study 2 examined the dispositional correlates of the IAS and whether the refined 14-item version offers practical advantages over the original 21-item scale.
+The findings clarify the conceptual boundaries of self-reported interoceptive accuracy and underscore the domain-specific nature of these standardized associations.
 
 <!-- Interoception and correlates - item specific -->
-The IAS correlated robustly with other self-report interoceptive measures, particularly MAIA facets reflecting awareness, regulation, and trust in bodily signals.
-These associations were stronger with monitoring of autonomic reactivity (BPQ) than with general body awareness (BPQ) replicating previosu findings [@brand2023; @campos2021; @todd2022].
+The IAS showed positive associations with most MAIA facets, except for the Not-Distracting and Not-Worrying subscales, replicating prior findings [@brand2023].
+Associations with the BPQ Body Awareness subscale were consistent with previous reports ona non-existing association between these measures [@murphy2019; @gaggero2021], whereas indices of autonomic reactivity were more strongly and negatively associated with IAS scores, supporting earlier observations that reactivity may reflect aspects of bodily signal processing captured by self-reported interoceptive accuracy [@todd2022].
 
-Across mood and interoceptive measures, most item pairings showed at least moderate correlations, suggesting that the IAS shares variance with affective and bodily awareness constructs.
-In contrast, associations with psychopathology were more selective: significant correlations were mainly observed for visceral pairings such as Hunger–Thirsty and Bruise–Blood sugar, while other pairings were weak or nonsignificant.
-This pattern points to variation in how different interoceptive domains relate to affective and clinical traits [@murphy2019; @koike2023].
+In contrast, measures of interoceptive difficulties, including alexithymia and interoceptive confusion, were negatively associated with IAS scores, consistent with prior research [@brand2023; @koike2023; @lin2023; @murphy2019].
+These associations were strongest for visceral pairings, such as Hungry–Thirsty and Bruise–Blood sugar, and weaker or nonsignificant for other bodily domains, highlighting the domain-specific nature of interoceptive self-report.
+
+Across mood and interoceptive variables, most item pairings displayed small-to-moderate standardized coefficients, indicating shared variance between interoceptive self-reports and affective tendencies.
+In contrast, associations with psychopathology were more selective: negative βs were primarily observed for visceral pairings such as Hungry–Thirsty and Bruise–Blood sugar, whereas other domains yielded weaker or nonsignificant effects.
+This pattern suggests that self-reported interoceptive accuracy is more strongly associated with affective and clinical traits for visceral sensations than for exteroceptive or respiratory ones [@murphy2019; @koike2023].
 
 <!-- Personality, worldview, and boundaries of interoception -->
-Associations with personality traits showed similar pattern.
-Effects for the full IAS often reflected contributions from specific pairings: Breathing–Heart correlated most strongly with Openness; Bruise–Blood sugar and Muscles–Pain with Extraversion; and Hunger–Thirsty with Neuroticism.
-Additionally, the negative correlation with Honesty–Humility in the full scale was mainly attributable to the Hunger–Thirsty and Bruise–Blood sugar pairings.
-These findings indicate that the strength of associations between interoceptive self-report and personality traits depends on the bodily domain represented by the items.
 
-Correlations with belief systems were small and inconsistent.
-Some primal world beliefs (e.g., perceiving the world as alive or comprehensible) showed weak positive associations with the full IAS and with certain pairings [@simkute2025interoception; @haustein2024interoception; @gabriele2022dissociations].
-These associations were not uniform across items, again reflecting variability in how interoceptive self-reports relate to broader cognitive or worldview constructs.
+Associations with personality traits followed a similar domain-specific structure.
+Effects for the full IAS largely reflected contributions from specific pairings: Openness showed its strongest βs for Breathing–Heart, Neuroticism and Honesty–Humility for Hungry–Thirsty and Bruise–Blood sugar, and Conscientiousness for the full scale.
+These results indicate that associations between interoceptive self-report and personality dimensions may depend on the bodily domain represented.
 
-Correlations with broader belief systems, including conspiracy beliefs and primal world beliefs, were generally small and inconsistent.
-Some weak positive associations were observed between the IAS and beliefs that the world is comprehensible or alive, and with certain conspiracy belief dimensions, particularly Global Conspiracies and Personal Wellbeing.
-These effects were largely limited to specific pairings, most notably Hunger–Thirsty and Bruise–Blood sugar, suggesting that any links between interoceptive self-report and belief systems are modest and not uniform across bodily domains.
+Associations with belief systems were uniformly small.
+Weak positive standardized coefficients emerged between the IAS and certain primal world beliefs (e.g., perceiving the world as comprehensible or alive) and selected conspiracy belief dimensions, particularly Global Conspiracies and Personal Wellbeing.
+These effects were limited to specific pairings - most often Hungry–Thirsty and Bruise–Blood sugar—indicating that links between interoceptive self-report and broader cognitive or worldview constructs are modest and domain-specific.
 
 <!-- Contextual sensitivity and scale refinement -->
-Certain item pairings, notably Hunger–Thirsty and Bruise–Blood sugar, correlated with mood and interoceptive measures as strongly as, or more strongly than, the full IAS.
-These pairings accounted for many of the significant relationships observed across variables, whereas others (e.g., Cough–Sneeze, Wind–Burp) showed few consistent effects.
-
-The refined 14-item IAS performed comparably to the original 21-item version, maintaining similar patterns of association while reducing item redundancy.
-This supports the practical utility of the shortened version, which captures the same correlational structure with improved efficiency and interpretability.
+The refined 14-item IAS performed similarly to the original 21-item version, reproducing comparable standardized effect patterns while reducing redundancy.
+This suggests that the shortened scale captures the same latent structure with improved efficiency and interpretability, though further validation across independent samples is warranted.
 
 <!-- Summary -->
-Overall, correlations between the IAS and external measures were not uniform but varied across bodily domains.
-The results indicate that some interoceptive item pairings, especially those representing visceral sensations, show stronger and more consistent relationships with interoceptive, affective, and personality measures.
-The refined 14-item IAS retains these patterns while providing a more concise and interpretable assessment of self-reported interoceptive accuracy.
+
+Overall, standardized effects between the IAS and external constructs were not uniform but varied across bodily domains.
+Visceral pairings, particularly Hungry–Thirsty and Bruise–Blood sugar, showed the strongest and most consistent standardized relationships with interoceptive, affective, and personality measures.
+The refined 14-item IAS preserves these domain-specific associations, offering a more parsimonious, though potentially approximateassessment of self-reported interoceptive accuracy.
 

### 2025-10-28 paper/1_Initial/manuscript.qmd
Summarize
@AnafNeves I think we can summarize the questionnaires list like that, without listing the scales details or item examples

@@
     roles:
-      - bla bla
+      - Writing – review & editing
     affiliations:
@@
 
-<!-- Interoception Related -->
-#### Interoception Related
+#### Interoception
 
+Interoception-related measures included the Multidimensional Assessment of Interoceptive Awareness Version-2 [MAIA-2, @mehling2018multidimensional], the Body Perception Questionnaire Short Form [BPQ-SF, @cabrera2018assessing], and the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia].
+We also included the Toronto Alexithymia Scale [TAS-20, @bagby1994twenty], and the Bermond–Vorst Alexithymia Questionnaire [BVAQ, @vorst2001validity], due to the close relationship between interoception deficits and alexithymia.
+<!--
 The Multidimensional Assessment of Interoceptive Awareness Version-2 [MAIA-2, @mehling2018multidimensional] is a 37-item questionnaire assessing eight dimensions of interoception: Noticing, Not-Distracting, Not-Worrying, Attention Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust.
-Responses are rated on a 6-point Likert scale (e.g., “I notice when I am uncomfortable in my body”).
+Responses are rated on a 6-point Likert scale (e.g., "I notice when I am uncomfortable in my body").
 
@@
 The BVAQ also provides two higher-order factors, namely affective and cognitive (e.g., “I like to tell others how I feel”).
+-->
 

### 2025-10-29 paper/1_Initial/manuscript.qmd
Summarised measures
@DominiqueMakowski

@@
 #### Mood and Anxiety Related
+Mood-related measures included the Beck Depression Inventory-II [BDI-II, @beck1996beck], the Patient Health Questionnaire-4 [PHQ-4, @kroenke2009ultra], the Patient Health Questionnaire-9 [PHQ-9, @kroenke2001phq], the Patient Health Questionnaire-15 [PHQ-15, @kroenke2002phq], the Short Mood and Feelings Questionnaire [SMFQ, @angold1995development], the State–Trait Anxiety Inventory Trait Version [STAI-T, @spielberger1970manual], and the Generalized Anxiety Disorder Scale [GAD-7, @spitzer2006brief].
+We also included the PHQ-2 [@kroenke2003patient] and General Anxiety Disorder-2 [GAD-2, @kroenke2007anxiety], which were combined with the PHQ-4 scores, and scores from the shorter version of the STAIT-5 [@zsido2020development], which were combined with the STAI-T.
+Mood measures were included given the well-established association between interoceptive deficits and mental health conditions [@khalsa2018].
+
+<!-- 
 The Beck Depression Inventory-II [BDI-II, @beck1996beck] is a 21-item measure of depressive symptom severity, including psychological (e.g., guilt) and physiological (e.g., loss of energy) components.
@@
 The Generalized Anxiety Disorder Scale [GAD-7, @spitzer2006brief] is a 7-item measure of generalized anxiety symptoms rated on a 4-point Likert scale (e.g., “Not being able to stop or control worrying”).
-
-<!-- Personality -->
-#### Personality
-The NEO Five-Factor Inventory, neuroticism subscale [NEO-FFI, @costa1992personality] is a 12-item measure of neuroticism, assessing the general tendency to experience negative emotions such as fear, sadness, or disgust.
-Items are rated on a 5-point Likert scale (e.g., “I often feel inferior to others”).
-
-The Mini International Personality Item Pool [MINI-IPIP6, @sibley2011mini] includes 24 items measuring six broad traits: Agreeableness, Conscientiousness, Neuroticism, Openness, Extraversion, and Honesty-Humility.
-Items were scored on visual analogue scales in our samples (originally 7-point Likert scales; e.g., “Have a vivid imagination”).
-
-The Big Five Inventory Short Form [BFI-S, @rammstedt2007measuring] is a 10-item measure of the Big Five traits, rated on a 7-point Likert scale (e.g., “I see myself as someone who … is considerate and kind to almost everyone”).
+-->
 
@@
 #### Psychopathology
-The Personality Inventory for DSM-5 Short Form [PID-5-SF, @thimm2016personality] consists of 25 items rated on a 4-point Likert scale, measuring five domains: disinhibition, antagonism, detachment, negative affect, and psychoticism (e.g., “Plenty of people are out to get me”).
+Personality pathology-related measures included the Personality Inventory for DSM-5 Short Form [PID-5-SF, @thimm2016personality], the Schizotypal Personality Questionnaire – Brief Revised [SPQ-BR, @davidson2016schizotypal], the McLean Screening Instrument for Borderline Personality Disorder [MSI-BPD, @zanarini2003zanarini], and the Autism Spectrum Quotient Short Form [ASQ-S, @hoekstra2011construction].
+Similarily, these measures were included due to established associations between various psychopathologies and interoceptive disruptions [@leao2025interoception].
+
+<!-- The Personality Inventory for DSM-5 Short Form [PID-5-SF, @thimm2016personality] consists of 25 items rated on a 4-point Likert scale, measuring five domains: disinhibition, antagonism, detachment, negative affect, and psychoticism (e.g., “Plenty of people are out to get me”).
 
@@
 Items are rated on a 4-point Likert scale (e.g., “I find it difficult to work out people’s intentions”).
+-->
+
+<!-- Personality -->
+#### Personality
+Personality-related measures included the NEO Five-Factor Inventory, Neuroticism subscale [NEO-FFI, @costa1992personality], the Mini International Personality Item Pool [MINI-IPIP6, @sibley2011mini], and the Big Five Inventory Short Form [BFI-S, @rammstedt2007measuring].
+Although associations between personality and interoception have been less frequently explored than those involving mood or psychopathology, previous research has identified links between neuroticism and extroversion and interoceptive sensibility using the MAIA and BPQ measures.
+This study therefore included extended personality measures to clarify the broader relationships between interoception and personality traits beyond neuroticism and extraversion [@pearson2022two].
+
+<!-- The NEO Five-Factor Inventory, neuroticism subscale [NEO-FFI, @costa1992personality] is a 12-item measure of neuroticism, assessing the general tendency to experience negative emotions such as fear, sadness, or disgust.
+Items are rated on a 5-point Likert scale (e.g., “I often feel inferior to others”).
+
+The Mini International Personality Item Pool [MINI-IPIP6, @sibley2011mini] includes 24 items measuring six broad traits: Agreeableness, Conscientiousness, Neuroticism, Openness, Extraversion, and Honesty-Humility.
+Items were scored on visual analogue scales in our samples (originally 7-point Likert scales; e.g., “Have a vivid imagination”).
+
+The Big Five Inventory Short Form [BFI-S, @rammstedt2007measuring] is a 10-item measure of the Big Five traits, rated on a 7-point Likert scale (e.g., “I see myself as someone who … is considerate and kind to almost everyone”).
+-->
 
@@
 #### Beliefs and Misbeliefs
-The Generic Conspiracist Beliefs Scale [GCBS, @brotherton2013measuring] is a 15-item measure assessing five dimensions of conspiracy beliefs: government malfeasance, extraterrestrial cover-up, malevolent global conspiracies, personal wellbeing, and control of information.
+Beliefs- and misbeliefs-related measures included the Generic Conspiracist Beliefs Scale [GCBS, @brotherton2013measuring], the Primal World Beliefs Inventory [PI-99, @clifton2019primal] and its short form [PI-18, @clifton2021brief], and the Lie Scale [LIE, @makowski2023structure].
+These instruments assess individual differences in conspiracist, world, and lying beliefs.
+This domain represents a novel avenue of research in the context of interoception, as such beliefs have not been previously assessed in relation to interoceptive processes.
+
+<!-- The Generic Conspiracist Beliefs Scale [GCBS, @brotherton2013measuring] is a 15-item measure assessing five dimensions of conspiracy beliefs: government malfeasance, extraterrestrial cover-up, malevolent global conspiracies, personal wellbeing, and control of information.
 Items are scored on a 5-point Likert scale (e.g., “Secret organizations communicate with extraterrestrials, but keep this fact from the public”).
@@
 Items are scored on visual analogue scales (e.g., “I am a good liar”).
+-->
 

### 2025-10-29 paper/1_Initial/manuscript.qmd
some changes to study 2 conclusion

@@
 The IAS showed positive associations with most MAIA facets, except for the Not-Distracting and Not-Worrying subscales, replicating prior findings [@brand2023].
-Associations with the BPQ Body Awareness subscale were consistent with previous reports ona non-existing association between these measures [@murphy2019; @gaggero2021], whereas indices of autonomic reactivity were more strongly and negatively associated with IAS scores, supporting earlier observations that reactivity may reflect aspects of bodily signal processing captured by self-reported interoceptive accuracy [@todd2022].
+Associations with the BPQ Body Awareness subscale were consistent with previous reports on a non-existing association between these measures [@murphy2019; @gaggero2021], whereas indices of autonomic reactivity were more strongly and negatively associated with IAS scores, supporting earlier observations that reactivity may reflect aspects of bodily signal processing captured by self-reported interoceptive accuracy [@todd2022].
 
@@
 Across mood and interoceptive variables, most item pairings displayed small-to-moderate standardized coefficients, indicating shared variance between interoceptive self-reports and affective tendencies.
-In contrast, associations with psychopathology were more selective: negative βs were primarily observed for visceral pairings such as Hungry–Thirsty and Bruise–Blood sugar, whereas other domains yielded weaker or nonsignificant effects.
-This pattern suggests that self-reported interoceptive accuracy is more strongly associated with affective and clinical traits for visceral sensations than for exteroceptive or respiratory ones [@murphy2019; @koike2023].
+In contrast, associations with psychopathology were more selective: negative associations were primarily observed for visceral pairings such as Hungry–Thirsty and Bruise–Blood sugar, whereas other domains yielded weaker or nonsignificant effects.
+This pattern suggests that self-reported interoceptive accuracy is more strongly associated with affective and clinical traits for visceral sensations than for somatic or respiratory reflexes [@murphy2019; @koike2023].
 
@@
 Associations with personality traits followed a similar domain-specific structure.
-Effects for the full IAS largely reflected contributions from specific pairings: Openness showed its strongest βs for Breathing–Heart, Neuroticism and Honesty–Humility for Hungry–Thirsty and Bruise–Blood sugar, and Conscientiousness for the full scale.
+Effects for the full IAS largely reflected contributions from specific pairings: Openness showed its strongest associations for Breathing–Heart, Neuroticism and Honesty–Humility for Hungry–Thirsty and Bruise–Blood sugar, and Conscientiousness for the full scale.
 These results indicate that associations between interoceptive self-report and personality dimensions may depend on the bodily domain represented.
@@
 Associations with belief systems were uniformly small.
-Weak positive standardized coefficients emerged between the IAS and certain primal world beliefs (e.g., perceiving the world as comprehensible or alive) and selected conspiracy belief dimensions, particularly Global Conspiracies and Personal Wellbeing.
+Weak positive associations emerged between the IAS and certain primal world beliefs (e.g., perceiving the world as comprehensible or alive) and selected conspiracy belief dimensions, particularly Global Conspiracies and Personal Wellbeing.
 These effects were limited to specific pairings - most often Hungry–Thirsty and Bruise–Blood sugar—indicating that links between interoceptive self-report and broader cognitive or worldview constructs are modest and domain-specific.
 
-<!-- Contextual sensitivity and scale refinement -->
-The refined 14-item IAS performed similarly to the original 21-item version, reproducing comparable standardized effect patterns while reducing redundancy.
-This suggests that the shortened scale captures the same latent structure with improved efficiency and interpretability, though further validation across independent samples is warranted.
-
-<!-- Summary -->
-
+<!-- Short IAS benefits and summary-->
+The 14-item IAS performed similarly to the original 21-item version, showing comparable patterns of association with mood, psychopathology, and interoceptive measures.
 Overall, standardized effects between the IAS and external constructs were not uniform but varied across bodily domains.
-Visceral pairings, particularly Hungry–Thirsty and Bruise–Blood sugar, showed the strongest and most consistent standardized relationships with interoceptive, affective, and personality measures.
-The refined 14-item IAS preserves these domain-specific associations, offering a more parsimonious, though potentially approximateassessment of self-reported interoceptive accuracy.
+Visceral item pairs, particularly Hungry–Thirsty and Bruise–Blood sugar, showed the strongest and most consistent relationships with interoceptive, affective, and personality measures, whereas other pairs contributed little unique information, particularily in measures of psychopathologies and beliefs.
+These findings suggest that the shorter scale efficiently preserves these domain-specific associations, offering a more parsimonious assessment of self-reported interoceptive accuracy, though further validation across independent samples is warranted.
 

### 2025-10-30 paper/1_Initial/manuscript.qmd
changes to manuscript

@@
 <!-- Study 2 findings -->
-
-<!-- - is the IAS really assessing interoception (lack of relationship with BPQ-awareness)
-- breathing - heart the most interoceptive items but less correlated (image figure 3?#)
-- Together, these results indicate that while the full IAS captures broad dispositional tendencies, its significant associations with external measures are frequently underpinned by a subset of item pairings, which appear more sensitive to specific interoceptive and affective domains.
--->
-
-Study 2 provided further evidence for a domain-specific perspective.
-Certain item pairings, particularly Hunger-Thirst, Bruise-Blood sugar, and Muscles-Pain, showed consistent negative correlations with depression and anxiety measures, sometimes approaching or even surpassing the strength of associations observed for the full IAS scale.
-Notably, Hunger–Thirst and Bruise–Blood sugar were also the only pairs, out of the seven examined, that displayed significant positive correlations with the BPQ Body Awareness subscale, whereas the full IAS scale showed no such association.
-
-Additionally, specific item pairings revealed distinct patterns of association with other interoceptive measures and mental health indices that were not captured by the full IAS.
-For instance, while the full IAS showed no significant associations with Borderline Personality, the Hunger-Thirst pair exhibited negative correlations.
-These findings collectively suggest that item-level analyses may uncover more nuanced relationships than those identified by the overall scale.
-This pattern highlights that questionnaires like the IAS may capture multiple facets of interoception rather than a single underlying dimension.
-
-These findings are in line with inconsistencies found in the literature concerning associations between the IAS and the BPQ Body Awareness.
-While some studies report significant negative associations [@lin2023], others have observed significant positive associations  [@brand2023; @campos2021; @gaggero2021; @todd2022], and others none at all [@murphy2019].
-In our study the full IAS was also not associated with the BPQ Body Awareness.
-This pattern is consistent with the idea that this subscale may capture maladaptive bodily experiences or autonomic dysfunction, rather than interoceptive accuracy per se.
-
-However, the Body Awareness subscale of the BPQ has also been criticized for its ambiguous instructions.
-It is often unclear whether respondents should interpret the items as assessing attentional focus on bodily sensations, perceived accuracy in detecting them, or simply the frequency of experiencing such signals.
-As a result, studies have reported that observed associations vary depending on how the BPQ Body Awareness is interpreted [@campos2021; @gabriele2022dissociations; @gaggero2021].
-As such, it is unclear whether the lack of a relationship between the IAS and the BPQ Body Awareness in this study reflects a genuine divergence between the constructs measured by the two scales, or instead arises from ambiguities in how the BPQ Body Awareness is operationalized and interpreted across studies.
-
-We highlight that some IAS pairings may capture interoceptive self-reported accuracy more effectively than the full IAS measure, raising questions about the interpretability of the full scale.
-In contrast , other pairings (e.g., Cough–Sneeze, Wind–Burp) were weakly or inconsistently related to other variables, raising concerns about their usefulness.
-Together, these findings indicate that the strength and relevance of interoceptive self-reported accuracy may vary systematically across physiological domains.
-
-At the same time, the interpretation of such associations is complicated by the lack of contextualisation in the items themselves.
-For example, a racing heart is often associated with anxiety, yet the same sensation can also arise during exercise or other forms of physiological arousal.
-Without contextual anchors, it remains unclear which bodily states participants are drawing upon when responding, highlighting the interpretive ambiguity of self-reports.
-In line with prior work emphasizing the importance of contextual factors in the measurement of interoception [@vlemincx2023novel], our results suggest that the value of self-report lies less in broad aggregation across domains and more in the targeted assessment of physiologically and situationally meaningful contexts.
-
-<!-- Correlates of IAS Across Psychological Domains -->
-The dispositional correlates of the IAS help delineate the conceptual boundaries of interoceptive accuracy as a construct.
-Self-reported interoceptive accuracy, as assessed by the IAS, has been robustly associated with mood-related outcomes, particularly depression and anxiety, underscoring its relevance for affective regulation and bodily state monitoring [@benau2023self; @brand2023].
-This aligns with a broader body of research linking affective conditions such as anxiety and depression with altered interoceptive processing [e.g.,@garfinkel2015knowing].
-
-However, recent findings have also reported null or inconsistent associations between interoceptive abilities and mental health symptomatology, suggesting that such relationships may not generalize across all interoceptive domains or measurement modalities (@banellis2025interoceptive; @jenkinson2024interoception).
-For instance, a recent review by @jenkinson2024interoception found no consistent evidence linking cardiac interoceptive accuracy tasks with anxiety or depression across multiple meta-analyses.Collectively, these findings indicate that relationships between interoceptive accuracy and mental health may vary across bodily domains and measurement modalities.
-This suggests that the IAS, while informative, may benefit from a more differentiated approach that accounts for domain-specific and contextual influences on self-reported interoceptive accuracy.
-
-In contrast to the relatively stronger associations observed with affective measures, correlations between IAS scores and personality traits were small but directionally consistent.
-Modest positive associations emerged with Openness, Agreeableness, and Conscientiousness, while Neuroticism and Extraversion showed near-zero relationships, and Honesty–Humility displayed weak negative correlations.
-This pattern suggests that self-reported interoceptive accuracy, as indexed by the IAS, shares limited but systematic overlap with broad dispositional tendencies -particularly those reflecting intellectual curiosity and creativity, patience and tolerance in interpersonal interactions, and diligence and organizational tendencies [@ashton2007empirical].
-
-Recent evidence supports the view that relationships between interoceptive measures and personality are multifaceted rather than uniform.
-For instance, @haustein2024interoception reported significant associations between interoceptive awareness (MAIA) and all personality traits except Agreeableness, with Openness showing positive correlations with Body Listening and Emotional Awareness, and Neuroticism showing negative correlations with Self- and Attention Regulation.
-Similarly, @simkute2025interoception found that task-based indices of interoceptive sensitivity related negatively to Extraversion.
-Collectively, these findings indicate that interoceptive constructs show distinct and sometimes opposing patterns of association across measurement modalities, suggesting that the IAS relates to a specific, self-evaluative aspect of interoceptive functioning rather than reflecting a general interoceptive or personality-based trait.
-
-A potential key reason for discrepancies in observed associations, including those seen with the IAS, is that self-report questionnaires in interoception often tap into distinct constructs rather than a common underlying dimension [@desmedt2022measures].
-Measures labeled as interoceptive sensibility, awareness, or self-reported accuracy capture partially overlapping but empirically distinct facets, with low intercorrelations between questionnaires and items.
-Consequently, differences in associations with psychological outcomes or personality traits may reflect differences in what each questionnaire assesses rather than true variation in interoceptive functioning.
-
-<!-- Limitations -->
-One limitation worth noting is that we did not evaluate the IAS alongside other widely used questionnaires, such as the BPQ or MAIA.
-Although both are frequently employed in interoception research, they present important limitations.
-For example, the MAIA-2 contains subscales (e.g., Not-Worrying, Not-Distracting) with weak reliability and minimal relation to a general interoception factor [@ferentzi2021examining; @rogowska2023validation].
-Several other subscales primarily reflect higher-level cognitive tendencies, such as mindfulness and attentional regulation, rather than interoceptive body awareness [@todd2022; @vig2023self].
-Similarly, the BPQ’s Body Awareness and Autonomic Reactivity subscales show conceptual and psychometric concerns, and BPQ scores often overlap substantially with negative affect, raising questions about their specificity as measures of interoceptive sensibility [@campos2021; @gabriele2022dissociations; @vig2023self].
-
-Because the IAS is a newly developed questionnaire and the only one designed to assess interoceptive self-reported accuracy - a dimension previously assessed solely through objective tasks such as the HDT and HCT - our focus was on evaluating its structure and correlates without introducing established measures with documented shortcomings.
-Nonetheless, future research should employ novel methods, such as Exploratory Graph Analysis, to clarify the convergent and divergent validity of these questionnaires across interoceptive domains.
-
-<!-- IAS limitations and potential improvements -->
-Nevertheless, these two studies revealed three main points.
-First,  in the datasets that included analogue-style ratings, these scales captured greater variability, further enhancing the ability to detect individual differences.
-Second, a shortened, 14-item version of the IAS retained strong psychometric integrity while removing unstable or redundant items.
-Third, specific item pairings allowed more precise differentiation among individuals and often outperformed global scores in predictive value.
-Nevertheless, even this refined IAS has important limitations.
-
-While the 14-item version improves interpretability and efficiency, it continues to underrepresent key interoceptive modalities such as cardiac, respiratory, and nuanced somatosensory signals, limiting its ability to capture the full breadth of interoceptive processes.
-This shortcoming underscores the need for broader coverage in future scale development.
-At the same time, analogue-style items and item pairings offer clear advantages: they increase response variability, allow more precise differentiation among individuals, and provide domain-specific indicators that often outperform global scores.
-
-Building on these insights, a next-generation interoception scale could balance breadth (multiple items per modality) with depth (domain-specific subscales), retain the benefits of analogue or wider rating ranges (e.g., 1–7 instead of 1–5), and optimize coverage across physiologically and psychologically relevant bodily domains.
-Such a scale would improve interpretability, sensitivity, and practical utility, ultimately enabling a more nuanced mapping of interoceptive abilities onto affective, cognitive, and health-related outcomes.
-
-<!-- Conclusion -->
-Taken together, these studies advance understanding of the IAS and interoceptive self-report more broadly.
-The refined 14-item IAS provides a more efficient and interpretable measure, capturing domain-specific interoceptive signals that show differential associations with psychological outcomes.
-Associations were consistently stronger with mood measures and compared to personality and beliefs, indicating that self-reported interoceptive accuracy relates more closely to affective experience than to stable dispositional traits.
-
-At the same time, current findings highlight limitations in modality coverage and item specificity, suggesting that future scale development should incorporate multimodal, context-sensitive, and continuous analogue ratings or wider discrete scales to better capture the richness of interoceptive processes and clarify their role in affective, cognitive, and health-related outcomes [@desmedt2022measures; @vlemincx2023novel].
-Ultimately, these studies show that the IAS is most informative when treated as a set of domain-specific, context-sensitive indicators rather than as a broad global index, advancing both the measurement and conceptual understanding of interoception.
+Consistent with prior research, self-reported interoceptive accuracy, as assessed by the IAS, showed reliable associations with other interoceptive and interoception-related measures [@brand2023; @garfinkel2015knowing; @gaggero2021].
+Positive correlations emerged with interoceptive sensibility, particularly with MAIA facets related to noticing and trusting bodily sensations, attention regulation, and awareness of mind–body integration.
+In contrast, negative associations were observed with interoceptive deficits such as alexithymia and interoceptive confusion.
 

### 2025-10-30 analysis/Study1.qmd
added another sample
not completed (eyes hurt, sleep needed)

@@
           att == 2) # only those that select 'no' the attention check
+
+```
+
+### Sample 17
+
+- Petzke et al 2024
+- STAI - is the stai sf with 6 items (we use stait-trait)
+
+```{r}
+
+df17 <- haven::read_sav("../data/Petzke2024/ETUDE1_main study.sav") |>
+  select(id, age_to_be_completed_that_year, Gender, starts_with("IA0"), PHQ_15_total, DIF_total, DDF_total, EOT_total, PHQ_4_total, BPQ_total, STAI_total) |>
+  rename(Age= age_to_be_completed_that_year,
+         Heart = IA01_01, Hungry = IA01_02, Breathing = IA01_03, Thirsty = IA01_04, Urinate = IA01_05, 
+         Defecate=IA01_06, Taste = IA01_07,Vomit = IA01_08, Sneeze = IA01_09, Cough = IA01_10, 
+         Temp = IA01_11, Sex_arousal = IA01_12, Wind = IA01_13, Burp = IA01_14,Muscles = IA01_15, 
+         Bruise = IA01_16, Pain = IA01_17, Blood_Sugar = IA01_18, Affective_touch = IA01_19, 
+         Tickle =IA01_20, Itch = IA01_21,
+         TAS_DIF = DIF_total, TAS_DDF =  DDF_total, TAS_EOT = EOT_total,
+         PHQ15_Sum = PHQ_15_total,
+         PHQ4_Sum = PHQ_4_total,
+         BPQ_BodyAwareness = BPQ_total,
+          ) |>
+   mutate(Gender = case_when(
+    Gender == 1 ~ "Male",
+    Gender == 2 ~ "Female",
+    Gender ==3 ~ "Other"))
+
+#Ranges
+df17$PHQ15_Sum <- df17$PHQ15_Sum/15
+df17$BPQ_BodyAwareness <- df17$BPQ_BodyAwareness/12
+
+df17$PHQ4_Depression <- (df13$PHQ4_Depression_4 + df13$PHQ4_Depression_3)/2
+df13$PHQ4_Anxiety <- (df13$PHQ4_Anxiety_2 + df13$PHQ4_Anxiety_1)/2
 

### 2025-10-31 analysis/Study1.qmd
added sample 17

--- 2025-10-21 analysis/Study1.qmd
@@
 
+### Sample 17
+
+- Petzke et al 2024
+- STAI - is the stai sf with 6 items for state anxiety (we use stait-t)
+- https://osf.io/ntpu4
+
+```{r}
+
+df17 <- haven::read_sav("../data/Petzke2024/ETUDE1_main study.sav") |>
+  mutate_all(as.numeric) |>
+  select(id, age_to_be_completed_that_year, Gender, starts_with(c("IA0", "PH01")), PHQ_15_total, DIF_total, DDF_total, EOT_total, PHQ_4_total, BPQ_total) |>
+  rename(Age= age_to_be_completed_that_year,
+         Heart = IA01_01, Hungry = IA01_02, Breathing = IA01_03, Thirsty = IA01_04, Urinate = IA01_05, 
+         Defecate=IA01_06, Taste = IA01_07,Vomit = IA01_08, Sneeze = IA01_09, Cough = IA01_10, 
+         Temp = IA01_11, Sex_arousal = IA01_12, Wind = IA01_13, Burp = IA01_14,Muscles = IA01_15, 
+         Bruise = IA01_16, Pain = IA01_17, Blood_Sugar = IA01_18, Affective_touch = IA01_19, 
+         Tickle =IA01_20, Itch = IA01_21,
+         TAS_DIF = DIF_total, TAS_DDF =  DDF_total, TAS_EOT = EOT_total,
+         PHQ15_Sum = PHQ_15_total,
+         PHQ4_Sum = PHQ_4_total,
+         BPQ_BodyAwareness = BPQ_total,
+          ) |>
+  mutate(Gender = case_when(
+    Gender == 1 ~ "Male",
+    Gender == 2 ~ "Female",
+    Gender == 3 ~ "Other"))|>
+   mutate(
+    Age_code = zap_labels(Age),      # remove SPSS labels, get raw numeric codes
+    Age = case_when(
+      Age_code == -9 ~ NA_real_,
+      TRUE ~ 2024 - (2000 + (21 - Age_code))  # compute actual age
+    ))
+
+#Ranges
+df17$PHQ15_Sum <- df17$PHQ15_Sum/15
+df17$BPQ_BodyAwareness <- df17$BPQ_BodyAwareness/12
+
+df17$PHQ4_Depression <- (df17$PH01_01 + df17$PH01_02)/2
+df17$PHQ4_Anxiety <- (df17$PH01_03 + df17$PH01_04)/2
+
+```
+
 :::
@@
 # Save all
-data <- list(df1a=df1a, df1b=df1b, df2=df2, df3=df3, df4=df4, df5=df5, df6=df6, df7a=df7a, df7b=df7b, df7c=df7c, df8a=df8a, df8b=df8b, df9=df9, df10=df10, df11 =df11 , df12 =df12 , df13  = df13 , df14 =df14 , df15  =df15, df16 = df16)
+data <- list(df1a=df1a, df1b=df1b, df2=df2, df3=df3, df4=df4, df5=df5, df6=df6, df7a=df7a, df7b=df7b, df7c=df7c, df8a=df8a, df8b=df8b, df9=df9, df10=df10, df11 =df11 , df12 =df12 , df13  = df13 , df14 =df14 , df15  =df15, df16 = df16, df17 = df17)
 save(data, file = "../data/data.RData")
@@
 - **Sample 16 **: Data from [Arjona's] study , included `r report::report_participants(df16 , age = "Age", gender = "Gender")`
-
-Total N = `r nrow(df1a) + nrow(df1b) + nrow(df2) + nrow(df3) + nrow(df4) + nrow(df5) + nrow(df6) + nrow(df7a) + nrow(df7b) + nrow(df7c) + nrow(df8a) + nrow(df8b) + nrow(df9) + nrow(df10) + nrow(df11) + nrow(df12) + nrow(df13) + nrow(df14) + nrow(df15) + nrow(df16)`.
+- **Sample 17 **: Data from [Petzke's](https://osf.io/seru4) study, downloaded from OSF, included `r report::report_participants(df17, age = "Age", gender = "Gender")`.
+
+Total N = `r nrow(df1a) + nrow(df1b) + nrow(df2) + nrow(df3) + nrow(df4) + nrow(df5) + nrow(df6) + nrow(df7a) + nrow(df7b) + nrow(df7c) + nrow(df8a) + nrow(df8b) + nrow(df9) + nrow(df10) + nrow(df11) + nrow(df12) + nrow(df13) + nrow(df14) + nrow(df15) + nrow(df16) + nrow(df17)` .
 
@@
 desc_df16 <- desc(df16)
-
-desc_total <- rbind(desc_df1a, desc_df1b, desc_df2, desc_df3, desc_df5, desc_df6, desc_df7a, desc_df7b, desc_df7c, desc_df8a, desc_df8b, desc_df9, desc_df10, desc_df11 , desc_df12 , desc_df13 , desc_df14 , desc_df15, desc_df16)
+desc_df17 <- desc(df17)
+
+desc_total <- rbind(desc_df1a, desc_df1b, desc_df2, desc_df3, desc_df5, desc_df6, desc_df7a, desc_df7b, desc_df7c, desc_df8a, desc_df8b, desc_df9, desc_df10, desc_df11 , desc_df12 , desc_df13 , desc_df14 , desc_df15, desc_df16, desc_df17)
 
@@
 table <- data.frame(
-  Sample = c('', 'Sample 1a', 'Sample 1b', 'Sample 2', 'Sample 3', 'Sample 4', 'Sample 5', 'Sample 6', '', 'Sample 7a', 'Sample 7b', 'Sample 7c', '', 'Sample 8a', 'Sample 8b', 'Sample 9', 'Sample 10', 'Sample 11', 'Sample 12', 'Sample 13', 'Sample 14', 'Sample 15', 'Sample 16', 'Sample 17'),
-  Reference = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Makowski et al., (2023c)', 'Makowski et al., (2024)', 'Poerio et al., (2024)', 'Poerio et al., unpublished', 'Arjona et al., unpublished', 'Total'),
-  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', 'English', 'English', 'English', 'English','English', ''),
-  N = c('', nrow(df1a), nrow(df1b), nrow(df2), nrow(df3), nrow(df4), nrow(df5_attention), nrow(df6),'', nrow(df7a), nrow(df7b), 802,'', nrow(df8a), nrow(df8b), nrow(df9), nrow(df10), nrow(df11), nrow(df12), nrow(df13), nrow(df14), nrow(df15), nrow(df16), 33272),
+  Sample = c('', 'Sample 1a', 'Sample 1b', 'Sample 2', 'Sample 3', 'Sample 4', 'Sample 5', 'Sample 6', '', 'Sample 7a', 'Sample 7b', 'Sample 7c', '', 'Sample 8a', 'Sample 8b', 'Sample 9', 'Sample 10', 'Sample 11', 'Sample 12', 'Sample 13', 'Sample 14', 'Sample 15', 'Sample 16', 'Sample 17', 'Sample 18'),
+  Reference = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Makowski et al., (2023c)', 'Makowski et al., (2024)', 'Poerio et al., (2024)', 'Poerio et al., unpublished', 'Arjona et al., unpublished', 'Petzke et al., (2024)',  'Total'),
+  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', 'English', 'English', 'English', 'English','English', 'German', ''),
+  N = c('', nrow(df1a), nrow(df1b), nrow(df2), nrow(df3), nrow(df4), nrow(df5_attention), nrow(df6),'', nrow(df7a), nrow(df7b), 802,'', nrow(df8a), nrow(df8b), nrow(df9), nrow(df10), nrow(df11), nrow(df12), nrow(df13), nrow(df14), nrow(df15), nrow(df16), nrow(df17), 33526),
   'Difference' = c('','', '', '', '', '', '', '', '', '', '', '', '', 'Collapsed "Itch" and "Tickling"', 'Collapsed "Itch" and "Tickling"', '', 'Analog scales.
-No Temperature, Blood sugar and Cough items', 'Analog scales', 'Analog scales', '', '', '', '', ''),
-  Age = c('', make_age(df1a$Age), make_age(df1b$Age), make_age(df2$Age), make_age(df3$Age), "48.6.6 ± 14.1*", make_age(df5_attention$Age), make_age(df6$Age),'', make_age(df7a$Age), make_age(df7b$Age), make_age(df7c$Age),'', make_age(df8a$Age), make_age(df8b$Age), make_age(df9$Age), make_age(df10$Age), make_age(df11$Age), make_age(df12$Age), make_age(df13$Age), make_age(df14$Age), make_age(df15$Age), make_age(df16$Age), '48.09 ± 13.1'),
-  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76','18-50', '17, 87', '18-57', '18-60', '18-79', '17-93'),
-  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', '50%*', '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '76%', '57.3%', '74.8%', '75.9%', '67.7%', '71.3%'),
+No Temperature, Blood sugar and Cough items', 'Analog scales', 'Analog scales', '', '', '', '', '', ''),
+  Age = c('', make_age(df1a$Age), make_age(df1b$Age), make_age(df2$Age), make_age(df3$Age), "48.6.6 ± 14.1*", make_age(df5_attention$Age), make_age(df6$Age),'', make_age(df7a$Age), make_age(df7b$Age), make_age(df7c$Age),'', make_age(df8a$Age), make_age(df8b$Age), make_age(df9$Age), make_age(df10$Age), make_age(df11$Age), make_age(df12$Age), make_age(df13$Age), make_age(df14$Age), make_age(df15$Age), make_age(df16$Age), make_age(df17$Age), '47.96 ± 13.1'),
+  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76','18-50', '17, 87', '18-57', '18-60', '18-79', '22-69', '17-93'),
+  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', '50%*', '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '76%', '57.3%', '74.8%', '75.9%', '67.7%', '68.5%', '71.3%'),
   Availability= c('osf.io/3m5nh', '', '', 'osf.io/5x9sg', 'osf.io/j6ef3', 'osf.io/ms354', 'osf.io/mp3cy', 'osf.io/xwz6g', 'osf.io/3f2h6', '', '', '','osf.io/3eztd','', '', 'osf.io/7p9u5', 'github.com/RealityBending/IllusionGameReliability', 'github.com/DominiqueMakowski/PHQ4R', 'github.com/RealityBending/InteroceptionPrimals',
 'github.com/RealityBending/InteroceptionScale',
-'osf.io/49wbv', '','', '')
+'osf.io/49wbv', '','', 'osf.io/seru4', '')
 )
@@
   mutate(Sample = "Sample 16")
-
-p1_data <- rbind(dens1a, dens1b, dens2, dens3, dens4, dens5, dens6, dens7a, dens7b, dens7c, dens8a, dens8b, dens9, dens10, dens11 , dens12, dens13, dens14, dens15, dens16)
+dens17  <- estimate_density(select(df17, all_of(ias_vars)), method = "kernSmooth") |>
+  mutate(Sample = "Sample 17")
+
+p1_data <- rbind(dens1a, dens1b, dens2, dens3, dens4, dens5, dens6, dens7a, dens7b, dens7c, dens8a, dens8b, dens9, dens10, dens11 , dens12, dens13, dens14, dens15, dens16, dens17)
 
@@
 p1 <- p1_data |>
-  mutate(Sample = fct_relevel(Sample, "Sample 1a", "Sample 1b", "Sample 2", "Sample 3", "Sample 4", "Sample 5", "Sample 6", "Sample 7a", "Sample 7b", "Sample 7c", "Sample 8a", "Sample 8b", "Sample 9", "Sample 10", "Sample 11", "Sample 12", "Sample 13", "Sample 14", "Sample 15"),
+  mutate(Sample = fct_relevel(Sample, "Sample 1a", "Sample 1b", "Sample 2", "Sample 3", "Sample 4", "Sample 5", "Sample 6", "Sample 7a", "Sample 7b", "Sample 7c", "Sample 8a", "Sample 8b", "Sample 9", "Sample 10", "Sample 11", "Sample 12", "Sample 13", "Sample 14", "Sample 15", 'Sample 16', 'Sample 17'),
          Parameter = ifelse(Parameter == "Affective_touch", "Affective touch", Parameter),
@@
   guides(color = guide_legend(ncol = 1)) +
-  facet_wrap(~Sample, scales = "free_y", nrow = 4) +
+  facet_wrap(~Sample, scales = "free_y", nrow = 3) +
   theme_minimal() +
@@
 data16   <- select(df16, all_of(dens16$Parameter))
+data17   <- select(df17, all_of(dens17$Parameter))
 
@@
   mutate(data10, Taste = NA, Cough = NA, Blood_Sugar = NA),  
-  data11,  data12 , data13, data14, data15, data16  
+  data11,  data12 , data13, data14, data15, data16, data17  
 ) 
@@
 
+#### Sample 17
+
+```{r}
+make_correlation(data17)
+```
 :::
@@
 uva16$keep_remove
+```
+
+#### Sample 17
+
+```{r}
+uva17  <- EGAnet::UVA(data = data17, cut.off = 0.3)
+uva17  
+uva17$keep_remove
 ```
@@
   uva15$keep_remove$remove,
-  uva16$keep_remove$remove)
+  uva16$keep_remove$remove,
+  uva17$keep_remove$remove)
 
@@
 data16 <- select(data16 , -Tickle)
+data17 <- select(data17 , -Tickle)
 ```
@@
 
-rez_efa <- make_efa(data_all, n = 3, cols = c("F1" = colors[["Wind"]], 
-                                              "F2" = colors[["Defecate"]], 
-                                              "F3" = colors[["Heart"]]))
+rez_efa <- make_efa(data_all, n = 3, cols = c("F1" = colors[["Cough"]], 
+                                              "F2" = colors[["Thirsty"]], 
+                                              "F3" = colors[["Bruise"]]))
 plot(rez_efa$n_fac)
@@
                    -Sex_arousal, -Temp)
+data17f <- select(data17, -Taste, -Affective_touch, -Vomit, -Itch,
+                   -Sex_arousal, -Temp)
 ```
@@
 
+### Sample 17
+
+#### Initial
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data17)
+rez_ega <- make_ega(data17, cols = c(
+  "C1" = colors[["Hungry"]], "C2" = colors[["Defecate"]], "C3" = colors[["Muscles"]], "C4" = colors[["Cough"]], 
+  "C5" = colors[["Itch"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data17, n = 5, cols = c("F1" = colors[["Sneeze"]], "F2" = colors[["Hungry"]], 
+                                            "F3" = colors[["Defecate"]], "F4" = colors[["Burp"]],
+                                            "F5" = colors[["Vomit"]]))
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+```
+
+::::
+
+#### Final
+
+:::: {.panel-tabset}
+
+##### Summary
+
+```{r}
+#| warning: false
+#| message: false
+#| fig-width: 12
+#| fig-height: 20
+
+rez_hclust <- make_hclust(data17f)
+rez_ega <- make_ega(data17f, cols = c(
+  "C1" = colors[["Hungry"]], "C2" = colors[["Defecate"]], "C3" = colors[["Cough"]], "C4" = colors[["Burp"]], 
+  "C5" = colors[["Muscles"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
+rez_efa <- make_efa(data17f, n = 4, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Hungry"]], 
+                                            "F3" = colors[["Urinate"]], "F4" = colors[["Sneeze"]]))
+rez_cfa17  <- make_cfa(data17f)
+
+rez_hclust$p / rez_ega$p / rez_efa$p
+```
+
+##### Details
+
+```{r}
+#| warning: false
+#| message: false
+
+plot(rez_hclust$pvclust, hang = -1, cex = 0.5)
+pvclust::pvrect(rez_hclust$pvclust, alpha=0.95, max.only=FALSE)
+
+stab <- EGAnet::itemStability(rez_ega$rez)
+rez_ega$table
+
+plot(rez_efa$n_fac)
+
+rez_cfa17$test
+```
+
+::::
+
 ## Scores
@@
   sample15 = add_empirical(data15 , "Sample 15"),
-  sample16 = add_empirical(data16, "Sample 16")
+  sample16 = add_empirical(data16, "Sample 16"),
+  sample17 = add_empirical(data17, "Sample 16")
 )

### 2025-10-31 analysis/Study1.qmd
updated script
minor

@@
   mutate_all(as.numeric) |>
-  select(id, age_to_be_completed_that_year, Gender, starts_with(c("IA0", "PH01")), PHQ_15_total, DIF_total, DDF_total, EOT_total, PHQ_4_total, BPQ_total) |>
+  select(age_to_be_completed_that_year, Gender, starts_with(c("IA0", "PH01")), PHQ_15_total, DIF_total, DDF_total, EOT_total, PHQ_4_total, BPQ_total) |>
   rename(Age= age_to_be_completed_that_year,
@@
 
+- the first optimal number of factors was 11, which, although too large for practical higher-order structure description, hints at the scattered nature of the items
+
 ```{r}
@@
   sample16 = add_empirical(data16, "Sample 16"),
-  sample17 = add_empirical(data17, "Sample 16")
+  sample17 = add_empirical(data17, "Sample 17")
 )

### 2025-10-31 analysis/study2.qmd
minor

@@
 df16 <- cbind(data$df16, scores$sample16)
+dff17 <- cbind(data$df17, scores$sample17)
 
@@
                 df8a=df8a, df8b=df8b, df9=df9, df10=df10, df11=df11, 
-                df12=df12, df14=df14, df15=df15, df16=df16)
+                df12=df12, df14=df14, df15=df15, df16=df16, df17 = df17)
 ```

### 2025-10-31 analysis/study2.qmd
minor

@@
 df16 <- cbind(data$df16, scores$sample16)
-dff17 <- cbind(data$df17, scores$sample17)
+df17 <- cbind(data$df17, scores$sample17)
 

### 2025-10-31 analysis/study2.qmd
updated study2

@@
   pool_coef(with = "BDI_Sum", component="Depression", category = "Mood", name = "Depression - BDI"), 
-  pool_coef(with = "PHQ4_Depression", component="Depression", category = "Mood", name = "Depression - PHQ-4"),
+  pool_coef(with = "PHQ4_Depression", component="Depression", category = "Mood", name = "Depression - PHQ-4", unequalrange=TRUE),
   pool_coef(with = "DEP", component = "Depression", category = "Mood", name = "Depression - MFQ")
@@
   pool_coef(with = "STAIT_Mean", component="Anxiety", category = "Mood", name = "Anxiety - STAI-T", unequalrange=TRUE), 
-  pool_coef(with = "PHQ4_Anxiety", component="Anxiety", category = "Mood", name = "Anxiety - PHQ-4"),
+  pool_coef(with = "PHQ4_Anxiety", component="Anxiety", category = "Mood", name = "Anxiety - PHQ-4",  unequalrange=TRUE),
   pool_coef(with = "GAD7_Sum", component="Anxiety", category = "Mood", name = "Anxiety - GAD-7")

### 2025-11-03 paper/1_Initial/manuscript.qmd
updated results section after adding sample 17

@@
 
-Study 1 will re-analyse and assess the factor structure of the IAS by taking advantage of the large number of open-access datasets [@brand2023; @campos2021; @lin2023; @murphy2019; @arslanova2022; @todd2022; @gaggero2021; @brand2022; @von2023; @poerio2024interoceptive].
+Study 1 will re-analyse and assess the factor structure of the IAS by taking advantage of the large number of open-access datasets [@brand2023; @campos2021; @lin2023; @murphy2019; @arslanova2022; @todd2022; @gaggero2021; @brand2022; @von2023; @poerio2024interoceptive; @petzke2024somatic].
 While combining these studies might provide a more robust and generalizable understanding of the IAS' factor structure, we also additionally provide an individual analysis (i.e., applying the same method on all samples separately) to add nuance to the general picture, as all studies differ in their sample size, demographic characteristics, language, and procedure.
@@
 We also included the data of five unpublished studies.
-A total of 16 datasets was included (see **Table 1**).
+A total of 17 datasets was included (see **Table 1**).
 
-The total number of participants was 33,272 participants (Mean = 48.09 $\pm$ 13.1, 71.3\% Female).
+The total number of participants was 33,526 participants (Mean = 47.96 $\pm$ 13.1, 71.3\% Female).
 
@@
 Name	BIC	RMSEA	Chi2	CFI	BF
-fit_g	13466.62	0.106	325.704	0.784	Inf
-fit_ega	15870.94	0.026	72.825	0.988	NA
-fit_egag	15892.96	0.059	180.403	0.924	1.654961e-05
-fit_hclustg	15911.16	0.065	210.828	0.905	1.846821e-09
-fit_hclust	15913.39	0.062	182.492	0.921	6.080789e-10
-fit_efa	15941.59	0.073	253.472	0.877	4.576430e-16
-fit_efag	15941.59	0.073	253.472	0.877	4.576430e-16 -->
+fit_g	940941.8	0.124	27,398.095	0.783	Inf
+fit_ega	1110166.4	0.035	2,334.112	0.984	NA
+fit_egag	1114563.1	0.054	6,876.395	0.952	0
+fit_hclust	1121159.8	0.078	13,441.878	0.906	0
+fit_hclustg	1122347.5	0.079	14,681.532	0.897	0
+fit_efag	1124348.4	0.083	16,703.253	0.883	0
+fit_efa	1124348.4	0.083	16,703.253	0.883	0 -->
 
@@
 fit_ega	25899.23	0.038	116.734	0.977	NA - sample 13
-fit_ega	3975.352	0.040	65.620	0.975	NA - sampple 14 -->
+fit_ega	3975.352	0.040	65.620	0.975	NA - sampple 14 
+fit_ega	8493.471	0.057	102.289	0.947	NA - sample 17
+-->
 
@@
 We then fitted and compared using CFA various candidate structures emerging from the previous analyses, including a 1-factor model (the G-model), a 3-factor model (EFA), a 3+1 model (EFA + general factor), a 5-factor model (HCA), a 5+1 model (HCA + general factor), a 7-factor model (EGA), and a 7+1 model (EGA + general factor).
-The EGA model with 7 factors of item pairs provided the best fit with the lowest RMSEA (0.026), lowest $\chi^2$ (72.825), highest CFI (0.988).
-It was followed by the EGA + general factor model (RMSEA = 0.059, $\chi^2$ = 180.403, CFI = 0.065), and the HCA model with 5 factors (RMSEA = 0.062, $\chi^2$ = 182.492, CFI = 0.921).
+The EGA model with 7 factors of item pairs provided the best fit with the lowest RMSEA (0.035), lowest $\chi^2$ (2,334.112), highest CFI (0.984).
+It was followed by the EGA + general factor model (RMSEA = 0.054, $\chi^2$ = 6,876.395, CFI = 0.952), and the HCA model with 5 factors (RMSEA = 0.078, $\chi^2$ = 13,441.878, CFI = 0.906).
 The other models performed poorly, with RMSEA > 0.08 and CFI < 0.90.
@@
 This result was relatively consistent across unique datasets with the EGA model providing the best fit.
-In all samples where CFA converged, it showed excellent performance with low RMSEA (≈ 0.025–0.052), high CFI (≥ 0.95), and substantially lower $\chi^2$ compared to alternative models.
+In all samples where CFA converged, it showed excellent performance with low RMSEA (≈ 0.025–0.057), high CFI (≥ 0.95), and substantially lower $\chi^2$ compared to alternative models.
 Adding a general factor systematically worsened fit, while hierarchical clustering and EFA-based models showed poorer performance (RMSEA > 0.05, CFI < 0.95).

### 2025-11-03 analysis/Study1.qmd
minor
updated study 1

@@
   mutate_all(as.numeric) |>
-  select(age_to_be_completed_that_year, Gender, starts_with(c("IA0", "PH01")), PHQ_15_total, DIF_total, DDF_total, EOT_total, PHQ_4_total, BPQ_total) |>
+  select(age_to_be_completed_that_year, Gender, starts_with(c("IA0", "PH01")), PHQ_15_total, DIF_total, DDF_total, EOT_total, PHQ_4_total, BPQ_total, starts_with("BP01_")) |>
   rename(Age= age_to_be_completed_that_year,
@@
 
+# df17$BPQ_BodyAwarenessManual <- rowMeans(df17[, grep("^BP01_", names(df17))], na.rm = TRUE)
+
 #Ranges
@@
 
-df17$PHQ4_Depression <- (df17$PH01_01 + df17$PH01_02)/2
-df17$PHQ4_Anxiety <- (df17$PH01_03 + df17$PH01_04)/2
+df17$PHQ4_Depression <- df17$PH01_01 + df17$PH01_02
+df17$PHQ4_Anxiety <- df17$PH01_03 + df17$PH01_04
 
@@
 - **Sample 16 **: Data from [Arjona's] study , included `r report::report_participants(df16 , age = "Age", gender = "Gender")`
-- **Sample 17 **: Data from [Petzke's](https://osf.io/seru4) study, downloaded from OSF, included `r report::report_participants(df17, age = "Age", gender = "Gender")`.
+- **Sample 17 **: Data from [Petzke's (2024)](https://osf.io/seru4) study, downloaded from OSF, included `r report::report_participants(df17, age = "Age", gender = "Gender")`.
 

### 2025-11-03 paper/1_Initial/manuscript.qmd
updated results

@@
 MAIA subscales showed robust positive standardized effects with the IAS.
-Noticing yielded the strongest association (mean β = .26), followed by Emotional Awareness (β = .20) and related subscales - Body Listening, Attention Regulation, Trusting, and Self-Regulation, each in the .20–.26 range, all significant.
+Noticing yielded the strongest association (mean β = .26), followed by Attention Regulation (mean β = .25) and related subscales - Body Listening, Trusting, Emotional Awareness and Self-Regulation, each in the .19–.24 range, all significant.
 Effects were generally strongest for the full IAS, except for Body Listening, which peaked for the Bruise–Blood pairing.
-Not Distracting was weakly but significantly positive (mean β = .06), primarily for Hungry–Thirsty, Bruise–Blood, and Muscles–Pain.
-Not Worrying was significant only for the full IAS and the Hungry–Thirsty and Urinate–Defecate pairings (β ≈ −.01 to .11).
+Not Distracting was weakly and significantly only for the full IAS, Hungry-Thirsty, Bruise-Blood sugar and the Muscles-Pain pairings (β ≈ −.02 to .06).
+Not Worrying was significant only for the full IAS and the Hungry–Thirsty and Urinate–Defecate pairings (β ≈ −.01 to .04).
 
 Autonomic Reactivity (BPQ; mean β = −.19) was reliably negative across pairings, reaching significance for all except the Bruise–Blood sugar and Breathing–Heart pairings.
-In contrast, Body Awareness (BPQ; mean β = .12) was weakly positive and significant only for Bruise–Blood.
+In contrast, Body Awareness (BPQ; mean β ≈ .15; range = .10 to .22) was positive and significant across most pairings with the exception of Wind-Burp and Urinate-Defecate.
 
 Interoceptive deficits showed consistent negative standardized effects.
-Alexithymia measures (TAS, BVAQ) were robustly negative (β ≈ −.18 to −.24), except for the BVAQ Affective subscale, which was positive for Bruise–Blood (β = .16).
-Interoceptive confusion (ICQ) was also strongly negative across all IAS measures (mean β ≈ −.42; range = −.49 to −.20).
+Alexithymia measures (TAS, BVAQ) were robustly negative (β ≈ −.13 to −.2), except for the BVAQ Affective subscale, which was positive for Bruise–Blood (β = .16).
+Interoceptive confusion (ICQ) was also negative across all IAS measures (mean β ≈ −.32; range = −.49 to −.20).
 
@@
 
-Depression (BDI; mean β = −.20) and anxiety (STAI-T; mean β = −.19) showed consistent negative associations across the IAS and pairings, strongest for Hungry–Thirsty.
-Related constructs diverged somewhat: MFQ was largely nonsignificant; PHQ-9 and other mood indices (PHQ-15, PHQ-4, GAD-7) produced weaker but often reliable negative βs (typically −.10 to −.15), with effects sometimes limited to particular pairings (e.g., PHQ-15 nonsignificant for Wind–Burp and Breathing–Heart).
-Hungry–Thirsty consistently yielded the strongest standardized effects.
+Depression (BDI; mean β = −.20) and anxiety (STAI-T; mean β = −.20) showed consistent negative associations across the IAS and its pairings, with the strongest effects observed for the Hungry–Thirsty dimension.
+Related constructs showed some divergence: the MFQ was largely nonsignificant except for a notable effect in the Breathing–Heart pairing, while somatic concerns (PHQ-15) were unrelated to the total scale but showed weak negative associations with the Hungry–Thirsty, Bruise–Blood sugar, and Urinate–Defecate pairings (β ≈ −.22 to −.05).
+Other mood indices (PHQ-9, PHQ-4, GAD-7) produced generally weaker but often reliable negative coefficients (typically −.10 to −.15), though effects sometimes appeared only for specific pairings (e.g., PHQ-4 nonsignificant for Wind–Burp and Breathing–Heart).
+Across measures, the Hungry–Thirsty pairing consistently yielded the strongest standardized effects.
 
@@
 Autistic traits (ASQ) were generally negatively associated with IAS scores.
-Imagination (mean β = −.18) showed the most consistent pattern across pairings except Cough–Sneeze.
-Most full-IAS associations were driven by Hungry–Thirsty, Bruise–Blood sugar, and Muscles–Pain, which yielded the largest negative coefficients.
-Beyond these, effects weakened or became nonsignificant- Patterns and Numbers showed none, and Borderline Personality was associated only with Hungry–Thirsty (mean β = −.14).
+Among ASQ subscales, Imagination (mean β = −.18) exhibited the most consistent pattern of negative associations across pairings, with the exception of Cough–Sneeze.
+The strongest full-scale effects were driven by the Hungry–Thirsty, Bruise–Blood sugar, and Muscles–Pain pairings, which yielded the largest negative coefficients.
+In contrast, associations weakened or became nonsignificant for other pairings.
 
-Schizotypal traits showed similarly negative coefficients, with Social Anxiety (mean β = −.11) and No Close Friends (mean β = −.12) most consistent.
-Some facets were unrelated to the overall IAS but linked to specific pairings: Unusual Perceptions with Muscles–Pain and Urinate–Defecate, and Eccentric with Hungry–Thirsty and Urinate–Defecate.
+A comparable trend was observed for maladaptive personality traits.
+Detachment, Psychoticism, and Negative Affect demonstrated the most reliable, albeit weak, negative associations with overall IAS scores (mean β range = −.08 to −.10), again primarily driven by the Hungry–Thirsty, Bruise–Blood sugar, and Muscles–Pain pairings.
+Other maladaptive traits were unrelated to IAS scores.
+Notably, Antagonism was the only trait to show a significant positive association, limited to the Bruise–Blood sugar pairing (β = .14), whereas Borderline Personality was uniquely associated with Hungry–Thirsty (mean β = −.14).
+
+Schizotypal traits showed a similarly negative pattern of associations.
+Social Anxiety (mean β = −.11) and No Close Friends (mean β = −.12) displayed the most consistent effects.
+Although some facets were unrelated to the overall IAS score, they were associated with specific pairings: Unusual Perceptions with Muscles–Pain and Urinate–Defecate, and Eccentric with Hungry–Thirsty and Urinate–Defecate.
 
@@
 Honesty–Humility (mean β = −.10) showed a small negative effect, primarily for Hungry–Thirsty and Bruise–Blood sugar.
-Neuroticism (mean β = −.13) was negatively associated with the IAS, with the strongest β for Bruise–Blood (β = −.23).
+Neuroticism (mean β = −.13) was negatively associated with the IAS, with the strongest β for Hungry-Thirsty (β = −.23).
 
-Primal world beliefs were largely null, with small positive standardized coefficients for certain beliefs: “Understandable,” “Alive,” and “Hierarchical” were weakly positive for the full IAS and Hungry–Thirsty (β ≈ .05–.10), while “Good” was uniquely positive for Muscles–Pain (β ≈ .09).
+Primal world beliefs were largely null, with small positive standardized coefficients for certain beliefs: “Understandable,” “Alive,” and “Hierarchical” were weakly positive for the full IAS and Hungry–Thirsty (β ≈ .08–.11), while “Good” was uniquely positive for Muscles–Pain (β ≈ .09).
 Within the Lying Profile, only Lying Contextuality showed a modest negative coefficient for Bruise–Blood (β = −.12).
@@
 Conspiracy Beliefs produced selective small positive effects.
-Global Conspiracies (GCBS) were associated with the full IAS and several pairings (mean β = .10), Government Malfeasance (β = .05) with Cough–Sneeze, and Extraterrestrial beliefs (β = .03) with Muscles–Pain.
+Global Conspiracies (GCBS) were associated with the full IAS and three pairings (mean β = .10), Personal Wellbeing with the full scale and the Hungry-Thirsty (mean β = .09), and Information Control (β = .06) with Cough–Sneeze.
 
@@
 
-Overall, the full IAS produced the greatest number of significant standardized effects (29), though many were driven by specific pairings rather than uniform scale-wide associations.
+Overall, the full IAS produced the greatest number of significant standardized effects (28), though many were driven by specific pairings rather than uniform scale-wide associations.
 Hungry–Thirsty (17) and Bruise–Blood sugar (10) consistently yielded the strongest standardized coefficients, especially for interoceptive, mood, and psychopathology measures.

### 2025-11-03 paper/1_Initial/manuscript.qmd
updated manuscript

@@
 Regarding its validity, the IAS has naturally been compared to other interoception-related measures, and shows a positive correlations with most facets of the MAIA [@mehling2018multidimensional; @gaggero2021], except for the Not-Distracting and Not-Worrying subscales [@brand2023] - which were previously highlighted as related to non-interoceptive abilities [@ferentzi2021examining].
-Interestingly, findings on the correlation between the IAS and the body awareness dimension of the BPQ, have been mixed: some studies report small positive correlations [@brand2023; @campos2021; @koike2023], while others find small negative correlations [@lin2023] or no correlation at all [@murphy2019; @gaggero2021].
+Interestingly, findings on the correlation between the IAS and the body awareness dimension of the BPQ, have been mixed: some studies report small positive correlations [@brand2023; @campos2021; @koike2023], while others find small negative correlations [@lin2023] or no correlation at all [@murphy2019].
 Positive correlations have also been observed with the "observation" and "description" subscales of the Five Facet Mindfulness Questionnaire [FFMQ, @baer2006using; @brand2023; @koike2023], as well as with the "non-reactivity" and "acting with awareness" subscales [@koike2023].
@@
 The IAS showed positive associations with most MAIA facets, except for the Not-Distracting and Not-Worrying subscales, replicating prior findings [@brand2023].
-Associations with the BPQ Body Awareness subscale were consistent with previous reports on a non-existing association between these measures [@murphy2019; @gaggero2021], whereas indices of autonomic reactivity were more strongly and negatively associated with IAS scores, supporting earlier observations that reactivity may reflect aspects of bodily signal processing captured by self-reported interoceptive accuracy [@todd2022].
+Associations with the BPQ Body Awareness subscale were consistent with previous reports on positive association between these measures [@brand2023; @campos2021; @koike2023; @gaggero2021], whereas indices of autonomic reactivity were more strongly and negatively associated with IAS scores, supporting earlier observations that reactivity may reflect aspects of bodily signal processing captured by self-reported interoceptive accuracy [@todd2022].
 
@@
 Associations with personality traits followed a similar domain-specific structure.
-Effects for the full IAS largely reflected contributions from specific pairings: Openness showed its strongest associations for Breathing–Heart, Neuroticism and Honesty–Humility for Hungry–Thirsty and Bruise–Blood sugar, and Conscientiousness for the full scale.
+Effects for the full IAS largely reflected contributions from specific pairings: Extraversion showed its strongest associations for Breathing–Heart, Neuroticism and Honesty–Humility for Hungry–Thirsty, and Openess, Conscientiousness and Agreeableness for the full scale.
 These results indicate that associations between interoceptive self-report and personality dimensions may depend on the bodily domain represented.
@@
 Weak positive associations emerged between the IAS and certain primal world beliefs (e.g., perceiving the world as comprehensible or alive) and selected conspiracy belief dimensions, particularly Global Conspiracies and Personal Wellbeing.
-These effects were limited to specific pairings - most often Hungry–Thirsty and Bruise–Blood sugar—indicating that links between interoceptive self-report and broader cognitive or worldview constructs are modest and domain-specific.
+These effects were limited to specific pairings, most often Hungry–Thirsty and Bruise–Blood sugar, indicating that links between interoceptive self-report and broader cognitive or worldview constructs are modest and domain-specific.
 

### 2025-11-04 paper/1_Initial/manuscript.qmd
minor

@@
 
-<!-- Mood and psychopathology -->
+<!-- Mood-->
 
@@
 
-Among Big Five traits, Openness (mean β = .10), Agreeableness (β = .08), and Conscientiousness (β = .11) showed small but consistent positive effects, most evident for the full IAS.
-Honesty–Humility (mean β = −.10) showed a small negative effect, primarily for Hungry–Thirsty and Bruise–Blood sugar.
-Neuroticism (mean β = −.13) was negatively associated with the IAS, with the strongest β for Hungry-Thirsty (β = −.23).
+Among the Big Five traits, Openness (mean β = .10), Agreeableness (mean β = .08), and Conscientiousness (mean β = .11) exhibited small yet consistent positive effects, most evident for the full IAS.
+Extraversion showed a weak but positive association, driven primarily by its stronger relation to the Bruise–Blood pairing (β = .17).
+In contrast, Honesty–Humility (mean β = −.10) demonstrated a small negative effect, most evident for the Hungry–Thirsty and Bruise–Blood sugar pairings.
+Finally, Neuroticism (mean β = −.23) was negatively associated with the IAS, with the strongest effect observed for the Hungry–Thirsty pairing (β = −.22).
 
@@
 <!-- Interoception and correlates - item specific -->
-The IAS showed positive associations with most MAIA facets, except for the Not-Distracting and Not-Worrying subscales, replicating prior findings [@brand2023].
+The IAS showed positive associations with most MAIA facets, except for the Not-Distracting and Not-Worrying subscales, replicating prior findings [@brand2023; @todd2022].
 Associations with the BPQ Body Awareness subscale were consistent with previous reports on positive association between these measures [@brand2023; @campos2021; @koike2023; @gaggero2021], whereas indices of autonomic reactivity were more strongly and negatively associated with IAS scores, supporting earlier observations that reactivity may reflect aspects of bodily signal processing captured by self-reported interoceptive accuracy [@todd2022].
@@
 
-Across mood and interoceptive variables, most item pairings displayed small-to-moderate standardized coefficients, indicating shared variance between interoceptive self-reports and affective tendencies.
+Across mood, most item pairings displayed small-to-moderate standardized coefficients, indicating shared variance between interoceptive self-reports and affective tendencies.
 In contrast, associations with psychopathology were more selective: negative associations were primarily observed for visceral pairings such as Hungry–Thirsty and Bruise–Blood sugar, whereas other domains yielded weaker or nonsignificant effects.
@@
 Associations with personality traits followed a similar domain-specific structure.
-Effects for the full IAS largely reflected contributions from specific pairings: Extraversion showed its strongest associations for Breathing–Heart, Neuroticism and Honesty–Humility for Hungry–Thirsty, and Openess, Conscientiousness and Agreeableness for the full scale.
+Effects for the full IAS largely reflected contributions from specific pairings: Extraversion showed its strongest associations for Bruise-Blood sugar, Neuroticism and Honesty–Humility for Hungry–Thirsty, and Openess, Conscientiousness and Agreeableness for the full scale.
 These results indicate that associations between interoceptive self-report and personality dimensions may depend on the bodily domain represented.
@@
 Visceral item pairs, particularly Hungry–Thirsty and Bruise–Blood sugar, showed the strongest and most consistent relationships with interoceptive, affective, and personality measures, whereas other pairs contributed little unique information, particularily in measures of psychopathologies and beliefs.
-These findings suggest that the shorter scale efficiently preserves these domain-specific associations, offering a more parsimonious assessment of self-reported interoceptive accuracy, though further validation across independent samples is warranted.
+These findings suggest that the shorter scale captures domain-specific patterns that were not evident in the full scale, offering a more efficient and nuanced measure of self-reported interoceptive accuracy, though further validation in independent samples is needed.
 

### 2025-11-04 paper/1_Initial/manuscript.qmd
added more to conclusion (unfinished)

@@
 Regarding its validity, the IAS has naturally been compared to other interoception-related measures, and shows a positive correlations with most facets of the MAIA [@mehling2018multidimensional; @gaggero2021], except for the Not-Distracting and Not-Worrying subscales [@brand2023] - which were previously highlighted as related to non-interoceptive abilities [@ferentzi2021examining].
-Interestingly, findings on the correlation between the IAS and the body awareness dimension of the BPQ, have been mixed: some studies report small positive correlations [@brand2023; @campos2021; @koike2023], while others find small negative correlations [@lin2023] or no correlation at all [@murphy2019].
+Interestingly, findings on the correlation between the IAS and the body awareness dimension of the BPQ, have been mixed: some studies report small positive correlations [@brand2023; @koike2023; @gaggero2021], while others find small negative correlations [@lin2023], a quadratic positve relationship [@campos2021] or no correlation at all [@murphy2019].
 Positive correlations have also been observed with the "observation" and "description" subscales of the Five Facet Mindfulness Questionnaire [FFMQ, @baer2006using; @brand2023; @koike2023], as well as with the "non-reactivity" and "acting with awareness" subscales [@koike2023].
@@
 The present study provides a comprehensive evaluation of the IAS, examining both its structure (study 1) and its dispositional correlates (study 2).
-These studies offer novel insights into the psychometric characteristics, conceptual interpretation, and practical applications of the IAS.
+These studies offer novel insights into the conceptual interpretation, and practical applications of the IAS.
 In this discussion, these findings are contextualized within the broader landscape of interoception research.
@@
 <!-- Study 1 findings -->
-A short version of the IAS was previously proposed by @lin2023, who suggested a 12-item version by removing items with local dependency, high difficulty, and/or low discrimination.
-Their parallel analysis supported a unidimensional structure, although this method tends to underestimate factor numbers in multidimensional data [@golino2017exploratory; @markos2024dimensionality].
+
+In Study 1, the factor structure of the IAS was reanalysed, leading to a refined 14-item version of the scale.
+A shorter IAS had previously been proposed by @lin2023, who developed a 12-item version by removing items with local dependency, high difficulty, or low discrimination.
+Their parallel analysis supported a unidimensional structure, although this method is known to underestimate the number of factors in multidimensional data [@golino2017exploratory; @markos2024dimensionality].
 Consequently, the 12-item IAS was interpreted as reflecting a single underlying factor of interoceptive accuracy.
 
-In contrast, Study 1 applied multiple complementary methods, including EGA, FA, and HCA.
-Across datasets and methods, the same tightly coupled item pairs consistently emerged, representing distinct bodily domains such as visceral sensations, musculoskeletal cues, and expulsion phenomena.
-Several items (e.g., Tickle, Taste, Affective Touch) were removed due to instability, redundancy, or weak associations, resulting in a refined 14-item IAS that retained psychometric robustness while improving interpretability and efficiency.
+In contrast, Study 1 applied multiple complementary analytical approaches, including EGA, FA, and HCA.
+Across datasets and methods, the same tightly coupled item pairs consistently emerged, corresponding to distinct bodily domains such as visceral sensations, musculoskeletal cues, and expulsion phenomena, after several items (e.g., Tickle, Taste, Affective Touch) were excluded due to instability, redundancy, or weak associations.
 
-These findings challenge the assumption of IAS unidimensionality [@murphy2019; @brand2023].
-Whereas @lin2023 ’s IRT-based approach treated locally dependent items as artefacts to be removed, our results suggest that such dependencies may reflect theoretically meaningful pairs (e.g., Heart–Breath).
-Because IRT assumes unidimensionality [@nguyen2014introduction], it may have obscured these structured item clusters rather than as theoretically relevant structures within interoceptive accuracy.
+These findings challenge the assumption that the IAS is unidimensional [@murphy2019; @brand2023].
+Whereas @lin2023’s Item Response Theory (IRT)-based approach treated locally dependent items as artefacts to be removed, our results suggest that such dependencies may instead represent theoretically meaningful relationships (e.g., Heart–Breathing).
+Because IRT assumes unidimensionality [@nguyen2014introduction], this approach may have obscured structured item clusters that capture distinct but interrelated aspects of interoceptive accuracy.
+Nevertheless, the resulting 14-item IAS from study 1 demonstrated greater interpretability and efficiency, although its psychometric properties require further validation.
 
 <!-- Study 2 findings -->
-Consistent with prior research, self-reported interoceptive accuracy, as assessed by the IAS, showed reliable associations with other interoceptive and interoception-related measures [@brand2023; @garfinkel2015knowing; @gaggero2021].
-Positive correlations emerged with interoceptive sensibility, particularly with MAIA facets related to noticing and trusting bodily sensations, attention regulation, and awareness of mind–body integration.
-In contrast, negative associations were observed with interoceptive deficits such as alexithymia and interoceptive confusion.
+
+Study 2 examined the associations between the IAS, its item pairs identified in Study 1, and a range of interoceptive, affective, psychopathological, personality, and related measures.
+Consistent with previous research, self-reported interoceptive accuracy as assessed by the IAS showed reliable associations with other interoceptive and interoception-related measures [@brand2023; @garfinkel2015knowing; @gaggero2021].
+Positive associations were found with interoceptive sensibility, particularly with MAIA facets reflecting noticing and trusting bodily sensations, attention regulation, and awareness of mind–body integration.
+In contrast, negative associations were observed with measures of interoceptive deficits, such as alexithymia and interoceptive confusion.
+
+Although the relationships between the BPQ–Body Awareness and the IAS, and between the BPQ–Autonomic Reactivity and the IAS, were both significant, they showed opposite directions: the former was positive, whereas the latter was negative.
+These results align with previous findings reporting a small positive association [@brand2023; @koike2023; @gaggero2021].
+However, the literature remains mixed regarding the direction, magnitude, and significance of the relationship between the body awareness subscale and the IAS, with some studies reporting negative associations [@lin2023] and others positive [@brand2023; @gaggero2021; @todd2022] and others quadratic [@campos2021].
+
+Moreover, the Body Awareness subscale has been criticised for its ambiguous instructions, specifically whether respondents are meant to indicate attentional focus on bodily sensations, perceived accuracy in detecting them, or simply the frequency of such sensations.
+As a result, associations with other measures may vary depending on how participants interpret the items [@campos2021; @gabriele2022dissociations; @gaggero2021].
+The theoretical focus of the BPQ-BA is also debated: some authors interpret it as assessing awareness of sensations during anxiety [@trevisan2021adaptive], whereas others view it as reflecting general awareness of both neutral and negative sensations [@desmedt2022].
+
+Thus, while we found a positive association between the BPQ–Body Awareness subscale and the IAS, this result should be interpreted with caution.
+Because we could not assess participants’ understanding of the BPQ items, we recommend that future studies using both the BPQ-BA and the IAS control for participants’ interpretation of the scale to clarify the nature of this relationship.
+
+Robust negative associations also emerged between the IAS and mood-related outcomes, aligning with broader evidence linking anxiety and depression to altered interoceptive processing [e.g., @brand2023; @khalsa2018; @nord2022interoceptive].
+However, recent studies have reported null or inconsistent associations between interoceptive abilities and mental health symptomatology, suggesting that these relationships may not generalize across bodily domains or measurement modalities [@banellis2025interoceptive; @jenkinson2024interoception].
+For instance, meta-analytic evidence indicates that cardiac interoceptive accuracy tasks are not consistently related to symptoms of depression or anxiety [@desmedt2022does; @jenkinson2024interoception].
+
+Most previous studies of interoceptive accuracy have relied on objective, performance-based tasks, whereas the IAS represents the first subjective measure explicitly designed to assess perceived interoceptive accuracy.
+However, correlations between IAS scores and objective measures are typically weak or absent [@arsllanova2022; @brand2023; @petzke2024somatic], highlighting a broader debate about how interoceptive accuracy should be conceptualised and measured.
+Many researchers argue that accuracy can only be assessed objectively through behavioural tasks, and that self-reports of interoceptive ability more appropriately reflect interoceptive sensibility - i.e., the self-perceived tendency to attend to and interpret bodily signals [@khalsa2018; @garfinkel2015knowing].
+
+Others propose that self-report measures should be distinguished according to the specific phenomenon assessed (e.g., attention vs perceived accuracy) to better align with contemporary conceptualisations of interoception [@desmedt2022measures; @murphy2019].
+Consistent with this view and the original aim of the validation paper, the IAS is a belief-based measure of one’s interoceptive ability rather than a direct index of accuracy.
+In other words, the IAS falls within the broader dimension of interoceptive sensibility or interoceptive self-report [@khalsa2018; @suksasilp2022towards], which does not imply a correlation with actual interoceptive performance.
+Ongoing discussions about terminology and measurement highlight the need for continued refinement to improve the reliability, validity, and conceptual clarity of interoceptive assessments [@desmedt2024conceptualization].
 

### 2025-11-04 paper/1_Initial/manuscript.qmd
added more to discussion (not finished)

@@
 
+<!-- Interoception and interoception-related -->
 Study 2 examined the associations between the IAS, its item pairs identified in Study 1, and a range of interoceptive, affective, psychopathological, personality, and related measures.
@@
 
-Although the relationships between the BPQ–Body Awareness and the IAS, and between the BPQ–Autonomic Reactivity and the IAS, were both significant, they showed opposite directions: the former was positive, whereas the latter was negative.
-These results align with previous findings reporting a small positive association [@brand2023; @koike2023; @gaggero2021].
+Although the relationships between the BPQ–Body Awareness and the IAS, and between the BPQ–Autonomic Reactivity and the IAS, were both significant, they showed opposite directions: the former was positive, whereas the latter was negative, aligning with previous findings [@brand2023; @koike2023; @gaggero2021].
 However, the literature remains mixed regarding the direction, magnitude, and significance of the relationship between the body awareness subscale and the IAS, with some studies reporting negative associations [@lin2023] and others positive [@brand2023; @gaggero2021; @todd2022] and others quadratic [@campos2021].
@@
 The theoretical focus of the BPQ-BA is also debated: some authors interpret it as assessing awareness of sensations during anxiety [@trevisan2021adaptive], whereas others view it as reflecting general awareness of both neutral and negative sensations [@desmedt2022].
-
 Thus, while we found a positive association between the BPQ–Body Awareness subscale and the IAS, this result should be interpreted with caution.
@@
 
+<!-- Mood -->
 Robust negative associations also emerged between the IAS and mood-related outcomes, aligning with broader evidence linking anxiety and depression to altered interoceptive processing [e.g., @brand2023; @khalsa2018; @nord2022interoceptive].
-However, recent studies have reported null or inconsistent associations between interoceptive abilities and mental health symptomatology, suggesting that these relationships may not generalize across bodily domains or measurement modalities [@banellis2025interoceptive; @jenkinson2024interoception].
-For instance, meta-analytic evidence indicates that cardiac interoceptive accuracy tasks are not consistently related to symptoms of depression or anxiety [@desmedt2022does; @jenkinson2024interoception].
+However, recent studies have reported null or inconsistent associations between interoceptive abilities and mental health symptomatology.
+For instance, meta-analytic evidence indicates that cardiac interoceptive accuracy tasks are not consistently related to symptoms of depression or anxiety [@desmedt2022does; @jenkinson2024interoception], uggesting that these relationships may not generalize across bodily domains or measurement modalities [@banellis2025interoceptive].
 
@@
 However, correlations between IAS scores and objective measures are typically weak or absent [@arsllanova2022; @brand2023; @petzke2024somatic], highlighting a broader debate about how interoceptive accuracy should be conceptualised and measured.
-Many researchers argue that accuracy can only be assessed objectively through behavioural tasks, and that self-reports of interoceptive ability more appropriately reflect interoceptive sensibility - i.e., the self-perceived tendency to attend to and interpret bodily signals [@khalsa2018; @garfinkel2015knowing].
+Some researchers argue that accuracy can only be assessed objectively through behavioural tasks, and that self-reports of interoceptive ability more appropriately reflect interoceptive sensibility - i.e., the self-perceived tendency to attend to bodily signals [@khalsa2018; @garfinkel2015knowing].
 
-Others propose that self-report measures should be distinguished according to the specific phenomenon assessed (e.g., attention vs perceived accuracy) to better align with contemporary conceptualisations of interoception [@desmedt2022measures; @murphy2019].
+Others propose that self-report measures should be distinguished according to the specific phenomenon assessed (e.g., attention vs perceived accuracy) to better align with contemporary conceptualisations of interoception [@desmedt2022measures].
 Consistent with this view and the original aim of the validation paper, the IAS is a belief-based measure of one’s interoceptive ability rather than a direct index of accuracy.
@@
 Ongoing discussions about terminology and measurement highlight the need for continued refinement to improve the reliability, validity, and conceptual clarity of interoceptive assessments [@desmedt2024conceptualization].
+
+<!-- IAS domainn-specific  -->
+While the IAS represents a promising tool within the evolving landscape of interoception measurement [@desmedt2022measures; @suksasilp2022towards], our study highlights a potential domain-specificity of the scale, i.e., certain bodily domains appear to drive the observed associations, suggesting that the IAS may not uniformly reflect general self-reported interoceptive accuracy across all sensations.
+
+Empirically, specific item pairs, most consistently Hunger–Thirst, Bruise–Blood sugar, and Muscles–Pain, showed reliable negative correlations with depression and anxiety, sometimes matching or exceeding effects observed for the full IAS.
+These pairings also exhibited the most consistent associations with psychopathology measures, whereas other pairings showed no robust significant relationships.
+Some pairings also revealed associations with other clinical or interoceptive measures (e.g., Hunger–Thirst with borderline personality indices) that were not apparent in the aggregate score of the full scale.
+In contrast, other pairings (e.g., Breathing–Heart, Cough–Sneeze, Wind–Burp) contributed little unique variance.
+These findings indicate that relying solely on the total IAS score may obscure meaningful relationships and caution against treating the scale as strictly unitary.
+
+Interpretation is further complicated by the lack of contextual information in IAS items.
+For instance, a racing heart could reflect anxiety or physical exertion; without context, it is unclear which bodily state participants report.
+Consistent with prior work emphasizing contextualized assessment [@vlemincx2023novel], our results suggest that the utility of self-report may lie less in broad aggregation across domains and more in targeted evaluation of physiologically and situationally meaningful sensations.
+Collectively, these findings underscore the value of domain-specific and potentially context-sensitive analyses for understanding the relevance and interpretability of self-reported interoception and suggest that the IAS may benefit from a more differentiated approach that accounts for these influences.
+
+<!-- Further improvements to the IAS -->
+Our results also suggest several avenues for improving the IAS.
+Analogue-style rating scales captured greater variability, enhancing sensitivity to individual differences, and specific item pairings allowed more precise differentiation among individuals, often outperforming global scores in predictive value.
+However, even the refined 14-item IAS has limitations: it underrepresents key interoceptive modalities such as cardiac, respiratory, and nuanced somatosensory signals, limiting its ability to capture the full breadth of interoceptive processes.
+
+These limitations highlight the need for future scale development that balances breadth (covering multiple items per modality) with depth (domain-specific subscales), incorporates contextualized item wording to clarify which bodily states participants report, retains the benefits of analogue or wider rating ranges (e.g., 1–7 instead of 1–5), and optimizes coverage across physiologically and psychologically relevant bodily domains.
+Such an approach would improve interpretability, sensitivity, and practical utility, enabling a more nuanced mapping of interoceptive abilities onto affective, cognitive, and health-related outcomes.
+
+<!-- Limitations -->
+Lastly, while we did not evaluate the IAS alongside other widely used questionnaires, such as the BPQ or MAIA, it is worth noting several limitations of these frequently used questionnaires.
+The MAIA-2 contains subscales (e.g., Not-Worrying, Not-Distracting) with weak reliability and minimal relation to a general interoception factor [@ferentzi2021examining; @rogowska2023validation].
+Other subscales primarily reflect higher-level cognitive tendencies, such as mindfulness and attentional regulation, rather than interoceptive body awareness [@todd2022; @vig2023self].
+Similarly, the BPQ’s Body Awareness and Autonomic Reactivity subscales show conceptual and psychometric concerns, and BPQ scores often overlap substantially with negative affect, raising questions about their specificity as measures of interoceptive sensibility [@campos2021; @gabriele2022dissociations; @vig2023self].
+
+Because the IAS is a newly developed questionnaire and the only one designed to assess interoceptive self-reported accuracy - a dimension previously assessed solely through objective tasks such as the HDT and HCT - our focus was on evaluating its structure and correlates without introducing established measures with documented shortcomings.
+Nonetheless, future research should employ novel methods, such as Exploratory Graph Analysis, to clarify the convergent and divergent validity of these questionnaires across interoceptive domains.
 

### 2025-11-04 paper/1_Initial/manuscript.qmd
minor

@@
 Their parallel analysis supported a unidimensional structure, although this method is known to underestimate the number of factors in multidimensional data [@golino2017exploratory; @markos2024dimensionality].
-Consequently, the 12-item IAS was interpreted as reflecting a single underlying factor of interoceptive accuracy.
+Consequently, the 12-item IAS was interpreted as reflecting a single underlying factor of interoceptive self-reported accuracy.
 
 In contrast, Study 1 applied multiple complementary analytical approaches, including EGA, FA, and HCA.
-Across datasets and methods, the same tightly coupled item pairs consistently emerged, corresponding to distinct bodily domains such as visceral sensations, musculoskeletal cues, and expulsion phenomena, after several items (e.g., Tickle, Taste, Affective Touch) were excluded due to instability, redundancy, or weak associations.
+Across datasets and methods, after several items (e.g., Tickle, Taste, Affective Touch) were excluded due to instability, redundancy, or weak associations, the same tightly coupled item pairs consistently emerged, corresponding to distinct bodily domains such as visceral sensations, musculoskeletal cues, and expulsion phenomena.
 
-These findings challenge the assumption that the IAS is unidimensional [@murphy2019; @brand2023].
+Our findings challenge the assumption that the IAS is unidimensional [@murphy2019; @brand2023].
 Whereas @lin2023’s Item Response Theory (IRT)-based approach treated locally dependent items as artefacts to be removed, our results suggest that such dependencies may instead represent theoretically meaningful relationships (e.g., Heart–Breathing).
-Because IRT assumes unidimensionality [@nguyen2014introduction], this approach may have obscured structured item clusters that capture distinct but interrelated aspects of interoceptive accuracy.
-Nevertheless, the resulting 14-item IAS from study 1 demonstrated greater interpretability and efficiency, although its psychometric properties require further validation.
+Because IRT assumes unidimensionality [@nguyen2014introduction], this approach may have obscured, in their paper, structured item clusters that capture distinct but interrelated aspects of interoceptive self-reported accuracy.
+Nevertheless, the resulting 14-item IAS from study 1 demonstrated greater interpretability and efficiency, although its psychometric properties still require further validation.
 
@@
 <!-- Interoception and interoception-related -->
-Study 2 examined the associations between the IAS, its item pairs identified in Study 1, and a range of interoceptive, affective, psychopathological, personality, and related measures.
+Study 2 examined the associations between the IAS, the item pairs identified in Study 1, and a range of interoceptive, affective, psychopathological, personality, and related measures.
 Consistent with previous research, self-reported interoceptive accuracy as assessed by the IAS showed reliable associations with other interoceptive and interoception-related measures [@brand2023; @garfinkel2015knowing; @gaggero2021].
@@
 Although the relationships between the BPQ–Body Awareness and the IAS, and between the BPQ–Autonomic Reactivity and the IAS, were both significant, they showed opposite directions: the former was positive, whereas the latter was negative, aligning with previous findings [@brand2023; @koike2023; @gaggero2021].
-However, the literature remains mixed regarding the direction, magnitude, and significance of the relationship between the body awareness subscale and the IAS, with some studies reporting negative associations [@lin2023] and others positive [@brand2023; @gaggero2021; @todd2022] and others quadratic [@campos2021].
+However, the literature remains mixed regarding the direction, magnitude, and significance of the relationship between the Body Awareness subscale and the IAS, with some studies reporting negative associations [@lin2023] and others positive [@brand2023; @gaggero2021; @todd2022] and others quadratic [@campos2021].
 
@@
 As a result, associations with other measures may vary depending on how participants interpret the items [@campos2021; @gabriele2022dissociations; @gaggero2021].
-The theoretical focus of the BPQ-BA is also debated: some authors interpret it as assessing awareness of sensations during anxiety [@trevisan2021adaptive], whereas others view it as reflecting general awareness of both neutral and negative sensations [@desmedt2022].
+The theoretical focus of the BPQ-BA has also been debated: some authors interpret it as assessing awareness of sensations during anxiety [@trevisan2021adaptive], whereas others view it as reflecting general awareness of both neutral and negative sensations [@desmedt2022].
 Thus, while we found a positive association between the BPQ–Body Awareness subscale and the IAS, this result should be interpreted with caution.
-Because we could not assess participants’ understanding of the BPQ items, we recommend that future studies using both the BPQ-BA and the IAS control for participants’ interpretation of the scale to clarify the nature of this relationship.
+Since we could not assess participants’ interpretation of the BPQ items, we recommend that future studies using both the Body Awareness subscale and the IAS control for participants’ interpretation to clarify the nature of this relationship.
 
@@
 However, recent studies have reported null or inconsistent associations between interoceptive abilities and mental health symptomatology.
-For instance, meta-analytic evidence indicates that cardiac interoceptive accuracy tasks are not consistently related to symptoms of depression or anxiety [@desmedt2022does; @jenkinson2024interoception], uggesting that these relationships may not generalize across bodily domains or measurement modalities [@banellis2025interoceptive].
+For instance, meta-analytic evidence indicates that cardiac interoceptive accuracy tasks are not consistently related to symptoms of depression or anxiety [@desmedt2022does; @jenkinson2024interoception], suggesting that these relationships may not generalize across bodily domains or measurement modalities [@banellis2025interoceptive].
 
 Most previous studies of interoceptive accuracy have relied on objective, performance-based tasks, whereas the IAS represents the first subjective measure explicitly designed to assess perceived interoceptive accuracy.
-However, correlations between IAS scores and objective measures are typically weak or absent [@arsllanova2022; @brand2023; @petzke2024somatic], highlighting a broader debate about how interoceptive accuracy should be conceptualised and measured.
+However, correlations between IAS scores and objective measures of accuracy are typically weak or absent [@arslanova2022; @brand2023; @petzke2024somatic], highlighting a broader debate about how interoceptive accuracy should be conceptualised and measured.
 Some researchers argue that accuracy can only be assessed objectively through behavioural tasks, and that self-reports of interoceptive ability more appropriately reflect interoceptive sensibility - i.e., the self-perceived tendency to attend to bodily signals [@khalsa2018; @garfinkel2015knowing].
@@
 These pairings also exhibited the most consistent associations with psychopathology measures, whereas other pairings showed no robust significant relationships.
+
 Some pairings also revealed associations with other clinical or interoceptive measures (e.g., Hunger–Thirst with borderline personality indices) that were not apparent in the aggregate score of the full scale.

### 2025-11-05 paper/1_Initial/manuscript.qmd
minor
incomplete conclusion

--- 2025-11-04 paper/1_Initial/manuscript.qmd
@@
 <!-- Aims -->
-The present study provides a comprehensive evaluation of the IAS, examining both its structure (study 1) and its dispositional correlates (study 2).
+The present mega-analysis provides a comprehensive evaluation of the IAS, examining both its structure (study 1) and its dispositional correlates (study 2).
 These studies offer novel insights into the conceptual interpretation, and practical applications of the IAS.
@@
 
-<!-- Study 1 findings -->
+<!-- Structural insights from Study 1 -->
 
-In Study 1, the factor structure of the IAS was reanalysed, leading to a refined 14-item version of the scale.
-A shorter IAS had previously been proposed by @lin2023, who developed a 12-item version by removing items with local dependency, high difficulty, or low discrimination.
-Their parallel analysis supported a unidimensional structure, although this method is known to underestimate the number of factors in multidimensional data [@golino2017exploratory; @markos2024dimensionality].
-Consequently, the 12-item IAS was interpreted as reflecting a single underlying factor of interoceptive accuracy.
+Study 1 re-analysed the IAS structure using a combination of traditional psychometric and network-based methods.
+Across these complementary approaches, seven stable item pairs consistently emerged (i.e., Hungry–Thirsty, Urinate–Defecate, Muscles–Pain, Breathing–Heart, Cough–Sneeze, Wind–Burp, and Bruise–Blood sugar) yielding a refined 14-item structure that demonstrated superior model fit and cross-dataset stability compared to previously proposed unidimensional or bifactor solutions.
+These findings challenge earlier interpretations of the IAS as reflecting a single latent construct [e.g., @brand2023; @murphy2019] and instead indicate that the scale captures multiple, interrelated but domain-specific clusters of bodily sensations.
 
-In contrast, Study 1 applied multiple complementary analytical approaches, including EGA, FA, and HCA.
-Across datasets and methods, the same tightly coupled item pairs consistently emerged, corresponding to distinct bodily domains such as visceral sensations, musculoskeletal cues, and expulsion phenomena, after several items (e.g., Tickle, Taste, Affective Touch) were excluded due to instability, redundancy, or weak associations.
+A shorter version of the IAS was previously proposed by @lin2023, who developed a 12-item form based on item response theory analyses.
+Their analysis supported a unidimensional structure, which they interpreted as indexing a single factor of self-reported interoceptive accuracy.
+In contrast, the present results suggest that apparent local dependencies between items may not represent measurement artefacts but rather theoretically meaningful associations among functionally or phenomenologically coupled sensations (e.g., Heart–Breathing), corresponding to distinct bodily domains such as visceral sensations, musculoskeletal cues, and expulsion phenomena.
 
-These findings challenge the assumption that the IAS is unidimensional [@murphy2019; @brand2023].
-Whereas @lin2023’s Item Response Theory (IRT)-based approach treated locally dependent items as artefacts to be removed, our results suggest that such dependencies may instead represent theoretically meaningful relationships (e.g., Heart–Breathing).
-Because IRT assumes unidimensionality [@nguyen2014introduction], this approach may have obscured structured item clusters that capture distinct but interrelated aspects of interoceptive accuracy.
-Nevertheless, the resulting 14-item IAS from study 1 demonstrated greater interpretability and efficiency, although its psychometric properties require further validation.
+Such pairings likely reflect sensations that co-occur physiologically or contextually, such as hunger and thirst, or coughing and sneezing, and tend to be perceived and appraised together.
+This pattern implies that perceived accuracy within one bodily domain generalizes to related sensations, yielding a clustered rather than continuous organization of interoceptive beliefs.
 
-<!-- Study 2 findings -->
+<!-- there is a paper that states this better but cannot find it yet --> 
+Notably, objective interoceptive accuracy tasks across modalities often show weak or absent associations [e.g., @bruni2023interoception; @ferentzi2018interoceptive; @garfinkel2016interoceptive], whereas self-reported interoceptive beliefs appear to cluster more strongly within shared physiological domains [**ref**].
+This divergence reinforces the view that subjective interoceptive accuracy may reflect a domain-specific self-belief system rather than a general perceptual ability.
 
-Study 2 examined the associations between the IAS, its item pairs identified in Study 1, and a range of interoceptive, affective, psychopathological, personality, and related measures.
-Consistent with previous research, self-reported interoceptive accuracy as assessed by the IAS showed reliable associations with other interoceptive and interoception-related measures [@brand2023; @garfinkel2015knowing; @gaggero2021].
-Positive associations were found with interoceptive sensibility, particularly with MAIA facets reflecting noticing and trusting bodily sensations, attention regulation, and awareness of mind–body integration.
-In contrast, negative associations were observed with measures of interoceptive deficits, such as alexithymia and interoceptive confusion.
+<!-- Dispositional correlates and domain specificity (Study 2) -->
 
-Although the relationships between the BPQ–Body Awareness and the IAS, and between the BPQ–Autonomic Reactivity and the IAS, were both significant, they showed opposite directions: the former was positive, whereas the latter was negative.
-These results align with previous findings reporting a small positive association [@brand2023; @koike2023; @gaggero2021].
-However, the literature remains mixed regarding the direction, magnitude, and significance of the relationship between the body awareness subscale and the IAS, with some studies reporting negative associations [@lin2023] and others positive [@brand2023; @gaggero2021; @todd2022] and others quadratic [@campos2021].
+<!-- Interoception and interoception-related -->
+Study 2 extended these findings by examining associations between IAS scores from the full scale and the pairings identified in study 1, with a broad set of interoceptive, affective, personality, and belief-related measures.
+Consistent with prior research [e.g., @brand2023; @garfinkel2015knowing; @gaggero2021], the IAS showed positive associations with measures of interoceptive sensibility (e.g., MAIA subscales reflecting noticing, attention regulation, and body trust) and negative associations with measures of interoceptive difficulties (e.g., alexithymia and interoceptive confusion).
 
-Moreover, the Body Awareness subscale has been criticised for its ambiguous instructions, specifically whether respondents are meant to indicate attentional focus on bodily sensations, perceived accuracy in detecting them, or simply the frequency of such sensations.
-As a result, associations with other measures may vary depending on how participants interpret the items [@campos2021; @gabriele2022dissociations; @gaggero2021].
-The theoretical focus of the BPQ-BA is also debated: some authors interpret it as assessing awareness of sensations during anxiety [@trevisan2021adaptive], whereas others view it as reflecting general awareness of both neutral and negative sensations [@desmedt2022].
+Although associations between the IAS and the BPQ subscales replicated prior work (e.g., @Brand2023; @Koike2023; @Gaggero2021), interpretation remains uncertain due to conceptual ambiguity in the BPQ–Body Awareness subscale.
+Prior studies have reported positive, negative, and even quadratic relationships (e.g., @Campos2021; @Lin2023), and some authors have suggested that these mixed findings stem from divergent interpretations of the items—specifically, whether they capture attentional focus on bodily sensations or perceived accuracy in detecting them (e.g., @Gabriele2022Dissociations; @Trevisan2021Adaptive).
+Thus, although we observed a positive association between the BPQ–Body Awareness and the IAS, this result should be interpreted with caution, and future studies should assess participants’ understanding of BPQ items to clarify the nature of this relationship.
 
-Thus, while we found a positive association between the BPQ–Body Awareness subscale and the IAS, this result should be interpreted with caution.
-Because we could not assess participants’ understanding of the BPQ items, we recommend that future studies using both the BPQ-BA and the IAS control for participants’ interpretation of the scale to clarify the nature of this relationship.
+<!-- Mood and psychopathological disorders domain specific -->
 
-Robust negative associations also emerged between the IAS and mood-related outcomes, aligning with broader evidence linking anxiety and depression to altered interoceptive processing [e.g., @brand2023; @khalsa2018; @nord2022interoceptive].
-However, recent studies have reported null or inconsistent associations between interoceptive abilities and mental health symptomatology, suggesting that these relationships may not generalize across bodily domains or measurement modalities [@banellis2025interoceptive; @jenkinson2024interoception].
-For instance, meta-analytic evidence indicates that cardiac interoceptive accuracy tasks are not consistently related to symptoms of depression or anxiety [@desmedt2022does; @jenkinson2024interoception].
+Across dispositional constructs, negative associations emerged between self-reported interoceptive accuracy (IAS) and a range of affective and psychopathological traits.
+Individuals reporting greater symptoms of depression and anxiety also tended to perceive themselves as less accurate in detecting bodily signals.
+Crucially, these associations were not uniform across bodily domains: the strongest effects consistently involved visceral items (e.g., hunger, thirst), whereas cardioceptive and respiratory items showed weaker or inconsistent patterns.
+This domain-specific pattern highlights that self-perceived accuracy in internal bodily regulation is more psychologically and clinically relevant than accuracy in reflexive or surface-bodily sensations.
 
-Most previous studies of interoceptive accuracy have relied on objective, performance-based tasks, whereas the IAS represents the first subjective measure explicitly designed to assess perceived interoceptive accuracy.
-However, correlations between IAS scores and objective measures are typically weak or absent [@arsllanova2022; @brand2023; @petzke2024somatic], highlighting a broader debate about how interoceptive accuracy should be conceptualised and measured.
-Many researchers argue that accuracy can only be assessed objectively through behavioural tasks, and that self-reports of interoceptive ability more appropriately reflect interoceptive sensibility - i.e., the self-perceived tendency to attend to and interpret bodily signals [@khalsa2018; @garfinkel2015knowing].
+This domain-specificity may help explain inconsistencies in the literature linking interoception and emotional symptomatology.
+Reviews and meta-analyses indicate that performance-based measures of cardiac interoceptive accuracy, historically the dominant index of interoception, are often unrelated to depression or anxiety [@jenkinson2024interoception; @banellis2025interoceptive; @adams2022association].
+In contrast, self-reported interoceptive measures show stronger, albeit sometimes divergent, associations with internalizing traits [e.g., @brand2022; @lin2023; @clemente2024relationship; @murphy2019].
+These discrepancies likely reflect the distinction between objective sensitivity and metacognitive self-belief [@khalsa2018; @garfinkel2015knowing; @suksasilp2022towards].
+Our results extend this view by demonstrating that even within self-reported interoception, relationships with affective traits are structured along bodily axes, reinforcing the importance of considering domain-specific facets of the IAS.
 
-Others propose that self-report measures should be distinguished according to the specific phenomenon assessed (e.g., attention vs perceived accuracy) to better align with contemporary conceptualisations of interoception [@desmedt2022measures; @murphy2019].
-Consistent with this view and the original aim of the validation paper, the IAS is a belief-based measure of one’s interoceptive ability rather than a direct index of accuracy.
-In other words, the IAS falls within the broader dimension of interoceptive sensibility or interoceptive self-report [@khalsa2018; @suksasilp2022towards], which does not imply a correlation with actual interoceptive performance.
-Ongoing discussions about terminology and measurement highlight the need for continued refinement to improve the reliability, validity, and conceptual clarity of interoceptive assessments [@desmedt2024conceptualization].
+Beyond mood, similar but weaker patterns emerged across other dispositional traits, again following a visceral-focused gradient.
+Autistic traits, schizotypal tendencies, and maladaptive personality dimensions generally correlated negatively with IAS scores, primarily for visceral items, whereas cardioceptive and respiratory beliefs contributed little.
+These findings align with evidence that interoceptive self-beliefs are attenuated in conditions involving social–emotional difficulties or reduced bodily awareness.
+For example, interoceptive dimensions predict interpersonal-like and disorganized-like schizotypal traits [@pasciucco2025predictive], and autistic individuals report subjective difficulties perceiving internal bodily states such as hunger, thirst, and fatigue, even when objective measures of accuracy are intact [@itoi2023relationship].
+More broadly, atypical interoception constitutes a transdiagnostic risk factor for psychopathology, again emphasizing differences across bodily domains [@brewer2023atypical].
+Collectively, these results underscore that diminished self-perceived interoceptive accuracy is not a uniform trait but varies systematically by bodily domain, with visceral beliefs showing the clearest psychological relevance.
+
+Taken together, the evidence indicates that the IAS reflects a domain-structured metacognitive construct, complementary to but distinct from objective interoceptive performance.
+Visceral beliefs—linked to hunger, thirst, or pain—consistently show the strongest relationships with emotional and dispositional traits, whereas cardioceptive and respiratory beliefs contribute little.
+Recognizing this domain specificity not only clarifies inconsistencies in prior studies emphasizing heartbeat detection but also highlights the importance of assessing a wider range of interoceptive modalities in future research, particularly those related to visceral homeostasis.
 

### 2025-11-06 paper/1_Initial/manuscript.qmd
General discussion re-written

@@
 
-Study 1 re-analysed the IAS structure using a combination of traditional psychometric and network-based methods.
-Across these complementary approaches, seven stable item pairs consistently emerged (i.e., Hungry–Thirsty, Urinate–Defecate, Muscles–Pain, Breathing–Heart, Cough–Sneeze, Wind–Burp, and Bruise–Blood sugar) yielding a refined 14-item structure that demonstrated superior model fit and cross-dataset stability compared to previously proposed unidimensional or bifactor solutions.
-These findings challenge earlier interpretations of the IAS as reflecting a single latent construct [e.g., @brand2023; @murphy2019] and instead indicate that the scale captures multiple, interrelated but domain-specific clusters of bodily sensations.
+<!-- Structural insights from Study 1 -->
 
-A shorter version of the IAS was previously proposed by @lin2023, who developed a 12-item form based on item response theory analyses.
-Their analysis supported a unidimensional structure, which they interpreted as indexing a single factor of self-reported interoceptive accuracy.
-In contrast, the present results suggest that apparent local dependencies between items may not represent measurement artefacts but rather theoretically meaningful associations among functionally or phenomenologically coupled sensations (e.g., Heart–Breathing), corresponding to distinct bodily domains such as visceral sensations, musculoskeletal cues, and expulsion phenomena.
+Study 1 re-analysed the IAS using complementary psychometric and network-based approaches.
+Across analyses, seven stable item pairings emerged (Hungry–Thirsty, Urinate–Defecate, Muscles–Pain, Breathing–Heart, Cough–Sneeze, Wind–Burp, and Bruise–Blood sugar), yielding a refined 14-item structure with superior fit and cross-dataset stability compared to previously proposed unidimensional or bifactor models.
+These results challenge interpretations of the IAS as a single latent construct [e.g., @brand2023; @murphy2019] and instead indicate that it captures multiple, interrelated but domain-specific clusters of bodily sensations.
 
-Such pairings likely reflect sensations that co-occur physiologically or contextually, such as hunger and thirst, or coughing and sneezing, and tend to be perceived and appraised together.
-This pattern implies that perceived accuracy within one bodily domain generalizes to related sensations, yielding a clustered rather than continuous organization of interoceptive beliefs.
-
-<!-- there is a paper that states this better but cannot find it yet --> 
-Notably, objective interoceptive accuracy tasks across modalities often show weak or absent associations [e.g., @bruni2023interoception; @ferentzi2018interoceptive; @garfinkel2016interoceptive], whereas self-reported interoceptive beliefs appear to cluster more strongly within shared physiological domains [**ref**].
-This divergence reinforces the view that subjective interoceptive accuracy may reflect a domain-specific self-belief system rather than a general perceptual ability.
+Unlike @lin2023, whose 12-item solution supported unidimensionality, the present findings suggest that local dependencies between items reflect meaningful theoretical coupling among functionally related sensations (e.g., Heart–Breathing).
+Such clustering likely mirrors the way bodily signals co-occur physiologically or phenomenologically (e.., hunger with thirst, coughing with sneezing) and are therefore perceived and evaluated together.
+Perceived accuracy in one bodily system may generalize to conceptually or functionally linked sensations, yielding a clustered rather than continuous organization of interoceptive beliefs.
+Consistent with this view, self-reported interoceptive awareness across related axes (e.g., cardiac and respiratory) tends to show positive associations [@garfinkel2016interoceptive], whereas objective measures of interoceptive accuracy across modalities typically show weak or absent correlations [@bruni2023interoception; @ferentzi2018interoceptive].
+This dissociation suggests that subjective interoceptive beliefs are structured according to functional bodily domains rather than reflecting a single general capacity.
 
@@
 <!-- Interoception and interoception-related -->
-Study 2 extended these findings by examining associations between IAS scores from the full scale and the pairings identified in study 1, with a broad set of interoceptive, affective, personality, and belief-related measures.
-Consistent with prior research [e.g., @brand2023; @garfinkel2015knowing; @gaggero2021], the IAS showed positive associations with measures of interoceptive sensibility (e.g., MAIA subscales reflecting noticing, attention regulation, and body trust) and negative associations with measures of interoceptive difficulties (e.g., alexithymia and interoceptive confusion).
+Study 2 extended these findings by examining the IAS’s associations with interoceptive, affective, personality, and belief-related traits.
+Consistent with prior work, the IAS correlated positively with adaptive aspects of interoceptive sensibility (e.g., MAIA subscales reflecting noticing, attention regulation, and body trust) and negatively with interoceptive difficulties, namely alexithymia and interoceptive confusion [e.g., @brand2023; @garfinkel2015knowing; @gaggero2021].
 
-Although associations between the IAS and the BPQ subscales replicated prior work (e.g., @Brand2023; @Koike2023; @Gaggero2021), interpretation remains uncertain due to conceptual ambiguity in the BPQ–Body Awareness subscale.
-Prior studies have reported positive, negative, and even quadratic relationships (e.g., @Campos2021; @Lin2023), and some authors have suggested that these mixed findings stem from divergent interpretations of the items—specifically, whether they capture attentional focus on bodily sensations or perceived accuracy in detecting them (e.g., @Gabriele2022Dissociations; @Trevisan2021Adaptive).
+<!-- Although associations between the IAS and the BPQ subscales replicated prior work (e.g., @brand2023; @koike2023; @gaggero2021), interpretation remains uncertain due to conceptual ambiguity in the BPQ–Body Awareness subscale.
+Prior studies have reported positive, negative, and even quadratic relationships (e.g., @campos2021; @lin2023), and some authors have suggested that these mixed findings stem from divergent interpretations of the items—specifically, whether they capture attentional focus on bodily sensations or perceived accuracy in detecting them (e.g., @gabriele2022Dissociations; @campos2021).
 Thus, although we observed a positive association between the BPQ–Body Awareness and the IAS, this result should be interpreted with caution, and future studies should assess participants’ understanding of BPQ items to clarify the nature of this relationship.
+-->
 
 <!-- Mood and psychopathological disorders domain specific -->
+Across dispositional constructs, individuals reporting higher symptoms of depression and anxiety tended to perceive themselves as less accurate in detecting bodily signals, in line with previous findings [e.g., @brand2023; @khalsa2018; @nord2022interoceptive].
+Crucially, these associations were not uniform across bodily domains: the strongest effects involved visceral sensations (e.g., hunger, thirst), whereas cardiorespiratory and expulsion domains showed weaker or inconsistent relationships.
+This domain specificity suggests that beliefs about one’s visceral accuracy may be more psychologically and clinically relevant than beliefs about reflexive or surface sensations.
 
-Across dispositional constructs, negative associations emerged between self-reported interoceptive accuracy (IAS) and a range of affective and psychopathological traits.
-Individuals reporting greater symptoms of depression and anxiety also tended to perceive themselves as less accurate in detecting bodily signals.
-Crucially, these associations were not uniform across bodily domains: the strongest effects consistently involved visceral items (e.g., hunger, thirst), whereas cardioceptive and respiratory items showed weaker or inconsistent patterns.
-This domain-specific pattern highlights that self-perceived accuracy in internal bodily regulation is more psychologically and clinically relevant than accuracy in reflexive or surface-bodily sensations.
+This pattern may help clarify inconsistencies in the literature linking interoception and emotion.
+Reviews and meta-analyses report that performance-based measures of interoceptive accuracy, particularly in cardioception, often show weak or absent correlations with depression and anxiety [@jenkinson2024interoception; @banellis2025interoceptive; @adams2022association].
+In contrast, self-reported interoceptive measures typically show stronger, often negative, associations with internalizing traits [e.g., @brand2022; @lin2023; @clemente2024relationship].
+These discrepancies likely reflect both conceptual distinctions between perceptual accuracy and metacognitive self-belief [@khalsa2018; @garfinkel2015knowing; @suksasilp2022towards] and variation in the bodily domains assessed.
+The present results extend this framework by demonstrating that associations between interoceptive self-beliefs and affective traits are concentrated in psychologically salient visceral domains.
+Thus, the field’s heavy reliance on cardioceptive tasks may have obscured more meaningful relationships in other interoceptive modalities.
 
-This domain-specificity may help explain inconsistencies in the literature linking interoception and emotional symptomatology.
-Reviews and meta-analyses indicate that performance-based measures of cardiac interoceptive accuracy, historically the dominant index of interoception, are often unrelated to depression or anxiety [@jenkinson2024interoception; @banellis2025interoceptive; @adams2022association].
-In contrast, self-reported interoceptive measures show stronger, albeit sometimes divergent, associations with internalizing traits [e.g., @brand2022; @lin2023; @clemente2024relationship; @murphy2019].
-These discrepancies likely reflect the distinction between objective sensitivity and metacognitive self-belief [@khalsa2018; @garfinkel2015knowing; @suksasilp2022towards].
-Our results extend this view by demonstrating that even within self-reported interoception, relationships with affective traits are structured along bodily axes, reinforcing the importance of considering domain-specific facets of the IAS.
+<!-- Psychopathology -->
+Beyond mood, similar though weaker patterns emerged for autistic traits, schizotypy, and maladaptive personality dimensions.
+These traits tended to correlate negatively with self-perceived interoceptive accuracy, particularly within visceral and musculoskeletal domains, while showing little or no association in other areas.
+This selective pattern suggests that diminished confidence in bodily perception may contribute to specific social–emotional and personality features, rather than reflecting a general interoceptive deficit.
+These results align with evidence that interoceptive self-beliefs, more than objective accuracy, track variation in emotional awareness, social connectedness, and psychopathology [@torregrossa2022interoceptive; @williams2023characterizing; @brand2022].
 
-Beyond mood, similar but weaker patterns emerged across other dispositional traits, again following a visceral-focused gradient.
-Autistic traits, schizotypal tendencies, and maladaptive personality dimensions generally correlated negatively with IAS scores, primarily for visceral items, whereas cardioceptive and respiratory beliefs contributed little.
-These findings align with evidence that interoceptive self-beliefs are attenuated in conditions involving social–emotional difficulties or reduced bodily awareness.
-For example, interoceptive dimensions predict interpersonal-like and disorganized-like schizotypal traits [@pasciucco2025predictive], and autistic individuals report subjective difficulties perceiving internal bodily states such as hunger, thirst, and fatigue, even when objective measures of accuracy are intact [@itoi2023relationship].
-More broadly, atypical interoception constitutes a transdiagnostic risk factor for psychopathology, again emphasizing differences across bodily domains [@brewer2023atypical].
-Collectively, these results underscore that diminished self-perceived interoceptive accuracy is not a uniform trait but varies systematically by bodily domain, with visceral beliefs showing the clearest psychological relevance.
+Taken together, these findings suggest that self-perceived interoceptive accuracy is a differentiated construct, varying systematically across bodily systems and psychological traits.
+Beliefs about visceral sensations, in particular, show the most consistent associations with affective and dispositional features.
+Although modest in magnitude, these effects underscore the value of considering domain-specificity when linking interoceptive beliefs to emotion and mental health.
 
-Taken together, the evidence indicates that the IAS reflects a domain-structured metacognitive construct, complementary to but distinct from objective interoceptive performance.
-Visceral beliefs—linked to hunger, thirst, or pain—consistently show the strongest relationships with emotional and dispositional traits, whereas cardioceptive and respiratory beliefs contribute little.
-Recognizing this domain specificity not only clarifies inconsistencies in prior studies emphasizing heartbeat detection but also highlights the importance of assessing a wider range of interoceptive modalities in future research, particularly those related to visceral homeostasis.
+<!-- Methodological and applied considerations -->
+Methodologically, combining traditional psychometrics with network-based approaches proved valuable.
+EGA complemented factor analysis by identifying meaningful inter-item dependencies, producing a more interpretable and stable structure.
+The refined 14-item IAS balances parsimony and predictive validity, illustrating how network-informed scale refinement, beyond scale development [@golino2017exploratory], can enhance construct clarity.
+
+The IAS nonetheless remains limited in scope.
+Certain interoceptive modalities (e.g., gastric, tactile) are underrepresented, and items lack contextual specification (e.g., physiological vs.
+affective triggers).
+For instance, a racing heart could signal anxiety or exercise; without context, it is unclear which state participants referenced from.
+Such ambiguities may constrain ecological validity and contribute to variability across studies [@vlemincx2023novel].
+Expanding item content and adopting context-specific phrasing will be important for future measurement development.
+
+Clinically, the domain-specific structure of the IAS highlights that interoceptive disruptions in affective and psychopathological conditions may center primarily on beliefs about visceral sensations rather than global interoceptive deficits.
+This perspective suggests new routes for targeted assessment and intervention focusing on specific bodily domains.
+
+<!-- Limitations and future directions -->
+Nonetheless, the current work is not without its limiations.
+This paper did not evaluate the IAS alongside other questionnaires such as the BPQ or MAIA, whose conceptual overlap and psychometric inconsistencies complicate interpretation [@ferentzi2021examining; @rogowska2023validation; @campos2021; @vig2023self].
+Because the IAS uniquely targets interoceptive self-reported accuracy, a dimension previously assessed only via performance tasks such as the HDT and HCT, our focus was on its structure and correlates rather than introducing established measures with documented shortcomings.
+Future work should employ contemporary analytic methods, such as EGA and network modeling, to evaluate convergent and discriminant validity across interoceptive domains and clarify how self-belief and accuracy measures jointly shape interoceptive functioning.
+
+<!-- Conclusion -->
 

### 2025-11-13 paper/1_Initial/manuscript.qmd
minor updates

@@
 This pattern may help clarify inconsistencies in the literature linking interoception and emotion.
-Reviews and meta-analyses report that performance-based measures of interoceptive accuracy, particularly in cardioception, often show weak or absent correlations with depression and anxiety [@jenkinson2024interoception; @banellis2025interoceptive; @adams2022association].
-In contrast, self-reported interoceptive measures typically show stronger, often negative, associations with internalizing traits [e.g., @brand2022; @lin2023; @clemente2024relationship].
+Reviews and meta-analyses report that performance-based measures of interoceptive accuracy, usually cardioception, often show weak or absent correlations with depression and anxiety [@jenkinson2024interoception; @banellis2025interoceptive; @adams2022association].
+In contrast, self-reported interoceptive measures, which contain items relevant to multiple bodily domains, typically show stronger, often negative, associations with internalizing traits [e.g., @brand2022; @lin2023; @clemente2024relationship].
 These discrepancies likely reflect both conceptual distinctions between perceptual accuracy and metacognitive self-belief [@khalsa2018; @garfinkel2015knowing; @suksasilp2022towards] and variation in the bodily domains assessed.
@@
 These traits tended to correlate negatively with self-perceived interoceptive accuracy, particularly within visceral and musculoskeletal domains, while showing little or no association in other areas.
-This selective pattern suggests that diminished confidence in bodily perception may contribute to specific social–emotional and personality features, rather than reflecting a general interoceptive deficit.
+This selective pattern suggests that diminished beliefs in bodily perception may contribute to specific social–emotional and personality features, rather than reflecting a general interoceptive deficit.
 These results align with evidence that interoceptive self-beliefs, more than objective accuracy, track variation in emotional awareness, social connectedness, and psychopathology [@torregrossa2022interoceptive; @williams2023characterizing; @brand2022].

### 2025-11-13 paper/1_Initial/manuscript.qmd
updated discussions
@DominiqueMakowski may you please leave some feedback on this version of the discussion

@@
 The IAS showed positive associations with most MAIA facets, except for the Not-Distracting and Not-Worrying subscales, replicating prior findings [@brand2023; @todd2022].
-Associations with the BPQ Body Awareness subscale were consistent with previous reports on positive association between these measures [@brand2023; @campos2021; @koike2023; @gaggero2021], whereas indices of autonomic reactivity were more strongly and negatively associated with IAS scores, supporting earlier observations that reactivity may reflect aspects of bodily signal processing captured by self-reported interoceptive accuracy [@todd2022].
+Associations with the BPQ Body Awareness subscale were consistent with previous reports on positive association between these measures [@brand2023; @koike2023; @gaggero2021], whereas indices of autonomic reactivity were more strongly and negatively associated with IAS scores, supporting earlier observations that reactivity may reflect aspects of bodily signal processing captured by self-reported interoceptive accuracy [@todd2022].
+In contrast, measures of interoceptive difficulties, including alexithymia and interoceptive confusion, were negatively associated with IAS scores, consistent with prior research [@brand2023; @koike2023; @lin2023; @murphy2019].
 
-In contrast, measures of interoceptive difficulties, including alexithymia and interoceptive confusion, were negatively associated with IAS scores, consistent with prior research [@brand2023; @koike2023; @lin2023; @murphy2019].
-These associations were strongest for visceral pairings, such as Hungry–Thirsty and Bruise–Blood sugar, and weaker or nonsignificant for other bodily domains, highlighting the domain-specific nature of interoceptive self-report.
+Although associations between the IAS and the BPQ subscales replicated prior work, interpretation remains uncertain due to conceptual ambiguity in the BPQ–Body Awareness subscale.
+Prior studies have reported non-existent [e.g., @murphy2019], negative, and even quadratic relationships (e.g., @campos2021; @lin2023), and some authors have suggested that these mixed findings stem from divergent interpretations of the items—specifically, whether they capture attentional focus on bodily sensations or perceived accuracy in detecting them (e.g., @gabriele2022Dissociations; @campos2021).
+Thus, although we observed a positive association between the BPQ–Body Awareness and the IAS, this result should be interpreted with caution, and future studies should assess participants’ understanding of BPQ items to clarify the nature of this relationship.
 
-Across mood, most item pairings displayed small-to-moderate standardized coefficients, indicating shared variance between interoceptive self-reports and affective tendencies.
+Across mood, most item pairings displayed small-to-moderate standardized coefficients, indicating shared variance between interoceptive self-reports and affective tendencies, aligning with previous findings [@murphy2019; @koike2023].
 In contrast, associations with psychopathology were more selective: negative associations were primarily observed for visceral pairings such as Hungry–Thirsty and Bruise–Blood sugar, whereas other domains yielded weaker or nonsignificant effects.
-This pattern suggests that self-reported interoceptive accuracy is more strongly associated with affective and clinical traits for visceral sensations than for somatic or respiratory reflexes [@murphy2019; @koike2023].
+This pattern suggests that self-reported interoceptive accuracy is more strongly associated with affective and clinical traits for visceral sensations than for somatic or respiratory reflexes.
 
@@
 
-<!-- Structural insights from Study 1 -->
-
 Study 1 re-analysed the IAS using complementary psychometric and network-based approaches.
@@
 Perceived accuracy in one bodily system may generalize to conceptually or functionally linked sensations, yielding a clustered rather than continuous organization of interoceptive beliefs.
-Consistent with this view, self-reported interoceptive awareness across related axes (e.g., cardiac and respiratory) tends to show positive associations [@garfinkel2016interoceptive], whereas objective measures of interoceptive accuracy across modalities typically show weak or absent correlations [@bruni2023interoception; @ferentzi2018interoceptive].
-This dissociation suggests that subjective interoceptive beliefs are structured according to functional bodily domains rather than reflecting a single general capacity.
+
+Consistent with this interpretation, self-reported interoceptive awareness across related bodily axes (e.g., cardiac and respiratory) tends to show positive associations [@garfinkel2016interoceptive], whereas objective measures of interoceptive accuracy across modalities typically show weak or absent correlations [@bruni2023interoception; @ferentzi2018interoceptive].
+This dissociation indicates that actual interoceptive abilities are largely domain-specific, while subjective interoceptive beliefs generalize across functionally related systems.
+Accordingly, the present clustering likely reflects the conceptual organization of interoceptive beliefs, structured by perceived bodily interdependence, rather than a single general interoceptive capacity.
 
@@
 
-<!-- Although associations between the IAS and the BPQ subscales replicated prior work (e.g., @brand2023; @koike2023; @gaggero2021), interpretation remains uncertain due to conceptual ambiguity in the BPQ–Body Awareness subscale.
-Prior studies have reported positive, negative, and even quadratic relationships (e.g., @campos2021; @lin2023), and some authors have suggested that these mixed findings stem from divergent interpretations of the items—specifically, whether they capture attentional focus on bodily sensations or perceived accuracy in detecting them (e.g., @gabriele2022Dissociations; @campos2021).
-Thus, although we observed a positive association between the BPQ–Body Awareness and the IAS, this result should be interpreted with caution, and future studies should assess participants’ understanding of BPQ items to clarify the nature of this relationship.
--->
-
 <!-- Mood and psychopathological disorders domain specific -->
 Across dispositional constructs, individuals reporting higher symptoms of depression and anxiety tended to perceive themselves as less accurate in detecting bodily signals, in line with previous findings [e.g., @brand2023; @khalsa2018; @nord2022interoceptive].
-Crucially, these associations were not uniform across bodily domains: the strongest effects involved visceral sensations (e.g., hunger, thirst), whereas cardiorespiratory and expulsion domains showed weaker or inconsistent relationships.
+Crucially, these associations were not uniform across bodily domains: the strongest, and most robust, effects involved visceral sensations (e.g., hunger, thirst), whereas cardiorespiratory and expulsion domains showed weaker or inconsistent relationships.
 This domain specificity suggests that beliefs about one’s visceral accuracy may be more psychologically and clinically relevant than beliefs about reflexive or surface sensations.
@@
 In contrast, self-reported interoceptive measures, which contain items relevant to multiple bodily domains, typically show stronger, often negative, associations with internalizing traits [e.g., @brand2022; @lin2023; @clemente2024relationship].
+
 These discrepancies likely reflect both conceptual distinctions between perceptual accuracy and metacognitive self-belief [@khalsa2018; @garfinkel2015knowing; @suksasilp2022towards] and variation in the bodily domains assessed.
@@
 This selective pattern suggests that diminished beliefs in bodily perception may contribute to specific social–emotional and personality features, rather than reflecting a general interoceptive deficit.
-These results align with evidence that interoceptive self-beliefs, more than objective accuracy, track variation in emotional awareness, social connectedness, and psychopathology [@torregrossa2022interoceptive; @williams2023characterizing; @brand2022].
 
-Taken together, these findings suggest that self-perceived interoceptive accuracy is a differentiated construct, varying systematically across bodily systems and psychological traits.
+These results align with previous evidence showing that interoceptive self-beliefs are meaningfully related to emotional awareness, social connectedness, and psychopathology [@torregrossa2022interoceptive; @williams2023characterizing; @brand2022].
+The present findings extend this literature by showing that these associations are domain-specific rather than global across bodily systems.
+
+Taken together, these findings suggest that self-perceived interoceptive accuracy is a differentiated construct, varying systematically across bodily systems.
 Beliefs about visceral sensations, in particular, show the most consistent associations with affective and dispositional features.
@@
 Methodologically, combining traditional psychometrics with network-based approaches proved valuable.
-EGA complemented factor analysis by identifying meaningful inter-item dependencies, producing a more interpretable and stable structure.
+EGA complemented, and often surpassed, factor analysis by identifying meaningful inter-item dependencies, producing a more interpretable and stable structure.
 The refined 14-item IAS balances parsimony and predictive validity, illustrating how network-informed scale refinement, beyond scale development [@golino2017exploratory], can enhance construct clarity.
@@
 The IAS nonetheless remains limited in scope.
-Certain interoceptive modalities (e.g., gastric, tactile) are underrepresented, and items lack contextual specification (e.g., physiological vs.
+Pairing items improved interpretability and outperformed an overall score of self-reported interoceptive accuracy in associations with affective and dispositional traits, but dimensions with only two items (one per bodily domain) remain suboptimal, particularly for constructs that are broad or conceptually ambiguous [@allen2022single], such as beliefs about interoceptive accuracy across multiple bodily systems.
+
+Because perceived accuracy in one system can generalize to conceptually or functionally related sensations, two-item clusters may overemphasize these links and fail to capture variability across unrelated domains, while overall scores risk obscuring meaningful relationships.This limitation is especially important given that researchers may assume interoceptive abilities generalize across bodily domains, when in fact they do not.
+Building on @desmedt2022measures’ observation of a “jingle fallacy” in using self-reported interoceptive measures, the present findings extend this caution by highlighting that assuming beliefs replicate across domains constitutes a similar jingle fallacy.
+
+Additionally, items lack contextual specification (e.g., physiological vs.
 affective triggers).
@@
 Such ambiguities may constrain ecological validity and contribute to variability across studies [@vlemincx2023novel].
-Expanding item content and adopting context-specific phrasing will be important for future measurement development.
+Expanding item content and adopting context-specific phrasing will be important for future measurement development to more comprehensively capture interoceptive beliefs.
 
@@
 Nonetheless, the current work is not without its limiations.
-This paper did not evaluate the IAS alongside other questionnaires such as the BPQ or MAIA, whose conceptual overlap and psychometric inconsistencies complicate interpretation [@ferentzi2021examining; @rogowska2023validation; @campos2021; @vig2023self].
-Because the IAS uniquely targets interoceptive self-reported accuracy, a dimension previously assessed only via performance tasks such as the HDT and HCT, our focus was on its structure and correlates rather than introducing established measures with documented shortcomings.
-Future work should employ contemporary analytic methods, such as EGA and network modeling, to evaluate convergent and discriminant validity across interoceptive domains and clarify how self-belief and accuracy measures jointly shape interoceptive functioning.
+This study focused exclusively on the IAS and did not evaluate the structure or subjective correlates of other commonly used interoception questionnaires, such as the BPQ or MAIA.
+Because the IAS uniquely targets interoceptive self-reported accuracy our focus was on its structure and correlates rather than introducing established measures with documented shortcomings [@ferentzi2021examining; @rogowska2023validation; @campos2021; @vig2023self].
+
+Another limitation is the lack of objective measures of interoceptive accuracy in this study.
+Incorporating cardiac, resporatory, and gastric performance-based measures would allow investigation of how beliefs about one’s interoceptive accuracy relate to actual performance.
+Such comparisons could clarify whether domain-specific self-reports reflect true perceptual sensitivity or primarily capture metacognitive and conceptual beliefs.
+Although prior research has shown weak or absent correlations between subjective and objective measures within the same domain [e.g., cardiac accuracy vs subjective accuracy, @brand2023; @petzke2024somatic; @arslanova2022], examining additional modalities, such as gastric perception, could reveal whether these patterns generalize across other interoceptive systems.
 
